### 2021-06-18 graphs_newt_snakes/Expected_results_fig.Rmd
updated help flie and added a place to make newt snake figures

---
title: "Fake Graphs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
setwd("~/Desktop/Proposal Old Drafts")
```

## This R Markdown is for my expected results Figs

#### Aim 1

Genetic Architecture by Resistance - Toxicity
-concerns that it might be messy might be useful to do trait A and trait B

```{r, aim 1 Genetic Architecture}
GA <- c("A", "B", "C", "D")
# Group A Large effect – High Mutation 
# Group B Large effect – Low Mutation
# Group C Small effect – High Mutation
# Group D Small effect – Low Mutation
my_GA_data <- as.data.frame(GA)
my_GA_data$fake <-c(3,1,0,-2)

#pdf("Resistance_of_Populations_as_the_Genetic_Architecture_of_Snake_Changes.pdf")
ggplot(my_GA_data, aes(GA, fake))+
  geom_hline(yintercept=0, color ="red")+
  geom_point(size=3, color = "darkgreen")+
  ggtitle("Resistance of Populations as the Genetic Architecture of Snake Changes") + 
  xlab("Genetic Architecture of Snake") + 
  ylab("Resistance-Toxicity") +
  theme_bw()

#pdf("Genetic_Architecture_Map.pdf", width=4, height=2.9)
test_grid <- expand.grid(X = GA, Y = GA)
test_grid$Z <- c(0, -1, -2, -3, 1, 0, -1, -2, 2, 1, 0, -1, 3, 2, 1, 0)
ggplot(test_grid, aes(X, Y, fill= Z)) + 
  geom_tile()+
  scale_y_discrete(limits = rev(levels(test_grid$Y)))+
  ggtitle("Genetic Architecture Map") + 
  xlab("Genetic Architecture of Resistance") + 
  ylab("Genetic Architecture of Toxicity") +
  scale_fill_viridis(name = "Resistance-Toxicity")+
  theme_bw()

```

Density of the Newt increases selection pressure

```{r, aim 1 Density}

newt_density <-  as.data.frame(n_d<-c(1:10))

pdf("Interaction_Strength_as_Newt_Density_Increases.pdf")
ggplot(newt_density, aes(n_d, n_d))+
  geom_point(size=3, color = "darkred")+
  ggtitle("Interaction Strength as Newt Density Increases") + 
  xlab("Newt Density") + 
  ylab("Interaction Strength") +
  theme_bw()

```

Spatial component. the mismatch will decrease as spatial structure increases

```{r, aim 1 spatial aspect}
spatial_structure <- runif(1000, min = 0.001, max = 5) # this is sigma
mismatch <- (exp(-(spatial_structure/2)))
sigma_effects <-  as.data.frame(spatial_structure, mismatch)
pdf("SigmaCurve.pdf")
ggplot(sigma_effects, aes(spatial_structure, mismatch))+
  geom_point(color = "green")+
  ggtitle("Sigma Curve") + 
  xlab("Spatial_structure ") + 
  ylab("Mismatch") +
  theme_bw()

#well mixed when sigma is large

```

Simulation on how likely the snake or new will die depending on their phenotype

```{r, aim 1 Probablity of Death}
Resistance <- c(0:5)
Toxicity <- c(0:3)
E <- 0.1
c <- 0.0
w <- 10
map <- expand.grid(Res = seq(min(Resistance), max(Resistance), length.out = 100), Tox = seq(min(Toxicity), max(Toxicity), length.out = 100))
map$r_t <- map$Res-map$Tox
map$outcome <- 1/(1+exp(-(map$r_t-c)/w))

test <- c(0, 0.0001, 0.001, 0.01, 0.1, 1, 10, 100, -0.0001, -0.001, -0.01, -0.1, -1, -10, -100)

test2 <- runif(1000, min = -100, max = 100)
survival_df <- as.data.frame(test2)
survival_df$outcome2 <- 1/(1+exp(-((survival_df$test2-c)/w)))
pdf("SurvivalCurve.pdf", width=2.5, height=2.5)
ggplot(survival_df, aes(test2, outcome2))+
  geom_point(color = "darkred")+
  ggtitle("Survival Curve") + 
  xlab("Snake-Newt") + 
  ylab("Survival") +
  theme_bw()

```

### Aim 2

Diversity! Trait and whole genome 
large/small dispersal 
interaction/ no interaction

```{r geographical distance vs gentic distance}
#dispersal <- runif(1000, min = 0, max = 3) # this is a range for large and small dispersal 
distance <- seq(0,35,3)  # this is distances that might be probable 
diversity_in_general <- as.data.frame(sort(distance))
names(diversity_in_general)<- "distance"
diversity_in_general$Genetic_i <- diversity_in_general$distance * 1/35 # finding Genetic Distance
diversity_in_general$Genetic_in <- diversity_in_general$distance * 1/70 + 0.05# finding Genetic Distance
diversity_in_general$Genetic_inn <- diversity_in_general$distance * 1/185 + 0.15 # finding Genetic Distance
# y = mx + b y ranges from 0 to 1
diversity_in_general$Genetic_no_interact <- diversity_in_general$distance * 1/60 
diversity_in_general$Genetic_no_interactn <- diversity_in_general$distance * 1/360 + 0.20
diversity_in_general$Genetic_no_interactnn <- 0.5

pdf("General_Diversity_Trend_For_Interactaction.pdf", width=4, height=2.9)
ggplot(diversity_in_general, aes(distance, Genetic_i, color = "darkred" ))+
  geom_point(size=5)+
  geom_point(data = diversity_in_general, aes(distance, Genetic_in, color = "darkgreen"), size=5)+
  geom_point(data = diversity_in_general, aes(distance, Genetic_inn, color = "purple"), size=5)+
  ggtitle("General Diversity Trend For Interactaction") + 
  xlab("Geographical Distance") + 
  ylab("Genetic Distance") +
  scale_color_identity(name = "Dispersal",
                          breaks = c("darkred", "darkgreen", "purple"),
                          labels = c("Small", "Medium", "Large"),
                          guide = "legend")+
  theme_bw()

pdf("General_Diversity_Trend_For_No_Interactaction.pdf")
ggplot(diversity_in_general, aes(distance, Genetic_no_interact, color = "darkred"))+
  geom_point( size=5)+
  geom_point(data = diversity_in_general, aes(distance, Genetic_no_interactn, color = "darkgreen"), size=5)+
  geom_point(data = diversity_in_general, aes(distance, Genetic_no_interactnn, color = "purple"), size=5)+
  ylim(0,1)+
  ggtitle("General Diversity Trend For No Interactaction") + 
  xlab("Geographical Distance") + 
  ylab("Genetic Distance") +
  theme_bw()+
  scale_color_identity(name = "Dispersal",
                        breaks = c("darkred", "darkgreen", "purple"),
                        labels = c("Small", "Medium", "Large"),
                        guide = "legend")
```

```{r geographical distance vs  pi for trait and for whole genome (focus on the interactions)}
library(reshape)
dispersal_distance <- rep(seq(0.35, 1.75, 0.35) ,5)
dispersal_diversity <- as.data.frame(sort(dispersal_distance))
names(dispersal_diversity)<- "dispersal_distance"
# interaction cause diversity of the trait to be lower and the genome to be higher than the trait but lower then no interaction
# no_interact both trait and genome will have similar levels of genetic diversity
# pi values (nucleotide diversity) range from 0 to 1, 0 low diversity 1 high diversity
# as dispersal distance increases pi goes down (sweeps)
 # dispersal distance 0.35 to 5.25
# high .6 low .2
# y = mx + b

exp(unique(-dispersal_distance))

trait_pi_i <- c()
whole_genome_pi_i <- c()
trait_pi_n <- c()
whole_genome_pi_n <- c()
for(i in unique(dispersal_distance)){
  trait_pi_i <- c(trait_pi_i, exp(-i) + c(0.05, 0.02, 0, -0.02, -0.05))
 whole_genome_pi_i <- c(whole_genome_pi_i, exp(-i) + c(0.1, 0.07, 0.05, 0.03, 0)- exp(-i)*.2)
 trait_pi_n <- c(trait_pi_n, exp(-i) + c(0.01, -0.01, -0.03, -0.05, -0.06))
whole_genome_pi_n <- c(whole_genome_pi_n, exp(-i) + c(0.01, -0.01, -0.03, -0.05, -0.06))
}

dispersal_diversity$trait_pi_i <-trait_pi_i
dispersal_diversity$whole_genome_pi_i <-whole_genome_pi_i
dispersal_diversity$trait_pi_n <- trait_pi_n 
dispersal_diversity$whole_genome_pi_n <- whole_genome_pi_n

dispersal_diversity_t<-t(dispersal_diversity)
dispersal_diversity_m <- melt(dispersal_diversity, id=c("dispersal_distance"))

pdf("dispersal_diversit.pdf", width=4.7, height=2.7)

ggplot(dispersal_diversity_m, aes(factor(dispersal_distance), value, fill=variable))+
  geom_boxplot(data=dispersal_diversity_m, aes(factor(dispersal_distance), value, fill=variable))+
  ggtitle("Levels of Genetic Diversity and Dispersal Distance") + 
  xlab("Dispersal Distance") + 
  ylab("Diversity (pi)") +
  theme_bw()+
  scale_fill_manual(name = "Legend", labels = c("Interaction/Trait", "Interaction/Genome", "No Interaction/Trait", "No Interaction/Genome"), values = c("lightblue", "steelblue", "greenyellow", "forestgreen") )
  #scale_fill_viridis_d(option="plasma", name = "Group", labels = c("Trait/Interaction", "Genome/Interaction", "Trait/No Interaction", "Genome/No Interaction"))
# position = position_dodge(-0.3)

```

```{r local vs global diversity levels}
large_dis
small_dis
interact
no_interact
trait 
whole_genome

```

### Aim 3

How convolution effects the genome 
machine learning ~ neural network

```{r manhatten plot or like gwas?}

```

### 2021-06-21 graphs_newt_snakes/fig_1000.Rmd
added some moresrun scripts to run differet msprime simulations to do 1000 gen test. I also updated the explination sheet

---
title: "1000 Graphs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
#setwd("~/Desktop/Proposal Old Drafts")
```

## This is a r file to show what the phenotypess are after 1000 generations
- A problem that I have been experiencing is that the phenotypes seem so go wild really quickly 
- This will be a graph that looks at the phenotypes of different simulations with a unique mutation rate and mutation effect size.

- Lets just visualize what the phenotypes are doing

## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

for (current_file in files){
  print(current_file)

  file <- read.table(current_file, header = TRUE)
  print(max(file$Newt_max_Pheno))
  print(max(file$Snake_max_Pheno))
  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}
```

```{r pressure, echo=FALSE}
ggplot()+
  geom_line(current_file, aes(gen, snake), color="blue")+
  geom_line(current_file, aes(gen, snake), color="red")+
  geom_point(size=3, color = "darkgreen")+
  ggtitle("How the Phenotypes Change Through the Generations") + 
  xlab("Generation") + 
  ylab("Phenotype Level") +
  theme_bw()
```

### 2021-06-24 graphs_newt_snakes/fig_1000.Rmd
I had ran a 1000 gen simulation and had mixed up the variables. Then, I had fixed it an reran it. Next, I did an experiment where I used the variables in both the msprime and the slim script. This update if mosly for the R script to see how different the phenotypes are. I also fixed parsing do that it would work on the cluster.

@@
 
+I made a mistake. I switched the mutation rates and the effect sizes
+
+```{r pressure, echo=FALSE}
+newt_max_pheno = 0
+snake_max_pheno = 0
+
+files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+
+  if (max(file$Newt_max_Pheno) > newt_max_pheno){
+    newt_max_pheno = max(file$Newt_max_Pheno) }
+
+  if (max(file$Snake_max_Pheno) > snake_max_pheno){
+    snake_max_pheno = max(file$Snake_max_Pheno) }
+}
+  print(newt_max_pheno)
+  print(snake_max_pheno)
+```
+## The Figure
+Loop through the files and find the max and min of each of the species pheotypes
+Then set up a graph with the max max
+Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time
+
+This is the correct one
 ```{r pressure, echo=FALSE}
@@
 for (current_file in files){
-  print(current_file)
+  #print(current_file)
 
   file <- read.table(current_file, header = TRUE)
-  print(max(file$Newt_max_Pheno))
-  print(max(file$Snake_max_Pheno))
+  #print(max(file$Newt_max_Pheno))
+  #print(max(file$Snake_max_Pheno))
   if (max(file$Newt_max_Pheno) > newt_max_pheno){
@@
 }
+
+  print(newt_max_pheno)
+  print(snake_max_pheno)
 ```
+## The Figure
+Loop through the files and find the max and min of each of the species pheotypes
+Then set up a graph with the max max
+Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time
+
+This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked.
+
+```{r pressure, echo=FALSE}
+newt_max_pheno = 0
+snake_max_pheno = 0
+
+files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+
+for (current_file in files){
+  print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
+  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
+  print(max(file$Newt_max_Pheno, na.rm = TRUE))
+  print(max(file$Snake_max_Pheno, na.rm = TRUE))
+  if (max(file$Newt_max_Pheno, na.rm = TRUE) > newt_max_pheno){
+    newt_max_pheno = max(file$Newt_max_Pheno, na.rm = TRUE) }
+
+  if (max(file$Snake_max_Pheno, na.rm = TRUE) > snake_max_pheno){
+    snake_max_pheno = max(file$Snake_max_Pheno, na.rm = TRUE) }
+}
+
+  print(newt_max_pheno)
+  print(snake_max_pheno)
+```
+some of these values are in quotes, why?
+
+Some other things that might be goo to look at:
+The average of the phenotypes
+The difference between the average phenotypes
 

### 2021-06-24 msprime/snake_newt_gv_.py

@@ -9,7 +9,7 @@ from sys import argv
 
 
 sequence_length = 100000000
-
+'''
 datadir = "newt_snake/data"
 snake_mu_rate = 1e-10
 newt_mu_rate = 1e-10  # does this need to be 50 times more than the snake?
@@ -23,8 +23,8 @@ newt_mu_rate = float(sys.argv[2])  # does this need to be 50 times more than the
 snake_mu_effect_sd = float(sys.argv[3])
 newt_mu_effect_sd = float(sys.argv[4])
 datadir = sys.argv[5]
-'''
-name_of_file = "both_su_" + str(snake_mu_rate) + "_nu_" + str(newt_mu_rate) + \
+
+name_of_file = "both_1000_su_" + str(snake_mu_rate) + "_nu_" + str(newt_mu_rate) + \
     "_sue_" + str(snake_mu_effect_sd) + "_nue_" + str(newt_mu_effect_sd) + ".init.trees"
 print(name_of_file)
 

### 2021-06-24 srun_scripts/parsing.sh

@@ -5,10 +5,10 @@ for file_name in "$1"/*;
 do 
 arrIN=(${file_name//_/ })
 
-snake_mu_rate=${arrIN[3]}
-newt_mu_rate=${arrIN[5]}
-snake_mu_effect_sd=${arrIN[7]}
-newt_mu_effect_sd_fix==${arrIN[9]}
+snake_mu_rate=${arrIN[5]}
+newt_mu_rate=${arrIN[7]}
+snake_mu_effect_sd=${arrIN[9]}
+newt_mu_effect_sd_fix==${arrIN[11]}
 newt_mu_effect_sd_fix=(${newt_mu_effect_sd_fix//.init/ })
 newt_mu_effect_sd=(${newt_mu_effect_sd_fix//=/ })
 

### 2021-06-24 graphs_newt_snakes/fig_1000.Rmd
I made a graph for how crazy the phenotypes can get under different paramiters. Had fun looping though files. still dont know why some values are in quotes

--- 2021-06-21 graphs_newt_snakes/fig_1000.Rmd
@@
 
+I made a mistake. I switched the mutation rates and the effect sizes
+
 ```{r pressure, echo=FALSE}
@@
 snake_max_pheno = 0
+true_max = 0
 
-files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
 
 for (current_file in files){
-  print(current_file)
+  #print(current_file)
 
   file <- read.table(current_file, header = TRUE)
-  print(max(file$Newt_max_Pheno))
-  print(max(file$Snake_max_Pheno))
+
   if (max(file$Newt_max_Pheno) > newt_max_pheno){
@@
 }
+  print(newt_max_pheno)
+  print(snake_max_pheno)
+
+  if (newt_max_pheno > snake_max_pheno){
+    true_max = newt_max_pheno }
+  if ( snake_max_pheno > newt_max_pheno){
+    true_max = snake_max_pheno }
+
 ```
+```{r pressure, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  ylim(0, true_max)+
+  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+ p <- p +
+  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
+  #Sys.sleep(2)
+
+}
+
+p 
+```
+
+## The Figure
+Loop through the files and find the max and min of each of the species pheotypes
+Then set up a graph with the max max
+Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time
+
+This is the correct one
+```{r pressure, echo=FALSE}
+newt_max_pheno = 0
+snake_max_pheno = 0
+true_max_2 = 0
+
+files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  #print(max(file$Newt_max_Pheno))
+  #print(max(file$Snake_max_Pheno))
+  if (max(file$Newt_max_Pheno) > newt_max_pheno){
+    newt_max_pheno = max(file$Newt_max_Pheno) }
+
+  if (max(file$Snake_max_Pheno) > snake_max_pheno){
+    snake_max_pheno = max(file$Snake_max_Pheno) }
+}
+
+  print(newt_max_pheno)
+  print(snake_max_pheno)
+
+    if (newt_max_pheno > snake_max_pheno){
+    true_max_2 = newt_max_pheno }
+  if ( snake_max_pheno > newt_max_pheno){
+    true_max_2 = snake_max_pheno }
+```
+
+```{r pressure, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  ylim(0, true_max_2)+
+  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+ p <- p +
+  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
+  #Sys.sleep(2)
+
+}
+
+p 
+```
+## The Figure
+Loop through the files and find the max and min of each of the species pheotypes
+Then set up a graph with the max max
+Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time
+
+This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked.
+
+```{r pressure, echo=FALSE}
+newt_max_pheno = 0
+snake_max_pheno = 0
+true_max_3 = 0
+
+files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
+  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
+  #print(max(file$Newt_max_Pheno, na.rm = TRUE))
+  #print(max(file$Snake_max_Pheno, na.rm = TRUE))
+  if (as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) > newt_max_pheno){
+    newt_max_pheno = as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) }
+
+  if (as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) > snake_max_pheno){
+    snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }
+}
+
+  print(newt_max_pheno)
+  print(snake_max_pheno)
+  if (newt_max_pheno > snake_max_pheno){
+    true_max_3 = newt_max_pheno }
+  if ( snake_max_pheno > newt_max_pheno){
+    true_max_3 = snake_max_pheno }
+```
+some of these values are in quotes, why?
+
+```{r pressure, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(0, true_max_3)+
+  #scale_y_continuous(trans=log10_trans(), limits=c(0,true_max_3))+
+  #scale_y_log10()+
+  scale_y_log10(limits=c(0.001,true_max_3))+
+  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+
+ p <- p +
+  geom_line(data=file, aes(y = as.numeric(Newt_mean_Pheno)), color = "darkred",na.rm=TRUE) + 
+  geom_line(data=file, aes(y = as.numeric(Snake_mean_Pheno)), color="steelblue", linetype="twodash", na.rm=TRUE) 
+  #Sys.sleep(2) na.rm=TRUE
+
+}
+
+p 
+```
+
+Some other things that might be goo to look at:
+The average of the phenotypes
+The difference between the average phenotypes
 

### 2021-06-26 msprime/snake_newt_gv_.py
made notes on what I did and tested vscode which is really cool

@@ -6,7 +6,7 @@ import os
 import sys
 from sys import argv
 # import util
-
+# testing vscode&git
 
 sequence_length = 100000000
 '''

### 2021-06-27 graphs_newt_snakes/fig_1000.Rmd
added a graph showing the difference between the means. Next step is to figure out what sims are going to the extreams.

@@
 true_max_3 = 0
+max_difference = 0
+min_difference = 0
 
@@
   file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
+
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
   #print(max(file$Newt_max_Pheno, na.rm = TRUE))
@@
     snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }
+
+ if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference){
+    min_difference = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
+  }
+
+  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference){
+    max_difference = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
+  }
+
       }
@@
   print(snake_max_pheno)
+  print(min_difference)
+  print(max_difference)
   if (newt_max_pheno > snake_max_pheno){
@@
 Some other things that might be goo to look at:
-The average of the phenotypes
+
 The difference between the average phenotypes
@@
 ```{r pressure, echo=FALSE}
-ggplot()+
-  geom_line(current_file, aes(gen, snake), color="blue")+
-  geom_line(current_file, aes(gen, snake), color="red")+
-  geom_point(size=3, color = "darkgreen")+
-  ggtitle("How the Phenotypes Change Through the Generations") + 
-  xlab("Generation") + 
-  ylab("Phenotype Level") +
+
+files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(min_difference, max_difference)+
+  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
+  #scale_y_log10()+
+  scale_y_log10(limits=c(0.001, max_difference))+
+  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
   theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
+  file$mean_dif[file$mean_dif == 0] <- 0.01
+  file$pos <- TRUE
+  file$pos[file$mean_dif < 0] <- FALSE
+
+ p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
+  #Sys.sleep(2) na.rm=TRUE
+ # color = "mediumseagreen"
+
+}
+
+p 
 ```

### 2021-06-28 graphs_newt_snakes/fig_1000.Rmd
updated the r figures for the 1000 gen simulation. There is osmthing oof about the difference graph (like the lines might not be connected to each other). goal is to think of better ways to do it

--- 2021-06-24 graphs_newt_snakes/fig_1000.Rmd
@@
 
-```{r pressure, echo=FALSE}
-newt_max_pheno = 0
-snake_max_pheno = 0
+```{r data from the mistake folder, echo=FALSE}
+newt_max_pheno_1 = 0
+snake_max_pheno_1 = 0
+newt_min_pheno_1 = 0
+snake_min_pheno_1 = 0
+true_max_1 = 0
+true_min_1 = 0
+min_difference_1 = 0
+max_difference_1 = 0
 
@@
 
-  if (max(file$Newt_max_Pheno) > newt_max_pheno){
-    newt_max_pheno = max(file$Newt_max_Pheno) }
+  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
+  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
+  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
+  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
 
-  if (max(file$Snake_max_Pheno) > snake_max_pheno){
-    snake_max_pheno = max(file$Snake_max_Pheno) }
+  if (max(file$Newt_max_Pheno) > newt_max_pheno_1){
+    newt_max_pheno_1 = max(file$Newt_max_Pheno) }
+
+  if (max(file$Snake_max_Pheno) > snake_max_pheno_1){
+    snake_max_pheno_1 = max(file$Snake_max_Pheno) }
+
+  if (min(file$Newt_min_Pheno) < newt_min_pheno_1){
+    newt_min_pheno_1 = min(file$Newt_min_Pheno) }
+
+  if (min(file$Snake_min_Pheno) > snake_min_pheno_1){
+    snake_min_pheno_1 = max(file$Snake_min_Pheno) }
+
+  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_1){
+    min_difference_1 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
   }
-  print(newt_max_pheno)
-  print(snake_max_pheno)
+
+  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_1){
+    max_difference_1 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
+  }
+}
+
+  print(newt_max_pheno_1)
+  print(snake_max_pheno_1)
+   print(newt_min_pheno_1)
+  print(snake_min_pheno_1)
+
+  if (newt_max_pheno_1 > snake_max_pheno_1){
+    true_max_1 = newt_max_pheno_1 }
+  if ( snake_max_pheno_1 > newt_max_pheno_1){
+    true_max_1 = snake_max_pheno_1 }
+
+    if (newt_min_pheno_1 < snake_min_pheno_1){
+    true_min_1 = newt_min_pheno_1 }
+  if ( snake_min_pheno_1 < newt_min_pheno_1){
+    true_min_1 = snake_min_pheno_1 }
+
 ```
+```{r phenotype graph for mistake sims, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(0, true_max_1)+
+  scale_y_log10(limits=c(true_min_1+0.8, true_max_1))+
+  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
+  ggtitle("Phenotype Measurements for Newts and Snakes") +
+  xlab("Generation") + ylab("Average Phenotypes")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+ p <- p +
+  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
+  #Sys.sleep(2)
+
+}
+
+p 
+```
+
+```{r difference wrong sim, echo=FALSE}
+
+## need to work on making this figure better 
+files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(min_difference, max_difference)+
+  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
+  #scale_y_log10()+
+  scale_y_log10(limits=c(min_difference_1, max_difference_1))+
+  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
+    ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
+  xlab("Generation") + ylab("Average Difference")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
+  file$mean_dif[file$mean_dif == 0] <- 0.01
+  file$pos <- TRUE
+  file$pos[file$mean_dif < 0] <- FALSE
+
+ p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
+  #Sys.sleep(2) na.rm=TRUE
+ # color = "mediumseagreen"
+
+}
+
+p 
+```
+
 ## The Figure
@@
 This is the correct one
-```{r pressure, echo=FALSE}
-newt_max_pheno = 0
-snake_max_pheno = 0
+```{r data 1 msprime photype graph, echo=FALSE}
+newt_max_pheno_2 = 0
+snake_max_pheno_2 = 0
+newt_min_pheno_2 = 0
+snake_min_pheno_2 = 0
+true_max_2 = 0
+true_min_2 = 0
+min_difference_2 = 0
+max_difference_2 = 0
 
@@
   #print(max(file$Snake_max_Pheno))
-  if (max(file$Newt_max_Pheno) > newt_max_pheno){
-    newt_max_pheno = max(file$Newt_max_Pheno) }
 
-  if (max(file$Snake_max_Pheno) > snake_max_pheno){
-    snake_max_pheno = max(file$Snake_max_Pheno) }
+  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
+  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
+  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
+  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+
+  if (max(file$Newt_max_Pheno) > newt_max_pheno_2){
+    newt_max_pheno_2 = max(file$Newt_max_Pheno) }
+
+  if (max(file$Snake_max_Pheno) > snake_max_pheno_2){
+    snake_max_pheno_2 = max(file$Snake_max_Pheno) }
+
+  if (min(file$Newt_min_Pheno) < newt_min_pheno_2){
+    newt_min_pheno_2 = max(file$Newt_min_Pheno) }
+
+  if (max(file$Snake_min_Pheno) < snake_min_pheno_2){
+    snake_min_pheno_2 = max(file$Snake_min_Pheno) }
+
+  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_2){
+      min_difference_2 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
   }
 
-  print(newt_max_pheno)
-  print(snake_max_pheno)
+  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_2){
+    max_difference_2 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
+  }
+}
+
+  print(newt_max_pheno_2)
+  print(snake_max_pheno_2)
+  print(newt_min_pheno_2)
+  print(snake_min_pheno_2)
+
+  if (newt_max_pheno_2 > snake_max_pheno_2){
+    true_max_2 = newt_max_pheno_2 }
+  if ( snake_max_pheno_2 > newt_max_pheno_2){
+    true_max_2 = snake_max_pheno_2 }
+
+  if (newt_min_pheno_2 < snake_min_pheno_2){
+    true_min_2 = newt_min_pheno_2 }
+  if ( snake_min_pheno_2 < newt_min_pheno_2){
+    true_min_2 = snake_min_pheno_2 }
 ```
+
+```{r data 1 msprime dif pheno graph, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(0, true_max_2)+
+  scale_y_log10(limits=c(true_min_2+0.5, true_max_2))+
+  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
+  ggtitle("Phenotype Measurements for Newts and Snakes") +
+  xlab("Generation") + ylab("Average Phenotypes")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+ p <- p +
+  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
+  #Sys.sleep(2)
+
+}
+
+p 
+```
+```{r data from multiple msprime, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(min_difference, max_difference)+
+  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
+  #scale_y_log10()+
+  scale_y_log10(limits=c(min_difference_2, max_difference_2))+
+  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
+    ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
+  xlab("Generation") + ylab("Average Difference")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
+  file$mean_dif[file$mean_dif == 0] <- 0.01
+  file$pos <- TRUE
+  file$pos[file$mean_dif < 0] <- FALSE
+
+ p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
+  #Sys.sleep(2) na.rm=TRUE
+ # color = "mediumseagreen"
+
+}
+
+p 
+```
+
 ## The Figure
@@
 ```{r pressure, echo=FALSE}
-newt_max_pheno = 0
-snake_max_pheno = 0
+newt_max_pheno_3 = 0
+snake_max_pheno_3 = 0
+newt_min_pheno_3 = 0
+snake_min_pheno_3 = 0
+true_max_3 = 0
+true_min_3 = 0
+max_difference_3 = 0
+min_difference_3 = 0
 
@@
 for (current_file in files){
-  print(current_file)
+  #print(current_file)
 
@@
   file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
-  print(max(file$Newt_max_Pheno, na.rm = TRUE))
-  print(max(file$Snake_max_Pheno, na.rm = TRUE))
-  if (max(file$Newt_max_Pheno, na.rm = TRUE) > newt_max_pheno){
-    newt_max_pheno = max(file$Newt_max_Pheno, na.rm = TRUE) }
+  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
+  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  #print(max(file$Newt_max_Pheno, na.rm = TRUE))
+  #print(max(file$Snake_max_Pheno, na.rm = TRUE))
 
-  if (max(file$Snake_max_Pheno, na.rm = TRUE) > snake_max_pheno){
-    snake_max_pheno = max(file$Snake_max_Pheno, na.rm = TRUE) }
+  if (as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) > newt_max_pheno_3){
+    newt_max_pheno_3 = as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) }
+
+  if (as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) > snake_max_pheno_3){
+    snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }
+
+  if (as.numeric(min(file$Newt_min_Pheno, na.rm = TRUE)) < newt_min_pheno_3){
+    newt_min_pheno_3 = as.numeric(max(file$Newt_min_Pheno, na.rm = TRUE)) }
+
+  if (as.numeric(max(file$Snake_min_Pheno, na.rm = TRUE)) < snake_min_pheno_3){
+    snake_min_pheno_3 = as.numeric(max(file$Snake_min_Pheno, na.rm = TRUE)) }
+
+ if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_3){
+    min_difference_3 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
   }
 
-  print(newt_max_pheno)
-  print(snake_max_pheno)
+  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_3){
+    max_difference_3 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
+  }
+
+      }
+
+  print(newt_max_pheno_3)
+  print(snake_max_pheno_3)
+  print(min_difference_3)
+  print(max_difference_3)
+  if (newt_max_pheno_3 > snake_max_pheno_3){
+    true_max_3 = newt_max_pheno_3 }
+  if ( snake_max_pheno_3 > newt_max_pheno_3){
+    true_max_3 = snake_max_pheno_3 }
+
+  if (newt_min_pheno_3 < snake_min_pheno_3){
+    true_min_3 = newt_min_pheno_3 }
+  if ( snake_max_pheno_3 < newt_max_pheno_3){
+    true_min_3 = snake_min_pheno_3 }
 ```
@@
 
+```{r pressure, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(0, true_max_3)+
+  #scale_y_continuous(trans=log10_trans(), limits=c(0,true_max_3))+
+  #scale_y_log10()+
+  scale_y_log10(limits=c(0.001,true_max_3))+
+  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
+  ggtitle("Phenotype Measurements for Newts and Snakes") +
+  xlab("Generation") + ylab("Average Phenotypes")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+
+ p <- p +
+  geom_line(data=file, aes(y = as.numeric(Newt_mean_Pheno)), color = "darkred",na.rm=TRUE) + 
+  geom_line(data=file, aes(y = as.numeric(Snake_mean_Pheno)), color="steelblue", linetype="twodash", na.rm=TRUE) 
+  #Sys.sleep(2) na.rm=TRUE
+
+}
+
+p 
+```
+
 Some other things that might be goo to look at:
-The average of the phenotypes
+
 The difference between the average phenotypes
@@
 ```{r pressure, echo=FALSE}
-ggplot()+
-  geom_line(current_file, aes(gen, snake), color="blue")+
-  geom_line(current_file, aes(gen, snake), color="red")+
-  geom_point(size=3, color = "darkgreen")+
-  ggtitle("How the Phenotypes Change Through the Generations") + 
-  xlab("Generation") + 
-  ylab("Phenotype Level") +
+
+files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(min_difference, max_difference)+
+  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
+  #scale_y_log10()+
+  scale_y_log10(limits=c(min_difference_3, max_difference_3))+
+  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
+  ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
+  xlab("Generation") + ylab("Average Difference")+
   theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
+  file$mean_dif[file$mean_dif == 0] <- 0.01
+  file$pos <- TRUE
+  file$pos[file$mean_dif < 0] <- FALSE
+
+ p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
+  #Sys.sleep(2) na.rm=TRUE
+ # color = "mediumseagreen"
+
+}
+
+p 
 ```

### 2021-07-02 graphs_newt_snakes/fig_1000.Rmd
adding the trasformations for the newt and snake phenotypes

@@
 ---
-title: "1000 Graphs"
+title: "Graphs for 1000  Generations"
 output: html_document
@@
 ## This is a r file to show what the phenotypess are after 1000 generations
-- A problem that I have been experiencing is that the phenotypes seem so go wild really quickly 
-- This will be a graph that looks at the phenotypes of different simulations with a unique mutation rate and mutation effect size.
+A problem that I have been experiencing is that the phenotypes seem so go wild really quickly
 
-- Lets just visualize what the phenotypes are doing
+This will be a graph that looks at the phenotypes of different simulations with a unique mutation rate and mutation effect size.
 
-## The Figure
-Loop through the files and find the max and min of each of the species pheotypes
-Then set up a graph with the max max
-Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time
+Lets just visualize what the phenotypes are doing
 
-I made a mistake. I switched the mutation rates and the effect sizes
+## The testing Paramiters 
+I used different values for snake_mu_effect_sd	newt_mu_effect_sd	snake_mu_rate	newt_mu_rate. I chose these parameters to see if there would be a seeable interaction in phenotypes 
+Other params:
+	sigma_i = 1, recomb=1e-8, sigma_in = 0.5, sigma_M = 0.33, SD=SI=surs=SM=sigma_in, L = 4, W=35.0, G=1e8, FECUN = 1/(L), RHO, FECUN/((1+FECUN) * K), interaction_rate =  0.05, PE = 0.1, w= 10, c = 0.0, initializeRecombinationRate(recomb), initializeMutationRate(1e-10), initializeGenomicElement(g1, 0, G-1)
+
+Other things: (kind of confusing)	
+	initializeMutationType("m1", 0.5, "n", 0, newt_mu_effect_sd);
+	initializeMutationType("m2", 0.5, "n", 0, snake_mu_effect_sd);
+	initializeGenomicElementType("g1", c(m1, m2), c(newt_mu_rate/mu_rate, 1)); // mutation proportions add the proportion (the target mutation rate)
+
+Snake/newt mu effect sd -> is the standard deviation that each mutation would "effect" a phenotype. Values: 0.01 0.05 0.2 0.5
+
+Snake/newt mu rate -> is the mutation rate that were assigned to newts and snakes. Values: 1.00E-08 1.00E-10 1.00E-12
+
+In total there were 144 combinations. One simulation per combination (this experiment was not repeated)
+
+## Project future goal as of summer 2021
+My summer 2021 goal is to get the 1 on 1 simulation to run *correctly*. For this to happen I would like the simulation to have:
+-Realistic phenotypes (snake 0-3, newt 0-1.5(thoughts 2021?))
+-See if the levels of toxicity and resistance interact 
+-See groups of mutations/ certain phenotypes
+
+# Mistake Simulations 
+I tried to run SLiM simulation different with the selected parameters and the MSprime   both_su_1e-10_nu_1e-10_sue_0.01_nue_0.01 (s/n u mutation rate, n/s ue mutation effect size).
+However I flipped the mutation rate and effect size. So... new experiment with really large mutation rate????
+
+# Makeing of the Figure
+Loop through the files and find the max and min of each of the species phenotypes
+Then set up a graph with the average phenotype
+
+This section of code loops though the files and finds the maximum and minumum pheotypes of newts and snakes.
+and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time
 
@@
 
-  print(newt_max_pheno_1)
-  print(snake_max_pheno_1)
-   print(newt_min_pheno_1)
-  print(snake_min_pheno_1)
+  print(paste0("Newt max pheno: ", newt_max_pheno_1))
+  print(paste0("Snake max phenot: ", snake_max_pheno_1))
+  print(paste0("Newt min pheno: ", newt_min_pheno_1))
+  print(paste0("Snake min Pheno: ", snake_min_pheno_1))
 
@@
 ```
+
+This section of code loops though the files and make two lines (red for newts blue for snakes).
+This figure shows how the pheotypes change over 1000 generations.
+It also keeps a minimum about of info in memory at a time.
+aka dont open all of the files and put it into a large dataframe.
+
 ```{r phenotype graph for mistake sims, echo=FALSE}
@@
 ```
+## Difference between snake and newt pheotypes
+
+This figure represents the difference between the snake and the newt phenotype.
+The pick lines indicat that the newt is more toxit than the snakes, while the blue line indicates that the snakes are more resitant than the newts
 
@@
   #scale_y_log10()+
-  scale_y_log10(limits=c(min_difference_1, max_difference_1))+
-  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
+  #scale_y_log10(limits=c(min_difference_1, max_difference_1))+
+  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
     ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
@@
 
-## The Figure
-Loop through the files and find the max and min of each of the species pheotypes
-Then set up a graph with the max max
-Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time
+## Trasforming the phenotypes back
 
-This is the correct one
+I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and
+
+```{r trasformation, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = exp(Newt_mean_Pheno/10)), color = "darkred") + 
+  ggtitle("Newt trasnformed vs un-trasformed") +
+  xlab("Trasnformed") + ylab("Untransformed")+
+  theme_bw()
+q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = exp(Snake_mean_Pheno/10)), color = "darkred") + 
+  ggtitle("Newt trasnformed vs un-trasformed") +
+  xlab("Trasnformed") + ylab("Untransformed")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+ p <- p + geom_line(data=file, aes(y = exp(Newt_mean_Pheno/10)), color = "darkred")
+
+ q <- q + geom_line(data=file, aes(y = exp(Snake_mean_Pheno/10)), color="steelblue", linetype="twodash")
+}
+
+p 
+q
+
+```
+
+# The Correct Experiment
+
+I ran 144 SLiM simulations with different parameters values and used the MSprime   both_su_1e-10_nu_1e-10_sue_0.01_nue_0.01 (s/n u mutation rate, n/s ue mutation effect size) file.
+
+Again I looped through the files and find the max and min of each of the species pheotypes
+Then set up a graph with the average pheotypes over 1000 generations (red line for newts blue linesfor snakes).
+
+This is the correct one:
+
 ```{r data 1 msprime photype graph, echo=FALSE}
@@
 
-  print(newt_max_pheno_2)
-  print(snake_max_pheno_2)
-  print(newt_min_pheno_2)
-  print(snake_min_pheno_2)
+  print(paste0("Newt max pheno: ", newt_max_pheno_2))
+  print(paste0("Snake max phenot: ", snake_max_pheno_2))
+  print(paste0("Newt min pheno: ", newt_min_pheno_2))
+  print(paste0("Snake min Pheno: ", snake_min_pheno_2))
 
@@
   xlim(0, 1000)+
-  #ylim(min_difference, max_difference)+
+  ylim(min_difference_2, max_difference_2)+
   #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
   #scale_y_log10()+
-  scale_y_log10(limits=c(min_difference_2, max_difference_2))+
-  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
+  #scale_y_log10(limits=c(min_difference_2, max_difference_2))+
+  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
     ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
@@
 
-## The Figure
-Loop through the files and find the max and min of each of the species pheotypes
-Then set up a graph with the max max
-Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time
+## Trasforming the phenotypes back
 
-This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked.
+I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and
 
-```{r pressure, echo=FALSE}
+```{r trasformation cor sim, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = exp(Newt_mean_Pheno/10)), color = "darkred") + 
+  ggtitle("Newt trasnformed vs un-trasformed") +
+  xlab("Trasnformed") + ylab("Untransformed")+
+  theme_bw()
+q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = exp(Snake_mean_Pheno/10)), color = "darkred") + 
+  ggtitle("Newt trasnformed vs un-trasformed") +
+  xlab("Trasnformed") + ylab("Untransformed")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+ p <- p + geom_line(data=file, aes(y = exp(Newt_mean_Pheno/10)), color = "darkred")
+
+ q <- q + geom_line(data=file, aes(y = exp(Snake_mean_Pheno/10)), color="steelblue", linetype="twodash")
+}
+
+p 
+q
+
+```
+
+# Expanded Experiment 
+This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked. I ran 144 SLiM simulations & MSprime with different parameters values.
+
+Again I looped through the files and find the max and min of each of the species pheotypes
+Then set up a graph with the average phenotypes over 1000 generations (red line for newts blue lines for snakes).
+
+```{r gathering data for dif var for msprim sim and slim, echo=FALSE}
 newt_max_pheno_3 = 0
@@
 
-  print(newt_max_pheno_3)
-  print(snake_max_pheno_3)
-  print(min_difference_3)
-  print(max_difference_3)
+  print(paste0("Newt max pheno: ", newt_max_pheno_3))
+  print(paste0("Snake max phenot: ", snake_max_pheno_3))
+  print(paste0("Min pheno dif: ", min_difference_3))
+  print(paste0("Max Pheno dif: ", max_difference_3))
+
   if (newt_max_pheno_3 > snake_max_pheno_3){
@@
 
-```{r pressure, echo=FALSE}
+```{r 2sims phenotypes, echo=FALSE}
 
@@
 
-```{r pressure, echo=FALSE}
+```{r 2sim phendif, echo=FALSE}
 
@@
 ```
+
+## Trasforming the phenotypes back
+
+I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and
+
+```{r trasformation 2sim, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = exp(Newt_mean_Pheno/10)), color = "darkred") + 
+  ggtitle("Newt trasnformed vs un-trasformed") +
+  xlab("Trasnformed") + ylab("Untransformed")+
+  theme_bw()
+q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = exp(Snake_mean_Pheno/10)), color = "darkred") + 
+  ggtitle("Newt trasnformed vs un-trasformed") +
+  xlab("Trasnformed") + ylab("Untransformed")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+   file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  #print(file$Newt_mean_Pheno)
+  #print(exp(file$Newt_mean_Pheno/10))
+  file <- read.table(current_file, header = TRUE)
+ p <- p + geom_line(data=file, aes(y = exp(as.numeric(Newt_mean_Pheno)/10)), color = "darkred")
+
+ q <- q + geom_line(data=file, aes(y = exp(as.numeric(Snake_mean_Pheno)/10)), color="steelblue", linetype="twodash")
+}
+
+#p 
+#q
+
+```

### 2021-07-05 graphs_newt_snakes/fig_1000.Rmd
fixed error in trasforming and added a phenotype changing graph to see how phenotpes were changing over 1000 gens. the one for 2 sims is not working yet

@@
 library(viridis)
+library(colorspace)
 #setwd("~/Desktop/Proposal Old Drafts")
@@
 ## This is a r file to show what the phenotypess are after 1000 generations
-A problem that I have been experiencing is that the phenotypes seem so go wild really quickly
+A problem that I have been experiencing is that the phenotypes seem so go wild really quickly. One species' phenotype balloons to be really high while the other species" phenotype stays really low.
 
@@
 
-Lets just visualize what the phenotypes are doing
+Lets just visualize what the phenotypes are doing.
 
@@
 I tried to run SLiM simulation different with the selected parameters and the MSprime   both_su_1e-10_nu_1e-10_sue_0.01_nue_0.01 (s/n u mutation rate, n/s ue mutation effect size).
-However I flipped the mutation rate and effect size. So... new experiment with really large mutation rate????
+However I flipped the mutation rate and effect size. So... new experiment with really large mutation rate and small effect size????
 
@@
   geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
-  ggtitle("Phenotype Measurements for Newts and Snakes") +
+  ggtitle("Wrong1sim: Phenotype Measurements for Newts and Snakes") +
   xlab("Generation") + ylab("Average Phenotypes")+
@@
   geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
-    ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
+    ggtitle("Wrong1sim: Difference Between Phenotypes (Snakes-Newts)") +
   xlab("Generation") + ylab("Average Difference")+
@@
 
+## How much did the phenotypes of newts and snakes change over 1000 generations
+
+For this figure I want there to be 2 sets of points (4 complete points) for each simulation taking the first and last mean phenotype for the newt and the snake.
+Essentially, asking if the phenotypes of the newts and snakes changed over 1000 generations?
+
+```{r pheno change, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=1:144)) +
+  xlim(0, 145)+
+  #ylim(newt_min_pheno_1, newt_max_pheno_1)+
+  geom_point(aes(x = 1, y = Newt_mean_Pheno[1]), color = darken("darkred")) +
+  geom_point(aes(x = 1, y = Newt_mean_Pheno[50]), color = lighten("darkred")) +
+  geom_point(aes(x = 1, y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
+  geom_point(aes(x = 1, y = Snake_mean_Pheno[50]), color = lighten("steelblue")) +
+  ggtitle("Wrong1sim: Phenotype Change") +
+  xlab("Simulation number") + ylab("Phenotype")+
+  theme_bw()
+i=1
+for (current_file in files){
+
+  file <- read.table(current_file, header = TRUE)
+ p <- p + geom_point(data= file, x = i, aes(y = Newt_mean_Pheno[1]), color = darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = Newt_mean_Pheno[50]), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[50]), color = lighten("steelblue"))
+ i = i+1
+}
+
+p
+
+```
+
 ## Trasforming the phenotypes back
 
-I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and
+I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and mu.
+
+I calculated the phenotypes from this expression, newt pheno = exp(inds_n.sumOfMutationsOfType(m1)/10).
+So to un-transform and find the # of mutations I need to ln both sides of the equation ln(pheno=e^(sumOfMutations/10)).
+Then solve for sumOfMutations,  sumOfMutations = 10 * ln(pheno)
+
+Notes:
+difference in the trees betw two chromosomes in a pop of size N is 4N
+so # of differing mutations is like 4 N L mu where L = genome length, mu = mutaiton rate per bp and if each mutation has an effect size that is N(0, sd=sigma), then the sum of K of these has mean 0 and SD= sigma * sqrt(K).
+So untransformed phenotypes (sum of effect sizes) should have mean 0 and SD= sigma * sqrt(4 N L mu).
+So, you'd work out what SD you want, then given mu solve for sigma (the SD of effect size)
 
@@
   #ylim(0, true_max_1)+
-  geom_line(aes(y = exp(Newt_mean_Pheno/10)), color = "darkred") + 
-  ggtitle("Newt trasnformed vs un-trasformed") +
+  geom_line(aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred") + 
+  ggtitle("Wrong1sim: Newt trasnformed vs un-trasformed") +
   xlab("Trasnformed") + ylab("Untransformed")+
@@
   #ylim(0, true_max_1)+
-  geom_line(aes(y = exp(Snake_mean_Pheno/10)), color = "darkred") + 
-  ggtitle("Newt trasnformed vs un-trasformed") +
+  geom_line(aes(y = (log(Snake_mean_Pheno)*10)), color = "steelblue") + 
+  ggtitle("Wrong1sim: Newt trasnformed vs un-trasformed") +
   xlab("Trasnformed") + ylab("Untransformed")+
@@
   file <- read.table(current_file, header = TRUE)
- p <- p + geom_line(data=file, aes(y = exp(Newt_mean_Pheno/10)), color = "darkred")
+ p <- p + geom_line(data=file, aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred")
 
- q <- q + geom_line(data=file, aes(y = exp(Snake_mean_Pheno/10)), color="steelblue", linetype="twodash")
+ q <- q + geom_line(data=file, aes(y = (log(Snake_mean_Pheno)*10)), color="steelblue", linetype="twodash")
 }
@@
   geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
-  ggtitle("Phenotype Measurements for Newts and Snakes") +
+  ggtitle("1sim: Phenotype Measurements for Newts and Snakes") +
   xlab("Generation") + ylab("Average Phenotypes")+
@@
 ```
+## Difference between snake and newt pheotypes
+
 ```{r data from multiple msprime, echo=FALSE}
@@
   geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
-    ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
+    ggtitle("1sim: Difference Between Phenotypes (Snakes-Newts)") +
   xlab("Generation") + ylab("Average Difference")+
@@
 ```
+## How much did the phenotypes of newts and snakes change over 1000 generations
+
+```{r 1sim pheno change, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=1:144)) +
+  xlim(0, 145)+
+  #ylim(newt_min_pheno_1, newt_max_pheno_1)+
+  geom_point(aes(x = 1, y = Newt_mean_Pheno[1]), color = darken("darkred")) +
+  geom_point(aes(x = 1, y = Newt_mean_Pheno[50]), color = lighten("darkred")) +
+  geom_point(aes(x = 1, y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
+  geom_point(aes(x = 1, y = Snake_mean_Pheno[50]), color = lighten("steelblue")) +
+  ggtitle("1sim: Phenotype Change") +
+  xlab("Simulation number") + ylab("Phenotype")+
+  theme_bw()
+i=1
+for (current_file in files){
+
+  file <- read.table(current_file, header = TRUE)
+ p <- p + geom_point(data= file, x = i, aes(y = Newt_mean_Pheno[1]), color = darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = Newt_mean_Pheno[50]), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[50]), color = lighten("steelblue"))
+ i = i+1
+}
+
+p
+
+```
 
 ## Trasforming the phenotypes back
-
-I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and
 
@@
   #ylim(0, true_max_1)+
-  geom_line(aes(y = exp(Newt_mean_Pheno/10)), color = "darkred") + 
-  ggtitle("Newt trasnformed vs un-trasformed") +
+  geom_line(aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred") + 
+  ggtitle("1sim: Newt trasnformed vs un-trasformed") +
   xlab("Trasnformed") + ylab("Untransformed")+
@@
   #ylim(0, true_max_1)+
-  geom_line(aes(y = exp(Snake_mean_Pheno/10)), color = "darkred") + 
-  ggtitle("Newt trasnformed vs un-trasformed") +
+  geom_line(aes(y = (log(Snake_mean_Pheno)*10)), color = "steelblue") + 
+  ggtitle("1sim: Newt trasnformed vs un-trasformed") +
   xlab("Trasnformed") + ylab("Untransformed")+
@@
 
-# Expanded Experiment 
+# Expanded Experiment 2sims: 
 This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked. I ran 144 SLiM simulations & MSprime with different parameters values.
@@
   geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
-  ggtitle("Phenotype Measurements for Newts and Snakes") +
+  ggtitle("2sims: Phenotype Measurements for Newts and Snakes") +
   xlab("Generation") + ylab("Average Phenotypes")+
@@
 
-Some other things that might be goo to look at:
-
-The difference between the average phenotypes
+## Difference between snake and newt pheotypes
 
@@
   geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
-  ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
+  ggtitle("2sims: Difference Between Phenotypes (Snakes-Newts)") +
   xlab("Generation") + ylab("Average Difference")+
@@
 ```
+## How much did the phenotypes of newts and snakes change over 1000 generations
+
+```{r 2sim pheno change, echo=FALSE}
+
+files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=1:144)) +
+  xlim(0, 145)+
+  geom_point(aes(x = 1, y = as.numeric(Newt_mean_Pheno[1])), color = darken("darkred")) +
+  geom_point(aes(x = 1, y = as.numeric(Newt_mean_Pheno[50])), color = lighten("darkred")) +
+  geom_point(aes(x = 1, y = as.numeric(Snake_mean_Pheno[1])), color = darken("steelblue")) +
+  geom_point(aes(x = 1, y = as.numeric(Snake_mean_Pheno[50])), color = lighten("steelblue")) +
+  ggtitle("2sim: Phenotype Change") +
+  xlab("Simulation number") + ylab("Phenotype")+
+  theme_bw()
+i=1
+for (current_file in files){
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
+  file <- file[complete.cases(file), ]
+ p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])), color = darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])), color = darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])), color = lighten("steelblue"))
+ i = i+1
+}
+
+p
+
+```
 
 ## Trasforming the phenotypes back
-
-I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and
 
@@
 file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
+p <- ggplot(file1, aes(x=as.numeric(Newt_mean_Pheno))) +
   #ylim(0, true_max_1)+
-  geom_line(aes(y = exp(Newt_mean_Pheno/10)), color = "darkred") + 
-  ggtitle("Newt trasnformed vs un-trasformed") +
+  geom_line(aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred") + 
+  ggtitle("2sims: Newt trasnformed vs un-trasformed") +
   xlab("Trasnformed") + ylab("Untransformed")+
   theme_bw()
-q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
+q <- ggplot(file1, aes(x=as.numeric(Snake_mean_Pheno))) +
   #ylim(0, true_max_1)+
-  geom_line(aes(y = exp(Snake_mean_Pheno/10)), color = "darkred") + 
-  ggtitle("Newt trasnformed vs un-trasformed") +
+  geom_line(aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color = "steelblue") + 
+  ggtitle("2sims: Newt trasnformed vs un-trasformed") +
   xlab("Trasnformed") + ylab("Untransformed")+
@@
   #print(exp(file$Newt_mean_Pheno/10))
+  #print(log(as.numeric(file$Newt_mean_Pheno))*10)
   file <- read.table(current_file, header = TRUE)
- p <- p + geom_line(data=file, aes(y = exp(as.numeric(Newt_mean_Pheno)/10)), color = "darkred")
+ p <- p + geom_line(data=file, aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred",na.rm = TRUE)
 
- q <- q + geom_line(data=file, aes(y = exp(as.numeric(Snake_mean_Pheno)/10)), color="steelblue", linetype="twodash")
+ q <- q + geom_line(data=file, aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color="steelblue", linetype="twodash", na.rm = FALSE)
 }
 
-#p 
-#q
+p
+q
 

### 2021-07-07 graphs_newt_snakes/fig_1000.Rmd
I updated the r file to include log in the figures and to fix some of the header. I think the dot plot would be cool with arrows. Why are the newts starting above the snakes?

@@
   ggtitle("Wrong1sim: Phenotype Measurements for Newts and Snakes") +
-  xlab("Generation") + ylab("Average Phenotypes")+
+  xlab("Generation") + ylab("Average Phenotypes (Log)")+
   theme_bw()
@@
 ```
+
 ## Difference between snake and newt pheotypes
@@
   ggtitle("1sim: Phenotype Measurements for Newts and Snakes") +
-  xlab("Generation") + ylab("Average Phenotypes")+
+  xlab("Generation") + ylab("Average Phenotypes (Log)")+
   theme_bw()
@@
   ggtitle("2sims: Phenotype Measurements for Newts and Snakes") +
-  xlab("Generation") + ylab("Average Phenotypes")+
+  xlab("Generation") + ylab("Average Phenotypes  (Log)")+
   theme_bw()
@@
   ggtitle("2sims: Difference Between Phenotypes (Snakes-Newts)") +
-  xlab("Generation") + ylab("Average Difference")+
+  xlab("Generation") + ylab("Average Difference (Log)")+
   theme_bw()
@@
   xlim(0, 145)+
+  scale_y_log10()+
   geom_point(aes(x = 1, y = as.numeric(Newt_mean_Pheno[1])), color = darken("darkred")) +
@@
   ggtitle("2sim: Phenotype Change") +
-  xlab("Simulation number") + ylab("Phenotype")+
+  xlab("Simulation number") + ylab("Phenotype  (Log)")+
   theme_bw()
@@
   file <- file[complete.cases(file), ]
- p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])), color = darken("darkred")) +
-   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])), color = darken("steelblue")) +
-  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])), color = lighten("steelblue"))
+ p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color = darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color = darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color = lighten("steelblue"))
  i = i+1

### 2021-07-07 msprime/snake_newt_gv_.py
I am testing the colored dots on vs code by adding a print statement to my msprime code

@@ -6,7 +6,8 @@ import os
 import sys
 from sys import argv
 # import util
-# testing vscode&git
+# testing vscode&git 
+print("hello")
 
 sequence_length = 100000000
 '''

### 2021-07-10 graphs_newt_snakes/fig_1000.Rmd
I am turning the r figures and data collection into functions its more difficult than I thought. I also worked on creating a bash script that can do two different loops to go through files in a folder and to use a csv to pull different varaables. This script worked very well!.

@@
 library(colorspace)
+
 #setwd("~/Desktop/Proposal Old Drafts")
@@
 
-```{r data from the mistake folder, echo=FALSE}
+```{r functions, echo=FALSE}
+
+collect_data_points <- function(files) {
   newt_max_pheno_1 = 0
@@
   max_difference_1 = 0
-
-files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+  mean = 0
+  sd = 0
 
@@
   file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  mean = mean(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno))
+  sd = sd(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno))
 
@@
 
-  print(paste0("Newt max pheno: ", newt_max_pheno_1))
-  print(paste0("Snake max phenot: ", snake_max_pheno_1))
-  print(paste0("Newt min pheno: ", newt_min_pheno_1))
-  print(paste0("Snake min Pheno: ", snake_min_pheno_1))
-
     if (newt_max_pheno_1 > snake_max_pheno_1){
@@
     true_min_1 = snake_min_pheno_1 }
+
+  return(c(newt_max_pheno_1, snake_max_pheno_1, newt_min_pheno_1, snake_min_pheno_1, true_max_1, true_min_1, min_difference_1, max_difference_1, mean, sd))
+}
+
+phenotype_graph <- function(files, the_mean, the_sd, title){
+
+  file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(0, true_max_1)+
+  scale_y_log10(limits=c(the_mean-(the_sd*10), the_mean+(the_sd*10)))+
+  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
+  ggtitle(title) +
+  xlab("Generation") + ylab("Average Phenotypes (Log)")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+ p <- p +
+  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
+  #Sys.sleep(2)
+}
+return(p)
+}
+
+differnce_graph <- function(files, the_mean, the_sd, title){
+
+  p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(min_difference, max_difference)+
+  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
+  #scale_y_log10()+
+  #scale_y_log10(limits=c(min_difference_1, max_difference_1))+
+  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
+    ggtitle(title) +
+  xlab("Generation") + ylab("Average Difference")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
+  file$mean_dif[file$mean_dif == 0] <- 0.01
+  file$pos <- TRUE
+  file$pos[file$mean_dif < 0] <- FALSE
+
+ p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
+  #Sys.sleep(2) na.rm=TRUE
+ # color = "mediumseagreen"
+
+}
+  return(p)
+}
+
+```
+
+```{r data from the mistake folder, echo=FALSE}
+files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files)
+
+newt_max_pheno_1 = out[1]
+snake_max_pheno_1 = out[2]
+newt_min_pheno_1  = out[3]
+snake_min_pheno_1 = out[4]
+true_max_1 = out[5]
+true_min_1 = out[6]
+min_difference_1 = out[7]
+max_difference_1 = out[8]
+my_mean = out[9]
+my_sd = out[10]
+
+print(paste0("Newt max pheno: ", newt_max_pheno_1))
+print(paste0("Snake max phenot: ", snake_max_pheno_1))
+print(paste0("Newt min pheno: ", newt_min_pheno_1))
+print(paste0("Snake min Pheno: ", snake_min_pheno_1))
+print(paste0("Mean of combined snake and newt: ", my_mean))
+print(paste0("Sd of combined snake and newt: ", my_sd))
 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=gen)) +
-  xlim(0, 1000)+
-  #ylim(0, true_max_1)+
-  scale_y_log10(limits=c(true_min_1+0.8, true_max_1))+
-  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
-  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
-  ggtitle("Wrong1sim: Phenotype Measurements for Newts and Snakes") +
-  xlab("Generation") + ylab("Average Phenotypes (Log)")+
-  theme_bw()
-
-for (current_file in files){
-  #print(current_file)
-
-  file <- read.table(current_file, header = TRUE)
- p <- p +
-  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
-  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
-  #Sys.sleep(2)
-
-}
+title="Wrong1sim: Phenotype Measurements for Newts and Snakes"
+p = phenotype_graph(files, my_mean, my_sd, title)
 
@@
 This figure represents the difference between the snake and the newt phenotype.
-The pick lines indicat that the newt is more toxit than the snakes, while the blue line indicates that the snakes are more resitant than the newts
+The pink lines indicate that the newt is more toxit than the snakes, while the blue line indicates that the snakes are more resitant than the newts
 

### 2021-07-11 graphs_newt_snakes/fig_1000.Rmd
I am turning mor of the figure script into functions. It is very slow.

--- 2021-07-07 graphs_newt_snakes/fig_1000.Rmd
@@
   max_difference_1 = 0
-
-files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+  mean = 0
+  sd = 0
+  mean_mean_dif = 0
+  sd_mean_dif = 0
 
@@
   file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  mean = mean(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno), na.rm = TRUE)
+  sd = sd(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno), na.rm = TRUE)
+  mean_mean_dif = mean(as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno),na.rm = TRUE)
+  sd_mean_dif = sd(as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno),na.rm = TRUE)
 
@@
     true_min_1 = snake_min_pheno_1 }
+
+  return(c(newt_max_pheno_1, snake_max_pheno_1, newt_min_pheno_1, snake_min_pheno_1, true_max_1, true_min_1, min_difference_1, max_difference_1, mean, sd, mean_mean_dif, sd_mean_dif))
+}
+
+phenotype_graph <- function(files, the_mean, the_sd, title, is_log=FALSE){
+
+  file1 <- read.table(files[1], header = TRUE)
+  file1$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file1$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
+  ggtitle(title) +
+  xlab("Generation") + ylab("Average Phenotypes")+
+  theme_bw()
+
+if(is_log==TRUE){
+  p = p + ylab("Average Phenotypes (Log)") + scale_y_log10(limits=c(the_mean-(the_sd*10), the_mean+(the_sd*10)))
+  }
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+ p <- p +
+  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
+  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
+  #Sys.sleep(2)
+}
+return(p)
+}
+
+differnce_graph <- function(files, the_mean, the_sd, title, is_log=FALSE){
+
+ file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
+  ggtitle(title) +
+  xlab("Generation") + ylab("Average Difference")+
+  theme_bw()
+
+if(is_log==TRUE){
+  p = p + scale_y_log10(limits=c(abs(the_mean)-the_sd*10, abs(the_mean)+the_sd*10)) + ylab("Average Difference (Log)")
+}
+
+if(is_log==FALSE){
+  p = p + ylim(abs(the_mean)-the_sd*10, abs(the_mean)+the_sd*10)
+}
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
+  file$mean_dif[file$mean_dif == 0] <- 0.01
+  file$pos <- "Snake"
+  file$pos[file$mean_dif < 0] <- "Newt"
+  file$pos[file$mean_dif ==  0.01] <- "Equal"
+
+ p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
+  #Sys.sleep(2) na.rm=TRUE
+ # color = "mediumseagreen"
+
+}
+return(p)
+}
+
+phenotype_change_graph <- function(files, the_mean, the_sd, title, is_log=FALSE){
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=1:144)) +
+  xlim(0, 145)+
+  ggtitle(title) +
+  xlab("Simulation number") + ylab("Phenotype")+
+  theme_bw()
+
+if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Phenotype  (Log)")
+
+}
+i=1
+for (current_file in files){
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
+  file <- file[complete.cases(file), ]
+ p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color = darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color = darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color = lighten("steelblue"))
+ i = i+1
+}
+return(p)
+}
+
+```
+
+```{r data from the mistake folder, echo=FALSE}
+files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files)
+
+newt_max_pheno_1 = out[1]
+snake_max_pheno_1 = out[2]
+newt_min_pheno_1  = out[3]
+snake_min_pheno_1 = out[4]
+true_max_1 = out[5]
+true_min_1 = out[6]
+min_difference_1 = out[7]
+max_difference_1 = out[8]
+my_mean = out[9]
+my_sd = out[10]
+mean_mean_dif = out[11]
+sd_mean_dif = out[12]
+
+print(paste0("Newt max pheno: ", newt_max_pheno_1))
+print(paste0("Snake max phenot: ", snake_max_pheno_1))
+print(paste0("Newt min pheno: ", newt_min_pheno_1))
+print(paste0("Snake min Pheno: ", snake_min_pheno_1))
+print(paste0("Mean of combined snake and newt: ", my_mean))
+print(paste0("Sd of combined snake and newt: ", my_sd))
+print(paste0("Mean of the mean difference: ", mean_mean_dif))
+print(paste0("SD of the mean difference: ", sd_mean_dif))
 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=gen)) +
-  xlim(0, 1000)+
-  #ylim(0, true_max_1)+
-  scale_y_log10(limits=c(true_min_1+0.8, true_max_1))+
-  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
-  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
-  ggtitle("Wrong1sim: Phenotype Measurements for Newts and Snakes") +
-  xlab("Generation") + ylab("Average Phenotypes (Log)")+
-  theme_bw()
-
-for (current_file in files){
-  #print(current_file)
-
-  file <- read.table(current_file, header = TRUE)
- p <- p +
-  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
-  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
-  #Sys.sleep(2)
-
-}
-
+title="Wrong1sim: Phenotype Measurements for Newts and Snakes"
+q = phenotype_graph(files, my_mean, my_sd, title, is_log = TRUE)
+p = phenotype_graph(files, my_mean, my_sd, title)
+q
 p 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=gen)) +
-  xlim(0, 1000)+
-  #ylim(min_difference, max_difference)+
-  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
-  #scale_y_log10()+
-  #scale_y_log10(limits=c(min_difference_1, max_difference_1))+
-  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
-    ggtitle("Wrong1sim: Difference Between Phenotypes (Snakes-Newts)") +
-  xlab("Generation") + ylab("Average Difference")+
-  theme_bw()
-
-for (current_file in files){
-  #print(current_file)
-
-  file <- read.table(current_file, header = TRUE)
-  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
-  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
-  file <- file[complete.cases(file), ]
-  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
-  file$mean_dif[file$mean_dif == 0] <- 0.01
-  file$pos <- TRUE
-  file$pos[file$mean_dif < 0] <- FALSE
-
- p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
-  #Sys.sleep(2) na.rm=TRUE
- # color = "mediumseagreen"
-
-}
+title = "Wrong1sim: Difference Between Phenotypes (Snakes-Newts)"
+p = differnce_graph(files, mean_mean_dif, sd_mean_dif, title, is_log=FALSE)
 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=1:144)) +
-  xlim(0, 145)+
-  #ylim(newt_min_pheno_1, newt_max_pheno_1)+
-  geom_point(aes(x = 1, y = Newt_mean_Pheno[1]), color = darken("darkred")) +
-  geom_point(aes(x = 1, y = Newt_mean_Pheno[50]), color = lighten("darkred")) +
-  geom_point(aes(x = 1, y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
-  geom_point(aes(x = 1, y = Snake_mean_Pheno[50]), color = lighten("steelblue")) +
-  ggtitle("Wrong1sim: Phenotype Change") +
-  xlab("Simulation number") + ylab("Phenotype")+
-  theme_bw()
-i=1
-for (current_file in files){
-
-  file <- read.table(current_file, header = TRUE)
- p <- p + geom_point(data= file, x = i, aes(y = Newt_mean_Pheno[1]), color = darken("darkred")) +
-   geom_point(data= file,x = i, aes(y = Newt_mean_Pheno[50]), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
-  geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[50]), color = lighten("steelblue"))
- i = i+1
-}
+title = "Wrong1sim: Phenotype Change"
+p=phenotype_change_graph(files, my_mean, my_sd, title, is_log=FALSE)
 

### 2021-07-11 graphs_newt_snakes/fig_1000.Rmd
still adding more to the r functions. getting closer to working

@@
   file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
-  mean = mean(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno), na.rm = TRUE)
-  sd = sd(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno), na.rm = TRUE)
+  file$Newt_mean_Pheno <- lapply(file$Newt_mean_Pheno,as.numeric)
+  file$Snake_mean_Pheno <- lapply(file$Snake_mean_Pheno,as.numeric)
+  file$Newt_max_Pheno <- lapply(file$Newt_max_Pheno,as.numeric)
+  file$Snake_max_Pheno <- lapply(file$Snake_max_Pheno,as.numeric)
+  file$Newt_min_Pheno <- lapply(file$Newt_min_Pheno,as.numeric)
+  file$Snake_min_Pheno <- lapply(file$Snake_min_Pheno,as.numeric)
+
+  mean = mean(c(as.numeric(file$Newt_mean_Pheno), as.numeric(file$Snake_mean_Pheno)), na.rm = TRUE)
+  sd = sd(c(as.numeric(file$Newt_mean_Pheno), as.numeric(file$Snake_mean_Pheno)), na.rm = TRUE)
   mean_mean_dif = mean(as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno),na.rm = TRUE)
@@
 
-  if (max(file$Newt_max_Pheno) > newt_max_pheno_1){
-    newt_max_pheno_1 = max(file$Newt_max_Pheno) }
+    if (max(as.numeric(file$Newt_max_Pheno), na.rm = TRUE) > newt_max_pheno_1){
+    newt_max_pheno_1 = max(as.numeric(file$Newt_max_Pheno), na.rm = TRUE) }
 
-  if (max(file$Snake_max_Pheno) > snake_max_pheno_1){
-    snake_max_pheno_1 = max(file$Snake_max_Pheno) }
+  if (max(as.numeric(file$Snake_max_Pheno), na.rm = TRUE) > snake_max_pheno_1){
+    snake_max_pheno_1 = max(as.numeric(file$Snake_max_Pheno), na.rm = TRUE) }
 
-  if (min(file$Newt_min_Pheno) < newt_min_pheno_1){
-    newt_min_pheno_1 = min(file$Newt_min_Pheno) }
+  if (min(as.numeric(file$Newt_min_Pheno), na.rm = TRUE) < newt_min_pheno_1){
+    newt_min_pheno_1 = min(as.numeric(file$Newt_min_Pheno), na.rm = TRUE) }
 
-  if (min(file$Snake_min_Pheno) > snake_min_pheno_1){
-    snake_min_pheno_1 = max(file$Snake_min_Pheno) }
+  if (min(as.numeric(file$Snake_min_Pheno), na.rm = TRUE) < snake_min_pheno_1){
+    snake_min_pheno_1 = min(as.numeric(file$Snake_min_Pheno), na.rm = TRUE) }
 
-  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_1){
-    min_difference_1 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
+  if (min(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - max(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE) < min_difference_1){
+    min_difference_1 = min(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - max(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE)
   }
 
-  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_1){
-    max_difference_1 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
+  if (max(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - min(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE) > max_difference_1){
+    max_difference_1 = max(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - min(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE)
   }
@@
 
+untrasform <- function(files, the_mean, the_sd, title1, title2, is_log=FALSE){
+
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=as.numeric(Newt_mean_Pheno))) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred") + 
+  ggtitle(title1) +
+  xlab("Trasnformed") + ylab("Untransformed")+
+  theme_bw()
+q <- ggplot(file1, aes(x=as.numeric(Snake_mean_Pheno))) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color = "steelblue") + 
+  ggtitle(title2) +
+  xlab("Trasnformed") + ylab("Untransformed")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  #print(file$Newt_mean_Pheno)
+  #print(exp(file$Newt_mean_Pheno/10))
+  #print(log(as.numeric(file$Newt_mean_Pheno))*10)
+  file <- read.table(current_file, header = TRUE)
+ p <- p + geom_line(data=file, aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred",na.rm = TRUE)
+
+ q <- q + geom_line(data=file, aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color="steelblue", linetype="twodash", na.rm = FALSE)
+}
+return(list(p,q))
+
+}
+
 ```
@@
 files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
-  #ylim(0, true_max_1)+
-  geom_line(aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred") + 
-  ggtitle("Wrong1sim: Newt trasnformed vs un-trasformed") +
-  xlab("Trasnformed") + ylab("Untransformed")+
-  theme_bw()
-q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
-  #ylim(0, true_max_1)+
-  geom_line(aes(y = (log(Snake_mean_Pheno)*10)), color = "steelblue") + 
-  ggtitle("Wrong1sim: Newt trasnformed vs un-trasformed") +
-  xlab("Trasnformed") + ylab("Untransformed")+
-  theme_bw()
 
-for (current_file in files){
-  #print(current_file)
-
-  file <- read.table(current_file, header = TRUE)
- p <- p + geom_line(data=file, aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred")
-
- q <- q + geom_line(data=file, aes(y = (log(Snake_mean_Pheno)*10)), color="steelblue", linetype="twodash")
-}
-
-p 
-q
+title1 = "Wrong1sim: Newt trasnformed vs un-trasformed"
+title2 = "Wrong1sim: Snake trasnformed vs un-trasformed"
+graph = untrasform(files, my_mean, my_sd, title1, title2, is_log=FALSE)
+graph[1]
+graph[2]
 
@@
 ```{r data 1 msprime photype graph, echo=FALSE}
-newt_max_pheno_2 = 0
-snake_max_pheno_2 = 0
-newt_min_pheno_2 = 0
-snake_min_pheno_2 = 0
-true_max_2 = 0
-true_min_2 = 0
-min_difference_2 = 0
-max_difference_2 = 0
-
 files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
 
-for (current_file in files){
-  #print(current_file)
+out = collect_data_points(files)
 
-  file <- read.table(current_file, header = TRUE)
-  #print(max(file$Newt_max_Pheno))
-  #print(max(file$Snake_max_Pheno))
+newt_max_pheno_1 = out[1]
+snake_max_pheno_1 = out[2]
+newt_min_pheno_1  = out[3]
+snake_min_pheno_1 = out[4]
+true_max_1 = out[5]
+true_min_1 = out[6]
+min_difference_1 = out[7]
+max_difference_1 = out[8]
+my_mean = out[9]
+my_sd = out[10]
+mean_mean_dif = out[11]
+sd_mean_dif = out[12]
 
-  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
-  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
-  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
-  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
-  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
-  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+print(paste0("Newt max pheno: ", newt_max_pheno_1))
+print(paste0("Snake max phenot: ", snake_max_pheno_1))
+print(paste0("Newt min pheno: ", newt_min_pheno_1))
+print(paste0("Snake min Pheno: ", snake_min_pheno_1))
+print(paste0("Mean of combined snake and newt: ", my_mean))
+print(paste0("Sd of combined snake and newt: ", my_sd))
+print(paste0("Mean of the mean difference: ", mean_mean_dif))
+print(paste0("SD of the mean difference: ", sd_mean_dif))
 
-  if (max(file$Newt_max_Pheno) > newt_max_pheno_2){
-    newt_max_pheno_2 = max(file$Newt_max_Pheno) }
-
-  if (max(file$Snake_max_Pheno) > snake_max_pheno_2){
-    snake_max_pheno_2 = max(file$Snake_max_Pheno) }
-
-  if (min(file$Newt_min_Pheno) < newt_min_pheno_2){
-    newt_min_pheno_2 = max(file$Newt_min_Pheno) }
-
-  if (max(file$Snake_min_Pheno) < snake_min_pheno_2){
-    snake_min_pheno_2 = max(file$Snake_min_Pheno) }
-
-  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_2){
-      min_difference_2 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
-  }
-
-  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_2){
-    max_difference_2 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
-  }
-}
-
-  print(paste0("Newt max pheno: ", newt_max_pheno_2))
-  print(paste0("Snake max phenot: ", snake_max_pheno_2))
-  print(paste0("Newt min pheno: ", newt_min_pheno_2))
-  print(paste0("Snake min Pheno: ", snake_min_pheno_2))
-
-  if (newt_max_pheno_2 > snake_max_pheno_2){
-    true_max_2 = newt_max_pheno_2 }
-  if ( snake_max_pheno_2 > newt_max_pheno_2){
-    true_max_2 = snake_max_pheno_2 }
-
-  if (newt_min_pheno_2 < snake_min_pheno_2){
-    true_min_2 = newt_min_pheno_2 }
-  if ( snake_min_pheno_2 < newt_min_pheno_2){
-    true_min_2 = snake_min_pheno_2 }
 ```
@@
 files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=gen)) +
-  xlim(0, 1000)+
-  #ylim(0, true_max_2)+
-  scale_y_log10(limits=c(true_min_2+0.5, true_max_2))+
-  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
-  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
-  ggtitle("1sim: Phenotype Measurements for Newts and Snakes") +
-  xlab("Generation") + ylab("Average Phenotypes (Log)")+
-  theme_bw()
-
-for (current_file in files){
-  #print(current_file)
-
-  file <- read.table(current_file, header = TRUE)
- p <- p +
-  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
-  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
-  #Sys.sleep(2)
-
-}
-
+title = "1sim: Phenotype Measurements for Newts and Snake"
+q = phenotype_graph(files, my_mean, my_sd, title, is_log = TRUE)
+p = phenotype_graph(files, my_mean, my_sd, title)
+q
 p 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=gen)) +
-  xlim(0, 1000)+
-  ylim(min_difference_2, max_difference_2)+
-  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
-  #scale_y_log10()+
-  #scale_y_log10(limits=c(min_difference_2, max_difference_2))+
-  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
-    ggtitle("1sim: Difference Between Phenotypes (Snakes-Newts)") +
-  xlab("Generation") + ylab("Average Difference")+
-  theme_bw()
 
-for (current_file in files){
-  #print(current_file)
-
-  file <- read.table(current_file, header = TRUE)
-  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
-  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
-  file <- file[complete.cases(file), ]
-  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
-  file$mean_dif[file$mean_dif == 0] <- 0.01
-  file$pos <- TRUE
-  file$pos[file$mean_dif < 0] <- FALSE
-
- p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
-  #Sys.sleep(2) na.rm=TRUE
- # color = "mediumseagreen"
-
-}
+title = "1sim: Difference Between Phenotypes (Snakes-Newts)"
+p = differnce_graph(files, mean_mean_dif, sd_mean_dif, title, is_log=FALSE)
 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=1:144)) +
-  xlim(0, 145)+
-  #ylim(newt_min_pheno_1, newt_max_pheno_1)+
-  geom_point(aes(x = 1, y = Newt_mean_Pheno[1]), color = darken("darkred")) +
-  geom_point(aes(x = 1, y = Newt_mean_Pheno[50]), color = lighten("darkred")) +
-  geom_point(aes(x = 1, y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
-  geom_point(aes(x = 1, y = Snake_mean_Pheno[50]), color = lighten("steelblue")) +
-  ggtitle("1sim: Phenotype Change") +
-  xlab("Simulation number") + ylab("Phenotype")+
-  theme_bw()
-i=1
-for (current_file in files){
 
-  file <- read.table(current_file, header = TRUE)
- p <- p + geom_point(data= file, x = i, aes(y = Newt_mean_Pheno[1]), color = darken("darkred")) +
-   geom_point(data= file,x = i, aes(y = Newt_mean_Pheno[50]), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
-  geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[50]), color = lighten("steelblue"))
- i = i+1
-}
+title = "1sim: Phenotype Change"
+p=phenotype_change_graph(files, my_mean, my_sd, title, is_log=FALSE)
 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
-  #ylim(0, true_max_1)+
-  geom_line(aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred") + 
-  ggtitle("1sim: Newt trasnformed vs un-trasformed") +
-  xlab("Trasnformed") + ylab("Untransformed")+
-  theme_bw()
-q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
-  #ylim(0, true_max_1)+
-  geom_line(aes(y = (log(Snake_mean_Pheno)*10)), color = "steelblue") + 
-  ggtitle("1sim: Newt trasnformed vs un-trasformed") +
-  xlab("Trasnformed") + ylab("Untransformed")+
-  theme_bw()
 
-for (current_file in files){
-  #print(current_file)
-
-  file <- read.table(current_file, header = TRUE)
- p <- p + geom_line(data=file, aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred")
-
- q <- q + geom_line(data=file, aes(y = (log(Snake_mean_Pheno)*10)), color="steelblue", linetype="twodash")
-}
-
-p 
-q
+title1 = "1som: Newt trasnformed vs un-trasformed"
+title2 = "g1sim: Snake trasnformed vs un-trasformed"
+graph = untrasform(files, my_mean, my_sd, title1, title2, is_log=FALSE)
+graph[1]
+graph[2]
 
@@
 ```{r gathering data for dif var for msprim sim and slim, echo=FALSE}
-newt_max_pheno_3 = 0
-snake_max_pheno_3 = 0
-newt_min_pheno_3 = 0
-snake_min_pheno_3 = 0
-true_max_3 = 0
-true_min_3 = 0
-max_difference_3 = 0
-min_difference_3 = 0
 
@@
 
-for (current_file in files){
-  #print(current_file)
+out = collect_data_points(files)
 
-  file <- read.table(current_file, header = TRUE)
-  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
-  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
-  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
-  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
-  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
-  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
-  #print(max(file$Newt_max_Pheno, na.rm = TRUE))
-  #print(max(file$Snake_max_Pheno, na.rm = TRUE))
+newt_max_pheno_1 = out[1]
+snake_max_pheno_1 = out[2]
+newt_min_pheno_1  = out[3]
+snake_min_pheno_1 = out[4]
+true_max_1 = out[5]
+true_min_1 = out[6]
+min_difference_1 = out[7]
+max_difference_1 = out[8]
+my_mean = out[9]
+my_sd = out[10]
+mean_mean_dif = out[11]
+sd_mean_dif = out[12]
 
-  if (as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) > newt_max_pheno_3){
-    newt_max_pheno_3 = as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) }
+print(paste0("Newt max pheno: ", newt_max_pheno_1))
+print(paste0("Snake max phenot: ", snake_max_pheno_1))
+print(paste0("Newt min pheno: ", newt_min_pheno_1))
+print(paste0("Snake min Pheno: ", snake_min_pheno_1))
+print(paste0("Mean of combined snake and newt: ", my_mean))
+print(paste0("Sd of combined snake and newt: ", my_sd))
+print(paste0("Mean of the mean difference: ", mean_mean_dif))
+print(paste0("SD of the mean difference: ", sd_mean_dif))
 
-  if (as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) > snake_max_pheno_3){
-    snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }
-
-  if (as.numeric(min(file$Newt_min_Pheno, na.rm = TRUE)) < newt_min_pheno_3){
-    newt_min_pheno_3 = as.numeric(max(file$Newt_min_Pheno, na.rm = TRUE)) }
-
-  if (as.numeric(max(file$Snake_min_Pheno, na.rm = TRUE)) < snake_min_pheno_3){
-    snake_min_pheno_3 = as.numeric(max(file$Snake_min_Pheno, na.rm = TRUE)) }
-
- if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_3){
-    min_difference_3 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
-  }
-
-  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_3){
-    max_difference_3 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
-  }
-
-      }
-
-  print(paste0("Newt max pheno: ", newt_max_pheno_3))
-  print(paste0("Snake max phenot: ", snake_max_pheno_3))
-  print(paste0("Min pheno dif: ", min_difference_3))
-  print(paste0("Max Pheno dif: ", max_difference_3))
-
-  if (newt_max_pheno_3 > snake_max_pheno_3){
-    true_max_3 = newt_max_pheno_3 }
-  if ( snake_max_pheno_3 > newt_max_pheno_3){
-    true_max_3 = snake_max_pheno_3 }
-
-  if (newt_min_pheno_3 < snake_min_pheno_3){
-    true_min_3 = newt_min_pheno_3 }
-  if ( snake_max_pheno_3 < newt_max_pheno_3){
-    true_min_3 = snake_min_pheno_3 }
 ```

### 2021-07-11 graphs_newt_snakes/fig_1000.Rmd
I got the functions to work. next step is to read in the new data and graph it.

@@
 library(colorspace)
+library(gridExtra)
 
@@
   file1 <- read.table(files[1], header = TRUE)
-  file1$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
-  file1$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file1$Newt_mean_Pheno[file1$Newt_mean_Pheno == "NULL"] <- NA
+  file1$Snake_mean_Pheno[file1$Snake_mean_Pheno == "NULL"] <- NA
 p <- ggplot(file1, aes(x=gen)) +
@@
 if(is_log==TRUE){
-  p = p + ylab("Average Phenotypes (Log)") + scale_y_log10(limits=c(the_mean-(the_sd*10), the_mean+(the_sd*10)))
+  p = p + ylab("Average Phenotypes (Log)") + scale_y_log10(limits=c(the_mean-(the_sd*3), the_mean+(the_sd*10)))
   }
@@
  p <- p +
-  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
-  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
+   geom_line(data=file, aes(y = as.numeric(Newt_mean_Pheno)), color = "darkred",na.rm=TRUE) +
+   geom_line(data=file, aes(y = as.numeric(Snake_mean_Pheno)), color="steelblue", linetype="twodash", na.rm=TRUE) 
   #Sys.sleep(2)
@@
 
-differnce_graph <- function(files, the_mean, the_sd, title, is_log=FALSE){
+differnce_graph <- function(files, the_mean, the_sd, min_difference_1, max_difference_1, title, is_log=FALSE){
 
@@
 if(is_log==TRUE){
-  p = p + scale_y_log10(limits=c(abs(the_mean)-the_sd*10, abs(the_mean)+the_sd*10)) + ylab("Average Difference (Log)")
+  p = p + scale_y_log10(limits=c(min_difference_1, max_difference_1)) + ylab("Average Difference (Log)")
 }
@@
 }
+
 i=1
@@
 ```{r phenotype graph for mistake sims, echo=FALSE}
+myfiles <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
 
-files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-title="Wrong1sim: Phenotype Measurements for Newts and Snakes"
-q = phenotype_graph(files, my_mean, my_sd, title, is_log = TRUE)
-p = phenotype_graph(files, my_mean, my_sd, title)
-q
+p = phenotype_graph(files=myfiles, the_mean=out[9], the_sd=out[10], title="Wrong1sim: Phenotype Measurements for Newts and Snakes", is_log=FALSE)
 p 
@@
 title = "Wrong1sim: Difference Between Phenotypes (Snakes-Newts)"
-p = differnce_graph(files, mean_mean_dif, sd_mean_dif, title, is_log=FALSE)
+p = differnce_graph(files, mean_mean_dif, sd_mean_dif, min_difference_1, max_difference_1, title, is_log=FALSE)
 
@@
 title = "1sim: Difference Between Phenotypes (Snakes-Newts)"
-p = differnce_graph(files, mean_mean_dif, sd_mean_dif, title, is_log=FALSE)
-
+p = differnce_graph(files, mean_mean_dif, sd_mean_dif, min_difference_1, max_difference_1, title, is_log=FALSE)
 p 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=gen)) +
-  xlim(0, 1000)+
-  #ylim(0, true_max_3)+
-  #scale_y_continuous(trans=log10_trans(), limits=c(0,true_max_3))+
-  #scale_y_log10()+
-  scale_y_log10(limits=c(0.001,true_max_3))+
-  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
-  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
-  ggtitle("2sims: Phenotype Measurements for Newts and Snakes") +
-  xlab("Generation") + ylab("Average Phenotypes  (Log)")+
-  theme_bw()
+# better limit
+title = "2sim: Phenotype Measurements for Newts and Snake"
+q = phenotype_graph(files, my_mean, my_sd, title, is_log = TRUE)
+p = phenotype_graph(files, my_mean, my_sd, title)
+q
+p
 
-for (current_file in files){
-  #print(current_file)
-
-  file <- read.table(current_file, header = TRUE)
-  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
-  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
-
- p <- p +
-  geom_line(data=file, aes(y = as.numeric(Newt_mean_Pheno)), color = "darkred",na.rm=TRUE) + 
-  geom_line(data=file, aes(y = as.numeric(Snake_mean_Pheno)), color="steelblue", linetype="twodash", na.rm=TRUE) 
-  #Sys.sleep(2) na.rm=TRUE
-
-}
-
-p 
 ```
@@
 files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=gen)) +
-  xlim(0, 1000)+
-  #ylim(min_difference, max_difference)+
-  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
-  #scale_y_log10()+
-  scale_y_log10(limits=c(min_difference_3, max_difference_3))+
-  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
-  ggtitle("2sims: Difference Between Phenotypes (Snakes-Newts)") +
-  xlab("Generation") + ylab("Average Difference (Log)")+
-  theme_bw()
 
-for (current_file in files){
-  #print(current_file)
-
-  file <- read.table(current_file, header = TRUE)
-  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
-  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
-  file <- file[complete.cases(file), ]
-  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
-  file$mean_dif[file$mean_dif == 0] <- 0.01
-  file$pos <- TRUE
-  file$pos[file$mean_dif < 0] <- FALSE
-
- p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
-  #Sys.sleep(2) na.rm=TRUE
- # color = "mediumseagreen"
-
-}
+title = "2sim: Difference Between Phenotypes (Snakes-Newts)"
+p = differnce_graph(files, mean_mean_dif, sd_mean_dif, min_difference_1, max_difference_1, title, is_log=TRUE)
 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=1:144)) +
-  xlim(0, 145)+
-  scale_y_log10()+
-  geom_point(aes(x = 1, y = as.numeric(Newt_mean_Pheno[1])), color = darken("darkred")) +
-  geom_point(aes(x = 1, y = as.numeric(Newt_mean_Pheno[50])), color = lighten("darkred")) +
-  geom_point(aes(x = 1, y = as.numeric(Snake_mean_Pheno[1])), color = darken("steelblue")) +
-  geom_point(aes(x = 1, y = as.numeric(Snake_mean_Pheno[50])), color = lighten("steelblue")) +
-  ggtitle("2sim: Phenotype Change") +
-  xlab("Simulation number") + ylab("Phenotype  (Log)")+
-  theme_bw()
-i=1
-for (current_file in files){
 
-  file <- read.table(current_file, header = TRUE)
-  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
-  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
-  file <- file[complete.cases(file), ]
- p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color = darken("darkred")) +
-   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color = darken("steelblue")) +
-  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color = lighten("steelblue"))
- i = i+1
-}
+title = "2sim: Phenotype Change"
+p=phenotype_change_graph(files, my_mean, my_sd, title, is_log=TRUE)
 
@@
 files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
-file1 <- read.table(files[1], header = TRUE)
-p <- ggplot(file1, aes(x=as.numeric(Newt_mean_Pheno))) +
-  #ylim(0, true_max_1)+
-  geom_line(aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred") + 
-  ggtitle("2sims: Newt trasnformed vs un-trasformed") +
-  xlab("Trasnformed") + ylab("Untransformed")+
-  theme_bw()
-q <- ggplot(file1, aes(x=as.numeric(Snake_mean_Pheno))) +
-  #ylim(0, true_max_1)+
-  geom_line(aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color = "steelblue") + 
-  ggtitle("2sims: Newt trasnformed vs un-trasformed") +
-  xlab("Trasnformed") + ylab("Untransformed")+
-  theme_bw()
 
-for (current_file in files){
-  #print(current_file)
-  file <- read.table(current_file, header = TRUE)
-  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
-  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
-  file <- file[complete.cases(file), ]
-  #print(file$Newt_mean_Pheno)
-  #print(exp(file$Newt_mean_Pheno/10))
-  #print(log(as.numeric(file$Newt_mean_Pheno))*10)
-  file <- read.table(current_file, header = TRUE)
- p <- p + geom_line(data=file, aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred",na.rm = TRUE)
+title1 = "1som: Newt trasnformed vs un-trasformed"
+title2 = "g1sim: Snake trasnformed vs un-trasformed"
+graph = untrasform(files, my_mean, my_sd, title1, title2, is_log=FALSE)
+graph[1]
+graph[2]
 
- q <- q + geom_line(data=file, aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color="steelblue", linetype="twodash", na.rm = FALSE)
-}
-
-p
-q
+#p
+#q
 

### 2021-07-12 graphs_newt_snakes/fig_1000.Rmd
I am begining to write about the 12 start simulations. I had to re run some things on the cluster because of some naaming probleams, but I think It will be all good in a bit.

@@
 ```
+
+# The 12 Starting Points Experiment!
+
+In the above few experiments I noticed that the newts seemed to start out with a higher phenotype potentially leading to a co-evolution advantage.
+Is there a change in the phenotypes due to the interaction in such a short time and would this "head-start" impact it?
+
+Also the 2 different simulations experiment was too chaotic to really see if there was any co-evolution going on so I decided to run one last set of simulations which I call the 12 starting points.
+
+In this experiment there are 12 msprime simulations where both newts and snakes have the same parameters so that they have about the same standing genetic variance. Here are the starting points:
+
+```{r 12 starting point tables, echo=FALSE}
+
+starting_points <- read.csv("~/Desktop/Coevo/data/slimtestvarables_short.csv", header = TRUE)
+knitr::kable(starting_points, digits = 20)
+
+```
+
+I then ran SliM simulations with the same values from the 1 simulation experiment.
+
+I think the best way to view the output will be by looking at all the results but separated by which trial it belongs to.
+I need to think a bit more oh how separating them will work, but I think it will have to be by name.
+Well I made a mistake and am currently rerunning the experiment.
+I guess we will have to see what happens

### 2021-07-13 graphs_newt_snakes/fig_1000.Rmd
Just added the 12 starting point figures. Some of them look really cool. Need to think more about what they mean. Also made a html file

@@
 
-# Makeing of the Figure
-Loop through the files and find the max and min of each of the species phenotypes
-Then set up a graph with the average phenotype
+# The Functions
 
-This section of code loops though the files and finds the maximum and minumum pheotypes of newts and snakes.
-and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time
+I made functions to collect data and make figures for all of the simulations that I run.
+The data generator will take a list of files and find things like max, min, mean and sd.
+The functions that creates the figures will usually take a list of files, a mean, sd and title.
+These functions will loop through the list of files and return the specific figure.
+On some there is also the option to log the y axis.
 
@@
   file$pos[file$mean_dif < 0] <- "Newt"
-  file$pos[file$mean_dif ==  0.01] <- "Equal"
+  file$pos[file$mean_dif ==  0.01] <- "ZEqual"
 
@@
    geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color = darken("steelblue")) +
-  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color = lighten("steelblue"))
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color = lighten("steelblue"))+
+  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1), size = 0.3, arrow = arrow(length = unit(0.5, "cm")), color="darkred")+
+   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1), size = 0.3, arrow = arrow(length = unit(0.5, "cm")), color="steelblue")
+
  i = i+1
@@
 ```
+
+# Data Collection and Making of the Figure
+
+Loop through the files and find the max and min of each of the species phenotypes
+Then set up a graph with the average phenotype:
 
@@
 
-## Difference between snake and newt pheotypes
+## Difference Between Snake and Newt Pheotypes
 
 This figure represents the difference between the snake and the newt phenotype.
-The pink lines indicate that the newt is more toxit than the snakes, while the blue line indicates that the snakes are more resitant than the newts
+The pink lines indicate that the newt is more toxic than the snakes, while the blue line indicates that the snakes are more resistant than the newts.
+Sometime there are neutral cases and the colors get mixed, but i have plans to fix this and make the figure better overall (7/13/2021).
 
@@
 Essentially, asking if the phenotypes of the newts and snakes changed over 1000 generations?
+I changed these points into arrows to show the direction of phenotype change.
 
@@
 
-## Trasforming the phenotypes back
+## Trasforming the Phenotypes Back
 
@@
 
-# The Correct Experiment
+# The Correct Experiment (Known as 1 Sim)
 
@@
 Again I looped through the files and find the max and min of each of the species pheotypes
-Then set up a graph with the average pheotypes over 1000 generations (red line for newts blue linesfor snakes).
+Then set up a graph with the average pheotypes over 1000 generations (red line for newts blue lines for snakes).
 
@@
 
-```{r data 1 msprime photype graph, echo=FALSE}
+```{r data 1 msprime data, echo=FALSE}
 files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
@@
 
-```{r data 1 msprime dif pheno graph, echo=FALSE}
+```{r data 1 msprime pheno graph, echo=FALSE}
 
@@
 title = "1sim: Phenotype Measurements for Newts and Snake"
-q = phenotype_graph(files, my_mean, my_sd, title, is_log = TRUE)
 p = phenotype_graph(files, my_mean, my_sd, title)
-q
 p 
@@
 
-```{r data from multiple msprime, echo=FALSE}
+```{r 1sim differences, echo=FALSE}
 
@@
 # Expanded Experiment 2sims:
-This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked. I ran 144 SLiM simulations & MSprime with different parameters values.
+
+This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked. I ran 143 SLiM simulations & MSprime with different parameters values.
 
@@
 ```
-some of these values are in quotes, why?
 
@@
 ```
+
 ## How much did the phenotypes of newts and snakes change over 1000 generations
@@
 
-#p
-#q
-
 ```
@@
 I guess we will have to see what happens
+
+```{r 12 points data collection, echo=FALSE}
+
+print("------------------------------------------------------------")
+print("                         TRIAL 1                            ")
+print("------------------------------------------------------------")
+
+files_1 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_1_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_1)
+
+newt_max_pheno_1_1 = out[1]
+snake_max_pheno_1_1 = out[2]
+newt_min_pheno_1_1  = out[3]
+snake_min_pheno_1_1 = out[4]
+true_max_1_1 = out[5]
+true_min_1_1 = out[6]
+min_difference_1_1 = out[7]
+max_difference_1_1 = out[8]
+my_mean_1 = out[9]
+my_sd_1 = out[10]
+mean_mean_dif_1 = out[11]
+sd_mean_dif_1 = out[12]
+
+print(paste0("Newt max pheno trial 1: ", newt_max_pheno_1_1))
+print(paste0("Snake max phenot trial 1: ", snake_max_pheno_1_1))
+print(paste0("Newt min pheno trial 1: ", newt_min_pheno_1_1))
+print(paste0("Snake min Pheno trial 1: ", snake_min_pheno_1_1))
+print(paste0("Mean of combined snake and newt trial 1: ", my_mean_1))
+print(paste0("Sd of combined snake and newt trial 1: ", my_sd_1))
+print(paste0("Mean of the mean difference trial 1: ", mean_mean_dif_1))
+print(paste0("SD of the mean difference trial 1: ", sd_mean_dif_1))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 2                            ")
+print("------------------------------------------------------------")
+
+files_2 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_2_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_2)
+
+newt_max_pheno_1_2 = out[1]
+snake_max_pheno_1_2 = out[2]
+newt_min_pheno_1_2  = out[3]
+snake_min_pheno_1_2 = out[4]
+true_max_1_2 = out[5]
+true_min_1_2 = out[6]
+min_difference_1_2 = out[7]
+max_difference_1_2 = out[8]
+my_mean_2 = out[9]
+my_sd_2 = out[10]
+mean_mean_dif_2 = out[11]
+sd_mean_dif_2 = out[12]
+
+print(paste0("Newt max pheno trial 2: ", newt_max_pheno_1_2))
+print(paste0("Snake max phenot trial 2: ", snake_max_pheno_1_2))
+print(paste0("Newt min pheno trial 2: ", newt_min_pheno_1_2))
+print(paste0("Snake min Pheno trial 2: ", snake_min_pheno_1_2))
+print(paste0("Mean of combined snake and newt trial 2: ", my_mean_2))
+print(paste0("Sd of combined snake and newt trial 2: ", my_sd_2))
+print(paste0("Mean of the mean difference trial 2: ", mean_mean_dif_2))
+print(paste0("SD of the mean difference trial 2: ", sd_mean_dif_2))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 3                            ")
+print("------------------------------------------------------------")
+
+files_3 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_3_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_3)
+
+newt_max_pheno_1_3 = out[1]
+snake_max_pheno_1_3 = out[2]
+newt_min_pheno_1_3  = out[3]
+snake_min_pheno_1_3 = out[4]
+true_max_1_3 = out[5]
+true_min_1_3 = out[6]
+min_difference_1_3 = out[7]
+max_difference_1_3 = out[8]
+my_mean_3 = out[9]
+my_sd_3 = out[10]
+mean_mean_dif_3 = out[11]
+sd_mean_dif_3 = out[12]
+
+print(paste0("Newt max pheno trial 3: ", newt_max_pheno_1_3))
+print(paste0("Snake max phenot trial 3: ", snake_max_pheno_1_3))
+print(paste0("Newt min pheno trial 3: ", newt_min_pheno_1_3))
+print(paste0("Snake min Pheno trial 3: ", snake_min_pheno_1_3))
+print(paste0("Mean of combined snake and newt trial 3: ", my_mean_3))
+print(paste0("Sd of combined snake and newt trial 3: ", my_sd_3))
+print(paste0("Mean of the mean difference trial 3: ", mean_mean_dif_3))
+print(paste0("SD of the mean difference trial 3: ", sd_mean_dif_3))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 4                            ")
+print("------------------------------------------------------------")
+
+files_4 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_4_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_4)
+
+newt_max_pheno_1_4 = out[1]
+snake_max_pheno_1_4 = out[2]
+newt_min_pheno_1_4  = out[3]
+snake_min_pheno_1_4 = out[4]
+true_max_1_4 = out[5]
+true_min_1_4 = out[6]
+min_difference_1_4 = out[7]
+max_difference_1_4 = out[8]
+my_mean_4 = out[9]
+my_sd_4 = out[10]
+mean_mean_dif_4 = out[11]
+sd_mean_dif_4 = out[12]
+
+print(paste0("Newt max pheno trial 4: ", newt_max_pheno_1_4))
+print(paste0("Snake max phenot trial 4: ", snake_max_pheno_1_4))
+print(paste0("Newt min pheno trial 4: ", newt_min_pheno_1_4))
+print(paste0("Snake min Pheno trial 4: ", snake_min_pheno_1_4))
+print(paste0("Mean of combined snake and newt trial 4: ", my_mean_4))
+print(paste0("Sd of combined snake and newt trial 4: ", my_sd_4))
+print(paste0("Mean of the mean difference trial 4: ", mean_mean_dif_4))
+print(paste0("SD of the mean difference trial 4: ", sd_mean_dif_4))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 5                            ")
+print("------------------------------------------------------------")
+
+files_5 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_5_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_5)
+
+newt_max_pheno_1_5 = out[1]
+snake_max_pheno_1_5 = out[2]
+newt_min_pheno_1_5  = out[3]
+snake_min_pheno_1_5 = out[4]
+true_max_1_5 = out[5]
+true_min_1_5 = out[6]
+min_difference_1_5 = out[7]
+max_difference_1_5 = out[8]
+my_mean_5 = out[9]
+my_sd_5 = out[10]
+mean_mean_dif_5 = out[11]
+sd_mean_dif_5 = out[12]
+
+print(paste0("Newt max pheno trial 5: ", newt_max_pheno_1_5))
+print(paste0("Snake max phenot trial 5: ", snake_max_pheno_1_5))
+print(paste0("Newt min pheno trial 5: ", newt_min_pheno_1_5))
+print(paste0("Snake min Pheno trial 5: ", snake_min_pheno_1_5))
+print(paste0("Mean of combined snake and newt trial 5: ", my_mean_5))
+print(paste0("Sd of combined snake and newt trial 5: ", my_sd_5))
+print(paste0("Mean of the mean difference trial 5: ", mean_mean_dif_5))
+print(paste0("SD of the mean difference trial 5: ", sd_mean_dif_5))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 6                            ")
+print("------------------------------------------------------------")
+
+files_6 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_6_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_6)
+
+newt_max_pheno_1_6 = out[1]
+snake_max_pheno_1_6 = out[2]
+newt_min_pheno_1_6  = out[3]
+snake_min_pheno_1_6 = out[4]
+true_max_1_6 = out[5]
+true_min_1_6 = out[6]
+min_difference_1_6 = out[7]
+max_difference_1_6 = out[8]
+my_mean_6 = out[9]
+my_sd_6 = out[10]
+mean_mean_dif_6 = out[11]
+sd_mean_dif_6 = out[12]
+
+print(paste0("Newt max pheno trial 6: ", newt_max_pheno_1_6))
+print(paste0("Snake max pheno trial 6: ", snake_max_pheno_1_6))
+print(paste0("Newt min pheno trial 6: ", newt_min_pheno_1_6))
+print(paste0("Snake min Pheno  trial 6: ", snake_min_pheno_1_6))
+print(paste0("Mean of combined snake and newt trial 6: ", my_mean_6))
+print(paste0("Sd of combined snake and newt trial 6: ", my_sd_6))
+print(paste0("Mean of the mean difference trial 6: ", mean_mean_dif_6))
+print(paste0("SD of the mean difference trial 6: ", sd_mean_dif_6))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 7                            ")
+print("------------------------------------------------------------")
+
+files_7 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_7_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_7)
+
+newt_max_pheno_1_7 = out[1]
+snake_max_pheno_1_7 = out[2]
+newt_min_pheno_1_7  = out[3]
+snake_min_pheno_1_7 = out[4]
+true_max_1_7 = out[5]
+true_min_1_7 = out[6]
+min_difference_1_7 = out[7]
+max_difference_1_7 = out[8]
+my_mean_7 = out[9]
+my_sd_7 = out[10]
+mean_mean_dif_7 = out[11]
+sd_mean_dif_7 = out[12]
+
+print(paste0("Newt max pheno trial 7: ", newt_max_pheno_1_7))
+print(paste0("Snake max phenot trial 7: ", snake_max_pheno_1_7))
+print(paste0("Newt min pheno trial 7: ", newt_min_pheno_1_7))
+print(paste0("Snake min Pheno trial 7: ", snake_min_pheno_1_7))
+print(paste0("Mean of combined snake and newt trial 7: ", my_mean_7))
+print(paste0("Sd of combined snake and newt trial 7: ", my_sd_7))
+print(paste0("Mean of the mean difference trial 7: ", mean_mean_dif_7))
+print(paste0("SD of the mean difference trial 7: ", sd_mean_dif_7))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 8                            ")
+print("------------------------------------------------------------")
+
+files_8 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_8_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_8)
+
+newt_max_pheno_1_8 = out[1]
+snake_max_pheno_1_8 = out[2]
+newt_min_pheno_1_8  = out[3]
+snake_min_pheno_1_8 = out[4]
+true_max_1_8 = out[5]
+true_min_1_8 = out[6]
+min_difference_1_8 = out[7]
+max_difference_1_8 = out[8]
+my_mean_8 = out[9]
+my_sd_8 = out[10]
+mean_mean_dif_8 = out[11]
+sd_mean_dif_8 = out[12]
+
+print(paste0("Newt max pheno trial 8: ", newt_max_pheno_1_8))
+print(paste0("Snake max phenot trial 8: ", snake_max_pheno_1_8))
+print(paste0("Newt min pheno trial 8: ", newt_min_pheno_1_8))
+print(paste0("Snake min Pheno trial 8: ", snake_min_pheno_1_8))
+print(paste0("Mean of combined snake and newt trial 8: ", my_mean_8))
+print(paste0("Sd of combined snake and newt trial 8: ", my_sd_8))
+print(paste0("Mean of the mean difference trial 8: ", mean_mean_dif_8))
+print(paste0("SD of the mean difference trial 8: ", sd_mean_dif_8))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 9                            ")
+print("------------------------------------------------------------")
+
+files_9 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_9", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_9)
+
+newt_max_pheno_1_9 = out[1]
+snake_max_pheno_1_9 = out[2]
+newt_min_pheno_1_9  = out[3]
+snake_min_pheno_1_9 = out[4]
+true_max_1_9 = out[5]
+true_min_1_9 = out[6]
+min_difference_1_9 = out[7]
+max_difference_1_9 = out[8]
+my_mean_9 = out[9]
+my_sd_9 = out[10]
+mean_mean_dif_9 = out[11]
+sd_mean_dif_9 = out[12]
+
+print(paste0("Newt max pheno trial 9: ", newt_max_pheno_1_9))
+print(paste0("Snake max phenot trial 9: ", snake_max_pheno_1_9))
+print(paste0("Newt min pheno trial 9: ", newt_min_pheno_1_9))
+print(paste0("Snake min Pheno trial 9: ", snake_min_pheno_1_9))
+print(paste0("Mean of combined snake and newt trial 9: ", my_mean_9))
+print(paste0("Sd of combined snake and newt trial 9: ", my_sd_9))
+print(paste0("Mean of the mean difference trial 9: ", mean_mean_dif_9))
+print(paste0("SD of the mean difference trial 9: ", sd_mean_dif_9))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 10                           ")
+print("------------------------------------------------------------")
+
+files_10 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_10_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_10)
+
+newt_max_pheno_1_10 = out[1]
+snake_max_pheno_1_10 = out[2]
+newt_min_pheno_1_10  = out[3]
+snake_min_pheno_1_10 = out[4]
+true_max_1_10 = out[5]
+true_min_1_10 = out[6]
+min_difference_1_10 = out[7]
+max_difference_1_10 = out[8]
+my_mean_10 = out[9]
+my_sd_10 = out[10]
+mean_mean_dif_10 = out[11]
+sd_mean_dif_10 = out[12]
+
+print(paste0("Newt max pheno trial 10: ", newt_max_pheno_1_10))
+print(paste0("Snake max phenot trial 10: ", snake_max_pheno_1_10))
+print(paste0("Newt min pheno trial 10: ", newt_min_pheno_1_10))
+print(paste0("Snake min Pheno trial 10: ", snake_min_pheno_1_10))
+print(paste0("Mean of combined snake and newt trial 10: ", my_mean_10))
+print(paste0("Sd of combined snake and newt trial 10: ", my_sd_10))
+print(paste0("Mean of the mean difference trial 10: ", mean_mean_dif_10))
+print(paste0("SD of the mean difference trial 10: ", sd_mean_dif_10))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 11                          ")
+print("------------------------------------------------------------")
+
+files_11 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_11_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_11)
+
+newt_max_pheno_1_11 = out[1]
+snake_max_pheno_1_11 = out[2]
+newt_min_pheno_1_11  = out[3]
+snake_min_pheno_1_11 = out[4]
+true_max_1_11 = out[5]
+true_min_1_11 = out[6]
+min_difference_1_11 = out[7]
+max_difference_1_11 = out[8]
+my_mean_11 = out[9]
+my_sd_11 = out[10]
+mean_mean_dif_11 = out[11]
+sd_mean_dif_11 = out[12]
+
+print(paste0("Newt max pheno trial 11: ", newt_max_pheno_1_11))
+print(paste0("Snake max phenot trial 11: ", snake_max_pheno_1_11))
+print(paste0("Newt min pheno trial 11: ", newt_min_pheno_1_11))
+print(paste0("Snake min Pheno trial 11: ", snake_min_pheno_1_11))
+print(paste0("Mean of combined snake and newt trial 11: ", my_mean_11))
+print(paste0("Sd of combined snake and newt trial 11: ", my_sd_11))
+print(paste0("Mean of the mean difference trial 11: ", mean_mean_dif_11))
+print(paste0("SD of the mean difference trial 11: ", sd_mean_dif_11))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 12                           ")
+print("------------------------------------------------------------")
+
+files_12 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_12_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_12)
+
+newt_max_pheno_1_12 = out[1]
+snake_max_pheno_1_12 = out[2]
+newt_min_pheno_1_12  = out[3]
+snake_min_pheno_1_12 = out[4]
+true_max_1_12 = out[5]
+true_min_1_12 = out[6]
+min_difference_1_12 = out[7]
+max_difference_1_12 = out[8]
+my_mean_12 = out[9]
+my_sd_12 = out[10]
+mean_mean_dif_12 = out[11]
+sd_mean_dif_12 = out[12]
+
+print(paste0("Newt max pheno trial 12: ", newt_max_pheno_1_12))
+print(paste0("Snake max pheno trial 12: ", snake_max_pheno_1_12))
+print(paste0("Newt min pheno trial 12: ", newt_min_pheno_1_12))
+print(paste0("Snake min Pheno trial 12: ", snake_min_pheno_1_12))
+print(paste0("Mean of combined snake and newt trial 12: ", my_mean_12))
+print(paste0("Sd of combined snake and newt trial 12: ", my_sd_12))
+print(paste0("Mean of the mean difference trial 12: ", mean_mean_dif_12))
+print(paste0("SD of the mean difference trial 12: ", sd_mean_dif_12))
+
+```
+
+```{r phenotype graph 12 points, echo=FALSE}
+
+title = "Trial 1 Phenotype Measurements for Newts and Snake"
+p_1 = phenotype_graph(files_1, my_mean_1, my_sd_1, title)
+#p_1
+
+title = "Trial 2 Phenotype Measurements for Newts and Snake"
+p_2 = phenotype_graph(files_2, my_mean_2, my_sd_2, title)
+#p_2
+
+title = "Trial 3 Phenotype Measurements for Newts and Snake Trial 3"
+p_3 = phenotype_graph(files_3, my_mean_3, my_sd_3, title)
+#p_3
+
+title = "Trial 4 Phenotype Measurements for Newts and Snake"
+p_4 = phenotype_graph(files_4, my_mean_4, my_sd_4, title)
+#p_4
+
+grid.arrange(p_1, p_2, p_3, p_4, nrow = 2)
+
+title = "Trial 5 Phenotype Measurements for Newts and Snake"
+p_5 = phenotype_graph(files_5, my_mean_5, my_sd_5, title)
+#p_5
+
+title = "Trial 6 Phenotype Measurements for Newts and Snake"
+p_6 = phenotype_graph(files_6, my_mean_6, my_sd_6, title)
+#p_6
+
+title = "Trial 7 Phenotype Measurements for Newts and Snake"
+p_7 = phenotype_graph(files_7, my_mean_7, my_sd_7, title)
+#p_7
+
+title = "Trial 8 Phenotype Measurements for Newts and Snake"
+p_8 = phenotype_graph(files_8, my_mean_8, my_sd_8, title)
+#p_8
+
+grid.arrange(p_5, p_6, p_7, p_8, nrow=2)
+
+title = "Trial 9 Phenotype Measurements for Newts and Snake"
+p_9 = phenotype_graph(files_9, my_mean_9, my_sd_9, title)
+#p_9
+
+title = "Trial 10 Phenotype Measurements for Newts and Snake"
+p_10 = phenotype_graph(files_10, my_mean_10, my_sd_10, title)
+#p_10
+
+title = "Trial 11 Phenotype Measurements for Newts and Snake"
+p_11 = phenotype_graph(files_11, my_mean_11, my_sd_11, title)
+#p_11
+
+title = "Trial 12  Phenotype Measurements for Newts and Snake"
+p_12 = phenotype_graph(files_12, my_mean_12, my_sd_12, title)
+#p_12
+
+grid.arrange(p_9, p_10, p_11, p_12, nrow=2)
+
+```
+
+## Difference between snake and newt pheotypes
+
+```{r 12 sim pheno dif, echo=FALSE}
+
+title = "Trial 1: Difference Between Phenotypes (Snakes-Newts)"
+d_1 = differnce_graph(files_1, mean_mean_dif_1, sd_mean_dif_1, min_difference_1_1, max_difference_1_1, title)
+
+title = "Trial 2: Difference Between Phenotypes (Snakes-Newts)"
+d_2 = differnce_graph(files_2, mean_mean_dif_2, sd_mean_dif_2, min_difference_1_2, max_difference_1_2, title)
+
+title = "Trial 3: Difference Between Phenotypes (Snakes-Newts)"
+d_3 = differnce_graph(files_3, mean_mean_dif_3, sd_mean_dif_3, min_difference_1_3, max_difference_1_3, title)
+
+title = "Trial 4: Difference Between Phenotypes (Snakes-Newts)"
+d_4 = differnce_graph(files_4, mean_mean_dif_4, sd_mean_dif_4, min_difference_1_4, max_difference_1_4, title)
+
+grid.arrange(d_1, d_2, d_3, d_4, nrow = 2)
+
+title = "Trial 5: Difference Between Phenotypes (Snakes-Newts)"
+d_5 = differnce_graph(files_5, mean_mean_dif_5, sd_mean_dif_5, min_difference_1_5, max_difference_1_5, title)
+
+title = "Trial 6: Difference Between Phenotypes (Snakes-Newts)"
+d_6 = differnce_graph(files_6, mean_mean_dif_6, sd_mean_dif_6, min_difference_1_6, max_difference_1_6, title)
+
+title = "Trial 7: Difference Between Phenotypes (Snakes-Newts)"
+d_7 = differnce_graph(files_7, mean_mean_dif_7, sd_mean_dif_7, min_difference_1_7, max_difference_1_7, title)
+
+title = "Trial 8: Difference Between Phenotypes (Snakes-Newts)"
+d_8 = differnce_graph(files_8, mean_mean_dif_8, sd_mean_dif_8, min_difference_1_8, max_difference_1_8, title)
+
+grid.arrange(d_5, d_6, d_7, d_8, nrow = 2)
+
+title = "Trial 9: Difference Between Phenotypes (Snakes-Newts)"
+d_9 = differnce_graph(files_9, mean_mean_dif_9, sd_mean_dif_9, min_difference_1_9, max_difference_1_9, title)
+
+title = "Trial 10: Difference Between Phenotypes (Snakes-Newts)"
+d_10 = differnce_graph(files_10, mean_mean_dif_10, sd_mean_dif_10, min_difference_1_10, max_difference_1_10, title)
+
+title = "Trial 11: Difference Between Phenotypes (Snakes-Newts)"
+d_11 = differnce_graph(files_11, mean_mean_dif_11, sd_mean_dif_11, min_difference_1_11, max_difference_1_11, title)
+
+title = "Trial 12: Difference Between Phenotypes (Snakes-Newts)"
+d_12 = differnce_graph(files_12, mean_mean_dif_12, sd_mean_dif_12, min_difference_1_12, max_difference_1_12, title)
+
+grid.arrange(d_9, d_10, d_11, d_12, nrow = 2)
+
+```
+
+## How much did the phenotypes of newts and snakes change over 1000 generations
+
+```{r 12 sim pheno change, echo=FALSE}
+
+title = "Trial 1 12sim: Phenotype Change"
+c_1=phenotype_change_graph(files_1, my_mean_1, my_sd_1, title)
+
+title = "Trial 2 12sim: Phenotype Change"
+c_2=phenotype_change_graph(files_2, my_mean_2, my_sd_2, title)
+
+title = "Trial 3 12sim: Phenotype Change"
+c_3=phenotype_change_graph(files_3, my_mean_3, my_sd_3, title)
+
+title = "Trial 4 12sim: Phenotype Change"
+c_4=phenotype_change_graph(files_4, my_mean_4, my_sd_4, title)
+
+grid.arrange(c_1, c_2, c_3, c_4, nrow = 2)
+
+title = "Trial 5 12sim: Phenotype Change"
+c_5=phenotype_change_graph(files_5, my_mean_5, my_sd_5, title)
+
+title = "Trial 6 12sim: Phenotype Change"
+c_6=phenotype_change_graph(files_6, my_mean_6, my_sd_6, title)
+
+title = "Trial 7 12sim: Phenotype Change"
+c_7=phenotype_change_graph(files_7, my_mean_7, my_sd_7, title)
+
+title = "Trial 8 12sim: Phenotype Change"
+c_8=phenotype_change_graph(files_8, my_mean_8, my_sd_8, title)
+
+grid.arrange(c_5, c_6, c_7, c_8, nrow = 2)
+
+title = "Trial 9 12sim: Phenotype Change"
+c_9=phenotype_change_graph(files_9, my_mean_9, my_sd_9, title)
+
+title = "Trial 10 12sim: Phenotype Change"
+c_10=phenotype_change_graph(files_10, my_mean_10, my_sd_10, title)
+
+title = "Trial 11 12sim: Phenotype Change"
+c_11=phenotype_change_graph(files_11, my_mean_11, my_sd_11, title)
+
+title = "Trial 12 12sim: Phenotype Change"
+c_12=phenotype_change_graph(files_12, my_mean_12, my_sd_12, title)
+
+grid.arrange(c_9, c_10, c_11, c_12, nrow = 2)
+
+```
+
+## Trasforming the phenotypes back
+
+```{r 12 point trasformation , echo=FALSE}
+
+title1 = "Trial 1: Newt trasnformed vs un-trasformed"
+title2 = "Trial 1: Snake trasnformed vs un-trasformed"
+graph_1 = untrasform(files_1, my_mean_1, my_sd_1, title1, title2, is_log=FALSE)
+
+title1 = "Trial 2: Newt trasnformed vs un-trasformed"
+title2 = "Trial 2: Snake trasnformed vs un-trasformed"
+graph_2 = untrasform(files_2, my_mean_2, my_sd_2, title1, title2, is_log=FALSE)
+
+title1 = "Trial 3: Newt trasnformed vs un-trasformed"
+title2 = "Trial 3: Snake trasnformed vs un-trasformed"
+graph_3 = untrasform(files_3, my_mean_3, my_sd_3, title1, title2, is_log=FALSE)
+
+title1 = "Trial 4: Newt trasnformed vs un-trasformed"
+title2 = "Trial 4: Snake trasnformed vs un-trasformed"
+graph_4 = untrasform(files_4, my_mean_4, my_sd_4, title1, title2, is_log=FALSE)
+
+grid.arrange(graph_1[[1]], graph_1[[2]], graph_2[[1]], graph_2[[2]], graph_3[[1]], graph_3[[2]], graph_4[[1]], graph_4[[2]], nrow = 4)
+
+title1 = "Trial 5: Newt trasnformed vs un-trasformed"
+title2 = "Trial 5: Snake trasnformed vs un-trasformed"
+graph_5 = untrasform(files_5, my_mean_5, my_sd_5, title1, title2, is_log=FALSE)
+
+title1 = "Trial 6: Newt trasnformed vs un-trasformed"
+title2 = "Trial 6: Snake trasnformed vs un-trasformed"
+graph_6 = untrasform(files_6, my_mean_6, my_sd_6, title1, title2, is_log=FALSE)
+
+title1 = "Trial 7: Newt trasnformed vs un-trasformed"
+title2 = "Trial 7: Snake trasnformed vs un-trasformed"
+graph_7 = untrasform(files_7, my_mean_7, my_sd_7, title1, title2, is_log=FALSE)
+
+title1 = "Trial 8: Newt trasnformed vs un-trasformed"
+title2 = "Trial 8: Snake trasnformed vs un-trasformed"
+graph_8 = untrasform(files_8, my_mean_8, my_sd_8, title1, title2, is_log=FALSE)
+
+grid.arrange(graph_5[[1]], graph_5[[2]], graph_6[[1]], graph_6[[2]], graph_7[[1]], graph_7[[2]], graph_8[[1]], graph_8[[2]], nrow = 4)
+
+title1 = "Trial 9: Newt trasnformed vs un-trasformed"
+title2 = "Trial 9: Snake trasnformed vs un-trasformed"
+graph_9 = untrasform(files_9, my_mean_9, my_sd_9, title1, title2, is_log=FALSE)
+
+title1 = "Trial 10: Newt trasnformed vs un-trasformed"
+title2 = "Trial 10: Snake trasnformed vs un-trasformed"
+graph_10 = untrasform(files_10, my_mean_10, my_sd_10, title1, title2, is_log=FALSE)
+
+title1 = "Trial 11: Newt trasnformed vs un-trasformed"
+title2 = "Trial 11: Snake trasnformed vs un-trasformed"
+graph_11 = untrasform(files_11, my_mean_11, my_sd_11, title1, title2, is_log=FALSE)
+
+title1 = "Trial 12: Newt trasnformed vs un-trasformed"
+title2 = "Trial 12: Snake trasnformed vs un-trasformed"
+graph_12 = untrasform(files_12, my_mean_12, my_sd_12, title1, title2, is_log=FALSE)
+
+grid.arrange(graph_9[[1]], graph_9[[2]], graph_10[[1]], graph_10[[2]], graph_11[[1]], graph_11[[2]], graph_12[[1]], graph_12[[2]], nrow = 4)
+
+```

### 2021-07-19 graphs_newt_snakes/fig_1000.Rmd
I updated my explination text file to reflect what i have been working on and how the cluster folders and files now look. I also made a new r markdown file to explore sigma and mu paramiter space.

@@
 My summer 2021 goal is to get the 1 on 1 simulation to run *correctly*. For this to happen I would like the simulation to have:
+
 -Realistic phenotypes (snake 0-3, newt 0-1.5(thoughts 2021?))

### 2021-07-19 graphs_newt_snakes/find_params.Rmd
I updated my explination text file to reflect what i have been working on and how the cluster folders and files now look. I also made a new r markdown file to explore sigma and mu paramiter space.

---
title: "Finding Sigma and Mu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)

#setwd("~/Desktop/Proposal Old Drafts")
```

## This is a r file to explore paramater values for my coevolution simulation

I ran a few experiments in the 1000 generation simulation and discovered that there were some combinations of sigma and mu that created "extreme" phenotypes (but not outside of the mathematical expectations). This markdown will hopefully help me visualize different values of sigma and mu and their resulting phenotypes.

### Math

$$
\text{Population size, } N = 10^4 
$$
$$
\text{Time to most recent comman ancestor, } 2N 
$$
$$
\text{Number of Mutations differ between two, } \sim 4N\mu L
$$
$$
\mu = \text{mutation rate / bp, My simulation } 10^-12 \text{ to } 10^-8
$$
$$
L = \text{sequence length }
$$
$$
\sigma = \text{effect size SD, My simulation } 0.01 \text{ to } 0.5
$$
$$
Var[phenotype] \sim 4N\mu L\sigma^2
$$
$$
SD[phenotype] \sim \sigma \sqrt{4N\mu L} -> \sigma \sqrt{\mu}*2*10^6
$$
$$
\mu = 10^-12 \sigma = 0.01, = 0.02
$$
$$
\mu = 10^-8 \sigma = 0.5, = 100
$$

```{r find sigma and mu, echo=FALSE}

sigma = seq(0.01, 0.5, length.out=100)
mu = seq(10^-12, 10^-8, length.out=100)

mat = mapply(rep, 1:4, 4:1)
my_grid <- as.data.frame(expand.grid(sigma, mu))
my_grid$results = mapply(`*`,sigma*2*10^6,rep(sqrt(mu),each=length(sigma)))

ggplot(my_grid, aes(x = Var1, y=Var2)) +
  geom_point(data=my_grid[my_grid$results <=5, ], aes(x = Var1, y=Var2), col="blue")+
  geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2), col="green")+
  ggtitle("Value Combinations That Might Work") +
  xlab("Sigma") + ylab("Mu")+
  theme_bw()

```

I think it would be cool to draw them as lines (like take the max Mu that would produce the correct phenotype for every sigma value)

```{r max unique values, echo=FALSE}

#2=sigma*sqrt(mu)*2*10^6
y_mu_2 = (2/(sigma*2*10^6))^2
y_mu_5 = (5/(sigma*2*10^6))^2
x_sigma_2 = 2/(sqrt(mu)*2*10^6)
x_sigma_5 = 5/(sqrt(mu)*2*10^6)
ggplot() +
  geom_line(aes(x = sigma, y=y_mu_5), col="blue")+
  geom_line(aes(x = sigma, y=y_mu_2), col="green")+
  geom_line(aes(x = x_sigma_5, y=mu), col="blue")+
  geom_line(aes(x = x_sigma_2, y=mu), col="green")+
  scale_y_log10()+
  #geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2), col="green")+
  ggtitle("Value Combinations That Might Work") +
  xlab("Sigma") + ylab("Mu (log)")+ #xlim(0, 0.6)+
  theme_bw()

```

### 2021-07-20 graphs_newt_snakes/fig_1000.Rmd
Added in the results from Peter sugestion about mutation rate. Now I am looking at the differences.

@@
 ```
+
+# The 12 Starting Points Experiment Redone with Peters SLiM code sugestions!
+
+I was worried about a few confusing parts in the SLiM code that dealt with the mutation rate of newts and snakes (discussed above). Peter suggested:
+newt_mu_rate = 1e-10;
+snake_mu_rate = 1e-11; 
+total_mu_rate = newt_mu_rate + snake_mu_rate:
+initializeMutationRate(total_mut_rate);
+initializeGenomicElementType("g1", c(m1, m2), c(newt_mu_rate, snake_mu_rate));
+
+Extra note: In my code snake_mu_rate is called mu_rate
+
+```{r 12 points redone data collection, echo=FALSE}
+
+print("------------------------------------------------------------")
+print("                         TRIAL 1                            ")
+print("------------------------------------------------------------")
+
+files_1r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_1_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_1r)
+
+newt_max_pheno_1_1r = out[1]
+snake_max_pheno_1_1r = out[2]
+newt_min_pheno_1_1r  = out[3]
+snake_min_pheno_1_1r = out[4]
+true_max_1_1r = out[5]
+true_min_1_1r = out[6]
+min_difference_1_1r = out[7]
+max_difference_1_1r = out[8]
+my_mean_1r = out[9]
+my_sd_1r = out[10]
+mean_mean_dif_1r = out[11]
+sd_mean_dif_1r = out[12]
+
+print(paste0("Newt max pheno trial 1: ", newt_max_pheno_1_1r))
+print(paste0("Snake max phenot trial 1: ", snake_max_pheno_1_1r))
+print(paste0("Newt min pheno trial 1: ", newt_min_pheno_1_1r))
+print(paste0("Snake min Pheno trial 1: ", snake_min_pheno_1_1r))
+print(paste0("Mean of combined snake and newt trial 1: ", my_mean_1r))
+print(paste0("Sd of combined snake and newt trial 1: ", my_sd_1r))
+print(paste0("Mean of the mean difference trial 1: ", mean_mean_dif_1r))
+print(paste0("SD of the mean difference trial 1: ", sd_mean_dif_1r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 2                            ")
+print("------------------------------------------------------------")
+
+files_2r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_2_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_2r)
+
+newt_max_pheno_1_2r = out[1]
+snake_max_pheno_1_2r = out[2]
+newt_min_pheno_1_2r  = out[3]
+snake_min_pheno_1_2r = out[4]
+true_max_1_2r = out[5]
+true_min_1_2r = out[6]
+min_difference_1_2r = out[7]
+max_difference_1_2r = out[8]
+my_mean_2r = out[9]
+my_sd_2r = out[10]
+mean_mean_dif_2r = out[11]
+sd_mean_dif_2r = out[12]
+
+print(paste0("Newt max pheno trial 2: ", newt_max_pheno_1_2r))
+print(paste0("Snake max phenot trial 2: ", snake_max_pheno_1_2r))
+print(paste0("Newt min pheno trial 2: ", newt_min_pheno_1_2r))
+print(paste0("Snake min Pheno trial 2: ", snake_min_pheno_1_2r))
+print(paste0("Mean of combined snake and newt trial 2: ", my_mean_2r))
+print(paste0("Sd of combined snake and newt trial 2: ", my_sd_2r))
+print(paste0("Mean of the mean difference trial 2: ", mean_mean_dif_2r))
+print(paste0("SD of the mean difference trial 2: ", sd_mean_dif_2r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 3                            ")
+print("------------------------------------------------------------")
+
+files_3r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_3_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_3r)
+
+newt_max_pheno_1_3r = out[1]
+snake_max_pheno_1_3r = out[2]
+newt_min_pheno_1_3r  = out[3]
+snake_min_pheno_1_3r = out[4]
+true_max_1_3r = out[5]
+true_min_1_3r = out[6]
+min_difference_1_3r = out[7]
+max_difference_1_3r = out[8]
+my_mean_3r = out[9]
+my_sd_3r = out[10]
+mean_mean_dif_3r = out[11]
+sd_mean_dif_3r = out[12]
+
+print(paste0("Newt max pheno trial 3: ", newt_max_pheno_1_3r))
+print(paste0("Snake max phenot trial 3: ", snake_max_pheno_1_3r))
+print(paste0("Newt min pheno trial 3: ", newt_min_pheno_1_3r))
+print(paste0("Snake min Pheno trial 3: ", snake_min_pheno_1_3r))
+print(paste0("Mean of combined snake and newt trial 3: ", my_mean_3r))
+print(paste0("Sd of combined snake and newt trial 3: ", my_sd_3r))
+print(paste0("Mean of the mean difference trial 3: ", mean_mean_dif_3r))
+print(paste0("SD of the mean difference trial 3: ", sd_mean_dif_3r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 4                            ")
+print("------------------------------------------------------------")
+
+files_4r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_4_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_4r)
+
+newt_max_pheno_1_4r = out[1]
+snake_max_pheno_1_4r = out[2]
+newt_min_pheno_1_4r  = out[3]
+snake_min_pheno_1_4r = out[4]
+true_max_1_4r = out[5]
+true_min_1_4r = out[6]
+min_difference_1_4r = out[7]
+max_difference_1_4r = out[8]
+my_mean_4r = out[9]
+my_sd_4r = out[10]
+mean_mean_dif_4r = out[11]
+sd_mean_dif_4r = out[12]
+
+print(paste0("Newt max pheno trial 4: ", newt_max_pheno_1_4r))
+print(paste0("Snake max phenot trial 4: ", snake_max_pheno_1_4r))
+print(paste0("Newt min pheno trial 4: ", newt_min_pheno_1_4r))
+print(paste0("Snake min Pheno trial 4: ", snake_min_pheno_1_4r))
+print(paste0("Mean of combined snake and newt trial 4: ", my_mean_4r))
+print(paste0("Sd of combined snake and newt trial 4: ", my_sd_4r))
+print(paste0("Mean of the mean difference trial 4: ", mean_mean_dif_4r))
+print(paste0("SD of the mean difference trial 4: ", sd_mean_dif_4r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 5                            ")
+print("------------------------------------------------------------")
+
+files_5r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_5_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_5r)
+
+newt_max_pheno_1_5r = out[1]
+snake_max_pheno_1_5r = out[2]
+newt_min_pheno_1_5r  = out[3]
+snake_min_pheno_1_5r = out[4]
+true_max_1_5r = out[5]
+true_min_1_5r = out[6]
+min_difference_1_5r = out[7]
+max_difference_1_5r = out[8]
+my_mean_5r = out[9]
+my_sd_5r = out[10]
+mean_mean_dif_5r = out[11]
+sd_mean_dif_5r = out[12]
+
+print(paste0("Newt max pheno trial 5: ", newt_max_pheno_1_5r))
+print(paste0("Snake max phenot trial 5: ", snake_max_pheno_1_5r))
+print(paste0("Newt min pheno trial 5: ", newt_min_pheno_1_5r))
+print(paste0("Snake min Pheno trial 5: ", snake_min_pheno_1_5r))
+print(paste0("Mean of combined snake and newt trial 5: ", my_mean_5r))
+print(paste0("Sd of combined snake and newt trial 5: ", my_sd_5r))
+print(paste0("Mean of the mean difference trial 5: ", mean_mean_dif_5r))
+print(paste0("SD of the mean difference trial 5: ", sd_mean_dif_5r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 6                            ")
+print("------------------------------------------------------------")
+
+files_6r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_6_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_6r)
+
+newt_max_pheno_1_6r = out[1]
+snake_max_pheno_1_6r = out[2]
+newt_min_pheno_1_6r  = out[3]
+snake_min_pheno_1_6r = out[4]
+true_max_1_6r = out[5]
+true_min_1_6r = out[6]
+min_difference_1_6r = out[7]
+max_difference_1_6r = out[8]
+my_mean_6r = out[9]
+my_sd_6r = out[10]
+mean_mean_dif_6r = out[11]
+sd_mean_dif_6r = out[12]
+
+print(paste0("Newt max pheno trial 6: ", newt_max_pheno_1_6r))
+print(paste0("Snake max pheno trial 6: ", snake_max_pheno_1_6r))
+print(paste0("Newt min pheno trial 6: ", newt_min_pheno_1_6r))
+print(paste0("Snake min Pheno  trial 6: ", snake_min_pheno_1_6r))
+print(paste0("Mean of combined snake and newt trial 6: ", my_mean_6r))
+print(paste0("Sd of combined snake and newt trial 6: ", my_sd_6r))
+print(paste0("Mean of the mean difference trial 6: ", mean_mean_dif_6r))
+print(paste0("SD of the mean difference trial 6: ", sd_mean_dif_6r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 7                            ")
+print("------------------------------------------------------------")
+
+files_7r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_7_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_7r)
+
+newt_max_pheno_1_7r = out[1]
+snake_max_pheno_1_7r = out[2]
+newt_min_pheno_1_7r  = out[3]
+snake_min_pheno_1_7r = out[4]
+true_max_1_7r = out[5]
+true_min_1_7r = out[6]
+min_difference_1_7r = out[7]
+max_difference_1_7r = out[8]
+my_mean_7r = out[9]
+my_sd_7r = out[10]
+mean_mean_dif_7r = out[11]
+sd_mean_dif_7r = out[12]
+
+print(paste0("Newt max pheno trial 7: ", newt_max_pheno_1_7r))
+print(paste0("Snake max phenot trial 7: ", snake_max_pheno_1_7r))
+print(paste0("Newt min pheno trial 7: ", newt_min_pheno_1_7r))
+print(paste0("Snake min Pheno trial 7: ", snake_min_pheno_1_7r))
+print(paste0("Mean of combined snake and newt trial 7: ", my_mean_7r))
+print(paste0("Sd of combined snake and newt trial 7: ", my_sd_7r))
+print(paste0("Mean of the mean difference trial 7: ", mean_mean_dif_7r))
+print(paste0("SD of the mean difference trial 7: ", sd_mean_dif_7r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 8                            ")
+print("------------------------------------------------------------")
+
+files_8r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_8_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_8r)
+
+newt_max_pheno_1_8r = out[1]
+snake_max_pheno_1_8r = out[2]
+newt_min_pheno_1_8r  = out[3]
+snake_min_pheno_1_8r = out[4]
+true_max_1_8r = out[5]
+true_min_1_8r = out[6]
+min_difference_1_8r = out[7]
+max_difference_1_8r = out[8]
+my_mean_8r = out[9]
+my_sd_8r = out[10]
+mean_mean_dif_8r = out[11]
+sd_mean_dif_8r = out[12]
+
+print(paste0("Newt max pheno trial 8: ", newt_max_pheno_1_8r))
+print(paste0("Snake max phenot trial 8: ", snake_max_pheno_1_8r))
+print(paste0("Newt min pheno trial 8: ", newt_min_pheno_1_8r))
+print(paste0("Snake min Pheno trial 8: ", snake_min_pheno_1_8r))
+print(paste0("Mean of combined snake and newt trial 8: ", my_mean_8r))
+print(paste0("Sd of combined snake and newt trial 8: ", my_sd_8r))
+print(paste0("Mean of the mean difference trial 8: ", mean_mean_dif_8r))
+print(paste0("SD of the mean difference trial 8: ", sd_mean_dif_8r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 9                            ")
+print("------------------------------------------------------------")
+
+files_9r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_9", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_9r)
+
+newt_max_pheno_1_9r = out[1]
+snake_max_pheno_1_9r = out[2]
+newt_min_pheno_1_9r  = out[3]
+snake_min_pheno_1_9r = out[4]
+true_max_1_9r = out[5]
+true_min_1_9r = out[6]
+min_difference_1_9r = out[7]
+max_difference_1_9r = out[8]
+my_mean_9r = out[9]
+my_sd_9r = out[10]
+mean_mean_dif_9r = out[11]
+sd_mean_dif_9r = out[12]
+
+print(paste0("Newt max pheno trial 9: ", newt_max_pheno_1_9r))
+print(paste0("Snake max phenot trial 9: ", snake_max_pheno_1_9r))
+print(paste0("Newt min pheno trial 9: ", newt_min_pheno_1_9r))
+print(paste0("Snake min Pheno trial 9: ", snake_min_pheno_1_9r))
+print(paste0("Mean of combined snake and newt trial 9: ", my_mean_9r))
+print(paste0("Sd of combined snake and newt trial 9: ", my_sd_9r))
+print(paste0("Mean of the mean difference trial 9: ", mean_mean_dif_9r))
+print(paste0("SD of the mean difference trial 9: ", sd_mean_dif_9r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 10                           ")
+print("------------------------------------------------------------")
+
+files_10r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_10_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_10r)
+
+newt_max_pheno_1_10r = out[1]
+snake_max_pheno_1_10r = out[2]
+newt_min_pheno_1_10r  = out[3]
+snake_min_pheno_1_10r = out[4]
+true_max_1_10r = out[5]
+true_min_1_10r = out[6]
+min_difference_1_10r = out[7]
+max_difference_1_10r = out[8]
+my_mean_10r = out[9]
+my_sd_10r = out[10]
+mean_mean_dif_10r = out[11]
+sd_mean_dif_10r = out[12]
+
+print(paste0("Newt max pheno trial 10: ", newt_max_pheno_1_10r))
+print(paste0("Snake max phenot trial 10: ", snake_max_pheno_1_10r))
+print(paste0("Newt min pheno trial 10: ", newt_min_pheno_1_10r))
+print(paste0("Snake min Pheno trial 10: ", snake_min_pheno_1_10r))
+print(paste0("Mean of combined snake and newt trial 10: ", my_mean_10r))
+print(paste0("Sd of combined snake and newt trial 10: ", my_sd_10r))
+print(paste0("Mean of the mean difference trial 10: ", mean_mean_dif_10r))
+print(paste0("SD of the mean difference trial 10: ", sd_mean_dif_10r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 11                          ")
+print("------------------------------------------------------------")
+
+files_11r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_11_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_11r)
+
+newt_max_pheno_1_11r = out[1]
+snake_max_pheno_1_11r = out[2]
+newt_min_pheno_1_11r  = out[3]
+snake_min_pheno_1_11r = out[4]
+true_max_1_11r = out[5]
+true_min_1_11r = out[6]
+min_difference_1_11r = out[7]
+max_difference_1_11r = out[8]
+my_mean_11r = out[9]
+my_sd_11r = out[10]
+mean_mean_dif_11r = out[11]
+sd_mean_dif_11r = out[12]
+
+print(paste0("Newt max pheno trial 11: ", newt_max_pheno_1_11r))
+print(paste0("Snake max phenot trial 11: ", snake_max_pheno_1_11r))
+print(paste0("Newt min pheno trial 11: ", newt_min_pheno_1_11r))
+print(paste0("Snake min Pheno trial 11: ", snake_min_pheno_1_11r))
+print(paste0("Mean of combined snake and newt trial 11: ", my_mean_11r))
+print(paste0("Sd of combined snake and newt trial 11: ", my_sd_11r))
+print(paste0("Mean of the mean difference trial 11: ", mean_mean_dif_11r))
+print(paste0("SD of the mean difference trial 11: ", sd_mean_dif_11r))
+
+print("------------------------------------------------------------")
+print("                         TRIAL 12                           ")
+print("------------------------------------------------------------")
+
+files_12r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_12_", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files_12r)
+
+newt_max_pheno_1_12r = out[1]
+snake_max_pheno_1_12r = out[2]
+newt_min_pheno_1_12r  = out[3]
+snake_min_pheno_1_12r = out[4]
+true_max_1_12r = out[5]
+true_min_1_12r = out[6]
+min_difference_1_12r = out[7]
+max_difference_1_12r = out[8]
+my_mean_12r = out[9]
+my_sd_12r = out[10]
+mean_mean_dif_12r = out[11]
+sd_mean_dif_12r = out[12]
+
+print(paste0("Newt max pheno trial 12: ", newt_max_pheno_1_12r))
+print(paste0("Snake max pheno trial 12: ", snake_max_pheno_1_12r))
+print(paste0("Newt min pheno trial 12: ", newt_min_pheno_1_12r))
+print(paste0("Snake min Pheno trial 12: ", snake_min_pheno_1_12r))
+print(paste0("Mean of combined snake and newt trial 12: ", my_mean_12r))
+print(paste0("Sd of combined snake and newt trial 12: ", my_sd_12r))
+print(paste0("Mean of the mean difference trial 12: ", mean_mean_dif_12r))
+print(paste0("SD of the mean difference trial 12: ", sd_mean_dif_12r))
+
+```
+
+```{r phenotype graph 12 points redone, echo=FALSE}
+
+title = "Trial 1 Phenotype Measurements for Newts and Snake"
+p_1r = phenotype_graph(files_1r, my_mean_1r, my_sd_1r, title)
+#p_1
+
+title = "Trial 2 Phenotype Measurements for Newts and Snake"
+p_2r = phenotype_graph(files_2r, my_mean_2r, my_sd_2r, title)
+#p_2
+
+title = "Trial 3 Phenotype Measurements for Newts and Snake Trial 3"
+p_3r = phenotype_graph(files_3r, my_mean_3r, my_sd_3r, title)
+#p_3
+
+title = "Trial 4 Phenotype Measurements for Newts and Snake"
+p_4r = phenotype_graph(files_4r, my_mean_4r, my_sd_4r, title)
+#p_4
+
+grid.arrange(p_1r, p_2r, p_3r, p_4r, nrow = 2)
+
+title = "Trial 5 Phenotype Measurements for Newts and Snake"
+p_5r = phenotype_graph(files_5r, my_mean_5r, my_sd_5r, title)
+#p_5
+
+title = "Trial 6 Phenotype Measurements for Newts and Snake"
+p_6r = phenotype_graph(files_6r, my_mean_6r, my_sd_6r, title)
+#p_6
+
+title = "Trial 7 Phenotype Measurements for Newts and Snake"
+p_7r = phenotype_graph(files_7r, my_mean_7r, my_sd_7r, title)
+#p_7
+
+title = "Trial 8 Phenotype Measurements for Newts and Snake"
+p_8r = phenotype_graph(files_8r, my_mean_8r, my_sd_8r, title)
+#p_8
+
+grid.arrange(p_5r, p_6r, p_7r, p_8r, nrow=2)
+
+title = "Trial 9 Phenotype Measurements for Newts and Snake"
+p_9r = phenotype_graph(files_9r, my_mean_9r, my_sd_9r, title)
+#p_9
+
+title = "Trial 10 Phenotype Measurements for Newts and Snake"
+p_10r = phenotype_graph(files_10r, my_mean_10r, my_sd_10r, title)
+#p_10
+
+title = "Trial 11 Phenotype Measurements for Newts and Snake"
+p_11r = phenotype_graph(files_11r, my_mean_11r, my_sd_11r, title)
+#p_11
+
+title = "Trial 12  Phenotype Measurements for Newts and Snake"
+p_12r = phenotype_graph(files_12r, my_mean_12r, my_sd_12r, title)
+#p_12
+
+grid.arrange(p_9r, p_10r, p_11r, p_12r, nrow=2)
+
+```
+
+## Difference between snake and newt pheotypes
+
+```{r 12 sim pheno dif redone, echo=FALSE}
+
+title = "Trial 1: Difference Between Phenotypes (Snakes-Newts)"
+d_1r = differnce_graph(files_1r, mean_mean_dif_1r, sd_mean_dif_1r, min_difference_1_1r, max_difference_1_1r, title)
+
+title = "Trial 2: Difference Between Phenotypes (Snakes-Newts)"
+d_2r = differnce_graph(files_2r, mean_mean_dif_2r, sd_mean_dif_2r, min_difference_1_2r, max_difference_1_2r, title)
+
+title = "Trial 3: Difference Between Phenotypes (Snakes-Newts)"
+d_3r = differnce_graph(files_3r, mean_mean_dif_3r, sd_mean_dif_3r, min_difference_1_3r, max_difference_1_3r, title)
+
+title = "Trial 4: Difference Between Phenotypes (Snakes-Newts)"
+d_4r = differnce_graph(files_4r, mean_mean_dif_4r, sd_mean_dif_4r, min_difference_1_4r, max_difference_1_4r, title)
+
+grid.arrange(d_1r, d_2r, d_3r, d_4r, nrow = 2)
+
+title = "Trial 5: Difference Between Phenotypes (Snakes-Newts)"
+d_5r = differnce_graph(files_5r, mean_mean_dif_5r, sd_mean_dif_5r, min_difference_1_5r, max_difference_1_5r, title)
+
+title = "Trial 6: Difference Between Phenotypes (Snakes-Newts)"
+d_6r = differnce_graph(files_6r, mean_mean_dif_6r, sd_mean_dif_6r, min_difference_1_6r, max_difference_1_6r, title)
+
+title = "Trial 7: Difference Between Phenotypes (Snakes-Newts)"
+d_7r = differnce_graph(files_7r, mean_mean_dif_7r, sd_mean_dif_7r, min_difference_1_7r, max_difference_1_7r, title)
+
+title = "Trial 8: Difference Between Phenotypes (Snakes-Newts)"
+d_8r = differnce_graph(files_8r, mean_mean_dif_8r, sd_mean_dif_8r, min_difference_1_8r, max_difference_1_8r, title)
+
+grid.arrange(d_5r, d_6r, d_7r, d_8r, nrow = 2)
+
+title = "Trial 9: Difference Between Phenotypes (Snakes-Newts)"
+d_9r = differnce_graph(files_9r, mean_mean_dif_9r, sd_mean_dif_9r, min_difference_1_9r, max_difference_1_9r, title)
+
+title = "Trial 10: Difference Between Phenotypes (Snakes-Newts)"
+d_10r = differnce_graph(files_10r, mean_mean_dif_10r, sd_mean_dif_10r, min_difference_1_10r, max_difference_1_10rr, title)
+
+title = "Trial 11: Difference Between Phenotypes (Snakes-Newts)"
+d_11r = differnce_graph(files_11r, mean_mean_dif_11r, sd_mean_dif_11r, min_difference_1_11r, max_difference_1_11r, title)
+
+title = "Trial 12: Difference Between Phenotypes (Snakes-Newts)"
+d_12r = differnce_graph(files_12r, mean_mean_dif_12r, sd_mean_dif_12r, min_difference_1_12r, max_difference_1_12r, title)
+
+grid.arrange(d_9r, d_10r, d_11r, d_12r, nrow = 2)
+
+```
+
+## How much did the phenotypes of newts and snakes change over 1000 generations
+
+```{r 12 sim pheno change redone, echo=FALSE}
+
+title = "Trial 1 12sim: Phenotype Change"
+c_1r=phenotype_change_graph(files_1r, my_mean_1r, my_sd_1r, title)
+
+title = "Trial 2 12sim: Phenotype Change"
+c_2r=phenotype_change_graph(files_2r, my_mean_2r, my_sd_2r, title)
+
+title = "Trial 3 12sim: Phenotype Change"
+c_3r=phenotype_change_graph(files_3r, my_mean_3r, my_sd_3r, title)
+
+title = "Trial 4 12sim: Phenotype Change"
+c_4r=phenotype_change_graph(files_4r, my_mean_4r, my_sd_4r, title)
+
+grid.arrange(c_1r, c_2r, c_3r, c_4r, nrow = 2)
+
+title = "Trial 5 12sim: Phenotype Change"
+c_5r=phenotype_change_graph(files_5r, my_mean_5r, my_sd_5r, title)
+
+title = "Trial 6 12sim: Phenotype Change"
+c_6r=phenotype_change_graph(files_6r, my_mean_6r, my_sd_6r, title)
+
+title = "Trial 7 12sim: Phenotype Change"
+c_7r=phenotype_change_graph(files_7r, my_mean_7r, my_sd_7r, title)
+
+title = "Trial 8 12sim: Phenotype Change"
+c_8r=phenotype_change_graph(files_8r, my_mean_8r, my_sd_8r, title)
+
+grid.arrange(c_5r, c_6r, c_7r, c_8r, nrow = 2)
+
+title = "Trial 9 12sim: Phenotype Change"
+c_9r=phenotype_change_graph(files_9r, my_mean_9r, my_sd_9r, title)
+
+title = "Trial 10 12sim: Phenotype Change"
+c_10r=phenotype_change_graph(files_10r, my_mean_10r, my_sd_10r, title)
+
+title = "Trial 11 12sim: Phenotype Change"
+c_11r=phenotype_change_graph(files_11r, my_mean_11r, my_sd_11r, title)
+
+title = "Trial 12 12sim: Phenotype Change"
+c_12r=phenotype_change_graph(files_12r, my_mean_12r, my_sd_12r, title)
+
+grid.arrange(c_9r, c_10r, c_11r, c_12r, nrow = 2)
+
+```
+
+## Trasforming the phenotypes back
+
+```{r 12 point trasformation redone, echo=FALSE}
+
+title1 = "Trial 1: Newt trasnformed vs un-trasformed"
+title2 = "Trial 1: Snake trasnformed vs un-trasformed"
+graph_1r = untrasform(files_1r, my_mean_1r, my_sd_1r, title1, title2, is_log=FALSE)
+
+title1 = "Trial 2: Newt trasnformed vs un-trasformed"
+title2 = "Trial 2: Snake trasnformed vs un-trasformed"
+graph_2r = untrasform(files_2r, my_mean_2r, my_sd_2r, title1, title2, is_log=FALSE)
+
+title1 = "Trial 3: Newt trasnformed vs un-trasformed"
+title2 = "Trial 3: Snake trasnformed vs un-trasformed"
+graph_3r = untrasform(files_3r, my_mean_3r, my_sd_3r, title1, title2, is_log=FALSE)
+
+title1 = "Trial 4: Newt trasnformed vs un-trasformed"
+title2 = "Trial 4: Snake trasnformed vs un-trasformed"
+graph_4r = untrasform(files_4r, my_mean_4r, my_sd_4r, title1, title2, is_log=FALSE)
+
+grid.arrange(graph_1r[[1]], graph_1r[[2]], graph_2r[[1]], graph_2r[[2]], graph_3r[[1]], graph_3r[[2]], graph_4r[[1]], graph_4r[[2]], nrow = 4)
+
+title1 = "Trial 5: Newt trasnformed vs un-trasformed"
+title2 = "Trial 5: Snake trasnformed vs un-trasformed"
+graph_5r = untrasform(files_5r, my_mean_5r, my_sd_5r, title1, title2, is_log=FALSE)
+
+title1 = "Trial 6: Newt trasnformed vs un-trasformed"
+title2 = "Trial 6: Snake trasnformed vs un-trasformed"
+graph_6r = untrasform(files_6r, my_mean_6r, my_sd_6r, title1, title2, is_log=FALSE)
+
+title1 = "Trial 7: Newt trasnformed vs un-trasformed"
+title2 = "Trial 7: Snake trasnformed vs un-trasformed"
+graph_7r = untrasform(files_7r, my_mean_7r, my_sd_7r, title1, title2, is_log=FALSE)
+
+title1 = "Trial 8: Newt trasnformed vs un-trasformed"
+title2 = "Trial 8: Snake trasnformed vs un-trasformed"
+graph_8r = untrasform(files_8r, my_mean_8r, my_sd_8r, title1, title2, is_log=FALSE)
+
+grid.arrange(graph_5r[[1]], graph_5r[[2]], graph_6r[[1]], graph_6r[[2]], graph_7r[[1]], graph_7r[[2]], graph_8r[[1]], graph_8r[[2]], nrow = 4)
+
+title1 = "Trial 9: Newt trasnformed vs un-trasformed"
+title2 = "Trial 9: Snake trasnformed vs un-trasformed"
+graph_9r = untrasform(files_9r, my_mean_9r, my_sd_9r, title1, title2, is_log=FALSE)
+
+title1 = "Trial 10: Newt trasnformed vs un-trasformed"
+title2 = "Trial 10: Snake trasnformed vs un-trasformed"
+graph_10r = untrasform(files_10r, my_mean_10r, my_sd_10r, title1, title2, is_log=FALSE)
+
+title1 = "Trial 11: Newt trasnformed vs un-trasformed"
+title2 = "Trial 11: Snake trasnformed vs un-trasformed"
+graph_11r = untrasform(files_11r, my_mean_11r, my_sd_11r, title1, title2, is_log=FALSE)
+
+title1 = "Trial 12: Newt trasnformed vs un-trasformed"
+title2 = "Trial 12: Snake trasnformed vs un-trasformed"
+graph_12r = untrasform(files_12r, my_mean_12r, my_sd_12r, title1, title2, is_log=FALSE)
+
+grid.arrange(graph_9r[[1]], graph_9r[[2]], graph_10r[[1]], graph_10r[[2]], graph_11r[[1]], graph_11r[[2]], graph_12r[[1]], graph_12r[[2]], nrow = 4)
+
+```

### 2021-07-20 graphs_newt_snakes/find_params.Rmd
made adjustments to nospace slim. I think the find_params.r had a graphing error due to the differences in how it was plotting the points. Going to work on making more graphs and rerunning the 12 start experiment with the corrected slim script.

@@
   geom_line(aes(x = sigma, y=y_mu_2), col="green")+
-  geom_line(aes(x = x_sigma_5, y=mu), col="blue")+
-  geom_line(aes(x = x_sigma_2, y=mu), col="green")+
+  #something might be out of order
+  #geom_line(aes(x = x_sigma_5, y=mu), col="blue")+
+  #geom_line(aes(x = x_sigma_2, y=mu), col="green")+
   scale_y_log10()+

### 2021-08-02 graphs_newt_snakes/find_params.Rmd
I reran the correctted slim script (12 starting points) and the numbers look wild. I also mare the line in params dots and they lined up perfectly.

--- 2021-07-19 graphs_newt_snakes/find_params.Rmd
@@
   geom_line(aes(x = sigma, y=y_mu_2), col="green")+
-  geom_line(aes(x = x_sigma_5, y=mu), col="blue")+
-  geom_line(aes(x = x_sigma_2, y=mu), col="green")+
+  #lines are out of order, but the points line up. Looks Good!
+  #geom_point(aes(x = x_sigma_5, y=mu), col="blue")+
+  #geom_point(aes(x = x_sigma_2, y=mu), col="green")+
   scale_y_log10()+

### 2021-08-03 graphs_newt_snakes/find_params.Rmd
I added a legend to the find param r markdown (today I will be adding more explination). I am working ou the the population size problem in nospace slim. How many of the newts interact with the snakes?

--- 2021-07-19 graphs_newt_snakes/find_params.Rmd
@@
 
+# Different Combinations
+
+Here I am using different values with the above formula to try to get the phenotypes of 5 and 2
+
 ```{r find sigma and mu, echo=FALSE}
@@
 
-ggplot(my_grid, aes(x = Var1, y=Var2)) +
-  geom_point(data=my_grid[my_grid$results <=5, ], aes(x = Var1, y=Var2), col="blue")+
-  geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2), col="green")+
+ggplot(my_grid, aes(x = Var1, y=Var2, colour = results)) +
+  geom_point(data=my_grid[my_grid$results <=5, ], aes(x = Var1, y=Var2, colour="Less than 5"))+
+  geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2, colour="Less than 2"))+
   ggtitle("Value Combinations That Might Work") +
   xlab("Sigma") + ylab("Mu")+  
-  theme_bw()
+  theme_bw()+
+  scale_color_manual(name = "Fake Phenotypes", values = c("Less than 5" = "blue", "Less than 2" = "green"))
 
@@
 ggplot() +
-  geom_line(aes(x = sigma, y=y_mu_5), col="blue")+
-  geom_line(aes(x = sigma, y=y_mu_2), col="green")+
-  geom_line(aes(x = x_sigma_5, y=mu), col="blue")+
-  geom_line(aes(x = x_sigma_2, y=mu), col="green")+
+  geom_line(aes(x = sigma, y=y_mu_5, colour="Less than 5"))+
+  geom_line(aes(x = sigma, y=y_mu_2, colour="Less than 2"))+
+  #lines are out of order, but the points line up. Looks Good!
+  #geom_point(aes(x = x_sigma_5, y=mu), col="blue")+
+  #geom_point(aes(x = x_sigma_2, y=mu), col="green")+
   scale_y_log10()+
@@
   xlab("Sigma") + ylab("Mu (log)")+ #xlim(0, 0.6)+
-  theme_bw()
+  theme_bw()+
+  scale_color_manual(name = "Fake Phenotypes", values = c("Less than 5" = "blue", "Less than 2" = "green"))
 

### 2021-08-04 graphs_newt_snakes/fig_1000.Rmd
I reran the correctted slim script (12 starting points) and the numbers look wild. I also mare the line in params dots and they lined up perfectly.
I updated the r markdown files for the 1000 gen experiments and the finding the correct params to help explain what I am doing and suggest some of the next steps to take.

@@
 
+## Fake Example of the Problem I have been seeing
+
+```{r fake exaple, echo=FALSE}
+gen <- seq(20, 1000, by = 20)
+  ex <- as.data.frame(gen)
+
+ex$Newt_mean_Pheno <- pexp(seq(0.2, 10, by = .2), rate = 1)*seq(1, 100, by = 2) + rnorm(50, mean = 0, sd = 5)
+  ex$Snake_mean_Pheno <-seq(.18, 5.1, by = .1) + + rnorm(50, mean = 0, sd = 5)
+p <- ggplot(ex, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = Newt_mean_Pheno, colour="Newt")) + 
+  geom_line(aes(y = Snake_mean_Pheno, colour="Snake"), linetype="twodash")+
+  ggtitle("Fake Example of What I was Observing") +
+  xlab("Generation") + ylab("Average Phenotypes")+
+  scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+  theme_bw()
+p
+```
+
 ## The testing Paramiters 
-I used different values for snake_mu_effect_sd	newt_mu_effect_sd	snake_mu_rate	newt_mu_rate. I chose these parameters to see if there would be a seeable interaction in phenotypes 
+I used different values for snake_mu_effect_sd	newt_mu_effect_sd	snake_mu_rate	newt_mu_rate. I chose these parameters to see if there would be a see-able interaction in phenotypes 
 Other params:
@@
 
-Snake/newt mu effect sd -> is the standard deviation that each mutation would "effect" a phenotype. Values: 0.01 0.05 0.2 0.5
-
-Snake/newt mu rate -> is the mutation rate that were assigned to newts and snakes. Values: 1.00E-08 1.00E-10 1.00E-12
+**Snake/newt mu effect sd -> is the standard deviation that each mutation would "effect" a phenotype. Values: 0.01 0.05 0.2 0.5**
+
+**Snake/newt mu rate -> is the mutation rate that were assigned to newts and snakes. Values: 1.00E-08 1.00E-10 1.00E-12**
 
@@
 
--Realistic phenotypes (snake 0-3, newt 0-1.5(thoughts 2021?))
--See if the levels of toxicity and resistance interact 
--See groups of mutations/ certain phenotypes
+* Realistic phenotypes (snake 0-3, newt 0-1.5(thoughts 2021?))
+* See if the levels of toxicity and resistance interact 
+* See groups of mutations/ certain phenotypes
 
@@
   #ylim(0, true_max_1)+
-  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
-  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
+  geom_line(aes(y = Newt_mean_Pheno, colour="Newt")) + 
+  geom_line(aes(y = Snake_mean_Pheno, colour="Snake"), linetype="twodash")+
   ggtitle(title) +
   xlab("Generation") + ylab("Average Phenotypes")+
+  scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
   theme_bw()
@@
   file <- file[complete.cases(file), ]
- p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color = darken("darkred")) +
-   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color = darken("steelblue")) +
-  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color = lighten("steelblue"))+
-  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1), size = 0.3, arrow = arrow(length = unit(0.5, "cm")), color="darkred")+
-   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1), size = 0.3, arrow = arrow(length = unit(0.5, "cm")), color="steelblue")
+ p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color= darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color=lighten("darkred"))  + 
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color=darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color=lighten("steelblue"))+
+  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1, colour="Newt"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))+
+   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1, colour="Snake"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))
 
@@
 }
+p <- p +
+ scale_colour_manual(name = "Species", values = c("Newt" = "darkred", "Snake"="steelblue"))
 return(p)
@@
 Loop through the files and find the max and min of each of the species phenotypes
-Then set up a graph with the average phenotype:
+Then set up a graph with the average phenotype per generation:
+I collected data ever 20 generations until 1000 generations were done
 
@@
 
+Here I have a questions why are the newts always starting off higher than the snakes????
+
 ## Difference Between Snake and Newt Pheotypes
@@
 
-I ran 144 SLiM simulations with different parameters values and used the MSprime   both_su_1e-10_nu_1e-10_sue_0.01_nue_0.01 (s/n u mutation rate, n/s ue mutation effect size) file.
+I ran 144 SLiM simulations(might be 143?) with different parameters values and used the MSprime file: both_su_1e-10_nu_1e-10_sue_0.01_nue_0.01 (s/n u mutation rate, n/s ue mutation effect size)
 
@@
 ```
+I noticed that in a majority of these the newts had a higher phenotype than the snakes.
 
@@
 Extra note: In my code snake_mu_rate is called mu_rate
+**I found an error in the code which was not giving the correct mutation rate to snakes**
 
@@
 
+Some of these values seem very large, but the means are not super bad.
+
 ```{r phenotype graph 12 points redone, echo=FALSE}
@@
 ```
+
+## Next Steps
+
+Some of these simulations still created very large phenotypes. I would like to know why
+*Was it the mutation or effect size values?
+*Is it the msprime simulation starting point?
+*Is the maximum value important? And if so what does it mean?
+*Compare simulated phenotype values to the predicted values from the equation mediated by the parameters
+*Is this caused by space?
+*Is it caused by co-evolution?

### 2021-08-04 msprime/test_snake_newt_msprime.py
I made a bash script that will take mutation rate and mutation effect size paramiters and run msprime and slim. I made seperate test files so that this can be run even when I am playing with the main file.

@@ -6,15 +6,14 @@ import os
 import sys
 from sys import argv
 # import util
-# testing vscode&git 
-#print("hello")
+
 
 sequence_length = 100000000
 '''
 datadir = "newt_snake/data"
 snake_mu_rate = 1e-10
 newt_mu_rate = 1e-10  # does this need to be 50 times more than the snake?
-snake_mu_effect_sd = 0.01
+snake_mu_effect_sd = 0.05
 newt_mu_effect_sd = 0.01
 name_of_file = "both_newt_snake_annotated.init.trees"
 

### 2021-08-04 srun_scripts/testslim_start_to_end.sh

@@ -1,0 +1,28 @@
+#!/usr/bin/env bash
+
+# Run these comands while in The Coevo folder
+# might have to run python ans slim one at a time?
+datadir="data/test" # directory to store the test files
+[ ! -d "$datadir" ] && mkdir -p "$datadir"
+
+outpath="data/test/text_files/" # the text output will be here
+[ ! -d "$outpath" ] && mkdir -p "$outpath"
+treename="data/test/tree_files/" # the tree output will be here
+[ ! -d "$treename" ] && mkdir -p "$treename"
+tag="test" # exrta info to identify what experiment I am workin on
+
+# Sample paramiter values
+snake_mu_rate=1E-10	
+newt_mu_rate=1E-10
+snake_mu_effect_sd=0.1
+newt_mu_effect_sd=0.1
+# the msprime file that slim uses (gennerates sgv)
+msprime_file="${datadir}/both_1000_su_${snake_mu_rate}_nu_${newt_mu_rate}_sue_${snake_mu_effect_sd}_nue_${newt_mu_effect_sd}_${tag}.init.trees"
+# help to name the slime file with the paramiters that I use
+namebase="test_su_${snake_mu_rate}_nu_${newt_mu_rate}_sue_${snake_mu_effect_sd}_nue_${newt_mu_effect_sd}"
+
+# the python script to generate diversity 
+python 'msprime/test_snake_newt_msprime.py' ${snake_mu_rate} ${newt_mu_rate} ${snake_mu_effect_sd} ${newt_mu_effect_sd} ${datadir} ${tag}
+
+# the spatial slim script that goes to 1000 generations
+slim -m -t -d "mu_rate = ${snake_mu_rate}" -d "newt_mu_rate = ${newt_mu_rate}" -d "snake_mu_effect_sd = ${snake_mu_effect_sd}" -d "newt_mu_effect_sd = ${newt_mu_effect_sd}" -d "msprime_file = '${msprime_file}'" -d "outpath = '${outpath}'" 'newt_snake/test_newt_snake_1on1.slim' > ${treename}/file_${namebase}_${tag}.txt;

### 2021-08-04 srun_scripts/testslim_start_to_end.sh
switched the folders for trees and text files, now it is fixed

@@ -25,4 +25,4 @@ namebase="test_su_${snake_mu_rate}_nu_${newt_mu_rate}_sue_${snake_mu_effect_sd}_
 python 'msprime/test_snake_newt_msprime.py' ${snake_mu_rate} ${newt_mu_rate} ${snake_mu_effect_sd} ${newt_mu_effect_sd} ${datadir} ${tag}
 
 # the spatial slim script that goes to 1000 generations
-slim -m -t -d "mu_rate = ${snake_mu_rate}" -d "newt_mu_rate = ${newt_mu_rate}" -d "snake_mu_effect_sd = ${snake_mu_effect_sd}" -d "newt_mu_effect_sd = ${newt_mu_effect_sd}" -d "msprime_file = '${msprime_file}'" -d "outpath = '${outpath}'" 'newt_snake/test_newt_snake_1on1.slim' > ${treename}/file_${namebase}_${tag}.txt;
+slim -m -t -d "mu_rate = ${snake_mu_rate}" -d "newt_mu_rate = ${newt_mu_rate}" -d "snake_mu_effect_sd = ${snake_mu_effect_sd}" -d "newt_mu_effect_sd = ${newt_mu_effect_sd}" -d "msprime_file = '${msprime_file}'" -d "outpath = '${treename}'" 'newt_snake/test_newt_snake_1on1.slim' > ${outpath}/file_${namebase}_${tag}.txt;

### 2021-08-06 graphs_newt_snakes/find_params.Rmd
I updated the r markdown files for the 1000 gen experiments and the finding the correct params to help explain what I am doing and suggest some of the next steps to take.
worked on showing and explaining the data that I generated with params that are suposed to get low phenotypes. About half-way done. A work in progress!

@@
 title: "Finding Sigma and Mu"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
 ```
+# Values to try
+
+For this experiment I ran 6 simulations with different sigma and mu values to try to get the phenotype of newts and snakes at or below a certain value (in this case 5 and 2).
+It do this experiment I set the values for SD[phenotype] and sigma (0.1, 0.2, 0.3) and solved for mu.
+I ran 1 simulation per pair (so far) just to see where the newt and snake phenotypes would end up.
+
+*For the less than 5* 
+Pairs:
+
+* sigma = 0.1, mu = 6.25e-10
+* sigma = 0.2, mu = 1.5625e-10
+* sigma = 0.3, mu = 6.944444e-11
+
+*For the less than 2* 
+Pairs:
+
+* sigma = 0.1, mu = 1e-10
+* sigma = 0.2, mu = 2.5e-11
+* sigma = 0.3, mu = 1.111111e-11
+
+```{r functions, echo=FALSE}
+
+collect_data_points <- function(files) {
+  newt_max_pheno_1 = 0
+  snake_max_pheno_1 = 0
+  newt_min_pheno_1 = 0
+  snake_min_pheno_1 = 0
+  true_max_1 = 0
+  true_min_1 = 0
+  min_difference_1 = 0
+  max_difference_1 = 0
+  mean = 0
+  sd = 0
+  mean_mean_dif = 0
+  sd_mean_dif = 0
+
+  for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+
+  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
+  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
+  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
+  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file$Newt_mean_Pheno <- lapply(file$Newt_mean_Pheno,as.numeric)
+  file$Snake_mean_Pheno <- lapply(file$Snake_mean_Pheno,as.numeric)
+  file$Newt_max_Pheno <- lapply(file$Newt_max_Pheno,as.numeric)
+  file$Snake_max_Pheno <- lapply(file$Snake_max_Pheno,as.numeric)
+  file$Newt_min_Pheno <- lapply(file$Newt_min_Pheno,as.numeric)
+  file$Snake_min_Pheno <- lapply(file$Snake_min_Pheno,as.numeric)
+
+  mean = mean(c(as.numeric(file$Newt_mean_Pheno), as.numeric(file$Snake_mean_Pheno)), na.rm = TRUE)
+  sd = sd(c(as.numeric(file$Newt_mean_Pheno), as.numeric(file$Snake_mean_Pheno)), na.rm = TRUE)
+  mean_mean_dif = mean(as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno),na.rm = TRUE)
+  sd_mean_dif = sd(as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno),na.rm = TRUE)
+
+    if (max(as.numeric(file$Newt_max_Pheno), na.rm = TRUE) > newt_max_pheno_1){
+    newt_max_pheno_1 = max(as.numeric(file$Newt_max_Pheno), na.rm = TRUE) }
+
+  if (max(as.numeric(file$Snake_max_Pheno), na.rm = TRUE) > snake_max_pheno_1){
+    snake_max_pheno_1 = max(as.numeric(file$Snake_max_Pheno), na.rm = TRUE) }
+
+  if (min(as.numeric(file$Newt_min_Pheno), na.rm = TRUE) < newt_min_pheno_1){
+    newt_min_pheno_1 = min(as.numeric(file$Newt_min_Pheno), na.rm = TRUE) }
+
+  if (min(as.numeric(file$Snake_min_Pheno), na.rm = TRUE) < snake_min_pheno_1){
+    snake_min_pheno_1 = min(as.numeric(file$Snake_min_Pheno), na.rm = TRUE) }
+
+  if (min(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - max(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE) < min_difference_1){
+    min_difference_1 = min(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - max(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE)
+  }
+
+  if (max(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - min(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE) > max_difference_1){
+    max_difference_1 = max(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - min(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE)
+  }
+  }
+
+    if (newt_max_pheno_1 > snake_max_pheno_1){
+    true_max_1 = newt_max_pheno_1 }
+  if ( snake_max_pheno_1 > newt_max_pheno_1){
+    true_max_1 = snake_max_pheno_1 }
+
+    if (newt_min_pheno_1 < snake_min_pheno_1){
+    true_min_1 = newt_min_pheno_1 }
+  if ( snake_min_pheno_1 < newt_min_pheno_1){
+    true_min_1 = snake_min_pheno_1 }
+
+  return(c(newt_max_pheno_1, snake_max_pheno_1, newt_min_pheno_1, snake_min_pheno_1, true_max_1, true_min_1, min_difference_1, max_difference_1, mean, sd, mean_mean_dif, sd_mean_dif))
+}
+
+phenotype_graph_s <- function(files, the_mean, the_sd, title, subt, is_log=FALSE, boxy=FALSE){
+
+  file1 <- read.table(files[1], header = TRUE)
+  file1$Newt_mean_Pheno[file1$Newt_mean_Pheno == "NULL"] <- NA
+  file1$Snake_mean_Pheno[file1$Snake_mean_Pheno == "NULL"] <- NA
+  file1$Newt_mean_Pheno[file1$Newt_sd_Pheno == "NULL"] <- NA
+  file1$Snake_mean_Pheno[file1$Snake_sd_Pheno == "NULL"] <- NA
+
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  #ylim(0, true_max_1)+
+  #geom_line(aes(y = Newt_mean_Pheno, colour="Newt")) + 
+  #geom_boxplot(aes(x=gen+5, group = gen, lower=Newt_mean_Pheno-Newt_sd_Pheno, upper=Newt_mean_Pheno+Newt_sd_Pheno, middle=Newt_mean_Pheno, ymin=Newt_mean_Pheno-3*Newt_sd_Pheno, ymax=Newt_mean_Pheno+3*Newt_sd_Pheno, colour="Newt"), stat="identity", position = position_dodge(width = 0.9), alpha = .3, width=3.15)+
+  #geom_line(aes(y = Snake_mean_Pheno, colour="Snake"), linetype="twodash")+
+  #geom_boxplot(aes(x=gen-5,group = gen, lower=Snake_mean_Pheno-Snake_sd_Pheno, upper=Snake_mean_Pheno+Snake_sd_Pheno, middle=Snake_mean_Pheno, ymin=Snake_mean_Pheno-3*Snake_sd_Pheno, ymax=Snake_mean_Pheno+3*Snake_sd_Pheno, colour="Snake"), stat="identity", position = "identity", alpha = .3, width=3.15)+
+  #geom_errorbar(aes(x = gen+5, colour="Newt", ymin = Newt_mean_Pheno - 2*Newt_sd_Pheno, ymax = Newt_mean_Pheno + 2*Newt_sd_Pheno))+ # error bar to show variation
+  #geom_errorbar(aes(x = gen-5, colour="Snake", ymin = Snake_mean_Pheno - 2*Snake_sd_Pheno, ymax = Snake_mean_Pheno + 2*Snake_sd_Pheno))+ # error bar to show variation
+  ggtitle(title, subtitle = subt) +
+  xlab("Generation") + ylab("Average Phenotypes")+
+  scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw()
+
+if(boxy==FALSE){
+ p= p + geom_line(aes(y = Newt_mean_Pheno, colour="Newt")) + geom_line(aes(y = Snake_mean_Pheno, colour="Snake"), linetype="twodash")
+
+}
+
+if(boxy==TRUE){
+  p = p +  geom_boxplot(aes(x=gen-5,group = gen, lower=Snake_mean_Pheno-Snake_sd_Pheno, upper=Snake_mean_Pheno+Snake_sd_Pheno, middle=Snake_mean_Pheno, ymin=Snake_mean_Pheno-3*Snake_sd_Pheno, ymax=Snake_mean_Pheno+3*Snake_sd_Pheno, colour="Snake"), stat="identity", position = "identity", alpha = .3, width=3.15)+
+      geom_boxplot(aes(x=gen+5, group = gen, lower=Newt_mean_Pheno-Newt_sd_Pheno, upper=Newt_mean_Pheno+Newt_sd_Pheno, middle=Newt_mean_Pheno, ymin=Newt_mean_Pheno-3*Newt_sd_Pheno, ymax=Newt_mean_Pheno+3*Newt_sd_Pheno, colour="Newt"), stat="identity", position = position_dodge(width = 0.9), alpha = .3, width=3.15)
+}
+
+if(is_log==TRUE){
+  p = p + ylab("Average Phenotypes (Log)") + scale_y_log10(limits=c(the_mean-(the_sd*3), the_mean+(the_sd*10)))
+  }
+
+return(p)
+}
+
+differnce_graph <- function(files, the_mean, the_sd, min_difference_1, max_difference_1, title, is_log=FALSE){
+
+ file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=gen)) +
+  xlim(0, 1000)+
+  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
+  ggtitle(title) +
+  xlab("Generation") + ylab("Average Difference")+
+  theme_bw()
+
+if(is_log==TRUE){
+  p = p + scale_y_log10(limits=c(min_difference_1, max_difference_1)) + ylab("Average Difference (Log)")
+}
+
+if(is_log==FALSE){
+  p = p + ylim(abs(the_mean)-the_sd*10, abs(the_mean)+the_sd*10)
+}
+
+for (current_file in files){
+  #print(current_file)
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
+  file$mean_dif[file$mean_dif == 0] <- 0.01
+  file$pos <- "Snake"
+  file$pos[file$mean_dif < 0] <- "Newt"
+  file$pos[file$mean_dif ==  0.01] <- "ZEqual"
+
+ p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
+  #Sys.sleep(2) na.rm=TRUE
+ # color = "mediumseagreen"
+
+}
+return(p)
+}
+
+phenotype_change_graph_s <- function(files, the_mean, the_sd, title, is_log=FALSE, xlim_value){
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=1:144)) +
+  xlim(0, xlim_value)+
+  ggtitle(title) +
+  xlab("Simulation number") + ylab("Phenotype")+
+  theme_bw()
+
+if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Phenotype  (Log)")
+
+}
+
+i=1
+for (current_file in files){
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
+  file <- file[complete.cases(file), ]
+ p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color= darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color=lighten("darkred"))  + 
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color=darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color=lighten("steelblue"))+
+  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1, colour="Newt"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))+
+   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1, colour="Snake"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))
+
+ i = i+1
+}
+p <- p +
+ scale_colour_manual(name = "Species", values = c("Newt" = "darkred", "Snake"="steelblue"))
+return(p)
+}
+
+untrasform <- function(files, the_mean, the_sd, title1, title2, is_log=FALSE){
+
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=as.numeric(Newt_mean_Pheno))) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred") + 
+  ggtitle(title1) +
+  xlab("Trasnformed") + ylab("Untransformed")+
+  theme_bw()
+q <- ggplot(file1, aes(x=as.numeric(Snake_mean_Pheno))) +
+  #ylim(0, true_max_1)+
+  geom_line(aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color = "steelblue") + 
+  ggtitle(title2) +
+  xlab("Transformed") + ylab("Untransformed")+
+  theme_bw()
+
+for (current_file in files){
+  #print(current_file)
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
+  file <- file[complete.cases(file), ]
+  #print(file$Newt_mean_Pheno)
+  #print(exp(file$Newt_mean_Pheno/10))
+  #print(log(as.numeric(file$Newt_mean_Pheno))*10)
+  file <- read.table(current_file, header = TRUE)
+ p <- p + geom_line(data=file, aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred",na.rm = TRUE)
+
+ q <- q + geom_line(data=file, aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color="steelblue", linetype="twodash", na.rm = FALSE)
+}
+return(list(p,q))
+
+}
+
+```
+
+# Test 1 Under 5
+
+For this test I ran 3 simulations (msprime and slim, a "set") to see if the phenotypes would be under 5.
+I looked at the maximum and minimum phenotypes for newts and snakes.
+The first set of figures below show the mean phenotypes for the newts and snakes every 20 generations.
+Newts are red and snakes are blue.
+Surprisingly, (or not?) the snakes have a higher mean phenotype.
+The phenotypes of both newts and snake are increasing as the generation increases.
+The second set of figures are boxplots calculated from the mean and standard deviation each generation for one simulation.
+Sense these are values for only one simulation the standard deviation can be large.
+
+Extra notes:
+
+* 1000 gen slim simulations only take a few minutes at most on the cluster 
+* boxplots are calculated from mean and sd (box is 2sd and line is 3sd)
+
+```{r data from the mistake folder, echo=FALSE}
+files <- list.files(path="~/Desktop/findparams/under_5", pattern="file_*", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files)
+
+newt_max_pheno_u5 = out[1]
+snake_max_pheno_u5 = out[2]
+newt_min_pheno_u5  = out[3]
+snake_min_pheno_u5 = out[4]
+true_max_u5 = out[5]
+true_min_u5 = out[6]
+min_difference_u5 = out[7]
+max_difference_u5 = out[8]
+my_mean_u5 = out[9]
+my_sd_u5 = out[10]
+mean_mean_dif_u5 = out[11]
+sd_mean_dif_u5 = out[12]
+
+print(paste0("Newt max pheno: ", newt_max_pheno_u5))
+print(paste0("Snake max phenot: ", snake_max_pheno_u5))
+print(paste0("Newt min pheno: ", newt_min_pheno_u5))
+print(paste0("Snake min Pheno: ", snake_min_pheno_u5))
+print(paste0("Mean of combined snake and newt: ", my_mean_u5))
+print(paste0("Sd of combined snake and newt: ", my_sd_u5))
+print(paste0("Mean of the mean difference: ", mean_mean_dif_u5))
+print(paste0("SD of the mean difference: ", sd_mean_dif_u5))
+
+```
+
+```{r phenotype graph for under 5, echo=FALSE}
+myfiles <- list.files(path="~/Desktop/findparams/under_5", pattern="file_*", full.names=TRUE, recursive=FALSE)
+
+# sigma = 0.1, mu = 6.25e-10
+# sigma = 0.2, mu = 1.5625e-10
+# sigma = 0.3, mu = 6.944444e-11
+
+p_1 = phenotype_graph_s(files=myfiles[1], the_mean=my_mean_u5, the_sd=my_sd_u5, title="Under 5: Phenotype Measurements for Newts and Snakes",subt="sigma = 0.2, mu = 1.5625e-10", is_log=FALSE)
+
+p_2 = phenotype_graph_s(files=myfiles[2], the_mean=my_mean_u5, the_sd=my_sd_u5, title="Under 5: Phenotype Measurements for Newts and Snakes",subt="sigma = 0.1, mu = 6.25e-10" , is_log=FALSE)
+
+p_3 = phenotype_graph_s(files=myfiles[3], the_mean=my_mean_u5, the_sd=my_sd_u5, title="Under 5: Phenotype Measurements for Newts and Snakes", subt="sigma = 0.3, mu = 6.944444e-11" , is_log=FALSE)
+
+grid.arrange(p_1, p_2, p_3, nrow=2)
+
+p_1 = phenotype_graph_s(files=myfiles[1], the_mean=my_mean_u5, the_sd=my_sd_u5, title="Under 5: Phenotype Measurements for Newts and Snakes",subt="sigma = 0.2, mu = 1.5625e-10", is_log=FALSE, boxy = TRUE)
+
+p_2 = phenotype_graph_s(files=myfiles[2], the_mean=my_mean_u5, the_sd=my_sd_u5, title="Under 5: Phenotype Measurements for Newts and Snakes",subt="sigma = 0.1, mu = 6.25e-10" , is_log=FALSE, boxy = TRUE)
+
+p_3 = phenotype_graph_s(files=myfiles[3], the_mean=my_mean_u5, the_sd=my_sd_u5, title="Under 5: Phenotype Measurements for Newts and Snakes", subt="sigma = 0.3, mu = 6.944444e-11" , is_log=FALSE, boxy = TRUE)
+
+grid.arrange(p_1, p_2, p_3, nrow=2)
+
+```
+
+Some things that I noticed was that snakes had a higher phenotype than the newts in all of the simulations.
+Snakes also had a higher standard deviation than newts.
+Sense there is only one simulation per test values I am not sure what a normal simulation would look like (solution run more simulations with the same values?
+should they used the same msprime file?).
+It looks like the phenotypes are going above 5, is this normal or just a fluke?
+I personally like aesthetics of the sigma = 0.1, mu = 6.25e-10 boxplot, is there some sort of space thing creating the high variance?
+
+# Looking at the difference for under 5
+
+Here I look at the difference between the snake and newt mean phenotypes (snake-newt).
+Pink lines indicate that the snake mean phenotype was higher than the newt mean phenotype.
+Blue lines indicate that the mean phenotype of newts was higher.
+In the three simulations that I ran for the under 5 test the snake phenotype was always higher than the newts phenotype.
+
+```{r difference under 5, echo=FALSE}
+
+## need to work on making this figure better 
+files <- list.files(path="~/Desktop/findparams/under_5", pattern="file_*", full.names=TRUE, recursive=FALSE)
+title = "Under 5: Difference Between Phenotypes (Snakes-Newts)"
+p = differnce_graph(files, mean_mean_dif_u5, sd_mean_dif_u5, min_difference_1_u5, max_difference_1_u5, title, is_log=FALSE)
+
+p
+```
+
+The difference between the mean snake phenotype and the mean newt phenotype (pink lines) increased as the generation increased.
+What does it mean when the difference between the mean was increasing?
+was the snake mean phenotype increasing faster than the newts?
+Where there a few snakes that got really resistance to the newts (increasing the overall mean)?
+Was the increase in the newts phenotype slower than the snakes, how to tell and if so why?
+Ironically, it kind of matches what is seen in the wild (snake resistance > newt toxin)?
+Would be cool to see the spatial aspect...
+
+# Showing the pheotype change for under 5
+
+Here, I just look at the starting and ending mean phenotypes values for each of the simulations.
+The arrows start at the beginning phenotypes and point to the ending phenotypes.
+Newts are red and snakes are blue.
+
+These are the simulation numbers:
+
+1. sigma = 0.2, mu = 1.5625e-10
+2. sigma = 0.1, mu = 6.25e-10
+3. sigma = 0.3, mu = 6.944444e-11
+
+```{r pheno change under 5, echo=FALSE}
+
+files <- list.files(path="~/Desktop/findparams/under_5", pattern="file_*", full.names=TRUE, recursive=FALSE)
+title = "Under 5: Phenotype Change"
+p=phenotype_change_graph_s(files, my_mean_u5, my_sd_u5, title, is_log=FALSE, xlim_value=4)
+
+p
+
+```
+
+There was a positive change in the snake phenotype for all three simulations.
+Why is one of then so much larger than the others?
+The newt phenotype increased in 2 out of 3 of the simulations.
+Again, why?
+
+# Trasforming Phenotypes for under 5
+
+I want to see what the un-transformed phenotypes are and compare them to their transformed form. To do this I use the mean phenotype values.
+
+I calculated the phenotypes from this expression, newt pheno = exp(inds_n.sumOfMutationsOfType(m1)/10).
+So to un-transform and find the # of mutations I need to ln both sides of the equation ln(pheno=e^(sumOfMutations/10)).
+Then solve for sumOfMutations,  sumOfMutations = 10 * ln(pheno)
+
+```{r trasformation under 5, echo=FALSE}
+
+files <- list.files(path="~/Desktop/findparams/under_5", pattern="file_*", full.names=TRUE, recursive=FALSE)
+
+title1 = "Under 5: Newt trasnformed vs un-trasformed"
+title2 = "Under 5: Snake trasnformed vs un-trasformed"
+graph = untrasform(files, my_mean_u5, my_sd_u5, title1, title2, is_log=FALSE)
+graph[1]
+graph[2]
+
+```
+
+Both the transformed lines curve and are 5 and under. How do I know if the phenotypes will remain 5 and under?
+
+# Test 2 Under 2
+
+For this test I again ran 3 simulations (msprime and slim, a "set") to see if the phenotypes would be 2 or under.
+I looked at the maximum and minimum phenotypes for newts and snakes.
+The first set of figures below show the mean phenotypes for the newts and snakes every 20 generations.
+Surprisingly, (or not?) the snakes have a higher mean phenotype.
+The phenotypes of both newts and snake are increasing as the generation increases.
+The second set of figures are boxplots calculated from the mean and standard deviation each generation for one simulation.
+Sense these are values for only one simulation the standard deviation can be large.
+
+```{r data from the under 2 folder, echo=FALSE}
+files <- list.files(path="~/Desktop/findparams/under_2", pattern="file_*", full.names=TRUE, recursive=FALSE)
+
+out = collect_data_points(files)
+
+newt_max_pheno_u2 = out[1]
+snake_max_pheno_u2 = out[2]
+newt_min_pheno_u2 = out[3]
+snake_min_pheno_u2 = out[4]
+true_max_u2 = out[5]
+true_min_u2 = out[6]
+min_difference_u2 = out[7]
+max_difference_u2 = out[8]
+my_mean_u2 = out[9]
+my_sd_u2 = out[10]
+mean_mean_dif_u2 = out[11]
+sd_mean_dif_u2 = out[12]
+
+print(paste0("Newt max pheno: ", newt_max_pheno_u2))
+print(paste0("Snake max phenot: ", snake_max_pheno_u2))
+print(paste0("Newt min pheno: ", newt_min_pheno_u2))
+print(paste0("Snake min Pheno: ", snake_min_pheno_u2))
+print(paste0("Mean of combined snake and newt: ", my_mean_u2))
+print(paste0("Sd of combined snake and newt: ", my_sd_u2))
+print(paste0("Mean of the mean difference: ", mean_mean_dif_u2))
+print(paste0("SD of the mean difference: ", sd_mean_dif_u2))
+
+```
+
+```{r phenotype graph for under 2, echo=FALSE}
+myfiles <- list.files(path="~/Desktop/findparams/under_2", pattern="file_*", full.names=TRUE, recursive=FALSE)
+
+# sigma = 0.1, mu = 1e-10
+# sigma = 0.2, mu = 2.5e-11
+# sigma = 0.3, mu = 1.111111e-11
+
+p_1 = phenotype_graph_s(files=myfiles[1], the_mean=my_mean_u2, the_sd=my_sd_u2, title="Under 2: Phenotype Measurements for Newts and Snakes",subt="sigma = 0.3, mu = 1.111111e-11", is_log=FALSE)
+
+p_2 = phenotype_graph_s(files=myfiles[2], the_mean=my_mean_u2, the_sd=my_sd_u2, title="Under 2: Phenotype Measurements for Newts and Snakes",subt="sigma = 0.1, mu = 1e-10" , is_log=FALSE)
+
+p_3 = phenotype_graph_s(files=myfiles[3], the_mean=my_mean_u2, the_sd=my_sd_u2, title="Under 2: Phenotype Measurements for Newts and Snakes", subt="sigma = 0.2, mu = 2.5e-11" , is_log=FALSE)
+
+grid.arrange(p_1, p_2, p_3, nrow=2)
+
+p_1 = phenotype_graph_s(files=myfiles[1], the_mean=my_mean_u2, the_sd=my_sd_u2, title="Under 2: Phenotype Measurements for Newts and Snakes",subt="sigma = 0.3, mu = 1.111111e-11", is_log=FALSE, boxy = TRUE)
+
+p_2 = phenotype_graph_s(files=myfiles[2], the_mean=my_mean_u2, the_sd=my_sd_u2, title="Under 2: Phenotype Measurements for Newts and Snakes",subt="sigma = 0.1, mu = 1e-10" , is_log=FALSE, boxy = TRUE)
+
+p_3 = phenotype_graph_s(files=myfiles[3], the_mean=my_mean_u2, the_sd=my_sd_u2, title="Under 2: Phenotype Measurements for Newts and Snakes", subt="sigma = 0.2, mu = 2.5e-11" , is_log=FALSE, boxy = TRUE)
+
+grid.arrange(p_1, p_2, p_3, nrow=2)
+
+```
+
+Wow, theses simulations are very different from each other
+
+```{r difference under 2, echo=FALSE}
+
+## need to work on making this figure better 
+files <- list.files(path="~/Desktop/findparams/under_2", pattern="file_*", full.names=TRUE, recursive=FALSE)
+title = "Under 2: Difference Between Phenotypes (Snakes-Newts)"
+p = differnce_graph(files, mean_mean_dif_u2, sd_mean_dif_u2, min_difference_1_u2, max_difference_1_u2, title, is_log=FALSE)
+
+p
+```
+
+```{r pheno change for under 2, echo=FALSE}
+
+files <- list.files(path="~/Desktop/findparams/under_2", pattern="file_*", full.names=TRUE, recursive=FALSE)
+title = "Under 5: Phenotype Change"
+p=phenotype_change_graph_s(files, my_mean_u2, my_sd_u2, title, is_log=FALSE, xlim_value=4)
+
+p
+
+```
+
+```{r trasformation under 2, echo=FALSE}
+
+files <- list.files(path="~/Desktop/findparams/under_2", pattern="file_*", full.names=TRUE, recursive=FALSE)
+
+title1 = "Under 2: Newt trasnformed vs un-trasformed"
+title2 = "Under 2: Snake trasnformed vs un-trasformed"
+graph = untrasform(files, my_mean_u2, my_sd_u2, title1, title2, is_log=FALSE)
+graph[1]
+graph[2]
+
+```

### 2021-08-10 graphs_newt_snakes/find_params.Rmd
trying to see what is normal in my simulations and running pairs of numbers for slim. Made find params nicer

@@
 output:
+  html_document: default
   pdf_document: default
-  html_document: default
 ---
@@
 if(is_log==FALSE){
+  if((abs(the_mean)-the_sd*10 < min_difference_1) & (abs(the_mean)+the_sd*10 > max_difference_1)){
     p = p + ylim(abs(the_mean)-the_sd*10, abs(the_mean)+the_sd*10)
+  }else{p = p + ylim(min_difference_1-the_sd*5, max_difference_1+the_sd*5)}
+
 }
@@
 title = "Under 5: Difference Between Phenotypes (Snakes-Newts)"
-p = differnce_graph(files, mean_mean_dif_u5, sd_mean_dif_u5, min_difference_1_u5, max_difference_1_u5, title, is_log=FALSE)
+p = differnce_graph(files, mean_mean_dif_u5, sd_mean_dif_u5, min_difference_u5, max_difference_u5, title, is_log=FALSE)
 
@@
 
-Wow, theses simulations are very different from each other
+Wow, theses simulations are very different from each other.
+Is there more variation between individuals when the average phenotype is higher.
+What do I expect from a normal run?
+How might the msprime impact the results?
+Like if there was a few more mutations in one species than the other, how whould I be able to compare different simulations?
+
+# Looking at the difference between phenotypes for under 2
+
+Here I graph the difference between phenotypes (snake resistance - newt toxicity).
+I sort of expected them to be "strait lines" because the newt and snake would be coevolving with each other.
+In this case two are slightly increasing?, but the difference seems to be close to 0.
+The other line is staying flat and snake resistance is higher than newt toxicity.
+Is this what I expect?
+
+Extra notes:
+
+* Found a way to make the limits on the graph nicer so they don't leave out any line (hopefully)
+* This time around the differences between the phenotypes was smaller than the paramiters used for under 5
 
@@
 title = "Under 2: Difference Between Phenotypes (Snakes-Newts)"
-p = differnce_graph(files, mean_mean_dif_u2, sd_mean_dif_u2, min_difference_1_u2, max_difference_1_u2, title, is_log=FALSE)
+p = differnce_graph(files, mean_mean_dif_u2, sd_mean_dif_u2, min_difference_u2, max_difference_u2, title, is_log=FALSE)
 
@@
 
+# Looking at the Phenotype change for under 2
+
+I graphed the starting and end mean phenotype for both the snakes and newts.
+The arrow points the way that the phenotype has moved (up = an increase, down = a decrease).
+Here the arrows look a lot smaller than the arrows for the under 5 experiment, but that might just be because of the very few experiments that I ran.
+
+These are the simulation numbers:
+
+1. sigma = 0.3, mu = 1.111111e-11
+2. sigma = 0.1, mu = 1e-10
+3. sigma = 0.2, mu = 2.5e-11
+
 ```{r pheno change for under 2, echo=FALSE}
@@
 files <- list.files(path="~/Desktop/findparams/under_2", pattern="file_*", full.names=TRUE, recursive=FALSE)
-title = "Under 5: Phenotype Change"
+title = "Under 2: Phenotype Change"
 p=phenotype_change_graph_s(files, my_mean_u2, my_sd_u2, title, is_log=FALSE, xlim_value=4)
@@
 ```
+
+I wonder if the difference between the starting mean phenotype will have an effect on the direction and lenght of the arrow? This could be just the randomness of 3 single simulations.
+
+# Trasforming the under 2 phenotypes
+
+I look at the un-transformed phenotypes compared to their transformed values.
+I use the mean phenotype values and calculated the phenotypes from this expression, newt pheno = exp(inds_n.sumOfMutationsOfType(m1)/10).
 
@@
 ```
+
+The transformation lines in the under 2 simulations look more linear than in the under 5 simulations.
+This might be do to the range in phenotypes being smaller.
+Based on the max/min and mean phenotypes and the transformation equation nothing seems unexpected.
+
+# Thoghts about next steps.
+
+I think the parameters that I chose are generating the phenotypes that I expect.
+It would be cool to pick one set of parameters (maybe sigma = 0.2, mu = 1.5625e-10) and do two things.
+One I would like to run a bunch of short simulations and see what a normal range of values are.
+Second I would like to extend the number of generations and see if the pheotypes keep increasing forever.
+
+I also want to start collecting more information, but I am not sure what information I should be collecting.
+Right now I have these columns `r colnames(read.table(files[1], header = TRUE))` and information recored in the trees

### 2021-08-10 graphs_newt_snakes/narmal_sim.Rmd
trying to see what is normal in my simulations and running pairs of numbers for slim. Made find params nicer

---
title: "What is a Normal Simulation Like"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)

#setwd("~/Desktop/Proposal Old Drafts")
```

# Goals

I will try to discern what a typical simulation looks like. I attempt to do this by looking at many simulations under the same parameters. There are 110 simulations for a combination. I don't think 100 repeated simulations will cover all the possible outcomes, but it will be a good beginning.

The first set of simulations I will look at parameters of sigma = 0.2, mu = 1.5625e-10. I will look at the means and standard deviation for each of the simulations over the 1000 generations. I am going to specifically look at the similarities and differences between each of theses simulations. I predict that they  will look similar at the beginning and vary as the amount of generations increases.

Newts and  snakes should evenly have the higher phenotype (be about 50-50).

- collect the means, highs, lows, and sds for the phenotypes of newts and snakes

thinking of making a data frame for each thing to look at columns -> generation, rows -> trials

```{r, making data frames}

making_data_frames <- function(files, spe_col) {
i=1
for (current_file in files){
  #print(current_file)
  if(i ==1){
    file <- read.table(current_file, header = TRUE)

    file[[spe_col]][file[[spe_col]] == "NULL"] <- NA

    file %>% 
      select(spe_col, gen) %>%
      #rownames_to_column() %>% 
      gather(variable, value, -gen) %>% 
      spread(gen, value) -> new_file

    new_file$variable[i] <- paste0(spe_col,"_trial_", i)
    i = i + 1
    next
    }
  file <- read.table(current_file, header = TRUE)

  file[[spe_col]][file[[spe_col]] == "NULL"] <- NA

file %>% 
  select(spe_col, gen) %>%
  #rownames_to_column() %>% 
  gather(variable, value, -gen) %>% 
  spread(gen, value) -> temp_file

temp_file$variable[1] <- paste0(spe_col,"_trial_", i)

new_file<-rbind(new_file, temp_file)
i = i + 1
}
return(new_file)
}

```

```{r, making figures}
phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE){
  data_frame_newt_temp <- Newt_file
  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]

  data_frame_snake_temp <- Snake_file
  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]

  Number <- colnames(data_frame_newt_temp)
  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
  data_frame_newt$type <- "Newt"
  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
  data_frame_snake$type <- "Snake"

 combo <- rbind(data_frame_newt, data_frame_snake)

 small_combo <- aggregate(as.numeric(combo$value),by=list(Number=as.numeric(combo$Number),type=combo$type),data=combo,FUN=mean, na.action = TRUE)

if(boxy==TRUE){
  p <- ggplot(combo) +
  #xlim(0, 1000)+
    ggtitle(title, subtitle = subt) +
    xlab("Generation") + ylab("Average Phenotypes")+
    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
    theme(plot.title = element_text(size=5)) +
    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(value), color=type) )
  }
if(boxy==FALSE){
  p <- ggplot(small_combo) +
  #xlim(0, 1000)+
    ggtitle(title, subtitle = subt) +
    xlab("Generation") + ylab("Average Phenotypes")+
    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
    theme(plot.title = element_text(size=5)) +
    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    geom_point(aes(x=factor(as.numeric(Number)), y=as.numeric(x), color=type) )
}

return(p)
}

```

```{r, data collection}

files <- list.files(path="~/Desktop/findparams_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)

file <- read.table(files[1], header = TRUE)

Newt_mean <- making_data_frames(files, all_of("Newt_mean_Pheno"))
Newt_min <- making_data_frames(files, all_of("Newt_min_Pheno"))
Newt_max <- making_data_frames(files, all_of("Newt_max_Pheno"))
Newt_sd <- making_data_frames(files, all_of("Newt_sd_Pheno"))
Snake_mean <- making_data_frames(files, all_of("Snake_mean_Pheno"))
Snake_min <- making_data_frames(files, all_of("Snake_min_Pheno"))
Snake_max <- making_data_frames(files, all_of("Snake_max_Pheno"))
Snake_sd <- making_data_frames(files, all_of("Snake_sd_Pheno"))
```

```{r, comparative figures for sigma = 0.2, mu = 1.5625e-10}
sp<-phenotype_boxplot(Newt_mean, Snake_mean, title="Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10")
sp

sdp<-phenotype_boxplot(Newt_sd, Snake_sd, title="Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE)
sdp

```

### 2021-08-11 graphs_newt_snakes/narmal_sim.Rmd
working on making figures to see what a normal simulation looks like. Added a bunch of new plots that compare the simulations with the same params to each other

@@
 library(tidyverse)
+require(reshape2)
 
@@
 
-Newts and  snakes should evenly have the higher phenotype (be about 50-50).
+Newts and  snakes should evenly have the larger phenotype (be about 50-50).
 
@@
     file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
-
+      # might want to change to all_of(spe_col)
     file %>% 
@@
 
+starting_end_comparison <- function(Newt_file, Snake_file, title, subt, f_point, l_point){
+
+  test_newt_mean<-dplyr::select(Newt_file, c(f_point,l_point))
+  test_newt_mean %>% 
+  rename(
+    "newt_start" = f_point,
+    "newt_end" = l_point
+    ) -> test_newt_mean
+
+  test_snake_mean<-dplyr::select(Snake_file, c(f_point, l_point))
+  test_snake_mean %>% 
+  rename(
+    "snake_start" = f_point,
+    "snake_end" = l_point
+    ) -> test_snake_mean
+  all_points <- cbind(test_newt_mean, test_snake_mean)
+  newt_adv_beg<- as.numeric(all_points$newt_start)- as.numeric(all_points$snake_start) >0
+  newt_adv_end<- as.numeric(all_points$newt_end)- as.numeric(all_points$snake_end) >0
+
+  data_frame_all_points<- data.frame(newt_adv_beg, newt_adv_end)
+  data_frame_all_points <- gather(data_frame_all_points, )
+
+  all_points.count<-as.data.frame(table(data_frame_all_points))
+
+  ggplot(all_points.count, aes(factor(key), (Freq/ nrow(test_newt_mean)), fill = value)) + geom_bar(stat="identity", position = "dodge") +
+    ggtitle(title, subtitle = subt) +
+    scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Snakes", "Newts"))+
+    xlab("Counts") + ylab("Frequency")+ scale_x_discrete(labels=c("Begining", "Ending"))+
+    theme_bw()
+
+}
+
+phenotype_trends <- function(file, title, subt, my_color, is_log=FALSE){
+  data_frame_temp <- as.data.frame(t(file))
+
+  colnames(data_frame_temp) <- data_frame_temp[1,]
+  names(data_frame_temp) <- colnames(data_frame_temp)
+  steps <- colnames(file[ , !(names(file) %in% "variable")])
+data_frame_temp <- data_frame_temp[-1, ] 
+data_frame_temp$steps <- as.numeric(unlist(steps))
+
+  graph_file <- melt(data_frame_temp,  id.vars = 'steps', variable.name = 'series')
+
+    p <- ggplot(graph_file, aes(steps, as.numeric(value))) + geom_line(aes(colour = series))+ 
+    ggtitle(title, subtitle = subt) +
+    scale_color_manual(values = rep(my_color, nrow(file)))+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw() + theme(legend.position="none")
+
+    if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Phenotype (Log)")
+    }
+    return(p)
+}
+
+phenotype_dif_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE){
+  data_frame_newt_temp <- Newt_file
+  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]
+
+  data_frame_snake_temp <- Snake_file
+  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]
+
+  Number <- colnames(data_frame_newt_temp)
+  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
+  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
+  dif <- as.numeric(data_frame_snake$value)-as.numeric(data_frame_newt$value)
+
+  df_dif <- as.data.frame(dif)
+  df_dif$Number <- as.numeric(data_frame_newt$Number)
+  df_dif$trial <- rep(Newt_mean$variable, ncol(Newt_mean)-1)
+  if(boxy==TRUE){
+ p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(dif)), color="darkolivegreen" )
+ }
+ if(boxy==FALSE){
+   p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_line(aes(x=as.numeric(Number), y=as.numeric(dif), color=trial ))+ 
+     theme(legend.position="none")+
+     scale_color_manual(values = rep("darkolivegreen", nrow(Newt_file)))
+
+ }
+  return(p)
+}
+
 ```
@@
 ```{r, comparative figures for sigma = 0.2, mu = 1.5625e-10}
-sp<-phenotype_boxplot(Newt_mean, Snake_mean, title="Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10")
+sp<-phenotype_boxplot(Newt_mean, Snake_mean, title="Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE)
 sp
@@
 
+sp2<-phenotype_boxplot(Newt_mean, Snake_mean, title="Averaging the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=FALSE)
+sp2
+
+sdp2<-phenotype_boxplot(Newt_sd, Snake_sd, title="Averaging the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=FALSE)
+sdp2
+
+sec<-starting_end_comparison(Newt_mean, Snake_mean, title="Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, Mean)", subt="sigma = 0.2, mu = 1.5625e-10", f_point="1", l_point="1000")
+sec
+
+sdsec<-starting_end_comparison(Newt_sd, Snake_sd, title="Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, SD)", subt="sigma = 0.2, mu = 1.5625e-10", f_point="1", l_point="1000")
+sdsec
+
+n<-phenotype_trends(Newt_mean, title="Newt Average Phenotype Trends By Generations", subt="sigma = 0.2, mu = 1.5625e-10", my_color="darkred", is_log=FALSE)
+n
+
+s<-phenotype_trends(Snake_mean, title="Snake Average Phenotype Trends By Generations", subt="sigma = 0.2, mu = 1.5625e-10", my_color="Steelblue", is_log=FALSE)
+s
+
+bp <- phenotype_dif_boxplot(Newt_mean, Snake_mean, title="Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=TRUE)
+bp
+
+bp2 <- phenotype_dif_boxplot(Newt_mean, Snake_mean, title="Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=FALSE)
+bp2
 ```

### 2021-08-11 graphs_newt_snakes/narmal_sim.Rmd
worked on the what is normal r markdown and talked about the results with Peter. Very tired today and have lots of new things to do. I really wish it would cool down.

@@
     file %>% 
-      select(spe_col, gen) %>%
+      select(all_of(spe_col), gen) %>%
       #rownames_to_column() %>% 
@@
 file %>% 
-  select(spe_col, gen) %>%
+  select(all_of(spe_col), gen) %>%
   #rownames_to_column() %>% 
@@
 ```{r, making figures}
-phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE){
+phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0){
   data_frame_newt_temp <- Newt_file
@@
   data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]
+
+   if(section==TRUE){
+
+   selcol = seq(1,ncol(data_frame_newt_temp), section_num)
+   data_frame_newt_temp <- data_frame_newt_temp %>% select(all_of(selcol))
+   data_frame_snake_temp <- data_frame_snake_temp %>% select(all_of(selcol))
+
+ }
 
@@
   rename(
-    "newt_start" = f_point,
-    "newt_end" = l_point
+    "newt_start" = all_of(f_point),
+    "newt_end" = all_of(l_point)
     ) -> test_newt_mean
@@
   rename(
-    "snake_start" = f_point,
-    "snake_end" = l_point
+    "snake_start" = all_of(f_point),
+    "snake_end" = all_of(l_point)
     ) -> test_snake_mean
@@
     scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Snakes", "Newts"))+
-    xlab("Counts") + ylab("Frequency")+ scale_x_discrete(labels=c("Begining", "Ending"))+
+    xlab("Counts") + ylab("Frequency")+ scale_x_discrete(labels=c("Beginning ", "Ending"))+
     theme_bw()
@@
 
-```{r, comparative figures for sigma = 0.2, mu = 1.5625e-10}
-sp<-phenotype_boxplot(Newt_mean, Snake_mean, title="Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE)
-sp
+# Comparisons
 
-sdp<-phenotype_boxplot(Newt_sd, Snake_sd, title="Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE)
-sdp
+To start I am going to compare newts and snakes starting and ending phenotypes.
+Put more specifically, I will look at each simulation and record which species had a higher phenotype at the beginning and end of each of the simulations.
+The hope is that both newts and snakes have an equal (random) opportunity to have a higher phenotype.
+The ending could be skewed if coevoultion took place (but it is unknown, and I predict that it will be close 1000gen isn't a long time).
+I will look at the difference in the mean phenotype and the difference in standard deviations.
 
-sp2<-phenotype_boxplot(Newt_mean, Snake_mean, title="Averaging the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=FALSE)
-sp2
-
-sdp2<-phenotype_boxplot(Newt_sd, Snake_sd, title="Averaging the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=FALSE)
-sdp2
+```{r, begining and end comparison }
 
@@
 
+```
+
+It looks like newts had a higher mean and sd in the beginning of the simulation more than half of the trials that I ran.
+Probably not statistically significant (thought is to run more simulations to see or look at the other combos that I ran and see if it still happens there).
+The ending phenotypes are strange.
+I do not really know if there is something happening or if the advantage from the beginning of the run is leading to a newt advantage.
+I want to look at the other parameters to see if this is a reoccurring trend.
+
+Next, I want to look at the distribution of mean phenotype values for every 100th generation.
+This will look into how the mean phenotype changes over time.
+I can look at the distributions of the mean and the standard devation of the phenotype.
+
+```{r, comparative figures for sigma = 0.2, mu = 1.5625e-10 change in phenotype}
+sp<-phenotype_boxplot(Newt_mean, Snake_mean, title="Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10)
+sp
+
+sdp<-phenotype_boxplot(Newt_sd, Snake_sd, title="Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10)
+sdp
+
+```
+
+It seems like the mean phenotype of the newts and snakes are not exploding when using this set of parameters.
+It does look like there is more variation in the average phenotypes and sd as the number of generations increased.
+Nothing out of the ordinary.
+
+Here, I will look at the barest of trends.
+Specifically, I will look at the trend of the mean of means and the mean of the standard deviation.
+This will show the average trend that my simulations are taking.
+
+```{r, general trends}
+sp2<-phenotype_boxplot(Newt_mean, Snake_mean, title="Averaging the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=FALSE)
+sp2
+
+sdp2<-phenotype_boxplot(Newt_sd, Snake_sd, title="Averaging the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=FALSE)
+sdp2
+
+```
+
+The phenotypes of newts and snakes are multiplicative, so the sd might go up faster? Is this why the standard devation has the weird curve?
+
+```{r, other figs}
 n<-phenotype_trends(Newt_mean, title="Newt Average Phenotype Trends By Generations", subt="sigma = 0.2, mu = 1.5625e-10", my_color="darkred", is_log=FALSE)

### 2021-08-12 graphs_newt_snakes/Space_display.Rmd
Made space r markdown that talkes generations and phenotypes and make spatial plots and distributions

---
title: "Space Display"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)

#setwd("~/Desktop/Proposal Old Drafts")
```

# Goals

I am trying to see if there are any spatial correlations between newts and snakes. Like any areas with elevated phenotypes with the newts and snakes

MSprime: both_1000_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.init.trees
text: file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt
SLiM: mu_rate_1.11e-11_newt_mu_rate_1.11e-11_snake_mu_effect_sd_0.3_newt_mu_effect_sd_0.3_sigma_0.5_ID_3913371281942_late_1000_.trees
* working on renaming the slim files to have the FN number, but right now I can connect them from the slim id in the .txt file

```{r space plot, echo=FALSE}
space_data <- read.table("~/Desktop/pulled_info_test.txt", header = TRUE)

ggplot(space_data[which(space_data$gen == 1),], aes(x=loc_x, y=loc_y, color=type)) +
    ggtitle("Start Space: Generation 1", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
    xlab("Longitude") + ylab("Latitude")+
    #theme(plot.title = element_text(size=5)) +
    theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+
    geom_point(aes(alpha=ind_phy))

ggplot(space_data[which(space_data$gen == 1000),], aes(x=loc_x, y=loc_y, color=type)) +
    ggtitle("End Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
    xlab("Longitude") + ylab("Latitude")+
    #theme(plot.title = element_text(size=5)) +
    scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Snakes", "Newts"))+
    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+
    theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    geom_point(aes(alpha=ind_phy))

```
# Distributions

Look at the phenotype distributions of newts and snakes in the 1st and 1000th generation. The dashed lines are the mean phenotype values

```{r distribution plot, echo=FALSE}

mu_1gen <- ddply(space_data[which(space_data$gen == 1),], "type", summarise, grp.mean=mean(ind_phy))
mu_1000gen <- ddply(space_data[which(space_data$gen == 1),], "type", summarise, grp.mean=mean(ind_phy))

ggplot(space_data[which(space_data$gen == 1),], aes(x=ind_phy, color=type, fill=type), alpha=0.3) +
  ggtitle("Start Space: Generation 1", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
  xlab("Phenotype") + ylab("Count")+
  geom_histogram(position="identity", alpha=0.3)+
  geom_vline(data=mu_1gen, aes(xintercept=grp.mean, color=type),
             linetype="dashed")+
  scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
  scale_fill_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
  theme_bw()

ggplot(space_data[which(space_data$gen == 1000),], aes(x=ind_phy, color=type, fill=type), alpha=0.3) +
  ggtitle("Start Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
  xlab("Phenotype") + ylab("Count")+
  geom_histogram(position="identity", alpha=0.3)+
  geom_vline(data=mu_1000gen, aes(xintercept=grp.mean, color=type),
             linetype="dashed")+
  scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
  scale_fill_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
  theme_bw()

```

### 2021-08-13 graphs_newt_snakes/narmal_sim.Rmd
I finally fished my notes about what a normal simulation would look like. I also ran the other 5 params combos, but need to think about them a bit more. It was weird that newts started out higher all 6 times, but maybe that is not so weird. There were some NAs that I need to take out of the mean caculation. overall it looks good.

--- 2021-08-10 graphs_newt_snakes/narmal_sim.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 library(ggplot2)
@@
     file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
-
+      # might want to change to all_of(spe_col)
     file %>% 
-      select(spe_col, gen) %>%
+      select(all_of(spe_col), gen) %>%
       #rownames_to_column() %>% 
@@
 ```{r, making figures}
-phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE){
+phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE){
   data_frame_newt_temp <- Newt_file
@@
 
+ if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+
+return(p)
+}
+
+starting_end_comparison <- function(Newt_file, Snake_file, title, subt, f_point, l_point, leg_off=FALSE){
+
+  test_newt_mean<-dplyr::select(Newt_file, c(all_of(f_point),all_of(l_point)))
+  test_newt_mean %>% 
+  rename(
+    "newt_start" = all_of(f_point),
+    "newt_end" = all_of(l_point)
+    ) -> test_newt_mean
+
+  test_snake_mean<-dplyr::select(Snake_file, c(all_of(f_point), all_of(l_point)))
+  test_snake_mean %>% 
+  rename(
+    "snake_start" = all_of(f_point),
+    "snake_end" = all_of(l_point)
+    ) -> test_snake_mean
+  all_points <- cbind(test_newt_mean, test_snake_mean)
+  newt_adv_beg<- as.numeric(all_points$newt_start)- as.numeric(all_points$snake_start) >0
+  newt_adv_end<- as.numeric(all_points$newt_end)- as.numeric(all_points$snake_end) >0
+
+  data_frame_all_points<- data.frame(newt_adv_beg, newt_adv_end)
+  data_frame_all_points <- gather(data_frame_all_points, )
+
+  all_points.count<-as.data.frame(table(data_frame_all_points))
+
+ p <-  ggplot(all_points.count, aes(factor(key), (Freq/ nrow(test_newt_mean)), fill = value)) + geom_bar(stat="identity", position = "dodge") +
+    ggtitle(title, subtitle = subt) +
+    scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Snakes", "Newts"))+
+    xlab("Counts") + ylab("Frequency")+ scale_x_discrete(labels=c("Beginning ", "Ending"))+
+    theme_bw()
+ if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+  return(p)
+}
+
+phenotype_trends <- function(file, title, subt, my_color, is_log=FALSE, leg_off=FALSE){
+  data_frame_temp <- as.data.frame(t(file))
+
+  colnames(data_frame_temp) <- data_frame_temp[1,]
+  names(data_frame_temp) <- colnames(data_frame_temp)
+  steps <- colnames(file[ , !(names(file) %in% "variable")])
+data_frame_temp <- data_frame_temp[-1, ] 
+data_frame_temp$steps <- as.numeric(unlist(steps))
+
+  graph_file <- melt(data_frame_temp,  id.vars = 'steps', variable.name = 'series')
+
+    p <- ggplot(graph_file, aes(steps, as.numeric(value))) + geom_line(aes(colour = series))+ 
+    ggtitle(title, subtitle = subt) +
+    scale_color_manual(values = rep(my_color, nrow(file)))+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw() + theme(legend.position="none")
+
+    if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Phenotype (Log)")
+    }
+     if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+    return(p)
+}
+
+phenotype_dif_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE){
+  data_frame_newt_temp <- Newt_file
+  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]
+
+  data_frame_snake_temp <- Snake_file 
+  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]
+
+  if(section==TRUE){
+
+   selcol = seq(1,ncol(data_frame_newt_temp), section_num)
+   data_frame_newt_temp <- data_frame_newt_temp %>% select(all_of(selcol))
+   data_frame_snake_temp <- data_frame_snake_temp %>% select(all_of(selcol))
+
+ }
+
+  Number <- colnames(data_frame_newt_temp)
+  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
+  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
+  dif <- as.numeric(data_frame_snake$value)-as.numeric(data_frame_newt$value)
+
+  df_dif <- as.data.frame(dif)
+  df_dif$Number <- as.numeric(data_frame_newt$Number)
+
+  if(boxy==TRUE){
+ p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(dif)), color="darkolivegreen" )
+ }
+ if(boxy==FALSE){
+   df_dif$trial <- rep(Newt_file$variable, ncol(Newt_file)-1)
+   p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_line(aes(x=as.numeric(Number), y=as.numeric(dif), color=trial ))+ 
+     theme(legend.position="none")+
+     scale_color_manual(values = rep("darkolivegreen", nrow(data_frame_newt_temp)))
+ }
+   if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
   return(p)
@@
 
-files <- list.files(path="~/Desktop/findparams_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+files <- list.files(path="~/Desktop/findparams_u5_new", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
 
@@
 
-```{r, comparative figures for sigma = 0.2, mu = 1.5625e-10}
-sp<-phenotype_boxplot(Newt_mean, Snake_mean, title="Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10")
-sp
+# Phenotype and SD Comparisons in Newts and Snakes
 
-sdp<-phenotype_boxplot(Newt_sd, Snake_sd, title="Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE)
-sdp
+To start I am going to compare newts and snakes starting and ending phenotypes.
+Put more specifically, I will look at each simulation and record which species had a higher phenotype at the beginning and end of each of the simulations.
+The hope is that both newts and snakes have an equal (random) opportunity to have a higher phenotype.
+The ending could be skewed if coevoultion took place (but it is unknown, and I predict that the phenotypes will be close at 1000gen because it isn't a long time).
+I will look at the difference in the mean phenotype and the difference in standard deviations.
+
+```{r, begining and end comparison }
+
+sec<-starting_end_comparison(Newt_mean, Snake_mean, title="Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, Mean)", subt="sigma = 0.2, mu = 1.5625e-10", f_point="1", l_point="1000")
+
+sdsec<-starting_end_comparison(Newt_sd, Snake_sd, title="Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, SD)", subt="sigma = 0.2, mu = 1.5625e-10", f_point="1", l_point="1000")
+
+grid.arrange(sec, sdsec, nrow=1)
 
 ```
+
+It looks like newts had a higher mean and sd in the beginning of the simulation more than half of the trials that I ran.
+Probably not statistically significant (thought is to run more simulations to see or look at the other combos that I ran and see if it still happens there).
+The ending phenotypes are strange.
+I do not really know if there is something happening or if the advantage from the beginning of the run is leading to a newt advantage.
+I want to look at the other parameters to see if this is a reoccurring trend.
+The species with a higher SD remained close to 50%, in fact it seems to have gotten closer to each other ass the simulations ran on.
+
+# Varation in the Phenotype of Newts and Snakes
+
+Next, I want to look at the distribution of mean phenotype values for every 100th generation.
+This will look into how the mean phenotype changes over time.
+I can look at the distributions of the mean and the standard deviation of the phenotype.
+I predict that the means will increase.
+The slop of the increase should be do to the interaction between species (maybe a larger increase could be obtained by stronger selection?).
+In my simulations there is interspecific an intraspecific interactions.
+I wonder which one (or both?) is having more of an effect on the populations phenotype.
+
+```{r, comparative figures this params}
+sp<-phenotype_boxplot(Newt_mean, Snake_mean, title="Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10)
+
+sdp<-phenotype_boxplot(Newt_sd, Snake_sd, title="Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10)
+
+grid.arrange(sp, sdp, nrow=1)
+```
+
+It seems like the mean phenotype of the newts and snakes are not exploding when using this set of parameters.
+They are however going up very slowly.
+It does look like there is more variation in the average phenotypes and sd as the number of generations increased.
+Nothing out of the ordinary.
+Why do some of the phenotpes in the simulations not increase while others do?
+What makes them different?
+
+# Phenotype Trends of Newts and Snakes
+
+Here, I will look at the barest of trends.
+Specifically, I will look at the trend of the mean of means and the mean of the standard deviation.
+This will show the average trend that my simulations are taking.
+
+```{r, general trends}
+sp2<-phenotype_boxplot(Newt_mean, Snake_mean, title="Averaging the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=FALSE)
+
+sdp2<-phenotype_boxplot(Newt_sd, Snake_sd, title="Averaging the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=FALSE)
+
+grid.arrange(sp2, sdp2, nrow=1)
+
+```
+
+The phenotypes of newts and snakes are multiplicative, so the sd might go up faster?
+Is this why the standard devation has the weird curve?
+There does seem to be some NAs in one of the simulations.
+Did the newts die out?
+
+# Individula Species Phenotype Trends
+
+In this section I am going to look at the general phenotype trend of newts and snakes for all of my simulations.
+In each of these figures there will be just one species (either a snake or a newt).
+This will look at how the phenotype of the newts and snakes change over time.
+I expect that newts and ssnake pheotype will increase over time.
+
+```{r, ind species figs}
+n<-phenotype_trends(Newt_mean, title="Newt Average Phenotype Trends By Generations", subt="sigma = 0.2, mu = 1.5625e-10", my_color="darkred", is_log=FALSE)
+
+s<-phenotype_trends(Snake_mean, title="Snake Average Phenotype Trends By Generations", subt="sigma = 0.2, mu = 1.5625e-10", my_color="Steelblue", is_log=FALSE)
+
+grid.arrange(n, s, nrow=1)
+```
+
+It seems like some of the phenotypes of newts and snakes increases over time, but some seem to not change at all.
+A few of the simulations seem to have a high starting phenotype value, why is this?
+I was expecting to see a smaller start value (around 5 for this set of parameters).
+However, most of the simulation begin under 5.
+I wonder what will happen if I were to set up a fitness cost for having a paarticular phenotype?
+
+# Differences
+
+This section focuses on the difference between the newt and the snake phenotype.
+I predict that the phenotype of the species remain close to each other.
+There is a chance that one species will "escape" and that the difference would be large.
+I expect (from our calculations) that the begining of the simulation the phenotypes of newts and snakes will be close (in all of them, so a stubby boxplot).
+As the generations increase I think that boxplot will grow, maybe due to coevolution maybe do to other factors?
+
+```{r, the differences}
+bp <- phenotype_dif_boxplot(Newt_mean, Snake_mean, title="Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=TRUE, section=TRUE, section_num=10)
+
+bp2 <- phenotype_dif_boxplot(Newt_mean, Snake_mean, title="Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=FALSE, section=FALSE, section_num=0)
+
+grid.arrange(bp, bp2, nrow=1)
+```
+
+The boxplots seem to remain in the center for all of the generations.
+There some points outside of the boxplots that R considers outliers (mostly they are from a particular simulation(s)).
+It seems like the phenotypes are closely matching with each other which is a good sign that they are coevolving (hopefully)?
+
+The last step in this rmarkdown is to check out the other paramiters and note if something seems out of the ordinary. I will split it by where the phenotype is supposed to start.
+
+# Under 5
+
+*For the less than 5* 
+Pairs:
+
+* sigma = 0.1, mu = 6.25e-10
+* sigma = 0.2, mu = 1.5625e-10 <- looked at above 
+* sigma = 0.3, mu = 6.944444e-11
+
+```{r, data collection under 5}
+
+files_0.1 <- list.files(path="~/Desktop/findparams_u5_new", pattern="nu_*6.25", full.names=TRUE, recursive=FALSE)
+
+Newt_mean_01 <- making_data_frames(files_0.1, all_of("Newt_mean_Pheno"))
+Newt_min_01 <- making_data_frames(files_0.1, all_of("Newt_min_Pheno"))
+Newt_max_01 <- making_data_frames(files_0.1, all_of("Newt_max_Pheno"))
+Newt_sd_01 <- making_data_frames(files_0.1, all_of("Newt_sd_Pheno"))
+Snake_mean_01 <- making_data_frames(files_0.1, all_of("Snake_mean_Pheno"))
+Snake_min_01 <- making_data_frames(files_0.1, all_of("Snake_min_Pheno"))
+Snake_max_01 <- making_data_frames(files_0.1, all_of("Snake_max_Pheno"))
+Snake_sd_01 <- making_data_frames(files_0.1, all_of("Snake_sd_Pheno"))
+
+files_0.3 <- list.files(path="~/Desktop/findparams_u5_new", pattern="nu_*6.9", full.names=TRUE, recursive=FALSE)
+
+Newt_mean_03 <- making_data_frames(files_0.3, all_of("Newt_mean_Pheno"))
+Newt_min_03 <- making_data_frames(files_0.3, all_of("Newt_min_Pheno"))
+Newt_max_03 <- making_data_frames(files_0.3, all_of("Newt_max_Pheno"))
+Newt_sd_03 <- making_data_frames(files_0.3, all_of("Newt_sd_Pheno"))
+Snake_mean_03 <- making_data_frames(files_0.3, all_of("Snake_mean_Pheno"))
+Snake_min_03 <- making_data_frames(files_0.3, all_of("Snake_min_Pheno"))
+Snake_max_03 <- making_data_frames(files_0.3, all_of("Snake_max_Pheno"))
+Snake_sd_03 <- making_data_frames(files_0.3, all_of("Snake_sd_Pheno"))
+
+```
+
+# Phenotype and SD Comparisons in Newts and Snakes
+
+```{r, begining and end comparison under 5}
+
+z<-starting_end_comparison(Newt_mean_01, Snake_mean_01, title="0.1: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, Mean)", subt="sigma = 0.1, mu = 6.25e-10", f_point="1", l_point="1000", leg_off = TRUE)
+
+y<-starting_end_comparison(Newt_sd_01, Snake_sd_01, title="0.1: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, SD)", subt="sigma = 0.1, mu = 6.25e-10", f_point="1", l_point="1000", leg_off = TRUE)
+
+x<-starting_end_comparison(Newt_mean_03, Snake_mean_03, title="0.3: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, Mean)", subt="sigma = 0.3, mu = 6.94e-11", f_point="1", l_point="1000", leg_off = TRUE)
+
+w<-starting_end_comparison(Newt_sd_03, Snake_sd_03, title="0.3: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, SD)", subt="sigma = 0.3, mu = 6.94e-11", f_point="1", l_point="1000", leg_off = TRUE)
+
+grid.arrange(z, y, nrow=1)
+grid.arrange( x, w, nrow=1)
+```
+
+# Varation in the Phenotype of Newts and Snakes
+
+```{r, comparative figures for u5}
+a<-phenotype_boxplot(Newt_mean_01, Snake_mean_01, title="01 Mean: Variation in Phenotype For N&S by Generation", subt="sigma = 0.1, mu = 6.25e-10", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+b<-phenotype_boxplot(Newt_sd_01, Snake_sd_01, title="01 SD: Variation in Phenotype For N&S by Generation", subt="sigma = 0.1, mu = 6.25e-10", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+c<-phenotype_boxplot(Newt_mean_03, Snake_mean_03, title="03 Mean: Variation in Phenotype For N&S by Generation", subt="sigma = 0.3, mu = 6.94e-11", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+d<-phenotype_boxplot(Newt_sd_03, Snake_sd_03, title="03 SD: Variation in Phenotype For N&S by Generation", subt="sigma = 0.3, mu = 6.94e-11", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+grid.arrange(a, b, nrow=1)
+grid.arrange(c, d, nrow=1)
+
+```
+
+# Individula Species Phenotype Trends
+
+```{r, ind species figs u5}
+n01<-phenotype_trends(Newt_mean_01, title="Newt Average Phenotype Trends By Generations", subt="sigma = 0.1, mu = 6.25e-10", my_color="darkred", is_log=FALSE)
+
+s01<-phenotype_trends(Snake_mean_01, title="Snake Average Phenotype Trends By Generations", subt="sigma = 0.1, mu = 6.25e-10", my_color="Steelblue", is_log=FALSE)
+
+n03<-phenotype_trends(Newt_mean_03, title="Newt Average Phenotype Trends By Generations", subt="sigma = 0.3, mu = 6.94e-11", my_color="darkred", is_log=FALSE)
+
+s03<-phenotype_trends(Snake_mean_03, title="Snake Average Phenotype Trends By Generations", subt="sigma = 0.3, mu = 6.94e-11", my_color="Steelblue", is_log=FALSE)
+
+grid.arrange(n01, s01,nrow=1)
+grid.arrange(n03, s03, nrow=1)
+```
+
+# Phenotype Trends of Newts and Snakes Under 5
+
+```{r, general trends under 5}
+e<-phenotype_boxplot(Newt_mean_01, Snake_mean_01, title="01 Mean: Averaging For N&S by Generation", subt="sigma = 0.1, mu = 6.25e-10", boxy=FALSE)
+
+f<-phenotype_boxplot(Newt_sd_01, Snake_sd_01, title="01 SD: Averaging For N&S by Generation", subt="sigma = 0.1, mu = 6.25e-10", boxy=FALSE)
+
+g<-phenotype_boxplot(Newt_mean_01, Snake_mean_03, title="03 Mean: Averaging For N&S by Generation", subt="sigma = 0.3, mu = 6.94e-11", boxy=FALSE)
+
+h<-phenotype_boxplot(Newt_sd_01, Snake_sd_03, title="03 SD: Averaging For N&S by Generation", subt="sigma = 0.3, mu = 6.94e-11", boxy=FALSE)
+
+grid.arrange(e, f, nrow=1)
+grid.arrange(g, h, nrow=1)
+
+```
+
+# Differences U5
+
+```{r, the differences u5}
+h <- phenotype_dif_boxplot(Newt_mean_01, Snake_mean_01, title="Differences", subt="sigma = 0.1, mu = 6.25e-10",boxy=TRUE, section=TRUE, section_num=10)
+
+i <- phenotype_dif_boxplot(Newt_mean_01, Snake_mean_01, title="Differences", subt="sigma = 0.1, mu = 6.25e-10",boxy=FALSE, section=FALSE, section_num=0)
+
+j <- phenotype_dif_boxplot(Newt_mean_03, Snake_mean_03, title="Differences", subt="sigma = 0.3, mu = 6.94e-11",boxy=TRUE, section=TRUE, section_num=10)
+
+k <- phenotype_dif_boxplot(Newt_mean_03, Snake_mean_03, title="Differences", subt="sigma = 0.3, mu = 6.94e-11",boxy=FALSE, section=FALSE, section_num=0)
+
+grid.arrange(h, i, nrow=1)
+grid.arrange(j, k, nrow=1)
+```
+
+# Under 2
+*For the less than 2* 
+Pairs:
+
+* sigma = 0.1, mu = 1e-10
+* sigma = 0.2, mu = 2.5e-11
+* sigma = 0.3, mu = 1.111111e-11
+
+```{r, data collection under 2}
+
+files_2_0.1 <- list.files(path="~/Desktop/findparams_u2_new", pattern="nue_*0.1", full.names=TRUE, recursive=FALSE)
+
+Newt_mean_2_01 <- making_data_frames(files_2_0.1, all_of("Newt_mean_Pheno"))
+Newt_min_2_01 <- making_data_frames(files_2_0.1, all_of("Newt_min_Pheno"))
+Newt_max_2_01 <- making_data_frames(files_2_0.1, all_of("Newt_max_Pheno"))
+Newt_sd_2_01 <- making_data_frames(files_2_0.1, all_of("Newt_sd_Pheno"))
+Snake_mean_2_01 <- making_data_frames(files_2_0.1, all_of("Snake_mean_Pheno"))
+Snake_min_2_01 <- making_data_frames(files_2_0.1, all_of("Snake_min_Pheno"))
+Snake_max_2_01 <- making_data_frames(files_2_0.1, all_of("Snake_max_Pheno"))
+Snake_sd_2_01 <- making_data_frames(files_2_0.1, all_of("Snake_sd_Pheno"))
+
+files_2_0.2 <- list.files(path="~/Desktop/findparams_u2_new", pattern="nue_*0.2", full.names=TRUE, recursive=FALSE)
+
+Newt_mean_2_02 <- making_data_frames(files_2_0.2, all_of("Newt_mean_Pheno"))
+Newt_min_2_02 <- making_data_frames(files_2_0.2, all_of("Newt_min_Pheno"))
+Newt_max_2_02 <- making_data_frames(files_2_0.2, all_of("Newt_max_Pheno"))
+Newt_sd_2_02 <- making_data_frames(files_2_0.2, all_of("Newt_sd_Pheno"))
+Snake_mean_2_02 <- making_data_frames(files_2_0.2, all_of("Snake_mean_Pheno"))
+Snake_min_2_02 <- making_data_frames(files_2_0.2, all_of("Snake_min_Pheno"))
+Snake_max_2_02 <- making_data_frames(files_2_0.2, all_of("Snake_max_Pheno"))
+Snake_sd_2_02 <- making_data_frames(files_2_0.2, all_of("Snake_sd_Pheno"))
+
+files_2_0.3 <- list.files(path="~/Desktop/findparams_u2_new", pattern="nue_*0.3", full.names=TRUE, recursive=FALSE)
+
+Newt_mean_2_03 <- making_data_frames(files_2_0.3, all_of("Newt_mean_Pheno"))
+Newt_min_2_03 <- making_data_frames(files_2_0.3, all_of("Newt_min_Pheno"))
+Newt_max_2_03 <- making_data_frames(files_2_0.3, all_of("Newt_max_Pheno"))
+Newt_sd_2_03 <- making_data_frames(files_2_0.3, all_of("Newt_sd_Pheno"))
+Snake_mean_2_03 <- making_data_frames(files_2_0.3, all_of("Snake_mean_Pheno"))
+Snake_min_2_03 <- making_data_frames(files_2_0.3, all_of("Snake_min_Pheno"))
+Snake_max_2_03 <- making_data_frames(files_2_0.3, all_of("Snake_max_Pheno"))
+Snake_sd_2_03 <- making_data_frames(files_2_0.3, all_of("Snake_sd_Pheno"))
+```
+
+# Phenotype and SD Comparisons in Newts and Snakes
+
+```{r, begining and end comparison under 2}
+
+a2<-starting_end_comparison(Newt_mean_2_01, Snake_mean_2_01, title="0.1: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, Mean)", subt="sigma = 0.1, mu = 1e-10", f_point="1", l_point="1000", leg_off = FALSE)
+
+b2<-starting_end_comparison(Newt_sd_2_01, Snake_sd_2_01, title="0.1: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, SD)", subt="sigma = 0.1, mu = 1e-10", f_point="1", l_point="1000", leg_off = FALSE)
+
+c2<-starting_end_comparison(Newt_mean_2_02, Snake_mean_2_02, title="0.2: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, Mean)", subt="sigma = 0.2, mu = 2.5e-11", f_point="1", l_point="1000", leg_off = FALSE)
+
+d2<-starting_end_comparison(Newt_sd_2_02, Snake_sd_2_02, title="0.2: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, SD)", subt="sigma = 0.2, mu = 2.5e-11", f_point="1", l_point="1000", leg_off = FALSE)
+
+e2<-starting_end_comparison(Newt_mean_2_03, Snake_mean_2_03, title="0.3: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, Mean)", subt="sigma = 0.3, mu = 1.11e-11", f_point="1", l_point="1000", leg_off = FALSE)
+
+f2<-starting_end_comparison(Newt_sd_2_03, Snake_sd_2_03, title="0.3: Comparison of Starting and Ending Newt and Snake Phenotypes (Larger, SD)", subt="sigma = 0.3, mu = 1.11e-11", f_point="1", l_point="1000", leg_off = FALSE)
+
+grid.arrange(a2, b2, nrow=1)
+grid.arrange(c2, d2, nrow=1)
+grid.arrange(e2, f2, nrow=1)
+```
+
+# Varation in the Phenotype of Newts and Snakes
+
+```{r, comparative figures for u2}
+p1<-phenotype_boxplot(Newt_mean_2_01, Snake_mean_2_01, title="01 Mean: Variation in Phenotype For N&S by Generation", subt="sigma = 0.1, mu = 1e-10", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+p2<-phenotype_boxplot(Newt_sd_2_01, Snake_sd_2_01, title="01 SD: Variation in Phenotype For N&S by Generation", subt="sigma = 0.1, mu = 1e-10", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+p3<-phenotype_boxplot(Newt_mean_2_02, Snake_mean_2_02, title="02 Mean: Variation in Phenotype For N&S by Generation", subt="sigma = 0.2, mu = 2.5e-11", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+p4<-phenotype_boxplot(Newt_sd_2_02, Snake_sd_2_02, title="02 SD: Variation in Phenotype For N&S by Generation", subt="sigma = 0.2, mu = 2.5e-11", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+p5<-phenotype_boxplot(Newt_mean_2_03, Snake_mean_2_03, title="03 Mean: Variation in Phenotype For N&S by Generation", subt="sigma = 0.3, mu = 1.11e-11", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+p6<-phenotype_boxplot(Newt_sd_2_03, Snake_sd_2_03, title="03 SD: Variation in Phenotype For N&S by Generation", subt="sigma = 0.3, mu = 1.11e-11", boxy=TRUE, section=TRUE, section_num=10, leg_off = TRUE)
+
+grid.arrange(p1, p2, nrow=1)
+grid.arrange(p3, p4, nrow=1)
+grid.arrange(p5, p6, nrow=1)
+```
+
+# Individula Species Phenotype Trends
+
+```{r, ind species figs u2}
+n21<-phenotype_trends(Newt_mean_2_01, title="Newt Average Phenotype Trends By Generations", subt="sigma = 0.1, mu = 1e-10", my_color="darkred", is_log=FALSE)
+
+s21<-phenotype_trends(Snake_mean_2_01, title="Snake Average Phenotype Trends By Generations", subt="sigma = 0.1, mu = 1e-10", my_color="Steelblue", is_log=FALSE)
+
+n22<-phenotype_trends(Newt_mean_2_02, title="Newt Average Phenotype Trends By Generations", subt="sigma = 0.2, mu = 2.5e-11", my_color="darkred", is_log=FALSE)
+
+s22<-phenotype_trends(Snake_mean_2_02, title="Snake Average Phenotype Trends By Generations", subt="sigma = 0.2, mu = 2.5e-11", my_color="Steelblue", is_log=FALSE)
+
+n23<-phenotype_trends(Newt_mean_2_03, title="Newt Average Phenotype Trends By Generations", subt="sigma = 0.3, mu = 1.11e-11", my_color="darkred", is_log=FALSE)
+
+s23<-phenotype_trends(Snake_mean_2_03, title="Snake Average Phenotype Trends By Generations", subt="sigma = 0.3, mu = 1.11e-11", my_color="Steelblue", is_log=FALSE)
+
+grid.arrange(n21, s21, nrow=1)
+grid.arrange(n22, s22, nrow=1)
+grid.arrange(n23, s23, nrow=1)
+```
+
+# Phenotype Trends of Newts and Snakes Under 5
+
+```{r, general trends under 2}
+q1<-phenotype_boxplot(Newt_mean_2_01, Snake_mean_2_01, title="01 Mean: Averaging For N&S by Generation", subt="sigma = 0.1, mu = 1e-10", boxy=FALSE)
+
+q2<-phenotype_boxplot(Newt_sd_2_01, Snake_sd_2_01, title="01 SD: Averaging For N&S by Generation", subt="sigma = 0.1, mu = 1e-10", boxy=FALSE)
+
+q3<-phenotype_boxplot(Newt_mean_2_02, Snake_mean_2_02, title="02 Mean: Averaging For N&S by Generation", subt="sigma = 0.2, mu = 2.5e-11", boxy=FALSE)
+
+q4<-phenotype_boxplot(Newt_sd_2_02, Snake_sd_2_02, title="02 SD: Averaging For N&S by Generation", subt="sigma = 0.2, mu = 2.5e-11", boxy=FALSE)
+
+q5<-phenotype_boxplot(Newt_mean_2_03, Snake_mean_2_03, title="03 Mean: Averaging For N&S by Generation", subt="sigma = 0.3, mu = 1.11e-11", boxy=FALSE)
+
+q6<-phenotype_boxplot(Newt_sd_2_03, Snake_sd_2_03, title="03 SD: Averaging For N&S by Generation", subt="sigma = 0.3, mu = 1.11e-11", boxy=FALSE)
+
+grid.arrange(q1, q2, nrow=1)
+grid.arrange(q3, q4, nrow=1)
+grid.arrange(q5, q6, nrow=1)
+
+```
+
+# Differences U2
+
+* sigma = 0.1, mu = 1e-10
+* sigma = 0.2, mu = 2.5e-11
+* sigma = 0.3, mu = 1.11e-11
+
+```{r, the differences u2}
+w1 <- phenotype_dif_boxplot(Newt_mean_2_01, Snake_mean_2_01, title="Differences", subt="sigma = 0.1, mu = 1e-10",boxy=TRUE, section=TRUE, section_num=10)
+
+w2 <- phenotype_dif_boxplot(Newt_mean_2_01, Snake_mean_2_01, title="Differences", subt="sigma = 0.1, mu = 1e-10",boxy=FALSE, section=FALSE, section_num=0)
+
+w3 <- phenotype_dif_boxplot(Newt_mean_2_02, Snake_mean_2_02, title="Differences", subt="sigma = 0.2, mu = 2.5e-11",boxy=TRUE, section=TRUE, section_num=10)
+
+w4 <- phenotype_dif_boxplot(Newt_mean_2_03, Snake_mean_2_03, title="Differences", subt="sigma = 0.2, mu = 2.5e-11",boxy=FALSE, section=FALSE, section_num=0)
+
+w5 <- phenotype_dif_boxplot(Newt_mean_2_03, Snake_mean_2_03, title="Differences", subt="sigma = 0.3, mu = 1.11e-11",boxy=TRUE, section=TRUE, section_num=10)
+
+w6 <- phenotype_dif_boxplot(Newt_mean_2_03, Snake_mean_2_03, title="Differences", subt="sigma = 0.3, mu = 1.11e-111",boxy=FALSE, section=FALSE, section_num=0)
+
+grid.arrange(w1, w2, nrow=1)
+grid.arrange(w3, w4, nrow=1)
+grid.arrange(w5, w6, nrow=1)
+```
+
+Will try to write more later 08/13/2021

### 2021-08-17 graphs_newt_snakes/Space_display.Rmd
this is the slim script i wrote to read in files and an ID to print out the 1st and 1000 generation phenotypes and locations
worked on improving the distribution figures and the files that it needs

@@
 ```{r space plot, echo=FALSE}
-space_data <- read.table("~/Desktop/pulled_info_test.txt", header = TRUE)
+space_data <- read.table("~/Desktop/Coevo/newt_snake/data/space_test/pulled_info_test.txt", header = TRUE)
+
+space_data$made_max= 0
+
+space_data$made_max<- ifelse(space_data$gen == 1 & space_data$type == "Newt", max(space_data[which(space_data$gen == 1 & space_data$type == "Newt"),]$ind_phy), 
+                             ifelse(space_data$gen == 1 & space_data$type == "Snake", max(space_data[which(space_data$gen == 1000 & space_data$type == "Snake"),]$ind_phy),
+                                    ifelse(space_data$gen == 1000 & space_data$type == "Newt", max(space_data[which(space_data$gen == 1000 & space_data$type == "Newt"),]$ind_phy), 
+                                           ifelse(space_data$gen == 1000 & space_data$type == "Snake", max(space_data[which(space_data$gen == 1000 & space_data$type == "Snake"),]$ind_phy), 0))))
+
+space_data$my_alpha <- space_data$ind_phy/space_data$made_max
 
@@
     theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
-    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+
-    geom_point(aes(alpha=ind_phy))
+    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+
+    geom_point(aes(alpha=ind_phy))+
+    scale_alpha_continuous(name = "Phenotype")
 
@@
     #theme(plot.title = element_text(size=5)) +
-    scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Snakes", "Newts"))+
-    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+
+    scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Newts", "Snakes"))+
+    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+
     theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
-    geom_point(aes(alpha=ind_phy))
+    geom_point(aes(alpha=ind_phy))+
+    scale_alpha_continuous(name = "Phenotype")
+
+ggplot(space_data[which(space_data$gen == 1),], aes(x=loc_x, y=loc_y, color=type)) +
+    ggtitle("Start Space: Generation 1", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
+    xlab("Longitude") + ylab("Latitude")+
+    #theme(plot.title = element_text(size=5)) +
+    theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+
+    geom_point(aes(alpha=my_alpha))+
+    scale_alpha_continuous(name = "Percentage")
+
+ggplot(space_data[which(space_data$gen == 1000),], aes(x=loc_x, y=loc_y, color=type)) +
+    ggtitle("End Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
+    xlab("Longitude") + ylab("Latitude")+
+    geom_point(aes(alpha=my_alpha, color=type)) +
+    scale_alpha_continuous(name = "Percentage")+
+    #theme(plot.title = element_text(size=5)) +
+    scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Newts", "Snakes"))+
+    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+
+    theme_bw()  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
 
@@
              linetype="dashed")+
-  scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
-  scale_fill_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
+  scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+ 
+  scale_fill_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+ 
   theme_bw()
@@
 ggplot(space_data[which(space_data$gen == 1000),], aes(x=ind_phy, color=type, fill=type), alpha=0.3) +
-  ggtitle("Start Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
+  ggtitle("End Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
   xlab("Phenotype") + ylab("Count")+

### 2021-08-17 graphs_newt_snakes/space_assemble.R

@@ -1,0 +1,97 @@
+#!/usr/bin/env Rscript
+# Plotting 4 plots on one png for the assembly line 
+args = commandArgs(trailingOnly=TRUE)
+# Packages
+library(ggplot2)
+library(gridExtra)
+library(plyr)
+
+#save_file="~/Desktop/pulled_info_test"
+save_file=args[1]
+folder_name=args[2]
+png(paste0(folder_name, "/", save_file, ".png"), width=800,height=1000)
+
+#path_to_file="~/Desktop/Coevo/newt_snake/data/space_test/pulled_info_test.txt"
+#text_sub_title="file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt"
+path_to_file=args[3]
+text_sub_title=args[4]
+space_data <- read.table(path_to_file, header = TRUE)
+
+space_data$made_max= 0
+
+space_data$made_max<- ifelse(space_data$gen == 1 & space_data$type == "Newt", max(space_data[which(space_data$gen == 1 & space_data$type == "Newt"),]$ind_phy), 
+                             ifelse(space_data$gen == 1 & space_data$type == "Snake", max(space_data[which(space_data$gen == 1000 & space_data$type == "Snake"),]$ind_phy),
+                                    ifelse(space_data$gen == 1000 & space_data$type == "Newt", max(space_data[which(space_data$gen == 1000 & space_data$type == "Newt"),]$ind_phy), 
+                                           ifelse(space_data$gen == 1000 & space_data$type == "Snake", max(space_data[which(space_data$gen == 1000 & space_data$type == "Snake"),]$ind_phy), 0))))
+
+space_data$my_alpha <- space_data$ind_phy/space_data$made_max
+
+p1<-ggplot(space_data[which(space_data$gen == 1),], aes(x=loc_x, y=loc_y, color=type)) +
+  ggtitle("Start Space: Generation 1", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
+  xlab("Longitude") + ylab("Latitude")+
+  #theme(plot.title = element_text(size=5)) +
+  theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
[…]

### 2021-08-17 graphs_newt_snakes/space_assemble.R
split the explination file into 2 to keep them strait. One is about the files and structer on the cluster the other is for the experiment I run - their explination and the files on my computer. Also I saved what I did on space_assemble which was make 6 figures and have the pheotype shading be a percentage and not what the phenotype is, it made it a bit easier to see the blue.

@@ -91,7 +91,7 @@ p6<-ggplot(space_data[which(space_data$gen == 1000),], aes(x=ind_phy, color=type
   scale_fill_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+ 
   theme_bw()
 
-grid.arrange(p1, p2, p3, p4, 
-             ncol = 2, nrow = 2)
+grid.arrange(p1, p2, p3, p4, p5, p6,
+             ncol = 2, nrow = 3)
 
 dev.off()

### 2021-08-24 graphs_newt_snakes/is_it_drift.Rmd
I looked at the data about food and added im my thoughts. I also wrote about the no mutation simulations

---
title: "Is It Drift?"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
setwd("~/Desktop/Coevo/graphs_newt_snakes")
```

## The Goal of this R Markdown is to determine if the increase in the Newt and Snake phenotypes is caused by drift

Background:

In the newts and snakes 1on1 simulations I noticed that the mean phenotype of newts and snakes increased at a steady rate. If the mean newt phenotype was higher than the mean snake phenotype at the beginning of the simulation, it would still be higher at the end of the simulation. This is somewhat expected, because its better for the newts to be more toxic than the snakes can handle. To be able to eat the newts, snakes need to increase their resistance. It makes since that both of the phenotypes increased, but it is weird that they never seemed to cross. It is also possible that these phenotypes increase because of drift.

![u2 red higher](data/phenotype_dis_sample/u2_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_3372316791.png)
![u2 blue higher](data/phenotype_dis_sample/u2_su_1e-10_nu_1e-10_sue_0.1_nue_0.1_2843220669.png)

⁩
I also noticed the distribution of newt and snake phenotypes were different between the under 5 and under 2 simulations. The under 2 were more normal while the under 5 had a long right tail. If I use the values for under 5 I could get more extreme phenotypes for some newts or snakes.

![u5 distribution](data/phenotype_dis_sample/u5_su_1.56e-10_nu_1.56e-10_sue_0.2_nue_0.2_506026437.png)

These observations lead me to ask, is drift causing the the mean of the higher phenotype to stay higher or is it selection?
To attempt to answer this question I will look at two things. 1 How many newts kill snakes (and vice-versa). 2 What would happen if there were no mutations (no genetic variation) and an artificial (beneficial) mutation was released into the population.

## The Newt and Snake Interaction

I have the mean amount and sd of newts and snakes that have been eaten by the opposite species. This info will hopefully give me an idea on how the newts and snakes are interacting.

```{r, making data frames}

making_data_frames <- function(files, spe_col) {
i=1
for (current_file in files){
 # print(current_file)

  if(i ==1){
    file <- read.table(current_file, header = TRUE)

    file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
      # might want to change to all_of(spe_col)
    file %>% 
      select(all_of(spe_col), gen) %>%
      #rownames_to_column() %>% 
      gather(variable, value, -gen) %>% 
      spread(gen, value) -> new_file

    new_file$variable[i] <- paste0(spe_col,"_trial_", i)
    i = i + 1
    next
    }
  file <- read.table(current_file, header = TRUE)

  file[[spe_col]][file[[spe_col]] == "NULL"] <- NA

file %>% 
  select(all_of(spe_col), gen) %>%
  #rownames_to_column() %>% 
  gather(variable, value, -gen) %>% 
  spread(gen, value) -> temp_file

temp_file$variable[1] <- paste0(spe_col,"_trial_", i)

new_file<-rbind(new_file, temp_file)
i = i + 1
}
return(new_file)
}

```

```{r, making figures}

phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE, x_label, y_label){
  data_frame_newt_temp <- Newt_file
  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]

  data_frame_snake_temp <- Snake_file
  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]

   if(section==TRUE){

   selcol = seq(1,ncol(data_frame_newt_temp), section_num)
   data_frame_newt_temp <- data_frame_newt_temp %>% select(all_of(selcol))
   data_frame_snake_temp <- data_frame_snake_temp %>% select(all_of(selcol))

 }

  Number <- colnames(data_frame_newt_temp)
  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
  data_frame_newt$type <- "Newt"
  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
  data_frame_snake$type <- "Snake"

 combo <- rbind(data_frame_newt, data_frame_snake)

 small_combo <- aggregate(as.numeric(combo$value),by=list(Number=as.numeric(combo$Number),type=combo$type),data=combo,FUN=mean, na.action = TRUE)

if(boxy==TRUE){
  p <- ggplot(combo) +
  #xlim(0, 1000)+
    ggtitle(title, subtitle = subt) +
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
    theme(plot.title = element_text(size=5)) +
    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(value), color=type) )
  }
if(boxy==FALSE){
  p <- ggplot(small_combo) +
  #xlim(0, 1000)+
    ggtitle(title, subtitle = subt) +
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
    theme(plot.title = element_text(size=5)) +
    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    geom_point(aes(x=factor(as.numeric(Number)), y=as.numeric(x), color=type) )
}

 if(leg_off==TRUE){
 p = p+ theme(legend.position = "none")}

return(p)
}

var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE){

  data_frame_newt_temp_x <- Newt_file_x
  data_frame_newt_temp_x <- data_frame_newt_temp_x[ , !(names(data_frame_newt_temp_x) %in% "variable")]

  data_frame_snake_temp_x <- Snake_file_x
  data_frame_snake_temp_x <- data_frame_snake_temp_x[ , !(names(data_frame_snake_temp_x) %in% "variable")]

  data_frame_newt_temp_y <- Newt_file_y
  data_frame_newt_temp_y <- data_frame_newt_temp_y[ , !(names(data_frame_newt_temp_y) %in% "variable")]

  data_frame_snake_temp_y <- Snake_file_y
  data_frame_snake_temp_y <- data_frame_snake_temp_y[ , !(names(data_frame_snake_temp_y) %in% "variable")]

  Number <- colnames(data_frame_newt_temp_x)
  data_frame_newt_x <- gather(data_frame_newt_temp_x, Number, value_x)
  data_frame_newt_x$type <- "Newt"
  data_frame_newt_y <- gather(data_frame_newt_temp_y, Number, value_y)
  data_frame_newt <- cbind(data_frame_newt_x, data_frame_newt_y)
  data_frame_newt <- data_frame_newt[-4]
  data_frame_snake_x <- gather(data_frame_snake_temp_x, Number, value_x)
  data_frame_snake_x$type <- "Snake"
  data_frame_snake_y <- gather(data_frame_snake_temp_y, Number, value_y)
  data_frame_snake <- cbind(data_frame_snake_x, data_frame_snake_y)
  data_frame_snake <- data_frame_snake[-4]

 combo <- rbind(data_frame_newt, data_frame_snake)
 combo_s <- combo[sample(nrow(combo), nrow(combo)), ]

p <- ggplot(combo_s) +
  #xlim(0, 1000)+
    ggtitle(title, subtitle = subt) +
    xlab(x_label) + ylab(y_label)+
    geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color=type), alpha=0.1)+
    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
    theme(plot.title = element_text(size=5)) +
    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
  if(logy==TRUE){
    p = p + scale_y_log10()
  }
  return(p)

}

```

Important things to look at:
mean_newts_eaten and mean_snakes_eaten (mean of #eaten/age)
sd_newts_eaten and sd_snakes_eaten (sd of #eaten/age)
Newt_pop_size and Snake_pop_size
Newt_density and Snake_density

```{r, food data input}

files <- list.files(path="~/Desktop/food/u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)

file <- read.table(files[1], header = TRUE)

Newt_mean <- making_data_frames(files, all_of("Newt_mean_Pheno"))
Newt_sd <- making_data_frames(files, all_of("Newt_sd_Pheno"))
Snake_mean <- making_data_frames(files, all_of("Snake_mean_Pheno"))
Snake_sd <- making_data_frames(files, all_of("Snake_sd_Pheno"))
mean_newts_eaten <- making_data_frames(files, all_of("mean_newts_eaten"))
mean_snakes_eaten <- making_data_frames(files, all_of("mean_snakes_eaten"))
sd_newts_eaten <- making_data_frames(files, all_of("sd_newts_eaten"))
sd_snakes_eaten <- making_data_frames(files, all_of("sd_snakes_eaten"))
Newt_pop_size <- making_data_frames(files, all_of("Newt_pop_size"))
Snake_pop_size <- making_data_frames(files, all_of("Snake_pop_size"))
Newt_density <- making_data_frames(files, all_of("Newt_density"))
Snake_density <- making_data_frames(files, all_of("Snake_density"))

```

To make sure my simulations are working correctly, I am going to graph the mean and standard deviation of newt and snake phenotypes by generation. I expect the mean phenotype to increase as the number of generations increase (because it has in the other simulations). I will also graph the mean and  standard deviation of the number of newts and snakes eaten by the other species (color indicates species that was killed). I predict that number of newts/snakes killed by the other species to increase as the number of generations increases (similar to what the phenotypes do). I also predict that the standard deviation of how many newts and snakes are killed by the other species to increase as the number of generations increases. This thought stems from the idea that the higher a phenotype on individual the more likely this individual will eat more of the other species. Although, this thought might be flawed if one species has a higher phenotype it is possible for 2 things to happen; 1 the other species may also have a high phenotype limiting the chance for successful encounters, or 2 if the species (and its' family & friends) has too high of a phenotype there might not be any of the opposite species around.

```{r, trying to see things by generoration}

sp<-phenotype_boxplot(Newt_mean, Snake_mean, title="Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=5, x_label="Generation", y_label="Average Phenotype")

sdp<-phenotype_boxplot(Newt_sd, Snake_sd, title="Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=5, x_label="Generation", y_label="Average Phenotype")

grid.arrange(sp, sdp, nrow=1)

spf<-phenotype_boxplot(mean_newts_eaten, mean_snakes_eaten, title="Mean Newts and Snakes killed by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=5, x_label="Generation", y_label="Average Killed")

sdpf<-phenotype_boxplot(sd_newts_eaten, sd_snakes_eaten, title="Sd of Newts and Snakes killed by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=5, x_label="Generation", y_label="Average Killed")

grid.arrange(spf, sdpf, nrow=1)
```

The phenotypes of newts and snakes go up as the generations increase. The SD also increases with time. For the amount of newts and snakes killed by the other species seemed to go up from the first generation and then decrease as the number of generations increased. There is a wide range of means for this plot, were some end up really high while others stay really low. It doesn't seem to be following what I had predicted (a higher phenotype = more of the other species killed). To get a better idea of what might influence newts and snakes being killed I will look at the different aspects of the newts and snakes interaction.

To get a better mental image of whats going on with the interaction I will plot density by newts/snakes killed, phenotype by newts/snakes killed, and population size by newts/snakes killed. I predict the density and population size plots should be very similar. I expect that a higher population size = higher density. I predict that as the density/population size increase the number of newts and snakes killed by the other species will increase. I would hope that phenotype by newts/snakes killed would also show an increasing pattern, as the phenotypes got larger the more newts and snakes would be killed. But since it did not look that way in the generation plot, I predict that there is no change in the amount of newts and snakes killed.

```{r, more figures}
p1 <- var_by_var(Newt_density, Snake_density, mean_newts_eaten, mean_snakes_eaten, title="Density vs Food", subt="sigma = 0.2, mu = 1.5625e-10", y_label="Species Killed by the Other Species", x_label="Density" )

p2 <- var_by_var( Newt_mean, Snake_mean, mean_newts_eaten, mean_snakes_eaten, title="Phenotype vs Food", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Phenotype", y_label="Species Killed by the Other Species")

p3 <- var_by_var( Newt_pop_size, Snake_pop_size, mean_newts_eaten, mean_snakes_eaten, title="Population Size vs Food", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Population Size", y_label="Species Killed by the Other Species")

grid.arrange(p1, p3, p2, nrow=2)
```

After plotting these three figures I noticed that density and population size are the same (weird I thought they would be similar not exact). There is a bit of confusion that I had when looking at these plots due to the color. Red is not only the newt density/population size/phenotype, it is also the amount of newts killed. The blue points represent the snake density/population size/phenotype and the amount of snakes killed. (Might refer to them as "newt deaths" and "snake deaths") They do show the trend I was expecting; higher density = more interactions. What I did not expect was the separation of color, newts seem to have lower population sizes and densities, while snakes had a higher population size and density. The strait line at 300 and .25 is from the simulations starting points. I found it weird that the data gets nosier as the population size/density gets to its highest point. Also it looks like the amount of newts and snakes killed by the other species decreases when the population density is over 0.75. Could this be due to one species having a low amount of individuals?

The phenotype vs food is a mess. I am having a lot of trouble seeing a potential trend. Maybe the way I chose to color the points is making this more difficult.

## Is it Coevolution

I ran a second experiment to see if the increase in phenotypes was due to coevolution or just drift. In this second experiment I created two populations with no mutations, every individual had the same phenotype. In the 15th generation I introduced new individuals into a population with a beneficial mutation to see if it would spread to the rest of the population. This mutation could only be passed down through mating and if there were no longer individuals with this mutation it would be lost forever. I fist ran this experiment with the newts being the population to get the mutation and then ran some experiments where the snakes got the mutation. I also ran experiments were both populations got a mutation in the 15th generation. I will repeat the simulation 50 times and record the outcome.

I predict that the mutation will increase and spread through out the population in some, but not all of the populations. But at what point is it drift? or is it selection? What fraction are we looking for?

Starting parameters:
sigma_i = 1, recomb=1e-8, sigma_in = 0.5, *sigma_M = 0.33*,  *K =1*,  SD = sigma_in,  SI = sigma_in,  surs = sigma_in,  SM = SI,  L = 4,  W = 35.0, G = 1e8, FECUN = 1/(L)),  RHO = FECUN/((1+FECUN) * K), initializeRecombinationRate(recomb)

Interaction Constants:
	 *interaction_rate = 0.05*,  PE = 0.1,  w = 10,  c = 0.0, *some_value = 30 (half number of new individuals)*,  *sc_size = 10 (selection coefficient)*

I bolded things that I thought might have an impact on if the mutation would spread

```{r, newt results table}

# experiment giving newt the mutation
Notes <- c("Newts", "interaction rate = 0.07", "sigma_M = 0.4", "sc_size = 0.5","sc_size = 15, some value = 60")

Yes <- c(8, 9, 11, 3, 16)/50
No <- c(42, 41, 39, 47, 34)/50

newt_results_df <- data.frame(Notes, Yes, No)
knitr::kable(newt_results_df, "simple")
```

Seems like having more individuals and a higher selection coefficient lead to the mutation spreading to all of the individuals in the population.

```{r, snake results table}
# experiment giving snake the mutation
Notes <- c("Snakes", "interaction rate = 0.5", "sigma_M = 0.4", "sc_size = 0.5","sc_size = 15, some value = 60")

Yes <- c(7, 10, 4, 0, 19)/50
No <- c(43, 40, 46, 50, 31)/50
snake_results_df <- data.frame(Notes, Yes, No)
knitr::kable(snake_results_df, "simple")
```

This is also the case when snakes get the mutation

```{r, both result table}
Notes <-("sc_size = 15, some vaalue = 60" )

Snake_Yes <- 15/50
Newt_Yes <- 15/50
Snake_No <- 35/50
Newt_No <- 35/50

both_results_df <- data.frame(Notes, Snake_Yes, Newt_Yes, Snake_No, Newt_No)
knitr::kable(both_results_df, "simple")

```

When both species get the mutation I saw each combination happen sometimes the mutation would spread in both the snakes and newts populations. Other times only the mutation woyld only spread in one population and there were time when the mutation dies out in both populations.

### 2021-08-26 srun_scripts/testslim_start_to_end.sh
testing the test slim start to end. it works for me. looked at the no mutation and worked on the beta global vaarables for 1on1

@@ -14,8 +14,8 @@ tag="test" # exrta info to identify what experiment I am workin on
 # Sample paramiter values
 snake_mu_rate=1E-10	
 newt_mu_rate=1E-10
-snake_mu_effect_sd=0.1
-newt_mu_effect_sd=0.1
+snake_mu_effect_sd=0.3
+newt_mu_effect_sd=0.3
 # the msprime file that slim uses (gennerates sgv)
 msprime_file="${datadir}/both_1000_su_${snake_mu_rate}_nu_${newt_mu_rate}_sue_${snake_mu_effect_sd}_nue_${newt_mu_effect_sd}_${tag}.init.trees"
 # help to name the slime file with the paramiters that I use

### 2021-08-26 graphs_newt_snakes/is_it_drift.Rmd
I updated my thoughts and concerces to is it drift R markdown. I also wrote about my next step plans

@@
 
-The phenotype vs food is a mess. I am having a lot of trouble seeing a potential trend. Maybe the way I chose to color the points is making this more difficult.
+The phenotype vs food is a mess.
+I am having a lot of trouble seeing a potential trend.
+Maybe the way I chose to color the points is making this more difficult.
+There probably is no trend.
+It seems like there is no correlation between phenotype and ability to kill the the other species.
+It might be better to look at an individuals' fitness and its ability not to die, in order to determine if having a higher phenotype is beneficial.
 
@@
 Starting parameters:
-sigma_i = 1, recomb=1e-8, sigma_in = 0.5, *sigma_M = 0.33*,  *K =1*,  SD = sigma_in,  SI = sigma_in,  surs = sigma_in,  SM = SI,  L = 4,  W = 35.0, G = 1e8, FECUN = 1/(L)),  RHO = FECUN/((1+FECUN) * K), initializeRecombinationRate(recomb)
+
+- sigma_i = 1, 
+- recomb=1e-8, 
+- sigma_in = 0.5,
+- **sigma_M = 0.33**, 
+- **K =1**, 
+- SD = sigma_in,  
+- SI = sigma_in,  
+- surs = sigma_in, 
+- SM = SI,  
+- L = 4,  
+- W = 35.0, 
+- G = 1e8, 
+- FECUN = 1/(L)),  
+- RHO = FECUN/((1+FECUN) * K), 
+- initializeRecombinationRate(recomb)
 
 Interaction Constants:
-	 *interaction_rate = 0.05*,  PE = 0.1,  w = 10,  c = 0.0, *some_value = 30 (half number of new individuals)*,  *sc_size = 10 (selection coefficient)*
+
+- **interaction_rate = 0.05**,  
+- PE = 0.1,  
+- w = 10,  
+- c = 0.0, 
+- **some_value = 30 (half number of new individuals)**, 
+- **sc_size = 10 (selection coefficient)**
 
 I bolded things that I thought might have an impact on if the mutation would spread
+
+### Newts Get the Mutation
 
@@
 
-Yes <- c(8, 9, 11, 3, 16)/50
-No <- c(42, 41, 39, 47, 34)/50
+Yes <- c(8, 9, 11, 3, 16)/50 * 100
+No <- c(42, 41, 39, 47, 34)/50 * 100
 
@@
 Seems like having more individuals and a higher selection coefficient lead to the mutation spreading to all of the individuals in the population.
+For most of the simulations the spreading out or dying out happens very quickly (under 1500 generations)
+
+###Snakes Get the Mutation
 
@@
 
-Yes <- c(7, 10, 4, 0, 19)/50
-No <- c(43, 40, 46, 50, 31)/50
+Yes <- c(7, 10, 4, 0, 19)/50 * 100
+No <- c(43, 40, 46, 50, 31)/50 * 100
 snake_results_df <- data.frame(Notes, Yes, No)
@@
 
-This is also the case when snakes get the mutation
+This is also the case when snakes get the mutation.
+Although it was peculiar when the selection coefficient was very small there were no cases when the artificial mutation spread throughout the population.
+
+###Both Newts and Snakes get the Mutation
 
@@
 
-Snake_Yes <- 15/50
-Newt_Yes <- 15/50
-Snake_No <- 35/50
-Newt_No <- 35/50
+Snake_Yes <- 15/50 * 100
+Newt_Yes <- 15/50 * 100
+Snake_No <- 35/50 * 100
+Newt_No <- 35/50 * 100
 
@@
 When both species get the mutation I saw each combination happen sometimes the mutation would spread in both the snakes and newts populations.
-Other times only the mutation woyld only spread in one population and there were time when the mutation dies out in both populations.
+Other times only the mutation would only spread in one population and there were time when the mutation dies out in both populations.
+
+Concluding notes:
+
+The artificial mutation either stays in the population increasing rapidly or dies out in a few generations, suggesting that the mutation is spreading due to selection.
+The mutation does spread do to selection, but I think it can be quicker and I am not sure if it is due to the interaction between snakes and newts.
+I want to increase the rate of the interaction without creating areas where newts and snakes don't interact (holes).
+I also want to test the prediction that a higher phenotype might protect an individual from death.
+First, I will look at the correlation between phenotype and fitness (a measure of how likely an individual will survive) and see if they are positively or negatively correlated.
+However, there might be problems crease by spatial structure that might impact the correlation.
+So, the second thing I will do is crease and run a no space simulation to see the direct consequence the interaction had on individuals phenotypes.
+The only problem is determining how many newt and snakes will be interacting with each other?

### 2021-08-30 graphs_newt_snakes/is_it_drift.Rmd
I looked at the interaction between the differece between snake and newt phenotypes and the amount of newts and snakes killed. I got a strange result and am wondering why? I also started the selection coefficients rmarkdown. I want to see if there is a corelation between phenotype and survibility.

@@
 
-var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE){
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE){
 
@@
 
+ if(subtract_x==FALSE){
    combo <- rbind(data_frame_newt, data_frame_snake)
    combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
-
    p <- ggplot(combo_s) +
@@
       theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+ }
+ if(subtract_x==TRUE){
+    subtract_val <- data_frame_snake_x$value_x - data_frame_newt_x$value_x
+    total_sub_dataframe <- data.frame(subtract_val, data_frame_newt_y$value_y, data_frame_snake_y$value_y)
+    total_sub_dataframe <- total_sub_dataframe[sample(nrow(total_sub_dataframe), nrow(total_sub_dataframe)), ]
+    colnames(total_sub_dataframe) <- c("SnakeMisNewt_Pheno","Newts_Killed","Snakes_Killed")
+     p <- ggplot(total_sub_dataframe) +
+      #xlim(0, 1000)+
+       ggtitle(title, subtitle = subt) +
+       xlab(x_label) + ylab(y_label)+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Newts_Killed), color="Newts_Killed"), alpha=0.1)+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Snakes_Killed), color="Snakes_Killed"), alpha=0.1)+
+        scale_colour_manual(name = "Species", values = c("Newts_Killed" = "darkred", "Snakes_Killed" = "steelblue"))+
+        theme(plot.title = element_text(size=5)) +
+        theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+}
   if(logy==TRUE){
@@
 It might be better to look at an individuals' fitness and its ability not to die, in order to determine if having a higher phenotype is beneficial.
+
+## What About The Difference between Phenotypes??
+
+It is possible that there might be an interaction between the phenotypes of newts and snakes and the amount of newts and snakes killed by the opposite species.
+To see if there might be a rough interaction I will look at the difference between the mean snake and the mean newt phenotype (snakes-newts) and the amount of individuals killed by the other species per year they  have been alive.
+I predict that when the phenotypess are similar there will be an equal amount of newts and snakes killed.
+When the phenotypes are different I will predict that the species with the higher phenotype will be killed less.
+
+```{r, pheno difference and amount killed}
+
+p4 <- var_by_var( Newt_mean, Snake_mean, mean_newts_eaten, mean_snakes_eaten, title="Phenotype Differences vs Individals Killed", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Mean Phenotype Difference (Snake - Newt)", y_label="Species Killed by the Other Species", subtract_x=TRUE)
+
+p4
+```
+
+This is the opposite of what I thought would occur.
+So much so I am triple checking the code.
+This figure makes it seem like there are more snakes killed the higher the snake phenotype is.
+Or there are less newts killed the higher the phenotype for the snake.
+Maybe this is an indication that newts and snakes are competing so that there are area of high resistance and areas of high toxicity which can cancel each other out but still produce a high mean phenotype?
+This seems very weird to me!
+I would need to look at the difference between individuals phenotypes based on their locations and then see where the killed values are coming from.
+Very strange result.
 

### 2021-08-30 graphs_newt_snakes/selection_coefficients.Rmd
I looked at the interaction between the differece between snake and newt phenotypes and the amount of newts and snakes killed. I got a strange result and am wondering why? I also started the selection coefficients rmarkdown. I want to see if there is a corelation between phenotype and survibility.

---
title: "Selection Coefficients"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
```

## My Goals

The goal of this experiment is to see if there is a link between the phenotype of a newt or snake and its ability to survive. This prediction stems from the idea that if a phenotype is higher in a newt or snake, the individual will survive an interaction with the opposite species. To look at this I will calculate the correlation between an individuals phenotype and an individuals SLiM fitnessScaling. There are some potential problems with this calculation, like space (some areas one phenotype might be beneficial, but it others not) and that the interaction is not very strong.

Beta calculation for the Newt: beta_n = cor(phenotypes_n, inds_n.fitnessScaling);
Beta calculation for the Snake:	beta_s = cor(phenotypes_s, inds_s.fitnessScaling);
**Must be calculated in early. fitnessScaling set to 0 if newt or snake is killed by the opposite species, but what about interspecific interactions (density dependence)**

## The interaction of Newts and Snakes

I was wondering how often newts and snakes interact in a SLiMulation so I had SLiM print out four values, snake_found_newt (when a snake was potentially able to find  a newt), newt_found (a snake found a newt), snake_deaths (snakes that were killed by newts), and newt_deaths (newts that were eaten by snakes). I also added the population size for newts and snakes to see in the number of interactions depend on the population size - which is linked to density. It looks like one the population size stabilizes (around 100 generations) there are 30-60 interactions each generation. Today 8/30/2021 I will run 20 of the same simulation to see if I can get a consensus on how many times newts and snake interact in each generation. Once I get this value I can plug it into nospace.slim to compare the results of the same simulation to a simulation with a lack of space. This will hopefully help me understand how space effects the coevolution of newts and snakes

## No Space SLiM Results

### 2021-08-30 graphs_newt_snakes/selection_coefficients.Rmd
I am working on finding the link between phenotype and surviverablity and thining about how to correctly set up no space slim

@@
 library(plyr)
+library(gridGraphics)
+library(grid)
 ```
@@
 
+```{r, making data frames}
+
+making_data_frames <- function(files, spe_col) {
+i=1
+for (current_file in files){
+ # print(current_file)
+
+  if(i ==1){
+    file <- read.table(current_file, header = TRUE)
+
+    file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+      # might want to change to all_of(spe_col)
+    file %>% 
+      select(all_of(spe_col), gen) %>%
+      #rownames_to_column() %>% 
+      gather(variable, value, -gen) %>% 
+      spread(gen, value) -> new_file
+
+    new_file$variable[i] <- paste0(spe_col,"_trial_", i)
+    i = i + 1
+    next
+    }
+  file <- read.table(current_file, header = TRUE)
+
+  file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+
+file %>% 
+  select(all_of(spe_col), gen) %>%
+  #rownames_to_column() %>% 
+  gather(variable, value, -gen) %>% 
+  spread(gen, value) -> temp_file
+
+temp_file$variable[1] <- paste0(spe_col,"_trial_", i)
+
+new_file<-rbind(new_file, temp_file)
+i = i + 1
+}
+return(new_file)
+}
+
+```
+
+```{r, making resueable figures}
+
+phenotype_trends <- function(file, title, subt, my_color, is_log=FALSE, leg_off=FALSE){
+  data_frame_temp <- as.data.frame(t(file))
+
+  colnames(data_frame_temp) <- data_frame_temp[1,]
+  names(data_frame_temp) <- colnames(data_frame_temp)
+  steps <- colnames(file[ , !(names(file) %in% "variable")])
+data_frame_temp <- data_frame_temp[-1, ] 
+data_frame_temp$steps <- as.numeric(unlist(steps))
+
+  graph_file <- melt(data_frame_temp,  id.vars = 'steps', variable.name = 'series')
+
+    p <- ggplot(graph_file, aes(steps, as.numeric(value))) + geom_line(aes(colour = series))+ 
+    ggtitle(title, subtitle = subt) +
+    scale_color_manual(values = rep(my_color, nrow(file)))+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw() + theme(legend.position="none")
+
+    if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Phenotype (Log)")
+    }
+     if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+    return(p)
+}
+
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE){
+
+  data_frame_newt_temp_x <- Newt_file_x
+  data_frame_newt_temp_x <- data_frame_newt_temp_x[ , !(names(data_frame_newt_temp_x) %in% "variable")]
+
+  data_frame_snake_temp_x <- Snake_file_x
+  data_frame_snake_temp_x <- data_frame_snake_temp_x[ , !(names(data_frame_snake_temp_x) %in% "variable")]
+
+  data_frame_newt_temp_y <- Newt_file_y
+  data_frame_newt_temp_y <- data_frame_newt_temp_y[ , !(names(data_frame_newt_temp_y) %in% "variable")]
+
+  data_frame_snake_temp_y <- Snake_file_y
+  data_frame_snake_temp_y <- data_frame_snake_temp_y[ , !(names(data_frame_snake_temp_y) %in% "variable")]
+
+  Number <- colnames(data_frame_newt_temp_x)
+  data_frame_newt_x <- gather(data_frame_newt_temp_x, Number, value_x)
+  data_frame_newt_x$type <- "Newt"
+  data_frame_newt_y <- gather(data_frame_newt_temp_y, Number, value_y)
+  data_frame_newt <- cbind(data_frame_newt_x, data_frame_newt_y)
+  data_frame_newt <- data_frame_newt[-4]
+  data_frame_snake_x <- gather(data_frame_snake_temp_x, Number, value_x)
+  data_frame_snake_x$type <- "Snake"
+  data_frame_snake_y <- gather(data_frame_snake_temp_y, Number, value_y)
+  data_frame_snake <- cbind(data_frame_snake_x, data_frame_snake_y)
+  data_frame_snake <- data_frame_snake[-4]
+
+ if(subtract_x==FALSE){
+   combo <- rbind(data_frame_newt, data_frame_snake)
+   combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
+   p <- ggplot(combo_s) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color=type), alpha=0.1)+
+      scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+ }
+ if(subtract_x==TRUE){
+    subtract_val <- data_frame_snake_x$value_x - data_frame_newt_x$value_x
+    total_sub_dataframe <- data.frame(subtract_val, data_frame_newt_y$value_y, data_frame_snake_y$value_y)
+    total_sub_dataframe <- total_sub_dataframe[sample(nrow(total_sub_dataframe), nrow(total_sub_dataframe)), ]
+    colnames(total_sub_dataframe) <- c("SnakeMisNewt_Pheno","Newts_Killed","Snakes_Killed")
+     p <- ggplot(total_sub_dataframe) +
+      #xlim(0, 1000)+
+       ggtitle(title, subtitle = subt) +
+       xlab(x_label) + ylab(y_label)+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Newts_Killed), color="Newts_Killed"), alpha=0.1)+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Snakes_Killed), color="Snakes_Killed"), alpha=0.1)+
+        scale_colour_manual(name = "Species", values = c("Newts_Killed" = "darkred", "Snakes_Killed" = "steelblue"))+
+        theme(plot.title = element_text(size=5)) +
+        theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+}
+  if(logy==TRUE){
+    p = p + scale_y_log10()
+  }
+  return(p)
+
+}
+```
+
+```{r, beta info}
+
+```
 ## The interaction of Newts and Snakes
@@
 
+```{r, the amount of interactions, fig.show='hide'}
+
+files <- list.files(path="~/Desktop/Coevo/data/interaction", pattern="txt", full.names=TRUE, recursive=FALSE)
+
+file <- read.table(files[1], header = TRUE)
+#gen    snake_found_newt    newt_found    snake_deaths    newt_deaths    snake_pop_size    newt_pop_size
+
+newt_found <- making_data_frames(files, all_of("newt_found"))
+snake_deaths <- making_data_frames(files, all_of("snake_deaths"))
+newt_deaths <- making_data_frames(files, all_of("newt_deaths"))
+snake_pop_size <- making_data_frames(files, all_of("snake_pop_size"))
+newt_pop_size <- making_data_frames(files, all_of("newt_pop_size"))
+
+hist(unlist(newt_found[ , 2:1001]), col="palevioletred", main="Number of Interactions", xlab="Interactions") 
+abline(v = mean(unlist(newt_found[ , 2:1001])), col = "red", lwd = 2)
+grid.echo()
+a <- grid.grab()
+
+b <- phenotype_trends(newt_found, title="Interaction Trends By Generations", subt="sigma = 0.1, mu = 1.0e-10", my_color="purple", is_log=FALSE)
+
+c <- var_by_var(newt_pop_size, snake_pop_size, newt_found, newt_found, title="Population Size vs Interaction", subt="sigma = 0.1, mu = 1.0e-10", y_label="Interaction", x_label="Population Size" )
+
+d <- var_by_var(newt_found, newt_found, newt_deaths, snake_deaths, title="Interaction vs Deaths", subt="sigma = 0.1, mu = 1.0e-10", y_label="Deaths", x_label="Number of Interactions" )
+
+grid.arrange(a , b, c, d, nrow=2)
+
+```
+
+```{r, interation plot display}
+grid.arrange(a , c, b, d, nrow=2)
+
+```
+
 ## No Space SLiM Results

### 2021-08-31 graphs_newt_snakes/selection_coefficients.Rmd
making graphes for betas

@@
 
-var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE){
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE){
 
@@
  }
+  if(by_gen==TRUE){
+    combo <- rbind(data_frame_newt, data_frame_snake)
+    combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
+       p <- ggplot(combo_s) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(Number), y=as.numeric(value_y), color=type), alpha=0.1)+
+      scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+}
   if(logy==TRUE){
@@
 ```{r, beta info}
+# graph the betas
+files <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+file <- read.table(files[1], header = TRUE)
+file$Newt_pop_size
+beta_n <- making_data_frames(files, all_of("beta_n"))
+beta_s <- making_data_frames(files, all_of("beta_s"))
+Newt_mean_Pheno <- making_data_frames(files, all_of("Newt_mean_Pheno"))
+Snake_mean_Pheno <- making_data_frames(files, all_of("Snake_mean_Pheno"))
+mean_newts_eaten <- making_data_frames(files, all_of("mean_newts_eaten"))
+mean_snakes_eaten <- making_data_frames(files, all_of("mean_snakes_eaten"))
+newt_deaths <- making_data_frames(files, all_of("newt_deaths"))
+snake_deaths <- making_data_frames(files, all_of("snake_deaths"))
+Newt_age <- making_data_frames(files, all_of("Newt_age"))
+Snake_age <- making_data_frames(files, all_of("Snake_age"))
+Newt_pop_size <- making_data_frames(files, all_of("Newt_pop_size"))
+Snake_pop_size <- making_data_frames(files, all_of("Snake_pop_size"))
+
+var_by_var( beta_n, beta_s, beta_n, beta_s, title="Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, mean_newts_eaten, mean_snakes_eaten, title="Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Deaths/age", subtract_x=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, newt_deaths, snake_deaths, title="Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Deaths", subtract_x=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_pop_size, Snake_pop_size, title="Differnece in mean phenotype by PopSize", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="PopSize", subtract_x=TRUE)
+
+var_by_var(  beta_n, beta_n, beta_s, beta_s, title="Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas")
 

### 2021-08-31 graphs_newt_snakes/selection_coefficients.Rmd
still making beta graphs

--- 2021-08-30 graphs_newt_snakes/selection_coefficients.Rmd
@@
 
-var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE){
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE){
 
@@
  }
+  if(by_gen==TRUE){
+    combo <- rbind(data_frame_newt, data_frame_snake)
+    combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
+       p <- ggplot(combo_s) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(Number), y=as.numeric(value_y), color=type), alpha=0.1)+
+      scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  }
+
+   if(just_two==TRUE){
+     just2 <- cbind(data_frame_newt_x, data_frame_snake_y)
+     just2 <- just2[-4]
+       p <- ggplot(just2) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y)), color = "darkgreen", alpha=0.1)+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  }
   if(logy==TRUE){
@@
 ```{r, beta info}
+# graph the betas
+files <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+file <- read.table(files[1], header = TRUE)
+file$Newt_pop_size
+beta_n <- making_data_frames(files, all_of("beta_n"))
+beta_s <- making_data_frames(files, all_of("beta_s"))
+Newt_mean_Pheno <- making_data_frames(files, all_of("Newt_mean_Pheno"))
+Snake_mean_Pheno <- making_data_frames(files, all_of("Snake_mean_Pheno"))
+mean_newts_eaten <- making_data_frames(files, all_of("mean_newts_eaten"))
+mean_snakes_eaten <- making_data_frames(files, all_of("mean_snakes_eaten"))
+newt_deaths <- making_data_frames(files, all_of("newt_deaths"))
+snake_deaths <- making_data_frames(files, all_of("snake_deaths"))
+Newt_age <- making_data_frames(files, all_of("Newt_age"))
+Snake_age <- making_data_frames(files, all_of("Snake_age"))
+Newt_pop_size <- making_data_frames(files, all_of("Newt_pop_size"))
+Snake_pop_size <- making_data_frames(files, all_of("Snake_pop_size"))
+```
+
+```{r, beta figures}
+var_by_var( beta_n, beta_s, beta_n, beta_s, title="Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, mean_newts_eaten, mean_snakes_eaten, title="Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Deaths/age", subtract_x=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, newt_deaths, snake_deaths, title="Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Deaths", subtract_x=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_pop_size, Snake_pop_size, title="Differnece in mean phenotype by PopSize", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="PopSize", subtract_x=TRUE)
+
+var_by_var(beta_n, beta_s, beta_n, beta_s, title="Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
+
+var_by_var(Newt_mean_Pheno, beta_s, beta_n, Snake_mean_Pheno, title="Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
+
+hist(unlist(beta_n[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), main="Beta Values", xlab="Beta",ylim=c(0,2100)) 
+hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), add = TRUE) 
+abline(v = mean(unlist(beta_n[ , 2:52])), col = rgb(255,192,203, max = 255), lwd = 2)
+abline(v = mean(unlist(beta_s[ , 2:52])), col = rgb(173,216,230, max = 255), lwd = 2)
 

### 2021-09-01 graphs_newt_snakes/selection_coefficients.Rmd
wrote my thoughts about the beta  figures

--- 2021-08-30 graphs_newt_snakes/selection_coefficients.Rmd
@@
 This prediction stems from the idea that if a phenotype is higher in a newt or snake, the individual will survive an interaction with the opposite species.
-To look at this I will calculate the correlation between an individuals phenotype and an individuals SLiM fitnessScaling.
+To look at this I will calculate the correlation between an individuals phenotype and an individuals SLiM fitnessScaling (I am calling it beta).
 There are some potential problems with this calculation, like space (some areas one phenotype might be beneficial, but it others not) and that the interaction is not very strong.
@@
     scale_color_manual(values = rep(my_color, nrow(file)))+
-    xlab("Generations") + ylab("Phenotype")+
+    xlab("Generations") + ylab("Interaction")+
     theme_bw() + theme(legend.position="none")
@@
     if(is_log==TRUE){
-  p = p + scale_y_log10() + ylab("Phenotype (Log)")
+  p = p + scale_y_log10() + ylab("Interaction (Log)")
     }
@@
     total_sub_dataframe <- total_sub_dataframe[sample(nrow(total_sub_dataframe), nrow(total_sub_dataframe)), ]
-    colnames(total_sub_dataframe) <- c("SnakeMisNewt_Pheno","Newts_Killed","Snakes_Killed")
+    colnames(total_sub_dataframe) <- c("SnakeMisNewt_Pheno","Newts","Snakes")
      p <- ggplot(total_sub_dataframe) +
@@
        xlab(x_label) + ylab(y_label)+
-       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Newts_Killed), color="Newts_Killed"), alpha=0.1)+
-       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Snakes_Killed), color="Snakes_Killed"), alpha=0.1)+
-        scale_colour_manual(name = "Species", values = c("Newts_Killed" = "darkred", "Snakes_Killed" = "steelblue"))+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Newts), color="Newts"), alpha=0.1)+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Snakes), color="Snakes"), alpha=0.1)+
+        scale_colour_manual(name = "Species", values = c("Newts" = "darkred", "Snakes" = "steelblue"))+
+        theme(plot.title = element_text(size=5)) +
+        theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+ }
+  if(by_gen==TRUE){
+    combo <- rbind(data_frame_newt, data_frame_snake)
+    combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
+       p <- ggplot(combo_s) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(Number), y=as.numeric(value_y), color=type), alpha=0.1)+
+      scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  }
+
+   if(just_two==TRUE){
+     just2 <- cbind(data_frame_newt_x, data_frame_snake_y)
+     just2 <- just2[-4]
+       p <- ggplot(just2) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y)), color = "darkgreen", alpha=0.1)+
       theme(plot.title = element_text(size=5)) +
@@
 ```{r, beta info}
+# graph the betas
+files <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+#file <- read.table(files[1], header = TRUE)
+beta_n <- making_data_frames(files, all_of("beta_n"))
+beta_s <- making_data_frames(files, all_of("beta_s"))
+Newt_mean_Pheno <- making_data_frames(files, all_of("Newt_mean_Pheno"))
+Snake_mean_Pheno <- making_data_frames(files, all_of("Snake_mean_Pheno"))
+mean_newts_eaten <- making_data_frames(files, all_of("mean_newts_eaten"))
+mean_snakes_eaten <- making_data_frames(files, all_of("mean_snakes_eaten"))
+newt_deaths <- making_data_frames(files, all_of("newt_deaths"))
+snake_deaths <- making_data_frames(files, all_of("snake_deaths"))
+Newt_age <- making_data_frames(files, all_of("Newt_age"))
+Snake_age <- making_data_frames(files, all_of("Snake_age"))
+Newt_pop_size <- making_data_frames(files, all_of("Newt_pop_size"))
+Snake_pop_size <- making_data_frames(files, all_of("Snake_pop_size"))
+```
+
+First, I  will look to see if there is an interaction between the newt and snake phenotypes and the amount of newts and snakes that are being killed (specifically killed by the other species).
+I predict that when snakes have a higher phenotype more newts will be killed and less snakes will be killed.
+When the phenotype of the newt is higher I  predict that more snakes will be killed.
+When the phenotypes of newts and snakes are similar I predict that both newts and snakes will be killed at the same rate.
+Previously, I had seen that there were less newts being killed when the snake phenotype was higher.
+
+```{r, dif of pheno by deatage}
+
+var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, mean_newts_eaten, mean_snakes_eaten, title="Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Deaths/age", subtract_x=TRUE)
+```
+
+I thought the results were strange (seems like less newts dying when snake phenotype is higher) so I looked into further into what might be happening.
+I recorded the number of newt and snake deaths (cause by the other species) every 20 generations and recorded the population sizes for each species.
+
+```{r, indepth obv of phenotype and surviver}
+ps1 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, newt_deaths, snake_deaths, title="Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Deaths", subtract_x=TRUE)
+
+ps2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_pop_size, Snake_pop_size, title="Differnece in mean phenotype by PopSize", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="PopSize", subtract_x=TRUE)
+
+grid.arrange(ps1, ps2, nrow=1)
+```
+
+I found that there was an interaction between the difference in phenotype of newts and snakes and survivability of sorts.
+When the phenotype of the snake is higher less snakes were dying, but so where less newts.
+Less newts dying is probably due to the population size of newts being diminished when the phenotype of the snake is high.
+It's possible that the most resistant snakes ate all of the newts in that area and just had fewer newts to eat.
+The reverse also happens when newts have a higher phenotype.
+There are less snakes and newts dying, bit the population size of snakes is small.
+Red and blue xmas tree and X marks the spot.
+
+Next, I look into the betas and am not sure what I expect.
+I know the interaction between newts and snakes is small each generation, but there seems to be some interaction between phenotype and the ability for an individual to survive.
+
+Lets look at the distribution
+
+```{r, beta distribution}
+
+hist(unlist(beta_n[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), main="Beta Values", xlab="Beta",ylim=c(0,2100)) 
+hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), add = TRUE) 
+abline(v = mean(unlist(beta_n[ , 2:52])), col = rgb(255,192,203, max = 255), lwd = 2)
+abline(v = mean(unlist(beta_s[ , 2:52])), col = rgb(173,216,230, max = 255), lwd = 2)
+legend("topright", c("Newt", "Snake"), fill=c(rgb(255,192,203, max = 255), rgb(173,216,230, max = 255)))
 
 ```
+
+The beta values for newts and snakes seem to be similar. The means are also very close.
+
+Lets plot the beta values for the newt against the beta values for the snake.
+
+```{r, comp betas}
+var_by_var(beta_n, beta_s, beta_n, beta_s, title="Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
+
+```
+
+I present to you the green eyeball.
+It looks like there is no correlation between newt beta values and snake beta values.
+Prediction: this might be due to space, some areas might have correlation while other don't.
+**This is one value for the entire area**
+
+Finally, the last few graphs are extra things to look at.
+
+```{r, beta figures}
+g1 <- var_by_var( beta_n, beta_s, beta_n, beta_s, title="Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
+
+g2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
+
+g3 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
+
+g4 <- var_by_var(Newt_mean_Pheno, beta_s, beta_n, Snake_mean_Pheno, title="Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
+
+grid.arrange(g1, g2, g3, g4, nrow=2)
+
+```
+
 ## The interaction of Newts and Snakes
@@
 
+It seems like newts and snakes interact between 20 and 60 times each generation.
+The mean is around 40.
+Snakes also seem to have a higher population size.
+The number of interactions become steady around 150 generations.
+As the number of interactions increase the number of death increase and its even between both species
+
 ## No Space SLiM Results
+
+next one

### 2021-09-02 graphs_newt_snakes/selection_coefficients.Rmd
added some more plots aand wrote some explinaation. I also added more to no space slim to make an interaction rate

@@
 
-```{r, making resueable figures}
+```{r, making resueable figures, results='hide', message=FALSE, warning=FALSE}
 
@@
 
-var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE){
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
 
@@
    }
+
+   if(colored==TRUE){
+     color3 <- cbind(data_frame_newt_x, data_frame_snake_y, data_frame_newt_y)
+     color3 <- color3[-c(1,3,4,6)]
+     suppressWarnings(suppressMessages(suppressPackageStartupMessages({require(scales)})))
+     amin <- 0.1
+     lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
+     lowcol <- paste0("#",   sep = "",
+                 paste(format(lowcol.hex, width = 2), collapse = ""))
+       p <- ggplot(color3) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color = value_y.1))+
+      theme(plot.title = element_text(size=5)) +
+      scale_colour_gradient(high = highcol, low = lowcol) + 
+      labs(colour = color_label) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  }
   if(logy==TRUE){
@@
   }
+
   return(p)
@@
 }
+
 ```
@@
 Red and blue xmas tree and X marks the spot.
+
+Sinse there seems to be an interaction between phenotype and population size, I will look at how the population size lines up with the mean phenotype of newts and snakes.
+I predict that there will be an arc of color ranging from light to dark depending on which species has a higher population size.
+
+```{r, popsize of newts and snakes with color of phenotype}
+vc1 <- var_by_var(Newt_pop_size, Newt_mean_Pheno, Newt_mean_Pheno, Snake_pop_size, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
+
+vc2 <- var_by_var(Newt_pop_size, Snake_mean_Pheno, Snake_mean_Pheno, Snake_pop_size, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")
+
+vc1 
+vc2
+# for(i in 1:107){
+# print(i)
+# Newt_mean_Pheno_1 <- making_data_frames(files[i], all_of("Newt_mean_Pheno"))
+# Snake_mean_Pheno_1 <- making_data_frames(files[i], all_of("Snake_mean_Pheno"))
+# Newt_pop_size_1 <- making_data_frames(files[i], all_of("Newt_pop_size"))
+# Snake_pop_size_1 <- making_data_frames(files[i], all_of("Snake_pop_size"))
+# 
+# naame_of_file= paste0("~/Desktop/figs/both_", i, ".png")
+# png(filename =naame_of_file)
+# vc_11 <- var_by_var(Newt_pop_size_1, Newt_mean_Pheno_1, Newt_mean_Pheno_1, Snake_pop_size_1, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
+# #dev.off()
+# 
+# #naame_of_file_2= paste0("~/Desktop/figs/snakes_", i, ".png")
+# #png(filename = naame_of_file_2)
+# vc_12 <- var_by_var(Newt_pop_size_1, Snake_mean_Pheno_1, Snake_mean_Pheno_1, Snake_pop_size_1, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")
+# print(grid.arrange(vc_11, vc_12))
+# dev.off()
+#}
+```
+
+I made some nice whale graphs!
+When the newt population size is large and the snakes population size is small the newt phenotype is high.
+When the newt population size is small and the snake population size is large the newts have a lower phenotype.
+Something strange happens with the phenotype of the snake, it is higher when the newt population size is large and the snake population size is small.
+The snake phenotype is also high when the snake population size is large and the newt population size is small.
+My theory is that the few remaining snakes in an area of very toxic newts are very resistant, but why don't we see the opposite happening in newts?
+<- this also happens in the snake-newt papers weird.
+I would be wary of the whale graphs because these are a combined results of 107 simulations with a sample collected every 20 generations. It might be different in each separate simulation.
 
@@
 
+Now, I am just going to run some numbers to see what the interaction rate was in my 1on1 slim simulation and what is should be set to in my nospace slim.
+In my 1on1 slimulations I us an interaction rate of 0.05 and surprisingly when I reverse calculate it from the mean number of interactions and mean population size I get 0.05 so it seems like it is working which is good (population specific to snake pop size).
+
+```{r, relationship of interaction and pop size}
+
+population_size = 700
+number_of_interaction = 40
+
+interaction_rate = number_of_interaction/population_size
+
+print(paste0("If the population size is ", population_size, " and the number of interactions is ", number_of_interaction, ", then the interation rate is ", interaction_rate, "."))
+
+population_size = 600
+number_of_interaction = 40
+interaction_rate = number_of_interaction/population_size
+
+print(paste0("If the population size is ", population_size, " and the number of interactions is ", number_of_interaction, ", then the interation rate is ", interaction_rate, "."))
+
+population_size = 800
+number_of_interaction = 40
+interaction_rate = number_of_interaction/population_size
+
+print(paste0("If the population size is ", population_size, " and the number of interactions is ", number_of_interaction, ", then the interation rate is ", interaction_rate, "."))
+
+interaction_rate = 0.05
+population_size = 700
+number_of_interaction = population_size*interaction_rate
+print(paste0("Now if I pick the interaction rate of ", interaction_rate, " and the number of individuals is ", population_size, ", the number of interactions should be ", number_of_interaction))
+
+var_by_var(newt_pop_size, newt_found, newt_found, snake_pop_size, title="Newt VS Snake Population Size Color = Number of Interaction", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Population Size", x_label="Newt Population Size", colored=TRUE, color_label="Interaction")
+
+```
+
+This light green cloud shows that when the population size is larger there are more interactions. This picture reminds me of a rain cloud.
+
+It seems like using the formula population_size*interaction_rate will get me the correct number of interactions every time so I should devise a way to have a normal distribution with a mean around 40.
+
 ## No Space SLiM Results

### 2021-09-03 R_script/test.R
testing git

@@ -5,6 +5,6 @@ file_info<- list.files("data/size", pattern="exp_K") #new files that i turned of
 place<-"data/size/"
 
 split_df = make_dichotomy(file_info, place)
-
+#adding a line for git
 file <- data.frame(split_df[1])
 dichotomy<-data.frame(split_df[2])

### 2021-09-03 R_script/test.R
testing git again

@@ -6,5 +6,6 @@ place<-"data/size/"
 
 split_df = make_dichotomy(file_info, place)
 #adding a line for git
+#second test for git
 file <- data.frame(split_df[1])
 dichotomy<-data.frame(split_df[2])

### 2021-09-03 R_script/test.R
testing git 3rd time

@@ -7,5 +7,6 @@ place<-"data/size/"
 split_df = make_dichotomy(file_info, place)
 #adding a line for git
 #second test for git
+# a third test for good measure
 file <- data.frame(split_df[1])
 dichotomy<-data.frame(split_df[2])

### 2021-09-06 graphs_newt_snakes/interact_between_pheno_popsize.R
I added slim onto the slim file. I also makde a r file to add lines to show how the population size moves throughout the simulation.

@@ -1,0 +1,134 @@
+
+# This r script is to show what happens to a populations phenotype as the 
+# population size of newts and snakes changes.
+
+# My goal here is to graph the population size of newts by the population size 
+# of snakes when the mean phenotype (resistance/toxin) as the color of the points
+
+
+library(ggplot2)
+library(viridis)
+library(colorspace)
+library(gridExtra)
+library(tidyverse)
+require(reshape2)
+library(plyr)
+library(grid)
+library(gridGraphics)
+
+
+making_data_frames <- function(files, spe_col) {
+  i=1
+  for (current_file in files){
+    # print(current_file)
+    
+    if(i ==1){
+      file <- read.table(current_file, header = TRUE)
+      
+      file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+      # might want to change to all_of(spe_col)
+      file %>% 
+        select(all_of(spe_col), gen) %>%
+        #rownames_to_column() %>% 
+        gather(variable, value, -gen) %>% 
+        spread(gen, value) -> new_file
+      
+      new_file$variable[i] <- paste0(spe_col,"_trial_", i)
+      i = i + 1
+      next
+    }
+    file <- read.table(current_file, header = TRUE)
+    
+    file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+    
+    file %>% 
+      select(all_of(spe_col), gen) %>%
+      #rownames_to_column() %>% 
+      gather(variable, value, -gen) %>% 
+      spread(gen, value) -> temp_file
+    
+    temp_file$variable[1] <- paste0(spe_col,"_trial_", i)
+    
+    new_file<-rbind(new_file, temp_file)
+    i = i + 1
+  }
+  return(new_file)
+}
+
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, color_label=NULL, highcol="darkseagreen"){
+  
+  data_frame_newt_temp_x <- Newt_file_x
+  data_frame_newt_temp_x <- data_frame_newt_temp_x[ , !(names(data_frame_newt_temp_x) %in% "variable")]
+  
+  data_frame_snake_temp_x <- Snake_file_x
[…]

### 2021-09-08 graphs_newt_snakes/selection_coefficients.Rmd
I added slim onto the slim file. I also makde a r file to add lines to show how the population size moves throughout the simulation.
added more to reproduction callback to increase the number of offsprings produced. I also made the normal distribution into a pois distribution so that an interger whould be picked. In the selection coefficents r markdown I added a line to calculate the number of interaction in a larger population.
I ran a test to see how many newts would be in a snake's range and added that to the selection coefficents r markdown file. I also made a test python file so that I co

@@
 
+interaction_rate = 0.05
+population_size = 3369
+number_of_interaction = population_size*interaction_rate
+print(paste0("Now if I pick the interaction rate of ", interaction_rate, " and the number of individuals is ", population_size, ", the number of interactions should be ", number_of_interaction))
+
 var_by_var(newt_pop_size, newt_found, newt_found, snake_pop_size, title="Newt VS Snake Population Size Color = Number of Interaction", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Population Size", x_label="Newt Population Size", colored=TRUE, color_label="Interaction")
@@
 
-## No Space SLiM Results
+## How many newts are near a snake???
 
-next one
+I had SLiM print out the amount of newts that were in the range of each newt for 1000 generations.
+The parameters/msprime file were  "newt_snake/data/both_1000_su_1e-10_nu_1e-10_sue_0.1_nue_0.1_try_this_peter.init.trees"
+
+```{r, how many newts in range}
+newts_in_snakes_range <- read.table("~/Desktop/how_many_newts_in_range.txt", header =FALSE)
+
+hist(newts_in_snakes_range$V1, c="darkorchid4", main="Number of Newts Near a Snake", xlab="Number of Newts")
+abline(v = mean(newts_in_snakes_range$V1), col = "black", lwd = 2)
+```
+
+This purple Loch Ness monster represents the number of newts that resign in a particulars snakes range.
+It seems the mean is around 4, so there are on average 4 newts in a snakes range.
+I got these values from this line of slim: i1.nearestNeighborsOfPoint(p1, mPoint, count=1000000), which might be something that I can control (change in the future?).
+
+## No Space SLiM
+
+Trying to make a realistic interaction between newts and snakes without space as a factor.
+I am also trying to make reproduction more realistic.
+
+### Peters thoughts on the factors that will make the interaction more realstic
+
+Suppose that they all live in a rectangular valley measuring **W** x **L** meters square. Each snake moves around in a range of area **As**. Say there are **Ns** snakes and **Nn** newts.
+
+1. How many newts on average are there in the range of a given snake? **As** * **Nn**/**W*****L**
+2. What proportion of newts are within the range of a given snake? (**As** * **Nn**/**W*****L**)**Nn**
+3.
+Suppose that when Nn == Ns we'd like each snake to encounter one newt on average every y years.
+What proportion of the newts within the snake's range should each snake encounter?
+((**As** * **Nn**/**W*****L**)**Nn**)/**y**

### 2021-09-08 python_script/test_python.py

@@ -1,0 +1,4 @@
+import sys
+import numpy as np
+print(sys.version)
+print("hello world")

### 2021-09-10 graphs_newt_snakes/nospace.Rmd
testing differences between space and no space. Begining no space analysis

--- 2021-09-01 graphs_newt_snakes/selection_coefficients.Rmd
@@
 ---
-title: "Selection Coefficients"
+title: "Nospace"
 output: html_document
@@
 
+## No Space?
+
+This is may no space experiment!
+I worked with Peter to make the 1on1 newt-snake simulation into a simulation that is not dependent on space.
+We changed a few things that were dependent on space like reproduction and the interaction, but everything else remained mostly the same.
+
+Some things to not is that in the reproduction callback new individuals will be paced near their parents, but their parents are randomly chosen for anywhere in the simulation.
+Population size is determined by the amount of individuals in the whole area.
+To choose the amount of interactions between newts and snake we use numNeighbors = rbinom(1, p1.individualCount, (interaction_rate * 2 * PI * surs^2)/W^2).
+This will choose a value based on a binomial distribution with the newt population as the size (amount that could be drawn) and a probability of success based on the interaction rate, area a snake and the total area of the simulation.
+
+Extra notes: From a fist glance at the visual output there is a lack of color (color represents phenotype)
+
 ## My Goals
 
-The goal of this experiment is to see if there is a link between the phenotype of a newt or snake and its ability to survive.
-This prediction stems from the idea that if a phenotype is higher in a newt or snake, the individual will survive an interaction with the opposite species.
-To look at this I will calculate the correlation between an individuals phenotype and an individuals SLiM fitnessScaling (I am calling it beta).
-There are some potential problems with this calculation, like space (some areas one phenotype might be beneficial, but it others not) and that the interaction is not very strong.
+The goal of this experiment is to see in there is a change in the newts and snakes phenotype that is not based on spatial interactions.
+Specifically, in this experiment there will be no spatial interaction (between newts and snakes).
+I will compare these results to all of my other simulations data!
 
-Beta calculation for the Newt: beta_n = cor(phenotypes_n, inds_n.fitnessScaling);
-Beta calculation for the Snake:	beta_s = cor(phenotypes_s, inds_s.fitnessScaling);
-**Must be calculated in early. fitnessScaling set to 0 if newt or snake is killed by the opposite species, but what about interspecific interactions (density dependence)**
+## The Specifics of the Simulations
+
+To make these simulations similar to the previous simulation experiments I use the same msprime files to start each of the SLiM simulations. I also keep the parameters the same.
 
@@
 for (current_file in files){
- # print(current_file)
+ #print(current_file)
 
@@
 # graph the betas
-files <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
-#file <- read.table(files[1], header = TRUE)
+files <- list.files(path="~/Desktop/nospace/u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+file <- read.table(files[51], header = TRUE)
 beta_n <- making_data_frames(files, all_of("beta_n"))
@@
 ```
-
-First, I  will look to see if there is an interaction between the newt and snake phenotypes and the amount of newts and snakes that are being killed (specifically killed by the other species).
-I predict that when snakes have a higher phenotype more newts will be killed and less snakes will be killed.
-When the phenotype of the newt is higher I  predict that more snakes will be killed.
-When the phenotypes of newts and snakes are similar I predict that both newts and snakes will be killed at the same rate.
-Previously, I had seen that there were less newts being killed when the snake phenotype was higher.
-
-```{r, dif of pheno by deatage}
-
-var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, mean_newts_eaten, mean_snakes_eaten, title="Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Deaths/age", subtract_x=TRUE)
-```
-
-I thought the results were strange (seems like less newts dying when snake phenotype is higher) so I looked into further into what might be happening.
-I recorded the number of newt and snake deaths (cause by the other species) every 20 generations and recorded the population sizes for each species.
-
-```{r, indepth obv of phenotype and surviver}
-ps1 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, newt_deaths, snake_deaths, title="Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Deaths", subtract_x=TRUE)
-
-ps2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_pop_size, Snake_pop_size, title="Differnece in mean phenotype by PopSize", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="PopSize", subtract_x=TRUE)
-
-grid.arrange(ps1, ps2, nrow=1)
-```
-
-I found that there was an interaction between the difference in phenotype of newts and snakes and survivability of sorts.
-When the phenotype of the snake is higher less snakes were dying, but so where less newts.
-Less newts dying is probably due to the population size of newts being diminished when the phenotype of the snake is high.
-It's possible that the most resistant snakes ate all of the newts in that area and just had fewer newts to eat.
-The reverse also happens when newts have a higher phenotype.
-There are less snakes and newts dying, bit the population size of snakes is small.
-Red and blue xmas tree and X marks the spot.
-
-Next, I look into the betas and am not sure what I expect.
-I know the interaction between newts and snakes is small each generation, but there seems to be some interaction between phenotype and the ability for an individual to survive.
-
-Lets look at the distribution
-
-```{r, beta distribution}
-
-hist(unlist(beta_n[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), main="Beta Values", xlab="Beta",ylim=c(0,2100)) 
-hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), add = TRUE) 
-abline(v = mean(unlist(beta_n[ , 2:52])), col = rgb(255,192,203, max = 255), lwd = 2)
-abline(v = mean(unlist(beta_s[ , 2:52])), col = rgb(173,216,230, max = 255), lwd = 2)
-legend("topright", c("Newt", "Snake"), fill=c(rgb(255,192,203, max = 255), rgb(173,216,230, max = 255)))
-
-```
-
-The beta values for newts and snakes seem to be similar. The means are also very close.
-
-Lets plot the beta values for the newt against the beta values for the snake.
-
-```{r, comp betas}
-var_by_var(beta_n, beta_s, beta_n, beta_s, title="Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
-
-```
-
-I present to you the green eyeball.
-It looks like there is no correlation between newt beta values and snake beta values.
-Prediction: this might be due to space, some areas might have correlation while other don't.
-**This is one value for the entire area**
-
-Finally, the last few graphs are extra things to look at.
-
-```{r, beta figures}
-g1 <- var_by_var( beta_n, beta_s, beta_n, beta_s, title="Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
-
-g2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
-
-g3 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
-
-g4 <- var_by_var(Newt_mean_Pheno, beta_s, beta_n, Snake_mean_Pheno, title="Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
-
-grid.arrange(g1, g2, g3, g4, nrow=2)
-
-```
-
-## The interaction of Newts and Snakes
-
-I was wondering how often newts and snakes interact in a SLiMulation so I had SLiM print out four values, snake_found_newt (when a snake was potentially able to find  a newt), newt_found (a snake found a newt), snake_deaths (snakes that were killed by newts), and newt_deaths (newts that were eaten by snakes).
-I also added the population size for newts and snakes to see in the number of interactions depend on the population size - which is linked to density.
-It looks like one the population size stabilizes (around 100 generations) there are 30-60 interactions each generation.
-Today 8/30/2021 I will run 20 of the same simulation to see if I can get a consensus on how many times newts and snake interact in each generation.
-Once I get this value I can plug it into nospace.slim to compare the results of the same simulation to a simulation with a lack of space.
-This will hopefully help me understand how space effects the coevolution of newts and snakes
-
-```{r, the amount of interactions, fig.show='hide'}
-
-files <- list.files(path="~/Desktop/Coevo/data/interaction", pattern="txt", full.names=TRUE, recursive=FALSE)
-
-file <- read.table(files[1], header = TRUE)
-#gen    snake_found_newt    newt_found    snake_deaths    newt_deaths    snake_pop_size    newt_pop_size
-
-newt_found <- making_data_frames(files, all_of("newt_found"))
-snake_deaths <- making_data_frames(files, all_of("snake_deaths"))
-newt_deaths <- making_data_frames(files, all_of("newt_deaths"))
-snake_pop_size <- making_data_frames(files, all_of("snake_pop_size"))
-newt_pop_size <- making_data_frames(files, all_of("newt_pop_size"))
-
-hist(unlist(newt_found[ , 2:1001]), col="palevioletred", main="Number of Interactions", xlab="Interactions") 
-abline(v = mean(unlist(newt_found[ , 2:1001])), col = "red", lwd = 2)
-grid.echo()
-a <- grid.grab()
-
-b <- phenotype_trends(newt_found, title="Interaction Trends By Generations", subt="sigma = 0.1, mu = 1.0e-10", my_color="purple", is_log=FALSE)
-
-c <- var_by_var(newt_pop_size, snake_pop_size, newt_found, newt_found, title="Population Size vs Interaction", subt="sigma = 0.1, mu = 1.0e-10", y_label="Interaction", x_label="Population Size" )
-
-d <- var_by_var(newt_found, newt_found, newt_deaths, snake_deaths, title="Interaction vs Deaths", subt="sigma = 0.1, mu = 1.0e-10", y_label="Deaths", x_label="Number of Interactions" )
-
-grid.arrange(a , b, c, d, nrow=2)
-
-```
-
-```{r, interation plot display}
-grid.arrange(a , c, b, d, nrow=2)
-
-```
-
-It seems like newts and snakes interact between 20 and 60 times each generation.
-The mean is around 40.
-Snakes also seem to have a higher population size.
-The number of interactions become steady around 150 generations.
-As the number of interactions increase the number of death increase and its even between both species
-
-## No Space SLiM Results
-
-next one

### 2021-09-13 graphs_newt_snakes/nospace.Rmd
worked on describing and comparing the no space simulation results to the spatial simulation results. Some of the reults are suprising

@@
 
-Extra notes: From a fist glance at the visual output there is a lack of color (color represents phenotype)
+Extra notes: From a first glance at the visual output there is a lack of color groups (color represents phenotype)
+
+### Space
+![Space](data/space_pic.png)
+### No Space
+![NoSpace](data/nospace_pic.png)
 
@@
 Specifically, in this experiment there will be no spatial interaction (between newts and snakes).
-I will compare these results to all of my other simulations data!
+I will compare these results to the results of all of my other simulations!
 
@@
 
+phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE, ylim_max=100){
+  data_frame_newt_temp <- Newt_file
+  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]
+
+  data_frame_snake_temp <- Snake_file
+  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]
+
+   if(section==TRUE){
+
+   selcol = seq(1,ncol(data_frame_newt_temp), section_num)
+   data_frame_newt_temp <- data_frame_newt_temp %>% select(all_of(selcol))
+   data_frame_snake_temp <- data_frame_snake_temp %>% select(all_of(selcol))
+
+   }
+   Number <- colnames(data_frame_newt_temp)
+  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
+  data_frame_newt$type <- "Newt"
+  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
+  data_frame_snake$type <- "Snake"
+
+ combo <- rbind(data_frame_newt, data_frame_snake)
+
+ small_combo <- aggregate(as.numeric(combo$value),by=list(Number=as.numeric(combo$Number),type=combo$type),data=combo,FUN=mean, na.action = TRUE)
+
+if(boxy==TRUE){
+  p <- ggplot(combo) +
+    ylim(0, ylim_max)+
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotypes")+
+    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(value), color=type) )
+  }
+if(boxy==FALSE){
+  p <- ggplot(small_combo) +
+  #xlim(0, 1000)+
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotypes")+
+    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_point(aes(x=factor(as.numeric(Number)), y=as.numeric(x), color=type) )
+}
+
+ if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+
+return(p)
+}
+
+phenotype_dif_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE){
+  data_frame_newt_temp <- Newt_file
+  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]
+
+  data_frame_snake_temp <- Snake_file 
+  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]
+
+  if(section==TRUE){
+
+   selcol = seq(1,ncol(data_frame_newt_temp), section_num)
+   data_frame_newt_temp <- data_frame_newt_temp %>% select(all_of(selcol))
+   data_frame_snake_temp <- data_frame_snake_temp %>% select(all_of(selcol))
+
+ }
+
+  Number <- colnames(data_frame_newt_temp)
+  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
+  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
+  dif <- as.numeric(data_frame_snake$value)-as.numeric(data_frame_newt$value)
+
+  df_dif <- as.data.frame(dif)
+  df_dif$Number <- as.numeric(data_frame_newt$Number)
+
+  if(boxy==TRUE){
+ p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(dif)), color="darkolivegreen" )
+ }
+ if(boxy==FALSE){
+   df_dif$trial <- rep(Newt_file$variable, ncol(Newt_file)-1)
+   p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_line(aes(x=as.numeric(Number), y=as.numeric(dif), color=trial ))+ 
+     theme(legend.position="none")+
+     scale_color_manual(values = rep("darkolivegreen", nrow(data_frame_newt_temp)))
+ }
+   if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+  return(p)
+}
+
+phenotype_change_graph_s <- function(files, title, is_log=FALSE, xlim_value){
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=1:144)) +
+  xlim(0, xlim_value)+
+  ggtitle(title) +
+  xlab("Simulation number") + ylab("Phenotype")+
+  theme_bw()
+
+if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Phenotype  (Log)")
+
+}
+
+i=1
+for (current_file in files){
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
+  file <- file[complete.cases(file), ]
+ p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color= darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color=lighten("darkred"))  + 
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color=darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color=lighten("steelblue"))+
+  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1, colour="Newt"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))+
+   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1, colour="Snake"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))
+
+ i = i+1
+}
+p <- p +
+ scale_colour_manual(name = "Species", values = c("Newt" = "darkred", "Snake"="steelblue"))
+return(p)
+}
+
 ```
 
-```{r, beta info}
-# graph the betas
+```{r, data info}
+# Files for No space results
 files <- list.files(path="~/Desktop/nospace/u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
@@
 Snake_mean_Pheno <- making_data_frames(files, all_of("Snake_mean_Pheno"))
+Newt_sd_Pheno <- making_data_frames(files, all_of("Newt_sd_Pheno"))
+Snake_sd_Pheno <- making_data_frames(files, all_of("Snake_sd_Pheno"))
 mean_newts_eaten <- making_data_frames(files, all_of("mean_newts_eaten"))
@@
 Snake_pop_size <- making_data_frames(files, all_of("Snake_pop_size"))
+
+# Files for space results
+files_u5 <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+
+beta_n_s <- making_data_frames(files_u5, all_of("beta_n"))
+beta_s_s <- making_data_frames(files_u5, all_of("beta_s"))
+Newt_mean_Pheno_s <- making_data_frames(files_u5, all_of("Newt_mean_Pheno"))
+Snake_mean_Pheno_s <- making_data_frames(files_u5, all_of("Snake_mean_Pheno"))
+Newt_sd_Pheno_s <- making_data_frames(files_u5, all_of("Newt_sd_Pheno"))
+Snake_sd_Pheno_s <- making_data_frames(files_u5, all_of("Snake_sd_Pheno"))
+mean_newts_eaten_s <- making_data_frames(files_u5, all_of("mean_newts_eaten"))
+mean_snakes_eaten_s <- making_data_frames(files_u5, all_of("mean_snakes_eaten"))
+newt_deaths_s <- making_data_frames(files_u5, all_of("newt_deaths"))
+snake_deaths_s <- making_data_frames(files_u5, all_of("snake_deaths"))
+Newt_age_s <- making_data_frames(files_u5, all_of("Newt_age"))
+Snake_age_s <- making_data_frames(files_u5, all_of("Snake_age"))
+Newt_pop_size_s <- making_data_frames(files_u5, all_of("Newt_pop_size"))
+Snake_pop_size_s <- making_data_frames(files_u5, all_of("Snake_pop_size"))
+
 ```
+
+## The distribution of Phenotypes
+
+see if there is a difference in the distribution of phenotypes between the space and no space simulations. Currently running 9-13-2021
+
+## How Restance and Toxin Levels Change Overtime
+
+Above, I looked at the distributions of newt and snake phenotypes for the 1st and 1000th generation.
+Next, I will look at how the phenotypes of newts and snakes change over 1000 generations.
+I will specifically focus on three types of graphs to show how the phenotypes of newts and snakes vary and change.
+
+The graphs I will be looking at are listed and described below:
+
+* phenotype change (finding sigma and mu): looks at the mean phenotype at the 1st generation and draws an arrow to the mean phenotype at the last generation one pair of lines for each simulation.
+* phenotype variation (from what is a normal sim): looks at all of the mean phenotypes of newts and snakes for the 1000 generations and creates box plots to show how the simulations differ for each other.
+This is also repeated for the standard deviation.
+* differences (from what is a normal sim): This figure creates box plots of how the difference between snake and newt phenotypes change over time.
+
+I will first show the results for space simulations followed by no space predictions and results.
+
+### Phenotype Change
+
+I predict that that the phenotypes of newts and snakes will change over 1000 generations.
+I think that both phenotypes will increase.
+The phenotype starting points should be the same between the space and no space simulation, but I am unsure on how they will differ.
+
+```{r, phenotype change}
+
+w1 <- phenotype_change_graph_s(files_u5, title="Change in Phenotype Space", is_log=TRUE, xlim_value=104)
+
+w1
+
+w2 <- phenotype_change_graph_s(files, title="Change in Phenotype NoSpace", is_log=TRUE, xlim_value=104)
+
+w2
+```
+
+After graphing the change in phenotypes for spatial and non-spatial simulations, it seems like the phenotypes of the non-spatial simulations got larger.
+If there are no spatial groups, any newt can run into any snake and only the one with the greater phenotype will survive.
+There wont be areas where a low phenotype could exist (unless that newt/snake was never chosen for an interaction).
+Maybe this creases an increased mean phenotype.
+Would no space lower the variation of a particular species phenotype?
+I wonder what would happen if I ran the spatial simulation with a larger area.
+### Phenotype Variation
+
+I predict that as the number of generations increase there should be an increase in variation of the mean phenotypes at that particular generation.
+I also predict that standard deviation between the simulation will also vary more as the number of generations increases.
+Now, if I compare the difference between space and no space simulations I think that no space simulation might have less variation in the standard deviation of the simulation.
+I predict this because there might a bunch of newts and snakes with similar phenotypes (within their species at the 1000th generation).
+But, the no space simulations could also have more variation in the mean phenotypes, solely based off of which newts and snakes are selected to interact.
+
+```{r, comparative figures this params}
+
+sp_s<-phenotype_boxplot(Newt_mean_Pheno_s, Snake_mean_Pheno_s, title="Space: Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=30)
+
+sdp_s<-phenotype_boxplot(Newt_sd_Pheno_s, Snake_sd_Pheno_s, title="Space: Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=30)
+
+grid.arrange(sp_s, sdp_s, nrow=1)
+
+sp<-phenotype_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=30)
+
+sdp<-phenotype_boxplot(Newt_sd_Pheno, Snake_sd_Pheno, title="NoSpace: Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=30)
+
+grid.arrange(sp, sdp, nrow=1)
+```
+
+There were more points in the no space simulations that were above my y-limit max value of 30.
+There are a lot more points above the boxplot in the no space simulations. Are the phenotypes running away?
+
+When looking at the differences between the space and no space simulation, the no space simulations had more variation between individual simulations in both the the mean average phenotype and the average standard deviation.
+Although, the mean line of the non-spatial sd boxplots seemed to be lower than the mean lines of the spatial sd boxplots.
+I wonder if the increase in variation between the no-space simulations is due to the random selection of newts and snake that interact.
+Maybe there is something about space that keeps the simulations more similar to each other???
+A graph showing the distribution of means and sds might be helpful.
+
+### Phenotype Differences
+
+I had predicted that the no space population would be more well mixed, meaning that there would be more newts and snakes with similar phenotypes (within the same species).
+But this prediction did not seem to be necessarily true.
+I wonder if the no space simulation will have an effect on the difference between the snake and newt phenotypes.
+I expect that there will be an increase in the variation of difference (some more positive values while others have a more negative values)as the number of generations increases.
+I suspect that in the no space simulation the mean phenotypes will either be more closely matched, because newts and snakes of similar phenotypes were interacting, or vastly different, because newts and snakes of different phenotypes were interacting.
+There also might be more variation between individual simulation in the no space simulation set.
+
+```{r, the differences}
+bp_s<- phenotype_dif_boxplot(Newt_mean_Pheno_s, Snake_mean_Pheno_s, title="Space: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=TRUE, section=TRUE, section_num=10)
+
+bp2_s <- phenotype_dif_boxplot(Newt_mean_Pheno_s, Snake_mean_Pheno_s, title="Space: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=FALSE, section=FALSE, section_num=0)
+
+grid.arrange(bp_s, bp2_s, nrow=1)
+
+bp <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=TRUE, section=TRUE, section_num=10)
+
+bp2 <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=FALSE, section=FALSE, section_num=0)
+
+grid.arrange(bp, bp2, nrow=1)
+```
+
+Well, just like in the mean phenotype graphs, the values in the mean phenotype differences graphs are much larger in the no space simulations.
+Although, the mean phenotype difference remains near zero in both the spatial and non-spatial simulations.
+As time increases the differences between phenotypes get larger at a faster rate in the no space simulations.
+What could be happening to create such a large difference between spatial and non-spatial newt and snake phenotypes?
+
+## Graphs from Selection coef
+
+* the spaceship, x, whales, and betas
+
+```{r, sel coef graphs}
+
+ps1_s <- var_by_var( Newt_mean_Pheno_s, Snake_mean_Pheno_s, mean_newts_eaten_s, mean_snakes_eaten_s, title="Space: Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="Deaths/age", subtract_x=TRUE)
+
+ps2_s <- var_by_var( Newt_mean_Pheno_s, Snake_mean_Pheno_s, Newt_pop_size_s, Snake_pop_size_s, title="Space: Differnece in mean phenotype by PopSize", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="PopSize", subtract_x=TRUE)
+
+grid.arrange(ps1_s, ps2_s, nrow=1)
+
+ps1 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, mean_newts_eaten, mean_snakes_eaten, title="NoSpace: Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="Deaths/age", subtract_x=TRUE)
+
+ps2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_pop_size, Snake_pop_size, title="NoSpace: Differnece in mean phenotype by PopSize", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="PopSize", subtract_x=TRUE)
+
+grid.arrange(ps1, ps2, nrow=1)
+```
+```{r, popsize of newts and snakes with color of phenotype}
+vc1 <- var_by_var(Newt_pop_size, Newt_mean_Pheno, Newt_mean_Pheno, Snake_pop_size, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
+
+vc2 <- var_by_var(Newt_pop_size, Snake_mean_Pheno, Snake_mean_Pheno, Snake_pop_size, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")
+
+vc1 
+vc2
+```
+
+```{r, beta distribution}
+
+hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="Beta Values", xlab="Beta", breaks=15) 
+hist(unlist(beta_n[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), add = TRUE, breaks=15) #ylim=c(0,2100)
+
+abline(v = mean(unlist(beta_n[ , 2:52])), col = rgb(255,192,203, max = 255), lwd = 2)
+abline(v = mean(unlist(beta_s[ , 2:52])), col = rgb(173,216,230, max = 255), lwd = 2)
+legend("topright", c("Newt", "Snake"), fill=c(rgb(255,192,203, max = 255), rgb(173,216,230, max = 255)))
+
+```
+
+```{r, comp betas}
+var_by_var(beta_n, beta_s, beta_n, beta_s, title="Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
+
+```
+
+```{r, beta figures}
+g1 <- var_by_var( beta_n, beta_s, beta_n, beta_s, title="Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
+
+g2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
+
+g3 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
+
+g4 <- var_by_var(Newt_mean_Pheno, beta_s, beta_n, Snake_mean_Pheno, title="Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
+
+grid.arrange(g1, g2, g3, g4, nrow=2)
+
+```

### 2021-09-14 graphs_newt_snakes/nospace.Rmd
I am writing about the results of the no space simulations

@@
 
-see if there is a difference in the distribution of phenotypes between the space and no space simulations. Currently running 9-13-2021
+see if there is a difference in the distribution of phenotypes between the space and no space simulations. Currently running 9-13-2021 then talapas was updating 9-14-2021
 
@@
 
-## Graphs from Selection coef
+## The Interaction
 
-* the spaceship, x, whales, and betas
+### Differnece in mean phenotype by Deaths/Age or Pouplation Size  (from Selection coef)
+
+Previously, I saw a strange interaction between the difference between snakes and newts phenotype and the amount of deaths/age.
+I saw that the higher a snakes phenotype there were less newts being eaten.
+The same was true that when a newts phenotype was higher there were less snakes being eaten.
+We speculated that this phenomenon was occurring due to less snakes or newts in simulations with higher phenotypes in the opposite species.
+When I re-graphed these results by replacing death/age with population size we were able to see that the population with a higher phenotype had more individuals and the other species population was lower.
+
+Originally, I had predicted that when the mean snakes phenotype was higher than the newts phenotype then there would be less snakes dying.
+But if the snakes have the higher phenotype, they were reducing the newts population size, totaling in less newts available to kill.
+The graph was really messy, so I wonder if spatial structure was influencing these results and if so how.
+So then I repeated these same figures with the data from no space simulations without really thinking there would be a significant difference.
 
@@
 ```
+
+Well, the no space simulation results look very different from the spatial simulations.
+It looks more like my original prediction where if snakes have a higher phenotype there would be less of them being killed and more newts being killed (in the death/age graph).
+A similar pattern between the space and no space emerged where as the phenotype of one population goes up the population size of that species also goes up, while the other species population size decreases.
+Although, the no space difference in mean phenotypes and population size did look very curved.
+I noticed that the population sizes in the no space simulations were larger than the population sizes in the space simulations, could this have an effect on the results?
+
+### Population size of Newts by Snakes with phenotype as color
+
+In the selection coefficients rmarkdown I made these beautiful whale plots that again showed (for the most part) that when a species phenotype was high then their population size is higher than the other species.
+Its really weird that these looked uniform across many simulations.
+Almost like some sort of conditions need to be met for a phenotype and population size to reach a particular value.
+In the spatial simulation there were cases where the snakes had a high phenotype and a low population size.
+There was also a fin where the newt and snake populations were not a steady-state yet.
+
+From the previous graphs I expected a similar trend in the no space simulations (higher the population size the higher the phenotype of a species).
+
 ```{r, popsize of newts and snakes with color of phenotype}
-vc1 <- var_by_var(Newt_pop_size, Newt_mean_Pheno, Newt_mean_Pheno, Snake_pop_size, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
 
-vc2 <- var_by_var(Newt_pop_size, Snake_mean_Pheno, Snake_mean_Pheno, Snake_pop_size, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")
+vc1_s <- var_by_var(Newt_pop_size_s, Newt_mean_Pheno_s, Newt_mean_Pheno_s, Snake_pop_size_s, title="Space: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
+
+vc2_s <- var_by_var(Newt_pop_size_s, Snake_mean_Pheno_s, Snake_mean_Pheno_s, Snake_pop_size_s, title="Space: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")
+
+vc1_s 
+vc2_s
+
+vc1 <- var_by_var(Newt_pop_size, Newt_mean_Pheno, Newt_mean_Pheno, Snake_pop_size, title="NoSpace: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
+
+vc2 <- var_by_var(Newt_pop_size, Snake_mean_Pheno, Snake_mean_Pheno, Snake_pop_size, title="NoSpace: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")
 
@@
 
+After graphing both the spatial and no space results there were a few differences that I noticed.
+First, the no space simulations don't have the in-between population size (the fin in the spatial graph).
+This might be due to the population sizes growing to their stead-state sizes within the first 20 generations.
+Second, I noticed that the population size of newts and snakes seems more linear in the no space simulations.
+This reflects the sigmoid shape of the above interaction graphs.
+Third, I noticed a difference in population size (they were larger in the no space simulations) and the phenotypes (also larger in the no space simulations).
+Does space prevent the phenotypes from get exponentially large?
+Beacuse the no space phenotypes got so much larger its kind of hard to compare the colors.
+Forth, there is a similar phenotype trend between the spatial and no space simulations.
+However, there is one no space simulation where the phenotype got really large when both populations sizes were middle sized.
+The color change seemed more uniform in the no space simulation results.
+Maybe the pattern is lighter in the middle and darker at the edges with the darkest edge at the point of the highest population size.
+(Might be worth it to do the arrow graphs for each of the individual simulations.) Final note the spatial results look cooler than the no space results.
+
+### Beta Distributions
+
+The interaction rate in both the space and no space simulations was 0.05.
+This value seems very low?
+Beta is the kind of like a selection coefficient, it will tell how strange section is.
+In the spatial simulations the beta values for nets and snakes were close to 0.
+This value indicates that selection is very weak or non-existent.
+I think that the beta values are low because the interaction rate which is my selective force is low and the non selective force (density dependence) is stronger.
+In the no space simulation there is still density dependent selection and a low interaction rate, so I don't expect the beta value to change that much.
+
 ```{r, beta distribution}
 
-hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="Beta Values", xlab="Beta", breaks=15) 
+hist(unlist(beta_s_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="Space: Beta Values", xlab="Beta", breaks=15) 
+hist(unlist(beta_n_s[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), add = TRUE, breaks=15) #ylim=c(0,2100)
+
+abline(v = mean(unlist(beta_n_s[ , 2:52])), col = rgb(255,192,203, max = 255), lwd = 2)
+abline(v = mean(unlist(beta_s_s[ , 2:52])), col = rgb(173,216,230, max = 255), lwd = 2)
+legend("topright", c("Newt", "Snake"), fill=c(rgb(255,192,203, max = 255), rgb(173,216,230, max = 255)))
+
+hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="NoSpace: Beta Values", xlab="Beta", breaks=15) 
 hist(unlist(beta_n[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), add = TRUE, breaks=15) #ylim=c(0,2100)
@@
 ```
+
+The beta values between no space and the space simulations don't seem to change that much.
+I noticed that the beta values range in no space were smaller from -0.1 to 0.1ish compared to the spatial simulation -0.2 to 0.2.
 

### 2021-09-14 graphs_newt_snakes/nospace.Rmd
look at the last few graphs

@@
 I noticed that the beta values range in no space were smaller from -0.1 to 0.1ish compared to the spatial simulation -0.2 to 0.2.
+I am not sure why
+
+Now I plot the newt betas by the snake betas to see if there is a relationship between them.
+In the spacial simulation the the points were clusters around 0 with an oval surrounding that.
+Since the beta distribution was similar between the space and no space simulations I think the same thing will happen.
 
 ```{r, comp betas}
-var_by_var(beta_n, beta_s, beta_n, beta_s, title="Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
+var_by_var(beta_n_s, beta_s_s, beta_n_s, beta_s_s, title="Space: Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
+
+var_by_var(beta_n, beta_s, beta_n, beta_s, title="NoSpace: Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
 
@@
 
+The clustering looks very similar between the no space and space simulations.
+It is possible that the no space is shifted a little bit to the right of 0, but I am not sure.
+I wonder what would happen if I increase the interaction rate?
+
+### Extra Figures
+
+These figures are to check to see if everything is working like how I would expect it to.
+I thought it would be fun to compare these results between the two different simulations to see if anything look different.
+
 ```{r, beta figures}
-g1 <- var_by_var( beta_n, beta_s, beta_n, beta_s, title="Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
 
-g2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
+g1_s <- var_by_var( beta_n_s, beta_s_s, beta_n_s, beta_s_s, title="Space: Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
 
-g3 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
+g2_s <- var_by_var( Newt_mean_Pheno_s, Snake_mean_Pheno_s, beta_n_s, beta_s_s, title="Space: Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
 
-g4 <- var_by_var(Newt_mean_Pheno, beta_s, beta_n, Snake_mean_Pheno, title="Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
+g3_s <- var_by_var( Newt_mean_Pheno_s, Snake_mean_Pheno_s, Newt_age_s, Snake_age_s, title="Space: Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
+
+g4_s <- var_by_var(Newt_mean_Pheno_s, beta_s_s, beta_n_s, Snake_mean_Pheno_s, title="Space: Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
+
+grid.arrange(g1_s, g2_s, g3_s, g4_s, nrow=2)
+
+g1 <- var_by_var( beta_n, beta_s, beta_n, beta_s, title="NoSpace: Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
+
+g2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="NoSpace: Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
+
+g3 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="NoSpace: Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
+
+g4 <- var_by_var(Newt_mean_Pheno, beta_s, beta_n, Snake_mean_Pheno, title="NoSpace: Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
 

### 2021-09-20 graphs_newt_snakes/nospace.Rmd
wrote about the extra figures and about the phenotype ditribution

@@
 
-## No Space?
+## What is No Space?
 
@@
 ![Space](data/space_pic.png)
+
 ### No Space
@@
 
-see if there is a difference in the distribution of phenotypes between the space and no space simulations. Currently running 9-13-2021 then talapas was updating 9-14-2021
+I will check to see if there is a difference in the distribution of phenotypes between the space and no space simulations.
+Currently running 9-13-2021 then talapas was updating 9-14-2021.
+I got to look at the phenotype distribution of the no space simulation on 9-20-21 and they look very similar to the phenotype distributions of the spatial simulations.
+Like in the spatial simulations the no space simulation the mean phenotype of the species did not cross.
+If one species had a phenotype advantage then they kept it or both the newt and snake phenotypes got very close.
+Here is an example:
+
+### Space
+![Space Dis](data/space_dist.png)
+
+### No Space
+![No Space Dis](data/nospace_dist.png)
 
@@
 ```
+
+The beta values for both the space and no space simulation seems to be centered around 0 at the beginning of the simulation.
+In the no space simulation the beta range seems to be going up (I wonder what would happen if I let it run for longer).
+Age seems to be similar between both simulations, although space has more older individuals.
+When I look at the graphs of the difference in phenotype and the beta values the shape of the blobs are different.
+In the space simulation the blob is kind of eye shape indicating a random relationship between the difference of snake and newt phenotype and beta values.
+In the no space simulation there might be some type of relationship between the beta values and the difference between newt and snake phenotype.
+If there is a difference (hard to tell because blue points are on top), when the snakes have a higher phenotype they also have a higher beta value.
+When snakes have a lower phenotype the beta value is smaller (the pattern might also apply to the newts).
+The phenotypes in no space got larger than the phenotype in the spatial simulations.
+Both of these look like sea grass.
+
+Some questions that I had after looking at the differences between the spatial and no space simulations are: why are there more individuals in the no space simulation and would more individuals change my results?
+What makes the phenotypes in no space get large so quickly?

### 2021-09-21 graphs_newt_snakes/What_is_sel_coef.Rmd
writing about what is a selection coefficent

---
title: "What is a Selection Coefficient?"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Figure out if there is selection in my simulation

The goal of this markdown is to read and think about selection coefficients. What really is a selection coefficient? How can it be measured? What is considered strong and/or weak? How do I pull it out of my simulation (can there be different selection coefficients for different types of selection)? What kind of math is behind it? How might it change in different simulations, like would it get stronger with more interaction? Does it change in different generations?

Currently, I measure selection with the variable beta. Beta is the correlation between phenotype and an individuals fitnessScaling. However, in my simulation there are two possible selective forces 1) the interaction between newts and snakes and 2) the density dependent selection. Now in no space simulation there is still both types of selection, but the density dependent selection is more like a K value.

### 2021-09-24 graphs_newt_snakes/combo_whale.R
I am working on updating the whale graph to be the difference betwen mean phenotypes. I also tried to run the no space simulations for longer.

@@ -1,0 +1,185 @@
+# This is the combo whale
+# x- newt population size, y- snake population size color = snake - newt
+
+library(ggplot2)
+library(viridis)
+library(colorspace)
+library(gridExtra)
+library(tidyverse)
+require(reshape2)
+library(plyr)
+library(gridGraphics)
+library(grid)
+
+making_data_frames <- function(files, spe_col) {
+  i=1
+  for (current_file in files){
+    #print(current_file)
+    
+    if(i ==1){
+      file <- read.table(current_file, header = TRUE)
+      
+      file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+      # might want to change to all_of(spe_col)
+      file %>% 
+        select(all_of(spe_col), gen) %>%
+        #rownames_to_column() %>% 
+        gather(variable, value, -gen) %>% 
+        spread(gen, value) -> new_file
+      
+      new_file$variable[i] <- paste0(spe_col,"_trial_", i)
+      i = i + 1
+      next
+    }
+    file <- read.table(current_file, header = TRUE)
+    
+    file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+    
+    file %>% 
+      select(all_of(spe_col), gen) %>%
+      #rownames_to_column() %>% 
+      gather(variable, value, -gen) %>% 
+      spread(gen, value) -> temp_file
+    
+    temp_file$variable[1] <- paste0(spe_col,"_trial_", i)
+    
+    new_file<-rbind(new_file, temp_file)
+    i = i + 1
+  }
+  return(new_file)
+}
+
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
+  
+  data_frame_newt_temp_x <- Newt_file_x
+  data_frame_newt_temp_x <- data_frame_newt_temp_x[ , !(names(data_frame_newt_temp_x) %in% "variable")]
+  
+  data_frame_snake_temp_x <- Snake_file_x
+  data_frame_snake_temp_x <- data_frame_snake_temp_x[ , !(names(data_frame_snake_temp_x) %in% "variable")]
+  
[…]

### 2021-09-24 graphs_newt_snakes/interact_between_pheno_popsize.R

@@ -111,7 +111,7 @@ var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, tit
 }
 
 
-files <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+files <- list.files(path="~/Desktop/nospace/u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
 i=1
 for(i in 1:107){
 print(i)
@@ -120,7 +120,7 @@ Snake_mean_Pheno_1 <- making_data_frames(files[i], all_of("Snake_mean_Pheno"))
 Newt_pop_size_1 <- making_data_frames(files[i], all_of("Newt_pop_size"))
 Snake_pop_size_1 <- making_data_frames(files[i], all_of("Snake_pop_size"))
 
-naame_of_file= paste0("~/Desktop/figs/both_", i, ".png")
+naame_of_file= paste0("~/Desktop/figs/nospace_", i, ".png")
 png(filename =naame_of_file)
 vc_11 <- var_by_var(Newt_pop_size_1, Newt_mean_Pheno_1, Newt_mean_Pheno_1, Snake_pop_size_1, title="Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", color_label="Newt Phenotype" , highcol="darkred")
 #dev.off()

### 2021-10-04 graphs_newt_snakes/nospce_10000.Rmd
I looked the the results from letting nospace runt tell 10000 generations.

--- 2021-09-14 graphs_newt_snakes/nospace.Rmd
@@
 ---
-title: "Nospace"
+title: "nospace_10000"
 output: html_document
@@
 
-## No Space?
+## What is No Space gen_10000?
 
-This is may no space experiment!
-I worked with Peter to make the 1on1 newt-snake simulation into a simulation that is not dependent on space.
-We changed a few things that were dependent on space like reproduction and the interaction, but everything else remained mostly the same.
-
-Some things to not is that in the reproduction callback new individuals will be paced near their parents, but their parents are randomly chosen for anywhere in the simulation.
-Population size is determined by the amount of individuals in the whole area.
-To choose the amount of interactions between newts and snake we use numNeighbors = rbinom(1, p1.individualCount, (interaction_rate * 2 * PI * surs^2)/W^2).
-This will choose a value based on a binomial distribution with the newt population as the size (amount that could be drawn) and a probability of success based on the interaction rate, area a snake and the total area of the simulation.
-
-Extra notes: From a first glance at the visual output there is a lack of color groups (color represents phenotype)
-
-### Space
-![Space](data/space_pic.png)
-### No Space
-![NoSpace](data/nospace_pic.png)
+This is my no space experiment out to 10,000!
 
 ## My Goals
-
-The goal of this experiment is to see in there is a change in the newts and snakes phenotype that is not based on spatial interactions.
-Specifically, in this experiment there will be no spatial interaction (between newts and snakes).
-I will compare these results to the results of all of my other simulations!
 
@@
 
-var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, logx=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
 
@@
     p = p + scale_y_log10()
+  }
+   if(logx==TRUE){
+    p = p + scale_x_log10()
   }
@@
 ```{r, data info}
-# Files for No space results
-files <- list.files(path="~/Desktop/nospace/u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+# Files for No space gen_10000 results
+files <- list.files(path="~/Desktop/nospace/gen_10000", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
 file <- read.table(files[51], header = TRUE)
@@
 
-see if there is a difference in the distribution of phenotypes between the space and no space simulations. Currently running 9-13-2021 then talapas was updating 9-14-2021
-
 ## How Restance and Toxin Levels Change Overtime
 
-Above, I looked at the distributions of newt and snake phenotypes for the 1st and 1000th generation.
-Next, I will look at how the phenotypes of newts and snakes change over 1000 generations.
-I will specifically focus on three types of graphs to show how the phenotypes of newts and snakes vary and change.
-
-The graphs I will be looking at are listed and described below:
-
-* phenotype change (finding sigma and mu): looks at the mean phenotype at the 1st generation and draws an arrow to the mean phenotype at the last generation one pair of lines for each simulation.
-* phenotype variation (from what is a normal sim): looks at all of the mean phenotypes of newts and snakes for the 1000 generations and creates box plots to show how the simulations differ for each other.
-This is also repeated for the standard deviation.
-* differences (from what is a normal sim): This figure creates box plots of how the difference between snake and newt phenotypes change over time.
-
-I will first show the results for space simulations followed by no space predictions and results.
-
 ### Phenotype Change
-
-I predict that that the phenotypes of newts and snakes will change over 1000 generations.
-I think that both phenotypes will increase.
-The phenotype starting points should be the same between the space and no space simulation, but I am unsure on how they will differ.
 
@@
 
-w1
-
 w2 <- phenotype_change_graph_s(files, title="Change in Phenotype NoSpace", is_log=TRUE, xlim_value=104)
 
+w1
 w2
@@
 
-After graphing the change in phenotypes for spatial and non-spatial simulations, it seems like the phenotypes of the non-spatial simulations got larger.
-If there are no spatial groups, any newt can run into any snake and only the one with the greater phenotype will survive.
-There wont be areas where a low phenotype could exist (unless that newt/snake was never chosen for an interaction).
-Maybe this creases an increased mean phenotype.
-Would no space lower the variation of a particular species phenotype?
-I wonder what would happen if I ran the spatial simulation with a larger area.
 ### Phenotype Variation
-
-I predict that as the number of generations increase there should be an increase in variation of the mean phenotypes at that particular generation.
-I also predict that standard deviation between the simulation will also vary more as the number of generations increases.
-Now, if I compare the difference between space and no space simulations I think that no space simulation might have less variation in the standard deviation of the simulation.
-I predict this because there might a bunch of newts and snakes with similar phenotypes (within their species at the 1000th generation).
-But, the no space simulations could also have more variation in the mean phenotypes, solely based off of which newts and snakes are selected to interact.
 
@@
 
-sp<-phenotype_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=30)
+sp<-phenotype_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=50, ylim_max=30)
 
-sdp<-phenotype_boxplot(Newt_sd_Pheno, Snake_sd_Pheno, title="NoSpace: Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=30)
+sdp<-phenotype_boxplot(Newt_sd_Pheno, Snake_sd_Pheno, title="NoSpace: Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=50, ylim_max=30)
 
@@
 
-There were more points in the no space simulations that were above my y-limit max value of 30.
-There are a lot more points above the boxplot in the no space simulations. Are the phenotypes running away?
-
-When looking at the differences between the space and no space simulation, the no space simulations had more variation between individual simulations in both the the mean average phenotype and the average standard deviation.
-Although, the mean line of the non-spatial sd boxplots seemed to be lower than the mean lines of the spatial sd boxplots.
-I wonder if the increase in variation between the no-space simulations is due to the random selection of newts and snake that interact.
-Maybe there is something about space that keeps the simulations more similar to each other???
-A graph showing the distribution of means and sds might be helpful.
-
 ### Phenotype Differences
-
-I had predicted that the no space population would be more well mixed, meaning that there would be more newts and snakes with similar phenotypes (within the same species).
-But this prediction did not seem to be necessarily true.
-I wonder if the no space simulation will have an effect on the difference between the snake and newt phenotypes.
-I expect that there will be an increase in the variation of difference (some more positive values while others have a more negative values)as the number of generations increases.
-I suspect that in the no space simulation the mean phenotypes will either be more closely matched, because newts and snakes of similar phenotypes were interacting, or vastly different, because newts and snakes of different phenotypes were interacting.
-There also might be more variation between individual simulation in the no space simulation set.
 
@@
 
-bp <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=TRUE, section=TRUE, section_num=10)
+bp <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=TRUE, section=TRUE, section_num=50)
 
@@
 
-Well, just like in the mean phenotype graphs, the values in the mean phenotype differences graphs are much larger in the no space simulations.
-Although, the mean phenotype difference remains near zero in both the spatial and non-spatial simulations.
-As time increases the differences between phenotypes get larger at a faster rate in the no space simulations.
-What could be happening to create such a large difference between spatial and non-spatial newt and snake phenotypes?
-
 ## The Interaction
@@
 ### Differnece in mean phenotype by Deaths/Age or Pouplation Size  (from Selection coef)
-
-Previously, I saw a strange interaction between the difference between snakes and newts phenotype and the amount of deaths/age.
-I saw that the higher a snakes phenotype there were less newts being eaten.
-The same was true that when a newts phenotype was higher there were less snakes being eaten.
-We speculated that this phenomenon was occurring due to less snakes or newts in simulations with higher phenotypes in the opposite species.
-When I re-graphed these results by replacing death/age with population size we were able to see that the population with a higher phenotype had more individuals and the other species population was lower.
-
-Originally, I had predicted that when the mean snakes phenotype was higher than the newts phenotype then there would be less snakes dying.
-But if the snakes have the higher phenotype, they were reducing the newts population size, totaling in less newts available to kill.
-The graph was really messy, so I wonder if spatial structure was influencing these results and if so how.
-So then I repeated these same figures with the data from no space simulations without really thinking there would be a significant difference.
 
@@
 grid.arrange(ps1, ps2, nrow=1)
+
 ```
 
-Well, the no space simulation results look very different from the spatial simulations.
-It looks more like my original prediction where if snakes have a higher phenotype there would be less of them being killed and more newts being killed (in the death/age graph).
-A similar pattern between the space and no space emerged where as the phenotype of one population goes up the population size of that species also goes up, while the other species population size decreases.
-Although, the no space difference in mean phenotypes and population size did look very curved.
-I noticed that the population sizes in the no space simulations were larger than the population sizes in the space simulations, could this have an effect on the results?
-
 ### Population size of Newts by Snakes with phenotype as color
-
-In the selection coefficients rmarkdown I made these beautiful whale plots that again showed (for the most part) that when a species phenotype was high then their population size is higher than the other species.
-Its really weird that these looked uniform across many simulations.
-Almost like some sort of conditions need to be met for a phenotype and population size to reach a particular value.
-In the spatial simulation there were cases where the snakes had a high phenotype and a low population size.
-There was also a fin where the newt and snake populations were not a steady-state yet.
-
-From the previous graphs I expected a similar trend in the no space simulations (higher the population size the higher the phenotype of a species).
 
@@
 
-After graphing both the spatial and no space results there were a few differences that I noticed.
-First, the no space simulations don't have the in-between population size (the fin in the spatial graph).
-This might be due to the population sizes growing to their stead-state sizes within the first 20 generations.
-Second, I noticed that the population size of newts and snakes seems more linear in the no space simulations.
-This reflects the sigmoid shape of the above interaction graphs.
-Third, I noticed a difference in population size (they were larger in the no space simulations) and the phenotypes (also larger in the no space simulations).
-Does space prevent the phenotypes from get exponentially large?
-Beacuse the no space phenotypes got so much larger its kind of hard to compare the colors.
-Forth, there is a similar phenotype trend between the spatial and no space simulations.
-However, there is one no space simulation where the phenotype got really large when both populations sizes were middle sized.
-The color change seemed more uniform in the no space simulation results.
-Maybe the pattern is lighter in the middle and darker at the edges with the darkest edge at the point of the highest population size.
-(Might be worth it to do the arrow graphs for each of the individual simulations.) Final note the spatial results look cooler than the no space results.
-
 ### Beta Distributions
-
-The interaction rate in both the space and no space simulations was 0.05.
-This value seems very low?
-Beta is the kind of like a selection coefficient, it will tell how strange section is.
-In the spatial simulations the beta values for nets and snakes were close to 0.
-This value indicates that selection is very weak or non-existent.
-I think that the beta values are low because the interaction rate which is my selective force is low and the non selective force (density dependence) is stronger.
-In the no space simulation there is still density dependent selection and a low interaction rate, so I don't expect the beta value to change that much.
 
@@
 
-The beta values between no space and the space simulations don't seem to change that much.
-I noticed that the beta values range in no space were smaller from -0.1 to 0.1ish compared to the spatial simulation -0.2 to 0.2.
-I am not sure why
-
-Now I plot the newt betas by the snake betas to see if there is a relationship between them.
-In the spacial simulation the the points were clusters around 0 with an oval surrounding that.
-Since the beta distribution was similar between the space and no space simulations I think the same thing will happen.
-
 ```{r, comp betas}
@@
 
-The clustering looks very similar between the no space and space simulations.
-It is possible that the no space is shifted a little bit to the right of 0, but I am not sure.
-I wonder what would happen if I increase the interaction rate?
-
 ### Extra Figures
-
-These figures are to check to see if everything is working like how I would expect it to.
-I thought it would be fun to compare these results between the two different simulations to see if anything look different.
 

### 2021-10-04 graphs_newt_snakes/beta_exploration.R

@@ -49,8 +49,9 @@ making_data_frames <- function(files, spe_col) {
   return(new_file)
 }
 
-var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, section=FALSE, section_num = 0, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
   
+  if(section==FALSE){
   data_frame_newt_temp_x <- Newt_file_x
   data_frame_newt_temp_x <- data_frame_newt_temp_x[ , !(names(data_frame_newt_temp_x) %in% "variable")]
   
@@ -62,7 +63,24 @@ var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, tit
   
   data_frame_snake_temp_y <- Snake_file_y
   data_frame_snake_temp_y <- data_frame_snake_temp_y[ , !(names(data_frame_snake_temp_y) %in% "variable")]
-  
+  }
+  if(section==TRUE){
+    
+    selcol = seq(1,ncol(Newt_file_x), section_num)
+    
+    data_frame_newt_temp_x <- Newt_file_x %>% select(all_of(selcol))
+    data_frame_newt_temp_x <- data_frame_newt_temp_x[ , !(names(data_frame_newt_temp_x) %in% "variable")]
+    
+    data_frame_snake_temp_x <- Snake_file_x %>% select(all_of(selcol))
+    data_frame_snake_temp_x <- data_frame_snake_temp_x[ , !(names(data_frame_snake_temp_x) %in% "variable")]
+    
+    data_frame_newt_temp_y <- Newt_file_y %>% select(all_of(selcol))
+    data_frame_newt_temp_y <- data_frame_newt_temp_y[ , !(names(data_frame_newt_temp_y) %in% "variable")]
+    
+    data_frame_snake_temp_y <- Snake_file_y %>% select(all_of(selcol))
[…]

### 2021-10-12 graphs_newt_snakes/nospce_10000.Rmd
I had an error when looking at the 10,000 gen data (mostly i was looking at thw 1000th gen) but I fixed that. I also went back and looked the first and 1000th generation beta values. it moved a bit more in the no space simulation.

@@
   file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
+  last_data_point <- nrow(file)
   file <- file[complete.cases(file), ]
  p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color= darken("darkred")) +
-   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color=lighten("darkred"))  + 
+   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[last_data_point])+0.1), color=lighten("darkred"))  + 
   geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color=darken("steelblue")) +
-  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color=lighten("steelblue"))+
-  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1, colour="Newt"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))+
-   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1, colour="Snake"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[last_data_point])+0.1), color=lighten("steelblue"))+
+  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[last_data_point])+0.1, colour="Newt"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))+
+   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[last_data_point])+0.1, colour="Snake"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))
 

### 2021-10-12 graphs_newt_snakes/beta_exploration.R

@@ -249,14 +249,14 @@ Snake_pop_size_s <- making_data_frames(files_u5, all_of("Snake_pop_size"))
 
 
 #beta distribution
-
+#space
 hist(unlist(beta_s_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="Space: Beta Values", xlab="Beta", breaks=15) 
 hist(unlist(beta_n_s[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), add = TRUE, breaks=15) #ylim=c(0,2100)
 
 abline(v = mean(unlist(beta_n_s[ , 2:52])), col = rgb(255,192,203, max = 255), lwd = 2)
 abline(v = mean(unlist(beta_s_s[ , 2:52])), col = rgb(173,216,230, max = 255), lwd = 2)
 legend("topright", c("Newt", "Snake"), fill=c(rgb(255,192,203, max = 255), rgb(173,216,230, max = 255)))
-
+#nospace
 hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="NoSpace: Beta Values", xlab="Beta", breaks=15) 
 hist(unlist(beta_n[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), add = TRUE, breaks=15) #ylim=c(0,2100)
 
@@ -264,11 +264,11 @@ abline(v = mean(unlist(beta_n[ , 2:52])), col = rgb(255,192,203, max = 255), lwd
 abline(v = mean(unlist(beta_s[ , 2:52])), col = rgb(173,216,230, max = 255), lwd = 2)
 legend("topright", c("Newt", "Snake"), fill=c(rgb(255,192,203, max = 255), rgb(173,216,230, max = 255)))
 #_gen_10000
-hist(unlist(beta_s_gen_10000[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="NoSpace gen 10,000: Beta Values", xlab="Beta", breaks=15) 
-hist(unlist(beta_n_gen_10000[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), add = TRUE, breaks=15) #ylim=c(0,2100)
[…]

### 2021-10-13 graphs_newt_snakes/What_is_sel_coef.Rmd
I wrote down the things I would like to do to test beta in the what is a sel coef markdown. and I am setting up to run the 10,000 gen space simulation so I was checking to make sure it runs
setting up the beta test

@@
 Now in no space simulation there is still both types of selection, but the density dependent selection is more like a K value.
+
+What I would like to do:
+
+-run a simulation where newts have an advantage (run msprime with under 5 var and under 2 var)
+-turn off mutations for newts
+-see if snake beta goes up <-prediction
+-watch newt beta <- I think it might stay around 0
+-print beta every generation 
+-compare space to no space
+
+(pairs)
+sigma_u2=( 0.1 0.2 0.3)
+mu_rate_u2=( 1e-10 2.5e-11 1.11e-11)
+sigma_u5=( 0.1 0.2 0.3)
+mu_rate_u5=( 6.25e-10 1.56e-10 6.94e-11)
+
+I made 6 msprime files where one species phenotype is under 2 and one is under 5. I kept the under 2 params the same and moved the under 5 to each of the three pairs.

### 2021-10-13 msprime/snake_newt_gv_.py

@@ -10,16 +10,17 @@ from sys import argv
 #print("hello")
 
 sequence_length = 100000000
+mytag="no_tag"
 '''
-datadir = "newt_snake/data"
-snake_mu_rate = 1e-10
+datadir = "/Users/victoria/Desktop/Coevo/newt_snake/data"
+snake_mu_rate = 6.94e-11
 newt_mu_rate = 1e-10  # does this need to be 50 times more than the snake?
-snake_mu_effect_sd = 0.01
+snake_mu_effect_sd = 0.03
 newt_mu_effect_sd = 0.01
 name_of_file = "both_newt_snake_annotated.init.trees"
-
+mytag="beta_exp"
 '''
-mytag="no_tag"
+
 snake_mu_rate = float(sys.argv[1])
 newt_mu_rate = float(sys.argv[2])  # does this need to be 50 times more than the snake?
 snake_mu_effect_sd = float(sys.argv[3])
@@ -27,7 +28,7 @@ newt_mu_effect_sd = float(sys.argv[4])
 datadir = sys.argv[5]
 mytag = sys.argv[6]
 
-name_of_file = "both_1000_su_" + str(snake_mu_rate) + "_nu_" + str(newt_mu_rate) + \
+name_of_file = "snake_adv3_su_" + str(snake_mu_rate) + "_nu_" + str(newt_mu_rate) + \
     "_sue_" + str(snake_mu_effect_sd) + "_nue_" + str(newt_mu_effect_sd) + "_" + mytag + ".init.trees"
 print(name_of_file)
 

### 2021-10-14 graphs_newt_snakes/nospce_10000.Rmd
I was writing what I was seeing in the space simulations when they are run for a long time. I am also looked at the dirstibtuion for space simulation results for 3000 gen.

@@
 This is my no space experiment out to 10,000!
+
+No space to 10,000 generations works, but space simulation does not one of the populations seems to die out before it reaches the end of the simulation.
+I wonder how to stop this from happening?
+maybe a function that makes it harder for them to find each other when the population is low.
+Under 2 seems to have run to completion.
+Now I am trying an under 2 msprime and a under 5 mutation rate (success).
+Maybe the file i was using was bad trying under 5 10000 gens again (does not work, still dies out).
+
+ Are the newts and snake coevolving?
+- it's difficult to tell.
+I can see patterns forming (certain phenotypes are clustering), but the mean phenotype doesn't move.
+But the distributions (at least for under 5) look different.
+
+ When I run the simulation for longer the phenotype of newts and snakes get large around 3000 -population size might be a consequence of a large phenotype. (looking at the distributions soon)
+
+ paste0("End Space: Generation", end_gen)
 

### 2021-10-14 graphs_newt_snakes/space_assemble.R

@@ -13,21 +13,22 @@ png(paste0(folder_name, "/", save_file, ".png"), width=800,height=1000)
 
 #path_to_file="~/Desktop/Coevo/newt_snake/data/space_test/pulled_info_test.txt"
 #text_sub_title="file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt"
+#path_to_file="~/Desktop/test_case_space_dis.txt"
 path_to_file=args[3]
 text_sub_title=args[4]
 space_data <- read.table(path_to_file, header = TRUE)
 
 space_data$made_max= 0
-
+end_gen = as.numeric(3000)
 space_data$made_max<- ifelse(space_data$gen == 1 & space_data$type == "Newt", max(space_data[which(space_data$gen == 1 & space_data$type == "Newt"),]$ind_phy), 
-                             ifelse(space_data$gen == 1 & space_data$type == "Snake", max(space_data[which(space_data$gen == 1000 & space_data$type == "Snake"),]$ind_phy),
-                                    ifelse(space_data$gen == 1000 & space_data$type == "Newt", max(space_data[which(space_data$gen == 1000 & space_data$type == "Newt"),]$ind_phy), 
-                                           ifelse(space_data$gen == 1000 & space_data$type == "Snake", max(space_data[which(space_data$gen == 1000 & space_data$type == "Snake"),]$ind_phy), 0))))
+                             ifelse(space_data$gen == 1 & space_data$type == "Snake", max(space_data[which(space_data$gen == 1 & space_data$type == "Snake"),]$ind_phy),
+                                    ifelse(space_data$gen == end_gen & space_data$type == "Newt", max(space_data[which(space_data$gen == end_gen & space_data$type == "Newt"),]$ind_phy), 
+                                           ifelse(space_data$gen == end_gen & space_data$type == "Snake", max(space_data[which(space_data$gen == end_gen & space_data$type == "Snake"),]$ind_phy), 0))))
 
 space_data$my_alpha <- space_data$ind_phy/space_data$made_max
 
[…]

### 2021-10-15 msprime/snake_newt_gv_.py
I was looking at what happens to beta as you change things like mu and sigma in the slim simulation. It is very hard to tell what is going on. I am also trying to look at the 3000gen data. I also made some more msprime files to make newts more adv than snakes.

@@ -11,12 +11,12 @@ from sys import argv
 
 sequence_length = 100000000
 mytag="no_tag"
-'''
+
 datadir = "/Users/victoria/Desktop/Coevo/newt_snake/data"
-snake_mu_rate = 6.94e-11
-newt_mu_rate = 1e-10  # does this need to be 50 times more than the snake?
-snake_mu_effect_sd = 0.03
-newt_mu_effect_sd = 0.01
+snake_mu_rate = 1e-10
+newt_mu_rate = 1e-4  # does this need to be 50 times more than the snake?
+snake_mu_effect_sd = 0.01
+newt_mu_effect_sd = 0.05
 name_of_file = "both_newt_snake_annotated.init.trees"
 mytag="beta_exp"
 '''
@@ -27,8 +27,8 @@ snake_mu_effect_sd = float(sys.argv[3])
 newt_mu_effect_sd = float(sys.argv[4])
 datadir = sys.argv[5]
 mytag = sys.argv[6]
-
-name_of_file = "snake_adv3_su_" + str(snake_mu_rate) + "_nu_" + str(newt_mu_rate) + \
+'''
+name_of_file = "newt_adv6_su_" + str(snake_mu_rate) + "_nu_" + str(newt_mu_rate) + \
     "_sue_" + str(snake_mu_effect_sd) + "_nue_" + str(newt_mu_effect_sd) + "_" + mytag + ".init.trees"
 print(name_of_file)
 

### 2021-10-15 graphs_newt_snakes/nospce_10000.Rmd
I was looking at what happens to beta as you change things like mu and sigma in the slim simulation. It is very hard to tell what is going on. I am also trying to look at the 3000gen data. I also made some more msprime files to make newts more adv than snakes.
I ran and looked at the data from the spatial simulation that ran to 3000gen. I want to compair it to the nospace 10000gen simulations.

@@
 # Files for space results
-files_u5 <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
-
+files_u5 <- list.files(path="~/Desktop/run_longer/gen_3000/u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+file <- read.table(files_u5[51], header = TRUE)
 beta_n_s <- making_data_frames(files_u5, all_of("beta_n"))

### 2021-11-05 graphs_newt_snakes/fitness_cost.Rmd
started to write down my thoughts in a rmarkdown for fitness cost

---
title: "Fitness Cost"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fitness Cost

In my newts and snakes simulation the phenotypes of both of the populations keeps increasing forever. In the spatial simulations this increase eventually leads to the death of one of the species and the collapses of the SLiM (something I currently calculate needs to have individuals) simulation. To have my simulation run essentially forever I wanted to add in a cost to having a high phenotype.

A cost would push the phenotypes back towards 0, but would also make it harder to observe selection. I ran one simulation with the cost (math version will be presented later) once and the phenotypes just keep decreasing. The simulation ran for a long time (5000 generations) and the population did not explode or decrease. Is it possible for the phenotypes to be completely pushed back to 0. Do we still see spots were coevolution is happening? Should I change the slope of the cost curve?

## Msprime simulations

Peter and I talked about why I couldn't get the phenotypes to start out higher and I want to make some figures about it.

### 2021-11-08 graphs_newt_snakes/What_is_sel_coef.Rmd
I am working on writing more details in the r markdown files for fitness cost and what is a sel coeff

@@
 I made 6 msprime files where one species phenotype is under 2 and one is under 5. I kept the under 2 params the same and moved the under 5 to each of the three pairs.
+
+## Testing for Selection
+
+This Is how I would like one of the phenotypes to look if there was an advantage. I was trying to use Msprime to get this type of distribution, but it wasn't working.
+
+```{r, distributions}
+snakes <- rnorm(10000, 5, 0.5)
+newts <- rnorm(10000, 2, 0.5)
+hist(snakes, col="steelblue", xlim = c(1, 6), main = "Phenotypes Distribution", xlab = "Phenotype (red=Newt, blue=Snake)")
+hist(newts, col="darkred", add = TRUE)
+
+```
+
+## Msprime simulations
+
+Msprime runs the simulation back in time to a coalescent point.
+Then it assigns mutations with SD()=theta.
+These mutations have an effect on a phenotype (resistance/toxicity) that are normally distributed around 0.
+Then the distribution under goes a log transformation, which centers it around 1.
+When I change the mu and sigma parameters I really change the normal distribution curve.
+I want to give either the newt or snake a phenotype advantage, the msprime simulation is not the place to do it (as its 11/08/2021 form).
+I can instead use the slim simulation to give newts or snakes a higher fitness by adding to their phenotype.
+
+![Space](data/msprime_notes.jpg)
+
+I wonder what happens to the phenotype distributions when I change mutation rate and mutation effect sizes (Maybe try different ones out and look at it through slim?).
+
+## Quant Gen book
+
+Heritability and genetic correlation page 54

### 2021-11-08 graphs_newt_snakes/fitness_cost.Rmd
I am working on writing more details in the r markdown files for fitness cost and what is a sel coeff

@@
 In my newts and snakes simulation the phenotypes of both of the populations keeps increasing forever.
-In the spatial simulations this increase eventually leads to the death of one of the species and the collapses of the SLiM (something I currently calculate needs to have individuals) simulation.
+In the spatial simulations this increase eventually leads to the death of one of the species and the collapses of the SLiM simulation (something I currently calculate needs to have individuals).
 To have my simulation run essentially forever I wanted to add in a cost to having a high phenotype.
 
+Too come up with a cost curve I thought about the biology behind the existence of a fitness cost in the context of newts and snakes.
+In snakes for every mutation that allows for them to be resistant to the toxin they partially break their mobility.
+So snakes become slower when they are more resistant and can be preyed upon by other predators.
+Newts are a bit more complicated.
+It is unknown if there is a fitness cost for being more toxic.
+Maybe producing toxin makes them slower, maybe it takes more energy to produce so there is less energy for offspring.
+
+Here is an example of what I think a fitness cost might look like (values are not realistic).
+As the phenotype gets larger the phenotype has a higher cost.
+So to keep a high cost phenotype there needs to be strong selection.
+
+```{r, fitness cost}
+
+phenotype <- c(0:5)
+plot(phenotype, phenotype^2, type = "l", main="Fitness Cost", xlab="Phenotype", ylab="Cost")
+abline(v=3, col="red")
+abline(h=9, col="red") # represents half of the individuals fitness
+```
+
 A cost would push the phenotypes back towards 0, but would also make it harder to observe selection.
-I ran one simulation with the cost (math version will be presented later) once and the phenotypes just keep decreasing.
+I ran one simulation with the cost once and the phenotypes just keep decreasing (math version will be presented later).
 The simulation ran for a long time (5000 generations) and the population did not explode or decrease.
@@
 Should I change the slope of the cost curve?
-
-## Msprime simulations
-
-Peter and I talked about why I couldn't get the phenotypes to start out higher and I want to make some figures about it.

### 2021-11-08 graphs_newt_snakes/fitness_cost.Rmd
worked a bit more describing what I was doing for fitness cost

@@
 
+I chose a phenotype of 3 to be half as good.
+This might be a tad too strong.
+To calculate cost I need to look at the fitness scaling (between 0 and 1) and make my chosen phenotype meet the line at half of the total fitness (0.5).
+
+Fitness scaling = e^-cost
+
+If a phenotype of 3 is half the total fitness the cost wold be log 2
+
+c(p) = (a/b)^2
+c(3) = (a/b)^2
+log(2) = (a/b)^2
+b = 3/log(2) = 10
+
+SO cost = (phenotype/10)^2
+
+**Special Note** Phenotype is arbitrary (scale for the snakes resistance)
+
 A cost would push the phenotypes back towards 0, but would also make it harder to observe selection.

### 2021-11-10 graphs_newt_snakes/fitness_cost.Rmd
I plotted the data from the cost simulatioms

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
+library(ggplot2)
+library(viridis)
+library(colorspace)
+library(gridExtra)
+library(tidyverse)
+require(reshape2)
+library(plyr)
+library(gridGraphics)
+library(grid)
 ```
@@
 Should I change the slope of the cost curve?
+
+```{r, making data frames}
+
+making_data_frames <- function(files, spe_col) {
+i=1
+for (current_file in files){
+ #print(current_file)
+
+  if(i ==1){
+    file <- read.table(current_file, header = TRUE)
+
+    file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+      # might want to change to all_of(spe_col)
+    file %>% 
+      select(all_of(spe_col), gen) %>%
+      #rownames_to_column() %>% 
+      gather(variable, value, -gen) %>% 
+      spread(gen, value) -> new_file
+
+    new_file$variable[i] <- paste0(spe_col,"_trial_", i)
+    i = i + 1
+    next
+    }
+  file <- read.table(current_file, header = TRUE)
+
+  file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+
+file %>% 
+  select(all_of(spe_col), gen) %>%
+  #rownames_to_column() %>% 
+  gather(variable, value, -gen) %>% 
+  spread(gen, value) -> temp_file
+
+temp_file$variable[1] <- paste0(spe_col,"_trial_", i)
+
+new_file<-rbind(new_file, temp_file)
+i = i + 1
+}
+return(new_file)
+}
+
+```
+
+```{r, making resueable figures, results='hide', message=FALSE, warning=FALSE}
+
+phenotype_trends <- function(file, title, subt, my_color, is_log=FALSE, leg_off=FALSE){
+  data_frame_temp <- as.data.frame(t(file))
+
+  colnames(data_frame_temp) <- data_frame_temp[1,]
+  names(data_frame_temp) <- colnames(data_frame_temp)
+  steps <- colnames(file[ , !(names(file) %in% "variable")])
+data_frame_temp <- data_frame_temp[-1, ] 
+data_frame_temp$steps <- as.numeric(unlist(steps))
+
+  graph_file <- melt(data_frame_temp,  id.vars = 'steps', variable.name = 'series')
+
+    p <- ggplot(graph_file, aes(steps, as.numeric(value))) + geom_line(aes(colour = series))+ 
+    ggtitle(title, subtitle = subt) +
+    scale_color_manual(values = rep(my_color, nrow(file)))+
+    xlab("Generations") + ylab("Interaction")+
+    theme_bw() + theme(legend.position="none")
+
+    if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Interaction (Log)")
+    }
+     if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+    return(p)
+}
+
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
+
+  data_frame_newt_temp_x <- Newt_file_x
+  data_frame_newt_temp_x <- data_frame_newt_temp_x[ , !(names(data_frame_newt_temp_x) %in% "variable")]
+
+  data_frame_snake_temp_x <- Snake_file_x
+  data_frame_snake_temp_x <- data_frame_snake_temp_x[ , !(names(data_frame_snake_temp_x) %in% "variable")]
+
+  data_frame_newt_temp_y <- Newt_file_y
+  data_frame_newt_temp_y <- data_frame_newt_temp_y[ , !(names(data_frame_newt_temp_y) %in% "variable")]
+
+  data_frame_snake_temp_y <- Snake_file_y
+  data_frame_snake_temp_y <- data_frame_snake_temp_y[ , !(names(data_frame_snake_temp_y) %in% "variable")]
+
+  Number <- colnames(data_frame_newt_temp_x)
+  data_frame_newt_x <- gather(data_frame_newt_temp_x, Number, value_x)
+  data_frame_newt_x$type <- "Newt"
+  data_frame_newt_y <- gather(data_frame_newt_temp_y, Number, value_y)
+  data_frame_newt <- cbind(data_frame_newt_x, data_frame_newt_y)
+  data_frame_newt <- data_frame_newt[-4]
+  data_frame_snake_x <- gather(data_frame_snake_temp_x, Number, value_x)
+  data_frame_snake_x$type <- "Snake"
+  data_frame_snake_y <- gather(data_frame_snake_temp_y, Number, value_y)
+  data_frame_snake <- cbind(data_frame_snake_x, data_frame_snake_y)
+  data_frame_snake <- data_frame_snake[-4]
+
+ if(subtract_x==FALSE){
+   combo <- rbind(data_frame_newt, data_frame_snake)
+   combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
+   p <- ggplot(combo_s) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color=type), alpha=0.1)+
+      scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+ }
+ if(subtract_x==TRUE){
+    subtract_val <- data_frame_snake_x$value_x - data_frame_newt_x$value_x
+    total_sub_dataframe <- data.frame(subtract_val, data_frame_newt_y$value_y, data_frame_snake_y$value_y)
+    total_sub_dataframe <- total_sub_dataframe[sample(nrow(total_sub_dataframe), nrow(total_sub_dataframe)), ]
+    colnames(total_sub_dataframe) <- c("SnakeMisNewt_Pheno","Newts","Snakes")
+     p <- ggplot(total_sub_dataframe) +
+      #xlim(0, 1000)+
+       ggtitle(title, subtitle = subt) +
+       xlab(x_label) + ylab(y_label)+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Newts), color="Newts"), alpha=0.1)+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Snakes), color="Snakes"), alpha=0.1)+
+        scale_colour_manual(name = "Species", values = c("Newts" = "darkred", "Snakes" = "steelblue"))+
+        theme(plot.title = element_text(size=5)) +
+        theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+ }
+  if(by_gen==TRUE){
+    combo <- rbind(data_frame_newt, data_frame_snake)
+    combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
+       p <- ggplot(combo_s) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(Number), y=as.numeric(value_y), color=type), alpha=0.1)+
+      scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  }
+
+   if(just_two==TRUE){
+     just2 <- cbind(data_frame_newt_x, data_frame_snake_y)
+     just2 <- just2[-4]
+       p <- ggplot(just2) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y)), color = "darkgreen", alpha=0.1)+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+   }
+
+   if(colored==TRUE){
+     color3 <- cbind(data_frame_newt_x, data_frame_snake_y, data_frame_newt_y)
+     color3 <- color3[-c(1,3,4,6)]
+     suppressWarnings(suppressMessages(suppressPackageStartupMessages({require(scales)})))
+     amin <- 0.1
+     lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
+     lowcol <- paste0("#",   sep = "",
+                 paste(format(lowcol.hex, width = 2), collapse = ""))
+       p <- ggplot(color3) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color = value_y.1))+
+      theme(plot.title = element_text(size=5)) +
+      scale_colour_gradient(high = highcol, low = lowcol) + 
+      labs(colour = color_label) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  }
+  if(logy==TRUE){
+    p = p + scale_y_log10()
+  }
+
+  return(p)
+
+}
+
+phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE, ylim_max=100){
+  data_frame_newt_temp <- Newt_file
+  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]
+
+  data_frame_snake_temp <- Snake_file
+  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]
+
+   if(section==TRUE){
+
+   selcol = seq(1,ncol(data_frame_newt_temp), section_num)
+   data_frame_newt_temp <- data_frame_newt_temp %>% select(all_of(selcol))
+   data_frame_snake_temp <- data_frame_snake_temp %>% select(all_of(selcol))
+
+   }
+   Number <- colnames(data_frame_newt_temp)
+  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
+  data_frame_newt$type <- "Newt"
+  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
+  data_frame_snake$type <- "Snake"
+
+ combo <- rbind(data_frame_newt, data_frame_snake)
+
+ small_combo <- aggregate(as.numeric(combo$value),by=list(Number=as.numeric(combo$Number),type=combo$type),data=combo,FUN=mean, na.action = TRUE)
+
+if(boxy==TRUE){
+  p <- ggplot(combo) +
+    ylim(0, ylim_max)+
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotypes")+
+    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(value), color=type) )
+  }
+if(boxy==FALSE){
+  p <- ggplot(small_combo) +
+  #xlim(0, 1000)+
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotypes")+
+    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_point(aes(x=factor(as.numeric(Number)), y=as.numeric(x), color=type) )
+}
+
+ if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+
+return(p)
+}
+
+phenotype_dif_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE){
+  data_frame_newt_temp <- Newt_file
+  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]
+
+  data_frame_snake_temp <- Snake_file 
+  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]
+
+  if(section==TRUE){
+
+   selcol = seq(1,ncol(data_frame_newt_temp), section_num)
+   data_frame_newt_temp <- data_frame_newt_temp %>% select(all_of(selcol))
+   data_frame_snake_temp <- data_frame_snake_temp %>% select(all_of(selcol))
+
+ }
+
+  Number <- colnames(data_frame_newt_temp)
+  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
+  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
+  dif <- as.numeric(data_frame_snake$value)-as.numeric(data_frame_newt$value)
+
+  df_dif <- as.data.frame(dif)
+  df_dif$Number <- as.numeric(data_frame_newt$Number)
+
+  if(boxy==TRUE){
+ p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(dif)), color="darkolivegreen" )
+ }
+ if(boxy==FALSE){
+   df_dif$trial <- rep(Newt_file$variable, ncol(Newt_file)-1)
+   p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_line(aes(x=as.numeric(Number), y=as.numeric(dif), color=trial ))+ 
+     theme(legend.position="none")+
+     scale_color_manual(values = rep("darkolivegreen", nrow(data_frame_newt_temp)))
+ }
+   if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+  return(p)
+}
+
+phenotype_change_graph_s <- function(files, title, is_log=FALSE, xlim_value){
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=1:144)) +
+  xlim(0, xlim_value)+
+  ggtitle(title) +
+  xlab("Simulation number") + ylab("Phenotype")+
+  theme_bw()
+
+if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Phenotype  (Log)")
+
+}
+
+i=1
+for (current_file in files){
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
+  file <- file[complete.cases(file), ]
+ p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color= darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color=lighten("darkred"))  + 
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color=darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color=lighten("steelblue"))+
+  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1, colour="Newt"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))+
+   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1, colour="Snake"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))
+
+ i = i+1
+}
+p <- p +
+ scale_colour_manual(name = "Species", values = c("Newt" = "darkred", "Snake"="steelblue"))
+return(p)
+}
+
+```
+
+```{r, data info}
+# Files for No space results
+files <- list.files(path="~/Desktop/cost_sim/gen_5000/u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+file <- read.table(files[51], header = TRUE)
+beta_n <- making_data_frames(files, all_of("beta_n"))
+beta_s <- making_data_frames(files, all_of("beta_s"))
+Newt_mean_Pheno <- making_data_frames(files, all_of("Newt_mean_Pheno"))
+Snake_mean_Pheno <- making_data_frames(files, all_of("Snake_mean_Pheno"))
+Newt_sd_Pheno <- making_data_frames(files, all_of("Newt_sd_Pheno"))
+Snake_sd_Pheno <- making_data_frames(files, all_of("Snake_sd_Pheno"))
+mean_newts_eaten <- making_data_frames(files, all_of("mean_newts_eaten"))
+mean_snakes_eaten <- making_data_frames(files, all_of("mean_snakes_eaten"))
+newt_deaths <- making_data_frames(files, all_of("newt_deaths"))
+snake_deaths <- making_data_frames(files, all_of("snake_deaths"))
+Newt_age <- making_data_frames(files, all_of("Newt_age"))
+Snake_age <- making_data_frames(files, all_of("Snake_age"))
+Newt_pop_size <- making_data_frames(files, all_of("Newt_pop_size"))
+Snake_pop_size <- making_data_frames(files, all_of("Snake_pop_size"))
+```
+
+```{r, phenotype change}
+
+phenotype_change_graph_s(files, title="Change in Phenotype Space", is_log=TRUE, xlim_value=104)
+
+```
+```{r, comparative figures this params}
+
+sp<-phenotype_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=5)
+
+sdp<-phenotype_boxplot(Newt_sd_Pheno, Snake_sd_Pheno, title="NoSpace: Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=5)
+
+grid.arrange(sp, sdp, nrow=1)
+```
+
+```{r, the differences}
+
+bp <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=TRUE, section=TRUE, section_num=10)
+
+bp2 <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=FALSE, section=FALSE, section_num=0)
+
+grid.arrange(bp, bp2, nrow=1)
+```
+
+```{r, sel coef graphs}
+
+ps1 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, mean_newts_eaten, mean_snakes_eaten, title="NoSpace: Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="Deaths/age", subtract_x=TRUE)
+
+ps2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_pop_size, Snake_pop_size, title="NoSpace: Differnece in mean phenotype by PopSize", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="PopSize", subtract_x=TRUE)
+
+grid.arrange(ps1, ps2, nrow=1)
+```
+
+```{r, popsize of newts and snakes with color of phenotype}
+
+vc1 <- var_by_var(Newt_pop_size, Newt_mean_Pheno, Newt_mean_Pheno, Snake_pop_size, title="NoSpace: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
+
+vc2 <- var_by_var(Newt_pop_size, Snake_mean_Pheno, Snake_mean_Pheno, Snake_pop_size, title="NoSpace: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")
+
+vc1 
+vc2
+```
+
+```{r, beta distribution}
+
+hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="NoSpace: Beta Values", xlab="Beta", breaks=15) 
+hist(unlist(beta_n[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), add = TRUE, breaks=15) #ylim=c(0,2100)
+
+abline(v = mean(unlist(beta_n[ , 2:52])), col = rgb(255,192,203, max = 255), lwd = 2)
+abline(v = mean(unlist(beta_s[ , 2:52])), col = rgb(173,216,230, max = 255), lwd = 2)
+legend("topright", c("Newt", "Snake"), fill=c(rgb(255,192,203, max = 255), rgb(173,216,230, max = 255)))
+
+```
+
+```{r, comp betas}
+
+var_by_var(beta_n, beta_s, beta_n, beta_s, title="NoSpace: Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
+
+```
+
+```{r, beta figures}
+
+g1 <- var_by_var( beta_n, beta_s, beta_n, beta_s, title="NoSpace: Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
+
+g2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="NoSpace: Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
+
+g3 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="NoSpace: Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
+
+g4 <- var_by_var(Newt_mean_Pheno, beta_s, beta_n, Snake_mean_Pheno, title="NoSpace: Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
+
+grid.arrange(g1, g2, g3, g4, nrow=2)
+
+```

### 2021-11-17 graphs_newt_snakes/fitness_cost.Rmd
I am writing about what I did in the fitness cost simulations. I am taking extra time to describe what my different figure functions can do (to help future me thanks in advance). I will need to cont writing about what each of the figures mean and write down my thoughts. I am also starting to try to get beta values in sections, but the thing peter pointed to has not worked yet. I am not sure it will work but I will try some more tomorrow. ps newt_snake_1on1 dispay (what I am editing) will NOT work on normal slim (using a function not out on the current version). This was my first experence with

@@
 So to keep a high cost phenotype there needs to be strong selection.
+The graph below is my initial idea on how fitness cost in my system should work.
 
@@
 
-I chose a phenotype of 3 to be half as good.
-This might be a tad too strong.
+I chose a phenotype of 3 to be half as good (this might be a tad too strong).
+I chose the value 3 because of the phenotypes of newts and snakes seen in the Brodies map.
 To calculate cost I need to look at the fitness scaling (between 0 and 1) and make my chosen phenotype meet the line at half of the total fitness (0.5).
@@
 I ran one simulation with the cost once and the phenotypes just keep decreasing (math version will be presented later).
-The simulation ran for a long time (5000 generations) and the population did not explode or decrease.
-Is it possible for the phenotypes to be completely pushed back to 0.
+The simulation ran for a long time (5000 generations) and the population size did not explode or decrease.
+Is it possible for the phenotypes to be completely pushed back to 0?
+Are non-zero phenotypes a sign of poitive selection (especially if they started above 0)?
 Do we still see spots were coevolution is happening?
 Should I change the slope of the cost curve?
+
+## Dataframe and Graphs
+
+I use the same method for building my dataframes and figures as I did in the nospace R markdown.
+My general theme is to make my figures and data frames reusable from simulation to simulation and from one variable to the next.
+It might be helpful to write some more information about each of the functions that I use.
 
@@
 phenotype_trends <- function(file, title, subt, my_color, is_log=FALSE, leg_off=FALSE){
+  # Looks at the mean phenotype of all of the simulations and graphs them as lines together
+  # good for seeing what all of the simulations are doing
+  # it can log the y axis and turn off the legend
   data_frame_temp <- as.data.frame(t(file))
@@
     scale_color_manual(values = rep(my_color, nrow(file)))+
-    xlab("Generations") + ylab("Interaction")+
+    xlab("Generations") + ylab("Phenotype")+
     theme_bw() + theme(legend.position="none")
@@
     if(is_log==TRUE){
-  p = p + scale_y_log10() + ylab("Interaction (Log)")
+  p = p + scale_y_log10() + ylab("Phenotype (Log)")
     }
@@
 var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
+
+  # very powerful and confusing graph. It can plot a max of 4 variables at a time!
+  # I use it to compare newts and snakes to each other
+  # I can log the y axis
+  # I can look at things by generation (uses just the newt x and snake x)
+  # I can compare newt to snake (uses the newt x and snake y)
+  # I can subtract (snake - newt) (subtracts the x value and plots the y value)
+  # Color can plot var by var and pick a 3rd var to color the points (use thenewt x, snake y and newt file y for the color)
 
@@
 phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE, ylim_max=100){
+  #this function can graph phenotype of all of the simulations (as a mean or boxplot) by generations (I can specify the amount of generations to show)
   data_frame_newt_temp <- Newt_file
@@
 phenotype_dif_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE){
+  #this function can graph to difference between phenotypes of all of the simulations (as lines or boxplot) by generations
+  #(I can specify the amount of generations to show)
   data_frame_newt_temp <- Newt_file
@@
 phenotype_change_graph_s <- function(files, title, is_log=FALSE, xlim_value){
+  # this shows me how the phenotype change in one single for each simulation
+  # it takes all of the files and reads all of them in to take the first and last point
+  # highly inefficient
 file1 <- read.table(files[1], header = TRUE)
@@
 
+## Simulations
+
+I ran a spatial antagonistic co-evolution simulation with a fitness cost.
+Both newts and snakes had the same mutation rate, mutation effect sizes and fitness costs.
+Here, fitness cost remained the same between all of the simulations, but the mutation rate and mutation effect size differed.
+I ran about 100 simulations to get a general idea of what might be happening in the simulations.
+I wanted to focus on what was happening to the phenotype of newts and snakes, while also observing other factors that I looked at in previous rmarkdowns (beta, phenotype differences, population sizes, ect).
+
 ```{r, data info}
@@
 
+## Exploring the Change in Phenotypes
+
 ```{r, phenotype change}
@@
 phenotype_change_graph_s(files, title="Change in Phenotype Space", is_log=TRUE, xlim_value=104)
+```
 
+```{r, looking at all sims phenotypes}
+a1<-phenotype_trends(Newt_mean_Pheno, "Newt Phenotype Simulation Trend", "sigma = 0.2, mu = 1.5625e-10", "darkred", is_log=FALSE, leg_off=FALSE)
+a2<-phenotype_trends(Snake_mean_Pheno, "Snake Phenotype Simulation Trend", "sigma = 0.2, mu = 1.5625e-10", "steelblue", is_log=FALSE, leg_off=FALSE)
+
+grid.arrange(a1, a2, nrow=1)
 ```
+
 ```{r, comparative figures this params}

### 2021-11-19 graphs_newt_snakes/fitness_cost.Rmd
I wrote down my thoughts about fitness cost and asked questions about the figures that I plotted

@@
 
+Here, I am looking at how the phenotypes of newts and snakes change from what they began at and what the ended at for all of the simulations that I ran.
+In all of the simulation the mean phenotype of the newts and snakes started out higher and after 5,000 generations it dropped.
+The phenotypes did not become 0.
+I kind of want them to hang out around 3.
+I wonder what would happen to the newt and snake phenotype if I kept the simulation running?
+
 ```{r, phenotype change}
@@
 ```
+
+I also graphed the newt and snake phenotype by generation for all of simulations.
+The typical trend that I saw was that the newt/snake phenotype would drop quickly then level out (it might be lowering slowly, but thats difficulat to tell).
 
@@
 
+When looking at the variation between the simulations for the mean phenotypes and the standard deviation I saw that the simulations seemed to match each other.
+There was little variation between the simulations.
+Is it possible for the interaction of selection and cost to make the newt and snake phenotypes more similar between simulations?
+Can the selection coef.
+be determined from these results?
+
 ```{r, comparative figures this params}
 
-sp<-phenotype_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=5)
+sp<-phenotype_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="Space: Variation in the Mean Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=5)
 
-sdp<-phenotype_boxplot(Newt_sd_Pheno, Snake_sd_Pheno, title="NoSpace: Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=5)
+sdp<-phenotype_boxplot(Newt_sd_Pheno, Snake_sd_Pheno, title="Space: Variation in the Sd of Phenotype For Newts and Snakes by Generation", subt="sigma = 0.2, mu = 1.5625e-10", boxy=TRUE, section=TRUE, section_num=10, ylim_max=5)
 
@@
 
+## The Difference Betwwen Snake and Newt Mean Phenotype
+
+As I have seen in most of my newt and snake simulations the difference between snake and newt mean phenotype was small.
+With the addition of a phenotype cost I see less simulations where either the newt or snake has a higher phenotype.
+Here, there are two simulations that show this happening.
+Does adding a cost keep one of the species from escaping the interaction?
+
 ```{r, the differences}
 
-bp <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=TRUE, section=TRUE, section_num=10)
+bp <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="Space: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=TRUE, section=TRUE, section_num=10)
 
-bp2 <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="NoSpace: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=FALSE, section=FALSE, section_num=0)
+bp2 <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="Space: Differences", subt="sigma = 0.2, mu = 1.5625e-10",boxy=FALSE, section=FALSE, section_num=0)
 
@@
 
+## Interaction Between Polulation Factors and Phenotype
+
+In this section I look at the interaction between population factors such as population size and the amount of newts and snakes killed and the phenotype of the newts and snakes.
+I will also try to compare these results to my simulations without cost.
+
+When I plotted the difference between mean phenotype and deaths/age I saw a square blob.
+There are too many points that were plotted on-top of each other to see a trend.
+A possible trend is that when the snake mean phenotype is higher more newts are dying.
+When the newt phenotype is higher there might be more snakes dying.
+This result is not what I saw in my other spatial simulation, it is more like what I saw in my nospace simulations.
+Why would this be occuring?
+I also saw a really weird interaction between population size and phenotype.
+When the snake phenotype was higher there were more newts and when the newt phenotype was higher there were more snakes.
+This is the exact opposite from what I had been seeing in the spatial and nospace simulations.
+Why would adding a cost to phenotypes be causing these patterns?
+Maybe, if the snake phenotype was higher then there would be more snakes, except that if the phenotype was higher there would be a cost lowering the amount of snakes.
+Maybe this does make sense.
+If newts or snakes had a high phenotype then there fitness would be lower which could lower the population size.
+
 ```{r, sel coef graphs}
 
-ps1 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, mean_newts_eaten, mean_snakes_eaten, title="NoSpace: Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="Deaths/age", subtract_x=TRUE)
+ps1 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, mean_newts_eaten, mean_snakes_eaten, title="Space: Differnece in mean phenotype by Deaths", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="Deaths/age", subtract_x=TRUE)
 
-ps2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_pop_size, Snake_pop_size, title="NoSpace: Differnece in mean phenotype by PopSize", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="PopSize", subtract_x=TRUE)
+ps2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_pop_size, Snake_pop_size, title="Space: Differnece in mean phenotype by PopSize", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Mean Pheno", y_label="PopSize", subtract_x=TRUE)
 
@@
 
+I also made my favorite whale plots!
+Except here I see the higher phenotype for a particular species when their population size is lower.
+I wonder if this is because of the interaction between newts and snakes and the cost of the phenotype.
+For example, maybe there are a lot of newts and they are interaction with snakes the only snakes to survive this interaction are snakes with a higher phenotype.
+The snakes have a higher phenotype are less fit so they reproduce less.
+I also saw a lot more in-between points where both the populations of newts and snakes were not large.
+The patter looks more like a hump and less like a curve.
+
 ```{r, popsize of newts and snakes with color of phenotype}
 
-vc1 <- var_by_var(Newt_pop_size, Newt_mean_Pheno, Newt_mean_Pheno, Snake_pop_size, title="NoSpace: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
+vc1 <- var_by_var(Newt_pop_size, Newt_mean_Pheno, Newt_mean_Pheno, Snake_pop_size, title="Space: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred")
 
-vc2 <- var_by_var(Newt_pop_size, Snake_mean_Pheno, Snake_mean_Pheno, Snake_pop_size, title="NoSpace: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")
+vc2 <- var_by_var(Newt_pop_size, Snake_mean_Pheno, Snake_mean_Pheno, Snake_pop_size, title="Space: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue")
 
@@
 
+## Beta Value and Other Comparisons
+
+I am currently working on a better way to measure the correlation between phenotype and fitness (beta).
+However, this is the old way that I have been measuring beta (which is for the whole population).
+The problem with this way of measuring beta is that ther migh be some area with a higher beat and areas with a lower beta which should cause the beta for the would population to be close to 0.
+
+So, when I plotted my beta values I was nor surprised to seem them clustered around 0. Beta does look to be slightly more negative. Could this be due to cost or is it just random chance?
+
 ```{r, beta distribution}
 
-hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="NoSpace: Beta Values", xlab="Beta", breaks=15) 
+hist(unlist(beta_s[ , 2:52]), col=rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue"), main="Space: Beta Values", xlab="Beta", breaks=15) 
 hist(unlist(beta_n[ , 2:52]), col=rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink"), add = TRUE, breaks=15) #ylim=c(0,2100)
@@
 
+The green eyeball of newt beta by snake beta values is centered around zero with a quite a few additional points neagtive for both the newts and the snakes.
+
 ```{r, comp betas}
 
-var_by_var(beta_n, beta_s, beta_n, beta_s, title="NoSpace: Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
+var_by_var(beta_n, beta_s, beta_n, beta_s, title="Space: Newt Betas by Snake Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt betas", y_label="Snake Betas", just_two = TRUE)
 
@@
 
+In the last set of figures I was surprised to see that beta values were very negative at the beginning of my simulation.
+This reflects on how quickly the newt and snake phenotype dropped in the beginning of the simulations.
+In the other three figures I did not notice any specfic patter or trend.
+It looks like a blob when looking at the difference between snake and newt phenotype vs age or beta.
+It also looks like a blob in the figure which plots newt mean phenotype by snake mean phenotype.
+
 ```{r, beta figures}
 
-g1 <- var_by_var( beta_n, beta_s, beta_n, beta_s, title="NoSpace: Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
+g1 <- var_by_var( beta_n, beta_s, beta_n, beta_s, title="Space: Betas By Generation", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Generation", y_label="Betas", by_gen=TRUE)
 
-g2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="NoSpace: Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
+g2 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, beta_n, beta_s, title="Space: Differnece in mean phenotype by Betas", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Betas", subtract_x=TRUE)
 
-g3 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="NoSpace: Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
+g3 <- var_by_var( Newt_mean_Pheno, Snake_mean_Pheno, Newt_age, Snake_age, title="Space: Differnece in mean phenotype by Age", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Dif in Pheno", y_label="Age", subtract_x=TRUE)
 
-g4 <- var_by_var(Newt_mean_Pheno, beta_s, beta_n, Snake_mean_Pheno, title="NoSpace: Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
+g4 <- var_by_var(Newt_mean_Pheno, beta_s, beta_n, Snake_mean_Pheno, title="Space: Newt Pheno by Snake Pheno", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Newt Mean Phenotype", y_label="Snake Mean Phenotype", just_two = TRUE)
 

### 2021-11-30 graphs_newt_snakes/What_is_sel_coef.Rmd
I am writing about selection coeffencts and staerting to try to get beta values for small sections of my simulations

@@
 
+To go about solving this problem I am reading part of the quantitative genetics book by Caballero.
+My goal is to find the response to selection.
+Typically the response to selection can be found by measuring how much the phenotype has changed, but there is also drift in my simulation (which theoretically can be moving the pehotypes around).
+So I specifically ask how **much** is selection moving things around?
+This is really a two part problem, first I need to find the correlation between fitness and phenotype (beta) for small sections, but then what does this correlation mean and how is it related to selection (possibly sel.
+coef.
+= cor/h^2)?
+To accomplish this I will work on it in two parts.
+Fist, I will try to calculate beta over small sections.
+Second, I will try to make a no-space simulation with a fixed phenotype for snakes or newts allow one to evolve and use theory to predict how much the mean phenotype should shift (easier said than done...).
+
 Currently, I measure selection with the variable beta.
@@
 -compare space to no space
+-manually make one phenotype higher by adding a value
 
@@
 mu_rate_u5=( 6.25e-10 1.56e-10 6.94e-11)
-
-I made 6 msprime files where one species phenotype is under 2 and one is under 5. I kept the under 2 params the same and moved the under 5 to each of the three pairs.
 

### 2021-12-16 graphs_newt_snakes/What_is_sel_coef.Rmd
I got the small area cov to be caculated. I need to figure out a better way to color it and save it (print it out in txt)
writing more about what i want to do in my selection experiment (the rmarkdown). working on improving the color for little beta in the newt snake 1on1. I am setting up the selection experiment for the no space slim. in nospaceslim1on1 i am trying out the writeFile funtion rating 10/10
I started to make graph/animations for the selection experiments

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
+library(ggplot2)
+library(viridis)
+library(colorspace)
+library(gridExtra)
+library(tidyverse)
+require(reshape2)
+library(plyr)
+library(gridGraphics)
+library(grid)
+library(gganimate)
+library(gifski)
+library(gapminder)
 ```
@@
 
-This Is how I would like one of the phenotypes to look if there was an advantage. I was trying to use Msprime to get this type of distribution, but it wasn't working.
+This is how I would like one of the phenotypes to look if there was an advantage. I was trying to use Msprime to get this type of distribution, but it wasn't working.
 
@@
 
-Heritability and genetic correlation page 54
+Heritability and genetic correlation page 54 might be more info in ch 9
+
+## NoSpace Selection Experiment
+
+Peter and I talked through a selection experiment in the nospace slimulation.
+We decided that newts' toxicity would be able to mutate and coevolve with to the snakes resistance (snakes phenotype is set to a value and unable to mutate).
+I picked parameters that would (hopefully) cause the newts toxicity phenotype to evolve quickly.
+I also tried increasing interaction rate and moving the snake resistant phenotype further or closer to the newt mean phenotype.
+
+I want to look at the newts' phenotype, fitness, and its ability to survive (based on phenotype) throughout the generations.
+Sometimes I get extreme newt phenotypes if the mutation rate is too high.
+In every simulation where newts became more toxic than snakes there was some competition between snakes and newts where snakes were eating any newt.
+Then newts and snakes were killing each other.
+Finally, newts were killing any snake that they met.
+The transition between newts being eaten by snakes to newts and snakes were killing each other took more time (generations) then when newt became more toxic than snakes.
+
+```{r, data}
+
+files <- list.files(path="~/Desktop/data", pattern="byind", full.names=TRUE, recursive=FALSE)
+file <- read.table(files[1], header = TRUE)
+```
+
+```{r, pheno dist graph, warning = F}
+#animation.hook="gifski"
+
+hist(file$phenotype[file$gen==1], col="darkred",xlim = c(0, 3), main = "Newt Phenotypes Distribution for 1st Gen", xlab = "Phenotype")
+#xlim = c(1, 6)
+
+p1<-ggplot(file, aes(phenotype)) + 
+  geom_histogram(col = "darkred", fill = "darkred", binwidth=30)+ 
+  theme_bw()+
+  scale_y_log10()+
+  xlim(-1, 1000) +
+  # gganimate specific bits:
+labs(title = 'Newt Phenotype Dist. Generation: {frame_time}', x = 'Phenotype', y = 'Count') +
+  transition_time(gen) +
+  ease_aes('linear')
+animate(p1, duration = 25, fps = 30, width = 400, height = 400, renderer = gifski_renderer())
+anim_save("data/gganimate1.gif")
+```
+
+```{r, pheno fit graph, warning = F}
+graph_file<-file
+title<-"Phenotype by Fitness"
+subt<-"extra stuff"
+    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
+    geom_point(colour = "darkred")+
+    ggtitle(title, subtitle = subt) +
+    #xlim(-1, 1000) +
+    theme_bw() + theme(legend.position="none")+
+    # gganimate specific bits:
+labs(title = 'Generation: {frame_time}', x = 'Phenotype', y = 'Fitness') +
+  transition_time(gen) +
+  ease_aes('linear')
+animate(p, duration = 25, fps = 30, width = 400, height = 400, renderer = gifski_renderer())
+anim_save("data/gganimate1_2.gif")
+```
+
+```{r, pheno fit graph log, warning = F}
+graph_file<-file
+title<-"Phenotype by Fitness"
+subt<-"extra stuff"
+    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
+    geom_point(colour = "darkred")+
+    ggtitle(title, subtitle = subt) +
+    #xlim(-1, 1000) +
+    scale_x_log10()+
+    theme_bw() + theme(legend.position="none")+
+    # gganimate specific bits:
+labs(title = 'Generation: {frame_time}', x = 'Phenotype (log)', y = 'Fitness') +
+  transition_time(gen) +
+  ease_aes('linear')
+animate(p, duration = 25, fps = 30, width = 400, height = 400, renderer = gifski_renderer())
+anim_save("data/gganimate1_2log.gif")
+
+```

### 2021-12-16 graphs_newt_snakes/What_is_sel_coef.Rmd
adding new graph to show fitness ditributions and fixing other animations that show dots moving (they were confusing)

@@
 files <- list.files(path="~/Desktop/data", pattern="byind", full.names=TRUE, recursive=FALSE)
-file <- read.table(files[1], header = TRUE)
+number=7
+file <- read.table(files[number], header = TRUE)
+file_name <- substr(files[number], 36, 168)
+print(paste0("File Name: ", file_name))
 ```
@@
 
-p1<-ggplot(file, aes(phenotype)) + 
-  geom_histogram(col = "darkred", fill = "darkred", binwidth=30)+ 
+p1<-ggplot(file[which(file$phenotype<=1001),], aes(phenotype)) + 
+  geom_histogram(col = "darkred", fill = "darkred", binwidth=0.05)+ 
   theme_bw()+
   scale_y_log10()+
-  xlim(-1, 1000) +
+  xlim(-1, max(file[which(file$phenotype<=1001),]$phenotype)) +
+  #ylim(1, 30)+
   # gganimate specific bits:
@@
   ease_aes('linear')
-animate(p1, duration = 25, fps = 30, width = 400, height = 400, renderer = gifski_renderer())
+animate(p1, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
+anim_save("data/gganimate1.gif")
+```
+
+```{r, fit dist graph, warning = F}
+#animation.hook="gifski"
+
+hist(file$fitness[file$gen==1], col="darkred",xlim = c(0, 1), main = "Newt Fitness Distribution for 1st Gen", xlab = "Fitness")
+#xlim = c(1, 6)
+
+p1<-ggplot(file, aes(fitness)) + 
+  geom_histogram(col = "darkred", fill = "darkred", binwidth=0.01)+ 
+  theme_bw()+
+  xlim(-0.2, 1.0)+
+  # gganimate specific bits:
+labs(title = 'Newt Fitness Dist. Generation: {frame_time}', x = 'Fitness', y = 'Count') +
+  transition_time(gen) +
+  ease_aes('linear')
+animate(p1, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
 anim_save("data/gganimate1.gif")
@@
 title<-"Phenotype by Fitness"
-subt<-"extra stuff"
+subt<-file_name
     p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
@@
   ease_aes('linear')
-animate(p, duration = 25, fps = 30, width = 400, height = 400, renderer = gifski_renderer())
+animate(p, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
 anim_save("data/gganimate1_2.gif")
@@
   ease_aes('linear')
-animate(p, duration = 25, fps = 30, width = 400, height = 400, renderer = gifski_renderer())
+animate(p, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
 anim_save("data/gganimate1_2log.gif")

### 2021-12-17 graphs_newt_snakes/What_is_sel_coef.Rmd
Figuring out better animations

@@
 files <- list.files(path="~/Desktop/data", pattern="byind", full.names=TRUE, recursive=FALSE)
-number=7
+number=1
 file <- read.table(files[number], header = TRUE)
@@
 print(paste0("File Name: ", file_name))
+
 ```
@@
   ease_aes('linear')
-animate(p1, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
+animate(p1, duration = 30 , fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
 anim_save("data/gganimate1.gif")
+#fps = round(max(file$gen)/33)
 ```
@@
   ease_aes('linear')
-animate(p1, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
+animate(p1, duration = 30, fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
 anim_save("data/gganimate1.gif")
@@
   ease_aes('linear')
-animate(p, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
+animate(p, duration = 30, fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
 anim_save("data/gganimate1_2.gif")
@@
   ease_aes('linear')
-animate(p, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
+animate(p, duration = 30, fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
 anim_save("data/gganimate1_2log.gif")

### 2022-01-04 graphs_newt_snakes/What_is_sel_coef.Rmd
making new figures for sel coefs and trying to figure out how to bin the data

@@
 files <- list.files(path="~/Desktop/data", pattern="byind", full.names=TRUE, recursive=FALSE)
-number=1
+number=7
 file <- read.table(files[number], header = TRUE)
@@
   ease_aes('linear')
-animate(p, duration = 30, fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
+animate(p, duration = 30, fps = round(max(graph_file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
 anim_save("data/gganimate1_2log.gif")
@@
 ```
+
+```{r, fitness and phenotype with gen bins}
+graph_file<-file
+graph_file$zone = "A"
+graph_file[which(graph_file$gen > 100 & graph_file$gen < 199),]$zone="B"
+graph_file[which(graph_file$gen > 200 & graph_file$gen < 299),]$zone="C"
+graph_file[which(graph_file$gen > 300 & graph_file$gen < 399),]$zone="D"
+graph_file[which(graph_file$gen > 400 & graph_file$gen < 499),]$zone="E"
+graph_file[which(graph_file$gen > 500 & graph_file$gen < 599),]$zone="F"
+graph_file[which(graph_file$gen > 600 & graph_file$gen < 699),]$zone="G"
+graph_file[which(graph_file$gen > 700 & graph_file$gen < 799),]$zone="H"
+graph_file[which(graph_file$gen > 800 & graph_file$gen < 899),]$zone="I"
+graph_file[which(graph_file$gen > 900 ),]$zone="J"
+
+title<-"1000gen Fitness, Color every 100gen"
+subt<-file_name
+    p <- ggplot(graph_file, aes(fitness, fill = zone)) +
+    geom_histogram( bins = 50)+
+    ggtitle(title, subtitle = subt) +
+    #xlim(-1, 1000) +
+    #scale_x_log10()+
+    theme_bw()
+
+p
+
+title<-"1000gen Phenotype, Color every 100gen"
+subt<-file_name
+    p <- ggplot(graph_file, aes(phenotype, fill = zone)) +
+    geom_histogram( bins = 50)+
+    ggtitle(title, subtitle = subt) +
+    #xlim(-1, 1000) +
+    #scale_x_log10()+
+    theme_bw()
+
+p
+
+```
+
+```{r, phenotype bins}
+
+graph_file<-file
+
+pmin = min(file$phenotype)
+pmax = max(file$phenotype)
+psd = sd(file$phenotype)
+pmean = mean(file$phenotype)
+
+bin(file$phenotype)
+graph_file$
+
+```

### 2022-01-06 graphs_newt_snakes/What_is_sel_coef.Rmd
thinking about how to make bins

@@
 ```{r, phenotype bins}
-
+library(OneR)
 graph_file<-file
-
+data = file$phenotype
 pmin = min(file$phenotype)
@@
 
-bin(file$phenotype)
-graph_file$
+mybins = bin(file$phenotype, nbins = 3)
+str(bin(data, nbins = 3, labels = c("small", "medium", "large")))
 

### 2022-01-18 graphs_newt_snakes/fitness_cost.Rmd
I have started to run slim scripts to find a good value for the fitness cost. I have updated the 1on1 scripts to run better (like reducing the phenotype caculations, and including the files that need to be written out

@@
 
-If a phenotype of 3 is half the total fitness the cost wold be log 2
+If a phenotype of 3 is half the total fitness the cost would be log 2
 
@@
 ```
+
+## Extra thoughts
+
+Right now the phenotype of newts and snakes goes down due to fitness cost.
+However, it does not go down to 0.
+Which might indicate that there is a benefit for having a costly phenotype.
+I think the cost is too high in this case.
+
+Original choice is 10 phenotypes dropped to ~0.3
+Next choice is 100 phenotypes hold around 2-3
+
+what would phenotypes be like for 10, 20, 30, 40, 50, 60, 70, 80, 90, and 100

### 2022-01-20 graphs_newt_snakes/fitness_cost.Rmd
I fixed my file naming system in cost1on1. I also looked at the data from the different cost values and made some cool graphs

--- 2021-11-19 graphs_newt_snakes/fitness_cost.Rmd
@@
 ```
+
+## Extra thoughts on different values for cost
+
+Right now the phenotype of newts and snakes goes down due to fitness cost.
+However, the mean phenotype of snakes and newts does not go down to 0.
+This result might indicate that there is a benefit for having a costly phenotype.
+I think the cost value I picked is too high in this case.
+
+Original choice is 10 phenotypes dropped to ~0.3
+Next choice is 100 phenotypes hold around 2-3?
+
+For this experiment I tested different cost values (exp(-('pheno'/cost_value)^2.
+The main question I asked was, what would phenotypes be like if my cost-value was set at 10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, and 200?
+I want to look at the mean and standard deviation of the newt and snake phenotypes between these simulations.
+
+I run one cost1on1 simulation per cost value. Each of these simulations start out with the same msprime file and run on different seeds.
+
+```{r, phenotypes at differnt costs data gather}
+
+files <- list.files(path="~/Desktop/data", pattern="costtest", full.names=TRUE, recursive=FALSE)
+number=1
+file <- read.table(files[number], header = TRUE)
+#file_name <- substr(files[number], 36, 186)
+#print(paste0("File Name: ", file_name))
+
+costnum <- as.numeric(unlist(strsplit(files[number], split= "_"))[30])
+file$cost <-costnum
+
+for(i in seq(2, length(files), 2)){
+  temp_file <- read.table(files[i], header = TRUE)
+  costnum<-as.numeric(unlist(strsplit(files[i], split= "_"))[30])
+  temp_file$cost <-costnum
+  file <- rbind(file, temp_file)
+
+}
+```
+
+```{r, phenotypes at differnt costs figure}
+pl1 <- ggplot(file, aes(gen, Newt_mean_Pheno, col=factor(cost))) + geom_line()+ 
+    ggtitle("Newt Mean Pheno by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+pl2 <- ggplot(file, aes(gen, Snake_mean_Pheno, col=factor(cost))) + geom_line()+ 
+    ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+pl3 <- ggplot(file, aes(gen, Newt_sd_Pheno, col=factor(cost))) + geom_line()+ 
+    ggtitle("Newt SD Pheno by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+pl4 <- ggplot(file, aes(gen, Snake_sd_Pheno, col=factor(cost))) + geom_line()+ 
+    ggtitle("Snake Sd Pheno by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+pl5 <- ggplot(file, aes(gen, Newt_max_Pheno, col=factor(cost))) + geom_line()+ 
+    ggtitle("Newt Max Pheno by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+pl6 <- ggplot(file, aes(gen, Snake_max_Pheno, col=factor(cost))) + geom_line()+ 
+    ggtitle("Snake Max Pheno by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+pl7 <- ggplot(file, aes(gen, Newt_min_Pheno, col=factor(cost))) + geom_line()+ 
+    ggtitle("Newt Min Pheno by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+pl8 <- ggplot(file, aes(gen, Snake_min_Pheno, col=factor(cost))) + geom_line()+ 
+    ggtitle("Snake Min Pheno by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+grid.arrange(pl1, pl2, nrow=1)
+grid.arrange(pl3, pl4, nrow=1)
+grid.arrange(pl5, pl6, nrow=1)
+grid.arrange(pl7, pl8, nrow=1)
+
+```
+
+Here I looked at the mean, sd, max, and min of newts and snakes phenotypes at every 20 generations (dots would be more accurate but lines are easier to see in this case).
+Each line is a simulation that I ran at a certain cost value.
+These cost values when from 10 to 200.
+It looks like the higher I set the cost value the larger the mean phenotype gets and stays.
+I also noticed that the standard deviation and maximum phenotype got larger as the cost value got larger.
+The minimum phenotype also seemed to get larger as the cost value was increased, but it varied a lot and looked to have been near or at 0 is some of the simulations.
+I feel like some of the max phenotypes for the newts and snakes are really high at some points in the simulations (occurring when the cost value is high).
+It seems like the higher the cost value (which is similar to the phenotype of half fitness?) the larger and more variable the phenotype of newts and snakes gets.
+
+## At Different Costs do the Mean Phenotpyes Still Match?
+
+My next thoughts in this experiment fell on the interaction between newts and snakes.
+To see if the newts and snakes are interacting I looked at the difference between the mean snake phenotype and the mean newt phenotype.
+This will (hopefully) show me that newts and snake phenotypes are similar and thus they are competing.
+In other words one of the species phenotype is not so high that the other species cannot compete.
+However, I would like to not that for each of these simulations I ran only one copy to get a general sence of what might be happing when the cost value was changed.
+
+```{r, cost and the dif between snake and newt}
+file$dif <- file$Snake_mean_Pheno-file$Newt_mean_Pheno
+
+ggplot(file, aes(gen, dif, col=factor(cost))) + geom_line()+ 
+    ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+```
+
+From this figure I looked at the difference between snake and newt mean phenotype over 5000 generations (data gathered every 20 gens).
+Each line is a simulation that I ran at a certain cost value ranging from 10 to 200.
+For the most part the two phenotypes remained close to each other.
+When the cost values are smaller the phenotype of newts and snakes is smaller and then the difference between them is smaller.
+When the cost value was higher then the difference between snake and newt phenotypes was higher.
+I liked how there were times in this simulation where it seems like newts are winning (negative values) and then in the smae simulation snakes seem to be winning (positive values).
+Maybe some evidence of a phenotype cycling?

### 2022-01-24 graphs_newt_snakes/Are_we_at_steadystate.Rmd
I am currently running a very long simulation to to see what happens overtime. I have also added some new graphs to fitness cost by looking at how different fitness cost effects the phenotype of the population. Even when there are different cost values all of the simulation reach a point where the it equiliborates on the time scale of drift. I have also started two new rmarkdowns/ experiments. One is to compare different genetic architectures (which I just finished running on the cluster) and the other is to look at steady-state of my co-evo cost simulation. I look forward to the results

---
title: "Are We At SteadyState Yet"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
```

## Goal

My aim is to run one cost_1on1 simulation for a really long time to determine if I am able to tell if the simulation has gone into steady state. The simulation the cost value will be 100 and I will run it for 10 million generations. The goal is to collect whole population data every 20th generation and individual data every 1000th generation

Approximation of data points:
gen/when data is collected 10000000/20 = 
gen/when data is collected * number of ind 10000000/1000*1500 = 1.5e+07

These files might be too big (we will see).

Things should stop changing by 2Ne generations. So maybe around 1,400 generations if my population size is around 700.

I have noticed that there seems to be no more variation in the populations. On SLiM all of the individuals in their respective populations have the same color indicating same phenotype

### 2022-01-24 graphs_newt_snakes/Comparing_GA.Rmd
I am currently running a very long simulation to to see what happens overtime. I have also added some new graphs to fitness cost by looking at how different fitness cost effects the phenotype of the population. Even when there are different cost values all of the simulation reach a point where the it equiliborates on the time scale of drift. I have also started two new rmarkdowns/ experiments. One is to compare different genetic architectures (which I just finished running on the cluster) and the other is to look at steady-state of my co-evo cost simulation. I look forward to the results

---
title: "Comparing Genetic Architectures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
```

## Purpose

Here I am doing a small experiment to compare different genetic architectures between snakes and newts. I will use the cost_1on1 simulation and my snake_newt_gv msprime simulation.

Outline

-Pick 4 different mu sigma combinations where mu*sigma^2 is constant (mu=1e-11, sigma=5) to (mu=1e-8, sigma=0.005) i.e (mu=1e-11, sigma=5, mu=1e-10, sigma=0.5, mu=1e-9, sigma=0.05 mu=1e-8, sigma=0.005)
-In total that will be 16 msprime simulations and 16 slim simulations
-make a co-evolutionary heatmap

Started to run msprim simulations on cluster

### 2022-01-24 graphs_newt_snakes/fitness_cost.Rmd
I am currently running a very long simulation to to see what happens overtime. I have also added some new graphs to fitness cost by looking at how different fitness cost effects the phenotype of the population. Even when there are different cost values all of the simulation reach a point where the it equiliborates on the time scale of drift. I have also started two new rmarkdowns/ experiments. One is to compare different genetic architectures (which I just finished running on the cluster) and the other is to look at steady-state of my co-evo cost simulation. I look forward to the results

@@
 log(2) = (a/b)^2
-b = 3/log(2) = 10
+b = 3/log(2) = 4.2
 
-SO cost = (phenotype/10)^2
+SO cost = (phenotype/4.2)^2
+
+I used 10 instead of 4.2 (due to math errors).
 
@@
 Maybe some evidence of a phenotype cycling?
+
+## An Equilibrium
+
+Is there a point where the cost of a phenotype reaches a balance with selection pressure experienced by the population?
+
+```{r, cost equlibrium}
+
+file$newt_equl <- file$Newt_mean_Pheno/file$cost
+file$snake_equl <- file$Snake_mean_Pheno/file$cost
+
+e1 <- ggplot(file, aes(gen, newt_equl, col=factor(cost))) + geom_line()+ 
+    ggtitle("Newt Mean Pheno/Cost by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype/Cost")+
+    theme_bw()
+
+e2 <- ggplot(file, aes(gen, snake_equl, col=factor(cost))) + geom_line()+ 
+    ggtitle("Snake Mean Pheno/Cost by Gen", subtitle = "Different Cost") +
+    xlab("Generations") + ylab("Phenotype/Cost")+
+    theme_bw()
+
+grid.arrange(e1, e2, nrow=1)
+```
+
+```{r, population size equlibrium}
+
+pop1 <- ggplot(file, aes(gen, Newt_pop_size, col=factor(cost))) + geom_line()+ 
+    ggtitle("Newt Popsize by Gen", subtitle = "Different Cost") +
+    xlab("Popsize") + ylab("Phenotype/Cost")+
+    theme_bw()
+
+pop2 <- ggplot(file, aes(gen, Snake_pop_size, col=factor(cost))) + geom_line()+ 
+    ggtitle("Snake Popsize by Gen", subtitle = "Different Cost") +
+    xlab("Popsize") + ylab("Phenotype/Cost")+
+    theme_bw()
+
+grid.arrange(pop1, pop2, nrow=1)
+```

### 2022-01-25 graphs_newt_snakes/Are_we_at_steadystate.Rmd
I am running cost1on1 for very long periods of time and am prining out the values. I want to see what happens when i change interaction rate and population size. Does a population go extinct? is ther coexistance or coevo? I am also writing and making more graphs in the rmarkdowns

@@
 
-I have noticed that there seems to be no more variation in the populations. On SLiM all of the individuals in their respective populations have the same color indicating same phenotype
+I have noticed that there seems to be no more variation in the populations.
+On SLiM all of the individuals in their respective populations have the same color indicating same phenotype.
+The beta values are all 0's.
+All of the phenotypes have gotten really small (very close to 0).
+There is no longer co-evolution, but maybe coexistence.
+
+More things that I have noticed: If interaction rate is higher like 0.15 or 0.10 then one of the populations will go extinct. This might change if the population size is larger

### 2022-01-25 graphs_newt_snakes/fitness_cost.Rmd
I am running cost1on1 for very long periods of time and am prining out the values. I want to see what happens when i change interaction rate and population size. Does a population go extinct? is ther coexistance or coevo? I am also writing and making more graphs in the rmarkdowns

@@
 abline(h=9, col="red") # represents half of the individuals fitness
+
 ```
@@
 ```
+
+```{r, is this pheno what I expect}
+phenotype <- c(0:200)
+plot(phenotype,exp(-(phenotype/200)^2), type = "l", main="Fitness Cost", xlab="Phenotype", ylab="Cost")
+lines(phenotype,exp(-(phenotype/150)^2))
+lines(phenotype,exp(-(phenotype/100)^2))
+lines(phenotype,exp(-(phenotype/50)^2))
+lines(phenotype,exp(-(phenotype/10)^2))
+```

### 2022-01-25 graphs_newt_snakes/Comparing_GA.Rmd
I am working on making plots to see if there is an obvious winner

@@
 
--Pick 4 different mu sigma combinations where mu*sigma^2 is constant (mu=1e-11, sigma=5) to (mu=1e-8, sigma=0.005) i.e (mu=1e-11, sigma=5, mu=1e-10, sigma=0.5, mu=1e-9, sigma=0.05 mu=1e-8, sigma=0.005)
+-Pick 4 different mu sigma combinations where mu*sigma^2 is constant (mu=1e-11, sigma=5) to (mu=1e-8, sigma=0.005) i.e ((mu=1e-11, sigma=5(A)), (mu=1e-10, sigma=0.5(B)), (mu=1e-9, sigma=0.05(C)), (mu=1e-8, sigma=0.005(D))) The ABCD represents the group of mu and sigma.
+When in the newt and snake simulation the groups will be paired to make 16 pairs.
 -In total that will be 16 msprime simulations and 16 slim simulations
+-See if there are any obvious winners
 -make a co-evolutionary heatmap
 
-Started to run msprim simulations on cluster
+I ran msprime simulations and the slim simulations on cluster in GA_lt folder.
+Mt goal is to first see if there is an obvious "winner" in the co-evolutionary arms race between these species.
+
+First, I want to look at the mean pheotypes of newts and snakes as the generations increase.
+Then I want to look at the difference between the mean phenotypes for each of the 16 simulations.
+I need to make the data frame to compare all 16 simulations.
+I noticed in the mu=1e-11, sigma=5 simulations that the staring pheotypes of some of the individulas were really high and sometimes the population crashed and died out.
+
+```{r, making data frames}
+
+making_data_frames <- function(files, spe_col) {
+i=1
+for (current_file in files){
+ #print(current_file)
+
+  if(i ==1){
+    file <- read.table(current_file, header = TRUE)
+
+    file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+      # might want to change to all_of(spe_col)
+    file %>% 
+      select(all_of(spe_col), gen) %>%
+      #rownames_to_column() %>% 
+      gather(variable, value, -gen) %>% 
+      spread(gen, value) -> new_file
+
+    new_file$variable[i] <- paste0(spe_col,"_output_", i)
+    i = i + 1
+    next
+    }
+  file <- read.table(current_file, header = TRUE)
+
+  file[[spe_col]][file[[spe_col]] == "NULL"] <- NA
+
+file %>% 
+  select(all_of(spe_col), gen) %>%
+  #rownames_to_column() %>% 
+  gather(variable, value, -gen) %>% 
+  spread(gen, value) -> temp_file
+
+temp_file$variable[1] <- paste0(spe_col,"_output_", i)
+
+new_file<-rbind(new_file, temp_file)
+i = i + 1
+}
+return(new_file)
+}
+
+```
+
+```{r, making resueable figures, results='hide', message=FALSE, warning=FALSE}
+
+phenotype_trends <- function(file, title, subt, my_color, is_log=FALSE, leg_off=FALSE){
+  # Looks at the mean phenotype of all of the simulations and graphs them as lines together
+  # good for seeing what all of the simulations are doing
+  # it can log the y axis and turn off the legend
+  data_frame_temp <- as.data.frame(t(file))
+
+  colnames(data_frame_temp) <- data_frame_temp[1,]
+  names(data_frame_temp) <- colnames(data_frame_temp)
+  steps <- colnames(file[ , !(names(file) %in% "variable")])
+data_frame_temp <- data_frame_temp[-1, ] 
+data_frame_temp$steps <- as.numeric(unlist(steps))
+
+  graph_file <- melt(data_frame_temp,  id.vars = 'steps', variable.name = 'series')
+
+  graph_file$series<-unlist(str_split_fixed(graph_file$series, "Pheno_", 2))[,2]
+
+    p <- ggplot(graph_file, aes(steps, as.numeric(value))) + geom_line(aes(colour = series))+ 
+    #ggtitle(title, subtitle = subt) +
+    #scale_color_manual(values = rep(my_color, nrow(file)))+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw() + theme(legend.position="none")
+
+    if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Phenotype (Log)")
+    }
+     if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+    return(p)
+}
+
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
+
+  # very powerful and confusing graph. It can plot a max of 4 variables at a time!
+  # I use it to compare newts and snakes to each other
+  # I can log the y axis
+  # I can look at things by generation (uses just the newt x and snake x)
+  # I can compare newt to snake (uses the newt x and snake y)
+  # I can subtract (snake - newt) (subtracts the x value and plots the y value)
+  # Color can plot var by var and pick a 3rd var to color the points (use thenewt x, snake y and newt file y for the color)
+
+  data_frame_newt_temp_x <- Newt_file_x
+  data_frame_newt_temp_x <- data_frame_newt_temp_x[ , !(names(data_frame_newt_temp_x) %in% "variable")]
+
+  data_frame_snake_temp_x <- Snake_file_x
+  data_frame_snake_temp_x <- data_frame_snake_temp_x[ , !(names(data_frame_snake_temp_x) %in% "variable")]
+
+  data_frame_newt_temp_y <- Newt_file_y
+  data_frame_newt_temp_y <- data_frame_newt_temp_y[ , !(names(data_frame_newt_temp_y) %in% "variable")]
+
+  data_frame_snake_temp_y <- Snake_file_y
+  data_frame_snake_temp_y <- data_frame_snake_temp_y[ , !(names(data_frame_snake_temp_y) %in% "variable")]
+
+  Number <- colnames(data_frame_newt_temp_x)
+  data_frame_newt_x <- gather(data_frame_newt_temp_x, Number, value_x)
+  data_frame_newt_x$type <- "Newt"
+  data_frame_newt_y <- gather(data_frame_newt_temp_y, Number, value_y)
+  data_frame_newt <- cbind(data_frame_newt_x, data_frame_newt_y)
+  data_frame_newt <- data_frame_newt[-4]
+  data_frame_snake_x <- gather(data_frame_snake_temp_x, Number, value_x)
+  data_frame_snake_x$type <- "Snake"
+  data_frame_snake_y <- gather(data_frame_snake_temp_y, Number, value_y)
+  data_frame_snake <- cbind(data_frame_snake_x, data_frame_snake_y)
+  data_frame_snake <- data_frame_snake[-4]
+
+ if(subtract_x==FALSE){
+   combo <- rbind(data_frame_newt, data_frame_snake)
+   combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
+   p <- ggplot(combo_s) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color=type), alpha=0.1)+
+      scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+ }
+ if(subtract_x==TRUE){
+    subtract_val <- data_frame_snake_x$value_x - data_frame_newt_x$value_x
+    total_sub_dataframe <- data.frame(subtract_val, data_frame_newt_y$value_y, data_frame_snake_y$value_y)
+    total_sub_dataframe <- total_sub_dataframe[sample(nrow(total_sub_dataframe), nrow(total_sub_dataframe)), ]
+    colnames(total_sub_dataframe) <- c("SnakeMisNewt_Pheno","Newts","Snakes")
+     p <- ggplot(total_sub_dataframe) +
+      #xlim(0, 1000)+
+       ggtitle(title, subtitle = subt) +
+       xlab(x_label) + ylab(y_label)+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Newts), color="Newts"), alpha=0.1)+
+       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Snakes), color="Snakes"), alpha=0.1)+
+        scale_colour_manual(name = "Species", values = c("Newts" = "darkred", "Snakes" = "steelblue"))+
+        theme(plot.title = element_text(size=5)) +
+        theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+ }
+  if(by_gen==TRUE){
+    combo <- rbind(data_frame_newt, data_frame_snake)
+    combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
+       p <- ggplot(combo_s) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(Number), y=as.numeric(value_y), color=type), alpha=0.1)+
+      scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  }
+
+   if(just_two==TRUE){
+     just2 <- cbind(data_frame_newt_x, data_frame_snake_y)
+     just2 <- just2[-4]
+       p <- ggplot(just2) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y)), color = "darkgreen", alpha=0.1)+
+      theme(plot.title = element_text(size=5)) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+   }
+
+   if(colored==TRUE){
+     color3 <- cbind(data_frame_newt_x, data_frame_snake_y, data_frame_newt_y)
+     color3 <- color3[-c(1,3,4,6)]
+     suppressWarnings(suppressMessages(suppressPackageStartupMessages({require(scales)})))
+     amin <- 0.1
+     lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
+     lowcol <- paste0("#",   sep = "",
+                 paste(format(lowcol.hex, width = 2), collapse = ""))
+       p <- ggplot(color3) +
+    #xlim(0, 1000)+
+      ggtitle(title, subtitle = subt) +
+      xlab(x_label) + ylab(y_label)+
+      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color = value_y.1))+
+      theme(plot.title = element_text(size=5)) +
+      scale_colour_gradient(high = highcol, low = lowcol) + 
+      labs(colour = color_label) +
+      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  }
+  if(logy==TRUE){
+    p = p + scale_y_log10()
+  }
+
+  return(p)
+
+}
+
+phenotype_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE, ylim_max=100){
+  #this function can graph phenotype of all of the simulations (as a mean or boxplot) by generations (I can specify the amount of generations to show)
+  data_frame_newt_temp <- Newt_file
+  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]
+
+  data_frame_snake_temp <- Snake_file
+  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]
+
+   if(section==TRUE){
+
+   selcol = seq(1,ncol(data_frame_newt_temp), section_num)
+   data_frame_newt_temp <- data_frame_newt_temp %>% select(all_of(selcol))
+   data_frame_snake_temp <- data_frame_snake_temp %>% select(all_of(selcol))
+
+   }
+   Number <- colnames(data_frame_newt_temp)
+  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
+  data_frame_newt$type <- "Newt"
+  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
+  data_frame_snake$type <- "Snake"
+
+ combo <- rbind(data_frame_newt, data_frame_snake)
+
+ small_combo <- aggregate(as.numeric(combo$value),by=list(Number=as.numeric(combo$Number),type=combo$type),data=combo,FUN=mean, na.action = TRUE)
+
+if(boxy==TRUE){
+  p <- ggplot(combo) +
+    ylim(0, ylim_max)+
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotypes")+
+    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(value), color=type) )
+  }
+if(boxy==FALSE){
+  p <- ggplot(small_combo) +
+  #xlim(0, 1000)+
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotypes")+
+    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_point(aes(x=factor(as.numeric(Number)), y=as.numeric(x), color=type) )
+}
+
+ if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+
+return(p)
+}
+
+phenotype_dif_boxplot <- function(Newt_file, Snake_file, title, subt, boxy=FALSE, section=FALSE, section_num=0, leg_off=FALSE){
+  #this function can graph to difference between phenotypes of all of the simulations (as lines or boxplot) by generations
+  #(I can specify the amount of generations to show)
+
+  data_frame_newt_temp <- Newt_file
+  data_frame_newt_temp <- data_frame_newt_temp[ , !(names(data_frame_newt_temp) %in% "variable")]
+
+  data_frame_snake_temp <- Snake_file 
+  data_frame_snake_temp <- data_frame_snake_temp[ , !(names(data_frame_snake_temp) %in% "variable")]
+
+  if(section==TRUE){
+
+   selcol = seq(1,ncol(data_frame_newt_temp), section_num)
+   data_frame_newt_temp <- data_frame_newt_temp %>% select(all_of(selcol))
+   data_frame_snake_temp <- data_frame_snake_temp %>% select(all_of(selcol))
+
+ }
+
+  Number <- colnames(data_frame_newt_temp)
+  data_frame_newt <- gather(data_frame_newt_temp, Number, value)
+  data_frame_snake <- gather(data_frame_snake_temp, Number, value)
+  dif <- as.numeric(data_frame_snake$value)-as.numeric(data_frame_newt$value)
+
+  df_dif <- as.data.frame(dif)
+  df_dif$Number <- as.numeric(data_frame_newt$Number)
+
+  if(boxy==TRUE){
+ p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_boxplot(aes(x=factor(as.numeric(Number)), y=as.numeric(dif)), color="darkolivegreen" )
+ }
+ if(boxy==FALSE){
+   usims<-length(unique(Newt_file$variable))
+   df_dif$trial <- rep(paste0("sim_",LETTERS[1:usims]), ncol(Newt_file)-1)
+   p <- ggplot(df_dif) +
+    ggtitle(title, subtitle = subt) +
+    #xlim(100, 5000)+
+    ylim(-5, 5)+
+    xlab("Generation") + ylab("Average Phenotype Differences")+
+    theme(plot.title = element_text(size=5)) +
+    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+    geom_line(aes(x=as.numeric(Number), y=as.numeric(dif), color=factor(trial)))
+    #scale_color_brewer(palette="viridis")
+    #theme(legend.position="none")
+    #scale_color_manual(values = rep("darkolivegreen", nrow(data_frame_newt_temp)))
+   p
+ }
+   if(leg_off==TRUE){
+ p = p+ theme(legend.position = "none")}
+  return(p)
+
+}
+
+phenotype_change_graph_s <- function(files, title, is_log=FALSE, xlim_value){
+  # this shows me how the phenotype change in one single for each simulation
+  # it takes all of the files and reads all of them in to take the first and last point
+  # highly inefficient
+file1 <- read.table(files[1], header = TRUE)
+p <- ggplot(file1, aes(x=1:144)) +
+  xlim(0, xlim_value)+
+  ggtitle(title) +
+  xlab("Simulation number") + ylab("Phenotype")+
+  theme_bw()
+
+if(is_log==TRUE){
+  p = p + scale_y_log10() + ylab("Phenotype  (Log)")
+
+}
+
+i=1
+for (current_file in files){
+
+  file <- read.table(current_file, header = TRUE)
+  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
+  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
+  file <- file[complete.cases(file), ]
+ p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color= darken("darkred")) +
+   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color=lighten("darkred"))  + 
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color=darken("steelblue")) +
+  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color=lighten("steelblue"))+
+  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1, colour="Newt"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))+
+   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1, colour="Snake"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))
+
+ i = i+1
+}
+p <- p +
+ scale_colour_manual(name = "Species", values = c("Newt" = "darkred", "Snake"="steelblue"))
+return(p)
+}
+
+```
+
+```{r, create dataframe}
+files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+file <- read.table(files[1], header = TRUE)
+Newt_mean_Pheno <- making_data_frames(files, all_of("Newt_mean_Pheno"))
+Snake_mean_Pheno <- making_data_frames(files, all_of("Snake_mean_Pheno"))
+```
+
+```{r, plots compairing sims}
+
+a1<-phenotype_trends(Newt_mean_Pheno, "Newt Phenotype Simulation Trend", "16 trials", "darkred", is_log=T, leg_off=FALSE)
+a2<-phenotype_trends(Snake_mean_Pheno, "Snake Phenotype Simulation Trend", "16 trial", "steelblue", is_log=T, leg_off=FALSE)
+
+grid.arrange(a1, a2, nrow=1)
+
+bp2 <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="Space: Differences", subt="16 trial",boxy=FALSE, section=FALSE, section_num=0)
+
+grid.arrange(bp2, nrow=1)
+```

### 2022-01-28 graphs_newt_snakes/Comparing_GA.Rmd
making more graphs to look at the 16 simulations

@@
 
-var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen"){
+var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE, by_gen=FALSE, just_two=FALSE, colored=FALSE, color_label=NULL, highcol="darkseagreen", facet=FALSE){
 
@@
     total_sub_dataframe <- data.frame(subtract_val, data_frame_newt_y$value_y, data_frame_snake_y$value_y)
+    total_sub_dataframe$wrap <- rep(1:16, length(Number))
     total_sub_dataframe <- total_sub_dataframe[sample(nrow(total_sub_dataframe), nrow(total_sub_dataframe)), ]
@@
         theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
  }
@@
    if(colored==TRUE){
+
      color3 <- cbind(data_frame_newt_x, data_frame_snake_y, data_frame_newt_y)
      color3 <- color3[-c(1,3,4,6)]
+     color3$wrap <- rep(1:16, length(Number))
      suppressWarnings(suppressMessages(suppressPackageStartupMessages({require(scales)})))
@@
       theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+       if(facet==TRUE){
+
+     p = p + facet_wrap(~wrap)
+  }
   }
@@
  Snake_mean_Pheno <- making_data_frames(files, all_of("Snake_mean_Pheno"))
+ Newt_pop_size <- making_data_frames(files, all_of("Newt_pop_size"))
+ Snake_pop_size <- making_data_frames(files, all_of("Snake_pop_size"))
 ```
@@
 
-a1<-phenotype_trends(Newt_mean_Pheno, "Newt Phenotype Simulation Trend", "16 trials", "darkred", is_log=T, leg_off=FALSE)
-a2<-phenotype_trends(Snake_mean_Pheno, "Snake Phenotype Simulation Trend", "16 trial", "steelblue", is_log=T, leg_off=FALSE)
+# a1<-phenotype_trends(Newt_mean_Pheno, "Newt Phenotype Simulation Trend", "16 trials", "darkred", is_log=T, leg_off=FALSE)
+# a2<-phenotype_trends(Snake_mean_Pheno, "Snake Phenotype Simulation Trend", "16 trial", "steelblue", is_log=T, leg_off=FALSE)
+# 
+# grid.arrange(a1, a2, nrow=1)
+# 
+# 
+# bp2 <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="Space: Differences", subt="16 trial",boxy=FALSE, section=FALSE, section_num=0)
+# 
+# grid.arrange(bp2, nrow=1)
+```
 
-grid.arrange(a1, a2, nrow=1)
+```{r, phenotypes at differnt costs data gather}
 
-bp2 <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="Space: Differences", subt="16 trial",boxy=FALSE, section=FALSE, section_num=0)
+files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+number=1
+GA_file <- read.table(files[number], header = TRUE)
+#file_name <- substr(files[number], 36, 186)
+#print(paste0("File Name: ", file_name))
 
-grid.arrange(bp2, nrow=1)
+GA_file$sim <-"A"
+
+for(i in seq(2, length(files), 1)){
+  temp_file <- read.table(files[i], header = TRUE)
+  temp_file$sim <-LETTERS[i]
+  GA_file <- rbind(GA_file, temp_file)
+
+}
+GA_file$dif <- GA_file$Snake_mean_Pheno-GA_file$Newt_mean_Pheno
 ```
+
+```{r easier dif plot}
+
+pl1 <- ggplot(GA_file, aes(gen, Newt_mean_Pheno, col=factor(sim))) + geom_line()+ 
+    ggtitle("Newt Mean Pheno by Gen", subtitle = "Different sim") +
+    ylim(0,10)+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+pl2 <- ggplot(GA_file, aes(gen, Snake_mean_Pheno, col=factor(sim))) + geom_line()+ 
+    ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Cost") +
+    ylim(0,10)+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw() 
+grid.arrange(pl1, pl2, nrow=1)
+
+ggplot(GA_file, aes(gen, dif, col=factor(sim))) + geom_line()+ 
+    ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+    ylim(-5,5)+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+```
+
+First things that I noticed it that there are some newt and snake phenotypes that start of really high
+
+lets look at other things like population size and newt deaths
+
+```{r population size}
+GA_file$Newt_pop_size
+sl1 <- ggplot(GA_file, aes(gen, Newt_pop_size, col=factor(sim))) + geom_line()+ 
+    ggtitle("Newt pop-size by Gen", subtitle = "Different sim") +
+    #ylim(0,10)+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+sl2 <- ggplot(GA_file, aes(gen, Snake_pop_size, col=factor(sim))) + geom_line()+ 
+    ggtitle("Snake pop-size by Gen", subtitle = "Different Cost") +
+    #ylim(0,10)+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw() 
+grid.arrange(sl1, sl2, nrow=1)
+
+vcf1 <- var_by_var(subset(Newt_pop_size, select = -c(2)), subset(Newt_mean_Pheno, select = -c(2)), subset(Newt_mean_Pheno, select = -c(2)), subset(Snake_pop_size, select = -c(2)), title="Space: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred", facet=FALSE)
+
+vcf2 <- var_by_var(subset(Newt_pop_size, select = -c(2)), subset(Snake_mean_Pheno, select = -c(2)), subset(Snake_mean_Pheno, select = -c(2)), subset(Snake_pop_size, select = -c(2)), title="Space: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue", facet=FALSE)
+
+vc1 <- var_by_var(subset(Newt_pop_size, select = -c(2)), subset(Newt_mean_Pheno, select = -c(2)), subset(Newt_mean_Pheno, select = -c(2)), subset(Snake_pop_size, select = -c(2)), title="Space: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Newt Phenotype" , highcol="darkred", facet=TRUE)
+
+vc2 <- var_by_var(subset(Newt_pop_size, select = -c(2)), subset(Snake_mean_Pheno, select = -c(2)), subset(Snake_mean_Pheno, select = -c(2)), subset(Snake_pop_size, select = -c(2)), title="Space: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake Phenotype", highcol="steelblue", facet=TRUE)
+
+vcf1 
+vcf2
+vc1 
+vc2
+```
+
+```{r, whale}
+title="Space: Newt VS Snake Population Size Color=S-N Phenotype"
+subt="16sims"
+y_label="Snake Popsize"
+x_label="Newt Popsize"
+dif <- ggplot(GA_file[ which(GA_file$gen!=1),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+dif
+```
+
+```{r,pheno by popsize}
+
+svc1 <- var_by_var(subset(Newt_mean_Pheno, select = -c(2)), subset(Newt_pop_size, select = -c(2)), subset(Newt_pop_size, select = -c(2)), subset(Snake_mean_Pheno, select = -c(2)), title="Space: Newt VS Snake Phenotype Color=Population Size", subt="Newt", y_label="Snake Phenotype", x_label="Newt Phenotype", colored=TRUE, color_label="Newt Popsize" , highcol="darkred", facet=TRUE)
+
+svc2 <- var_by_var(subset(Newt_mean_Pheno, select = -c(2)), subset(Snake_pop_size, select = -c(2)), subset(Snake_pop_size, select = -c(2)), subset(Snake_mean_Pheno, select = -c(2)), title="Space: Newt VS Snake Phenotype Color=Population Size", subt="Snake", y_label="Snake Phenotype", x_label="Newt Phenotype", colored=TRUE, color_label="Snake Popsize", highcol="steelblue", facet=TRUE)
+
+svc1 
+svc2
+
+```
+```{r, mean predation}
+GA_file$mean_predation <- GA_file$newt_deaths/GA_file$Newt_pop_size
+
+title="Space: Newt VS Snake Population Size Color=Mean_predation"
+subt="16sims newt_deaths/Newt_pop_size"
+y_label="Snake Popsize"
+x_label="Newt Popsize"
+pre <- ggplot(GA_file[ which(GA_file$gen!=1),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = mean_predation))+
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "darkolivegreen4", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+pre
+
+```
+
+```{r, 20000 gen}
+files <- list.files(path="~/Desktop/GA_lt/gen_20000/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+number=1
+GA_file_20 <- read.table(files[number], header = TRUE)
+#file_name <- substr(files[number], 36, 186)
+#print(paste0("File Name: ", file_name))
+
+GA_file_20$sim <-"A"
+
+for(i in seq(2, length(files), 1)){
+  temp_file <- read.table(files[i], header = TRUE)
+  temp_file$sim <-LETTERS[i]
+  GA_file_20 <- rbind(GA_file_20, temp_file)
+
+}
+GA_file_20$dif <- GA_file_20$Snake_mean_Pheno-GA_file_20$Newt_mean_Pheno
+
+title="Space: Newt VS Snake Population Size Color=S-N Phenotype"
+subt="20000 Gen 16sims"
+y_label="Snake Popsize"
+x_label="Newt Popsize"
+dif <- ggplot(GA_file_20[ which(GA_file_20$gen!=1),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+dif
+```
+
+```{r, what does the params have to do with it}
+params <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit.csv", header = TRUE)
+params$Newt_mean_Pheno<-0
+params$Snake_mean_Pheno<-0
+params$Newt_pop_size<-0
+params$Snake_pop_size<-0
+params$dif<-0
+params$Newt_mean_Pheno_20<-0
+params$Snake_mean_Pheno_20<-0
+params$Newt_pop_size_20<-0
+params$Snake_pop_size_20<-0
+params$dif_20<-0
+
+for(i in seq(1, nrow(params), 1)){
+
+  sumitup <- GA_file[ which(GA_file$gen>=1500 & GA_file$sim ==LETTERS[i]),]
+  sumitup_20 <- GA_file_20[ which(GA_file_20$gen>=2500 & GA_file_20$sim ==LETTERS[i]),]
+  params$Newt_mean_Pheno[i]<-mean(sumitup$Newt_mean_Pheno)
+  params$Snake_mean_Pheno[i]<-mean(sumitup$Snake_mean_Pheno)
+  params$Newt_pop_size[i]<-mean(sumitup$Newt_pop_size)
+  params$Snake_pop_size[i]<-mean(sumitup$Snake_pop_size)
+  params$dif[i]<-mean(sumitup$dif)
+  params$Newt_mean_Pheno_20[i]<-mean(sumitup_20$Newt_mean_Pheno)
+  params$Snake_mean_Pheno_20[i]<-mean(sumitup_20$Snake_mean_Pheno)
+  params$Newt_pop_size_20[i]<-mean(sumitup_20$Newt_pop_size)
+  params$Snake_pop_size_20[i]<-mean(sumitup_20$Snake_pop_size)
+  params$dif_20[i]<-mean(sumitup_20$dif)
+
+}
+
+```

### 2022-01-28 graphs_newt_snakes/Comparing_GA.Rmd
made a new graph to compare newt-snake pop size by plotting popsize with color and shape determined by the GAs in the simulation

@@
   sumitup <- GA_file[ which(GA_file$gen>=1500 & GA_file$sim ==LETTERS[i]),]
-  sumitup_20 <- GA_file_20[ which(GA_file_20$gen>=2500 & GA_file_20$sim ==LETTERS[i]),]
+  sumitup_20 <- GA_file_20[ which(GA_file_20$gen>=3500 & GA_file_20$sim ==LETTERS[i]),]
   params$Newt_mean_Pheno[i]<-mean(sumitup$Newt_mean_Pheno)
@@
 
+title="Space: Newt VS Snake Population Size"
+subt="Gen 16sims"
+y_label="Snake Popsize"
+x_label="Newt Popsize"
+
+params$newt_mu_effect_sd
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+
+t16 <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+t16
+
+t16g <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = "Gen 16sims 20000Gen") +
+  xlab(x_label) + ylab(y_label)+
+  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
+  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+t16g
+
+t16d <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab("DIF: s-n")+
+  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(dif), color = factor(snake), shape=factor(newt)), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+t16d
+
+t16d2 <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab("Snake pop size") + ylab("DIF: s-n")+
+  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
+  geom_point(aes(x=as.numeric(Snake_pop_size), y=as.numeric(dif), color = factor(snake), shape=factor(newt)), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+t16d2
+
 ```

### 2022-02-01 graphs_newt_snakes/Comparing_GA.Rmd
made more graphs, wrote down new values to try for mu and sigma

@@
 library(grid)
+library("reshape")
 ```
@@
 ```{r population size}
-GA_file$Newt_pop_size
+
 sl1 <- ggplot(GA_file, aes(gen, Newt_pop_size, col=factor(sim))) + geom_line()+ 
@@
 
+```{r, 100000 gen}
+files <- list.files(path="~/Desktop/GA_lt/gen_100000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+number=1
+GA_file_100 <- read.table(files[number], header = TRUE)
+#file_name <- substr(files[number], 36, 186)
+#print(paste0("File Name: ", file_name))
+
+GA_file_100$sim <-"A"
+
+for(i in seq(2, length(files), 1)){
+
+  temp_file <- read.table(files[i], header = TRUE)
+  temp_file$sim <-LETTERS[i]
+  GA_file_100 <- rbind(GA_file_100, temp_file)
+
+}
+GA_file_100$dif <- GA_file_100$Snake_mean_Pheno-GA_file_100$Newt_mean_Pheno
+
+title="Space: Newt VS Snake Population Size Color=S-N Phenotype"
+subt="100000 Gen 16sims"
+y_label="Snake Popsize"
+x_label="Newt Popsize"
+dif <- ggplot(GA_file_100[ which(GA_file_100$gen!=1),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+dif
+```
+
 ```{r, what does the params have to do with it}
@@
 params$dif_20<-0
+
+params$Newt_mean_Pheno_100<-0
+params$Snake_mean_Pheno_100<-0
+params$Newt_pop_size_100<-0
+params$Snake_pop_size_100<-0
+params$dif_100<-0
 
@@
 
-params$newt_mu_effect_sd
-
 params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
@@
 t16
-
-t16g <- ggplot(params) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = "Gen 16sims 20000Gen") +
-  xlab(x_label) + ylab(y_label)+
-  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
-  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)), size=3)+
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  #facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
-t16g
 
@@
 ```
+```{r, 20000gen simple params}
+
+t16g <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = "Gen 16sims 20000Gen") +
+  xlab(x_label) + ylab(y_label)+
+  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
+  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+t16g
+
+```
+
+```{r, 1000000gen}
+
+```
+
+```{r, building a heatmap}
+                                      # Install reshape package
+
+params_small <- params[-c(1:7, 9:20)]
+
+data_melt <- melt(params_small)
+
+ggp <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_gradient(low = "green", high = "black", name = "Newt Population Size") 
+ggp
+
+params_small <- params[-c(1:8, 10:20)]
+
+data_melt <- melt(params_small)
+
+ggp21 <- ggplot(data_melt, aes(newt, snake)) +    # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_viridis_c(name = "Snake Population Size")
+  #scale_fill_gradient(low = "green", high = "black") 
+ggp21
+
+params_small <- params[-c(1:9, 11:20)]
+data_melt <- melt(params_small)
+
+gdif <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = "Snake-Newt") 
+gdif
+
+params_small <- params[-c(1:14, 16:20)]
+data_melt <- melt(params_small)
+
+gdif <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 20000") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = "Snake-Newt") 
+gdif
+
+#TESTING
+GA_file_20$Newt_mean_Pheno
+ggplot(GA_file_20, aes(gen, dif, col=factor(sim))) + geom_line()+ 
+  facet_wrap(~sim)+
+    ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+    ylim(-5,5)+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+ggplot(GA_file_20, aes(gen, Newt_mean_Pheno, col=factor(sim))) + geom_line()+ 
+  facet_wrap(~sim)+
+    ggtitle("Newt_mean_Pheno by Gen", subtitle = "Different Sim") +
+    ylim(-5,5)+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+ggplot(GA_file_20, aes(gen, Snake_mean_Pheno, col=factor(sim))) + geom_line()+ 
+  facet_wrap(~sim)+
+    ggtitle("Snake_mean_Pheno by Gen", subtitle = "Different Sim") +
+    ylim(-5,5)+
+    xlab("Generations") + ylab("Phenotype")+
+    theme_bw()
+
+ggplot(GA_file_20, aes(gen, Newt_pop_size, col=factor(sim))) + geom_line()+ 
+    ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+
+    xlab("Generations") + ylab("Newt_pop_size")+
+    theme_bw()
+
+ggplot(GA_file_20, aes(gen, Snake_pop_size, col=factor(sim))) + geom_line()+ 
+    ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+
+    xlab("Generations") + ylab("Snake_pop_size")+
+    theme_bw()
+
+```
+
+thoughts
+
+a simulation with no interaction
+
+check that that column is the variance 
+mu*sig^2 = 2.5e-13
+2.5e-12 vs 2.5e-13
+
+try to check out the sigma values 0.015
+1e-8*(0.005)^2=2.5e-13
+1e-9*(0.05)^2=2.5e-12
+1e-10*(0.5)^2=2.5e-11
+1e-11*(5)^2=2.5e-10
+
+lets set everything to 2.5e-11
+
+Now making the smprime with these
+1e-12*(5)^2 = 2.5e-11
+1e-10*(0.5)^2 = 2.5e-11
+1e-8*(0.05)^2 = 2.5e-11
+1e-6*(0.005)^2 = 2.5e-11

### 2022-02-02 graphs_newt_snakes/Comparing_GA.Rmd
I am writing down my observations and looking at the new data. Results are different.

--- 2022-01-28 graphs_newt_snakes/Comparing_GA.Rmd
@@
 
--Pick 4 different mu sigma combinations where mu*sigma^2 is constant (mu=1e-11, sigma=5) to (mu=1e-8, sigma=0.005) i.e ((mu=1e-11, sigma=5(A)), (mu=1e-10, sigma=0.5(B)), (mu=1e-9, sigma=0.05(C)), (mu=1e-8, sigma=0.005(D))) The ABCD represents the group of mu and sigma.
+-Pick 4 different mu sigma combinations where mu*sigma^2 is constant (mu=1e-11, sigma=5) to (mu=1e-8, sigma=0.005). 
+-I picked values where mu*sigma was constant mu=1e-11, sigma=5(A), mu=1e-10, sigma=0.5(B), mu=1e-9, sigma=0.05(C), mu=1e-8, sigma=0.005(D).
+The ABCD represents the group of mu and sigma.
 When in the newt and snake simulation the groups will be paired to make 16 pairs.
@@
 
+Rerunning this experiment with these values
+1e-12*(5)^2 = 2.5e-11
+1e-10*(0.5)^2 = 2.5e-11
+1e-8*(0.05)^2 = 2.5e-11
+1e-6*(0.005)^2 = 2.5e-11
+*Things with 1e-6 mutation rate go every slow and end up with large file sizes. Might want to think about a different set*
+
+adding 1e-9*(0.1581139)^2
+adding 1e-11*(1.581139)^2
+
 I ran msprime simulations and the slim simulations on cluster in GA_lt folder.
-Mt goal is to first see if there is an obvious "winner" in the co-evolutionary arms race between these species.
+My goal is to first see if there is an obvious "winner" in the co-evolutionary arms race between these species.
 
@@
 I need to make the data frame to compare all 16 simulations.
-I noticed in the mu=1e-11, sigma=5 simulations that the staring pheotypes of some of the individulas were really high and sometimes the population crashed and died out.
+I noticed in the mu=1e-11, sigma=5 simulations that the starting pheotypes of some of the individuals were really high and sometimes the population crashed and died out.
+
+Rcode noate: I have code to make my dataframes, it combines many simulations into one graph-able dataframe. Then, I have some functions that can be called to make some figures.
 
@@
   # Color can plot var by var and pick a 3rd var to color the points (use thenewt x, snake y and newt file y for the color)
-
+  #Newt_file_x <- Newt_pop_size
+  #Newt_file_y <- Newt_mean_Pheno
+  #Snake_file_x <- Snake_pop_size
+  #Snake_file_y <- Snake_mean_Pheno
   data_frame_newt_temp_x <- Newt_file_x
@@
     total_sub_dataframe <- data.frame(subtract_val, data_frame_newt_y$value_y, data_frame_snake_y$value_y)
-    total_sub_dataframe$wrap <- rep(1:16, length(Number))
+    total_sub_dataframe$wrap <- rep(1:25, length(Number))
     total_sub_dataframe <- total_sub_dataframe[sample(nrow(total_sub_dataframe), nrow(total_sub_dataframe)), ]
@@
      color3 <- color3[-c(1,3,4,6)]
-     color3$wrap <- rep(1:16, length(Number))
+     color3$wrap <- rep(1:25, length(Number))
      suppressWarnings(suppressMessages(suppressPackageStartupMessages({require(scales)})))
@@
 ```{r, create dataframe}
- files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+ #files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+files <- list.files(path="~/Desktop/GA_lt/doover/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
  file <- read.table(files[1], header = TRUE)
@@
 
+The first step in seeing if there is a winner in the coevolution interaction is to read in the data and look at the results.
+I make a dataframe named GA_file.
+It contains all of the data points from my 16 simulations.
+I normally look at one varable at a time from all of my simulations, but since there are so feww I can look at them all at once.
+There are 4016 observations with 28 variables which contains information from both newts and snakes.
+
 ```{r, phenotypes at differnt costs data gather}
 
-files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+#files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+
+files <- list.files(path="~/Desktop/GA_lt/doover/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+
 number=1
@@
 ```
+
+The first thing I want to look at are the difference between snake and newt phenotypes as the number of generations increases.
 
@@
 
+```{r, 100000 gen}
+files <- list.files(path="~/Desktop/GA_lt/gen_100000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+number=1
+GA_file_100 <- read.table(files[number], header = TRUE)
+#file_name <- substr(files[number], 36, 186)
+#print(paste0("File Name: ", file_name))
+
+GA_file_100$sim <-"A"
+
+for(i in seq(2, length(files), 1)){
+
+  temp_file <- read.table(files[i], header = TRUE)
+  temp_file$sim <-LETTERS[i]
+  GA_file_100 <- rbind(GA_file_100, temp_file)
+
+}
+GA_file_100$dif <- GA_file_100$Snake_mean_Pheno-GA_file_100$Newt_mean_Pheno
+
+title="Space: Newt VS Snake Population Size Color=S-N Phenotype"
+subt="100000 Gen 16sims"
+y_label="Snake Popsize"
+x_label="Newt Popsize"
+dif <- ggplot(GA_file_100[ which(GA_file_100$gen!=1),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+dif
+```
+
 ```{r, what does the params have to do with it}
-params <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit.csv", header = TRUE)
+#params6 <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit_old.csv", header = TRUE)
+params <- read.csv("/Users/victoria/Desktop/GAtestvar_lit.csv", header = TRUE)
 params$Newt_mean_Pheno<-0
@@
 params$dif<-0
-params$Newt_mean_Pheno_20<-0
-params$Snake_mean_Pheno_20<-0
-params$Newt_pop_size_20<-0
-params$Snake_pop_size_20<-0
-params$dif_20<-0
+#params$Newt_mean_Pheno_20<-0
+#params$Snake_mean_Pheno_20<-0
+#params$Newt_pop_size_20<-0
+#params$Snake_pop_size_20<-0
+#params$dif_20<-0
+
+#params$Newt_mean_Pheno_100<-0
+#params$Snake_mean_Pheno_100<-0
+#params$Newt_pop_size_100<-0
+#params$Snake_pop_size_100<-0
+#params$dif_100<-0
 
@@
   sumitup <- GA_file[ which(GA_file$gen>=1500 & GA_file$sim ==LETTERS[i]),]
-  sumitup_20 <- GA_file_20[ which(GA_file_20$gen>=3500 & GA_file_20$sim ==LETTERS[i]),]
+  #sumitup_20 <- GA_file_20[ which(GA_file_20$gen>=3500 & GA_file_20$sim ==LETTERS[i]),]
   params$Newt_mean_Pheno[i]<-mean(sumitup$Newt_mean_Pheno)
@@
   params$dif[i]<-mean(sumitup$dif)
-  params$Newt_mean_Pheno_20[i]<-mean(sumitup_20$Newt_mean_Pheno)
-  params$Snake_mean_Pheno_20[i]<-mean(sumitup_20$Snake_mean_Pheno)
-  params$Newt_pop_size_20[i]<-mean(sumitup_20$Newt_pop_size)
-  params$Snake_pop_size_20[i]<-mean(sumitup_20$Snake_pop_size)
-  params$dif_20[i]<-mean(sumitup_20$dif)
+  #params$Newt_mean_Pheno_20[i]<-mean(sumitup_20$Newt_mean_Pheno)
+  #params$Snake_mean_Pheno_20[i]<-mean(sumitup_20$Snake_mean_Pheno)
+  #params$Newt_pop_size_20[i]<-mean(sumitup_20$Newt_pop_size)
+  #params$Snake_pop_size_20[i]<-mean(sumitup_20$Snake_pop_size)
+  #params$dif_20[i]<-mean(sumitup_20$dif)
 
@@
 x_label="Newt Popsize"
-
-params$newt_mu_effect_sd
 
@@
 ```
+```{r, 20000gen simple params}
+
+t16g <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = "Gen 16sims 20000Gen") +
+  xlab(x_label) + ylab(y_label)+
+  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
+  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+t16g
+
+```
+
+```{r, 1000000gen}
+
+```
+
+```{r, building a heatmap}
+                                      # Install reshape package
+
+#params_small <- params[-c(1:7, 9:20)]
+params_small <- params[-c(1:7, 9:10)]
+data_melt <- melt(params_small)
+
+ggp <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_gradient(low = "green", high = "black", name = "Newt Population Size") 
+ggp
+
+#params_small <- params[-c(1:8, 10:20)]
+params_small <- params[-c(1:8, 10)]
+data_melt <- melt(params_small)
+
+ggp21 <- ggplot(data_melt, aes(newt, snake)) +    # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_viridis_c(name = "Snake Population Size")
+  #scale_fill_gradient(low = "green", high = "black") 
+ggp21
+
+params_small <- params[-c(1:9)]
+data_melt <- melt(params_small)
+
+gdif <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = "Snake-Newt") 
+gdif
+
+# params_small <- params[-c(1:14, 16:20)]
+# data_melt <- melt(params_small) 
+# 
+# gdif <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+#   ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 20000") +
+#   xlab("Newt GA") + ylab("Snake GA")+
+#   geom_tile(aes(fill = value))+ 
+#   scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = "Snake-Newt") 
+# gdif  
+# 
+# 
+# #TESTING
+# GA_file_20$Newt_mean_Pheno
+# ggplot(GA_file_20, aes(gen, dif, col=factor(sim))) + geom_line()+ 
+#   facet_wrap(~sim)+
+#     ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+#     ylim(-5,5)+
+#     xlab("Generations") + ylab("Phenotype")+
+#     theme_bw() 
+# 
+# ggplot(GA_file_20, aes(gen, Newt_mean_Pheno, col=factor(sim))) + geom_line()+ 
+#   facet_wrap(~sim)+
+#     ggtitle("Newt_mean_Pheno by Gen", subtitle = "Different Sim") +
+#     ylim(-5,5)+
+#     xlab("Generations") + ylab("Phenotype")+
+#     theme_bw() 
+# 
+# ggplot(GA_file_20, aes(gen, Snake_mean_Pheno, col=factor(sim))) + geom_line()+ 
+#   facet_wrap(~sim)+
+#     ggtitle("Snake_mean_Pheno by Gen", subtitle = "Different Sim") +
+#     ylim(-5,5)+
+#     xlab("Generations") + ylab("Phenotype")+
+#     theme_bw() 
+# 
+# ggplot(GA_file_20, aes(gen, Newt_pop_size, col=factor(sim))) + geom_line()+ 
+#     ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+#     
+#     xlab("Generations") + ylab("Newt_pop_size")+
+#     theme_bw() 
+# 
+# ggplot(GA_file_20, aes(gen, Snake_pop_size, col=factor(sim))) + geom_line()+ 
+#     ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+#     
+#     xlab("Generations") + ylab("Snake_pop_size")+
+#     theme_bw() 
+# 
+#
+
+```
+
+thoughts
+
+a simulation with no interaction
+
+check that that column is the variance 
+mu*sig^2 = 2.5e-13
+2.5e-12 vs 2.5e-13
+
+try to check out the sigma values 0.015
+1e-8*(0.005)^2=2.5e-13
+1e-9*(0.05)^2=2.5e-12
+1e-10*(0.5)^2=2.5e-11
+1e-11*(5)^2=2.5e-10
+
+lets set everything to 2.5e-11
+
+Now making the smprime with these
+1e-12*(5)^2 = 2.5e-11
+1e-10*(0.5)^2 = 2.5e-11
+1e-8*(0.05)^2 = 2.5e-11
+1e-6*(0.005)^2 = 2.5e-11

### 2022-02-07 graphs_newt_snakes/Comparing_GA.Rmd
I worked on my writing an made some clean/clearer figures

--- 2022-01-28 graphs_newt_snakes/Comparing_GA.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+#knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)
+
 library(ggplot2)
@@
 
+First run this experiment with these values
+
+- 1e-8*(0.005)^2 = 2.5e-13
+- 1e-9*(0.05)^2 = 2.5e-12
+- 1e-10*(0.5)^2 = 2.5e-11
+- 1e-11*(5.0)^2 = 2.5e-10
+
+Rerunning this experiment with these values
+
+- 1e-8*(0.05)^2 = 2.5e-11
+- 1e-9*(0.1581139)^2 = 2.5e-11
+- 1e-10*(0.5)^2 = 2.5e-11
+- 1e-11*(1.581139)^2 = 2.5e-11
+- 1e-12*(5)^2 = 2.5e-11
+
+*Things with 1e-6 mutation rate go every slow and end up with large file sizes. Might want to think about a different set*
+
 I ran msprime simulations and the slim simulations on cluster in GA_lt folder.
-Mt goal is to first see if there is an obvious "winner" in the co-evolutionary arms race between these species.
+My goal is to first see if there is an obvious "winner" in the co-evolutionary arms race between these species.
 
@@
 I need to make the data frame to compare all 16 simulations.
-I noticed in the mu=1e-11, sigma=5 simulations that the staring pheotypes of some of the individulas were really high and sometimes the population crashed and died out.
+I noticed in the mu=1e-11, sigma=5 simulations that the starting pheotypes of some of the individuals were really high and sometimes the population crashed and died out.
+
+R-code noate: I have code to make my dataframes, it combines many simulations into one graph-able dataframe. Then, I have some functions that can be called to make some figures.
 
@@
   # Color can plot var by var and pick a 3rd var to color the points (use thenewt x, snake y and newt file y for the color)
-
+  #Newt_file_x <- Newt_pop_size
+  #Newt_file_y <- Newt_mean_Pheno
+  #Snake_file_x <- Snake_pop_size
+  #Snake_file_y <- Snake_mean_Pheno
+  number_of_files = length(unique(Newt_file_x$variable))
   data_frame_newt_temp_x <- Newt_file_x
@@
     total_sub_dataframe <- data.frame(subtract_val, data_frame_newt_y$value_y, data_frame_snake_y$value_y)
-    total_sub_dataframe$wrap <- rep(1:16, length(Number))
+    total_sub_dataframe$wrap <- rep(1:number_of_files, length(Number))
     total_sub_dataframe <- total_sub_dataframe[sample(nrow(total_sub_dataframe), nrow(total_sub_dataframe)), ]
@@
      color3 <- color3[-c(1,3,4,6)]
-     color3$wrap <- rep(1:16, length(Number))
+     color3$wrap <- rep(1:number_of_files, length(Number))
      suppressWarnings(suppressMessages(suppressPackageStartupMessages({require(scales)})))
@@
  files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+#files <- list.files(path="~/Desktop/GA_lt/doover/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
  file <- read.table(files[1], header = TRUE)
@@
 
-```{r, plots compairing sims}
+The first step in seeing if there is a winner in the coevolution interaction is to read in the data and look at the results.
+I make a dataframe named GA_file.
+It contains all of the data points from my 16 simulations.
+I normally look at one variable at a time from all of my simulations, but since there are so few I can look at them all at once.
+There are over 4,000 observations with 28 variables which contains information from both newts and snakes.
+I focus on the mean phenotype of both the newt and the snake, usually creating a variable that looks at the difference between the mean pheotypes.
 
-# a1<-phenotype_trends(Newt_mean_Pheno, "Newt Phenotype Simulation Trend", "16 trials", "darkred", is_log=T, leg_off=FALSE)
-# a2<-phenotype_trends(Snake_mean_Pheno, "Snake Phenotype Simulation Trend", "16 trial", "steelblue", is_log=T, leg_off=FALSE)
-# 
-# grid.arrange(a1, a2, nrow=1)
-# 
-# 
-# bp2 <- phenotype_dif_boxplot(Newt_mean_Pheno, Snake_mean_Pheno, title="Space: Differences", subt="16 trial",boxy=FALSE, section=FALSE, section_num=0)
-# 
-# grid.arrange(bp2, nrow=1)
-```
+Since there are 16 simulations, for convenience I print out the simulation letter with the paramiter I used for the snake and newt mutation rate and mutation effect size
 
@@
 files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+
+#files <- list.files(path="~/Desktop/GA_lt/doover/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+
 number=1
@@
 
-for(i in seq(2, length(files), 1)){
+for(i in seq(1, length(files), 1)){
   temp_file <- read.table(files[i], header = TRUE)
@@
   GA_file <- rbind(GA_file, temp_file)
+  myletter <- LETTERS[i]
+  snake_mu_rate <- unlist(str_split(unlist(str_split(files[i],"snake_mu_rate_"))[2], "_"))[1]
+  newt_mu_rate <- unlist(str_split(unlist(str_split(files[i],"newt_mu_rate_"))[2], "_"))[1]
+  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  print(paste0("Simulation ", LETTERS[i],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))
 
@@
 GA_file$dif <- GA_file$Snake_mean_Pheno-GA_file$Newt_mean_Pheno
+
 ```
 
-```{r easier dif plot}
+The first thing I want to look at are the difference between snake and newt mean phenotypes as the number of generations increases.
+The first graph presented is the newt mean phenotype for all simulations as the number of generations increases.
+There are some lines that are squiggly and some lines that are flat.
+The second plot is the represents the snake mean phenotype as the number of generations increases for all the simulations.
+The third plot, shows both the newt and snake mean phenotype (red, blue) and the difference between the snake mean phenotype and the newt mean phenotype (snake-newt, black).
+
+```{r, easier dif plot}
 
@@
     ggtitle("Newt Mean Pheno by Gen", subtitle = "Different sim") +
-    ylim(0,10)+
+    ylim(0,7.5)+
     xlab("Generations") + ylab("Phenotype")+
@@
 
-pl2 <- ggplot(GA_file, aes(gen, Snake_mean_Pheno, col=factor(sim))) + geom_line()+ 
+pl2 <- ggplot(GA_file, aes(gen, Snake_mean_Pheno, col=factor(sim))) + geom_line() + 
     ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Cost") +
-    ylim(0,10)+
+    ylim(0,7.5)+
     xlab("Generations") + ylab("Phenotype")+
@@
 
+ggplot(GA_file) +
+    facet_wrap(~sim)+
+    geom_line(aes(gen, dif, col="dif"))+
+    ggtitle("Phenotpe by Gen For all Sims", subtitle = "Different Sim") +
+    geom_line(aes(gen, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+
+    geom_line(aes(gen, Newt_mean_Pheno, color="Newt_mean_Pheno"))+
+    ylim(-5,5)+
+    xlab("Generations") + ylab("Phenotype")+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
 ```
 
-First things that I noticed it that there are some newt and snake phenotypes that start of really high
+First things that I noticed, are that there are some newt and snake phenotypes that start of really high (I had to cut them so 1st gen is not present).
+These really high phenotypes dropped after the first generation and were seen in simulations that had a higher mu*si^2 value (last 2 rows/columns).
+A question that I had after seeing these plots are why are some of them (snake/newt mean phenotypes) flat?
+Also, the combination of mu times sigma^2 increases the amount of variation.
+For snakes variation going up as you go down the rows (least A->E->I->M most) and for newts variation increases as you go across the columns (least M->N->O->P most).
+It might not be strange to see flat phenotype lines in species who have a low variation, but I expected more competition when the GAs were the same.
+The simulations that seemed to have the most completion were K, L, O, and P.
+It might be a generation problem, it there where more generations would variation eventually increase?
+This is one value for the whole simulation, what is occurring at different spatial points throughout the simulation (P.S.
+I recorded all individuals phenotype, species, fitness, and locations)?
 
-lets look at other things like population size and newt deaths
+Next, I checked the population size of newts and snakes through out the 5,000 generations.
+I found that snake population size seems to be higher than newt population size.
+The way that the colors are stacked indicates that some GA combinations lead to higher population sizes in a species.
+It is hard to tell which GA leads to a higher population size, but I would hypothesize that the simulations with higher variance (mu*si^2) will increase a species population size.
+I also looked at the relationship between newt and snake population size and newt/snake phenotype for all of the simulations combined.
 
-```{r population size}
-GA_file$Newt_pop_size
+```{r, population size}
+
 sl1 <- ggplot(GA_file, aes(gen, Newt_pop_size, col=factor(sim))) + geom_line()+ 
@@
 vcf2
-vc1 
-vc2
+#vc1 
+#vc2
 ```
+
+When looking at the combined simulation data you can see a relationship between population size and phenotype.
+As a species population size grows so does its phenotype.
+For example when the population size of the newts is large then the phenotype of the newts is larger that the phenotype of the newts when the newt population is smaller.
+However, it is difficult to discern what is going on in each individual simulation and how close the newts and snakes phenotype match.
+
+To get a better idea of what is going on in each simulation I plot newt population size by snake population size and color the points with the difference between snake and newt mean phenotype.
+The results are really cool to look at!
 
@@
 
+The relationship between a species population size and the "whining" species can be a times easy to spot (C, G, O, I, J, L, and P), but at other times it can be hard to discern.
+When snakes are "winning" their population size is greater than the newts.
+When the newts are "winning" their population size is equal or greater then the snakes.
+There are other question that I have for this figure, like why are A, F, K, and P not beige?
+Or why the species with highest variation is not "winning" in the co-evolutionary arms race?
+I wonder if I would get these sames results if I ran the simulation for longer?
+- I suspect not because it seems like the colors are getting lighter (as least they look this way in the plot).
+
+To do a reverse check I plot newt mean phenotype by snake mean phenotype and color with the population size.
+It is not as pretty as the other graph, but it does show that when the phenotype of a species is low it ofter has a smaller population size.
+I find the smears sort of funny.
+
 ```{r,pheno by popsize}
@@
 ```
+I also decided to look at the mean predation of newts by taking newt death (caused by snakes) and dividing by the total newt population size (not sure if this counts the newts that just died).
+Predation does not look all that different to me.
+
 ```{r, mean predation}
@@
 
+I also repeade the experiment with 20,000 and then again with 100,000 generations.
+
 ```{r, 20000 gen}
-files <- list.files(path="~/Desktop/GA_lt/gen_20000/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+files_20 <- list.files(path="~/Desktop/GA_lt/gen_20000/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
 number=1
-GA_file_20 <- read.table(files[number], header = TRUE)
+GA_file_20 <- read.table(files_20[number], header = TRUE)
 #file_name <- substr(files[number], 36, 186)
@@
 
-for(i in seq(2, length(files), 1)){
-  temp_file <- read.table(files[i], header = TRUE)
+for(i in seq(1, length(files_20), 1)){
+  temp_file <- read.table(files_20[i], header = TRUE)
   temp_file$sim <-LETTERS[i]
   GA_file_20 <- rbind(GA_file_20, temp_file)
+  myletter <- LETTERS[i]
+  snake_mu_rate <- unlist(str_split(unlist(str_split(files_20[i],"snake_mu_rate_"))[2], "_"))[1]
+  newt_mu_rate <- unlist(str_split(unlist(str_split(files_20[i],"newt_mu_rate_"))[2], "_"))[1]
+  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(files_20[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(files_20[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  print(paste0("20,000 Gen Simulation ", LETTERS[i],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))
 
 }
+
 GA_file_20$dif <- GA_file_20$Snake_mean_Pheno-GA_file_20$Newt_mean_Pheno
@@
 
+```{r, 100000 gen}
+files_100 <- list.files(path="~/Desktop/GA_lt/gen_100000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+number=1
+GA_file_100 <- read.table(files_100[number], header = TRUE)
+#file_name <- substr(files[number], 36, 186)
+#print(paste0("File Name: ", file_name))
+#blank<-GA_file_100
+#blank[,2:length(blank)] = 0
+#write.csv(blank, "~/Desktop/GA_lt/gen_100000/lit/text_files/blank.csv")
+
+GA_file_100$sim <-"A"
+for(i in seq(1, length(files_100), 1)){
+  temp_file <- read.table(files_100[i], header = TRUE)
+  temp_file$sim <-LETTERS[i]
+  GA_file_100 <- rbind(GA_file_100, temp_file)
+  myletter <- LETTERS[i]
+  snake_mu_rate <- unlist(str_split(unlist(str_split(files_100[i],"snake_mu_rate_"))[2], "_"))[1]
+  newt_mu_rate <- unlist(str_split(unlist(str_split(files_100[i],"newt_mu_rate_"))[2], "_"))[1]
+  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(files_100[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(files_100[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  print(paste0("100,000 Gen Simulation ", LETTERS[i],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))
+
+}
+
+GA_file_100$dif <- GA_file_100$Snake_mean_Pheno-GA_file_100$Newt_mean_Pheno
+
+title="Space: Newt VS Snake Population Size Color=S-N Phenotype"
+subt="100000 Gen 16sims"
+y_label="Snake Popsize"
+x_label="Newt Popsize"
+dif <- ggplot(GA_file_100[ which(GA_file_100$gen!=1),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+dif
+```
+
 ```{r, what does the params have to do with it}
-params <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit.csv", header = TRUE)
+params <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit_old.csv", header = TRUE)
+#params <- read.csv("/Users/victoria/Desktop/GAtestvar_lit.csv", header = TRUE)
 params$Newt_mean_Pheno<-0
@@
 params$dif<-0
+
 params$Newt_mean_Pheno_20<-0
@@
 
+params$Newt_mean_Pheno_100<-0
+params$Snake_mean_Pheno_100<-0
+params$Newt_pop_size_100<-0
+params$Snake_pop_size_100<-0
+params$dif_100<-0
+
 for(i in seq(1, nrow(params), 1)){
 
-  sumitup <- GA_file[ which(GA_file$gen>=1500 & GA_file$sim ==LETTERS[i]),]
+  sumitup <- GA_file[which(GA_file$gen>=1500 & GA_file$sim ==LETTERS[i]),]
   sumitup_20 <- GA_file_20[ which(GA_file_20$gen>=3500 & GA_file_20$sim ==LETTERS[i]),]
+  sumitup_100 <- GA_file_100[ which(GA_file_100$gen>=90000 & GA_file_100$sim ==LETTERS[i]),]
+
   params$Newt_mean_Pheno[i]<-mean(sumitup$Newt_mean_Pheno)
@@
   params$dif[i]<-mean(sumitup$dif)
+
   params$Newt_mean_Pheno_20[i]<-mean(sumitup_20$Newt_mean_Pheno)
@@
   params$dif_20[i]<-mean(sumitup_20$dif)
+
+  params$Newt_mean_Pheno_100[i]<-mean(sumitup_100$Newt_mean_Pheno, na.rm = TRUE)
+  params$Snake_mean_Pheno_100[i]<-mean(sumitup_100$Snake_mean_Pheno, na.rm = TRUE)
+  params$Newt_pop_size_100[i]<-mean(sumitup_100$Newt_pop_size, na.rm = TRUE)
+  params$Snake_pop_size_100[i]<-mean(sumitup_100$Snake_pop_size, na.rm = TRUE)
+  params$dif_100[i]<-mean(sumitup_100$dif, na.rm = TRUE)
 
@@
 ```
+```{r, 20000gen simple params}
+
+t16g <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = "Gen 16sims 20000Gen") +
+  xlab(x_label) + ylab(y_label)+
+  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
+  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+t16g
+
+```
+
+```{r, 1000000gen}
+truth<-params[which(params$trial !=1 & params$trial !=16),]
+
+t16g10 <- ggplot(params[which(params$trial !=1 & params$trial !=16),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = "Gen 16sims 100000Gen") +
+  xlab(x_label) + ylab(y_label)+
+  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
+  geom_point(aes(x=as.numeric(Newt_pop_size_100), y=as.numeric(Snake_pop_size_100), color = factor(snake), shape=factor(newt)), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+t16g10
+
+```
+
+```{r, building a heatmap}
+                                      # Install reshape package
+
+params_small <- params[-c(1:7, 9:20)]
+#params_small <- params[-c(1:7, 9:10)]
+data_melt <- melt(params_small)
+
+ggp <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_gradient(low = "green", high = "black", name = "Newt Population Size") 
+ggp
+
+params_small <- params[-c(1:8, 10:20)]
+#params_small <- params[-c(1:8, 10)]
+data_melt <- melt(params_small)
+
+ggp21 <- ggplot(data_melt, aes(newt, snake)) +    # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_viridis_c(name = "Snake Population Size")
+  #scale_fill_gradient(low = "green", high = "black") 
+ggp21
+
+params_small <- params[-c(1:9, 11:20)]
+data_melt <- melt(params_small) 
+# 
+gdif5 <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 5000") +
+   xlab("Newt GA") + ylab("Snake GA")+
+   geom_tile(aes(fill = value))+ 
+  scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = "Snake-Newt") 
+ gdif5
+
+params_small <- params[-c(1:13, 15:20)]
+#params_small <- params[-c(1:8, 10)]
+data_melt <- melt(params_small)
+
+ggp212 <- ggplot(data_melt, aes(newt, snake)) +    # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 20000") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_viridis_c(name = "Snake Population Size")
+  #scale_fill_gradient(low = "green", high = "black") 
+ggp212
+
+params_small <- params[-c(1:14, 16:20)]
+data_melt <- melt(params_small) 
+# 
+gdif <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 20000") +
+   xlab("Newt GA") + ylab("Snake GA")+
+   geom_tile(aes(fill = value))+ 
+  scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = "Snake-Newt") 
+ gdif
+
+ params_small <- params[-c(1:18, 20)]
+params_small[params_small==0]<-NA
+data_melt <- melt(params_small)
+
+ggp2123 <- ggplot(data_melt, aes(newt, snake)) +    # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 100000") +
+  xlab("Newt GA") + ylab("Snake GA")+
+  geom_tile(aes(fill = value))+ 
+  scale_fill_viridis_c(name = "Snake Population Size")
+  #scale_fill_gradient(low = "green", high = "black") 
+ggp2123
+
+ params_small <- params[-c(1:19)]
+ params_small[params_small==0]<-NA
+data_melt <- melt(params_small) 
+#
+
+gdif10 <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 100000") +
+   xlab("Newt GA") + ylab("Snake GA")+
+   geom_tile(aes(fill = value))+ 
+  scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = "Snake-Newt") 
+ gdif10  
+# 
+#
+
+ # params_small <- params[-c(1:9)]
+# data_melt <- melt(params_small) 
+# 
+# gdif <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+#   ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap") +
+#   xlab("Newt GA") + ylab("Snake GA")+
+#   geom_tile(aes(fill = value))+ 
+#   scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = "Snake-Newt") 
+# gdif
+
+# #TESTING
+# GA_file_20$Newt_mean_Pheno
+# ggplot(GA_file_20, aes(gen, dif, col=factor(sim))) + geom_line()+ 
+#   facet_wrap(~sim)+
+#     ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+#     ylim(-5,5)+
+#     xlab("Generations") + ylab("Phenotype")+
+#     theme_bw() 
+# 
+# ggplot(GA_file_20, aes(gen, Newt_mean_Pheno, col=factor(sim))) + geom_line()+ 
+#   facet_wrap(~sim)+
+#     ggtitle("Newt_mean_Pheno by Gen", subtitle = "Different Sim") +
+#     ylim(-5,5)+
+#     xlab("Generations") + ylab("Phenotype")+
+#     theme_bw() 
+# 
+# ggplot(GA_file_20, aes(gen, Snake_mean_Pheno, col=factor(sim))) + geom_line()+ 
+#   facet_wrap(~sim)+
+#     ggtitle("Snake_mean_Pheno by Gen", subtitle = "Different Sim") +
+#     ylim(-5,5)+
+#     xlab("Generations") + ylab("Phenotype")+
+#     theme_bw() 
+# 
+# ggplot(GA_file_20, aes(gen, Newt_pop_size, col=factor(sim))) + geom_line()+ 
+#     ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+#     
+#     xlab("Generations") + ylab("Newt_pop_size")+
+#     theme_bw() 
+# 
+# ggplot(GA_file_20, aes(gen, Snake_pop_size, col=factor(sim))) + geom_line()+ 
+#     ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+#     
+#     xlab("Generations") + ylab("Snake_pop_size")+
+#     theme_bw() 
+# 
+#
+
+```
+
+thoughts
+
+a simulation with no interaction
+
+check that that column is the variance 
+mu*sig^2 = 2.5e-13
+2.5e-12 vs 2.5e-13
+
+try to check out the sigma values 0.015
+1e-8*(0.005)^2=2.5e-13
+1e-9*(0.05)^2=2.5e-12
+1e-10*(0.5)^2=2.5e-11
+1e-11*(5)^2=2.5e-10
+
+lets set everything to 2.5e-11
+
+Now making the smprime with these
+1e-12*(5)^2 = 2.5e-11
+1e-10*(0.5)^2 = 2.5e-11
+1e-8*(0.05)^2 = 2.5e-11
+1e-6*(0.005)^2 = 2.5e-11

### 2022-02-07 graphs_newt_snakes/Comparing_GA.Rmd
Writting more and making the r markdown look better

@@
 My goal is to first see if there is an obvious "winner" in the co-evolutionary arms race between these species.
+
+## Explore Phenotype and Population Size
 
@@
 
+## 16 Simulation Plots
+
 To get a better idea of what is going on in each simulation I plot newt population size by snake population size and color the points with the difference between snake and newt mean phenotype.
@@
 I also decided to look at the mean predation of newts by taking newt death (caused by snakes) and dividing by the total newt population size (not sure if this counts the newts that just died).
-Predation does not look all that different to me.
+Predation does not look all that different between simulations to me.
+Should it look different?
 
@@
   theme(plot.title = element_text(size=5)) +
-  scale_colour_gradient2(high = "darkolivegreen4", mid = "beige", low = "darkred")+
+  scale_colour_gradient2(high = "darkolivegreen4", low = "beige")+
   #labs(colour = color_label) +
@@
 
-I also repeade the experiment with 20,000 and then again with 100,000 generations.
+Thoughts about predation: If there were lots of newts and snake predation would be higher.
+If newts had a lower phenotype predation would be higher.
+If the interaction rate was higher there might be more predation.
+Right now I do not see any trends.
+It seems very well mixed.
+
+To examined what would happen if I kept running my simulations for longer I repeated the experiment with 20,000 generations and then again with 100,000 generations.
+Below are the summary figures for these simulations.
+The first figure presented shows all 16 simulations the x axis is newt population size and the y axis is snake population size.
+The color of the points is the difference between snake mean phenotype and newt mean phenotype.
+If the point is blue snakes have a higher phenotype, if the point is beige snakes and newts have a similar, and if the point is red newts have a higher phenotype.
 
@@
 ```
+
+The 20,000 generation plot shows a similar pattern to the 5,000 generation plot where there is a higher phenotype when one species has has a mu-rate & effect sd of 1.0e-10 & 0.5.
+In this simulation set the plots along the diagonal A F K P look more neutral.
+
+Next, I plotted the same figure with the 100,000 generation data. Two of the GAs simulation would not finish (I ran out of memory on A and individuals on P, possibly I will try to rerun them).
 
@@
 
+These results show a very different pattern in the newt snake phenotype.
+A higher phenotype occurs when the other species has a lower variation (mu*si^2).
+I wonder if this is due to drift (the flat lines).
+I also find it weird how neutral the some of the simulations in the third column and row look.
+So I decided to plot the mean newt phenotype, snake mean phenotype and the difference betwwen snake-newt phenotype as the number of gernerations increased.
+
+```{r, GA_file_100 phenotype}
+ggplot(GA_file_100) +
+    facet_wrap(~sim)+
+    geom_line(aes(gen, dif, col="dif"))+
+    ggtitle("Phenotpe by Gen For all Sims", subtitle = "Different Sim") +
+    geom_line(aes(gen, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+
+    geom_line(aes(gen, Newt_mean_Pheno, color="Newt_mean_Pheno"))+
+    ylim(-5,10)+
+    xlab("Generations") + ylab("Phenotype")+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+```
+
+This is kind of a cool result!
+It seems like when mu*si^2 is low that species has a disadvantage and cannot coevolve with the other species.
+It also seems that when the mu-rate & effect sd are 1.0e-10 & 0.5 there might be and advantage for that species for some time, but the other species can catch up.
+
+## Summarized Data
+
+For this last section summarized the data to presented in one plot.
+I summarize the last half of the data for 5,000 generations the last 1,500 generations for 20,00- generations and the last 10,000 generations for the 100,000 simulation.
+
 ```{r, what does the params have to do with it}
@@
 
-  sumitup <- GA_file[which(GA_file$gen>=1500 & GA_file$sim ==LETTERS[i]),]
+  sumitup <- GA_file[which(GA_file$gen>=2500 & GA_file$sim ==LETTERS[i]),]
   sumitup_20 <- GA_file_20[ which(GA_file_20$gen>=3500 & GA_file_20$sim ==LETTERS[i]),]
@@
 ```
+
+##Heatmap
 

### 2022-02-08 graphs_newt_snakes/Comparing_GA.Rmd
I finished a good draft with the graph results and the figure disrciptions and some explination. It is very long

@@
 
-First things that I noticed, are that there are some newt and snake phenotypes that start of really high (I had to cut them so 1st gen is not present).
+Some things that I noticed, are that there are some newt and snake phenotypes that start of really high (I had to cut them so 1st gen is not present).
 These really high phenotypes dropped after the first generation and were seen in simulations that had a higher mu*si^2 value (last 2 rows/columns).
@@
 
-svc1 
-svc2
-
-```
+grid.arrange(svc1, svc2, nrow=1)
+
+```
+
 I also decided to look at the mean predation of newts by taking newt death (caused by snakes) and dividing by the total newt population size (not sure if this counts the newts that just died).
@@
 It seems very well mixed.
+
+## Longer Simulations
 
@@
   newt_mu_effect_sd <- unlist(str_split(unlist(str_split(files_20[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  print(paste0("20,000 Gen Simulation ", LETTERS[i],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))
+  print(paste0("20,000 Gen Simulation ", LETTERS[i],": Snake (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))
 
@@
   newt_mu_effect_sd <- unlist(str_split(unlist(str_split(files_100[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  print(paste0("100,000 Gen Simulation ", LETTERS[i],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))
+  print(paste0("100,000 Gen Simulation ", LETTERS[i],": Snake (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))
 
@@
     geom_line(aes(gen, dif, col="dif"))+
-    ggtitle("Phenotpe by Gen For all Sims", subtitle = "Different Sim") +
+    ggtitle("Phenotpe by Gen For all Sims", subtitle = "100,000Gen Different Sim") +
     geom_line(aes(gen, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+
@@
 
-For this last section summarized the data to presented in one plot.
-I summarize the last half of the data for 5,000 generations the last 1,500 generations for 20,00- generations and the last 10,000 generations for the 100,000 simulation.
+For this section summarized the data to presented in one plot.
+I summarize the last half of the data for 5,000 generations the last 1,500 generations for 20,000 generations and the last 10,000 generations for the 100,000 simulation.
+By summarizing the data I can try to compare the GA of the snakes tot the GA of the newts through information of their population sizes and phenotypes.
+I summarize by taking the mean value of a specific parameter.
+
+In each of these plots color will represent the GA of the snake and shape will represent the GA of the newt.
+The colors and shapes are labeled with the mutation rate and mutation effect size sd seperated by a subscript.
 
@@
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
-t16d
 
@@
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
-t16d2
-
-```
+
+grid.arrange(t16d, t16d2, nrow=1)
+
+```
+
+The first figure in this section plots newts population size by snakes population size.
+As we saw previously, a larger population size indicates that a species has a higher phenotype or might be "winning" in a coevolutionary arms race.
+In this figure I can see four chunks, a top left a middle left, middle right, and bottom right each containing either 3 or 5 points.
+The top left chunk I think snakes are successfully winning, the have a much larger population size than newts and their phenotype was higher (seen in 16 sim plot).
+The middle left chunk snakes could be winning, the snake population size was larger, but the was not a big difference between newts and snake phenotypes.
+In the middle right chunk, the snake population size was a bit larger than newt population size, but newts often had a higher mean phenotype so I think the newts are winning.
+In the bottom right chunk newts are winning, they have both a larger population size and a higher phenotype.
+For the different GAs I noticed that a species is more likely to win if; first they have a GA with 1e-10_0.5, second they do not have a GA of 1e-11_5, third when snakes and newts had the same GA the pehnotypes were similar or newts were winning.
+The second and third plots show either newt or snake population size by the difference between snake and newt mean phenotype.
+They show/confirm what I saw in the first plot upper chunk snakes are winning, lower chunk newts are winning, center chunks harder to tell.
+I dont see any direct pattern of color and shape, there might be an interaction pattern, but I havent been able to spot it.
+
+## Summarize data Longer SImulations
+
+I also summarized and examined the data for the simulations that I ran longer than the 5,000 generations.
+The results some-what agree and disagree with the above figures.
+First, the 20,000 generation figure looks similar to the 5,000 generation.
+There are sill 4 groups altho the groups seem to be spreading out more.
+There seems to be some clear winners, but some of the clear winners are different than what I saw in the 5,000gen experiment.
+Some of the shapes are clustering together like the plus and squares.
+There might be a color pattern red, green , purple, blue, but I am not sure.
+
+In the 100,000 generation experiment the results look very different than the 5,000 or 20,000 generations.
+There are three distinct groups.
+One where the snakes are winning and one wher the newts are winning.
+Any species that did not have the 1e-8_0.005 was winning.
+Newts tended to lose more than the snakes.
+There are several points that are sticking arounfd the center.
+I wonder if I can turn this into an animation?
+
 ```{r, 20000gen simple params}
+title="Space: Newt VS Snake Population Size"
+subt="Gen 16sims 20000Gen"
+y_label="Snake Popsize"
+x_label="Newt Popsize"
 
@@
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
-t16g
+
+t1620 <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab("DIF: s-n")+
+  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
+  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(dif_20), color = factor(snake), shape=factor(newt)), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+grid.arrange(t16g, t1620, nrow=1)
 
@@
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
-t16g10
+
+params[params==0]<-NA
+t1610 <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = "Gen 16sims 100000Gen") +
+  xlab(x_label) + ylab("DIF: s-n")+
+  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
+  geom_point(aes(x=as.numeric(Newt_pop_size_100), y=as.numeric(dif_100), color = factor(snake), shape=factor(newt)), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+grid.arrange(t16g10, t1610, nrow=1)
 
@@
 
+The last result section of this markdown will hold the results of my heat maps.
+My experiment had 16 simulations with 4 different types of GA for both the newts and snakes.
+My goal was to see if I could easily determine a winner from these results.
+All of the heat maps will have the GA of the newt along the x-axis and the GA of the snake along the y-axis.
+The intersection of the axis (a box) is one simulation that I ran.
+Each box will have a color that is either the population size of the snake or the diffence between snake mean phenotype and newt mean phenotype.
+
 ```{r, building a heatmap}
-                                      # Install reshape package
-
-params_small <- params[-c(1:7, 9:20)]
-#params_small <- params[-c(1:7, 9:10)]
-data_melt <- melt(params_small)
-
-ggp <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
-  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap") +
-  xlab("Newt GA") + ylab("Snake GA")+
-  geom_tile(aes(fill = value))+ 
-  scale_fill_gradient(low = "green", high = "black", name = "Newt Population Size") 
-ggp
+# params_small <- params[-c(1:7, 9:20)]
+# #params_small <- params[-c(1:7, 9:10)]
+# data_melt <- melt(params_small) 
+# 
+# ggp <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
+#   ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap") +
+#   xlab("Newt GA") + ylab("Snake GA")+
+#   geom_tile(aes(fill = value))+ 
+#   scale_fill_gradient(low = "green", high = "black", name = "Newt Population Size") 
+# ggp
 
@@
 
+```
+
+For the 5,000 generation simulation I have created two heat maps.
+The first heatmap shows how the GA of newts and snakes effected the size of the snake population.
+As we saw in earier results the simulations with the smallest snake population size ocurred when the newts had a GA of 1e-10 and 0.5.
+The simulations where the snake had the largest population size ocurred when the snakes had a GA of 1e-10 and 0.5.
+Now in the second figure we can really look at the difference between snake and newt phenotype.
+I see similar results, but I also noticed that a species phenotype was higher when the other speces had a GA of 1e-11 and 5 (except when they meet).
+The boxes along the diagonol seem close to neutral or newts had a higher phenotype.
+Now I will look at the results from the 20,000 generation experiment.
+
+```{r, heatmap for 20000}
 params_small <- params[-c(1:13, 15:20)]
@@
  gdif  
-
+```
+
+In the 20,000 generation experiment the results look similar to the results in the 5,000 generation experiments.
+Here snakes and newts with the GA of 1e-10 and 0.05 have an advantage both in population size and phenotype.
+I see less of a pattern when the GA is 1e-11 and 5.
+The diganal seems to be more neutral in this result.
+I might also see a losing pattern stating to form the the GA is 1e-1 and 0.005 (light, dark, other color).
+There is a bit of an odd symmetry here.
+Lastly, I will look at the results from the 100,000 generation simulations.
+Again the two grey boxes are where my simulation failed to run (no memory and individuals died out)
+
+```{r, heatmap 100}
  params_small <- params[-c(1:18, 20)]
@@
  gdif10  
+```
+
+Again, these results are very different when compared to the 5,000 and 20,000 generation simulations.
+The only pattern that I see is that when either the newt or snake has a GA of 1e-8 and 0.005 the other species has a higher phenotype and population size.
+Most of the other simulations ended up being close to neutral except when the snake GA is 1e-10_0.5 and the newt GA is 1e-11_5.
+I no longer see an advantage when the GA is 1e-10_0.5.
+I wonder why this occurred.
+Is this what steady state looks like?
+Is coevolution still occurring?
+Why did that one box get really blue?
+Is the species who is winning because the other species 1e-8_0.005 because that GA is not realistic?
+Are the effects of the mutations too low?
+I wonder how this boxplot would look though a series of time steps.
+
+```{r, test figs}
+
 # 
@@
 
-thoughts
-
-a simulation with no interaction
-
-check that that column is the variance 
-mu*sig^2 = 2.5e-13
-2.5e-12 vs 2.5e-13
-
-try to check out the sigma values 0.015
-1e-8*(0.005)^2=2.5e-13
-1e-9*(0.05)^2=2.5e-12
-1e-10*(0.5)^2=2.5e-11
-1e-11*(5)^2=2.5e-10
-
-lets set everything to 2.5e-11
-
-Now making the smprime with these
-1e-12*(5)^2 = 2.5e-11
-1e-10*(0.5)^2 = 2.5e-11
-1e-8*(0.05)^2 = 2.5e-11
-1e-6*(0.005)^2 = 2.5e-11
+## Conclusion & Thoughts
+
+It was really cool to see how different GA effect effects the phenotype and population sizes of newts and snakes.
+It is really confusing trying to compare GA that have different orders of magnitude.
+I wonder if mutation rate or effect size sd drives coevolution or a combination of the two of them.
+If I repeated the experiment would the results be the same?
+
+Something I would like to try next is to see these results ib a simulation with no interaction.

### 2022-02-09 graphs_newt_snakes/Comparing_GA_part_2.Rmd
I made GA part 2 flie. got the graphs to work. Need to interpret and write about them.

--- 2022-02-08 graphs_newt_snakes/Comparing_GA.Rmd
@@
 ---
-title: "Comparing Genetic Architectures"
+title: "Comparing GA Part 2"
 output: html_document
@@
 
-Here I am doing a small experiment to compare different genetic architectures between snakes and newts. I will use the cost_1on1 simulation and my snake_newt_gv msprime simulation.
+Here I am doing a contuation of the small experiment to compare different genetic architectures between snakes and newts. I will use the cost_1on1 simulation and my snake_newt_gv msprime simulation.
 
@@
 
--Pick 4 different mu sigma combinations where mu*sigma^2 is constant (mu=1e-11, sigma=5) to (mu=1e-8, sigma=0.005). 
--I picked values where mu*sigma was constant mu=1e-11, sigma=5(A), mu=1e-10, sigma=0.5(B), mu=1e-9, sigma=0.05(C), mu=1e-8, sigma=0.005(D).
-The ABCD represents the group of mu and sigma.
-When in the newt and snake simulation the groups will be paired to make 16 pairs.
--In total that will be 16 msprime simulations and 16 slim simulations
+-Pick 5 different mu sigma combinations where mu*sigma^2 is constant 
+-In total that will be 25 msprime simulations and 25 slim simulations
 -See if there are any obvious winners
 -make a co-evolutionary heatmap
-
-First run this experiment with these values
-
-- 1e-8*(0.005)^2 = 2.5e-13
-- 1e-9*(0.05)^2 = 2.5e-12
-- 1e-10*(0.5)^2 = 2.5e-11
-- 1e-11*(5.0)^2 = 2.5e-10
 
@@
 
-I ran msprime simulations and the slim simulations on cluster in GA_lt folder.
+These are the results of the 25sims experiment. As a note the long sigma (1.581139) might be at a slight advantage because variation is 2.500001e-11
+
+I ran msprime simulations and the slim simulations on cluster in GA_lt doover folder.
 My goal is to first see if there is an obvious "winner" in the co-evolutionary arms race between these species.
+And then to compare to part 1 of the experiment when some GA have an advantage/disadvatage
 
@@
 First, I want to look at the mean pheotypes of newts and snakes as the generations increase.
-Then I want to look at the difference between the mean phenotypes for each of the 16 simulations.
-I need to make the data frame to compare all 16 simulations.
+Then I want to look at the difference between the mean phenotypes for each of the 25 simulations.
+I need to make the data frame to compare all 25 simulations.
 I noticed in the mu=1e-11, sigma=5 simulations that the starting pheotypes of some of the individuals were really high and sometimes the population crashed and died out.
@@
 ```{r, create dataframe}
- files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
-#files <- list.files(path="~/Desktop/GA_lt/doover/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+files <- list.files(path="~/Desktop/GA_lt/doover/gen_5000/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
  file <- read.table(files[1], header = TRUE)
@@
 I make a dataframe named GA_file.
-It contains all of the data points from my 16 simulations.
+It contains all of the data points from my 25 simulations.
 I normally look at one variable at a time from all of my simulations, but since there are so few I can look at them all at once.
@@
 
-Since there are 16 simulations, for convenience I print out the simulation letter with the paramiter I used for the snake and newt mutation rate and mutation effect size
+Since there are 25 simulations, for convenience I print out the simulation letter with the paramiter I used for the snake and newt mutation rate and mutation effect size
 
@@
 
-files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
-
-#files <- list.files(path="~/Desktop/GA_lt/doover/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
-
+files <- list.files(path="~/Desktop/GA_lt/doover/gen_5000/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
 number=1
@@
     ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
-    ylim(-5,5)+
+    ylim(-7,7)+
     xlab("Generations") + ylab("Phenotype")+
@@
     geom_line(aes(gen, Newt_mean_Pheno, color="Newt_mean_Pheno"))+
-    ylim(-5,5)+
+    ylim(-5,10)+
     xlab("Generations") + ylab("Phenotype")+
@@
 
-## 16 Simulation Plots
+## 25 Simulation Plots
 
@@
 title="Space: Newt VS Snake Population Size Color=S-N Phenotype"
-subt="16sims"
+subt="25sims"
 y_label="Snake Popsize"
@@
 title="Space: Newt VS Snake Population Size Color=Mean_predation"
-subt="16sims newt_deaths/Newt_pop_size"
+subt="25sims newt_deaths/Newt_pop_size"
 y_label="Snake Popsize"
@@
 Below are the summary figures for these simulations.
-The first figure presented shows all 16 simulations the x axis is newt population size and the y axis is snake population size.
+The first figure presented shows all 25 simulations the x axis is newt population size and the y axis is snake population size.
 The color of the points is the difference between snake mean phenotype and newt mean phenotype.
@@
 ```{r, 20000 gen}
-files_20 <- list.files(path="~/Desktop/GA_lt/gen_20000/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+files_20 <- list.files(path="~/Desktop/GA_lt/doover/gen_20000/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
 number=1
@@
 title="Space: Newt VS Snake Population Size Color=S-N Phenotype"
-subt="20000 Gen 16sims"
+subt="20000 Gen 25sims"
 y_label="Snake Popsize"
@@
 ```{r, 100000 gen}
-files_100 <- list.files(path="~/Desktop/GA_lt/gen_100000/lit/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+files_100 <- list.files(path="~/Desktop/GA_lt/doover/gen_100000/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
 number=1
@@
 title="Space: Newt VS Snake Population Size Color=S-N Phenotype"
-subt="100000 Gen 16sims"
+subt="100000 Gen 25sims"
 y_label="Snake Popsize"
@@
 ```{r, what does the params have to do with it}
-params <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit_old.csv", header = TRUE)
+params <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit_25.csv", header = TRUE)
 #params <- read.csv("/Users/victoria/Desktop/GAtestvar_lit.csv", header = TRUE)
@@
 title="Space: Newt VS Snake Population Size"
-subt="Gen 16sims"
+subt="Gen 25sims"
 y_label="Snake Popsize"
@@
 
-t16 <- ggplot(params) +
+t25 <- ggplot(params) +
   #xlim(0, 1000)+
@@
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
-t16
-
-t16d <- ggplot(params) +
+t25
+
+t25d <- ggplot(params) +
   #xlim(0, 1000)+
@@
 
-t16d2 <- ggplot(params) +
+t25d2 <- ggplot(params) +
   #xlim(0, 1000)+
@@
 
-grid.arrange(t16d, t16d2, nrow=1)
+grid.arrange(t25d, t25d2, nrow=1)
 
@@
 In this figure I can see four chunks, a top left a middle left, middle right, and bottom right each containing either 3 or 5 points.
-The top left chunk I think snakes are successfully winning, the have a much larger population size than newts and their phenotype was higher (seen in 16 sim plot).
+The top left chunk I think snakes are successfully winning, the have a much larger population size than newts and their phenotype was higher (seen in 25 sim plot).
 The middle left chunk snakes could be winning, the snake population size was larger, but the was not a big difference between newts and snake phenotypes.
@@
 title="Space: Newt VS Snake Population Size"
-subt="Gen 16sims 20000Gen"
+subt="Gen 25sims 20000Gen"
 y_label="Snake Popsize"
@@
 
-t16g <- ggplot(params) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = "Gen 16sims 20000Gen") +
+t25g <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = "Gen 25sims 20000Gen") +
   xlab(x_label) + ylab(y_label)+
@@
 
-t1620 <- ggplot(params) +
+t2520 <- ggplot(params) +
   #xlim(0, 1000)+
@@
 
-grid.arrange(t16g, t1620, nrow=1)
+grid.arrange(t25g, t2520, nrow=1)
 
@@
 ```{r, 1000000gen}
-truth<-params[which(params$trial !=1 & params$trial !=16),]
-
-t16g10 <- ggplot(params[which(params$trial !=1 & params$trial !=16),]) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = "Gen 16sims 100000Gen") +
+truth<-params[which(params$trial !=1 & params$trial !=25),]
+
+t25g10 <- ggplot(params[which(params$trial !=1 & params$trial !=25),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = "Gen 25sims 100000Gen") +
   xlab(x_label) + ylab(y_label)+
@@
 params[params==0]<-NA
-t1610 <- ggplot(params) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = "Gen 16sims 100000Gen") +
+t2510 <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = "Gen 25sims 100000Gen") +
   xlab(x_label) + ylab("DIF: s-n")+
@@
 
-grid.arrange(t16g10, t1610, nrow=1)
+grid.arrange(t25g10, t2510, nrow=1)
 
@@
 The last result section of this markdown will hold the results of my heat maps.
-My experiment had 16 simulations with 4 different types of GA for both the newts and snakes.
+My experiment had 25 simulations with 4 different types of GA for both the newts and snakes.
 My goal was to see if I could easily determine a winner from these results.
@@
 ```{r, building a heatmap}
-# params_small <- params[-c(1:7, 9:20)]
-# #params_small <- params[-c(1:7, 9:10)]
-# data_melt <- melt(params_small) 
-# 
-# ggp <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
-#   ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap") +
-#   xlab("Newt GA") + ylab("Snake GA")+
-#   geom_tile(aes(fill = value))+ 
-#   scale_fill_gradient(low = "green", high = "black", name = "Newt Population Size") 
-# ggp
 
 params_small <- params[-c(1:8, 10:20)]
-#params_small <- params[-c(1:8, 10)]
 data_melt <- melt(params_small)
@@
 ggp21 <- ggplot(data_melt, aes(newt, snake)) +    # Create heatmap with ggplot2
-  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap") +
+  ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap") +
   xlab("Newt GA") + ylab("Snake GA")+
@@
 gdif5 <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
-  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 5000") +
+  ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap 5000") +
    xlab("Newt GA") + ylab("Snake GA")+
@@
 ggp212 <- ggplot(data_melt, aes(newt, snake)) +    # Create heatmap with ggplot2
-  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 20000") +
+  ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap 20000") +
   xlab("Newt GA") + ylab("Snake GA")+
@@
 gdif <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
-  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 20000") +
+  ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap 20000") +
    xlab("Newt GA") + ylab("Snake GA")+
@@
 ggp2123 <- ggplot(data_melt, aes(newt, snake)) +    # Create heatmap with ggplot2
-  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 100000") +
+  ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap 100000") +
   xlab("Newt GA") + ylab("Snake GA")+
@@
 gdif10 <- ggplot(data_melt, aes(newt, snake)) +                           # Create heatmap with ggplot2
-  ggtitle("Newt GA by Snake GA", subtitle = "16 Sim Heatmap 100000") +
+  ggtitle("Newt GA by Snake GA", subtitle = "25 Sim Heatmap 100000") +
    xlab("Newt GA") + ylab("Snake GA")+

### 2022-02-14 graphs_newt_snakes/Comparing_GA_part_2.Rmd
I am working on the writing part

@@
 My goal is to first see if there is an obvious "winner" in the co-evolutionary arms race between these species.
-And then to compare to part 1 of the experiment when some GA have an advantage/disadvatage
+And then to compare to part 1 of the experiment when some GA have an advantage/disadvantage
 
@@
 I need to make the data frame to compare all 25 simulations.
-I noticed in the mu=1e-11, sigma=5 simulations that the starting pheotypes of some of the individuals were really high and sometimes the population crashed and died out.
-
-R-code noate: I have code to make my dataframes, it combines many simulations into one graph-able dataframe. Then, I have some functions that can be called to make some figures.
+
+R-code noate: I have code to make my dataframes, it combines many simulations into one graph-able dataframe.
+Then, I have some functions that can be called to make some figures.
+Will need to change this once more simulations are run.
 
@@
 I normally look at one variable at a time from all of my simulations, but since there are so few I can look at them all at once.
-There are over 4,000 observations with 28 variables which contains information from both newts and snakes.
+There are over 6,000 observations with 28 variables which contains information from both newts and snakes.
 I focus on the mean phenotype of both the newt and the snake, usually creating a variable that looks at the difference between the mean pheotypes.
@@
 The first thing I want to look at are the difference between snake and newt mean phenotypes as the number of generations increases.
-The first graph presented is the newt mean phenotype for all simulations as the number of generations increases.
-There are some lines that are squiggly and some lines that are flat.
-The second plot is the represents the snake mean phenotype as the number of generations increases for all the simulations.
-The third plot, shows both the newt and snake mean phenotype (red, blue) and the difference between the snake mean phenotype and the newt mean phenotype (snake-newt, black).
 
@@
 
-Some things that I noticed, are that there are some newt and snake phenotypes that start of really high (I had to cut them so 1st gen is not present).
-These really high phenotypes dropped after the first generation and were seen in simulations that had a higher mu*si^2 value (last 2 rows/columns).
-A question that I had after seeing these plots are why are some of them (snake/newt mean phenotypes) flat?
-Also, the combination of mu times sigma^2 increases the amount of variation.
-For snakes variation going up as you go down the rows (least A->E->I->M most) and for newts variation increases as you go across the columns (least M->N->O->P most).
-It might not be strange to see flat phenotype lines in species who have a low variation, but I expected more competition when the GAs were the same.
-The simulations that seemed to have the most completion were K, L, O, and P.
-It might be a generation problem, it there where more generations would variation eventually increase?
-This is one value for the whole simulation, what is occurring at different spatial points throughout the simulation (P.S.
-I recorded all individuals phenotype, species, fitness, and locations)?
+describe results
 
 Next, I checked the population size of newts and snakes through out the 5,000 generations.
-I found that snake population size seems to be higher than newt population size.
-The way that the colors are stacked indicates that some GA combinations lead to higher population sizes in a species.
-It is hard to tell which GA leads to a higher population size, but I would hypothesize that the simulations with higher variance (mu*si^2) will increase a species population size.
-I also looked at the relationship between newt and snake population size and newt/snake phenotype for all of the simulations combined.
 
@@
 
-When looking at the combined simulation data you can see a relationship between population size and phenotype.
-As a species population size grows so does its phenotype.
-For example when the population size of the newts is large then the phenotype of the newts is larger that the phenotype of the newts when the newt population is smaller.
-However, it is difficult to discern what is going on in each individual simulation and how close the newts and snakes phenotype match.
+desrbe plots
 
@@
 
-The relationship between a species population size and the "whining" species can be a times easy to spot (C, G, O, I, J, L, and P), but at other times it can be hard to discern.
-When snakes are "winning" their population size is greater than the newts.
-When the newts are "winning" their population size is equal or greater then the snakes.
-There are other question that I have for this figure, like why are A, F, K, and P not beige?
-Or why the species with highest variation is not "winning" in the co-evolutionary arms race?
-I wonder if I would get these sames results if I ran the simulation for longer?
-- I suspect not because it seems like the colors are getting lighter (as least they look this way in the plot).
+describe this plot and talk about how it compares to the 16 sim one
 
 To do a reverse check I plot newt mean phenotype by snake mean phenotype and color with the population size.
-It is not as pretty as the other graph, but it does show that when the phenotype of a species is low it ofter has a smaller population size.
-I find the smears sort of funny.
 
@@
 
-Thoughts about predation: If there were lots of newts and snake predation would be higher.
-If newts had a lower phenotype predation would be higher.
-If the interaction rate was higher there might be more predation.
-Right now I do not see any trends.
-It seems very well mixed.
+Thoughts about predation:
 
@@
 
-The 20,000 generation plot shows a similar pattern to the 5,000 generation plot where there is a higher phenotype when one species has has a mu-rate & effect sd of 1.0e-10 & 0.5.
-In this simulation set the plots along the diagonal A F K P look more neutral.
-
-Next, I plotted the same figure with the 100,000 generation data. Two of the GAs simulation would not finish (I ran out of memory on A and individuals on P, possibly I will try to rerun them).
+compare 20,000 generation plot 5,000 generation plot
+
+Next, I plotted the same figure with the 100,000 generation data.
 
@@
 
-These results show a very different pattern in the newt snake phenotype.
-A higher phenotype occurs when the other species has a lower variation (mu*si^2).
-I wonder if this is due to drift (the flat lines).
-I also find it weird how neutral the some of the simulations in the third column and row look.
-So I decided to plot the mean newt phenotype, snake mean phenotype and the difference betwwen snake-newt phenotype as the number of gernerations increased.
+note differences between 10000, 20000, and 5000 gen plots.
+Next, I plotted the mean newt phenotype, snake mean phenotype and the difference between snake-newt phenotype as the number of generations increased.
 
@@
 
-This is kind of a cool result!
-It seems like when mu*si^2 is low that species has a disadvantage and cannot coevolve with the other species.
-It also seems that when the mu-rate & effect sd are 1.0e-10 & 0.5 there might be and advantage for that species for some time, but the other species can catch up.
+what are the reults and what do they mean? how do they compare with the other set of simulations
 
@@
 In each of these plots color will represent the GA of the snake and shape will represent the GA of the newt.
-The colors and shapes are labeled with the mutation rate and mutation effect size sd seperated by a subscript.
+The colors and shapes are labeled with the mutation rate and mutation effect size sd separated by a subscript.
 
@@
 
-The first figure in this section plots newts population size by snakes population size.
-As we saw previously, a larger population size indicates that a species has a higher phenotype or might be "winning" in a coevolutionary arms race.
-In this figure I can see four chunks, a top left a middle left, middle right, and bottom right each containing either 3 or 5 points.
-The top left chunk I think snakes are successfully winning, the have a much larger population size than newts and their phenotype was higher (seen in 25 sim plot).
-The middle left chunk snakes could be winning, the snake population size was larger, but the was not a big difference between newts and snake phenotypes.
-In the middle right chunk, the snake population size was a bit larger than newt population size, but newts often had a higher mean phenotype so I think the newts are winning.
-In the bottom right chunk newts are winning, they have both a larger population size and a higher phenotype.
-For the different GAs I noticed that a species is more likely to win if; first they have a GA with 1e-10_0.5, second they do not have a GA of 1e-11_5, third when snakes and newts had the same GA the pehnotypes were similar or newts were winning.
-The second and third plots show either newt or snake population size by the difference between snake and newt mean phenotype.
-They show/confirm what I saw in the first plot upper chunk snakes are winning, lower chunk newts are winning, center chunks harder to tell.
-I dont see any direct pattern of color and shape, there might be an interaction pattern, but I havent been able to spot it.
+describe the figures not the shapes and colors. How does this compare to the 16 sims?
 
@@
 I also summarized and examined the data for the simulations that I ran longer than the 5,000 generations.
-The results some-what agree and disagree with the above figures.
-First, the 20,000 generation figure looks similar to the 5,000 generation.
-There are sill 4 groups altho the groups seem to be spreading out more.
-There seems to be some clear winners, but some of the clear winners are different than what I saw in the 5,000gen experiment.
-Some of the shapes are clustering together like the plus and squares.
-There might be a color pattern red, green , purple, blue, but I am not sure.
-
-In the 100,000 generation experiment the results look very different than the 5,000 or 20,000 generations.
-There are three distinct groups.
-One where the snakes are winning and one wher the newts are winning.
-Any species that did not have the 1e-8_0.005 was winning.
-Newts tended to lose more than the snakes.
-There are several points that are sticking arounfd the center.
-I wonder if I can turn this into an animation?
+
+other comparisions
 
@@
 The last result section of this markdown will hold the results of my heat maps.
-My experiment had 25 simulations with 4 different types of GA for both the newts and snakes.
+My experiment had 25 simulations with 5 different types of GA for both the newts and snakes.
 My goal was to see if I could easily determine a winner from these results.
@@
 The intersection of the axis (a box) is one simulation that I ran.
-Each box will have a color that is either the population size of the snake or the diffence between snake mean phenotype and newt mean phenotype.
+Each box will have a color that is either the population size of the snake or the difference between snake mean phenotype and newt mean phenotype.
 
@@
 The first heatmap shows how the GA of newts and snakes effected the size of the snake population.
-As we saw in earier results the simulations with the smallest snake population size ocurred when the newts had a GA of 1e-10 and 0.5.
-The simulations where the snake had the largest population size ocurred when the snakes had a GA of 1e-10 and 0.5.
-Now in the second figure we can really look at the difference between snake and newt phenotype.
-I see similar results, but I also noticed that a species phenotype was higher when the other speces had a GA of 1e-11 and 5 (except when they meet).
-The boxes along the diagonol seem close to neutral or newts had a higher phenotype.
-Now I will look at the results from the 20,000 generation experiment.
+Describe Now I will look at the results from the 20,000 generation experiment.
 
@@
 
-In the 20,000 generation experiment the results look similar to the results in the 5,000 generation experiments.
-Here snakes and newts with the GA of 1e-10 and 0.05 have an advantage both in population size and phenotype.
-I see less of a pattern when the GA is 1e-11 and 5.
-The diganal seems to be more neutral in this result.
-I might also see a losing pattern stating to form the the GA is 1e-1 and 0.005 (light, dark, other color).
-There is a bit of an odd symmetry here.
+Write about the 20,000 generation experiment results
+
 Lastly, I will look at the results from the 100,000 generation simulations.
-Again the two grey boxes are where my simulation failed to run (no memory and individuals died out)
 
@@
 
-Again, these results are very different when compared to the 5,000 and 20,000 generation simulations.
-The only pattern that I see is that when either the newt or snake has a GA of 1e-8 and 0.005 the other species has a higher phenotype and population size.
-Most of the other simulations ended up being close to neutral except when the snake GA is 1e-10_0.5 and the newt GA is 1e-11_5.
-I no longer see an advantage when the GA is 1e-10_0.5.
-I wonder why this occurred.
-Is this what steady state looks like?
-Is coevolution still occurring?
-Why did that one box get really blue?
-Is the species who is winning because the other species 1e-8_0.005 because that GA is not realistic?
-Are the effects of the mutations too low?
-I wonder how this boxplot would look though a series of time steps.
+Write about final results. Also talk about how these results are similar/differ from the 16 sim experiment
 
@@
 ## Conclusion & Thoughts
-
-It was really cool to see how different GA effect effects the phenotype and population sizes of newts and snakes.
-It is really confusing trying to compare GA that have different orders of magnitude.
-I wonder if mutation rate or effect size sd drives coevolution or a combination of the two of them.
-If I repeated the experiment would the results be the same?
-
-Something I would like to try next is to see these results ib a simulation with no interaction.

### 2022-02-17 graphs_newt_snakes/Comparing_GA.Rmd
i fixed my descriptions of figures

@@
 
-Rerunning this experiment with these values
+*Above values' results discussed in this document*
+
+These Genetic Architectures (GA) range from having a faster mutation rate with small effect size to having a slower mutation rate with a large effect size.
+
+Rerunning this experiment with these values: Presented in Comparing GA part 2
 
@@
 
-First, I want to look at the mean pheotypes of newts and snakes as the generations increase.
+First, I want to look at the mean phenotype of newts and snakes as the generations increase.
 Then I want to look at the difference between the mean phenotypes for each of the 16 simulations.
 I need to make the data frame to compare all 16 simulations.
-I noticed in the mu=1e-11, sigma=5 simulations that the starting pheotypes of some of the individuals were really high and sometimes the population crashed and died out.
-
-R-code noate: I have code to make my dataframes, it combines many simulations into one graph-able dataframe. Then, I have some functions that can be called to make some figures.
+I noticed in the mu=1e-11, sigma=5 simulations that the starting phenotypes of some of the individuals were really high and sometimes the population crashed and died out.
+
+R-code note: I have code to make my dataframes, it combines many simulations into one graph-able dataframe. Then, I have some functions that can be called to make some figures.
 
@@
 There are over 4,000 observations with 28 variables which contains information from both newts and snakes.
-I focus on the mean phenotype of both the newt and the snake, usually creating a variable that looks at the difference between the mean pheotypes.
-
-Since there are 16 simulations, for convenience I print out the simulation letter with the paramiter I used for the snake and newt mutation rate and mutation effect size
+I focus on the mean phenotype of both the newt and the snake, usually creating a variable that looks at the difference between the mean phenotypes.
+
+Since there are 16 simulations, for convenience I print out the simulation letter with the parameters I used for the snake and newt mutation rate and mutation effect size
 
@@
 
+The flat lines seem to occur when the GA has a mutation rate is large, but the effect size is very small.
+This happens for both newts and snakes when they have this specific GA (seen first row snakes, and first column newts).
+
 Next, I checked the population size of newts and snakes through out the 5,000 generations.
@@
 
+Is the relationship between population size and phenotype what you would expect?
+When snakes are able to eat newts, snake shave a higher phenotype and thus their population grows.
+However, if newts population gets lower then drift can act more strongly.
+We also have to take into account how often snake and newts interact.
+In theses simulations the interaction rate is only 5%.
+It is low which can impact the strength of selection.
+Another not is the size of the populations they are are the smaller size, it is possible for drift to also have some effect on the populations phenotypes.
+I could increase population size (through fecundity) and also increase the interaction rate.
+
 To do a reverse check I plot newt mean phenotype by snake mean phenotype and color with the population size.
-It is not as pretty as the other graph, but it does show that when the phenotype of a species is low it ofter has a smaller population size.
+It is not as pretty as the other graph, but it does show that when the phenotype of a species is low it often has a smaller population size.
 I find the smears sort of funny.
@@
 If the interaction rate was higher there might be more predation.
-Right now I do not see any trends.
+Right now I do not see any striking trends, except there might be more predation when snake population size is higher.
 It seems very well mixed.
@@
 I also find it weird how neutral the some of the simulations in the third column and row look.
-So I decided to plot the mean newt phenotype, snake mean phenotype and the difference betwwen snake-newt phenotype as the number of gernerations increased.
+So I decided to plot the mean newt phenotype, snake mean phenotype and the difference between snake-newt phenotype as the number of generations increased.
 
@@
 It also seems that when the mu-rate & effect sd are 1.0e-10 & 0.5 there might be and advantage for that species for some time, but the other species can catch up.
+Something that I would like to point out is that when a phenotype gets close to 0 like the newts in L and N then it is extremely difficult for them to evolve away from 0.
+They get trapped in e^-value, where even a less negative value will still produce a tiny phenotype.
+A really cool example to look at is in J.
+At first snakes have a higher phenotype then newts steadily catch up.
+These results suggests that I should run my simulations for longer.
 
@@
 In the bottom right chunk newts are winning, they have both a larger population size and a higher phenotype.
-For the different GAs I noticed that a species is more likely to win if; first they have a GA with 1e-10_0.5, second they do not have a GA of 1e-11_5, third when snakes and newts had the same GA the pehnotypes were similar or newts were winning.
+For the different GAs I noticed that a species is more likely to win if; first they have a GA with 1e-10_0.5, second they do not have a GA of 1e-11_5, third when snakes and newts had the same GA the phenotypes were similar or newts were winning.
 The second and third plots show either newt or snake population size by the difference between snake and newt mean phenotype.
 They show/confirm what I saw in the first plot upper chunk snakes are winning, lower chunk newts are winning, center chunks harder to tell.
-I dont see any direct pattern of color and shape, there might be an interaction pattern, but I havent been able to spot it.
+I don't see any direct pattern of color and shape, there might be an interaction pattern, but I haven't been able to spot it.
 
@@
 First, the 20,000 generation figure looks similar to the 5,000 generation.
-There are sill 4 groups altho the groups seem to be spreading out more.
+There are sill 4 groups although the groups seem to be spreading out more.
 There seems to be some clear winners, but some of the clear winners are different than what I saw in the 5,000gen experiment.
@@
 There are three distinct groups.
-One where the snakes are winning and one wher the newts are winning.
+One where the snakes are winning and one where the newts are winning.
 Any species that did not have the 1e-8_0.005 was winning.
 Newts tended to lose more than the snakes.
-There are several points that are sticking arounfd the center.
+There are several points that are sticking around the center.
 I wonder if I can turn this into an animation?
@@
 The first heatmap shows how the GA of newts and snakes effected the size of the snake population.
-As we saw in earier results the simulations with the smallest snake population size ocurred when the newts had a GA of 1e-10 and 0.5.
-The simulations where the snake had the largest population size ocurred when the snakes had a GA of 1e-10 and 0.5.
+As we saw in earlier results the simulations with the smallest snake population size occurred when the newts had a GA of 1e-10 and 0.5.
+The simulations where the snake had the largest population size occurred when the snakes had a GA of 1e-10 and 0.5.
 Now in the second figure we can really look at the difference between snake and newt phenotype.
-I see similar results, but I also noticed that a species phenotype was higher when the other speces had a GA of 1e-11 and 5 (except when they meet).
-The boxes along the diagonol seem close to neutral or newts had a higher phenotype.
+I see similar results, but I also noticed that a species phenotype was higher when the other species had a GA of 1e-11 and 5 (except when they meet).
+The boxes along the diagonal seem close to neutral or newts had a higher phenotype.
 Now I will look at the results from the 20,000 generation experiment.
@@
 I see less of a pattern when the GA is 1e-11 and 5.
-The diganal seems to be more neutral in this result.
+The diagonal seems to be more neutral in this result.
 I might also see a losing pattern stating to form the the GA is 1e-1 and 0.005 (light, dark, other color).
@@
 It is really confusing trying to compare GA that have different orders of magnitude.
-I wonder if mutation rate or effect size sd drives coevolution or a combination of the two of them.
+I wonder if mutation rate or effect size sd drives co-evolution or a combination of the two of them.
 If I repeated the experiment would the results be the same?
 
-Something I would like to try next is to see these results ib a simulation with no interaction.
+Something I would like to try next is to see these results is a simulation with no interaction or a simulation with no space.
+
+I would like to repeat this experiment with replicas.
+But I need to thing about how to graphically show my results.
+I am also thinking about the best ways to include space in my results.
+I might start out with something easy like just plotting the location and phenotype of individuals over time and work my way towards something more complicated.
+
+There are some papers that I would like to read and think about:

### 2022-02-20 graphs_newt_snakes/Comparing_GA_part_2.Rmd
finished writing my thoghts on GA2 and fixed some title error on GA1

@@
 
-Here I am doing a contuation of the small experiment to compare different genetic architectures between snakes and newts. I will use the cost_1on1 simulation and my snake_newt_gv msprime simulation.
+Here I am doing a continuation of the small experiment to compare different genetic architectures between snakes and newts. I will use the cost_1on1 simulation and my snake_newt_gv msprime simulation.
 
@@
 
-R-code noate: I have code to make my dataframes, it combines many simulations into one graph-able dataframe.
+R-code note: I have code to make my dataframes, it combines many simulations into one graph-able dataframe.
 Then, I have some functions that can be called to make some figures.
 Will need to change this once more simulations are run.
+I think these dataframes and pre-made figures might help when I start having reps.
 
@@
 There are over 6,000 observations with 28 variables which contains information from both newts and snakes.
-I focus on the mean phenotype of both the newt and the snake, usually creating a variable that looks at the difference between the mean pheotypes.
-
-Since there are 25 simulations, for convenience I print out the simulation letter with the paramiter I used for the snake and newt mutation rate and mutation effect size
+I focus on the mean phenotype of both the newt and the snake, usually creating a variable that looks at the difference between the mean phenotypes.
+
+Since there are 25 simulations, for convenience I print out the simulation letter with the parameter I used for the snake and newt mutation rate and mutation effect size.
+
+Here are all of the simulations and the identification letter:
 
@@
 The first thing I want to look at are the difference between snake and newt mean phenotypes as the number of generations increases.
+I ran these simulations for 5,000 generations shown on the x-axis.
+The y-axis is the mean phenotype value.
+Each line represents a different simulation.
+Each graph here is showing either newt mean phenotype or snake mean phenotype for all 25 simulations.
 
@@
 ggplot(GA_file, aes(gen, dif, col=factor(sim))) + geom_line()+ 
-    ggtitle("Snake Mean Pheno by Gen", subtitle = "Different Sim") +
+    ggtitle("Snake-Newt Mean Pheno by Gen", subtitle = "Different Sim") +
     ylim(-7,7)+
@@
 
-describe results
+The first set of figures show that mean phenotype for both newts and snake ranges from 0 to 6.
+There are a few simulations where the phenotype look flat, but most of the simulations look like the phenotype is steadily increasing.
+There is a cost in this simulation, which can be seen decreasing the mean phenotype in some of the simulation (look closely at the beginning of the simulations).
+
+When looking at the difference between phenotypes there are some that start out above/below zero and stay that way, ant there are others that hang out near zero possible crossing the zero line.
+Are there any simulations that start out above/below the zero mark and cross it and stay that way?
+
+In the figure that separates newts mean phenotype, snakes mean phenotype and the difference between snakes and newt phenotype (red, blue, black) we can see where the phenotype flat lines and where the phenotype increase.
+The GA for snakes is decreasing mu rate and increasing effect size as you go down.
+The GA for newts decreasing mu rate and increasing effect size as you go across.
+A few possibility for flat phenotypes: they could have a negative value (e^x) where a less negative value doesn't get further away from 0, there could be a large difference between snake and newt phenotype where the other species cant catch up.
+I do not see a GA related trend for flat lines only a large difference in phenotype trends.
+These trends would probably change if I were to re-run this experiment.
 
@@
 
-desrbe plots
+The population size figures for newts and snakes are the first set of figures shown in this section.
+The generation time is shown on the x-axis and the size of the species population is shown on the y-axis.
+Snake population size gets a bit bigger than newt population size.
+However, there is a different balance between newt and snake population size in this set of simulations when compared to part 1.
+The snake population size does not get as high.
+When looking at the figures where newt population size is on the x-axis and snake population sixe is on the y-axis the shade of the point represents the mean phenotype at that point in the simulation.
+These plots contain all of the points from all 25 simulations.
+There is still a trend in the phenotype being larger in the species with a larger population size.
+However, I also see an area of high value phenotypes in the center when both species population size is similar in size (600 newts - 700 snakes).
 
@@
 
-describe this plot and talk about how it compares to the 16 sim one
+This figure separates the 25 simulations that I ran.
+Each letter is one simulation with a specific GA for newts and snakes.
+The GA for snakes is decreasing mu rate and increasing effect size as you go down.
+The GA for newts decreasing mu rate and increasing effect size as you go across.
+The color of the points is the difference between snake mean phenotype and newt mean phenotype.
+A lot of the difference between phenotypes are either 0 or close to 0.
+No trends really pop out to me.
 
@@
 ```
+
+Here this set of figures has newt mean phenotype on the x-axis and snake mean phenotype on the y-axis.
+The color of the points is depicted by the size of the species population.
+I expected that the the darker points wouls show up when one species phenotype was lower that the other.
+For example if the the newts had a higher phenotype than snakes I would expect the newt population size to be dark red.
+In some of the simulations like 3, 8, 10 it looks like the population size of the newts in decreasing at the snake phenotype increases.
+A strinking thing that I note is the lack of horizontal lines.
+What could this mean?
 
@@
 
-Thoughts about predation:
+In the plot about predation newt population size in on the x-axis and snake population size is on the y-axis.
+The shade of the points is the amount of newts eaten by snakes over the newts population size.
+There is more predation when the population size of snakes is higher and newt populations are smaller.
+There is less predation when newt population is higher than snake population.
+It seems like in each of the tiny figures that darker green is seen in mostly the left points and lighter green is seen in the right most points.
+As a whole figure I do not see a trend between the GA.
+I wonder if there would be a slight trend seen in replica simulations.
 
@@
 To examined what would happen if I kept running my simulations for longer I repeated the experiment with 20,000 generations and then again with 100,000 generations.
+Note that all of these simulations 5,000 gen, 20,000 gen and 100,000 gen have the same starting conditions (msprime simulations).
 Below are the summary figures for these simulations.
@@
 If the point is blue snakes have a higher phenotype, if the point is beige snakes and newts have a similar, and if the point is red newts have a higher phenotype.
+
+Here are the simulations that I ran:
 
@@
 
-compare 20,000 generation plot 5,000 generation plot
-
-Next, I plotted the same figure with the 100,000 generation data.
+This figures shows the difference between snake mean phenotype and newt mean phenotype for all 25 simulations with the newt population size on the x-axis and the snake population size on the y-axis for 20,000 generations.
+These results are very similar to the 5,000 generations.
+To me its is striking to see W and K both have long red tails.
+I wonder what the results of many replicas would look like?
+Are there minute details between the GAs that I am not picking up by looking the mean phenotype for the whole population?
+
+Next, I plotted the same figure with the 100,000 generation data. Here are the simulations that I ran:
 
@@
 
-note differences between 10000, 20000, and 5000 gen plots.
+This figures shows the difference between snake mean phenotype and newt mean phenotype for all 25 simulations with the newt population size on the x-axis and the snake population size on the y-axis for 100,000 generations.
+There is not  striking difference between this figure and the ones from 20,000 and 5,000 generations.
+All of the plots have a very low difference in snake and newt phenotype.
+Simulations F and H  have a constant blue color, indicating the snake phenotype was always lager than the newt phenotype.
+I wonder what was going on in the newt phenotype (possibly a flat line).
+Simulation Y goes from neutral to red and simulation W goes from red to neutral.
+Simulation G, I, L, M, N, O, Q, R, T, U, V, and X have points that are blue, red, and beige.
+I want to take a closer look at O, because the population sizes and phenotype seem to have a large range.
+
 Next, I plotted the mean newt phenotype, snake mean phenotype and the difference between snake-newt phenotype as the number of generations increased.
@@
     geom_line(aes(gen, dif, col="dif"))+
-    ggtitle("Phenotpe by Gen For all Sims", subtitle = "100,000Gen Different Sim") +
+    ggtitle("Phenotpe by Gen For all Sims", subtitle = "100,000 Gen ") +
     geom_line(aes(gen, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+
@@
 
-what are the reults and what do they mean? how do they compare with the other set of simulations
+This figures shows the difference between snake mean phenotype and newt mean phenotype (in black), newt phenotype (red), and snake phenotype (blue) for 100,000 generations.
+The GA for snakes is decreasing mu rate and increasing effect size as you go down.
+The GA for newts decreasing mu rate and increasing effect size as you go across.
+Here we can clearly see some trends!
+It seems like at the lowest mutation rate/ high effect size GA the mean phenotype line for both snakes (row 5) and newts (column 5) are relatively flat.
+But there still seems to be co-evolution going on (the phenotypes are closely matched at some points in time).
+Simulations H, F and, O are strange the newt phenotype goes to 0 and remains there.
+Simulation F looks extremely weird.
+I wonder if the initial slope of the simulations differ between GAs?
 
@@
 I summarize the last half of the data for 5,000 generations the last 1,500 generations for 20,000 generations and the last 10,000 generations for the 100,000 simulation.
-By summarizing the data I can try to compare the GA of the snakes tot the GA of the newts through information of their population sizes and phenotypes.
+By summarizing the data I can try to compare the GA of the snakes to the GA of the newts through information of their population sizes and phenotypes.
 I summarize by taking the mean value of a specific parameter.
@@
 
-describe the figures not the shapes and colors. How does this compare to the 16 sims?
+This figure shows all 25 simulations for 5,000 generations in one plot.
+Each color and shape combo is one simulation with a GA for the neat and a genetic architecture for the snake.
+Normally, I would expect that a simulation that resulted with a species that had a higher population size than the other species would result in a "co-evolution win", but it is a bit difficult to tell since many of the simulations were more neutral.
+There was no easy to identify patter between snakes or newts having specific GA (no color or shape clustering).
+This result does match what I saw when plotting the difference between snake and newt phenotype.
 
@@
 
-other comparisions
+These are other comparisons for 20,000 and 100,000 generations.
+Each point on the plot is one simulation with a GA for newts (shape) and a GA for snakes (color).
+The x-axis is newt population size and the y- axis is either snake population size or the difference between snake and newt mean phenotype.
 
@@
 
+This is the 20,000 generation figure.
+There is only one snake "winner" having both a higher phenotype and a larger population size.
+The vast majority of points fall into neither newts or snakes are winning or newts are winning.
+Again trying to see an obvious trend between the GA is difficult.
+I can see that newts lowest mutation rate/ high effect size often results in the newt "win".
+There are not very many simulations where the snakes population size was super high.
+
+Next, lets look at the 100,000 generation summary plot.
+
 ```{r, 1000000gen}
@@
 
-##Heatmap
+In this plot the points seem to spread out more and at the same time cluster closer together near 0.
+We can easily see the simulations were the newts phenotype went to 0: F, H, O and T.
+It is strange that the only simulations where the snake can "win" is when the newt phenotype is not evolving.
+I have noticed that the pink colored points are clustered toward the bottom, but the cross-box is not really close to the top.
+I wonder if there would be more separation if I ran the simulations for longer?
+I wonder if I re-ran the msprime simulation if there would be no snake "winners"
+
+## Heatmap
 
@@
 
+Note: When reading this figure, the snake GA has flipped, now as you go down the mutation rate increase and the effect size has decreased.
+The GA of the newt has mutation rate decreasing and effect size increase as its read across.
+
 For the 5,000 generation simulation I have created two heat maps.
 The first heatmap shows how the GA of newts and snakes effected the size of the snake population.
-Describe Now I will look at the results from the 20,000 generation experiment.
+If you squint a bit it seems like snake population size is larger in the simulations on the left side of the image.
+There is no difference in snake population size from the top to the bottom.
+This suggests that the newt GA has an impact on the size of the snake population.
+If there are more mutations of small effect in the newt then the snake will have a larger population size regardless of GA (not true in all simulation cases).
+I would like to check this further with reps.
+When looking at the same figure, but colored with the difference between snake and newt mean phenotype, we can see that all of the blue points are on the left side of the simulation.
+This mirrors what we see in the figure above it.
+
+Now I will look at the results from the 20,000 generation experiment.
 
@@
 
-Write about the 20,000 generation experiment results
+The first heatmap for 20,000 generation shows how the GA of newts and snakes effected the size of the snake population.
+There is less of a difference between the left and right side, but there are darker squares on the right side.
+There is again no difference in snake population size from the top to the bottom.
+This suggests that the newt GA has an impact on the size of the snake population.
+In this case when there are less mutations of large effect in the newt then the snake will have a smaller population size regardless of GA (not true in all simulation cases).
+The bright yellow square probably has a newt phenotype close to 0.
+When looking at the next figure (the one colored by the difference between mean phenotypes) we can see darker red squares to the right of the image.
+We can especially see a column of red when news have a GA of 1e-12_5.
+Most of the square are neutral or red with only one blue square
 
@@
  params_small <- params[-c(1:18, 20)]
-params_small[params_small==0]<-NA
+
 data_melt <- melt(params_small)
@@
  params_small <- params[-c(1:19)]
- params_small[params_small==0]<-NA
+
 data_melt <- melt(params_small) 
@@
 
-Write about final results. Also talk about how these results are similar/differ from the 16 sim experiment
+In the final set of heat maps, the results are even more confusing.
+There is less of a difference between the right and left side, but potentially a difference between the top and bottom.
+There seems to be lighter squares on the bottom (but this might be due to all of the sims where the newts phenotype went to 0).
+In the 100,000 generation heat map colored by snake-newt mean phenotype there are dark red squares in the upper half of the figure.
+These results indicate that a snake GA with a slower mutation rate and a larger effect size would result in newts having a higher phenotype regardless of the newts GA.
+Something that I noticed is that all the corners of the simulation have a low snake population size and a larger newt phenotype, why is this occurring?
+Is this potentially due to a cycle?
+Why are there so few blue squares?
+Would these results hold if I ran more simulations and ran them for longer?
 
@@
 ## Conclusion & Thoughts
+
+My main conclusion to this experiment is that when the GA for news and snakes have the same potential for genetic variance that it is difficult to see a co-evolution "winner".
+I wonder if "winning" might cycle though time or needs more time to occur.
+It is even possible that "winning" might not occur.
+
+When I think about this experiment (same genetic variance) vs the other experiment (different genetic variance) it is easier to see a winner in the different genetic variance experiment.
+In the summary plots the obvious winners got further from the 0 line and when the species were still competing clustered closer to the 0 line.
+In this experiment there didn't seem to be a best GA, although the GA with a low mutation rate and high effect size did seem to be flatter.
+All-in-all I think it would be best to run both experiments again with may reps and different msprime files.

### 2022-02-24 graphs_newt_snakes/Comparing_GA_part_2.Rmd
I am working on an animation that shows clumps of individuals phenotypes over the course of the simulation. I am also trying to make a boxplot of phenotypes and predation

@@
 
+## Data as box plots
+
+Here I want to look at some boxplots of the phenotype and predation from the 100,000 generation simulation.
+
+```{r, boxplottinh}
+GA_file_100$mean_predation <- GA_file_100$newt_deaths/GA_file_100$Newt_pop_size
+
+GA_file_100$gen_boxy <- round_any(GA_file_100$gen, 1000, f = ceiling) 
+ggplot(data = GA_file_100[which(GA_file_100$gen_boxy>=95000),], aes(x = factor(gen_boxy), y = mean_predation)) +
+  facet_wrap(~sim)+
+  geom_boxplot() +
+  xlab("Generation") +
+  ylab("mean_predation")
+
+```
+
 ## Summarized Data

### 2022-02-24 graphs_newt_snakes/byind_GA.R

@@ -1,0 +1,56 @@
+#This will be the file that I use to animate the individual GA data
+
+library(ggplot2)
+library(viridis)
+library(colorspace)
+library(gridExtra)
+library(tidyverse)
+require(reshape2)
+library(plyr)
+library(gridGraphics)
+library(grid)
+library(gganimate)
+library(gifski)
+library(gapminder)
+
+files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA2_litby", full.names=TRUE, recursive=FALSE)
+
+
+number=1
+myGA_file <- read.table(files[number], header = TRUE)
+
+#max_newt_pheno = max(GA_file[GA_file$species=="N",]$phenotype)
+#max_snake_pheno = max(GA_file[GA_file$species=="S",]$phenotype)
+
+graph_file<-myGA_file
+frames<-max(graph_file$gen)/100+1
+my_duration <- 20
+my_fps<-frames/my_duration
+title<-"Phenotype bin Space By Generation"
+subt<-"sim details"
+
+ggplot(graph_file, aes(loc_x, loc_y, color=species, group=species, alpha = phenotype/max(phenotype))) +
+  #geom_point(data=graph_file[which(graph_file$species=="N"),],aes(alpha = phenotype/max_newt_pheno, shape=species),colour = "darkred")+ #colour = "darkred"
+  #geom_point(data=graph_file[which(graph_file$species=="S"),],aes(alpha = phenotype/max_snake_pheno, shape=species), colour = "steelblue")+ #colour = "steelblue"
+  geom_point()+
+  scale_color_manual(values=c('darkred', 'steelblue'))+
+  ggtitle(title, subtitle = subt) +
+  #xlim(-1, 1000) +
+  theme_bw()
+
+
+p <- ggplot(graph_file, aes(loc_x, loc_y, color=species, group=species, alpha = phenotype/max(phenotype))) +
+  geom_point()+
+  scale_color_manual(values=c('darkred', 'steelblue'))+
+  ggtitle(title, subtitle = subt) +
+  #xlim(-1, 1000) +
+  theme_bw() +
+  # gganimate specific bits:
+  labs(title = 'Generation: {frame_time}', x = 'x loc', y = 'y loc') +
+  transition_time(gen) +
+  ease_aes('linear')
+animate(p, duration = my_duration, fps = my_fps, nframes=frames, width = 600, height = 400, renderer = gifski_renderer())
+anim_save("data/gganimateGA1.gif")
+
+
+

### 2022-02-25 graphs_newt_snakes/byind_GA.R
I found a good value to make the animations. I now need to make it work on the cluster and see it it will work when I run the simulations for longer.

@@ -13,7 +13,7 @@ library(gganimate)
 library(gifski)
 library(gapminder)
 
-files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA2_litby", full.names=TRUE, recursive=FALSE)
+files <- list.files(path="~/Desktop/GA_lt/gen_5000/lit/text_files", pattern="GA4_litby", full.names=TRUE, recursive=FALSE)
 
 
 number=1
@@ -23,8 +23,8 @@ myGA_file <- read.table(files[number], header = TRUE)
 #max_snake_pheno = max(GA_file[GA_file$species=="S",]$phenotype)
 
 graph_file<-myGA_file
-frames<-max(graph_file$gen)/100+1
-my_duration <- 20
+frames<-length(unique(graph_file$gen))
+my_duration <- 50
 my_fps<-frames/my_duration
 title<-"Phenotype bin Space By Generation"
 subt<-"sim details"
@@ -50,7 +50,7 @@ p <- ggplot(graph_file, aes(loc_x, loc_y, color=species, group=species, alpha = 
   transition_time(gen) +
   ease_aes('linear')
 animate(p, duration = my_duration, fps = my_fps, nframes=frames, width = 600, height = 400, renderer = gifski_renderer())
-anim_save("data/gganimateGA1.gif")
+anim_save("data/gganimateGA4.gif")
 
 
 

### 2022-03-13 graphs_newt_snakes/Correlation.Rmd
I am trying to make a snakemake file for my co-evolution project to make running simulations more stream-line. I am also editing my animaltions and trying to see if I can get correlation values out of r. I testing different grid sizes and cor caculations in the cost1on1 slim. After running cost1on1 I am starting to plot the correlation results (they kind of look like fuzzy caterpillars). I have plans on edititng the slim script to make the newts and snakes beginning pheno more similar.

---
title: "Correlation"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library("reshape")
```

## Goals

I am starting to investigate what is going on in small scales in my co-evolution simulation. I decided to get newt and snake information and see in they were correlated in 5-5 grids. I collected correlated data from the GA experiments from the 5,000, 20,000, and 100,000 simulations. I also will examine how the correlation values change when the grid has more boxes (smaller area to compare).

GA1 experiment values

- 1e-8*(0.005)^2 = 2.5e-13
- 1e-9*(0.05)^2 = 2.5e-12
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(5.0)^2 = 2.5e-10

GA2 experiment values

- 1e-8*(0.05)^2 = 2.5e-11
- 1e-9*(0.1581139)^2 = 2.5e-11
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(1.581139)^2 = 2.5e-11
- 1e-12*(5)^2 = 2.5e-11

collected info:
	mean_newt_pheno_By_mean_snake_pheno = cor(c(newt_mean_pheno), c(snake_mean_pheno));
	num_newts_By_num_snakes = cor(c(newt_sum_ind), c(snake_sum_ind));
	sum_newt_pheno_By_num_snake = cor(c(newt_sum_pheno), c(snake_sum_ind));
	sum_snake_pheno_By_num_newt = cor(c(snake_sum_pheno), c(newt_sum_ind));
	sum_newt_pheno_By_num_newt = cor(c(newt_sum_pheno), c(newt_sum_ind));
	sum_snake_pheno_By_snake_newt = cor(c(snake_sum_pheno), c(snake_sum_ind));

Tested Grids

- (5, 5)
- (8, 8)
- (10, 10)
- (20, 20)

```{r, Cor data gather}

lit_files <- list.files(path="~/Desktop/cor/text_files", pattern="_lit_", full.names=TRUE, recursive=FALSE)

cor_files <- list.files(path="~/Desktop/cor/text_files", pattern="_cor_", full.names=TRUE, recursive=FALSE)

#files <- list.files(path="~/Desktop/GA_lt/doover/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)

number=1
cor_file <- read.table(cor_files[number], header = TRUE)
GA_file <- read.table(lit_files[number], header = TRUE)

GA_file$sim <-"A"
cor_file$sim <-"A"

for(i in seq(1, length(lit_files), 1)){
  lit_temp_file <- read.table(lit_files[i], header = TRUE)
  lit_temp_file$sim <-LETTERS[i]
  cor_temp_file <- read.table(cor_files[i], header = TRUE)
  cor_temp_file$sim <-LETTERS[i]
  cor_file <- rbind(cor_file, cor_temp_file)
  GA_file <- rbind(GA_file, lit_temp_file)
  myletter <- LETTERS[i]
  snake_mu_rate <- unlist(str_split(unlist(str_split(lit_files[i],"snake_mu_rate_"))[2], "_"))[1]
  newt_mu_rate <- unlist(str_split(unlist(str_split(lit_files[i],"newt_mu_rate_"))[2], "_"))[1]
  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  print(paste0("Simulation ", LETTERS[i],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))

}
GA_file$dif <- GA_file$Snake_mean_Pheno-GA_file$Newt_mean_Pheno

```

```{r, lest see that correlation}

title="Space: Newt VS Snake"
subt="Grid 5 by 5"
y_label="Generation"
x_label="Correlation"

ggplot(cor_file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "mean_newt_pheno_By_mean_snake_pheno"))+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(num_newts_By_num_snakes), color = "num_newts_By_num_snakes"))+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_newt_pheno_By_num_snake), color = "sum_newt_pheno_By_num_snake"))+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_num_newt), color = "sum_snake_pheno_By_num_newt"))+
  #geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_newt_pheno_By_num_newt), color = "sum_newt_pheno_By_num_newt"))+
  #geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_snake_newt), color = "sum_snake_pheno_By_snake_newt"))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_manual(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

ggplot(GA_file) +
    facet_wrap(~sim)+
    geom_line(aes(gen, dif, col="dif"))+
    ggtitle("Phenotpe by Gen For all Sims", subtitle = subt) +
    geom_line(aes(gen, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+
    geom_line(aes(gen, Newt_mean_Pheno, color="Newt_mean_Pheno"))+
    ylim(-5,10)+
    xlab("Generations") + ylab("Phenotype")+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

```

### 2022-03-13 graphs_newt_snakes/byind_GA.R

@@ -166,3 +166,7 @@ for (i in 6550555:nrow(myGA_file)){
 }
 making_a_grid
 
+write.csv(myGA_file,"~/Desktop/with_grid_litbyind_snake_mu_rate_1.0e-08_newt_mu_rate_1.0e-08_snake_mu_effect_sd_0.05_newt_mu_effect_sd_0.05_sigma_0.5_FN_2949665473_ID_4086676209290_cost_100_interaction_rate_0.05_late_5000.csv", row.names = FALSE)
+
+
+

### 2022-03-14 graphs_newt_snakes/Comparing_GA_part_2.Rmd
i am making more figures for the comparing GA specifically boxplots. I also plotted all the data from the cor datasets and they look like fuzzy catterplilars

@@
 
+## Boxplots
+
+I wanted a better way to discern if there was a difference between the simulations that I ran, so I plotted the final results (last 1000 and 100 generations) as a boxplot.
+I plot the simulation type (letters also GA) on the x-axis and the phenotype and predation on the y-axis.
+Hopefully, these boxplots will show a relative difference between the predation and phenotype between different GA.
+More simulations might change the result.
+
+```{r, boxplotting}
+title="Space: Newt VS Snake Boxplot Color=Mean_predation"
+subt="25sims newt_deaths/Newt_pop_size last 1000gen"
+y_label="Mean_predation"
+x_label="Simulation"
+ggplot(GA_file[ which(GA_file$gen>4000),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation)), color="darkolivegreen4")+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+title="Space: Newt VS Snake Boxplot Color=Mean_predation"
+subt="25sims newt_deaths/Newt_pop_size last 100gen"
+y_label="Mean_predation"
+x_label="Simulation"
+ggplot(GA_file[ which(GA_file$gen>4900),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation)), color="darkolivegreen4")+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+title="Space: Newt VS Snake Boxplot Phenotype"
+subt="25sims dif last 1000gen"
+y_label="dif"
+x_label="Simulation"
+ggplot(GA_file[ which(GA_file$gen>4000),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif)), color="darkorchid4")+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno)), color="darkred")+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno)), color="steelblue")+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+title="Space: Newt VS Snake Boxplot Phenotype"
+subt="25sims dif last 100gen"
+y_label="dif"
+x_label="Simulation"
+ggplot(GA_file[ which(GA_file$gen>4900),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif)), color="darkorchid4")+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno)), color="darkred")+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno)), color="steelblue")+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+```
+
 ## Longer Simulations

### 2022-03-14 graphs_newt_snakes/Correlation.Rmd
i am making more figures for the comparing GA specifically boxplots. I also plotted all the data from the cor datasets and they look like fuzzy catterplilars

@@
 ```{r, Cor data gather}
+#Reading in the names of files to cycle through them
+lit_5000_files <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA6_lit_", full.names=TRUE, recursive=FALSE)
+cor_5000_files <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA6_cor_", full.names=TRUE, recursive=FALSE)
 
-lit_files <- list.files(path="~/Desktop/cor/text_files", pattern="_lit_", full.names=TRUE, recursive=FALSE)
+lit_20000_files <- list.files(path="~/Desktop/cor_20000/text_files", pattern="GA6_lit_", full.names=TRUE, recursive=FALSE)
+cor_20000_files <- list.files(path="~/Desktop/cor_20000/text_files", pattern="GA6_cor_", full.names=TRUE, recursive=FALSE)
 
-cor_files <- list.files(path="~/Desktop/cor/text_files", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+lit_100000_files <- list.files(path="~/Desktop/cor_20000/text_files", pattern="GA6_lit_", full.names=TRUE, recursive=FALSE)
+cor_100000_files <- list.files(path="~/Desktop/cor_20000/text_files", pattern="GA6_cor_", full.names=TRUE, recursive=FALSE)
+
+lit_5000_files_88 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA88_lit_", full.names=TRUE, recursive=FALSE)
+cor_5000_files_88 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA88_cor_", full.names=TRUE, recursive=FALSE)
+
+lit_5000_files_1010 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA1010_lit_", full.names=TRUE, recursive=FALSE)
+cor_5000_files_1010 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA1010_cor_", full.names=TRUE, recursive=FALSE)
+
+GA2_lit_5000_files <- list.files(path="~/Desktop/cor_GA2_5000/text_files", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
+GA2_cor_5000_files <- list.files(path="~/Desktop/cor_GA2_5000/text_files", pattern="GA55_cor_", full.names=TRUE, recursive=FALSE)
 
 #files <- list.files(path="~/Desktop/GA_lt/doover/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
+# Reading in the first file from the list to add a new column. To compare simulations with different params
+number=1
+cor_5000_file <- read.table(cor_5000_files[number], header = TRUE)
+GA_5000_file <- read.table(lit_5000_files[number], header = TRUE)
 
-number=1
-cor_file <- read.table(cor_files[number], header = TRUE)
-GA_file <- read.table(lit_files[number], header = TRUE)
+cor_20000_file <- read.table(cor_20000_files[number], header = TRUE)
+GA_20000_file <- read.table(lit_20000_files[number], header = TRUE)
 
-GA_file$sim <-"A"
-cor_file$sim <-"A"
+cor_100000_file <- read.table(cor_100000_files[number], header = TRUE)
+GA_100000_file <- read.table(lit_100000_files[number], header = TRUE)
 
-for(i in seq(1, length(lit_files), 1)){
-  lit_temp_file <- read.table(lit_files[i], header = TRUE)
+cor_5000_file_88 <- read.table(cor_5000_files_88[number], header = TRUE)
+GA_5000_file_88 <- read.table(lit_5000_files_88[number], header = TRUE)
+
+cor_5000_file_1010 <- read.table(cor_5000_files_1010[number], header = TRUE)
+GA_5000_file_1010 <- read.table(lit_5000_files_1010[number], header = TRUE)
+
+GA2_cor_5000_file <- read.table(GA2_cor_5000_files[number], header = TRUE)
+GA2_GA_5000_file <- read.table(GA2_lit_5000_files[number], header = TRUE)
+
+GA_5000_file$sim <-"A"
+cor_5000_file$sim <-"A"
+
+GA_20000_file$sim <-"A"
+cor_20000_file$sim <-"A"
+
+GA_100000_file$sim <-"A"
+cor_100000_file$sim <-"A"
+
+GA_5000_file_88$sim <-"A"
+cor_5000_file_88$sim <-"A"
+
+GA_5000_file_1010$sim <-"A"
+cor_5000_file_1010$sim <-"A"
+
+GA2_GA_5000_file$sim <-"A"
+GA2_cor_5000_file$sim <-"A"
+
+#Cycle through the different simulations to make one file. Not recommended for large files, but right now mine are small
+for(i in seq(1, length(GA2_lit_5000_files), 1)){
+  myletter <- LETTERS[i]
+
+  GA2_lit_temp_file <- read.table(GA2_lit_5000_files[i], header = TRUE)
+  GA2_lit_temp_file$sim <-LETTERS[i]
+  GA2_cor_temp_file <- read.table(GA2_cor_5000_files[i], header = TRUE)
+  GA2_cor_temp_file$sim <-LETTERS[i]
+
+  GA2_GA_5000_file <- rbind(GA2_GA_5000_file, GA2_lit_temp_file)
+  GA2_cor_5000_file <- rbind(GA2_cor_5000_file, GA2_cor_temp_file)
+
+  if (i<=length(lit_5000_files)){
+  lit_temp_file <- read.table(lit_5000_files[i], header = TRUE)
   lit_temp_file$sim <-LETTERS[i]
-  cor_temp_file <- read.table(cor_files[i], header = TRUE)
+
+  lit_temp_file_2 <- read.table(lit_20000_files[i], header = TRUE)
+  lit_temp_file_2$sim <-LETTERS[i]
+
+  lit_temp_file_3 <- read.table(lit_100000_files[i], header = TRUE)
+  lit_temp_file_3$sim <-LETTERS[i]
+
+  lit_temp_file_4 <- read.table(lit_5000_files_88[i], header = TRUE)
+  lit_temp_file_4$sim <-LETTERS[i]
+
+  lit_temp_file_5 <- read.table(lit_5000_files_1010[i], header = TRUE)
+  lit_temp_file_5$sim <-LETTERS[i]
+
+  cor_temp_file <- read.table(cor_5000_files[i], header = TRUE)
   cor_temp_file$sim <-LETTERS[i]
-  cor_file <- rbind(cor_file, cor_temp_file)
-  GA_file <- rbind(GA_file, lit_temp_file)
-  myletter <- LETTERS[i]
-  snake_mu_rate <- unlist(str_split(unlist(str_split(lit_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  newt_mu_rate <- unlist(str_split(unlist(str_split(lit_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+
+  cor_temp_file_2 <- read.table(cor_20000_files[i], header = TRUE)
+  cor_temp_file_2$sim <-LETTERS[i]
+
+  cor_temp_file_3 <- read.table(cor_100000_files[i], header = TRUE)
+  cor_temp_file_3$sim <-LETTERS[i]
+
+  cor_temp_file_4 <- read.table(cor_5000_files_88[i], header = TRUE)
+  cor_temp_file_4$sim <-LETTERS[i]
+
+  cor_temp_file_5 <- read.table(cor_5000_files_1010[i], header = TRUE)
+  cor_temp_file_5$sim <-LETTERS[i]
+
+  GA_5000_file <- rbind(GA_5000_file, lit_temp_file)
+  GA_20000_file <- rbind(GA_20000_file, lit_temp_file_2)
+  GA_100000_file <- rbind(GA_100000_file, lit_temp_file_3)
+  GA_5000_file_88 <- rbind(GA_5000_file_88, lit_temp_file_4)
+  GA_5000_file_1010 <- rbind(GA_5000_file_1010, lit_temp_file_5)
+
+  cor_5000_file <- rbind(cor_5000_file, cor_temp_file)
+  cor_20000_file <- rbind(cor_20000_file, cor_temp_file_2)
+  cor_100000_file <- rbind(cor_100000_file, cor_temp_file_3)
+  cor_5000_file_88 <- rbind(cor_5000_file_88, cor_temp_file_4)
+  cor_5000_file_1010 <- rbind(cor_5000_file_1010, cor_temp_file_5)
+
+  snake_mu_rate <- unlist(str_split(unlist(str_split(lit_5000_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  newt_mu_rate <- unlist(str_split(unlist(str_split(lit_5000_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_5000_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_5000_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
   print(paste0("Simulation ", LETTERS[i],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))
+  }
 
 }
-GA_file$dif <- GA_file$Snake_mean_Pheno-GA_file$Newt_mean_Pheno
 
+# Calculating the difference between mean snake pheno and mean newt pheno
+
+GA_5000_file$dif <- GA_5000_file$Snake_mean_Pheno-GA_5000_file$Newt_mean_Pheno
+GA_20000_file$dif <- GA_20000_file$Snake_mean_Pheno-GA_20000_file$Newt_mean_Pheno
+GA_100000_file$dif <- GA_100000_file$Snake_mean_Pheno-GA_100000_file$Newt_mean_Pheno
+GA_5000_file_88$dif <- GA_5000_file_88$Snake_mean_Pheno-GA_5000_file_88$Newt_mean_Pheno
+GA_5000_file_1010$dif <- GA_5000_file_1010$Snake_mean_Pheno-GA_5000_file_1010$Newt_mean_Pheno
+GA2_GA_5000_file$dif <- GA2_GA_5000_file$Snake_mean_Pheno-GA2_GA_5000_file$Newt_mean_Pheno
+GA2_GA_5000_file$dif <- GA2_GA_5000_file$Snake_mean_Pheno-GA2_GA_5000_file$Newt_mean_Pheno
 ```
 
-```{r, lest see that correlation}
+```{r, reusable figures, results='hide', message=FALSE, warning=FALSE}
 
-title="Space: Newt VS Snake"
-subt="Grid 5 by 5"
-y_label="Generation"
-x_label="Correlation"
+cors_by_gen <- function(file, title, subt, x_label, y_label){
 
-ggplot(cor_file) +
+plot <- ggplot(file) +
   #xlim(0, 1000)+
@@
   geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_num_newt), color = "sum_snake_pheno_By_num_newt"))+
-  #geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_newt_pheno_By_num_newt), color = "sum_newt_pheno_By_num_newt"))+
-  #geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_snake_newt), color = "sum_snake_pheno_By_snake_newt"))+
   theme(plot.title = element_text(size=5)) +
-  #scale_colour_manual(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
+
   facet_wrap(~sim)+
@@
 
-ggplot(GA_file) +
+  return(plot)
+}
+trends_by_gen <- function(file, title, subt, x_label, y_label){
+  plot <- ggplot(file) +
     facet_wrap(~sim)+
     geom_line(aes(gen, dif, col="dif"))+
-    ggtitle("Phenotpe by Gen For all Sims", subtitle = subt) +
+    ggtitle(title, subtitle = subt) +
     geom_line(aes(gen, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+
@@
     ylim(-5,10)+
-    xlab("Generations") + ylab("Phenotype")+
+    xlab(x_label) + ylab(y_label)+
     scale_color_manual(name = "Type",
@@
     theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  return(plot)
+}
 
 ```
+
+```{r, lest see that correlation}
+
+title="Space: Newt VS Snake"
+subt="5,000 Gen Grid 5 by 5"
+y_label="Generation"
+x_label="Correlation"
+cors_by_gen(cor_5000_file, title, subt, x_label, y_label)
+
+y_label="Phenotype"
+title="Phenotpe by Gen For all Sims"
+subt="GA1 5000 Gen"
+trends_by_gen(GA_5000_file, title, subt, x_label, y_label)
+
+```
+```{r, cor 5000 zooom}
+
+title="ZOOM Space: Newt VS Snake"
+subt="5,000 Gen Grid 5 by 5"
+y_label="Generation"
+x_label="Correlation"
+cors_by_gen(cor_5000_file[ which(cor_5000_file$gen<200),], title, subt, x_label, y_label)
+
+title="ZOOM Phenotpe by Gen For all Sims"
+subt="GA1 5000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA_5000_file[ which(GA_5000_file$gen<200),], title, subt, x_label, y_label)
+
+```
+
+```{r, correlation 20000}
+
+title="Space: Newt VS Snake"
+subt="20,000 Gen Grid 5 by 5"
+y_label="Generation"
+x_label="Correlation"
+cors_by_gen(cor_20000_file, title, subt, x_label, y_label)
+
+title="Phenotpe by Gen For all Sims"
+subt="GA1 20000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA_20000_file, title, subt, x_label, y_label)
+
+```
+
+```{r, correlation 100000}
+
+title="Space: Newt VS Snake"
+subt="100,000 Gen Grid 5 by 5"
+y_label="Generation"
+x_label="Correlation"
+cors_by_gen(cor_100000_file, title, subt, x_label, y_label)
+
+title="Phenotpe by Gen For all Sims"
+subt="GA1 100000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA_100000_file, title, subt, x_label, y_label)
+
+```
+
+```{r, correlation 5000 88}
+
+title="Space: Newt VS Snake"
+subt="5,000 Gen Grid 8 by 8"
+y_label="Generation"
+x_label="Correlation"
+cors_by_gen(cor_5000_file_88, title, subt, x_label, y_label)
+
+title="Phenotpe by Gen For all Sims"
+subt="GA1 5,000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA_5000_file_88, title, subt, x_label, y_label)
+
+```
+
+```{r, correlation 5000 1010}
+
+title="Space: Newt VS Snake"
+subt="5,000 Gen Grid 10 by 10"
+y_label="Generation"
+x_label="Correlation"
+cors_by_gen(cor_5000_file_1010, title, subt, x_label, y_label)
+
+title="Phenotpe by Gen For all Sims"
+subt="GA1 5,000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA_5000_file_1010, title, subt, x_label, y_label)
+
+```
+
+```{r, GA2 correlation}
+
+title="GA2 Space: Newt VS Snake"
+subt="5,000 Gen Grid 5 by 5"
+y_label="Generation"
+x_label="Correlation"
+cors_by_gen(GA2_cor_5000_file, title, subt, x_label, y_label)
+
+title="Phenotpe by Gen For all Sims"
+subt="GA2 5,000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA2_GA_5000_file, title, subt, x_label, y_label)
+
+```
+
+```{r, cor 5000 GA2 zooom}
+
+title="GA2 ZOOM Space: Newt VS Snake"
+subt="5,000 Gen Grid 5 by 5"
+y_label="Generation"
+x_label="Correlation"
+cors_by_gen(GA2_cor_5000_file[ which(GA2_cor_5000_file$gen<200),], title, subt, x_label, y_label)
+
+title="ZOOM Phenotpe by Gen For all Sims"
+subt="GA2 5,000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA2_GA_5000_file[ which(GA2_GA_5000_file$gen<200),], title, subt, x_label, y_label)
+
+```

### 2022-03-16 graphs_newt_snakes/Comparing_GA_part_2.Rmd
working on fixing the correlation plots, and trying to figure out if there is a problem

@@
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+```
+
+These figures show the predation level for the last 1000 and 100 generations on the y-axis.
+The x-axis has the simulations that I ran with different parameters.
+For every chunk of five letters the snakes GA stays the same while the newts GA decreases mutation rate and increases effect size.
+Every fifth letter the newts GA stays the same while the snakes GA decreases mutation rate and increases effect size.
+The first thing that I noticed is that there is more variation in predation in the 1000 gen figures than in the 100 gen figure.
+This is probably due to more generations being considered.
+I noticed that higher predation matches up to a higher phenotype, but not in all of the cases
+
+```{r, boxplotting the phenotype}
 
@@
 ```
+These figures show the mean newt phenotype, mean snake phenotype, and the difference between snake and newt mean phenotype (red, blue, and purple) for the last 1000 and 100 generations on the y-axis.
+The x-axis has the simulations that I ran with different parameters.
+For every chunk of five letters the snakes GA stays the same while the newts GA decreases mutation rate and increases effect size.
+Every fifth letter the newts GA stays the same while the snakes GA decreases mutation rate and increases effect size.
+I noticed that the newts have a higher phenotype in most of the simulations.
+I wonder if there is a connection between GA and species phenotype.
 
@@
 
-Here I want to look at some boxplots of the phenotype and predation from the 100,000 generation simulation.
-
-```{r, boxplottinh}
-GA_file_100$mean_predation <- GA_file_100$newt_deaths/GA_file_100$Newt_pop_size
-
-GA_file_100$gen_boxy <- round_any(GA_file_100$gen, 1000, f = ceiling) 
-ggplot(data = GA_file_100[which(GA_file_100$gen_boxy>=95000),], aes(x = factor(gen_boxy), y = mean_predation)) +
-  facet_wrap(~sim)+
-  geom_boxplot() +
-  xlab("Generation") +
-  ylab("mean_predation")
-
-```
+I wanted a better way to discern if there was a difference between the simulations that I ran, so I plotted the final results (last 1000 and 100 generations) as a boxplot.
+I plot the simulation type (letters also GA) on the x-axis and the phenotype and predation on the y-axis.
+Hopefully, these boxplots will show a relative difference between the predation and phenotype between different GA.
+More simulations might change the result.
+
+```{r, boxplotting 100000}
+title="Space: Newt VS Snake Boxplot Color=Mean_predation"
+subt="25sims 100000gen newt_deaths/Newt_pop_size last 1000gen"
+y_label="Mean_predation"
+x_label="Simulation"
+
+data_subset1 <- GA_file_100[which(GA_file_100$gen>4000 & GA_file_100$gen<=5000),]
+data_subset1$group <- "A 5000"
+data_subset2 <- GA_file_100[which(GA_file_100$gen>19000 & GA_file_100$gen<=20000),]
+data_subset2$group <- "B 20000"
+data_subset3 <- GA_file_100[which(GA_file_100$gen>99000),]
+data_subset3$group <- "C 100000"
+
+data_subset<-rbind(data_subset1, data_subset2, data_subset3)
+
+ggplot(data_subset) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation), fill=group), color="black")+
+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+data_subset1 <- GA_file_100[which(GA_file_100$gen>4900 & GA_file_100$gen<=5000),]
+data_subset1$group <- "A 5000"
+data_subset2 <- GA_file_100[which(GA_file_100$gen>19900 & GA_file_100$gen<=20000),]
+data_subset2$group <- "B 20000"
+data_subset3 <- GA_file_100[which(GA_file_100$gen>99900),]
+data_subset3$group <- "C 100000"
+
+data_subset_small<-rbind(data_subset1, data_subset2, data_subset3)
+
+title="Space: Newt VS Snake Boxplot Color=Mean_predation"
+subt="25sims 100000gen newt_deaths/Newt_pop_size last 100gen"
+y_label="Mean_predation"
+x_label="Simulation"
+ggplot(data_subset_small) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation), fill=group), color="black")+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+```
+
+These figures show the predation level for the last 1000 and 100 generations (for 5000, 20000, and 100000, generation within the same simulation) on the y-axis.
+The x-axis has the simulations that I ran with different parameters.
+For every chunk of five letters the snakes GA stays the same while the newts GA decreases mutation rate and increases effect size.
+Every fifth letter the newts GA stays the same while the snakes GA decreases mutation rate and increases effect size.
+These values seem to differ by simulation, F and H are specifically larger than the others.
+The predation figures match the phenotypes in the next figure set.
+
+```{r, boxplotting the phenotype}
+
+title="Space: Newt VS Snake Boxplot Phenotype"
+subt="25sims dif last 1000gen"
+y_label="dif"
+x_label="Simulation"
+ggplot(data_subset) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif), fill=group), color="darkorchid4")+
+  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno), fill=group), color="darkred")+
+  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno), fill=group), color="steelblue")+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+title="Space: Newt VS Snake Boxplot Phenotype"
+subt="25sims dif last 100gen"
+y_label="dif"
+x_label="Simulation"
+ggplot(data_subset_small) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif), fill=group), color="darkorchid4")+
+  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno), fill=group), color="darkred")+
+  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno), fill=group), color="steelblue")+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+```
+These figures show the mean newt phenotype, mean snake phenotype, and the difference between snake and newt mean phenotype (red, blue, and purple) for the last 1000 and 100 generations on the y-axis.
+The x-axis has the simulations that I ran with different parameters with three groups (5000, 20,000, and 100,000).
+For every chunk of five letters the snakes GA stays the same while the newts GA decreases mutation rate and increases effect size.
+Every fifth letter the newts GA stays the same while the snakes GA decreases mutation rate and increases effect size.
+I see some larger flucations in the mean phenotype difference with in a simulations.
+There could be cycling
 

### 2022-03-16 graphs_newt_snakes/Correlation.Rmd
working on fixing the correlation plots, and trying to figure out if there is a problem

@@
 
+lit_5000_files_2020 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA2020_lit_", full.names=TRUE, recursive=FALSE)
+cor_5000_files_2020 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA2020_cor_", full.names=TRUE, recursive=FALSE)
+
 GA2_lit_5000_files <- list.files(path="~/Desktop/cor_GA2_5000/text_files", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
@@
 
+cor_5000_file_2020 <- read.table(cor_5000_files_2020[number], header = TRUE)
+GA_5000_file_2020 <- read.table(lit_5000_files_2020[number], header = TRUE)
+
 GA2_cor_5000_file <- read.table(GA2_cor_5000_files[number], header = TRUE)
@@
 cor_5000_file_1010$sim <-"A"
+
+GA_5000_file_2020$sim <-"A"
+cor_5000_file_2020$sim <-"A"
 
@@
 
+  lit_temp_file_6 <- read.table(lit_5000_files_2020[i], header = TRUE)
+  lit_temp_file_6$sim <-LETTERS[i]
+
   cor_temp_file <- read.table(cor_5000_files[i], header = TRUE)
@@
 
+  cor_temp_file_6 <- read.table(cor_5000_files_2020[i], header = TRUE)
+  cor_temp_file_6$sim <-LETTERS[i]
+
   GA_5000_file <- rbind(GA_5000_file, lit_temp_file)
@@
   GA_5000_file_1010 <- rbind(GA_5000_file_1010, lit_temp_file_5)
+  GA_5000_file_2020 <- rbind(GA_5000_file_2020, lit_temp_file_6)
 
@@
   cor_5000_file_1010 <- rbind(cor_5000_file_1010, cor_temp_file_5)
+  cor_5000_file_2020 <- rbind(cor_5000_file_2020, cor_temp_file_6)
 
@@
 GA_5000_file_1010$dif <- GA_5000_file_1010$Snake_mean_Pheno-GA_5000_file_1010$Newt_mean_Pheno
+GA_5000_file_2020$dif <- GA_5000_file_2020$Snake_mean_Pheno-GA_5000_file_2020$Newt_mean_Pheno
 GA2_GA_5000_file$dif <- GA2_GA_5000_file$Snake_mean_Pheno-GA2_GA_5000_file$Newt_mean_Pheno
@@
 
+```{r, correlation 5000 2020}
+
+title="Space: Newt VS Snake"
+subt="5,000 Gen Grid 20 by 20"
+y_label="Generation"
+x_label="Correlation"
+cors_by_gen(cor_5000_file_2020, title, subt, x_label, y_label)
+
+title="Phenotpe by Gen For all Sims"
+subt="GA1 5,000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA_5000_file_2020, title, subt, x_label, y_label)
+
+```
+
 ```{r, GA2 correlation}

### 2022-03-17 graphs_newt_snakes/Correlation.Rmd
I am working on fixing the cor caculation problem. I think I have a fix

@@
 I am starting to investigate what is going on in small scales in my co-evolution simulation.
-I decided to get newt and snake information and see in they were correlated in 5-5 grids.
+I decided to get newt and snake information and see in they were correlated in n-n grids.
 I collected correlated data from the GA experiments from the 5,000, 20,000, and 100,000 simulations.
-I also will examine how the correlation values change when the grid has more boxes (smaller area to compare).
+(I also tested the correlations with and without perUnitArea=T.
+It turns out when you don't have perUnitArea=T the edge of the simulation has a greater effect on the calculations turning the correlation positive.) I also will examine how the correlation values change when the grid has more boxes (smaller area to compare).
+I will specifically, test 5 by 5, 8 by 8, 10 by 10 and 20 by 20 grids
+
+#Simulation Background
+
+My simulation has newts and snakes coevolving in an arms race!
+The newts are toxic and interact with resistant snakes.
+Snakes are attacking and eating the newts, and in order to eat more newts they are becoming more resistant.
+However, if a snake eats a newt that is more toxic the snake dies.
+As snakes become more resistant, less toxic newts are being devoured, leaving only the most toxic newts.
+These toxic newts reproduce and create even more toxic newts.
+The cycle contentiously repeats.
+My simulation is run in a two-dimensional space with a x and y axis.
 
@@
 - (20, 20)
+
+Something I noticed when playing around with different variables in my simulation was that there was a large effect when I was changing interaction rate.
+So I will also look at that here.
+Special note when interaction rate is increased newts and snake may avoid each other.
 

### 2022-03-17 graphs_newt_snakes/Comparing_GA_part_2.Rmd
I made a line graph that shows how the diffence between mean phenotypes of snakes and newts goes though cycles

@@
 
+GA_file_100$mean_predation <- GA_file_100$newt_deaths/GA_file_100$Newt_pop_size
+
 data_subset1 <- GA_file_100[which(GA_file_100$gen>4000 & GA_file_100$gen<=5000),]
@@
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+title="Space: Newt VS Snake Mean_predation"
+subt="Sim A 100000gen newt_deaths/Newt_pop_size "
+y_label="Mean_predation"
+x_label="Generation"
+ggplot(GA_file_100[which(GA_file_100$sim=="A"), ]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_line(aes(x=gen, y=as.numeric(mean_predation)), color="black")+
+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
 ```
@@
 
-title="Space: Newt VS Snake Boxplot Phenotype"
+title="Space: Snake-Newt Mean Phenotype Boxplot"
 subt="25sims dif last 1000gen"
@@
 
-title="Space: Newt VS Snake Boxplot Phenotype"
+title="Space: Snake-Newt Mean Phenotype Boxplot"
 subt="25sims dif last 100gen"
@@
   #geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno), fill=group), color="steelblue")+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+title="Space: Snake-Newt Mean Phenotype"
+subt="Sim A 100000 gen newt_mean_pheno "
+y_label="Mean_predation"
+x_label="Generation"
+ggplot(GA_file_100[which(GA_file_100$sim=="A"), ]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_line(aes(x=gen, y=as.numeric(dif)), color="darkorchid4")+
+
   theme(plot.title = element_text(size=5)) +

### 2022-03-18 graphs_newt_snakes/Comparing_GA_part_2.Rmd
I finally fished writing my thoughts about the bot plots that I made in the GA2 markdown. Looks like there is some correlation btween predation and newt/snake phenotype! I also fished re-running correlation with the slim fix. Now things are more negativily correlated. I need to add it what happens when interaction rate is changed and write my thoughts, but this is a good start

@@
 
-```{r, boxplotting the phenotype}
+```{r, boxplotting the phenotype duo}
 
@@
 The predation figures match the phenotypes in the next figure set.
+I also looked at the predation for one simulation (A) for all 100,000 generations.
+It seems to have periods where it is high and other periods when it is low.
 
@@
 subt="25sims dif last 1000gen"
-y_label="dif"
+y_label="Mean Phenotype Difference"
 x_label="Simulation"
@@
 subt="25sims dif last 100gen"
-y_label="dif"
+y_label="Mean Phenotype Difference"
 x_label="Simulation"
@@
 subt="Sim A 100000 gen newt_mean_pheno "
-y_label="Mean_predation"
+y_label="Mean Phenotype Difference"
 x_label="Generation"
@@
 Every fifth letter the newts GA stays the same while the snakes GA decreases mutation rate and increases effect size.
-I see some larger flucations in the mean phenotype difference with in a simulations.
-There could be cycling
+I see some larger fluctuations in the mean phenotype difference with in a simulations.
+There could be cycling phenotypes!
+
+I was looking at the mean predation and the mean difference between the phenotypes and wondered if they were related.
+If they were related my next question would be how?
+My thought was that if snakes had a higher phenotype more newts would be preyed upon and when newts had a higher phenotype less of them would be preyed upon.
+However, I didn't know if it would be matched in the same generation or take a few generations to line up.
+So I decided to overlay the mean predation and mean dif phenotype plots.
+
+```{r, graph overlay}
+library(ggpubr)
+title="Space: Newt VS Snake Mean_predation and Mean Phenotype difference"
+y_label="Means"
+x_label="Generation"
+my_letter="U"
+subt=paste0("Sim ",my_letter, " 100000gen")
+ggplot(GA_file_100[which(GA_file_100$sim==my_letter), ]) +
+  #xlim(0, 25000)+
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_line(aes(x=gen, y=as.numeric(mean_predation)*100), color="black")+
+  geom_line(aes(x=gen, y=as.numeric(dif)), color="darkorchid4")+
+  geom_hline(yintercept=mean(as.numeric(GA_file_100[which(GA_file_100$sim==my_letter),]$mean_predation)*100), color = "red")+ # mean predation
+  geom_hline(yintercept=mean(as.numeric(GA_file_100[which(GA_file_100$sim==my_letter),]$dif)), color = "red")+ # mean phenotype dif
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+  stat_cor(aes(x=mean_predation, y=dif), method="pearson", label.y.npc="bottom", label.x.npc = "middle")
+
+#for(i in 1:25){
+  #print(cor(GA_file_100[which(GA_file_100$sim==LETTERS[i]),]$dif, GA_file_100[which(GA_file_100$sim==LETTERS[i]),]$mean_predation)
+#)
+#}
+```
+
+What I observed was not too surprising.
+When the mean phenotype difference was higher (snakes had a higher mean phenotype) often the mean predation was higher.
+When the mean phenotype difference was lower (newts had a higher phenotype) the mean predation was lower.
+I looked at the correlation values between mean phenotype difference and mean predation and saw correlations that ranged between 0.17 to 0.64, where most where between 0.3-0.4.
+I wonder how to calculate the correlation with phenotype and mean predation values from different years?
+Or if the correlation goes up or down depending on how close the newts and snake are in phenotype?
 

### 2022-03-18 graphs_newt_snakes/Correlation.Rmd
I finally fished writing my thoughts about the bot plots that I made in the GA2 markdown. Looks like there is some correlation btween predation and newt/snake phenotype! I also fished re-running correlation with the slim fix. Now things are more negativily correlated. I need to add it what happens when interaction rate is changed and write my thoughts, but this is a good start

@@
 #Reading in the names of files to cycle through them
-lit_5000_files <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA6_lit_", full.names=TRUE, recursive=FALSE)
-cor_5000_files <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA6_cor_", full.names=TRUE, recursive=FALSE)
+lit_5000_files <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA5_lit_", full.names=TRUE, recursive=FALSE)
+cor_5000_files <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA5_cor_", full.names=TRUE, recursive=FALSE)
 
-lit_20000_files <- list.files(path="~/Desktop/cor_20000/text_files", pattern="GA6_lit_", full.names=TRUE, recursive=FALSE)
-cor_20000_files <- list.files(path="~/Desktop/cor_20000/text_files", pattern="GA6_cor_", full.names=TRUE, recursive=FALSE)
+lit_5000_files_HI <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
+cor_5000_files_HI <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA55_cor_", full.names=TRUE, recursive=FALSE)
 
-lit_100000_files <- list.files(path="~/Desktop/cor_20000/text_files", pattern="GA6_lit_", full.names=TRUE, recursive=FALSE)
-cor_100000_files <- list.files(path="~/Desktop/cor_20000/text_files", pattern="GA6_cor_", full.names=TRUE, recursive=FALSE)
+lit_20000_files <- list.files(path="~/Desktop/cor_20000/cor_byUnit/text_files", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
+cor_20000_files <- list.files(path="~/Desktop/cor_20000/cor_byUnit/text_files", pattern="GA55_cor_", full.names=TRUE, recursive=FALSE)
 
-lit_5000_files_88 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA88_lit_", full.names=TRUE, recursive=FALSE)
-cor_5000_files_88 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA88_cor_", full.names=TRUE, recursive=FALSE)
+lit_100000_files <- list.files(path="~/Desktop/cor_20000/cor_byUnit/text_files", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
+cor_100000_files <- list.files(path="~/Desktop/cor_20000/cor_byUnit/text_files", pattern="GA55_cor_", full.names=TRUE, recursive=FALSE)
 
-lit_5000_files_1010 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA1010_lit_", full.names=TRUE, recursive=FALSE)
-cor_5000_files_1010 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA1010_cor_", full.names=TRUE, recursive=FALSE)
+lit_5000_files_88 <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA88_lit_", full.names=TRUE, recursive=FALSE)
+cor_5000_files_88 <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA88_cor_", full.names=TRUE, recursive=FALSE)
 
-lit_5000_files_2020 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA2020_lit_", full.names=TRUE, recursive=FALSE)
-cor_5000_files_2020 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA2020_cor_", full.names=TRUE, recursive=FALSE)
+lit_5000_files_1010 <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA1010_lit_", full.names=TRUE, recursive=FALSE)
+cor_5000_files_1010 <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA1010_cor_", full.names=TRUE, recursive=FALSE)
 
-GA2_lit_5000_files <- list.files(path="~/Desktop/cor_GA2_5000/text_files", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
-GA2_cor_5000_files <- list.files(path="~/Desktop/cor_GA2_5000/text_files", pattern="GA55_cor_", full.names=TRUE, recursive=FALSE)
+lit_5000_files_2020 <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA2020_lit_", full.names=TRUE, recursive=FALSE)
+cor_5000_files_2020 <- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA2020_cor_", full.names=TRUE, recursive=FALSE)
+
+GA2_lit_5000_files <- list.files(path="~/Desktop/cor_GA2_5000/cor_byUnit/text_files", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
+GA2_cor_5000_files <- list.files(path="~/Desktop/cor_GA2_5000/cor_byUnit/text_files", pattern="GA55_cor_", full.names=TRUE, recursive=FALSE)
 

### 2022-03-23 graphs_newt_snakes/Correlation.Rmd
I put in the wild cards for the snakemake file. I also looked more at the correlations

@@
 cors_by_gen <- function(file, title, subt, x_label, y_label){
+  print("TA = mean_newt_pheno_By_mean_snake_pheno")
+  print("TB = num_newts_By_num_snakes")
+  print("TC = sum_newt_pheno_By_num_snake")
+  print("TD = sum_snake_pheno_By_num_newt")
 
@@
   xlab(x_label) + ylab(y_label)+
-  geom_line(aes(x=as.numeric(gen), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "mean_newt_pheno_By_mean_snake_pheno"))+
-  geom_line(aes(x=as.numeric(gen), y=as.numeric(num_newts_By_num_snakes), color = "num_newts_By_num_snakes"))+
-  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_newt_pheno_By_num_snake), color = "sum_newt_pheno_By_num_snake"))+
-  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_num_newt), color = "sum_snake_pheno_By_num_newt"))+
+  geom_line(aes(x=as.numeric(gen), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "TA"))+
+  geom_line(aes(x=as.numeric(gen), y=as.numeric(num_newts_By_num_snakes), color = "TB"))+
+  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_newt_pheno_By_num_snake), color = "TC"))+
+  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_num_newt), color = "TD"))+
   theme(plot.title = element_text(size=5)) +
@@
 trends_by_gen(GA_5000_file, title, subt, x_label, y_label)
+
+title="Space: Newt VS Snake"
+subt="5,000 Gen Grid 5 by 5"
+y_label="Generation"
+x_label="Correlation"
+my_letter="A"
+subt=paste0("Sim ", subt, " ", my_letter)
+cors_by_gen(cor_5000_file[which(cor_5000_file$sim==my_letter), ], title, subt, x_label, y_label)
 

### 2022-03-24 Snakemake/snake_newt_gv_ sm.py
I am still working on making the snakemake file names correct. I am also saving a version of the msprime and eventually slim 1on1 cost sim that will work with snakemake

@@ -1,0 +1,239 @@
+import pyslim
+import tskit
+import msprime
+import numpy as np
+import os
+import sys
+from sys import argv
+# import util
+
+
+sequence_length = 100000000
+'''
+datadir = "newt_snake/data"
+snake_mu_rate = 1e-10
+newt_mu_rate = 1e-10  # does this need to be 50 times more than the snake?
+snake_mu_effect_sd = 0.05
+newt_mu_effect_sd = 0.01
+name_of_file = "both_newt_snake_annotated.init.trees"
+
+'''
+mytag="no_tag"
+snake_mu_rate = float(sys.argv[1])
+newt_mu_rate = float(sys.argv[2])  # does this need to be 50 times more than the snake?
+snake_mu_effect_sd = float(sys.argv[3])
+newt_mu_effect_sd = float(sys.argv[4])
+datadir = sys.argv[5]
+mytag = sys.argv[6]
+myrep = sys.argv[7]
+myseed = sys.argv[8]
+
+name_of_file = mytag + "_trees_su_" + str(snake_mu_rate) + "_nu_" + str(newt_mu_rate) + \
+    "_sue_" + str(snake_mu_effect_sd) + "_nue_" + str(newt_mu_effect_sd) + \
+    _rep_ + str(myrep) +"_seed_" + str(myseed) + ".init.trees"
+print(name_of_file)
+
+
+def add_mutations(ts, mut_type, mu_rate, effect_sd, next_id=0):
+    # s_fn draws the selection coefficient
+    # need to assign metadata to be able to put the mutations in
+    mut_model = msprime.SLiMMutationModel(type=mut_type, next_id=next_id)
+    mts = msprime.sim_mutations(
+        ts,
+        mu_rate,
+        model=mut_model,
+    )
+    print(f"The tree sequence now has {mts.num_mutations} mutations, at "
+          f"{mts.num_sites} distinct sites.")
+    tables = mts.tables
+    tables.mutations.clear()
+    mut_map = {}
+    for m in mts.mutations():
+        md_list = m.metadata["mutation_list"]
+        slim_ids = m.derived_state.split(",")
+        assert len(slim_ids) == len(md_list)
+        for sid, md in zip(slim_ids, md_list):
+            if sid not in mut_map:
+                mut_map[sid] = np.random.normal(loc=0.0, scale=effect_sd)
+            md["selection_coeff"] = mut_map[sid]
+        tables.mutations.add_row(
+            site=m.site,
[…]

### 2022-03-25 Snakemake/snake_newt_gv_ sm.py
I am getting closer to having the snakemake file work. not there yet...

@@ -30,7 +30,7 @@ myseed = sys.argv[8]
 
 name_of_file = mytag + "_trees_su_" + str(snake_mu_rate) + "_nu_" + str(newt_mu_rate) + \
     "_sue_" + str(snake_mu_effect_sd) + "_nue_" + str(newt_mu_effect_sd) + \
-    _rep_ + str(myrep) +"_seed_" + str(myseed) + ".init.trees"
+    "_rep_" + str(myrep) +"_SLIMseed_" + str(myseed) + ".init.trees"
 print(name_of_file)
 
 

### 2022-03-30 graphs_newt_snakes/Correlation.Rmd
working on writing about coevoultion correlations

--- 2022-03-18 graphs_newt_snakes/Correlation.Rmd
@@
 (I also tested the correlations with and without perUnitArea=T.
-It turns out when you don't have perUnitArea=T the edge of the simulation has a greater effect on the calculations turning the correlation positive.) I also will examine how the correlation values change when the grid has more boxes (smaller area to compare).
+It turns out when you don't have perUnitArea=T the edge of the simulation has a greater effect on the calculations turning the correlations positive.) I also will examine how the correlation values change when the grid has more boxes (smaller area to compare).
 I will specifically, test 5 by 5, 8 by 8, 10 by 10 and 20 by 20 grids
 
-#Simulation Background
+# Simulation Background
 
@@
 
-GA1 experiment values
+GA1 experiment values:
 
@@
 
-GA2 experiment values
+GA2 experiment values:
 
@@
 collected info:
-	mean_newt_pheno_By_mean_snake_pheno = cor(c(newt_mean_pheno), c(snake_mean_pheno));
-	num_newts_By_num_snakes = cor(c(newt_sum_ind), c(snake_sum_ind));
-	sum_newt_pheno_By_num_snake = cor(c(newt_sum_pheno), c(snake_sum_ind));
-	sum_snake_pheno_By_num_newt = cor(c(snake_sum_pheno), c(newt_sum_ind));
-	sum_newt_pheno_By_num_newt = cor(c(newt_sum_pheno), c(newt_sum_ind));
-	sum_snake_pheno_By_snake_newt = cor(c(snake_sum_pheno), c(snake_sum_ind));
+
+- mean_newt_pheno_By_mean_snake_pheno = cor(c(newt_mean_pheno), c(snake_mean_pheno));
+- num_newts_By_num_snakes = cor(c(newt_sum_ind), c(snake_sum_ind));
+- sum_newt_pheno_By_num_snake = cor(c(newt_sum_pheno), c(snake_sum_ind));
+- sum_snake_pheno_By_num_newt = cor(c(snake_sum_pheno), c(newt_sum_ind));
+- sum_newt_pheno_By_num_newt = cor(c(newt_sum_pheno), c(newt_sum_ind));
+- sum_snake_pheno_By_snake_newt = cor(c(snake_sum_pheno), c(snake_sum_ind));
 
@@
 
+## My Prediction
+
+Before running this experiment, I thought about the possible outcomes.
+I am looking at relationships between species phenotypes, population size, and resistance and toxicity between different sized regions.
+I predicted that the number of newts and the amount of toxicity & the number of snakes and the amount of resistance will be very correlated (green line).
+I also predicted that when newts and snakes are co-evolving then their phenotypes would be positively correlated (blue line).
+I think that the number of newts will be negativity correlated with the population size of snakes and vice-versa (purple line).
+For example, if there are more snakes in a specific region (and the amount of snakes are increasing) then there wold be less newts (and the amount of newts would be decreasing).
+I also predict that the amount of toxin in a region will be negatively correlated with the population size of snakes & that resistance will also be negatively correlated with the population size of newts (red line).
+For example, if the newts on a specific region become more toxic (increasing the total amount of toxicity) the number of snakes will decrease (as they try to eat a more toxic newt they die).
+Below is a graphical representation of my predictions.
+
+```{r, cor prediction}
+
+timeline = 0:100
+
+five_six = c(0, .2, .4, .7)
+five_six = c(five_six, rep.int(1, length(timeline)-length(five_six)))
+three_four = c(rep(0,9), -.03, -.1, rep(-.2,5), rep(-.3,4), rep(-.4,3), rep(-.5,3), rep(-.6,2))
+three_four = c(three_four, rep(-.7, length(timeline)-length(three_four)))
+two = c(rep(0,13),rep(-.05,9), rep(-.1,7), rep(-.2,5), rep(-.3,3))
+two = c(two, rep(-.4, length(timeline)-length(two)))
+one = c(rep(0,8), rep(0.2,5), rep(0.3,4), rep(0.4,9), rep(0.5,8), rep(0.6,7))
+one = c(one, rep(0.7, length(timeline)-length(one)))
+
+plot(timeline, one, type="l", col="blue", ylim=c(-1, 1),)
+lines(timeline, two, col="purple")
+lines(timeline, three_four, col="red")
+lines(timeline, five_six, col="green")
+legend(35, 0.5, legend=c("newt by snake pheno", "#newts by #snakes", "toxin by #snakes & resistance by #newts", "#newts by toxin & #snakes by resitance"), col=c("blue","purple", "red", "green"), lty=1, cex=0.8)
+```
+
+After, plotting the results number of newts by the amount toxin and the number of snakes by the amount of resistance was very close to 1. It is not plotted in my main results.
+
+## Data collection
+
+First, I process the data that I collected from the cost 1on1 slim simulations.
+There are 16 different simulations in the GA1 experiment and 25 different simulations in the GA2 experiment (I will refer to these simulations as groups).
+Here I will output the groups simulation letter along with the mutation rate and effect size of both newts and snakes.
+I collected data from 8 different simulations groups testing what happens as the length of the simulation increases as and testing how the size of the measured area effects the correlation calculations.
+
 ```{r, Cor data gather}
@@
 
-lit_100000_files <- list.files(path="~/Desktop/cor_20000/cor_byUnit/text_files", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
-cor_100000_files <- list.files(path="~/Desktop/cor_20000/cor_byUnit/text_files", pattern="GA55_cor_", full.names=TRUE, recursive=FALSE)
+lit_100000_files <- list.files(path="~/Desktop/cor_100000/cor_byUnit/text_files", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
+cor_100000_files <- list.files(path="~/Desktop/cor_100000/cor_byUnit/text_files", pattern="GA55_cor_", full.names=TRUE, recursive=FALSE)
 
@@
 cors_by_gen <- function(file, title, subt, x_label, y_label){
+  print("CA = mean_newt_pheno_By_mean_snake_pheno")
+  print("CB = num_newts_By_num_snakes")
+  print("CC = sum_newt_pheno_By_num_snake")
+  print("CD = sum_snake_pheno_By_num_newt")
 
@@
   xlab(x_label) + ylab(y_label)+
-  geom_line(aes(x=as.numeric(gen), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "mean_newt_pheno_By_mean_snake_pheno"))+
-  geom_line(aes(x=as.numeric(gen), y=as.numeric(num_newts_By_num_snakes), color = "num_newts_By_num_snakes"))+
-  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_newt_pheno_By_num_snake), color = "sum_newt_pheno_By_num_snake"))+
-  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_num_newt), color = "sum_snake_pheno_By_num_newt"))+
+  geom_line(aes(x=as.numeric(gen), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_line(aes(x=as.numeric(gen), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
   theme(plot.title = element_text(size=5)) +
@@
 
+## Correlation Caculations for 5 by 5 grid
+
+Correlation values were collected every 10th generation with the exception of the 1st generation (calculations started gen 2).
+The first figure presented is the correlation calculations for simulation A up to 5,000 generations with a 5 by 5 grid.
+The red line represents calculation A which is the correlation between mean newt phenotype and mean snake phenotype (I predict this would be positive).
+The green line (CB) is the correlation between the number of newts and the number of snakes (I predicted this would be negative).
+The blue line is (CC) and represents the correlation between the sum of toxicity and the number of snakes.
+The purple line (CD) is the correlation between the amount of resistance and the number of newt (predicted to be negative).
+The second figure shows the correlation calculations for all 16 simulations.
+The third figure shows the mean newt phenotype (red) the snake mean phenotype (blue) and the difference between the snake mean phenotype and the newt mean phenotype (black).
+I want to use the third figure which is a whole population calculation to the second figure which has a more localized calculation.
+
 ```{r, lest see that correlation}
@@
 subt="5,000 Gen Grid 5 by 5"
-y_label="Generation"
-x_label="Correlation"
+x_label="Generation"
+y_label="Correlation"
+my_letter="A"
+subt=paste0("Sim ", my_letter, " ", subt)
+cors_by_gen(cor_5000_file[which(cor_5000_file$sim==my_letter), ], title, subt, x_label, y_label)
+
+title="Space: Newt VS Snake"
+subt="5,000 Gen Grid 5 by 5"
+x_label="Generation"
+y_label="Correlation"
 cors_by_gen(cor_5000_file, title, subt, x_label, y_label)
@@
 y_label="Phenotype"
+x_label="Generation"
 title="Phenotpe by Gen For all Sims"
@@
 ```
+
+loooking at the figures
+
 ```{r, cor 5000 zooom}
@@
 subt="5,000 Gen Grid 5 by 5"
-y_label="Generation"
-x_label="Correlation"
+x_label="Generation"
+y_label="Correlation"
 cors_by_gen(cor_5000_file[ which(cor_5000_file$gen<200),], title, subt, x_label, y_label)
@@
 subt="20,000 Gen Grid 5 by 5"
-y_label="Generation"
-x_label="Correlation"
+x_label="Generation"
+y_label="Correlation"
 cors_by_gen(cor_20000_file, title, subt, x_label, y_label)
@@
 subt="100,000 Gen Grid 5 by 5"
-y_label="Generation"
-x_label="Correlation"
+x_label="Generation"
+y_label="Correlation"
 cors_by_gen(cor_100000_file, title, subt, x_label, y_label)
@@
 subt="5,000 Gen Grid 8 by 8"
-y_label="Generation"
-x_label="Correlation"
+x_label="Generation"
+y_label="Correlation"
 cors_by_gen(cor_5000_file_88, title, subt, x_label, y_label)
@@
 subt="5,000 Gen Grid 10 by 10"
-y_label="Generation"
-x_label="Correlation"
+x_label="Generation"
+y_label="Correlation"
 cors_by_gen(cor_5000_file_1010, title, subt, x_label, y_label)
@@
 subt="5,000 Gen Grid 20 by 20"
-y_label="Generation"
-x_label="Correlation"
+x_label="Generation"
+y_label="Correlation"
 cors_by_gen(cor_5000_file_2020, title, subt, x_label, y_label)
@@
 
+## GA2 Simulations
+
+```{r ga2 values}
+
+for(i in seq(1, length(GA2_lit_5000_files), 1)){
+  myletter <- LETTERS[i]
+
+  snake_mu_rate <- unlist(str_split(unlist(str_split(GA2_lit_5000_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  newt_mu_rate <- unlist(str_split(unlist(str_split(GA2_lit_5000_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_lit_5000_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_lit_5000_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  print(paste0("Simulation ", LETTERS[i],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")" ))
+  }
+
+```
+
 ```{r, GA2 correlation}
@@
 subt="5,000 Gen Grid 5 by 5"
-y_label="Generation"
-x_label="Correlation"
+x_label="Generation"
+y_label="Correlation"
 cors_by_gen(GA2_cor_5000_file, title, subt, x_label, y_label)
@@
 subt="5,000 Gen Grid 5 by 5"
-y_label="Generation"
-x_label="Correlation"
+x_label="Generation"
+y_label="Correlation"
 cors_by_gen(GA2_cor_5000_file[ which(GA2_cor_5000_file$gen<200),], title, subt, x_label, y_label)

### 2022-04-02 graphs_newt_snakes/Correlation.Rmd
I am writing more about what I see in my cor study. I also decided to add GA2 30,000 to the study because the londer version of that simulation alows the other speciece to catch up and creates some interesting results?

@@
 
+GA2_lit_30000_files <- list.files(path="~/Desktop/cor_GA2_30000", pattern="GA55_lit_", full.names=TRUE, recursive=FALSE)
+GA2_cor_30000_files <- list.files(path="~/Desktop/cor_GA2_30000/", pattern="GA55_cor_", full.names=TRUE, recursive=FALSE)
+
 #files <- list.files(path="~/Desktop/GA_lt/doover/text_files", pattern="GA_lit_", full.names=TRUE, recursive=FALSE)
@@
 
+GA2_cor_30000_file <- read.table(GA2_cor_30000_files[number], header = TRUE)
+GA2_GA_30000_file <- read.table(GA2_lit_30000_files[number], header = TRUE)
+
 GA_5000_file$sim <-"A"
@@
 
+GA2_GA_30000_file$sim <-"A"
+GA2_cor_30000_file$sim <-"A"
+
 #Cycle through the different simulations to make one file. Not recommended for large files, but right now mine are small
@@
 
+  GA2_lit_30_temp_file <- read.table(GA2_lit_30000_files[i], header = TRUE)
+  GA2_lit_30_temp_file$sim <-LETTERS[i]
+  GA2_cor_30_temp_file <- read.table(GA2_cor_30000_files[i], header = TRUE)
+  GA2_cor_30_temp_file$sim <-LETTERS[i]
+
   GA2_GA_5000_file <- rbind(GA2_GA_5000_file, GA2_lit_temp_file)
   GA2_cor_5000_file <- rbind(GA2_cor_5000_file, GA2_cor_temp_file)
+
+  GA2_GA_30000_file <- rbind(GA2_GA_30000_file, GA2_lit_30_temp_file)
+  GA2_cor_30000_file <- rbind(GA2_cor_30000_file, GA2_cor_30_temp_file)
 
@@
 GA2_GA_5000_file$dif <- GA2_GA_5000_file$Snake_mean_Pheno-GA2_GA_5000_file$Newt_mean_Pheno
+GA2_GA_30000_file$dif <- GA2_GA_30000_file$Snake_mean_Pheno-GA2_GA_30000_file$Newt_mean_Pheno
 ```
@@
 
-loooking at the figures
+Looking at the figures, can I really tell what is going on?
+
+In the first figure of the correlation calculations in simulation A my answer would be "no".
+There are some concerns that I have.
+My first concern is why is CA starting out a **perfect** correlation.
+The second concern is the variability between each measurement.
+The points seem to jump around a lot, sometime being negative to being positive in 10 or so generations.
+These correlation values look like they are running through a cycle.
+I do not know if this is concerning but the blue, green, and purple lines are practically on top of each other.
+Is this due to both newts and snakes having the same GA or is the amount of newts (population size or phenotype) have similar trends to snakes?
+
+In the second figure my answer would be "maybe".
+There is definitely a difference between the correlation values between these simulations, seen especially in the red line.
+Sometimes the red line is very high (correlation of 1) and sometimes it is lower or sometimes negative.
+For the most part the green, blue, and purple lines are close to each other.
+However, these three lines do differ in some of the simulations particularly when one of the species has a larger effect size.
+
+In the third figure I would say there is something going on, but is it coevolution "IDK".
+I have plotted this figure before and talked about its implications in Comparing GA.
+But now I want to combine what we see here with the figure above it.
+Let's first look at what the correlation lines are doing when the mean newt phenotypes of newts and snakes are similar/close or cross (A, B, D, E, F, G, M, N).
+In about half of these there is a high correlation between newt and snake phenotype, but in the other half the correlation is low or a bit negative.
+If we look at the correlations for the when the mean newt and snake phenotypes are further apart (C, H, I, J, K, L, O, P) the correlation between mean newt phenotype and mean snake phenotype is smaller.
+However, there might be an increase in the mean newt and mean snake correlation when the newt phenotype is (significantly) higher than the snake phenotype (C, O, P).
+I wonder if there is any avoiding occurring?
+Simulation N is a particular interesting case to look at.
+
+#### Zooming in on Correlation Caculations for 5 by 5 grid
+
+This subsection is looking at the above figures, but at a zoomed in section.
+I only look at the first 200 generations.
+The goal is to see where the correlation calculations begin and see how they change on a smaller, easier to see time scale.
 
@@
 y_label="Correlation"
-cors_by_gen(cor_5000_file[ which(cor_5000_file$gen<200),], title, subt, x_label, y_label)
+cors_by_gen(cor_5000_file[ which(cor_5000_file$gen<201),], title, subt, x_label, y_label)
 
@@
 y_label="Phenotype"
-trends_by_gen(GA_5000_file[ which(GA_5000_file$gen<200),], title, subt, x_label, y_label)
+trends_by_gen(GA_5000_file[ which(GA_5000_file$gen<201),], title, subt, x_label, y_label)
 
 ```
+
+Here the four correlations are calculated and collected every 10 generations.
+The mean phenotype of newts and snakes are collected every 20 generations.
+The difference in collect times might lead to more smoothness in one plot vs the other (in this case I don't think that is happening).
+In the first graph I noticed that the red line (correlation of mean newt phenotype with mean snake phenotype) starts out very positively correlated in some of the simulations.
+Is this high positive correlation normal or random?
+When looking at both figures its weird how differently the correlation look when it seems like the mean phenotype of newts and snakes are unchanging.
+By looking at the correlation plot I wonder what is occurring to create some positive and negative correlations especially for CB, CC, and CD?
+Because nothing seems dramatic from the total population phenotype mean.
+What other information might be useful?
 
@@
 y_label="Correlation"
-cors_by_gen(GA2_cor_5000_file[ which(GA2_cor_5000_file$gen<200),], title, subt, x_label, y_label)
+cors_by_gen(GA2_cor_5000_file[ which(GA2_cor_5000_file$gen<210),], title, subt, x_label, y_label)
 
@@
 y_label="Phenotype"
-trends_by_gen(GA2_GA_5000_file[ which(GA2_GA_5000_file$gen<200),], title, subt, x_label, y_label)
+trends_by_gen(GA2_GA_5000_file[ which(GA2_GA_5000_file$gen<210),], title, subt, x_label, y_label)
 
 ```
+
+```{r, GA2 30000 correlation}
+
+title="GA2 Space: Newt VS Snake"
+subt="30,000 Gen Grid 5 by 5"
+x_label="Generation"
+y_label="Correlation"
+cors_by_gen(GA2_cor_30000_file, title, subt, x_label, y_label)
+
+title="Phenotpe by Gen For all Sims"
+subt="GA2 30,000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA2_GA_30000_file, title, subt, x_label, y_label)
+
+```
+
+```{r, cor 30000 GA2 mid zooom}
+
+title="GA2 ZOOM Space: Newt VS Snake"
+subt="30,000 Gen Grid 5 by 5"
+x_label="Generation"
+y_label="Correlation"
+cors_by_gen(GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=10000 & GA2_cor_30000_file$gen<11010),], title, subt, x_label, y_label)
+
+title="ZOOM Phenotpe by Gen For all Sims"
+subt="GA2 30,000 Gen"
+y_label="Phenotype"
+trends_by_gen(GA2_GA_30000_file[ which(GA2_GA_30000_file$gen>=10000 & GA2_GA_30000_file$gen<11010),], title, subt, x_label, y_label)
+
+```

### 2022-04-05 graphs_newt_snakes/Correlation.Rmd
I am writng more about the correlations. I am getting close to the last section

@@
 }
+
+boxplot_cors_by_gen <- function(file, subt, x_label, y_label){
+
+  plot <- ggplot(file) +
+  ylim(-1.1, 1.1)+
+  ggtitle(subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+#boxplot_cors_by_gen(cor_5000_file[which(cor_5000_file$gen>4000),], subt, x_label, y_label)
+
 trends_by_gen <- function(file, title, subt, x_label, y_label){
@@
 
+## Running the experiment for longer
+
+The next section I run the GA1 simulations for 20,000 generations and 100,000 generations. To see if there are any major correlation changes that might occur when running my simulation for longer.
+
 ```{r, correlation 20000}
@@
 ```
+
+The 20,000 generation plots looks very similar to the 5,000 generation plots. It does not look like anything dramatically changes.
 
@@
 
+Wow, it is extremely hard to tell what is going on when you plot all 100,000 generations at the same time!
+Something is going on that differentiates these simulations from each other.
+Some of the simulations have a lower CA or higher CD.
+Overall, it does not look like increasing the amount of generations has an effect of the correlation values (after a certain amount of generations nothing really changes, but maybe it cycles).
+It is difficult to determine what is going on in the simulation by looking at correlations alone.
+Take F and H from the 100,000  generation for an example.
+Both F and H have a higher CA throughout the simulation CB, CC, and CD are all about the same, but the average mean phenotype for the simulation looks very different.
+Maybe looking at the variance between different simulations peaks and valleys will give me a better idea of what is happening?
+
+## Camparing Corrilations at Different Simulation Lengths
+
+Here I am going to condense the data down to 1 box plot per calculation per simulation over the last 1,000 generations (of the 5,000, 20,000, and 100,000 generation simulations).
+This will hopefully be an easier plot to read and compare results between different simulation lengths.
+There will be three plots the first plot (top left) will be the results for the last 1,000 generations of the 5,000 generation simulation.
+The second plot (top right) will be the results for the last 1,000 generation of the 20,000 generation plot.
+The third plot (bottom left) will be the results of the last 1,000 generations of the 100,000 generation simulation.
+All plots will show the 16 genetic architecture experiments (in this case they are unlabeled due to space, but each starts with A and continues left to right then down to the next line).
+The x-axis and y-axis are also unlabeled (due to space), but represents which correlation was calculated and its value respectively.
+The four correlation calculations see printed below:
+
+```{r, boxplotting 5000}
+  print("CA = mean_newt_pheno_By_mean_snake_pheno")
+  print("CB = num_newts_By_num_snakes")
+  print("CC = sum_newt_pheno_By_num_snake")
+  print("CD = sum_snake_pheno_By_num_newt")
+
+title="Space: Newt VS Snake"
+subt="16sims last 1000Gen 5000, Grid 5 by 5"
+x_label="Type"
+y_label="Correlation"
+G1<-boxplot_cors_by_gen(cor_5000_file[which(cor_5000_file$gen>4000),], subt, x_label, y_label)
+title="Space: Newt VS Snake"
+subt="16sims last 1000Gen 20000, Grid 5 by 5"
+x_label="Type"
+y_label="Correlation"
+G2<-boxplot_cors_by_gen(cor_20000_file[which(cor_20000_file$gen>19000),], subt, x_label, y_label)
+title="Space: Newt VS Snake"
+subt="16sims last 1000Gen 100000, Grid 5 by 5"
+x_label="Type"
+y_label="Correlation"
+G3<-boxplot_cors_by_gen(cor_100000_file[which(cor_100000_file$gen>99000),], subt, x_label, y_label)
+
+print("Difference in simulation length")
+grid.arrange(G1, G2, G3, nrow=2)
+
+```
+
+The box plots differ between each of the 16 simulations, but are relatively similar between the different simulation lengths (when only looking at 1,000 generations).
+I was surprised that the box plots had similar lengths between the different simulation times.
+The correlation between newt phenotype and snake phenotype (CA red) is mostly positive, but can be negative or zero.
+The correlation between number of newts (newt density) and number of snakes (snake density) (CB green), the correlation between the amount of toxin and the number of snakes (CC blue), and the correlation between the amount of resistance and the number of snakes (CD purple) is mostly negative.
+These values are negative and do not get past -0.5.
+
+## Corrilation Values as the Number of Boxes Increases
+
+I re-ran the 5,000 generation simulation, but changed the grid size by decreasing the area where the correlation could be calculated.
+In this case I tried to divide an 35 by 35 area by 8, 10, and 20 boxes.
+As the number of boxes increase the area in which things may be calculated decreases.
+The goal is to get close to finding a good amount of area to calculation local adaptation, while not being too large or too small.
+I will compare the results of the following simulations.
+Note: I ran 16 slim simulations 4 times (setting the grid at 5, 8, 10, 20) with the same msprime files
+
 ```{r, correlation 5000 88}
@@
 ```
+
+When I increased the number of grids to 8 by 8, the correlation values got lower.
+The different correlation calculations that I made were less correlated and do not fluctuate between measurements as much as they did when the grid was 5 by 5.
 
@@
 
+When I increased the number of grids to 10 by 10, the correlation values looked very similar to the 8 by 8 grid.
+The 10 by 10 grid had less correlated vales when compared to the 5 by 5 grid.
+These  correlation calculations were less correlated and do not fluctuate between measurements as much as they did when the grid was 5 by 5.
+It is also possible that the 10 by 10 grid was just a little bit less correlated than the 8 by 8, but it is a bit difficult to tell.
+
 ```{r, correlation 5000 2020}
@@
 ```
+When I change the grid to a 20 by 20 everything was negatively correlated and the correlations did not jump around.
+
+## Camparing Corrilations at Different Grid
+
+Similar to what I did before, I made box plots of the last 1,000 generation of the 5,000 generation simulations.
+Here, I will visually compare how changing the amount of area where the correlation calculations took place effect the correlation output.
+In the top left will be the box plots of the correlations from the 5 by 5 grid to the right is the 8 by 8 grid.
+Under the 5 by 5 grind will be the 10 by 10 grid and next to it will be the 20 by 20 grid box plots.
+To save space and see the results there are no labels on the x-axis (correlation calculation), the y-axis (correlation values), or the simulation letter (A starts on the top left and continues right and then to the next line).
+The four correlation calculations are printed below:
+
+```{r, boxplotting 5000 dif size}
+  print("CA = mean_newt_pheno_By_mean_snake_pheno")
+  print("CB = num_newts_By_num_snakes")
+  print("CC = sum_newt_pheno_By_num_snake")
+  print("CD = sum_snake_pheno_By_num_newt")
+
+title="Space: Newt VS Snake"
+subt="16sims last 1000Gen 5000, Grid 8 by 8"
+x_label="Type"
+y_label="Correlation"
+G4<-boxplot_cors_by_gen(cor_5000_file_88[which(cor_5000_file_88$gen>4000),], subt, x_label, y_label)
+
+title="Space: Newt VS Snake"
+subt="16sims last 1000Gen 5000, Grid 10 by 10"
+x_label="Type"
+y_label="Correlation"
+G5<-boxplot_cors_by_gen(cor_5000_file_1010[which(cor_5000_file_1010$gen>4000),], subt, x_label, y_label)
+
+title="Space: Newt VS Snake"
+subt="16sims last 1000Gen 5000, Grid 20 by 20"
+x_label="Type"
+y_label="Correlation"
+G6<-boxplot_cors_by_gen(cor_5000_file_2020[which(cor_5000_file_2020$gen>4000),], subt, x_label, y_label)
+
+print("Difference in amount of grids")
+grid.arrange(G1, G4, G5, G6, nrow=2)
+
+```
+
+At the number or grids increases the area in which individuals (phenotype or count) shrinks.
+This area shrinkage can lead to area where few individuals are which could have an effect on the correlation calculations.
+By decreasing the size of the measured area the variance between data collect points decreases (easily spotted with the red box plot newt phenotype by snake phenotype).
+When I increased the grid number there was less correlation both in the positive and negative directions.
+When the grid value was very high (20) everything became centered around 0.
+What is the best method for choosing the grid size?
+Is the correlation between the things I measure proof of co-evolution (especially when some of the values started of at 1)?
 
 ## GA2 Simulations
+
+Now, I am going to look at the correlations that I calculated for the GA2 experiment.
+In this experiment the variance for mutations is equal between the species (mu*(effect_size^2)).
+Below, is the simulation letter and its associated mutation rate and effect size.
 

### 2022-04-07 graphs_newt_snakes/Correlation.Rmd
I finally got all of my graphs made and writen about for the correlation experiment. That took awhile to do

@@
 
-```{r, Cor data gather}
+```{r, Cor data gather, cache=TRUE}
 #Reading in the names of files to cycle through them
@@
 
-```{r, reusable figures, results='hide', message=FALSE, warning=FALSE}
+```{r, reusable figures, results='hide', message=FALSE, warning=FALSE, cache=TRUE}
 
@@
 
+boxplot_cors_by_type_gen <- function(file, subt, x_label, y_label, mycolor){
+
+  plot <- ggplot(file) +
+  ylim(-1.1, 1.1)+
+  ggtitle(subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor("1"), y=as.numeric(C1)), color = mycolor)+
+  geom_boxplot(aes(x=factor("2"), y=as.numeric(C2)), color = mycolor)+
+  geom_boxplot(aes(x=factor("3"), y=as.numeric(C3)), color = mycolor)+
+  geom_boxplot(aes(x=factor("4"), y=as.numeric(C4)), color = mycolor)+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
 trends_by_gen <- function(file, title, subt, x_label, y_label){
@@
 
-```{r, lest see that correlation}
+```{r, lest see that correlation, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, cor 5000 zooom}
+```{r, cor 5000 zooom, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, correlation 20000}
+```{r, correlation 20000, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, correlation 100000}
+```{r, correlation 100000, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, boxplotting 5000}
+```{r, boxplotting 5000, fig.height = 8, fig.width = 8, cache=TRUE}
   print("CA = mean_newt_pheno_By_mean_snake_pheno")
@@
 
-print("Difference in simulation length")
-grid.arrange(G1, G2, G3, nrow=2)
+grid.arrange(G1, G2, G3, nrow=2, top=textGrob("Last 1,000 Gens for Different Simulation Lengths",gp=gpar(fontsize=16,font=3)))
 
@@
 
-```{r, correlation 5000 88}
+```{r, correlation 5000 88, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, correlation 5000 1010}
+```{r, correlation 5000 1010, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, correlation 5000 2020}
+```{r, correlation 5000 2020, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, boxplotting 5000 dif size}
+```{r, boxplotting 5000 dif size, fig.height = 8, fig.width = 8, cache=TRUE}
   print("CA = mean_newt_pheno_By_mean_snake_pheno")
@@
 
-print("Difference in amount of grids")
-grid.arrange(G1, G4, G5, G6, nrow=2)
+grid.arrange(G1, G4, G5, G6, nrow=2, top=textGrob("1000 Gen at Differnt Time Points",gp=gpar(fontsize=16,font=3)))
 
@@
 
-```{r ga2 values}
+```{r ga2 values, cache=TRUE}
 
@@
 
-```{r, GA2 correlation}
+The next section contains the results of the correlation calculations and mean phenotypes in the GA2 experiment.
+The first figure shows 4 correlation results, which were collected with a 5 by 5 grid.
+The correlation between mean newt phenotype and mean snake phenotype is the red line (CA).
+The correlation between the number of newts and the number of snakes is the green line (CB).
+The correlation between the sum of toxicity and the number of snakes is the blue line (CC).
+The correlation between the amount of resistance and the number of newt is the purple line (CD).
+This figure shows all 25 simulations in this set.
+The second figure shows the mean newt phenotype (red) the snake mean phenotype (blue) and the difference between the snake mean phenotype and the newt mean phenotype (black) for all 25 simulations.
+
+```{r, GA2 correlation, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, cor 5000 GA2 zooom}
+The first figure shows the 4 correlation calculations collected every 10 generations for a 5,000 simulation.
+The first thing that I noticed in the first figure was a diminished CA correlation value.
+I did notice that CA values got a bit higher when the mean newt and snake values on the second plot intersected.
+These results were similar to the results seen in the GA1 experiment, with the exception of lower CA values.
+CB, CC, CD are all negative and generally fluctuate between 0 and -0.5.
+CA has a larger positive fluctuation between 0.0 and 1.
+The second figure shows the interaction of the mean snake and mean newt phenotypes.
+In this figure the phenotypes are often close to each other.
+I looked at both figures and wondered if maybe 5,000 generations was not enough time for a co-evolutionary relationship to form or stabilize.
+I also wondered why CA was lower (and did not start at 1) in this set of simulations.
+
+#### Zooming in on Correlation Caculations for 5 by 5 grid GA2
+
+Now, I am going to look at the zoomed in section of the GA2 5,000 generation simulations.
+I plotted the first 200 generations of my simulation and looked at the four correlation calculations and the newt & snake mean phenotype.
+Mostly, I want to look at where the correlations start off at and see how they immediately change.
+I want to compare the mean newt and snake phenotypes to the correlations.
+
+```{r, cor 5000 GA2 zooom, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, GA2 30000 correlation}
+The first thing I looked at was the second figure.
+The blue and red lines are not close together and it doesn't look like there a lot of movement in most of the simulations.
+Some of the red and blue lines decrease, and very few of the lines seem to increase.
+However, when looking at the correlation plots a lot of things are happening.
+There are some cases where things are falling and in other simulations things are going up.
+The blue, green, and purple generally start near 0.
+The red line usually starts off positive then decreases then goes back up.
+Its kind of weird how all four correlation lines can cluster at a certain time, but the mean phenotypes don't seem to change.
+I looked back at the zoomed in version of the GA1 experiment and found that the red line is a lot further away from the other lines in this experiment set.
+There was more of a trend in the GA1 experiment than in the GA2 experiment.
+Maybe it takes more time for co-evolution to occur when the variation between newts and snakes are the same.
+
+## 30,000 Generation Results
+
+In this section, I re-run the 25 GA2 simulations and increased the amount of generations to 30,000 (after looking at the 100,000 gen results).
+Here, I will again look at the four correlation calculations (CA, CB, CC, CD) and the mean newt and snake phenotypes.
+I hope to see more interaction between newt and snake mean phenotypes and a stabilization in the correlation calculations.
+
+```{r, GA2 30000 correlation, fig.height = 8, fig.width = 10, cache=TRUE}
 
@@
 
-```{r, cor 30000 GA2 mid zooom}
+After looking at the results, I noticed that the the red line (newt and snake phenotype correlation) generally stays high after a certain amount of generations.
+It is really difficult to see how the purple, blue, and green correlation lines interact.
+It seems like they are mostly overlap each other.
+It looks like these three correlations might become a bit more negative as the number of generations increase (at lease in some of the simulations).
+When looking at the second figure the mean newt and mean snake phenotype usually start out at with one species phenotype being higher and as the number of generations increase both phenotypes increase and eventually cross.
+There were four simulation where there was no crossing between mean newt and snake phenotype (B, F, H, Y).
+When snake mean phenotype was higher the correlation between newt and snake phenotype was diminished (F, H), but when newt mean phenotype was higher the correlation was a bit higher (B, Y).
 
-title="GA2 ZOOM Space: Newt VS Snake"
+#### Zooming in on 1,000 gen Period of Correlation Caculations for 5 by 5 grid
+
+From the above section I wanted to zoom in on a 1,000 generation section where newt and snake phenotypes seem to be increasing. I choose to look at a section between 10,000 and 11,000 generations.
+
+```{r, cor 30000 GA2 mid zooom, fig.height = 8, fig.width = 10, cache=TRUE}
+
+title="GA2 midZOOM Space: Newt VS Snake"
 subt="30,000 Gen Grid 5 by 5"
@@
 
-title="ZOOM Phenotpe by Gen For all Sims"
+title="midZOOM Phenotpe by Gen For all Sims"
 subt="GA2 30,000 Gen"
@@
 ```
+
+I mainly focus on looking for trends in the correlation results and the first one I noticed was how some of the four correlations seem to be following the same up and down pattern (most notably F, H, I, L, M).
+The blue, green and purple lines are mostly the same.
+The red line is usually positive and separated from the three other correlation lines.
+When I add in the second figure to what I observe in the first figure I start thinking about the how the difference in correlations might be dependent on which species currently has a higher phenotype (maybe over all or locally?).
+Potentially, when the newt mean phenotype is higher (overall) snakes in areas with high local newt phenotypes are under under selection to be more resistant.
+This selection might create a strong correlation between newt and snake phenotype, but when snakes meet or proceed the high newt phenotype the correlation gets weaker (S, U, V).
+
+## Boxplot at Different Time Points
+
+To get a better visual of what might be happening to the correlation calculation when I take them at different intervals.
+I decided to look at box plots.
+The first box plot I look at all four correlation calculations for each simulation separated by four 1,000 generation sections.
+The first section is the first 1,000 generation.
+The second section is taken from the 4,000- 5,000 generations.
+The third section is from the 10,000-11,000 generation and the last section is the lass 1,000 generation (29,000-30,000).
+As before, there are no labels on the x-axis (correlation calculation), the y-axis (correlation values), or the simulation letter (A starts on the top left and continues right and then to the next line).
+The four correlation calculations are printed below:
+
+```{r, boxplotting 30000 dif time, fig.height = 8, fig.width = 8, cache=TRUE}
+  print("CA = mean_newt_pheno_By_mean_snake_pheno")
+  print("CB = num_newts_By_num_snakes")
+  print("CC = sum_newt_pheno_By_num_snake")
+  print("CD = sum_snake_pheno_By_num_newt")
+
+title="Space: Newt VS Snake"
+subt="25sims first 1000Gen, Grid 5 by 5"
+x_label="Type"
+y_label="Correlation"
+G7<-boxplot_cors_by_gen(GA2_cor_30000_file[which(GA2_cor_30000_file$gen<=1000),], subt, x_label, y_label)
+
+title="Space: Newt VS Snake"
+subt="25sims 4000-5000 gen, Grid 5 by 5"
+x_label="Type"
+y_label="Correlation"
+G8<-boxplot_cors_by_gen(GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=4000 & GA2_cor_30000_file$gen<=5000),], subt, x_label, y_label)
+
+title="Space: Newt VS Snake"
+subt="25sims 10000-11000, Grid 5 by 5"
+x_label="Type"
+y_label="Correlation"
+G9<-boxplot_cors_by_gen(GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=10000 & GA2_cor_30000_file$gen<=11000),], subt, x_label, y_label)
+
+title="Space: Newt VS Snake"
+subt="25sims last 1000Gen 30000, Grid 5 by 5"
+x_label="Type"
+y_label="Correlation"
+G10<-boxplot_cors_by_gen(GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=29000),], subt, x_label, y_label)
+
+grid.arrange(G7, G8, G9, G10, nrow=2, top=textGrob("1,000 Gen at Different Timepoints By Simulation",gp=gpar(fontsize=16,font=3)))
+
+```
+
+This figure is super difficult to read!
+The only thing I can tell is that the red box is consistently higher than the three other boxes.
+In the first 5,000 generations the purple box might be less negatively correlated in some of the simulations.
+However, for the most part the green, blue, and purple box plots look very similar.
+To see if the correlations were going up or down as the simulation kept running I decided to group the different box plots by which calculation I made.
+
+The first graph (red) in the next figure is the correlation between newt and snake phenotype (CA) at the four different time points (1 = 0-1,000 gen, 2 = 4,000-5,000 gen, 3 = 10,000-11,000 gen, 4 = 29,000-30,000 gen).
+The second, third and fourth graph (green, blue, purple) is the correlation between number of newts and number of snakes (CB), the correlation between the amount of toxin and snakes (CC), and the correlation between resistance and number of newts (CD).
+Again, 1 = 0-1,000 gen, 2 = 4,000-5,000 gen, 3 = 10,000-11,000 gen, 4 = 29,000-30,000 gen.
+
+```{r, regrouping the box plot, cache=TRUE}
+# out.width = "1026", out.height = "528"
+myvars <- c("gen", "mean_newt_pheno_By_mean_snake_pheno", "sim")
+data_CA<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen<=1000),][myvars]
+names(data_CA)[names(data_CA) == 'mean_newt_pheno_By_mean_snake_pheno'] <- 'C1'
+CA2<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=4000 & GA2_cor_30000_file$gen<=5000),]$mean_newt_pheno_By_mean_snake_pheno
+CA3<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=10000 & GA2_cor_30000_file$gen<=11000),]$mean_newt_pheno_By_mean_snake_pheno
+CA4<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=29000),]$mean_newt_pheno_By_mean_snake_pheno
+data_CA$C2 <- CA2
+data_CA$C3 <- CA3
+data_CA$C4 <- CA4
+
+myvars <- c("gen", "num_newts_By_num_snakes", "sim")
+data_CB<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen<=1000),][myvars]
+names(data_CB)[names(data_CB) == 'num_newts_By_num_snakes'] <- 'C1'
+CB2<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=4000 & GA2_cor_30000_file$gen<=5000),]$num_newts_By_num_snakes
+CB3<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=10000 & GA2_cor_30000_file$gen<=11000),]$num_newts_By_num_snakes
+CB4<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=29000),]$num_newts_By_num_snakes
+data_CB$C2 <- CB2
+data_CB$C3 <- CB3
+data_CB$C4 <- CB4
+
+myvars <- c("gen", "sum_newt_pheno_By_num_snake", "sim")
+data_CC<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen<=1000),][myvars]
+names(data_CC)[names(data_CC) == 'sum_newt_pheno_By_num_snake'] <- 'C1'
+CC2<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=4000 & GA2_cor_30000_file$gen<=5000),]$sum_newt_pheno_By_num_snake
+CC3<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=10000 & GA2_cor_30000_file$gen<=11000),]$sum_newt_pheno_By_num_snake
+CC4<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=29000),]$sum_newt_pheno_By_num_snake
+data_CC$C2 <- CC2
+data_CC$C3 <- CC3
+data_CC$C4 <- CC4
+
+myvars <- c("gen", "sum_snake_pheno_By_num_newt", "sim")
+data_CD<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen<=1000),][myvars]
+names(data_CD)[names(data_CD) == 'sum_snake_pheno_By_num_newt'] <- 'C1'
+CD2<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=4000 & GA2_cor_30000_file$gen<=5000),]$sum_snake_pheno_By_num_newt
+CD3<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=10000 & GA2_cor_30000_file$gen<=11000),]$sum_snake_pheno_By_num_newt
+CD4<-GA2_cor_30000_file[which(GA2_cor_30000_file$gen>=29000),]$sum_snake_pheno_By_num_newt
+data_CD$C2 <- CD2
+data_CD$C3 <- CD3
+data_CD$C4 <- CD4
+
+subt="CAs"
+x_label="Type"
+y_label="Correlation"
+CAs<-boxplot_cors_by_type_gen(data_CA, subt, x_label, y_label, mycolor="#F8766D")
+
+subt="CBs"
+x_label="Type"
+y_label="Correlation"
+CBs<-boxplot_cors_by_type_gen(data_CB, subt, x_label, y_label, mycolor="#7CAE00")
+
+subt="CCs"
+x_label="Type"
+y_label="Correlation"
+CCs<-boxplot_cors_by_type_gen(data_CC, subt, x_label, y_label, mycolor="#00BFC4")
+
+subt="CDs"
+x_label="Type"
+y_label="Correlation"
+CDs<-boxplot_cors_by_type_gen(data_CD, subt, x_label, y_label, mycolor="#C77CFF")
+
+```
+
+```{r, regrouping the box plot figure, fig.height = 8, fig.width = 8, cache=TRUE}
+
+grid.arrange(CAs, CBs, CCs, CDs, nrow=2, top = textGrob("1,000 Gens Grouped by Caculation",gp=gpar(fontsize=16,font=3)))
+
+```
+
+The trend between time points was easier to see in this figure.
+Generally, the correlation between newt and snake phenotype increased at the number of generation increased (except F).
+The correlation between number of newts and number of snakes (CB), the correlation between the amount of toxin and snakes (CC), and the correlation between resistance and number of newts (CD) generally stay about the same.
+There are instances where they seem to move in a curved motion (like ~).
+It makes me wonder what makes these correlations stay between 0 and -0.5.
+I am also curious to how the correlations are connect to each other, if they are connect to each other.
+
+## Future Ideas
+
+- How does interaction rate effect the correlation calculations?
+- How does avoidance change correlation?
+- When I run multiple trials how do I show that information?
+
+## Conclusion
+
+Write after meeting with Peter

### 2022-04-07 Snakemake/snake_newt_gv_sm.py
updated the names on the file to include a tag and take away the slim seed

@@ -26,11 +26,11 @@ newt_mu_effect_sd = float(sys.argv[4])
 datadir = sys.argv[5]
 mytag = sys.argv[6]
 myrep = sys.argv[7]
-myseed = sys.argv[8]
+myID = sys.argv[8]
 
 name_of_file = mytag + "_trees_su_" + str(snake_mu_rate) + "_nu_" + str(newt_mu_rate) + \
     "_sue_" + str(snake_mu_effect_sd) + "_nue_" + str(newt_mu_effect_sd) + \
-    "_rep_" + str(myrep) +"_SLIMseed_" + str(myseed) + ".init.trees"
+    "_rep_" + str(myrep) +"_ID_" + str(myID) + ".init.trees"
 print(name_of_file)
 
 

### 2022-04-08 graphs_newt_snakes/correlation_part2.Rmd
I am starting a new correlation document to look at the newt & snake phenotype correlation and to explore other factors that might be going in to the slim cor score. I am going to try to get slim to same some more stuff

---
title: "correlation_part2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Comparing newt and snake phenotype correlation

newt and snake data from Hanifin et al. 2008

```{r, reak data cor}
snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
snewt$mean_res = snewt$mean_toxin+snewt$dif
cor(snewt$mean_toxin, snewt$mean_res)

```

## More data from the slim simulation

might be a specific generation or a small set of generations, If I can get the data to be saved and then interpreted by R
make a list in a coulmn 
how to proporsion and recreate what I see in the slim map (the different box and their dims)

### 2022-04-12 graphs_newt_snakes/correlation_part2.Rmd
I started a cor part 2 file to look more at the individual locations (both at previous data and slim data. I also am trying to figure out logs and functions to help me make better files

@@
 knitr::opts_chunk$set(echo = TRUE)
+library(tidyverse)
+library(ggmap)
+library(ggplot2)
+library(sf)
+library(mapview)
 ```
@@
 cor(snewt$mean_toxin, snewt$mean_res)
+(sites <- data.frame(longitude = snewt$lon, latitude = snewt$lat))
+just_loc <- data.frame(snewt$lon, snewt$lat)
+snewt$lon<- snewt$lon *-1
+locations_sf <- st_as_sf(snewt, coords = c("lon", "lat"), crs = 4326)
+mapview(locations_sf)
+```
 
+```{r, more maps}
+library("rnaturalearth")
+library("rnaturalearthdata")
+library("tools")
+library("maps")
+
+world <- ne_countries(scale = "medium", returnclass = "sf")
+states <- st_as_sf(maps::map("state", plot = FALSE, fill = TRUE))
+states$ID <- toTitleCase(states$ID)
+
+ggplot(data = world) +
+  geom_sf() +
+  geom_sf(data = states, fill = NA)+
+  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_res), size = 5, shape = 22, ) +
+  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_toxin), size = 3, shape = 21, ) +
+  scale_fill_viridis_c()+
+  coord_sf(xlim = c(-130.4494, -111.6764), ylim = c(29.742, 54.9415), expand = FALSE)
 ```
@@
 might be a specific generation or a small set of generations, If I can get the data to be saved and then interpreted by R
-make a list in a coulmn 
-how to proporsion and recreate what I see in the slim map (the different box and their dims)
+make a list in a column 
+how to proportion and recreate what I see in the slim map (the different box and their dims)

### 2022-04-18 graphs_newt_snakes/GAs_conclusion.Rmd
I am working on ways to graph a summary of my reps

---
title: "GAs Conclusion"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library("reshape")
```

### Goal

The goal of this markdown is to determine a conclusion to the genetic architecture (GA) experiment. I have run 4 replicas for each of the GA sets and will now summarize the results.

GA1 experiment values:

- 1e-8*(0.005)^2 = 2.5e-13
- 1e-9*(0.05)^2 = 2.5e-12
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(5.0)^2 = 2.5e-10

GA2 experiment values:

- 1e-8*(0.05)^2 = 2.5e-11
- 1e-9*(0.1581139)^2 = 2.5e-11
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(1.581139)^2 = 2.5e-11
- 1e-12*(5)^2 = 2.5e-11

This is a two dimensional simulation where newts and snakes are co-evolving. The newts develop a toxin and the snakes develop resistance. Resistance and toxicity are the phenotype that I measured and as the snakes and newts co-evolve these phenotypes get larger.  As snakes become more resistant, less toxic newts are being devoured, leaving only the most toxic newts. These toxic newts reproduce and create even more toxic newts. The cycle contentiously repeats. However, the growth of the phenotype is not unlimited, there is a burden for having a higher phenotype (fitness cost). If a snake eats a newt that is more toxic the snake dies.

```{r, data gathering}
lit_30 <- list.files(path="~/Desktop/GA1_rep", pattern="_lit_", full.names=TRUE, recursive=FALSE)
lit_30_G2 <- list.files(path="~/Desktop/GA2_rep", pattern="_lit_", full.names=TRUE, recursive=FALSE)

lit_30_file<-read.csv(lit_30[1], header = TRUE)
replica <- unlist(str_split(unlist(str_split(lit_30[1],"rep_"))[3], "_"))[1]
lit_30_file$rep<-replica
lit_30_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_rate_"))[2], "_"))[1]
lit_30_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_rate_"))[2], "_"))[1]
lit_30_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
lit_30_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
lit_30_file$sim <-"A"

lit_30_G2_file<-read.csv(lit_30_G2[1], header = TRUE)
replica <- unlist(str_split(unlist(str_split(lit_30_G2[1],"rep_"))[3], "_"))[1]
lit_30_G2_file$rep<-replica
lit_30_G2_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_rate_"))[2], "_"))[1]
lit_30_G2_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
lit_30_G2_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_effect_sd_"))[2], "_"))[1]
lit_30_G2_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_effect_sd_"))[2], "_"))[1]

lit_30_G2_file$sim <-"A"

oldstand=0
letter=1
for(i in seq(2, length(lit_30_G2), 1)){
  stand <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
  if (stand!=oldstand){
    oldstand=stand
    letter = letter + 1
  }

  GA2_lit_temp_file <- read.csv(lit_30_G2[i], header = TRUE)
  GA2_lit_temp_file$sim <-LETTERS[letter]
  GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30_G2[i],"rep_"))[3], "_"))[1]
  GA2_lit_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_rate_"))[2], "_"))[1]
  GA2_lit_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
  GA2_lit_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  GA2_lit_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_effect_sd_"))[2], "_"))[1]

  lit_30_G2_file <- rbind(lit_30_G2_file, GA2_lit_temp_file)

  if (i<=length(lit_30)){
  cor_temp_file <- read.csv(lit_30[i], header = TRUE)
  cor_temp_file$sim <-LETTERS[letter]
  cor_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30[i],"rep_"))[3], "_"))[1]
  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_rate_"))[2], "_"))[1]
  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_rate_"))[2], "_"))[1]
  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  lit_30_file <- rbind(lit_30_file, cor_temp_file)
  rep <-unlist(str_split(unlist(str_split(lit_30[i],"rep_"))[3], "_"))[1]

  snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_rate_"))[2], "_"))[1]
  newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_rate_"))[2], "_"))[1]
  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  print(paste0("Simulation ", LETTERS[letter],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")",  " rep: ", rep))
  }

}

```

```{r, data summarizing}

##summarizing data with mean and error bars for the different GA experiments

#GA1_lit<-lit_30_file[which(lit_30_file$generation>=10000 & lit_30_file$gen<=110000 ),]
#GA2_lit<-lit_30_G2_file[which(lit_30_G2_file$generation>=10000 & lit_30_G2_file$gen<=110000 ),]

title="Space: Newt VS Snake Population Size"
subt="Gen 25sims"
y_label="Snake Popsize"
x_label="Newt Popsize"

lit_30_G2_file$snake <- paste0(lit_30_G2_file$snake_mu_rate, "_",lit_30_G2_file$snake_mu_effect_sd)
lit_30_G2_file$newt <- paste0(lit_30_G2_file$newt_mu_rate, "_",lit_30_G2_file$newt_mu_effect_sd)
lit_30_G2_file$newt_snake <- paste0(lit_30_G2_file$newt, "_", lit_30_G2_file$snake)
lit_30_G2_file$newt_snake_rep <- paste0(lit_30_G2_file$newt_snake, "_", lit_30_G2_file$rep)

params <- data_frame()

params$snake_mu_rate <- 0
  params$newt_mu_rate <- 0
  params$snake_mu_effect_sd <- 0
  params$newt_mu_effect_sd <- 0

params$rep<-5
params$Newt_mean_Pheno<-0
params$Snake_mean_Pheno<-0
params$Newt_pop_size<-0
params$Snake_pop_size<-0
params$dif<-0

for(i in unique(lit_30_G2_file$newt_snake_rep)){
  print(i)
# might need to loop through length
  sumitup <- lit_30_G2_file[which(lit_30_G2_file$gen>=2500 & lit_30_G2_file$newt_snake_rep ==i),]

  lit_30_file <- rbind(lit_30_file, cor_temp_file)
# need a temp file then I need to calculate these values and bind it to the params file
  # i also will need to get a line numer to take these values
  params$Newt_mean_Pheno[i]<-mean(sumitup$Newt_mean_Pheno)
  params$Snake_mean_Pheno[i]<-mean(sumitup$Snake_mean_Pheno)
  params$Newt_pop_size[i]<-mean(sumitup$Newt_pop_size)
  params$Snake_pop_size[i]<-mean(sumitup$Snake_pop_size)
  params$dif[i]<-mean(sumitup$dif)

}
t25 <- ggplot(lit_30_G2_file[which(lit_30_G2_file$gen>=2500),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
t25

```

```{r, heatmap}

```

### 2022-04-18 graphs_newt_snakes/correlation_part2.Rmd
I am working on ways to graph a summary of my reps

@@
 how to proportion and recreate what I see in the slim map (the different box and their dims)
+
+GA1 experiment values:
+
+- 1e-8*(0.005)^2 = 2.5e-13
+- 1e-9*(0.05)^2 = 2.5e-12
+- 1e-10*(0.5)^2 = 2.5e-11
+- 1e-11*(5.0)^2 = 2.5e-10
+
+GA2 experiment values:
+
+- 1e-8*(0.05)^2 = 2.5e-11
+- 1e-9*(0.1581139)^2 = 2.5e-11
+- 1e-10*(0.5)^2 = 2.5e-11
+- 1e-11*(1.581139)^2 = 2.5e-11
+- 1e-12*(5)^2 = 2.5e-11
+
+```{r, cor by location}
+
+cor_grid_30 <- list.files(path="~/Desktop/GA1_rep", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+cor_grid_30_G2 <- list.files(path="~/Desktop/GA2_rep", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+
+cor_grid_30_file<-read.csv(cor_grid_30[1], header = TRUE)
+replica <- unlist(str_split(unlist(str_split(cor_grid_30[1],"rep_"))[3], "_"))[1]
+cor_grid_30_file$rep<-replica
+cor_grid_30_file$sim <-"A"
+
+cor_grid_30_G2_file<-read.csv(cor_grid_30_G2[1], header = TRUE)
+replica <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"rep_"))[3], "_"))[1]
+cor_grid_30_G2_file$rep<-replica
+cor_grid_30_G2_file$sim <-"A"
+i=2
+oldstand=0
+letter=1
+for(i in seq(2, length(cor_grid_30_G2), 1)){
+  stand <- unlist(str_split(unlist(str_split(cor_grid_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
+  if (stand!=oldstand){
+    oldstand=stand
+    letter = letter + 1
+  }
+
+  GA2_lit_temp_file <- read.csv(cor_grid_30_G2[i], header = TRUE)
+  GA2_lit_temp_file$sim <-LETTERS[letter]
+  GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30_G2[i],"rep_"))[3], "_"))[1]
+
+  cor_grid_30_G2_file <- rbind(cor_grid_30_G2_file, GA2_lit_temp_file)
+
+  if (i<=length(cor_grid_30)){
+  cor_temp_file <- read.csv(cor_grid_30[i], header = TRUE)
+  cor_temp_file$sim <-LETTERS[letter]
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30[i],"rep_"))[3], "_"))[1]
+  cor_grid_30_file <- rbind(cor_grid_30_file, cor_temp_file)
+  rep <-unlist(str_split(unlist(str_split(cor_grid_30[i],"rep_"))[3], "_"))[1]
+
+  snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_rate_"))[2], "_"))[1]
+  newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_rate_"))[2], "_"))[1]
+  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  print(paste0("Simulation ", LETTERS[letter],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")",  " rep: ", rep))
+  }
+
+}
+
+```
+
+```{r, small sample}
+
+GA1<-cor_grid_30_file[which(cor_grid_30_file$generation>=10000 & cor_grid_30_file$gen<=110000 ),]
+GA2<-cor_grid_30_G2_file[which(cor_grid_30_G2_file$generation>=10000 & cor_grid_30_G2_file$gen<=110000 ),]
+
+```

### 2022-04-19 graphs_newt_snakes/GAs_conclusion.Rmd
I am trying to figure out a conclusion, but made a cool animation

@@
 library(grid)
+library(knitr)
+library(kableExtra)
 library("reshape")
@@
 
-The goal of this markdown is to determine a conclusion to the genetic architecture (GA) experiment. I have run 4 replicas for each of the GA sets and will now summarize the results.
+The goal of this markdown is to determine a conclusion to the genetic architecture (GA) experiment. I have run 4 replicas for each of the GA sets and will summarize the results.
+
+This is a two dimensional co-evolution simulation where newts have developed a toxin and snakes have evolved resistance to this toxin.
+Resistance and toxicity are the phenotype that I measured and as the snakes and newts co-evolve these phenotypes get larger.
+As snakes become more resistant, less toxic newts are being devoured, leaving only the most toxic newts.
+These toxic newts reproduce and create even more toxic newts.
+The cycle contentiously repeats.
+However, the growth of the phenotype is not unlimited, there is a burden for having a higher phenotype (fitness cost).
+
+Resistance and toxicity are quantitative traits that are the sum of effects from mutations on these specific phenotypes.
+In my simulations I create different genetic architectures (GA) for resistance and toxicity to see if there is an effect on the how the population co-evolve.
+Genetic architectures are a combination of mutation rates and the standard deviation of the mutation effect size.
+I have ran two types of genetic architecture studies one where one species is at an evolutionary disadvantage (one species will have less variance) and the other study has the same level of variance.
+In the study where there is no variance disadvantage I test the effects of mutation rate and effect size to see if one or the other has a large effect on how a population can co-evolve.
+In the study where there is a disadvantage I not only look at the effects of mutation rate and effect size, but also look at how a disadvantage can effect a population undergoing co-evolution.
+The disadvantage experiment is GA1 (16 simulations) and the same level of variance is GA2 (25 simulations).
+
+Each of the simulations contain their own neutral msprime simulation (to generate genetic diversity) followed by the slim simulation (populations are co-evolving).
 
@@
 
-This is a two dimensional simulation where newts and snakes are co-evolving.
-The newts develop a toxin and the snakes develop resistance.
-Resistance and toxicity are the phenotype that I measured and as the snakes and newts co-evolve these phenotypes get larger.
-As snakes become more resistant, less toxic newts are being devoured, leaving only the most toxic newts.
-These toxic newts reproduce and create even more toxic newts.
-The cycle contentiously repeats.
-However, the growth of the phenotype is not unlimited, there is a burden for having a higher phenotype (fitness cost).
-If a snake eats a newt that is more toxic the snake dies.
+The first thing I do is gather the data from each GA set, paying attention to all of the parameters especially the replica number.
+I typically give each simulation a letter associated with the mutation rate and effect size.
+Here are the trial letters and the parameters associated with it.
 
 ```{r, data gathering}
+
+para_table <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit.csv", header = TRUE)
+para_table$trial<-LETTERS[para_table$trial]
+para_table <- data.frame("Trial"=para_table$trial, "Snake Mu Rate"=para_table$snake_mu_rate, "Snake effect size"= para_table$snake_mu_effect_sd, "Newt Mu Rate"=para_table$newt_mu_rate, "Newt effect size"= para_table$newt_mu_effect_sd)
+#kable(para_table, caption="GA2 Params")
+
+para_table %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
+    kable(., caption="GA1 Params") %>%
+ kable_styling("striped")
+
+para_table <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit_25.csv", header = TRUE)
+para_table$trial<-LETTERS[para_table$trial]
+para_table <- data.frame("Trial"=para_table$trial, "Snake Mu Rate"=para_table$snake_mu_rate, "Snake effect size"= para_table$snake_mu_effect_sd, "Newt Mu Rate"=para_table$newt_mu_rate, "Newt effect size"= para_table$newt_mu_effect_sd)
+#kable(para_table, caption="GA2 Params")
+
+para_table %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
+    kable(., caption="GA2 Params") %>%
+ kable_styling("striped")
+
 lit_30 <- list.files(path="~/Desktop/GA1_rep", pattern="_lit_", full.names=TRUE, recursive=FALSE)
@@
 lit_30_file$rep<-replica
-lit_30_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_rate_"))[2], "_"))[1]
-lit_30_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_rate_"))[2], "_"))[1]
-lit_30_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-lit_30_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+lit_30_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_rate_"))[2], "_"))[1]
+lit_30_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_rate_"))[2], "_"))[1]
+lit_30_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_effect_sd_"))[2], "_"))[1]
+lit_30_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_effect_sd_"))[2], "_"))[1]
 lit_30_file$sim <-"A"
@@
 lit_30_G2_file$rep<-replica
-lit_30_G2_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_rate_"))[2], "_"))[1]
-lit_30_G2_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
-lit_30_G2_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-lit_30_G2_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+lit_30_G2_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_rate_"))[2], "_"))[1]
+lit_30_G2_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_rate_"))[2], "_"))[1]
+lit_30_G2_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_effect_sd_"))[2], "_"))[1]
+lit_30_G2_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_effect_sd_"))[2], "_"))[1]
 
@@
 letter=1
-for(i in seq(2, length(lit_30_G2), 1)){
+for(i in seq(1, length(lit_30_G2), 1)){
   stand <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
@@
   newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  print(paste0("Simulation ", LETTERS[letter],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")",  " rep: ", rep))
+  #print(paste0("Simulation ", LETTERS[letter],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")",  " rep: ", rep))
   }
@@
 
+lit_30_file$dif <- lit_30_file$Snake_mean_Pheno-lit_30_file$Newt_mean_Pheno
+lit_30_G2_file$dif <- lit_30_G2_file$Snake_mean_Pheno-lit_30_G2_file$Newt_mean_Pheno
 ```
 
-```{r, data summarizing}
+```{r, general file and graph making}
 
-##summarizing data with mean and error bars for the different GA experiments
+#the functions to make the params file and the summary and heatmap figures
 
-#GA1_lit<-lit_30_file[which(lit_30_file$generation>=10000 & lit_30_file$gen<=110000 ),]
-#GA2_lit<-lit_30_G2_file[which(lit_30_G2_file$generation>=10000 & lit_30_G2_file$gen<=110000 ),]
-
-title="Space: Newt VS Snake Population Size"
-subt="Gen 25sims"
-y_label="Snake Popsize"
-x_label="Newt Popsize"
-
-lit_30_G2_file$snake <- paste0(lit_30_G2_file$snake_mu_rate, "_",lit_30_G2_file$snake_mu_effect_sd)
-lit_30_G2_file$newt <- paste0(lit_30_G2_file$newt_mu_rate, "_",lit_30_G2_file$newt_mu_effect_sd)
-lit_30_G2_file$newt_snake <- paste0(lit_30_G2_file$newt, "_", lit_30_G2_file$snake)
-lit_30_G2_file$newt_snake_rep <- paste0(lit_30_G2_file$newt_snake, "_", lit_30_G2_file$rep)
-
+create_parm_file <- function(file, min_gen, max_gen){
 params <- data_frame()
 
-params$snake_mu_rate <- 0
-  params$newt_mu_rate <- 0
-  params$snake_mu_effect_sd <- 0
-  params$newt_mu_effect_sd <- 0
+for(i in 1:length(unique(file$newt_snake_rep))){
 
-params$rep<-5
-params$Newt_mean_Pheno<-0
-params$Snake_mean_Pheno<-0
-params$Newt_pop_size<-0
-params$Snake_pop_size<-0
-params$dif<-0
+  pattern=unique(file$newt_snake_rep)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep ==pattern),]
 
-for(i in unique(lit_30_G2_file$newt_snake_rep)){
-  print(i)
-# might need to loop through length
-  sumitup <- lit_30_G2_file[which(lit_30_G2_file$gen>=2500 & lit_30_G2_file$newt_snake_rep ==i),]
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=sumitup$snake_mu_rate[1],
+                           newt_mu_rate=sumitup$newt_mu_rate[1],
+                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
+                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
+                           rep=sumitup$rep[1])
 
-  lit_30_file <- rbind(lit_30_file, cor_temp_file)
-# need a temp file then I need to calculate these values and bind it to the params file
-  # i also will need to get a line numer to take these values
-  params$Newt_mean_Pheno[i]<-mean(sumitup$Newt_mean_Pheno)
-  params$Snake_mean_Pheno[i]<-mean(sumitup$Snake_mean_Pheno)
-  params$Newt_pop_size[i]<-mean(sumitup$Newt_pop_size)
-  params$Snake_pop_size[i]<-mean(sumitup$Snake_pop_size)
-  params$dif[i]<-mean(sumitup$dif)
+  params <- rbind(params, params_temp)
+}
 
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$newt_snake <- paste0(params$newt, "_", params$snake)
+return(params)
 }
-t25 <- ggplot(lit_30_G2_file[which(lit_30_G2_file$gen>=2500),]) +
+
+GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+
+file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen)
+
+my_plot <- ggplot(params) +
   #xlim(0, 1000)+
-  ggtitle(title, subtitle = subt) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "gen to ", max_gen, " gen")) +
   xlab(x_label) + ylab(y_label)+
-  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)),size=3)+
+  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
 #  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
@@
   #facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
-t25
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+
+build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
+  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+
+  params<-create_parm_file(file, min_gen, max_gen)
+
+ my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
+  ggtitle(title, subtitle = subt) +
+  xlab(x_label) + ylab(y_label)+
+  geom_tile(aes(fill = get(fill_line)))
+ if(red_blue==FALSE){
+  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text)
+  }
+ if(red_blue==TRUE){
+  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text)
+ }
+  return(my_plot)
+}
+
+```
+
+First, I will look at a summary plot for the different GA sets. There are four points for each GA set (one for each replica).
+
+```{r, graphing the summary}
+
+GA_summary(lit_30_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+GA_summary(lit_30_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 25sims", y_label="Snake Popsize", x_label="Dif")
+
+GA_summary(lit_30_G2_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+GA_summary(lit_30_G2_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 25sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 
+#params_GA1
+
+build_heatmap(lit_30_file, min_gen=5000, max_gen=10000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(lit_30_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+build_heatmap(lit_30_G2_file, min_gen=5000, max_gen=10000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(lit_30_G2_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
 ```
+```{r, plot experiment}
+library(plotly)
+library(gapminder)
+#GA_summary(lit_30_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+#lit_30_file$generation
+
+lit_30_file$snake <- paste0(lit_30_file$snake_mu_rate, "_",lit_30_file$snake_mu_effect_sd)
+lit_30_file$newt_snake <- paste0(lit_30_file$newt_mu_rate, "_", lit_30_file$newt_mu_effect_sd, "_", lit_30_file$snake_mu_rate, "_", lit_30_file$snake_mu_effect_sd)
+lit_30_file$sim
+#params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+#params$newt_snake <- paste0(params$newt, "_", params$snake)
+
+lit_30_file_min<-lit_30_file[which(lit_30_file$generation>=5000 & lit_30_file$generation<=5350),]
+p <- lit_30_file_min %>%
+  plot_ly(
+    x = ~Newt_pop_size, 
+    y = ~Snake_pop_size, 
+    color = ~factor(sim), 
+    #shape = ~factor(newt)
+    frame = ~generation, 
+    #text = ~country, 
+    #hoverinfo = "text",
+    type = 'scatter',
+    mode = 'markers'
+  ) %>%
+  layout(
+    xaxis = list(
+      type = "log"
+    )
+  )
+
+p
+```

### 2022-04-19 graphs_newt_snakes/correlation_part2.Rmd
I am trying to figure out a conclusion, but made a cool animation

--- 2022-04-12 graphs_newt_snakes/correlation_part2.Rmd
@@
 how to proportion and recreate what I see in the slim map (the different box and their dims)
+
+GA1 experiment values:
+
+- 1e-8*(0.005)^2 = 2.5e-13
+- 1e-9*(0.05)^2 = 2.5e-12
+- 1e-10*(0.5)^2 = 2.5e-11
+- 1e-11*(5.0)^2 = 2.5e-10
+
+GA2 experiment values:
+
+- 1e-8*(0.05)^2 = 2.5e-11
+- 1e-9*(0.1581139)^2 = 2.5e-11
+- 1e-10*(0.5)^2 = 2.5e-11
+- 1e-11*(1.581139)^2 = 2.5e-11
+- 1e-12*(5)^2 = 2.5e-11
+
+```{r, cor by location}
+
+cor_grid_30 <- list.files(path="~/Desktop/GA1_rep", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+cor_grid_30_G2 <- list.files(path="~/Desktop/GA2_rep", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+
+cor_grid_30_file<-read.csv(cor_grid_30[1], header = TRUE)
+replica <- unlist(str_split(unlist(str_split(cor_grid_30[1],"rep_"))[3], "_"))[1]
+cor_grid_30_file$rep<-replica
+cor_grid_30_file$sim <-"A"
+cor_grid_30_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30[i],"rep_"))[3], "_"))[1]
+cor_grid_30_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[1],"snake_mu_rate_"))[2], "_"))[1]
+cor_grid_30_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[1],"newt_mu_rate_"))[2], "_"))[1]
+cor_grid_30_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[1],"snake_mu_effect_sd_"))[2], "_"))[1]
+cor_grid_30_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[1],"newt_mu_effect_sd_"))[2], "_"))[1]
+
+cor_grid_30_G2_file<-read.csv(cor_grid_30_G2[1], header = TRUE)
+replica <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"rep_"))[3], "_"))[1]
+cor_grid_30_G2_file$rep<-replica
+cor_grid_30_G2_file$sim <-"A"
+cor_grid_30_G2_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30_G2[i],"rep_"))[3], "_"))[1]
+cor_grid_30_G2_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"snake_mu_rate_"))[2], "_"))[1]
+cor_grid_30_G2_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"newt_mu_rate_"))[2], "_"))[1]
+cor_grid_30_G2_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"snake_mu_effect_sd_"))[2], "_"))[1]
+cor_grid_30_G2_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"newt_mu_effect_sd_"))[2], "_"))[1]
+
+i=2
+oldstand=0
+letter=1
+for(i in seq(2, length(cor_grid_30_G2), 1)){
+  stand <- unlist(str_split(unlist(str_split(cor_grid_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
+  if (stand!=oldstand){
+    oldstand=stand
+    letter = letter + 1
+  }
+
+  GA2_lit_temp_file <- read.csv(cor_grid_30_G2[i], header = TRUE)
+  GA2_lit_temp_file$sim <-LETTERS[letter]
+  GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30_G2[i],"rep_"))[3], "_"))[1]
+  GA2_lit_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30_G2[i],"snake_mu_rate_"))[2], "_"))[1]
+GA2_lit_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_rate_"))[2], "_"))[1]
+GA2_lit_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+GA2_lit_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+
+  cor_grid_30_G2_file <- rbind(cor_grid_30_G2_file, GA2_lit_temp_file)
+
+  if (i<=length(cor_grid_30)){
+  cor_temp_file <- read.csv(cor_grid_30[i], header = TRUE)
+  cor_temp_file$sim <-LETTERS[letter]
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_rate_"))[2], "_"))[1]
+cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_rate_"))[2], "_"))[1]
+cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  cor_grid_30_file <- rbind(cor_grid_30_file, cor_temp_file)
+  rep <-unlist(str_split(unlist(str_split(cor_grid_30[i],"rep_"))[3], "_"))[1]
+
+  snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_rate_"))[2], "_"))[1]
+  newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_rate_"))[2], "_"))[1]
+  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  print(paste0("Simulation ", LETTERS[letter],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")",  " rep: ", rep))
+  }
+
+}
+
+```
+
+```{r, small sample}
+
+GA1<-cor_grid_30_file[which(cor_grid_30_file$generation>=10000 & cor_grid_30_file$gen<=110000 ),]
+GA2<-cor_grid_30_G2_file[which(cor_grid_30_G2_file$generation>=10000 & cor_grid_30_G2_file$gen<=110000 ),]
+length(GA1$generation)
+
+GA1<-cor_grid_30_file[which(cor_grid_30_file$generation==10001 & rep==0),]
+GA1_mean = GA1[ , grepl( "mean" , names( GA1 ) ) ]
+GA1T<-data.frame(t(GA1_mean))
+GA1T
+```

### 2022-04-20 graphs_newt_snakes/GAs_conclusion.Rmd
cool animations

@@
 
-lit_30_file<-read.csv(lit_30[1], header = TRUE)
-replica <- unlist(str_split(unlist(str_split(lit_30[1],"rep_"))[3], "_"))[1]
-lit_30_file$rep<-replica
-lit_30_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_rate_"))[2], "_"))[1]
-lit_30_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_rate_"))[2], "_"))[1]
-lit_30_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_effect_sd_"))[2], "_"))[1]
-lit_30_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_effect_sd_"))[2], "_"))[1]
-lit_30_file$sim <-"A"
+lit_30_file<- data.frame()
+# 
+# lit_30_file<-read.csv(lit_30[1], header = TRUE)
+# replica <- unlist(str_split(unlist(str_split(lit_30[1],"rep_"))[3], "_"))[1]
+# lit_30_file$rep<-replica
+# lit_30_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_rate_"))[2], "_"))[1]
+# lit_30_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_rate_"))[2], "_"))[1]
+# lit_30_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_effect_sd_"))[2], "_"))[1]
+# lit_30_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_effect_sd_"))[2], "_"))[1]
+# lit_30_file$sim <-"A"
 
-lit_30_G2_file<-read.csv(lit_30_G2[1], header = TRUE)
-replica <- unlist(str_split(unlist(str_split(lit_30_G2[1],"rep_"))[3], "_"))[1]
-lit_30_G2_file$rep<-replica
-lit_30_G2_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_rate_"))[2], "_"))[1]
-lit_30_G2_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_rate_"))[2], "_"))[1]
-lit_30_G2_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_effect_sd_"))[2], "_"))[1]
-lit_30_G2_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_effect_sd_"))[2], "_"))[1]
+# lit_30_G2_file<-read.csv(lit_30_G2[1], header = TRUE)
+# replica <- unlist(str_split(unlist(str_split(lit_30_G2[1],"rep_"))[3], "_"))[1]
+# lit_30_G2_file$rep<-replica
+# lit_30_G2_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_rate_"))[2], "_"))[1]
+# lit_30_G2_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_rate_"))[2], "_"))[1]
+# lit_30_G2_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_effect_sd_"))[2], "_"))[1]
+# lit_30_G2_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_effect_sd_"))[2], "_"))[1]
+# 
+# lit_30_G2_file$sim <-"A"
 
-lit_30_G2_file$sim <-"A"
-
+lit_30_G2_file <- data.frame()
 oldstand=0
-letter=1
+letter=0
+newt_unique=0
+newt_numb = 0
 for(i in seq(1, length(lit_30_G2), 1)){
   stand <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
+  up <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  phrase = paste0(stand, "_", up)
   if (stand!=oldstand){
@@
 
+    if (phrase=="1.0e-08_0.05" ){
+    newt_numb =  1
+   }
+    if (phrase=="1.0e-09_0.158114"){
+    newt_numb =  2
+   }
+      if (phrase=="1.0e-10_0.5"){
+    newt_numb =  3
+   }
+    if (phrase=="1.0e-11_1.58114"){
+    newt_numb =  4
+   }
+
+      if (phrase=="1.0e-12_5.0"){
+    newt_numb =  5
+   }
+
   GA2_lit_temp_file <- read.csv(lit_30_G2[i], header = TRUE)
   GA2_lit_temp_file$sim <-LETTERS[letter]
+   GA2_lit_temp_file$size <-newt_numb
   GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30_G2[i],"rep_"))[3], "_"))[1]
@@
   if (i<=length(lit_30)){
+
+  stand <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_rate_"))[2], "_"))[1]
+  up <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  phrase = paste0(stand, "_", up)
+
+   if (phrase=="1.0e-08_0.005"){
+    newt_numb =  1
+   }
+    if (phrase=="1.0e-09_0.05"){
+    newt_numb =  2
+   }
+      if (phrase=="1.0e-10_0.5"){
+    newt_numb =  3
+   }
+    if (phrase=="1.0e-11_5.0"){
+    newt_numb =  4
+   }
+
   cor_temp_file <- read.csv(lit_30[i], header = TRUE)
   cor_temp_file$sim <-LETTERS[letter]
+  cor_temp_file$size <-newt_numb
   cor_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30[i],"rep_"))[3], "_"))[1]
@@
 
+#lit_30_file$sim
 lit_30_file$snake <- paste0(lit_30_file$snake_mu_rate, "_",lit_30_file$snake_mu_effect_sd)
-lit_30_file$newt_snake <- paste0(lit_30_file$newt_mu_rate, "_", lit_30_file$newt_mu_effect_sd, "_", lit_30_file$snake_mu_rate, "_", lit_30_file$snake_mu_effect_sd)
-lit_30_file$sim
-#params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+lit_30_file$newt <- paste0(lit_30_file$newt_mu_rate, "_",lit_30_file$newt_mu_effect_sd)
+
+lit_30_file$newt_snake_rep <- paste0(lit_30_file$newt_mu_rate, "_", lit_30_file$newt_mu_effect_sd, "_", lit_30_file$snake_mu_rate, "_", lit_30_file$snake_mu_effect_sd, "_", lit_30_file$rep)
+
+unique(lit_30_G2_file$snake)
 #params$newt_snake <- paste0(params$newt, "_", params$snake)
 
-lit_30_file_min<-lit_30_file[which(lit_30_file$generation>=5000 & lit_30_file$generation<=5350),]
+lit_30_file_min<-lit_30_file[which(lit_30_file$generation>=5000 & lit_30_file$generation<=5550),]
 p <- lit_30_file_min %>%
+  plot_ly(
+    x = ~Newt_pop_size, 
+    y = ~Snake_pop_size, 
+    color = ~factor(snake), 
+    size = ~size,
+    frame = ~generation, 
+    text = ~factor(newt_snake_rep), 
+    hoverinfo = "text",
+    type = 'scatter',
+    mode = 'markers'
+  ) %>%
+  layout(
+    xaxis = list(
+      type = "log"
+    )
+  )
+
+p
+
+lit_30_G2_file$snake <- paste0(lit_30_G2_file$snake_mu_rate, "_",lit_30_G2_file$snake_mu_effect_sd)
+
+lit_30_G2_file$newt <- paste0(lit_30_G2_file$newt_mu_rate, "_",lit_30_G2_file$newt_mu_effect_sd)
+
+lit_30_G2_file$newt_snake_rep <- paste0(lit_30_G2_file$newt_mu_rate, "_", lit_30_G2_file$newt_mu_effect_sd, "_", lit_30_G2_file$snake_mu_rate, "_", lit_30_G2_file$snake_mu_effect_sd, "_", lit_30_G2_file$rep)
+
+lit_30_G2_file_mini<-lit_30_G2_file[which(lit_30_G2_file$generation>=0 & lit_30_G2_file$generation<=5000),]
+p <- lit_30_G2_file_mini %>%
   plot_ly(
@@
     frame = ~generation, 
-    #text = ~country, 
-    #hoverinfo = "text",
+    text = ~factor(sim), 
+    hoverinfo = "text",
     type = 'scatter',

### 2022-04-21 graphs_newt_snakes/GAs_conclusion.Rmd
writhing the conclusion

@@
   #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "gen to ", max_gen, " gen")) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
   xlab(x_label) + ylab(y_label)+
@@
  my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
-  ggtitle(title, subtitle = subt) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
   xlab(x_label) + ylab(y_label)+
@@
 
+trends_by_gen <- function(file, title, subt, x_label, y_label){
+
+  plot <- ggplot(file) +
+    facet_wrap(~sim)+
+    geom_line(aes(generation, dif, col="dif"))+
+    ggtitle(title, subtitle = subt) +
+    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"))+
+    ylim(-5,10)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  return(plot)
+  }
+
 ```
 
-First, I will look at a summary plot for the different GA sets. There are four points for each GA set (one for each replica).
+First, I will look at a plot of how the mean phenotype of newts and snakes changes overtime.
+Each of these plots contains four replicas for all GA combinations (letter label is the experiment that was run, 16 Sim is from GA1 and 25 Sim is from GA2).
+Each of these plots has three lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype.
+Note this is a mean for the entire population.
+
+```{r, graphing by gen}
+trends_by_gen(lit_30_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+trends_by_gen(lit_30_G2_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+```
+
+After looking at the GA1 and GA2 figures, I noticed that there are similarities between the four replicas (blue, red, and black lines follow similar trends).
+In the GA1 figure there is a strong trend increasing replica variability as the GA of newts creates an advantage (gets a smaller mutation rate and larger effect size).
+There is a similar pattern in variability of the replicas in snakes, as the replica variability increases so is the phenotype variability.
+I also noticed that newts seem to have a higher phenotype more often than snakes.
+In the GA2 figure the mean phenotypes of newts and snake are more closely matched (16/25).
+My question is why are there a collective difference in some of these simulation?
+
+Next, I will discuss a summary plot for the different GA sets.
+The first plot has the newt population size by snake population size (a larger population size might indicate a co-evolution advantage) and the second plot is the difference between snake and newt mean phenotype and snake population size.
+There are four points for each GA set (one for each replica).
+Color will represent the four GAs of the snake and the shapes will represent the four GAs of newts.
+Each plot will have a starting generation and an ending generation (that can easily be changed).
 
@@
 
+The species which has the phenotype variance advantage will have a co-evolution advantage until the effect of some mutations is so large that that species losses its advantage to the cost of the phenotype.
+In the GA1 experiment snakes have a higher phenotype when their GA is blue or green and when paired with a newt GA of the plus and circle.
+Newts have a higher phenotype and population size when their GA is a square or triangle and when paired with a snake GA of purple or red.
+
+In the GA2 experiment results are not as easy to summarize.
+Many of the simulations result with similar population sizes or a low mean phenotype difference.
+The results depicted depend on the generations shown in the plot.
+A possible conclusion for this experiment is that the larger the effect size and smaller the mutation rate the more it is likely for one species to have a co-evolutionary advantage.
+For example lets look at the blue square with a X, Newts have a small mutation rate and a larger effect size for the same set of generations one replica of the same simulation shows the the snakes are winning and one simulation shows that the newts are winning.
+This could be that the newts got a few "lucky" mutations creating a higher phenotype leading them to "win" the co-evolutionary arms race or that the newts have not gotten any mutations or large effect and the snakes have slowly accumulated more mutations which have less of effect.
+
+(there could still be an advantage from the beginning)
+
 ```{r, heatmap}
@@
 
-build_heatmap(lit_30_G2_file, min_gen=5000, max_gen=10000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(lit_30_G2_file, min_gen=5000, max_gen=10000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
-build_heatmap(lit_30_G2_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(lit_30_G2_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 
-unique(lit_30_G2_file$snake)
+#unique(lit_30_G2_file$snake)
 #params$newt_snake <- paste0(params$newt, "_", params$snake)
@@
 lit_30_file_min<-lit_30_file[which(lit_30_file$generation>=5000 & lit_30_file$generation<=5550),]
+p <- lit_30_file_min %>%
+  plot_ly(
+    x = ~Newt_pop_size, 
+    y = ~Snake_pop_size, 
+    color = ~factor(snake), 
+    size = ~size,
+    frame = ~generation, 
+    text = ~factor(newt_snake_rep), 
+    hoverinfo = "text",
+    type = 'scatter',
+    mode = 'markers'
+  ) %>%
+  layout(
+    xaxis = list(
+      type = "log"
+    )
+  )
+
+#p
+
+lit_30_file_min<-lit_30_file[which(lit_30_file$generation>=0 & lit_30_file$generation<=30000),]
 p <- lit_30_file_min %>%
@@
 
-lit_30_G2_file_mini<-lit_30_G2_file[which(lit_30_G2_file$generation>=0 & lit_30_G2_file$generation<=5000),]
+lit_30_G2_file_mini<-lit_30_G2_file[which(lit_30_G2_file$generation>=0 & lit_30_G2_file$generation<=30000),]
 p <- lit_30_G2_file_mini %>%
@@
     y = ~Snake_pop_size, 
-    color = ~factor(sim), 
-    #shape = ~factor(newt)
+    color = ~factor(snake), 
+    size = ~size,
     frame = ~generation, 

### 2022-04-21 graphs_newt_snakes/GAs_conclusion.Rmd
more wrting and figure updating

@@
 ```{r, graphing by gen}
-trends_by_gen(lit_30_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+trends_by_gen(lit_30_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations")
 
-trends_by_gen(lit_30_G2_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Snake Popsize", x_label="Newt Popsize")
+trends_by_gen(lit_30_G2_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Mean Phenotype", x_label="Generations")
 
@@
 
+This next section is a more visual representation of the summary plots.
+Here, there will be four heatmaps.
+The first two show the results from the GA1 experiment with the last two showing the results from the GA2 experiment.
+The heatmaps have the newt GAs on the x-axis and the snake GAs and the simulation replication number on the y-axis.
+The colors in the heat might will either be yellow to purple for the snake population size or blue to red for the difference in mean phenotypes.
+
 ```{r, heatmap}
@@
 
-lit_30_file$newt_snake_rep <- paste0(lit_30_file$newt_mu_rate, "_", lit_30_file$newt_mu_effect_sd, "_", lit_30_file$snake_mu_rate, "_", lit_30_file$snake_mu_effect_sd, "_", lit_30_file$rep)
+lit_30_file$newt_snake_rep <- paste0("Newt_",lit_30_file$newt_mu_rate, "_", lit_30_file$newt_mu_effect_sd, "_Snake_",lit_30_file$snake_mu_rate, "_", lit_30_file$snake_mu_effect_sd, "_", lit_30_file$rep)
 
@@
 
-lit_30_G2_file$newt_snake_rep <- paste0(lit_30_G2_file$newt_mu_rate, "_", lit_30_G2_file$newt_mu_effect_sd, "_", lit_30_G2_file$snake_mu_rate, "_", lit_30_G2_file$snake_mu_effect_sd, "_", lit_30_G2_file$rep)
+lit_30_G2_file$newt_snake_rep <- paste0("Newt_",lit_30_G2_file$newt_mu_rate, "_", lit_30_G2_file$newt_mu_effect_sd, "_Snake_", lit_30_G2_file$snake_mu_rate, "_", lit_30_G2_file$snake_mu_effect_sd, "_", lit_30_G2_file$rep)
 
@@
     frame = ~generation, 
-    text = ~factor(sim), 
+    text = ~factor(newt_snake_rep), 
     hoverinfo = "text",

### 2022-05-19 graphs_newt_snakes/Comparing_GA.Rmd
I forgot to add in the paper suggestions. They are there now
finished writing my thoghts on GA2 and fixed some title error on GA1
I am improving my work and figures. No huge changes in slim. I am fixing some of the graphs in the r markdown and I fixed one huge mistage in the GAs conclusion. I am current working on the cor part 2 and will have a cool graph by the end of tonight hopefully

@@
   facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
 dif
+# for the poster
+# title="Newt & Snake Mean Phenotype as Generations Increases"
+# subt="Newt & Snake GA: Mutation Rate 1e-10, Effect size 0.5"
+# y_label="Mean Phenotype"
+# x_label="Generations"
+# ggplot(GA_file_100[ which(GA_file_100$gen!=1 & GA_file_100$sim=="K"),]) +
+#   xlim(0, 30000)+
+#   ggtitle(title, subtitle = subt) +
+#   xlab(x_label) + ylab(y_label)+
+#   geom_line(aes(x=as.numeric(gen), y=as.numeric(Snake_mean_Pheno)),size=1, color = "steelblue")+
+#   geom_line(aes(x=as.numeric(gen), y=as.numeric(Newt_mean_Pheno)),size=1, color = "darkred")+
+#   theme(plot.title = element_text(size=5)) +
+#   #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+#   #labs(colour = color_label) +
+#   #facet_wrap(~sim)+
+#   theme_bw(base_size = 14,) 
+# theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14),
+#                       axis.text.y = element_text(size = 14), 
+#                       strip.background = element_blank(), 
+#                       axis.text=element_text(size=16), 
+#                       axis.title=element_text(size=18),
+#                       strip.text.x = element_blank())
 ```
@@
 
-##Heatmap
+## Heatmap
 
@@
 There are some papers that I would like to read and think about:
+
+Interactions between Genetic Drift, Gene Flow, and Selection Mosaics Drive Parasite Local Adaptation
+
+Rethinking Conventional Wisdom: Are Locally Adapted Parasites Ahead in the Coevolutionary Race?
+
+Evolution of spatially structured host–parasite interactions

### 2022-05-19 graphs_newt_snakes/Dac_2022.Rmd
I am improving my work and figures. No huge changes in slim. I am fixing some of the graphs in the r markdown and I fixed one huge mistage in the GAs conclusion. I am current working on the cor part 2 and will have a cool graph by the end of tonight hopefully

---
title: "graph dor DAC"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, fitness graph}
setCOST=100
Phenotype= seq(1, 20, 0.5)
the_y = exp(-(Phenotype/setCOST)^2)

plot(Phenotype, the_y, type="l", lwd=3)

Phenotype= seq(1, 20, 0.5)
Cost = 1-exp(-(Phenotype/setCOST)^2)

plot(Phenotype, Cost, type="l", lwd=3)
#how to change this to the probably of survival

```

### 2022-05-19 graphs_newt_snakes/GAs_conclusion.Rmd
I am improving my work and figures. No huge changes in slim. I am fixing some of the graphs in the r markdown and I fixed one huge mistage in the GAs conclusion. I am current working on the cor part 2 and will have a cool graph by the end of tonight hopefully

@@
 
-para_table <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit.csv", header = TRUE)
+para_table <- read.csv("/Users/victoria/Desktop/Coevo/data/GA1_values.csv", header = TRUE)
 para_table$trial<-LETTERS[para_table$trial]
@@
   xlab(x_label) + ylab(y_label)+
-  geom_tile(aes(fill = get(fill_line)))
+  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
  if(red_blue==FALSE){
@@
     facet_wrap(~sim)+
-    geom_line(aes(generation, dif, col="dif"))+
+    geom_line(aes(generation, dif, group=rep, col="dif"))+
     ggtitle(title, subtitle = subt) +
-    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+
-    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"))+
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
     ylim(-5,10)+
@@
 
-GA_summary(lit_30_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 25sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(lit_30_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
-GA_summary(lit_30_G2_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(lit_30_G2_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 25sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
@@
 
-build_heatmap(lit_30_G2_file, min_gen=5000, max_gen=10000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+#build_heatmap(lit_30_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=F)
+
+build_heatmap(lit_30_G2_file, min_gen=10000, max_gen=11000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(lit_30_G2_file, min_gen=000, max_gen=5000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(lit_30_G2_file, min_gen=15000, max_gen=20000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(lit_30_G2_file, min_gen=20000, max_gen=25000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(lit_30_G2_file, min_gen=25000, max_gen=30000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 

### 2022-05-19 graphs_newt_snakes/correlation_part2.Rmd
I am improving my work and figures. No huge changes in slim. I am fixing some of the graphs in the r markdown and I fixed one huge mistage in the GAs conclusion. I am current working on the cor part 2 and will have a cool graph by the end of tonight hopefully

--- 2022-04-12 graphs_newt_snakes/correlation_part2.Rmd
@@
 snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
+
 snewt$mean_res = snewt$mean_toxin+snewt$dif
@@
 how to proportion and recreate what I see in the slim map (the different box and their dims)
+
+GA1 experiment values:
+
+- 1e-8*(0.005)^2 = 2.5e-13
+- 1e-9*(0.05)^2 = 2.5e-12
+- 1e-10*(0.5)^2 = 2.5e-11
+- 1e-11*(5.0)^2 = 2.5e-10
+
+GA2 experiment values:
+
+- 1e-8*(0.05)^2 = 2.5e-11
+- 1e-9*(0.1581139)^2 = 2.5e-11
+- 1e-10*(0.5)^2 = 2.5e-11
+- 1e-11*(1.581139)^2 = 2.5e-11
+- 1e-12*(5)^2 = 2.5e-11
+
+```{r, cor by location}
+
+#cor_grid_30 <- list.files(path="~/Desktop/GA1_rep", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+#cor_grid_30_G2 <- list.files(path="~/Desktop/GA2_rep", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+cor_grid_30 <- list.files(path="~/Desktop/GA1_csv_notperarea", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+cor_grid_30_G2 <- list.files(path="~/Desktop/GA2_csv_notperarea", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+
+cor_grid_30_file<-read.csv(cor_grid_30[1], header = TRUE)
+replica <- unlist(str_split(unlist(str_split(cor_grid_30[1],"rep_"))[3], "_"))[1]
+cor_grid_30_file$rep<-replica
+cor_grid_30_file$sim <-"A"
+cor_grid_30_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30[1],"rep_"))[3], "_"))[1]
+cor_grid_30_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[1],"snake_mu_rate_"))[2], "_"))[1]
+cor_grid_30_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[1],"newt_mu_rate_"))[2], "_"))[1]
+cor_grid_30_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[1],"snake_mu_effect_sd_"))[2], "_"))[1]
+cor_grid_30_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[1],"newt_mu_effect_sd_"))[2], "_"))[1]
+
+cor_grid_30_G2_file<-read.csv(cor_grid_30_G2[1], header = TRUE)
+replica <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"rep_"))[3], "_"))[1]
+cor_grid_30_G2_file$rep<-replica
+cor_grid_30_G2_file$sim <-"A"
+cor_grid_30_G2_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"rep_"))[3], "_"))[1]
+cor_grid_30_G2_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"snake_mu_rate_"))[2], "_"))[1]
+cor_grid_30_G2_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"newt_mu_rate_"))[2], "_"))[1]
+cor_grid_30_G2_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"snake_mu_effect_sd_"))[2], "_"))[1]
+cor_grid_30_G2_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30_G2[1],"newt_mu_effect_sd_"))[2], "_"))[1]
+
+oldstand=0
+letter=1
+for(i in seq(1, length(cor_grid_30_G2), 1)){
+  stand <- unlist(str_split(unlist(str_split(cor_grid_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
+  if (stand!=oldstand){
+    oldstand=stand
+    #letter = letter + 1
+  }
+  letter = i
+  GA2_lit_temp_file <- read.csv(cor_grid_30_G2[i], header = TRUE)
+  GA2_lit_temp_file$sim <-LETTERS[letter]
+  GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30_G2[i],"rep_"))[3], "_"))[1]
+  GA2_lit_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30_G2[i],"snake_mu_rate_"))[2], "_"))[1]
+GA2_lit_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_rate_"))[2], "_"))[1]
+GA2_lit_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+GA2_lit_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+
+  cor_grid_30_G2_file <- rbind(cor_grid_30_G2_file, GA2_lit_temp_file)
+
+  if (i<=length(cor_grid_30)){
+  cor_temp_file <- read.csv(cor_grid_30[i], header = TRUE)
+  cor_temp_file$sim <-LETTERS[letter]
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(cor_grid_30[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_rate_"))[2], "_"))[1]
+cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_rate_"))[2], "_"))[1]
+cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  cor_grid_30_file <- rbind(cor_grid_30_file, cor_temp_file)
+  rep <-unlist(str_split(unlist(str_split(cor_grid_30[i],"rep_"))[3], "_"))[1]
+
+  snake_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_rate_"))[2], "_"))[1]
+  newt_mu_rate <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_rate_"))[2], "_"))[1]
+  snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_grid_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  print(paste0("Simulation ", LETTERS[letter],": Snake mu-rate & effect sd (", snake_mu_rate,", ", snake_mu_effect_sd, ") Newt mu-rate & effect sd (", newt_mu_rate, ", ", newt_mu_effect_sd, ")",  " rep: ", rep))
+  }
+
+}
+
+```
+
+```{r, small sample}
+
+cor_grid_30_file$snake <- paste0(cor_grid_30_file$snake_mu_rate, "_",cor_grid_30_file$snake_mu_effect_sd)
+cor_grid_30_file$newt <- paste0(cor_grid_30_file$newt_mu_rate, "_",cor_grid_30_file$newt_mu_effect_sd)
+
+cor_grid_30_file$newt_snake_rep <- paste0("Newt_",cor_grid_30_file$newt_mu_rate, "_", cor_grid_30_file$newt_mu_effect_sd, "_Snake_",cor_grid_30_file$snake_mu_rate, "_", cor_grid_30_file$snake_mu_effect_sd, "_", cor_grid_30_file$rep)
+
+#GA1_mean = cor_grid_30_file[ , grepl( "mean" , names( cor_grid_30_file ) ) ]
+
+#unique(cor_grid_30_file$newt_snake_rep)
+
+GA1<-cor_grid_30_file[which(cor_grid_30_file$generation>=10000 & cor_grid_30_file$gen<=110000 ),]
+#GA2<-cor_grid_30_G2_file[which(cor_grid_30_G2_file$generation>=10000 & cor_grid_30_G2_file$gen<=110000 ),]
+#length(GA1$generation)
+
+#GA1<-cor_grid_30_file[which(cor_grid_30_file$generation<=50 & cor_grid_30_file$newt_snake_rep=="Newt_1.0e-08_0.005_Snake_1.0e-09_0.05_2"),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+#How to remake the dataframe into gen, newt_value, snake_value, location (x, y)?
+
+GA1_t <- data.frame(t(GA1_mean))
+
+loc_x = 1
+loc_y = 5
+skip = 1
+GA1_t$loc_x = 0
+GA1_t$loc_y = 0
+GA1_t$species = 0
+grid_info <- as.character(rownames(GA1_t))
+for (i in 2:nrow(GA1_t)){
+   #print(as.numeric(unlist(str_split(i,"_pheno_"))[2]))
+
+  GA1_t$species[i] = unlist(str_split(grid_info[i],"_mean"))[1]
+
+  if(loc_y==0){
+    loc_x = loc_x + 1
+    loc_y = 5
+  }
+  #print(paste0(loc_x, " ", loc_y))
+  GA1_t$loc_x[i]= loc_x
+GA1_t$loc_y[i] = loc_y
+
+  if (skip %% 2 == 0 ){
+    loc_y = loc_y - 1
+  } 
+  skip = skip +1
+
+}
+
+GA1_t$names<- rownames(GA1_t)
+
+GA1_mean = cor_grid_30_file[,grepl( "mean" , names(cor_grid_30_file)) ]
+GA1_mean$generation <- cor_grid_30_file$generation
+GA1_mean$rep <- cor_grid_30_file$rep
+GA1_mean$snake_mu_rate <- cor_grid_30_file$snake_mu_rate
+GA1_mean$newt_mu_rate <- cor_grid_30_file$newt_mu_rate
+GA1_mean$snake_mu_effect_sd <- cor_grid_30_file$snake_mu_effect_sd
+GA1_mean$newt_mu_effect_sd <- cor_grid_30_file$newt_mu_effect_sd
+GA1_mean$snake <- cor_grid_30_file$snake
+GA1_mean$newt <- cor_grid_30_file$newt
+GA1_mean$newt_snake_rep <- cor_grid_30_file$newt_snake_rep
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_24, factor_key=TRUE)
+
+data_long_mean$lox <- GA1_t[match(data_long_mean$condition, GA1_t$names),"loc_x"]
+data_long_mean$loy <- GA1_t[match(data_long_mean$condition, GA1_t$names),"loc_y"]
+data_long_mean$species <- GA1_t[match(data_long_mean$condition, GA1_t$names),"species"]
+
+GA1_max = cor_grid_30_file[,grepl( "max" , names(cor_grid_30_file)) ]
+GA1_max$generation <- cor_grid_30_file$generation
+GA1_max$rep <- cor_grid_30_file$rep
+GA1_max$snake_mu_rate <- cor_grid_30_file$snake_mu_rate
+GA1_max$newt_mu_rate <- cor_grid_30_file$newt_mu_rate
+GA1_max$snake_mu_effect_sd <- cor_grid_30_file$snake_mu_effect_sd
+GA1_max$newt_mu_effect_sd <- cor_grid_30_file$newt_mu_effect_sd
+GA1_max$snake <- cor_grid_30_file$snake
+GA1_max$newt <- cor_grid_30_file$newt
+GA1_max$newt_snake_rep <- cor_grid_30_file$newt_snake_rep
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_24, factor_key=TRUE)
+
+data_long_max$lox <- data_long_mean$lox 
+data_long_max$loy <- data_long_mean$loy
+data_long_max$species <- data_long_mean$species
+
+```
+
+```{r, grid graph values}
+
+GA1_onefile<-data_long_mean[which(data_long_mean$newt_snake_rep=="Newt_1.0e-10_0.5_Snake_1.0e-10_0.5_0" & data_long_max$gen==29981 ),]
+
+#GA1_onefile<-data_long_mean[which(data_long_mean$newt_snake_rep==unique(data_long_mean$newt_snake_rep)[16] & data_long_max$gen==29981 ),]
+
+#GA1_onefile<-data_long_max[which(data_long_max$newt_snake_rep=="Newt_1.0e-10_0.5_Snake_1.0e-10_0.5_0" & data_long_max$gen==29051 ),]
+
+ggplot(GA1_onefile)+
+
+  geom_point(data = GA1_onefile[which(GA1_onefile$species=="snake"),], aes(x = lox, y = loy, fill = measurement), size = 10, shape = 22, ) +
+  geom_point(data = GA1_onefile[which(GA1_onefile$species=="newt"),], aes(x = lox, y = loy, fill = measurement), size = 7, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()
+
+```
+
+```{r, corelation plots}
+
+cor_files <- list.files(path="~/Desktop/GA1_rep", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+cor_GA2_files <- list.files(path="~/Desktop/GA2_rep", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+lit_30 <- list.files(path="~/Desktop/GA1_rep", pattern="_lit_", full.names=TRUE, recursive=FALSE)
+lit_30_G2 <- list.files(path="~/Desktop/GA2_rep", pattern="_lit_", full.names=TRUE, recursive=FALSE)
+
+lit_30_file<- data.frame()
+lit_30_G2_file <- data.frame()
+
+number=1
+#cor_file <- read.csv(cor_files[number], header = TRUE)
+#cor_file$sim <-"A"
+#cor_GA2_file <- read.csv(cor_GA2_files[number], header = TRUE)
+#cor_GA2_file$sim <-"A"
+
+cor_file<- data.frame()
+cor_GA2_file<- data.frame()
+oldstand=0
+letter=0
+newt_unique=0
+newt_numb = 0
+for(i in seq(1, length(cor_GA2_files), 1)){
+  stand <- unlist(str_split(unlist(str_split(cor_GA2_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  up <- unlist(str_split(unlist(str_split(cor_GA2_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  phrase = paste0(stand, "_", up)
+  if (stand!=oldstand){
+    oldstand=stand
+    letter = letter + 1
+  }
+
+    if (phrase=="1.0e-08_0.05" ){
+    newt_numb =  1
+   }
+    if (phrase=="1.0e-09_0.158114"){
+    newt_numb =  2
+   }
+      if (phrase=="1.0e-10_0.5"){
+    newt_numb =  3
+   }
+    if (phrase=="1.0e-11_1.58114"){
+    newt_numb =  4
+   }
+
+      if (phrase=="1.0e-12_5.0"){
+    newt_numb =  5
+   }
+
+  GA2_cor_temp_file <- read.csv(cor_GA2_files[i], header = TRUE)
+  GA2_cor_temp_file$sim <-LETTERS[letter]
+  GA2_cor_temp_file$size <-newt_numb
+  GA2_cor_temp_file$rep <-unlist(str_split(unlist(str_split(cor_GA2_files[i],"rep_"))[3], "_"))[1]
+  GA2_cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_GA2_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  GA2_cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_GA2_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  GA2_cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_GA2_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  GA2_cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_GA2_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+
+  cor_GA2_file <- rbind(cor_GA2_file, GA2_cor_temp_file)
+
+  GA2_lit_temp_file <- read.csv(lit_30_G2[i], header = TRUE)
+  GA2_lit_temp_file$sim <-LETTERS[letter]
+  GA2_lit_temp_file$size <-newt_numb
+  GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30_G2[i],"rep_"))[3], "_"))[1]
+  GA2_lit_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_rate_"))[2], "_"))[1]
+  GA2_lit_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
+  GA2_lit_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  GA2_lit_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+
+  lit_30_G2_file <- rbind(lit_30_G2_file, GA2_lit_temp_file)
+
+  if (i<=length(cor_files)){
+  stand <- unlist(str_split(unlist(str_split(cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  up <- unlist(str_split(unlist(str_split(cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  phrase = paste0(stand, "_", up)
+
+   if (phrase=="1.0e-08_0.005"){
+    newt_numb =  1
+   }
+    if (phrase=="1.0e-09_0.05"){
+    newt_numb =  2
+   }
+      if (phrase=="1.0e-10_0.5"){
+    newt_numb =  3
+   }
+    if (phrase=="1.0e-11_5.0"){
+    newt_numb =  4
+   }
+  cor_temp_file <- read.csv(cor_files[i], header = TRUE)
+  cor_temp_file$sim <-LETTERS[letter]
+  cor_temp_file$size <-newt_numb
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(cor_files[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  cor_file <- rbind(cor_file, cor_temp_file)
+
+  GA1_temp_file <- read.csv(lit_30[i], header = TRUE)
+  GA1_temp_file$sim <-LETTERS[letter]
+  GA1_temp_file$size <-newt_numb
+  GA1_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30[i],"rep_"))[3], "_"))[1]
+  GA1_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_rate_"))[2], "_"))[1]
+  GA1_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_rate_"))[2], "_"))[1]
+  GA1_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  GA1_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  lit_30_file <- rbind(lit_30_file, GA1_temp_file)
+
+  #print(paste0("Simulation ", LETTERS[letter],": Snake mu-rate & effect sd (", cor_temp_file$snake_mu_rate[i],", ", cor_temp_file$snake_mu_effect_sd[i], ") Newt mu-rate & effect sd (", cor_temp_file$newt_mu_rate[i], ", ",cor_temp_file$ newt_mu_effect_sd[i], ")" ))
+  }
+
+}
+lit_30_file$dif <- lit_30_file$Snake_mean_Pheno-lit_30_file$Newt_mean_Pheno
+lit_30_G2_file$dif <- lit_30_G2_file$Snake_mean_Pheno-lit_30_G2_file$Newt_mean_Pheno
+
+```
+
+```{r, cor box set up}
+
+boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_hline(yintercept=real_snewt_cor)+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+    facet_wrap(~sim)+
+    geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = subt) +
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
+    ylim(-5,10)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  return(plot)
+}
+
+boxplot_cors_by_gen(cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", 10000, 15000)
+
+boxplot_cors_by_gen(cor_GA2_file, "Simulation Correlation Comparied to Real Correlation", "GA2", "newt/snake GAs&rep", "Cor", 10000, 15000)
+
+trends_by_gen(lit_30_file, "test", "GA1", "newt/snake GAs&rep", "Cor", 10000, 15000)
+
+```

### 2022-05-19 graphs_newt_snakes/fitness_cost.Rmd
I am improving my work and figures. No huge changes in slim. I am fixing some of the graphs in the r markdown and I fixed one huge mistage in the GAs conclusion. I am current working on the cor part 2 and will have a cool graph by the end of tonight hopefully

@@
 
-files <- list.files(path="~/Desktop/data", pattern="costtest", full.names=TRUE, recursive=FALSE)
+files <- list.files(path="~/Desktop/data/cost_test", pattern="costtest_", full.names=TRUE, recursive=FALSE)
 number=1
@@
 
-costnum <- as.numeric(unlist(strsplit(files[number], split= "_"))[30])
+costnum <- as.numeric(unlist(strsplit(files[number], split= "_"))[31])
 file$cost <-costnum
@@
   temp_file <- read.table(files[i], header = TRUE)
-  costnum<-as.numeric(unlist(strsplit(files[i], split= "_"))[30])
+  costnum<-as.numeric(unlist(strsplit(files[i], split= "_"))[31])
   temp_file$cost <-costnum
@@
     xlab("Generations") + ylab("Phenotype")+
+  xlim(0, 5001)+
     theme_bw()

### 2022-05-19 graphs_newt_snakes/combo_whale.R

@@ -122,8 +122,8 @@ Newt_pop_size <- making_data_frames(files, all_of("Newt_pop_size"))
 Snake_pop_size <- making_data_frames(files, all_of("Snake_pop_size"))
 
 # Files for space results
-files_u5 <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
-
+#files_u5 <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
+files_u5<- list.files(path="~/Desktop/cor_5000/cor_byUnit/text_files", pattern="GA5_lit_", full.names=TRUE, recursive=FALSE)
 beta_n_s <- making_data_frames(files_u5, all_of("beta_n"))
 beta_s_s <- making_data_frames(files_u5, all_of("beta_s"))
 Newt_mean_Pheno_s <- making_data_frames(files_u5, all_of("Newt_mean_Pheno"))
@@ -142,7 +142,8 @@ Snake_pop_size_s <- making_data_frames(files_u5, all_of("Snake_pop_size"))
 
 vc1 <- var_by_var(Newt_pop_size, Snake_mean_Pheno, Newt_mean_Pheno, Snake_pop_size, title="NoSpace: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake-Newt Phenotype" , highcol="darkred") 
 
-vc2_s <- var_by_var(Newt_pop_size_s, Snake_mean_Pheno_s, Newt_mean_Pheno_s, Snake_pop_size_s, title="Space: Newt VS Snake Population Size Color=Phenotype", subt="sigma = 0.1, mu = 1.0e-10", y_label="Snake Popsize", x_label="Newt Popsize", colored=TRUE, color_label="Snake-Newt Phenotype", highcol="steelblue") 
+end = 3
[…]

### 2022-05-19 graphs_newt_snakes/correlation_part2.Rmd
I made some cool figures

@@
 library(mapview)
+library(ggpubr)
+theme_set(theme_pubr())
 ```
@@
 
-trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  real_snewt_var = var(snewt$dif)
+  cfile$newt_snake_rep <- paste0("Newt_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_Snake_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
+  var_cor_table=data.frame()
+
+  for(i in 1:length(unique(file$newt_snake_rep))){
+    pattern<-unique(file$newt_snake_rep)[i]
+    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]
+    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]
+
+    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
+    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+  }
+
+  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
+  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+
+  plot <- ggplot(var_cor_table) +
+  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  #xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+  return(plot)
+}
+
+trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
-    facet_wrap(~sim)+
-    geom_line(aes(generation, dif, group=rep, col="dif"))+
-    ggtitle(title, subtitle = subt) +
+  cfile$newt_snake_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]) +
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
     geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
     geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
-    ylim(-5,10)+
-    xlab(x_label) + ylab(y_label)+
+    #ylim(0,10)+
+    #xlab(x_label) + ylab(y_label)+
     scale_color_manual(name = "Type",
-values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
-labels = c("Snake", "Newt", "Dif"))+
-    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
-  return(plot)
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() +theme(legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
+                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
+
+  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]) +
+    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
+    #ggtitle(title, subtitle = subt) +
+    ylim(-1.1, 1.1)+
+    #xlab(x_label_cor) + ylab(y_label)+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(),
+                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
+
+  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]
+  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]
+  toDelete <- seq(0, nrow(cfile), 2)
+  cfile_short <-  cfile[-toDelete, ]
+  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
+    print(paste0("pattern ", pattern))
+  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
+  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
+  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
+  return(figure)
 }
+
+```
+
+```{r, myplots}
 
@@
 
-trends_by_gen(lit_30_file, "test", "GA1", "newt/snake GAs&rep", "Cor", 10000, 15000)
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=5000, pattern="1.0e-10_0.5_1.0e-10_0.5_3")
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=10000, max_gen=15000, pattern="1.0e-10_0.5_1.0e-10_0.5_3")
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=5000, pattern="1.0e-08_0.005_1.0e-08_0.005_1")
+
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern="1.0e-09_0.05_1.0e-08_0.005_2")
+
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern="1.0e-08_0.005_1.0e-09_0.05_2")
+
+trends_by_gen(lit_30_G2_file, cor_GA2_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern="1.0e-08_0.05_1.0e-08_0.05_2")
 
 ```
+
+```{r, varation}
+snake_info<-data_long_mean[which(data_long_mean$species=="snake"),]
+newt_info<-data_long_mean[which(data_long_mean$species=="newt"),]
+
+names(newt_info)[names(newt_info) == 'measurement'] <- 'newt_toxin'
+newt_info$snake_res<-snake_info$measurement
+newt_info$dif<-newt_info$snake_res-newt_info$newt_toxin
+
+var_cor(newt_info, cor_file, "var by cor", "mini", "var", "cor", 10000, 15000)
+
+```

### 2022-05-19 graphs_newt_snakes/correlation_part2.Rmd
Peter and I talked about the per unit caculations and found an error in the correlations

@@
 
-GA1_onefile<-data_long_mean[which(data_long_mean$newt_snake_rep=="Newt_1.0e-10_0.5_Snake_1.0e-10_0.5_0" & data_long_max$gen==29981 ),]
+GA1_onefile<-data_long_mean[which(data_long_mean$newt_snake_rep=="Newt_1.0e-10_0.5_Snake_1.0e-10_0.5_0" & data_long_max$gen==10981 ),]
 
@@
   scale_fill_viridis_c()+
+  theme_bw()
+
+unique(data_long_mean$newt_snake_rep)
+
+GA1_onefile_2<-data_long_mean[which(data_long_mean$newt_snake_rep=="Newt_1.0e-08_0.005_Snake_1.0e-08_0.005_0" & data_long_max$gen==10981 ),]
+
+ggplot(GA1_onefile_2)+
+
+  geom_point(data = GA1_onefile_2[which(GA1_onefile_2$species=="snake"),], aes(x = lox, y = loy, fill = measurement), size = 10, shape = 22, ) +
+  geom_point(data = GA1_onefile_2[which(GA1_onefile_2$species=="newt"),], aes(x = lox, y = loy, fill = measurement), size = 7, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()
+
+```
+
+```{r pheno scatter}
+
+snake_info<-data_long_mean[which(data_long_mean$species=="snake"),]
+newt_info<-data_long_mean[which(data_long_mean$species=="newt"),]
+
+names(newt_info)[names(newt_info) == 'measurement'] <- 'newt_toxin'
+newt_info$snake_res<-snake_info$measurement
+newt_info$dif<-newt_info$snake_res-newt_info$newt_toxin
+pattern<-"Newt_1.0e-08_0.005_Snake_1.0e-08_0.005_0"
+scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation>14000 & newt_info$generation<15000 ),]
+scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation==20981 ),]
+#scatter_pheno[scatter_pheno == 0] <- NA
+#scatter_pheno[scatter_pheno == 1] <- NA
+ggplot(scatter_pheno)+
+ ggtitle(paste0(" pattern ", pattern, " From ", min(scatter_pheno$generation), " gen to ", max(scatter_pheno$generation), " gen"))+
+  geom_point(aes(y = newt_toxin, x = snake_res, color=generation), size = 3) 
   theme_bw()
@@
   plot <- ggplot(var_cor_table) +
-  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
-  #xlab(x_label) + ylab(y_label)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
   geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+

### 2022-05-20 graphs_newt_snakes/GAs_conclusion.Rmd
added more figures (hist) to ga concl and looked at the corrected cor in cor rmarkdown.

@@
 
+whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  #geom_histogram(aes(dif))+
+  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+}
+
+pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(dif), fill="aquamarine4")+
+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
 ```
@@
 My question is why are there a collective difference in some of these simulation?
+
+```{r, whale}
+min_gen=5000
+max_gen=10000
+rep=0
+
+whale_gen(lit_30_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+
+pop_size_hist(lit_30_file, title="Snake-Newt Popsize Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize",  min_gen=min_gen, max_gen=max_gen, rep=rep )
+
+pheno_dif_hist(lit_30_file, title="Snake-Newt Phenotype Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype",  min_gen=min_gen, max_gen=max_gen, rep=rep )
+
+file<-lit_30_file[ which(lit_30_file$generation>=min_gen & lit_30_file$generation<=max_gen & lit_30_file$rep==rep),]
+plot.x <- ggplot(file) + geom_boxplot(aes(newt_snake_rep, dif))
+plot.y <- ggplot(file) + geom_boxplot(aes(newt_snake_rep, Snake_pop_size-Newt_pop_size))
+
+grid.arrange(plot.x, plot.y, ncol=2)
+
+plot.x <- layer_data(plot.x)[,1:6]
+plot.y <- layer_data(plot.y)[,1:6]
+colnames(plot.x) <- paste0("x.", gsub("y", "", colnames(plot.x)))
+colnames(plot.y) <- paste0("y.", gsub("y", "", colnames(plot.y)))
+df <- cbind(plot.x, plot.y); rm(plot.x, plot.y)
+df$category <- sort(unique(file$newt_snake_rep))
+df.outliers <- df %>%
+  select(category, x.middle, x.outliers, y.middle, y.outliers) %>%
+  data.table::data.table()
+#df.outliers <- df.outliers[, list(x.outliers = unlist(x.outliers), y.outliers = unlist(y.outliers)), by = list(category, x.middle, y.middle)]
+ggplot(df, aes(fill = category, color = category)) +
+
+  # 2D box defined by the Q1 & Q3 values in each dimension, with outline
+  geom_rect(aes(xmin = x.lower, xmax = x.upper, ymin = y.lower, ymax = y.upper), alpha = 0.3) +
+  geom_rect(aes(xmin = x.lower, xmax = x.upper, ymin = y.lower, ymax = y.upper), 
+            color = "black", fill = NA) +
+
+  # whiskers for x-axis dimension with ends
+  geom_segment(aes(x = x.min, y = y.middle, xend = x.max, yend = y.middle)) + #whiskers
+  geom_segment(aes(x = x.min, y = y.lower, xend = x.min, yend = y.upper)) + #lower end
+  geom_segment(aes(x = x.max, y = y.lower, xend = x.max, yend = y.upper)) + #upper end
+
+  # whiskers for y-axis dimension with ends
+  geom_segment(aes(x = x.middle, y = y.min, xend = x.middle, yend = y.max)) + #whiskers
+  geom_segment(aes(x = x.lower, y = y.min, xend = x.upper, yend = y.min)) + #lower end
+  geom_segment(aes(x = x.lower, y = y.max, xend = x.upper, yend = y.max)) + #upper end
+
+  # outliers
+  #geom_point(data = df.outliers, aes(x = x.outliers, y = y.middle), size = 3, shape = 1) + # x-direction
+  #geom_point(data = df.outliers, aes(x = x.middle, y = y.outliers), size = 3, shape = 1) + # y-direction
+
+  xlab("s-n mean pheno") + ylab("s-n pop size") +  
+  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      legend.position="right",
+                      legend.text=element_text(size=5),
+                      panel.grid.major = element_blank(), 
+                      panel.grid.minor = element_blank(),
+                      panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+```
 

### 2022-05-20 graphs_newt_snakes/correlation_part2.Rmd
added more figures (hist) to ga concl and looked at the corrected cor in cor rmarkdown.

@@
 
-cor_files <- list.files(path="~/Desktop/GA1_rep", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+cor_files <- list.files(path="~/Desktop/csv_GA1_long", pattern="_cor_", full.names=TRUE, recursive=FALSE)
 cor_GA2_files <- list.files(path="~/Desktop/GA2_rep", pattern="_cor_", full.names=TRUE, recursive=FALSE)
-lit_30 <- list.files(path="~/Desktop/GA1_rep", pattern="_lit_", full.names=TRUE, recursive=FALSE)
+lit_30 <- list.files(path="~/Desktop/csv_GA1_long", pattern="_lit_", full.names=TRUE, recursive=FALSE)
 lit_30_G2 <- list.files(path="~/Desktop/GA2_rep", pattern="_lit_", full.names=TRUE, recursive=FALSE)
@@
   file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  unique(file$sim)
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
@@
   geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
-  geom_hline(yintercept=real_snewt_cor)+
+  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+    geom_hline(yintercept=0, linetype="solid")+
   #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
@@
   theme(plot.title = element_text(size=5)) +
-  facet_wrap(~sim)+
+  facet_wrap(~newt_snake)+
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
@@
 
+four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
+  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  geom_hline(yintercept=0, linetype="solid")+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~newt_snake)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
 ```
@@
 
-boxplot_cors_by_gen(cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", 10000, 15000)
+boxplot_cors_by_gen(cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", 4000, 5000)
 
-boxplot_cors_by_gen(cor_GA2_file, "Simulation Correlation Comparied to Real Correlation", "GA2", "newt/snake GAs&rep", "Cor", 10000, 15000)
+four_types_boxplot_cors_by_gen(cor_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", 4000, 5000)
 
-trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=5000, pattern="1.0e-10_0.5_1.0e-10_0.5_3")
-trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=10000, max_gen=15000, pattern="1.0e-10_0.5_1.0e-10_0.5_3")
-trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=5000, pattern="1.0e-08_0.005_1.0e-08_0.005_1")
+boxplot_cors_by_gen(cor_GA2_file, "Simulation Correlation Comparied to Real Correlation", "GA2", "newt/snake GAs&rep", "Cor", 4000, 5000)
 
-trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern="1.0e-09_0.05_1.0e-08_0.005_2")
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=5000, pattern="1.0e-10_0.5_1.0e-10_0.5_0")
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=10000, max_gen=15000, pattern="1.0e-10_0.5_1.0e-10_0.5_0")
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=5000, pattern="1.0e-08_0.005_1.0e-08_0.005_0")
 
-trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern="1.0e-08_0.005_1.0e-09_0.05_2")
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern="1.0e-09_0.05_1.0e-08_0.005_0")
 
-trends_by_gen(lit_30_G2_file, cor_GA2_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern="1.0e-08_0.05_1.0e-08_0.05_2")
+trends_by_gen(lit_30_file, cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern="1.0e-08_0.005_1.0e-09_0.05_0")
+
+trends_by_gen(lit_30_G2_file, cor_GA2_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern="1.0e-08_0.05_1.0e-08_0.05_0")
 

### 2022-05-27 graphs_newt_snakes/GAs_conclusion.Rmd
looking at correlations, currtly things are not spatially correlated. this might be due to the small map and population size. I added H with increases the length in the simulation. I am excited to see the results

@@
   file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
+  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
   #xlim(0, 1000)+
@@
   xlab(x_label) + ylab(y_label)+
-  #geom_histogram(aes(dif))+
   geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
-  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  xlim((-1*themax)-5, themax+5)+
   theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
   facet_wrap(~sim)+
@@
   file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  themin <- min(file$dif) 
+  themax <- max(file$dif)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
   #xlim(0, 1000)+
@@
   geom_histogram(aes(dif), fill="aquamarine4")+
+  xlim((-1*true_max)-1, true_max+1)+
 
@@
 }
+
+two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
 ```
@@
 
+two_hist(lit_30_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )
+
 file<-lit_30_file[ which(lit_30_file$generation>=min_gen & lit_30_file$generation<=max_gen & lit_30_file$rep==rep),]
+file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
 plot.x <- ggplot(file) + geom_boxplot(aes(newt_snake_rep, dif))

### 2022-05-27 graphs_newt_snakes/running_100000gen.Rmd
looking at correlations, currtly things are not spatially correlated. this might be due to the small map and population size. I added H with increases the length in the simulation. I am excited to see the results

---
title: "Running 100,000 Gen"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
```

### Goal

figure out a main conclusion for the poster!

GA1 experiment values:

- 1e-8*(0.005)^2 = 2.5e-13
- 1e-9*(0.05)^2 = 2.5e-12
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(5.0)^2 = 2.5e-10

GA2 experiment values:

- 1e-8*(0.05)^2 = 2.5e-11
- 1e-9*(0.1581139)^2 = 2.5e-11
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(1.581139)^2 = 2.5e-11
- 1e-12*(5)^2 = 2.5e-11

```{r, data tables}

para_table <- read.csv("/Users/victoria/Desktop/Coevo/data/GA1_values.csv", header = TRUE)
para_table$trial<-LETTERS[para_table$trial]
para_table <- data.frame("Trial"=para_table$trial, "Snake Mu Rate"=para_table$snake_mu_rate, "Snake effect size"= para_table$snake_mu_effect_sd, "Newt Mu Rate"=para_table$newt_mu_rate, "Newt effect size"= para_table$newt_mu_effect_sd)
#kable(para_table, caption="GA2 Params")

para_table %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
    kable(., caption="GA1 Params") %>%
 kable_styling("striped")

para_table <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit_25.csv", header = TRUE)
para_table$trial<-LETTERS[para_table$trial]
para_table <- data.frame("Trial"=para_table$trial, "Snake Mu Rate"=para_table$snake_mu_rate, "Snake effect size"= para_table$snake_mu_effect_sd, "Newt Mu Rate"=para_table$newt_mu_rate, "Newt effect size"= para_table$newt_mu_effect_sd)
#kable(para_table, caption="GA2 Params")

para_table %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
    kable(., caption="GA2 Params") %>%
 kable_styling("striped")
```

```{r, data gathering}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

GA1_long <- list.files(path="~/Desktop/GA1_long_csv", pattern="_lit_", full.names=TRUE, recursive=FALSE)
GA2_long <- list.files(path="~/Desktop/GA2_long_csv", pattern="_lit_", full.names=TRUE, recursive=FALSE)
GA1_cor_files <- list.files(path="~/Desktop/GA1_long_csv", pattern="_cor_", full.names=TRUE, recursive=FALSE)
GA2_cor_files <- list.files(path="~/Desktop/GA2_long_csv", pattern="_cor_", full.names=TRUE, recursive=FALSE)

GA1_long_file<- data.frame()
GA2_long_file <- data.frame()
GA1_cor_file<- data.frame()
GA2_cor_file<- data.frame()
oldstand=0
letter=0
newt_unique=0
newt_numb = 0
for(i in seq(1, length(GA2_long), 1)){
  stand <- unlist(str_split(unlist(str_split(GA2_long[i],"newt_mu_rate_"))[2], "_"))[1]
  up <- unlist(str_split(unlist(str_split(GA2_long[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  phrase = paste0(stand, "_", up)
  if (stand!=oldstand){
    oldstand=stand
    letter = letter + 1
  }

    if (phrase=="1.0e-08_0.05" ){
    newt_numb =  1
   }
    if (phrase=="1.0e-09_0.158114"){
    newt_numb =  2
   }
      if (phrase=="1.0e-10_0.5"){
    newt_numb =  3
   }
    if (phrase=="1.0e-11_1.58114"){
    newt_numb =  4
   }

      if (phrase=="1.0e-12_5.0"){
    newt_numb =  5
   }

  GA2_lit_temp_file <- read.csv(GA2_long[i], header = TRUE)
  GA2_lit_temp_file$sim <-LETTERS[letter]
   GA2_lit_temp_file$size <-newt_numb
  GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(GA2_long[i],"rep_"))[3], "_"))[1]
  GA2_lit_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA2_long[i],"snake_mu_rate_"))[2], "_"))[1]
  GA2_lit_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA2_long[i],"newt_mu_rate_"))[2], "_"))[1]
  GA2_lit_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_long[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  GA2_lit_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_long[i],"newt_mu_effect_sd_"))[2], "_"))[1]

  GA2_cor_temp_file <- read.csv(GA2_cor_files[i], header = TRUE)
  GA2_cor_temp_file$sim <-LETTERS[letter]
  GA2_cor_temp_file$size <-newt_numb
  GA2_cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA2_cor_files[i],"rep_"))[3], "_"))[1]
  GA2_cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA2_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
  GA2_cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA2_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
  GA2_cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  GA2_cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]

  GA2_cor_file <- rbind(GA2_cor_file, GA2_cor_temp_file)

  GA2_long_file <- rbind(GA2_long_file, GA2_lit_temp_file)

  if (i<=length(GA1_long)){

  stand <- unlist(str_split(unlist(str_split(GA1_long[i],"newt_mu_rate_"))[2], "_"))[1]
  up <- unlist(str_split(unlist(str_split(GA1_long[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  phrase = paste0(stand, "_", up)

   if (phrase=="1.0e-08_0.005"){
    newt_numb =  1
   }
    if (phrase=="1.0e-09_0.05"){
    newt_numb =  2
   }
      if (phrase=="1.0e-10_0.5"){
    newt_numb =  3
   }
    if (phrase=="1.0e-11_5.0"){
    newt_numb =  4
   }

  GA1_temp_file <- read.csv(GA1_long[i], header = TRUE)
  GA1_temp_file$sim <-LETTERS[letter]
  GA1_temp_file$size <-newt_numb
  GA1_temp_file$rep <-unlist(str_split(unlist(str_split(GA1_long[i],"rep_"))[3], "_"))[1]
  GA1_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA1_long[i],"snake_mu_rate_"))[2], "_"))[1]
  GA1_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA1_long[i],"newt_mu_rate_"))[2], "_"))[1]
  GA1_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_long[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  GA1_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_long[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  GA1_long_file <- rbind(GA1_long_file, GA1_temp_file)

  cor_temp_file <- read.csv(GA1_cor_files[i], header = TRUE)
  cor_temp_file$sim <-LETTERS[letter]
  cor_temp_file$size <-newt_numb
  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA1_cor_files[i],"rep_"))[3], "_"))[1]
  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA1_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA1_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  GA1_cor_file <- rbind(GA1_cor_file, cor_temp_file)

  }

}

GA1_long_file$dif <- GA1_long_file$Snake_mean_Pheno-GA1_long_file$Newt_mean_Pheno
GA2_long_file$dif <- GA2_long_file$Snake_mean_Pheno-GA2_long_file$Newt_mean_Pheno
```

```{r, cor box set up}

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~newt_snake)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=rep))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~newt_snake)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~newt_snake)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  real_snewt_var = var(snewt$dif)
  cfile$newt_snake_rep <- paste0("Newt_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_Snake_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
  var_cor_table=data.frame()

  for(i in 1:length(unique(file$newt_snake_rep))){
    pattern<-unique(file$newt_snake_rep)[i]
    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]
    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]

    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  }

  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)

  plot <- ggplot(var_cor_table) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

  return(plot)
}

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
 file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  cfile$newt_snake_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]
  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]
  toDelete <- seq(0, nrow(cfile), 2)
  cfile_short <-  cfile[-toDelete, ]
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}

four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~newt_snake)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

```

```{r, general file and graph making}

#the functions to make the params file and the summary and heatmap figures

create_parm_file <- function(file, min_gen, max_gen){
params <- data_frame()

for(i in 1:length(unique(file$newt_snake_rep))){

  pattern=unique(file$newt_snake_rep)[i]
  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep ==pattern),]

  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=sumitup$snake_mu_rate[1],
                           newt_mu_rate=sumitup$newt_mu_rate[1],
                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
                           rep=sumitup$rep[1])

  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$newt_snake <- paste0(params$newt, "_", params$snake)
return(params)
}

GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}

build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)

  params<-create_parm_file(file, min_gen, max_gen)

 my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
 if(red_blue==FALSE){
  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text)
  }
 if(red_blue==TRUE){
  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text)
 }
  return(my_plot)
}

trends_by_gen <- function(file, title, subt, x_label, y_label){

  plot <- ggplot(file) +
    facet_wrap(~sim)+
    geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = subt) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    ylim(-5,10)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
  return(plot)
}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
  xlim((-1*themax)-5, themax+5)+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)
}

pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  themin <- min(file$dif) 
  themax <- max(file$dif)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(dif), fill="aquamarine4")+
  xlim((-1*true_max)-1, true_max+1)+

  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

```

First, I will look at a plot of how the mean phenotype of newts and snakes changes overtime. Each of these plots contains four replicas for all GA combinations (letter label is the experiment that was run, 16 Sim is from GA1 and 25 Sim is from GA2). Each of these plots has three lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype. Note this is a mean for the entire population.

```{r, graphing by gen}
trends_by_gen(GA1_long_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations")

trends_by_gen(GA2_long_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Mean Phenotype", x_label="Generations")

```

```{r, whale}
min_gen=5000
max_gen=10000
rep=0

whale_gen(GA1_long_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )

#pop_size_hist(GA1_long_file, title="Snake-Newt Popsize Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize",  min_gen=min_gen, max_gen=max_gen, rep=rep )

#pheno_dif_hist(GA1_long_file, title="Snake-Newt Phenotype Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype",  min_gen=min_gen, max_gen=max_gen, rep=rep )

two_hist(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )

```

```{r, combo myplots}
#files
#GA1_long_file
#GA2_long_file 
#GA1_cor_file
#GA2_cor_file

ginmin = 9000
ginmax = 10000

boxplot_cors_by_gen(GA1_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

boxplot_cors_by_gen(GA2_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA2", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

four_types_boxplot_cors_by_gen(GA1_cor_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

four_types_boxplot_cors_by_gen(GA2_cor_file, "Simulation four Correlation", "GA2", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

hist_cors_by_gen_col_rep(GA1_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

hist_cors_by_gen_col_rep(GA2_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

hist_cors_by_gen_col_rep_nofill(GA1_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

```{r, ga1 cor and pheno}
GA1_pattern <- unique(paste0(GA1_long_file$snake_mu_rate, "_", GA1_long_file$snake_mu_effect_sd,"_",GA1_long_file$newt_mu_rate, "_", GA1_long_file$newt_mu_effect_sd, "_", GA1_long_file$rep))
for(i in 1:length(GA1_pattern)){
  myine<-cor_trends_by_gen(GA1_long_file, GA1_cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern=GA1_pattern[i])
  plot(myine)
}

```

```{r, ga2 cor}
GA2_pattern <- unique(paste0(GA2_long_file$newt_mu_rate, "_", GA2_long_file$newt_mu_effect_sd, "_", GA2_long_file$snake_mu_rate, "_", GA2_long_file$snake_mu_effect_sd, "_", GA2_long_file$rep))

for(i in 1:length(GA2_pattern)){
  myine<-cor_trends_by_gen(GA2_long_file, GA2_cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern=GA2_pattern[i])
  plot(myine)
}

```

```{r, early plots}

min_gen=5000
max_gen=10000

for(i in 1:length(unique(GA1_long_file$rep))){
  myine<-whale_gen(GA1_long_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i])
  plot(myine)
  myine<-two_hist(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i] )
  plot(myine)
}

cor_trends_by_gen(GA1_long_file, GA1_cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-08_0.005_1.0e-09_0.05_0")

```

```{r, mis plots}

min_gen=20000
max_gen=25000
rep=0

for(i in 1:length(unique(GA1_long_file$rep))){
  myine<-whale_gen(GA1_long_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i])
  plot(myine)
  myine<-two_hist(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i] )
  plot(myine)
}

cor_trends_by_gen(GA1_long_file, GA1_cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-08_0.005_1.0e-09_0.05_0")

```

```{r, late plots}

min_gen=95000
max_gen=100000
rep=0

for(i in 1:length(unique(GA1_long_file$rep))){
  myine<-whale_gen(GA1_long_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i])
  plot(myine)
  myine<-two_hist(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i] )
  plot(myine)
}

cor_trends_by_gen(GA1_long_file, GA1_cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-08_0.005_1.0e-09_0.05_0")

```

```{r, really cool square plots}
file<-GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep),]
file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
plot.x <- ggplot(file) + geom_boxplot(aes(newt_snake_rep, dif))
plot.y <- ggplot(file) + geom_boxplot(aes(newt_snake_rep, Snake_pop_size-Newt_pop_size))

grid.arrange(plot.x, plot.y, ncol=2)

plot.x <- layer_data(plot.x)[,1:6]
plot.y <- layer_data(plot.y)[,1:6]
colnames(plot.x) <- paste0("x.", gsub("y", "", colnames(plot.x)))
colnames(plot.y) <- paste0("y.", gsub("y", "", colnames(plot.y)))
df <- cbind(plot.x, plot.y); rm(plot.x, plot.y)
df$category <- sort(unique(file$newt_snake_rep))
df.outliers <- df %>%
  select(category, x.middle, x.outliers, y.middle, y.outliers) %>%
  data.table::data.table()
#df.outliers <- df.outliers[, list(x.outliers = unlist(x.outliers), y.outliers = unlist(y.outliers)), by = list(category, x.middle, y.middle)]
ggplot(df, aes(fill = category, color = category)) +

  # 2D box defined by the Q1 & Q3 values in each dimension, with outline
  geom_rect(aes(xmin = x.lower, xmax = x.upper, ymin = y.lower, ymax = y.upper), alpha = 0.3) +
  geom_rect(aes(xmin = x.lower, xmax = x.upper, ymin = y.lower, ymax = y.upper), 
            color = "black", fill = NA) +

  # whiskers for x-axis dimension with ends
  geom_segment(aes(x = x.min, y = y.middle, xend = x.max, yend = y.middle)) + #whiskers
  geom_segment(aes(x = x.min, y = y.lower, xend = x.min, yend = y.upper)) + #lower end
  geom_segment(aes(x = x.max, y = y.lower, xend = x.max, yend = y.upper)) + #upper end

  # whiskers for y-axis dimension with ends
  geom_segment(aes(x = x.middle, y = y.min, xend = x.middle, yend = y.max)) + #whiskers
  geom_segment(aes(x = x.lower, y = y.min, xend = x.upper, yend = y.min)) + #lower end
  geom_segment(aes(x = x.lower, y = y.max, xend = x.upper, yend = y.max)) + #upper end

  # outliers
  #geom_point(data = df.outliers, aes(x = x.outliers, y = y.middle), size = 3, shape = 1) + # x-direction
  #geom_point(data = df.outliers, aes(x = x.middle, y = y.outliers), size = 3, shape = 1) + # y-direction

  xlab("s-n mean pheno") + ylab("s-n pop size") +  
  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      legend.position="right",
                      legend.text=element_text(size=5),
                      panel.grid.major = element_blank(), 
                      panel.grid.minor = element_blank(),
                      panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

```

Next, I will discuss a summary plot for the different GA sets. The first plot has the newt population size by snake population size (a larger population size might indicate a co-evolution advantage) and the second plot is the difference between snake and newt mean phenotype and snake population size. There are four points for each GA set (one for each replica). Color will represent the four GAs of the snake and the shapes will represent the four GAs of newts. Each plot will have a starting generation and an ending generation (that can easily be changed).

```{r, graphing the summary}

GA_summary(GA1_long_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

GA_summary(GA1_long_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

GA_summary(GA2_long_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 25sims", y_label="Snake Popsize", x_label="Newt Popsize")

GA_summary(GA2_long_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 25sims", y_label="Snake Popsize", x_label="Dif")

```

This next section is a more visual representation of the summary plots. Here, there will be four heatmaps. The first two show the results from the GA1 experiment with the last two showing the results from the GA2 experiment. The heatmaps have the newt GAs on the x-axis and the snake GAs and the simulation replication number on the y-axis. The colors in the heat might will either be yellow to purple for the snake population size or blue to red for the difference in mean phenotypes.

```{r, heatmap}

#params_GA1

build_heatmap(GA1_long_file, min_gen=5000, max_gen=10000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

build_heatmap(GA1_long_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

#build_heatmap(GA1_long_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=F)

build_heatmap(GA2_long_file, min_gen=10000, max_gen=11000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

build_heatmap(GA2_long_file, min_gen=000, max_gen=5000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

build_heatmap(GA2_long_file, min_gen=15000, max_gen=20000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

build_heatmap(GA2_long_file, min_gen=20000, max_gen=25000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

build_heatmap(GA2_long_file, min_gen=25000, max_gen=30000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

build_heatmap(GA2_long_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

### 2022-05-29 graphs_newt_snakes/Dac_2022.Rmd
made some more figures for the poster. started to look at the lond file named tall data. Made a back up snakemake file

@@
 ```
+
+```{r, my plots for poster}
+
+min_gen=100
+max_gen=20000
+rep=0
+unique(GA1_long_file$snake_mu_rate)
+ggplot(GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep & GA1_long_file$snake_mu_rate=="1.0e-10" & GA1_long_file$newt_mu_rate=="1.0e-10"),]) +
+    #facet_wrap(~sim)+
+    geom_line(aes(generation, dif, col="dif"), size=1 )+
+    ggtitle("test", subtitle = paste0(" From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"), size=1 )+
+    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"), size=1 )+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54", size=1 )+
+    ylim(-5,8)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+ggsave(
+  "~/Desktop/newt_snake_coevo_example.pdf",
+  plot = last_plot(),
+  scale = 1,
+  width = 7,
+  height = 5,
+  #units = c("in"),
+  dpi = 300,
+  limitsize = TRUE,
+  bg = NULL,
+)
+```

### 2022-05-29 graphs_newt_snakes/Tall_GA1.Rmd
made some more figures for the poster. started to look at the lond file named tall data. Made a back up snakemake file

--- 2022-05-27 graphs_newt_snakes/running_100000gen.Rmd
@@
 ---
-title: "Running 100,000 Gen"
+title: "Tall"
 output: html_document
@@
 
-GA2 experiment values:
-
-- 1e-8*(0.05)^2 = 2.5e-11
-- 1e-9*(0.1581139)^2 = 2.5e-11
-- 1e-10*(0.5)^2 = 2.5e-11
-- 1e-11*(1.581139)^2 = 2.5e-11
-- 1e-12*(5)^2 = 2.5e-11
-
-```{r, data tables}
-
-para_table <- read.csv("/Users/victoria/Desktop/Coevo/data/GA1_values.csv", header = TRUE)
-para_table$trial<-LETTERS[para_table$trial]
-para_table <- data.frame("Trial"=para_table$trial, "Snake Mu Rate"=para_table$snake_mu_rate, "Snake effect size"= para_table$snake_mu_effect_sd, "Newt Mu Rate"=para_table$newt_mu_rate, "Newt effect size"= para_table$newt_mu_effect_sd)
-#kable(para_table, caption="GA2 Params")
-
-para_table %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
-    kable(., caption="GA1 Params") %>%
- kable_styling("striped")
-
-para_table <- read.csv("/Users/victoria/Desktop/Coevo/data/GAtestvar_lit_25.csv", header = TRUE)
-para_table$trial<-LETTERS[para_table$trial]
-para_table <- data.frame("Trial"=para_table$trial, "Snake Mu Rate"=para_table$snake_mu_rate, "Snake effect size"= para_table$snake_mu_effect_sd, "Newt Mu Rate"=para_table$newt_mu_rate, "Newt effect size"= para_table$newt_mu_effect_sd)
-#kable(para_table, caption="GA2 Params")
-
-para_table %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
-    kable(., caption="GA2 Params") %>%
- kable_styling("striped")
-```
-
 ```{r, data gathering}
@@
 
-GA1_long <- list.files(path="~/Desktop/GA1_long_csv", pattern="_lit_", full.names=TRUE, recursive=FALSE)
-GA2_long <- list.files(path="~/Desktop/GA2_long_csv", pattern="_lit_", full.names=TRUE, recursive=FALSE)
-GA1_cor_files <- list.files(path="~/Desktop/GA1_long_csv", pattern="_cor_", full.names=TRUE, recursive=FALSE)
-GA2_cor_files <- list.files(path="~/Desktop/GA2_long_csv", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+GA1_tall <- list.files(path="~/Desktop/tall_map", pattern="_lit_", full.names=TRUE, recursive=FALSE)
+GA1_tall_cor_files <- list.files(path="~/Desktop/tall_map", pattern="_cor_", full.names=TRUE, recursive=FALSE)
 
-GA1_long_file<- data.frame()
-GA2_long_file <- data.frame()
-GA1_cor_file<- data.frame()
-GA2_cor_file<- data.frame()
+GA1_tall_tall_file<- data.frame()
+GA1_cor_tall_file<- data.frame()
+
 oldstand=0
@@
 newt_numb = 0
-for(i in seq(1, length(GA2_long), 1)){
-  stand <- unlist(str_split(unlist(str_split(GA2_long[i],"newt_mu_rate_"))[2], "_"))[1]
-  up <- unlist(str_split(unlist(str_split(GA2_long[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+for(i in seq(1, length(GA1_tall), 1)){
+  stand <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  up <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
   phrase = paste0(stand, "_", up)
@@
 
-  GA2_lit_temp_file <- read.csv(GA2_long[i], header = TRUE)
-  GA2_lit_temp_file$sim <-LETTERS[letter]
-   GA2_lit_temp_file$size <-newt_numb
-  GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(GA2_long[i],"rep_"))[3], "_"))[1]
-  GA2_lit_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA2_long[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA2_lit_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA2_long[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA2_lit_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_long[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA2_lit_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_long[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  if (i<=length(GA1_tall)){
 
-  GA2_cor_temp_file <- read.csv(GA2_cor_files[i], header = TRUE)
-  GA2_cor_temp_file$sim <-LETTERS[letter]
-  GA2_cor_temp_file$size <-newt_numb
-  GA2_cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA2_cor_files[i],"rep_"))[3], "_"))[1]
-  GA2_cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA2_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA2_cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA2_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA2_cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA2_cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA2_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-
-  GA2_cor_file <- rbind(GA2_cor_file, GA2_cor_temp_file)
-
-  GA2_long_file <- rbind(GA2_long_file, GA2_lit_temp_file)
-
-  if (i<=length(GA1_long)){
-
-  stand <- unlist(str_split(unlist(str_split(GA1_long[i],"newt_mu_rate_"))[2], "_"))[1]
-  up <- unlist(str_split(unlist(str_split(GA1_long[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  stand <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  up <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
   phrase = paste0(stand, "_", up)
@@
 
-  GA1_temp_file <- read.csv(GA1_long[i], header = TRUE)
+  GA1_temp_file <- read.csv(GA1_tall[i], header = TRUE)
   GA1_temp_file$sim <-LETTERS[letter]
   GA1_temp_file$size <-newt_numb
-  GA1_temp_file$rep <-unlist(str_split(unlist(str_split(GA1_long[i],"rep_"))[3], "_"))[1]
-  GA1_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA1_long[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA1_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA1_long[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA1_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_long[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA1_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_long[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  GA1_long_file <- rbind(GA1_long_file, GA1_temp_file)
+  GA1_temp_file$rep <-unlist(str_split(unlist(str_split(GA1_tall[i],"rep_"))[3], "_"))[1]
+  GA1_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA1_tall[i],"snake_mu_rate_"))[2], "_"))[1]
+  GA1_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  GA1_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  GA1_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  GA1_tall_tall_file <- rbind(GA1_tall_tall_file, GA1_temp_file)
 
-  cor_temp_file <- read.csv(GA1_cor_files[i], header = TRUE)
+  cor_temp_file <- read.csv(GA1_tall_cor_files[i], header = TRUE)
   cor_temp_file$sim <-LETTERS[letter]
   cor_temp_file$size <-newt_numb
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA1_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA1_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA1_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  GA1_cor_file <- rbind(GA1_cor_file, cor_temp_file)
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  GA1_cor_tall_file <- rbind(GA1_cor_tall_file, cor_temp_file)
 
@@
 
-GA1_long_file$dif <- GA1_long_file$Snake_mean_Pheno-GA1_long_file$Newt_mean_Pheno
-GA2_long_file$dif <- GA2_long_file$Snake_mean_Pheno-GA2_long_file$Newt_mean_Pheno
+GA1_tall_tall_file$dif <- GA1_tall_tall_file$Snake_mean_Pheno-GA1_tall_tall_file$Newt_mean_Pheno
 ```
@@
     #xlab(x_label_cor) + ylab(y_label)+
+    geom_hline(yintercept=0, linetype="dashed")+
     theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
@@
 
-trends_by_gen <- function(file, title, subt, x_label, y_label){
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 
-  plot <- ggplot(file) +
+  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
     facet_wrap(~sim)+
     geom_line(aes(generation, dif, group=rep, col="dif"))+
-    ggtitle(title, subtitle = subt) +
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
     geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
     geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
-    ylim(-5,10)+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
+    ylim(-10,10)+
     xlab(x_label) + ylab(y_label)+
@@
 labels = c("Snake", "Newt", "Dif"))+
-    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
   return(plot)
@@
 
+two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+  print(data_points)
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file=GA1_tall_tall_file
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$newt_deaths)
+  thepopmax <- max(file$newt_deaths)
+  thedifmin <- min(file$snake_deaths) 
+  thedifmax <- max(file$snake_deaths)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+  print(data_points)
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
+  #scale_y_continuous(labels = scales::percent)+
+  #xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  #geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_death_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=20000, max_gen=25000)
+
 ```
@@
 ```{r, graphing by gen}
-trends_by_gen(GA1_long_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations")
+trends_by_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
 
-trends_by_gen(GA2_long_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Mean Phenotype", x_label="Generations")
+#trends_by_gen(GA2_long_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Mean Phenotype", x_label="Generations", 1, 50000)
 
@@
 
-whale_gen(GA1_long_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 
-#pop_size_hist(GA1_long_file, title="Snake-Newt Popsize Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize",  min_gen=min_gen, max_gen=max_gen, rep=rep )
+#pop_size_hist(GA1_tall_tall_file, title="Snake-Newt Popsize Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize",  min_gen=min_gen, max_gen=max_gen, rep=rep )
 
-#pheno_dif_hist(GA1_long_file, title="Snake-Newt Phenotype Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype",  min_gen=min_gen, max_gen=max_gen, rep=rep )
+#pheno_dif_hist(GA1_tall_tall_file, title="Snake-Newt Phenotype Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype",  min_gen=min_gen, max_gen=max_gen, rep=rep )
 
-two_hist(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )
+two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )
+
+two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen)
 
@@
 #files
-#GA1_long_file
+#GA1_tall_tall_file
 #GA2_long_file 
-#GA1_cor_file
+#GA1_cor_tall_file
 #GA2_cor_file
 
-ginmin = 9000
-ginmax = 10000
+ginmin = 10000
+ginmax = 15000
 
-boxplot_cors_by_gen(GA1_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
-boxplot_cors_by_gen(GA2_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA2", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+four_types_boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
-four_types_boxplot_cors_by_gen(GA1_cor_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
-four_types_boxplot_cors_by_gen(GA2_cor_file, "Simulation four Correlation", "GA2", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-hist_cors_by_gen_col_rep(GA1_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-hist_cors_by_gen_col_rep(GA2_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-hist_cors_by_gen_col_rep_nofill(GA1_cor_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+hist_cors_by_gen_col_rep_nofill(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
@@
 ```{r, ga1 cor and pheno}
-GA1_pattern <- unique(paste0(GA1_long_file$snake_mu_rate, "_", GA1_long_file$snake_mu_effect_sd,"_",GA1_long_file$newt_mu_rate, "_", GA1_long_file$newt_mu_effect_sd, "_", GA1_long_file$rep))
+GA1_pattern <- unique(paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep))
 for(i in 1:length(GA1_pattern)){
-  myine<-cor_trends_by_gen(GA1_long_file, GA1_cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern=GA1_pattern[i])
-  plot(myine)
-}
-
-```
-
-```{r, ga2 cor}
-GA2_pattern <- unique(paste0(GA2_long_file$newt_mu_rate, "_", GA2_long_file$newt_mu_effect_sd, "_", GA2_long_file$snake_mu_rate, "_", GA2_long_file$snake_mu_effect_sd, "_", GA2_long_file$rep))
-
-for(i in 1:length(GA2_pattern)){
-  myine<-cor_trends_by_gen(GA2_long_file, GA2_cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=0, max_gen=15000, pattern=GA2_pattern[i])
+  myine<-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=25000, pattern=GA1_pattern[i])
   plot(myine)
@@
 
-for(i in 1:length(unique(GA1_long_file$rep))){
-  myine<-whale_gen(GA1_long_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i])
+for(i in 1:length(unique(GA1_tall_tall_file$rep))){
+  myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i] )
+  myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
   plot(myine)
@@
 
-cor_trends_by_gen(GA1_long_file, GA1_cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-08_0.005_1.0e-09_0.05_0")
+cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-09_0.05_1.0e-09_0.05_0")
 
@@
 
-min_gen=20000
-max_gen=25000
+min_gen=10000
+max_gen=15000
 rep=0
 
-for(i in 1:length(unique(GA1_long_file$rep))){
-  myine<-whale_gen(GA1_long_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i])
+for(i in 1:length(unique(GA1_tall_tall_file$rep))){
+  myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i] )
+  myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
   plot(myine)
@@
 
-min_gen=95000
-max_gen=100000
+min_gen=25000
+max_gen=30000
 rep=0
 
-for(i in 1:length(unique(GA1_long_file$rep))){
-  myine<-whale_gen(GA1_long_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i])
+for(i in 1:length(unique(GA1_tall_tall_file$rep))){
+  myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_long_file$rep)[i] )
+  myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
   plot(myine)
@@
 
-cor_trends_by_gen(GA1_long_file, GA1_cor_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-08_0.005_1.0e-09_0.05_0")
-
-```
-
-```{r, really cool square plots}
-file<-GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep),]
-file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-plot.x <- ggplot(file) + geom_boxplot(aes(newt_snake_rep, dif))
-plot.y <- ggplot(file) + geom_boxplot(aes(newt_snake_rep, Snake_pop_size-Newt_pop_size))
-
-grid.arrange(plot.x, plot.y, ncol=2)
-
-plot.x <- layer_data(plot.x)[,1:6]
-plot.y <- layer_data(plot.y)[,1:6]
-colnames(plot.x) <- paste0("x.", gsub("y", "", colnames(plot.x)))
-colnames(plot.y) <- paste0("y.", gsub("y", "", colnames(plot.y)))
-df <- cbind(plot.x, plot.y); rm(plot.x, plot.y)
-df$category <- sort(unique(file$newt_snake_rep))
-df.outliers <- df %>%
-  select(category, x.middle, x.outliers, y.middle, y.outliers) %>%
-  data.table::data.table()
-#df.outliers <- df.outliers[, list(x.outliers = unlist(x.outliers), y.outliers = unlist(y.outliers)), by = list(category, x.middle, y.middle)]
-ggplot(df, aes(fill = category, color = category)) +
-
-  # 2D box defined by the Q1 & Q3 values in each dimension, with outline
-  geom_rect(aes(xmin = x.lower, xmax = x.upper, ymin = y.lower, ymax = y.upper), alpha = 0.3) +
-  geom_rect(aes(xmin = x.lower, xmax = x.upper, ymin = y.lower, ymax = y.upper), 
-            color = "black", fill = NA) +
-
-  # whiskers for x-axis dimension with ends
-  geom_segment(aes(x = x.min, y = y.middle, xend = x.max, yend = y.middle)) + #whiskers
-  geom_segment(aes(x = x.min, y = y.lower, xend = x.min, yend = y.upper)) + #lower end
-  geom_segment(aes(x = x.max, y = y.lower, xend = x.max, yend = y.upper)) + #upper end
-
-  # whiskers for y-axis dimension with ends
-  geom_segment(aes(x = x.middle, y = y.min, xend = x.middle, yend = y.max)) + #whiskers
-  geom_segment(aes(x = x.lower, y = y.min, xend = x.upper, yend = y.min)) + #lower end
-  geom_segment(aes(x = x.lower, y = y.max, xend = x.upper, yend = y.max)) + #upper end
-
-  # outliers
-  #geom_point(data = df.outliers, aes(x = x.outliers, y = y.middle), size = 3, shape = 1) + # x-direction
-  #geom_point(data = df.outliers, aes(x = x.middle, y = y.outliers), size = 3, shape = 1) + # y-direction
-
-  xlab("s-n mean pheno") + ylab("s-n pop size") +  
-  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      strip.background = element_blank(), 
-                      strip.text.x = element_blank(), 
-                      legend.position="right",
-                      legend.text=element_text(size=5),
-                      panel.grid.major = element_blank(), 
-                      panel.grid.minor = element_blank(),
-                      panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
+cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-09_0.05_1.0e-09_0.05_0")
 
@@
 
-GA_summary(GA1_long_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(GA1_tall_tall_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
-GA_summary(GA1_long_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-GA_summary(GA2_long_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 25sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-GA_summary(GA2_long_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 25sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(GA1_tall_tall_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 
-build_heatmap(GA1_long_file, min_gen=5000, max_gen=10000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(GA1_tall_tall_file, min_gen=5000, max_gen=10000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
-build_heatmap(GA1_long_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(GA1_tall_tall_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
-#build_heatmap(GA1_long_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=F)
-
-build_heatmap(GA2_long_file, min_gen=10000, max_gen=11000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-build_heatmap(GA2_long_file, min_gen=000, max_gen=5000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-build_heatmap(GA2_long_file, min_gen=15000, max_gen=20000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-build_heatmap(GA2_long_file, min_gen=20000, max_gen=25000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-build_heatmap(GA2_long_file, min_gen=25000, max_gen=30000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-build_heatmap(GA2_long_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="25 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+#build_heatmap(GA1_tall_tall_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=F)
 

### 2022-05-29 graphs_newt_snakes/correlation_part2.Rmd
made some more figures for the poster. started to look at the lond file named tall data. Made a back up snakemake file

@@
 library(ggpubr)
-theme_set(theme_pubr())
+#theme_set(theme_pubr())
 ```
@@
   geom_sf(data = states, fill = NA)+
-  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_res), size = 5, shape = 22, ) +
-  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_toxin), size = 3, shape = 21, ) +
-  scale_fill_viridis_c()+
-  coord_sf(xlim = c(-130.4494, -111.6764), ylim = c(29.742, 54.9415), expand = FALSE)
+  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_res), size = 6, shape = 22, ) +
+  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_toxin), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+  coord_sf(xlim = c(-127, -115), ylim = c(34, 50.5), expand = FALSE)
+
+ggplot(data = world) +
+  geom_sf() +
+  geom_sf(data = states, fill = NA)+
+  #geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_res), size = 6, shape = 22, ) +
+  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_toxin), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+  coord_sf(xlim = c(-127, -115), ylim = c(34, 50.5), expand = FALSE)
+
+ggplot(data = world) +
+  geom_sf() +
+  geom_sf(data = states, fill = NA)+
+  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_res), size = 6, shape = 22, ) +
+  #geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_toxin), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
+  coord_sf(xlim = c(-127, -115), ylim = c(34, 50.5), expand = FALSE)
+
 ```

### 2022-06-24 graphs_newt_snakes/Dac_2022.Rmd
looking at some new data

--- 2022-05-19 graphs_newt_snakes/Dac_2022.Rmd
@@
 ```
+
+```{r, my plots for poster}
+
+min_gen=100
+max_gen=20000
+rep=0
+unique(GA1_long_file$snake_mu_rate)
+ggplot(GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep & GA1_long_file$snake_mu_rate=="1.0e-10" & GA1_long_file$newt_mu_rate=="1.0e-10"),]) +
+    #facet_wrap(~sim)+
+    geom_line(aes(generation, dif, col="dif"), size=1 )+
+    ggtitle("test", subtitle = paste0(" From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"), size=1 )+
+    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"), size=1 )+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54", size=1 )+
+    ylim(-5,8)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+# ggsave(
+#   "~/Desktop/newt_snake_coevo_example.pdf",
+#   plot = last_plot(),
+#   scale = 1,
+#   width = 7,
+#   height = 5,
+#   #units = c("in"),
+#   dpi = 300,
+#   limitsize = TRUE,
+#   bg = NULL,
+# )
+
+title="Snake-Newt Winning Hist"
+subt="Gen 16sims"
+y_label="Count"
+x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)"
+min_gen=5000
+max_gen=15000
+
+GA1_long_file$snake_GA<-paste0(GA1_long_file$snake_mu_rate, "_", GA1_long_file$snake_mu_effect_sd)
+  GA1_long_file$newt_GA<-paste0(GA1_long_file$newt_mu_rate, "_", GA1_long_file$newt_mu_effect_sd)
+
+  GA1_fig_file<-GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen),]
+
+  thepopmin <- min(GA1_fig_file$Snake_pop_size-GA1_fig_file$Newt_pop_size)/100 
+  thepopmax <- max(GA1_fig_file$Snake_pop_size-GA1_fig_file$Newt_pop_size)/100
+  thedifmin <- min(GA1_fig_file$dif) 
+  thedifmax <- max(GA1_fig_file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(GA1_fig_file[which(GA1_fig_file$generation>=min_gen & GA1_fig_file$generation<=max_gen  &  GA1_fig_file$snake_GA==GA1_fig_file$snake_GA[1] &  GA1_fig_file$newt_GA==GA1_fig_file$newt_GA[1]),])
+  print(data_points)
+  GA1_fig_file$dif_pop<- GA1_fig_file$Snake_pop_size - GA1_fig_file$Newt_pop_size
+
+ggplot(GA1_fig_file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=(dif_pop)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+
+  scale_y_continuous(labels = scales::percent)+
+#limits=c(0, .6)
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggsave(
+  "~/Desktop/newt_snake_hist.pdf",
+  plot = last_plot(),
+  scale = 1,
+  width = 14,
+  height = 6,
+  #units = c("in"),
+  dpi = 300,
+  limitsize = TRUE,
+  bg = NULL,
+)
+
+title="Snake-Newt Winning Hist"
+subt="Gen 16sims"
+y_label="Count"
+x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)"
+min_gen=85000
+max_gen=100000
+
+GA1_long_file$snake_GA<-paste0(GA1_long_file$snake_mu_rate, "_", GA1_long_file$snake_mu_effect_sd)
+  GA1_long_file$newt_GA<-paste0(GA1_long_file$newt_mu_rate, "_", GA1_long_file$newt_mu_effect_sd)
+
+  GA1_fig_file<-GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen),]
+
+  thepopmin <- min(GA1_fig_file$Snake_pop_size-GA1_fig_file$Newt_pop_size)/100 
+  thepopmax <- max(GA1_fig_file$Snake_pop_size-GA1_fig_file$Newt_pop_size)/100
+  thedifmin <- min(GA1_fig_file$dif) 
+  thedifmax <- max(GA1_fig_file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(GA1_fig_file[which(GA1_fig_file$generation>=min_gen & GA1_fig_file$generation<=max_gen  &  GA1_fig_file$snake_GA==GA1_fig_file$snake_GA[1] &  GA1_fig_file$newt_GA==GA1_fig_file$newt_GA[1]),])
+  print(data_points)
+ggplot(GA1_fig_file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+
+  scale_y_continuous(labels = scales::percent)+
+  #xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggsave(
+  "~/Desktop/newt_snake_hist_late.pdf",
+  plot = last_plot(),
+  scale = 1,
+  width = 7,
+  height = 5,
+  #units = c("in"),
+  dpi = 300,
+  limitsize = TRUE,
+  bg = NULL,
+)
+
+fakedata<-as.data.frame(rnorm(1000,0, 2))
+
+ggplot(fakedata) +
+  ggtitle("Phenotype Dif")+
+geom_histogram(aes(x=`rnorm(1000, 0, 2)`), fill="#8B008B",  alpha = 0.65, bins = 20)+
+theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+# ggsave(
+#   "~/Desktop/hist_pheno_dif.pdf",
+#   plot = last_plot(),
+#   scale = 1,
+#   width = 7,
+#   height = 5,
+#   #units = c("in"),
+#   dpi = 300,
+#   limitsize = TRUE,
+#   bg = NULL,
+# )
+
+fakedata$popsize<-rnorm(1000,0, 4)
+
+ggplot(fakedata) +
+  ggtitle("Phenotype Dif")+
+geom_histogram(aes(x=popsize), fill="#008B00",  alpha = 0.65, bins = 20)+
+theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+# ggsave(
+#   "~/Desktop/hist_popsize_dif.pdf",
+#   plot = last_plot(),
+#   scale = 1,
+#   width = 7,
+#   height = 5,
+#   #units = c("in"),
+#   dpi = 300,
+#   limitsize = TRUE,
+#   bg = NULL,
+# )
+```
+
+```{r, more plots for poster}
+min_gen=100
+max_gen=6000
+rep=0
+pattern="1.0e-09_0.5_1.0e-10_0.05_0"
+GA1_long_file$snake_GA
+unique(GA1_long_file$snake_mu_rate)
+ggplot(GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep & GA1_long_file$snake_mu_rate=="1.0e-09" & GA1_long_file$newt_mu_rate=="1.0e-10"),]) +
+    #facet_wrap(~sim)+
+    ggtitle("test", subtitle = paste0(" From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"), size=1 )+
+    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"), size=1 )+
+    ylim(-5,8)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+# ggsave(
+#   "~/Desktop/catch_up_part1.pdf",
+#   plot = last_plot(),
+#   scale = 1,
+#   width = 7,
+#   height = 5,
+#   #units = c("in"),
+#   dpi = 300,
+#   limitsize = TRUE,
+#   bg = NULL,
+# )
+
+min_gen=4500
+max_gen=85000
+rep=0
+pattern="1.0e-09_0.5_1.0e-10_0.05_0"
+GA1_long_file$snake_GA
+unique(GA1_long_file$snake_mu_rate)
+ggplot(GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep & GA1_long_file$snake_mu_rate=="1.0e-09" & GA1_long_file$newt_mu_rate=="1.0e-10"),]) +
+    #facet_wrap(~sim)+
+    ggtitle("test", subtitle = paste0(" From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"), size=1 )+
+    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"), size=1 )+
+    ylim(-5,8)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+# ggsave(
+#   "~/Desktop/catch_up_part2.pdf",
+#   plot = last_plot(),
+#   scale = 1,
+#   width = 7,
+#   height = 5,
+#   #units = c("in"),
+#   dpi = 300,
+#   limitsize = TRUE,
+#   bg = NULL,
+# )
+
+min_gen=80000
+max_gen=99999
+rep=0
+pattern="1.0e-09_0.5_1.0e-10_0.05_0"
+GA1_long_file$snake_GA
+unique(GA1_long_file$snake_mu_rate)
+ggplot(GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep & GA1_long_file$snake_mu_rate=="1.0e-09" & GA1_long_file$newt_mu_rate=="1.0e-10"),]) +
+    #facet_wrap(~sim)+
+    ggtitle("test", subtitle = paste0(" From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"), size=1 )+
+    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"), size=1 )+
+    ylim(-5,8)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+# ggsave(
+#   "~/Desktop/catch_up_part3.pdf",
+#   plot = last_plot(),
+#   scale = 1,
+#   width = 7,
+#   height = 5,
+#   #units = c("in"),
+#   dpi = 300,
+#   limitsize = TRUE,
+#   bg = NULL,
+# )
+min_gen=100
+max_gen=99999
+rep=0
+pattern="1.0e-09_0.5_1.0e-10_0.05_0"
+GA1_long_file$snake_GA
+unique(GA1_long_file$snake_mu_rate)
+ggplot(GA1_long_file[ which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep & GA1_long_file$snake_mu_rate=="1.0e-09" & GA1_long_file$newt_mu_rate=="1.0e-10"),]) +
+    #facet_wrap(~sim)+
+    ggtitle("test", subtitle = paste0(" From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"), size=1 )+
+    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"), size=1 )+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+# ggsave(
+#   "~/Desktop/catch_up_all.pdf",
+#   plot = last_plot(),
+#   scale = 1,
+#   width = 7,
+#   height = 5,
+#   #units = c("in"),
+#   dpi = 300,
+#   limitsize = TRUE,
+#   bg = NULL,
+# )
+```

### 2022-06-24 graphs_newt_snakes/Tall_GA1.Rmd
looking at some new data

@@
 theme_set(theme_pubr())
+library(stringr)
+library(patchwork)
 ```
@@
 GA1_tall_cor_files <- list.files(path="~/Desktop/tall_map", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+grid_tall_files <- list.files(path="~/Desktop/tall_map", pattern="_grid_", full.names=TRUE, recursive=FALSE)
 
@@
 GA1_cor_tall_file<- data.frame()
+grid_tall_file<-data.frame()
 
@@
    }
-
+  print(newt_numb)
   if (i<=length(GA1_tall)){
@@
 
+  grid_temp_file <- read.csv(grid_tall_files[i], header = TRUE)
+  grid_temp_file$sim <-LETTERS[letter]
+  grid_temp_file$size <-newt_numb
+  grid_temp_file$rep <-unlist(str_split(unlist(str_split(grid_tall_files[i],"rep_"))[3], "_"))[1]
+  grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  grid_tall_file <- rbind(grid_tall_file, grid_temp_file)
+
   }
@@
 GA1_tall_tall_file$dif <- GA1_tall_tall_file$Snake_mean_Pheno-GA1_tall_tall_file$Newt_mean_Pheno
+
+grid_tall_file$snake_newt_rep <- paste0("Snake_",grid_tall_file$snake_mu_rate, "_", grid_tall_file$snake_mu_effect_sd, "_Newt_",grid_tall_file$newt_mu_rate, "_", grid_tall_file$newt_mu_effect_sd, "_", grid_tall_file$rep)
 ```
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
- file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-  cfile$newt_snake_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]) +
+ file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+  cfile$snake_newt_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
     #geom_line(aes(generation, dif, group=rep, col="dif"))+
@@
 
-  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]) +
+  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
     geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
@@
     #xlab(x_label_cor) + ylab(y_label)+
-    geom_hline(yintercept=0, linetype="dashed")+
     theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
@@
 
-  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]
-  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]
+  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
+  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
   toDelete <- seq(0, nrow(cfile), 2)
@@
 ```{r, graphing by gen}
-trends_by_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
+trends_by_gen(GA1_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
 
@@
 for(i in 1:length(GA1_pattern)){
-  myine<-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=25000, pattern=GA1_pattern[i])
+  myine<-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
   plot(myine)
@@
 ```
+
+## What is up with the corilations
+
+```{r, cor grid by location}
+
+#grid_tall_file
+
+file_name= "Snake_1.0e-09_0.05_Newt_1.0e-09_0.05_2"
+spegen=25001
+
+GA1<-grid_tall_file[which(grid_tall_file$snake_newt_rep==file_name & grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+```{r, plot experiment}
+library(plotly)
+library(gapminder)
+
+file_name= "Snake_1.0e-09_0.05_Newt_1.0e-09_0.05_2"
+spegen=25001
+
+plotty_mean <- gather(grid_tall_file[which(grid_tall_file$snake_newt_rep==file_name),][,grepl("generation|mean", names(grid_tall_file)) ], condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+plotty_mean[,c("species","type", "type2","location")]<- str_split_fixed(plotty_mean$condition, "_", 4)
+
+#snake<-plotty_mean[which(plotty_mean$species=="snake"),]
+#newt<-plotty_mean[which(plotty_mean$species=="newt"),]
+#newt$snake_value <- snake$measurement
+
+plotty_mean_min<-plotty_mean
+plotty_mean_min_s<-plotty_mean_min[which(plotty_mean_min$species=="snake"),]
+plotty_mean_min_s$newt_values<-plotty_mean_min[which(plotty_mean_min$species=="newt"),"measurement"]
+plotty_mean_min_s$edge <- "not edge"
+plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(0, 1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20, 39, 40, 59, 60, 79, 80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98,99)
+
+plotty_mean_min_s$info[plotty_mean_min_s$edge=="TRUE"]  <- "edge"
+plotty_mean_min_s$info[plotty_mean_min_s$edge=="FALSE"]  <- "middle"
+plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 19, 80, 99)] <- "corner"
+
+p <- plotty_mean_min_s %>%
+  plot_ly(
+    x = ~as.numeric(newt_values), 
+    y = ~as.numeric(measurement), 
+    frame = ~generation, 
+    text = ~factor(location), 
+    color = ~factor(info), 
+    hoverinfo = "text",
+    type = 'scatter',
+    mode = 'markers'
+  ) %>%
+  layout(
+    xaxis = list(
+      type = "log"
+    )
+  )
+p
+```

### 2022-06-24 graphs_newt_snakes/running_100000gen.Rmd
looking at some new data

@@
 
-trends_by_gen <- function(file, title, subt, x_label, y_label){
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 
-  plot <- ggplot(file) +
+  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
     facet_wrap(~sim)+
     geom_line(aes(generation, dif, group=rep, col="dif"))+
-    ggtitle(title, subtitle = subt) +
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
     geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
     geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
-    ylim(-5,10)+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54", size=0.7)+
+    ylim(-7,10)+
     xlab(x_label) + ylab(y_label)+
@@
 
+two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+  print(data_points)
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+two_hist_all_rep(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=25000, max_gen=30000)
+
 ```
@@
 ```{r, graphing by gen}
-trends_by_gen(GA1_long_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations")
+trends_by_gen(GA1_long_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
 
-trends_by_gen(GA2_long_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Mean Phenotype", x_label="Generations")
+#trends_by_gen(GA2_long_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Mean Phenotype", x_label="Generations", 1, 50000)
+
+ggsave(
+  "~/Desktop/newt_snake_coevo_16.pdf",
+  plot = last_plot(),
+  scale = 1,
+  width = 7,
+  height = 5,
+  #units = c("in"),
+  dpi = 300,
+  limitsize = TRUE,
+  bg = NULL,
+)
+```
+
+```{r, the scatter of pheno and pop size}
+min_gen=5000
+max_gen=15000
+
+rep=2
+
+drop_lows <- GA1_long_file[which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep),]
+
+drop_lows$popsize_dif<-drop_lows$Snake_pop_size-drop_lows$Newt_pop_size
+mean(abs(drop_lows$dif))
+value=sd(abs(drop_lows$dif))*3
+
+#drop_lows[which(drop_lows$dif>0),]$Newt_mean_Pheno = NA
+#drop_lows[which(drop_lows$dif>0),]$Newt_pop_size = NA
+#drop_lows[which(drop_lows$dif<0),]$Snake_mean_Pheno = NA
+#drop_lows[which(drop_lows$dif<0),]$Snake_pop_size = NA
+
+h <- hist(drop_lows$dif, breaks=18, plot=FALSE)
+cuts <- cut(h$breaks, c(-Inf,(abs(min(drop_lows$dif))-value)+min(drop_lows$dif),
+                        max(drop_lows$dif)-(max(drop_lows$dif)-value+.5),max(drop_lows$dif)))
+
+#pdf("~/Desktop/dif_in_phenotype_hist.pdf", width = 7, height = 5)
+plot(h, col=c("yellow","grey","yellow")[cuts])
+#dev.off()
+
+# ggplot(drop_lows[which(abs(drop_lows$dif)>=value),]) +
+#   #xlim(0, 1000)+
+#   #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+#   #xlab(x_label) + ylab(y_label)+
+#   geom_point(aes(x=as.numeric(Newt_mean_Pheno), y=abs(popsize_dif)), color = "darkred",size=3)+
+#   geom_point(aes(x=as.numeric(Snake_mean_Pheno), y=abs(popsize_dif)), color = "steelblue",size=3)+
+# #  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+#   geom_smooth(aes(x=Newt_mean_Pheno, y=abs(popsize_dif)), method=lm, se=FALSE, fullrange=TRUE, color = "darkred")+
+#   geom_smooth(aes(x=Snake_mean_Pheno, y=abs(popsize_dif)), method=lm, se=FALSE, fullrange=TRUE, color = "steelblue")+
+#   theme(plot.title = element_text(size=5)) +
+#   #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+#   #labs(colour = color_label) +
+#   #facet_wrap(~sim)+
+#   theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+# 
+# ggsave("~/Desktop/dif_in_phenotype_popsize.pdf", plot = last_plot(), scale = 1,
+#   width = 7, height = 5, dpi = 300, limitsize = TRUE, bg = NULL)
+
+ggplot(drop_lows)  +
+ ggtitle(paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  geom_point(aes(x=as.numeric(dif), y=popsize_dif), color = "darkgreen",size=3)+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+ggsave("~/Desktop/dif_phenotype_dif_popsize.pdf", plot = last_plot(), scale = 1,
+  width = 7, height = 5, dpi = 300, limitsize = TRUE, bg = NULL)
+
+ggplot(drop_lows[which(abs(drop_lows$dif)>=value),])  +
+  ylim(600, 1200)+
+  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  #xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_mean_Pheno), y=abs(Newt_pop_size)), color = "darkred",size=3)+
+  geom_point(aes(x=as.numeric(Snake_mean_Pheno), y=abs(Snake_pop_size)), color = "steelblue",size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  #geom_smooth(aes(x=Newt_mean_Pheno, y=Newt_pop_size), method=lm, se=FALSE, fullrange=TRUE, color = "darkred")+
+  #geom_smooth(aes(x=Snake_mean_Pheno, y=Snake_pop_size), method=lm, se=FALSE, fullrange=TRUE, color = "steelblue")+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+#ggsave("~/Desktop/phenotype_popsize.pdf", plot = last_plot(), scale = 1,
+ # width = 7, height = 5, dpi = 300, limitsize = TRUE, bg = NULL)
 
@@
 two_hist(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )
+
+two_hist_all_rep(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen)
 

### 2022-07-12 graphs_newt_snakes/Tall_GA1.Rmd
this is the write up for the tall map

@@
 
-### Goal
+### Goal:
 
-figure out a main conclusion for the poster!
+Think & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs) can lead to. 
+I.E. is there spacial correlation between the phenotype? If so when/why?
+
+### Questions:
+
+Can I find a certain GA or set of GAs that are similar to the correlation between real newts and snake phenotypes across different locations in space?
+
+### Background
+
+Evolution textbooks often highlight the interaction of toxic newts with resistant snakes as a model example of co-evolution.
+As newts become more toxic snakes become more resistant leading to their phenotypes being highly correlated across space.
+There are about 3-4 mutations that make a snake resistant to the toxin have been discovered.
+One-two of these mutations have a large effect leading to a high toxin resistance in snakes.
+However, these mutations break an ion-channel leading the snakes to be slower (potentially more venerable to predators).
+This suggests that the genetic architecture (GA)  for resistance within snakes has a low mutation rate with a large effect size.
+The mutations that allow newts to be toxic (or at least resistant to their own toxin) have yet to be determined (2022).
+Thus we may ask are there many or only a few mutations that lead to newt toxicity?
+Do these mutations have a large or small effect?
+
+### Experiment
+
+I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction at different genetic architectures (GAs) in a spatial setting.
+I hypothesized that we would see an interaction (co-evolutionary arms race) between newt and snake phenotype under some GA combinations when newts and snakes were evolving over geographical space.
+Each GA is paired with another GA creating 16 combinations.
 
@@
 - 1e-11*(5.0)^2 = 2.5e-10
+
+Landscape: 20 by 5 grid. A tall map!
+
+Observations to make:
+
+- How do phenotypes change over time?
+- What are the phenotypes of newts and snakes spatially? And are they correlated? 
+- Are newts and snakes interacting, in other words are there spatial locations overlapping?
+- Is there a noticeable difference between the GA combinations?
+
+### The data
+
+I gather text file data from different files and have to do some table wrangling to get it into a format I can graph.
+I use information gathered from the entire population; data containing a mean value for the entire map (lit), correlation data based off of local populations that were divided into grids (cor) and data collected from grid based populations (grid).
+These simulations have a msprime (coalescent/burn in/random genetic variation) and then run for 50,000 generations in SLiM (co-evolution) (all with the same GA values).
 
@@
 
+GA1_tall_tall_file$group_rep <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep)
+
+GA1_tall_tall_file$group <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd)
+
 grid_tall_file$snake_newt_rep <- paste0("Snake_",grid_tall_file$snake_mu_rate, "_", grid_tall_file$snake_mu_effect_sd, "_Newt_",grid_tall_file$newt_mu_rate, "_", grid_tall_file$newt_mu_effect_sd, "_", grid_tall_file$rep)
@@
   theme(plot.title = element_text(size=5)) +
+  xlim(-1.1, 1.1)+
   facet_wrap(~newt_snake)+
@@
   theme(plot.title = element_text(size=5)) +
+  #stat_bin(bins=30)+
   facet_wrap(~newt_snake)+
@@
                       axis.title.y = element_blank())
+
+suppressMessages(print(plot))
 
@@
 
-First, I will look at a plot of how the mean phenotype of newts and snakes changes overtime.
-Each of these plots contains four replicas for all GA combinations (letter label is the experiment that was run, 16 Sim is from GA1 and 25 Sim is from GA2).
-Each of these plots has three lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype.
-Note this is a mean for the entire population.
+### Mean Phenotype Whole Simulation
+
+First, I will look at a plot of how the mean phenotype of the entire population of newts and snakes changes overtime.
+Each of these plots has three colored lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype.
+There are 4 line per color that represent the different replicas that I ran.
+**Note this is a mean for the entire population.** Mutational variance increases for the snakes as you go down (top to bottom) the figure and increases for the newts as you go across (left to right).
 
@@
 
-#trends_by_gen(GA2_long_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Mean Phenotype", x_label="Generations", 1, 50000)
+aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group), FUN=mean)
+
+aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
 
 ```
+
+The first thing that I noticed is that newt mean phenotype and snake mean phenotype seem to follow each other.
+I wonder if they are both drifting up?
+The second thing I noticed is that this figure is not symmetrical.
+The mean difference between snake and newt phenotype is not equal between the two species when their GAs are flipped.
+In the first row, as mutation variance goes up for the newts and stays for constant for the snakes the average difference is 0.03, 2.8, 2.7, 0.09 (first row left to right).
+When the mutation variance goes up for the snakes and stays the same for the newts (first column) the  average difference is 0.03, 2.0, 2.2, 0.03 (first row left to right).
+This indicates that there might be different selection pressure for newts and snakes, which is similar describes other works that discuss predator-prey interactions.
+Snakes really only had a higher phenotype when newts had a low mutation variance.
+Even when snakes had a higher mutational variance, newts still had a higher phenotype on average (the entire length of the simulation).
+I had predicted that a higher mutational variance would lead to a higher mean phenotype, but that seems not to be the case.
+Now there are some caveats to this observation; 1) these observations change over time, like pre 10,000 generations things look a lot different and different conclusions can be made (discussed lower).
+2) There is a cost to having a high phenotype.
+In the last row & column mutations that arise might have too high of a phenotype and die out quickly (making the cost higher might change some of the results, it would be cool to see if the top right difference between newt and snake mean phenotype grows with a more relaxed cost).
+This observation is interesting to me for two reasons 1) in the real newt-snake example snakes always seem to have a higher phenotype and 2) snakes seem to have more of a genetic architecture with a few mutations of high effect size.
+There are some other real factors that I think about like the difference between life history factors of newts and snake (reproduction 1-2 years vs 5-6 years or the ability to move around)
+
+### Mean Phenotype Beggining Simulation
+
+I like to focus on the beginning of the simulation when newts and snakes are first starting to co-evolve right before some of the slopes start to flat line (15,000 generations).
+
+```{r, graphing by gen}
+trends_by_gen(GA1_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 15000)
+
+aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=15000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=15000),]$group), FUN=mean)
+
+aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=15000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=15000),]$group_rep), FUN=mean)
+
+```
+
+After looking at this section of the data, newts have a higher phenotype on average.
+Snakes often only have a higher phenotype when the GA of newts has low mutational variance.
+Is there a way to measure the mutational variance within my species?
+This would help determine if the cost function was limiting the number of fixing mutations in the GA with the highest mutational variance.
+Another thing I would like to note, is that when the GA of newts and snakes are the same newts usually end up with a higher phenotype.
+The case of the third GA for snakes and the 4 GA for newts is extremely weird (is it the only instance where snakes end up with a higher phenotype that is consistently higher through out the simulation and not in the first column).
+
+### Connection between higher phenotype and population
+
+The next few figures in this write up depict the connection between higher phenotype and higher population size.
+I predicted that the species with a higher phenotype would have a larger population size.
+My thought process was that if newts were really toxic and snakes tried to eat them, lots of snakes would die.
+And if snakes were really resistant lots of newts would get eaten.
+But how would this work in real life?
+I.E.
+Population sizes might not depend on resistance & toxicity.
 
@@
 
-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )
+two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )
 
-two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen)
+two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)
 
 ```
+
+I looked at the results between 5,000 - 10,000 generations where I saw most of the increase in newt and snake phenotype.
+The first figure plot newt population size by snake population size with the color representing the difference between snake and newt mean phenotype (red=newts have a higher mean phenotype, blue=snakes have a higher mean phenotype).
+The there is GA (an intermediate one) seems to do better then all of the other GAs (blue row, red column).
+However, this is dependent on the point in the simulation you focus on.
+The next two plots show the difference between snake and newt population size (green) and phenotype (purple).
+For the most part these suggest that when the mean phenotype is higher so is the population size.
+This also shows the asymmetrical nature between the predator-prey interaction (higher max population sizes seen in snakes).
+
+### Correlation
+
+The next section I aim to look at how correlated newt and snakes are at local populations across the geographical area.
+I am examining correlation between newt and snake phenotypes, population sizes newts and snakes, amount of toxin and snake population, and the amount of resistance and newt population size.
+I predicted that there would be a positive correlation between the phenotypes, and a negative correlation between population sizes, and the amount of toxin/resistance and population size.
+Below is a legend for the first two plots.
+The third plot is colored by trial
+
+Legend:
+
+- "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
+- "CB" = num_newts_By_num_snakes (Green)
+- "CC" = sum_newt_pheno_By_num_snake (Blue)
+- "CD" = sum_snake_pheno_By_num_newt (Purple)
+
+I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
+The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
+The second figure shows the the results of all 4 trials for each correlation measurement I made from 10,000-15,000 generations.
+The third plot takes the information from the fist plot and shows the distribution of correlation values by each trial (solid line at 0, dashed line at real newt-snake correlation).
 
@@
 
-hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
-hist_cors_by_gen_col_rep_nofill(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+#hist_cors_by_gen_col_rep_nofill(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
 ```
+
+The first thing that I noticed in the first figure, was that most of the correlation values were not as positive as the real newt-snake correlation.
+This could change depending on which generation window we look through (see figure set below).
+I also wonder if correlation occurs more when one of the species has a higher phenotype (like newt phenotype drive snake phenotype, but snake phenotype does not drive newt phenotype).
+When looking a figure 2 it seems like most values are no different from 0.
+This troubles me, but I have some thoughts.
+1) These simulations are very stochastic and having high and low values averaged together might be 0.
+2) Results might be 0.
+3) Results are not 0 but close.
+4) It might depend on generation window.
+5) What is happen in my simulation leading to correlation/no correlation (maybe not getting good local measurements)?
+I wonder if we only used some of the grids (like the corners) if the correlation values would change.
+The most informative figure to me in this set was the third one.
+The color represents the simulation trial, and it really displays the stochastic nature of my simulation.
+I think there are distinct differences between the GA combinations, but its hard to make a solid description between them.
+
+I decided to look at the trial correlation distributions for different windows of time for all 16 GA combination.
+Each of these figures are over a 5,000 generation window.
+They start at the beginning of the simulation a move through the conclusion of my simulation.
+There are four independant (msprime/slim) trials for each GA combination.
+
+```{r, ga1 cor by dif windows}
+
+ginmin = 0
+ginmax = 5000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 5000
+ginmax = 10000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 10000
+ginmax = 15000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 15000
+ginmax = 20000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 20000
+ginmax = 25000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 25000
+ginmax = 30000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 30000
+ginmax = 35000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 35000
+ginmax = 40000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 40000
+ginmax = 45000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 45000
+ginmax = 50000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+```
+
+Flipping through the 10 figures is like looking through a cartoon flip book.
+Things seem to be moving like waves in different directions (more positive or negative?).
+The only GA simulation that matches the real newt-snake data is the first one (high mutation rate- low effect size).
+These simulations reach an area of high correlation, because the change in phenotype occurs rapidly in small effects.
+I wondered if given more time or more space if any other of the GA combination would become more correlated?
+How are the mean phenotypes for the entire population getting higher without there being correlation at the local level?
+What do the local population distribution of newts and snakes look like (is there some avoidance or weird density effect)?
+How are NAs changing this measurement?
+Is there a difference in the local correlation when a certain species is driving convolution?
+
+### Correlation across time
+
+In this section I plot the mean phenotype of newts, the mean phenotype of snakes, and there local correlation values across 50,000 generations.
+There are 4 trials for each GA combination.
+I also print out some correlation values; 1) whole population mean snake phenotype and local correlation, 2) whole population mean newt phenotype and local correlation, 3) difference between mean snake and mean newt phenotype and local correlation, and 4) correlation between mean snake and newt phenotype.
+My thoughts on looking at these correlations were that it might be possible that the local correlations might be more correlated to one of the species.
 
@@
 ```
+
+The results from all of the correlations and mean phenotypes are very messy!
+The correlation values range from 0.99 to -0.62, but lets take a deeper look into the correlation values based on GA combination.
+(must be careful when thinking about the correlation sign with difference)
+
+Results by Pattern:
+
+* 1.0e-08_0.005_1.0e-08_0.005 
+  + Newt ans snake mean phenotype is positively correlated (68-91)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+* 1.0e-08_0.005_1.0e-09_0.05 
+  + Newt ans snake mean phenotype is correlated (72-88)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+* 1.0e-08_0.005_1.0e-10_0.5 
+  + Newt ans snake mean phenotype is a bit less positively correlated (49-62)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+* 1.0e-08_0.005_1.0e-11_5.0 
+  + Newt ans snake mean phenotype is positively correlated in 3 trials (80-83)
+  + Newt ans snake mean phenotype is negatively correlated in one trial where newt mean phenotype is 0 (-0.44)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+* 1.0e-09_0.05_1.0e-08_0.005 
+  + Newt ans snake mean phenotype is positively correlated (69-93)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Possibly random, but the correlation between snake & local and difference & local were nearly identical for all four trials.
+* 1.0e-09_0.05_1.0e-09_0.05 
+  + 
+* 1.0e-09_0.05_1.0e-10_0.5 
+  + 
+* 1.0e-09_0.05_1.0e-11_5.0 
+  + 
+* 1.0e-10_0.5_1.0e-08_0.005 
+  + 
+* 1.0e-10_0.5_1.0e-09_0.05 
+  + 
+* 1.0e-10_0.5_1.0e-10_0.5 
+  + 
+* 1.0e-10_0.5_1.0e-11_5.0 
+  + 
+* 1.0e-11_5.0_1.0e-08_0.005 
+  + 
+* 1.0e-11_5.0_1.0e-09_0.05 
+  + 
+* 1.0e-11_5.0_1.0e-10_0.5 
+  + 
+* 1.0e-11_5.0_1.0e-11_5.0 
+  +
 
@@
 
-## What is up with the corilations
+## What is up with the correlations
 

### 2022-07-13 graphs_newt_snakes/Tall_GA1.Rmd
I have written down more explination

@@
   xlab(x_label) + ylab(y_label)+
-  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
+
  if(red_blue==FALSE){
-  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text)
+  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=8))
   }
  if(red_blue==TRUE){
-  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text)
- }
+  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
+ }
+
   return(my_plot)
@@
   #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
   xlab(x_label) + ylab(y_label)+
@@
   data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
-  print(data_points)
+
 dif <- ggplot(file) +
@@
   xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+
-  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
   scale_y_continuous(labels = scales::percent)+
@@
 
-two_hist_death_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 
@@
 
-I like to focus on the beginning of the simulation when newts and snakes are first starting to co-evolve right before some of the slopes start to flat line (15,000 generations).
+I like to focus on the beginning of the simulation when newts and snakes are first starting to co-evolve right before some of the slopes start to flat line (~15,000 generations).
 
@@
 
-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )
-
-two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)
+suppressMessages(print(two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+suppressMessages(print(two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
 
@@
 This also shows the asymmetrical nature between the predator-prey interaction (higher max population sizes seen in snakes).
+The population size is also more variable than the phenotype (dif in population size has a wider range).
 
@@
 They start at the beginning of the simulation a move through the conclusion of my simulation.
-There are four independant (msprime/slim) trials for each GA combination.
+There are four independent (msprime/slim) trials for each GA combination.
 
@@
 * 1.0e-08_0.005_1.0e-08_0.005 
-  + Newt ans snake mean phenotype is positively correlated (68-91)
+  + Newt and snake mean phenotype is positively correlated (68-91)
   + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Mean phenotype tend to go up, when crossing the local correlation goes down
 * 1.0e-08_0.005_1.0e-09_0.05 
-  + Newt ans snake mean phenotype is correlated (72-88)
+  + Newt and snake mean phenotype is correlated (72-88)
   + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Snake mean phenotype mostly flat
 * 1.0e-08_0.005_1.0e-10_0.5 
-  + Newt ans snake mean phenotype is a bit less positively correlated (49-62)
+  + Newt and snake mean phenotype is a bit less positively correlated (49-62)
   + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Snake mean phenotype mostly flat
 * 1.0e-08_0.005_1.0e-11_5.0 
-  + Newt ans snake mean phenotype is positively correlated in 3 trials (80-83)
-  + Newt ans snake mean phenotype is negatively correlated in one trial where newt mean phenotype is 0 (-0.44)
+  + Newt and snake mean phenotype is positively correlated in 3 trials (80-83)
+  + Newt and snake mean phenotype is negatively correlated in one trial where newt mean phenotype is 0 (-0.44)
   + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Snake mean phenotype mostly flat, newt mean phenotype has been able to exceed snake mean phenotype
 * 1.0e-09_0.05_1.0e-08_0.005 
-  + Newt ans snake mean phenotype is positively correlated (69-93)
+  + Newt and snake mean phenotype is positively correlated (69-93)
   + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
   + Possibly random, but the correlation between snake & local and difference & local were nearly identical for all four trials.
+  + Newt mean phenotype mostly flat, snake mean phenotype can start lower and enceed newt mean phenotype
 * 1.0e-09_0.05_1.0e-09_0.05 
-  + 
+  + Newt and snake mean phenotype is positively correlated (90-99)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Mean phenotype tend to go up and cross together a lot
 * 1.0e-09_0.05_1.0e-10_0.5 
-  + 
+  + Newt and snake mean phenotype is positively correlated (80-96)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Mean phenotype tend to go up together. Newt mean phenotype has larger jumps than snake mean phenotype. 
+  + Sometimes it takes time for the snake mean phenotype to catch up to the newt mean phenotype
 * 1.0e-09_0.05_1.0e-11_5.0 
-  + 
+  + Newt and snake mean phenotype is positively correlated (89-95)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Mean phenotype tend to go up together. Newt mean phenotype has larger jumps than snake mean phenotype. 
 * 1.0e-10_0.5_1.0e-08_0.005 
-  + 
+  + Newt and snake mean phenotype is a bit less positively correlated (42-60)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Newt mean phenotype mostly flat, but slowly rises overtime (does not catch up) 
 * 1.0e-10_0.5_1.0e-09_0.05 
-  + 
+  + Newt and snake mean phenotype is positively correlated (67-89)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + These mean phenotypes are strange. The snake mean phenotype has larger jumps. Newt and snake mean phenotypes closly match
 * 1.0e-10_0.5_1.0e-10_0.5 
-  + 
+  + Newt and snake mean phenotype is positively correlated (61-91)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype) (all of them are close to 0)
+  + Snake and newt mean phenotype closely match, newt mean phenotype is larger than snake mean phenotype
 * 1.0e-10_0.5_1.0e-11_5.0 
-  + 
+  + Newt and snake mean phenotype is positively correlated (79-91)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype) (all of them are close to 0)
+  + snake and newt mean phenotypes closely match and intersect a lot.
 * 1.0e-11_5.0_1.0e-08_0.005 
-  + 
+  + Newt and snake mean phenotype is positively correlated in 2 trials (40, 57)
+  + Newt and snake mean phenotype is negatively correlated in 2 trials (-19, -48) 
+  + lots of red and blue flat lines
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Possibly random, but the correlation between snake & local and difference & local were nearly identical for all trials where newt mean phenotype flat-lined.
+  + newt mean phenotype remain small. The mean phenotypes do not intersect
 * 1.0e-11_5.0_1.0e-09_0.05 
-  + 
+  + Newt and snake mean phenotype is positively correlated (84-95)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + The correlation between the difference and local correlation values was slightly negative (3 trials)
+  + Snake mean phenotype has larger jumps, but the newt mean phenotype has a higher level of toxicity
 * 1.0e-11_5.0_1.0e-10_0.5 
-  + 
+  + Newt and snake mean phenotype is positively correlated (43-83)
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + The correlation between the difference and local correlation values was slightly negative (4 trials)
+  + Snake and newt mean phenotype go up together and intersect
 * 1.0e-11_5.0_1.0e-11_5.0 
-  +
+  + Newt and snake mean phenotype is positively correlated in 3 trials (39-80)
+  + Newt and snake mean phenotype is negatively correlated in 1 trial (-4) 
+  + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
+  + Newt mean phenotype is bigger than snake mean phenotype, even though they have the same GA
+
+### What happens over time (looking at the beginning. middle, and late part of my simulations)
+
+I have noticed that my results change during different stages of my simulation.
+In the beginning of the simulation (100-5,000 generations), newt and snake mean phenotypes seem to start interacting by slowly getting larger.
+In the middle of my simulation (10,000-15,000 generations), newt and snake mean phenotypes are getting larger at an increased rate.
+In the late part of my simulation (25,000-30,000 generations), newt and snake mean phenotypes are more stable (phenotypes are no longer dramatically increasing).
+
+First, I look at the beginning of my simulations.
+I look at how newt/snake mean phenotypes and population sizes interact.
+I look at a pair of plots for each trial to observe their similarities and differences.
+First we compare newt population size to snake population size, with individual points' color representing the difference between snake and newt mean phenotype (red=more toxic blue=more resistant).
+The entire plot is composed of a 5,000 generation span, with each data point being from one generation.
+The second plot in the pair is a histogram of the differences between snake and newt phenotype and population size (green=phenotype dif, purple=population size dif).
+In the differences histogram points on the right of the 0 (black line) indicate snakes have a higher value, while points on the left of the line indicate newts have a higher value.
 
@@
 
-min_gen=5000
-max_gen=10000
+min_gen=100
+max_gen=5000
 
 for(i in 1:length(unique(GA1_tall_tall_file$rep))){
-  myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
+  myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
-  plot(myine)
-}
-
-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-09_0.05_1.0e-09_0.05_0")
+  myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
+  suppressMessages(plot(myine))
+}
+
+```
+
+At the beginning of the simulations newt and snake population size is the same.
+Newt and snake phenotypes at the beginning of the simulation are a result of their set GAs (from msprime).
+Overtime and through their co-evolution the population sizes and phenotypes of newts and snakes vary based on the GA combination.
+I ask what are the similarities/differences between the trials and what how do the GA combinations differ from each other?
+
+In the scatter plots I noticed two shapes that form, a hill which typically is red (newts have higher phenotype) and a boomerang which is typically blue (snakes have a higher phenotype).
+I also noticed that not very many of the GA combinations flip between the two colors.
+There are noticeable differences between the GA combinations, the evolution in each of them is not identical.
+However, these changes differ across the trials (simulation is very stochastic).
+
+The histogram plots mirror what I observed in the scatter plots.
+Each GA combination plot looks very similar to each other.
+Between the different GA and trials it seems that snakes are likely to have a larger population size.
+In the beginning of the simulations the difference between newt ans snake phenotype is very close to 0.
+
+##### Summary
+
+Next, I will look at some summary plots.
+These plots display newt population size by snake population size and the difference between mean snake and newt phenotype by snake population size.
+Each color of the points is the GA of snakes and each shape of the points is the GA of newts.
+There are 4 of the same shape/color combination for each of the trials.
+My goal is to observe is there are clusters of shapes/colors.
+
+```{r, early plots summary}
+
+min_gen=100
+max_gen=5000
+
+# summary
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+##### Heatmap
+
+```{r, early plots Heatmap}
+
+min_gen=100
+max_gen=5000
+#heatmap
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 for(i in 1:length(unique(GA1_tall_tall_file$rep))){
-  myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
+  myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
-  plot(myine)
-}
-
-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-09_0.05_1.0e-09_0.05_0")
+  myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
+suppressMessages(plot(myine))
+}
+
+```
+
+##### Summary
+
+```{r, mid plots summary}
+
+min_gen=10000
+max_gen=15000
+
+# summary
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+##### Heatmap
+
+```{r, mid plots Heatmap}
+
+min_gen=10000
+max_gen=15000
+#heatmap
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 max_gen=30000
-rep=0
 
 for(i in 1:length(unique(GA1_tall_tall_file$rep))){
-  myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
+  myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
-  plot(myine)
-}
-
-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=min_gen, max_gen=max_gen, pattern="1.0e-09_0.05_1.0e-09_0.05_0")
+  myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
+  suppressMessages(plot(myine))
+}
+
+```
+
+##### Summary
+
+```{r, late plots summary}
+
+min_gen=25000
+max_gen=30000
+
+# summary
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+##### Heatmap
+
+```{r, late plots Heatmap}
+
+min_gen=25000
+max_gen=30000
+#heatmap
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 file_name= "Snake_1.0e-09_0.05_Newt_1.0e-09_0.05_2"
+spegen=25001
+
+GA1<-grid_tall_file[which(grid_tall_file$snake_newt_rep==file_name & grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+```{r, cor grid by location round 2}
+
+#grid_tall_file
+
+file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3"
 spegen=25001

### 2022-07-18 graphs_newt_snakes/Tall_GA1.Rmd
finished my write up to the tall map and made an html. I snet this to Peter and am excited to hear his response.

@@
 title: "Tall"
-output: html_document
+output:
+  html_document: default
+  pdf_document: default
 ---
@@
 
-### Goal:
-
-Think & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs) can lead to. 
-I.E. is there spacial correlation between the phenotype? If so when/why?
+## Goal:
+
+Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to.
 
@@
 Can I find a certain GA or set of GAs that are similar to the correlation between real newts and snake phenotypes across different locations in space?
-
-### Background
+I.E.
+is there spacial correlation between newt and snake phenotype?
+If so when/why?
+
+Why does mutational variance matter?
+
+## Background
 
 Evolution textbooks often highlight the interaction of toxic newts with resistant snakes as a model example of co-evolution.
-As newts become more toxic snakes become more resistant leading to their phenotypes being highly correlated across space.
-There are about 3-4 mutations that make a snake resistant to the toxin have been discovered.
-One-two of these mutations have a large effect leading to a high toxin resistance in snakes.
-However, these mutations break an ion-channel leading the snakes to be slower (potentially more venerable to predators).
+As newts become more toxic, snakes become more resistant, leading to their phenotypes being highly correlated across space.
+There are about 3-4 mutations discovered, that make a snakes resistant to toxin.
+One-two of these mutations have a large effect leading to high toxin resistance.
+However, these mutations break an ion-channel leading to a decrease in crawling speed (potentially making a snake more venerable to predators).
 This suggests that the genetic architecture (GA) for resistance within snakes has a low mutation rate with a large effect size.
-The mutations that allow newts to be toxic (or at least resistant to their own toxin) have yet to be determined (2022).
-Thus we may ask are there many or only a few mutations that lead to newt toxicity?
+In newts, the mutations that allow them to be toxic (or at least resistant to their own toxin) have yet to be determined (2022).
+Thus we may ask, are there many or only a few mutations that lead to newt toxicity?
 Do these mutations have a large or small effect?
 
-### Experiment
-
-I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction at different genetic architectures (GAs) in a spatial setting.
+## Experiment
+
+I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction with different genetic architectures (GAs) in a spatial setting.
 I hypothesized that we would see an interaction (co-evolutionary arms race) between newt and snake phenotype under some GA combinations when newts and snakes were evolving over geographical space.
@@
 These simulations have a msprime (coalescent/burn in/random genetic variation) and then run for 50,000 generations in SLiM (co-evolution) (all with the same GA values).
+I ran four trials for each GA combination.
 
@@
  if(red_blue==FALSE){
-  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=8))
+  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
   }
@@
 
-### Mean Phenotype Whole Simulation
+## Mean Phenotype Whole Simulation
 
@@
 There are 4 line per color that represent the different replicas that I ran.
-**Note this is a mean for the entire population.** Mutational variance increases for the snakes as you go down (top to bottom) the figure and increases for the newts as you go across (left to right).
+**Note this is a mean for the entire population.** Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).
 
@@
 This indicates that there might be different selection pressure for newts and snakes, which is similar describes other works that discuss predator-prey interactions.
-Snakes really only had a higher phenotype when newts had a low mutation variance.
+
+Snakes had a higher phenotype when newts had a low mutation variance.
 Even when snakes had a higher mutational variance, newts still had a higher phenotype on average (the entire length of the simulation).
@@
 2) There is a cost to having a high phenotype.
-In the last row & column mutations that arise might have too high of a phenotype and die out quickly (making the cost higher might change some of the results, it would be cool to see if the top right difference between newt and snake mean phenotype grows with a more relaxed cost).
-This observation is interesting to me for two reasons 1) in the real newt-snake example snakes always seem to have a higher phenotype and 2) snakes seem to have more of a genetic architecture with a few mutations of high effect size.
-There are some other real factors that I think about like the difference between life history factors of newts and snake (reproduction 1-2 years vs 5-6 years or the ability to move around)
+In the last row & column mutations that arise might have too high of a phenotype and die out quickly (making the cost higher might change some of the results/ it would be cool to see if the top right difference between newt and snake mean phenotype grows with a more relaxed cost).
+This observation is interesting to me for two reasons a) in the real newt-snake example snakes always seem to have a higher phenotype and b) snakes seem to have more of a genetic architecture with a few mutations of high effect size.
+There are some other real factors that I think about like the difference between life history factors of newts and snake (reproduction 1-2 years vs 5-6 years or the ability to move around).
 
@@
 
-```{r, graphing by gen}
+```{r, graphing by gen trends}
 trends_by_gen(GA1_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 15000)
@@
 Another thing I would like to note, is that when the GA of newts and snakes are the same newts usually end up with a higher phenotype.
-The case of the third GA for snakes and the 4 GA for newts is extremely weird (is it the only instance where snakes end up with a higher phenotype that is consistently higher through out the simulation and not in the first column).
-
-### Connection between higher phenotype and population
+The case of the 3rd GA for snakes and the 4th GA for newts is extremely weird (is it the only instance where snakes end up with a higher phenotype that is consistently higher through out the simulation and not in the first column).
+
+#### Connection between higher phenotype and population
 
@@
 I looked at the results between 5,000 - 10,000 generations where I saw most of the increase in newt and snake phenotype.
-The first figure plot newt population size by snake population size with the color representing the difference between snake and newt mean phenotype (red=newts have a higher mean phenotype, blue=snakes have a higher mean phenotype).
-The there is GA (an intermediate one) seems to do better then all of the other GAs (blue row, red column).
+The first plot has newt population size by snake population size with the color representing the difference between snake and newt mean phenotype (red=newts have a higher mean phenotype, blue=snakes have a higher mean phenotype).
+The third GA (an intermediate one) seems to do better then all of the other GAs (blue row (3), red column (3)).
 However, this is dependent on the point in the simulation you focus on.
@@
 This also shows the asymmetrical nature between the predator-prey interaction (higher max population sizes seen in snakes).
-The population size is also more variable than the phenotype (dif in population size has a wider range).
-
-### Correlation
+The population size is also more variable than the phenotype (difference in population size has a wider range).
+
+## Correlation
 
 The next section I aim to look at how correlated newt and snakes are at local populations across the geographical area.
-I am examining correlation between newt and snake phenotypes, population sizes newts and snakes, amount of toxin and snake population, and the amount of resistance and newt population size.
+I am examining correlation between newt and snake phenotypes, population sizes of newts and snakes, amount of toxin and snake population, and the amount of resistance and newt population size.
 I predicted that there would be a positive correlation between the phenotypes, and a negative correlation between population sizes, and the amount of toxin/resistance and population size.
 Below is a legend for the first two plots.
-The third plot is colored by trial
+The third plot is colored by trial.
 
@@
 
-boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
@@
 I also wonder if correlation occurs more when one of the species has a higher phenotype (like newt phenotype drive snake phenotype, but snake phenotype does not drive newt phenotype).
+
 When looking a figure 2 it seems like most values are no different from 0.
@@
 4) It might depend on generation window.
-5) What is happen in my simulation leading to correlation/no correlation (maybe not getting good local measurements)?
+5) What is happening in my simulation leading to correlation/no correlation (maybe not getting good local measurements)?
 I wonder if we only used some of the grids (like the corners) if the correlation values would change.
+
 The most informative figure to me in this set was the third one.
@@
 
-I decided to look at the trial correlation distributions for different windows of time for all 16 GA combination.
+I decided to look at the trial correlation distributions for different windows of time for all 16 GA combinations.
 Each of these figures are over a 5,000 generation window.
@@
 Things seem to be moving like waves in different directions (more positive or negative?).
-The only GA simulation that matches the real newt-snake data is the first one (high mutation rate- low effect size).
-These simulations reach an area of high correlation, because the change in phenotype occurs rapidly in small effects.
+The only GA simulation that matches the real newt-snake data is the first one (high mutation rate-low effect size).
+These simulations reach an area of high correlation, is it because the change in phenotype occurs rapidly in small effects?
 I wondered if given more time or more space if any other of the GA combination would become more correlated?
@@
 What do the local population distribution of newts and snakes look like (is there some avoidance or weird density effect)?
-How are NAs changing this measurement?
+How are NAs (not enough individuals in a certain area) changing this measurement?
 Is there a difference in the local correlation when a certain species is driving convolution?
 
-### Correlation across time
+## Correlation across time
 
@@
   + Possibly random, but the correlation between snake & local and difference & local were nearly identical for all four trials.
-  + Newt mean phenotype mostly flat, snake mean phenotype can start lower and enceed newt mean phenotype
+  + Newt mean phenotype mostly flat, snake mean phenotype can start lower and exceed newt mean phenotype
 * 1.0e-09_0.05_1.0e-09_0.05 
@@
 * 1.0e-10_0.5_1.0e-08_0.005 
-  + Newt and snake mean phenotype is a bit less positively correlated (42-60)
+  + Newt and snake mean phenotype is less positively correlated (42-60)
   + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
@@
   + Local phenotype correlation is not consistently correlated to snake mean phenotype, newt mean phenotype, or the difference (snake-newt mean phenotype)
-  + These mean phenotypes are strange. The snake mean phenotype has larger jumps. Newt and snake mean phenotypes closly match
+  + These mean phenotypes are strange. The snake mean phenotype has larger jumps. Newt and snake mean phenotypes closely match
 * 1.0e-10_0.5_1.0e-10_0.5 
@@
 
-### What happens over time (looking at the beginning. middle, and late part of my simulations)
+## What happens over time (looking at the beginning. middle, and late part of my simulations)
 
@@
 In the middle of my simulation (10,000-15,000 generations), newt and snake mean phenotypes are getting larger at an increased rate.
-In the late part of my simulation (25,000-30,000 generations), newt and snake mean phenotypes are more stable (phenotypes are no longer dramatically increasing).
+In the late part of my simulation (45,000-50,000 generations), newt and snake mean phenotypes are more stable (phenotypes are no longer dramatically increasing).
 
@@
 
-##### Summary
+#### Summary
 
@@
 
-##### Heatmap
+After a quick glance there does seem to be some grouping occurring.
+A lot of blue and green points seem to be higher in the line (snakes have a higher population size & phenotype).
+This indicates that the intermediate snake GAs do well in the early stages of a co-evolutionary arms race.
+There is also a group of + signs that are also located at the top of the line, suggesting that newt GA 4 does worse in an arms race.
+We can see a similar effect when snake GA is GA #4, purple points cluster at the bottom of the line.
+A group of squares cluster towards the bottom of the line, indicating that newts with the third GA have a higher population size and phenotype during the early part of the simulation.
+It is strange that triangles do not do the same thing??
+<- could this be something that might be occurring to a difference in selection pressure?
+
+#### Heatmap
+
+In this section I look at a simulation summary presented as a heatmap.
+This heatmap averages the snake population size or snake-newt mean phenotype over a selected range of generations.
+This heat map gives a simplified picture of what is occurring over a 5,000 generation portion of my simulation for both the GA combinations and trials.
+The goal is to see patterns that are similar between the trials and different between the GA combinations.
 
@@
 ```
+
+Surprisingly, even towards (at lease what I consider near) the beginning of the simulation we can see some pattern emerging.
+Specifically, I can see that the third column has fewer snakes (purple) and a higher newt phenotype (red) than the rest of the simulations.
+The snake GA set of 1.0e-10/0.5 has a higher population size of snakes and leans to a higher snake phenotype.
+Something is a bit off for the snake GA set of 1.0e-9/0.05, there are some areas of a higher population size, but the newts have a slightly larger phenotype.
+Sometimes the newt population size is higher, but the snakes have a larger phenotype.
+
+### Mid-simulation
 
@@
 
-##### Summary
+As newts and snakes co-evolution their population sizes and phenotypes should be a result of their genetic architecture.
+In this time frame the newts seem to have a higher phenotype in their middle genetic architecture (#2, #3 column).
+It is not perfectly identical across the trials, but more often than not, newts with GA #2, #3 are winning in a co-evolutionary arms race.
+If newts have only a slightly higher phenotype they do not have a larger population size.
+
+The scatter plots all have a smear shape that is either in a linear or flat line.
+None of GA combinations have a large range in phenotypes or population sizes, and very few show the change from one species having a higher phenotype to another.
+
+The histogram plots mirror what I observed in the scatter plots.
+The difference between snake and newt phenotype doesn't change all that much, but population size does.
+A surprising observation is that just a little bit more resistance leads to a higher population size in snakes than a little bit of toxicity does in newts.
+
+#### Summary
 
@@
 
-##### Heatmap
+It's weird that it looks like there are two lines?
+One line with snake GA of #2 and #3 (blue and green) and another with snake GA of #1 and #4 (pink and purple).
+I noticed that newt GA #2 and #3 (squares and triangles) tended to be in the lower part of the line (newts more successful).
+There are a lot of blue and green circles toward the top of the plots indicating newt GA #1 does worse when snake GA is #2 or #3.
+There are a lot of blue, pink, and green + toward the top of the plots, which suggests that newt GA #4 does worse when snake GA is #1, #2 or #3.
+
+#### Heatmap
 
@@
 
+Both of these heatmaps show major similarities between the trials.
+When newts have a GA of #2 and #3 the newt phenotype and population size is larger.
+When the newt GA is #3 there is an even larger newt advantage.
+When the newts have a GA of #1 or #4 snakes have a larger population size and phenotype.
+This result hold regardless of the snakes GA.
+Although, snakes with GA #3 have a large advantage over newts with GA #1 or #4.
+
+### Late simulation
+
 ```{r, late plots}
 
-min_gen=25000
-max_gen=30000
+min_gen=45000
+max_gen=50000
 
@@
 ```
-
-##### Summary
+In the later stages of my simulation things have been running for a while and hopefully populations will be in equilibrium.
+Space makes getting to an equilibrium state difficult to define.
+Hypothetically, there could be areas that are co-evolving and areas that are not, an individuals can move between different areas, leading to a steady sate that cycles.
+When looking at the scatter plots I noticed that there was only one row and one column that had consistently had one species with higher population sizes and phenotypes.
+The species that had the first GA would typically be losing in a co-evolutionary arms race.
+The species that ended up with the lowest mutation variance ended up being left behind.
+When both species had GA #1 the phenotype was neutral while snakes had a larger population size.
+Most of the scatter plots have slight blue and red dotes, with the histograms having small phenotype differences, and larger snake population size.
+Snakes having a GA of #4 also still had them at a disadvantage (newts had a larger phenotype and population size).
+
+#### Summary
 
@@
 
-min_gen=25000
-max_gen=30000
+min_gen=45000
+max_gen=50000
 
@@
 
-##### Heatmap
+Wow each color is in its own line!
+Snake GA #2 and #3 lead to a higher snake population size and phenotype.
+Newt GA #1 (circles) tend to lead to lower newt population sizes and phenotypes.
+Newt GA #2 and #3 (triangles and squares) lead to a higher new phenotype and population size.
+Snake GA #1 and #4 lead to newts having a larger population size and phenotype.
+There is some sort of pattern appearing from the GA combinations.
+Best to worst snake GA #2 -> #3 -> #4 -> #1!
+Best to worst newt GA #2 -> #3 -> #4 -> #1 OMG these match over population size!
+There is a difference between the GAs!
+
+#### Heatmap
 
@@
 
-min_gen=25000
-max_gen=30000
+min_gen=45000
+max_gen=50000
 #heatmap
@@
 
-Next, I will discuss a summary plot for the different GA sets.
-The first plot has the newt population size by snake population size (a larger population size might indicate a co-evolution advantage) and the second plot is the difference between snake and newt mean phenotype and snake population size.
-There are four points for each GA set (one for each replica).
-Color will represent the four GAs of the snake and the shapes will represent the four GAs of newts.
-Each plot will have a starting generation and an ending generation (that can easily be changed).
-
-```{r, graphing the summary}
-
-GA_summary(GA1_tall_tall_file, min_gen=5000, max_gen=10000, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-GA_summary(GA1_tall_tall_file, min_gen=5000, max_gen=10000, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-```
-
-This next section is a more visual representation of the summary plots.
-Here, there will be four heatmaps.
-The first two show the results from the GA1 experiment with the last two showing the results from the GA2 experiment.
-The heatmaps have the newt GAs on the x-axis and the snake GAs and the simulation replication number on the y-axis.
-The colors in the heat might will either be yellow to purple for the snake population size or blue to red for the difference in mean phenotypes.
-
-```{r, heatmap}
-
-#params_GA1
-
-build_heatmap(GA1_tall_tall_file, min_gen=5000, max_gen=10000, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-build_heatmap(GA1_tall_tall_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-#build_heatmap(GA1_tall_tall_file, min_gen=5000, max_gen=10000, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=F)
-
-```
+As I saw with the summary plots there is remarkable color gradient going from GA #2 -> #3 -> #4 -> #1 for both the newts and snakes.
+For example the 4th row set (snake GA #4), snake population size grows in the order from GA #2 -> #3 -> #4 -> #1.
+In this row newt phenotype diminishes GA #2 -> #3 -> #4 -> #1.
+The same thing happens in in the columns.
+Column 1 (newt GA #1) snake population size and phenotype get smaller from GA #2 -> #3 -> #4 -> #1.
+All column gradients go lighter to darker in order GA #2 -> #3 -> #4 -> #1.
+All row gradients go lighter to darker in GA #2 -> #3 -> #4 -> #1.
 
 ## What is up with the correlations
+
+We got to see how the correlation of local phenotype changed overtime.
+Now, I will take a closer look at what is occurring at the local level.
+There were 100 local measurements taken every 20 generation for all of my simulation.
+I took in information about the number of individuals, the min/mean/max phenotype, and the phenotypes sd.
+To see what is going on, I will plot a measurement (i.e.
+phenotype) of both newts and snakes at each local population.
+I will also local newt phenotype by local snake phenotype to see the if there truly is correlation.
+In the correlation plots I color each point by its location in the map corner, edge, middle (orange, green, blue).
+
+We will look at two simulations.
+1) Snake_1.0e-09_0.05_Newt_1.0e-09_0.05_2 which did not have a high correlation in the plots above.
+2) Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3 which had high correlation values.
+I will show two plots for each file, one in the middle of my simulation (25,000 gen) and one towards the end (49,000 gen).
+Snake and newt local phenotypes will be squares and circles, respectively.
+Locations run 1-5 on the x-axis and 1-20 on the y axis.
+The locations are more evenly space in SLiM, because my map was tall (please ignore the squished-ness here).
+
+### Snake_1.0e-09_0.05_Newt_1.0e-09_0.05_2
 
@@
 
-```{r, cor grid by location round 2}
+After examining this plot, I see that there is no obvious correlation between newt and snake phenotype.
+There is one area with a higher newt phenotype, but that area does not also have a higher snake phenotype.
+There is only one area where newts and snakes have a low phenotype and that low phenotype is probably increasing the correlation (possibly incorrectly).
+I also try to look to see if the edges differ from the center of my simulations.
+In this case it seems like center and edges of my simulation are very similar.
+So now let's look at the later plot.
+
+```{r, cor grid by location lateer}
 
@@
 
-file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3"
-spegen=25001
+file_name= "Snake_1.0e-09_0.05_Newt_1.0e-09_0.05_2"
+spegen=49001
 
@@
 ```
+
+In a later section of this simulation I see a newt phenotype range (darker in the center lighter on the edges) that is not repeated in the snakes (very much the same across the map).
+There is no correlation between newt and snake phenotypes in this plot.
+There is no difference between corner, edge, or middle sample in my simulation.
+
+### Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3
+
+This simulation was more correlated (in a previous section) than the simulation we just observed above.
+
+```{r, cor grid by location round 2}
+
+#grid_tall_file
+
+file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3"
+spegen=25001
+
+GA1<-grid_tall_file[which(grid_tall_file$snake_newt_rep==file_name & grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+The fist thing I noticed in this simulation were stripes that looked so similar that I wondered if my data collection was malfunctioning.
+But after a closer inspection they are not identical.
+There are areas where both newt and snake phenotypes are high and areas where both newt and snake phenotypes are low.
+This leads to a positive correlation between local newt and snake phenotype.
+It is interesting to see them presented in stripes.
+I thought it would look more like squares or blocks.
+I think something is up with how I have placed the locations here.
+There is no noticeable difference between the corner, edge, or middle samples of my simulation.
+Now, lets look at a later point in this simulation.
+
+```{r, cor grid by location round 2 later}
+
+#grid_tall_file
+
+file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3"
+spegen=49001
+
+GA1<-grid_tall_file[which(grid_tall_file$snake_newt_rep==file_name & grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+At a later point in this simulation there is still some stripe action, but there is also a bit of a gradient.
+It seems like the snake phenotype is higher on the edges than in the center.
+There some grey patches in the left, so there might not be a bunch of newts on the left side of the map.
+There is no noticeable difference between the corner, edge, or middle section of my simulation map.
+The stripe-ness still bewilders me...
+
+## Animation of correlation
+
+In this plot we look at how the newt and snake phenotypes in "uncorrelated" Snake_1.0e-09_0.05_Newt_1.0e-09_0.05_2 file interact though-out time.
+I wonder if there is too much stochasticity in the simulation to get a good correlation between newts and snakes.
+Here we will look at how newt and snake phenotypes at local areas are interacting
 

### 2022-07-21 graphs_newt_snakes/GA3.Rmd
I figured out that there was a grid making problem where I switched columns for rows and have corrected it. I also discoved that when there was only 1 individual in a grid the phenotype was automatically set to one. I also corrected this. I have also started preparing for a new simulation with different mutation rates and effect sizes for the lowest mutatinal varance from GA1

---
title: "GA3"
output: html_document
date: '2022-07-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

GA3 file will be the slow evolution file.

- 1e-8*(0.005)^2 = 2.5e-13
- 1e-9*(0.0158)^2 = 2.5e-13
- 1e-10*(0.05)^2 = 2.5e-13
- 1e-11*(0.158)^2 = 2.5e-13

### 2022-07-21 graphs_newt_snakes/Tall_GA1.Rmd
I figured out that there was a grid making problem where I switched columns for rows and have corrected it. I also discoved that when there was only 1 individual in a grid the phenotype was automatically set to one. I also corrected this. I have also started preparing for a new simulation with different mutation rates and effect sizes for the lowest mutatinal varance from GA1

@@
 
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+#data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+#data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+data_long_mean_short$y_loc<- rep(c(rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(2, 2)),20)
+data_long_mean_short$x_loc<-c(rep.int(1, 10),rep.int(2, 10),rep.int(3, 10),rep.int(4, 10),rep.int(5, 10),rep.int(6, 10),rep.int(7, 10),rep.int(8, 10),rep.int(9, 10),rep.int(10, 10),rep.int(11, 10),rep.int(12, 10),rep.int(13, 10),rep.int(14, 10),rep.int(15, 10),rep.int(16, 10),rep.int(17, 10),rep.int(18, 10),rep.int(19, 10),rep.int(20, 10))
 
@@
 
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[newt$location %in% list(0, 4, 95, 99)] <- "corner"
+newt$info[newt$location %in% list(1,2,3,5, 9,10, 14,15, 19,20, 24,25, 29,30, 34,35, 39,40, 44,45, 49,50, 54,55, 59,60, 64,65, 69,70, 74,75, 79,80, 84,85, 89,90, 94, 96, 97,98)]   <- "edge"
+
+#newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+#newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
 newt$info[is.na(newt$info)]<- "middle"
@@
 file_name= "Snake_1.0e-09_0.05_Newt_1.0e-09_0.05_2"
-spegen=25001
 
@@
 plotty_mean_min_s$newt_values<-plotty_mean_min[which(plotty_mean_min$species=="newt"),"measurement"]
-plotty_mean_min_s$edge <- "not edge"
-plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(0, 1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20, 39, 40, 59, 60, 79, 80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98,99)
+plotty_mean_min_s$edge <- "FALSE"
+#plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(0, 1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20, 39, 40, 59, 60, 79, 80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98,99)
+
+plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(1,2,3,5, 9,10, 14,15, 19,20, 24,25, 29,30, 34,35, 39,40, 44,45, 49,50, 54,55, 59,60, 64,65, 69,70, 74,75, 79,80, 84,85, 89,90, 94, 96, 97,98)
 
@@
 plotty_mean_min_s$info[plotty_mean_min_s$edge=="FALSE"]  <- "middle"
-plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 19, 80, 99)] <- "corner"
-
+#plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 19, 80, 99)] <- "corner"
+plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 4, 95, 99)] <- "corner"
 p <- plotty_mean_min_s %>%

### 2022-07-22 graphs_newt_snakes/Tall_GA1.Rmd
thinking about what an allele is in slim

@@
 plotty_mean_min_s$newt_values<-plotty_mean_min[which(plotty_mean_min$species=="newt"),"measurement"]
-plotty_mean_min_s$edge <- "FALSE"
+#plotty_mean_min_s$edge <- "FALSE"
 #plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(0, 1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20, 39, 40, 59, 60, 79, 80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98,99)
 
-plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(1,2,3,5, 9,10, 14,15, 19,20, 24,25, 29,30, 34,35, 39,40, 44,45, 49,50, 54,55, 59,60, 64,65, 69,70, 74,75, 79,80, 84,85, 89,90, 94, 96, 97,98)
-
-plotty_mean_min_s$info[plotty_mean_min_s$edge=="TRUE"]  <- "edge"
-plotty_mean_min_s$info[plotty_mean_min_s$edge=="FALSE"]  <- "middle"
-#plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 19, 80, 99)] <- "corner"
-plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 4, 95, 99)] <- "corner"
+#plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(1,2,3,5, 9,10, 14,15, 19,20, 24,25, 29,30, 34,35, 39,40, 44,45, 49,50, 54,55, 59,60, 64,65, 69,70, 74,75, 79,80, 84,85, 89,90, 94, 96, 97,98)
+
+#plotty_mean_min_s$info[plotty_mean_min_s$edge=="TRUE"]  <- "edge"
+#plotty_mean_min_s$info[plotty_mean_min_s$edge=="FALSE"]  <- "middle"
+plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 19, 80, 99)] <- "corner"
+plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(1,2,3,5, 9,10, 14,15, 19,20, 24,25, 29,30, 34,35, 39,40, 44,45, 49,50, 54,55, 59,60, 64,65, 69,70, 74,75, 79,80, 84,85, 89,90, 94, 96, 97,98)] <- "edge"
+plotty_mean_min_s$info[is.na(plotty_mean_min_s$info)]<- "middle"
+#unique(plotty_mean_min_s$info)
 p <- plotty_mean_min_s %>%
   plot_ly(
-    x = ~as.numeric(newt_values), 
-    y = ~as.numeric(measurement), 
+    x = ~as.numeric(newt_values), # newt pheno
+    y = ~as.numeric(measurement), #snake pheno
     frame = ~generation, 
     text = ~factor(location), 
-    color = ~factor(info), 
+    color = ~info, 
     hoverinfo = "text",

### 2022-07-22 graphs_newt_snakes/GA3.Rmd
I fixed the way the grid was orgonized. I also strated the GA3 experiment

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+#knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)
+
+library(ggplot2)
+library(viridis)
+library(colorspace)
+library(gridExtra)
+library(tidyverse)
+require(reshape2)
+library(plyr)
+library(gridGraphics)
+library(grid)
+library(knitr)
+library(kableExtra)
+library("reshape")
+library(ggplot2)
+library(ggpubr)
+theme_set(theme_pubr())
+library(stringr)
+library(patchwork)
 ```
@@
 GA3 file will be the slow evolution file.
+The main goal will be testing to see if there is an effect caused by mutation rate or effect size when the mutational variance between two species is the same.
+
+Prediction: Higher mutation rate will be advantages in the beginning of a simulation. A higher effect size might lead to more spatial co-evolution. Space might separate the effects.
+
+For the initial part of this experiment I will only be running one trial per GA combination
+
+GA combinations:
 
@@
 - 1e-11*(0.158)^2 = 2.5e-13
+
+```{r, data gathering}
+
+snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
+
+GA1_tall <- list.files(path="~/Desktop/tall_map", pattern="_lit_", full.names=TRUE, recursive=FALSE)
+GA1_tall_cor_files <- list.files(path="~/Desktop/tall_map", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+grid_tall_files <- list.files(path="~/Desktop/tall_map", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+
+GA1_tall_tall_file<- data.frame()
+GA1_cor_tall_file<- data.frame()
+grid_tall_file<-data.frame()
+
+oldstand=0
+letter=0
+newt_unique=0
+newt_numb = 0
+for(i in seq(1, length(GA1_tall), 1)){
+  stand <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  up <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  phrase = paste0(stand, "_", up)
+  if (stand!=oldstand){
+    oldstand=stand
+    letter = letter + 1
+  }
+
+    if (phrase=="1.0e-08_0.05" ){
+    newt_numb =  1
+   }
+    if (phrase=="1.0e-09_0.158114"){
+    newt_numb =  2
+   }
+      if (phrase=="1.0e-10_0.5"){
+    newt_numb =  3
+   }
+    if (phrase=="1.0e-11_1.58114"){
+    newt_numb =  4
+   }
+
+      if (phrase=="1.0e-12_5.0"){
+    newt_numb =  5
+   }
+  print(newt_numb)
+  if (i<=length(GA1_tall)){
+
+  stand <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  up <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  phrase = paste0(stand, "_", up)
+
+   if (phrase=="1.0e-08_0.005"){
+    newt_numb =  1
+   }
+    if (phrase=="1.0e-09_0.05"){
+    newt_numb =  2
+   }
+      if (phrase=="1.0e-10_0.5"){
+    newt_numb =  3
+   }
+    if (phrase=="1.0e-11_5.0"){
+    newt_numb =  4
+   }
+
+  GA1_temp_file <- read.csv(GA1_tall[i], header = TRUE)
+  GA1_temp_file$sim <-LETTERS[letter]
+  GA1_temp_file$size <-newt_numb
+  GA1_temp_file$rep <-unlist(str_split(unlist(str_split(GA1_tall[i],"rep_"))[3], "_"))[1]
+  GA1_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA1_tall[i],"snake_mu_rate_"))[2], "_"))[1]
+  GA1_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  GA1_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  GA1_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  GA1_tall_tall_file <- rbind(GA1_tall_tall_file, GA1_temp_file)
+
+  cor_temp_file <- read.csv(GA1_tall_cor_files[i], header = TRUE)
+  cor_temp_file$sim <-LETTERS[letter]
+  cor_temp_file$size <-newt_numb
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA1_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  GA1_cor_tall_file <- rbind(GA1_cor_tall_file, cor_temp_file)
+
+  grid_temp_file <- read.csv(grid_tall_files[i], header = TRUE)
+  grid_temp_file$sim <-LETTERS[letter]
+  grid_temp_file$size <-newt_numb
+  grid_temp_file$rep <-unlist(str_split(unlist(str_split(grid_tall_files[i],"rep_"))[3], "_"))[1]
+  grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  grid_tall_file <- rbind(grid_tall_file, grid_temp_file)
+
+  }
+
+}
+
+GA1_tall_tall_file$dif <- GA1_tall_tall_file$Snake_mean_Pheno-GA1_tall_tall_file$Newt_mean_Pheno
+
+GA1_tall_tall_file$group_rep <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep)
+
+GA1_tall_tall_file$group <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd)
+
+grid_tall_file$snake_newt_rep <- paste0("Snake_",grid_tall_file$snake_mu_rate, "_", grid_tall_file$snake_mu_effect_sd, "_Newt_",grid_tall_file$newt_mu_rate, "_", grid_tall_file$newt_mu_effect_sd, "_", grid_tall_file$rep)
+```

### 2022-07-22 graphs_newt_snakes/Tall_GA1.Rmd
I fixed the way the grid was orgonized. I also strated the GA3 experiment

@@
 
-data_long_mean_short$y_loc<- rep(c(rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(2, 2)),20)
+data_long_mean_short$y_loc<- rep(c(rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),20)
 data_long_mean_short$x_loc<-c(rep.int(1, 10),rep.int(2, 10),rep.int(3, 10),rep.int(4, 10),rep.int(5, 10),rep.int(6, 10),rep.int(7, 10),rep.int(8, 10),rep.int(9, 10),rep.int(10, 10),rep.int(11, 10),rep.int(12, 10),rep.int(13, 10),rep.int(14, 10),rep.int(15, 10),rep.int(16, 10),rep.int(17, 10),rep.int(18, 10),rep.int(19, 10),rep.int(20, 10))
@@
 The stripe-ness still bewilders me...
+
+I had rows and columns flipped. After correcting for that everything looks better!
 

### 2022-07-27 graphs_newt_snakes/GA3.Rmd
looked at one trail from GA3 and didnt look impresive. I am running the next 3 trials and reruning GA1 with corrected grids. I am also thinking of ways to track allele freqs in a meaningful way. Right now there are some notes in cost1on1 slim, but i plan on doing some reading (to see what kind of information is useful) before I spend a lot of time on coding

--- 2022-07-21 graphs_newt_snakes/GA3.Rmd
@@
 - 1e-11*(0.158)^2 = 2.5e-13
+
+```{r, data gathering}
+
+snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
+
+GA3_tall <- list.files(path="~/Desktop/GA3", pattern="_lit_", full.names=TRUE, recursive=FALSE)
+GA3_tall_cor_files <- list.files(path="~/Desktop/GA3", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+GA3_GA3_grid_tall_files <- list.files(path="~/Desktop/GA3", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+
+GA3_tall_tall_file<- data.frame()
+GA3_cor_tall_file<- data.frame()
+GA3_GA3_grid_tall_file<-data.frame()
+
+#oldstand=0
+letter=0
+#newt_unique=0
+#newt_numb = 0
+for(i in seq(1, length(GA3_tall), 1)){
+  stand <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  up <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  phrase = paste0(stand, "_", up)
+  letter = letter +1
+  # if (stand!=oldstand){
+  #   oldstand=stand
+  #   letter = letter + 1
+  # }
+  # 
+  #   if (phrase=="1.0e-08_0.05" ){
+  #   newt_numb =  1
+  #  }
+  #   if (phrase=="1.0e-09_0.158114"){
+  #   newt_numb =  2
+  #  }
+  #     if (phrase=="1.0e-10_0.5"){
+  #   newt_numb =  3
+  #  }
+  #   if (phrase=="1.0e-11_1.58114"){
+  #   newt_numb =  4
+  #  }
+  # 
+  #     if (phrase=="1.0e-12_5.0"){
+  #   newt_numb =  5
+  #  }
+  # print(newt_numb)
+  # 
+  # if (i<=length(GA3_tall)){
+
+  # stand <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  # up <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  # phrase = paste0(stand, "_", up)
+  # 
+  #  if (phrase=="1.0e-08_0.005"){
+  #   newt_numb =  1
+  #  }
+  #   if (phrase=="1.0e-09_0.05"){
+  #   newt_numb =  2
+  #  }
+  #     if (phrase=="1.0e-10_0.5"){
+  #   newt_numb =  3
+  #  }
+  #   if (phrase=="1.0e-11_5.0"){
+  #   newt_numb =  4
+  #  }
+
+  GA3_temp_file <- read.csv(GA3_tall[i], header = TRUE)
+  GA3_temp_file$sim <-LETTERS[letter]
+  #GA3_temp_file$size <-newt_numb
+  GA3_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall[i],"rep_"))[3], "_"))[1]
+  GA3_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_rate_"))[2], "_"))[1]
+  GA3_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  GA3_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  GA3_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  GA3_tall_tall_file <- rbind(GA3_tall_tall_file, GA3_temp_file)
+
+  cor_temp_file <- read.csv(GA3_tall_cor_files[i], header = TRUE)
+  cor_temp_file$sim <-LETTERS[letter]
+  #cor_temp_file$size <-newt_numb
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  GA3_cor_tall_file <- rbind(GA3_cor_tall_file, cor_temp_file)
+
+  GA3_grid_temp_file <- read.csv(GA3_GA3_grid_tall_files[i], header = TRUE)
+  GA3_grid_temp_file$sim <-LETTERS[letter]
+  #GA3_grid_temp_file$size <-newt_numb
+  GA3_grid_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"rep_"))[3], "_"))[1]
+  GA3_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  GA3_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  GA3_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  GA3_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  GA3_GA3_grid_tall_file <- rbind(GA3_GA3_grid_tall_file, GA3_grid_temp_file)
+
+  }
+
+GA3_tall_tall_file$dif <- GA3_tall_tall_file$Snake_mean_Pheno-GA3_tall_tall_file$Newt_mean_Pheno
+
+GA3_tall_tall_file$group_rep <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep)
+
+GA3_tall_tall_file$group <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd)
+
+GA3_GA3_grid_tall_file$snake_newt_rep <- paste0("Snake_",GA3_GA3_grid_tall_file$snake_mu_rate, "_", GA3_GA3_grid_tall_file$snake_mu_effect_sd, "_Newt_",GA3_GA3_grid_tall_file$newt_mu_rate, "_", GA3_GA3_grid_tall_file$newt_mu_effect_sd, "_", GA3_GA3_grid_tall_file$rep)
+
+```
+
+```{r, cor box set up}
+
+boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+    geom_hline(yintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~newt_snake)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=rep))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  xlim(-1.1, 1.1)+
+  facet_wrap(~newt_snake)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  #stat_bin(bins=30)+
+  facet_wrap(~newt_snake)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+suppressMessages(print(plot))
+
+  return(plot)
+}
+
+var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  real_snewt_var = var(snewt$dif)
+  cfile$newt_snake_rep <- paste0("Newt_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_Snake_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
+  var_cor_table=data.frame()
+
+  for(i in 1:length(unique(file$newt_snake_rep))){
+    pattern<-unique(file$newt_snake_rep)[i]
+    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]
+    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]
+
+    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
+    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+  }
+
+  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
+  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+
+  plot <- ggplot(var_cor_table) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+  return(plot)
+}
+
+cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+ file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+  cfile$snake_newt_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
+    #ylim(0,10)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() +theme(legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
+                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
+
+  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
+    #ggtitle(title, subtitle = subt) +
+    ylim(-1.1, 1.1)+
+    #xlab(x_label_cor) + ylab(y_label)+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(),
+                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
+
+  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
+  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
+  toDelete <- seq(0, nrow(cfile), 2)
+  cfile_short <-  cfile[-toDelete, ]
+  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
+    print(paste0("pattern ", pattern))
+  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
+  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
+  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
+  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
+  return(figure)
+}
+
+four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
+  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  geom_hline(yintercept=0, linetype="solid")+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~newt_snake)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+```
+
+```{r, general file and graph making}
+
+#the functions to make the params file and the summary and heatmap figures
+
+create_parm_file <- function(file, min_gen, max_gen){
+params <- data_frame()
+
+for(i in 1:length(unique(file$newt_snake_rep))){
+
+  pattern=unique(file$newt_snake_rep)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep ==pattern),]
+
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=sumitup$snake_mu_rate[1],
+                           newt_mu_rate=sumitup$newt_mu_rate[1],
+                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
+                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
+                           rep=sumitup$rep[1])
+
+  params <- rbind(params, params_temp)
+}
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$newt_snake <- paste0(params$newt, "_", params$snake)
+return(params)
+}
+
+GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+
+file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+
+build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
+  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+
+  params<-create_parm_file(file, min_gen, max_gen)
+
+ my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
+
+ if(red_blue==FALSE){
+  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
+  }
+ if(red_blue==TRUE){
+  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
+ }
+
+  return(my_plot)
+}
+
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+
+  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
+    facet_wrap(~sim)+
+    geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
+    ylim(-1.,2.5)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+  return(plot)
+}
+
+whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
+  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
+  xlim((-1*themax)-5, themax+5)+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+}
+
+pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  themin <- min(file$dif) 
+  themax <- max(file$dif)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(dif), fill="aquamarine4")+
+  xlim((-1*true_max)-1, true_max+1)+
+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file=GA3_tall_tall_file
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$newt_deaths)
+  thepopmax <- max(file$newt_deaths)
+  thedifmin <- min(file$snake_deaths) 
+  thedifmax <- max(file$snake_deaths)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
+  #scale_y_continuous(labels = scales::percent)+
+  #xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  #geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+#two_hist_death_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+
+```
+
+## Mean Phenotype Whole Simulation
+
+```{r, graphing by gen}
+trends_by_gen(GA3_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA3", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
+
+aggregate(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$dif, list(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$group), FUN=mean)
+
+#aggregate(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$dif, list(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
+
+```
+
+#### Connection between higher phenotype and population
+
+```{r, whale}
+min_gen=5000
+max_gen=10000
+rep=0
+
+whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+
+suppressMessages(print(two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+suppressMessages(print(two_hist_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+
+```
+
+## Correlation
+
+Legend:
+
+- "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
+- "CB" = num_newts_By_num_snakes (Green)
+- "CC" = sum_newt_pheno_By_num_snake (Blue)
+- "CD" = sum_snake_pheno_By_num_newt (Purple)
+
+```{r, combo myplots}
+#files
+#GA3_tall_tall_file
+#GA2_long_file 
+#GA3_cor_tall_file
+#GA2_cor_file
+
+ginmin = 10000
+ginmax = 15000
+
+boxplot_cors_by_gen(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+four_types_boxplot_cors_by_gen(GA3_cor_tall_file, "Simulation four Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+```
+
+```{r, GA3 cor by dif windows}
+
+ginmin = 0
+ginmax = 5000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 5000
+ginmax = 10000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 10000
+ginmax = 15000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 15000
+ginmax = 20000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 20000
+ginmax = 25000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 25000
+ginmax = 30000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 30000
+ginmax = 35000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 35000
+ginmax = 40000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 40000
+ginmax = 45000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+ginmin = 45000
+ginmax = 50000
+suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+
+```
+
+## Correlation across time
+
+```{r, GA3 cor and pheno}
+GA3_pattern <- unique(paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep))
+for(i in 1:length(GA3_pattern)){
+  myine<-cor_trends_by_gen(GA3_tall_tall_file, GA3_cor_tall_file, "test", "GA3", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA3_pattern[i])
+  plot(myine)
+}
+
+```
+
+## What happens over time (looking at the beginning. middle, and late part of my simulations)
+
+```{r, early plots}
+
+min_gen=100
+max_gen=5000
+
+for(i in 1:length(unique(GA3_tall_tall_file$rep))){
+  myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
+  plot(myine)
+  myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
+  suppressMessages(plot(myine))
+}
+
+```
+
+#### Summary
+
+```{r, early plots summary}
+
+min_gen=100
+max_gen=5000
+
+# summary
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+#### Heatmap
+
+```{r, early plots Heatmap}
+
+min_gen=100
+max_gen=5000
+#heatmap
+build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+```
+
+### Mid-simulation
+
+```{r, mis plots}
+
+min_gen=10000
+max_gen=15000
+rep=0
+
+for(i in 1:length(unique(GA3_tall_tall_file$rep))){
+  myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
+  plot(myine)
+  myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
+suppressMessages(plot(myine))
+}
+
+```
+
+#### Summary
+
+```{r, mid plots summary}
+
+min_gen=10000
+max_gen=15000
+
+# summary
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+#### Heatmap
+
+```{r, mid plots Heatmap}
+
+min_gen=10000
+max_gen=15000
+#heatmap
+build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+```
+
+### Late simulation
+
+```{r, late plots}
+
+min_gen=45000
+max_gen=50000
+
+for(i in 1:length(unique(GA3_tall_tall_file$rep))){
+  myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
+  plot(myine)
+  myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
+  suppressMessages(plot(myine))
+}
+
+```
+
+#### Summary
+
+```{r, late plots summary}
+
+min_gen=45000
+max_gen=50000
+
+# summary
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+#### Heatmap
+
+```{r, late plots Heatmap}
+
+min_gen=45000
+max_gen=50000
+#heatmap
+build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+```
+
+## What is up with the correlations
+
+### file
+
+```{r, cor grid by location}
+
+#GA3_grid_tall_file
+
+file_name= "Snake_1.0e-11_0.158_Newt_1.0e-10_0.05_0"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+spegen=20001
+#unique(GA3_grid_tall_file$snake_newt_rep)
+GA3<-GA3_grid_tall_file[which(GA3_grid_tall_file$snake_newt_rep==file_name & GA3_grid_tall_file$generation==spegen),]
+
+GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
+
+GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
+
+GA3_data_long_mean_short<-GA3_data_long_mean
+
+GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(GA3_data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
+newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
+newt_GA3$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
+
+newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA3)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### file
+
+```{r, cor grid by location}
+
+#GA3_grid_tall_file
+
+file_name= "Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+spegen=30001
+#unique(GA3_grid_tall_file$snake_newt_rep)
+GA3<-GA3_grid_tall_file[which(GA3_grid_tall_file$snake_newt_rep==file_name & GA3_grid_tall_file$generation==spegen),]
+
+GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
+
+GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
+
+GA3_data_long_mean_short<-GA3_data_long_mean
+
+GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(GA3_data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
+newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
+newt_GA3$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
+
+newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA3)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```

### 2022-07-29 graphs_newt_snakes/GA3.Rmd
working on a way to track influential alleles. writing about GA3

@@
 GA3_GA3_grid_tall_file<-data.frame()
-
-#oldstand=0
-letter=0
-#newt_unique=0
-#newt_numb = 0
+name_list<-c()
+cor_name_list<-c()
+grid_name_list<-c()
 for(i in seq(1, length(GA3_tall), 1)){
-  stand <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  up <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  phrase = paste0(stand, "_", up)
-  letter = letter +1
-  # if (stand!=oldstand){
-  #   oldstand=stand
-  #   letter = letter + 1
-  # }
-  # 
-  #   if (phrase=="1.0e-08_0.05" ){
-  #   newt_numb =  1
-  #  }
-  #   if (phrase=="1.0e-09_0.158114"){
-  #   newt_numb =  2
-  #  }
-  #     if (phrase=="1.0e-10_0.5"){
-  #   newt_numb =  3
-  #  }
-  #   if (phrase=="1.0e-11_1.58114"){
-  #   newt_numb =  4
-  #  }
-  # 
-  #     if (phrase=="1.0e-12_5.0"){
-  #   newt_numb =  5
-  #  }
-  # print(newt_numb)
-  # 
-  # if (i<=length(GA3_tall)){
-
-  # stand <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  # up <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  # phrase = paste0(stand, "_", up)
-  # 
-  #  if (phrase=="1.0e-08_0.005"){
-  #   newt_numb =  1
-  #  }
-  #   if (phrase=="1.0e-09_0.05"){
-  #   newt_numb =  2
-  #  }
-  #     if (phrase=="1.0e-10_0.5"){
-  #   newt_numb =  3
-  #  }
-  #   if (phrase=="1.0e-11_5.0"){
-  #   newt_numb =  4
-  #  }
+  print(i)
+  #sim
 
   GA3_temp_file <- read.csv(GA3_tall[i], header = TRUE)
-  GA3_temp_file$sim <-LETTERS[letter]
-  #GA3_temp_file$size <-newt_numb
-  GA3_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall[i],"rep_"))[3], "_"))[1]
+  GA3_temp_file$rep <- unlist(str_split(unlist(str_split(GA3_tall[i],"rep_"))[3], "_"))[1]
   GA3_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_rate_"))[2], "_"))[1]
@@
   GA3_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  name_list<-c(paste0(GA3_temp_file$snake_mu_rate[1], GA3_temp_file$newt_mu_rate[1], GA3_temp_file$snake_mu_effect_sd[1], GA3_temp_file$newt_mu_effect_sd[1]),name_list)
+  GA3_temp_file$sim <- LETTERS[length(unique(name_list))]
   GA3_tall_tall_file <- rbind(GA3_tall_tall_file, GA3_temp_file)
+  print(GA3_temp_file$sim[1])
 
   cor_temp_file <- read.csv(GA3_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-LETTERS[letter]
-  #cor_temp_file$size <-newt_numb
+  cor_temp_file$sim <-
   cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"rep_"))[3], "_"))[1]
@@
   cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
+  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
   GA3_cor_tall_file <- rbind(GA3_cor_tall_file, cor_temp_file)
+  print(cor_temp_file$sim[1])
 
   GA3_grid_temp_file <- read.csv(GA3_GA3_grid_tall_files[i], header = TRUE)
-  GA3_grid_temp_file$sim <-LETTERS[letter]
-  #GA3_grid_temp_file$size <-newt_numb
+  GA3_grid_temp_file$sim <-
   GA3_grid_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"rep_"))[3], "_"))[1]
@@
   GA3_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  grid_name_list<-c(paste0(GA3_grid_temp_file$snake_mu_rate[1], GA3_grid_temp_file$newt_mu_rate[1], GA3_grid_temp_file$snake_mu_effect_sd[1], GA3_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
+  GA3_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
   GA3_GA3_grid_tall_file <- rbind(GA3_GA3_grid_tall_file, GA3_grid_temp_file)
+   print(GA3_grid_temp_file$sim[1])
 
@@
 #unique(GA3_grid_tall_file$snake_newt_rep)
-GA3<-GA3_grid_tall_file[which(GA3_grid_tall_file$snake_newt_rep==file_name & GA3_grid_tall_file$generation==spegen),]
+GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
 
@@
 ```
+
+```{r, cor grid by location}
+
+#GA3_grid_tall_file
+
+file_name= "Snake_1.0e-10_0.05_Newt_1.0e-11_0.158_3"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+spegen=14001
+#unique(GA3_grid_tall_file$snake_newt_rep)
+GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
+
+GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
+
+GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
+
+GA3_data_long_mean_short<-GA3_data_long_mean
+
+GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(GA3_data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
+newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
+newt_GA3$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
+
+newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA3)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+```{r, cor grid by location}
+
+#GA3_grid_tall_file
+
+file_name= "Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+spegen=1001
+#spegen=30001
+#unique(GA3_grid_tall_file$snake_newt_rep)
+GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
+
+GA3_ind = GA3[,grepl("generation|num_ind", names(GA3)) ]
+
+GA3_data_long_ind <- gather(GA3_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA3_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_ind$condition, "_", 4)
+
+GA3_data_long_ind_short<-GA3_data_long_ind
+
+GA3_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA3_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA3_data_long_ind_short$measurement[GA3_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA3_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="snake"),]
+newt_GA3<-GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="newt"),]
+newt_GA3$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
+
+newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA3)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+```{r, cor grid by location}
+
+#GA3_grid_tall_file
+
+file_name= "Snake_1.0e-10_0.05_Newt_1.0e-09_0.0158_1"
+
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+spegen=49991
+#spegen=30001
+#unique(GA3_grid_tall_file$snake_newt_rep)
+GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
+
+GA3_ind = GA3[,grepl("generation|num_ind", names(GA3)) ]
+
+GA3_data_long_ind <- gather(GA3_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA3_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_ind$condition, "_", 4)
+
+GA3_data_long_ind_short<-GA3_data_long_ind
+
+GA3_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA3_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA3_data_long_ind_short$measurement[GA3_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA3_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="snake"),]
+newt_GA3<-GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="newt"),]
+newt_GA3$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
+
+newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA3)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```

### 2022-08-09 graphs_newt_snakes/Heritability.Rmd
I am looking at data from the random phenotype draw.

--- 2022-07-27 graphs_newt_snakes/GA3.Rmd
@@
 ---
-title: "GA3"
+title: "Heritability"
 output: html_document
-date: '2022-07-21'
+date: '2022-08-05'
 ---
@@
 library(knitr)
-library(kableExtra)
 library("reshape")
-library(ggplot2)
-library(ggpubr)
-theme_set(theme_pubr())
-library(stringr)
-library(patchwork)
+
 ```
 
-GA3 file will be the slow evolution file.
-The main goal will be testing to see if there is an effect caused by mutation rate or effect size when the mutational variance between two species is the same.
+## Goal:
 
-Prediction: Higher mutation rate will be advantages in the beginning of a simulation. A higher effect size might lead to more spatial co-evolution. Space might separate the effects.
+In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-heritable trait. I expect to see no spatial phenotype correlation
 
-For the initial part of this experiment I will only be running one trial per GA combination
+### Questions:
 
-GA combinations:
+What happens when a co-evolving trait is not heritable?
 
-- 1e-8*(0.005)^2 = 2.5e-13
-- 1e-9*(0.0158)^2 = 2.5e-13
-- 1e-10*(0.05)^2 = 2.5e-13
-- 1e-11*(0.158)^2 = 2.5e-13
+## Background
 
@@
 
-GA3_tall <- list.files(path="~/Desktop/GA3", pattern="_lit_", full.names=TRUE, recursive=FALSE)
-GA3_tall_cor_files <- list.files(path="~/Desktop/GA3", pattern="_cor_", full.names=TRUE, recursive=FALSE)
-GA3_GA3_grid_tall_files <- list.files(path="~/Desktop/GA3", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+her_tall <- list.files(path="~/Desktop/no_hair", pattern="_lit_", full.names=TRUE, recursive=FALSE)
+her_tall_cor_files <- list.files(path="~/Desktop/no_hair", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+her_her_grid_tall_files <- list.files(path="~/Desktop/no_hair", pattern="_grid_", full.names=TRUE, recursive=FALSE)
 
-GA3_tall_tall_file<- data.frame()
-GA3_cor_tall_file<- data.frame()
-GA3_GA3_grid_tall_file<-data.frame()
+her_tall_tall_file<- data.frame()
+her_cor_tall_file<- data.frame()
+her_her_grid_tall_file<-data.frame()
+name_list<-c()
+cor_name_list<-c()
+grid_name_list<-c()
+for(i in seq(1, length(her_tall), 1)){
+  print(i)
+  #sim
 
-#oldstand=0
-letter=0
-#newt_unique=0
-#newt_numb = 0
-for(i in seq(1, length(GA3_tall), 1)){
-  stand <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  up <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  phrase = paste0(stand, "_", up)
-  letter = letter +1
-  # if (stand!=oldstand){
-  #   oldstand=stand
-  #   letter = letter + 1
-  # }
-  # 
-  #   if (phrase=="1.0e-08_0.05" ){
-  #   newt_numb =  1
-  #  }
-  #   if (phrase=="1.0e-09_0.158114"){
-  #   newt_numb =  2
-  #  }
-  #     if (phrase=="1.0e-10_0.5"){
-  #   newt_numb =  3
-  #  }
-  #   if (phrase=="1.0e-11_1.58114"){
-  #   newt_numb =  4
-  #  }
-  # 
-  #     if (phrase=="1.0e-12_5.0"){
-  #   newt_numb =  5
-  #  }
-  # print(newt_numb)
-  # 
-  # if (i<=length(GA3_tall)){
+  her_temp_file <- read.csv(her_tall[i], header = TRUE)
+  her_temp_file$rep <- unlist(str_split(unlist(str_split(her_tall[i],"rep_"))[3], "_"))[1]
+  her_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_tall[i],"snake_mu_rate_"))[2], "_"))[1]
+  her_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  her_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  her_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  name_list<-c(paste0(her_temp_file$snake_mu_rate[1], her_temp_file$newt_mu_rate[1], her_temp_file$snake_mu_effect_sd[1], her_temp_file$newt_mu_effect_sd[1]),name_list)
+  her_temp_file$sim <- LETTERS[length(unique(name_list))]
+  her_tall_tall_file <- rbind(her_tall_tall_file, her_temp_file)
+  print(her_temp_file$sim[1])
 
-  # stand <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  # up <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  # phrase = paste0(stand, "_", up)
-  # 
-  #  if (phrase=="1.0e-08_0.005"){
-  #   newt_numb =  1
-  #  }
-  #   if (phrase=="1.0e-09_0.05"){
-  #   newt_numb =  2
-  #  }
-  #     if (phrase=="1.0e-10_0.5"){
-  #   newt_numb =  3
-  #  }
-  #   if (phrase=="1.0e-11_5.0"){
-  #   newt_numb =  4
-  #  }
+  cor_temp_file <- read.csv(her_tall_cor_files[i], header = TRUE)
+  cor_temp_file$sim <-
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(her_tall_cor_files[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
+  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
+  her_cor_tall_file <- rbind(her_cor_tall_file, cor_temp_file)
+  print(cor_temp_file$sim[1])
 
-  GA3_temp_file <- read.csv(GA3_tall[i], header = TRUE)
-  GA3_temp_file$sim <-LETTERS[letter]
-  #GA3_temp_file$size <-newt_numb
-  GA3_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall[i],"rep_"))[3], "_"))[1]
-  GA3_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  GA3_tall_tall_file <- rbind(GA3_tall_tall_file, GA3_temp_file)
-
-  cor_temp_file <- read.csv(GA3_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-LETTERS[letter]
-  #cor_temp_file$size <-newt_numb
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  GA3_cor_tall_file <- rbind(GA3_cor_tall_file, cor_temp_file)
-
-  GA3_grid_temp_file <- read.csv(GA3_GA3_grid_tall_files[i], header = TRUE)
-  GA3_grid_temp_file$sim <-LETTERS[letter]
-  #GA3_grid_temp_file$size <-newt_numb
-  GA3_grid_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"rep_"))[3], "_"))[1]
-  GA3_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  GA3_GA3_grid_tall_file <- rbind(GA3_GA3_grid_tall_file, GA3_grid_temp_file)
+  her_grid_temp_file <- read.csv(her_her_grid_tall_files[i], header = TRUE)
+  her_grid_temp_file$sim <-
+  her_grid_temp_file$rep <-unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"rep_"))[3], "_"))[1]
+  her_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  her_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  her_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  her_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  grid_name_list<-c(paste0(her_grid_temp_file$snake_mu_rate[1], her_grid_temp_file$newt_mu_rate[1], her_grid_temp_file$snake_mu_effect_sd[1], her_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
+  her_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
+  her_her_grid_tall_file <- rbind(her_her_grid_tall_file, her_grid_temp_file)
+   print(her_grid_temp_file$sim[1])
 
@@
 
-GA3_tall_tall_file$dif <- GA3_tall_tall_file$Snake_mean_Pheno-GA3_tall_tall_file$Newt_mean_Pheno
+her_tall_tall_file$dif <- her_tall_tall_file$Snake_mean_Pheno-her_tall_tall_file$Newt_mean_Pheno
 
-GA3_tall_tall_file$group_rep <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep)
+her_tall_tall_file$group_rep <- paste0(her_tall_tall_file$snake_mu_rate, "_", her_tall_tall_file$snake_mu_effect_sd,"_",her_tall_tall_file$newt_mu_rate, "_", her_tall_tall_file$newt_mu_effect_sd, "_", her_tall_tall_file$rep)
 
-GA3_tall_tall_file$group <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd)
+her_tall_tall_file$group <- paste0(her_tall_tall_file$snake_mu_rate, "_", her_tall_tall_file$snake_mu_effect_sd,"_",her_tall_tall_file$newt_mu_rate, "_", her_tall_tall_file$newt_mu_effect_sd)
 
-GA3_GA3_grid_tall_file$snake_newt_rep <- paste0("Snake_",GA3_GA3_grid_tall_file$snake_mu_rate, "_", GA3_GA3_grid_tall_file$snake_mu_effect_sd, "_Newt_",GA3_GA3_grid_tall_file$newt_mu_rate, "_", GA3_GA3_grid_tall_file$newt_mu_effect_sd, "_", GA3_GA3_grid_tall_file$rep)
+her_her_grid_tall_file$snake_newt_rep <- paste0("Snake_",her_her_grid_tall_file$snake_mu_rate, "_", her_her_grid_tall_file$snake_mu_effect_sd, "_Newt_",her_her_grid_tall_file$newt_mu_rate, "_", her_her_grid_tall_file$newt_mu_effect_sd, "_", her_her_grid_tall_file$rep)
 
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=GA3_tall_tall_file
+  #file=her_tall_tall_file
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 
@@
 ```{r, graphing by gen}
-trends_by_gen(GA3_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA3", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
+trends_by_gen(her_tall_tall_file, title="Space Tall: Newt VS Snake Population Size her", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
 
-aggregate(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$dif, list(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$group), FUN=mean)
+aggregate(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$dif, list(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$group), FUN=mean)
 
-#aggregate(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$dif, list(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
+#aggregate(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$dif, list(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
 
@@
 
-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 
-suppressMessages(print(two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+suppressMessages(print(two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
 
-suppressMessages(print(two_hist_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+suppressMessages(print(two_hist_all_rep(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
 
@@
 #files
-#GA3_tall_tall_file
+#her_tall_tall_file
 #GA2_long_file 
-#GA3_cor_tall_file
+#her_cor_tall_file
 #GA2_cor_file
@@
 
-boxplot_cors_by_gen(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
-four_types_boxplot_cors_by_gen(GA3_cor_tall_file, "Simulation four Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+four_types_boxplot_cors_by_gen(her_cor_tall_file, "Simulation four Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 
-```{r, GA3 cor by dif windows}
+```{r, her cor by dif windows}
 
@@
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 
-```{r, GA3 cor and pheno}
-GA3_pattern <- unique(paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep))
-for(i in 1:length(GA3_pattern)){
-  myine<-cor_trends_by_gen(GA3_tall_tall_file, GA3_cor_tall_file, "test", "GA3", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA3_pattern[i])
+```{r, her cor and pheno}
+her_pattern <- unique(paste0(her_tall_tall_file$snake_mu_rate, "_", her_tall_tall_file$snake_mu_effect_sd,"_",her_tall_tall_file$newt_mu_rate, "_", her_tall_tall_file$newt_mu_effect_sd, "_", her_tall_tall_file$rep))
+for(i in 1:length(her_pattern)){
+  myine<-cor_trends_by_gen(her_tall_tall_file, her_cor_tall_file, "test", "her", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=her_pattern[i])
   plot(myine)
@@
 
-for(i in 1:length(unique(GA3_tall_tall_file$rep))){
-  myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
+for(i in 1:length(unique(her_tall_tall_file$rep))){
+  myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
+  myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
   suppressMessages(plot(myine))
@@
 # summary
-GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
-GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 ```
@@
 #heatmap
-build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
-build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 
-for(i in 1:length(unique(GA3_tall_tall_file$rep))){
-  myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
+for(i in 1:length(unique(her_tall_tall_file$rep))){
+  myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
+  myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
 suppressMessages(plot(myine))
@@
 
-#GA3_grid_tall_file
+#her_grid_tall_file
 
-file_name= "Snake_1.0e-11_0.158_Newt_1.0e-10_0.05_0"
+file_name= "Snake_1.0e-11_5.0_Newt_1.0e-11_5.0_0"
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
@@
 spegen=20001
-#unique(GA3_grid_tall_file$snake_newt_rep)
-GA3<-GA3_grid_tall_file[which(GA3_grid_tall_file$snake_newt_rep==file_name & GA3_grid_tall_file$generation==spegen),]
+#unique(her_grid_tall_file$snake_newt_rep)
+her<-her_her_grid_tall_file[which(her_her_grid_tall_file$snake_newt_rep==file_name & her_her_grid_tall_file$generation==spegen),]
 
-GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
+her_mean = her[,grepl("generation|mean", names(her)) ]
 
-GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+her_data_long_mean <- gather(her_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
 
-GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
+her_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(her_data_long_mean$condition, "_", 4)
 
-GA3_data_long_mean_short<-GA3_data_long_mean
+her_data_long_mean_short<-her_data_long_mean
 
-GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+her_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+her_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
 
-main_plot<-ggplot(GA3_data_long_mean_short)+
+main_plot<-ggplot(her_data_long_mean_short)+
   labs(title = "Mean Phenotype of Locations",
@@
               fill = "Toxicity/Resistance")+
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  geom_point(data = her_data_long_mean_short[which(her_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = her_data_long_mean_short[which(her_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
   scale_fill_viridis_c()+
@@
 
-snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
-newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
-newt_GA3$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
+snake<-her_data_long_mean_short[which(her_data_long_mean_short$species=="snake"),]
+newt_her<-her_data_long_mean_short[which(her_data_long_mean_short$species=="newt"),]
+newt_her$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_her$measurement), use="complete.obs")
 
-newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
+newt_her$info[newt_her$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_her$info[newt_her$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_her$info[is.na(newt_her$info)]<- "middle"
 
-extra_plot <- ggplot(newt_GA3)+
+extra_plot <- ggplot(newt_her)+
   ggtitle("Mean Phenotype") +
@@
 ```
-
-### file
-
-```{r, cor grid by location}
-
-#GA3_grid_tall_file
-
-file_name= "Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0"
-#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
-
-spegen=30001
-#unique(GA3_grid_tall_file$snake_newt_rep)
-GA3<-GA3_grid_tall_file[which(GA3_grid_tall_file$snake_newt_rep==file_name & GA3_grid_tall_file$generation==spegen),]
-
-GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
-
-GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
-
-GA3_data_long_mean_short<-GA3_data_long_mean
-
-GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(GA3_data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
-newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
-newt_GA3$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
-
-newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
-
-extra_plot <- ggplot(newt_GA3)+
-  ggtitle("Mean Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```

### 2022-08-19 graphs_newt_snakes/GA3.Rmd
working on writing more about GA3. Starting to figure out how to run slim on the large map. And messing around in slim to see where most of the time is sticking.

@@
 grid_name_list<-c()
-for(i in seq(1, length(GA3_tall), 1)){
+for(i in seq(1, length(GA3_tall)/2, 1)){
   print(i)
@@
   }
-
+ ###to set first half 
+GA3_tall_tall_file_p1<- GA3_tall_tall_file
+GA3_cor_tall_file_p1<- GA3_cor_tall_file
+GA3_GA3_grid_tall_file_p1<-GA3_GA3_grid_tall_file
+
+for(i in seq((length(GA3_tall)/2+1), length(GA3_tall), 1)){
+  print(i)
+  #sim
+
+  GA3_temp_file <- read.csv(GA3_tall[i], header = TRUE)
+  GA3_temp_file$rep <- unlist(str_split(unlist(str_split(GA3_tall[i],"rep_"))[3], "_"))[1]
+  GA3_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_rate_"))[2], "_"))[1]
+  GA3_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  GA3_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  GA3_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  name_list<-c(paste0(GA3_temp_file$snake_mu_rate[1], GA3_temp_file$newt_mu_rate[1], GA3_temp_file$snake_mu_effect_sd[1], GA3_temp_file$newt_mu_effect_sd[1]),name_list)
+  GA3_temp_file$sim <- LETTERS[length(unique(name_list))]
+  GA3_tall_tall_file <- rbind(GA3_tall_tall_file, GA3_temp_file)
+  print(GA3_temp_file$sim[1])
+
+  cor_temp_file <- read.csv(GA3_tall_cor_files[i], header = TRUE)
+  cor_temp_file$sim <-
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
+  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
+  GA3_cor_tall_file <- rbind(GA3_cor_tall_file, cor_temp_file)
+  print(cor_temp_file$sim[1])
+
+  GA3_grid_temp_file <- read.csv(GA3_GA3_grid_tall_files[i], header = TRUE)
+  GA3_grid_temp_file$sim <-
+  GA3_grid_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"rep_"))[3], "_"))[1]
+  GA3_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  GA3_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  GA3_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  GA3_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  grid_name_list<-c(paste0(GA3_grid_temp_file$snake_mu_rate[1], GA3_grid_temp_file$newt_mu_rate[1], GA3_grid_temp_file$snake_mu_effect_sd[1], GA3_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
+  GA3_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
+  GA3_GA3_grid_tall_file <- rbind(GA3_GA3_grid_tall_file, GA3_grid_temp_file)
+   print(GA3_grid_temp_file$sim[1])
+
+  }
+
+ ###to combine second half with first
+GA3_tall_tall_file<- rbind(GA3_tall_tall_file_p1, GA3_tall_tall_file)
+GA3_cor_tall_file<- rbind(GA3_cor_tall_file_p1, GA3_cor_tall_file)
+GA3_GA3_grid_tall_file<-rbind(GA3_GA3_grid_tall_file_p1, GA3_GA3_grid_tall_file)
+
+# making row edits to the dataframe for graphing
 GA3_tall_tall_file$dif <- GA3_tall_tall_file$Snake_mean_Pheno-GA3_tall_tall_file$Newt_mean_Pheno
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+
+  pattern="1.0e-08_0.005_1.0e-10_0.05_2"
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
@@
   cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
+
+  if(nrow(cfile)>nrow(file)){
     toDelete <- seq(0, nrow(cfile), 2)
     cfile_short <-  cfile[-toDelete, ]
+  }else{
+    cfile_short <-  cfile
+  }
   figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
@@
 GA3_pattern <- unique(paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep))
+
 for(i in 1:length(GA3_pattern)){
@@
 
+min_gen=10000
+max_gen=15000
+
+# summary
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+min_gen=45000
+max_gen=50000
+
+# summary
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+min_gen=100
+max_gen=5000
+
 GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-```
-
-#### Heatmap
+
+min_gen=10000
+max_gen=15000
+
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+min_gen=45000
+max_gen=50000
+
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
 
@@
 
-build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
-
-### Mid-simulation
-
-```{r, mis plots}
-
-min_gen=10000
-max_gen=15000
-rep=0
-
-for(i in 1:length(unique(GA3_tall_tall_file$rep))){
-  myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
-  plot(myine)
-  myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
-suppressMessages(plot(myine))
-}
-
-```
-
-#### Summary
-
-```{r, mid plots summary}
-
-min_gen=10000
-max_gen=15000
-
-# summary
-GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-```
-
-#### Heatmap
-
-```{r, mid plots Heatmap}
-
 min_gen=10000
@@
 
-build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
-
-### Late simulation
-
-```{r, late plots}
-
-min_gen=45000
-max_gen=50000
-
-for(i in 1:length(unique(GA3_tall_tall_file$rep))){
-  myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
-  plot(myine)
-  myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
-  suppressMessages(plot(myine))
-}
-
-```
-
-#### Summary
-
-```{r, late plots summary}
-
-min_gen=45000
-max_gen=50000
-
-# summary
-GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-```
-
-#### Heatmap
-
-```{r, late plots Heatmap}
-
 min_gen=45000
@@
 build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+min_gen=100
+max_gen=5000
+build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+min_gen=10000
+max_gen=15000
+#heatmap
+
+build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+min_gen=45000
+max_gen=50000
+#heatmap
 
@@
 GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
-
+GA3<-GA3[1,]
 GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
@@
 GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
-
+GA3<-GA3[1,]
 GA3_ind = GA3[,grepl("generation|num_ind", names(GA3)) ]

### 2022-08-19 graphs_newt_snakes/big_map.Rmd
working on writing more about GA3. Starting to figure out how to run slim on the large map. And messing around in slim to see where most of the time is sticking.

---
title: "Big_map"
output: html_document
date: '2022-08-18'
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
library(stringr)
library(patchwork)
```

In this markdown I would like to run my newts and snake simulation on a larger map. The prediction that is when I create a larger map there will be more opportunities for different areas to co-evolve, creating a mosaic pattern. The BIG map to be 100 times larger than the long map. The demotions would be; length=1,400 width=350. This would increase the amount of individuals and grid data-points in my simulations.

In my current simulations, there are about 6,000 individuals (combination of newts and snakes). If I increase the map's area by 100 I expect that the number of individuals would also increase by 100 (~600,000). To make these simulations work/run faster I will increase the starting population size to 2,500 per each species. I also plan on taking information from the simulations less often (e.g. taking information every 50 generations instead of 20) and for a shorter amount of time (e.g. from 50,000 generation to only 10,000 generations).

My previous simulations ran for 50,000 generations and took a day or less to run (msprime+slim). I will make some plots to see how long these larger simulations will take to run

```{r, data gathering}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

big_map_tall <- list.files(path="~/Desktop/big_map", pattern="_lit_", full.names=TRUE, recursive=FALSE)
big_map_tall_cor_files <- list.files(path="~/Desktop/big_map", pattern="_cor_", full.names=TRUE, recursive=FALSE)
big_map_grid_tall_files <- list.files(path="~/Desktop/big_map", pattern="_grid_", full.names=TRUE, recursive=FALSE)

big_map_tall_tall_file<- data.frame()
big_map_cor_tall_file<- data.frame()
big_map_grid_tall_file<-data.frame()
name_list<-c()
cor_name_list<-c()
grid_name_list<-c()
for(i in seq(1, length(big_map_tall)/2, 1)){
  print(i)
  #sim

  big_map_temp_file <- read.csv(big_map_tall[i], header = TRUE)
  big_map_temp_file$rep <- unlist(str_split(unlist(str_split(big_map_tall[i],"rep_"))[3], "_"))[1]
  big_map_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall[i],"snake_mu_rate_"))[2], "_"))[1]
  big_map_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall[i],"newt_mu_rate_"))[2], "_"))[1]
  big_map_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  big_map_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  name_list<-c(paste0(big_map_temp_file$snake_mu_rate[1], big_map_temp_file$newt_mu_rate[1], big_map_temp_file$snake_mu_effect_sd[1], big_map_temp_file$newt_mu_effect_sd[1]),name_list)
  big_map_temp_file$sim <- LETTERS[length(unique(name_list))]
  big_map_tall_tall_file <- rbind(big_map_tall_tall_file, big_map_temp_file)
  print(big_map_temp_file$sim[1])

  cor_temp_file <- read.csv(big_map_tall_cor_files[i], header = TRUE)
  cor_temp_file$sim <-
  cor_temp_file$rep <-unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"rep_"))[3], "_"))[1]
  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
  big_map_cor_tall_file <- rbind(big_map_cor_tall_file, cor_temp_file)
  print(cor_temp_file$sim[1])

  big_map_grid_temp_file <- read.csv(big_map_grid_tall_files[i], header = TRUE)
  big_map_grid_temp_file$sim <-
  big_map_grid_temp_file$rep <-unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"rep_"))[3], "_"))[1]
  big_map_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
  big_map_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
  big_map_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  big_map_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  grid_name_list<-c(paste0(big_map_grid_temp_file$snake_mu_rate[1], big_map_grid_temp_file$newt_mu_rate[1], big_map_grid_temp_file$snake_mu_effect_sd[1], big_map_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
  big_map_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
  big_map_grid_tall_file <- rbind(big_map_grid_tall_file, big_map_grid_temp_file)
   print(big_map_grid_temp_file$sim[1])

  }
 ###to set first half 
big_map_tall_tall_file_p1<- big_map_tall_tall_file
big_map_cor_tall_file_p1<- big_map_cor_tall_file
big_map_grid_tall_file_p1<-big_map_grid_tall_file

for(i in seq((length(big_map_tall)/2+1), length(big_map_tall), 1)){
  print(i)
  #sim

  big_map_temp_file <- read.csv(big_map_tall[i], header = TRUE)
  big_map_temp_file$rep <- unlist(str_split(unlist(str_split(big_map_tall[i],"rep_"))[3], "_"))[1]
  big_map_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall[i],"snake_mu_rate_"))[2], "_"))[1]
  big_map_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall[i],"newt_mu_rate_"))[2], "_"))[1]
  big_map_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  big_map_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  name_list<-c(paste0(big_map_temp_file$snake_mu_rate[1], big_map_temp_file$newt_mu_rate[1], big_map_temp_file$snake_mu_effect_sd[1], big_map_temp_file$newt_mu_effect_sd[1]),name_list)
  big_map_temp_file$sim <- LETTERS[length(unique(name_list))]
  big_map_tall_tall_file <- rbind(big_map_tall_tall_file, big_map_temp_file)
  print(big_map_temp_file$sim[1])

  cor_temp_file <- read.csv(big_map_tall_cor_files[i], header = TRUE)
  cor_temp_file$sim <-
  cor_temp_file$rep <-unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"rep_"))[3], "_"))[1]
  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
  big_map_cor_tall_file <- rbind(big_map_cor_tall_file, cor_temp_file)
  print(cor_temp_file$sim[1])

  big_map_grid_temp_file <- read.csv(big_map_grid_tall_files[i], header = TRUE)
  big_map_grid_temp_file$sim <-
  big_map_grid_temp_file$rep <-unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"rep_"))[3], "_"))[1]
  big_map_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
  big_map_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
  big_map_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  big_map_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  grid_name_list<-c(paste0(big_map_grid_temp_file$snake_mu_rate[1], big_map_grid_temp_file$newt_mu_rate[1], big_map_grid_temp_file$snake_mu_effect_sd[1], big_map_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
  big_map_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
  big_map_grid_tall_file <- rbind(big_map_grid_tall_file, big_map_grid_temp_file)
   print(big_map_grid_temp_file$sim[1])

  }

big_map_tall_tall_file$dif <- big_map_tall_tall_file$Snake_mean_Pheno-big_map_tall_tall_file$Newt_mean_Pheno

big_map_tall_tall_file$group_rep <- paste0(big_map_tall_tall_file$snake_mu_rate, "_", big_map_tall_tall_file$snake_mu_effect_sd,"_",big_map_tall_tall_file$newt_mu_rate, "_", big_map_tall_tall_file$newt_mu_effect_sd, "_", big_map_tall_tall_file$rep)

big_map_tall_tall_file$group <- paste0(big_map_tall_tall_file$snake_mu_rate, "_", big_map_tall_tall_file$snake_mu_effect_sd,"_",big_map_tall_tall_file$newt_mu_rate, "_", big_map_tall_tall_file$newt_mu_effect_sd)

big_map_grid_tall_file$snake_newt_rep <- paste0("Snake_",big_map_grid_tall_file$snake_mu_rate, "_", big_map_grid_tall_file$snake_mu_effect_sd, "_Newt_",big_map_grid_tall_file$newt_mu_rate, "_", big_map_grid_tall_file$newt_mu_effect_sd, "_", big_map_grid_tall_file$rep)

```

### 2022-08-19 graphs_newt_snakes/GA3.Rmd
working on writing about the file results. Finding problems with some of them

@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-
-  pattern="1.0e-08_0.005_1.0e-10_0.05_2"
+#file=GA3_tall_tall_file
+#cfile=GA3_cor_tall_file 
+ # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
@@
     cfile_short <-  cfile
+  }
+
+  if(nrow(cfile_short)>nrow(file)){
+      toDelete <- seq(0, nrow(cfile_short), 2)
+      cfile_short <-  cfile_short[-toDelete, ]
     }
@@
 
-```{r, GA3 cor and pheno}
+```{r, GA3 cor and pheno, results="hide"}
 GA3_pattern <- unique(paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep))
@@
 
-```{r, cor grid by location}
+```{r, cor grid by location 1}
 
@@
 
-```{r, cor grid by location}
+```{r, cor grid by location 2}
 
@@
 
-```{r, cor grid by location}
+```{r, cor grid by location 3}
 
@@
 
-```{r, cor grid by location}
+```{r, cor grid by location 4}
 
 #GA3_grid_tall_file
-
-file_name= "Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0"
+file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_0"
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
 
-spegen=1001
+spegen=15001
+#unique(GA3_grid_tall_file$snake_newt_rep)
+GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
+GA3<-GA3[1,]
+GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
+
+GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
+
+GA3_data_long_mean_short<-GA3_data_long_mean
+
+GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(GA3_data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
+newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
+newt_GA3$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
+
+newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA3)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
 #spegen=30001
@@
 
-```{r, cor grid by location}
+```{r, cor grid by location 5}
 

### 2022-08-19 graphs_newt_snakes/no_interact.Rmd
working on writing about the file results. Finding problems with some of them

--- 2022-08-09 graphs_newt_snakes/Heritability.Rmd
@@
 ---
-title: "Heritability"
+title: "no interaction"
 output: html_document
-date: '2022-08-05'
+date: '2022-08-19'
 ---
@@
 
-In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-heritable trait. I expect to see no spatial phenotype correlation
+In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-interitable trait. I expect to see no spatial phenotype correlation
 
@@
 
-What happens when a co-evolving trait is not heritable?
+What happens when a co-evolving trait is not interitable?
 
@@
 
-```{r, data gathering}
+```{r, data gatintering}
 
@@
 
-her_tall <- list.files(path="~/Desktop/no_hair", pattern="_lit_", full.names=TRUE, recursive=FALSE)
-her_tall_cor_files <- list.files(path="~/Desktop/no_hair", pattern="_cor_", full.names=TRUE, recursive=FALSE)
-her_her_grid_tall_files <- list.files(path="~/Desktop/no_hair", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+inter_tall <- list.files(path="~/Desktop/no_interaction", pattern="_lit_", full.names=TRUE, recursive=FALSE)
+inter_tall_cor_files <- list.files(path="~/Desktop/no_interaction", pattern="_cor_", full.names=TRUE, recursive=FALSE)
+inter_inter_grid_tall_files <- list.files(path="~/Desktop/no_interaction", pattern="_grid_", full.names=TRUE, recursive=FALSE)
 
-her_tall_tall_file<- data.frame()
-her_cor_tall_file<- data.frame()
-her_her_grid_tall_file<-data.frame()
+inter_tall_tall_file<- data.frame()
+inter_cor_tall_file<- data.frame()
+inter_inter_grid_tall_file<-data.frame()
 name_list<-c()
@@
 grid_name_list<-c()
-for(i in seq(1, length(her_tall), 1)){
+for(i in seq(1, length(inter_tall), 1)){
   print(i)
@@
 
-  her_temp_file <- read.csv(her_tall[i], header = TRUE)
-  her_temp_file$rep <- unlist(str_split(unlist(str_split(her_tall[i],"rep_"))[3], "_"))[1]
-  her_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  her_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  her_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  her_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  name_list<-c(paste0(her_temp_file$snake_mu_rate[1], her_temp_file$newt_mu_rate[1], her_temp_file$snake_mu_effect_sd[1], her_temp_file$newt_mu_effect_sd[1]),name_list)
-  her_temp_file$sim <- LETTERS[length(unique(name_list))]
-  her_tall_tall_file <- rbind(her_tall_tall_file, her_temp_file)
-  print(her_temp_file$sim[1])
+  inter_temp_file <- read.csv(inter_tall[i], header = TRUE)
+  inter_temp_file$rep <- unlist(str_split(unlist(str_split(inter_tall[i],"rep_"))[2], "_"))[1]
+  inter_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_tall[i],"snake_mu_rate_"))[2], "_"))[1]
+  inter_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(inter_tall[i],"newt_mu_rate_"))[2], "_"))[1]
+  inter_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  inter_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  name_list<-c(paste0(inter_temp_file$snake_mu_rate[1], inter_temp_file$newt_mu_rate[1], inter_temp_file$snake_mu_effect_sd[1], inter_temp_file$newt_mu_effect_sd[1]),name_list)
+  inter_temp_file$sim <- LETTERS[length(unique(name_list))]
+  inter_tall_tall_file <- rbind(inter_tall_tall_file, inter_temp_file)
+  print(inter_temp_file$sim[1])
 
-  cor_temp_file <- read.csv(her_tall_cor_files[i], header = TRUE)
+  cor_temp_file <- read.csv(inter_tall_cor_files[i], header = TRUE)
   cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(her_tall_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
   cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
   cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
-  her_cor_tall_file <- rbind(her_cor_tall_file, cor_temp_file)
+  inter_cor_tall_file <- rbind(inter_cor_tall_file, cor_temp_file)
   print(cor_temp_file$sim[1])
 
-  her_grid_temp_file <- read.csv(her_her_grid_tall_files[i], header = TRUE)
-  her_grid_temp_file$sim <-
-  her_grid_temp_file$rep <-unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"rep_"))[3], "_"))[1]
-  her_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  her_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  her_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  her_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  grid_name_list<-c(paste0(her_grid_temp_file$snake_mu_rate[1], her_grid_temp_file$newt_mu_rate[1], her_grid_temp_file$snake_mu_effect_sd[1], her_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
-  her_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
-  her_her_grid_tall_file <- rbind(her_her_grid_tall_file, her_grid_temp_file)
-   print(her_grid_temp_file$sim[1])
+  inter_grid_temp_file <- read.csv(inter_inter_grid_tall_files[i], header = TRUE)
+  inter_grid_temp_file$sim <-
+  inter_grid_temp_file$rep <-unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"rep_"))[3], "_"))[1]
+  inter_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
+  inter_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
+  inter_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
+  inter_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
+  grid_name_list<-c(paste0(inter_grid_temp_file$snake_mu_rate[1], inter_grid_temp_file$newt_mu_rate[1], inter_grid_temp_file$snake_mu_effect_sd[1], inter_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
+  inter_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
+  inter_inter_grid_tall_file <- rbind(inter_inter_grid_tall_file, inter_grid_temp_file)
+   print(inter_grid_temp_file$sim[1])
 
@@
 
-her_tall_tall_file$dif <- her_tall_tall_file$Snake_mean_Pheno-her_tall_tall_file$Newt_mean_Pheno
+inter_tall_tall_file$dif <- inter_tall_tall_file$Snake_mean_Pheno-inter_tall_tall_file$Newt_mean_Pheno
 
-her_tall_tall_file$group_rep <- paste0(her_tall_tall_file$snake_mu_rate, "_", her_tall_tall_file$snake_mu_effect_sd,"_",her_tall_tall_file$newt_mu_rate, "_", her_tall_tall_file$newt_mu_effect_sd, "_", her_tall_tall_file$rep)
+inter_tall_tall_file$group_rep <- paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd, "_", inter_tall_tall_file$rep)
 
-her_tall_tall_file$group <- paste0(her_tall_tall_file$snake_mu_rate, "_", her_tall_tall_file$snake_mu_effect_sd,"_",her_tall_tall_file$newt_mu_rate, "_", her_tall_tall_file$newt_mu_effect_sd)
+inter_tall_tall_file$group <- paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd)
 
-her_her_grid_tall_file$snake_newt_rep <- paste0("Snake_",her_her_grid_tall_file$snake_mu_rate, "_", her_her_grid_tall_file$snake_mu_effect_sd, "_Newt_",her_her_grid_tall_file$newt_mu_rate, "_", her_her_grid_tall_file$newt_mu_effect_sd, "_", her_her_grid_tall_file$rep)
+inter_inter_grid_tall_file$snake_newt_rep <- paste0("Snake_",inter_inter_grid_tall_file$snake_mu_rate, "_", inter_inter_grid_tall_file$snake_mu_effect_sd, "_Newt_",inter_inter_grid_tall_file$newt_mu_rate, "_", inter_inter_grid_tall_file$newt_mu_effect_sd, "_", inter_inter_grid_tall_file$rep)
 
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=her_tall_tall_file
+  #file=inter_tall_tall_file
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 
@@
 ```{r, graphing by gen}
-trends_by_gen(her_tall_tall_file, title="Space Tall: Newt VS Snake Population Size her", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
+trends_by_gen(inter_tall_tall_file, title="Space Tall: Newt VS Snake Population Size inter", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
 
-aggregate(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$dif, list(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$group), FUN=mean)
+aggregate(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$dif, list(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$group), FUN=mean)
 
-#aggregate(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$dif, list(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
+#aggregate(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$dif, list(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
 
@@
 
-#### Connection between higher phenotype and population
+#### Connection between higinter phenotype and population
 
@@
 max_gen=10000
-rep=0
+rep=3
 
-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 
-suppressMessages(print(two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+suppressMessages(print(two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
 
-suppressMessages(print(two_hist_all_rep(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+suppressMessages(print(two_hist_all_rep(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
 
@@
 #files
-#her_tall_tall_file
+#inter_tall_tall_file
 #GA2_long_file 
-#her_cor_tall_file
+#inter_cor_tall_file
 #GA2_cor_file
@@
 
-boxplot_cors_by_gen(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
-four_types_boxplot_cors_by_gen(her_cor_tall_file, "Simulation four Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+four_types_boxplot_cors_by_gen(inter_cor_tall_file, "Simulation four Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 
-```{r, her cor by dif windows}
+```{r, inter cor by dif windows}
 
@@
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 
@@
 
-```{r, her cor and pheno}
-her_pattern <- unique(paste0(her_tall_tall_file$snake_mu_rate, "_", her_tall_tall_file$snake_mu_effect_sd,"_",her_tall_tall_file$newt_mu_rate, "_", her_tall_tall_file$newt_mu_effect_sd, "_", her_tall_tall_file$rep))
-for(i in 1:length(her_pattern)){
-  myine<-cor_trends_by_gen(her_tall_tall_file, her_cor_tall_file, "test", "her", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=her_pattern[i])
+```{r, inter cor and pheno}
+inter_pattern <- unique(paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd, "_", inter_tall_tall_file$rep))
+for(i in 1:length(inter_pattern)){
+  myine<-cor_trends_by_gen(inter_tall_tall_file, inter_cor_tall_file, "test", "inter", "newt/snake GAs&rep","otinter", "Cor", min_gen=100, max_gen=50000, pattern=inter_pattern[i])
   plot(myine)
@@
 
-for(i in 1:length(unique(her_tall_tall_file$rep))){
-  myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
+for(i in 1:length(unique(inter_tall_tall_file$rep))){
+  myine<-whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
+  myine<-two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i] )
   suppressMessages(plot(myine))
@@
 # summary
-GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
-GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 ```
@@
 #heatmap
-build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
-build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 
-for(i in 1:length(unique(her_tall_tall_file$rep))){
-  myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
+for(i in 1:length(unique(inter_tall_tall_file$rep))){
+  myine<-whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i])
   plot(myine)
-  myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
+  myine<-two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i] )
 suppressMessages(plot(myine))
@@
 
-#her_grid_tall_file
+#inter_grid_tall_file
 
@@
 spegen=20001
-#unique(her_grid_tall_file$snake_newt_rep)
-her<-her_her_grid_tall_file[which(her_her_grid_tall_file$snake_newt_rep==file_name & her_her_grid_tall_file$generation==spegen),]
+#unique(inter_grid_tall_file$snake_newt_rep)
+inter<-inter_inter_grid_tall_file[which(inter_inter_grid_tall_file$snake_newt_rep==file_name & inter_inter_grid_tall_file$generation==spegen),]
 
-her_mean = her[,grepl("generation|mean", names(her)) ]
+inter_mean = inter[,grepl("generation|mean", names(inter)) ]
 
-her_data_long_mean <- gather(her_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+inter_data_long_mean <- gatinter(inter_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
 
-her_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(her_data_long_mean$condition, "_", 4)
+inter_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(inter_data_long_mean$condition, "_", 4)
 
-her_data_long_mean_short<-her_data_long_mean
+inter_data_long_mean_short<-inter_data_long_mean
 
-her_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-her_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+inter_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+inter_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
 
-main_plot<-ggplot(her_data_long_mean_short)+
+main_plot<-ggplot(inter_data_long_mean_short)+
   labs(title = "Mean Phenotype of Locations",
@@
               fill = "Toxicity/Resistance")+
-  geom_point(data = her_data_long_mean_short[which(her_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = her_data_long_mean_short[which(her_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  geom_point(data = inter_data_long_mean_short[which(inter_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = inter_data_long_mean_short[which(inter_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
   scale_fill_viridis_c()+
@@
 
-snake<-her_data_long_mean_short[which(her_data_long_mean_short$species=="snake"),]
-newt_her<-her_data_long_mean_short[which(her_data_long_mean_short$species=="newt"),]
-newt_her$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_her$measurement), use="complete.obs")
+snake<-inter_data_long_mean_short[which(inter_data_long_mean_short$species=="snake"),]
+newt_inter<-inter_data_long_mean_short[which(inter_data_long_mean_short$species=="newt"),]
+newt_inter$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_inter$measurement), use="complete.obs")
 
-newt_her$info[newt_her$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_her$info[newt_her$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_her$info[is.na(newt_her$info)]<- "middle"
+newt_inter$info[newt_inter$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_inter$info[newt_inter$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_inter$info[is.na(newt_inter$info)]<- "middle"
 
-extra_plot <- ggplot(newt_her)+
+extra_plot <- ggplot(newt_inter)+
   ggtitle("Mean Phenotype") +

### 2022-08-19 graphs_newt_snakes/GA3.Rmd
found a but that swithced newt and snake varables when plotting the correlations with the phenotypes. fixed

@@
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
-  cfile$snake_newt_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
+  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +

### 2022-08-19 graphs_newt_snakes/Heritability.Rmd
found a but that swithced newt and snake varables when plotting the correlations with the phenotypes. fixed

@@
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
-  cfile$snake_newt_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
+  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
+
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +

### 2022-08-19 graphs_newt_snakes/no_interact.Rmd
found a but that swithced newt and snake varables when plotting the correlations with the phenotypes. fixed

@@
   cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"rep_"))[3], "_"))[1]
+  cor_temp_file$rep <-unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"rep_"))[2], "_"))[1]
   cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
@@
   inter_grid_temp_file$sim <-
-  inter_grid_temp_file$rep <-unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"rep_"))[3], "_"))[1]
+  inter_grid_temp_file$rep <-unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"rep_"))[2], "_"))[1]
   inter_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+ #file=inter_tall_tall_file
+#cfile=inter_cor_tall_file 
+  #pattern="1.0e-08_0.005_1.0e-09_0.0158_2"
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
-  cfile$snake_newt_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
+  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
@@
   cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
+
+  if(nrow(cfile)>nrow(file)){
     toDelete <- seq(0, nrow(cfile), 2)
     cfile_short <-  cfile[-toDelete, ]
+  }else{
+    cfile_short <-  cfile
+  }
+
+  if(nrow(cfile_short)>nrow(file)){
+      toDelete <- seq(0, nrow(cfile_short), 2)
+      cfile_short <-  cfile_short[-toDelete, ]
+    }
   figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
@@
 max_gen=10000
-rep=3
+rep=0
 

### 2022-08-22 graphs_newt_snakes/no_interact.Rmd
i fixed the problem with naming and reknit the file for tall GA1. I also am beginning to look at the dat for the no interaction plots.

@@
 
-inter_data_long_mean <- gatinter(inter_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+inter_data_long_mean <- gather(inter_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
 
@@
 ```
+
+```{r, cor grid by location}
+
+#inter_grid_tall_file
+
+file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+spegen=13001
+#unique(inter_grid_tall_file$snake_newt_rep)
+inter<-inter_inter_grid_tall_file[which(inter_inter_grid_tall_file$snake_newt_rep==file_name & inter_inter_grid_tall_file$generation==spegen),]
+
+inter_mean = inter[,grepl("generation|mean", names(inter)) ]
+
+inter_data_long_mean <- gather(inter_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+inter_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(inter_data_long_mean$condition, "_", 4)
+
+inter_data_long_mean_short<-inter_data_long_mean
+
+inter_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+inter_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(inter_data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = inter_data_long_mean_short[which(inter_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = inter_data_long_mean_short[which(inter_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-inter_data_long_mean_short[which(inter_data_long_mean_short$species=="snake"),]
+newt_inter<-inter_data_long_mean_short[which(inter_data_long_mean_short$species=="newt"),]
+newt_inter$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_inter$measurement), use="complete.obs")
+
+newt_inter$info[newt_inter$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_inter$info[newt_inter$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_inter$info[is.na(newt_inter$info)]<- "middle"
+
+extra_plot <- ggplot(newt_inter)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```

### 2022-08-24 graphs_newt_snakes/GA3.Rmd
found a error where I switched newts and snakes

@@
 
+```{bash, data file gathering}
+#!/usr/bin/env bash
+
+# Run these comands while in The the folder that contains the file you would like to condence
+# Goal is to condence all the text files into one file 
+# Requirements: need to have the same name and need to add additional columns
+foldername=bash_test
+thefolder=/Users/victoria/Desktop/${foldername}/*
+#echo ${thefolder}
+
+#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."
+
+if [[ -f /Users/victoria/Desktop/bash_test/all_lit.txt ]] && [[ -f /Users/victoria/Desktop/bash_test/all_grid.txt ]] && [[ -f /Users/victoria/Desktop/bash_test/all_cor.txt ]]
+then
+  echo "All cor, lit, and grid files exist!"
+  echo "This program will now end!"
+  exit 0
+fi
+
+#creating the files
+echo 'generation,Newt_age,Snake_age,Newt_density,Snake_density,Newt_min_Pheno,Newt_max_Pheno,Newt_mean_Pheno,Newt_sd_Pheno,Snake_min_Pheno,Snake_max_Pheno,Snake_mean_Pheno,Snake_sd_Pheno,Newt_pop_size,Snake_pop_size,mean_newts_eaten,sd_newts_eaten,mean_snakes_eaten,sd_snakes_eaten,beta_n,beta_s,snake_found_newt,newt_found,snake_deaths,newt_deaths,time,rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd' > /Users/victoria/Desktop/bash_test/all_lit.txt
+echo 'generation,newt_num_ind_0,snake_num_ind_0,newt_max_pheno_0,snake_max_pheno_0,newt_mean_pheno_0,snake_mean_pheno_0,newt_sd_pheno_0,snake_sd_pheno_0,newt_min_pheno_0,snake_min_pheno_0,newt_num_ind_1,snake_num_ind_1,newt_max_pheno_1,snake_max_pheno_1,newt_mean_pheno_1,snake_mean_pheno_1,newt_sd_pheno_1,snake_sd_pheno_1,newt_min_pheno_1,snake_min_pheno_1,newt_num_ind_2,snake_num_ind_2,newt_max_pheno_2,snake_max_pheno_2,newt_mean_pheno_2,snake_mean_pheno_2,newt_sd_pheno_2,snake_sd_pheno_2,newt_min_pheno_2,snake_min_pheno_2,newt_num_ind_3,snake_num_ind_3,newt_max_pheno_3,snake_max_pheno_3,newt_mean_pheno_3,snake_mean_pheno_3,newt_sd_pheno_3,snake_sd_pheno_3,newt_min_pheno_3,snake_min_pheno_3,newt_num_ind_4,snake_num_ind_4,newt_max_pheno_4,snake_max_pheno_4,newt_mean_pheno_4,snake_mean_pheno_4,newt_sd_pheno_4,snake_sd_pheno_4,newt_min_pheno_4,snake_min_pheno_4,newt_num_ind_5,snake_num_ind_5,newt_max_pheno_5,snake_max_pheno_5,newt_mean_pheno_5,snake_mean_pheno_5,newt_sd_pheno_5,snake_sd_pheno_5,newt_min_pheno_5,snake_min_pheno_5,newt_num_ind_6,snake_num_ind_6,newt_max_pheno_6,snake_max_pheno_6,newt_mean_pheno_6,snake_mean_pheno_6,newt_sd_pheno_6,snake_sd_pheno_6,newt_min_pheno_6,snake_min_pheno_6,newt_num_ind_7,snake_num_ind_7,newt_max_pheno_7,snake_max_pheno_7,newt_mean_pheno_7,snake_mean_pheno_7,newt_sd_pheno_7,snake_sd_pheno_7,newt_min_pheno_7,snake_min_pheno_7,newt_num_ind_8,snake_num_ind_8,newt_max_pheno_8,snake_max_pheno_8,newt_mean_pheno_8,snake_mean_pheno_8,newt_sd_pheno_8,snake_sd_pheno_8,newt_min_pheno_8,snake_min_pheno_8,newt_num_ind_9,snake_num_ind_9,newt_max_pheno_9,snake_max_pheno_9,newt_mean_pheno_9,snake_mean_pheno_9,newt_sd_pheno_9,snake_sd_pheno_9,newt_min_pheno_9,snake_min_pheno_9,newt_num_ind_10,snake_num_ind_10,newt_max_pheno_10,snake_max_pheno_10,newt_mean_pheno_10,snake_mean_pheno_10,newt_sd_pheno_10,snake_sd_pheno_10,newt_min_pheno_10,snake_min_pheno_10,newt_num_ind_11,snake_num_ind_11,newt_max_pheno_11,snake_max_pheno_11,newt_mean_pheno_11,snake_mean_pheno_11,newt_sd_pheno_11,snake_sd_pheno_11,newt_min_pheno_11,snake_min_pheno_11,newt_num_ind_12,snake_num_ind_12,newt_max_pheno_12,snake_max_pheno_12,newt_mean_pheno_12,snake_mean_pheno_12,newt_sd_pheno_12,snake_sd_pheno_12,newt_min_pheno_12,snake_min_pheno_12,newt_num_ind_13,snake_num_ind_13,newt_max_pheno_13,snake_max_pheno_13,newt_mean_pheno_13,snake_mean_pheno_13,newt_sd_pheno_13,snake_sd_pheno_13,newt_min_pheno_13,snake_min_pheno_13,newt_num_ind_14,snake_num_ind_14,newt_max_pheno_14,snake_max_pheno_14,newt_mean_pheno_14,snake_mean_pheno_14,newt_sd_pheno_14,snake_sd_pheno_14,newt_min_pheno_14,snake_min_pheno_14,newt_num_ind_15,snake_num_ind_15,newt_max_pheno_15,snake_max_pheno_15,newt_mean_pheno_15,snake_mean_pheno_15,newt_sd_pheno_15,snake_sd_pheno_15,newt_min_pheno_15,snake_min_pheno_15,newt_num_ind_16,snake_num_ind_16,newt_max_pheno_16,snake_max_pheno_16,newt_mean_pheno_16,snake_mean_pheno_16,newt_sd_pheno_16,snake_sd_pheno_16,newt_min_pheno_16,snake_min_pheno_16,newt_num_ind_17,snake_num_ind_17,newt_max_pheno_17,snake_max_pheno_17,newt_mean_pheno_17,snake_mean_pheno_17,newt_sd_pheno_17,snake_sd_pheno_17,newt_min_pheno_17,snake_min_pheno_17,newt_num_ind_18,snake_num_ind_18,newt_max_pheno_18,snake_max_pheno_18,newt_mean_pheno_18,snake_mean_pheno_18,newt_sd_pheno_18,snake_sd_pheno_18,newt_min_pheno_18,snake_min_pheno_18,newt_num_ind_19,snake_num_ind_19,newt_max_pheno_19,snake_max_pheno_19,newt_mean_pheno_19,snake_mean_pheno_19,newt_sd_pheno_19,snake_sd_pheno_19,newt_min_pheno_19,snake_min_pheno_19,newt_num_ind_20,snake_num_ind_20,newt_max_pheno_20,snake_max_pheno_20,newt_mean_pheno_20,snake_mean_pheno_20,newt_sd_pheno_20,snake_sd_pheno_20,newt_min_pheno_20,snake_min_pheno_20,newt_num_ind_21,snake_num_ind_21,newt_max_pheno_21,snake_max_pheno_21,newt_mean_pheno_21,snake_mean_pheno_21,newt_sd_pheno_21,snake_sd_pheno_21,newt_min_pheno_21,snake_min_pheno_21,newt_num_ind_22,snake_num_ind_22,newt_max_pheno_22,snake_max_pheno_22,newt_mean_pheno_22,snake_mean_pheno_22,newt_sd_pheno_22,snake_sd_pheno_22,newt_min_pheno_22,snake_min_pheno_22,newt_num_ind_23,snake_num_ind_23,newt_max_pheno_23,snake_max_pheno_23,newt_mean_pheno_23,snake_mean_pheno_23,newt_sd_pheno_23,snake_sd_pheno_23,newt_min_pheno_23,snake_min_pheno_23,newt_num_ind_24,snake_num_ind_24,newt_max_pheno_24,snake_max_pheno_24,newt_mean_pheno_24,snake_mean_pheno_24,newt_sd_pheno_24,snake_sd_pheno_24,newt_min_pheno_24,snake_min_pheno_24,newt_num_ind_25,snake_num_ind_25,newt_max_pheno_25,snake_max_pheno_25,newt_mean_pheno_25,snake_mean_pheno_25,newt_sd_pheno_25,snake_sd_pheno_25,newt_min_pheno_25,snake_min_pheno_25,newt_num_ind_26,snake_num_ind_26,newt_max_pheno_26,snake_max_pheno_26,newt_mean_pheno_26,snake_mean_pheno_26,newt_sd_pheno_26,snake_sd_pheno_26,newt_min_pheno_26,snake_min_pheno_26,newt_num_ind_27,snake_num_ind_27,newt_max_pheno_27,snake_max_pheno_27,newt_mean_pheno_27,snake_mean_pheno_27,newt_sd_pheno_27,snake_sd_pheno_27,newt_min_pheno_27,snake_min_pheno_27,newt_num_ind_28,snake_num_ind_28,newt_max_pheno_28,snake_max_pheno_28,newt_mean_pheno_28,snake_mean_pheno_28,newt_sd_pheno_28,snake_sd_pheno_28,newt_min_pheno_28,snake_min_pheno_28,newt_num_ind_29,snake_num_ind_29,newt_max_pheno_29,snake_max_pheno_29,newt_mean_pheno_29,snake_mean_pheno_29,newt_sd_pheno_29,snake_sd_pheno_29,newt_min_pheno_29,snake_min_pheno_29,newt_num_ind_30,snake_num_ind_30,newt_max_pheno_30,snake_max_pheno_30,newt_mean_pheno_30,snake_mean_pheno_30,newt_sd_pheno_30,snake_sd_pheno_30,newt_min_pheno_30,snake_min_pheno_30,newt_num_ind_31,snake_num_ind_31,newt_max_pheno_31,snake_max_pheno_31,newt_mean_pheno_31,snake_mean_pheno_31,newt_sd_pheno_31,snake_sd_pheno_31,newt_min_pheno_31,snake_min_pheno_31,newt_num_ind_32,snake_num_ind_32,newt_max_pheno_32,snake_max_pheno_32,newt_mean_pheno_32,snake_mean_pheno_32,newt_sd_pheno_32,snake_sd_pheno_32,newt_min_pheno_32,snake_min_pheno_32,newt_num_ind_33,snake_num_ind_33,newt_max_pheno_33,snake_max_pheno_33,newt_mean_pheno_33,snake_mean_pheno_33,newt_sd_pheno_33,snake_sd_pheno_33,newt_min_pheno_33,snake_min_pheno_33,newt_num_ind_34,snake_num_ind_34,newt_max_pheno_34,snake_max_pheno_34,newt_mean_pheno_34,snake_mean_pheno_34,newt_sd_pheno_34,snake_sd_pheno_34,newt_min_pheno_34,snake_min_pheno_34,newt_num_ind_35,snake_num_ind_35,newt_max_pheno_35,snake_max_pheno_35,newt_mean_pheno_35,snake_mean_pheno_35,newt_sd_pheno_35,snake_sd_pheno_35,newt_min_pheno_35,snake_min_pheno_35,newt_num_ind_36,snake_num_ind_36,newt_max_pheno_36,snake_max_pheno_36,newt_mean_pheno_36,snake_mean_pheno_36,newt_sd_pheno_36,snake_sd_pheno_36,newt_min_pheno_36,snake_min_pheno_36,newt_num_ind_37,snake_num_ind_37,newt_max_pheno_37,snake_max_pheno_37,newt_mean_pheno_37,snake_mean_pheno_37,newt_sd_pheno_37,snake_sd_pheno_37,newt_min_pheno_37,snake_min_pheno_37,newt_num_ind_38,snake_num_ind_38,newt_max_pheno_38,snake_max_pheno_38,newt_mean_pheno_38,snake_mean_pheno_38,newt_sd_pheno_38,snake_sd_pheno_38,newt_min_pheno_38,snake_min_pheno_38,newt_num_ind_39,snake_num_ind_39,newt_max_pheno_39,snake_max_pheno_39,newt_mean_pheno_39,snake_mean_pheno_39,newt_sd_pheno_39,snake_sd_pheno_39,newt_min_pheno_39,snake_min_pheno_39,newt_num_ind_40,snake_num_ind_40,newt_max_pheno_40,snake_max_pheno_40,newt_mean_pheno_40,snake_mean_pheno_40,newt_sd_pheno_40,snake_sd_pheno_40,newt_min_pheno_40,snake_min_pheno_40,newt_num_ind_41,snake_num_ind_41,newt_max_pheno_41,snake_max_pheno_41,newt_mean_pheno_41,snake_mean_pheno_41,newt_sd_pheno_41,snake_sd_pheno_41,newt_min_pheno_41,snake_min_pheno_41,newt_num_ind_42,snake_num_ind_42,newt_max_pheno_42,snake_max_pheno_42,newt_mean_pheno_42,snake_mean_pheno_42,newt_sd_pheno_42,snake_sd_pheno_42,newt_min_pheno_42,snake_min_pheno_42,newt_num_ind_43,snake_num_ind_43,newt_max_pheno_43,snake_max_pheno_43,newt_mean_pheno_43,snake_mean_pheno_43,newt_sd_pheno_43,snake_sd_pheno_43,newt_min_pheno_43,snake_min_pheno_43,newt_num_ind_44,snake_num_ind_44,newt_max_pheno_44,snake_max_pheno_44,newt_mean_pheno_44,snake_mean_pheno_44,newt_sd_pheno_44,snake_sd_pheno_44,newt_min_pheno_44,snake_min_pheno_44,newt_num_ind_45,snake_num_ind_45,newt_max_pheno_45,snake_max_pheno_45,newt_mean_pheno_45,snake_mean_pheno_45,newt_sd_pheno_45,snake_sd_pheno_45,newt_min_pheno_45,snake_min_pheno_45,newt_num_ind_46,snake_num_ind_46,newt_max_pheno_46,snake_max_pheno_46,newt_mean_pheno_46,snake_mean_pheno_46,newt_sd_pheno_46,snake_sd_pheno_46,newt_min_pheno_46,snake_min_pheno_46,newt_num_ind_47,snake_num_ind_47,newt_max_pheno_47,snake_max_pheno_47,newt_mean_pheno_47,snake_mean_pheno_47,newt_sd_pheno_47,snake_sd_pheno_47,newt_min_pheno_47,snake_min_pheno_47,newt_num_ind_48,snake_num_ind_48,newt_max_pheno_48,snake_max_pheno_48,newt_mean_pheno_48,snake_mean_pheno_48,newt_sd_pheno_48,snake_sd_pheno_48,newt_min_pheno_48,snake_min_pheno_48,newt_num_ind_49,snake_num_ind_49,newt_max_pheno_49,snake_max_pheno_49,newt_mean_pheno_49,snake_mean_pheno_49,newt_sd_pheno_49,snake_sd_pheno_49,newt_min_pheno_49,snake_min_pheno_49,newt_num_ind_50,snake_num_ind_50,newt_max_pheno_50,snake_max_pheno_50,newt_mean_pheno_50,snake_mean_pheno_50,newt_sd_pheno_50,snake_sd_pheno_50,newt_min_pheno_50,snake_min_pheno_50,newt_num_ind_51,snake_num_ind_51,newt_max_pheno_51,snake_max_pheno_51,newt_mean_pheno_51,snake_mean_pheno_51,newt_sd_pheno_51,snake_sd_pheno_51,newt_min_pheno_51,snake_min_pheno_51,newt_num_ind_52,snake_num_ind_52,newt_max_pheno_52,snake_max_pheno_52,newt_mean_pheno_52,snake_mean_pheno_52,newt_sd_pheno_52,snake_sd_pheno_52,newt_min_pheno_52,snake_min_pheno_52,newt_num_ind_53,snake_num_ind_53,newt_max_pheno_53,snake_max_pheno_53,newt_mean_pheno_53,snake_mean_pheno_53,newt_sd_pheno_53,snake_sd_pheno_53,newt_min_pheno_53,snake_min_pheno_53,newt_num_ind_54,snake_num_ind_54,newt_max_pheno_54,snake_max_pheno_54,newt_mean_pheno_54,snake_mean_pheno_54,newt_sd_pheno_54,snake_sd_pheno_54,newt_min_pheno_54,snake_min_pheno_54,newt_num_ind_55,snake_num_ind_55,newt_max_pheno_55,snake_max_pheno_55,newt_mean_pheno_55,snake_mean_pheno_55,newt_sd_pheno_55,snake_sd_pheno_55,newt_min_pheno_55,snake_min_pheno_55,newt_num_ind_56,snake_num_ind_56,newt_max_pheno_56,snake_max_pheno_56,newt_mean_pheno_56,snake_mean_pheno_56,newt_sd_pheno_56,snake_sd_pheno_56,newt_min_pheno_56,snake_min_pheno_56,newt_num_ind_57,snake_num_ind_57,newt_max_pheno_57,snake_max_pheno_57,newt_mean_pheno_57,snake_mean_pheno_57,newt_sd_pheno_57,snake_sd_pheno_57,newt_min_pheno_57,snake_min_pheno_57,newt_num_ind_58,snake_num_ind_58,newt_max_pheno_58,snake_max_pheno_58,newt_mean_pheno_58,snake_mean_pheno_58,newt_sd_pheno_58,snake_sd_pheno_58,newt_min_pheno_58,snake_min_pheno_58,newt_num_ind_59,snake_num_ind_59,newt_max_pheno_59,snake_max_pheno_59,newt_mean_pheno_59,snake_mean_pheno_59,newt_sd_pheno_59,snake_sd_pheno_59,newt_min_pheno_59,snake_min_pheno_59,newt_num_ind_60,snake_num_ind_60,newt_max_pheno_60,snake_max_pheno_60,newt_mean_pheno_60,snake_mean_pheno_60,newt_sd_pheno_60,snake_sd_pheno_60,newt_min_pheno_60,snake_min_pheno_60,newt_num_ind_61,snake_num_ind_61,newt_max_pheno_61,snake_max_pheno_61,newt_mean_pheno_61,snake_mean_pheno_61,newt_sd_pheno_61,snake_sd_pheno_61,newt_min_pheno_61,snake_min_pheno_61,newt_num_ind_62,snake_num_ind_62,newt_max_pheno_62,snake_max_pheno_62,newt_mean_pheno_62,snake_mean_pheno_62,newt_sd_pheno_62,snake_sd_pheno_62,newt_min_pheno_62,snake_min_pheno_62,newt_num_ind_63,snake_num_ind_63,newt_max_pheno_63,snake_max_pheno_63,newt_mean_pheno_63,snake_mean_pheno_63,newt_sd_pheno_63,snake_sd_pheno_63,newt_min_pheno_63,snake_min_pheno_63,newt_num_ind_64,snake_num_ind_64,newt_max_pheno_64,snake_max_pheno_64,newt_mean_pheno_64,snake_mean_pheno_64,newt_sd_pheno_64,snake_sd_pheno_64,newt_min_pheno_64,snake_min_pheno_64,newt_num_ind_65,snake_num_ind_65,newt_max_pheno_65,snake_max_pheno_65,newt_mean_pheno_65,snake_mean_pheno_65,newt_sd_pheno_65,snake_sd_pheno_65,newt_min_pheno_65,snake_min_pheno_65,newt_num_ind_66,snake_num_ind_66,newt_max_pheno_66,snake_max_pheno_66,newt_mean_pheno_66,snake_mean_pheno_66,newt_sd_pheno_66,snake_sd_pheno_66,newt_min_pheno_66,snake_min_pheno_66,newt_num_ind_67,snake_num_ind_67,newt_max_pheno_67,snake_max_pheno_67,newt_mean_pheno_67,snake_mean_pheno_67,newt_sd_pheno_67,snake_sd_pheno_67,newt_min_pheno_67,snake_min_pheno_67,newt_num_ind_68,snake_num_ind_68,newt_max_pheno_68,snake_max_pheno_68,newt_mean_pheno_68,snake_mean_pheno_68,newt_sd_pheno_68,snake_sd_pheno_68,newt_min_pheno_68,snake_min_pheno_68,newt_num_ind_69,snake_num_ind_69,newt_max_pheno_69,snake_max_pheno_69,newt_mean_pheno_69,snake_mean_pheno_69,newt_sd_pheno_69,snake_sd_pheno_69,newt_min_pheno_69,snake_min_pheno_69,newt_num_ind_70,snake_num_ind_70,newt_max_pheno_70,snake_max_pheno_70,newt_mean_pheno_70,snake_mean_pheno_70,newt_sd_pheno_70,snake_sd_pheno_70,newt_min_pheno_70,snake_min_pheno_70,newt_num_ind_71,snake_num_ind_71,newt_max_pheno_71,snake_max_pheno_71,newt_mean_pheno_71,snake_mean_pheno_71,newt_sd_pheno_71,snake_sd_pheno_71,newt_min_pheno_71,snake_min_pheno_71,newt_num_ind_72,snake_num_ind_72,newt_max_pheno_72,snake_max_pheno_72,newt_mean_pheno_72,snake_mean_pheno_72,newt_sd_pheno_72,snake_sd_pheno_72,newt_min_pheno_72,snake_min_pheno_72,newt_num_ind_73,snake_num_ind_73,newt_max_pheno_73,snake_max_pheno_73,newt_mean_pheno_73,snake_mean_pheno_73,newt_sd_pheno_73,snake_sd_pheno_73,newt_min_pheno_73,snake_min_pheno_73,newt_num_ind_74,snake_num_ind_74,newt_max_pheno_74,snake_max_pheno_74,newt_mean_pheno_74,snake_mean_pheno_74,newt_sd_pheno_74,snake_sd_pheno_74,newt_min_pheno_74,snake_min_pheno_74,newt_num_ind_75,snake_num_ind_75,newt_max_pheno_75,snake_max_pheno_75,newt_mean_pheno_75,snake_mean_pheno_75,newt_sd_pheno_75,snake_sd_pheno_75,newt_min_pheno_75,snake_min_pheno_75,newt_num_ind_76,snake_num_ind_76,newt_max_pheno_76,snake_max_pheno_76,newt_mean_pheno_76,snake_mean_pheno_76,newt_sd_pheno_76,snake_sd_pheno_76,newt_min_pheno_76,snake_min_pheno_76,newt_num_ind_77,snake_num_ind_77,newt_max_pheno_77,snake_max_pheno_77,newt_mean_pheno_77,snake_mean_pheno_77,newt_sd_pheno_77,snake_sd_pheno_77,newt_min_pheno_77,snake_min_pheno_77,newt_num_ind_78,snake_num_ind_78,newt_max_pheno_78,snake_max_pheno_78,newt_mean_pheno_78,snake_mean_pheno_78,newt_sd_pheno_78,snake_sd_pheno_78,newt_min_pheno_78,snake_min_pheno_78,newt_num_ind_79,snake_num_ind_79,newt_max_pheno_79,snake_max_pheno_79,newt_mean_pheno_79,snake_mean_pheno_79,newt_sd_pheno_79,snake_sd_pheno_79,newt_min_pheno_79,snake_min_pheno_79,newt_num_ind_80,snake_num_ind_80,newt_max_pheno_80,snake_max_pheno_80,newt_mean_pheno_80,snake_mean_pheno_80,newt_sd_pheno_80,snake_sd_pheno_80,newt_min_pheno_80,snake_min_pheno_80,newt_num_ind_81,snake_num_ind_81,newt_max_pheno_81,snake_max_pheno_81,newt_mean_pheno_81,snake_mean_pheno_81,newt_sd_pheno_81,snake_sd_pheno_81,newt_min_pheno_81,snake_min_pheno_81,newt_num_ind_82,snake_num_ind_82,newt_max_pheno_82,snake_max_pheno_82,newt_mean_pheno_82,snake_mean_pheno_82,newt_sd_pheno_82,snake_sd_pheno_82,newt_min_pheno_82,snake_min_pheno_82,newt_num_ind_83,snake_num_ind_83,newt_max_pheno_83,snake_max_pheno_83,newt_mean_pheno_83,snake_mean_pheno_83,newt_sd_pheno_83,snake_sd_pheno_83,newt_min_pheno_83,snake_min_pheno_83,newt_num_ind_84,snake_num_ind_84,newt_max_pheno_84,snake_max_pheno_84,newt_mean_pheno_84,snake_mean_pheno_84,newt_sd_pheno_84,snake_sd_pheno_84,newt_min_pheno_84,snake_min_pheno_84,newt_num_ind_85,snake_num_ind_85,newt_max_pheno_85,snake_max_pheno_85,newt_mean_pheno_85,snake_mean_pheno_85,newt_sd_pheno_85,snake_sd_pheno_85,newt_min_pheno_85,snake_min_pheno_85,newt_num_ind_86,snake_num_ind_86,newt_max_pheno_86,snake_max_pheno_86,newt_mean_pheno_86,snake_mean_pheno_86,newt_sd_pheno_86,snake_sd_pheno_86,newt_min_pheno_86,snake_min_pheno_86,newt_num_ind_87,snake_num_ind_87,newt_max_pheno_87,snake_max_pheno_87,newt_mean_pheno_87,snake_mean_pheno_87,newt_sd_pheno_87,snake_sd_pheno_87,newt_min_pheno_87,snake_min_pheno_87,newt_num_ind_88,snake_num_ind_88,newt_max_pheno_88,snake_max_pheno_88,newt_mean_pheno_88,snake_mean_pheno_88,newt_sd_pheno_88,snake_sd_pheno_88,newt_min_pheno_88,snake_min_pheno_88,newt_num_ind_89,snake_num_ind_89,newt_max_pheno_89,snake_max_pheno_89,newt_mean_pheno_89,snake_mean_pheno_89,newt_sd_pheno_89,snake_sd_pheno_89,newt_min_pheno_89,snake_min_pheno_89,newt_num_ind_90,snake_num_ind_90,newt_max_pheno_90,snake_max_pheno_90,newt_mean_pheno_90,snake_mean_pheno_90,newt_sd_pheno_90,snake_sd_pheno_90,newt_min_pheno_90,snake_min_pheno_90,newt_num_ind_91,snake_num_ind_91,newt_max_pheno_91,snake_max_pheno_91,newt_mean_pheno_91,snake_mean_pheno_91,newt_sd_pheno_91,snake_sd_pheno_91,newt_min_pheno_91,snake_min_pheno_91,newt_num_ind_92,snake_num_ind_92,newt_max_pheno_92,snake_max_pheno_92,newt_mean_pheno_92,snake_mean_pheno_92,newt_sd_pheno_92,snake_sd_pheno_92,newt_min_pheno_92,snake_min_pheno_92,newt_num_ind_93,snake_num_ind_93,newt_max_pheno_93,snake_max_pheno_93,newt_mean_pheno_93,snake_mean_pheno_93,newt_sd_pheno_93,snake_sd_pheno_93,newt_min_pheno_93,snake_min_pheno_93,newt_num_ind_94,snake_num_ind_94,newt_max_pheno_94,snake_max_pheno_94,newt_mean_pheno_94,snake_mean_pheno_94,newt_sd_pheno_94,snake_sd_pheno_94,newt_min_pheno_94,snake_min_pheno_94,newt_num_ind_95,snake_num_ind_95,newt_max_pheno_95,snake_max_pheno_95,newt_mean_pheno_95,snake_mean_pheno_95,newt_sd_pheno_95,snake_sd_pheno_95,newt_min_pheno_95,snake_min_pheno_95,newt_num_ind_96,snake_num_ind_96,newt_max_pheno_96,snake_max_pheno_96,newt_mean_pheno_96,snake_mean_pheno_96,newt_sd_pheno_96,snake_sd_pheno_96,newt_min_pheno_96,snake_min_pheno_96,newt_num_ind_97,snake_num_ind_97,newt_max_pheno_97,snake_max_pheno_97,newt_mean_pheno_97,snake_mean_pheno_97,newt_sd_pheno_97,snake_sd_pheno_97,newt_min_pheno_97,snake_min_pheno_97,newt_num_ind_98,snake_num_ind_98,newt_max_pheno_98,snake_max_pheno_98,newt_mean_pheno_98,snake_mean_pheno_98,newt_sd_pheno_98,snake_sd_pheno_98,newt_min_pheno_98,snake_min_pheno_98,newt_num_ind_99,snake_num_ind_99,newt_max_pheno_99,snake_max_pheno_99,newt_mean_pheno_99,snake_mean_pheno_99,newt_sd_pheno_99,snake_sd_pheno_99,newt_min_pheno_99,snake_min_pheno_99,rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd' > /Users/victoria/Desktop/bash_test/all_grid.txt
+echo 'generation,mean_newt_pheno_By_mean_snake_pheno,num_newts_By_num_snakes,sum_newt_pheno_By_num_snake,sum_snake_pheno_By_num_newt,sum_newt_pheno_By_num_newt,sum_snake_pheno_By_snake_newt,rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd' > /Users/victoria/Desktop/bash_test/all_cor.txt
+
+for filename in $thefolder*.text;
+  do 
+#getting the variables 
+my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
+my_other_type=$(echo ${filename} |sed 's/.*GA520_//; s/_.*//')
+snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
+snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
+newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
+newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
+rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
+#echo ${newt_mu_rate}	
+# echo $my_type
+# echo $my_other_type
+# these new columns adding them to the data
+sed -i '' -e 's/$/,'${rep}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
+#infile >outfile
+if [[ $my_type == "lit" ]]
+then
+    tail -n +2 -q $filename >> /Users/victoria/Desktop/bash_test/all_lit.txt
+fi
+
+if [[ $my_type == "grid" ]]
+then
+    tail -n +2 -q $filename >> /Users/victoria/Desktop/bash_test/all_grid.txt
+fi
+
+if [[ $my_other_type == "cor" ]]
+then
+    tail -n +2 -q $filename >> /Users/victoria/Desktop/bash_test/all_cor.txt
+fi
+
+done
+
+```
+
 ```{r, data gathering}
@@
 
-GA3_tall <- list.files(path="~/Desktop/GA3", pattern="_lit_", full.names=TRUE, recursive=FALSE)
-GA3_tall_cor_files <- list.files(path="~/Desktop/GA3", pattern="_cor_", full.names=TRUE, recursive=FALSE)
-GA3_GA3_grid_tall_files <- list.files(path="~/Desktop/GA3", pattern="_grid_", full.names=TRUE, recursive=FALSE)
-
-GA3_tall_tall_file<- data.frame()
-GA3_cor_tall_file<- data.frame()
-GA3_GA3_grid_tall_file<-data.frame()
-name_list<-c()
-cor_name_list<-c()
-grid_name_list<-c()
-for(i in seq(1, length(GA3_tall)/2, 1)){
-  print(i)
-  #sim
-
-  GA3_temp_file <- read.csv(GA3_tall[i], header = TRUE)
-  GA3_temp_file$rep <- unlist(str_split(unlist(str_split(GA3_tall[i],"rep_"))[3], "_"))[1]
-  GA3_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  name_list<-c(paste0(GA3_temp_file$snake_mu_rate[1], GA3_temp_file$newt_mu_rate[1], GA3_temp_file$snake_mu_effect_sd[1], GA3_temp_file$newt_mu_effect_sd[1]),name_list)
-  GA3_temp_file$sim <- LETTERS[length(unique(name_list))]
-  GA3_tall_tall_file <- rbind(GA3_tall_tall_file, GA3_temp_file)
-  print(GA3_temp_file$sim[1])
-
-  cor_temp_file <- read.csv(GA3_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
-  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
-  GA3_cor_tall_file <- rbind(GA3_cor_tall_file, cor_temp_file)
-  print(cor_temp_file$sim[1])
-
-  GA3_grid_temp_file <- read.csv(GA3_GA3_grid_tall_files[i], header = TRUE)
-  GA3_grid_temp_file$sim <-
-  GA3_grid_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"rep_"))[3], "_"))[1]
-  GA3_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  grid_name_list<-c(paste0(GA3_grid_temp_file$snake_mu_rate[1], GA3_grid_temp_file$newt_mu_rate[1], GA3_grid_temp_file$snake_mu_effect_sd[1], GA3_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
-  GA3_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
-  GA3_GA3_grid_tall_file <- rbind(GA3_GA3_grid_tall_file, GA3_grid_temp_file)
-   print(GA3_grid_temp_file$sim[1])
-
-  }
- ###to set first half 
-GA3_tall_tall_file_p1<- GA3_tall_tall_file
-GA3_cor_tall_file_p1<- GA3_cor_tall_file
-GA3_GA3_grid_tall_file_p1<-GA3_GA3_grid_tall_file
-
-for(i in seq((length(GA3_tall)/2+1), length(GA3_tall), 1)){
-  print(i)
-  #sim
-
-  GA3_temp_file <- read.csv(GA3_tall[i], header = TRUE)
-  GA3_temp_file$rep <- unlist(str_split(unlist(str_split(GA3_tall[i],"rep_"))[3], "_"))[1]
-  GA3_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  name_list<-c(paste0(GA3_temp_file$snake_mu_rate[1], GA3_temp_file$newt_mu_rate[1], GA3_temp_file$snake_mu_effect_sd[1], GA3_temp_file$newt_mu_effect_sd[1]),name_list)
-  GA3_temp_file$sim <- LETTERS[length(unique(name_list))]
-  GA3_tall_tall_file <- rbind(GA3_tall_tall_file, GA3_temp_file)
-  print(GA3_temp_file$sim[1])
-
-  cor_temp_file <- read.csv(GA3_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
-  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
-  GA3_cor_tall_file <- rbind(GA3_cor_tall_file, cor_temp_file)
-  print(cor_temp_file$sim[1])
-
-  GA3_grid_temp_file <- read.csv(GA3_GA3_grid_tall_files[i], header = TRUE)
-  GA3_grid_temp_file$sim <-
-  GA3_grid_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"rep_"))[3], "_"))[1]
-  GA3_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  grid_name_list<-c(paste0(GA3_grid_temp_file$snake_mu_rate[1], GA3_grid_temp_file$newt_mu_rate[1], GA3_grid_temp_file$snake_mu_effect_sd[1], GA3_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
-  GA3_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
-  GA3_GA3_grid_tall_file <- rbind(GA3_GA3_grid_tall_file, GA3_grid_temp_file)
-   print(GA3_grid_temp_file$sim[1])
-
-  }
-
- ###to combine second half with first
-GA3_tall_tall_file<- rbind(GA3_tall_tall_file_p1, GA3_tall_tall_file)
-GA3_cor_tall_file<- rbind(GA3_cor_tall_file_p1, GA3_cor_tall_file)
-GA3_GA3_grid_tall_file<-rbind(GA3_GA3_grid_tall_file_p1, GA3_GA3_grid_tall_file)
-
-# making row edits to the dataframe for graphing
+GA3_tall_tall_file<- read.csv("~/Desktop/bash_test/all_lit.txt" , header = TRUE)
+
+GA3_tall_tall_file$group_rep <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep)
+
+GA3_tall_tall_file$group <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd)
+
+GA3_tall_tall_file$sim=LETTERS[factor(GA3_tall_tall_file$group)]
 GA3_tall_tall_file$dif <- GA3_tall_tall_file$Snake_mean_Pheno-GA3_tall_tall_file$Newt_mean_Pheno
 
-GA3_tall_tall_file$group_rep <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep)
-
-GA3_tall_tall_file$group <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd)
-
+GA3_cor_tall_file<- read.csv("~/Desktop/bash_test/all_cor.txt" , header = TRUE)
+GA3_cor_tall_file$group_rep <- paste0(GA3_cor_tall_file$snake_mu_rate, "_", GA3_cor_tall_file$snake_mu_effect_sd,"_",GA3_cor_tall_file$newt_mu_rate, "_", GA3_cor_tall_file$newt_mu_effect_sd, "_", GA3_cor_tall_file$rep)
+GA3_cor_tall_file$group <- paste0(GA3_cor_tall_file$snake_mu_rate, "_", GA3_cor_tall_file$snake_mu_effect_sd,"_",GA3_cor_tall_file$newt_mu_rate, "_", GA3_cor_tall_file$newt_mu_effect_sd)
+GA3_cor_tall_file$sim=LETTERS[factor(GA3_cor_tall_file$group)]
+
+GA3_GA3_grid_tall_file<-read.csv("~/Desktop/bash_test/all_grid.txt" , header = TRUE)
+GA3_GA3_grid_tall_file$group <- paste0(GA3_GA3_grid_tall_file$snake_mu_rate, "_", GA3_GA3_grid_tall_file$snake_mu_effect_sd,"_",GA3_GA3_grid_tall_file$newt_mu_rate, "_", GA3_GA3_grid_tall_file$newt_mu_effect_sd)
+GA3_GA3_grid_tall_file$group_rep <- paste0(GA3_GA3_grid_tall_file$snake_mu_rate, "_", GA3_GA3_grid_tall_file$snake_mu_effect_sd,"_",GA3_GA3_grid_tall_file$newt_mu_rate, "_", GA3_GA3_grid_tall_file$newt_mu_effect_sd, "_", GA3_GA3_grid_tall_file$rep)
+
+GA3_GA3_grid_tall_file$sim=LETTERS[factor(GA3_GA3_grid_tall_file$group)]
 GA3_GA3_grid_tall_file$snake_newt_rep <- paste0("Snake_",GA3_GA3_grid_tall_file$snake_mu_rate, "_", GA3_GA3_grid_tall_file$snake_mu_effect_sd, "_Newt_",GA3_GA3_grid_tall_file$newt_mu_rate, "_", GA3_GA3_grid_tall_file$newt_mu_effect_sd, "_", GA3_GA3_grid_tall_file$rep)
@@
   real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
   unique(file$sim)
@@
   theme(plot.title = element_text(size=5)) +
-  facet_wrap(~newt_snake)+
+  facet_wrap(~snake_newt)+
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
@@
   real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  unique(file$sim)
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  #unique(file$sim)
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
@@
   xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=rep))+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
   geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
@@
   xlim(-1.1, 1.1)+
-  facet_wrap(~newt_snake)+
+  facet_wrap(~snake_newt)+
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
@@
   #stat_bin(bins=30)+
-  facet_wrap(~newt_snake)+
+  facet_wrap(~snake_newt)+
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
@@
   real_snewt_var = var(snewt$dif)
-  cfile$newt_snake_rep <- paste0("Newt_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_Snake_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
   var_cor_table=data.frame()
 
-  for(i in 1:length(unique(file$newt_snake_rep))){
-    pattern<-unique(file$newt_snake_rep)[i]
-    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]
-    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]
+  for(i in 1:length(unique(file$snake_newt_rep))){
+    pattern<-unique(file$snake_newt_rep)[i]
+    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
+    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
 
@@
 four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
-  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
@@
 
-for(i in 1:length(unique(file$newt_snake_rep))){
-
-  pattern=unique(file$newt_snake_rep)[i]
-  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep ==pattern),]
+for(i in 1:length(unique(file$snake_newt_rep))){
+
+  pattern=unique(file$snake_newt_rep)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]
 
@@
 params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
-params$newt_snake <- paste0(params$newt, "_", params$snake)
+params$snake_newt <- paste0(params$snake, "_", params$newt)
 return(params)
@@
 
-file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
 
@@
 build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
-  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-
+  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
   params<-create_parm_file(file, min_gen, max_gen)
@@
 
-file_name= "Snake_1.0e-11_0.158_Newt_1.0e-10_0.05_0"
+file_name= "Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
@@
 
-file_name= "Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0"
+file_name= "Snake_1e-08_0.005_Newt_1e-11_0.158_0"
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
@@
 
-file_name= "Snake_1.0e-10_0.05_Newt_1.0e-11_0.158_3"
+file_name= "Snake_1e-10_0.05_Newt_1e-11_0.158_3"
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
@@
 #GA3_grid_tall_file
-file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_0"
+file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_0"
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
@@
 
-file_name= "Snake_1.0e-10_0.05_Newt_1.0e-09_0.0158_1"
+file_name= "Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
 

### 2022-08-24 graphs_newt_snakes/Heritability.Rmd
fixed the newt and snake naming

@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+#file=GA3_tall_tall_file
+#cfile=GA3_cor_tall_file 
+ # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
   cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
-
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
@@
 
-for(i in 1:length(unique(file$newt_snake_rep))){
+for(i in 1:length(unique(file$snake_newt_rep))){
 
-  pattern=unique(file$newt_snake_rep)[i]
-  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep ==pattern),]
+  pattern=unique(file$snake_newt_rep)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]
 
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=her_tall_tall_file
+  #file=GA3_tall_tall_file
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 

### 2022-08-24 graphs_newt_snakes/Tall_GA1.Rmd
fixed the newt and snake nameing

@@
   real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  #file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
   unique(file$sim)
@@
   real_snewt_var = var(snewt$dif)
-  cfile$newt_snake_rep <- paste0("Newt_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_Snake_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
+  #cfile$snake_newt_rep <- paste0("Newt_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_Snake_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
   var_cor_table=data.frame()
 
-  for(i in 1:length(unique(file$newt_snake_rep))){
-    pattern<-unique(file$newt_snake_rep)[i]
-    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]
-    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]
+  for(i in 1:length(unique(file$snake_newt_rep))){
+    pattern<-unique(file$snake_newt_rep)[i]
+    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
+    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
 
@@
 four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
-  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
@@
 params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
-params$newt_snake <- paste0(params$newt, "_", params$snake)
+params$snake_newt_rep <- paste0(params$snake, "_", params$newt)
 return(params)
@@
 build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
-  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
+  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
 
@@
 ```
+
 In the later stages of my simulation things have been running for a while and hopefully populations will be in equilibrium.

### 2022-08-24 graphs_newt_snakes/no_interact.Rmd
fixed the newt and snake names

@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
- #file=inter_tall_tall_file
-#cfile=inter_cor_tall_file 
-  #pattern="1.0e-08_0.005_1.0e-09_0.0158_2"
+#file=GA3_tall_tall_file
+#cfile=GA3_cor_tall_file 
+ # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
@@
 params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$snake_newt <- paste0(params$snake, "_", params$newt)
+return(params)
+}
+
+GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+
+build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
+  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+  params<-create_parm_file(file, min_gen, max_gen)
+
+ my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
+
+ if(red_blue==FALSE){
+  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
+  }
+ if(red_blue==TRUE){
+  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
+ }
+
+  return(my_plot)
+}
+
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+
+  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
+    facet_wrap(~sim)+
+    geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
+    ylim(-1.,2.5)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+  return(plot)
+}
+
+whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
+  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
+  xlim((-1*themax)-5, themax+5)+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+}
+
+pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  themin <- min(file$dif) 
+  themax <- max(file$dif)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(dif), fill="aquamarine4")+
+  xlim((-1*true_max)-1, true_max+1)+
+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file=GA3_tall_tall_file
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$newt_deaths)
+  thepopmax <- max(file$newt_deaths)
+  thedifmin <- min(file$snake_deaths) 
+  thedifmax <- max(file$snake_deaths)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
+  #scale_y_continuous(labels = scales::percent)+
+  #xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  #geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+#two_hist_death_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+
+```
+
+```{r, general file and graph making}
+
+#the functions to make the params file and the summary and heatmap figures
+
+create_parm_file <- function(file, min_gen, max_gen){
+params <- data_frame()
+
+for(i in 1:length(unique(file$newt_snake_rep))){
+
+  pattern=unique(file$newt_snake_rep)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep ==pattern),]
+
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=sumitup$snake_mu_rate[1],
+                           newt_mu_rate=sumitup$newt_mu_rate[1],
+                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
+                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
+                           rep=sumitup$rep[1])
+
+  params <- rbind(params, params_temp)
+}
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
 params$newt_snake <- paste0(params$newt, "_", params$snake)
@@
 ```
+
+```{r, time}
+
+min_gen=0
+max_gen=10000
+x_label="generation"
+y_label="time (hours)"
+subt="test"
+title="time test"
+plot <- ggplot(inter_tall_tall_file[ which(inter_tall_tall_file$generation>=min_gen & inter_tall_tall_file$generation<=max_gen),]) +
+    facet_wrap(~sim)+
+    geom_line(aes(generation, time/3600, group=rep), col="grey")+
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    xlab(x_label) + ylab(y_label)+
+    theme_bw()  +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),strip.background = element_blank(), strip.text.x = element_blank())
+
+plot
+
+```

### 2022-08-29 graphs_newt_snakes/GA3.Rmd
I am writing and making my markdown more readable

--- 2022-08-19 graphs_newt_snakes/GA3.Rmd
@@
 
+## Data Colllection
+
+I have created some bash script to run through all the files in my data folders and add some columns and coagulate all of the files into one file per data set.
+In this case, there are three data sets; one for whole population data (lit), one for correlation data (cor), and one for individual grids (grid).
+After these all file is created, I load it into R and finish adding in some comparative columns.
+I also load in my figure creation functions.
+There originally was a problem with naming where I was putting the newt information in first (fixed, but is something to be aware of moving forward).
+
+```{bash, data file gathering}
+#!/usr/bin/env bash
+
+# Run these comands while in The the folder that contains the file you would like to condence
+# Goal is to condence all the text files into one file 
+# Requirements: need to have the same name and need to add additional columns
+thepath=/Users/victoria/Desktop/
+foldername=GA3
+thefolder=${thepath}${foldername}/*
+
+add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"
+
+cor_head_file=$(find ${thepath}${foldername} -name "*_cor_*" | head -n 1)
+cor_head=$(head -n 1 "${cor_head_file}")
+
+grid_head_file=$(find ${thepath}${foldername} -name "*_grid_*" | head -n 1)
+grid_head=$(head -n 1 "${grid_head_file}")
+
+lit_head_file=$(find ${thepath}${foldername} -name "*_lit_*" | head -n 1)
+lit_head=$(head -n 1 "${lit_head_file}")
+
+#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."
+
+if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
+then
+  echo "All cor, lit, and grid files exist!"
+  echo "This program will now end!"
+  exit 0
+fi
+
+#creating the files
+echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
+echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
+echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt
+
+for filename in $thefolder*.text;
+  do 
+#getting the variables 
+#my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
+my_other_type=$(echo ${filename} |sed 's/.*GA520_//; s/_.*//')
+snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
+snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
+newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
+newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
+rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
+#echo ${newt_mu_rate}	
+# echo $my_type
+# echo $my_other_type
+# these new columns adding them to the data
+sed -i '' -e 's/$/,'${rep}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
+#infile >outfile
+if [[ $my_type == "lit" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
+fi
+
+if [[ $my_type == "grid" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
+fi
+
+if [[ $my_other_type == "cor" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
+fi
+
+done
+
+```
+
 ```{r, data gathering}
 
+folder="GA3"
+filelocation=paste0("~/Desktop/",folder)
+
 snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
 
-GA3_tall <- list.files(path="~/Desktop/GA3", pattern="_lit_", full.names=TRUE, recursive=FALSE)
-GA3_tall_cor_files <- list.files(path="~/Desktop/GA3", pattern="_cor_", full.names=TRUE, recursive=FALSE)
-GA3_GA3_grid_tall_files <- list.files(path="~/Desktop/GA3", pattern="_grid_", full.names=TRUE, recursive=FALSE)
-
-GA3_tall_tall_file<- data.frame()
-GA3_cor_tall_file<- data.frame()
-GA3_GA3_grid_tall_file<-data.frame()
-name_list<-c()
-cor_name_list<-c()
-grid_name_list<-c()
-for(i in seq(1, length(GA3_tall)/2, 1)){
-  print(i)
-  #sim
-
-  GA3_temp_file <- read.csv(GA3_tall[i], header = TRUE)
-  GA3_temp_file$rep <- unlist(str_split(unlist(str_split(GA3_tall[i],"rep_"))[3], "_"))[1]
-  GA3_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  name_list<-c(paste0(GA3_temp_file$snake_mu_rate[1], GA3_temp_file$newt_mu_rate[1], GA3_temp_file$snake_mu_effect_sd[1], GA3_temp_file$newt_mu_effect_sd[1]),name_list)
-  GA3_temp_file$sim <- LETTERS[length(unique(name_list))]
-  GA3_tall_tall_file <- rbind(GA3_tall_tall_file, GA3_temp_file)
-  print(GA3_temp_file$sim[1])
-
-  cor_temp_file <- read.csv(GA3_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
-  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
-  GA3_cor_tall_file <- rbind(GA3_cor_tall_file, cor_temp_file)
-  print(cor_temp_file$sim[1])
-
-  GA3_grid_temp_file <- read.csv(GA3_GA3_grid_tall_files[i], header = TRUE)
-  GA3_grid_temp_file$sim <-
-  GA3_grid_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"rep_"))[3], "_"))[1]
-  GA3_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  grid_name_list<-c(paste0(GA3_grid_temp_file$snake_mu_rate[1], GA3_grid_temp_file$newt_mu_rate[1], GA3_grid_temp_file$snake_mu_effect_sd[1], GA3_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
-  GA3_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
-  GA3_GA3_grid_tall_file <- rbind(GA3_GA3_grid_tall_file, GA3_grid_temp_file)
-   print(GA3_grid_temp_file$sim[1])
-
-  }
- ###to set first half 
-GA3_tall_tall_file_p1<- GA3_tall_tall_file
-GA3_cor_tall_file_p1<- GA3_cor_tall_file
-GA3_GA3_grid_tall_file_p1<-GA3_GA3_grid_tall_file
-
-for(i in seq((length(GA3_tall)/2+1), length(GA3_tall), 1)){
-  print(i)
-  #sim
-
-  GA3_temp_file <- read.csv(GA3_tall[i], header = TRUE)
-  GA3_temp_file$rep <- unlist(str_split(unlist(str_split(GA3_tall[i],"rep_"))[3], "_"))[1]
-  GA3_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  name_list<-c(paste0(GA3_temp_file$snake_mu_rate[1], GA3_temp_file$newt_mu_rate[1], GA3_temp_file$snake_mu_effect_sd[1], GA3_temp_file$newt_mu_effect_sd[1]),name_list)
-  GA3_temp_file$sim <- LETTERS[length(unique(name_list))]
-  GA3_tall_tall_file <- rbind(GA3_tall_tall_file, GA3_temp_file)
-  print(GA3_temp_file$sim[1])
-
-  cor_temp_file <- read.csv(GA3_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
-  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
-  GA3_cor_tall_file <- rbind(GA3_cor_tall_file, cor_temp_file)
-  print(cor_temp_file$sim[1])
-
-  GA3_grid_temp_file <- read.csv(GA3_GA3_grid_tall_files[i], header = TRUE)
-  GA3_grid_temp_file$sim <-
-  GA3_grid_temp_file$rep <-unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"rep_"))[3], "_"))[1]
-  GA3_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  GA3_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  GA3_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(GA3_GA3_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  grid_name_list<-c(paste0(GA3_grid_temp_file$snake_mu_rate[1], GA3_grid_temp_file$newt_mu_rate[1], GA3_grid_temp_file$snake_mu_effect_sd[1], GA3_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
-  GA3_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
-  GA3_GA3_grid_tall_file <- rbind(GA3_GA3_grid_tall_file, GA3_grid_temp_file)
-   print(GA3_grid_temp_file$sim[1])
-
-  }
-
- ###to combine second half with first
-GA3_tall_tall_file<- rbind(GA3_tall_tall_file_p1, GA3_tall_tall_file)
-GA3_cor_tall_file<- rbind(GA3_cor_tall_file_p1, GA3_cor_tall_file)
-GA3_GA3_grid_tall_file<-rbind(GA3_GA3_grid_tall_file_p1, GA3_GA3_grid_tall_file)
-
-# making row edits to the dataframe for graphing
+GA3_tall_tall_file<- read.csv(paste0(filelocation, "/all_lit.txt") , header = TRUE)
+
+GA3_tall_tall_file$group_rep <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep)
+
+GA3_tall_tall_file$group <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd)
+
+GA3_tall_tall_file$sim=LETTERS[factor(GA3_tall_tall_file$group)]
 GA3_tall_tall_file$dif <- GA3_tall_tall_file$Snake_mean_Pheno-GA3_tall_tall_file$Newt_mean_Pheno
 
-GA3_tall_tall_file$group_rep <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep)
-
-GA3_tall_tall_file$group <- paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd)
-
+GA3_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
+GA3_cor_tall_file$group_rep <- paste0(GA3_cor_tall_file$snake_mu_rate, "_", GA3_cor_tall_file$snake_mu_effect_sd,"_",GA3_cor_tall_file$newt_mu_rate, "_", GA3_cor_tall_file$newt_mu_effect_sd, "_", GA3_cor_tall_file$rep)
+GA3_cor_tall_file$group <- paste0(GA3_cor_tall_file$snake_mu_rate, "_", GA3_cor_tall_file$snake_mu_effect_sd,"_",GA3_cor_tall_file$newt_mu_rate, "_", GA3_cor_tall_file$newt_mu_effect_sd)
+GA3_cor_tall_file$sim=LETTERS[factor(GA3_cor_tall_file$group)]
+
+GA3_GA3_grid_tall_file<-read.csv(paste0(filelocation,"/all_grid.txt") , header = TRUE)
+GA3_GA3_grid_tall_file$group <- paste0(GA3_GA3_grid_tall_file$snake_mu_rate, "_", GA3_GA3_grid_tall_file$snake_mu_effect_sd,"_",GA3_GA3_grid_tall_file$newt_mu_rate, "_", GA3_GA3_grid_tall_file$newt_mu_effect_sd)
+GA3_GA3_grid_tall_file$group_rep <- paste0(GA3_GA3_grid_tall_file$snake_mu_rate, "_", GA3_GA3_grid_tall_file$snake_mu_effect_sd,"_",GA3_GA3_grid_tall_file$newt_mu_rate, "_", GA3_GA3_grid_tall_file$newt_mu_effect_sd, "_", GA3_GA3_grid_tall_file$rep)
+
+GA3_GA3_grid_tall_file$sim=LETTERS[factor(GA3_GA3_grid_tall_file$group)]
 GA3_GA3_grid_tall_file$snake_newt_rep <- paste0("Snake_",GA3_GA3_grid_tall_file$snake_mu_rate, "_", GA3_GA3_grid_tall_file$snake_mu_effect_sd, "_Newt_",GA3_GA3_grid_tall_file$newt_mu_rate, "_", GA3_GA3_grid_tall_file$newt_mu_effect_sd, "_", GA3_GA3_grid_tall_file$rep)
@@
   real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-  file$newt_snake <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  unique(file$sim)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
@@
 
-## Mean Phenotype Whole Simulation
-
+## Mean Phenotype Whole Simulation {.tabset}
+
+Information to be typed
+
+### Phenotype differences
 ```{r, graphing by gen}
@@
 
+#aggregate(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$dif, list(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
+
+```
+
+### Table of average Differences
+
+```{r, average difference}
 aggregate(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$dif, list(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$group), FUN=mean)
-
-#aggregate(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$dif, list(GA3_tall_tall_file[which(GA3_tall_tall_file$generation>=100 & GA3_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
-
-```
-
-#### Connection between higher phenotype and population
-
+```
+
+## {-}
+
+explanation
+
+## Connection between higher phenotype and population {.tabset}
+
+more info
+
+### Phenotype differences
 ```{r, whale}
@@
 whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+```
+
+### Phenotype & Populationsize differences
+```{r, popsize and pheno}
 
@@
 
-suppressMessages(print(two_hist_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
-
-```
+#suppressMessages(print(two_hist_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+
+```
+
+## {-}
+
+explanation
 
@@
 
-Legend:
-
-- "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
-- "CB" = num_newts_By_num_snakes (Green)
-- "CC" = sum_newt_pheno_By_num_snake (Blue)
-- "CD" = sum_snake_pheno_By_num_newt (Purple)
+Info
 
@@
 
+# Legend: Not needed currently
+# 
+# - "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
+# - "CB" = num_newts_By_num_snakes (Green)
+# - "CC" = sum_newt_pheno_By_num_snake (Blue)
+# - "CD" = sum_snake_pheno_By_num_newt (Purple)
+
 ginmin = 10000
@@
 
-four_types_boxplot_cors_by_gen(GA3_cor_tall_file, "Simulation four Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-```
-
+#four_types_boxplot_cors_by_gen(GA3_cor_tall_file, "Simulation four Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+Explanation
+
+## Correlation Histograms {.tabset}
+
+what did I do and why Time slices to see general trends
+
+### Plot 1
 ```{r, GA3 cor by dif windows}
-
 ginmin = 0
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+```
+
+### Plot 2
+
+```{r, GA3 cor by dif windows 2}
 ginmin = 5000
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+```
+
+### Plot 3
+```{r, GA3 cor by dif windows 3}
 ginmin = 10000
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+```
+
+### Plot 4
+```{r, GA3 cor by dif windows 4}
 ginmin = 15000
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+```
+
+### Plot 5
+```{r, GA3 cor by dif windows 5}
 ginmin = 20000
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+```
+
+### Plot 6
+```{r, GA3 cor by dif windows 6}
 ginmin = 25000
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+```
+
+### Plot 7
+```{r, GA3 cor by dif windows 7}
 ginmin = 30000
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+```
+
+### Plot 8
+```{r, GA3 cor by dif windows 8}
 ginmin = 35000
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+```
+
+### Plot 9
+```{r, GA3 cor by dif windows 9}
 ginmin = 40000
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+```
+
+### Plot 10
+```{r, GA3 cor by dif windows 10}
 ginmin = 45000
@@
 suppressMessages(print(hist_cors_by_gen_col_rep(GA3_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA3", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-```
-
-## Correlation across time
-
+```
+
+## {-}
+
+What does it mean?
+
+## Correlation across time {.tabset}
+
+All of the correlations across time look very similar.
+Generally, mean newt and snake phenotypes (red and blue) go up overtime while the local correlation between the two fluctuates.
+Sometime one mean phenotype stays flat.
+The local correlations range from being very positive to being very negative.
+How can the correlation start to suddenly go up and then fall?
+It is hard to notice any differences between the GA combinations.
+For space I have chosen 3 random figures.
+
+### Random 1
 ```{r, GA3 cor and pheno, results="hide"}
@@
 
-for(i in 1:length(GA3_pattern)){
-  myine<-cor_trends_by_gen(GA3_tall_tall_file, GA3_cor_tall_file, "test", "GA3", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA3_pattern[i])
-  plot(myine)
-}
-
-```
-
-## What happens over time (looking at the beginning. middle, and late part of my simulations)
+myrandomlist=sample.int(length(GA3_pattern), 3)
+
+# for(i in myrandomlist){
+#   myine<-cor_trends_by_gen(GA3_tall_tall_file, GA3_cor_tall_file, "test", "GA3", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA3_pattern[i])
+#   plot(myine)
+# }
+
+cor_trends_by_gen(GA3_tall_tall_file, GA3_cor_tall_file, "test", "GA3", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA3_pattern[myrandomlist[1]])
+
+```
+
+### Random 2
+```{r, random cor-pheno plot 2}
+
+cor_trends_by_gen(GA3_tall_tall_file, GA3_cor_tall_file, "test", "GA3", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA3_pattern[myrandomlist[2]])
+```
+
+### Random 3
+```{r, random cor-pheno plot 3}
+
+cor_trends_by_gen(GA3_tall_tall_file, GA3_cor_tall_file, "test", "GA3", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA3_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+Explain general figures
+
+## What happens over time (looking at the beginning. middle, and late part of my simulations) {.tabset}
+
+### Pheno Beginning
 
@@
 
-for(i in 1:length(unique(GA3_tall_tall_file$rep))){
-  myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
-  plot(myine)
-  myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
-  suppressMessages(plot(myine))
-}
-
-```
-
-#### Summary
-
-```{r, early plots summary}
+# for(i in 1:length(unique(GA3_tall_tall_file$rep))){
+#   myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[1])
+```
+
+### Pheno Middle
+
+```{r, middle plots}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(GA3_tall_tall_file$rep))){
+#   myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[1])
+```
+
+### Pheno End
+
+```{r, end plots}
+
+min_gen=45000
+max_gen=50000
+
+# for(i in 1:length(unique(GA3_tall_tall_file$rep))){
+#   myine<-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[1])
+```
+
+### Dif Beginning 
+```{r, early plots 1a}
 
@@
 
+# for(i in 1:length(unique(GA3_tall_tall_file$rep))){
+#   myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[1] )
+
+```
+
+### Dif Middle 
+```{r, early plots 2a}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(GA3_tall_tall_file$rep))){
+#   myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[1] )
+
+```
+
+### Dif End 
+```{r, early plots 3a}
+
+min_gen=45000
+max_gen=50000
+
+# for(i in 1:length(unique(GA3_tall_tall_file$rep))){
+#   myine<-two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA3_tall_tall_file$rep)[1] )
+
+```
+
+## {-}
+
+## Summary {.tabset}
+
+Describe
+
+### Early-Sim Population Size Summary
+
+```{r, early plots summary}
+
+min_gen=100
+max_gen=5000
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Mid-Sim Population Size Summary
+```{r, plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+
 # summary
 GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-min_gen=10000
-max_gen=15000
+```
+
+### Late-Sim Population Size Summary
+```{r, plots summary 3}
+min_gen=45000
+max_gen=50000
 
@@
 
+```
+
+### Early Difference Summary
+```{r, dif plots summary 1}
+
+min_gen=100
+max_gen=5000
+
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+### Mid Difference Summary
+```{r, dif plots summary 2}
+min_gen=25000
+max_gen=30000
+
+GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
 min_gen=45000
 max_gen=50000
-
-# summary
-GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-min_gen=100
-max_gen=5000
-
+```
+
+### Late Difference Summary
+```{r, dif plots summary 3}
 GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
-min_gen=10000
-max_gen=15000
-
-GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-min_gen=45000
-max_gen=50000
-
-GA_summary(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-```
+```
+
+## {-}
+
+Explain
+
+## Heatmap {.tabset}
+
+What should I be focusing on here?
+
+### Population Size (Early)
 
@@
 build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-min_gen=10000
-max_gen=15000
+```
+
+### Population Size (Mid)  
+```{r, early plots Heatmap 2}
+min_gen=25000
+max_gen=30000
 #heatmap
@@
 
+```
+
+### Population Size (Late) 
+```{r, early plots Heatmap 3}
 min_gen=45000
@@
 build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
+```
+
+### Phenotype (Early) 
+```{r, early plots Heatmap pheno 1}
 min_gen=100
@@
 build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-min_gen=10000
-max_gen=15000
+```
+
+### Phenotype (Mid) 
+```{r, early plots Heatmap pheno 2}
+
+min_gen=25000
+max_gen=30000
 #heatmap
@@
 build_heatmap(GA3_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
+```
+
+### Phenotype (Late) 
+```{r, early plots Heatmap pheno 3}
 min_gen=45000
@@
 
+## {-}
+
+Explanations
+
 ## What is up with the correlations
 
-### file
+Need to add tabs to show the mean, max, min, and population size. #3 high + cor, 0 cor, -cor
 
@@
 
-file_name= "Snake_1.0e-10_0.05_Newt_1.0e-09_0.0158_1"
+file_name= "Snake_1e-10_0.05_Newt_1e-09_0.0158_0"
 

### 2022-08-29 graphs_newt_snakes/Heritability.Rmd
I am writing and making my markdown more readable

@@
 
+```{bash, data file gathering}
+#!/usr/bin/env bash
+
+# Run these comands while in The the folder that contains the file you would like to condence
+# Goal is to condence all the text files into one file 
+# Requirements: need to have the same name and need to add additional columns
+thepath=/Users/victoria/Desktop/
+foldername=no_hair
+thefolder=${thepath}${foldername}/*
+
+add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"
+
+cor_head_file=$(find ${thepath}${foldername} -name "*_cor_*" | head -n 1)
+cor_head=$(head -n 1 "${cor_head_file}")
+
+grid_head_file=$(find ${thepath}${foldername} -name "*_grid_*" | head -n 1)
+grid_head=$(head -n 1 "${grid_head_file}")
+
+lit_head_file=$(find ${thepath}${foldername} -name "*_lit_*" | head -n 1)
+lit_head=$(head -n 1 "${lit_head_file}")
+
+#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."
+
+if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
+then
+  echo "All cor, lit, and grid files exist!"
+  echo "This program will now end!"
+  exit 0
+fi
+
+#creating the files
+echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
+echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
+echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt
+
+for filename in $thefolder*.text;
+  do 
+#getting the variables 
+my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
+snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
+snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
+newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
+newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
+rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
+#echo ${newt_mu_rate}	
+# echo $my_type
+# echo $my_other_type
+# these new columns adding them to the data
+sed -i '' -e 's/$/,'${rep}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
+#infile >outfile
+if [[ $my_type == "lit" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
+fi
+
+if [[ $my_type == "grid" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
+fi
+
+if [[ $my_type == "cor" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
+fi
+
+done
+
+```
+
 ```{r, data gathering}
@@
 
-her_tall <- list.files(path="~/Desktop/no_hair", pattern="_lit_", full.names=TRUE, recursive=FALSE)
-her_tall_cor_files <- list.files(path="~/Desktop/no_hair", pattern="_cor_", full.names=TRUE, recursive=FALSE)
-her_her_grid_tall_files <- list.files(path="~/Desktop/no_hair", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+folder="no_hair"
+filelocation=paste0("~/Desktop/",folder)
 
-her_tall_tall_file<- data.frame()
-her_cor_tall_file<- data.frame()
-her_her_grid_tall_file<-data.frame()
-name_list<-c()
-cor_name_list<-c()
-grid_name_list<-c()
-for(i in seq(1, length(her_tall), 1)){
-  print(i)
-  #sim
-
-  her_temp_file <- read.csv(her_tall[i], header = TRUE)
-  her_temp_file$rep <- unlist(str_split(unlist(str_split(her_tall[i],"rep_"))[3], "_"))[1]
-  her_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  her_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  her_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  her_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  name_list<-c(paste0(her_temp_file$snake_mu_rate[1], her_temp_file$newt_mu_rate[1], her_temp_file$snake_mu_effect_sd[1], her_temp_file$newt_mu_effect_sd[1]),name_list)
-  her_temp_file$sim <- LETTERS[length(unique(name_list))]
-  her_tall_tall_file <- rbind(her_tall_tall_file, her_temp_file)
-  print(her_temp_file$sim[1])
-
-  cor_temp_file <- read.csv(her_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(her_tall_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
-  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
-  her_cor_tall_file <- rbind(her_cor_tall_file, cor_temp_file)
-  print(cor_temp_file$sim[1])
-
-  her_grid_temp_file <- read.csv(her_her_grid_tall_files[i], header = TRUE)
-  her_grid_temp_file$sim <-
-  her_grid_temp_file$rep <-unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"rep_"))[3], "_"))[1]
-  her_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  her_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  her_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  her_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  grid_name_list<-c(paste0(her_grid_temp_file$snake_mu_rate[1], her_grid_temp_file$newt_mu_rate[1], her_grid_temp_file$snake_mu_effect_sd[1], her_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
-  her_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
-  her_her_grid_tall_file <- rbind(her_her_grid_tall_file, her_grid_temp_file)
-   print(her_grid_temp_file$sim[1])
-
-  }
-
-her_tall_tall_file$dif <- her_tall_tall_file$Snake_mean_Pheno-her_tall_tall_file$Newt_mean_Pheno
+her_tall_tall_file<- read.csv(paste0(filelocation, "/all_lit.txt") , header = TRUE)
 
@@
 
+her_tall_tall_file$sim=LETTERS[factor(her_tall_tall_file$group)]
+her_tall_tall_file$dif <- her_tall_tall_file$Snake_mean_Pheno-her_tall_tall_file$Newt_mean_Pheno
+
+her_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
+her_cor_tall_file$group_rep <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd, "_", her_cor_tall_file$rep)
+her_cor_tall_file$group <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd)
+her_cor_tall_file$sim=LETTERS[factor(her_cor_tall_file$group)]
+
+her_her_grid_tall_file<-read.csv(paste0(filelocation,"/all_grid.txt") , header = TRUE)
+her_her_grid_tall_file$group <- paste0(her_her_grid_tall_file$snake_mu_rate, "_", her_her_grid_tall_file$snake_mu_effect_sd,"_",her_her_grid_tall_file$newt_mu_rate, "_", her_her_grid_tall_file$newt_mu_effect_sd)
+her_her_grid_tall_file$group_rep <- paste0(her_her_grid_tall_file$snake_mu_rate, "_", her_her_grid_tall_file$snake_mu_effect_sd,"_",her_her_grid_tall_file$newt_mu_rate, "_", her_her_grid_tall_file$newt_mu_effect_sd, "_", her_her_grid_tall_file$rep)
+
+her_her_grid_tall_file$sim=LETTERS[factor(her_her_grid_tall_file$group)]
 her_her_grid_tall_file$snake_newt_rep <- paste0("Snake_",her_her_grid_tall_file$snake_mu_rate, "_", her_her_grid_tall_file$snake_mu_effect_sd, "_Newt_",her_her_grid_tall_file$newt_mu_rate, "_", her_her_grid_tall_file$newt_mu_effect_sd, "_", her_her_grid_tall_file$rep)
@@
 #cfile=GA3_cor_tall_file 
- # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
+ # pattern="1e-10_0.05_1e-08_0.005_3"
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
@@
 
-file_name= "Snake_1.0e-11_5.0_Newt_1.0e-11_5.0_0"
-#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+file_name= "Snake_1e-11_5_Newt_1e-11_5_0"
+#Snake_1e-09_0.05_Newt_1e-09_0.05_2
+#Snake_1e-08_0.005_Newt_1e-11_0.158_0
 

### 2022-08-29 graphs_newt_snakes/corcompare.Rmd
I am writing and making my markdown more readable

---
title: "Cor Compare"
output: html_document
date: '2022-08-26'
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library("reshape")

```

## Corilation Compare!

I have run four separate experiments and now I will compare their different correlations to see if I can tell the difference between each of the four experiments.

Experiments:

- tall map with 5 sections
- tall map with 7 sections
- tall map with 5 sections no heritability
- tall map with 5 sections no interaction

I am investigating the correlation calculations. I predicted that though co-evolution (interaction & evolution) species' phenotypes would become spatially correlated. I saw some very high correlations (around 0.5) in some of these simulations. To see if there is a difference between the correlations in my experiment I will create some comparative histograms.

Predictions:

-  5 sections & 7 sections will have *similar* correlation distributions
- no heritability & no interaction correlation distributions will look *very different* from 5 sections & 7 sections

```{r, loading in the data}

GA1_cor_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor.txt" , header = TRUE)
GA1_cor_tall_file$group_rep <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd, "_", GA1_cor_tall_file$rep)
GA1_cor_tall_file$group <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd)
GA1_cor_tall_file$sim=LETTERS[factor(GA1_cor_tall_file$group)]
GA1_cor_tall_file$experiment = "A"

GA1_cor_tall_7_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor_7.txt" , header = TRUE)
GA1_cor_tall_7_file$group_rep <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd, "_", GA1_cor_tall_7_file$rep)
GA1_cor_tall_7_file$group <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd)
GA1_cor_tall_7_file$sim=LETTERS[factor(GA1_cor_tall_7_file$group)]
GA1_cor_tall_7_file$experiment = "B"

her_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
her_cor_tall_file$group_rep <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd, "_", her_cor_tall_file$rep)
her_cor_tall_file$group <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd)
her_cor_tall_file$sim=LETTERS[factor(her_cor_tall_file$group)]
her_cor_tall_file$experiment = "C"

inter_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
inter_cor_tall_file$group_rep <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd, "_", inter_cor_tall_file$rep)
inter_cor_tall_file$group <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd)
inter_cor_tall_file$sim=LETTERS[factor(inter_cor_tall_file$group)]
inter_cor_tall_file$experiment = "D"

all_cor_exp = rbind(GA1_cor_tall_file, GA1_cor_tall_7_file, her_cor_tall_file, inter_cor_tall_file)

```

```{r, making the fig}

hist_cors_by_gen_col_all_exp_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity")+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                    strip.background = element_blank(), strip.text.x = element_blank(),
                   title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                    axis.title.y = element_blank())

  return(plot)
}

dens_cors_by_gen_col_all_exp_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity")+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                    strip.background = element_blank(), strip.text.x = element_blank(),
                   title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                    axis.title.y = element_blank())

  return(plot)
}
```

```{r, cor com figs}

ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

```

```{r, density com figs}

ginmin = 0
ginmax = 5000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 5000
ginmax = 10000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 10000
ginmax = 15000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 15000
ginmax = 20000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 20000
ginmax = 25000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 25000
ginmax = 30000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 30000
ginmax = 35000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 35000
ginmax = 40000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 40000
ginmax = 45000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 45000
ginmax = 50000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

```

```{r, one big one}

ginmin = 0
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

```

# next step is to count the high and the lows 
like make a lower limit like must be above 0.3

### 2022-08-29 graphs_newt_snakes/no_interact.Rmd
I am writing and making my markdown more readable

@@
 
-In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-interitable trait. I expect to see no spatial phenotype correlation
+In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-interactible trait. I expect to see no spatial phenotype correlation
 
@@
 
-```{r, data gatintering}
+```{bash, data file gathering}
+#!/usr/bin/env bash
+
+# Run these comands while in The the folder that contains the file you would like to condence
+# Goal is to condence all the text files into one file 
+# Requirements: need to have the same name and need to add additional columns
+thepath=/Users/victoria/Desktop/
+foldername=no_interaction
+thefolder=${thepath}${foldername}/*
+
+add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"
+
+cor_head_file=$(find ${thepath}${foldername} -name "*_cor_*" | head -n 1)
+cor_head=$(head -n 1 "${cor_head_file}")
+
+grid_head_file=$(find ${thepath}${foldername} -name "*_grid_*" | head -n 1)
+grid_head=$(head -n 1 "${grid_head_file}")
+
+lit_head_file=$(find ${thepath}${foldername} -name "*_lit_*" | head -n 1)
+lit_head=$(head -n 1 "${lit_head_file}")
+
+#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."
+
+if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
+then
+  echo "All cor, lit, and grid files exist!"
+  echo "This program will now end!"
+  exit 0
+fi
+
+#creating the files
+echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
+echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
+echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt
+
+for filename in $thefolder*.text;
+  do 
+#getting the variables 
+my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
+snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
+snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
+newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
+newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
+rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
+#echo ${newt_mu_rate}	
+# echo $my_type
+# echo $my_other_type
+# these new columns adding them to the data
+sed -i '' -e 's/$/,'${rep}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
+#infile >outfile
+if [[ $my_type == "lit" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
+fi
+
+if [[ $my_type == "grid" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
+fi
+
+if [[ $my_type == "cor" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
+fi
+
+done
+
+```
+
+```{r, data gathering}
 
@@
 
-inter_tall <- list.files(path="~/Desktop/no_interaction", pattern="_lit_", full.names=TRUE, recursive=FALSE)
-inter_tall_cor_files <- list.files(path="~/Desktop/no_interaction", pattern="_cor_", full.names=TRUE, recursive=FALSE)
-inter_inter_grid_tall_files <- list.files(path="~/Desktop/no_interaction", pattern="_grid_", full.names=TRUE, recursive=FALSE)
-
-inter_tall_tall_file<- data.frame()
-inter_cor_tall_file<- data.frame()
-inter_inter_grid_tall_file<-data.frame()
-name_list<-c()
-cor_name_list<-c()
-grid_name_list<-c()
-for(i in seq(1, length(inter_tall), 1)){
-  print(i)
-  #sim
-
-  inter_temp_file <- read.csv(inter_tall[i], header = TRUE)
-  inter_temp_file$rep <- unlist(str_split(unlist(str_split(inter_tall[i],"rep_"))[2], "_"))[1]
-  inter_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  inter_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(inter_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  inter_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  inter_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  name_list<-c(paste0(inter_temp_file$snake_mu_rate[1], inter_temp_file$newt_mu_rate[1], inter_temp_file$snake_mu_effect_sd[1], inter_temp_file$newt_mu_effect_sd[1]),name_list)
-  inter_temp_file$sim <- LETTERS[length(unique(name_list))]
-  inter_tall_tall_file <- rbind(inter_tall_tall_file, inter_temp_file)
-  print(inter_temp_file$sim[1])
-
-  cor_temp_file <- read.csv(inter_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"rep_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
-  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
-  inter_cor_tall_file <- rbind(inter_cor_tall_file, cor_temp_file)
-  print(cor_temp_file$sim[1])
-
-  inter_grid_temp_file <- read.csv(inter_inter_grid_tall_files[i], header = TRUE)
-  inter_grid_temp_file$sim <-
-  inter_grid_temp_file$rep <-unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"rep_"))[2], "_"))[1]
-  inter_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  inter_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  inter_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  inter_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  grid_name_list<-c(paste0(inter_grid_temp_file$snake_mu_rate[1], inter_grid_temp_file$newt_mu_rate[1], inter_grid_temp_file$snake_mu_effect_sd[1], inter_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
-  inter_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
-  inter_inter_grid_tall_file <- rbind(inter_inter_grid_tall_file, inter_grid_temp_file)
-   print(inter_grid_temp_file$sim[1])
-
-  }
-
+folder="no_interaction"
+filelocation=paste0("~/Desktop/",folder)
+
+inter_tall_tall_file<- read.csv(paste0(filelocation, "/all_lit.txt") , header = TRUE)
+
+inter_tall_tall_file$group_rep <- paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd, "_", inter_tall_tall_file$rep)
+
+inter_tall_tall_file$group <- paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd)
+
+inter_tall_tall_file$sim=LETTERS[factor(inter_tall_tall_file$group)]
 inter_tall_tall_file$dif <- inter_tall_tall_file$Snake_mean_Pheno-inter_tall_tall_file$Newt_mean_Pheno
 
-inter_tall_tall_file$group_rep <- paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd, "_", inter_tall_tall_file$rep)
-
-inter_tall_tall_file$group <- paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd)
-
+inter_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
+inter_cor_tall_file$group_rep <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd, "_", inter_cor_tall_file$rep)
+inter_cor_tall_file$group <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd)
+inter_cor_tall_file$sim=LETTERS[factor(inter_cor_tall_file$group)]
+
+inter_inter_grid_tall_file<-read.csv(paste0(filelocation,"/all_grid.txt") , header = TRUE)
+inter_inter_grid_tall_file$group <- paste0(inter_inter_grid_tall_file$snake_mu_rate, "_", inter_inter_grid_tall_file$snake_mu_effect_sd,"_",inter_inter_grid_tall_file$newt_mu_rate, "_", inter_inter_grid_tall_file$newt_mu_effect_sd)
+inter_inter_grid_tall_file$group_rep <- paste0(inter_inter_grid_tall_file$snake_mu_rate, "_", inter_inter_grid_tall_file$snake_mu_effect_sd,"_",inter_inter_grid_tall_file$newt_mu_rate, "_", inter_inter_grid_tall_file$newt_mu_effect_sd, "_", inter_inter_grid_tall_file$rep)
+
+inter_inter_grid_tall_file$sim=LETTERS[factor(inter_inter_grid_tall_file$group)]
 inter_inter_grid_tall_file$snake_newt_rep <- paste0("Snake_",inter_inter_grid_tall_file$snake_mu_rate, "_", inter_inter_grid_tall_file$snake_mu_effect_sd, "_Newt_",inter_inter_grid_tall_file$newt_mu_rate, "_", inter_inter_grid_tall_file$newt_mu_effect_sd, "_", inter_inter_grid_tall_file$rep)
@@
 
-file_name= "Snake_1.0e-11_5.0_Newt_1.0e-11_5.0_0"
+file_name= "Snake_1e-11_5_Newt_1e-11_5_0"
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
@@
 
-file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3"
+file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0

### 2022-08-31 graphs_newt_snakes/GA1_tall_redo_md.Rmd
made a realy nice markdown-html (GA3). Also fixed up the last bit of confusion with the newt_snake snake_newt by making the facetwrap use sim which is what I use for everything else.

---
title: "GA1 redo"
output: html_document
date: '2022-08-01'
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
library(stringr)
library(patchwork)
```

## Goal:

Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to. This markdown is investigation what is up with the different levels of correlation between rectangles and squares. After fixing the row vs column error I looked at the correlation data and found that there was less correlation. So I decided to investigate why that might be and run a few more experiments. I am running an experiment to test how changing the square size might impact the calculations. I also plan on changing the interaction rate (but want to look at the math/ feasibility of it). This file contains results discussed in Tall_GA1!

### Questions:

What does it mean to be correlated?

## Background

I investigated the correlations between snake and newt phenotypes at the local grid locations along with population level phenotype. I found there was a lot of correlation when populations slowly adapt! However, after a closer investigation I found that these correlations were from a rectangle shaped area and not a square one. Here, I rerun the experiment with he correct square grids and discuss how the results differ. I also aim to investigate how changing the area/shape of the grids will influence correlation results. I am also thinking of ways to gather and incorperate allele information.

## Experiment

I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction with different genetic architectures (GAs) in a spatial setting. I hypothesized that we would see an interaction (co-evolutionary arms race) between newt and snake phenotype under some GA combinations when newts and snakes were evolving over geographical space. Each GA is paired with another GA creating 16 combinations.

GA1 experiment values:

- 1e-8*(0.005)^2 = 2.5e-13
- 1e-9*(0.05)^2 = 2.5e-12
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(5.0)^2 = 2.5e-10

Landscape: 20 by 5 grid. A tall map!: 35*4 H, 35 W 
New Landscape 28 by 7 grid: 35*4 H, 35 W

### The data

I gather text file data from different files and have to do some table wrangling to get it into a format I can graph. I use information gathered from the entire population; data containing a mean value for the entire map (lit), correlation data based off of local populations that were divided into grids (cor) and data collected from grid based populations (grid). These simulations have a msprime (coalescent/burn in/random genetic variation) and then run for 50,000 generations in SLiM (co-evolution) (all with the same GA values). I run 4 trials for every GA combination and try two different grid sizes 20 by 5 (large) and 24 by 7 (small) in SLiM. These slim simulations use the same msprime simulation, but can statistically be different.

```{bash, data file gathering}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=GA1_tall_redo
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA520_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

cor_head_file_7=$(find ${thepath}${foldername} -name "*_GA728_cor_*" | head -n 1)
cor_head_7=$(head -n 1 "${cor_head_file_7}")

grid_head_file_7=$(find ${thepath}${foldername} -name "*_GA287_grid_*" | head -n 1)
grid_head_7=$(head -n 1 "${grid_head_file_7}")

lit_head_file_7=$(find ${thepath}${foldername} -name "*_GA287_lit_*" | head -n 1)
lit_head_7=$(head -n 1 "${lit_head_file_7}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt
echo ${lit_head_7}${add_in_column} > ${thepath}${foldername}/all_lit_7.txt
echo ${grid_head_7}${add_in_column} > ${thepath}${foldername}/all_grid_7.txt
echo ${cor_head_7}${add_in_column} > ${thepath}${foldername}/all_cor_7.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
my_other_type=$(echo ${filename} |sed 's/.*GA520_//; s/_.*//')
my_type_2=$(echo ${filename} |sed 's/.*GA287_//; s/_.*//') #testing a second grid system
my_other_type_2=$(echo ${filename} |sed 's/.*GA728_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_other_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

if [[ $my_type_2 == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit_7.txt
fi

if [[ $my_type_2 == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid_7.txt
fi

if [[ $my_other_type_2 == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor_7.txt
fi
done

```

```{r, data gathering}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

GA1_tall_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_lit.txt" , header = TRUE)

GA1_tall_tall_file$group_rep <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep)

GA1_tall_tall_file$group <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd)

GA1_tall_tall_file$sim=LETTERS[factor(GA1_tall_tall_file$group)]
GA1_tall_tall_file$dif <- GA1_tall_tall_file$Snake_mean_Pheno-GA1_tall_tall_file$Newt_mean_Pheno

GA1_cor_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor.txt" , header = TRUE)
GA1_cor_tall_file$group_rep <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd, "_", GA1_cor_tall_file$rep)
GA1_cor_tall_file$group <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd)
GA1_cor_tall_file$sim=LETTERS[factor(GA1_cor_tall_file$group)]

GA1_grid_tall_file<-read.csv("~/Desktop/GA1_tall_redo/all_grid.txt" , header = TRUE)
GA1_grid_tall_file$group <- paste0(GA1_grid_tall_file$snake_mu_rate, "_", GA1_grid_tall_file$snake_mu_effect_sd,"_",GA1_grid_tall_file$newt_mu_rate, "_", GA1_grid_tall_file$newt_mu_effect_sd)
GA1_grid_tall_file$group_rep <- paste0(GA1_grid_tall_file$snake_mu_rate, "_", GA1_grid_tall_file$snake_mu_effect_sd,"_",GA1_grid_tall_file$newt_mu_rate, "_", GA1_grid_tall_file$newt_mu_effect_sd, "_", GA1_grid_tall_file$rep)

GA1_grid_tall_file$sim=LETTERS[factor(GA1_grid_tall_file$group)]
GA1_grid_tall_file$snake_newt_rep <- paste0("Snake_",GA1_grid_tall_file$snake_mu_rate, "_", GA1_grid_tall_file$snake_mu_effect_sd, "_Newt_",GA1_grid_tall_file$newt_mu_rate, "_", GA1_grid_tall_file$newt_mu_effect_sd, "_", GA1_grid_tall_file$rep)

GA1_tall_tall_7_file<- read.csv("~/Desktop/GA1_tall_redo/all_lit_7.txt" , header = TRUE)

GA1_tall_tall_7_file$group_rep <- paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd, "_", GA1_tall_tall_7_file$rep)

GA1_tall_tall_7_file$group <- paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd)

GA1_tall_tall_7_file$sim=LETTERS[factor(GA1_tall_tall_7_file$group)]
GA1_tall_tall_7_file$dif <- GA1_tall_tall_7_file$Snake_mean_Pheno-GA1_tall_tall_7_file$Newt_mean_Pheno

GA1_cor_tall_7_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor_7.txt" , header = TRUE)
GA1_cor_tall_7_file$group_rep <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd, "_", GA1_cor_tall_7_file$rep)
GA1_cor_tall_7_file$group <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd)
GA1_cor_tall_7_file$sim=LETTERS[factor(GA1_cor_tall_7_file$group)]

GA1_grid_tall_7_file<-read.csv("~/Desktop/GA1_tall_redo/all_grid_7.txt" , header = TRUE)
GA1_grid_tall_7_file$group <- paste0(GA1_grid_tall_7_file$snake_mu_rate, "_", GA1_grid_tall_7_file$snake_mu_effect_sd,"_",GA1_grid_tall_7_file$newt_mu_rate, "_", GA1_grid_tall_7_file$newt_mu_effect_sd)
GA1_grid_tall_7_file$group_rep <- paste0(GA1_grid_tall_7_file$snake_mu_rate, "_", GA1_grid_tall_7_file$snake_mu_effect_sd,"_",GA1_grid_tall_7_file$newt_mu_rate, "_", GA1_grid_tall_7_file$newt_mu_effect_sd, "_", GA1_grid_tall_7_file$rep)

GA1_grid_tall_7_file$sim=LETTERS[factor(GA1_grid_tall_7_file$group)]
GA1_grid_tall_7_file$snake_newt_rep <- paste0("Snake_",GA1_grid_tall_7_file$snake_mu_rate, "_", GA1_grid_tall_7_file$snake_mu_effect_sd, "_Newt_",GA1_grid_tall_7_file$newt_mu_rate, "_", GA1_grid_tall_7_file$newt_mu_effect_sd, "_", GA1_grid_tall_7_file$rep)

```

```{r, cor box set up}

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

suppressMessages(print(plot))

  return(plot)
}

var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  real_snewt_var = var(snewt$dif)
  var_cor_table=data.frame()

  for(i in 1:length(unique(file$snake_newt_rep))){
    pattern<-unique(file$snake_newt_rep)[i]
    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]

    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  }

  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)

  plot <- ggplot(var_cor_table) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

  return(plot)
}

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=GA1_tall_tall_file
#cfile=GA1_cor_tall_file 
 # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]

  if(nrow(cfile)>nrow(file)){
    toDelete <- seq(0, nrow(cfile), 2)
    cfile_short <-  cfile[-toDelete, ]
  }else{
    cfile_short <-  cfile
  }

  if(nrow(cfile_short)>nrow(file)){
      toDelete <- seq(0, nrow(cfile_short), 2)
      cfile_short <-  cfile_short[-toDelete, ]
    }
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}

four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

```

```{r, general file and graph making}

#the functions to make the params file and the summary and heatmap figures

create_parm_file <- function(file, min_gen, max_gen){
params <- data_frame()

for(i in 1:length(unique(file$snake_newt_rep))){

  pattern=unique(file$snake_newt_rep)[i]
  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]

  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=sumitup$snake_mu_rate[1],
                           newt_mu_rate=sumitup$newt_mu_rate[1],
                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
                           rep=sumitup$rep[1])

  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$snake_newt <- paste0(params$snake, "_", params$newt)
return(params)
}

GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}

build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
  params<-create_parm_file(file, min_gen, max_gen)

 my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))

 if(red_blue==FALSE){
  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
  }
 if(red_blue==TRUE){
  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
 }

  return(my_plot)
}

trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){

  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
  return(plot)
}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
  xlim((-1*themax)-5, themax+5)+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)
}

pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  themin <- min(file$dif) 
  themax <- max(file$dif)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(dif), fill="aquamarine4")+
  xlim((-1*true_max)-1, true_max+1)+

  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]

  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])

dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file=GA1_tall_tall_file
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]

  thepopmin <- min(file$newt_deaths)
  thepopmax <- max(file$newt_deaths)
  thedifmin <- min(file$snake_deaths) 
  thedifmax <- max(file$snake_deaths)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])

dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
  #scale_y_continuous(labels = scales::percent)+
  #xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  #geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

#two_hist_death_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)

```

## Mean Phenotype Whole Simulation

First, I will look at a plot of how the mean phenotype of the entire population of newts and snakes changes overtime. Each of these plots has three colored lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype. There are 4 line per color that represent the different replicas that I ran. **Note this is a mean for the entire population.** Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).

```{r, graphing by gen}
trends_by_gen(GA1_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)

aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group), FUN=mean)

aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)

trends_by_gen(GA1_tall_tall_7_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)

aggregate(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$dif, list(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$group), FUN=mean)

aggregate(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$dif, list(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$group_rep), FUN=mean)

```

#### Connection between higher phenotype and population

```{r, whale}
min_gen=5000
max_gen=10000
rep=0

whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )

suppressMessages(print(two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))

whale_gen(GA1_tall_tall_7_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )

suppressMessages(print(two_hist_all_rep(GA1_tall_tall_7_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))

```

I looked at the results between 5,000 - 10,000 generations where I saw most of the increase in newt and snake phenotype. The first plot has newt population size by snake population size with the color representing the difference between snake and newt mean phenotype (red=newts have a higher mean phenotype, blue=snakes have a higher mean phenotype). The third GA (an intermediate one) seems to do better then all of the other GAs (blue row (3), red column (3)). However, this is dependent on the point in the simulation you focus on. The next two plots show the difference between snake and newt population size (green) and phenotype (purple). For the most part these suggest that when the mean phenotype is higher so is the population size. This also shows the asymmetrical nature between the predator-prey interaction (higher max population sizes seen in snakes). The population size is also more variable than the phenotype (difference in population size has a wider range).

## Correlation

The next section I aim to look at how correlated newt and snakes are at local populations across the geographical area. I am examining correlation between newt and snake phenotypes, population sizes of newts and snakes, amount of toxin and snake population, and the amount of resistance and newt population size. I predicted that there would be a positive correlation between the phenotypes, and a negative correlation between population sizes, and the amount of toxin/resistance and population size. Below is a legend for the first two plots. The third plot is colored by trial.

Legend:

- "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
- "CB" = num_newts_By_num_snakes (Green)
- "CC" = sum_newt_pheno_By_num_snake (Blue)
- "CD" = sum_snake_pheno_By_num_newt (Purple)

I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations. The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s). The second figure shows the the results of all 4 trials for each correlation measurement I made from 10,000-15,000 generations. The third plot takes the information from the fist plot and shows the distribution of correlation values by each trial (solid line at 0, dashed line at real newt-snake correlation).

```{r, combo myplots}
#files
#GA1_tall_tall_file
#GA2_long_file 
#GA1_cor_tall_file
#GA2_cor_file

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

four_types_boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

boxplot_cors_by_gen(GA1_cor_tall_7_file, "Simulation Correlation 7 Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

four_types_boxplot_cors_by_gen(GA1_cor_tall_7_file, "Simulation four Correlation 7", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation 7 Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

```

## Results {.tabset}

### Plot 1
```{r, ga1 cor by dif windows}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, ga1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, ga1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, ga1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, ga1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, ga1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, ga1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, ga1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, ga1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, ga1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```
## {-}

## Results {.tabset}

### Plot 1
```{r, ga1 cor by dif windows}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, ga1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, ga1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, ga1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, ga1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, ga1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, ga1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, ga1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, ga1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, ga1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```
## {-}

## Correlation across time

```{r, ga1 cor and pheno}
GA1_pattern <- unique(paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep))
for(i in 1:length(GA1_pattern)){
  myine<-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
  plot(myine)
}

```

```{r, ga1 cor 7 and pheno}
GA1_pattern_7 <- unique(paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd, "_", GA1_tall_tall_7_file$rep))
for(i in 1:length(GA1_pattern_7)){
  myine<-cor_trends_by_gen(GA1_tall_tall_7_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern_7[i])
  plot(myine)
}

```

## What happens over time (looking at the beginning. middle, and late part of my simulations)

```{r, early plots summary}

min_gen=100
max_gen=5000
GA1_tall_tall_7_file_temp<-GA1_tall_tall_7_file
GA1_tall_tall_7_file_temp$rep<-as.numeric(GA1_tall_tall_7_file_temp$rep)+4
test<-rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp)

# summary
GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

min_gen=10000
max_gen=15000

# summary
GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

min_gen=45000
max_gen=50000

# summary
GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

min_gen=100
max_gen=5000

GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

min_gen=10000
max_gen=15000

GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

min_gen=45000
max_gen=50000

GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

```{r, early plots Heatmap}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

min_gen=10000
max_gen=15000
#heatmap
build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

min_gen=45000
max_gen=50000
#heatmap
build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

min_gen=100
max_gen=5000
build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

min_gen=10000
max_gen=15000
#heatmap

build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

min_gen=45000
max_gen=50000
#heatmap

build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## What is up with the correlations

### Snake_1e-09_0.05_Newt_1e-09_0.05_2

```{r, cor grid by location}

#GA1_grid_tall_file

file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
spegen=25001

GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]

GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]

data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)

data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)

data_long_mean_short<-data_long_mean

data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

main_plot<-ggplot(data_long_mean_short)+
  labs(title = "Mean Phenotype of Locations",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()+
  theme(legend.justification = "top")

snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
newt$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")

newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
newt$info[is.na(newt$info)]<- "middle"

extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

```

```{r, cor grid by location}

#GA1_grid_tall_7_file

file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
spegen=25001

GA1<-GA1_grid_tall_7_file[which(GA1_grid_tall_7_file$snake_newt_rep==file_name & GA1_grid_tall_7_file$generation==spegen),]

GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]

data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)

data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)

data_long_mean_short<-data_long_mean

data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

main_plot<-ggplot(data_long_mean_short)+
  labs(title = "Mean Phenotype of Locations",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()+
  theme(legend.justification = "top")

snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
newt$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")

newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
newt$info[is.na(newt$info)]<- "middle"

extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

```

```{r, cor grid by location}

#GA1_grid_tall_file

file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
spegen=26051

GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]

GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]

data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)

data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)

data_long_mean_short<-data_long_mean

data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

main_plot<-ggplot(data_long_mean_short)+
  labs(title = "Mean Phenotype of Locations",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()+
  theme(legend.justification = "top")

snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
newt$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")

newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
newt$info[is.na(newt$info)]<- "middle"

extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

# max phenotype

GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]

GA1_max = GA1[,grepl("generation|max", names(GA1)) ]

data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)

data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)

data_long_max_short<-data_long_max

data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

main_plot<-ggplot(data_long_max_short)+
  labs(title = "Max Phenotype of Locations",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()+
  theme(legend.justification = "top")

snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
newt$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")

newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
newt$info[is.na(newt$info)]<- "middle"

extra_plot <- ggplot(newt)+
  ggtitle("Max Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

# max phenotype

GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]

GA1_min = GA1[,grepl("generation|min", names(GA1)) ]

data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)

data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)

data_long_min_short<-data_long_min

data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

main_plot<-ggplot(data_long_min_short)+
  labs(title = "Min Phenotype of Locations",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()+
  theme(legend.justification = "top")

snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
newt$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")

newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
newt$info[is.na(newt$info)]<- "middle"

extra_plot <- ggplot(newt)+
  ggtitle("Min Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

#GA1_grid_tall_file population size

GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]

GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]

GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)

GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)

GA1_data_long_ind_short<-GA1_data_long_ind

GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA

main_plot<-ggplot(GA1_data_long_ind_short)+
  labs(title = "Locations of Ind",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Number of Individuals")+
  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c(option = "plasma")+
  theme_bw()+
  theme(legend.justification = "top")

snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
newt_GA1$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")

newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
newt_GA1$info[is.na(newt_GA1$info)]<- "middle"

extra_plot <- ggplot(newt_GA1)+
  ggtitle("Num of Ind") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

```

### Snake_1e-08_0.005_Newt_1e-08_0.005_3

```{r, cor grid by location round 2}

#GA1_grid_tall_file

file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
spegen=25001

GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]

GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]

data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)

data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)

data_long_mean_short<-data_long_mean

data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

main_plot<-ggplot(data_long_mean_short)+
  labs(title = "Mean Phenotype of Locations",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()+
  theme(legend.justification = "top")

snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
newt$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")

newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
newt$info[is.na(newt$info)]<- "middle"

extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

# SD

GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]

data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)

data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)

data_long_sd_short<-data_long_sd

data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

main_plot<-ggplot(data_long_sd_short)+
  labs(title = "SD Phenotype of Locations",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()+
  theme(legend.justification = "top")

snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
newt$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")

newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
newt$info[is.na(newt$info)]<- "middle"

extra_plot <- ggplot(newt)+
  ggtitle("SD Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

# max phenotype

GA1_max = GA1[,grepl("generation|max", names(GA1)) ]

data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)

data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)

data_long_max_short<-data_long_max

data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

main_plot<-ggplot(data_long_max_short)+
  labs(title = "Max Phenotype of Locations",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()+
  theme(legend.justification = "top")

snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
newt$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")

newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
newt$info[is.na(newt$info)]<- "middle"

extra_plot <- ggplot(newt)+
  ggtitle("Max Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

# min phenotype

GA1_min = GA1[,grepl("generation|min", names(GA1)) ]

data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)

data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)

data_long_min_short<-data_long_min

data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

main_plot<-ggplot(data_long_min_short)+
  labs(title = "Min Phenotype of Locations",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()+
  theme(legend.justification = "top")

snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
newt$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")

newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
newt$info[is.na(newt$info)]<- "middle"

extra_plot <- ggplot(newt)+
  ggtitle("Min Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

#GA1_grid_tall_file population size

GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]

GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)

GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)

GA1_data_long_ind_short<-GA1_data_long_ind

GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))

GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA

main_plot<-ggplot(GA1_data_long_ind_short)+
  labs(title = "Locations of Ind",
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Number of Individuals")+
  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c(option = "plasma")+
  theme_bw()+
  theme(legend.justification = "top")

snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
newt_GA1$snake_value <- snake$measurement
cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")

newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
newt_GA1$info[is.na(newt_GA1$info)]<- "middle"

extra_plot <- ggplot(newt_GA1)+
  ggtitle("Num of Ind") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

#try to arrage the grids

main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)

```

### 2022-08-31 graphs_newt_snakes/GA3.Rmd
made a realy nice markdown-html (GA3). Also fixed up the last bit of confusion with the newt_snake snake_newt by making the facetwrap use sim which is what I use for everything else.

@@
 GA3 file will be the slow evolution file.
-The main goal will be testing to see if there is an effect caused by mutation rate or effect size when the mutational variance between two species is the same.
-
-Prediction: Higher mutation rate will be advantages in the beginning of a simulation. A higher effect size might lead to more spatial co-evolution. Space might separate the effects.
-
-For the initial part of this experiment I will only be running one trial per GA combination
+The main goal will be testing to see if there is an effect caused by mutation rate or effect size when the mutational variance between two species is the same (a low).
+
+Prediction: Higher mutation rate will be advantages in the beginning of a simulation.
+A higher effect size might lead to more spatial co-evolution.
+Space might influence the effects.
+- A non-spatial simulation with these values might be fun to compare
+
+For the initial part of this experiment I will run four trials per GA combination
 
@@
 In this case, there are three data sets; one for whole population data (lit), one for correlation data (cor), and one for individual grids (grid).
-After these all file is created, I load it into R and finish adding in some comparative columns.
+After all of these files are created, I load it into R and finish adding in some comparative columns.
 I also load in my figure creation functions.
@@
   real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  #file=GA3_cor_tall_file
+  #file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  myplot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
   ylim(-1.1, 1.1)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
-  xlab(x_label) + ylab(y_label)+
+  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  #xlab(x_label) + ylab(y_label)+
   geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
@@
   theme(plot.title = element_text(size=5)) +
-  facet_wrap(~snake_newt)+
+  facet_wrap(~sim)+
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
@@
 
-  return(plot)
+  return(myplot)
 }
@@
   real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+   #file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
   #unique(file$sim)
@@
   xlim(-1.1, 1.1)+
-  facet_wrap(~snake_newt)+
+  facet_wrap(~sim)+
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
@@
   real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  #file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
   unique(file$sim)
@@
   #stat_bin(bins=30)+
-  facet_wrap(~snake_newt)+
+  facet_wrap(~sim)+
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
@@
 four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
-  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  #file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
@@
 
-  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
-  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/1000 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/1000
   thedifmin <- min(file$dif) 
@@
   geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
-  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/1000, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
   scale_y_continuous(labels = scales::percent)+
-  xlim((-1*true_max)-1, true_max+1)+
+  xlim((-1*true_max), true_max)+
   # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
@@
 
-Information to be typed
+The first thing that I observe is the general mean newt and snake phenotype trends across time.
+In the phenotype differences figure the red and blue lines represent mean newt and snake phenotype.
+The black lines are the differences between mean phenotypes of snakes and newts.
+The table shows the average mean phenotype differences from generation 100 to 50,000.
+In both the figure and table there will be a positive value when snakes have a higher phenotype and a negative value when newts have a higher phenotype.
 
@@
 
-explanation
+In the phenotype differences figure the mean phenotypes of newts and snakes generally goes up.
+There are a few cases where the mean phenotype stays flat.
+There are two cases where the mean phenotype goes down (L, N, very rare).
+In most of the simulations newts end up having a higher mean phenotype (more black lines lower then 0 and negative means in the table).
+In the table, a larger value (both positive and negative) might indicate agreement between the simulation.
+A value closer to 0 can indicate a small difference between snake and newt mean phenotype or larger but opposite differences between snake and newt mean phenotype.
 
@@
 
-more info
+Previous results show that there is a connection between phenotype and population size.
+Typically, when one species has a larger phenotype they also have a larger population size (special note; snakes tend to have slightly larger population size when newt and snake phenotypes are close).
+The phenotype differences figure shows the newt population size by snake population size.
+Each dot is one time point from the simulation, the dots shown are from generation 5,000 to 10,000.
+The color of the dots is the difference between snake and newt mean phenotype (more blue snakes have a higher phenotype, more red newts have a higher phenotype).
+The figure of phenotype and population size differences has two histograms.
+The purple histogram shows the difference between snake and newt phenotype.
+The green histogram shows the difference between snake and newt population size divided by 1000.
+I show one trials result below.
 
@@
 
-suppressMessages(print(two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+suppressMessages(print(two_hist(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
 
@@
 
-explanation
+In these figures, snakes often had a larger population size (even when newts phenotype is larger).
+In the phenotype differences figure, GA combinations that had resulted in higher newt phenotypes also resulted with a closer snake-newt population size.
+The cluster of the results tended to be in the right bottom corner.
+When snakes had a larger phenotype the clues of points tended to be in the top left corner.
+When looking at the histograms the difference between phenotypes is small, but newts have a higher mean phenotype in more than half of the GA combinations.
+The more positive the mean phenotype the difference the more positive the mean population size difference.
 
@@
 
-Info
+This next section is about spatial correlation!
+Over the course of two species co-evolving I predicted that there would be some areas in space when the phenotypes would both be higher and some areas when the phenotypes would both be lower.
+If this were true the spacial correlation would be high.
+However, the spatial correlation can also be negative or close to 0.
+It could be close to 0 if the mean phenotypes are randomly paired though out different locations.
+It could be negative if there is a high-low relationship between the phenotypes.
+
+Collecting an accurate spatial correlation is difficult.
+What is the correct time point or set of time points to be measuring from?
+What is the correct amount of area to be measuring from?
+How does the spreading of phenotype affect this measurement?
+How does spatial correlation change over time?
+In this figure there are four box plots per GA combination.
+Each of these box plot is form a different trial.
+the dashed black line is the real newt and snake spatial correlation.
 
@@
 
-Explanation
+After looking at this figure, I can see that there is a larger range of correlation values.
+The can sometimes be positive, near 0, or negative.
+Very few reach (or come near) the real newt-snake correlation.
+How do you find the correct time slice to look for spatial correlation?
+How would these phenotypes become spatially correlated and then become not spatially correlated.
 
@@
 
-what did I do and why Time slices to see general trends
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
 
@@
 What does it mean?
+Correlations seem to change a lot from time chunk to time chunk.
+They can go from positive to negative.
+Sometimes the trials seem to disagree.
+To get a better understanding of what might be going on in my simulation, I will plat the mean snake and newt phenotype and the spatial correlation over time.
 
@@
 
-Explain general figures
-
-## What happens over time (looking at the beginning. middle, and late part of my simulations) {.tabset}
+I still wonder why the correlation values go up and down, because the mean newt and snake phenotype keeps going up.
+I wonder if the individuals might be moving around too much.
+I wonder what would happen on a larger map?
+
+## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
 
@@
 
+In the beginning of the simulation you can see how the population size of newts and snakes rises.
+You can also see that for most of the GA combinations there is already one species that has a phenotypic advantage.
+Over time the population size figure becomes more of an oval.
+The color gets more intense in the middle and end figures.
+In the purple and green figures the difference in snake and newt phenotype gets more pronounce from the beginning to the middle of the simulation.
+The difference in population size fluctuates a bit, but there are no noticeable terns in these figures.
+
 ## Summary {.tabset}
 
-Describe
+In a previous simulation study (tall GA3) I saw a difference in population size and phenotype between the different GAs.
+I will try to see if these GA combination lead to differences in phenotypes and population sizes.
+We will compare newt population size to snake population size with each shape indicating newt GA and each color indicating snake GA.
+We will walk though the beginning, middle, and end of my simulation.
+We will also look at the snake population size by the difference between snake and newt phenotypes
 
@@
 
-Explain
+After looking at the early population size summary, I noticed that at time when on the population size first spread out then started to gather in the center (into a diagonal line).
+There was no pattern or grouping between the shapes or colors.
+I saw the same thing in the difference summary.
+To confirm these finding I will now look at the heat maps.
 
@@
 
-What should I be focusing on here?
+In this section I look at the heat maps for snake population size and mean phenotype difference for the beginning, middle, and end of my simulation.
+For all of these plots newt GA will be on the x-axis.
+The snake GA and simulation trial will be on the y-axis (each four can be read as a group).
+*This map y-axis is switched compared to all the other figures.* For the population size maps as the color goes from dark (purple) to light (yellow) the snake population size increases.
+For the difference phenotype maps the mean difference goes from blue to red, with blue indicating snakes have a higher phenotype and red indicating that newts have a higher phenotype.
 
@@
 
-Explanations
+Again, I did not see a pattern between the GAs. I also did not see very good agreement between the trials. Results seemed very variable.
 
@@
 
-Need to add tabs to show the mean, max, min, and population size. #3 high + cor, 0 cor, -cor
-
-```{r, cor grid by location 1}
-
-#GA3_grid_tall_file
-
-file_name= "Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+This is the final section of this experiments' markdown.
+There are three examples shown below.
+In each example there will be a map like plot (x and y are locations) with snake (square) and newt (circle) phenotype and population size represented with color.
+Each example will have the mean phenotype, max phenotype, min phenotype, and population size.
+These examples will highlight a high positive, low, and high negative spatial correlation.
+
+### High Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid high cor mean}
+
+#GA3_GA3_grid_tall_file
+
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
 
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
-
-spegen=20001
-#unique(GA3_grid_tall_file$snake_newt_rep)
+spegen=30001
+
 GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
@@
 
-GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
-
-GA3_data_long_mean_short<-GA3_data_long_mean
-
-GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(GA3_data_long_mean_short)+
+data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
   labs(title = "Mean Phenotype of Locations",
@@
               fill = "Toxicity/Resistance")+
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
   scale_fill_viridis_c()+
@@
 
-snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
-newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
-newt_GA3$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
-
-newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
-
-extra_plot <- ggplot(newt_GA3)+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
   ggtitle("Mean Phenotype") +
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-### file
-
-```{r, cor grid by location 2}
-
-#GA3_grid_tall_file
-
-file_name= "Snake_1e-08_0.005_Newt_1e-11_0.158_0"
-#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
-
+```
+
+#### SD 
+```{r, cor grid high cor SD}
+
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
 spegen=30001
-#unique(GA3_grid_tall_file$snake_newt_rep)
-GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
-GA3<-GA3[1,]
-GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
-
-GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
-
-GA3_data_long_mean_short<-GA3_data_long_mean
-
-GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(GA3_data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
+# SD
+
+GA3_sd = GA3[,grepl("generation|sd", names(GA3)) ]
+
+data_long_sd <- gather(GA3_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
               subtitle = paste0(file_name, ", Generation: ", spegen),
               fill = "Toxicity/Resistance")+
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
   scale_fill_viridis_c()+
@@
 
-snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
-newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
-newt_GA3$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
-
-newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
-
-extra_plot <- ggplot(newt_GA3)+
-  ggtitle("Mean Phenotype") +
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
   xlab("Newt") + ylab("Snake")+
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-```{r, cor grid by location 3}
-
-#GA3_grid_tall_file
-
-file_name= "Snake_1e-10_0.05_Newt_1e-11_0.158_3"
-#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
-
-spegen=14001
-#unique(GA3_grid_tall_file$snake_newt_rep)
-GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
-
-GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
-
-GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
-
-GA3_data_long_mean_short<-GA3_data_long_mean
-
-GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(GA3_data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
+```
+
+#### Max Phenotype 
+```{r, cor grid high cor max}
+
+# max phenotype
+
+GA3_max = GA3[,grepl("generation|max", names(GA3)) ]
+
+data_long_max <- gather(GA3_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
               subtitle = paste0(file_name, ", Generation: ", spegen),
               fill = "Toxicity/Resistance")+
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
   scale_fill_viridis_c()+
@@
 
-snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
-newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
-newt_GA3$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
-
-newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
-
-extra_plot <- ggplot(newt_GA3)+
-  ggtitle("Mean Phenotype") +
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
   xlab("Newt") + ylab("Snake")+
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-```{r, cor grid by location 4}
-
-#GA3_grid_tall_file
-file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_0"
-#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
-
-spegen=15001
-#unique(GA3_grid_tall_file$snake_newt_rep)
-GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
-GA3<-GA3[1,]
-GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
-
-GA3_data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-GA3_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_mean$condition, "_", 4)
-
-GA3_data_long_mean_short<-GA3_data_long_mean
-
-GA3_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA3_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(GA3_data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
+```
+
+#### Min Phenotype 
+```{r, cor grid high cor min}
+
+# min phenotype
+
+GA3_min = GA3[,grepl("generation|min", names(GA3)) ]
+
+data_long_min <- gather(GA3_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
               subtitle = paste0(file_name, ", Generation: ", spegen),
               fill = "Toxicity/Resistance")+
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
   scale_fill_viridis_c()+
@@
 
-snake<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="snake"),]
-newt_GA3<-GA3_data_long_mean_short[which(GA3_data_long_mean_short$species=="newt"),]
-newt_GA3$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
-
-newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
-
-extra_plot <- ggplot(newt_GA3)+
-  ggtitle("Mean Phenotype") +
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
   xlab("Newt") + ylab("Snake")+
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-#spegen=30001
-#unique(GA3_grid_tall_file$snake_newt_rep)
-GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
-GA3<-GA3[1,]
+```
+
+#### Population Size
+```{r, cor grid high cor popsize}
+
+# popsize
+#GA3_GA3_grid_tall_file population size
+
 GA3_ind = GA3[,grepl("generation|num_ind", names(GA3)) ]
@@
 
-```{r, cor grid by location 5}
-
-#GA3_grid_tall_file
-
-file_name= "Snake_1e-10_0.05_Newt_1e-09_0.0158_0"
+### {-}
+
+### Near Zero Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid zerp cor mean}
+
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=20001
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
 
@@
 
-#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
-
-spegen=49991
-#spegen=30001
-#unique(GA3_grid_tall_file$snake_newt_rep)
 GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
+
+GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
+
+data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### SD 
+```{r, cor grid zero cor SD}
+
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=20001
+# SD
+
+GA3_sd = GA3[,grepl("generation|sd", names(GA3)) ]
+
+data_long_sd <- gather(GA3_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid zero cor max}
+
+# max phenotype
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=20001
+GA3_max = GA3[,grepl("generation|max", names(GA3)) ]
+
+data_long_max <- gather(GA3_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid zero cor min}
+
+# min phenotype
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=20001
+GA3_min = GA3[,grepl("generation|min", names(GA3)) ]
+
+data_long_min <- gather(GA3_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid zer cor popsize}
+
+# max phenotype
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=20001
 
@@
 ```
+
+### {-}
+
+### Negative Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid neg cor mean}
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=48001
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+# file_name= "Snake_1e-08_0.005_Newt_1e-11_0.158_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-11_0.158_3"
+# file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-09_0.0158_0"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
+
+GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]
+
+data_long_mean <- gather(GA3_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### SD 
+```{r, cor grid neg cor SD}
+
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=48001
+# SD
+
+GA3_sd = GA3[,grepl("generation|sd", names(GA3)) ]
+
+data_long_sd <- gather(GA3_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid neg cor max}
+
+# max phenotype
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=48001
+
+GA3_max = GA3[,grepl("generation|max", names(GA3)) ]
+
+data_long_max <- gather(GA3_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid neg cor min}
+
+# min phenotype
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=48001
+GA3_min = GA3[,grepl("generation|min", names(GA3)) ]
+
+data_long_min <- gather(GA3_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid neg cor popsize}
+
+# max phenotype
+
+file_name="Snake_1e-10_0.05_Newt_1e-09_0.0158_1"
+spegen=48001
+GA3_ind = GA3[,grepl("generation|num_ind", names(GA3)) ]
+
+GA3_data_long_ind <- gather(GA3_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA3_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA3_data_long_ind$condition, "_", 4)
+
+GA3_data_long_ind_short<-GA3_data_long_ind
+
+GA3_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA3_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA3_data_long_ind_short$measurement[GA3_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA3_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="snake"),]
+newt_GA3<-GA3_data_long_ind_short[which(GA3_data_long_ind_short$species=="newt"),]
+newt_GA3$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA3$measurement), use="complete.obs")
+
+newt_GA3$info[newt_GA3$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA3$info[newt_GA3$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA3$info[is.na(newt_GA3$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA3)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}

### 2022-08-31 graphs_newt_snakes/corcompare.Rmd
made a realy nice markdown-html (GA3). Also fixed up the last bit of confusion with the newt_snake snake_newt by making the facetwrap use sim which is what I use for everything else.

@@
   xlim(-1.1, 1.1)+
-  facet_wrap(~snake_newt)+
+  facet_wrap(~sim)+
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),

### 2022-09-06 graphs_newt_snakes/GA1_tall_redo_md.Rmd
writing my interpretations

@@
 }
+GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
 
@@
 
-trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){
 
@@
     geom_hline(yintercept=0, linetype="dashed", color="gray54")+
-    ylim(-1.,2.5)+
+    #ylim(-1.,2.5)+
     xlab(x_label) + ylab(y_label)+
@@
 
-## Mean Phenotype Whole Simulation
+Important files
+GA1_tall_tall_file
+GA1_cor_tall_file
+GA1_grid_tall_file
+GA1_tall_tall_7_file
+GA1_cor_tall_7_file
+GA1_grid_tall_7_file
+
+## Mean Phenotype Whole Simulation {.tabset}
 
@@
 
+### Phenotype differences (5 sec)
 ```{r, graphing by gen}
-trends_by_gen(GA1_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
-
+trends_by_gen(GA1_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+#aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
+
+```
+
+### Table of average Differences (5 sec)
+
+```{r, average difference}
 aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group), FUN=mean)
-
-aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
-
-trends_by_gen(GA1_tall_tall_7_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
-
+```
+
+### Phenotype differences (7 sec)
+```{r, graphing by gen 7}
+trends_by_gen(GA1_tall_tall_7_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+#aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
+
+```
+
+### Table of average Differences (7 sec)
+
+```{r, average difference 7}
 aggregate(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$dif, list(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$group), FUN=mean)
-
-aggregate(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$dif, list(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$group_rep), FUN=mean)
-
-```
-
-#### Connection between higher phenotype and population
-
+```
+
+## {-}
+
+## Connection between higher phenotype and population (5 sec) {.tabset}
+
+Notes
+
+### Phenotype differences
 ```{r, whale}
@@
 whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-
-suppressMessages(print(two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+```
+
+### Phenotype & Populationsize differences
+```{r, popsize and pheno}
+
+suppressMessages(print(two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+
+```
+
+## {-}
+
+## Connection between higher phenotype and population (7 sec) {.tabset}
+
+Notes
+
+### Phenotype differences (7 sec) 
+```{r, whale 7}
+min_gen=5000
+max_gen=10000
+rep=0
 
 whale_gen(GA1_tall_tall_7_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-
-suppressMessages(print(two_hist_all_rep(GA1_tall_tall_7_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
-
-```
+```
+
+### Phenotype & Populationsize differences (7 sec) 
+```{r, popsize and pheno 7}
+
+suppressMessages(print(two_hist(GA1_tall_tall_7_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+```
+
+## {-}
 
@@
 
-## Correlation
+## Correlation {.tabset}
 
@@
 
-Legend:
-
-- "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
-- "CB" = num_newts_By_num_snakes (Green)
-- "CC" = sum_newt_pheno_By_num_snake (Blue)
-- "CD" = sum_snake_pheno_By_num_newt (Purple)
-
 I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
@@
 
+### Five sections 
 ```{r, combo myplots}
@@
 
-four_types_boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-boxplot_cors_by_gen(GA1_cor_tall_7_file, "Simulation Correlation 7 Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-four_types_boxplot_cors_by_gen(GA1_cor_tall_7_file, "Simulation four Correlation 7", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation 7 Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-```
-
-## Results {.tabset}
+#four_types_boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+### Seven sections
+```{r, combo myplots 7}
+
+ginmin = 10000
+ginmax = 15000
+
+boxplot_cors_by_gen(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+## {-}
+
+After looking at this figure, I can see that there is a larger range of correlation values.
+The can sometimes be positive, near 0, or negative.
+Very few reach (or come near) the real newt-snake correlation.
+How do you find the correct time slice to look for spatial correlation?
+How would these phenotypes become spatially correlated and then become not spatially correlated.
+
+## Correlation Histograms (5 sec) {.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
 
 ### Plot 1
-```{r, ga1 cor by dif windows}
+```{r, GA1 cor by dif windows}
 ginmin = 0
@@
 
-```{r, ga1 cor by dif windows 2}
+```{r, GA1 cor by dif windows 2}
 ginmin = 5000
@@
 ### Plot 3
-```{r, ga1 cor by dif windows 3}
+```{r, GA1 cor by dif windows 3}
 ginmin = 10000
@@
 ### Plot 4
-```{r, ga1 cor by dif windows 4}
+```{r, GA1 cor by dif windows 4}
 ginmin = 15000
@@
 ### Plot 5
-```{r, ga1 cor by dif windows 5}
+```{r, GA1 cor by dif windows 5}
 ginmin = 20000
@@
 ### Plot 6
-```{r, ga1 cor by dif windows 6}
+```{r, GA1 cor by dif windows 6}
 ginmin = 25000
@@
 ### Plot 7
-```{r, ga1 cor by dif windows 7}
+```{r, GA1 cor by dif windows 7}
 ginmin = 30000
@@
 ### Plot 8
-```{r, ga1 cor by dif windows 8}
+```{r, GA1 cor by dif windows 8}
 ginmin = 35000
@@
 ### Plot 9
-```{r, ga1 cor by dif windows 9}
+```{r, GA1 cor by dif windows 9}
 ginmin = 40000
@@
 ### Plot 10
-```{r, ga1 cor by dif windows 10}
+```{r, GA1 cor by dif windows 10}
 ginmin = 45000
@@
 ```
+
 ## {-}
 
-## Results {.tabset}
-
-### Plot 1
-```{r, ga1 cor by dif windows}
+## Correlation Histograms (7 sec) {.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
+
+### Plot 1 (7 sec)
+```{r, GA1 cor by dif windows (7 sec)}
 ginmin = 0
@@
 
-### Plot 2
-
-```{r, ga1 cor by dif windows 2}
+### Plot 2 (7 sec)
+
+```{r, GA1 cor by dif windows 2 (7 sec)}
 ginmin = 5000
@@
 
-### Plot 3
-```{r, ga1 cor by dif windows 3}
+### Plot 3 (7 sec)
+```{r, GA1 cor by dif windows 3 (7 sec)}
 ginmin = 10000
@@
 
-### Plot 4
-```{r, ga1 cor by dif windows 4}
+### Plot 4 (7 sec)
+```{r, GA1 cor by dif windows 4 (7 sec)}
 ginmin = 15000
@@
 
-### Plot 5
-```{r, ga1 cor by dif windows 5}
+### Plot 5 (7 sec)
+```{r, GA1 cor by dif windows 5 (7 sec)}
 ginmin = 20000
@@
 
-### Plot 6
-```{r, ga1 cor by dif windows 6}
+### Plot 6 (7 sec)
+```{r, GA1 cor by dif windows 6 (7 sec)}
 ginmin = 25000
@@
 
-### Plot 7
-```{r, ga1 cor by dif windows 7}
+### Plot 7 (7 sec)
+```{r, GA1 cor by dif windows 7 (7 sec)}
 ginmin = 30000
@@
 
-### Plot 8
-```{r, ga1 cor by dif windows 8}
+### Plot 8 (7 sec)
+```{r, GA1 cor by dif windows 8 (7 sec)}
 ginmin = 35000
@@
 
-### Plot 9
-```{r, ga1 cor by dif windows 9}
+### Plot 9 (7 sec)
+```{r, GA1 cor by dif windows 9 (7 sec)}
 ginmin = 40000
@@
 
-### Plot 10
-```{r, ga1 cor by dif windows 10}
+### Plot 10 (7 sec)
+```{r, GA1 cor by dif windows 10 (7 sec)}
 ginmin = 45000
@@
 ```
+
 ## {-}
 
-## Correlation across time
-
-```{r, ga1 cor and pheno}
+## Correlation across time {.tabset}
+
+notes
+
+### Random 1 (5 sec)
+```{r, GA1 cor and pheno, results="hide"}
 GA1_pattern <- unique(paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep))
-for(i in 1:length(GA1_pattern)){
-  myine<-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
-  plot(myine)
-}
-
-```
-
-```{r, ga1 cor 7 and pheno}
-GA1_pattern_7 <- unique(paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd, "_", GA1_tall_tall_7_file$rep))
-for(i in 1:length(GA1_pattern_7)){
-  myine<-cor_trends_by_gen(GA1_tall_tall_7_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern_7[i])
-  plot(myine)
-}
-
-```
-
-## What happens over time (looking at the beginning. middle, and late part of my simulations)
-
-```{r, early plots summary}
+
+myrandomlist=sample.int(length(GA1_pattern), 3)
+
+# for(i in myrandomlist){
+#   myine<-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   plot(myine)
+# }
+
+cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2 (5 sec)
+```{r, random cor-pheno plot 2}
+
+cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3 (5 sec)
+```{r, random cor-pheno plot 3}
+
+cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+### Random 1 (7 sec)
+```{r, GA1 cor and pheno 7}
+GA1_pattern <- unique(paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd, "_", GA1_tall_tall_7_file$rep))
+
+myrandomlist=sample.int(length(GA1_pattern), 3)
+
+# for(i in myrandomlist){
+#   myine<-cor_trends_by_gen(GA1_tall_tall_7_file, GA1_cor_tall_7_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   plot(myine)
+# }
+
+cor_trends_by_gen(GA1_tall_tall_7_file, GA1_cor_tall_7_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2 (7 sec)
+```{r, random cor-pheno plot 2 7}
+
+cor_trends_by_gen(GA1_tall_tall_7_file, GA1_cor_tall_7_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3 (7 sec)
+```{r, random cor-pheno plot 3 7}
+
+cor_trends_by_gen(GA1_tall_tall_7_file, GA1_cor_tall_7_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+
+### Pheno Beginning
+
+```{r, early plots}
 
@@
 max_gen=5000
-GA1_tall_tall_7_file_temp<-GA1_tall_tall_7_file
-GA1_tall_tall_7_file_temp$rep<-as.numeric(GA1_tall_tall_7_file_temp$rep)+4
-test<-rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp)
-
-# summary
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-min_gen=10000
-max_gen=15000
-
-# summary
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+# for(i in 1:length(unique(GA1_tall_tall_file$rep))){
+#   myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[1])
+```
+
+### Pheno Middle
+
+```{r, middle plots}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(GA1_tall_tall_file$rep))){
+#   myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[1])
+```
+
+### Pheno End
+
+```{r, end plots}
 
@@
 
-# summary
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+# for(i in 1:length(unique(GA1_tall_tall_file$rep))){
+#   myine<-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[1])
+```
+
+### Dif Beginning 
+```{r, early plots 1a}
 
@@
 
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-min_gen=10000
-max_gen=15000
-
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+# for(i in 1:length(unique(GA1_tall_tall_file$rep))){
+#   myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[1] )
+
+```
+
+### Dif Middle 
+```{r, early plots 2a}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(GA1_tall_tall_file$rep))){
+#   myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[1] )
+
+```
+
+### Dif End 
+```{r, early plots 3a}
 
@@
 
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-```
+# for(i in 1:length(unique(GA1_tall_tall_file$rep))){
+#   myine<-two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_file$rep)[1] )
+
+```
+
+## {-}
+
+## What happens over time (looking at the beginning, middle, and late part of my simulations) (7 sec) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+
+### Pheno Beginning (7 sec)
+
+```{r, early plots 7}
+
+min_gen=100
+max_gen=5000
+
+whale_gen(GA1_tall_tall_7_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_7_file$rep)[1])
+```
+
+### Pheno Middle (7 sec)
+
+```{r, middle plots 7}
+
+min_gen=25000
+max_gen=30000
+
+whale_gen(GA1_tall_tall_7_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_7_file$rep)[1])
+```
+
+### Pheno End (7 sec)
+
+```{r, end plots 7}
+
+min_gen=45000
+max_gen=50000
+
+whale_gen(GA1_tall_tall_7_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_7_file$rep)[1])
+```
+
+### Dif Beginning (7 sec)
+```{r, early plots 1a7}
+
+min_gen=100
+max_gen=5000
+
+two_hist(GA1_tall_tall_7_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_7_file$rep)[1] )
+
+```
+
+### Dif Middle (7 sec)
+```{r, early plots 2a7}
+
+min_gen=25000
+max_gen=30000
+
+two_hist(GA1_tall_tall_7_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_7_file$rep)[1] )
+
+```
+
+### Dif End (7 sec)
+```{r, early plots 3a7}
+
+min_gen=45000
+max_gen=50000
+
+two_hist(GA1_tall_tall_7_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_tall_tall_7_file$rep)[1] )
+
+```
+
+## {-}
+
+explane
+
+## Summary {.tabset}
+
+notes
+
+### Early-Sim Population Size Summary
+
+```{r, early plots summary}
+
+min_gen=100
+max_gen=5000
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Mid-Sim Population Size Summary
+```{r, plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+
+# summary
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Late-Sim Population Size Summary
+```{r, plots summary 3}
+min_gen=45000
+max_gen=50000
+
+# summary
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+```
+
+### Early Difference Summary
+```{r, dif plots summary 1}
+
+min_gen=100
+max_gen=5000
+
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+### Mid Difference Summary
+```{r, dif plots summary 2}
+min_gen=25000
+max_gen=30000
+
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
+
+### Late Difference Summary
+```{r, dif plots summary 3}
+min_gen=45000
+max_gen=50000
+GA_summary(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
+
+### By Snake GA (Early)
+```{r, snakega plots summary 1}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Mid)
+```{r, snakega plots summary 2}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Late)
+```{r, snakega plots summary 3}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Early)
+```{r, newtga plots summary 1}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Mid)
+```{r, newtga plots summary 2}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Late)
+```{r, newtga plots summary 3}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+## {-}
+
+## Summary (7 sec) {.tabset}
+
+notes
+
+### Early-Sim Population Size Summary (7 sec)
+
+```{r, early plots summary 7}
+
+min_gen=100
+max_gen=5000
+GA_summary(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Mid-Sim Population Size Summary (7 sec)
+```{r, plots summary 27}
+# summary
+
+min_gen=25000
+max_gen=30000
+
+# summary
+GA_summary(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Late-Sim Population Size Summary (7 sec)
+```{r, plots summary 37}
+min_gen=45000
+max_gen=50000
+
+# summary
+GA_summary(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+```
+
+### Early Difference Summary (7 sec)
+```{r, dif plots summary 17}
+
+min_gen=100
+max_gen=5000
+
+GA_summary(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+### Mid Difference Summary (7 sec)
+```{r, dif plots summary 27}
+min_gen=25000
+max_gen=30000
+
+GA_summary(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
+
+### Late Difference Summary (7 sec)
+```{r, dif plots summary 37}
+min_gen=45000
+max_gen=50000
+GA_summary(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
+
+### By Snake GA (Early) (7 sec)
+```{r, snakega plots summary 17}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Mid) (7 sec)
+```{r, snakega plots summary 27}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Late) (7 sec)
+```{r, snakega plots summary 37}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Early) (7 sec)
+```{r, newtga plots summary 17}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Mid) (7 sec)
+```{r, newtga plots summary 27}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Late) 7
+```{r, newtga plots summary 37}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+## {-}
+
+expla
+
+## Heatmap {.tabset}
+
+notes
+
+### Population Size (Early)
 
@@
 #heatmap
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-min_gen=10000
-max_gen=15000
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+```
+
+### Population Size (Mid)  
+```{r, early plots Heatmap 2}
+min_gen=25000
+max_gen=30000
 #heatmap
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### Population Size (Late) 
+```{r, early plots Heatmap 3}
 min_gen=45000
@@
 #heatmap
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+```
+
+### Phenotype (Early) 
+```{r, early plots Heatmap pheno 1}
 min_gen=100
 max_gen=5000
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-min_gen=10000
-max_gen=15000
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### Phenotype (Mid) 
+```{r, early plots Heatmap pheno 2}
+
+min_gen=25000
+max_gen=30000
 #heatmap
 
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### Phenotype (Late) 
+```{r, early plots Heatmap pheno 3}
 min_gen=45000
@@
 
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
+build_heatmap(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+```
+
+## {-}
+
+## Heatmap (7 sec) {.tabset}
+
+notes
+
+### Population Size (Early) (7 sec)
+
+```{r, early plots Heatmap7}
+
+min_gen=100
+max_gen=5000
+#heatmap
+build_heatmap(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+```
+
+### Population Size (Mid) (7 sec)  
+```{r, early plots Heatmap 27}
+min_gen=25000
+max_gen=30000
+#heatmap
+build_heatmap(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### Population Size (Late) (7 sec)
+```{r, early plots Heatmap 37}
+min_gen=45000
+max_gen=50000
+#heatmap
+build_heatmap(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+```
+
+### Phenotype (Early) (7 sec)
+```{r, early plots Heatmap pheno 17}
+min_gen=100
+max_gen=5000
+build_heatmap(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### Phenotype (Mid) (7 sec)
+```{r, early plots Heatmap pheno 27}
+
+min_gen=25000
+max_gen=30000
+#heatmap
+
+build_heatmap(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### Phenotype (Late) (7 sec)
+```{r, early plots Heatmap pheno 37}
+min_gen=45000
+max_gen=50000
+#heatmap
+
+build_heatmap(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+```
+
+## {-}
 
@@
 
-### Snake_1e-09_0.05_Newt_1e-09_0.05_2
-
-```{r, cor grid by location}
+file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
+file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
+
+## What is up with the correlations
+
+notes
+
+### Early Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid high cor mean}
 
@@
 
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-spegen=25001
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
 
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-```{r, cor grid by location}
-
-#GA1_grid_tall_7_file
-
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
+```
+
+#### SD 
+```{r, cor grid high cor SD}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid high cor max}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid high cor min}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid high cor popsize}
+
+# popsize
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+#GA1_grid_tall_file population size
+
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}
+
+### Middle Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid zerp cor mean}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
 spegen=25001
-
-GA1<-GA1_grid_tall_7_file[which(GA1_grid_tall_7_file$snake_newt_rep==file_name & GA1_grid_tall_7_file$generation==spegen),]
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
 
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-```{r, cor grid by location}
-
-#GA1_grid_tall_file
-
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-spegen=26051
+```
+
+#### SD 
+```{r, cor grid zero cor SD}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid zero cor max}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid zero cor min}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid zer cor popsize}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}
+
+### Late Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid neg cor mean}
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+# file_name= "Snake_1e-08_0.005_Newt_1e-11_0.158_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-11_0.158_3"
+# file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-09_0.0158_0"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
 
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### SD 
+```{r, cor grid neg cor SD}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid neg cor max}
 
 # max phenotype
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
 
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# max phenotype
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
+```
+
+#### Min Phenotype 
+```{r, cor grid neg cor min}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
 GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-#GA1_grid_tall_file population size
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
+```
+
+#### Population Size
+```{r, cor grid neg cor popsize}
+
+# max phenotype
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
 GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
@@
 
-### Snake_1e-08_0.005_Newt_1e-08_0.005_3
-
-```{r, cor grid by location round 2}
+### {-}
+
+## What is up with the correlations (7 sec)
+
+notes
+
+### Early Simulation Correlation (7 sec) {.tabset}
+
+#### Mean (7 sec) 
+```{r, cor grid high cor mean 7}
 
@@
 
-file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
-spegen=25001
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA1<-GA1_grid_tall_7_file[which(GA1_grid_tall_7_file$snake_newt_rep==file_name & GA1_grid_tall_7_file$generation==spegen),]
 
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
+```
+
+#### SD (7 sec) 
+```{r, cor grid high cor SD 7}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
 # SD
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype (7 sec) 
+```{r, cor grid high cor max 7}
 
 # max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
 
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype (7 sec) 
+```{r, cor grid high cor min 7}
 
 # min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
 
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
+```
+
+#### Population Size (7 sec)
+```{r, cor grid high cor popsize 7}
+
+# popsize
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
 #GA1_grid_tall_file population size
@@
 ```
+
+### {-}
+
+### Middle Simulation Correlation {.tabset}
+
+#### Mean (7 sec)
+```{r, cor grid zerp cor mean 7}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA1<-GA1_grid_tall_7_file[which(GA1_grid_tall_7_file$snake_newt_rep==file_name & GA1_grid_tall_7_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### SD (7 sec) 
+```{r, cor grid zero cor SD 7}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype (7 sec) 
+```{r, cor grid zero cor max 7}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype (7 sec)
+```{r, cor grid zero cor min 7}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size (7 sec)
+```{r, cor grid zer cor popsize 7}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}
+
+### Late Simulation Correlation {.tabset}
+
+#### Mean  (7 sec)
+```{r, cor grid neg cor mean 7}
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+# file_name= "Snake_1e-08_0.005_Newt_1e-11_0.158_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-11_0.158_3"
+# file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-09_0.0158_0"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA1<-GA1_grid_tall_7_file[which(GA1_grid_tall_7_file$snake_newt_rep==file_name & GA1_grid_tall_7_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### SD  (7 sec)
+```{r, cor grid neg cor SD 7}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype  (7 sec)
+```{r, cor grid neg cor max 7}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype (7 sec)
+```{r, cor grid neg cor min 7}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size (7 sec)
+```{r, cor grid neg cor popsize 7}
+
+# max phenotype
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}

### 2022-09-06 graphs_newt_snakes/GA3.Rmd
writing my interpretations

@@
 
-whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```

### 2022-09-06 graphs_newt_snakes/Heritability.Rmd
writing my interpretations

@@
 library(knitr)
+library(kableExtra)
 library("reshape")
+library(ggplot2)
+library(ggpubr)
+theme_set(theme_pubr())
+library(stringr)
+library(patchwork)
 
@@
 
-In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-heritable trait. I expect to see no spatial phenotype correlation
+In this experiment I am observing a "co-evolving" population with a non-heritable trait.
+I will break my simulation and make the trait a random draw (rnorm(1, 3, 2)).
+Newts and snakes will still interact, but their phenotype will be determined by this random draw.
+This random draw should create a mean phenotype near 1.
 
@@
 
-What happens when a co-evolving trait is not heritable?
+What happens when a co-evolving trait is not heritable? Can the two species co-evolve? With there be spatial correlation? What will the cost function do to newt and snake phenotypes?
 
 ## Background
+
+In my regular co-evolution experimental simulations newts and snakes have a phenotype based on mutations and their effect sizes.
+When newts and snakes interact the species that has a higher phenotype is deemed a "winner" and survives, while the other one dies.
+Over many interactions and generations newts and snakes co-evolve.
+The phenotype of newts and snakes typically increase.
+However, unlike the real newts and snakes I have yet to see consistent high levels of spatial correlation.
+I am running further experiments to get a better of how different aspects of my system (heritability and interaction) can affect phenotype and spatial correlation.
+In this experiment I take away the ability for a phenotype to be inherited.
+I predict that there will be no spatial phenotype correlation and no phenotype increase.
 
@@
   real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  unique(file$sim)
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  #file=her_cor_tall_file
+  #file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  myplot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
   ylim(-1.1, 1.1)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
-  xlab(x_label) + ylab(y_label)+
+  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  #xlab(x_label) + ylab(y_label)+
   geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=GA3_tall_tall_file
-#cfile=GA3_cor_tall_file 
- # pattern="1e-10_0.05_1e-08_0.005_3"
+#file=her_tall_tall_file
+#cfile=her_cor_tall_file 
+ # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
@@
   geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+
+GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
 #  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
@@
 
-#two_hist_death_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
-
-```
-
-## Mean Phenotype Whole Simulation
-
+#two_hist_death_all_rep(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+
+```
+
+## The Data
+
+I ran four trials per GA combination (I look back and find this unnecessarily, because phenotype is reassigned to be a random draw).
+After running my simulations, I gathered my data into three files; data containing a mean value for the entire map (lit), correlation data based off of local populations that were divided into grids (cor) and data collected from grid based populations (grid).
+These simulations have a msprime (coalescent/burn in/random genetic variation) and then run for 50,000 generations in SLiM (co-evolution) (all with the same GA values).
+
+GA1 experiment values:
+
+- 1e-8*(0.005)^2 = 2.5e-13
+- 1e-9*(0.05)^2 = 2.5e-12
+- 1e-10*(0.5)^2 = 2.5e-11
+- 1e-11*(5.0)^2 = 2.5e-10
+
+Landscape: 20 by 5 grid. A tall map!: 35*4 H, 35 W
+
+## Mean Phenotype Whole Simulation {.tabset}
+
+The first result I will look at is a plot of how the mean phenotype of the entire population of newts and snakes changes overtime.
+Each of these plots has three colored lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype.
+Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).
+The table represents the average difference between mean snake phenotype and mean newt phenotype between the four trials.
+
+### Phenotype differences
 ```{r, graphing by gen}
-trends_by_gen(her_tall_tall_file, title="Space Tall: Newt VS Snake Population Size her", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
-
+trends_by_gen(her_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
+
+#aggregate(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$dif, list(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
+
+```
+
+### Table of average Differences
+
+```{r, average difference}
 aggregate(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$dif, list(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$group), FUN=mean)
-
-#aggregate(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$dif, list(her_tall_tall_file[which(her_tall_tall_file$generation>=100 & her_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
-
-```
-
-#### Connection between higher phenotype and population
-
+```
+
+## {-}
+
+The average newt and snake phenotype over time in this experiment is 1. There is pretty much no difference between snake and newt phenotypes. The GA has no influence on the newt and snake phenotype.
+
+## Connection between higher phenotype and population {.tabset}
+
+In my previous simulations, I saw a relationship between population size and phenotype.
+Species with a higher phenotype often had a higher population size (except that snakes had a slightly larger population size when the phenotypes where equal).
+Here, I will plot newt population size by snake population size with the points color indicating the difference between mean snake and mean newt phenotype (blue=snakes, red=newts have a higher phenotype).
+I also plot histograms of the differences between snake and newt population size (green) and phenotype (purple).
+To get these histogram on the same plot I devied population size by 1000.
+
+### Phenotype differences
 ```{r, whale}
@@
 
-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-
-suppressMessages(print(two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
-
-suppressMessages(print(two_hist_all_rep(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
-
-```
+whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+```
+
+### Phenotype & Populationsize differences
+```{r, popsize and pheno}
+
+suppressMessages(print(two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+
+```
+
+## {-}
+
+The phenotype difference plot indicates that there is a relationship between newt ans snake population, but no relationship to phenotype.
+When snakes have a larger population size newts tend to have a smaller population size and vise-versa.
+The differences between newt and snake phenotype is very small.
+In the histograms snakes tend to have a larger population size for a majority of the simulation (eyeballing mean is around 500).
+Again, there is no difference between snake and newt mean phenotype.
+There is no GA impact seen in either of these figures.
 
@@
 
-Legend:
-
-- "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
-- "CB" = num_newts_By_num_snakes (Green)
-- "CC" = sum_newt_pheno_By_num_snake (Blue)
-- "CD" = sum_snake_pheno_By_num_newt (Purple)
+In this next section I look at spatial correlation.
+Spatial correlation could be positive, negative, or near 0.
+It is positive when both species are high or low in different areas.
+It is negative when the species are high/low and low/high.
+And it is near 0 when there is no relationship between the two phenotypes.
 
@@
 
-boxplot_cors_by_gen(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-four_types_boxplot_cors_by_gen(her_cor_tall_file, "Simulation four Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-```
-
-```{r, her cor by dif windows}
-
+boxplot_cors_by_gen(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(her_cor_tall_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+After looking at this figure, I can see that there is a very small range of correlation values, centered around 0.
+None few reach (or come near) the real newt-snake correlation.
+Wheb these trats are not be inherited this make
+
+## Correlation Histograms {.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked with each value being a single measurement at a particular time point.
+
+### Plot 1
+```{r, GA1 cor by dif windows}
 ginmin = 0
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 2
+
+```{r, GA1 cor by dif windows 2}
 ginmin = 5000
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 3
+```{r, GA1 cor by dif windows 3}
 ginmin = 10000
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 4
+```{r, GA1 cor by dif windows 4}
 ginmin = 15000
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 5
+```{r, GA1 cor by dif windows 5}
 ginmin = 20000
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 6
+```{r, GA1 cor by dif windows 6}
 ginmin = 25000
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 7
+```{r, GA1 cor by dif windows 7}
 ginmin = 30000
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 8
+```{r, GA1 cor by dif windows 8}
 ginmin = 35000
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 9
+```{r, GA1 cor by dif windows 9}
 ginmin = 40000
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 10
+```{r, GA1 cor by dif windows 10}
 ginmin = 45000
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "her", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-```
-
-## Correlation across time
-
-```{r, her cor and pheno}
-her_pattern <- unique(paste0(her_tall_tall_file$snake_mu_rate, "_", her_tall_tall_file$snake_mu_effect_sd,"_",her_tall_tall_file$newt_mu_rate, "_", her_tall_tall_file$newt_mu_effect_sd, "_", her_tall_tall_file$rep))
-for(i in 1:length(her_pattern)){
-  myine<-cor_trends_by_gen(her_tall_tall_file, her_cor_tall_file, "test", "her", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=her_pattern[i])
-  plot(myine)
-}
-
-```
-
-## What happens over time (looking at the beginning. middle, and late part of my simulations)
+suppressMessages(print(hist_cors_by_gen_col_rep(her_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+## {-}
+
+All plots look the same.
+All correlations are centered around 0 and do not go past +/- 0.5.
+There are no strong correlations.
+I can conclude that there would be no random correlations when newt and snake phenotype is drawn at random.
+A good subsequent experiment would be to make one of these phenotype heritable and the other not.
+Could this situation lead to high spatial correlations or a high phenotype.
+
+## Correlation across time {.tabset}
+
+In this next section I look at the mean newt/snake phenotype (red/blue) and spatial correlation (pink) across time for all GAs. Below we will look at 3 randomly chosen results.
+
+### Random 1
+```{r, GA1 cor and pheno}
+GA1_pattern <- unique(paste0(her_tall_tall_file$snake_mu_rate, "_", her_tall_tall_file$snake_mu_effect_sd,"_",her_tall_tall_file$newt_mu_rate, "_", her_tall_tall_file$newt_mu_effect_sd, "_", her_tall_tall_file$rep))
+
+myrandomlist=sample.int(length(GA1_pattern), 3)
+
+# for(i in myrandomlist){
+#   myine<-cor_trends_by_gen(her_tall_tall_file, her_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   plot(myine)
+# }
+
+cor_trends_by_gen(her_tall_tall_file, her_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2
+```{r, random cor-pheno plot 2}
+
+cor_trends_by_gen(her_tall_tall_file, her_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3
+```{r, random cor-pheno plot 3}
+
+cor_trends_by_gen(her_tall_tall_file, her_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+Each of these randomly chosen simulation results look very similar.
+The mean phenotypes of newts and snake jump around every generation, which creates a very fuzzy caterpillar look.
+The newt and snake spatial phenotype correlation hovers around 0.
+There are a few instances where it gets close to +/- 0.5, but never crosses.
+The spatial correlation also jumps around (does not continue in a strait line).
+
+## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+In this experiment phenotypes where not heritable, each individual had a randomly chose phenotype (from a normal distribution).
+The plots that follow will show two things; 1) newt by snake population size with each dot repersenting the difference between snake and newt mean phenotype (blue=snake has a higher phenotype/ red=newt has a higher phenotype), and 2) histograms of the difference between snake and newt phenotype and population size (purple and green, respectively).
+
+### Pheno Beginning
 
@@
 
-for(i in 1:length(unique(her_tall_tall_file$rep))){
-  myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
-  plot(myine)
-  myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
-  suppressMessages(plot(myine))
-}
-
-```
-
-#### Summary
-
-```{r, early plots summary}
+# for(i in 1:length(unique(her_tall_tall_file$rep))){
+#   myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[1])
+```
+
+### Pheno Middle
+
+```{r, middle plots}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(her_tall_tall_file$rep))){
+#   myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[1])
+```
+
+### Pheno End
+
+```{r, end plots}
+
+min_gen=45000
+max_gen=50000
+
+# for(i in 1:length(unique(her_tall_tall_file$rep))){
+#   myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[1])
+```
+
+### Dif Beginning 
+```{r, early plots 1a}
 
@@
 
+# for(i in 1:length(unique(her_tall_tall_file$rep))){
+#   myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[1] )
+
+```
+
+### Dif Middle 
+```{r, early plots 2a}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(her_tall_tall_file$rep))){
+#   myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[1] )
+
+```
+
+### Dif End 
+```{r, early plots 3a}
+
+min_gen=45000
+max_gen=50000
+
+# for(i in 1:length(unique(her_tall_tall_file$rep))){
+#   myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[1] )
+
+```
+
+## {-}
+
+From these results, I can tell that there is a relationship between newt and snake population size.
+Snakes tend to have a larger population size even when the snake and newt phenotypes are even.
+This is likely caused by the increase in fitness when a newt is successfully eaten.
+The phenotypes are very random.
+
+## Summary {.tabset}
+
+The next section of plots contain my main summaries about GA.
+There are four types of plots; plots 1 & 2 observe patterns caused by newt and snake GA when comparing newt population size by snake population size and the difference between snake and newt mean phenotype by snake population size, plots 3 & 4 take a deeper look to see if the GA of snake or newt affects the difference between phenotypes.
+In these four types of plots I will at the beginning, middle, and end of my simulation.
+The color of the points is snake GA and the shape of the points is newt GA.
+The combination of shape and color is the GA of that particular simulation.
+There are for trial (points) for each GA combination.
+
+### Early-Sim Population Size Summary
+
+```{r, early plots summary}
+
+min_gen=100
+max_gen=5000
+GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Mid-Sim Population Size Summary
+```{r, plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+
 # summary
 GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Late-Sim Population Size Summary
+```{r, plots summary 3}
+min_gen=45000
+max_gen=50000
+
+# summary
+GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+```
+
+### Early Difference Summary
+```{r, dif plots summary 1}
+
+min_gen=100
+max_gen=5000
 
@@
 
-#### Heatmap
+### Mid Difference Summary
+```{r, dif plots summary 2}
+min_gen=25000
+max_gen=30000
+
+GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+min_gen=45000
+max_gen=50000
+```
+
+### Late Difference Summary
+```{r, dif plots summary 3}
+GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
+
+### By Snake GA (Early)
+```{r, snakega plots summary 1}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Mid)
+```{r, snakega plots summary 2}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Late)
+```{r, snakega plots summary 3}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Early)
+```{r, newtga plots summary 1}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+
+```
+
+### By Newt GA (Mid)
+```{r, newtga plots summary 2}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VSNewt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+
+```
+
+### By Newt GA (Late)
+```{r, newtga plots summary 3}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+
+```
+
+## {-}
+
+These plots confirm that there no relationship between GA and phenotype.
+There is a relationship between snake and newt population.
+When snake population size is high newt population size is smaller.
+When newts have a high population size, snake population size is smaller.
+These figures show that snakes will tend to have a larger population size when the newt and snake phenotypes are about even.
+
+## Heatmap {.tabset}
+
+The heatmap section is a different visual representation of the mean snake population size or snake-newt phenotype difference of a time slice.
+There will be two plots at different time stages (beginning, middle, and end of my simulation).
+One plot will show the average snake population size with yellow being a high population size and purple being low population size.
+The figure will show the difference between mean snake and newt phenotype, where blue indicated that snakes have a higher phenotype and red indicates that newts have a higher phenotype.
+The x-axis of these plots is the newt GA.
+The y-axis of these plots are the snake GA and trial number.
+Each figure should be read in groups of 4 (matching snake GA).
+
+### Population Size (Early)
 
@@
 build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
-
-### Mid-simulation
-
-```{r, mis plots}
-
-min_gen=10000
-max_gen=15000
-rep=0
-
-for(i in 1:length(unique(her_tall_tall_file$rep))){
-  myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
-  plot(myine)
-  myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
-suppressMessages(plot(myine))
-}
-
-```
-
-#### Summary
-
-```{r, mid plots summary}
-
-min_gen=10000
-max_gen=15000
-
-# summary
-GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-```
-
-#### Heatmap
-
-```{r, mid plots Heatmap}
-
-min_gen=10000
-max_gen=15000
+```
+
+### Population Size (Mid)  
+```{r, early plots Heatmap 2}
+min_gen=25000
+max_gen=30000
 #heatmap
@@
 
-build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
-
-### Late simulation
-
-```{r, late plots}
-
-min_gen=45000
-max_gen=50000
-
-for(i in 1:length(unique(her_tall_tall_file$rep))){
-  myine<-whale_gen(her_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i])
-  plot(myine)
-  myine<-two_hist(her_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(her_tall_tall_file$rep)[i] )
-  suppressMessages(plot(myine))
-}
-
-```
-
-#### Summary
-
-```{r, late plots summary}
-
-min_gen=45000
-max_gen=50000
-
-# summary
-GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-GA_summary(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-```
-
-#### Heatmap
-
-```{r, late plots Heatmap}
-
+```
+
+### Population Size (Late) 
+```{r, early plots Heatmap 3}
 min_gen=45000
@@
 build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
+```
+
+### Phenotype (Early) 
+```{r, early plots Heatmap pheno 1}
+min_gen=100
+max_gen=5000
 build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
+```
+
+### Phenotype (Mid) 
+```{r, early plots Heatmap pheno 2}
+
+min_gen=25000
+max_gen=30000
+#heatmap
+
+build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### Phenotype (Late) 
+```{r, early plots Heatmap pheno 3}
+min_gen=45000
+max_gen=50000
+#heatmap
+
+build_heatmap(her_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+```
+
+## {-}
+
+There is very little agreement between trials in both snake population size and phenotype differences.
+Most colors tend to be in the center of the two extremes.
+The results change drastically between each of the time slices.
 
@@
 
-### file
-
-```{r, cor grid by location}
-
-#her_grid_tall_file
-
-file_name= "Snake_1e-11_5_Newt_1e-11_5_0"
-#Snake_1e-09_0.05_Newt_1e-09_0.05_2
-#Snake_1e-08_0.005_Newt_1e-11_0.158_0
-
-spegen=20001
-#unique(her_grid_tall_file$snake_newt_rep)
-her<-her_her_grid_tall_file[which(her_her_grid_tall_file$snake_newt_rep==file_name & her_her_grid_tall_file$generation==spegen),]
-
-her_mean = her[,grepl("generation|mean", names(her)) ]
-
-her_data_long_mean <- gather(her_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-her_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(her_data_long_mean$condition, "_", 4)
-
-her_data_long_mean_short<-her_data_long_mean
-
-her_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-her_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(her_data_long_mean_short)+
+This sections takes a more in depth view of how newt and snake phenotype can be correlated on a local level.
+I look at the mean phenotype, phenotype standard deviation (sd), max phenotype, min phenotype, and population of newts and snakes for a time point at the beginning, middle and end of my simulation.
+Each plot shows a local average of my test parameter (mean, sd, max,  ...) for a smaller area of my larger map.
+Newt are represented by circles, and snake are represented by squares.
+Graphs with a phenotype parameter range from low (purple) through blue and green to a high (yellow).
+The population size figures range from low (purple) through pink and orange to a high (yellow).
+When not enough individuals where in an area the shape is colored grey.
+The second smaller plot in the figure shows the newt by snake on the current parameter with point color indication location (corner=pink, edge=green, middle=blue).
+
+### Early Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid high cor mean}
+
+#her_her_grid_tall_file
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA1<-her_her_grid_tall_file[which(her_her_grid_tall_file$snake_newt_rep==file_name & her_her_grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
   labs(title = "Mean Phenotype of Locations",
@@
               fill = "Toxicity/Resistance")+
-  geom_point(data = her_data_long_mean_short[which(her_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = her_data_long_mean_short[which(her_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
   scale_fill_viridis_c()+
@@
 
-snake<-her_data_long_mean_short[which(her_data_long_mean_short$species=="snake"),]
-newt_her<-her_data_long_mean_short[which(her_data_long_mean_short$species=="newt"),]
-newt_her$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_her$measurement), use="complete.obs")
-
-newt_her$info[newt_her$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_her$info[newt_her$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_her$info[is.na(newt_her$info)]<- "middle"
-
-extra_plot <- ggplot(newt_her)+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
   ggtitle("Mean Phenotype") +
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
+```
+
+#### SD 
+```{r, cor grid high cor SD}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid high cor max}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid high cor min}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid high cor popsize}
+
+# popsize
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+#her_her_grid_tall_file population size
+
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}
+
+### Middle Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid zerp cor mean}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA1<-her_her_grid_tall_file[which(her_her_grid_tall_file$snake_newt_rep==file_name & her_her_grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### SD 
+```{r, cor grid zero cor SD}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid zero cor max}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid zero cor min}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid zer cor popsize}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}
+
+### Late Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid neg cor mean}
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+# file_name= "Snake_1e-08_0.005_Newt_1e-11_0.158_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-11_0.158_3"
+# file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-09_0.0158_0"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA1<-her_her_grid_tall_file[which(her_her_grid_tall_file$snake_newt_rep==file_name & her_her_grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### SD 
+```{r, cor grid neg cor SD}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid neg cor max}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid neg cor min}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid neg cor popsize}
+
+# max phenotype
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}

### 2022-09-06 graphs_newt_snakes/no_interact.Rmd
writing my interpretations

@@
 ---
-title: "no interaction"
+title: "No Interaction"
 output: html_document
@@
 library(knitr)
+library(kableExtra)
 library("reshape")
+library(ggpubr)
+theme_set(theme_pubr())
+library(stringr)
+library(patchwork)
 
@@
 
+# Important file names
+file_name= "Snake_1e-11_5_Newt_1e-11_5_0"
+file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+inter_tall_tall_file
+inter_cor_tall_file
+inter_inter_grid_tall_file
+
 ```{r, cor box set up}
@@
   real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  unique(file$sim)
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  #file=inter_cor_tall_file
+  #file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  myplot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
   ylim(-1.1, 1.1)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
-  xlab(x_label) + ylab(y_label)+
+  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  #xlab(x_label) + ylab(y_label)+
   geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=GA3_tall_tall_file
-#cfile=GA3_cor_tall_file 
+#file=inter_tall_tall_file
+#cfile=inter_cor_tall_file 
  # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=GA3_tall_tall_file
+  #file=inter_tall_tall_file
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(GA3_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
-
-```
-
-```{r, general file and graph making}
-
-#the functions to make the params file and the summary and heatmap figures
-
-create_parm_file <- function(file, min_gen, max_gen){
-params <- data_frame()
-
-for(i in 1:length(unique(file$newt_snake_rep))){
-
-  pattern=unique(file$newt_snake_rep)[i]
-  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep ==pattern),]
-
-  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
-                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
-                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
-                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
-                           Newt_pop_size=mean(sumitup$Newt_pop_size),
-                           Snake_pop_size=mean(sumitup$Snake_pop_size),
-                           dif=mean(sumitup$dif),
-                           snake_mu_rate=sumitup$snake_mu_rate[1],
-                           newt_mu_rate=sumitup$newt_mu_rate[1],
-                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
-                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
-                           rep=sumitup$rep[1])
-
-  params <- rbind(params, params_temp)
-}
-
-params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
-params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
-params$newt_snake <- paste0(params$newt, "_", params$snake)
-return(params)
-}
-
-GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
-
-file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-
-params<-create_parm_file(file, min_gen, max_gen)
-
-my_plot <- ggplot(params) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
-#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  #facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
-
-return(my_plot)
-}
-
-build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
-  file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
-
-  params<-create_parm_file(file, min_gen, max_gen)
-
- my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
-
- if(red_blue==FALSE){
-  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
-  }
- if(red_blue==TRUE){
-  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
- }
-
-  return(my_plot)
-}
-
-trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
-
-   plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
-    facet_wrap(~sim)+
-    geom_line(aes(generation, dif, group=rep, col="dif"))+
-    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
-    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
-    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
-    ylim(-1.,2.5)+
-    xlab(x_label) + ylab(y_label)+
-    scale_color_manual(name = "Type",
-values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
-labels = c("Snake", "Newt", "Dif"))+
-    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
-                      strip.background = element_blank(), strip.text.x = element_blank(),
-                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
-                      axis.title.y = element_blank())
-  return(plot)
-}
-
-whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
-  xlab(x_label) + ylab(y_label)+
-  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      # strip.background = element_blank(), 
-                      # strip.text.x = element_blank(), 
-                      # panel.grid.major = element_blank(), 
-                      # panel.grid.minor = element_blank(),
-                      # panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
-pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
-  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
-  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
-  true_max <- max(abs(themin), abs(themax))
-dif <- ggplot(file) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
-  xlim((-1*themax)-5, themax+5)+
-  theme(plot.title = element_text(size=5)) +
-  facet_wrap(~sim)+
-  geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      # strip.background = element_blank(), 
-                      # strip.text.x = element_blank(), 
-                      # panel.grid.major = element_blank(), 
-                      # panel.grid.minor = element_blank(),
-                      # panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-}
-
-pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
-
-  themin <- min(file$dif) 
-  themax <- max(file$dif)
-  true_max <- max(abs(themin), abs(themax))
-dif <- ggplot(file) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(dif), fill="aquamarine4")+
-  xlim((-1*true_max)-1, true_max+1)+
-
-  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      # strip.background = element_blank(), 
-                      # strip.text.x = element_blank(), 
-                      # panel.grid.major = element_blank(), 
-                      # panel.grid.minor = element_blank(),
-                      # panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
-two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
-
-  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
-  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
-  thedifmin <- min(file$dif) 
-  thedifmax <- max(file$dif)
-  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
-
-  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
-dif <- ggplot(file) +
-
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
-  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
-  scale_y_continuous(labels = scales::percent)+
-  xlim((-1*true_max)-1, true_max+1)+
-  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      # strip.background = element_blank(), 
-                      # strip.text.x = element_blank(), 
-                      # panel.grid.major = element_blank(), 
-                      # panel.grid.minor = element_blank(),
-                      # panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
-two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
-
-  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
-  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
-  thedifmin <- min(file$dif) 
-  thedifmax <- max(file$dif)
-  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
-
-  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
-
-dif <- ggplot(file) +
-
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
-  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
-  scale_y_continuous(labels = scales::percent)+
-  xlim((-1*true_max)-1, true_max+1)+
-  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      #strip.background = element_blank(), 
-                      strip.text.x = element_blank(), 
-                      #panel.grid.major = element_blank(), 
-                      #panel.grid.minor = element_blank(),
-                      #panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
-two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=inter_tall_tall_file
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
-
-  thepopmin <- min(file$newt_deaths)
-  thepopmax <- max(file$newt_deaths)
-  thedifmin <- min(file$snake_deaths) 
-  thedifmax <- max(file$snake_deaths)
-  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
-
-  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
-
-dif <- ggplot(file) +
-
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
-  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
-  #scale_y_continuous(labels = scales::percent)+
-  #xlim((-1*true_max)-1, true_max+1)+
-  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  #geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      #strip.background = element_blank(), 
-                      strip.text.x = element_blank(), 
-                      #panel.grid.major = element_blank(), 
-                      #panel.grid.minor = element_blank(),
-                      #panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
 #two_hist_death_all_rep(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
@@
 
+notes
+
+## Mean Phenotype Whole Simulation {.tabset}
+
+notes
+
+### Phenotype differences
 ```{r, graphing by gen}
-trends_by_gen(inter_tall_tall_file, title="Space Tall: Newt VS Snake Population Size inter", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
-
+trends_by_gen(inter_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
+
+#aggregate(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$dif, list(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
+
+```
+
+### Table of average Differences
+
+```{r, average difference}
 aggregate(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$dif, list(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$group), FUN=mean)
-
-#aggregate(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$dif, list(inter_tall_tall_file[which(inter_tall_tall_file$generation>=100 & inter_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
-
-```
-
-#### Connection between higinter phenotype and population
-
+```
+
+## {-}
+
+Explain
+
+## Connection between higher phenotype and population {.tabset}
+
+Notes
+
+### Phenotype differences
 ```{r, whale}
@@
 whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-
-suppressMessages(print(two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
-
-suppressMessages(print(two_hist_all_rep(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
-
-```
+```
+
+### Phenotype & Populationsize differences
+```{r, popsize and pheno}
+
+suppressMessages(print(two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+
+```
+
+## {-}
+
+explain
 
@@
 
-Legend:
-
-- "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
-- "CB" = num_newts_By_num_snakes (Green)
-- "CC" = sum_newt_pheno_By_num_snake (Blue)
-- "CD" = sum_snake_pheno_By_num_newt (Purple)
+notes
 
@@
 
-boxplot_cors_by_gen(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-four_types_boxplot_cors_by_gen(inter_cor_tall_file, "Simulation four Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-```
-
-```{r, inter cor by dif windows}
-
+boxplot_cors_by_gen(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(inter_cor_tall_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+After looking at this figure, I can see that there is a larger range of correlation values.
+The can sometimes be positive, near 0, or negative.
+Very few reach (or come near) the real newt-snake correlation.
+How do you find the correct time slice to look for spatial correlation?
+How would these phenotypes become spatially correlated and then become not spatially correlated.
+
+## Correlation Histograms {.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
+
+### Plot 1
+```{r, GA1 cor by dif windows}
 ginmin = 0
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 2
+
+```{r, GA1 cor by dif windows 2}
 ginmin = 5000
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 3
+```{r, GA1 cor by dif windows 3}
 ginmin = 10000
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 4
+```{r, GA1 cor by dif windows 4}
 ginmin = 15000
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 5
+```{r, GA1 cor by dif windows 5}
 ginmin = 20000
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 6
+```{r, GA1 cor by dif windows 6}
 ginmin = 25000
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 7
+```{r, GA1 cor by dif windows 7}
 ginmin = 30000
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 8
+```{r, GA1 cor by dif windows 8}
 ginmin = 35000
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 9
+```{r, GA1 cor by dif windows 9}
 ginmin = 40000
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+### Plot 10
+```{r, GA1 cor by dif windows 10}
 ginmin = 45000
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-```
-
-## Correlation across time
-
-```{r, inter cor and pheno}
-inter_pattern <- unique(paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd, "_", inter_tall_tall_file$rep))
-for(i in 1:length(inter_pattern)){
-  myine<-cor_trends_by_gen(inter_tall_tall_file, inter_cor_tall_file, "test", "inter", "newt/snake GAs&rep","otinter", "Cor", min_gen=100, max_gen=50000, pattern=inter_pattern[i])
-  plot(myine)
-}
-
-```
-
-## What happens over time (looking at the beginning. middle, and late part of my simulations)
+suppressMessages(print(hist_cors_by_gen_col_rep(inter_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
+## {-}
+
+exp
+
+## Correlation across time {.tabset}
+
+notes
+
+### Random 1
+```{r, GA1 cor and pheno, results="hide"}
+GA1_pattern <- unique(paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd, "_", inter_tall_tall_file$rep))
+
+myrandomlist=sample.int(length(GA1_pattern), 3)
+
+# for(i in myrandomlist){
+#   myine<-cor_trends_by_gen(inter_tall_tall_file, inter_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   plot(myine)
+# }
+
+cor_trends_by_gen(inter_tall_tall_file, inter_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2
+```{r, random cor-pheno plot 2}
+
+cor_trends_by_gen(inter_tall_tall_file, inter_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3
+```{r, random cor-pheno plot 3}
+
+cor_trends_by_gen(inter_tall_tall_file, inter_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+I still wonder why the correlation values go up and down, because the mean newt and snake phenotype keeps going up.
+I wonder if the individuals might be moving around too much.
+I wonder what would happen on a larger map?
+
+## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+
+### Pheno Beginning
 
@@
 
-for(i in 1:length(unique(inter_tall_tall_file$rep))){
-  myine<-whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i])
-  plot(myine)
-  myine<-two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i] )
-  suppressMessages(plot(myine))
-}
-
-```
-
-#### Summary
-
-```{r, early plots summary}
+# for(i in 1:length(unique(inter_tall_tall_file$rep))){
+#   myine<-whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[1])
+```
+
+### Pheno Middle
+
+```{r, middle plots}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(inter_tall_tall_file$rep))){
+#   myine<-whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[1])
+```
+
+### Pheno End
+
+```{r, end plots}
+
+min_gen=45000
+max_gen=50000
+
+# for(i in 1:length(unique(inter_tall_tall_file$rep))){
+#   myine<-whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[1])
+```
+
+### Dif Beginning 
+```{r, early plots 1a}
 
@@
 
+# for(i in 1:length(unique(inter_tall_tall_file$rep))){
+#   myine<-two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[1] )
+
+```
+
+### Dif Middle 
+```{r, early plots 2a}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(inter_tall_tall_file$rep))){
+#   myine<-two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[1] )
+
+```
+
+### Dif End 
+```{r, early plots 3a}
+
+min_gen=45000
+max_gen=50000
+
+# for(i in 1:length(unique(inter_tall_tall_file$rep))){
+#   myine<-two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[1] )
+
+```
+
+## {-}
+
+explane
+
+## Summary {.tabset}
+
+notes
+
+### Early-Sim Population Size Summary
+
+```{r, early plots summary}
+
+min_gen=100
+max_gen=5000
+GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Mid-Sim Population Size Summary
+```{r, plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+
 # summary
 GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Late-Sim Population Size Summary
+```{r, plots summary 3}
+min_gen=45000
+max_gen=50000
+
+# summary
+GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+```
+
+### Early Difference Summary
+```{r, dif plots summary 1}
+
+min_gen=100
+max_gen=5000
 
@@
 
-#### Heatmap
+### Mid Difference Summary
+```{r, dif plots summary 2}
+min_gen=25000
+max_gen=30000
+
+GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
+
+### Late Difference Summary
+```{r, dif plots summary 3}
+min_gen=45000
+max_gen=50000
+GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
+
+### By Snake GA (Early)
+```{r, snakega plots summary 1}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Mid)
+```{r, snakega plots summary 2}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Late)
+```{r, snakega plots summary 3}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Early)
+```{r, newtga plots summary 1}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Mid)
+```{r, newtga plots summary 2}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Late)
+```{r, newtga plots summary 3}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+## {-}
+
+expla
+
+## Heatmap {.tabset}
+
+notes
+
+### Population Size (Early)
 
@@
 build_heatmap(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-build_heatmap(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
-
-### Mid-simulation
-
-```{r, mis plots}
-
-min_gen=10000
-max_gen=15000
-rep=0
-
-for(i in 1:length(unique(inter_tall_tall_file$rep))){
-  myine<-whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i])
-  plot(myine)
-  myine<-two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i] )
-suppressMessages(plot(myine))
-}
-
-```
-
-#### Summary
-
-```{r, mid plots summary}
-
-min_gen=10000
-max_gen=15000
-
-# summary
-GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-```
-
-#### Heatmap
-
-```{r, mid plots Heatmap}
-
-min_gen=10000
-max_gen=15000
+```
+
+### Population Size (Mid)  
+```{r, early plots Heatmap 2}
+min_gen=25000
+max_gen=30000
 #heatmap
@@
 
-build_heatmap(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
-
-### Late simulation
-
-```{r, late plots}
-
-min_gen=45000
-max_gen=50000
-
-for(i in 1:length(unique(inter_tall_tall_file$rep))){
-  myine<-whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i])
-  plot(myine)
-  myine<-two_hist(inter_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(inter_tall_tall_file$rep)[i] )
-  suppressMessages(plot(myine))
-}
-
-```
-
-#### Summary
-
-```{r, late plots summary}
-
-min_gen=45000
-max_gen=50000
-
-# summary
-GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-GA_summary(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-```
-
-#### Heatmap
-
-```{r, late plots Heatmap}
-
+```
+
+### Population Size (Late) 
+```{r, early plots Heatmap 3}
 min_gen=45000
@@
 build_heatmap(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
+```
+
+### Phenotype (Early) 
+```{r, early plots Heatmap pheno 1}
+min_gen=100
+max_gen=5000
 build_heatmap(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
+```
+
+### Phenotype (Mid) 
+```{r, early plots Heatmap pheno 2}
+
+min_gen=25000
+max_gen=30000
+#heatmap
+
+build_heatmap(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### Phenotype (Late) 
+```{r, early plots Heatmap pheno 3}
+min_gen=45000
+max_gen=50000
+#heatmap
+
+build_heatmap(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+```
+
+## {-}
+
+exp
 
@@
 
-### file
-
-```{r, cor grid by location}
-
-#inter_grid_tall_file
-
-file_name= "Snake_1e-11_5_Newt_1e-11_5_0"
+notes
+
+### Early Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid high cor mean}
+
+#inter_inter_grid_tall_file
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+
 #Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
 
-spegen=20001
-#unique(inter_grid_tall_file$snake_newt_rep)
-inter<-inter_inter_grid_tall_file[which(inter_inter_grid_tall_file$snake_newt_rep==file_name & inter_inter_grid_tall_file$generation==spegen),]
-
-inter_mean = inter[,grepl("generation|mean", names(inter)) ]
-
-inter_data_long_mean <- gather(inter_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-inter_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(inter_data_long_mean$condition, "_", 4)
-
-inter_data_long_mean_short<-inter_data_long_mean
-
-inter_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-inter_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(inter_data_long_mean_short)+
+GA1<-inter_inter_grid_tall_file[which(inter_inter_grid_tall_file$snake_newt_rep==file_name & inter_inter_grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
   labs(title = "Mean Phenotype of Locations",
@@
               fill = "Toxicity/Resistance")+
-  geom_point(data = inter_data_long_mean_short[which(inter_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = inter_data_long_mean_short[which(inter_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
   scale_fill_viridis_c()+
@@
 
-snake<-inter_data_long_mean_short[which(inter_data_long_mean_short$species=="snake"),]
-newt_inter<-inter_data_long_mean_short[which(inter_data_long_mean_short$species=="newt"),]
-newt_inter$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_inter$measurement), use="complete.obs")
-
-newt_inter$info[newt_inter$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_inter$info[newt_inter$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_inter$info[is.na(newt_inter$info)]<- "middle"
-
-extra_plot <- ggplot(newt_inter)+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
   ggtitle("Mean Phenotype") +
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-```{r, cor grid by location}
-
-#inter_grid_tall_file
-
-file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
-#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
-
-spegen=13001
-#unique(inter_grid_tall_file$snake_newt_rep)
-inter<-inter_inter_grid_tall_file[which(inter_inter_grid_tall_file$snake_newt_rep==file_name & inter_inter_grid_tall_file$generation==spegen),]
-
-inter_mean = inter[,grepl("generation|mean", names(inter)) ]
-
-inter_data_long_mean <- gather(inter_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-inter_data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(inter_data_long_mean$condition, "_", 4)
-
-inter_data_long_mean_short<-inter_data_long_mean
-
-inter_data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-inter_data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(inter_data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
+```
+
+#### SD 
+```{r, cor grid high cor SD}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
               subtitle = paste0(file_name, ", Generation: ", spegen),
               fill = "Toxicity/Resistance")+
-  geom_point(data = inter_data_long_mean_short[which(inter_data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = inter_data_long_mean_short[which(inter_data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
   scale_fill_viridis_c()+
@@
 
-snake<-inter_data_long_mean_short[which(inter_data_long_mean_short$species=="snake"),]
-newt_inter<-inter_data_long_mean_short[which(inter_data_long_mean_short$species=="newt"),]
-newt_inter$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_inter$measurement), use="complete.obs")
-
-newt_inter$info[newt_inter$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_inter$info[newt_inter$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_inter$info[is.na(newt_inter$info)]<- "middle"
-
-extra_plot <- ggplot(newt_inter)+
-  ggtitle("Mean Phenotype") +
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
   xlab("Newt") + ylab("Snake")+
@@
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
+```
+
+#### Max Phenotype 
+```{r, cor grid high cor max}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid high cor min}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid high cor popsize}
+
+# popsize
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=101
+#inter_inter_grid_tall_file population size
+
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}
+
+### Middle Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid zerp cor mean}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA1<-inter_inter_grid_tall_file[which(inter_inter_grid_tall_file$snake_newt_rep==file_name & inter_inter_grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### SD 
+```{r, cor grid zero cor SD}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid zero cor max}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid zero cor min}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid zer cor popsize}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=25001
+
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}
+
+### Late Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid neg cor mean}
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+ #"Snake_1e-11_0.158_Newt_1e-10_0.05_0"
+# file_name= "Snake_1e-08_0.005_Newt_1e-11_0.158_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-11_0.158_3"
+# file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_0"
+# file_name= "Snake_1e-10_0.05_Newt_1e-09_0.0158_0"
+#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
+
+GA1<-inter_inter_grid_tall_file[which(inter_inter_grid_tall_file$snake_newt_rep==file_name & inter_inter_grid_tall_file$generation==spegen),]
+
+GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
+
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+
+data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
+
+data_long_mean_short<-data_long_mean
+
+data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_mean_short)+
+  labs(title = "Mean Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
+newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### SD 
+```{r, cor grid neg cor SD}
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+# SD
+
+GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
+
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+
+data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
+
+data_long_sd_short<-data_long_sd
+
+data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_sd_short)+
+  labs(title = "SD Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
+newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("SD Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Max Phenotype 
+```{r, cor grid neg cor max}
+
+# max phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+
+GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
+
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+
+data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
+
+data_long_max_short<-data_long_max
+
+data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_max_short)+
+  labs(title = "Max Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
+newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Max Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Min Phenotype 
+```{r, cor grid neg cor min}
+
+# min phenotype
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
+
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+
+data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
+
+data_long_min_short<-data_long_min
+
+data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+main_plot<-ggplot(data_long_min_short)+
+  labs(title = "Min Phenotype of Locations",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
+newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
+newt$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
+
+newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[is.na(newt$info)]<- "middle"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Min Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+```
+
+#### Population Size
+```{r, cor grid neg cor popsize}
+
+# max phenotype
+
+file_name="Snake_1e-08_0.005_Newt_1e-08_0.005_3"
+spegen=48001
+GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
+
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+
+GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
+
+GA1_data_long_ind_short<-GA1_data_long_ind
+
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+
+GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
+
+main_plot<-ggplot(GA1_data_long_ind_short)+
+  labs(title = "Locations of Ind",
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Number of Individuals")+
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c(option = "plasma")+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
+newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
+newt_GA1$snake_value <- snake$measurement
+cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
+
+newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
+
+extra_plot <- ggplot(newt_GA1)+
+  ggtitle("Num of Ind") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+#try to arrage the grids
+
+main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
+
+```
+
+### {-}
 

### 2022-09-09 graphs_newt_snakes/no_interact.Rmd
I finished my writing, got some coor results

@@
 
-In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-interactible trait. I expect to see no spatial phenotype correlation
+In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-interactive trait.
+Newts and snakes have heritable traits, but their interaction is not determined by their phenotype.
+Instead, when newts and snakes interact, the outcome is determined by a coin flip.
+SLiM code changes: (1) prob_of_survive = runif(1); survive = runif(1) < prob_of_survive; //Things changes probably of snakes survival to 50%.
+If snake survives, newt dies.
+If snake dies, newt survives.
+Interaction not based on phenotypes
 
@@
 
-What happens when a co-evolving trait is not interitable?
+What happens when a co-evolving trait is not interactive?
 
 ## Background
+
+In this experiment I keep everything about my simulation the same as GA1 tall (landscape size, fitness, cost, GA combinations, heritability) and change the interaction.
+Without the interaction of newts and snakes relying on their phenotype, there is no selection selecting for higher phenotypes.
+This experiment took away interspecific competition, but left in intraspecific competition (density dependent).
+I will explore how the lack of newt-snake phenotype dependent interaction affect newt/snake mean phenotype and spatial correlations.
+I predict that there will be no spatial phenotype correlation.
+I have no idea what to predict about the phenotypes.
 
@@
 ```
-
-# Important file names
-file_name= "Snake_1e-11_5_Newt_1e-11_5_0"
-file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
-inter_tall_tall_file
-inter_cor_tall_file
-inter_inter_grid_tall_file
 
@@
 
-## Mean Phenotype Whole Simulation
-
-notes
-
 ## Mean Phenotype Whole Simulation {.tabset}
 
-notes
+This section explores how mutation rate with mutation effect size (GAs of newts and snakes) and the lack of newt-snake interaction affects newt and snake phenotypes over time.
+This figure has 16 GA combinations with four trials per combination.
+Mean newt phenotype is represented by the red lines, while mean snake phenotype is represented by the blue lines.
+The black lines is the difference between snake and newt mean phenotype.
+This section also has a table that states the average difference between snake and newt mean phenotypes from 100-50,000 generations.
 
@@
 
-Explain
+Wow, this figure is really interesting.
+It is very mirrored across the diagonal.
+It seems like when there is a GA with more effect size variance the species' phenotype drops (fairly quickly) to 0.
+The phenotypes of newts and snakes tend to stay around one or drop to 0.
+None of the phenotypes continuously increase.
+By looking at the table I see that the biggest difference in phenotype occurs when one species has a GA of 1e-11_5 and the other has a GA of 1e-08_0.005.
+I notices when GA were either the same or low (1e-08_0.005, 1e-09_0.05) the difference between snake and newt phenotype was small (~ 0.2 or lower).
+When the GA was high (1e-10_0.5, 1e-11_5) or further apart the difference between snake and newt phenotype was large (~ 0.43 or higher).
+Species with a higher mutational variance tended to have a lower mean phenotype.
+The difference in mutational variance lead to a positive or negative mean phenotype difference (when newts had a higher mutational variance the snake-newt mean phenotype difference was positive).
 
@@
 
-Notes
+The newt few figures check to see if there is a connection between population size and phenotype.
+The first figure compares the population size of newts and snake to the difference between mean snake and newt phenotype for a time slice (5,000-10,000 generations).
+Color in this plot represents the difference between snake and newt phenotype, with blue indicating snakes have a larger phenotype and red indicating newts have a larger phenotype.
+Cream color points indicate that the two phenotypes are nearly the same.
+The second figure present the histograms of the difference between snake and newt population size (green) and phenotype (purple) for a time slice (5,000-10,000 generations).
 
@@
 
-whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(inter_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
-explain
+The Newt VS Snake Population Size figure is very symmetrical.
+The species that has a higher mutational variance tends to have a lower phenotype.
+This figure can also be read as: the species with a larger mutational effect size has a lower phenotype or the species with a higher mutation rate has a higher phenotype.
+This plot matches what I observed in the section above: when GA were either the same or low (1e-08_0.005, 1e-09_0.05) the difference between snake and newt phenotype was small & when the GA was high (1e-10_0.5, 1e-11_5) or further apart the difference between snake and newt phenotype was large.
+When looking at the phenotype and population size differences plots I noticed a few patterns.
+Going across the difference in phenotype size moves right (snakes have a larger population size), going down the difference in phenotype size moves left (newts have a larger population size).
+The population sizes say about the same.
+Population size is not connected to phenotype?
 
@@
 
-notes
+The correlation section looks at how correlated newt and snake phenotypes are at a local level.
+The simulation map is divided into smaller grids, then the mean phenotype of newts and snakes is collected and a correlation value is calculated.
+The figure below shows the results of four trials for all 16 GA combinations.
+Snake mutation rate decreases while mutation effect size increase from left to right.
+Newt mutation rate decreases while mutation effect size increase from top to bottom.
+Newt and snake mutation rate and effect size are equal across the diagonal.
 
@@
 
-After looking at this figure, I can see that there is a larger range of correlation values.
-The can sometimes be positive, near 0, or negative.
-Very few reach (or come near) the real newt-snake correlation.
-How do you find the correct time slice to look for spatial correlation?
-How would these phenotypes become spatially correlated and then become not spatially correlated.
+After looking at this figure, I can see that there is a range of correlation values.
+The correlation values can sometimes be positive, near 0, or negative.
+Some approach the real newt-snake correlation, which was unexpected.
+How often would newt and snake phenotypes be randomly correlated?
+How does individuals movements affect spatial correlation (my thought here: newts and snake phenotypes can become correlated if a newt and snake who live in a general vicinity both get a mutation that increases their fitness and the mutation spreads)?
+How does newt and snake interaction change correlation and the way a new mutation spreads?
 
@@
 
-exp
+As I move through time chunks there is a lot of movement of spatial correlation values.
+Most correlation values are near 0, but a few become very correlated (both positive and negative).
+The most noticeable ones occur in the first group of four (A, B, E, F).
+I wonder if there is an even number of strong positive and negative correlation values (this would make it more of a random process).
 
@@
 
-notes
+This next section examines how newt and snake mean phenotype (red and blue) and the newt-snake phenotype (pink) is correlated across time.
+There are three randomly chosen figures to represent the 16 GA combinations.
 
 ### Random 1
-```{r, GA1 cor and pheno, results="hide"}
+```{r, GA1 cor and pheno}
 GA1_pattern <- unique(paste0(inter_tall_tall_file$snake_mu_rate, "_", inter_tall_tall_file$snake_mu_effect_sd,"_",inter_tall_tall_file$newt_mu_rate, "_", inter_tall_tall_file$newt_mu_effect_sd, "_", inter_tall_tall_file$rep))
@@
 
-I still wonder why the correlation values go up and down, because the mean newt and snake phenotype keeps going up.
+In this simulation experiment, newt and snakes have an interaction not based on their phenotype.
+This reduces the section presser placed on newts and snakes in a co-evolutionary arms race.
+In each of these examples newt/snake mean phenotype(s) drop close to 0 or stay around one.
+Potentially, they either drop or stay at one due a combination of mutation effect size and phenotype cost.
+Theoretically, if there is a cost for having a higher phenotype and no benefit, the mean phenotype would decrease.
+However, the mean phenotype is more likely to decrease to zero is there is a larger mutation effect size or more mutational variance.
+The spatial correlation goes up and down, making me wonder why.
+There is no reason for there to be high correlation, but it can happen randomly.
 I wonder if the individuals might be moving around too much.
 I wonder what would happen on a larger map?
+It would be cool to look at the spread of different mutations with different GA through the map/grids.
+It would also be interesting to change the number of grids to see if it effects this correlation calculation.
 
@@
 
-This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time (beginning, middle, and end of my simulation).
 The populations start off with about 250 individuals each.
 Each individual has a different genetic background created from msprime.
+Plots show newt by snake population size, with the point color representing the difference between mean snake and newt phenotype.
+The other plots show histograms of difference between snakes and newts phenotype and population size (purple and green).
 
@@
 
-explane
+As seen in some previous plots, results are very mirrored across the diagonal.
+It seems like which ever species has a higher mutational variance or higher mutational effect size had a lower phenotype (seen in both types of figures).
+The populations remained constant across GA combinations (both types of figures).
+After an initial population size increase, population sizes became steady (snakes had a higher population size, probably due to fitness advantage for randomly being successful in eating a newt).
 
@@
 
-notes
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
 
@@
 
-GA_summary_by_species(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(inter_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt Population Size", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
 
@@
 
-expla
+After examining these plots I found that there is no relationship between GA and population size or population size and phenotype.
+However, there is an interaction between GA and phenotype blue/purple on the left and red/green on the right & (to a less noticeable degree) triangle/circle on the left and square/plus on the right (higher mutational variance lead to a lower phenotype).
+When looking at the by snake plot, GA newt GA is lined up from lowest mutation variance to highest mutational variance.
+This suggest that a higher newt variance led to a lower newt phenotype (possibly pushed down due to cost and no interaction).
+This pattern is reversed when looking at the plot of newt GA.
+On the newt GA plot, snake GA is lined up purple, blue, green, and red.
+This also indicates that a higher mutational variance led to a lower phenotype.
+This is really interesting!
 
@@
 
-notes
+This next sections shows the results of the previous section in a more condensed fashion.
+There are two types of plots.
+Each have newt GA on the x-axis and snake GA and trial number on the y-axis.
+The first plot set shows the snake population size, while the second plot set shows the difference between mean snake and newt phenotype.
 
@@
 
-exp
+The results of this section how that there is no relationship between GA and population size (colors seem random).
+There is a ver noticeable relationship between GA and phenotype.
+Again, the difference in phenotype is symmetrical across the diagonal (right diagonal this time).
+Species have a higher phenotype is they have a GA with lower mutational variance.
+This might be due to the mutational effect size distribution and phenotype cost.
+What would change if I re-did this simulation and removed the cost?
+- I think that it is possible for the phenotypes to drift upwards
 
@@
 
-notes
+This is the last results section.
+These are the results from the grid calculations.
+I divided my map up into smaller area (grids) and calculated mean phenotype, SD phenotype, max phenotype, min phenotype, and population size.
+In each of these plots newts are represented by circles and snakes are represented by squares.
+Parameter values increase from a dark color to a lighter color (green-blue themed for phenotype, orange-pinked themed for population size) There is also a subplot that plots each parameter (mean, sd...) of newt by snake colored by map location (red=corner, green=edge, blue=middle).
+I look at the some simulation at one time in the begging, middle, and end.
 
@@
 ### {-}
+
+## Extra
+
+This is a bonus section showing how long my simulation took to get to certain generations
 

### 2022-09-16 graphs_newt_snakes/GA1_tall_redo_md.Rmd
I re ran the GA 1 tall experiment, and examined the results

@@
 Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to.
-This markdown is investigation what is up with the different levels of correlation between rectangles and squares.
+This markdown is investigation what is up with the different levels of correlation between rectangles and squares (in connection with GA1 tall).
 After fixing the row vs column error I looked at the correlation data and found that there was less correlation.
@@
 However, after a closer investigation I found that these correlations were from a rectangle shaped area and not a square one.
-Here, I rerun the experiment with he correct square grids and discuss how the results differ.
+Here, I rerun the experiment with the correct square grids and discuss how the results differ.
 I also aim to investigate how changing the area/shape of the grids will influence correlation results.
-I am also thinking of ways to gather and incorperate allele information.
+I am also thinking of ways to gather and incorporate allele information.
 
@@
 New Landscape 28 by 7 grid: 35*4 H, 35 W
+
+Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.
 
@@
 These slim simulations use the same msprime simulation, but can statistically be different.
+
+The two data sets in this experiment have the same msprime burn-in (16 msprime trees), but have different slim results.
+For the most part the additional slim simulation (the ones with a smaller grid) can be used as additional trials.
+They will only differ in the way correlation and grid values are calculated.
+Cor and Grid files are effected.
+Lit file not effected.
 
@@
 
-Important files
-GA1_tall_tall_file
-GA1_cor_tall_file
-GA1_grid_tall_file
-GA1_tall_tall_7_file
-GA1_cor_tall_7_file
-GA1_grid_tall_7_file
-
 ## Mean Phenotype Whole Simulation {.tabset}
@@
 **Note this is a mean for the entire population.** Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).
+The table shows the mean difference between snake and newt phenotype for the four trials.
+There are two sets of data 5 sections and 7 sections.
+Since we are looking at whole population means, the results of this section do not differ in data collection.
 
@@
 
+The mean phenotype of newts and snakes typically goes up as the number of generation increases.
+When there is a large gap in mutational variance (B, C, E, I) there tends to be some phenotype flat lining.
+Sometimes newt and snakes mean phenotypes are close, while at other times they are further apart.
+The average difference between snake and newt mean phenotypes -2.8 to 2.7 (which is very similar between the two simulation sets).
+
 ## Connection between higher phenotype and population (5 sec) {.tabset}
 
-Notes
-
-### Phenotype differences
+In  previous experiments like GA1 tall map, I saw a connection between newt/snake phenotype and population size.
+Typically, when a species had a higher phenotype they also had a larger population size.
+This relation between phenotype and population size had specific outcomes that depended on the GA of newts and snakes.
+
+This section contains two figures for both data sets.
+The first figure compares the population size of newts and snakes to the difference between mean snake and mean newt phenotype for a time slice (5,000-10,000 generations).
+Color in this plot is the difference between snake and newt phenotype, with blue indicating snakes have a larger phenotype and red indicating newts have a larger phenotype.
+Cream color points indicate that the two phenotypes are nearly the same.
+The second figure present the histograms of the difference between snake and newt population size (green) and phenotype (purple) for a time slice (5,000-10,000 generations).
+Since the data in this section was calculated for whole population 5 sections and 7 sections can be considered the same.
+
+### Phenotype differences (5 sec) 
 ```{r, whale}
@@
 max_gen=10000
-rep=0
-
-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-```
-
-### Phenotype & Populationsize differences
+rep=1
+
+whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+```
+
+### Phenotype & Populationsize differences (5 sec) 
 ```{r, popsize and pheno}
@@
 ```
-
-## {-}
-
-## Connection between higher phenotype and population (7 sec) {.tabset}
-
-Notes
 
@@
 max_gen=10000
-rep=0
-
-whale_gen(GA1_tall_tall_7_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+rep=1
+
+whale_gen(GA1_tall_tall_7_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 The population size is also more variable than the phenotype (difference in population size has a wider range).
+There are minute differences between the 5 section and 7 section figures, but for the most part they are very similar to each-other (similar at the GA combinations level).
 
@@
 
-The next section I aim to look at how correlated newt and snakes are at local populations across the geographical area.
-I am examining correlation between newt and snake phenotypes, population sizes of newts and snakes, amount of toxin and snake population, and the amount of resistance and newt population size.
-I predicted that there would be a positive correlation between the phenotypes, and a negative correlation between population sizes, and the amount of toxin/resistance and population size.
-Below is a legend for the first two plots.
-The third plot is colored by trial.
-
+The next section I aim to look at how correlated newt and snakes are at local populations across the geographical area for both the 5 and 7 sections.
+I am examining correlation between newt and snake phenotypes and I predicted that there would be a positive correlation between the phenotypes.
 I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
 The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
-The second figure shows the the results of all 4 trials for each correlation measurement I made from 10,000-15,000 generations.
-The third plot takes the information from the fist plot and shows the distribution of correlation values by each trial (solid line at 0, dashed line at real newt-snake correlation).
+I try to compare the 5 sections to 7 sections to see if there is a significant difference between the two.
+I will also compare these results to the rectangular correlation values.
 
@@
 
-After looking at this figure, I can see that there is a larger range of correlation values.
-The can sometimes be positive, near 0, or negative.
-Very few reach (or come near) the real newt-snake correlation.
-How do you find the correct time slice to look for spatial correlation?
-How would these phenotypes become spatially correlated and then become not spatially correlated.
+After looking at this figure, I can see that there is a range of correlation values.
+Most spatial phenotype correlation values are at or just above 0.
+There are a few that are very positive or negative.
+I do not see a huge difference between having 5 or 7 sections.
+It would have been better to have done one simulation and spit out these two values (I might rerun this experiment and have more grid values to test, but they would all be in one simulation).
+The spatial correlation results seem lower to the ones that are in GA1 tall (with rectangular grid slices).
+I tested the correlation calculation of squares vs rectangles with Peter in points.RMD.
+We used all individuals data points to see if there was a significant difference between squares and rectangles, but found none.
+It is possible that more or less grids would increase or decrease spatial phenotype correlation, but there might not be a perfect value to get the most accurate understanding of what is going on between newt and snake phenotypes on the local level.
 
@@
 The histogram values are stacked.
+This section only looks at the 5 sections.
 
@@
 
+The spatial correlations move around a lot. None of them line up on the real newt and snake spatial phenotype correlation value ~0.7. (More discussion after the correlation histograms 7 section)
+
 ## Correlation Histograms (7 sec) {.tabset}
@@
 The histogram values are stacked.
+These are the 7 section results.
 
@@
 
+After examining these sets of data, I cannot see a noticeable difference in newt-snake phenotype spatial correlation.
+I would like to run another experiment that collects correlation data for many different grid settings.
+I would also like to see how increasing the size of the map would effect these results.
+I wonder if the area where newts and snakes are co-evolving overlap a grid line.
+How can we tell what is occurring at the individual level?
+Like how specific (beneficial) mutations are moving within populations.
+Or how individuals might be moving into one area because of a lack of other individuals.
+Essentially, what is occurring in my simulation.
+
 ## Correlation across time {.tabset}
 
-notes
+Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
 
 ### Random 1 (5 sec)
-```{r, GA1 cor and pheno, results="hide"}
+```{r, GA1 cor and pheno}
 GA1_pattern <- unique(paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep))
@@
 
+All six of these plots show mean newt and snake phenotype increasing (very few show no change).
+Sometimes, the mean newt and snake phenotype are far apart, but often they are close together.
+The size of the mean phenotype jumps (small or large) is determined by the GA of the species (higher mutation effect size = larger jumps).
+These plots also show that the phenotype spatial correlation fluctuates between being positive and being negative.
+I wonder if there is a connection between the difference in newt and snake mean phenotype and the local spation correlation.
+
 ## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
@@
 Each individual has a different genetic background created from msprime.
+Then each msprime simulation is put into slim and data is generated.
+Plots show newt by snake population size, with the point color representing the difference between mean snake and newt phenotype (red=newts have a higher phenotype and blue=snakes have a higher phenotype).
+The other plots show histograms of difference between snakes and newts phenotype and population size (purple and green).
+First I will look at 5 sections then I will look at 7 sections.
+This is whole population data, there is no difference between the 5 and 7 sections measurements.
 
@@
 
-## What happens over time (looking at the beginning, middle, and late part of my simulations) (7 sec) {.tabset}
-
-This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
-The populations start off with about 250 individuals each.
-Each individual has a different genetic background created from msprime.
+## {.tabset}
 
@@
 
-explane
+The results looked so similar between the 5 sections and 7 sections I had to double check my code!
+(probably because they had the same starting conditions) In the beginning of the simulation both newt and snake population grows.
+The difference in phenotype quickly becomes polarized.
+The population size reaches a steady point and then newts and snakes co-evolve.
+In the middle part of my simulation, the difference between newt and snakes mean phenotype solidifies.
+Often, the difference in mean phenotype decreases (where compared to the beginning of the simulation).
+When the GA has a high mutation rate and low mutation effect size (GA 1), the difference in mean phenotype grows.
+This leads to the species with GA 1 losing the co-evolutionary arms race.
+More frequent smaller steps does not help a species win in an arms race (might also be due to lower mutational variance).
+The histograms reflect what is seen in the scatter plots.
 
@@
 
-notes
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
+These are whole population calculations so the 5 section and 7 section data sets are not calculated differently.
 
@@
 
-GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
 
@@
 
-GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(GA1_tall_tall_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
 
@@
 
-## Summary (7 sec) {.tabset}
-
-notes
+## {.tabset}
 
@@
 
-GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
 
@@
 
-GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
 
@@
 
-GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(GA1_tall_tall_7_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
 
@@
 
-expla
+There is a whole lot going on in theses summary plots!
+Firstly, both 5 section and 7 section are very similar (not unexpected because there is no calculation difference).
+The first plot (newt population size by snake population size), all the points (shapes and colors) are clustered.
+There is some color separation (blue/green at the top left and purple/red at the bottom right).
+There is also a little bit of a shape separation (circle at the top left and squares at the bottom right).
+At time goes on GA patterns emerge.
+There are lines of color and lines of shapes.
+The best GA for newts and snakes was 1e-09_0.05 (can be seen as green near the top of all the lines of shapes and triangles near the bottom right look at all the lines of color).
+In the phenotype difference by snake population size figure there is some color separation (blue/green at the top right and purple/red at the bottom left) and some shape separation (circle at the top right and squares at the bottom left).
+Over time the points spread out and more green-circles end up in the top right and red-triangles/squares end up in the bottom left.
+When putting these figures together it seems like the population size of snakes is lower when the newt phenotype is larger than the snake phenotype.
+
+After looking at the By GA plots, I can see that there is both shape and color separation.
+Intermediate GA do better (1e-09_0.05 & 1e-10_0.5) in a co-evolutionary arms race.
+The GA with the lowest mutational variance (1e-08_0.005) did the worst.
+The benefit for a particular GA was not the same between species.
+For example, when newts had a GA of 1e-10_0.5 the mean phenotype difference ranged from -3 to 0, indicating that newts had a higher phenotype or where equal to snake phenotype no matter what GA the snake had.
+But when snake had a GA of 1e-10_0.5 the mean phenotype difference ranged from 2.2 to -1.5, indicating that snakes had a higher phenotype only when newts had certain GA (1e-08_0.005, 1e-11_5.0).
+
+What I learned in this section:
+
+- GA of 1e-10_0.5 did the best for newts and snakes
+- GAs lead to different snake-newt phenotype outcomes
 
@@
 
-notes
+In the heatmap plots each GA combination and trails is presented by combining newt GA in the x-axis to snake GA and trial number in the y-axis.
+The result is the color in that section.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+I look at 3 time slices for both types of heatmaps and for the 5 and 7 section results (measurements were the same).
 
@@
 
-notes
-
 ### Population Size (Early) (7 sec)
@@
 
+Heatmap results are very similar between the 5 and 7 sections.
+At the beginning of the simulation, snake population size was large for all snake GAs and in 3 out of the 4 newt GAs.
+The third GA (1e-10_0.5) had less snakes and more newts.
+The snake population was even smaller when snakes had GA 4 (1e-11_5.0).
+As the number of generations increased to the mid section of my simulation (the end section was the same) snake population size was large for all snake GAs, but only in 2 out of the 4 newt GAs.
+The second and third GA (1e-09_0.05 & 1e-10_0.5) had less snakes and more newts.
+When looking at each column of newt GA, snakes GA 2 (1e-09_0.05) consistently had a larger snake population size.
+Conversely, when looking at the rows of snake GA, newt GA 2 (1e-09_0.05) consistently had a smaller snake population size.
+The same pattern is seen in the difference between phenotype heat map.
+First GA 3 (1e-10_0.5) has a phenotype advantage, then as the number of generations increases GA 2 (1e-09_0.05) has an advantage.
+Something I found interesting, is that on average newts have higher levels of toxicity than snakes levels of resistance.
+It seems strange that an intermediate level of mutational variance has a better outcome in a co-evolutionary arms race.
+
 ## What is up with the correlations
 
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-
-## What is up with the correlations
-
-notes
+This section goes over the results from the grid calculations, which are different for the 5 and 7 sections.
+I divided my map up into smaller area (grids) and calculated mean phenotype, SD phenotype, max phenotype, min phenotype, and population size.
+In each of these plots newts are represented by circles and snakes are represented by squares.
+Parameter values increase from a dark color to a lighter color (green-blue themed for phenotype, orange-pinked themed for population size) There is also a subplot that plots each parameter (mean, sd…) of newt by snake colored by map location (red=corner, green=edge, blue=middle).
+I look at the some simulation at one time in the begging, middle, and end.
 
@@
 
-notes
-
 ### Early Simulation Correlation (7 sec) {.tabset}
@@
 
-data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
+data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_195, factor_key=TRUE)
 
@@
 data_long_mean_short<-data_long_mean
-
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+#28 by 7 
+#392 entries
+data_long_mean_short$y_loc<- rep(c(rep.int(28, 2),rep.int(27, 2),rep.int(26, 2),rep.int(25, 2),rep.int(24, 2),rep.int(23, 2),rep.int(22, 2),rep.int(21, 2),rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),7)
+data_long_mean_short$x_loc<-c(rep.int(1, 56),rep.int(2, 56),rep.int(3, 56),rep.int(4, 56),rep.int(5, 56),rep.int(6, 56),rep.int(7, 56))
 
@@
 
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
+newt$info[newt$location %in% list(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26,  28, 55, 56, 83, 84, 111, 112, 139, 140, 167, 169, 170, 171, 172, 173, 174, 175, 176, 177, 178, 179, 180, 181, 182, 183, 184, 185, 186, 187, 188, 189, 190, 191, 192, 193, 194)]   <- "edge"
+newt$info[newt$location %in% list(0, 27, 168, 195)] <- "corner"
 newt$info[is.na(newt$info)]<- "middle"
@@
 
-data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
+data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_195, factor_key=TRUE)
 
@@
 
-data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+#28 by 7 
+#392 entries
+data_long_sd_short$y_loc<- rep(c(rep.int(28, 2),rep.int(27, 2),rep.int(26, 2),rep.int(25, 2),rep.int(24, 2),rep.int(23, 2),rep.int(22, 2),rep.int(21, 2),rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),7)
+data_long_sd_short$x_loc<-c(rep.int(1, 56),rep.int(2, 56),rep.int(3, 56),rep.int(4, 56),rep.int(5, 56),rep.int(6, 56),rep.int(7, 56))
 
@@
 
-data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
+data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_195, factor_key=TRUE)
 
@@
 
-data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+#28 by 7 
+#392 entries
+data_long_max_short$y_loc<- rep(c(rep.int(28, 2),rep.int(27, 2),rep.int(26, 2),rep.int(25, 2),rep.int(24, 2),rep.int(23, 2),rep.int(22, 2),rep.int(21, 2),rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),7)
+data_long_max_short$x_loc<-c(rep.int(1, 56),rep.int(2, 56),rep.int(3, 56),rep.int(4, 56),rep.int(5, 56),rep.int(6, 56),rep.int(7, 56))
 
@@
 
-data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
+data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_195, factor_key=TRUE)
 
@@
 
-data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+data_long_min_short$y_loc<- rep(c(rep.int(28, 2),rep.int(27, 2),rep.int(26, 2),rep.int(25, 2),rep.int(24, 2),rep.int(23, 2),rep.int(22, 2),rep.int(21, 2),rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),7)
+data_long_min_short$x_loc<-c(rep.int(1, 56),rep.int(2, 56),rep.int(3, 56),rep.int(4, 56),rep.int(5, 56),rep.int(6, 56),rep.int(7, 56))
 
@@
 
-GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
+GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_195, factor_key=TRUE)
 
@@
 
-GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+GA1_data_long_ind_short$y_loc<- rep(c(rep.int(28, 2),rep.int(27, 2),rep.int(26, 2),rep.int(25, 2),rep.int(24, 2),rep.int(23, 2),rep.int(22, 2),rep.int(21, 2),rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),7)
+GA1_data_long_ind_short$x_loc<-c(rep.int(1, 56),rep.int(2, 56),rep.int(3, 56),rep.int(4, 56),rep.int(5, 56),rep.int(6, 56),rep.int(7, 56))
 
@@
 
-newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
+newt_GA1$info[newt_GA1$location %in% list(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26,  28, 55, 56, 83, 84, 111, 112, 139, 140, 167, 169, 170, 171, 172, 173, 174, 175, 176, 177, 178, 179, 180, 181, 182, 183, 184, 185, 186, 187, 188, 189, 190, 191, 192, 193, 194)]   <- "edge"
+newt_GA1$info[newt_GA1$location %in% list(0, 27, 168, 195)] <- "corner"
 newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
@@
 #try to arrage the grids
-
 main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
@@
 
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+data_long_mean_short$y_loc<- rep(c(rep.int(28, 2),rep.int(27, 2),rep.int(26, 2),rep.int(25, 2),rep.int(24, 2),rep.int(23, 2),rep.int(22, 2),rep.int(21, 2),rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),7)
+data_long_mean_short$x_loc<-c(rep.int(1, 56),rep.int(2, 56),rep.int(3, 56),rep.int(4, 56),rep.int(5, 56),rep.int(6, 56),rep.int(7, 56))
 
@@
 
-data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+data_long_sd_short$y_loc<- rep(c(rep.int(28, 2),rep.int(27, 2),rep.int(26, 2),rep.int(25, 2),rep.int(24, 2),rep.int(23, 2),rep.int(22, 2),rep.int(21, 2),rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),7)
+data_long_sd_short$x_loc<-c(rep.int(1, 56),rep.int(2, 56),rep.int(3, 56),rep.int(4, 56),rep.int(5, 56),rep.int(6, 56),rep.int(7, 56))
 
@@
 
-data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
+data_long_max_short$y_loc<- rep(c(rep.int(28, 2),rep.int(27, 2),rep.int(26, 2),rep.int(25, 2),rep.int(24, 2),rep.int(23, 2),rep.int(22, 2),rep.int(21, 2),rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),7)
+data_long_max_short$x_loc<-c(rep.int(1, 56),rep.int(2, 56),rep.int(3, 56),rep.int(4, 56),rep.int(5, 56),rep.int(6, 56),rep.int(7, 56))
 

### 2022-09-23 graphs_newt_snakes/corcompare.Rmd
I am looking at correlations from different experiments. trying to see if there are big picture differences

@@
 library("reshape")
+library(dplyr)
 
@@
 
-- tall map with 5 sections
-- tall map with 7 sections
-- tall map with 5 sections no heritability
-- tall map with 5 sections no interaction
+- [A] tall map with 5 sections
+- [B] tall map with 7 sections
+- [C] tall map with 5 sections no heritability
+- [D] tall map with 5 sections no interaction
 
@@
 
+snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
+
 GA1_cor_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor.txt" , header = TRUE)
@@
 
-her_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
+her_cor_tall_file<- read.csv("~/Desktop/no_hair/all_cor.txt", header = TRUE)
 her_cor_tall_file$group_rep <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd, "_", her_cor_tall_file$rep)
@@
 
-inter_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
+inter_cor_tall_file<- read.csv("~/Desktop/no_interaction/all_cor.txt", header = TRUE)
 inter_cor_tall_file$group_rep <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd, "_", inter_cor_tall_file$rep)
@@
 all_cor_exp = rbind(GA1_cor_tall_file, GA1_cor_tall_7_file, her_cor_tall_file, inter_cor_tall_file)
+
+all_cor_exp$group_exp=paste0(all_cor_exp$group, "_", all_cor_exp$experiment)
 
@@
 }
+```
+
+## Comparing the Mean
+
+```{r, looking at the mean}
+
+all_cor_exp %>%
+  group_by(experiment) %>%
+  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)
+
+all_cor_exp %>%
+  group_by(group_exp) %>%
+  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)
+
+```
+
+I want to compare the different cor values from the simulations, but i also want to look at it simulation by simulation.
+
+I think trials within a simulation experiment (A, B, C, D) should be the same (same mu and mu effect size).
+
+They should also be different between different GA combinations
+
+same GA should be differwent in the different experiments
+
+```{r, wilcoxn test}
+
+wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB
+
+wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC
+
+wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD
+
+wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC
+
+wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD
+
+wilcox.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD
+
+```
+
+```{r, t test}
+
+#t.test(GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep <= 1,]$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep >= 2,]$mean_newt_pheno_By_mean_snake_pheno) #AA
+
+t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC
+
+t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD
+
+t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC
+
+t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD
+
+t.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD
+
+t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB
+
 ```

### 2022-09-26 graphs_newt_snakes/corcompare.Rmd
looking at the cor data in more depth

@@
 GA1_cor_tall_file$experiment = "A"
+toDelete <- seq(2, nrow(GA1_cor_tall_file), 2)
+GA1_cor_tall_file_even = GA1_cor_tall_file[-toDelete,]
 
@@
 GA1_cor_tall_7_file$experiment = "B"
+toDelete <- seq(2, nrow(GA1_cor_tall_7_file), 2)
+GA1_cor_tall_7_file_even = GA1_cor_tall_7_file[-toDelete,]
 
@@
 her_cor_tall_file$experiment = "C"
+toDelete <- seq(2, nrow(her_cor_tall_file), 2)
+her_cor_tall_file_even = her_cor_tall_file[-toDelete,]
 
@@
 
-all_cor_exp = rbind(GA1_cor_tall_file, GA1_cor_tall_7_file, her_cor_tall_file, inter_cor_tall_file)
+all_cor_exp = rbind(GA1_cor_tall_file_even, GA1_cor_tall_7_file_even, her_cor_tall_file_even, inter_cor_tall_file)
 
 all_cor_exp$group_exp=paste0(all_cor_exp$group, "_", all_cor_exp$experiment)
+all_cor_exp$exp_group=paste0(all_cor_exp$experiment, "_", all_cor_exp$group)
 
@@
   return(plot)
+}
+
+counting_threshold <- function(file, treshold, whichgroup, p_n_b, min_gen, max_gen){
+
+  file=file[which(file$gen>=min_gen & file$gen<=max_gen),]
+
+  if(p_n_b == "p"){
+  table <-  file %>%
+  group_by(get(whichgroup)) %>%
+  tally(mean_newt_pheno_By_mean_snake_pheno >= treshold)
+  return(table)
+  }
+
+  if(p_n_b == "n"){
+  table <-  file %>%
+  group_by(get(whichgroup)) %>%
+  tally(mean_newt_pheno_By_mean_snake_pheno <= -treshold)
+  return(table)
+  }
+
+  if(p_n_b == "b"){
+  table <-  file %>%
+  group_by(get(whichgroup)) %>%
+  tally(mean_newt_pheno_By_mean_snake_pheno <= -treshold | mean_newt_pheno_By_mean_snake_pheno >= treshold)
+  return(table)
+  }else{
+    print("p_n_b needs to be positive, negative, or both (p, n, or b)")
+  }
+
 }
@@
 t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB
+
+```
+
+```{r, thresholds}
+
+file = all_cor_exp
+treshold = 0.3
+p_n_b = "p"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+
+file = all_cor_exp
+treshold = 0.3
+p_n_b = "b"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+
+file = all_cor_exp
+treshold = 0.5
+p_n_b = "b"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+
+file = all_cor_exp
+treshold = 0.7
+p_n_b = "b"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+
+file = all_cor_exp
+treshold = 0.7
+p_n_b = "b"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+```
+
+```{r, distribuuution plots, fig.height = 11, fig.width = 5}
+
+dummy<-all_cor_exp %>%
+  group_by(group_exp) %>%
+  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)
+
+ggplot(all_cor_exp[which(all_cor_exp$gen>=min_gen & all_cor_exp$gen<=max_gen),])+
+   #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  #xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=mean_newt_pheno_By_mean_snake_pheno, fill=experiment))+ #, y=threshold
+ # theme(plot.title = element_text(size=5)) +
+ # xlim(-.1, 1.1)+
+  #geom_vline(data = dummy, aes(xintercept = name))+
+  facet_grid(group~experiment)+
+  #facet_wrap(~group_exp)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
+                    strip.background = element_blank(), strip.text.x = element_blank(),
+                   title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                    axis.title.y = element_blank())
+```
+
+```{r, other plots}
+dummy<-all_cor_exp %>%
+  group_by(experiment) %>%
+  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)
+
+ggplot(all_cor_exp[which(all_cor_exp$gen>=min_gen & all_cor_exp$gen<=max_gen),])+
+   #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  #xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=mean_newt_pheno_By_mean_snake_pheno, fill=experiment))+ #, y=threshold
+ # theme(plot.title = element_text(size=5)) +
+ # xlim(-.1, 1.1)+
+  geom_vline(data = dummy, aes(xintercept = name))+
+  facet_wrap(~experiment)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
+                    strip.background = element_blank(), strip.text.x = element_blank(),
+                   title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                    axis.title.y = element_blank())
 

### 2022-09-29 graphs_newt_snakes/corcompare.Rmd
looking more at the correlations and preping for the grid experiment

@@
 library(dplyr)
-
+library(ggside)
 ```
@@
 
-all_cor_exp %>%
+all_the_means = all_cor_exp %>%
   group_by(group_exp) %>%
@@
 
+all_the_means$exp <- str_split_fixed(all_the_means$group_exp, "5_", 3)[,3]
+
+exclude_b <- all_the_means[which(all_the_means$exp!='B'),]
+exclude_c <- all_the_means[which(all_the_means$exp!='C'),]
+
+print("Anovas from mean of A and B")
+res.aov2ab <- aov(name ~ exp, data = exclude_c[which(exclude_c$exp!='D'),])
+summary(res.aov2ab)
+print("Anovas from mean of A and C")
+res.aov2ac <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='D'),])
+summary(res.aov2ac)
+print("Anovas from mean of A and D")
+res.aov2ad <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='C'),])
+summary(res.aov2ad)
+print("Anovas from mean of C and D")
+res.aov2cd <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='A'),])
+summary(res.aov2cd)
 ```
@@
 
-same GA should be differwent in the different experiments
+same GA should be different in the different experiments
 
@@
 
-```
-
-```{r, thresholds}
-
-file = all_cor_exp
-treshold = 0.3
-p_n_b = "p"
-min_gen = 100
-max_gen =50000
-whichgroup = "experiment"
-
-counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
-
-file = all_cor_exp
-treshold = 0.3
-p_n_b = "b"
-min_gen = 100
-max_gen =50000
-whichgroup = "experiment"
-
-counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
-
-file = all_cor_exp
-treshold = 0.5
-p_n_b = "b"
-min_gen = 100
-max_gen =50000
-whichgroup = "experiment"
-
-counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
-
-file = all_cor_exp
-treshold = 0.7
-p_n_b = "b"
-min_gen = 100
-max_gen =50000
-whichgroup = "experiment"
-
-counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
-
-file = all_cor_exp
-treshold = 0.7
-p_n_b = "b"
-min_gen = 100
-max_gen =50000
-whichgroup = "experiment"
 ```
@@
 like make a lower limit like must be above 0.3
+
+```{r, thresholds}
+
+file = all_cor_exp
+treshold = 0.3
+p_n_b = "p"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+
+file = all_cor_exp
+treshold = 0.3
+p_n_b = "b"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+
+file = all_cor_exp
+treshold = 0.5
+p_n_b = "b"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+
+file = all_cor_exp
+treshold = 0.7
+p_n_b = "b"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+
+file = all_cor_exp
+treshold = 0.7
+p_n_b = "b"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+```
+
+```{r, ggslide test}
+
+ggplot(all_cor_exp) + 
+  #geom_point(size = 2) +
+  #geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=rep))+
+  geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity")+
+  #geom_xsidehistogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity") +
+  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
+  scale_ysidex_discrete(guide = guide_axis(angle = 45))
+
+```

### 2022-09-29 graphs_newt_snakes/grid_test.Rmd
looking more at the correlations and preping for the grid experiment

---
title: "Grid Test"
output: html_document
date: '2022-09-27'
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
library(stringr)
library(patchwork)
```

## Goal:

Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to. This markdown is investigation what is up with the different levels of correlation between rectangles and squares (in connection with GA1 tall). After fixing the row vs column error I looked at the correlation data and found that there was less correlation. So I decided to investigate why that might be and run a few more experiments. I am running an experiment to test how changing the square size might impact the calculations. I also plan on changing the interaction rate (but want to look at the math/ feasibility of it). This file contains results discussed in Tall_GA1!

### Questions:

How does grid size impact the spatial correlation of newt and snake phenotypes?

## Background

## Experiment

I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction with different genetic architectures (GAs) in a spatial setting. I hypothesized that we would see an interaction (co-evolutionary arms race) between newt and snake phenotype under some GA combinations when newts and snakes were evolving over geographical space. Each GA is paired with another GA creating 16 combinations.

GA1 experiment values:

- 1e-8*(0.005)^2 = 2.5e-13
- 1e-9*(0.05)^2 = 2.5e-12
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(5.0)^2 = 2.5e-10

Landscape: A tall map!: 35*4 H, 35 W

I tested grid sizes for my tall landscape:

- grid 2X8, area 306.25 (approx)
- grid 3X12, area 136.11 (approx)
- grid 4X16, area 76.56 (approx)
- grid 5X20, area 49 (approx)
- grid 6X24, area 34.02 (approx)
- grid 7X28, area 25 (approx)

Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.

### The data

## Preping the data by making singular files

```{bash, data file gathering}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=GA1_dif_grid
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

lit_head_file=$(find ${thepath}${foldername} -name "*_GA1234567_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

cor_head_file_2=$(find ${thepath}${foldername} -name "*_GA2_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

cor_head_file_3=$(find ${thepath}${foldername} -name "*_GA3_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

cor_head_file_4=$(find ${thepath}${foldername} -name "*_GA4_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

cor_head_file_5=$(find ${thepath}${foldername} -name "*_GA5_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

cor_head_file_6=$(find ${thepath}${foldername} -name "*_GA6_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

cor_head_file_7=$(find ${thepath}${foldername} -name "*_GA7_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file_2=$(find ${thepath}${foldername} -name "*_GA2_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

grid_head_file_3=$(find ${thepath}${foldername} -name "*_GA3_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

grid_head_file_4=$(find ${thepath}${foldername} -name "*_GA4_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

grid_head_file_5=$(find ${thepath}${foldername} -name "*_GA5_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

grid_head_file_6=$(find ${thepath}${foldername} -name "*_GA6_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

grid_head_file_7=$(find ${thepath}${foldername} -name "*_GA7_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid_2.txt ]] && [[ -f ${thepath}${foldername}/all_cor_2.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid_2.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid_3.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid_4.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid_5.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid_6.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid_7.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor_2.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor_3.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor_4.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor_5.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor_6.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor_7.txt

for filename in $thefolder*.text;
  do 
#getting the variables

my_type=$(echo ${filename} |sed 's/.*GA1234567_//; s/_.*//')
my_type_2=$(echo ${filename} |sed 's/.*GA2_//; s/_.*//')
my_type_3=$(echo ${filename} |sed 's/.*GA3_//; s/_.*//')
my_type_4=$(echo ${filename} |sed 's/.*GA4_//; s/_.*//')
my_type_5=$(echo ${filename} |sed 's/.*GA5_//; s/_.*//')
my_type_6=$(echo ${filename} |sed 's/.*GA6_//; s/_.*//')
my_type_7=$(echo ${filename} |sed 's/.*GA7_//; s/_.*//')

snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type_2 == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid_2.txt
fi

if [[ $my_type_2 == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor_2.txt
fi

if [[ $my_type_3 == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid_3.txt
fi

if [[ $my_type_3 == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor_3.txt
fi

if [[ $my_type_4 == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid_4.txt
fi

if [[ $my_type_4 == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor_4.txt
fi

if [[ $my_type_5 == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid_5.txt
fi

if [[ $my_type_5 == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor_5.txt
fi

if [[ $my_type_6 == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid_6.txt
fi

if [[ $my_type_6 == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor_6.txt
fi

if [[ $my_type_7 == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid_7.txt
fi

if [[ $my_type_7 == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor_7.txt
fi

done

```

## Loading in/ Combining the files to compare different grid sizes

```{r, loading in the data}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

GA1_lit_grid_file<- read.csv("~/Desktop/GA1_dif_grid/all_lit.txt" , header = TRUE)
GA1_lit_grid_file$group_rep <- paste0(GA1_lit_grid_file$snake_mu_rate, "_", GA1_lit_grid_file$snake_mu_effect_sd,"_",GA1_lit_grid_file$newt_mu_rate, "_", GA1_lit_grid_file$newt_mu_effect_sd, "_", GA1_lit_grid_file$rep)
GA1_lit_grid_file$group <- paste0(GA1_lit_grid_file$snake_mu_rate, "_", GA1_lit_grid_file$snake_mu_effect_sd,"_",GA1_lit_grid_file$newt_mu_rate, "_", GA1_lit_grid_file$newt_mu_effect_sd)
GA1_lit_grid_file$sim=LETTERS[factor(GA1_lit_grid_file$group)]

GA1_cor_grid_2_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_2.txt" , header = TRUE)
GA1_cor_grid_2_file$group_rep <- paste0(GA1_cor_grid_2_file$snake_mu_rate, "_", GA1_cor_grid_2_file$snake_mu_effect_sd,"_",GA1_cor_grid_2_file$newt_mu_rate, "_", GA1_cor_grid_2_file$newt_mu_effect_sd, "_", GA1_cor_grid_2_file$rep)
GA1_cor_grid_2_file$group <- paste0(GA1_cor_grid_2_file$snake_mu_rate, "_", GA1_cor_grid_2_file$snake_mu_effect_sd,"_",GA1_cor_grid_2_file$newt_mu_rate, "_", GA1_cor_grid_2_file$newt_mu_effect_sd)
GA1_cor_grid_2_file$sim=LETTERS[factor(GA1_cor_grid_2_file$group)]
GA1_cor_grid_2_file$grid_num = 2

GA1_cor_grid_3_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_3.txt" , header = TRUE)
GA1_cor_grid_3_file$group_rep <- paste0(GA1_cor_grid_3_file$snake_mu_rate, "_", GA1_cor_grid_3_file$snake_mu_effect_sd,"_",GA1_cor_grid_3_file$newt_mu_rate, "_", GA1_cor_grid_3_file$newt_mu_effect_sd, "_", GA1_cor_grid_3_file$rep)
GA1_cor_grid_3_file$group <- paste0(GA1_cor_grid_3_file$snake_mu_rate, "_", GA1_cor_grid_3_file$snake_mu_effect_sd,"_",GA1_cor_grid_3_file$newt_mu_rate, "_", GA1_cor_grid_3_file$newt_mu_effect_sd)
GA1_cor_grid_3_file$sim=LETTERS[factor(GA1_cor_grid_3_file$group)]
GA1_cor_grid_3_file$grid_num = 3

GA1_cor_grid_4_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_4.txt" , header = TRUE)
GA1_cor_grid_4_file$group_rep <- paste0(GA1_cor_grid_4_file$snake_mu_rate, "_", GA1_cor_grid_4_file$snake_mu_effect_sd,"_",GA1_cor_grid_4_file$newt_mu_rate, "_", GA1_cor_grid_4_file$newt_mu_effect_sd, "_", GA1_cor_grid_4_file$rep)
GA1_cor_grid_4_file$group <- paste0(GA1_cor_grid_4_file$snake_mu_rate, "_", GA1_cor_grid_4_file$snake_mu_effect_sd,"_",GA1_cor_grid_4_file$newt_mu_rate, "_", GA1_cor_grid_4_file$newt_mu_effect_sd)
GA1_cor_grid_4_file$sim=LETTERS[factor(GA1_cor_grid_4_file$group)]
GA1_cor_grid_4_file$grid_num = 4

GA1_cor_grid_5_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_5.txt" , header = TRUE)
GA1_cor_grid_5_file$group_rep <- paste0(GA1_cor_grid_5_file$snake_mu_rate, "_", GA1_cor_grid_5_file$snake_mu_effect_sd,"_",GA1_cor_grid_5_file$newt_mu_rate, "_", GA1_cor_grid_5_file$newt_mu_effect_sd, "_", GA1_cor_grid_5_file$rep)
GA1_cor_grid_5_file$group <- paste0(GA1_cor_grid_5_file$snake_mu_rate, "_", GA1_cor_grid_5_file$snake_mu_effect_sd,"_",GA1_cor_grid_5_file$newt_mu_rate, "_", GA1_cor_grid_5_file$newt_mu_effect_sd)
GA1_cor_grid_5_file$sim=LETTERS[factor(GA1_cor_grid_5_file$group)]
GA1_cor_grid_5_file$grid_num = 5

GA1_cor_grid_6_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_6.txt" , header = TRUE)
GA1_cor_grid_6_file$group_rep <- paste0(GA1_cor_grid_6_file$snake_mu_rate, "_", GA1_cor_grid_6_file$snake_mu_effect_sd,"_",GA1_cor_grid_6_file$newt_mu_rate, "_", GA1_cor_grid_6_file$newt_mu_effect_sd, "_", GA1_cor_grid_6_file$rep)
GA1_cor_grid_6_file$group <- paste0(GA1_cor_grid_6_file$snake_mu_rate, "_", GA1_cor_grid_6_file$snake_mu_effect_sd,"_",GA1_cor_grid_6_file$newt_mu_rate, "_", GA1_cor_grid_6_file$newt_mu_effect_sd)
GA1_cor_grid_6_file$sim=LETTERS[factor(GA1_cor_grid_6_file$group)]
GA1_cor_grid_6_file$grid_num = 6

GA1_cor_grid_7_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_7.txt" , header = TRUE)
GA1_cor_grid_7_file$group_rep <- paste0(GA1_cor_grid_7_file$snake_mu_rate, "_", GA1_cor_grid_7_file$snake_mu_effect_sd,"_",GA1_cor_grid_7_file$newt_mu_rate, "_", GA1_cor_grid_7_file$newt_mu_effect_sd, "_", GA1_cor_grid_7_file$rep)
GA1_cor_grid_7_file$group <- paste0(GA1_cor_grid_7_file$snake_mu_rate, "_", GA1_cor_grid_7_file$snake_mu_effect_sd,"_",GA1_cor_grid_7_file$newt_mu_rate, "_", GA1_cor_grid_7_file$newt_mu_effect_sd)
GA1_cor_grid_7_file$sim=LETTERS[factor(GA1_cor_grid_7_file$group)]
GA1_cor_grid_7_file$grid_num = 7

# GA1_grid_grid_2_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_2.txt" , header = TRUE)
# GA1_grid_grid_2_file$group_rep <- paste0(GA1_grid_grid_2_file$snake_mu_rate, "_", GA1_grid_grid_2_file$snake_mu_effect_sd,"_",GA1_grid_grid_2_file$newt_mu_rate, "_", GA1_grid_grid_2_file$newt_mu_effect_sd, "_", GA1_grid_grid_2_file$rep)
# GA1_grid_grid_2_file$group <- paste0(GA1_grid_grid_2_file$snake_mu_rate, "_", GA1_grid_grid_2_file$snake_mu_effect_sd,"_",GA1_grid_grid_2_file$newt_mu_rate, "_", GA1_grid_grid_2_file$newt_mu_effect_sd)
# GA1_grid_grid_2_file$sim=LETTERS[factor(GA1_grid_grid_2_file$group)]
# GA1_grid_grid_2_file$grid_num = 2
# 
# 
# GA1_grid_grid_3_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_3.txt" , header = TRUE)
# GA1_grid_grid_3_file$group_rep <- paste0(GA1_grid_grid_3_file$snake_mu_rate, "_", GA1_grid_grid_3_file$snake_mu_effect_sd,"_",GA1_grid_grid_3_file$newt_mu_rate, "_", GA1_grid_grid_3_file$newt_mu_effect_sd, "_", GA1_grid_grid_3_file$rep)
# GA1_grid_grid_3_file$group <- paste0(GA1_grid_grid_3_file$snake_mu_rate, "_", GA1_grid_grid_3_file$snake_mu_effect_sd,"_",GA1_grid_grid_3_file$newt_mu_rate, "_", GA1_grid_grid_3_file$newt_mu_effect_sd)
# GA1_grid_grid_3_file$sim=LETTERS[factor(GA1_grid_grid_3_file$group)]
# GA1_grid_grid_3_file$grid_num = 3
# 
# GA1_grid_grid_4_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_4.txt" , header = TRUE)
# GA1_grid_grid_4_file$group_rep <- paste0(GA1_grid_grid_4_file$snake_mu_rate, "_", GA1_grid_grid_4_file$snake_mu_effect_sd,"_",GA1_grid_grid_4_file$newt_mu_rate, "_", GA1_grid_grid_4_file$newt_mu_effect_sd, "_", GA1_grid_grid_4_file$rep)
# GA1_grid_grid_4_file$group <- paste0(GA1_grid_grid_4_file$snake_mu_rate, "_", GA1_grid_grid_4_file$snake_mu_effect_sd,"_",GA1_grid_grid_4_file$newt_mu_rate, "_", GA1_grid_grid_4_file$newt_mu_effect_sd)
# GA1_grid_grid_4_file$sim=LETTERS[factor(GA1_grid_grid_4_file$group)]
# GA1_grid_grid_4_file$grid_num = 4
# 
# GA1_grid_grid_5_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_5.txt" , header = TRUE)
# GA1_grid_grid_5_file$group_rep <- paste0(GA1_grid_grid_5_file$snake_mu_rate, "_", GA1_grid_grid_5_file$snake_mu_effect_sd,"_",GA1_grid_grid_5_file$newt_mu_rate, "_", GA1_grid_grid_5_file$newt_mu_effect_sd, "_", GA1_grid_grid_5_file$rep)
# GA1_grid_grid_5_file$group <- paste0(GA1_grid_grid_5_file$snake_mu_rate, "_", GA1_grid_grid_5_file$snake_mu_effect_sd,"_",GA1_grid_grid_5_file$newt_mu_rate, "_", GA1_grid_grid_5_file$newt_mu_effect_sd)
# GA1_grid_grid_5_file$sim=LETTERS[factor(GA1_grid_grid_5_file$group)]
# GA1_grid_grid_5_file$grid_num = 5
# 
# GA1_grid_grid_6_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_6.txt" , header = TRUE)
# GA1_grid_grid_6_file$group_rep <- paste0(GA1_grid_grid_6_file$snake_mu_rate, "_", GA1_grid_grid_6_file$snake_mu_effect_sd,"_",GA1_grid_grid_6_file$newt_mu_rate, "_", GA1_grid_grid_6_file$newt_mu_effect_sd, "_", GA1_grid_grid_6_file$rep)
# GA1_grid_grid_6_file$group <- paste0(GA1_grid_grid_6_file$snake_mu_rate, "_", GA1_grid_grid_6_file$snake_mu_effect_sd,"_",GA1_grid_grid_6_file$newt_mu_rate, "_", GA1_grid_grid_6_file$newt_mu_effect_sd)
# GA1_grid_grid_6_file$sim=LETTERS[factor(GA1_grid_grid_6_file$group)]
# GA1_grid_grid_6_file$grid_num = 6
# 
# GA1_grid_grid_7_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_7.txt" , header = TRUE)
# GA1_grid_grid_7_file$group_rep <- paste0(GA1_grid_grid_7_file$snake_mu_rate, "_", GA1_grid_grid_7_file$snake_mu_effect_sd,"_",GA1_grid_grid_7_file$newt_mu_rate, "_", GA1_grid_grid_7_file$newt_mu_effect_sd, "_", GA1_grid_grid_7_file$rep)
# GA1_grid_grid_7_file$group <- paste0(GA1_grid_grid_7_file$snake_mu_rate, "_", GA1_grid_grid_7_file$snake_mu_effect_sd,"_",GA1_grid_grid_7_file$newt_mu_rate, "_", GA1_grid_grid_7_file$newt_mu_effect_sd)
# GA1_grid_grid_7_file$sim=LETTERS[factor(GA1_grid_grid_7_file$group)]
# GA1_grid_grid_7_file$grid_num = 7

all_cor_grid = rbind(GA1_cor_grid_2_file, GA1_cor_grid_3_file, GA1_cor_grid_4_file,  GA1_cor_grid_5_file,  GA1_cor_grid_6_file,  GA1_cor_grid_7_file)

all_cor_grid$group_exp=paste0(all_cor_grid$group, "_", all_cor_grid$experiment)
all_cor_grid$exp_group=paste0(all_cor_grid$experiment, "_", all_cor_grid$group)

# all_grid_grid = rbind(GA1_grid_grid_2_file, GA1_grid_grid_3_file, GA1_grid_grid_4_file,  GA1_grid_grid_5_file,  GA1_grid_grid_6_file,  GA1_grid_grid_7_file)
# 
# all_grid_grid$group_exp=paste0(all_grid_grid$group, "_", all_grid_grid$experiment)
# all_grid_grid$exp_group=paste0(all_grid_grid$experiment, "_", all_grid_grid$group)

```

### 2022-09-30 graphs_newt_snakes/corcompare.Rmd
more cor calc

@@
 all_cor_exp$exp_group=paste0(all_cor_exp$experiment, "_", all_cor_exp$group)
+all_cor_exp$group_exp_rep=paste0(all_cor_exp$group, "_", all_cor_exp$experiment, "_",all_cor_exp$rep)
 
@@
 
+print("One mean per GA")
+
 all_the_means = all_cor_exp %>%
@@
 exclude_c <- all_the_means[which(all_the_means$exp!='C'),]
+
+print("Anovas from mean of A and B")
+res.aov2ab <- aov(name ~ exp, data = exclude_c[which(exclude_c$exp!='D'),])
+summary(res.aov2ab)
+print("Anovas from mean of A and C")
+res.aov2ac <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='D'),])
+summary(res.aov2ac)
+print("Anovas from mean of A and D")
+res.aov2ad <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='C'),])
+summary(res.aov2ad)
+print("Anovas from mean of C and D")
+res.aov2cd <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='A'),])
+summary(res.aov2cd)
+
+print("One mean per rep")
+
+all_the_means_byrep = all_cor_exp %>%
+  group_by(group_exp_rep) %>%
+  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)
+
+all_the_means_byrep$exp <- str_split_fixed(all_the_means_byrep$group_exp_rep, "_", 6)[,5]
+
+exclude_b <- all_the_means_byrep[which(all_the_means_byrep$exp!='B'),]
+exclude_c <- all_the_means_byrep[which(all_the_means_byrep$exp!='C'),]
 
@@
 
+ggplot(all_cor_exp) + 
+  #geom_point(size = 2) +
+  #geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=rep))+
+  geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)*3,fill=factor(experiment)), alpha=0.4, position="identity")+
+  #geom_xsidehistogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity") +
+  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
+  scale_ysidex_discrete(guide = guide_axis(angle = 45))
+
+#all_cor_exp$num_newts_By_num_snakes
+ggplot(all_cor_exp) + 
+  #geom_point(size = 2) +
+  geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
+  #geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)*3,fill=factor(experiment)), alpha=0.4, position="identity")+
+    geom_xsideline(aes(generation, num_newts_By_num_snakes, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
+  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
+  scale_ysidex_discrete(guide = guide_axis(angle = 45))
+
+ggplot(all_cor_exp) + 
+  #geom_point(size = 2) +
+  geom_line(aes(generation, num_newts_By_num_snakes, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
+  #geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)*3,fill=factor(experiment)), alpha=0.4, position="identity")+
+    geom_xsideline(aes(generation, num_newts_By_num_snakes, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
+  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
+  scale_ysidex_discrete(guide = guide_axis(angle = 45)) 
 ```

### 2022-10-04 graphs_newt_snakes/big_map.Rmd
I looked at the big map data. I got slim to stop when one population goes extenct. I am still looking at cor results.

@@
 
+```{bash, data file gathering}
+#!/usr/bin/env bash
+
+# Run these comands while in The the folder that contains the file you would like to condence
+# Goal is to condence all the text files into one file 
+# Requirements: need to have the same name and need to add additional columns
+thepath=/Users/victoria/Desktop/
+foldername=big_map
+thefolder=${thepath}${foldername}/*
+
+add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"
+
+cor_head_file=$(find ${thepath}${foldername} -name "*_GA20050_cor_*" | head -n 1)
+cor_head=$(head -n 1 "${cor_head_file}")
+
+grid_head_file=$(find ${thepath}${foldername} -name "*_GA20050_grid_*" | head -n 1)
+grid_head=$(head -n 1 "${grid_head_file}")
+
+lit_head_file=$(find ${thepath}${foldername} -name "*_GA20050_lit_*" | head -n 1)
+lit_head=$(head -n 1 "${lit_head_file}")
+
+#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."
+
+if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
+then
+  echo "All cor, lit, and grid files exist!"
+  echo "This program will now end!"
+  exit 0
+fi
+
+#creating the files
+echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
+echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
+echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt
+
+for filename in $thefolder*.text;
+  do 
+#getting the variables 
+my_type=$(echo ${filename} |sed 's/.*GA20050_//; s/_.*//')
+snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
+snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
+newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
+newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
+rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
+#echo ${newt_mu_rate}	
+# echo $my_type
+# echo $my_other_type
+# these new columns adding them to the data
+sed -i '' -e 's/$/,'${rep}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
+#infile >outfile
+if [[ $my_type == "lit" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
+fi
+
+if [[ $my_type == "grid" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
+fi
+
+if [[ $my_type == "cor" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
+fi
+
+done
+
+```
+
 ```{r, data gathering}
@@
 
-big_map_tall <- list.files(path="~/Desktop/big_map", pattern="_lit_", full.names=TRUE, recursive=FALSE)
-big_map_tall_cor_files <- list.files(path="~/Desktop/big_map", pattern="_cor_", full.names=TRUE, recursive=FALSE)
-big_map_grid_tall_files <- list.files(path="~/Desktop/big_map", pattern="_grid_", full.names=TRUE, recursive=FALSE)
+big_map_tall<- read.csv("~/Desktop/big_map/all_lit.txt" , header = TRUE)
 
-big_map_tall_tall_file<- data.frame()
-big_map_cor_tall_file<- data.frame()
-big_map_grid_tall_file<-data.frame()
-name_list<-c()
-cor_name_list<-c()
-grid_name_list<-c()
-for(i in seq(1, length(big_map_tall)/2, 1)){
-  print(i)
-  #sim
+big_map_tall$group_rep <- paste0(big_map_tall$snake_mu_rate, "_", big_map_tall$snake_mu_effect_sd,"_",big_map_tall$newt_mu_rate, "_", big_map_tall$newt_mu_effect_sd, "_", big_map_tall$rep)
 
-  big_map_temp_file <- read.csv(big_map_tall[i], header = TRUE)
-  big_map_temp_file$rep <- unlist(str_split(unlist(str_split(big_map_tall[i],"rep_"))[3], "_"))[1]
-  big_map_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  big_map_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  big_map_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  big_map_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  name_list<-c(paste0(big_map_temp_file$snake_mu_rate[1], big_map_temp_file$newt_mu_rate[1], big_map_temp_file$snake_mu_effect_sd[1], big_map_temp_file$newt_mu_effect_sd[1]),name_list)
-  big_map_temp_file$sim <- LETTERS[length(unique(name_list))]
-  big_map_tall_tall_file <- rbind(big_map_tall_tall_file, big_map_temp_file)
-  print(big_map_temp_file$sim[1])
+big_map_tall$group <- paste0(big_map_tall$snake_mu_rate, "_", big_map_tall$snake_mu_effect_sd,"_",big_map_tall$newt_mu_rate, "_", big_map_tall$newt_mu_effect_sd)
 
-  cor_temp_file <- read.csv(big_map_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
-  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
-  big_map_cor_tall_file <- rbind(big_map_cor_tall_file, cor_temp_file)
-  print(cor_temp_file$sim[1])
+big_map_tall$sim=LETTERS[factor(big_map_tall$group)]
+big_map_tall$dif <- big_map_tall$Snake_mean_Pheno-big_map_tall$Newt_mean_Pheno
+big_map_tall$snake_newt_rep <- paste0("Snake_",big_map_tall$snake_mu_rate, "_", big_map_tall$snake_mu_effect_sd, "_Newt_",big_map_tall$newt_mu_rate, "_", big_map_tall$newt_mu_effect_sd, "_", big_map_tall$rep)
 
-  big_map_grid_temp_file <- read.csv(big_map_grid_tall_files[i], header = TRUE)
-  big_map_grid_temp_file$sim <-
-  big_map_grid_temp_file$rep <-unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"rep_"))[3], "_"))[1]
-  big_map_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  big_map_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  big_map_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  big_map_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  grid_name_list<-c(paste0(big_map_grid_temp_file$snake_mu_rate[1], big_map_grid_temp_file$newt_mu_rate[1], big_map_grid_temp_file$snake_mu_effect_sd[1], big_map_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
-  big_map_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
-  big_map_grid_tall_file <- rbind(big_map_grid_tall_file, big_map_grid_temp_file)
-   print(big_map_grid_temp_file$sim[1])
+big_map_cor<- read.csv("~/Desktop/big_map/all_cor.txt" , header = TRUE)
+big_map_cor$group_rep <- paste0(big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd,"_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd, "_", big_map_cor$rep)
+big_map_cor$group <- paste0(big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd,"_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd)
+big_map_cor$sim=LETTERS[factor(big_map_cor$group)]
+big_map_cor$snake_newt_rep <- paste0("Snake_",big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd, "_Newt_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd, "_", big_map_cor$rep)
 
+big_map_grid<-read.csv("~/Desktop/big_map/all_grid.txt" , header = TRUE)
+big_map_grid$group <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd)
+big_map_grid$group_rep <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd, "_", big_map_grid$rep)
+
+big_map_grid$sim=LETTERS[factor(big_map_grid$group)]
+big_map_grid$snake_newt_rep <- paste0("Snake_",big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd, "_Newt_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd, "_", big_map_grid$rep)
+
+```
+
+```{r, cor box set up}
+
+boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+    geom_hline(yintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
 }
- ###to set first half 
-big_map_tall_tall_file_p1<- big_map_tall_tall_file
-big_map_cor_tall_file_p1<- big_map_cor_tall_file
-big_map_grid_tall_file_p1<-big_map_grid_tall_file
 
-for(i in seq((length(big_map_tall)/2+1), length(big_map_tall), 1)){
-  print(i)
-  #sim
+hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  #unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  xlim(-1.1, 1.1)+
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
 
-  big_map_temp_file <- read.csv(big_map_tall[i], header = TRUE)
-  big_map_temp_file$rep <- unlist(str_split(unlist(str_split(big_map_tall[i],"rep_"))[3], "_"))[1]
-  big_map_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall[i],"snake_mu_rate_"))[2], "_"))[1]
-  big_map_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall[i],"newt_mu_rate_"))[2], "_"))[1]
-  big_map_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  big_map_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  name_list<-c(paste0(big_map_temp_file$snake_mu_rate[1], big_map_temp_file$newt_mu_rate[1], big_map_temp_file$snake_mu_effect_sd[1], big_map_temp_file$newt_mu_effect_sd[1]),name_list)
-  big_map_temp_file$sim <- LETTERS[length(unique(name_list))]
-  big_map_tall_tall_file <- rbind(big_map_tall_tall_file, big_map_temp_file)
-  print(big_map_temp_file$sim[1])
+  return(plot)
+}
 
-  cor_temp_file <- read.csv(big_map_tall_cor_files[i], header = TRUE)
-  cor_temp_file$sim <-
-  cor_temp_file$rep <-unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"rep_"))[3], "_"))[1]
-  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
-  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
-  big_map_cor_tall_file <- rbind(big_map_cor_tall_file, cor_temp_file)
-  print(cor_temp_file$sim[1])
+hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  #stat_bin(bins=30)+
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
 
-  big_map_grid_temp_file <- read.csv(big_map_grid_tall_files[i], header = TRUE)
-  big_map_grid_temp_file$sim <-
-  big_map_grid_temp_file$rep <-unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"rep_"))[3], "_"))[1]
-  big_map_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
-  big_map_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
-  big_map_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
-  big_map_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(big_map_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
-  grid_name_list<-c(paste0(big_map_grid_temp_file$snake_mu_rate[1], big_map_grid_temp_file$newt_mu_rate[1], big_map_grid_temp_file$snake_mu_effect_sd[1], big_map_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
-  big_map_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
-  big_map_grid_tall_file <- rbind(big_map_grid_tall_file, big_map_grid_temp_file)
-   print(big_map_grid_temp_file$sim[1])
+suppressMessages(print(plot))
+
+  return(plot)
+}
+
+var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  real_snewt_var = var(snewt$dif)
+  var_cor_table=data.frame()
+
+  for(i in 1:length(unique(file$snake_newt_rep))){
+    pattern<-unique(file$snake_newt_rep)[i]
+    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
+    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
+
+    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
+    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+  }
+
+  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
+  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+
+  plot <- ggplot(var_cor_table) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+  return(plot)
+}
+
+cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+#file=big_map_tall
+#cfile=big_map_cor 
+ # pattern="Snake_1e-11_5_Newt_1e-10_0.5_0"
+
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
+    #ylim(0,10)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() +theme(legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
+                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
+
+  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
+    #ggtitle(title, subtitle = subt) +
+    ylim(-1.1, 1.1)+
+    #xlab(x_label_cor) + ylab(y_label)+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(),
+                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
+figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
+
+  return(figure)
+}
+
+four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  geom_hline(yintercept=0, linetype="solid")+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+```
+
+```{r, general file and graph making}
+
+#the functions to make the params file and the summary and heatmap figures
+
+create_parm_file <- function(file, min_gen, max_gen){
+params <- data_frame()
+
+for(i in 1:length(unique(file$snake_newt_rep))){
+
+  pattern=unique(file$snake_newt_rep)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]
+
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=sumitup$snake_mu_rate[1],
+                           newt_mu_rate=sumitup$newt_mu_rate[1],
+                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
+                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
+                           rep=sumitup$rep[1])
+
+  params <- rbind(params, params_temp)
+}
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$snake_newt <- paste0(params$snake, "_", params$newt)
+return(params)
+}
+
+GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+
+build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
+  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+  params<-create_parm_file(file, min_gen, max_gen)
+
+ my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
+
+ if(red_blue==FALSE){
+  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
+  }
+ if(red_blue==TRUE){
+  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
+ }
+
+  return(my_plot)
+}
+
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){
+
+  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
+    facet_wrap(~sim)+
+    geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
+    #ylim(-1.,2.5)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+  return(plot)
+}
+
+whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
 
@@
 
-big_map_tall_tall_file$dif <- big_map_tall_tall_file$Snake_mean_Pheno-big_map_tall_tall_file$Newt_mean_Pheno
+pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
+  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
+  xlim((-1*themax)-5, themax+5)+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
 
-big_map_tall_tall_file$group_rep <- paste0(big_map_tall_tall_file$snake_mu_rate, "_", big_map_tall_tall_file$snake_mu_effect_sd,"_",big_map_tall_tall_file$newt_mu_rate, "_", big_map_tall_tall_file$newt_mu_effect_sd, "_", big_map_tall_tall_file$rep)
+return(dif)
+}
 
-big_map_tall_tall_file$group <- paste0(big_map_tall_tall_file$snake_mu_rate, "_", big_map_tall_tall_file$snake_mu_effect_sd,"_",big_map_tall_tall_file$newt_mu_rate, "_", big_map_tall_tall_file$newt_mu_effect_sd)
+pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
 
-big_map_grid_tall_file$snake_newt_rep <- paste0("Snake_",big_map_grid_tall_file$snake_mu_rate, "_", big_map_grid_tall_file$snake_mu_effect_sd, "_Newt_",big_map_grid_tall_file$newt_mu_rate, "_", big_map_grid_tall_file$newt_mu_effect_sd, "_", big_map_grid_tall_file$rep)
+  themin <- min(file$dif) 
+  themax <- max(file$dif)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(dif), fill="aquamarine4")+
+  xlim((-1*true_max)-1, true_max+1)+
+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file=big_map_tall
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$newt_deaths)
+  thepopmax <- max(file$newt_deaths)
+  thedifmin <- min(file$snake_deaths) 
+  thedifmax <- max(file$snake_deaths)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
+  #scale_y_continuous(labels = scales::percent)+
+  #xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  #geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+#two_hist_death_all_rep(big_map_tall, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+
+grid_plot<- function(file_name, spegen, file, type, row_num, col_num){
+
+GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
+GA1_type = paste0("generation|", type)
+
+GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
+GA1_type <- GA1_type[-1]
+
+data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
+data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)
+
+data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),5)
+
+data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))
+
+main_plot<-ggplot(data_long_type_comp)+
+
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  ylim(0, 200)+
+  xlim(0, 51)+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+if(type != "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance                                                          ")+
+ scale_fill_viridis_c()
+}
+if(type == "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Newt/Snake Phenotype                                                         ")+
+scale_fill_viridis_c(option = "plasma")
+}
+
+snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
+newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
+newt$snake_value <- snake$measurement
+print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))
+
+newt$info <- "middle"
+newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
+return(final_plot)}
 
 ```
+
+### Phenotype differences 
+```{r, graphing by gen}
+trends_by_gen(big_map_tall, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+```
+
+```{r, average difference}
+aggregate(big_map_tall[which(big_map_tall$generation>=100 & big_map_tall$generation<=50000),]$dif, list(big_map_tall[which(big_map_tall$generation>=100 & big_map_tall$generation<=50000),]$group), FUN=mean)
+```
+
+## Connection between higher phenotype and population (5 sec) {.tabset}
+
+### Phenotype differences
+```{r, whale}
+min_gen=100
+max_gen=10000
+rep=0
+
+whale_gen(big_map_tall, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+```
+
+### Phenotype & Populationsize differences 
+```{r, popsize and pheno}
+
+suppressMessages(print(two_hist(big_map_tall, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+```
+
+## {-}
+
+### correlation
+```{r, combo myplots}
+
+ginmin = 100
+ginmax = 10000
+
+boxplot_cors_by_gen(big_map_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+## Correlation across time {.tabset}
+
+Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
+
+### Random 1 
+```{r, GA1 cor and pheno}
+GA1_pattern <- unique(big_map_tall$snake_newt_rep)
+
+myrandomlist=sample.int(length(GA1_pattern), 3)
+
+cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=10000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2 
+```{r, random cor-pheno plot 2}
+
+cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3 
+```{r, random cor-pheno plot 3}
+
+cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+## Summary {.tabset}
+
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
+These are whole population calculations so the 5 section and 7 section data sets are not calculated differently.
+
+### Early-Sim Population Size Summary
+
+```{r, early plots summary}
+
+min_gen=100
+max_gen=10000
+GA_summary(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Early Difference Summary
+```{r, dif plots summary 1}
+
+min_gen=100
+max_gen=10000
+
+GA_summary(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+### By Snake GA 
+```{r, snakega plots summary 1}
+min_gen=100
+max_gen=10000
+#
+
+GA_summary_by_species(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA 
+```{r, newtga plots summary 1}
+min_gen=100
+max_gen=10000
+#
+
+GA_summary_by_species(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+
+```
+
+## {-}
+
+## Heatmap {.tabset}
+
+### Population Size
+
+```{r, early plots Heatmap}
+
+min_gen=100
+max_gen=10000
+#heatmap
+build_heatmap(big_map_tall, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+```
+
+### Phenotype 
+```{r, early plots Heatmap pheno 1}
+min_gen=100
+max_gen=10000
+build_heatmap(big_map_tall, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+## {-}
+
+## What is up with the correlations
+
+#### Mean 
+```{r, cor grid high cor mean, fig.height=6, fig.width=8}
+
+file=big_map_grid
+file_name="Snake_1e-11_5_Newt_1e-10_0.5_0"
+spegen=9501
+type="mean"
+row_num=200
+col_num=50
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+```{r, cor grid high cor popsize, fig.height=6, fig.width=8}
+
+file=big_map_grid
+file_name="Snake_1e-11_5_Newt_1e-10_0.5_0"
+spegen=9501
+type="num_ind"
+row_num=200
+col_num=50
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+```

### 2022-10-04 graphs_newt_snakes/corcompare.Rmd
I looked at the big map data. I got slim to stop when one population goes extenct. I am still looking at cor results.

@@
 
-ggplot(all_cor_exp) + 
-  #geom_point(size = 2) +
-  geom_line(aes(generation, num_newts_By_num_snakes, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
-  #geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)*3,fill=factor(experiment)), alpha=0.4, position="identity")+
-    geom_xsideline(aes(generation, num_newts_By_num_snakes, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
-  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
-  scale_ysidex_discrete(guide = guide_axis(angle = 45)) 
 ```

### 2022-10-07 graphs_newt_snakes/dif_cost.Rmd
looking at grids and started the cost markdown. I am also tring to put a map into my slim sim

--- 2022-08-31 graphs_newt_snakes/GA1_tall_redo_md.Rmd
@@
 ---
-title: "GA1 redo"
+title: "Different Cost"
 output: html_document
-date: '2022-08-01'
+date: '2022-10-06'
 ---
@@
 
-What does it mean to be correlated?
+How does grid size impact the spatial correlation of newt and snake phenotypes?
 
 ## Background
-
-I investigated the correlations between snake and newt phenotypes at the local grid locations along with population level phenotype.
-I found there was a lot of correlation when populations slowly adapt!
-However, after a closer investigation I found that these correlations were from a rectangle shaped area and not a square one.
-Here, I rerun the experiment with he correct square grids and discuss how the results differ.
-I also aim to investigate how changing the area/shape of the grids will influence correlation results.
-I am also thinking of ways to gather and incorperate allele information.
 
@@
 
-Landscape: 20 by 5 grid. A tall map!: 35*4 H, 35 W 
-New Landscape 28 by 7 grid: 35*4 H, 35 W
+Landscape: A tall map!: 35*4 H, 35 W
+
+I tested different cost values:
+
+  - 50
+  - 100
+  - 150
+  - 200
+  - 250
+
+Each GA combination, trial, and cost has its own msprime simulation.
 
@@
 
-I gather text file data from different files and have to do some table wrangling to get it into a format I can graph.
-I use information gathered from the entire population; data containing a mean value for the entire map (lit), correlation data based off of local populations that were divided into grids (cor) and data collected from grid based populations (grid).
-These simulations have a msprime (coalescent/burn in/random genetic variation) and then run for 50,000 generations in SLiM (co-evolution) (all with the same GA values).
-I run 4 trials for every GA combination and try two different grid sizes 20 by 5 (large) and 24 by 7 (small) in SLiM.
-These slim simulations use the same msprime simulation, but can statistically be different.
+## Preping the data by making singular files
 
@@
 thepath=/Users/victoria/Desktop/
-foldername=GA1_tall_redo
+foldername=GA1_dif_costs
 thefolder=${thepath}${foldername}/*
 
-add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"
+add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd,cost"
 
-cor_head_file=$(find ${thepath}${foldername} -name "*_GA520_cor_*" | head -n 1)
+lit_head_file=$(find ${thepath}${foldername} -name "*_lit_*" | head -n 1)
+lit_head=$(head -n 1 "${lit_head_file}")
+
+cor_head_file_2=$(find ${thepath}${foldername} -name "*_cor_*" | head -n 1)
 cor_head=$(head -n 1 "${cor_head_file}")
 
-grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
+grid_head_file_2=$(find ${thepath}${foldername} -name "*_grid_*" | head -n 1)
 grid_head=$(head -n 1 "${grid_head_file}")
-
-lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
-lit_head=$(head -n 1 "${lit_head_file}")
-
-cor_head_file_7=$(find ${thepath}${foldername} -name "*_GA728_cor_*" | head -n 1)
-cor_head_7=$(head -n 1 "${cor_head_file_7}")
-
-grid_head_file_7=$(find ${thepath}${foldername} -name "*_GA287_grid_*" | head -n 1)
-grid_head_7=$(head -n 1 "${grid_head_file_7}")
-
-lit_head_file_7=$(find ${thepath}${foldername} -name "*_GA287_lit_*" | head -n 1)
-lit_head_7=$(head -n 1 "${lit_head_file_7}")
-
-#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
-#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
-#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."
 
@@
 echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt
-echo ${lit_head_7}${add_in_column} > ${thepath}${foldername}/all_lit_7.txt
-echo ${grid_head_7}${add_in_column} > ${thepath}${foldername}/all_grid_7.txt
-echo ${cor_head_7}${add_in_column} > ${thepath}${foldername}/all_cor_7.txt
 
@@
 #getting the variables
+
 my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
-my_other_type=$(echo ${filename} |sed 's/.*GA520_//; s/_.*//')
-my_type_2=$(echo ${filename} |sed 's/.*GA287_//; s/_.*//') #testing a second grid system
-my_other_type_2=$(echo ${filename} |sed 's/.*GA728_//; s/_.*//')
 snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
@@
 newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
+cost=$(echo ${filename} |sed 's/.*cost_//; s/_.*//')
 rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
@@
 sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
+sed -i '' -e 's/$/,'${cost}'/' $filename
 #infile >outfile
@@
 
-if [[ $my_other_type == "cor" ]]
+if [[ $my_type == "cor" ]]
 then
@@
 
-if [[ $my_type_2 == "lit" ]]
-then
-    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit_7.txt
-fi
-
-if [[ $my_type_2 == "grid" ]]
-then
-    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid_7.txt
-fi
-
-if [[ $my_other_type_2 == "cor" ]]
-then
-    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor_7.txt
-fi
 done
@@
 ```
-
-```{r, data gathering}
-
-snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
-
-GA1_tall_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_lit.txt" , header = TRUE)
-
-GA1_tall_tall_file$group_rep <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep)
-
-GA1_tall_tall_file$group <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd)
-
-GA1_tall_tall_file$sim=LETTERS[factor(GA1_tall_tall_file$group)]
-GA1_tall_tall_file$dif <- GA1_tall_tall_file$Snake_mean_Pheno-GA1_tall_tall_file$Newt_mean_Pheno
-
-GA1_cor_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor.txt" , header = TRUE)
-GA1_cor_tall_file$group_rep <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd, "_", GA1_cor_tall_file$rep)
-GA1_cor_tall_file$group <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd)
-GA1_cor_tall_file$sim=LETTERS[factor(GA1_cor_tall_file$group)]
-
-GA1_grid_tall_file<-read.csv("~/Desktop/GA1_tall_redo/all_grid.txt" , header = TRUE)
-GA1_grid_tall_file$group <- paste0(GA1_grid_tall_file$snake_mu_rate, "_", GA1_grid_tall_file$snake_mu_effect_sd,"_",GA1_grid_tall_file$newt_mu_rate, "_", GA1_grid_tall_file$newt_mu_effect_sd)
-GA1_grid_tall_file$group_rep <- paste0(GA1_grid_tall_file$snake_mu_rate, "_", GA1_grid_tall_file$snake_mu_effect_sd,"_",GA1_grid_tall_file$newt_mu_rate, "_", GA1_grid_tall_file$newt_mu_effect_sd, "_", GA1_grid_tall_file$rep)
-
-GA1_grid_tall_file$sim=LETTERS[factor(GA1_grid_tall_file$group)]
-GA1_grid_tall_file$snake_newt_rep <- paste0("Snake_",GA1_grid_tall_file$snake_mu_rate, "_", GA1_grid_tall_file$snake_mu_effect_sd, "_Newt_",GA1_grid_tall_file$newt_mu_rate, "_", GA1_grid_tall_file$newt_mu_effect_sd, "_", GA1_grid_tall_file$rep)
-
-GA1_tall_tall_7_file<- read.csv("~/Desktop/GA1_tall_redo/all_lit_7.txt" , header = TRUE)
-
-GA1_tall_tall_7_file$group_rep <- paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd, "_", GA1_tall_tall_7_file$rep)
-
-GA1_tall_tall_7_file$group <- paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd)
-
-GA1_tall_tall_7_file$sim=LETTERS[factor(GA1_tall_tall_7_file$group)]
-GA1_tall_tall_7_file$dif <- GA1_tall_tall_7_file$Snake_mean_Pheno-GA1_tall_tall_7_file$Newt_mean_Pheno
-
-GA1_cor_tall_7_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor_7.txt" , header = TRUE)
-GA1_cor_tall_7_file$group_rep <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd, "_", GA1_cor_tall_7_file$rep)
-GA1_cor_tall_7_file$group <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd)
-GA1_cor_tall_7_file$sim=LETTERS[factor(GA1_cor_tall_7_file$group)]
-
-GA1_grid_tall_7_file<-read.csv("~/Desktop/GA1_tall_redo/all_grid_7.txt" , header = TRUE)
-GA1_grid_tall_7_file$group <- paste0(GA1_grid_tall_7_file$snake_mu_rate, "_", GA1_grid_tall_7_file$snake_mu_effect_sd,"_",GA1_grid_tall_7_file$newt_mu_rate, "_", GA1_grid_tall_7_file$newt_mu_effect_sd)
-GA1_grid_tall_7_file$group_rep <- paste0(GA1_grid_tall_7_file$snake_mu_rate, "_", GA1_grid_tall_7_file$snake_mu_effect_sd,"_",GA1_grid_tall_7_file$newt_mu_rate, "_", GA1_grid_tall_7_file$newt_mu_effect_sd, "_", GA1_grid_tall_7_file$rep)
-
-GA1_grid_tall_7_file$sim=LETTERS[factor(GA1_grid_tall_7_file$group)]
-GA1_grid_tall_7_file$snake_newt_rep <- paste0("Snake_",GA1_grid_tall_7_file$snake_mu_rate, "_", GA1_grid_tall_7_file$snake_mu_effect_sd, "_Newt_",GA1_grid_tall_7_file$newt_mu_rate, "_", GA1_grid_tall_7_file$newt_mu_effect_sd, "_", GA1_grid_tall_7_file$rep)
-
-```
-
-```{r, cor box set up}
-
-boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
- snewt$mean_res = snewt$mean_toxin+snewt$dif
-  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  unique(file$sim)
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
-  ylim(-1.1, 1.1)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
-  xlab(x_label) + ylab(y_label)+
-  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
-  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
-    geom_hline(yintercept=0, linetype="solid")+
-  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
-  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
-  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
-  theme(plot.title = element_text(size=5)) +
-  facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
-                      strip.background = element_blank(), strip.text.x = element_blank(),
-                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
-                      axis.title.y = element_blank())
-
-  return(plot)
-}
-
-hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
- snewt$mean_res = snewt$mean_toxin+snewt$dif
-  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  #unique(file$sim)
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
-  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
-  geom_vline(xintercept=0, linetype="solid")+
-  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
-  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
-  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
-  theme(plot.title = element_text(size=5)) +
-  xlim(-1.1, 1.1)+
-  facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
-                      strip.background = element_blank(), strip.text.x = element_blank(),
-                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
-                      axis.title.y = element_blank())
-
-  return(plot)
-}
-
-hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
- snewt$mean_res = snewt$mean_toxin+snewt$dif
-  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  unique(file$sim)
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
-  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
-  geom_vline(xintercept=0, linetype="solid")+
-  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
-  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
-  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
-  theme(plot.title = element_text(size=5)) +
-  #stat_bin(bins=30)+
-  facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
-                      strip.background = element_blank(), strip.text.x = element_blank(),
-                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
-                      axis.title.y = element_blank())
-
-suppressMessages(print(plot))
-
-  return(plot)
-}
-
-var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
-  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
-  real_snewt_var = var(snewt$dif)
-  var_cor_table=data.frame()
-
-  for(i in 1:length(unique(file$snake_newt_rep))){
-    pattern<-unique(file$snake_newt_rep)[i]
-    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
-    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
-
-    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
-    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
-  }
-
-  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
-  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
-
-  plot <- ggplot(var_cor_table) +
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
-  xlab(x_label) + ylab(y_label)+
-  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
-  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
-  theme(plot.title = element_text(size=5)) +
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
-
-  return(plot)
-}
-
-cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=GA1_tall_tall_file
-#cfile=GA1_cor_tall_file 
- # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
- file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
-  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
-    #geom_line(aes(generation, dif, group=rep, col="dif"))+
-      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
-    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
-    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
-    #ylim(0,10)+
-    #xlab(x_label) + ylab(y_label)+
-    scale_color_manual(name = "Type",
-values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
-labels = c("Snake", "Newt"))+
-    theme_bw() +theme(legend.position="none",
-                      strip.background = element_blank(), strip.text.x = element_blank(),
-                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
-                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
-                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
-
-  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
-    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
-    #ggtitle(title, subtitle = subt) +
-    ylim(-1.1, 1.1)+
-    #xlab(x_label_cor) + ylab(y_label)+
-    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
-                      strip.background = element_blank(), strip.text.x = element_blank(),
-                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
-                      axis.title.y = element_blank(),
-                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
-
-  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
-  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
-
-  if(nrow(cfile)>nrow(file)){
-    toDelete <- seq(0, nrow(cfile), 2)
-    cfile_short <-  cfile[-toDelete, ]
-  }else{
-    cfile_short <-  cfile
-  }
-
-  if(nrow(cfile_short)>nrow(file)){
-      toDelete <- seq(0, nrow(cfile_short), 2)
-      cfile_short <-  cfile_short[-toDelete, ]
-    }
-  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
-    print(paste0("pattern ", pattern))
-  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
-  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
-  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
-  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
-  return(figure)
-}
-
-four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
-  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
-  ylim(-1.1, 1.1)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
-  xlab(x_label) + ylab(y_label)+
-  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
-  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
-  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
-  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
-  geom_hline(yintercept=0, linetype="solid")+
-  theme(plot.title = element_text(size=5)) +
-  facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
-                      strip.background = element_blank(), strip.text.x = element_blank(),
-                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
-                      axis.title.y = element_blank())
-
-  return(plot)
-}
-
-```
-
-```{r, general file and graph making}
-
-#the functions to make the params file and the summary and heatmap figures
-
-create_parm_file <- function(file, min_gen, max_gen){
-params <- data_frame()
-
-for(i in 1:length(unique(file$snake_newt_rep))){
-
-  pattern=unique(file$snake_newt_rep)[i]
-  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]
-
-  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
-                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
-                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
-                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
-                           Newt_pop_size=mean(sumitup$Newt_pop_size),
-                           Snake_pop_size=mean(sumitup$Snake_pop_size),
-                           dif=mean(sumitup$dif),
-                           snake_mu_rate=sumitup$snake_mu_rate[1],
-                           newt_mu_rate=sumitup$newt_mu_rate[1],
-                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
-                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
-                           rep=sumitup$rep[1])
-
-  params <- rbind(params, params_temp)
-}
-
-params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
-params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
-params$snake_newt <- paste0(params$snake, "_", params$newt)
-return(params)
-}
-
-GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
-
-file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
-
-params<-create_parm_file(file, min_gen, max_gen)
-
-my_plot <- ggplot(params) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
-#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  #facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
-
-return(my_plot)
-}
-
-build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
-  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
-  params<-create_parm_file(file, min_gen, max_gen)
-
- my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
-
- if(red_blue==FALSE){
-  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
-  }
- if(red_blue==TRUE){
-  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
- }
-
-  return(my_plot)
-}
-
-trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
-
-  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
-    facet_wrap(~sim)+
-    geom_line(aes(generation, dif, group=rep, col="dif"))+
-    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
-    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
-    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
-    ylim(-1.,2.5)+
-    xlab(x_label) + ylab(y_label)+
-    scale_color_manual(name = "Type",
-values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
-labels = c("Snake", "Newt", "Dif"))+
-    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
-                      strip.background = element_blank(), strip.text.x = element_blank(),
-                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
-                      axis.title.y = element_blank())
-  return(plot)
-}
-
-whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
-  xlab(x_label) + ylab(y_label)+
-  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      # strip.background = element_blank(), 
-                      # strip.text.x = element_blank(), 
-                      # panel.grid.major = element_blank(), 
-                      # panel.grid.minor = element_blank(),
-                      # panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
-pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
-  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
-  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
-  true_max <- max(abs(themin), abs(themax))
-dif <- ggplot(file) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
-  xlim((-1*themax)-5, themax+5)+
-  theme(plot.title = element_text(size=5)) +
-  facet_wrap(~sim)+
-  geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      # strip.background = element_blank(), 
-                      # strip.text.x = element_blank(), 
-                      # panel.grid.major = element_blank(), 
-                      # panel.grid.minor = element_blank(),
-                      # panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-}
-
-pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
-
-  themin <- min(file$dif) 
-  themax <- max(file$dif)
-  true_max <- max(abs(themin), abs(themax))
-dif <- ggplot(file) +
-  #xlim(0, 1000)+
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(dif), fill="aquamarine4")+
-  xlim((-1*true_max)-1, true_max+1)+
-
-  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      # strip.background = element_blank(), 
-                      # strip.text.x = element_blank(), 
-                      # panel.grid.major = element_blank(), 
-                      # panel.grid.minor = element_blank(),
-                      # panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
-two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
-
-  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
-  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
-  thedifmin <- min(file$dif) 
-  thedifmax <- max(file$dif)
-  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
-
-  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
-dif <- ggplot(file) +
-
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
-  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
-  scale_y_continuous(labels = scales::percent)+
-  xlim((-1*true_max)-1, true_max+1)+
-  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      # strip.background = element_blank(), 
-                      # strip.text.x = element_blank(), 
-                      # panel.grid.major = element_blank(), 
-                      # panel.grid.minor = element_blank(),
-                      # panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
-two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file$rep==rep
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
-
-  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
-  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
-  thedifmin <- min(file$dif) 
-  thedifmax <- max(file$dif)
-  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
-
-  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
-
-dif <- ggplot(file) +
-
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
-  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
-  scale_y_continuous(labels = scales::percent)+
-  xlim((-1*true_max)-1, true_max+1)+
-  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      #strip.background = element_blank(), 
-                      strip.text.x = element_blank(), 
-                      #panel.grid.major = element_blank(), 
-                      #panel.grid.minor = element_blank(),
-                      #panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
-two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=GA1_tall_tall_file
-  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
-  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-
-  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
-
-  thepopmin <- min(file$newt_deaths)
-  thepopmax <- max(file$newt_deaths)
-  thedifmin <- min(file$snake_deaths) 
-  thedifmax <- max(file$snake_deaths)
-  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
-
-  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
-
-dif <- ggplot(file) +
-
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
-  xlab(x_label) + ylab(y_label)+
-  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
-  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
-  #scale_y_continuous(labels = scales::percent)+
-  #xlim((-1*true_max)-1, true_max+1)+
-  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
-  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
-  theme(plot.title = element_text(size=5)) +
-  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
-  #labs(colour = color_label) +
-  facet_wrap(~sim)+
-  #geom_vline(xintercept = 0)+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      #strip.background = element_blank(), 
-                      strip.text.x = element_blank(), 
-                      #panel.grid.major = element_blank(), 
-                      #panel.grid.minor = element_blank(),
-                      #panel.background = element_blank(), 
-                      axis.line = element_line(colour = "black"))
-
-return(dif)
-
-}
-
-#two_hist_death_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
-
-```
-
-## Mean Phenotype Whole Simulation
-
-First, I will look at a plot of how the mean phenotype of the entire population of newts and snakes changes overtime.
-Each of these plots has three colored lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype.
-There are 4 line per color that represent the different replicas that I ran.
-**Note this is a mean for the entire population.** Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).
-
-```{r, graphing by gen}
-trends_by_gen(GA1_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
-
-aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group), FUN=mean)
-
-aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
-
-trends_by_gen(GA1_tall_tall_7_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
-
-aggregate(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$dif, list(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$group), FUN=mean)
-
-aggregate(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$dif, list(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$group_rep), FUN=mean)
-
-```
-
-#### Connection between higher phenotype and population
-
-```{r, whale}
-min_gen=5000
-max_gen=10000
-rep=0
-
-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-
-suppressMessages(print(two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
-
-whale_gen(GA1_tall_tall_7_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-
-suppressMessages(print(two_hist_all_rep(GA1_tall_tall_7_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
-
-```
-
-I looked at the results between 5,000 - 10,000 generations where I saw most of the increase in newt and snake phenotype.
-The first plot has newt population size by snake population size with the color representing the difference between snake and newt mean phenotype (red=newts have a higher mean phenotype, blue=snakes have a higher mean phenotype).
-The third GA (an intermediate one) seems to do better then all of the other GAs (blue row (3), red column (3)).
-However, this is dependent on the point in the simulation you focus on.
-The next two plots show the difference between snake and newt population size (green) and phenotype (purple).
-For the most part these suggest that when the mean phenotype is higher so is the population size.
-This also shows the asymmetrical nature between the predator-prey interaction (higher max population sizes seen in snakes).
-The population size is also more variable than the phenotype (difference in population size has a wider range).
-
-## Correlation
-
-The next section I aim to look at how correlated newt and snakes are at local populations across the geographical area.
-I am examining correlation between newt and snake phenotypes, population sizes of newts and snakes, amount of toxin and snake population, and the amount of resistance and newt population size.
-I predicted that there would be a positive correlation between the phenotypes, and a negative correlation between population sizes, and the amount of toxin/resistance and population size.
-Below is a legend for the first two plots.
-The third plot is colored by trial.
-
-Legend:
-
-- "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
-- "CB" = num_newts_By_num_snakes (Green)
-- "CC" = sum_newt_pheno_By_num_snake (Blue)
-- "CD" = sum_snake_pheno_By_num_newt (Purple)
-
-I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
-The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
-The second figure shows the the results of all 4 trials for each correlation measurement I made from 10,000-15,000 generations.
-The third plot takes the information from the fist plot and shows the distribution of correlation values by each trial (solid line at 0, dashed line at real newt-snake correlation).
-
-```{r, combo myplots}
-#files
-#GA1_tall_tall_file
-#GA2_long_file 
-#GA1_cor_tall_file
-#GA2_cor_file
-
-ginmin = 10000
-ginmax = 15000
-
-boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-four_types_boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-boxplot_cors_by_gen(GA1_cor_tall_7_file, "Simulation Correlation 7 Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-four_types_boxplot_cors_by_gen(GA1_cor_tall_7_file, "Simulation four Correlation 7", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation 7 Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-```
-
-## Results {.tabset}
-
-### Plot 1
-```{r, ga1 cor by dif windows}
-ginmin = 0
-ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 2
-
-```{r, ga1 cor by dif windows 2}
-ginmin = 5000
-ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 3
-```{r, ga1 cor by dif windows 3}
-ginmin = 10000
-ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 4
-```{r, ga1 cor by dif windows 4}
-ginmin = 15000
-ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 5
-```{r, ga1 cor by dif windows 5}
-ginmin = 20000
-ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 6
-```{r, ga1 cor by dif windows 6}
-ginmin = 25000
-ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 7
-```{r, ga1 cor by dif windows 7}
-ginmin = 30000
-ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 8
-```{r, ga1 cor by dif windows 8}
-ginmin = 35000
-ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 9
-```{r, ga1 cor by dif windows 9}
-ginmin = 40000
-ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 10
-```{r, ga1 cor by dif windows 10}
-ginmin = 45000
-ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-## {-}
-
-## Results {.tabset}
-
-### Plot 1
-```{r, ga1 cor by dif windows}
-ginmin = 0
-ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 2
-
-```{r, ga1 cor by dif windows 2}
-ginmin = 5000
-ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 3
-```{r, ga1 cor by dif windows 3}
-ginmin = 10000
-ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 4
-```{r, ga1 cor by dif windows 4}
-ginmin = 15000
-ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 5
-```{r, ga1 cor by dif windows 5}
-ginmin = 20000
-ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 6
-```{r, ga1 cor by dif windows 6}
-ginmin = 25000
-ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 7
-```{r, ga1 cor by dif windows 7}
-ginmin = 30000
-ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 8
-```{r, ga1 cor by dif windows 8}
-ginmin = 35000
-ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 9
-```{r, ga1 cor by dif windows 9}
-ginmin = 40000
-ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 10
-```{r, ga1 cor by dif windows 10}
-ginmin = 45000
-ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-## {-}
-
-## Correlation across time
-
-```{r, ga1 cor and pheno}
-GA1_pattern <- unique(paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep))
-for(i in 1:length(GA1_pattern)){
-  myine<-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
-  plot(myine)
-}
-
-```
-
-```{r, ga1 cor 7 and pheno}
-GA1_pattern_7 <- unique(paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd, "_", GA1_tall_tall_7_file$rep))
-for(i in 1:length(GA1_pattern_7)){
-  myine<-cor_trends_by_gen(GA1_tall_tall_7_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern_7[i])
-  plot(myine)
-}
-
-```
-
-## What happens over time (looking at the beginning. middle, and late part of my simulations)
-
-```{r, early plots summary}
-
-min_gen=100
-max_gen=5000
-GA1_tall_tall_7_file_temp<-GA1_tall_tall_7_file
-GA1_tall_tall_7_file_temp$rep<-as.numeric(GA1_tall_tall_7_file_temp$rep)+4
-test<-rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp)
-
-# summary
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-min_gen=10000
-max_gen=15000
-
-# summary
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-min_gen=45000
-max_gen=50000
-
-# summary
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-min_gen=100
-max_gen=5000
-
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-min_gen=10000
-max_gen=15000
-
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-min_gen=45000
-max_gen=50000
-
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-```
-
-```{r, early plots Heatmap}
-
-min_gen=100
-max_gen=5000
-#heatmap
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-min_gen=10000
-max_gen=15000
-#heatmap
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-min_gen=45000
-max_gen=50000
-#heatmap
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-min_gen=100
-max_gen=5000
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-min_gen=10000
-max_gen=15000
-#heatmap
-
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-min_gen=45000
-max_gen=50000
-#heatmap
-
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-```
-
-## What is up with the correlations
-
-### Snake_1e-09_0.05_Newt_1e-09_0.05_2
-
-```{r, cor grid by location}
-
-#GA1_grid_tall_file
-
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-spegen=25001
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
-
-data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
-
-data_long_mean_short<-data_long_mean
-
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
-newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Mean Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-```{r, cor grid by location}
-
-#GA1_grid_tall_7_file
-
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-spegen=25001
-
-GA1<-GA1_grid_tall_7_file[which(GA1_grid_tall_7_file$snake_newt_rep==file_name & GA1_grid_tall_7_file$generation==spegen),]
-
-GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
-
-data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
-
-data_long_mean_short<-data_long_mean
-
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
-newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Mean Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-```{r, cor grid by location}
-
-#GA1_grid_tall_file
-
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-spegen=26051
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
-
-data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
-
-data_long_mean_short<-data_long_mean
-
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
-newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Mean Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# max phenotype
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
-
-data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
-
-data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
-
-data_long_max_short<-data_long_max
-
-data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_max_short)+
-  labs(title = "Max Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
-newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Max Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# max phenotype
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
-
-data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
-
-data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
-
-data_long_min_short<-data_long_min
-
-data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_min_short)+
-  labs(title = "Min Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
-newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Min Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-#GA1_grid_tall_file population size
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
-
-GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
-
-GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
-
-GA1_data_long_ind_short<-GA1_data_long_ind
-
-GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
-
-main_plot<-ggplot(GA1_data_long_ind_short)+
-  labs(title = "Locations of Ind",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Number of Individuals")+
-  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c(option = "plasma")+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
-newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
-newt_GA1$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
-
-newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
-
-extra_plot <- ggplot(newt_GA1)+
-  ggtitle("Num of Ind") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-### Snake_1e-08_0.005_Newt_1e-08_0.005_3
-
-```{r, cor grid by location round 2}
-
-#GA1_grid_tall_file
-
-file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
-spegen=25001
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
-
-data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
-
-data_long_mean_short<-data_long_mean
-
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
-newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Mean Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# SD
-
-GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
-
-data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
-
-data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
-
-data_long_sd_short<-data_long_sd
-
-data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_sd_short)+
-  labs(title = "SD Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
-newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("SD Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# max phenotype
-
-GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
-
-data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
-
-data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
-
-data_long_max_short<-data_long_max
-
-data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_max_short)+
-  labs(title = "Max Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
-newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Max Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# min phenotype
-
-GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
-
-data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
-
-data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
-
-data_long_min_short<-data_long_min
-
-data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_min_short)+
-  labs(title = "Min Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
-newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Min Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-#GA1_grid_tall_file population size
-
-GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
-
-GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
-
-GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
-
-GA1_data_long_ind_short<-GA1_data_long_ind
-
-GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
-
-main_plot<-ggplot(GA1_data_long_ind_short)+
-  labs(title = "Locations of Ind",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Number of Individuals")+
-  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c(option = "plasma")+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
-newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
-newt_GA1$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
-
-newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
-
-extra_plot <- ggplot(newt_GA1)+
-  ggtitle("Num of Ind") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```

### 2022-10-07 graphs_newt_snakes/grid_test.Rmd
looking at grids and started the cost markdown. I am also tring to put a map into my slim sim

@@
 thepath=/Users/victoria/Desktop/
-foldername=GA1_dif_grid
+foldername=GA1_dif_grids
 thefolder=${thepath}${foldername}/*
@@
 
-GA1_lit_grid_file<- read.csv("~/Desktop/GA1_dif_grid/all_lit.txt" , header = TRUE)
+GA1_lit_grid_file<- read.csv("~/Desktop/GA1_dif_grids/all_lit.txt" , header = TRUE)
 GA1_lit_grid_file$group_rep <- paste0(GA1_lit_grid_file$snake_mu_rate, "_", GA1_lit_grid_file$snake_mu_effect_sd,"_",GA1_lit_grid_file$newt_mu_rate, "_", GA1_lit_grid_file$newt_mu_effect_sd, "_", GA1_lit_grid_file$rep)
@@
 GA1_lit_grid_file$sim=LETTERS[factor(GA1_lit_grid_file$group)]
+GA1_lit_grid_file$dif=GA1_lit_grid_file$Snake_mean_Pheno-GA1_lit_grid_file$Newt_mean_Pheno
 
-GA1_cor_grid_2_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_2.txt" , header = TRUE)
+GA1_cor_grid_2_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_2.txt" , header = TRUE)
 GA1_cor_grid_2_file$group_rep <- paste0(GA1_cor_grid_2_file$snake_mu_rate, "_", GA1_cor_grid_2_file$snake_mu_effect_sd,"_",GA1_cor_grid_2_file$newt_mu_rate, "_", GA1_cor_grid_2_file$newt_mu_effect_sd, "_", GA1_cor_grid_2_file$rep)
@@
 
-GA1_cor_grid_3_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_3.txt" , header = TRUE)
+GA1_cor_grid_3_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_3.txt" , header = TRUE)
 GA1_cor_grid_3_file$group_rep <- paste0(GA1_cor_grid_3_file$snake_mu_rate, "_", GA1_cor_grid_3_file$snake_mu_effect_sd,"_",GA1_cor_grid_3_file$newt_mu_rate, "_", GA1_cor_grid_3_file$newt_mu_effect_sd, "_", GA1_cor_grid_3_file$rep)
@@
 
-GA1_cor_grid_4_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_4.txt" , header = TRUE)
+GA1_cor_grid_4_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_4.txt" , header = TRUE)
 GA1_cor_grid_4_file$group_rep <- paste0(GA1_cor_grid_4_file$snake_mu_rate, "_", GA1_cor_grid_4_file$snake_mu_effect_sd,"_",GA1_cor_grid_4_file$newt_mu_rate, "_", GA1_cor_grid_4_file$newt_mu_effect_sd, "_", GA1_cor_grid_4_file$rep)
@@
 
-GA1_cor_grid_5_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_5.txt" , header = TRUE)
+GA1_cor_grid_5_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_5.txt" , header = TRUE)
 GA1_cor_grid_5_file$group_rep <- paste0(GA1_cor_grid_5_file$snake_mu_rate, "_", GA1_cor_grid_5_file$snake_mu_effect_sd,"_",GA1_cor_grid_5_file$newt_mu_rate, "_", GA1_cor_grid_5_file$newt_mu_effect_sd, "_", GA1_cor_grid_5_file$rep)
@@
 
-GA1_cor_grid_6_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_6.txt" , header = TRUE)
+GA1_cor_grid_6_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_6.txt" , header = TRUE)
 GA1_cor_grid_6_file$group_rep <- paste0(GA1_cor_grid_6_file$snake_mu_rate, "_", GA1_cor_grid_6_file$snake_mu_effect_sd,"_",GA1_cor_grid_6_file$newt_mu_rate, "_", GA1_cor_grid_6_file$newt_mu_effect_sd, "_", GA1_cor_grid_6_file$rep)
@@
 
-GA1_cor_grid_7_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_7.txt" , header = TRUE)
+GA1_cor_grid_7_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_7.txt" , header = TRUE)
 GA1_cor_grid_7_file$group_rep <- paste0(GA1_cor_grid_7_file$snake_mu_rate, "_", GA1_cor_grid_7_file$snake_mu_effect_sd,"_",GA1_cor_grid_7_file$newt_mu_rate, "_", GA1_cor_grid_7_file$newt_mu_effect_sd, "_", GA1_cor_grid_7_file$rep)
@@
 
-# GA1_grid_grid_2_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_2.txt" , header = TRUE)
+# GA1_grid_grid_2_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_2.txt" , header = TRUE)
 # GA1_grid_grid_2_file$group_rep <- paste0(GA1_grid_grid_2_file$snake_mu_rate, "_", GA1_grid_grid_2_file$snake_mu_effect_sd,"_",GA1_grid_grid_2_file$newt_mu_rate, "_", GA1_grid_grid_2_file$newt_mu_effect_sd, "_", GA1_grid_grid_2_file$rep)
@@
 # 
-# GA1_grid_grid_3_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_3.txt" , header = TRUE)
+# GA1_grid_grid_3_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_3.txt" , header = TRUE)
 # GA1_grid_grid_3_file$group_rep <- paste0(GA1_grid_grid_3_file$snake_mu_rate, "_", GA1_grid_grid_3_file$snake_mu_effect_sd,"_",GA1_grid_grid_3_file$newt_mu_rate, "_", GA1_grid_grid_3_file$newt_mu_effect_sd, "_", GA1_grid_grid_3_file$rep)
@@
 # 
-# GA1_grid_grid_4_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_4.txt" , header = TRUE)
+# GA1_grid_grid_4_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_4.txt" , header = TRUE)
 # GA1_grid_grid_4_file$group_rep <- paste0(GA1_grid_grid_4_file$snake_mu_rate, "_", GA1_grid_grid_4_file$snake_mu_effect_sd,"_",GA1_grid_grid_4_file$newt_mu_rate, "_", GA1_grid_grid_4_file$newt_mu_effect_sd, "_", GA1_grid_grid_4_file$rep)
@@
 # 
-# GA1_grid_grid_5_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_5.txt" , header = TRUE)
+# GA1_grid_grid_5_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_5.txt" , header = TRUE)
 # GA1_grid_grid_5_file$group_rep <- paste0(GA1_grid_grid_5_file$snake_mu_rate, "_", GA1_grid_grid_5_file$snake_mu_effect_sd,"_",GA1_grid_grid_5_file$newt_mu_rate, "_", GA1_grid_grid_5_file$newt_mu_effect_sd, "_", GA1_grid_grid_5_file$rep)
@@
 # 
-# GA1_grid_grid_6_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_6.txt" , header = TRUE)
+# GA1_grid_grid_6_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_6.txt" , header = TRUE)
 # GA1_grid_grid_6_file$group_rep <- paste0(GA1_grid_grid_6_file$snake_mu_rate, "_", GA1_grid_grid_6_file$snake_mu_effect_sd,"_",GA1_grid_grid_6_file$newt_mu_rate, "_", GA1_grid_grid_6_file$newt_mu_effect_sd, "_", GA1_grid_grid_6_file$rep)
@@
 # 
-# GA1_grid_grid_7_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_7.txt" , header = TRUE)
+# GA1_grid_grid_7_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_7.txt" , header = TRUE)
 # GA1_grid_grid_7_file$group_rep <- paste0(GA1_grid_grid_7_file$snake_mu_rate, "_", GA1_grid_grid_7_file$snake_mu_effect_sd,"_",GA1_grid_grid_7_file$newt_mu_rate, "_", GA1_grid_grid_7_file$newt_mu_effect_sd, "_", GA1_grid_grid_7_file$rep)
@@
 
-# all_grid_grid = rbind(GA1_grid_grid_2_file, GA1_grid_grid_3_file, GA1_grid_grid_4_file,  GA1_grid_grid_5_file,  GA1_grid_grid_6_file,  GA1_grid_grid_7_file)
-# 
-# all_grid_grid$group_exp=paste0(all_grid_grid$group, "_", all_grid_grid$experiment)
-# all_grid_grid$exp_group=paste0(all_grid_grid$experiment, "_", all_grid_grid$group)
+```
+
+```{r, cor box set up}
+
+boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+    geom_hline(yintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+boxplot_cor_grid_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(grid_num), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = factor(grid_num)))+
+  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+    geom_hline(yintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  #unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  xlim(-1.1, 1.1)+
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  #stat_bin(bins=30)+
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+suppressMessages(print(plot))
+
+  return(plot)
+}
+
+var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  real_snewt_var = var(snewt$dif)
+  var_cor_table=data.frame()
+
+  for(i in 1:length(unique(file$snake_newt_rep))){
+    pattern<-unique(file$snake_newt_rep)[i]
+    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
+    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
+
+    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
+    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+  }
+
+  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
+  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+
+  plot <- ggplot(var_cor_table) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+  return(plot)
+}
+
+cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+#file=GA1_lit_grid_file
+#cfile=all_cor_grid 
+ # pattern="1e-11_5_1e-11_5_0"
+ # pattern="1e-11_5_1e-11_5_0"  
+ file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
+
+  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
+    #ylim(0,10)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() +theme(legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
+                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
+cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col=factor(grid_num)))+
+    #ggtitle(title, subtitle = subt) +
+    ylim(-1.1, 1.1)+
+    #xlab(x_label_cor) + ylab(y_label)+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(),
+                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
+
+  figure <- ggarrange(plot_1, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
+
+  return(figure)
+}
+
+pop_size_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+#file=GA1_lit_grid_file
+#cfile=all_cor_grid 
+ # pattern="1e-11_5_1e-11_5_0"
+ # pattern="1e-11_5_1e-11_5_0"  
+ file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
+
+  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
+    geom_line(aes(generation, Snake_pop_size, group=rep, color="Snake"),)+
+    geom_line(aes(generation, Newt_pop_size, group=rep, color="Newt"))+
+    #ylim(0,10)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake" = "steelblue", "Newt" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() +theme(legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
+                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
+cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+    geom_line(aes(generation, num_newts_By_num_snakes, col=factor(grid_num)))+
+    #ggtitle(title, subtitle = subt) +
+    ylim(-1.1, 1.1)+
+    #xlab(x_label_cor) + ylab(y_label)+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(),
+                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
+
+  figure <- ggarrange(plot_1, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
+
+  return(figure)
+}
+
+four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  geom_hline(yintercept=0, linetype="solid")+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
 
 ```
+
+```{r, general file and graph making}
+
+#the functions to make the params file and the summary and heatmap figures
+
+create_parm_file <- function(file, min_gen, max_gen){
+params <- data_frame()
+
+for(i in 1:length(unique(file$snake_newt_rep))){
+
+  pattern=unique(file$snake_newt_rep)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]
+
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=sumitup$snake_mu_rate[1],
+                           newt_mu_rate=sumitup$newt_mu_rate[1],
+                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
+                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
+                           rep=sumitup$rep[1])
+
+  params <- rbind(params, params_temp)
+}
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$snake_newt <- paste0(params$snake, "_", params$newt)
+return(params)
+}
+
+GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+
+build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
+  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+  params<-create_parm_file(file, min_gen, max_gen)
+
+ my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
+
+ if(red_blue==FALSE){
+  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
+  }
+ if(red_blue==TRUE){
+  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
+ }
+
+  return(my_plot)
+}
+
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){
+
+  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
+    facet_wrap(~sim)+
+    geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
+    #ylim(-1.,2.5)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+  return(plot)
+}
+
+whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
+  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
+  xlim((-1*themax)-5, themax+5)+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+}
+
+pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  themin <- min(file$dif) 
+  themax <- max(file$dif)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(dif), fill="aquamarine4")+
+  xlim((-1*true_max)-1, true_max+1)+
+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file=GA1_lit_grid_file
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$newt_deaths)
+  thepopmax <- max(file$newt_deaths)
+  thedifmin <- min(file$snake_deaths) 
+  thedifmax <- max(file$snake_deaths)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
+  #scale_y_continuous(labels = scales::percent)+
+  #xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  #geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+grid_plot<- function(file_name, spegen, file, type, row_num, col_num){
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
+GA1_type = paste0("generation|", type)
+
+GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
+GA1_type <- GA1_type[-1]
+
+data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
+data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)
+
+data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)
+
+data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))
+
+main_plot<-ggplot(data_long_type_comp)+
+
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  #ylim(0, row_num)+
+  #xlim(0, col_num)+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+if(type != "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+ scale_fill_viridis_c()
+}
+if(type == "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Newt/Snake Phenotype")+
+scale_fill_viridis_c(option = "plasma")
+}
+
+snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
+newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
+newt$snake_value <- snake$measurement
+print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))
+
+newt$info <- "middle"
+newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
+return(final_plot)}
+
+```
+
+generations
+```{r, graphing by gen}
+trends_by_gen(GA1_lit_grid_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+```
+```{r, whale}
+min_gen=5000
+max_gen=10000
+rep=1
+
+whale_gen(GA1_lit_grid_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+```
+```{r, combo myplots}
+
+ginmin = 10000
+ginmax = 15000
+
+boxplot_cors_by_gen(GA1_cor_grid_2_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+boxplot_cors_by_gen(GA1_cor_grid_3_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+boxplot_cors_by_gen(GA1_cor_grid_4_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+boxplot_cors_by_gen(GA1_cor_grid_5_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+boxplot_cors_by_gen(GA1_cor_grid_6_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+boxplot_cors_by_gen(GA1_cor_grid_7_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(all_cor_grid, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+## Correlation Histograms  {.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
+This section only looks at the 5 sections.
+
+### Plot 1
+```{r, GA1 cor by dif windows}
+ginmin = 0
+ginmax = 5000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 2
+
+```{r, GA1 cor by dif windows 2}
+ginmin = 5000
+ginmax = 10000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 3
+```{r, GA1 cor by dif windows 3}
+ginmin = 10000
+ginmax = 15000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 4
+```{r, GA1 cor by dif windows 4}
+ginmin = 15000
+ginmax = 20000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 5
+```{r, GA1 cor by dif windows 5}
+ginmin = 20000
+ginmax = 25000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 6
+```{r, GA1 cor by dif windows 6}
+ginmin = 25000
+ginmax = 30000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 7
+```{r, GA1 cor by dif windows 7}
+ginmin = 30000
+ginmax = 35000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 8
+```{r, GA1 cor by dif windows 8}
+ginmin = 35000
+ginmax = 40000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 9
+```{r, GA1 cor by dif windows 9}
+ginmin = 40000
+ginmax = 45000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 10
+```{r, GA1 cor by dif windows 10}
+ginmin = 45000
+ginmax = 50000
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+## {-}
+
+## Phenotype Correlation across time {.tabset}
+
+Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
+
+### Random 1 (5 sec)
+```{r, GA1 cor and pheno}
+GA1_pattern <- unique(paste0(GA1_lit_grid_file$snake_mu_rate, "_", GA1_lit_grid_file$snake_mu_effect_sd,"_",GA1_lit_grid_file$newt_mu_rate, "_", GA1_lit_grid_file$newt_mu_effect_sd, "_", GA1_lit_grid_file$rep))
+
+myrandomlist=sample.int(length(GA1_pattern), 3)
+
+cor_trends_by_gen(GA1_lit_grid_file, all_cor_grid, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2 (5 sec)
+```{r, random cor-pheno plot 2}
+
+cor_trends_by_gen(GA1_lit_grid_file, all_cor_grid, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3 (5 sec)
+```{r, random cor-pheno plot 3}
+
+cor_trends_by_gen(GA1_lit_grid_file, all_cor_grid, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+## Population Size Correlation across time {.tabset}
+
+### Random 1 
+```{r, GA1 pop size 1}
+pop_size_trends_by_gen(GA1_lit_grid_file, all_cor_grid, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2 
+```{r, random pop size plot 2}
+
+pop_size_trends_by_gen(GA1_lit_grid_file, all_cor_grid, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3 
+```{r, random pop size plot 3}
+
+pop_size_trends_by_gen(GA1_lit_grid_file, all_cor_grid, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+```{r, red in grid files}
+require(readr)
+GA1_grid_grid_2_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_2.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+GA1_grid_grid_2_file$group_rep <- paste0(GA1_grid_grid_2_file$snake_mu_rate, "_", GA1_grid_grid_2_file$snake_mu_effect_sd,"_",GA1_grid_grid_2_file$newt_mu_rate, "_", GA1_grid_grid_2_file$newt_mu_effect_sd, "_", GA1_grid_grid_2_file$rep)
+GA1_grid_grid_2_file$group <- paste0(GA1_grid_grid_2_file$snake_mu_rate, "_", GA1_grid_grid_2_file$snake_mu_effect_sd,"_",GA1_grid_grid_2_file$newt_mu_rate, "_", GA1_grid_grid_2_file$newt_mu_effect_sd)
+GA1_grid_grid_2_file$sim=LETTERS[factor(GA1_grid_grid_2_file$group)]
+GA1_grid_grid_2_file$grid_num = 2
+
+GA1_grid_grid_3_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_3.txt" , header = TRUE)%>%  filter(between(generation, 9000, 10000))
+GA1_grid_grid_3_file$group_rep <- paste0(GA1_grid_grid_3_file$snake_mu_rate, "_", GA1_grid_grid_3_file$snake_mu_effect_sd,"_",GA1_grid_grid_3_file$newt_mu_rate, "_", GA1_grid_grid_3_file$newt_mu_effect_sd, "_", GA1_grid_grid_3_file$rep)
+GA1_grid_grid_3_file$group <- paste0(GA1_grid_grid_3_file$snake_mu_rate, "_", GA1_grid_grid_3_file$snake_mu_effect_sd,"_",GA1_grid_grid_3_file$newt_mu_rate, "_", GA1_grid_grid_3_file$newt_mu_effect_sd)
+GA1_grid_grid_3_file$sim=LETTERS[factor(GA1_grid_grid_3_file$group)]
+GA1_grid_grid_3_file$grid_num = 3
+
+GA1_grid_grid_4_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_4.txt" , header = TRUE)%>%  filter(between(generation, 9000, 10000))
+GA1_grid_grid_4_file$group_rep <- paste0(GA1_grid_grid_4_file$snake_mu_rate, "_", GA1_grid_grid_4_file$snake_mu_effect_sd,"_",GA1_grid_grid_4_file$newt_mu_rate, "_", GA1_grid_grid_4_file$newt_mu_effect_sd, "_", GA1_grid_grid_4_file$rep)
+GA1_grid_grid_4_file$group <- paste0(GA1_grid_grid_4_file$snake_mu_rate, "_", GA1_grid_grid_4_file$snake_mu_effect_sd,"_",GA1_grid_grid_4_file$newt_mu_rate, "_", GA1_grid_grid_4_file$newt_mu_effect_sd)
+GA1_grid_grid_4_file$sim=LETTERS[factor(GA1_grid_grid_4_file$group)]
+GA1_grid_grid_4_file$grid_num = 4
+
+GA1_grid_grid_5_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_5.txt" , header = TRUE)%>%  filter(between(generation, 9000, 10000))
+GA1_grid_grid_5_file$group_rep <- paste0(GA1_grid_grid_5_file$snake_mu_rate, "_", GA1_grid_grid_5_file$snake_mu_effect_sd,"_",GA1_grid_grid_5_file$newt_mu_rate, "_", GA1_grid_grid_5_file$newt_mu_effect_sd, "_", GA1_grid_grid_5_file$rep)
+GA1_grid_grid_5_file$group <- paste0(GA1_grid_grid_5_file$snake_mu_rate, "_", GA1_grid_grid_5_file$snake_mu_effect_sd,"_",GA1_grid_grid_5_file$newt_mu_rate, "_", GA1_grid_grid_5_file$newt_mu_effect_sd)
+GA1_grid_grid_5_file$sim=LETTERS[factor(GA1_grid_grid_5_file$group)]
+GA1_grid_grid_5_file$grid_num = 5
+
+GA1_grid_grid_6_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_6.txt" , header = TRUE)%>%  filter(between(generation, 9000, 10000))
+GA1_grid_grid_6_file$group_rep <- paste0(GA1_grid_grid_6_file$snake_mu_rate, "_", GA1_grid_grid_6_file$snake_mu_effect_sd,"_",GA1_grid_grid_6_file$newt_mu_rate, "_", GA1_grid_grid_6_file$newt_mu_effect_sd, "_", GA1_grid_grid_6_file$rep)
+GA1_grid_grid_6_file$group <- paste0(GA1_grid_grid_6_file$snake_mu_rate, "_", GA1_grid_grid_6_file$snake_mu_effect_sd,"_",GA1_grid_grid_6_file$newt_mu_rate, "_", GA1_grid_grid_6_file$newt_mu_effect_sd)
+GA1_grid_grid_6_file$sim=LETTERS[factor(GA1_grid_grid_6_file$group)]
+GA1_grid_grid_6_file$grid_num = 6
+
+GA1_grid_grid_7_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_7.txt" , header = TRUE)%>%  filter(between(generation, 9000, 10000))
+GA1_grid_grid_7_file$group_rep <- paste0(GA1_grid_grid_7_file$snake_mu_rate, "_", GA1_grid_grid_7_file$snake_mu_effect_sd,"_",GA1_grid_grid_7_file$newt_mu_rate, "_", GA1_grid_grid_7_file$newt_mu_effect_sd, "_", GA1_grid_grid_7_file$rep)
+GA1_grid_grid_7_file$group <- paste0(GA1_grid_grid_7_file$snake_mu_rate, "_", GA1_grid_grid_7_file$snake_mu_effect_sd,"_",GA1_grid_grid_7_file$newt_mu_rate, "_", GA1_grid_grid_7_file$newt_mu_effect_sd)
+GA1_grid_grid_7_file$sim=LETTERS[factor(GA1_grid_grid_7_file$group)]
+GA1_grid_grid_7_file$grid_num = 7
+
+```
+
+## Grid Figs {.tabset}
+
+### 2 
+```{r, cor grid 2 high cor mean}
+
+file=GA1_grid_grid_2_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9981
+type="mean"
+col_num=2
+row_num=col_num*4
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### 3 
+```{r, cor grid 3 high cor mean}
+
+file=GA1_grid_grid_3_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="mean"
+col_num=3
+row_num=col_num*4
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### 4 
+```{r, cor grid 4 high cor mean}
+
+file=GA1_grid_grid_4_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="mean"
+col_num=4
+row_num=col_num*4
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### 5
+```{r, cor grid 5 high cor mean}
+
+file=GA1_grid_grid_5_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="mean"
+col_num=5
+row_num=col_num*4
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### 6 
+```{r, cor grid 6 high cor mean}
+
+file=GA1_grid_grid_6_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="mean"
+col_num=6
+row_num=col_num*4
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### 7
+```{r, cor grid 7 high cor mean}
+
+file=GA1_grid_grid_7_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="mean"
+col_num=7
+row_num=col_num*4
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### 2 Pop Size
+```{r, cor grid 2 popsize}
+
+file=GA1_grid_grid_2_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="num_ind"
+col_num=2
+row_num=col_num*4
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+```
+
+### 3 Pop Size
+```{r, cor grid 3 popsize}
+
+file=GA1_grid_grid_3_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="num_ind"
+col_num=3
+row_num=col_num*4
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+```
+
+### 4 Pop Size
+```{r, cor grid 4 popsize}
+
+file=GA1_grid_grid_4_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="num_ind"
+col_num=4
+row_num=col_num*4
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+```
+
+### 5 Pop Size
+```{r, cor grid 5 popsize}
+
+file=GA1_grid_grid_5_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="num_ind"
+col_num=5
+row_num=col_num*4
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+```
+
+### 6 Pop Size
+```{r, cor grid 6 popsize}
+
+file=GA1_grid_grid_6_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="num_ind"
+col_num=6
+row_num=col_num*4
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+```
+
+### 7 Pop Size
+```{r, cor grid 7 popsize}
+
+file=GA1_grid_grid_7_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9501
+type="num_ind"
+col_num=7
+row_num=col_num*4
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+```
+## {-}

### 2022-10-17 graphs_newt_snakes/big_map.Rmd
Looking at how differt grid values, cost values, and map size impast newt and snake coevolution. More wrtiing too come.

@@
 
+```{bash, data file gathering longer run}
+#!/usr/bin/env bash
+
+# Run these comands while in The the folder that contains the file you would like to condence
+# Goal is to condence all the text files into one file 
+# Requirements: need to have the same name and need to add additional columns
+thepath=/Users/victoria/Desktop/
+foldername=big_map_30
+thefolder=${thepath}${foldername}/*
+
+add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"
+
+cor_head_file=$(find ${thepath}${foldername} -name "*_GA20050_cor_*" | head -n 1)
+cor_head=$(head -n 1 "${cor_head_file}")
+
+grid_head_file=$(find ${thepath}${foldername} -name "*_GA20050_grid_*" | head -n 1)
+grid_head=$(head -n 1 "${grid_head_file}")
+
+lit_head_file=$(find ${thepath}${foldername} -name "*_GA20050_lit_*" | head -n 1)
+lit_head=$(head -n 1 "${lit_head_file}")
+
+#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
+#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."
+
+if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
+then
+  echo "All cor, lit, and grid files exist!"
+  echo "This program will now end!"
+  exit 0
+fi
+
+#creating the files
+echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
+echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
+echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt
+
+for filename in $thefolder*.text;
+  do 
+#getting the variables 
+my_type=$(echo ${filename} |sed 's/.*GA20050_//; s/_.*//')
+snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
+snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
+newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
+newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
+rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
+#echo ${newt_mu_rate}	
+# echo $my_type
+# echo $my_other_type
+# these new columns adding them to the data
+sed -i '' -e 's/$/,'${rep}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
+sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
+#infile >outfile
+if [[ $my_type == "lit" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
+fi
+
+if [[ $my_type == "grid" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
+fi
+
+if [[ $my_type == "cor" ]]
+then
+    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
+fi
+
+done
+
+```
+
 ```{r, data gathering}
@@
 big_map_tall<- read.csv("~/Desktop/big_map/all_lit.txt" , header = TRUE)
+filter_col=grepl( "X" , names( big_map_tall ))
+big_map_tall= big_map_tall[, filter_col==FALSE]
+big_map_tall_30<- read.csv("~/Desktop/big_map_30/all_lit.txt" , header = TRUE)
+big_map_tall_30$rep=1
+big_map_tall<-rbind(big_map_tall, big_map_tall_30)
 
@@
 big_map_cor<- read.csv("~/Desktop/big_map/all_cor.txt" , header = TRUE)
+filter_col=grepl( "X" , names( big_map_cor ))
+big_map_cor= big_map_cor[, filter_col==FALSE]
+big_map_cor_30<- read.csv("~/Desktop/big_map_30/all_cor.txt" , header = TRUE)
+big_map_cor_30$rep=1
+big_map_cor<-rbind(big_map_cor, big_map_cor_30)
 big_map_cor$group_rep <- paste0(big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd,"_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd, "_", big_map_cor$rep)
@@
 big_map_grid<-read.csv("~/Desktop/big_map/all_grid.txt" , header = TRUE)
+filter_col=grepl( "X" , names( big_map_grid ))
+big_map_grid= big_map_grid[, filter_col==FALSE]
+big_map_grid_30<- read.csv("~/Desktop/big_map_30/all_grid.txt" , header = TRUE)
+big_map_grid_30$rep=1
+big_map_grid<-rbind(big_map_grid, big_map_grid_30)
 big_map_grid$group <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd)
 big_map_grid$group_rep <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd, "_", big_map_grid$rep)
-
 big_map_grid$sim=LETTERS[factor(big_map_grid$group)]
@@
 min_gen=100
-max_gen=10000
-rep=0
+max_gen=30000
+rep=1
 
@@
 ginmin = 100
-ginmax = 10000
+ginmax = 30000
 
@@
 
-cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=10000, pattern=GA1_pattern[myrandomlist[1]])
+cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=30000, pattern=GA1_pattern[myrandomlist[1]])
 
@@
 min_gen=100
-max_gen=10000
+max_gen=30000
 GA_summary(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
@@
 min_gen=100
-max_gen=10000
+max_gen=30000
 
@@
 min_gen=100
-max_gen=10000
+max_gen=30000
 #
@@
 min_gen=100
-max_gen=10000
+max_gen=30000
 #heatmap
@@
 min_gen=100
-max_gen=10000
+max_gen=30000
 build_heatmap(big_map_tall, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

### 2022-10-17 graphs_newt_snakes/dif_cost.Rmd
Looking at how differt grid values, cost values, and map size impast newt and snake coevolution. More wrtiing too come.

@@
 
-How does grid size impact the spatial correlation of newt and snake phenotypes?
+How does cost size impact the spatial correlation of newt and snake phenotypes?
 
@@
 
-# Run these comands while in The the folder that contains the file you would like to condence
-# Goal is to condence all the text files into one file 
+# Run these commands while in The the folder that contains the file you would like to condence
+# Goal is to condense all the text files into one file 
 # Requirements: need to have the same name and need to add additional columns
 thepath=/Users/victoria/Desktop/
-foldername=GA1_dif_costs
+foldername=GA1_dif_cost
 thefolder=${thepath}${foldername}/*
@@
 
-cor_head_file_2=$(find ${thepath}${foldername} -name "*_cor_*" | head -n 1)
+cor_head_file=$(find ${thepath}${foldername} -name "*_cor_*" | head -n 1)
 cor_head=$(head -n 1 "${cor_head_file}")
 
-grid_head_file_2=$(find ${thepath}${foldername} -name "*_grid_*" | head -n 1)
+grid_head_file=$(find ${thepath}${foldername} -name "*_grid_*" | head -n 1)
 grid_head=$(head -n 1 "${grid_head_file}")
@@
 then
-  echo "All cor, lit, and grid files exist!"
+  echo "All cor, lit, and cost files exist!"
   echo "This program will now end!"
@@
 echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
-echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
+echo ${cost_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
 echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt
@@
 newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
-cost=$(echo ${filename} |sed 's/.*cost_//; s/_.*//')
+cost=$(echo ${filename} |sed 's/.*_cost_//; s/_.*//')
 rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
@@
 ```
+
+```{r, read in the files}
+snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
+
+GA1_lit_cost_file<- read.csv("~/Desktop/GA1_dif_cost/all_lit.txt" , header = TRUE)
+GA1_lit_cost_file$group_rep <- paste0(GA1_lit_cost_file$snake_mu_rate, "_", GA1_lit_cost_file$snake_mu_effect_sd,"_",GA1_lit_cost_file$newt_mu_rate, "_", GA1_lit_cost_file$newt_mu_effect_sd, "_", GA1_lit_cost_file$rep)
+GA1_lit_cost_file$group <- paste0(GA1_lit_cost_file$snake_mu_rate, "_", GA1_lit_cost_file$snake_mu_effect_sd,"_",GA1_lit_cost_file$newt_mu_rate, "_", GA1_lit_cost_file$newt_mu_effect_sd)
+GA1_lit_cost_file$sim=LETTERS[factor(GA1_lit_cost_file$group)]
+GA1_lit_cost_file$dif=as.numeric(GA1_lit_cost_file$Snake_mean_Pheno)-as.numeric(GA1_lit_cost_file$Newt_mean_Pheno)
+
+GA1_lit_cost_file$Snake_mean_Pheno<-as.numeric(GA1_lit_cost_file$Snake_mean_Pheno)
+GA1_lit_cost_file$generation<-as.numeric(GA1_lit_cost_file$generation)
+GA1_lit_cost_file$Newt_mean_Pheno<-as.numeric(GA1_lit_cost_file$Newt_mean_Pheno)
+
+GA1_cor_cost_file<- read.csv("~/Desktop/GA1_dif_cost/all_cor.txt" , header = TRUE)
+GA1_cor_cost_file$group_rep <- paste0(GA1_cor_cost_file$snake_mu_rate, "_", GA1_cor_cost_file$snake_mu_effect_sd,"_",GA1_cor_cost_file$newt_mu_rate, "_", GA1_cor_cost_file$newt_mu_effect_sd, "_", GA1_cor_cost_file$rep)
+GA1_cor_cost_file$group <- paste0(GA1_cor_cost_file$snake_mu_rate, "_", GA1_cor_cost_file$snake_mu_effect_sd,"_",GA1_cor_cost_file$newt_mu_rate, "_", GA1_cor_cost_file$newt_mu_effect_sd)
+GA1_cor_cost_file$sim=LETTERS[factor(GA1_cor_cost_file$group)]
+
+#GA1_lit_cost_file<-GA1_lit_cost_file[-c(115502), ] 
+# GA1_grid_cost_file<- read.csv("~/Desktop/GA1_dif_cost/all_grid.txt" , header = TRUE)
+# GA1_grid_cost_file$group_rep <- paste0(GA1_grid_cost_file$snake_mu_rate, "_", GA1_grid_cost_file$snake_mu_effect_sd,"_",GA1_grid_cost_file$newt_mu_rate, "_", GA1_grid_cost_file$newt_mu_effect_sd, "_", GA1_grid_cost_file$rep)
+# GA1_grid_cost_file$group <- paste0(GA1_grid_cost_file$snake_mu_rate, "_", GA1_grid_cost_file$snake_mu_effect_sd,"_",GA1_grid_cost_file$newt_mu_rate, "_", GA1_grid_cost_file$newt_mu_effect_sd)
+# GA1_grid_cost_file$sim=LETTERS[factor(GA1_grid_cost_file$group)]
+
+```
+
+```{r, cor box set up}
+
+boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  #unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(cost), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = factor(cost)))+
+  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+    geom_hline(yintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+boxplot_cor_grid_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(grid_num), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = factor(grid_num)))+
+  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+    geom_hline(yintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  #unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  xlim(-1.1, 1.1)+
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  #stat_bin(bins=30)+
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+suppressMessages(print(plot))
+
+  return(plot)
+}
+
+var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  real_snewt_var = var(snewt$dif)
+  var_cor_table=data.frame()
+
+  for(i in 1:length(unique(file$snake_newt_rep))){
+    pattern<-unique(file$snake_newt_rep)[i]
+    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
+    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
+
+    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
+    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+  }
+
+  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
+  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+
+  plot <- ggplot(var_cor_table) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+  return(plot)
+}
+
+cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+#file=GA1_lit_cost_file
+#cfile=GA1_cor_cost_file 
+ # pattern="1e-11_5_1e-11_5_0"
+ # pattern="1e-11_5_1e-11_5_0"  
+ file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
+
+  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
+    geom_line(aes(generation, Snake_mean_Pheno, group=cost, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=cost, color="Newt_mean_Pheno"))+
+    #ylim(0,10)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() +theme(legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
+                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
+cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col=factor(cost)))+
+    #ggtitle(title, subtitle = subt) +
+    ylim(-1.1, 1.1)+
+    #xlab(x_label_cor) + ylab(y_label)+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(),
+                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
+
+  figure <- ggarrange(plot_1, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
+
+  return(figure)
+}
+
+pop_size_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+#file=GA1_lit_cost_file
+#cfile=GA1_cor_cost_file 
+ # pattern="1e-11_5_1e-11_5_0"
+ # pattern="1e-11_5_1e-11_5_0"  
+ file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
+
+  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
+    geom_line(aes(generation, Snake_pop_size, group=cost, color="Snake"),)+
+    geom_line(aes(generation, Newt_pop_size, group=cost, color="Newt"))+
+    #ylim(0,10)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake" = "steelblue", "Newt" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() +theme(legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
+                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
+cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+    geom_line(aes(generation, num_newts_By_num_snakes, col=factor(cost)))+
+    #ggtitle(title, subtitle = subt) +
+    ylim(-1.1, 1.1)+
+    #xlab(x_label_cor) + ylab(y_label)+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(),
+                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
+
+  figure <- ggarrange(plot_1, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
+
+  return(figure)
+}
+
+```
+
+```{r, general file and graph making}
+
+#the functions to make the params file and the summary and heatmap figures
+
+create_parm_file <- function(file, min_gen, max_gen, cost){
+params <- data_frame()
+
+for(i in 1:length(unique(file$snake_newt_rep))){
+
+  pattern=unique(file$snake_newt_rep)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern & file$cost==cost),]
+
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=sumitup$snake_mu_rate[1],
+                           newt_mu_rate=sumitup$newt_mu_rate[1],
+                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
+                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
+                           rep=sumitup$rep[1])
+
+  params <- rbind(params, params_temp)
+}
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$snake_newt <- paste0(params$snake, "_", params$newt)
+return(params)
+}
+
+ create_parm_file_nc <- function(file, min_gen, max_gen){
+
+   file$test_factor <- paste0(file$cost, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params <- data_frame()
+
+for(i in 1:length(unique(file$test_factor))){
+
+  pattern=unique(file$test_factor)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$test_factor ==pattern),]
+
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=sumitup$snake_mu_rate[1],
+                           newt_mu_rate=sumitup$newt_mu_rate[1],
+                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
+                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
+                           rep=sumitup$rep[1],
+                           cost=sumitup$cost[1])
+
+  params <- rbind(params, params_temp)
+}
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$snake_newt <- paste0(params$snake, "_", params$newt)
+return(params)
+}
+
+GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label, cost){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen, cost)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+
+build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
+
+  params<-create_parm_file_nc(file, min_gen, max_gen)
+
+ my_plot <- ggplot(params, aes(newt, paste0(cost, "_", snake, "_", rep))) +    # Create heatmap with ggplot2
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
+
+ if(red_blue==FALSE){
+  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
+  }
+ if(red_blue==TRUE){
+  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
+ }
+
+  return(my_plot)
+}
+
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){
+ file$generation<-as.numeric(file$generation)
+ file$Snake_mean_Pheno<-as.numeric(file$Snake_mean_Pheno)
+ file$Newt_mean_Pheno<-as.numeric(file$Newt_mean_Pheno)
+  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
+    facet_wrap(~sim)+
+    geom_line(aes(generation, as.numeric(dif), group=cost, col="dif"))+
+    #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, group=cost, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=cost, color="Newt_mean_Pheno"))+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
+    #ylim(-1.,2.5)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+  return(plot)
+}
+
+whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+whale_gen_by_cost <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep, cost){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep & file$cost==cost),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep, " cost ", cost)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
+  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
+  xlim((-1*themax)-5, themax+5)+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+}
+
+pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  themin <- min(file$dif) 
+  themax <- max(file$dif)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(dif), fill="aquamarine4")+
+  xlim((-1*true_max)-1, true_max+1)+
+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file=GA1_lit_cost_file
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$newt_deaths)
+  thepopmax <- max(file$newt_deaths)
+  thedifmin <- min(file$snake_deaths) 
+  thedifmax <- max(file$snake_deaths)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
+  #scale_y_continuous(labels = scales::percent)+
+  #xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  #geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+grid_plot<- function(file_name, spegen, file, type, row_num, col_num, cost){
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen & file$cost==cost),]
+GA1_type = paste0("generation|", type)
+
+GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
+GA1_type <- GA1_type[-1]
+
+data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
+data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)
+
+data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)
+
+data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))
+
+main_plot<-ggplot(data_long_type_comp)+
+
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  #ylim(0, row_num)+
+  #xlim(0, col_num)+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+if(type != "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+ scale_fill_viridis_c()
+}
+if(type == "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Newt/Snake Phenotype")+
+scale_fill_viridis_c(option = "plasma")
+}
+
+snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
+newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
+newt$snake_value <- snake$measurement
+print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))
+
+newt$info <- "middle"
+newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
+return(final_plot)}
+
+```
+
+generations
+
+```{r, graphing by gen}
+
+trends_by_gen(GA1_lit_cost_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=0)
+
+```
+
+```{r, whale}
+min_gen=5000
+max_gen=10000
+rep=0
+
+whale_gen(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+```
+
+```{r, combo myplots}
+
+ginmin = 0
+ginmax = 30000
+#thecolors=c("#F8766D", "#B79F00", "#00BA38", "#00BFC4", "#619CFF", "#F564E3")
+
+boxplot_cors_by_gen(GA1_cor_cost_file, "Cost: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+## Correlation Histograms  {.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
+This section only looks at the 5 sections.
+
+### Plot 1
+```{r, GA1 cor by dif windows}
+ginmin = 0
+ginmax = 5000
+boxplot_cors_by_gen(GA1_cor_cost_file, "Cost: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 2
+
+```{r, GA1 cor by dif windows 2}
+ginmin = 5000
+ginmax = 10000
+boxplot_cors_by_gen(GA1_cor_cost_file, "Cost: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 3
+```{r, GA1 cor by dif windows 3}
+ginmin = 10000
+ginmax = 15000
+boxplot_cors_by_gen(GA1_cor_cost_file, "Cost: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 4
+```{r, GA1 cor by dif windows 4}
+ginmin = 15000
+ginmax = 20000
+boxplot_cors_by_gen(GA1_cor_cost_file, "Cost: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 5
+```{r, GA1 cor by dif windows 5}
+ginmin = 20000
+ginmax = 25000
+boxplot_cors_by_gen(GA1_cor_cost_file, "Cost: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 6
+```{r, GA1 cor by dif windows 6}
+ginmin = 25000
+ginmax = 30000
+boxplot_cors_by_gen(GA1_cor_cost_file, "Cost: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+## {-}
+
+## Phenotype Correlation across time {.tabset}
+
+Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
+
+### Random 1 (5 sec)
+```{r, GA1 cor and pheno}
+GA1_pattern <- unique(paste0(GA1_lit_cost_file$snake_mu_rate, "_", GA1_lit_cost_file$snake_mu_effect_sd,"_",GA1_lit_cost_file$newt_mu_rate, "_", GA1_lit_cost_file$newt_mu_effect_sd, "_", GA1_lit_cost_file$rep))
+
+myrandomlist=sample.int(length(GA1_pattern), 3)
+
+cor_trends_by_gen(GA1_lit_cost_file, GA1_cor_cost_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=30000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2 (5 sec)
+```{r, random cor-pheno plot 2}
+
+cor_trends_by_gen(GA1_lit_cost_file, GA1_cor_cost_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3 (5 sec)
+```{r, random cor-pheno plot 3}
+
+cor_trends_by_gen(GA1_lit_cost_file, GA1_cor_cost_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+## Population Size Correlation across time {.tabset}
+
+### Random 1 
+```{r, GA1 pop size 1}
+pop_size_trends_by_gen(GA1_lit_cost_file, GA1_cor_cost_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2 
+```{r, random pop size plot 2}
+
+pop_size_trends_by_gen(GA1_lit_cost_file, GA1_cor_cost_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3 
+```{r, random pop size plot 3}
+
+pop_size_trends_by_gen(GA1_lit_cost_file, GA1_cor_cost_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+## What happens over time (looking at the beginning and late part of my simulations) {.tabset}
+
+### Pheno Beginning 50
+
+```{r, early 50 plots}
+
+min_gen=100
+max_gen=5000
+cost=50
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+### Pheno Beginning 100
+
+```{r, early 100 plots}
+
+min_gen=100
+max_gen=5000
+cost=100
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+### Pheno Beginning 150
+
+```{r, early 150 plots}
+
+min_gen=100
+max_gen=5000
+cost=150
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+### Pheno Beginning 200
+
+```{r, early 200 plots}
+
+min_gen=100
+max_gen=5000
+cost=200
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+### Pheno Beginning 250
+
+```{r, early 250 plots}
+
+min_gen=100
+max_gen=5000
+cost=250
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+### Pheno End 50
+
+```{r, late 50 plots}
+
+min_gen=25000
+max_gen=30000
+cost=50
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+### Pheno End 100
+
+```{r, late 100 plots}
+
+min_gen=25000
+max_gen=30000
+cost=100
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+### Pheno End 150
+
+```{r, late 150 plots}
+
+min_gen=25000
+max_gen=30000
+cost=150
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+### Pheno End 200
+
+```{r, late 200 plots}
+
+min_gen=25000
+max_gen=30000
+cost=200
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+### Pheno End 250
+
+```{r, late 250 plots}
+
+min_gen=25000
+max_gen=30000
+cost=250
+
+whale_gen_by_cost(GA1_lit_cost_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_cost_file$rep)[1], cost)
+```
+
+## {-}
+
+## Summary {.tabset}
+
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
+These are whole population calculations so the 5 section and 7 section data sets are not calculated differently.
+
+### Cost: 50 Late-Sim Population Size Summary 
+```{r, 50 plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+cost=50
+
+# summary
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
+```
+
+### Cost: 100 Late-Sim Population Size Summary 
+```{r, 100 plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+cost=100
+
+# summary
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
+```
+
+### Cost: 150 Late-Sim Population Size Summary 
+```{r, 150 plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+cost=150
+
+# summary
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
+```
+
+### Cost: 200 Late-Sim Population Size Summary 
+```{r, 200 plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+cost=200
+
+# summary
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
+```
+
+### Cost: 250 Late-Sim Population Size Summary 
+```{r, 250 plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+cost=250
+
+# summary
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
+```
+
+### Cost: 50 Late Difference Summary
+```{r, 50 dif plots summary 2}
+min_gen=25000
+max_gen=30000
+cost=50
+
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
+
+```
+
+### Cost: 100 Late Difference Summary
+```{r, 100 dif plots summary 2}
+min_gen=25000
+max_gen=30000
+cost=100
+
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
+
+```
+
+### Cost: 150 Late Difference Summary
+```{r, 150 dif plots summary 2}
+min_gen=25000
+max_gen=30000
+cost=150
+
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
+
+```
+
+### Cost: 200 Late Difference Summary
+```{r, 200 dif plots summary 2}
+min_gen=25000
+max_gen=30000
+cost=200
+
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
+
+```
+
+### Cost: 250 Late Difference Summary
+```{r, 250 dif plots summary 2}
+min_gen=25000
+max_gen=30000
+cost=250
+
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
+
+```
+
+## {-}
+
+## Heatmap {.tabset}
+
+### Cost: Population Size (Early)  
+```{r, cost earlyplots Heatmap}
+min_gen=0
+max_gen=5000
+
+build_heatmap(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### Cost: Population Size (Late)  
+```{r, cost plots Heatmap}
+min_gen=25000
+max_gen=30000
+
+build_heatmap(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### Cost: Phenotype (Early) 
+```{r, cost earlyplots Heatmap pheno}
+
+min_gen=0
+max_gen=5000
+
+build_heatmap(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### Cost: Phenotype (Late) 
+```{r, cost plots Heatmap pheno}
+
+min_gen=25000
+max_gen=30000
+
+build_heatmap(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+## {-}
+
+##Grid {.tabset}
+
+```{r, red in grid files}
+require(readr)
+GA1_grid_cost_file<- read.csv("~/Desktop/GA1_dif_cost/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+GA1_grid_cost_file$group_rep <- paste0(GA1_grid_cost_file$snake_mu_rate, "_", GA1_grid_cost_file$snake_mu_effect_sd,"_",GA1_grid_cost_file$newt_mu_rate, "_", GA1_grid_cost_file$newt_mu_effect_sd, "_", GA1_grid_cost_file$rep)
+GA1_grid_cost_file$group <- paste0(GA1_grid_cost_file$snake_mu_rate, "_", GA1_grid_cost_file$snake_mu_effect_sd,"_",GA1_grid_cost_file$newt_mu_rate, "_", GA1_grid_cost_file$newt_mu_effect_sd)
+GA1_grid_cost_file$sim=LETTERS[factor(GA1_grid_cost_file$group)]
+GA1_grid_cost_file$grid_num = 5
+
+```
+
+## Grid Figs {.tabset}
+
+### 50
+```{r, cor grid 2 high cor mean}
+
+file=GA1_grid_cost_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9981
+type="mean"
+col_num=5
+row_num=col_num*4
+cost=50
+
+grid_plot(file_name, spegen, file, type, row_num, col_num, cost)
+```
+
+### 100
+```{r, cost 100 high cor mean}
+
+file=GA1_grid_cost_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9981
+type="mean"
+col_num=5
+row_num=col_num*4
+cost=100
+
+grid_plot(file_name, spegen, file, type, row_num, col_num, cost)
+```
+
+### 150
+```{r, cost 150 high cor mean}
+
+file=GA1_grid_cost_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9981
+type="mean"
+col_num=5
+row_num=col_num*4
+cost=150
+
+grid_plot(file_name, spegen, file, type, row_num, col_num, cost)
+```
+
+### 200
+```{r, cost 200 high cor mean}
+
+file=GA1_grid_cost_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9981
+type="mean"
+col_num=5
+row_num=col_num*4
+cost=200
+
+grid_plot(file_name, spegen, file, type, row_num, col_num, cost)
+```
+
+### 250
+```{r, cost 250 high cor mean}
+
+file=GA1_grid_cost_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=9981
+type="mean"
+col_num=5
+row_num=col_num*4
+cost=250
+
+grid_plot(file_name, spegen, file, type, row_num, col_num, cost)
+```
+
+## {-}

### 2022-10-17 graphs_newt_snakes/grid_test.Rmd
Looking at how differt grid values, cost values, and map size impast newt and snake coevolution. More wrtiing too come.

@@
 
-boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, mycolor){
  snewt$mean_res = snewt$mean_toxin+snewt$dif
@@
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-  unique(file$sim)
+  #unique(file$sim)
   plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
@@
   xlab(x_label) + ylab(y_label)+
-  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
+  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno)), color = mycolor)+
   geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
@@
 ```
+
 ```{r, whale}
@@
 ```
+
 ```{r, combo myplots}
@@
 ginmax = 15000
-
-boxplot_cors_by_gen(GA1_cor_grid_2_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-boxplot_cors_by_gen(GA1_cor_grid_3_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-boxplot_cors_by_gen(GA1_cor_grid_4_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-boxplot_cors_by_gen(GA1_cor_grid_5_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-boxplot_cors_by_gen(GA1_cor_grid_6_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-boxplot_cors_by_gen(GA1_cor_grid_7_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+thecolors=c("#F8766D", "#B79F00", "#00BA38", "#00BFC4", "#619CFF", "#F564E3")
+
+boxplot_cors_by_gen(GA1_cor_grid_2_file, "Grid 2: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[1])
+
+boxplot_cors_by_gen(GA1_cor_grid_3_file, "Grid 3: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[2])
+
+boxplot_cors_by_gen(GA1_cor_grid_4_file, "Grid 4: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[3])
+
+boxplot_cors_by_gen(GA1_cor_grid_5_file, "Grid 5: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[4])
+
+boxplot_cors_by_gen(GA1_cor_grid_6_file, "Grid 6: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[5])
+
+boxplot_cors_by_gen(GA1_cor_grid_7_file, "Grid 7: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[6])
 
@@
 ginmax = 5000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```
@@
 ginmax = 10000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```
@@
 ginmax = 15000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```
@@
 ginmax = 20000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```
@@
 ginmax = 25000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```
@@
 ginmax = 30000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```
@@
 ginmax = 35000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```
@@
 ginmax = 40000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```
@@
 ginmax = 45000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```
@@
 ginmax = 50000
-boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 ```

### 2022-10-20 graphs_newt_snakes/dif_cost.Rmd
Looked at more data and added maps to my slim script! Need to fix corcompare to look nicer and spend a lot of time writing about all of these new results.

@@
 
-trends_by_gen(GA1_lit_cost_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=0)
+trends_by_gen(GA1_lit_cost_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 30000, rep=0)
 

### 2022-10-20 graphs_newt_snakes/interaction_rate_inv.Rmd
Looked at more data and added maps to my slim script! Need to fix corcompare to look nicer and spend a lot of time writing about all of these new results.

--- 2022-10-07 graphs_newt_snakes/dif_cost.Rmd
@@
 ---
-title: "Different Cost"
+title: "Different Interaction Rates"
 output: html_document
-date: '2022-10-06'
+date: '2022-10-17'
 ---
@@
 Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to.
-This markdown is investigation what is up with the different levels of correlation between rectangles and squares (in connection with GA1 tall).
-After fixing the row vs column error I looked at the correlation data and found that there was less correlation.
-So I decided to investigate why that might be and run a few more experiments.
-I am running an experiment to test how changing the square size might impact the calculations.
-I also plan on changing the interaction rate (but want to look at the math/ feasibility of it).
-This file contains results discussed in Tall_GA1!
+This markdown is investigating
 
 ### Questions:
-
-How does grid size impact the spatial correlation of newt and snake phenotypes?
 
@@
 
-I tested different cost values:
+I tested different interaction rates:
 
-  - 50
-  - 100
-  - 150
-  - 200
-  - 250
+  - 0.01
+  - 0.025
+  - 0.05
+  - 0.075
+  - 0.10
+  - 0.125
+  - 0.15
+  - 0.20
+  - 0.25
+  - 0.30
+  - 0.35
 
-Each GA combination, trial, and cost has its own msprime simulation.
+Each GA combination, trial, and interaction rate has its own msprime simulation.
+
+Sometimes a higher interaction rate will lead to a species extinction, so ending values are approximate
 
@@
 
-# Run these comands while in The the folder that contains the file you would like to condence
-# Goal is to condence all the text files into one file 
+# Run these commands while in The the folder that contains the file you would like to condence
+# Goal is to condense all the text files into one file 
 # Requirements: need to have the same name and need to add additional columns
 thepath=/Users/victoria/Desktop/
-foldername=GA1_dif_costs
+foldername=interaction_rate
 thefolder=${thepath}${foldername}/*
 
-add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd,cost"
+add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd,interrate"
 
@@
 echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
-echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
+echo ${interrate_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
 echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt
@@
 newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
-cost=$(echo ${filename} |sed 's/.*cost_//; s/_.*//')
+interrate=$(echo ${filename} |sed 's/.*_interaction_rate_//; s/_.*//')
 rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
@@
 sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
-sed -i '' -e 's/$/,'${cost}'/' $filename
+sed -i '' -e 's/$/,'${interrate}'/' $filename
 #infile >outfile
@@
 ```
+
+```{r, read in the files}
+snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
+
+GA1_lit_interrate_file<- read.csv("~/Desktop/interaction_rate/all_lit.txt" , header = TRUE)
+GA1_lit_interrate_file$group_rep <- paste0(GA1_lit_interrate_file$snake_mu_rate, "_", GA1_lit_interrate_file$snake_mu_effect_sd,"_",GA1_lit_interrate_file$newt_mu_rate, "_", GA1_lit_interrate_file$newt_mu_effect_sd, "_", GA1_lit_interrate_file$rep)
+GA1_lit_interrate_file$group <- paste0(GA1_lit_interrate_file$snake_mu_rate, "_", GA1_lit_interrate_file$snake_mu_effect_sd,"_",GA1_lit_interrate_file$newt_mu_rate, "_", GA1_lit_interrate_file$newt_mu_effect_sd)
+GA1_lit_interrate_file$sim=LETTERS[factor(GA1_lit_interrate_file$group)]
+GA1_lit_interrate_file$dif=as.numeric(GA1_lit_interrate_file$Snake_mean_Pheno)-as.numeric(GA1_lit_interrate_file$Newt_mean_Pheno)
+
+GA1_lit_interrate_file$Snake_mean_Pheno<-as.numeric(GA1_lit_interrate_file$Snake_mean_Pheno)
+GA1_lit_interrate_file$generation<-as.numeric(GA1_lit_interrate_file$generation)
+GA1_lit_interrate_file$Newt_mean_Pheno<-as.numeric(GA1_lit_interrate_file$Newt_mean_Pheno)
+
+GA1_cor_interrate_file<- read.csv("~/Desktop/interaction_rate/all_cor.txt" , header = TRUE)
+GA1_cor_interrate_file$group_rep <- paste0(GA1_cor_interrate_file$snake_mu_rate, "_", GA1_cor_interrate_file$snake_mu_effect_sd,"_",GA1_cor_interrate_file$newt_mu_rate, "_", GA1_cor_interrate_file$newt_mu_effect_sd, "_", GA1_cor_interrate_file$rep)
+GA1_cor_interrate_file$group <- paste0(GA1_cor_interrate_file$snake_mu_rate, "_", GA1_cor_interrate_file$snake_mu_effect_sd,"_",GA1_cor_interrate_file$newt_mu_rate, "_", GA1_cor_interrate_file$newt_mu_effect_sd)
+GA1_cor_interrate_file$sim=LETTERS[factor(GA1_cor_interrate_file$group)]
+
+unique(GA1_lit_interrate_file$rep)
+
+GA1_lit_interrate_file <- GA1_lit_interrate_file[which(GA1_lit_interrate_file$rep==0),]
+GA1_cor_interrate_file <- GA1_cor_interrate_file[which(GA1_cor_interrate_file$rep==0),]
+
+```
+
+```{r, cor box set up}
+
+boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  #unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(interrate), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = factor(interrate)))+
+  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+    geom_hline(yintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+boxplot_cor_grid_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ylim(-1.1, 1.1)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(grid_num), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = factor(grid_num)))+
+  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+    geom_hline(yintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  #unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  xlim(-1.1, 1.1)+
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+  return(plot)
+}
+
+hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  unique(file$sim)
+  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
+  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
+  geom_vline(xintercept=0, linetype="solid")+
+  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
+  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
+  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
+  theme(plot.title = element_text(size=5)) +
+  #stat_bin(bins=30)+
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+suppressMessages(print(plot))
+
+  return(plot)
+}
+
+var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  real_snewt_var = var(snewt$dif)
+  var_cor_table=data.frame()
+
+  for(i in 1:length(unique(file$snake_newt_rep))){
+    pattern<-unique(file$snake_newt_rep)[i]
+    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
+    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
+
+    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
+    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+  }
+
+  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
+  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
+
+  plot <- ggplot(var_cor_table) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
+  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
+  theme(plot.title = element_text(size=5)) +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
+
+  return(plot)
+}
+
+cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+#file=GA1_lit_interrate_file
+#cfile=GA1_cor_interrate_file 
+ # pattern="1e-11_5_1e-11_5_0"
+ # pattern="1e-11_5_1e-11_5_0"  
+ file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
+
+  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
+    geom_line(aes(generation, Snake_mean_Pheno, group=interrate, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=interrate, color="Newt_mean_Pheno"))+
+    #ylim(0,10)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() +theme(legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
+                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
+cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col=factor(interrate)))+
+    #ggtitle(title, subtitle = subt) +
+    ylim(-1.1, 1.1)+
+    #xlab(x_label_cor) + ylab(y_label)+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(),
+                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
+
+  figure <- ggarrange(plot_1, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
+
+  return(figure)
+}
+
+pop_size_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+#file=GA1_lit_interrate_file
+#cfile=GA1_cor_interrate_file 
+ # pattern="1e-11_5_1e-11_5_0"
+ # pattern="1e-11_5_1e-11_5_0"  
+ file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
+
+  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
+    geom_line(aes(generation, Snake_pop_size, group=interrate, color="Snake"),)+
+    geom_line(aes(generation, Newt_pop_size, group=interrate, color="Newt"))+
+    #ylim(0,10)+
+    #xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake" = "steelblue", "Newt" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() +theme(legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
+                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
+cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+    geom_line(aes(generation, num_newts_By_num_snakes, col=factor(interrate)))+
+    #ggtitle(title, subtitle = subt) +
+    ylim(-1.1, 1.1)+
+    #xlab(x_label_cor) + ylab(y_label)+
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank(),
+                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
+
+  figure <- ggarrange(plot_1, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
+
+  return(figure)
+}
+
+```
+
+```{r, general file and graph making}
+
+#the functions to make the params file and the summary and heatmap figures
+
+create_parm_file <- function(file, min_gen, max_gen, interrate){
+params <- data_frame()
+
+for(i in 1:length(unique(file$snake_newt_rep))){
+
+  pattern=unique(file$snake_newt_rep)[i]
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern & file$interrate==interrate),]
+
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=sumitup$snake_mu_rate[1],
+                           newt_mu_rate=sumitup$newt_mu_rate[1],
+                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
+                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
+                           rep=sumitup$rep[1])
+
+  params <- rbind(params, params_temp)
+}
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$snake_newt <- paste0(params$snake, "_", params$newt)
+return(params)
+}
+
+ create_parm_file_nc <- function(file, min_gen, max_gen){
+
+   file$test_factor <- paste0(file$interrate, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params <- data_frame()
+
+for(i in 1:length(unique(file$test_factor))){
+
+  pattern=unique(file$test_factor)[i]
+
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$test_factor ==pattern),]
+
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=unlist(strsplit(pattern, "_"))[2],
+                           newt_mu_rate=unlist(strsplit(pattern, "_"))[4],
+                           snake_mu_effect_sd=unlist(strsplit(pattern, "_"))[3],
+                           newt_mu_effect_sd=unlist(strsplit(pattern, "_"))[5],
+                           rep=unlist(strsplit(pattern, "_"))[6],
+                           interrate=unlist(strsplit(pattern, "_"))[1],
+                           test_factor=pattern)
+
+  params <- rbind(params, params_temp)
+}
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$snake_newt <- paste0(params$snake, "_", params$newt)
+return(params)
+}
+
+GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label, interrate){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params<-create_parm_file(file, min_gen, max_gen, interrate)
+
+my_plot <- ggplot(params) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  #facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
+
+return(my_plot)
+}
+
+build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
+
+  params<-create_parm_file_nc(file, min_gen, max_gen)
+
+ my_plot <- ggplot(params, aes(newt,  paste0(interrate, "_", snake, "_", rep))) +    # Create heatmap with ggplot2
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
+
+ if(red_blue==FALSE){
+  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
+  }
+ if(red_blue==TRUE){
+  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
+ }
+
+  return(my_plot)
+}
+
+trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){
+ file$generation<-as.numeric(file$generation)
+ file$Snake_mean_Pheno<-as.numeric(file$Snake_mean_Pheno)
+ file$Newt_mean_Pheno<-as.numeric(file$Newt_mean_Pheno)
+  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
+    facet_wrap(~sim)+
+    geom_line(aes(generation, as.numeric(dif), group=interrate, col="dif"))+
+    #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, group=interrate, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=interrate, color="Newt_mean_Pheno"))+
+    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
+    #ylim(-1.,2.5)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+  return(plot)
+}
+
+whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+whale_gen_by_interrate <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep, interrate){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep & file$interrate==interrate),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep, " interrate ", interrate)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
+  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
+  xlim((-1*themax)-5, themax+5)+
+  theme(plot.title = element_text(size=5)) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+}
+
+pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  themin <- min(file$dif) 
+  themax <- max(file$dif)
+  true_max <- max(abs(themin), abs(themax))
+dif <- ggplot(file) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(dif), fill="aquamarine4")+
+  xlim((-1*true_max)-1, true_max+1)+
+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
+  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
+  thedifmin <- min(file$dif) 
+  thedifmax <- max(file$dif)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
+  scale_y_continuous(labels = scales::percent)+
+  xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
+  #file=GA1_lit_interrate_file
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
+
+  thepopmin <- min(file$newt_deaths)
+  thepopmax <- max(file$newt_deaths)
+  thedifmin <- min(file$snake_deaths) 
+  thedifmax <- max(file$snake_deaths)
+  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))
+
+  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
+
+dif <- ggplot(file) +
+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
+  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
+  #scale_y_continuous(labels = scales::percent)+
+  #xlim((-1*true_max)-1, true_max+1)+
+  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
+  #labs(colour = color_label) +
+  facet_wrap(~sim)+
+  #geom_vline(xintercept = 0)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      #strip.background = element_blank(), 
+                      strip.text.x = element_blank(), 
+                      #panel.grid.major = element_blank(), 
+                      #panel.grid.minor = element_blank(),
+                      #panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+grid_plot<- function(file_name, spegen, file, type, row_num, col_num, interrate){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen & file$interrate==interrate),]
+GA1_type = paste0("generation|", type)
+
+GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
+GA1_type <- GA1_type[-1]
+
+data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
+data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)
+
+data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)
+
+data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))
+
+main_plot<-ggplot(data_long_type_comp)+
+
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  #ylim(0, row_num)+
+  #xlim(0, col_num)+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+if(type != "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+ scale_fill_viridis_c()
+}
+if(type == "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Newt/Snake Phenotype")+
+scale_fill_viridis_c(option = "plasma")
+}
+
+snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
+newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
+newt$snake_value <- snake$measurement
+print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))
+
+newt$info <- "middle"
+newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
+return(final_plot)}
+
+```
+
+generations
+
+```{r, graphing by gen}
+
+trends_by_gen(GA1_lit_interrate_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=0)
+
+```
+
+```{r, whale}
+min_gen=5000
+max_gen=10000
+rep=0
+
+whale_gen(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+```
+
+```{r, combo myplots}
+
+ginmin = 0
+ginmax = 50000
+#thecolors=c("#F8766D", "#B79F00", "#00BA38", "#00BFC4", "#619CFF", "#F564E3")
+
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+## Correlation Histograms  {.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
+This section only looks at the 5 sections.
+
+### Plot 1
+```{r, GA1 cor by dif windows1}
+ginmin = 0
+ginmax = 5000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 2
+
+```{r, GA1 cor by dif windows 2}
+ginmin = 5000
+ginmax = 10000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 3
+```{r, GA1 cor by dif windows 3}
+ginmin = 10000
+ginmax = 15000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 4
+```{r, GA1 cor by dif windows 4}
+ginmin = 15000
+ginmax = 20000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 5
+```{r, GA1 cor by dif windows 5}
+ginmin = 20000
+ginmax = 25000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 6
+```{r, GA1 cor by dif windows 6}
+ginmin = 25000
+ginmax = 30000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 7
+```{r, GA1 cor by dif windows 7}
+ginmin = 30000
+ginmax = 35000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 8
+```{r, GA1 cor by dif windows 8}
+ginmin = 35000
+ginmax = 40000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 9
+```{r, GA1 cor by dif windows 9}
+ginmin = 40000
+ginmax = 45000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+### Plot 10
+```{r, GA1 cor by dif windows 10}
+ginmin = 45000
+ginmax = 50000
+boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+```
+
+## {-}
+
+## Phenotype Correlation across time {.tabset}
+
+Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
+
+### Random 1 (5 sec)
+```{r, GA1 cor and pheno}
+GA1_pattern <- unique(paste0(GA1_lit_interrate_file$snake_mu_rate, "_", GA1_lit_interrate_file$snake_mu_effect_sd,"_",GA1_lit_interrate_file$newt_mu_rate, "_", GA1_lit_interrate_file$newt_mu_effect_sd, "_", GA1_lit_interrate_file$rep))
+
+myrandomlist=sample.int(length(GA1_pattern), 3)
+
+cor_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2 (5 sec)
+```{r, random cor-pheno plot 2}
+
+cor_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3 (5 sec)
+```{r, random cor-pheno plot 3}
+
+cor_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+## Population Size Correlation across time {.tabset}
+
+### Random 1 
+```{r, GA1 pop size 1}
+pop_size_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2 
+```{r, random pop size plot 2}
+
+pop_size_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3 
+```{r, random pop size plot 3}
+
+pop_size_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
+## {-}
+
+## What happens over time (looking at the beginning and late part of my simulations) {.tabset}
+
+### Pheno Beginning 0.01
+
+```{r, early 0.01 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.01
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.025
+
+```{r, early 0.025 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.025
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.05
+
+```{r, early 0.05 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.05
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.075
+
+```{r, early 0.075 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.075
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.10
+
+```{r, early 0.10 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.10
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.125
+
+```{r, early 0.125 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.125
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.15
+
+```{r, early 0.15 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.15
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.20
+
+```{r, early 0.20 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.20
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.25
+
+```{r, early 0.25 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.25
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.30
+
+```{r, early 0.30 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.30
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno Beginning 0.35
+
+```{r, early 0.35 plots}
+
+min_gen=100
+max_gen=5000
+interrate=0.35
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.01
+
+```{r, late 0.01 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.01
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.025
+
+```{r, late 0.025 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.025
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.05
+
+```{r, late 0.05 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.05
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.075
+
+```{r, late 0.075 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.075
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.10
+
+```{r, late 0.10 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.10
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.125
+
+```{r, late 0.125 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.125
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.15
+
+```{r, late 0.15 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.15
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.20
+
+```{r, late 0.20 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.20
+
+#whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.25
+
+```{r, late 0.25 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.25
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.30
+
+```{r, late 0.30 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.30
+
+#whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+### Pheno End 0.35
+
+```{r, late 0.35 plots}
+
+min_gen=45000
+max_gen=50000
+interrate=0.35
+
+whale_gen_by_interrate(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(GA1_lit_interrate_file$rep)[1], interrate)
+```
+
+## {-}
+
+## Heatmap {.tabset}
+
+### interrate: Population Size (Early)  
+```{r, interrate earlyplots Heatmap1, fig.height=4}
+min_gen=100
+max_gen=5000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Population Size (EM1)  
+```{r, interrate earlyplots Heatmap2, fig.height=4}
+min_gen=5000
+max_gen=10000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Population Size (EM2)  
+```{r, interrate earlyplots Heatmap3, fig.height=4}
+min_gen=10000
+max_gen=15000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Population Size (EM3)  
+```{r, interrate earlyplots Heatmap4, fig.height=4}
+min_gen=15000
+max_gen=20000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Population Size (EM4)  
+```{r, interrate earlyplots Heatmap5, fig.height=4}
+min_gen=20000
+max_gen=25000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Population Size (Mid)  
+```{r, interrate midplots Heatmap6, fig.height=4}
+min_gen=25000
+max_gen=30000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Population Size (ML1)  
+```{r, interrate midplots Heatmap7, fig.height=4}
+min_gen=30000
+max_gen=35000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Population Size (ML2)  
+```{r, interrate midplots Heatmap8, fig.height=4}
+min_gen=35000
+max_gen=40000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Population Size (ML3)  
+```{r, interrate midplots Heatmap9, fig.height=4}
+min_gen=40000
+max_gen=45000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Population Size (Late)  
+```{r, interrate plots Heatmap10, fig.height=4}
+min_gen=45000
+max_gen=50000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### interrate: Phenotype (Early) 
+```{r, interrate earlyplots Heatmap1 pheno, fig.height=4}
+
+min_gen=100
+max_gen=5000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### interrate: Phenotype (EM1) 
+```{r, interrate earlyplots Heatmap2 pheno, fig.height=4}
+
+min_gen=5000
+max_gen=10000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### interrate: Phenotype (EM2) 
+```{r, interrate earlyplots Heatmap3 pheno, fig.height=4}
+
+min_gen=10000
+max_gen=15000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### interrate: Phenotype (EM3) 
+```{r, interrate earlyplots Heatmap4 pheno, fig.height=4}
+
+min_gen=15000
+max_gen=20000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### interrate: Phenotype (EM4) 
+```{r, interrate earlyplots Heatmap5 pheno, fig.height=4}
+
+min_gen=20000
+max_gen=25000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### interrate: Phenotype (Mid) 
+```{r, interrate earlyplots Heatmap6 pheno, fig.height=4}
+
+min_gen=25000
+max_gen=30000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### interrate: Phenotype (ML1) 
+```{r, interrate earlyplots Heatmap7 pheno, fig.height=4}
+
+min_gen=30000
+max_gen=35000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### interrate: Phenotype (ML2) 
+```{r, interrate earlyplots Heatmap8 pheno, fig.height=4}
+
+min_gen=35000
+max_gen=40000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### interrate: Phenotype (ML3) 
+```{r, interrate earlyplots Heatmap9 pheno, fig.height=4}
+
+min_gen=40000
+max_gen=45000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### interrate: Phenotype (Late) 
+```{r, interrate plots Heatmap10 pheno, fig.height=4}
+
+min_gen=45000
+max_gen=50000
+
+build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+## {-}
+
+##Grid {.tabset}
+
+```{r, red in grid files}
+require(readr)
+GA1_grid_interrate_file<- read.csv("~/Desktop/interaction_rate/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 10000, 15000))
+GA1_grid_interrate_file$group_rep <- paste0(GA1_grid_interrate_file$snake_mu_rate, "_", GA1_grid_interrate_file$snake_mu_effect_sd,"_",GA1_grid_interrate_file$newt_mu_rate, "_", GA1_grid_interrate_file$newt_mu_effect_sd, "_", GA1_grid_interrate_file$rep)
+GA1_grid_interrate_file$group <- paste0(GA1_grid_interrate_file$snake_mu_rate, "_", GA1_grid_interrate_file$snake_mu_effect_sd,"_",GA1_grid_interrate_file$newt_mu_rate, "_", GA1_grid_interrate_file$newt_mu_effect_sd)
+GA1_grid_interrate_file$sim=LETTERS[factor(GA1_grid_interrate_file$group)]
+GA1_grid_interrate_file$grid_num = 5
+
+GA1_grid_interrate_file$snake_newt_rep <- paste0(GA1_grid_interrate_file$snake_mu_rate, "_", GA1_grid_interrate_file$snake_mu_effect_sd,"_",GA1_grid_interrate_file$newt_mu_rate, "_", GA1_grid_interrate_file$newt_mu_effect_sd, "_", GA1_grid_interrate_file$rep)
+
+```
+
+## Grid Figs {.tabset}
+
+### 0.01
+```{r, cor 0.01 high cor mean}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.01
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),])
+if(value!=0){
+grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) 
+}
+```
+
+### 0.025
+```{r, cor 0.025 high cor mean}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.025
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),])
+if(value!=0){
+ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) 
+}
+```
+
+### 0.05
+```{r, cor 0.05 high cor mean}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.05
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.075
+```{r, cor 0.075 high cor mean}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.075
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.10
+```{r, cor 0.10 high cor mean1}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.10
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),])
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.125
+```{r, cor 0.125 high cor mean 1}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.125
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ 
+  grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) 
+  }
+```
+
+### 0.15
+```{r, cor 0.15 high cor mean 1}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.15
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.20
+```{r, cor 0.20 high cor mean 1}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.20
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.25
+```{r, cor 0.25 high cor mean 1}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.25
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.30
+```{r, cor 0.30 high cor mean 1}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.30
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.35
+```{r, cor 0.35 high cor mean 1}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[1]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.35
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+## {-}
+
+## Grid Figs 2 {.tabset}
+
+### 0.01
+```{r, cor 0.01 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.01
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.025
+```{r, cor 0.025 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.025
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.05
+```{r, cor 0.05 high cor mea2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.05
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.075
+```{r, cor 0.075 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.075
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.10
+```{r, cor 0.10 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.10
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.125
+```{r, cor 0.125 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.125
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.15
+```{r, cor 0.15 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.15
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.20
+```{r, cor 0.20 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.20
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),])
+
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.25
+```{r, cor 0.25 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.25
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.30
+```{r, cor 0.30 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.30
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.35
+```{r, cor 0.35 high cor mean2}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[2]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.35
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+## {-}
+
+## Grid Figs {.tabset}
+
+### 0.01
+```{r, cor 0.01 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.01
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.025
+```{r, cor 0.025 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.025
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.05
+```{r, cor 0.05 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.05
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.075
+```{r, cor 0.075 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.075
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.10
+```{r, cor 0.10 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.10
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.125
+```{r, cor 0.125 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.125
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.15
+```{r, cor 0.15 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.15
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.20
+```{r, cor 0.20 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.20
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.25
+```{r, cor 0.25 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.25
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.30
+```{r, cor 0.30 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.30
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),])
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+### 0.35
+```{r, cor 0.35 high cor mean3}
+
+file=GA1_grid_interrate_file
+file_name=GA1_pattern[myrandomlist[3]]
+spegen=14981
+type="mean"
+col_num=5
+row_num=col_num*4
+interrate=0.35
+
+value<-nrow(GA1_grid_interrate_file[which(GA1_grid_interrate_file$snake_newt_rep==file_name & GA1_grid_interrate_file$generation==spegen & GA1_grid_interrate_file$interrate==interrate),]) 
+if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+```
+
+## {-}

### 2022-10-21 graphs_newt_snakes/dif_cost_grade.Rmd
I am preping for the cost gradiant results

--- 2022-08-31 graphs_newt_snakes/GA1_tall_redo_md.Rmd
@@
 ---
-title: "GA1 redo"
+title: "Cost Gradient"
 output: html_document
-date: '2022-08-01'
+date: '2022-10-21'
 ---
@@
 
-Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to.
-This markdown is investigation what is up with the different levels of correlation between rectangles and squares.
-After fixing the row vs column error I looked at the correlation data and found that there was less correlation.
-So I decided to investigate why that might be and run a few more experiments.
-I am running an experiment to test how changing the square size might impact the calculations.
-I also plan on changing the interaction rate (but want to look at the math/ feasibility of it).
-This file contains results discussed in Tall_GA1!
-
 ### Questions:
@@
 ## Background
-
-I investigated the correlations between snake and newt phenotypes at the local grid locations along with population level phenotype.
-I found there was a lot of correlation when populations slowly adapt!
-However, after a closer investigation I found that these correlations were from a rectangle shaped area and not a square one.
-Here, I rerun the experiment with he correct square grids and discuss how the results differ.
-I also aim to investigate how changing the area/shape of the grids will influence correlation results.
-I am also thinking of ways to gather and incorperate allele information.
 
@@
 
-Landscape: 20 by 5 grid. A tall map!: 35*4 H, 35 W 
-New Landscape 28 by 7 grid: 35*4 H, 35 W
+Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.
 
 ### The data
-
-I gather text file data from different files and have to do some table wrangling to get it into a format I can graph.
-I use information gathered from the entire population; data containing a mean value for the entire map (lit), correlation data based off of local populations that were divided into grids (cor) and data collected from grid based populations (grid).
-These simulations have a msprime (coalescent/burn in/random genetic variation) and then run for 50,000 generations in SLiM (co-evolution) (all with the same GA values).
-I run 4 trials for every GA combination and try two different grid sizes 20 by 5 (large) and 24 by 7 (small) in SLiM.
-These slim simulations use the same msprime simulation, but can statistically be different.
 
@@
 thepath=/Users/victoria/Desktop/
-foldername=GA1_tall_redo
+foldername=cost_grade
 thefolder=${thepath}${foldername}/*
@@
 
-cor_head_file=$(find ${thepath}${foldername} -name "*_GA520_cor_*" | head -n 1)
+cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
 cor_head=$(head -n 1 "${cor_head_file}")
@@
 lit_head=$(head -n 1 "${lit_head_file}")
-
-cor_head_file_7=$(find ${thepath}${foldername} -name "*_GA728_cor_*" | head -n 1)
-cor_head_7=$(head -n 1 "${cor_head_file_7}")
-
-grid_head_file_7=$(find ${thepath}${foldername} -name "*_GA287_grid_*" | head -n 1)
-grid_head_7=$(head -n 1 "${grid_head_file_7}")
-
-lit_head_file_7=$(find ${thepath}${foldername} -name "*_GA287_lit_*" | head -n 1)
-lit_head_7=$(head -n 1 "${lit_head_file_7}")
 
@@
 my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
-my_other_type=$(echo ${filename} |sed 's/.*GA520_//; s/_.*//')
-my_type_2=$(echo ${filename} |sed 's/.*GA287_//; s/_.*//') #testing a second grid system
-my_other_type_2=$(echo ${filename} |sed 's/.*GA728_//; s/_.*//')
 snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
@@
 
-GA1_tall_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_lit.txt" , header = TRUE)
-
-GA1_tall_tall_file$group_rep <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep)
-
-GA1_tall_tall_file$group <- paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd)
-
-GA1_tall_tall_file$sim=LETTERS[factor(GA1_tall_tall_file$group)]
-GA1_tall_tall_file$dif <- GA1_tall_tall_file$Snake_mean_Pheno-GA1_tall_tall_file$Newt_mean_Pheno
-
-GA1_cor_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor.txt" , header = TRUE)
-GA1_cor_tall_file$group_rep <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd, "_", GA1_cor_tall_file$rep)
-GA1_cor_tall_file$group <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd)
-GA1_cor_tall_file$sim=LETTERS[factor(GA1_cor_tall_file$group)]
-
-GA1_grid_tall_file<-read.csv("~/Desktop/GA1_tall_redo/all_grid.txt" , header = TRUE)
-GA1_grid_tall_file$group <- paste0(GA1_grid_tall_file$snake_mu_rate, "_", GA1_grid_tall_file$snake_mu_effect_sd,"_",GA1_grid_tall_file$newt_mu_rate, "_", GA1_grid_tall_file$newt_mu_effect_sd)
-GA1_grid_tall_file$group_rep <- paste0(GA1_grid_tall_file$snake_mu_rate, "_", GA1_grid_tall_file$snake_mu_effect_sd,"_",GA1_grid_tall_file$newt_mu_rate, "_", GA1_grid_tall_file$newt_mu_effect_sd, "_", GA1_grid_tall_file$rep)
-
-GA1_grid_tall_file$sim=LETTERS[factor(GA1_grid_tall_file$group)]
-GA1_grid_tall_file$snake_newt_rep <- paste0("Snake_",GA1_grid_tall_file$snake_mu_rate, "_", GA1_grid_tall_file$snake_mu_effect_sd, "_Newt_",GA1_grid_tall_file$newt_mu_rate, "_", GA1_grid_tall_file$newt_mu_effect_sd, "_", GA1_grid_tall_file$rep)
-
-GA1_tall_tall_7_file<- read.csv("~/Desktop/GA1_tall_redo/all_lit_7.txt" , header = TRUE)
-
-GA1_tall_tall_7_file$group_rep <- paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd, "_", GA1_tall_tall_7_file$rep)
-
-GA1_tall_tall_7_file$group <- paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd)
-
-GA1_tall_tall_7_file$sim=LETTERS[factor(GA1_tall_tall_7_file$group)]
-GA1_tall_tall_7_file$dif <- GA1_tall_tall_7_file$Snake_mean_Pheno-GA1_tall_tall_7_file$Newt_mean_Pheno
-
-GA1_cor_tall_7_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor_7.txt" , header = TRUE)
-GA1_cor_tall_7_file$group_rep <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd, "_", GA1_cor_tall_7_file$rep)
-GA1_cor_tall_7_file$group <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd)
-GA1_cor_tall_7_file$sim=LETTERS[factor(GA1_cor_tall_7_file$group)]
-
-GA1_grid_tall_7_file<-read.csv("~/Desktop/GA1_tall_redo/all_grid_7.txt" , header = TRUE)
-GA1_grid_tall_7_file$group <- paste0(GA1_grid_tall_7_file$snake_mu_rate, "_", GA1_grid_tall_7_file$snake_mu_effect_sd,"_",GA1_grid_tall_7_file$newt_mu_rate, "_", GA1_grid_tall_7_file$newt_mu_effect_sd)
-GA1_grid_tall_7_file$group_rep <- paste0(GA1_grid_tall_7_file$snake_mu_rate, "_", GA1_grid_tall_7_file$snake_mu_effect_sd,"_",GA1_grid_tall_7_file$newt_mu_rate, "_", GA1_grid_tall_7_file$newt_mu_effect_sd, "_", GA1_grid_tall_7_file$rep)
-
-GA1_grid_tall_7_file$sim=LETTERS[factor(GA1_grid_tall_7_file$group)]
-GA1_grid_tall_7_file$snake_newt_rep <- paste0("Snake_",GA1_grid_tall_7_file$snake_mu_rate, "_", GA1_grid_tall_7_file$snake_mu_effect_sd, "_Newt_",GA1_grid_tall_7_file$newt_mu_rate, "_", GA1_grid_tall_7_file$newt_mu_effect_sd, "_", GA1_grid_tall_7_file$rep)
+cost_grade_lit<- read.csv("~/Desktop/cost_grade/all_lit.txt" , header = TRUE)
+
+cost_grade_lit$group_rep <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep)
+
+cost_grade_lit$group <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd)
+
+cost_grade_lit$sim=LETTERS[factor(cost_grade_lit$group)]
+cost_grade_lit$dif <- cost_grade_lit$Snake_mean_Pheno-cost_grade_lit$Newt_mean_Pheno
+
+cost_grade_cor<- read.csv("~/Desktop/cost_grade/all_cor.txt" , header = TRUE)
+cost_grade_cor$group_rep <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd, "_", cost_grade_cor$rep)
+cost_grade_cor$group <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd)
+cost_grade_cor$sim=LETTERS[factor(cost_grade_cor$group)]
 
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=GA1_tall_tall_file
-#cfile=GA1_cor_tall_file 
+#file=cost_grade_lit
+#cfile=cost_grade_cor 
  # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=GA1_tall_tall_file
+  #file=cost_grade_lit
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
-
-```
-
-## Mean Phenotype Whole Simulation
-
-First, I will look at a plot of how the mean phenotype of the entire population of newts and snakes changes overtime.
-Each of these plots has three colored lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype.
-There are 4 line per color that represent the different replicas that I ran.
-**Note this is a mean for the entire population.** Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).
-
+#two_hist_death_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+
+```
+
+## Mean Phenotype Whole Simulation {.tabset}
+
+### Phenotype differences 
 ```{r, graphing by gen}
-trends_by_gen(GA1_tall_tall_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
-
-aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group), FUN=mean)
-
-aggregate(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$dif, list(GA1_tall_tall_file[which(GA1_tall_tall_file$generation>=100 & GA1_tall_tall_file$generation<=50000),]$group_rep), FUN=mean)
-
-trends_by_gen(GA1_tall_tall_7_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)
-
-aggregate(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$dif, list(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$group), FUN=mean)
-
-aggregate(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$dif, list(GA1_tall_tall_7_file[which(GA1_tall_tall_7_file$generation>=100 & GA1_tall_tall_7_file$generation<=50000),]$group_rep), FUN=mean)
-
-```
-
-#### Connection between higher phenotype and population
-
+trends_by_gen(cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+#aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group_rep), FUN=mean)
+
+```
+
+### Table of average Differences
+
+```{r, average difference}
+aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group), FUN=mean)
+```
+
+## {-}
+
+## Connection between higher phenotype and population{.tabset}
+
+### Phenotype differences 
 ```{r, whale}
@@
 max_gen=10000
-rep=0
-
-whale_gen(GA1_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-
-suppressMessages(print(two_hist_all_rep(GA1_tall_tall_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
-
-whale_gen(GA1_tall_tall_7_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-
-suppressMessages(print(two_hist_all_rep(GA1_tall_tall_7_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
-
-```
-
-I looked at the results between 5,000 - 10,000 generations where I saw most of the increase in newt and snake phenotype.
-The first plot has newt population size by snake population size with the color representing the difference between snake and newt mean phenotype (red=newts have a higher mean phenotype, blue=snakes have a higher mean phenotype).
-The third GA (an intermediate one) seems to do better then all of the other GAs (blue row (3), red column (3)).
-However, this is dependent on the point in the simulation you focus on.
-The next two plots show the difference between snake and newt population size (green) and phenotype (purple).
-For the most part these suggest that when the mean phenotype is higher so is the population size.
-This also shows the asymmetrical nature between the predator-prey interaction (higher max population sizes seen in snakes).
-The population size is also more variable than the phenotype (difference in population size has a wider range).
+rep=1
+
+whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+```
+
+### Phenotype & Populationsize differences
+```{r, popsize and pheno}
+
+suppressMessages(print(two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+
+```
+
+## {-}
 
@@
 
-The next section I aim to look at how correlated newt and snakes are at local populations across the geographical area.
-I am examining correlation between newt and snake phenotypes, population sizes of newts and snakes, amount of toxin and snake population, and the amount of resistance and newt population size.
-I predicted that there would be a positive correlation between the phenotypes, and a negative correlation between population sizes, and the amount of toxin/resistance and population size.
-Below is a legend for the first two plots.
-The third plot is colored by trial.
-
-Legend:
-
-- "CA" = mean_newt_pheno_By_mean_snake_pheno (Pink)
-- "CB" = num_newts_By_num_snakes (Green)
-- "CC" = sum_newt_pheno_By_num_snake (Blue)
-- "CD" = sum_snake_pheno_By_num_newt (Purple)
-
-I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
-The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
-The second figure shows the the results of all 4 trials for each correlation measurement I made from 10,000-15,000 generations.
-The third plot takes the information from the fist plot and shows the distribution of correlation values by each trial (solid line at 0, dashed line at real newt-snake correlation).
-
+### cor
 ```{r, combo myplots}
-#files
-#GA1_tall_tall_file
-#GA2_long_file 
-#GA1_cor_tall_file
-#GA2_cor_file
 
@@
 
-boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-four_types_boxplot_cors_by_gen(GA1_cor_tall_file, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-boxplot_cors_by_gen(GA1_cor_tall_7_file, "Simulation Correlation 7 Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-four_types_boxplot_cors_by_gen(GA1_cor_tall_7_file, "Simulation four Correlation 7", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation 7 Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-
-```
-
-## Results {.tabset}
+boxplot_cors_by_gen(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(cost_grade_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+## Correlation Histograms{.tabset}
 
 ### Plot 1
-```{r, ga1 cor by dif windows}
+```{r, GA1 cor by dif windows}
 ginmin = 0
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 
-```{r, ga1 cor by dif windows 2}
+```{r, GA1 cor by dif windows 2}
 ginmin = 5000
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ### Plot 3
-```{r, ga1 cor by dif windows 3}
+```{r, GA1 cor by dif windows 3}
 ginmin = 10000
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ### Plot 4
-```{r, ga1 cor by dif windows 4}
+```{r, GA1 cor by dif windows 4}
 ginmin = 15000
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ### Plot 5
-```{r, ga1 cor by dif windows 5}
+```{r, GA1 cor by dif windows 5}
 ginmin = 20000
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ### Plot 6
-```{r, ga1 cor by dif windows 6}
+```{r, GA1 cor by dif windows 6}
 ginmin = 25000
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ### Plot 7
-```{r, ga1 cor by dif windows 7}
+```{r, GA1 cor by dif windows 7}
 ginmin = 30000
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ### Plot 8
-```{r, ga1 cor by dif windows 8}
+```{r, GA1 cor by dif windows 8}
 ginmin = 35000
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ### Plot 9
-```{r, ga1 cor by dif windows 9}
+```{r, GA1 cor by dif windows 9}
 ginmin = 40000
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ### Plot 10
-```{r, ga1 cor by dif windows 10}
+```{r, GA1 cor by dif windows 10}
 ginmin = 45000
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
+suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
+
 ## {-}
 
-## Results {.tabset}
-
-### Plot 1
-```{r, ga1 cor by dif windows}
-ginmin = 0
-ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 2
-
-```{r, ga1 cor by dif windows 2}
-ginmin = 5000
-ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 3
-```{r, ga1 cor by dif windows 3}
-ginmin = 10000
-ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 4
-```{r, ga1 cor by dif windows 4}
-ginmin = 15000
-ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 5
-```{r, ga1 cor by dif windows 5}
-ginmin = 20000
-ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 6
-```{r, ga1 cor by dif windows 6}
-ginmin = 25000
-ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 7
-```{r, ga1 cor by dif windows 7}
-ginmin = 30000
-ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 8
-```{r, ga1 cor by dif windows 8}
-ginmin = 35000
-ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 9
-```{r, ga1 cor by dif windows 9}
-ginmin = 40000
-ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
-
-### Plot 10
-```{r, ga1 cor by dif windows 10}
-ginmin = 45000
-ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(GA1_cor_tall_7_file, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
-```
+## Correlation across time {.tabset}
+
+### Random 1  
+```{r, GA1 cor and pheno}
+GA1_pattern <- unique(paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep))
+
+myrandomlist=sample.int(length(GA1_pattern), 3)
+
+# for(i in myrandomlist){
+#   myine<-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   plot(myine)
+# }
+
+cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+
+```
+
+### Random 2  
+```{r, random cor-pheno plot 2}
+
+cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+```
+
+### Random 3  
+```{r, random cor-pheno plot 3}
+
+cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+```
+
 ## {-}
 
-## Correlation across time
-
-```{r, ga1 cor and pheno}
-GA1_pattern <- unique(paste0(GA1_tall_tall_file$snake_mu_rate, "_", GA1_tall_tall_file$snake_mu_effect_sd,"_",GA1_tall_tall_file$newt_mu_rate, "_", GA1_tall_tall_file$newt_mu_effect_sd, "_", GA1_tall_tall_file$rep))
-for(i in 1:length(GA1_pattern)){
-  myine<-cor_trends_by_gen(GA1_tall_tall_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
-  plot(myine)
-}
-
-```
-
-```{r, ga1 cor 7 and pheno}
-GA1_pattern_7 <- unique(paste0(GA1_tall_tall_7_file$snake_mu_rate, "_", GA1_tall_tall_7_file$snake_mu_effect_sd,"_",GA1_tall_tall_7_file$newt_mu_rate, "_", GA1_tall_tall_7_file$newt_mu_effect_sd, "_", GA1_tall_tall_7_file$rep))
-for(i in 1:length(GA1_pattern_7)){
-  myine<-cor_trends_by_gen(GA1_tall_tall_7_file, GA1_cor_tall_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern_7[i])
-  plot(myine)
-}
-
-```
-
-## What happens over time (looking at the beginning. middle, and late part of my simulations)
-
-```{r, early plots summary}
+## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+### Pheno Beginning
+
+```{r, early plots}
 
@@
 max_gen=5000
-GA1_tall_tall_7_file_temp<-GA1_tall_tall_7_file
-GA1_tall_tall_7_file_temp$rep<-as.numeric(GA1_tall_tall_7_file_temp$rep)+4
-test<-rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp)
-
-# summary
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
-
-min_gen=10000
-max_gen=15000
-
-# summary
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+# for(i in 1:length(unique(cost_grade_lit$rep))){
+#   myine<-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1])
+```
+
+### Pheno Middle
+
+```{r, middle plots}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(cost_grade_lit$rep))){
+#   myine<-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1])
+```
+
+### Pheno End
+
+```{r, end plots}
 
@@
 
-# summary
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+# for(i in 1:length(unique(cost_grade_lit$rep))){
+#   myine<-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i])
+#   plot(myine)
+# 
+# }
+whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1])
+```
+
+### Dif Beginning 
+```{r, early plots 1a}
 
@@
 
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-min_gen=10000
-max_gen=15000
-
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+# for(i in 1:length(unique(cost_grade_lit$rep))){
+#   myine<-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1] )
+
+```
+
+### Dif Middle 
+```{r, early plots 2a}
+
+min_gen=25000
+max_gen=30000
+
+# for(i in 1:length(unique(cost_grade_lit$rep))){
+#   myine<-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1] )
+
+```
+
+### Dif End 
+```{r, early plots 3a}
 
@@
 
-GA_summary(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
-
-```
+# for(i in 1:length(unique(cost_grade_lit$rep))){
+#   myine<-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i] )
+#   suppressMessages(plot(myine))
+# }
+
+two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1] )
+
+```
+
+## {-}
+
+## Summary {.tabset}
+
+### Early-Sim Population Size Summary
+
+```{r, early plots summary}
+
+min_gen=100
+max_gen=5000
+GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Mid-Sim Population Size Summary
+```{r, plots summary 2}
+# summary
+
+min_gen=25000
+max_gen=30000
+
+# summary
+GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Late-Sim Population Size Summary
+```{r, plots summary 3}
+min_gen=45000
+max_gen=50000
+
+# summary
+GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+
+```
+
+### Early Difference Summary
+```{r, dif plots summary 1}
+
+min_gen=100
+max_gen=5000
+
+GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+```
+
+### Mid Difference Summary
+```{r, dif plots summary 2}
+min_gen=25000
+max_gen=30000
+
+GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
+
+### Late Difference Summary
+```{r, dif plots summary 3}
+min_gen=45000
+max_gen=50000
+GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+
+```
+
+### By Snake GA (Early)
+```{r, snakega plots summary 1}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Mid)
+```{r, snakega plots summary 2}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Snake GA (Late)
+```{r, snakega plots summary 3}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+
+```
+
+### By Newt GA (Early)
+```{r, newtga plots summary 1}
+min_gen=100
+max_gen=5000
+#
+
+GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+
+```
+
+### By Newt GA (Mid)
+```{r, newtga plots summary 2}
+min_gen=25000
+max_gen=30000
+#
+
+GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+
+```
+
+### By Newt GA (Late)
+```{r, newtga plots summary 3}
+min_gen=45000
+max_gen=50000
+#
+
+GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+
+```
+
+## {-}
+
+## Heatmap {.tabset}
+
+### Population Size (Early)
 
@@
 #heatmap
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-min_gen=10000
-max_gen=15000
+build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+```
+
+### Population Size (Mid)  
+```{r, early plots Heatmap 2}
+min_gen=25000
+max_gen=30000
 #heatmap
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
+build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+
+```
+
+### Population Size (Late) 
+```{r, early plots Heatmap 3}
 min_gen=45000
@@
 #heatmap
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
+build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+```
+
+### Phenotype (Early) 
+```{r, early plots Heatmap pheno 1}
 min_gen=100
 max_gen=5000
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
-min_gen=10000
-max_gen=15000
+build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### Phenotype (Mid) 
+```{r, early plots Heatmap pheno 2}
+
+min_gen=25000
+max_gen=30000
 #heatmap
 
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-
+build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+```
+
+### Phenotype (Late) 
+```{r, early plots Heatmap pheno 3}
 min_gen=45000
@@
 
-build_heatmap(rbind(GA1_tall_tall_file, GA1_tall_tall_7_file_temp), min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+
+```
+
+## {-}
+
+```{r, red in grid files}
+require(readr)
+cost_grade_grid<- read.csv("~/Desktop/GA1_dif_cost/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
+cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
+cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
+cost_grade_grid$grid_num = 5
 
@@
 
-### Snake_1e-09_0.05_Newt_1e-09_0.05_2
-
-```{r, cor grid by location}
-
-#GA1_grid_tall_file
-
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-spegen=25001
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
-
-data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
-
-data_long_mean_short<-data_long_mean
-
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
-newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Mean Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-```{r, cor grid by location}
-
-#GA1_grid_tall_7_file
-
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-spegen=25001
-
-GA1<-GA1_grid_tall_7_file[which(GA1_grid_tall_7_file$snake_newt_rep==file_name & GA1_grid_tall_7_file$generation==spegen),]
-
-GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
-
-data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
-
-data_long_mean_short<-data_long_mean
-
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
-newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Mean Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-```{r, cor grid by location}
-
-#GA1_grid_tall_file
-
-file_name= "Snake_1e-09_0.05_Newt_1e-09_0.05_2"
-spegen=26051
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
-
-data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
-
-data_long_mean_short<-data_long_mean
-
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
-newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Mean Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# max phenotype
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
-
-data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
-
-data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
-
-data_long_max_short<-data_long_max
-
-data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_max_short)+
-  labs(title = "Max Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
-newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Max Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# max phenotype
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
-
-data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
-
-data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
-
-data_long_min_short<-data_long_min
-
-data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_min_short)+
-  labs(title = "Min Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
-newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Min Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-#GA1_grid_tall_file population size
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
-
-GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
-
-GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
-
-GA1_data_long_ind_short<-GA1_data_long_ind
-
-GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
-
-main_plot<-ggplot(GA1_data_long_ind_short)+
-  labs(title = "Locations of Ind",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Number of Individuals")+
-  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c(option = "plasma")+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
-newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
-newt_GA1$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
-
-newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
-
-extra_plot <- ggplot(newt_GA1)+
-  ggtitle("Num of Ind") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
-
-### Snake_1e-08_0.005_Newt_1e-08_0.005_3
-
-```{r, cor grid by location round 2}
-
-#GA1_grid_tall_file
-
-file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
-spegen=25001
-
-GA1<-GA1_grid_tall_file[which(GA1_grid_tall_file$snake_newt_rep==file_name & GA1_grid_tall_file$generation==spegen),]
-
-GA1_mean = GA1[,grepl("generation|mean", names(GA1)) ]
-
-data_long_mean <- gather(GA1_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
-
-data_long_mean[,c("species","type", "type2","location")]<- str_split_fixed(data_long_mean$condition, "_", 4)
-
-data_long_mean_short<-data_long_mean
-
-data_long_mean_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_mean_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_mean_short)+
-  labs(title = "Mean Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_mean_short[which(data_long_mean_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_mean_short[which(data_long_mean_short$species=="snake"),]
-newt<-data_long_mean_short[which(data_long_mean_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Mean Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# SD
-
-GA1_sd = GA1[,grepl("generation|sd", names(GA1)) ]
-
-data_long_sd <- gather(GA1_sd, condition, measurement, newt_sd_pheno_0:snake_sd_pheno_99, factor_key=TRUE)
-
-data_long_sd[,c("species","type", "type2","location")]<- str_split_fixed(data_long_sd$condition, "_", 4)
-
-data_long_sd_short<-data_long_sd
-
-data_long_sd_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_sd_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_sd_short)+
-  labs(title = "SD Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_sd_short[which(data_long_sd_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_sd_short[which(data_long_sd_short$species=="snake"),]
-newt<-data_long_sd_short[which(data_long_sd_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("SD Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# max phenotype
-
-GA1_max = GA1[,grepl("generation|max", names(GA1)) ]
-
-data_long_max <- gather(GA1_max, condition, measurement, newt_max_pheno_0:snake_max_pheno_99, factor_key=TRUE)
-
-data_long_max[,c("species","type", "type2","location")]<- str_split_fixed(data_long_max$condition, "_", 4)
-
-data_long_max_short<-data_long_max
-
-data_long_max_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_max_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_max_short)+
-  labs(title = "Max Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_max_short[which(data_long_max_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_max_short[which(data_long_max_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_max_short[which(data_long_max_short$species=="snake"),]
-newt<-data_long_max_short[which(data_long_max_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Max Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-# min phenotype
-
-GA1_min = GA1[,grepl("generation|min", names(GA1)) ]
-
-data_long_min <- gather(GA1_min, condition, measurement, newt_min_pheno_0:snake_min_pheno_99, factor_key=TRUE)
-
-data_long_min[,c("species","type", "type2","location")]<- str_split_fixed(data_long_min$condition, "_", 4)
-
-data_long_min_short<-data_long_min
-
-data_long_min_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-data_long_min_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-main_plot<-ggplot(data_long_min_short)+
-  labs(title = "Min Phenotype of Locations",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Toxicity/Resistance")+
-  geom_point(data = data_long_min_short[which(data_long_min_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = data_long_min_short[which(data_long_min_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c()+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-data_long_min_short[which(data_long_min_short$species=="snake"),]
-newt<-data_long_min_short[which(data_long_min_short$species=="newt"),]
-newt$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs")
-
-newt$info[newt$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt$info[newt$location %in% list(0, 19, 80, 99)] <- "corner"
-newt$info[is.na(newt$info)]<- "middle"
-
-extra_plot <- ggplot(newt)+
-  ggtitle("Min Phenotype") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-#GA1_grid_tall_file population size
-
-GA1_ind = GA1[,grepl("generation|num_ind", names(GA1)) ]
-
-GA1_data_long_ind <- gather(GA1_ind, condition, measurement, newt_num_ind_0:snake_num_ind_99, factor_key=TRUE)
-
-GA1_data_long_ind[,c("species","type", "type2","location")]<- str_split_fixed(GA1_data_long_ind$condition, "_", 4)
-
-GA1_data_long_ind_short<-GA1_data_long_ind
-
-GA1_data_long_ind_short$y_loc<- rep(c(rep.int(20, 2),rep.int(19, 2),rep.int(18, 2),rep.int(17, 2),rep.int(16, 2),rep.int(15, 2),rep.int(14, 2),rep.int(13, 2),rep.int(12, 2),rep.int(11, 2),rep.int(10, 2),rep.int(9, 2),rep.int(8, 2),rep.int(7, 2),rep.int(6, 2),rep.int(5, 2),rep.int(4, 2),rep.int(3, 2),rep.int(2, 2),rep.int(1, 2)),5)
-GA1_data_long_ind_short$x_loc<-c(rep.int(1, 40),rep.int(2, 40),rep.int(3, 40),rep.int(4, 40),rep.int(5, 40))
-
-GA1_data_long_ind_short$measurement[GA1_data_long_ind_short$measurement == 0]  <- NA
-
-main_plot<-ggplot(GA1_data_long_ind_short)+
-  labs(title = "Locations of Ind",
-              subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Number of Individuals")+
-  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
-  geom_point(data = GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
-  scale_fill_viridis_c(option = "plasma")+
-  theme_bw()+
-  theme(legend.justification = "top")
-
-snake<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="snake"),]
-newt_GA1<-GA1_data_long_ind_short[which(GA1_data_long_ind_short$species=="newt"),]
-newt_GA1$snake_value <- snake$measurement
-cor(as.numeric(snake$measurement), as.numeric(newt_GA1$measurement), use="complete.obs")
-
-newt_GA1$info[newt_GA1$location %in% list(1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,20, 39, 40, 59, 60, 79, 81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98)]   <- "edge"
-newt_GA1$info[newt_GA1$location %in% list(0, 19, 80, 99)] <- "corner"
-newt_GA1$info[is.na(newt_GA1$info)]<- "middle"
-
-extra_plot <- ggplot(newt_GA1)+
-  ggtitle("Num of Ind") +
-  xlab("Newt") + ylab("Snake")+
-  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
-  theme_bw()+
-   theme(text = element_text(size=10),title =element_text(size=8),
-         legend.text = element_text(size = 8),
-         legend.position ="bottom",
-         legend.key.size = unit(0.1, "lines"),
-         legend.title=element_blank())+
-  guides(shape = guide_legend(override.aes = list(size = 1)),
-         color = guide_legend(override.aes = list(size = 1)))
-
-#try to arrage the grids
-
-main_plot +  inset_element(extra_plot, left = 1., bottom = -0.12, right = 1.35, top = 0.5)
-
-```
+### Early Simulation Correlation {.tabset}
+
+#### Mean 
+```{r, cor grid high cor mean}
+
+file=cost_grade_grid
+file_name="Snake_1e-11_5_Newt_1e-10_0.5_0"
+spegen=9501
+type="mean"
+row_num=200
+col_num=50
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+```{r, cor grid high cor popsize}
+
+file=cost_grade_grid
+file_name="Snake_1e-11_5_Newt_1e-10_0.5_0"
+spegen=9501
+type="num_ind"
+row_num=200
+col_num=50
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+```
+
+### {-}

### 2022-11-03 graphs_newt_snakes/dif_cost_grade.Rmd
I got the cost gradent results back and there is cor

@@
 
+grid_plot<- function(file_name, spegen, file, type, row_num, col_num){
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
+GA1_type = paste0("generation|", type)
+
+GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
+GA1_type <- GA1_type[-1]
+
+data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
+data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)
+
+data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)
+
+data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))
+
+main_plot<-ggplot(data_long_type_comp)+
+
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
+  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
+  scale_fill_viridis_c()+
+  #ylim(0, row_num)+
+  #xlim(0, col_num)+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+if(type != "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Toxicity/Resistance")+
+ scale_fill_viridis_c()
+}
+if(type == "num_ind"){
+main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+              subtitle = paste0(file_name, ", Generation: ", spegen),
+              fill = "Newt/Snake Phenotype")+
+scale_fill_viridis_c(option = "plasma")
+}
+
+snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
+newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
+newt$snake_value <- snake$measurement
+print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))
+
+newt$info <- "middle"
+newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+   theme(text = element_text(size=10),title =element_text(size=8),
+         legend.text = element_text(size = 8),
+         legend.position ="bottom",
+         legend.key.size = unit(0.1, "lines"),
+         legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
+return(final_plot)}
+
 ```
@@
 require(readr)
-cost_grade_grid<- read.csv("~/Desktop/GA1_dif_cost/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
 cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
@@
 
-### Early Simulation Correlation {.tabset}
-
-#### Mean 
+## Early Simulation Correlation {.tabset}
+
+### Mean 
 ```{r, cor grid high cor mean}
@@
 file=cost_grade_grid
-file_name="Snake_1e-11_5_Newt_1e-10_0.5_0"
+file_name="1e-11_5_1e-10_0.5_0"
 spegen=9501
 type="mean"
-row_num=200
-col_num=50
+row_num=20
+col_num=5
 
@@
 
+### Max 
+```{r, cor grid high cor max}
+
+file=cost_grade_grid
+file_name="1e-11_5_1e-10_0.5_0"
+spegen=9501
+type="max"
+row_num=20
+col_num=5
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### Min 
+```{r, cor grid high cor min}
+
+file=cost_grade_grid
+file_name="1e-11_5_1e-10_0.5_0"
+spegen=9501
+type="min"
+row_num=20
+col_num=5
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### popsize
 ```{r, cor grid high cor popsize}
@@
 file=cost_grade_grid
-file_name="Snake_1e-11_5_Newt_1e-10_0.5_0"
+file_name="1e-11_5_1e-10_0.5_0"
 spegen=9501
 type="num_ind"
-row_num=200
-col_num=50
+row_num=20
+col_num=5
 grid_plot(file_name, spegen, file, type, row_num, col_num)
@@
 
-### {-}
+## {-}
+
+```{r, red in grid files 2}
+require(readr)
+cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
+cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
+cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
+cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
+cost_grade_grid$grid_num = 5
+
+```
+
+## Late Simulation Correlation {.tabset}
+
+### Mean 
+```{r, cor grid high cor mean late}
+
+file=cost_grade_grid
+file_name="1e-11_5_1e-10_0.5_0"
+spegen=44501
+type="mean"
+row_num=20
+col_num=5
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### Max 
+```{r, cor grid high cor max late}
+
+file=cost_grade_grid
+file_name="1e-11_5_1e-10_0.5_0"
+spegen=44501
+type="max"
+row_num=20
+col_num=5
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+### Min 
+```{r, cor grid high cor min late}
+
+file=cost_grade_grid
+file_name="1e-11_5_1e-10_0.5_0"
+spegen=44501
+type="min"
+row_num=20
+col_num=5
+
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+## Pop size
+```{r, cor grid high cor popsize late}
+
+file=cost_grade_grid
+file_name="1e-11_5_1e-10_0.5_0"
+spegen=44501
+type="num_ind"
+row_num=20
+col_num=5
+grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+```
+
+## {-}

### 2022-11-03 graphs_newt_snakes/newt_change.Rmd
I got the cost gradent results back and there is cor

--- 2022-11-03 graphs_newt_snakes/dif_cost_grade.Rmd
@@
 ---
-title: "Cost Gradient"
+title: "newt change"
 output: html_document
-date: '2022-10-21'
+date: '2022-11-03'
 ---
@@
 thepath=/Users/victoria/Desktop/
-foldername=cost_grade
+foldername=newt_change
 thefolder=${thepath}${foldername}/*
@@
 
-cost_grade_lit<- read.csv("~/Desktop/cost_grade/all_lit.txt" , header = TRUE)
-
-cost_grade_lit$group_rep <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep)
-
-cost_grade_lit$group <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd)
-
-cost_grade_lit$sim=LETTERS[factor(cost_grade_lit$group)]
-cost_grade_lit$dif <- cost_grade_lit$Snake_mean_Pheno-cost_grade_lit$Newt_mean_Pheno
-
-cost_grade_cor<- read.csv("~/Desktop/cost_grade/all_cor.txt" , header = TRUE)
-cost_grade_cor$group_rep <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd, "_", cost_grade_cor$rep)
-cost_grade_cor$group <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd)
-cost_grade_cor$sim=LETTERS[factor(cost_grade_cor$group)]
+newt_change_lit<- read.csv("~/Desktop/newt_change/all_lit.txt" , header = TRUE)
+
+newt_change_lit$group_rep <- paste0(newt_change_lit$snake_mu_rate, "_", newt_change_lit$snake_mu_effect_sd,"_",newt_change_lit$newt_mu_rate, "_", newt_change_lit$newt_mu_effect_sd, "_", newt_change_lit$rep)
+
+newt_change_lit$group <- paste0(newt_change_lit$snake_mu_rate, "_", newt_change_lit$snake_mu_effect_sd,"_",newt_change_lit$newt_mu_rate, "_", newt_change_lit$newt_mu_effect_sd)
+
+newt_change_lit$sim=LETTERS[factor(newt_change_lit$group)]
+newt_change_lit$dif <- newt_change_lit$Snake_mean_Pheno-newt_change_lit$Newt_mean_Pheno
+
+newt_change_cor<- read.csv("~/Desktop/newt_change/all_cor.txt" , header = TRUE)
+newt_change_cor$group_rep <- paste0(newt_change_cor$snake_mu_rate, "_", newt_change_cor$snake_mu_effect_sd,"_",newt_change_cor$newt_mu_rate, "_", newt_change_cor$newt_mu_effect_sd, "_", newt_change_cor$rep)
+newt_change_cor$group <- paste0(newt_change_cor$snake_mu_rate, "_", newt_change_cor$snake_mu_effect_sd,"_",newt_change_cor$newt_mu_rate, "_", newt_change_cor$newt_mu_effect_sd)
+newt_change_cor$sim=LETTERS[factor(newt_change_cor$group)]
 
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=cost_grade_lit
-#cfile=cost_grade_cor 
+#file=newt_change_lit
+#cfile=newt_change_cor 
  # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=cost_grade_lit
+  #file=newt_change_lit
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 
 grid_plot<- function(file_name, spegen, file, type, row_num, col_num){
+
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
@@
 newt$info <- "middle"
-newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
-
-newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+#need to look into, coloring problem
+newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-1-row_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-row_num):(col_num*row_num-2)))]   <- "edge"
 
@@
 ```{r, graphing by gen}
-trends_by_gen(cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
-
-#aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group_rep), FUN=mean)
+trends_by_gen(newt_change_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+#aggregate(newt_change_lit[which(newt_change_lit$generation>=100 & newt_change_lit$generation<=50000),]$dif, list(newt_change_lit[which(newt_change_lit$generation>=100 & newt_change_lit$generation<=50000),]$group_rep), FUN=mean)
 
@@
 ```{r, average difference}
-aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group), FUN=mean)
+aggregate(newt_change_lit[which(newt_change_lit$generation>=100 & newt_change_lit$generation<=50000),]$dif, list(newt_change_lit[which(newt_change_lit$generation>=100 & newt_change_lit$generation<=50000),]$group), FUN=mean)
 ```
@@
 
-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(newt_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
-suppressMessages(print(two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
-
-#suppressMessages(print(two_hist_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+suppressMessages(print(two_hist(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
 
@@
 
-boxplot_cors_by_gen(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-#four_types_boxplot_cors_by_gen(cost_grade_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(newt_change_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(newt_change_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
@@
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ```{r, GA1 cor and pheno}
-GA1_pattern <- unique(paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep))
+GA1_pattern <- unique(paste0(newt_change_lit$snake_mu_rate, "_", newt_change_lit$snake_mu_effect_sd,"_",newt_change_lit$newt_mu_rate, "_", newt_change_lit$newt_mu_effect_sd, "_", newt_change_lit$rep))
 
@@
 # for(i in myrandomlist){
-#   myine<-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   myine<-cor_trends_by_gen(newt_change_lit, newt_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
 #   plot(myine)
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+cor_trends_by_gen(newt_change_lit, newt_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
 
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+cor_trends_by_gen(newt_change_lit, newt_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
 ```
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+cor_trends_by_gen(newt_change_lit, newt_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
 ```
@@
 
-# for(i in 1:length(unique(cost_grade_lit$rep))){
-#   myine<-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i])
+# for(i in 1:length(unique(newt_change_lit$rep))){
+#   myine<-whale_gen(newt_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(newt_change_lit$rep)[i])
 #   plot(myine)
@@
 # }
-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1])
+whale_gen(newt_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(newt_change_lit$rep)[1])
 ```
@@
 
-# for(i in 1:length(unique(cost_grade_lit$rep))){
-#   myine<-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i] )
+# for(i in 1:length(unique(newt_change_lit$rep))){
+#   myine<-two_hist(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(newt_change_lit$rep)[i] )
 #   suppressMessages(plot(myine))
@@
 
-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1] )
+two_hist(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(newt_change_lit$rep)[1] )
 
@@
 max_gen=5000
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
@@
 
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 ```
@@
 
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 max_gen=50000
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 
-GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
 
@@
 
-GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+GA_summary_by_species(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
 
@@
 #heatmap
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 ```
@@
 #heatmap
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
@@
 max_gen=5000
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 require(readr)
-cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
-cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
-cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
-cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
-cost_grade_grid$grid_num = 5
+newt_change_grid<- read.csv("~/Desktop/newt_change/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+newt_change_grid$group_rep <- paste0(newt_change_grid$snake_mu_rate, "_", newt_change_grid$snake_mu_effect_sd,"_",newt_change_grid$newt_mu_rate, "_", newt_change_grid$newt_mu_effect_sd, "_", newt_change_grid$rep)
+newt_change_grid$group <- paste0(newt_change_grid$snake_mu_rate, "_", newt_change_grid$snake_mu_effect_sd,"_",newt_change_grid$newt_mu_rate, "_", newt_change_grid$newt_mu_effect_sd)
+newt_change_grid$sim=LETTERS[factor(newt_change_grid$group)]
+newt_change_grid$grid_num = 5
 
@@
 
-file=cost_grade_grid
+file=newt_change_grid
 file_name="1e-11_5_1e-10_0.5_0"
@@
 require(readr)
-cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
-cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
-cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
-cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
-cost_grade_grid$grid_num = 5
+newt_change_grid<- read.csv("~/Desktop/newt_change/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
+newt_change_grid$group_rep <- paste0(newt_change_grid$snake_mu_rate, "_", newt_change_grid$snake_mu_effect_sd,"_",newt_change_grid$newt_mu_rate, "_", newt_change_grid$newt_mu_effect_sd, "_", newt_change_grid$rep)
+newt_change_grid$group <- paste0(newt_change_grid$snake_mu_rate, "_", newt_change_grid$snake_mu_effect_sd,"_",newt_change_grid$newt_mu_rate, "_", newt_change_grid$newt_mu_effect_sd)
+newt_change_grid$sim=LETTERS[factor(newt_change_grid$group)]
+newt_change_grid$grid_num = 5
 

### 2022-11-03 graphs_newt_snakes/dif_cost_grade.Rmd
I fixed the color dot problem

@@
 newt$info <- "middle"
-newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
-
-newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-1-row_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num-row_num), row_num),  c((col_num*row_num-row_num):(col_num*row_num-2)))]   <- "edge"
 
@@
 
-## Pop size
+### Pop size
 ```{r, cor grid high cor popsize late}

### 2022-11-03 graphs_newt_snakes/newt_change.Rmd
I fixed the color dot problem

@@
 
-newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-row_num):(col_num*row_num-2)))]   <- "edge"
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num-row_num), row_num),  c((col_num*row_num-row_num):(col_num*row_num-2)))]   <- "edge"
 

### 2022-11-07 graphs_newt_snakes/big_map.Rmd
I wrote my thoughts about the big map experiment

@@
 The prediction that is when I create a larger map there will be more opportunities for different areas to co-evolve, creating a mosaic pattern.
-The BIG map to be 100 times larger than the long map.
+The BIG map to be 100 times larger (area wise) than the long map.
 The demotions would be; length=1,400 width=350.
@@
 taking information every 50 generations instead of 20) and for a shorter amount of time (e.g.
-from 50,000 generation to only 10,000 generations).
-
-My previous simulations ran for 50,000 generations and took a day or less to run (msprime+slim). I will make some plots to see how long these larger simulations will take to run
+from 50,000 generation to only 10,000 generations and 30,000 generations).
+
+My previous simulations ran for 50,000 generations and took a day or less to run (msprime+slim). I will make some plots to see how long these larger simulations will take to run.
+
+After running some of theses simulations, it takes about 3-7 days to run 10,000 generations and longer to run 30,000 generations.
+To make the simulations run faster I limit the amount of data I collect i.e.
+collecting data every 100 or 1,000 generations.
+
+Genetic architecture (GA) experiment values:
+
+1e-9*(0.05)^2 = 2.5e-12
+1e-10*(0.5)^2 = 2.5e-11
+1e-11*(5.0)^2 = 2.5e-10
 
@@
   geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
-  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
+  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/1000, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
   scale_y_continuous(labels = scales::percent)+
@@
               subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Newt/Snake Phenotype                                                         ")+
+              fill = "Newt/Snake Popsize                                                         ")+
 scale_fill_viridis_c(option = "plasma")
@@
 ### Phenotype differences
+
+The first part of this report examines how the mean whole population newt and snake phenotype changes over time.
+Red line represents the newts while the blue line snake the snakes.
+The black line is the difference between snake ans newt mean phenotype.
+Newt and snake genetic architectures (GAs) are the same down the diagonal (top right to bottom left).
+As we move across the columns newt GA increases in mutational variance.
+As we move down the rows the mutational variance of snake GA increases.
+There are two simulations shown in each of theses figures one ends at 10,000 generations and the other ends at 30,000 generations.
+They each have their own msprime file (there are slightly different starting levels of genetic variation).
+
 ```{r, graphing by gen}
@@
 
+These results show that the mean phenotype of newts and snakes follow similar patterns under the specific genetic architecture combinations (blue and red lines in each fig follow similar paths).
+In most cases it seems that the mean newt and snake phenotype increases over time.
+It seems  like it takes more than 10,000 generations for most of these simulations to reach a constant mean phenotype.
+Most of the simulations reach a steady mean phenotype by 30,000 generations.
+Overall, the mean phenotypes of the big maps are very similar to the mean phenotype of the smaller maps.
+
 ## Connection between higher phenotype and population (5 sec) {.tabset}
+
+In the smaller maps with the same GA combinations there was a link between population size and average phenotype differences (snake - newt mean phenotype).
+When the snake population size was large the snakes had a higher phenotype.
+When newts had a larger phenotype, newts also had a larger population size.
 
@@
 
-### correlation
+In these figures the average population size of newts and snakes were about 33,000.
+The difference in population size ranged from 0 to 20,000.
+The mean phenotype of newts and snakes were close, but newts seem to have a phenotype advantage in most of the GA combinations.
+When snakes had a GA with few mutations of large effect, their mean phenotype was larger then the newts mean phenotype.
+
+### Correlation
+
+The next section examines the spatial correlation of the local mean phenotypes of snakes and newts.
+We predicted that in areas where newts phenotypes were large snakes phenotype would also be large.
+In areas where newt phenotype was small we predicted that snake phenotype would also be small.
+The prediction would result in a strong positive spatial correlation between newt and snake local phenotypes.
+I first present the spatial phenotype correlation for the entire simulation.
+The dashed line in the empirical newt-snake spatial correlation result.
+Each box plot represents one simulation trial.
+Trial 0 is the simulation that ran to 10,000 generations and trial 1 is the simulation that ran to 30,000 generations.
+(I ran things longer to see if the spatial phenotype correlation would improve with time).
+
 ```{r, combo myplots}
@@
 
+These results show that the spatial correlation between newt and snake phenotypes is slightly positive.
+It is nowhere near the empirical newt-snake spatial correlation results.
+Increasing the time had little to no effect on the spatial correlation.
+Increasing the size of the simulation did not increase the spatial correlation that is scene in real newts and snake phenotypes.
+
 ## Correlation across time {.tabset}
 
-Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment.
+Next, we will examine three randomly chosen plots from this experiment.
 Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
@@
 ## {-}
+
+Mean newt and snake phenotypes can either go up, go down, or stay constant near zero.
+Sometimes the mean phenotypes go down together, other times they both go up.
+Occasionally, one species phenotype goes up while the other species phenotype stays constant.
+In all of these cases the spatial correlation does not seem to change.
 
@@
 There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
-There are three figures in each set, taken at the begging, middle, and end time chunks.
-These are whole population calculations so the 5 section and 7 section data sets are not calculated differently.
-
-### Early-Sim Population Size Summary
+
+### Population Size Summary
 
@@
 
-### Early Difference Summary
+###  Difference Summary
 ```{r, dif plots summary 1}
@@
 
+Most of the summarized simulation results seem to be the same for the different length trials.
+There is a slight color and shape patterns.
+Regardless of the newt GA the best Snake GA was 1e-10_0.5 (green) and the worst was 1e-11_5.0 (blue).
+Regardless of the snake GA the best Newt GA was 1e-10_0.5 (triangle) and the worst was 1e-11_5.0 (square).
+The species that had the GA of 1e-11_5.0 typically did poorly.
+It was difficult for me to see a clear "winner" when the GA of newts and snakes were the same.
+
 ## Heatmap {.tabset}
+
+The heat map represents the summarized results of the previous section in a different format.
+There are two heat maps, 1) shows the snakes population size and 2) shows the difference in mean phenotype.
+In plot 1 when the snakes have a larger population size the color of the box will be more yellow and when the snakes have a lower population size the box will be more purple.
+In plot 2 id newts have a higher phenotype the box will be more red and when snakes have a larger phenotype the box will be more blue.
+Again trial 0 is the simulation that only ran tell 10,000 generations and trial 1 ran to 30,000 generations.
 
@@
 
+Overall, these results show that when a species has a GA of 1e-11_5.0 they typically has a lower phenotype and population size.
+From these figures it seems like newts have more of advantage in most of the GA combinations (2/3 snake population size and phenotype are low).
+
 ## What is up with the correlations
+
+In this last section I show the local mean phenotype and population size of newts (circles) and snakes (square).
+In the mean phenotype plot, the more resistant or toxic a snake or newt is the more yellow the square or circle.
+In the population size plot, the larger a local population is the more bright/yellow the circle or square is.
+There is a small sub plot showing the individual newt and snake values (phenotype or population size) colored by location in the artificial map.
+It is difficult to see the squares in these plots, but overall I see no patterns of clustering.
 

### 2022-11-07 graphs_newt_snakes/snake_change.Rmd
I wrote my thoughts about the big map experiment

--- 2022-11-03 graphs_newt_snakes/newt_change.Rmd
@@
 ---
-title: "newt change"
+title: "snake change"
 output: html_document
-date: '2022-11-03'
+date: '2022-11-04'
 ---
@@
 thepath=/Users/victoria/Desktop/
-foldername=newt_change
+foldername=snake_change
 thefolder=${thepath}${foldername}/*
@@
 
-newt_change_lit<- read.csv("~/Desktop/newt_change/all_lit.txt" , header = TRUE)
-
-newt_change_lit$group_rep <- paste0(newt_change_lit$snake_mu_rate, "_", newt_change_lit$snake_mu_effect_sd,"_",newt_change_lit$newt_mu_rate, "_", newt_change_lit$newt_mu_effect_sd, "_", newt_change_lit$rep)
-
-newt_change_lit$group <- paste0(newt_change_lit$snake_mu_rate, "_", newt_change_lit$snake_mu_effect_sd,"_",newt_change_lit$newt_mu_rate, "_", newt_change_lit$newt_mu_effect_sd)
-
-newt_change_lit$sim=LETTERS[factor(newt_change_lit$group)]
-newt_change_lit$dif <- newt_change_lit$Snake_mean_Pheno-newt_change_lit$Newt_mean_Pheno
-
-newt_change_cor<- read.csv("~/Desktop/newt_change/all_cor.txt" , header = TRUE)
-newt_change_cor$group_rep <- paste0(newt_change_cor$snake_mu_rate, "_", newt_change_cor$snake_mu_effect_sd,"_",newt_change_cor$newt_mu_rate, "_", newt_change_cor$newt_mu_effect_sd, "_", newt_change_cor$rep)
-newt_change_cor$group <- paste0(newt_change_cor$snake_mu_rate, "_", newt_change_cor$snake_mu_effect_sd,"_",newt_change_cor$newt_mu_rate, "_", newt_change_cor$newt_mu_effect_sd)
-newt_change_cor$sim=LETTERS[factor(newt_change_cor$group)]
+snake_change_lit<- read.csv("~/Desktop/snake_change/all_lit.txt" , header = TRUE)
+
+snake_change_lit$group_rep <- paste0(snake_change_lit$snake_mu_rate, "_", snake_change_lit$snake_mu_effect_sd,"_",snake_change_lit$newt_mu_rate, "_", snake_change_lit$newt_mu_effect_sd, "_", snake_change_lit$rep)
+
+snake_change_lit$group <- paste0(snake_change_lit$snake_mu_rate, "_", snake_change_lit$snake_mu_effect_sd,"_",snake_change_lit$newt_mu_rate, "_", snake_change_lit$newt_mu_effect_sd)
+
+snake_change_lit$sim=LETTERS[factor(snake_change_lit$group)]
+snake_change_lit$dif <- snake_change_lit$Snake_mean_Pheno-snake_change_lit$Newt_mean_Pheno
+
+snake_change_cor<- read.csv("~/Desktop/snake_change/all_cor.txt" , header = TRUE)
+snake_change_cor$group_rep <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd, "_", snake_change_cor$rep)
+snake_change_cor$group <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd)
+snake_change_cor$sim=LETTERS[factor(snake_change_cor$group)]
 
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=newt_change_lit
-#cfile=newt_change_cor 
+#file=snake_change_lit
+#cfile=snake_change_cor 
  # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=newt_change_lit
+  #file=snake_change_lit
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(snake_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 
@@
 ```{r, graphing by gen}
-trends_by_gen(newt_change_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
-
-#aggregate(newt_change_lit[which(newt_change_lit$generation>=100 & newt_change_lit$generation<=50000),]$dif, list(newt_change_lit[which(newt_change_lit$generation>=100 & newt_change_lit$generation<=50000),]$group_rep), FUN=mean)
+trends_by_gen(snake_change_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+#aggregate(snake_change_lit[which(snake_change_lit$generation>=100 & snake_change_lit$generation<=50000),]$dif, list(snake_change_lit[which(snake_change_lit$generation>=100 & snake_change_lit$generation<=50000),]$group_rep), FUN=mean)
 
@@
 ```{r, average difference}
-aggregate(newt_change_lit[which(newt_change_lit$generation>=100 & newt_change_lit$generation<=50000),]$dif, list(newt_change_lit[which(newt_change_lit$generation>=100 & newt_change_lit$generation<=50000),]$group), FUN=mean)
+aggregate(snake_change_lit[which(snake_change_lit$generation>=100 & snake_change_lit$generation<=50000),]$dif, list(snake_change_lit[which(snake_change_lit$generation>=100 & snake_change_lit$generation<=50000),]$group), FUN=mean)
 ```
@@
 
-whale_gen(newt_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(snake_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
-suppressMessages(print(two_hist(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
-
-#suppressMessages(print(two_hist_all_rep(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+suppressMessages(print(two_hist(snake_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(snake_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
 
@@
 
-boxplot_cors_by_gen(newt_change_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-#four_types_boxplot_cors_by_gen(newt_change_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(snake_change_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(snake_change_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
@@
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(newt_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(snake_change_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ```{r, GA1 cor and pheno}
-GA1_pattern <- unique(paste0(newt_change_lit$snake_mu_rate, "_", newt_change_lit$snake_mu_effect_sd,"_",newt_change_lit$newt_mu_rate, "_", newt_change_lit$newt_mu_effect_sd, "_", newt_change_lit$rep))
+GA1_pattern <- unique(paste0(snake_change_lit$snake_mu_rate, "_", snake_change_lit$snake_mu_effect_sd,"_",snake_change_lit$newt_mu_rate, "_", snake_change_lit$newt_mu_effect_sd, "_", snake_change_lit$rep))
 
@@
 # for(i in myrandomlist){
-#   myine<-cor_trends_by_gen(newt_change_lit, newt_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   myine<-cor_trends_by_gen(snake_change_lit, snake_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
 #   plot(myine)
@@
 
-cor_trends_by_gen(newt_change_lit, newt_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+cor_trends_by_gen(snake_change_lit, snake_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
 
@@
 
-cor_trends_by_gen(newt_change_lit, newt_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+cor_trends_by_gen(snake_change_lit, snake_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
 ```
@@
 
-cor_trends_by_gen(newt_change_lit, newt_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+cor_trends_by_gen(snake_change_lit, snake_change_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
 ```
@@
 
-# for(i in 1:length(unique(newt_change_lit$rep))){
-#   myine<-whale_gen(newt_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(newt_change_lit$rep)[i])
+# for(i in 1:length(unique(snake_change_lit$rep))){
+#   myine<-whale_gen(snake_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(snake_change_lit$rep)[i])
 #   plot(myine)
@@
 # }
-whale_gen(newt_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(newt_change_lit$rep)[1])
+whale_gen(snake_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(snake_change_lit$rep)[1])
 ```
@@
 
-# for(i in 1:length(unique(newt_change_lit$rep))){
-#   myine<-two_hist(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(newt_change_lit$rep)[i] )
+# for(i in 1:length(unique(snake_change_lit$rep))){
+#   myine<-two_hist(snake_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(snake_change_lit$rep)[i] )
 #   suppressMessages(plot(myine))
@@
 
-two_hist(newt_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(newt_change_lit$rep)[1] )
+two_hist(snake_change_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(snake_change_lit$rep)[1] )
 
@@
 max_gen=5000
-GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(snake_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(snake_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(snake_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
@@
 
-GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(snake_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 ```
@@
 
-GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(snake_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 max_gen=50000
-GA_summary(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(snake_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 
-GA_summary_by_species(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(snake_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
 
@@
 
-GA_summary_by_species(newt_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+GA_summary_by_species(snake_change_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
 
@@
 #heatmap
-build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(snake_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 ```
@@
 #heatmap
-build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(snake_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
@@
 max_gen=5000
-build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(snake_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(snake_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(newt_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(snake_change_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 require(readr)
-newt_change_grid<- read.csv("~/Desktop/newt_change/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
-newt_change_grid$group_rep <- paste0(newt_change_grid$snake_mu_rate, "_", newt_change_grid$snake_mu_effect_sd,"_",newt_change_grid$newt_mu_rate, "_", newt_change_grid$newt_mu_effect_sd, "_", newt_change_grid$rep)
-newt_change_grid$group <- paste0(newt_change_grid$snake_mu_rate, "_", newt_change_grid$snake_mu_effect_sd,"_",newt_change_grid$newt_mu_rate, "_", newt_change_grid$newt_mu_effect_sd)
-newt_change_grid$sim=LETTERS[factor(newt_change_grid$group)]
-newt_change_grid$grid_num = 5
+snake_change_grid<- read.csv("~/Desktop/snake_change/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+snake_change_grid$group_rep <- paste0(snake_change_grid$snake_mu_rate, "_", snake_change_grid$snake_mu_effect_sd,"_",snake_change_grid$newt_mu_rate, "_", snake_change_grid$newt_mu_effect_sd, "_", snake_change_grid$rep)
+snake_change_grid$group <- paste0(snake_change_grid$snake_mu_rate, "_", snake_change_grid$snake_mu_effect_sd,"_",snake_change_grid$newt_mu_rate, "_", snake_change_grid$newt_mu_effect_sd)
+snake_change_grid$sim=LETTERS[factor(snake_change_grid$group)]
+snake_change_grid$grid_num = 5
 
@@
 
-file=newt_change_grid
+file=snake_change_grid
 file_name="1e-11_5_1e-10_0.5_0"
@@
 require(readr)
-newt_change_grid<- read.csv("~/Desktop/newt_change/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
-newt_change_grid$group_rep <- paste0(newt_change_grid$snake_mu_rate, "_", newt_change_grid$snake_mu_effect_sd,"_",newt_change_grid$newt_mu_rate, "_", newt_change_grid$newt_mu_effect_sd, "_", newt_change_grid$rep)
-newt_change_grid$group <- paste0(newt_change_grid$snake_mu_rate, "_", newt_change_grid$snake_mu_effect_sd,"_",newt_change_grid$newt_mu_rate, "_", newt_change_grid$newt_mu_effect_sd)
-newt_change_grid$sim=LETTERS[factor(newt_change_grid$group)]
-newt_change_grid$grid_num = 5
+snake_change_grid<- read.csv("~/Desktop/snake_change/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
+snake_change_grid$group_rep <- paste0(snake_change_grid$snake_mu_rate, "_", snake_change_grid$snake_mu_effect_sd,"_",snake_change_grid$newt_mu_rate, "_", snake_change_grid$newt_mu_effect_sd, "_", snake_change_grid$rep)
+snake_change_grid$group <- paste0(snake_change_grid$snake_mu_rate, "_", snake_change_grid$snake_mu_effect_sd,"_",snake_change_grid$newt_mu_rate, "_", snake_change_grid$newt_mu_effect_sd)
+snake_change_grid$sim=LETTERS[factor(snake_change_grid$group)]
+snake_change_grid$grid_num = 5
 

### 2022-11-08 graphs_newt_snakes/grid_test.Rmd
I did the write up for how different grid sizes can influence the cor and grid results

@@
 Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to.
-This markdown is investigation what is up with the different levels of correlation between rectangles and squares (in connection with GA1 tall).
+This markdown is investigation what is up with the different levels of correlation between different sizes of rectangles (in connection with GA1 tall).
 After fixing the row vs column error I looked at the correlation data and found that there was less correlation.
-So I decided to investigate why that might be and run a few more experiments.
-I am running an experiment to test how changing the square size might impact the calculations.
-I also plan on changing the interaction rate (but want to look at the math/ feasibility of it).
+To investigate why the correlation changed, I ran a few more experiments, testing how changing the area of local adaptation (the square size) might impact the spatial phenotype correlation calculations.
 This file contains results discussed in Tall_GA1!
 
+Future experiment: Changing the interaction rate.
+
 ### Questions:
 
-How does grid size impact the spatial correlation of newt and snake phenotypes?
-
-## Background
+How does grid size (area of local adaption) impact the spatial correlation of newt and snake phenotypes?
+
+Prediction: There would be an optimum size of a grid, that captured a good amount of information.
+For example, a grid that was too large would contain to much information that was averaged over.
+A grid that was too small would not have enough individuals to make a meaningful calculation.
 
@@
 
-I tested grid sizes for my tall landscape:
+I tested grid sizes for my tall landscape (all grids were square shaped):
 
@@
 
-Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.
-
-### The data
-
-## Preping the data by making singular files
+## The data
+
+I ran 4 trials per GA combination.
+Each simulation collected whole population information, phenotype and population spatial correlations and local (grid) information.
+There are different spatial correlation and grid calculations for the different grid sizes (2-7).
+Each of these cancellations were done within a signal simulation so that comparison between grid sizes would be simplified.
+Each GA combination and trial has its own msprime simulation.
 
@@
 
-## Loading in/ Combining the files to compare different grid sizes
+## Phenotype differences
+This section examines how the whole population mean newt and snake phenotype changes over time.
+Red line represents the newts mean phenotype, while the blue line snake the snakes mean phenotype.
+The black line is the difference between snake ans newt mean phenotype.
+Newt and snake genetic architectures (GAs) are the same down the diagonal (top right to bottom left).
+As we move across the columns newt GA increases in mutational variance.
+As we move down the rows the mutational variance of snake GA increases.
+There are four simulations shown in each of theses figures.
 
@@
 newt$info <- "middle"
-newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
-
-newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-(row_num-2)), row_num), seq((row_num-1+row_num), (col_num*row_num-1-(row_num-row_num)), row_num),  c((col_num*row_num-row_num):(col_num*row_num-2)))]<- "edge"
+newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-1-row_num, col_num*row_num-1)] <- "corner"
 
@@
 
-generations
 ```{r, graphing by gen}
@@
 ```
+
+The mean phenotype of newts and snakes follow similar patterns under the specific genetic architecture combinations (blue and red lines in each fig follow similar paths).
+In most cases it seems that the mean newt and snake phenotype increases over time.
+Most of the simulations reach a steady mean phenotype by 30,000 generations.
+When the mutational variance is low (first row for snakes and first column for newts) convolution does not see to be occurring.
+The mean phenotypes of newts and snakes are not symmetrical across the diagonal.
+This could indicate that there are different selection pressures for the newts and snakes.
+
+## Connection between higher phenotype and population (5 sec)
+
+In some of my previous experiments there is a link between population size and average phenotype differences (snake - newt mean phenotype).
+When the snake population size was large the snakes had a higher phenotype.
+When newts had a larger phenotype, newts also had a larger population size.
+I present this plot again to confirm that it is still occurring (nothing unusual seen here).
 
@@
 
+## Correlation {.tabset}
+The next section examines the spatial correlation of the local mean phenotypes of snakes and newts.
+We predicted that in areas where newts phenotypes were large snakes phenotype would also be large.
+In areas where newt phenotype was small we predicted that snake phenotype would also be small.
+The prediction would result in a strong positive spatial correlation between newt and snake local phenotypes.
+I first present the spatial phenotype correlation for the entire simulation.
+The dashed line in the empirical newt-snake spatial correlation result.
+Each box plot represents one simulation trial.
+Trial 0 is the simulation that ran to 10,000 generations and trial 1 is the simulation that ran to 30,000 generations.
+(I ran things longer to see if the spatial phenotype correlation would improve with time).
+
+### 2 Grid
 ```{r, combo myplots}
@@
 thecolors=c("#F8766D", "#B79F00", "#00BA38", "#00BFC4", "#619CFF", "#F564E3")
-
 boxplot_cors_by_gen(GA1_cor_grid_2_file, "Grid 2: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[1])
-
+```
+
+### 3 Grid
+```{r, combo myplots 3}
 boxplot_cors_by_gen(GA1_cor_grid_3_file, "Grid 3: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[2])
-
+```
+
+### 4 Grid
+```{r, combo myplots 4}
 boxplot_cors_by_gen(GA1_cor_grid_4_file, "Grid 4: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[3])
-
+```
+
+### 5 Grid
+```{r, combo myplots5}
 boxplot_cors_by_gen(GA1_cor_grid_5_file, "Grid 5: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[4])
-
+```
+
+### 6 Grid
+```{r, combo myplots 6}
 boxplot_cors_by_gen(GA1_cor_grid_6_file, "Grid 6: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[5])
-
+```
+
+### 7 Grid
+```{r, combo myplots 7}
 boxplot_cors_by_gen(GA1_cor_grid_7_file, "Grid 7: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[6])
-
-#four_types_boxplot_cors_by_gen(all_cor_grid, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-```
-
-## Correlation Histograms  {.tabset}
-
-In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
-Each color is a different trial per GA combination.
-The histogram values are stacked.
-This section only looks at the 5 sections.
+```
+
+## {-}
+
+It is difficult to tell what is happening as I decrease the size of the grids, but I think that some of the spatial correlations are getting closer to zero (less positive and less negative).
+
+## Correlation In Time Chunks  {.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at the correlation values for all four trials.
+Each color is a different grid size and contains information from all four trials.
 
@@
 
+From this figure set, is clear to see that the smaller the grid size the less variance across simulations and the closer the result is to 0.
+Oddly, there seems to be some arc patterns when the GA has minimal variance (first row and first column).
+This section leads me to conclude that grid sizes 2 and 3 are too large and grid sizes 6 and 7 are too small.
+
 ## Phenotype Correlation across time {.tabset}
 
-Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment.
+Next, we will examine three randomly chosen plots from this experiment.
 Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
 Newt whole population mean phenotype is red, while snake mean phenotype is blue.
-The pink line is the phenotype spatial correlation.
-
-### Random 1 (5 sec)
+The different color lines are the phenotype spatial correlation colored by grid size.
+Color from largest grid to smallest grid: red, yellow, green, light blue, dark blue, and pink.
+
+### Random 1 
 ```{r, GA1 cor and pheno}
@@
 
-### Random 2 (5 sec)
+### Random 2 
 ```{r, random cor-pheno plot 2}
@@
 
-### Random 3 (5 sec)
+### Random 3 
 ```{r, random cor-pheno plot 3}
@@
 
+Mean newt and snake phenotypes can either go up, go down, or stay constant near zero.
+Sometimes the mean phenotypes go down together, other times they both go up.
+Occasionally, one species phenotype goes up while the other species phenotype stays constant.
+In all of these cases the spatial correlation is the most extreme when the grid size is large and close to 0 when the grid size is small.
+
 ## Population Size Correlation across time {.tabset}
+
+Next, we will examine the population sized of the three randomly chosen simulations (same simulations from above).
+Time (in generations) in on the x-axis and both mean population size and population size spatial correlation in on the y-axis.
+Newt population size is red, while snake phenotype size is blue.
+The different color lines are the popualtion size spatial correlation colored by grid size.
+Color from largest grid to smallest grid: red, yellow, green, light blue, dark blue, and pink.
 
@@
 ## {-}
+
+Newt and snake population size intentionally goes up, then can stay constant or increase/decrease with time.
+In all of these cases the spatial correlation is the most extreme when the grid size is large and closer to 0 when the grid size is small.
+The correlation between newt and snake population size is always positive.
+Its gets smaller as the number of grids increases (grid size gets smaller) due to the way slim is not taking the smaller edge/corner areas when calculating the correlation (easy to see in the grid figs).
 
@@
 
+In this last section I show the local mean phenotype and population size of newts (circles) and snakes (square) for the different grid sizes.
+In the mean phenotype plot, the more resistant or toxic a snake or newt is the more yellow the square or circle.
+In the population size plot, the larger a local population is the more bright/yellow the circle or square is.
+There is a small sub plot showing the individual newt and snake values (phenotype or population size) colored by location in the artificial map.
+
+Overall: As the number of grids increase the spatial correlation (both phenotype and population size) gets closer to zero.
+I do not understand why there is no positive phenotype correlation in these plots and I also do not entirely understand why the correlation gets closer to zero.
+I do understand why the correlation gets smaller in the population grid plots, it is due to the edge calculations (seen in the sub plots).
+
 ### 2 
@@
 ```
+
+## {-}
+
+## {.tabset}
 

### 2022-11-15 graphs_newt_snakes/corcompare.Rmd
Looked at more data and added maps to my slim script! Need to fix corcompare to look nicer and spend a lot of time writing about all of these new results.
I finished the write up for cor compare

--- 2022-09-29 graphs_newt_snakes/corcompare.Rmd
@@
 ---
-title: "Cor Compare"
+title: "Corilation Compare!"
 output: html_document
@@
 
-## Corilation Compare!
+## Background
 
-I have run four separate experiments and now I will compare their different correlations to see if I can tell the difference between each of the four experiments.
+I have run four separate experiments and now I will compare their different phenotype spatial correlations to see if I can tell the difference between each of the four experiments.
 
@@
 
-I am investigating the correlation calculations.
+I am investigating the spatial phenotype correlation calculations.
 I predicted that though co-evolution (interaction & evolution) species' phenotypes would become spatially correlated.
@@
 
--  5 sections & 7 sections will have *similar* correlation distributions
-- no heritability & no interaction correlation distributions will look *very different* from 5 sections & 7 sections
+-  5 sections & 7 sections will have **similar** correlation distributions
+- no heritability & no interaction correlation distributions will look **very different** from 5 sections & 7 sections
 
@@
 
+First, I will try comparing the mean spatial correlations between the different experiments.
+Now within these four experiments, there are 16 GA combinations, which can have an effect on spatial phenotype correlation.
+Because each of these experiments contain the same GA combinations and the same amount of trials, it should be okay to compare them.
+
+Note: Some of the simulations had fewer data points (data collected every 20 generations instead of 10).
+To account for fewer data points in some of the simulations, I cut about half of the data (everything had matching generations).
+
+Here are the mean spatial phenotype correlation values:
+
 ```{r, looking at the mean}
@@
   summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)
+```
+
+I ran some anovas to compare the spatial correlations between the different experiments.
+First, I got one mean per GA combination.
+So all four trials were combined to create one spatial correlation mean.
+
+```{r, mean anovas}
+#print("One mean per GA")
 
@@
 
+exclude_a <- all_the_means[which(all_the_means$exp!='A'),]
 exclude_b <- all_the_means[which(all_the_means$exp!='B'),]
@@
 
-print("Anovas from mean of A and B")
+#print("Anovas from mean of A and B")
 res.aov2ab <- aov(name ~ exp, data = exclude_c[which(exclude_c$exp!='D'),])
-summary(res.aov2ab)
-print("Anovas from mean of A and C")
+MYaov2ab = unlist(summary(res.aov2ab))
+print(paste0("Anovas from mean of A and B, F value: ", MYaov2ab[7], " Pr(>F) value: ",MYaov2ab[9]))
+
+#print("Anovas from mean of A and C")
 res.aov2ac <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='D'),])
-summary(res.aov2ac)
-print("Anovas from mean of A and D")
+MYaov2ac <- unlist(summary(res.aov2ac))
+print(paste0("Anovas from mean of A and C, F value: ", MYaov2ac[7], " Pr(>F) value: ",MYaov2ac[9]))
+
+#print("Anovas from mean of B and C")
+res.aov2bc <- aov(name ~ exp, data = exclude_a[which(exclude_a$exp!='D'),])
+MYaov2bc <- unlist(summary(res.aov2bc))
+print(paste0("Anovas from mean of B and C, F value: ", MYaov2bc[7], " Pr(>F) value: ",MYaov2bc[9]))
+
+#print("Anovas from mean of A and D")
 res.aov2ad <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='C'),])
-summary(res.aov2ad)
-print("Anovas from mean of C and D")
+MYaov2ad <- unlist(summary(res.aov2ad))
+print(paste0("Anovas from mean of A and D, F value: ", MYaov2ad[7], " Pr(>F) value: ",MYaov2ad[9]))
+
+#print("Anovas from mean of B and D")
+res.aov2bd <- aov(name ~ exp, data = exclude_a[which(exclude_a$exp!='C'),])
+MYaov2bd <- unlist(summary(res.aov2bd))
+print(paste0("Anovas from mean of B and D, F value: ", MYaov2bd[7], " Pr(>F) value: ",MYaov2bd[9]))
+
+#print("Anovas from mean of C and D")
 res.aov2cd <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='A'),])
-summary(res.aov2cd)
+MYaov2cd <- unlist(summary(res.aov2cd))
+print(paste0("Anovas from mean of C and D, F value: ", MYaov2cd[7], " Pr(>F) value: ",MYaov2cd[9]))
 ```
 
-I want to compare the different cor values from the simulations, but i also want to look at it simulation by simulation.
+I ran some more anovas to compare the spatial correlations between the different experiments.
+This time there is one mean per GA combination trial.
+So all four trials have their own spatial correlation mean.
 
+```{r, second anavo one mean per rep}
+#print("One mean per rep")
+
+all_the_means_byrep = all_cor_exp %>%
+  group_by(group_exp_rep) %>%
+  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)
+
+all_the_means_byrep$exp <- str_split_fixed(all_the_means_byrep$group_exp_rep, "_", 6)[,5]
+
+exclude_a <- all_the_means_byrep[which(all_the_means_byrep$exp!='A'),]
+exclude_b <- all_the_means_byrep[which(all_the_means_byrep$exp!='B'),]
+exclude_c <- all_the_means_byrep[which(all_the_means_byrep$exp!='C'),]
+
+#print("Anovas from mean of A and B")
+res.aov2ab <- aov(name ~ exp, data = exclude_c[which(exclude_c$exp!='D'),])
+MYaov2ab <- unlist(summary(res.aov2ab))
+print(paste0("Anovas from mean of A and B, F value: ", MYaov2ab[7], " Pr(>F) value: ",MYaov2ab[9]))
+
+#print("Anovas from mean of A and C")
+res.aov2ac <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='D'),])
+MYaov2ac <- unlist(summary(res.aov2ac))
+print(paste0("Anovas from mean of A and C, F value: ", MYaov2ac[7], " Pr(>F) value: ",MYaov2ac[9]))
+
+#print("Anovas from mean of B and C")
+res.aov2bc <- aov(name ~ exp, data = exclude_a[which(exclude_a$exp!='D'),])
+MYaov2bc <- unlist(summary(res.aov2bc))
+print(paste0("Anovas from mean of B and C, F value: ", MYaov2bc[7], " Pr(>F) value: ",MYaov2bc[9]))
+
+#print("Anovas from mean of A and D")
+res.aov2ad <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='C'),])
+MYaov2ad <- unlist(summary(res.aov2ad))
+print(paste0("Anovas from mean of A and D, F value: ", MYaov2ad[7], " Pr(>F) value: ",MYaov2ad[9]))
+
+#print("Anovas from mean of B and D")
+res.aov2bd <- aov(name ~ exp, data = exclude_a[which(exclude_a$exp!='C'),])
+MYaov2bd <- unlist(summary(res.aov2bd))
+print(paste0("Anovas from mean of B and D, F value: ", MYaov2bd[7], " Pr(>F) value: ",MYaov2bd[9]))
+
+#print("Anovas from mean of C and D")
+res.aov2cd <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='A'),])
+MYaov2cd <- unlist(summary(res.aov2cd))
+print(paste0("Anovas from mean of C and D, F value: ", MYaov2cd[7], " Pr(>F) value: ",MYaov2cd[9]))
+```
+
+Instead on taking the mean spatial correlation, I wanted to compare the series of correlation values from the each of my GA combinations.
 I think trials within a simulation experiment (A, B, C, D) should be the same (same mu and mu effect size).
-
-They should also be different between different GA combinations
-
-same GA should be different in the different experiments
+The spatial correlation might be different between different GA combinations within an experiment (A, B, C, D), but different between these experiments.
+Its a bit difficult to split my data up to make these comparisons, but I did run some wilcoxon tests and t-tests.
+Most everything was significantly different (only tested between experiments) in the wilcoxon test.
+In the Two Sample t-test when compering experiments AC, AD, BC, BD were different, but CD was not different.
+The Two Sample t-test between AB as only slightly different p-value = 0.02601.
 
@@
 
-wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB
-
-wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC
-
-wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD
-
-wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC
-
-wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD
-
-wilcox.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD
+# wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB
+# 
+# wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC
+# 
+# wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD
+# 
+# wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC
+# 
+# wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD
+# 
+# wilcox.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD
 
@@
 #t.test(GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep <= 1,]$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep >= 2,]$mean_newt_pheno_By_mean_snake_pheno) #AA
-
-t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC
-
-t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD
-
-t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC
-
-t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD
-
-t.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD
-
-t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB
+# 
+# t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC
+# 
+# t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD
+# 
+# t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC
+# 
+# t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD
+# 
+# t.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD
+# 
+# 
+# t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB
 
@@
 
-```{r, distribuuution plots, fig.height = 11, fig.width = 5}
+## Distribution Plot
+
+In this section I examine the distribution of spatial phenotype correlation between each of the four experiments by genetic architecture (GA) combination.
+In this figure there are 4 trials per GA combination and experiment.
+There are sixteen GA combinations and four experiments (red = tall map 5 sections, green = tall map 7 sections, blue = no heritability, purple = no interaction).
+The labels on the right are the GA combinations.
+
+```{r, distribuuution plots, fig.height = 11, fig.width = 8}
+
+max_gen=5000
+min_gen=100
 
@@
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
+                      strip.text.y = element_text(angle = 45, size = 6),
                     strip.background = element_blank(), strip.text.x = element_blank(),
-                   title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                   title =element_text(size=4, face='bold'), axis.title.x = element_blank(),
                     axis.title.y = element_blank())
 ```
+
+This plot is not the easiest to read.
+However, after staring at if for awhile I noticed that the no heritability experiment did not change between GA combos.
+Red (tall map 5 sections), green (tall map 7 sections), and purple (no interaction) look very similar for some of the GA combinations, but differ in GA combinations where the mutational variance in both the newts and snakes was high.
+I thought the distributions between A and B would be more similar.
+The mean of experiment B results seems to be similar to experiment A, but the distribution seems a bit more narrow.
+It is very difficult to tell if things are truly similar or different.
+
+## Whole Distribution Plot
+
+In this section I combine all of the trails and GA combinations to see if the spatial correlation distribution differs overall between the experiments.
+Here red is the tall map 5 sections, green is the tall map 7 sections, blue is the experiment that has no heritability, and purple there is no interaction.
 
@@
 
-```{r, cor com figs}
+There are some very noticeable differences between the four experiments.
+One the mean of experiment A and B (tall map 5 sections & tall map 7 sections) are very similar, both are positive.
+Experiment B is narrower than experiment A.
+Experiment C is a perfect histogram with a mean at 0.
+Experiment D has a similar width to experiment A, but the mean is closer to 0.
+
+## Spatial Correlation Over Time {.tabset}
+
+In this sections I will walk through the spatial phenotype correlates of all 4 experiments in 5,000 generation chunks.
+The color represents the experiment (red = tall map 5 sections, green = tall map 7 sections, blue = no heritability, purple = no interaction).
+One type of plot is a general histogram an the other is a density plot.
+They are not stacked.
+The goal of these plots is to see how spatial correlation changes as time increases.
+The dashed line is the real newt and snake spatial phenotype correlation.
+
+### Section 1
+```{r, cor com figs 1}
 
@@
 
+```
+
+### Section 2
+```{r, cor com figs 2}
+
 ginmin = 5000
@@
 suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 3
+```{r, cor com figs 3}
 ginmin = 10000
@@
 suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 4
+```{r, cor com figs 4}
 ginmin = 15000
@@
 suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 5
+```{r, cor com figs 5}
 ginmin = 20000
@@
 suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 6
+```{r, cor com figs 6}
 ginmin = 25000
@@
 suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 7
+```{r, cor com figs 7}
 ginmin = 30000
@@
 suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 8
+```{r, cor com figs 8}
 ginmin = 35000
@@
 suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 9
+```{r, cor com figs 9}
 ginmin = 40000
@@
 suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 10
+```{r, cor com figs 10}
 ginmin = 45000
@@
 
-```{r, density com figs}
+## {-}
+
+## {.tabset}
+
+### Section 1
+```{r, density com figs 1}
 
@@
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 2
+```{r, density com figs 2}
 ginmin = 5000
@@
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 3
+```{r, density com figs 3}
 ginmin = 10000
@@
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 4
+```{r, density com figs 4}
 ginmin = 15000
@@
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 5
+```{r, density com figs 5}
 ginmin = 20000
@@
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 6
+```{r, density com figs 6}
 ginmin = 25000
@@
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 7
+```{r, density com figs 7}
 ginmin = 30000
@@
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 8
+```{r, density com figs 8}
 ginmin = 35000
@@
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 9
+```{r, density com figs 9}
 ginmin = 40000
@@
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Section 10
+```{r, density com figs 10}
 ginmin = 45000
@@
 
+## {-}
+
+There are a few points of interest to note in these spatial correlation results.
+First, the no heritability distribution always remains the same (regardless of GA combination or time).
+When the GA combination has higher mutational variance there is less of a range in the possible spatial correlations, especially when there is no interaction.
+The spatial correlations in these simulations do not consistently reach the high levels of spatial correlation seen in the real newt and snake population.
+Experiment D seems to either be more variable in spatial correlation (more spread out, different in different simulation trial) or centered to the just to the left of zero (cor is negative).
+I think that there is a lot of noise and over lap.
+From these spatial correlation values I cannot immediately see the difference in all of the GA combinations (there is not one rule I would use to define all of these results).
+
+## Whole Correlation by GA Combinations {.tabset}
+
+This section will focus on the showing the spatial correlation for the whole simulation separated by GA combination.
+The goal is to see if the overall spatial correlation simulation results differ between experiments.
+Dashed line is the real newt and snake phenotype correlation value.
+Colors: red = tall map 5 sections, green = tall map 7 sections, blue = no heritability, purple = no interaction
+
+### Hist
 ```{r, one big one}
@@
 suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+```
 
+### Density
+```{r, one big one density}
+ginmin = 0
+ginmax = 50000
 suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
@@
 
-# next step is to count the high and the lows 
-like make a lower limit like must be above 0.3
+ Again, no heritability stands out as unchanging.
+At GA combinations where there is low variation red (tall map 5 sections), green (tall map 7 sections), and purple (no interaction) look ver similar.
+At the genetic variation in one of the species increases, the spatial correlation in no interaction simulation becomes more negative.
 
-```{r, thresholds}
+## {-}
+
+##  The Highs and the Lows {.tabset}
+
+This section examines the amount of data points that reach and exceed an arbitrary limit.
+For example, I pick a limit of 0.3, and I would like to count the amount of spatial correlation points are above 0.3 or below -0.3.
+I can also look at just the positive or negative correlations.
+The goal of this section is to see how the different experiments (A, B, C, D) vary in the edges of the spatial correlation.
+
+### Positive 0.3
+
+```{r, thresholds 1}
 
@@
 counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
+
+### Negative 0.3
+
+```{r, thresholds 1a}
+
+file = all_cor_exp
+treshold = 0.3
+p_n_b = "n"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
+
+### Both 0.3 
+```{r, thresholds 2}
 
@@
 counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
 
+### Positive 0.5
+
+```{r, thresholds 2b}
+
+file = all_cor_exp
+treshold = 0.5
+p_n_b = "p"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
+
+### Negative 0.5
+
+```{r, thresholds 2a}
+
+file = all_cor_exp
+treshold = 0.5
+p_n_b = "n"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
+
+### Both 0.5 
+```{r, thresholds 3}
 file = all_cor_exp
@@
 counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
 
+### Positive 0.7
+
+```{r, thresholds 3b}
+
+file = all_cor_exp
+treshold = 0.7
+p_n_b = "p"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
+
+### Negative 0.7
+
+```{r, thresholds 3a}
+
+file = all_cor_exp
+treshold = 0.7
+p_n_b = "n"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
+
+### Both 0.7 
+```{r, thresholds 4}
 file = all_cor_exp
@@
 
+```
+
+### Positive 0.9
+
+```{r, thresholds 5b}
+
 file = all_cor_exp
-treshold = 0.7
+treshold = 0.9
+p_n_b = "p"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
+
+### Negative 0.9
+
+```{r, thresholds 5a}
+
+file = all_cor_exp
+treshold = 0.9
+p_n_b = "n"
+min_gen = 100
+max_gen =50000
+whichgroup = "experiment"
+
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
+```
+
+### Both 0.9 
+```{r, thresholds 5}
+file = all_cor_exp
+treshold = 0.9
 p_n_b = "b"
@@
 whichgroup = "experiment"
+counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
 ```
+## {-}
 
+From this analysis of generations 100 to 50,000 I can see that no heritability (experiment C) has very few high spatial correlation measurements.
+The tall map 7 sections (experiment B) also has fewer high correlation measurements.
+Both tall map 5 sections and no interaction (A and D) have similar high correlation measurements.
+When the limit is low (0.3) there is more negative correlations in experiment D.
+But when the limit gets higher the amount of positive correlations in experiment D becomes a lot larger than the amount of negative correlation values.
+There are more negative correlation in experiment A when the limit is high.
+If I just look at the last 5,000 generations I see a similar pattern.
+
+## Multi Plots {.tabset}
+
+In this section I am testing out the ggplot multi plot function (ggslide).
+It adds side plot on the side or top.
+So I decided to look at the distribution of correlation values in both a density and a boxplot.
+I also attempted to graph the phenotype spatial correlation and population spatial correlation through out time.
+These plots contain all data points from all GA combinations and trials.
+
+### phenotype spatial correlation distribution
 ```{r, ggslide test}
+
+# ggplot(all_cor_exp) + 
+#   #geom_point(size = 2) +
+#   #geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=rep))+
+#   geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity")+
+#   #geom_xsidehistogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity") +
+#   geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
+#   scale_ysidex_discrete(guide = guide_axis(angle = 45))
 
@@
   #geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=rep))+
-  geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity")+
+  geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)*3,fill=factor(experiment)), alpha=0.4, position="identity")+
   #geom_xsidehistogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity") +
+  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
+  scale_ysidex_discrete(guide = guide_axis(angle = 45)) 
+```
+
+### phenotype | population spatial correlation through time 
+```{r ggslide 3 plots}
+#all_cor_exp$num_newts_By_num_snakes
+ggplot(all_cor_exp) + 
+  #geom_point(size = 2) +
+  geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
+  #geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)*3,fill=factor(experiment)), alpha=0.4, position="identity")+
+    geom_xsideline(aes(generation, num_newts_By_num_snakes, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
   geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
@@
 ```
+
+## {-}
+
+The findings from this figure highlights that experiment A and B have a positive phenotype spatial correlation.
+In the experiments with no heritability and no interaction, the mean spatial phenotype correlation is zero or negative.
+The second figure shows that time doesn't have a strong association with a particular spatial correlation value.
+There is a problem with the population size spatial correlation in experiment C and D.
+The correlation should be more negative, but I switched the slim function to not account for the smaller areas (which is wrong) and had a huge effect on the correlation measurement.
+I imagine if I reran this experiment the no heritability and no interaction simulation would have the same population size spatial correlation as A and B (since the interaction is density dependent even though the way they interact is random).
+
+## Overall Thoughts
+
+My over all thought about the spatial phenotype correlation values is that they are not doing what I expect.
+There seems to be something missing in my simulation preventing a strong positive phenotype spatial correlation.
+My next experiments will look at how the cost function and interaction rate.
+I wonder if changing these will have an impact on my simulation.

### 2022-11-15 graphs_newt_snakes/dif_cost.Rmd
I am preping for the cost gradiant results
I am making improvements to the cost dif file, like including more legends

@@
 Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to.
-This markdown is investigation what is up with the different levels of correlation between rectangles and squares (in connection with GA1 tall).
-After fixing the row vs column error I looked at the correlation data and found that there was less correlation.
-So I decided to investigate why that might be and run a few more experiments.
-I am running an experiment to test how changing the square size might impact the calculations.
+This markdown is investigation what is up with the different levels of phenotype spatial correlation values.
+I am running an experiment to test how changing the cost of a phenotype might impact these calculations.
 I also plan on changing the interaction rate (but want to look at the math/ feasibility of it).
-This file contains results discussed in Tall_GA1!
 
@@
 
-## Background
-
 ## Experiment
@@
 I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction with different genetic architectures (GAs) in a spatial setting.
-I hypothesized that we would see an interaction (co-evolutionary arms race) between newt and snake phenotype under some GA combinations when newts and snakes were evolving over geographical space.
-Each GA is paired with another GA creating 16 combinations.
+
+Landscape: A tall map!: 35*4 H, 35 W
 
@@
 - 1e-11*(5.0)^2 = 2.5e-10
-
-Landscape: A tall map!: 35*4 H, 35 W
 
@@
 
-Each GA combination, trial, and cost has its own msprime simulation.
-
-### The data
-
-## Preping the data by making singular files
+The higher a cost value the less impacting on the phenotype it is.
+
+Each GA combination, trial, and cost has its own msprime simulation. There is only 1 trial per cost value.
 
@@
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+ last_point=file[ which(file$generation==max(file$generation) & file$snake_newt_rep==pattern),]
+
   cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
@@
     geom_line(aes(generation, Newt_mean_Pheno, group=cost, color="Newt_mean_Pheno"))+
+    geom_point(data=last_point, aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno", shape=factor(cost)))+
+
+    geom_point(data=last_point, aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno", shape=factor(cost)))+ 
     #ylim(0,10)+
@@
 values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
-labels = c("Snake", "Newt"))+
-    theme_bw() +theme(legend.position="none",
+labels = c("Snake", "Newt"),
+guide = "none")+
+    theme_bw() +theme(legend.position="right",
+                      legend.title=element_text(size=7), 
+                      legend.text=element_text(size=6),
                       strip.background = element_blank(), strip.text.x = element_blank(),
@@
     #xlab(x_label_cor) + ylab(y_label)+
-    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right",
+                      legend.title=element_text(size=7), 
+                      legend.text=element_text(size=6),
                       strip.background = element_blank(), strip.text.x = element_blank(),
@@
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
+  last_point=file[ which(file$generation==max(file$generation) & file$snake_newt_rep==pattern),]
+
   cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
@@
     geom_line(aes(generation, Newt_pop_size, group=cost, color="Newt"))+
+    geom_point(data=last_point, aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno", shape=factor(cost)))+
+
+    geom_point(data=last_point, aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno", shape=factor(cost)))+
     #ylim(0,10)+
@@
 values = c( "Snake" = "steelblue", "Newt" = "darkred"),
-labels = c("Snake", "Newt"))+
-    theme_bw() +theme(legend.position="none",
+labels = c("Snake", "Newt"),
+guide = "none")+
+    theme_bw() +theme(legend.position="right",
+                      legend.title=element_text(size=7), 
+                      legend.text=element_text(size=6),
                       strip.background = element_blank(), strip.text.x = element_blank(),
@@
  file$Newt_mean_Pheno<-as.numeric(file$Newt_mean_Pheno)
+ last_point=file[ which(file$generation==max(file$generation)),]
   plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
@@
     geom_line(aes(generation, as.numeric(dif), group=cost, col="dif"))+
+    geom_point(data=last_point, aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno", shape=factor(cost)))+ #, shape=cost, col="dif"
+
+    geom_point(data=last_point, aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno", shape=factor(cost)))+ #, shape=cost, col="dif"
     #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
@@
 labels = c("Snake", "Newt", "Dif"))+
-    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right",
                       strip.background = element_blank(), strip.text.x = element_blank(),
@@
 
-generations
+## Mean Newt and Snke Phenotype by Generation
 
@@
 
-##Grid {.tabset}
+##Grid
 

### 2022-11-15 graphs_newt_snakes/dif_cost.Rmd
fixed the graph points

@@
     geom_line(aes(generation, Newt_pop_size, group=cost, color="Newt"))+
-    geom_point(data=last_point, aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno", shape=factor(cost)))+
-
-    geom_point(data=last_point, aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno", shape=factor(cost)))+
+    geom_point(data=last_point, aes(generation, Snake_pop_size, color="Snake", shape=factor(cost)))+
+
+    geom_point(data=last_point, aes(generation, Newt_pop_size, color="Newt", shape=factor(cost)))+
     #ylim(0,10)+

### 2022-11-21 graphs_newt_snakes/dif_cost.Rmd
I have added my explination for the different cost values

@@
 
-Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to.
-This markdown is investigation what is up with the different levels of phenotype spatial correlation values.
-I am running an experiment to test how changing the cost of a phenotype might impact these calculations.
+Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) under different cost settings.
+This markdown investigates the phenotype spatial correlation as the cost of a high phenotype changes (for both newts and snakes).
 I also plan on changing the interaction rate (but want to look at the math/ feasibility of it).
@@
 
-GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label, cost){
+GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
 
@@
 
-params<-create_parm_file(file, min_gen, max_gen, cost)
+params<-create_parm_file_nc(file, min_gen, max_gen)
 
@@
   xlab(x_label) + ylab(y_label)+
-  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
+  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt), size=factor(cost)))+
 #  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
@@
 
- my_plot <- ggplot(params, aes(newt, paste0(cost, "_", snake, "_", rep))) +    # Create heatmap with ggplot2
+ my_plot <- ggplot(params, aes(newt, paste0(snake, "_", cost))) +    # Create heatmap with ggplot2
   ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
@@
   xlab(x_label) + ylab(y_label)+
-  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif, shape=factor(cost)))+
   #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
@@
 newt$info <- "middle"
-newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
-
-newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+#need to look into, coloring problem
+newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-1-row_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num-row_num), row_num),  c((col_num*row_num-row_num):(col_num*row_num-2)))]   <- "edge"
 
@@
 
+In this first section I look at the entire populations mean phenotype for both snakes (blue) and newts (red).
+The difference between mean snake and mean newt phenotype is shown on the black line.
+For each GA combination there are 5 sets of lines (5 red, blue, $ black).
+Each shape at the set of lines corresponds to the cost value, which 50 = circle, 100 = triangle, 150 = square, 200 = plus, and 250 = square with an x.
+The higher the cost values the less costly a high phenotype for the species is.
+The cost values range from 50 (more costly) to 250 (less costly).
+
 ```{r, graphing by gen}
@@
 ```
+
+The first things that I saw was how high the phenotypes got when the cost value when up.
+The phenotype seems to reach an optimum spot (an equilibrium) depending on what the cost value is for most of the GA combinations.
+For GA combinations that had one species with a low mutational variance the mean phenotype of the population did not get very high.
+It might take the simulation a bit more time to reach an equilibrium mean phenotype.
+When there is room for the phenotype to change newts and snakes mean phenotype costly follow each other.
+
+## Interaction of Population size and Phenotype
+
+Nest, I observe the interaction between the population size of newts and snakes and the mean phenotype difference (snakes-newts).
+Here, newt population size is on the x-axis while snake population size is on the y-axis.
+Blue points occur when the mean snake phenotype is higher and red points occur when the newt mean phenotype is larger.
+I added the cost values as shapes.
 
@@
 
+It seems like each cost value clusters together with some overlapping other cost values or completely different form others.
+For example when the GA combination has a high mutational variance for both newts and snakes (K, L, O, P) the cost values all overlap.
+When at least one of the species has a lower mutational variance there is more of a range in the results (different population sizes & mean phenotype).
+
+## Phenotype Spatial Correlation of 30,000 Generations
+
+Phenotype Spatial Correlation of 30,000 Generations
+
+This  section examines the spatial correlation of newts and snakes local phenotype for the different cost values.
+Each cost values has its own boxplot color.
+There are five boxplots per GA combination.
+This figure contains the correlation results for the entire length of the simulations.
+
 ```{r, combo myplots}
@@
 
-## Correlation Histograms  {.tabset}
-
-In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
-Each color is a different trial per GA combination.
-The histogram values are stacked.
-This section only looks at the 5 sections.
+There is no spatial phenotype correlation pattern between the cost value and the GA combination.
+Each of these boxplots are an identical simulation so there is some randomness between the differ cost values within the GA combination.
+The spatial phenotype correlation seems very random.
+The only GA where it might not be random is when both newts and snakes have a low mutational variance (the correlation seems to be decreasing).
+
+## Correlations in Time-slices  {.tabset}
+
+In order to understand how spatial correlations are changing with time, I took 5,000 generation time slices to look at the correlation values of all five cost values.
+Each color is a different cost value per GA combination.
 
@@
 
+The spatial phenotype correlation between newts and snakes seems to jump around between time slices.
+There is no clear direction the boxplots are moving in.
+Sometimes the correlation is negative, near zero or positive.
+The spatial correlation seems random.
+
 ## Phenotype Correlation across time {.tabset}
 
-Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment.
-Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Next, we will examine three randomly chosen GA combinations with all of the different cost values from this experiment.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis (with cost values indicated by shape and color).
 Newt whole population mean phenotype is red, while snake mean phenotype is blue.
-The pink line is the phenotype spatial correlation.
-
-### Random 1 (5 sec)
+The multi-colored lines are the phenotype spatial correlation for a specific cost value.
+
+### Random 1 
 ```{r, GA1 cor and pheno}
@@
 
+Again, the spatial correlation of newt and snake phenotypes seems very random.
+Even when both newt and snake mean phenotypes are going up the spatial correlation fluctuates from positive to negative.
+No one cost value makes the spatial correlation larger or smaller (all cost values have correlations that overlap with none having a significant greater variance).
+
 ## Population Size Correlation across time {.tabset}
+
+Next, we will examine three randomly chosen GA combinations with all of the different cost values from this experiment.
+Time (in generations) in on the x-axis and both population size and population size spatial correlation in on the y-axis (with cost values indicated by shape and color).
+Newt whole population  population size is red, while snake  population size is blue.
+The multi-colored lines are the population size spatial correlation for a specific cost value.
 
@@
 
+There might be a relationship between cost and spatial population size correlations.
+First, I would like to note that these values should be negatively correlated, but sense I did not set the per-area true the edges and corners are smaller throwing my correlation values off.
+I think that the higher the cost value the more negatively correlated the population size between newts and snakes.
+If one species has a higher phenotype there would be less of the other species.
+This would be occurring in different areas of my simulation creating a stronger negative correlation.
+Or there is something else occurring that I am not currently taking into account.
+
 ## What happens over time (looking at the beginning and late part of my simulations) {.tabset}
+
+Now, I will take a glace at the how the population size of newts and snakes as well as the mean phenotype difference between snake and newts changed between the different cost values.
+I will look at my simulation results from the beginning and end of the simulation.
+Color indicate the mean phenotype difference (blue = snakes have a higher mean phenotype, red = newts have a higher mean phenotype).
 
@@
 
+All of the beginning figures look very similar.
+The population size of newts and snakes starts out small and then grows.
+Sometimes the snake population size and mean phenotype gets larger and other times the newt population size nd mean phenotype gets larger.
+Near the end of the simulation (last 5,000 generations) there are differences between the different cost values.
+I found as you increase the cost the larger the difference in newt and snake population size becomes between the different GA combinations.
+I can see this by witnessing the clusters getting smaller, but really the x & y axis are really just getting larger.
+When the cost value was low the population sizes and the difference between mean phenotype between GA combinations were close.
+As the cost value went up, the difference between snake and newt mean phenotype increased.
+
 ## Summary {.tabset}
@@
 In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+Shape size represents the cost value (the larger the cost value the larger the shape).
 There 16 color-shape combinations (with 4 repeats for trials).
-There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
-There are three figures in each set, taken at the begging, middle, and end time chunks.
-These are whole population calculations so the 5 section and 7 section data sets are not calculated differently.
-
-### Cost: 50 Late-Sim Population Size Summary 
+There are two sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size.
+These are whole population calculations and are done for the least 5,000 generations.
+
+### Cost: Late-Sim Population Size Summary 
 ```{r, 50 plots summary 2}
@@
 max_gen=30000
-cost=50
 
 # summary
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
-```
-
-### Cost: 100 Late-Sim Population Size Summary 
-```{r, 100 plots summary 2}
-# summary
-
-min_gen=25000
-max_gen=30000
-cost=100
-
-# summary
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
-```
-
-### Cost: 150 Late-Sim Population Size Summary 
-```{r, 150 plots summary 2}
-# summary
-
-min_gen=25000
-max_gen=30000
-cost=150
-
-# summary
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
-```
-
-### Cost: 200 Late-Sim Population Size Summary 
-```{r, 200 plots summary 2}
-# summary
-
-min_gen=25000
-max_gen=30000
-cost=200
-
-# summary
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
-```
-
-### Cost: 250 Late-Sim Population Size Summary 
-```{r, 250 plots summary 2}
-# summary
-
-min_gen=25000
-max_gen=30000
-cost=250
-
-# summary
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", cost)
-```
-
-### Cost: 50 Late Difference Summary
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+```
+
+### Cost: Late Difference Summary
 ```{r, 50 dif plots summary 2}
@@
 max_gen=30000
-cost=50
-
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
-
-```
-
-### Cost: 100 Late Difference Summary
-```{r, 100 dif plots summary 2}
-min_gen=25000
-max_gen=30000
-cost=100
-
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
-
-```
-
-### Cost: 150 Late Difference Summary
-```{r, 150 dif plots summary 2}
-min_gen=25000
-max_gen=30000
-cost=150
-
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
-
-```
-
-### Cost: 200 Late Difference Summary
-```{r, 200 dif plots summary 2}
-min_gen=25000
-max_gen=30000
-cost=200
-
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
-
-```
-
-### Cost: 250 Late Difference Summary
-```{r, 250 dif plots summary 2}
-min_gen=25000
-max_gen=30000
-cost=250
-
-GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif", cost)
+
+GA_summary(GA1_lit_cost_file, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 
+There seems to be some pattern between the different GA combinations and cost values.
+Previously I noted, that there is both shape and color separation, and that intermediate GA do better (1e-09_0.05 & 1e-10_0.5) in a co-evolutionary arms race.
+Here that is still true but it is more difficult to see when I change the cost values.
+A higher cost value increases the difference in population size and phenotype difference, it exaggerates the difference.
+When the cost values and the mutational variance of at lease one of the species are high they cluster (both newts and snakes have close phenotypes and population sizes, snakes tend to always have a slightly larger population size and newts are slightly more toxic).
+If given more time, I think there would be greater separation of colors, shapes, and cost values.
+
 ## Heatmap {.tabset}
+
+In the heatmap plots each GA combination and cost is presented by combining newt GA in the x-axis to snake GA and cost value in the y-axis.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+I fist look at early and then late simulation data.
 
@@
 
-##Grid
+There is some cool population size and phenotype variation between different cost values within the same GA combination.
+The lowest cost value was always more neutral.
+As the cost value increased both the snake population size and mean phenotype diverged to either end.
+Sometimes it was not the highest cost values that resulted in the most dramatic out come.
+I saw more dramatic outcomes when the mutation variance was lower.
+My summary for this experiment is that increasing the cost value will only highlight the differences caused by the GA combinations.
+The ending results will remain the same, but may take longer to reach.
 
@@
 
+This last section looks at the local population phenotype for newts and snakes (circles and squares).
+I plot the results from generation 9981 for the GA combination 1e-10_0.5_1e-10_0.5_0.
+Color represents both toxicity and resistance.
+The sub plot is the phenotype for the newt by the phenotype for the snake, color indicates the location on the map (red=corner, green=edge, blue=middle).
+
 ### 50
@@
 file=GA1_grid_cost_file
-file_name=GA1_pattern[myrandomlist[1]]
+file_name="1e-10_0.5_1e-10_0.5_0"
 spegen=9981

### 2022-11-22 graphs_newt_snakes/interaction_rate_inv.Rmd
made a grade interaction rate slim

@@
 
-Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size) can lead to.
-This markdown is investigating
+Think, explore, & write about what the co-evolutionary interaction between newts & snakes with different genetic architectures (GAs, combination of mutation rate & mutation effect size).
+This markdown is investigating what happens to the newt and snake population when I increase the interaction rate.
 
 ### Questions:
-
-## Background
+How does changing the interaction rate affect the survival of the newt or snake population?
+Is there a change in the spatial phenotype correlation?
+Does the interaction rate lead to different phenotype outcome (typical interaction rate is 0.05)?
+What does changing the interaction rate mean in order of how many snakes encounter a newt in their lifetime?
 
@@
 
-  - 0.01
+  - 0.01 lowest amount of interaction
   - 0.025
@@
   - 0.30
-  - 0.35
+  - 0.35 highest amount of interaction
 
@@
 Sometimes a higher interaction rate will lead to a species extinction, so ending values are approximate
-
-### The data
-
-## Preping the data by making singular files
 
@@
 
-unique(GA1_lit_interrate_file$rep)
+#had an odd thing happen on the cluster that was adding reps to my data (I  ignore these other values)
+#unique(GA1_lit_interrate_file$rep)
 
@@
  file$Newt_mean_Pheno<-as.numeric(file$Newt_mean_Pheno)
+ file$group_rate<- paste0(file$group, "_", file$interrate)
+
+ last_point <- file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)
+
   plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
@@
     geom_line(aes(generation, Newt_mean_Pheno, group=interrate, color="Newt_mean_Pheno"))+
+    geom_point(data=last_point, aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno", shape=factor(interrate)))+ #, shape=cost, col="dif"
+    geom_point(data=last_point, aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno", shape=factor(interrate)))+
     geom_hline(yintercept=0, linetype="dashed", color="gray54")+
@@
 labels = c("Snake", "Newt", "Dif"))+
-    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+       theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right",
                       strip.background = element_blank(), strip.text.x = element_blank(),
@@
   xlab(x_label) + ylab(y_label)+
-  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif, shape=factor(interrate)))+
   #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
@@
 
-generations
+## How Often do Newts and Snakes Interact
+
+```{r, how oftern do they interact}
+
+#GA1_lit_interrate_file$newt_found
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("snake_found_newt") +
+  xlab("Generations") + ylab("snake_found_newt")+
+  geom_point(aes(x = as.numeric(generation), y = as.numeric(snake_found_newt), color=factor(interrate)), size = 1 )+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("snake_found_newt") +
+  xlab("Generations") + ylab("snake_found_newt")+
+  facet_wrap(~group)+
+  geom_point(aes(x = as.numeric(generation), y = as.numeric(snake_found_newt), color=factor(interrate)), size = 1 )+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("newt_found") +
+  xlab("Generations") + ylab("newt_found")+
+  facet_wrap(~group)+
+  geom_point(aes(x = as.numeric(generation), y = as.numeric(newt_found), color=factor(interrate)), size = 1 )+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("newt_found") +
+  xlab("Generations") + ylab("newt_found")+
+  geom_point(aes(x = as.numeric(generation), y = as.numeric(newt_found), color=factor(interrate)), size = 1 )+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Snake can potentially find a newt") +
+  xlab("snake_found_newt") +
+  geom_histogram(aes(x = as.numeric(snake_found_newt), fill=factor(interrate)),  alpha = 0.65, position="identity")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Snake can potentially find a newt") +
+  xlab("snake_found_newt") +
+  geom_histogram(aes(x = as.numeric(snake_found_newt), fill=factor(interrate)),  alpha = 0.65, position="identity")+
+  facet_wrap(~group)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Snake found a Newt") +
+  xlab("newt_found") +
+  geom_histogram(aes(x = as.numeric(newt_found), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Snake age") +
+  xlab("Snake_age") +
+  geom_histogram(aes(x = as.numeric(Snake_age), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  xlim(0, 10)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Newt age") +
+  xlab("Newt_age") +
+  geom_histogram(aes(x = as.numeric(Newt_age), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  xlim(0, 10)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Snake found a Newt") +
+  xlab("newt_found") +
+  geom_histogram(aes(x = as.numeric(newt_found), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  facet_wrap(~group)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Newt_pop_size") +
+  xlab("Newt_pop_size") +
+  geom_histogram(aes(x = as.numeric(Newt_pop_size), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Snake_pop_size") +
+  xlab("Snake_pop_size") +
+  geom_histogram(aes(x = as.numeric(Snake_pop_size), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Newt_mean_Pheno") +
+  xlab("Newt_mean_Pheno") +
+  geom_histogram(aes(x = as.numeric(Newt_mean_Pheno), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  xlim(0, 12)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Snake_mean_Pheno") +
+  xlab("Snake_mean_Pheno") +
+  geom_histogram(aes(x = as.numeric(Snake_mean_Pheno), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  xlim(0, 12)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Interactions by population size") +
+  xlab("newt pop size") + ylab("snake popsize")+
+  facet_wrap(~interrate)+
+  geom_point(aes(x = as.numeric(Newt_pop_size), y = as.numeric(Snake_pop_size), color=newt_found), size = 1 )+
+  scale_color_viridis_c(name = "newt_found")+
+  theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right")
+GA1_lit_interrate_file$group_rate<- paste0(GA1_lit_interrate_file$group, "_", GA1_lit_interrate_file$interrate)
+last_point <- GA1_lit_interrate_file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)
+
+ggplot(last_point)+
+  ggtitle("How long did the sim last") +
+  xlab("newt popsize") + ylab("snake popsize")+
+  facet_wrap(~interrate)+
+  geom_point(aes(x = as.numeric(Newt_pop_size), y = as.numeric(Snake_pop_size), color=generation), size = 1 )+
+  scale_color_viridis_c(name = "generation")+
+  theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right")
+
+```
+
+## Mean Phenotype Whole Simulation
+
+First, I will look at a plot of how the mean phenotype of the entire population of newts and snakes changes overtime.
+Each of these plots has three colored lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype.
+There are 11 line per color that represent the different interaction rates that I ran.
+Note this is a mean for the entire population.
+Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).
 

### 2022-12-05 graphs_newt_snakes/interaction_rate_inv.Rmd
I finished writing

--- 2022-10-20 graphs_newt_snakes/interaction_rate_inv.Rmd
@@
 
-cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern,interrate_cap){
 #file=GA1_lit_interrate_file
@@
   cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
-
-  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+  last_point <- file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)
+  lp_trial = last_point[which(last_point$snake_newt_rep==pattern &last_point$interrate<=interrate_cap),]
+
+  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern & file$interrate<=interrate_cap),]) +
+
     #geom_line(aes(generation, dif, group=rep, col="dif"))+
@@
     geom_line(aes(generation, Newt_mean_Pheno, group=interrate, color="Newt_mean_Pheno"))+
+    geom_point(data=lp_trial, aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno", shape=factor(interrate)),size = 3)+
+
+    geom_point(data=lp_trial, aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno", shape=factor(interrate)),size = 3)+ 
     #ylim(0,10)+
@@
 labels = c("Snake", "Newt"))+
-    theme_bw() +theme(legend.position="none",
-                      strip.background = element_blank(), strip.text.x = element_blank(),
+    theme_bw() +theme(strip.background = element_blank(), strip.text.x = element_blank(),
                       title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
@@
                       plot.margin=unit(c(1,1,+0.3,1), "cm"))
-cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern & file$interrate<=interrate_cap),]) +
     geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col=factor(interrate)))+
@@
     #xlab(x_label_cor) + ylab(y_label)+
-    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                       strip.background = element_blank(), strip.text.x = element_blank(),
@@
 
-pop_size_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
+pop_size_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern, interrate_cap){
 #file=GA1_lit_interrate_file
@@
 
-  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
+  last_point <- file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)
+  lp_trial = last_point[which(last_point$snake_newt_rep==pattern &last_point$interrate<=interrate_cap),]
+
+  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern & file$interrate<=interrate_cap),]) +
     #geom_line(aes(generation, dif, group=rep, col="dif"))+
@@
     geom_line(aes(generation, Newt_pop_size, group=interrate, color="Newt"))+
+
+    geom_point(data=lp_trial, aes(generation, Snake_pop_size, color="Snake", shape=factor(interrate)),size = 3)+
+
+    geom_point(data=lp_trial, aes(generation, Newt_pop_size, color="Newt", shape=factor(interrate)),size = 3)+ 
     #ylim(0,10)+
@@
                       plot.margin=unit(c(1,1,+0.3,1), "cm"))
-cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
+cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern & file$interrate<=interrate_cap),]) +
     geom_line(aes(generation, num_newts_By_num_snakes, col=factor(interrate)))+
@@
     #xlab(x_label_cor) + ylab(y_label)+
-    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                       strip.background = element_blank(), strip.text.x = element_blank(),
@@
 
- my_plot <- ggplot(params, aes(newt,  paste0(interrate, "_", snake, "_", rep))) +    # Create heatmap with ggplot2
+ my_plot <- ggplot(params, aes(newt, paste0(snake, "_", interrate))) +    # Create heatmap with ggplot2
   ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
@@
 
-whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
+whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep, interrate_cap){
   #file$rep==rep
@@
   file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
-dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep & file$interrate<=interrate_cap),]) +
   #xlim(0, 1000)+
@@
 if(type == "num_ind"){
-main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
               subtitle = paste0(file_name, ", Generation: ", spegen),
-              fill = "Newt/Snake Phenotype")+
+              fill = "Newt/Snake PopSize")+
 scale_fill_viridis_c(option = "plasma")
@@
 newt$info <- "middle"
-newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"
-
-newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"
+
+#need to look into, coloring problem
+newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"
 
@@
 
-generations
-
+## How Often do Newts and Snakes Interact {.tabset}
+First, I wanted to do some data exploration!
+So I examined how manipulating the interaction rate would effect some population dynamics.
+I wanted to pin-point how often snakes could potentially and actuality interact with newts (one is looping through snakes with newts near by and one is counting the amount of times a snake encountered a newt, respectively).
+These are presented as histograms colored by the interaction rate (look closely at title).
+I also wanted to explore how interaction rate could impact the population size and mean phenotype of snakes and newts.
+These are also shown as histograms where color indicates the interaction rate.
+I also looked for an interaction between interaction rate, the population size of newts and snakes, and the number of interactions that occurred within a generation.
+
+### Potential Interaction
+```{r, how oftern do they interact Potential Interaction}
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Potential Interaction") +
+  xlab("Snake can Potentially Find a Newt, Param: snake_found_newt") +
+  ylab("Count") +
+  geom_histogram(aes(x = as.numeric(snake_found_newt), fill=factor(interrate)),  alpha = 0.65, position="identity")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black")) 
+```
+
+### True Number of Interactions
+```{r, True Number of Interactions}
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Number of Interactions") +
+  xlab("Snake found a Newt, Param: newt_found") +
+  ylab("Count") +
+  geom_histogram(aes(x = as.numeric(newt_found), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black")) 
+```
+
+### Newt and Snake Population Size
+```{r, newt and snake pop size by interaction rate}
+newtfig <- ggplot(GA1_lit_interrate_file)+
+  ggtitle("Newt Population Size") +
+  xlab("Newt_pop_size") +
+  geom_histogram(aes(x = as.numeric(Newt_pop_size), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      legend.position='none',
+                      axis.line = element_line(colour = "black"))
+
+snakefig <- ggplot(GA1_lit_interrate_file)+
+  ggtitle("Snake Population Size") +
+  xlab("Snake_pop_size") +
+  geom_histogram(aes(x = as.numeric(Snake_pop_size), fill=factor(interrate)), alpha = 0.65, position="identity") +
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(),
+                      legend.position='none',
+                      axis.line = element_line(colour = "black"))
+
+grid.arrange(newtfig, snakefig, ncol = 2)
+```
+
+### Newt and Snake Mean Phenotype
+```{r, newt and snake meanphenotype by interaction rate}
+newtfig <- ggplot(GA1_lit_interrate_file)+
+  ggtitle("Newt Mean Phenotype") +
+  xlab("Average Newt Phenotype") +
+  geom_histogram(aes(x = as.numeric(Newt_mean_Pheno), fill=factor(interrate)), alpha = 0.65, position="identity") + xlim(0, 12)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      legend.position='none',
+                      axis.line = element_line(colour = "black"))
+
+snakefig <- ggplot(GA1_lit_interrate_file)+
+  ggtitle("Snake Mean Phenotype") +
+  xlab("Average Snake Phenotype") +
+  geom_histogram(aes(x = as.numeric(Snake_mean_Pheno), fill=factor(interrate)), alpha = 0.65, position="identity") + xlim(0, 12)+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(),
+                      legend.position='none',
+                      axis.line = element_line(colour = "black"))
+
+grid.arrange(newtfig, snakefig, ncol = 2)
+```
+
+### How Interaction rate changes the population size
+```{r, tale of the interaction rate and pop size}
+ggplot(GA1_lit_interrate_file)+
+  ggtitle("Number of Interactions by Newt and Snake Population Size") +
+  xlab("Newt Population Size") + ylab("Snake Population Size")+
+  facet_wrap(~interrate)+
+  geom_point(aes(x = as.numeric(Newt_pop_size), y = as.numeric(Snake_pop_size), color=newt_found), size = 1 )+
+  scale_color_viridis_c(name = "newt_found")+
+  theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right")
+GA1_lit_interrate_file$group_rate<- paste0(GA1_lit_interrate_file$group, "_", GA1_lit_interrate_file$interrate)
+last_point <- GA1_lit_interrate_file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)
+```
+
+## {-}
+
+Changing the interaction rate has major consequences for my simulation.
+If the interaction rate is too low there is not enough selection to increase the mean phenotype of newts and snakes.
+If the interaction rate is too large there is too much competition between newts and snakes leading to an extinction of one of the species.
+In my simulation the potential interaction is noted if there is a newt near a snake.
+This measurement is a combination of the snakes population size and how close the species are to each other.
+The true number of interactions is based on a mathematical formula that increases the probably of interaction with increasing the interaction rate, but also decreases the probability of interaction with an increase in distance to a newt.
+This explains why low interaction rates have less interactions, while also explaining why higher interaction rates also have less interactions.
+Interaction rate has consequences for newt and snake population size and phenotype.
+At lower interaction rates newts and snakes have a higher population size, but lower mean phenotype.
+At slightly larger interaction rates newts and snakes have a lower population size, but a higher mean phenotype.
+At the largest interaction rates the newt and snake populations reach extreme population sizes and high mean phenotypes as one of the species goes extinct.
+For fun, I explored how each  interaction rate changed the population sizes of newts and snakes and the number of interaction that occurred.
+I found that an interaction rate that is too low or too high ends up having less interactions overall.
+There is small area of parameter space where interaction rate can be set to (0.025 to 0.075).
+
+surs = 0.5
+mPoint = c(ind_snake.x,ind_snake.y);
+newtNeighbors = i1.nearestNeighborsOfPoint(p1, mPoint, count=1000000);// could make count smaller (limit the number of newts nearby)
+distance = i1.distanceToPoint(newtNeighbors, mPoint);// vector of distances 
+probablity = interaction_rate * exp(-(distance^2)/(2*(surs^2)))
+newt_meet_snake = newtNeighbors[runif(length(newtNeighbors)) < probablity]
+distance might go up and down based on how close newts and snakes
+
+```{r, extra plots that deminstrate that it is consistance across the GA combos}
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("snake_found_newt") +
+#   xlab("Generations") + ylab("snake_found_newt")+
+#   geom_point(aes(x = as.numeric(generation), y = as.numeric(snake_found_newt), color=factor(interrate)), size = 1 )+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("snake_found_newt") +
+#   xlab("Generations") + ylab("snake_found_newt")+
+#   facet_wrap(~group)+
+#   geom_point(aes(x = as.numeric(generation), y = as.numeric(snake_found_newt), color=factor(interrate)), size = 1 )+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("newt_found") +
+#   xlab("Generations") + ylab("newt_found")+
+#   facet_wrap(~group)+
+#   geom_point(aes(x = as.numeric(generation), y = as.numeric(newt_found), color=factor(interrate)), size = 1 )+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("newt_found") +
+#   xlab("Generations") + ylab("newt_found")+
+#   geom_point(aes(x = as.numeric(generation), y = as.numeric(newt_found), color=factor(interrate)), size = 1 )+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Snake can potentially find a newt") +
+#   xlab("snake_found_newt") +
+#   geom_histogram(aes(x = as.numeric(snake_found_newt), fill=factor(interrate)),  alpha = 0.65, position="identity")+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Snake can potentially find a newt") +
+#   xlab("snake_found_newt") +
+#   geom_histogram(aes(x = as.numeric(snake_found_newt), fill=factor(interrate)),  alpha = 0.65, position="identity")+
+#   facet_wrap(~group)+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Snake found a Newt") +
+#   xlab("newt_found") +
+#   geom_histogram(aes(x = as.numeric(newt_found), fill=factor(interrate)), alpha = 0.65, position="identity") +
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Snake age") +
+#   xlab("Snake_age") +
+#   geom_histogram(aes(x = as.numeric(Snake_age), fill=factor(interrate)), alpha = 0.65, position="identity") +
+#   xlim(0, 10)+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Newt age") +
+#   xlab("Newt_age") +
+#   geom_histogram(aes(x = as.numeric(Newt_age), fill=factor(interrate)), alpha = 0.65, position="identity") +
+#   xlim(0, 10)+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Snake found a Newt") +
+#   xlab("newt_found") +
+#   geom_histogram(aes(x = as.numeric(newt_found), fill=factor(interrate)), alpha = 0.65, position="identity") +
+#   facet_wrap(~group)+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Newt_pop_size") +
+#   xlab("Newt_pop_size") +
+#   geom_histogram(aes(x = as.numeric(Newt_pop_size), fill=factor(interrate)), alpha = 0.65, position="identity") +
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Snake_pop_size") +
+#   xlab("Snake_pop_size") +
+#   geom_histogram(aes(x = as.numeric(Snake_pop_size), fill=factor(interrate)), alpha = 0.65, position="identity") +
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Newt_mean_Pheno") +
+#   xlab("Newt_mean_Pheno") +
+#   geom_histogram(aes(x = as.numeric(Newt_mean_Pheno), fill=factor(interrate)), alpha = 0.65, position="identity") +
+#   xlim(0, 12)+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Snake_mean_Pheno") +
+#   xlab("Snake_mean_Pheno") +
+#   geom_histogram(aes(x = as.numeric(Snake_mean_Pheno), fill=factor(interrate)), alpha = 0.65, position="identity") +
+#   xlim(0, 12)+
+#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+#                       # strip.background = element_blank(), 
+#                       # strip.text.x = element_blank(), 
+#                       # panel.grid.major = element_blank(), 
+#                       # panel.grid.minor = element_blank(),
+#                       # panel.background = element_blank(), 
+#                       axis.line = element_line(colour = "black")) 
+# 
+# ggplot(GA1_lit_interrate_file)+
+#   ggtitle("Interactions by population size") +
+#   xlab("newt pop size") + ylab("snake popsize")+
+#   facet_wrap(~interrate)+
+#   geom_point(aes(x = as.numeric(Newt_pop_size), y = as.numeric(Snake_pop_size), color=newt_found), size = 1 )+
+#   scale_color_viridis_c(name = "newt_found")+
+#   theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right")
+# GA1_lit_interrate_file$group_rate<- paste0(GA1_lit_interrate_file$group, "_", GA1_lit_interrate_file$interrate)
+# last_point <- GA1_lit_interrate_file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)
+# 
+# 
+# ggplot(last_point)+
+#   ggtitle("How long did the sim last") +
+#   xlab("newt popsize") + ylab("snake popsize")+
+#   facet_wrap(~interrate)+
+#   geom_point(aes(x = as.numeric(Newt_pop_size), y = as.numeric(Snake_pop_size), color=generation), size = 1 )+
+#   scale_color_viridis_c(name = "generation")+
+#   theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right")
+
+```
+
+## Mean Phenotype Whole Simulation & The Interaction With Population size  {.tabset}
+
+Next, I will look at a plot of how the mean phenotype of the entire population of newts and snakes changes overtime.
+Each of these plots has three colored lines, red for the mean newt phenotype, blue for the mean snake phenotype, and black for the difference between mean snake and mean newt phenotype.
+There are 11 lines per color with a shape at the last data point collected that represent the different interaction rates.
+Note this is a mean for the entire population.
+Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).
+
+In previous experiments, I saw a connection between newt/snake phenotype and population size.
+Typically, when a species had a higher phenotype they also had a larger population size.
+This relation between phenotype and population size had specific outcomes that depended on the GA of newts and snakes.
+In this plot I look at how interaction rate might change this observation.
+Here some of the interaction rates are shown as shapes (I choose to limit the number of interaction rayes I was looking at).
+
+### Mean Phenotype As Time Increases
 ```{r, graphing by gen}
@@
 
+### Relationship Between Popsize and Phenotype
 ```{r, whale}
@@
 
-whale_gen(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-```
+whale_gen(GA1_lit_interrate_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=rep, interrate_cap=0.125)
+```
+
+## {-}
+
+As I have mentioned before, higher interaction rates lead to a populations extinction (for many of them the extinction happens very early > 5,000 generations).
+However, it does seem that higher interaction rates can lead to a higher mean phenotype.
+Higher interaction rates seem to run in simulation where both newts and snakes have a larger amount of mutational variance.
+
+The relationship between newt and snake population sizes and the difference between mean phenotype is affected by a change in the interaction rate.
+A lower interaction rate has higher population sizes and lower mean phenotype differences.
+I found that as the interaction rate increases the larger the range in population sizes became.
+I also noticed that larger interaction rates tended to have a larger difference between mean phenotypes and that newts seemed to have larger phenotypes.
 
@@
 
-ginmin = 0
-ginmax = 50000
-#thecolors=c("#F8766D", "#B79F00", "#00BA38", "#00BFC4", "#619CFF", "#F564E3")
-
-boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-```
-
-## Correlation Histograms  {.tabset}
-
-In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
-Each color is a different trial per GA combination.
-The histogram values are stacked.
-This section only looks at the 5 sections.
+# ginmin = 0
+# ginmax = 50000
+# #thecolors=c("#F8766D", "#B79F00", "#00BA38", "#00BFC4", "#619CFF", "#F564E3")
+# 
+# boxplot_cors_by_gen(GA1_cor_interrate_file, "interrate: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+```
+
+## Correlation Across Time  {.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all correlation values for each of the different interaction rate.
+Each color is a different interaction rate.
+Each plot is one GA combination.
+Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).
 
@@
 
+The range of colors in these plots is so pretty!
+There was no interaction rate that lead to my simulated newts and snakes having a high correlated phenotype similar to the real newt and snake (dashed line) correlation.
+As the interaction rate increased there was more variation in spatial phenotype correlation.
+I think this might be due to major decreases in a species population size that occurred when interaction rates were large.
+Simulations that had one or more species with a higher level of mutational variance were able to persist larger interaction rates.
+
 ## Phenotype Correlation across time {.tabset}
 
-Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment.
+Next, we will examine three randomly chosen plots from this experiment.
 Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
 Newt whole population mean phenotype is red, while snake mean phenotype is blue.
-The pink line is the phenotype spatial correlation.
-
-### Random 1 (5 sec)
+The multi-colored line line is the phenotype spatial correlation at different interaction rates.
+
+### Random 1 
 ```{r, GA1 cor and pheno}
@@
 
-cor_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
-
-```
-
-### Random 2 (5 sec)
+cor_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]], interrate_cap= 0.125)
+
+```
+
+### Random 2 
 ```{r, random cor-pheno plot 2}
 
-cor_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
-```
-
-### Random 3 (5 sec)
+cor_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]], interrate_cap= 0.125)
+```
+
+### Random 3 
 ```{r, random cor-pheno plot 3}
 
-cor_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+cor_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]], interrate_cap= 0.125)
 ```
@@
 
+There is no relationship between mean phenotype and phenotype spatial correlations.
+The mean phenotype of newts and snakes goes up over time, but the spatial correlation seems to randomly go up and down.
+Simulations with a high interaction rate typically end up with higher phenotypes, but when the interaction rate is too high a species will die out.
+The higher the interaction rate the more variable the spatial correlation may get.
+
 ## Population Size Correlation across time {.tabset}
+
+Now, we will examine the population size of the three randomly chosen plots from this experiment.
+Time (in generations) in on the x-axis and both population size and population size spatial correlation in on the y-axis.
+Newt population size is red, while snake population size is blue.
+The multi-colored line line is the population spatial correlation at different interaction rates.
 
@@
 ```{r, GA1 pop size 1}
-pop_size_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+pop_size_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]], interrate_cap= 0.125)
 
@@
 
-pop_size_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+pop_size_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]],interrate_cap= 0.125)
 ```
@@
 
-pop_size_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+pop_size_trends_by_gen(GA1_lit_interrate_file, GA1_cor_interrate_file, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]],interrate_cap= 0.125)
 ```
@@
 
+There is a connection between population size and interaction rate.
+The interaction rate has an effect on the population size, but it is difficult to tell because the how different the population sizes are at the smaller sized edges and corners.
+If all of the measured areas were the same size I predict that there would be more negative correlation.
+
 ## What happens over time (looking at the beginning and late part of my simulations) {.tabset}
+
+This section explores how changing the interaction rate affects the first and last 5,000 generations of my co-evolution simulation.
+Newt and snake population size are on the x and y axis and the point color is the difference between snake and newt mean phenotype.
+Each plot contains many time points from one simulation with a set GA combination.
+Mutational variance increases for the snakes as you go down the figure (top to bottom) and increases for the newts as you go across (left to right).
 
@@
 
+In the early part of my simulation I noticed that as the interaction rate because larger the population size drastically turns in one species favor.
+A higher interaction rate led to a larger difference between mean phenotype.
+In the last part of my simulation there are less and less simulations that reach the last 5,000 generations.
+There is also more difference between GA combinations as the interaction rate increases.
+For example, each of the the GA combinations ending up having very different population sizes (when compared to lower interaction rates).
+Some intermediate interaction rates ended up having the largest phenotype differences (potentially due to having more interactions do to the immersion of both species).
+
 ## Heatmap {.tabset}
 
+This section explores the heatmap plots where the GA of the newt is on the x-axins and the GA of the snake along with the interaction rate for the simulation is on the y-axis.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+The simulation result is the color in that section.
+
 ### interrate: Population Size (Early)  
-```{r, interrate earlyplots Heatmap1, fig.height=4}
+```{r, interrate earlyplots Heatmap1, fig.height=6, out.height=6}
 min_gen=100
 max_gen=5000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-```
-
-### interrate: Population Size (EM1)  
-```{r, interrate earlyplots Heatmap2, fig.height=4}
-min_gen=5000
-max_gen=10000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-```
-
-### interrate: Population Size (EM2)  
-```{r, interrate earlyplots Heatmap3, fig.height=4}
-min_gen=10000
-max_gen=15000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-```
-
-### interrate: Population Size (EM3)  
-```{r, interrate earlyplots Heatmap4, fig.height=4}
-min_gen=15000
-max_gen=20000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-```
-
-### interrate: Population Size (EM4)  
-```{r, interrate earlyplots Heatmap5, fig.height=4}
-min_gen=20000
-max_gen=25000
 
@@
 
-### interrate: Population Size (ML1)  
-```{r, interrate midplots Heatmap7, fig.height=4}
-min_gen=30000
-max_gen=35000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-```
-
-### interrate: Population Size (ML2)  
-```{r, interrate midplots Heatmap8, fig.height=4}
-min_gen=35000
-max_gen=40000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-```
-
-### interrate: Population Size (ML3)  
-```{r, interrate midplots Heatmap9, fig.height=4}
-min_gen=40000
-max_gen=45000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
-
-```
-
 ### interrate: Population Size (Late)  
@@
 
-### interrate: Phenotype (EM1) 
-```{r, interrate earlyplots Heatmap2 pheno, fig.height=4}
-
-min_gen=5000
-max_gen=10000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-```
-
-### interrate: Phenotype (EM2) 
-```{r, interrate earlyplots Heatmap3 pheno, fig.height=4}
-
-min_gen=10000
-max_gen=15000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-```
-
-### interrate: Phenotype (EM3) 
-```{r, interrate earlyplots Heatmap4 pheno, fig.height=4}
-
-min_gen=15000
-max_gen=20000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-```
-
-### interrate: Phenotype (EM4) 
-```{r, interrate earlyplots Heatmap5 pheno, fig.height=4}
-
-min_gen=20000
-max_gen=25000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-```
-
 ### interrate: Phenotype (Mid) 
@@
 
-### interrate: Phenotype (ML1) 
-```{r, interrate earlyplots Heatmap7 pheno, fig.height=4}
-
-min_gen=30000
-max_gen=35000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-```
-
-### interrate: Phenotype (ML2) 
-```{r, interrate earlyplots Heatmap8 pheno, fig.height=4}
-
-min_gen=35000
-max_gen=40000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-```
-
-### interrate: Phenotype (ML3) 
-```{r, interrate earlyplots Heatmap9 pheno, fig.height=4}
-
-min_gen=40000
-max_gen=45000
-
-build_heatmap(GA1_lit_interrate_file, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
-```
-
 ### interrate: Phenotype (Late) 
@@
 
-##Grid {.tabset}
+It seems like higher interaction rates can lead to more differences in snake population size and a larger mean phenotype differences.
+These results depend on the GA of both the newt and snake, with more variable results appearing when the GA have intermediate phenotype variance (medium mu rate and effect size).
+It is difficult to tell what is occurring overtime due to the simulations ending early.
 
@@
 
+This last section will explore how large a snake/newt phenotype or population size is at a certain local region.
+The squares represent local snakes population values, while the circles represent local newt values.
+The sub-plots show how the values play out over the samples being located on an edge, corner, or middle of the map.
+In my true simulation there is no space all of these should be touching.
+
 ### 0.01
@@
 }
+
+type="num_ind"
+if(value!=0){
+grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) 
+}
 ```
@@
 }
+type="num_ind"
+if(value!=0){
+grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) 
+}
 ```
@@
 if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+type="num_ind"
+if(value!=0){
+grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) 
+}
 ```
@@
 if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+
+type="num_ind"
+if(value!=0){
+grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) 
+}
 ```
@@
 if(value!=0){ grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) }
+type="num_ind"
+if(value!=0){
+grid_plot(file_name, spegen, file, type, row_num, col_num, interrate) 
+}
+
 ```
@@
 
-## Grid Figs {.tabset}
+## Grid Figs 3 {.tabset}
 

### 2022-12-06 graphs_newt_snakes/dif_cost_grade.Rmd
I created the interrate grade and snake grade file. I ran or re-ran all of the data to look at the correlation between phenotypes as well as other results. Next step I will spend more time exploring these results

@@
 grid_plot<- function(file_name, spegen, file, type, row_num, col_num){
+
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
@@
 newt$info <- "middle"
-newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-1-row_num, col_num*row_num-1)] <- "corner"
-
-newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num-row_num), row_num),  c((col_num*row_num-row_num):(col_num*row_num-2)))]   <- "edge"
+
+#need to look into, coloring problem
+newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"
 
@@
 ```{r, graphing by gen}
-trends_by_gen(cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+trends_by_gen(cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 250, 50000, rep=1)
 

### 2022-12-06 graphs_newt_snakes/interrate_grade.Rmd
I created the interrate grade and snake grade file. I ran or re-ran all of the data to look at the correlation between phenotypes as well as other results. Next step I will spend more time exploring these results

--- 2022-12-06 graphs_newt_snakes/dif_cost_grade.Rmd
@@
 ---
-title: "Cost Gradient"
+title: "Interaction Grade"
 output: html_document
-date: '2022-10-21'
+date: '2022-12-06'
 ---
@@
 thepath=/Users/victoria/Desktop/
-foldername=cost_grade
+foldername=interrate_grade
 thefolder=${thepath}${foldername}/*
@@
 
-cost_grade_lit<- read.csv("~/Desktop/cost_grade/all_lit.txt" , header = TRUE)
-
-cost_grade_lit$group_rep <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep)
-
-cost_grade_lit$group <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd)
-
-cost_grade_lit$sim=LETTERS[factor(cost_grade_lit$group)]
-cost_grade_lit$dif <- cost_grade_lit$Snake_mean_Pheno-cost_grade_lit$Newt_mean_Pheno
-
-cost_grade_cor<- read.csv("~/Desktop/cost_grade/all_cor.txt" , header = TRUE)
-cost_grade_cor$group_rep <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd, "_", cost_grade_cor$rep)
-cost_grade_cor$group <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd)
-cost_grade_cor$sim=LETTERS[factor(cost_grade_cor$group)]
+interrate_grade_lit<- read.csv("~/Desktop/interrate_grade/all_lit.txt" , header = TRUE)
+
+interrate_grade_lit$group_rep <- paste0(interrate_grade_lit$snake_mu_rate, "_", interrate_grade_lit$snake_mu_effect_sd,"_",interrate_grade_lit$newt_mu_rate, "_", interrate_grade_lit$newt_mu_effect_sd, "_", interrate_grade_lit$rep)
+
+interrate_grade_lit$group <- paste0(interrate_grade_lit$snake_mu_rate, "_", interrate_grade_lit$snake_mu_effect_sd,"_",interrate_grade_lit$newt_mu_rate, "_", interrate_grade_lit$newt_mu_effect_sd)
+
+interrate_grade_lit$sim=LETTERS[factor(interrate_grade_lit$group)]
+interrate_grade_lit$dif <- interrate_grade_lit$Snake_mean_Pheno-interrate_grade_lit$Newt_mean_Pheno
+
+interrate_grade_cor<- read.csv("~/Desktop/interrate_grade/all_cor.txt" , header = TRUE)
+interrate_grade_cor$group_rep <- paste0(interrate_grade_cor$snake_mu_rate, "_", interrate_grade_cor$snake_mu_effect_sd,"_",interrate_grade_cor$newt_mu_rate, "_", interrate_grade_cor$newt_mu_effect_sd, "_", interrate_grade_cor$rep)
+interrate_grade_cor$group <- paste0(interrate_grade_cor$snake_mu_rate, "_", interrate_grade_cor$snake_mu_effect_sd,"_",interrate_grade_cor$newt_mu_rate, "_", interrate_grade_cor$newt_mu_effect_sd)
+interrate_grade_cor$sim=LETTERS[factor(interrate_grade_cor$group)]
 
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=cost_grade_lit
-#cfile=cost_grade_cor 
+#file=interrate_grade_lit
+#cfile=interrate_grade_cor 
  # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=cost_grade_lit
+  #file=interrate_grade_lit
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 
@@
 ```{r, graphing by gen}
-trends_by_gen(cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 250, 50000, rep=1)
-
-#aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group_rep), FUN=mean)
+trends_by_gen(interrate_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+#aggregate(interrate_grade_lit[which(interrate_grade_lit$generation>=100 & interrate_grade_lit$generation<=50000),]$dif, list(interrate_grade_lit[which(interrate_grade_lit$generation>=100 & interrate_grade_lit$generation<=50000),]$group_rep), FUN=mean)
 
@@
 ```{r, average difference}
-aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group), FUN=mean)
+aggregate(interrate_grade_lit[which(interrate_grade_lit$generation>=100 & interrate_grade_lit$generation<=50000),]$dif, list(interrate_grade_lit[which(interrate_grade_lit$generation>=100 & interrate_grade_lit$generation<=50000),]$group), FUN=mean)
 ```
@@
 
-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(interrate_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
-suppressMessages(print(two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
-
-#suppressMessages(print(two_hist_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+suppressMessages(print(two_hist(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
 
@@
 
-boxplot_cors_by_gen(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-#four_types_boxplot_cors_by_gen(cost_grade_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(interrate_grade_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
@@
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ```{r, GA1 cor and pheno}
-GA1_pattern <- unique(paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep))
+GA1_pattern <- unique(paste0(interrate_grade_lit$snake_mu_rate, "_", interrate_grade_lit$snake_mu_effect_sd,"_",interrate_grade_lit$newt_mu_rate, "_", interrate_grade_lit$newt_mu_effect_sd, "_", interrate_grade_lit$rep))
 
@@
 # for(i in myrandomlist){
-#   myine<-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   myine<-cor_trends_by_gen(interrate_grade_lit, interrate_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
 #   plot(myine)
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+cor_trends_by_gen(interrate_grade_lit, interrate_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
 
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+cor_trends_by_gen(interrate_grade_lit, interrate_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
 ```
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+cor_trends_by_gen(interrate_grade_lit, interrate_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
 ```
@@
 
-# for(i in 1:length(unique(cost_grade_lit$rep))){
-#   myine<-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i])
+# for(i in 1:length(unique(interrate_grade_lit$rep))){
+#   myine<-whale_gen(interrate_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(interrate_grade_lit$rep)[i])
 #   plot(myine)
@@
 # }
-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1])
+whale_gen(interrate_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(interrate_grade_lit$rep)[1])
 ```
@@
 
-# for(i in 1:length(unique(cost_grade_lit$rep))){
-#   myine<-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i] )
+# for(i in 1:length(unique(interrate_grade_lit$rep))){
+#   myine<-two_hist(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(interrate_grade_lit$rep)[i] )
 #   suppressMessages(plot(myine))
@@
 
-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1] )
+two_hist(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(interrate_grade_lit$rep)[1] )
 
@@
 max_gen=5000
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
@@
 
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 ```
@@
 
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 max_gen=50000
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 
-GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
 
@@
 
-GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+GA_summary_by_species(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
 
@@
 #heatmap
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 ```
@@
 #heatmap
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
@@
 max_gen=5000
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 require(readr)
-cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
-cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
-cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
-cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
-cost_grade_grid$grid_num = 5
+interrate_grade_grid<- read.csv("~/Desktop/interrate_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+interrate_grade_grid$group_rep <- paste0(interrate_grade_grid$snake_mu_rate, "_", interrate_grade_grid$snake_mu_effect_sd,"_",interrate_grade_grid$newt_mu_rate, "_", interrate_grade_grid$newt_mu_effect_sd, "_", interrate_grade_grid$rep)
+interrate_grade_grid$group <- paste0(interrate_grade_grid$snake_mu_rate, "_", interrate_grade_grid$snake_mu_effect_sd,"_",interrate_grade_grid$newt_mu_rate, "_", interrate_grade_grid$newt_mu_effect_sd)
+interrate_grade_grid$sim=LETTERS[factor(interrate_grade_grid$group)]
+interrate_grade_grid$grid_num = 5
 
@@
 
-file=cost_grade_grid
+file=interrate_grade_grid
 file_name="1e-11_5_1e-10_0.5_0"
@@
 require(readr)
-cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
-cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
-cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
-cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
-cost_grade_grid$grid_num = 5
+interrate_grade_grid<- read.csv("~/Desktop/interrate_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
+interrate_grade_grid$group_rep <- paste0(interrate_grade_grid$snake_mu_rate, "_", interrate_grade_grid$snake_mu_effect_sd,"_",interrate_grade_grid$newt_mu_rate, "_", interrate_grade_grid$newt_mu_effect_sd, "_", interrate_grade_grid$rep)
+interrate_grade_grid$group <- paste0(interrate_grade_grid$snake_mu_rate, "_", interrate_grade_grid$snake_mu_effect_sd,"_",interrate_grade_grid$newt_mu_rate, "_", interrate_grade_grid$newt_mu_effect_sd)
+interrate_grade_grid$sim=LETTERS[factor(interrate_grade_grid$group)]
+interrate_grade_grid$grid_num = 5
 

### 2022-12-06 graphs_newt_snakes/newt_change.Rmd
I created the interrate grade and snake grade file. I ran or re-ran all of the data to look at the correlation between phenotypes as well as other results. Next step I will spend more time exploring these results

@@
 newt$info <- "middle"
+
 #need to look into, coloring problem
-newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-1-row_num, col_num*row_num-1)] <- "corner"
-
-newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num-row_num), row_num),  c((col_num*row_num-row_num):(col_num*row_num-2)))]   <- "edge"
+newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"
 

### 2022-12-06 graphs_newt_snakes/no_inter_cost_grade.Rmd
I created the interrate grade and snake grade file. I ran or re-ran all of the data to look at the correlation between phenotypes as well as other results. Next step I will spend more time exploring these results

--- 2022-12-06 graphs_newt_snakes/dif_cost_grade.Rmd
@@
 ---
-title: "Cost Gradient"
+title: "No Interaction on a Cost Grade"
 output: html_document
-date: '2022-10-21'
+date: '2022-12-06'
 ---
@@
 thepath=/Users/victoria/Desktop/
-foldername=cost_grade
+foldername=no_interaction_cost_grade
 thefolder=${thepath}${foldername}/*
@@
 
-cost_grade_lit<- read.csv("~/Desktop/cost_grade/all_lit.txt" , header = TRUE)
-
-cost_grade_lit$group_rep <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep)
-
-cost_grade_lit$group <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd)
-
-cost_grade_lit$sim=LETTERS[factor(cost_grade_lit$group)]
-cost_grade_lit$dif <- cost_grade_lit$Snake_mean_Pheno-cost_grade_lit$Newt_mean_Pheno
-
-cost_grade_cor<- read.csv("~/Desktop/cost_grade/all_cor.txt" , header = TRUE)
-cost_grade_cor$group_rep <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd, "_", cost_grade_cor$rep)
-cost_grade_cor$group <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd)
-cost_grade_cor$sim=LETTERS[factor(cost_grade_cor$group)]
+no_interaction_cost_grade_lit<- read.csv("~/Desktop/no_interaction_cost_grade/all_lit.txt" , header = TRUE)
+
+no_interaction_cost_grade_lit$group_rep <- paste0(no_interaction_cost_grade_lit$snake_mu_rate, "_", no_interaction_cost_grade_lit$snake_mu_effect_sd,"_",no_interaction_cost_grade_lit$newt_mu_rate, "_", no_interaction_cost_grade_lit$newt_mu_effect_sd, "_", no_interaction_cost_grade_lit$rep)
+
+no_interaction_cost_grade_lit$group <- paste0(no_interaction_cost_grade_lit$snake_mu_rate, "_", no_interaction_cost_grade_lit$snake_mu_effect_sd,"_",no_interaction_cost_grade_lit$newt_mu_rate, "_", no_interaction_cost_grade_lit$newt_mu_effect_sd)
+
+no_interaction_cost_grade_lit$sim=LETTERS[factor(no_interaction_cost_grade_lit$group)]
+no_interaction_cost_grade_lit$dif <- no_interaction_cost_grade_lit$Snake_mean_Pheno-no_interaction_cost_grade_lit$Newt_mean_Pheno
+
+no_interaction_cost_grade_cor<- read.csv("~/Desktop/no_interaction_cost_grade/all_cor.txt" , header = TRUE)
+no_interaction_cost_grade_cor$group_rep <- paste0(no_interaction_cost_grade_cor$snake_mu_rate, "_", no_interaction_cost_grade_cor$snake_mu_effect_sd,"_",no_interaction_cost_grade_cor$newt_mu_rate, "_", no_interaction_cost_grade_cor$newt_mu_effect_sd, "_", no_interaction_cost_grade_cor$rep)
+no_interaction_cost_grade_cor$group <- paste0(no_interaction_cost_grade_cor$snake_mu_rate, "_", no_interaction_cost_grade_cor$snake_mu_effect_sd,"_",no_interaction_cost_grade_cor$newt_mu_rate, "_", no_interaction_cost_grade_cor$newt_mu_effect_sd)
+no_interaction_cost_grade_cor$sim=LETTERS[factor(no_interaction_cost_grade_cor$group)]
 
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=cost_grade_lit
-#cfile=cost_grade_cor 
+#file=no_interaction_cost_grade_lit
+#cfile=no_interaction_cost_grade_cor 
  # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=cost_grade_lit
+  #file=no_interaction_cost_grade_lit
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 
@@
 ```{r, graphing by gen}
-trends_by_gen(cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 250, 50000, rep=1)
-
-#aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group_rep), FUN=mean)
+trends_by_gen(no_interaction_cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+#aggregate(no_interaction_cost_grade_lit[which(no_interaction_cost_grade_lit$generation>=100 & no_interaction_cost_grade_lit$generation<=50000),]$dif, list(no_interaction_cost_grade_lit[which(no_interaction_cost_grade_lit$generation>=100 & no_interaction_cost_grade_lit$generation<=50000),]$group_rep), FUN=mean)
 
@@
 ```{r, average difference}
-aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group), FUN=mean)
+aggregate(no_interaction_cost_grade_lit[which(no_interaction_cost_grade_lit$generation>=100 & no_interaction_cost_grade_lit$generation<=50000),]$dif, list(no_interaction_cost_grade_lit[which(no_interaction_cost_grade_lit$generation>=100 & no_interaction_cost_grade_lit$generation<=50000),]$group), FUN=mean)
 ```
@@
 
-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(no_interaction_cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
-suppressMessages(print(two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
-
-#suppressMessages(print(two_hist_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+suppressMessages(print(two_hist(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
 
@@
 
-boxplot_cors_by_gen(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-#four_types_boxplot_cors_by_gen(cost_grade_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(no_interaction_cost_grade_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
@@
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ```{r, GA1 cor and pheno}
-GA1_pattern <- unique(paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep))
+GA1_pattern <- unique(paste0(no_interaction_cost_grade_lit$snake_mu_rate, "_", no_interaction_cost_grade_lit$snake_mu_effect_sd,"_",no_interaction_cost_grade_lit$newt_mu_rate, "_", no_interaction_cost_grade_lit$newt_mu_effect_sd, "_", no_interaction_cost_grade_lit$rep))
 
@@
 # for(i in myrandomlist){
-#   myine<-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   myine<-cor_trends_by_gen(no_interaction_cost_grade_lit, no_interaction_cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
 #   plot(myine)
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+cor_trends_by_gen(no_interaction_cost_grade_lit, no_interaction_cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
 
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+cor_trends_by_gen(no_interaction_cost_grade_lit, no_interaction_cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
 ```
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+cor_trends_by_gen(no_interaction_cost_grade_lit, no_interaction_cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
 ```
@@
 
-# for(i in 1:length(unique(cost_grade_lit$rep))){
-#   myine<-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i])
+# for(i in 1:length(unique(no_interaction_cost_grade_lit$rep))){
+#   myine<-whale_gen(no_interaction_cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_interaction_cost_grade_lit$rep)[i])
 #   plot(myine)
@@
 # }
-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1])
+whale_gen(no_interaction_cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_interaction_cost_grade_lit$rep)[1])
 ```
@@
 
-# for(i in 1:length(unique(cost_grade_lit$rep))){
-#   myine<-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i] )
+# for(i in 1:length(unique(no_interaction_cost_grade_lit$rep))){
+#   myine<-two_hist(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_interaction_cost_grade_lit$rep)[i] )
 #   suppressMessages(plot(myine))
@@
 
-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1] )
+two_hist(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_interaction_cost_grade_lit$rep)[1] )
 
@@
 max_gen=5000
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
@@
 
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 ```
@@
 
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 max_gen=50000
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 
-GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
 
@@
 
-GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+GA_summary_by_species(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
 
@@
 #heatmap
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 ```
@@
 #heatmap
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
@@
 max_gen=5000
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 require(readr)
-cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
-cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
-cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
-cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
-cost_grade_grid$grid_num = 5
+no_interaction_cost_grade_grid<- read.csv("~/Desktop/no_interaction_cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+no_interaction_cost_grade_grid$group_rep <- paste0(no_interaction_cost_grade_grid$snake_mu_rate, "_", no_interaction_cost_grade_grid$snake_mu_effect_sd,"_",no_interaction_cost_grade_grid$newt_mu_rate, "_", no_interaction_cost_grade_grid$newt_mu_effect_sd, "_", no_interaction_cost_grade_grid$rep)
+no_interaction_cost_grade_grid$group <- paste0(no_interaction_cost_grade_grid$snake_mu_rate, "_", no_interaction_cost_grade_grid$snake_mu_effect_sd,"_",no_interaction_cost_grade_grid$newt_mu_rate, "_", no_interaction_cost_grade_grid$newt_mu_effect_sd)
+no_interaction_cost_grade_grid$sim=LETTERS[factor(no_interaction_cost_grade_grid$group)]
+no_interaction_cost_grade_grid$grid_num = 5
 
@@
 
-file=cost_grade_grid
+file=no_interaction_cost_grade_grid
 file_name="1e-11_5_1e-10_0.5_0"
@@
 require(readr)
-cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
-cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
-cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
-cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
-cost_grade_grid$grid_num = 5
+no_interaction_cost_grade_grid<- read.csv("~/Desktop/no_interaction_cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
+no_interaction_cost_grade_grid$group_rep <- paste0(no_interaction_cost_grade_grid$snake_mu_rate, "_", no_interaction_cost_grade_grid$snake_mu_effect_sd,"_",no_interaction_cost_grade_grid$newt_mu_rate, "_", no_interaction_cost_grade_grid$newt_mu_effect_sd, "_", no_interaction_cost_grade_grid$rep)
+no_interaction_cost_grade_grid$group <- paste0(no_interaction_cost_grade_grid$snake_mu_rate, "_", no_interaction_cost_grade_grid$snake_mu_effect_sd,"_",no_interaction_cost_grade_grid$newt_mu_rate, "_", no_interaction_cost_grade_grid$newt_mu_effect_sd)
+no_interaction_cost_grade_grid$sim=LETTERS[factor(no_interaction_cost_grade_grid$group)]
+no_interaction_cost_grade_grid$grid_num = 5
 

### 2022-12-06 graphs_newt_snakes/points.Rmd
I created the interrate grade and snake grade file. I ran or re-ran all of the data to look at the correlation between phenotypes as well as other results. Next step I will spend more time exploring these results

---
title: "byindvidual"
output: html_document
date: '2022-08-03'
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
library(stringr)
library(patchwork)
```

```{r, data gathering}

info <- read.table("~/Desktop/test.txt", header=TRUE)

f <- function(x, y, ph, xbreaks, ybreaks){
  xb <- cut(x, xbreaks)
  yb <- cut(y, ybreaks)
  phb <- tapply(ph, list(xb, yb), mean)
  return(phb)
}

```

```{r, data plotting tall}

width=35
height=35*4
n=5
m=20
xbreaks <- seq(0, width, length.out=n)
ybreaks <- seq(0, height, length.out=m)

s <- with(info[info$species=="S",], f(loc_x, loc_y, phenotype, xbreaks, ybreaks))
n <- with(info[info$species=="N",], f(loc_x, loc_y, phenotype, xbreaks, ybreaks))

stopifnot(all(colnames(s)==colnames(n)) && all(rownames(s)==rownames(n)))

cor(as.vector(s),as.vector(n), use="pairwise")

n=7
m=28
xbreaks <- seq(0, width, length.out=n)
ybreaks <- seq(0, height, length.out=m)

s <- with(info[info$species=="S",], f(loc_x, loc_y, phenotype, xbreaks, ybreaks))
n <- with(info[info$species=="N",], f(loc_x, loc_y, phenotype, xbreaks, ybreaks))

stopifnot(all(colnames(s)==colnames(n)) && all(rownames(s)==rownames(n)))

cor(as.vector(s),as.vector(n), use="pairwise")

image(ybreaks,xbreaks, t(n))
with(info[info$species=="N",], points(loc_y, loc_x, pch=20,cex=0.5, col=rev(heat.colors(24))[as.numeric(cut(phenotype,24))]))

image(ybreaks,xbreaks, t(s))
with(info[info$species=="S",], points(loc_y, loc_x, pch=20,cex=0.5, col=rev(heat.colors(24))[as.numeric(cut(phenotype,24))]))

```

```{r, plotting long}

width=35
height=35*4
n=5
m=20
xbreaks <- seq(0, width, length.out=n)
ybreaks <- seq(0, height, length.out=m)

s <- with(info[info$species=="S",], f(loc_x, loc_y, phenotype, xbreaks, ybreaks))
n <- with(info[info$species=="N",], f(loc_x, loc_y, phenotype, xbreaks, ybreaks))

stopifnot(all(colnames(s)==colnames(n)) && all(rownames(s)==rownames(n)))

cor(as.vector(s),as.vector(n), use="pairwise")

image(ybreaks,xbreaks, t(n))
with(info[info$species=="N",], points(loc_y, loc_x, pch=20,cex=0.5, col=rev(heat.colors(24))[as.numeric(cut(phenotype,24))]))

image(ybreaks,xbreaks, t(s))
with(info[info$species=="S",], points(loc_y, loc_x, pch=20,cex=0.5, col=rev(heat.colors(24))[as.numeric(cut(phenotype,24))]))

```

```{r, find the nearest neghbor}

```

### 2022-12-06 graphs_newt_snakes/snake_change.Rmd
I created the interrate grade and snake grade file. I ran or re-ran all of the data to look at the correlation between phenotypes as well as other results. Next step I will spend more time exploring these results

@@
 grid_plot(file_name, spegen, file, type, row_num, col_num)
+
 ```

### 2023-01-11 graphs_newt_snakes/bob_notes.Rmd
added some more r markdown for a few experiments

---
title: "Bob Simulation Sugestion"
output: html_document
date: '2023-01-10'
---

---
title: "Moving Together"
output: html_document
date: '2023-01-10'
---
```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
library(stringr)
library(patchwork)
```

## Goal:

### Questions:

What does it mean to be correlated? Bob made some sugestions for the caculation of phenotype and the slope of the interaction.
prob_of_survive = 1.0/(1+exp(-((compair_pheno-c)/w))) In this equation c=0 and w=10. W may be too high, which could limit interaction/coevolution outcomes.
The way phenotypes are defined might be creating a multiplicative effect: exp(ind.sumOfMutationsOfType(m2)/10))

## Background

## Experiment

I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction with different genetic architectures (GAs) in a spatial setting. I hypothesized that we would see an interaction (co-evolutionary arms race) between newt and snake phenotype under some GA combinations when newts and snakes were evolving over geographical space. Each GA is paired with another GA creating 16 combinations.

GA1 experiment values:

- 1e-8*(0.005)^2 = 2.5e-13
- 1e-9*(0.05)^2 = 2.5e-12
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(5.0)^2 = 2.5e-10

Each GA combination and trial has its own msprime simulation.
I ran 3 experiments a) no exp in the phenotype, b) lower w and, c) both no exp and a lower w

### The data

many of the experiments did not run to completion (i will run this part 3 times)

```{bash, data file gathering 1}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=bob_suggestion/both_lower_w_no_exp
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{bash, data file gathering 2}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=bob_suggestion/lower_w
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{bash, data file gathering 3}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=bob_suggestion/no_exp
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{r, data gathering}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

both_lower_w_no_exp_lit<- read.csv("~/Desktop/bob_suggestion/both_lower_w_no_exp/all_lit.txt" , header = TRUE)

both_lower_w_no_exp_lit$group_rep <- paste0(both_lower_w_no_exp_lit$snake_mu_rate, "_", both_lower_w_no_exp_lit$snake_mu_effect_sd,"_",both_lower_w_no_exp_lit$newt_mu_rate, "_", both_lower_w_no_exp_lit$newt_mu_effect_sd, "_", both_lower_w_no_exp_lit$rep)

both_lower_w_no_exp_lit$group <- paste0(both_lower_w_no_exp_lit$snake_mu_rate, "_", both_lower_w_no_exp_lit$snake_mu_effect_sd,"_",both_lower_w_no_exp_lit$newt_mu_rate, "_", both_lower_w_no_exp_lit$newt_mu_effect_sd)

both_lower_w_no_exp_lit$sim=LETTERS[factor(both_lower_w_no_exp_lit$group)]
both_lower_w_no_exp_lit$dif <- both_lower_w_no_exp_lit$Snake_mean_Pheno-both_lower_w_no_exp_lit$Newt_mean_Pheno

both_lower_w_no_exp_cor<- read.csv("~/Desktop/both_lower_w_no_exp/all_cor.txt" , header = TRUE)
both_lower_w_no_exp_cor$group_rep <- paste0(both_lower_w_no_exp_cor$snake_mu_rate, "_", both_lower_w_no_exp_cor$snake_mu_effect_sd,"_",both_lower_w_no_exp_cor$newt_mu_rate, "_", both_lower_w_no_exp_cor$newt_mu_effect_sd, "_", both_lower_w_no_exp_cor$rep)
both_lower_w_no_exp_cor$group <- paste0(both_lower_w_no_exp_cor$snake_mu_rate, "_", both_lower_w_no_exp_cor$snake_mu_effect_sd,"_",both_lower_w_no_exp_cor$newt_mu_rate, "_", both_lower_w_no_exp_cor$newt_mu_effect_sd)
both_lower_w_no_exp_cor$sim=LETTERS[factor(both_lower_w_no_exp_cor$group)]

# lower w
lower_w_lit<- read.csv("~/Desktop/bob_suggestion/lower_w/all_lit.txt" , header = TRUE)

lower_w_lit$group_rep <- paste0(lower_w_lit$snake_mu_rate, "_", lower_w_lit$snake_mu_effect_sd,"_",lower_w_lit$newt_mu_rate, "_", lower_w_lit$newt_mu_effect_sd, "_", lower_w_lit$rep)

lower_w_lit$group <- paste0(lower_w_lit$snake_mu_rate, "_", lower_w_lit$snake_mu_effect_sd,"_",lower_w_lit$newt_mu_rate, "_", lower_w_lit$newt_mu_effect_sd)

lower_w_lit$sim=LETTERS[factor(lower_w_lit$group)]
lower_w_lit$dif <- lower_w_lit$Snake_mean_Pheno-lower_w_lit$Newt_mean_Pheno

lower_w_cor<- read.csv("~/Desktop/lower_w/all_cor.txt" , header = TRUE)
lower_w_cor$group_rep <- paste0(lower_w_cor$snake_mu_rate, "_", lower_w_cor$snake_mu_effect_sd,"_",lower_w_cor$newt_mu_rate, "_", lower_w_cor$newt_mu_effect_sd, "_", lower_w_cor$rep)
lower_w_cor$group <- paste0(lower_w_cor$snake_mu_rate, "_", lower_w_cor$snake_mu_effect_sd,"_",lower_w_cor$newt_mu_rate, "_", lower_w_cor$newt_mu_effect_sd)
lower_w_cor$sim=LETTERS[factor(lower_w_cor$group)]

# no exp

no_exp_lit<- read.csv("~/Desktop/bob_suggestion/no_exp/all_lit.txt" , header = TRUE)

no_exp_lit$group_rep <- paste0(no_exp_lit$snake_mu_rate, "_", no_exp_lit$snake_mu_effect_sd,"_",no_exp_lit$newt_mu_rate, "_", no_exp_lit$newt_mu_effect_sd, "_", no_exp_lit$rep)

no_exp_lit$group <- paste0(no_exp_lit$snake_mu_rate, "_", no_exp_lit$snake_mu_effect_sd,"_",no_exp_lit$newt_mu_rate, "_", no_exp_lit$newt_mu_effect_sd)

no_exp_lit$sim=LETTERS[factor(no_exp_lit$group)]
no_exp_lit$dif <- no_exp_lit$Snake_mean_Pheno-no_exp_lit$Newt_mean_Pheno

no_exp_cor<- read.csv("~/Desktop/no_exp/all_cor.txt" , header = TRUE)
no_exp_cor$group_rep <- paste0(no_exp_cor$snake_mu_rate, "_", no_exp_cor$snake_mu_effect_sd,"_",no_exp_cor$newt_mu_rate, "_", no_exp_cor$newt_mu_effect_sd, "_", no_exp_cor$rep)
no_exp_cor$group <- paste0(no_exp_cor$snake_mu_rate, "_", no_exp_cor$snake_mu_effect_sd,"_",no_exp_cor$newt_mu_rate, "_", no_exp_cor$newt_mu_effect_sd)
no_exp_cor$sim=LETTERS[factor(no_exp_cor$group)]

```

```{r, cor box set up}

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

suppressMessages(print(plot))

  return(plot)
}

var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  real_snewt_var = var(snewt$dif)
  var_cor_table=data.frame()

  for(i in 1:length(unique(file$snake_newt_rep))){
    pattern<-unique(file$snake_newt_rep)[i]
    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]

    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  }

  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)

  plot <- ggplot(var_cor_table) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

  return(plot)
}

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=both_lower_w_no_exp_lit
#cfile=both_lower_w_no_exp_cor 
 # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]

  if(nrow(cfile)>nrow(file)){
    toDelete <- seq(0, nrow(cfile), 2)
    cfile_short <-  cfile[-toDelete, ]
  }else{
    cfile_short <-  cfile
  }

  if(nrow(cfile_short)>nrow(file)){
      toDelete <- seq(0, nrow(cfile_short), 2)
      cfile_short <-  cfile_short[-toDelete, ]
    }
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}

four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

```

```{r, general file and graph making}

#the functions to make the params file and the summary and heatmap figures

create_parm_file <- function(file, min_gen, max_gen){
params <- data_frame()

for(i in 1:length(unique(file$snake_newt_rep))){

  pattern=unique(file$snake_newt_rep)[i]
  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]

  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=sumitup$snake_mu_rate[1],
                           newt_mu_rate=sumitup$newt_mu_rate[1],
                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
                           rep=sumitup$rep[1])

  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$snake_newt <- paste0(params$snake, "_", params$newt)
return(params)
}

GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}
GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}

build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
  params<-create_parm_file(file, min_gen, max_gen)

 my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))

 if(red_blue==FALSE){
  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
  }
 if(red_blue==TRUE){
  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
 }

  return(my_plot)
}

trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){

  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
  return(plot)
}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
  xlim((-1*themax)-5, themax+5)+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)
}

pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  themin <- min(file$dif) 
  themax <- max(file$dif)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(dif), fill="aquamarine4")+
  xlim((-1*true_max)-1, true_max+1)+

  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]

  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])

dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file=both_lower_w_no_exp_lit
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]

  thepopmin <- min(file$newt_deaths)
  thepopmax <- max(file$newt_deaths)
  thedifmin <- min(file$snake_deaths) 
  thedifmax <- max(file$snake_deaths)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])

dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
  #scale_y_continuous(labels = scales::percent)+
  #xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  #geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

#two_hist_death_all_rep(both_lower_w_no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)

grid_plot<- function(file_name, spegen, file, type, row_num, col_num){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
GA1_type = paste0("generation|", type)

GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
GA1_type <- GA1_type[-1]

data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)

data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)

data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))

main_plot<-ggplot(data_long_type_comp)+

  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  #ylim(0, row_num)+
  #xlim(0, col_num)+
  theme_bw()+
  theme(legend.justification = "top")

if(type != "num_ind"){
main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
 scale_fill_viridis_c()
}
if(type == "num_ind"){
main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Newt/Snake PopSize")+
scale_fill_viridis_c(option = "plasma")
}

snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
newt$snake_value <- snake$measurement
print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))

newt$info <- "middle"

#need to look into, coloring problem
newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"

extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
return(final_plot)}

```

## Mean Phenotype Whole Simulation {.tabset}

### Phenotype differences (both_lower_w_no_exp)
```{r, graphing by gen}
trends_by_gen(both_lower_w_no_exp_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

#aggregate(both_lower_w_no_exp_lit[which(both_lower_w_no_exp_lit$generation>=100 & both_lower_w_no_exp_lit$generation<=50000),]$dif, list(both_lower_w_no_exp_lit[which(both_lower_w_no_exp_lit$generation>=100 & both_lower_w_no_exp_lit$generation<=50000),]$group_rep), FUN=mean)

```

### Table of average Differences (both_lower_w_no_exp)

```{r, average difference}
aggregate(both_lower_w_no_exp_lit[which(both_lower_w_no_exp_lit$generation>=100 & both_lower_w_no_exp_lit$generation<=50000),]$dif, list(both_lower_w_no_exp_lit[which(both_lower_w_no_exp_lit$generation>=100 & both_lower_w_no_exp_lit$generation<=50000),]$group), FUN=mean) 
```

### Phenotype differences (lower_w)
```{r, graphing by gen lw}
trends_by_gen(lower_w_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

```

### Table of average Differences (lower_w)

```{r, average difference lw}
aggregate(lower_w_lit[which(lower_w_lit$generation>=100 & lower_w_lit$generation<=50000),]$dif, list(lower_w_lit[which(lower_w_lit$generation>=100 & lower_w_lit$generation<=50000),]$group), FUN=mean) 
```

### Phenotype differences (no_exp)
```{r, graphing by gen ne}
trends_by_gen(no_exp_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

```

### Table of average Differences (no_exp)

```{r, average difference ne}
aggregate(no_exp_lit[which(no_exp_lit$generation>=100 & no_exp_lit$generation<=50000),]$dif, list(no_exp_lit[which(no_exp_lit$generation>=100 & no_exp_lit$generation<=50000),]$group), FUN=mean) 
```

## {-}

## Connection between higher phenotype and population{.tabset}

### Phenotype differences (both_lower_w_no_exp)
```{r, whale}
min_gen=5000
max_gen=10000
rep=1

whale_gen(both_lower_w_no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (both_lower_w_no_exp)
```{r, popsize and pheno}

suppressMessages(print(two_hist(both_lower_w_no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

### Phenotype differences (lower_wp)
```{r, whale lw}
min_gen=5000
max_gen=10000
rep=1

whale_gen(lower_wp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (lower_wp)
```{r, popsize and pheno lw}

suppressMessages(print(two_hist(lower_wp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

### Phenotype differences (no_exp)
```{r, whale ne}
min_gen=5000
max_gen=10000
rep=1

whale_gen(no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (no_exp)
```{r, popsize and pheno ne}

suppressMessages(print(two_hist(no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

## {-}

## Correlation{.tabset}
HEREREERERERER
### cor (both_lower_w_no_exp)
```{r, combo myplots}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

### cor (lower_w)
```{r, combo myplots lw}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(lower_w_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

### cor (no_exp)
```{r, combo myplots ne}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(no_exp_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

## {-}

## Correlation Histograms Both{.tabset}

### Plot 1
```{r, GA1 cor by dif windows}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(both_lower_w_no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation Histograms Lower w {.tabset}

### Plot 1
```{r, GA1 cor by dif windows lw}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2 lw}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3 lw}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4 lw}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5 lw}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6 lw}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7 lw}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8 lw}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9 lw}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10 lw}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(lower_w_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation Histograms no exp {.tabset}

### Plot 1
```{r, GA1 cor by dif windows ne}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2 ne}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3 ne}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4 ne}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5 ne}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6 ne}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7 ne}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8 ne}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9 ne}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10 ne}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(no_exp_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation across time (both_lower_w_no_exp)  {.tabset}

### Random 1 (both_lower_w_no_exp)  
```{r, GA1 cor and pheno}
GA1_pattern <- unique(paste0(both_lower_w_no_exp_lit$snake_mu_rate, "_", both_lower_w_no_exp_lit$snake_mu_effect_sd,"_",both_lower_w_no_exp_lit$newt_mu_rate, "_", both_lower_w_no_exp_lit$newt_mu_effect_sd, "_", both_lower_w_no_exp_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(both_lower_w_no_exp_lit, both_lower_w_no_exp_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(both_lower_w_no_exp_lit, both_lower_w_no_exp_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (both_lower_w_no_exp)
```{r, random cor-pheno plot 2}

cor_trends_by_gen(both_lower_w_no_exp_lit, both_lower_w_no_exp_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (both_lower_w_no_exp)
```{r, random cor-pheno plot 3}

cor_trends_by_gen(both_lower_w_no_exp_lit, both_lower_w_no_exp_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## Correlation across time (lower_w)  {.tabset}

### Random 1 (lower_w)  
```{r, GA1 cor and pheno  lw}
GA1_pattern <- unique(paste0(lower_w_lit$snake_mu_rate, "_", lower_w_lit$snake_mu_effect_sd,"_",lower_w_lit$newt_mu_rate, "_", lower_w_lit$newt_mu_effect_sd, "_", lower_w_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(lower_w_lit, lower_w_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(lower_w_lit, lower_w_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (lower_w)
```{r, random cor-pheno plot 2  lw}

cor_trends_by_gen(lower_w_lit, lower_w_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (lower_w)
```{r, random cor-pheno plot 3  lw}

cor_trends_by_gen(lower_w_lit, lower_w_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## Correlation across time (no_exp)  {.tabset}

### Random 1 (no_exp)  
```{r, GA1 cor and pheno ne}
GA1_pattern <- unique(paste0(no_exp_lit$snake_mu_rate, "_", no_exp_lit$snake_mu_effect_sd,"_",no_exp_lit$newt_mu_rate, "_", no_exp_lit$newt_mu_effect_sd, "_", no_exp_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(no_exp_lit, no_exp_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(no_exp_lit, no_exp_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (no_exp)
```{r, random cor-pheno plot 2 ne}

cor_trends_by_gen(no_exp_lit, no_exp_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (no_exp)
```{r, random cor-pheno plot 3 ne}

cor_trends_by_gen(no_exp_lit, no_exp_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (both_lower_w_no_exp) {.tabset}

### Pheno Beginning (both_lower_w_no_exp)

```{r, early plots}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(both_lower_w_no_exp_lit$rep))){
#   myine<-whale_gen(both_lower_w_no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(both_lower_w_no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[1])
```

### Pheno Middle (both_lower_w_no_exp)

```{r, middle plots}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(both_lower_w_no_exp_lit$rep))){
#   myine<-whale_gen(both_lower_w_no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(both_lower_w_no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[1])
```

### Pheno End (both_lower_w_no_exp)

```{r, end plots}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(both_lower_w_no_exp_lit$rep))){
#   myine<-whale_gen(both_lower_w_no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(both_lower_w_no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[1])
```

### Dif Beginning (both_lower_w_no_exp)
```{r, early plots 1a}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(both_lower_w_no_exp_lit$rep))){
#   myine<-two_hist(both_lower_w_no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(both_lower_w_no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[1] )

```

### Dif Middle (both_lower_w_no_exp)
```{r, early plots 2a}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(both_lower_w_no_exp_lit$rep))){
#   myine<-two_hist(both_lower_w_no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(both_lower_w_no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[1] )

```

### Dif End (both_lower_w_no_exp)
```{r, early plots 3a}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(both_lower_w_no_exp_lit$rep))){
#   myine<-two_hist(both_lower_w_no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(both_lower_w_no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(both_lower_w_no_exp_lit$rep)[1] )

```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (lower_w) {.tabset}

### Pheno Beginning (lower_w)

```{r, early plots lw}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(lower_w_lit$rep))){
#   myine<-whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[1])
```

### Pheno Middle (lower_w)

```{r, middle plots lw}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(lower_w_lit$rep))){
#   myine<-whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[1])
```

### Pheno End (lower_w)

```{r, end plots lw}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(lower_w_lit$rep))){
#   myine<-whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[1])
```

### Dif Beginning (lower_w)
```{r, early plots 1a lw}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(lower_w_lit$rep))){
#   myine<-two_hist(lower_w_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(lower_w_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[1] )

```

### Dif Middle (lower_w)
```{r, early plots 2a lw}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(lower_w_lit$rep))){
#   myine<-two_hist(lower_w_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(lower_w_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[1] )

```

### Dif End (lower_w)
```{r, early plots 3a lw}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(lower_w_lit$rep))){
#   myine<-two_hist(lower_w_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(lower_w_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(lower_w_lit$rep)[1] )

```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (no_exp) {.tabset}

### Pheno Beginning (no_exp)

```{r, early plots ne}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(no_exp_lit$rep))){
#   myine<-whale_gen(no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[1])
```

### Pheno Middle (no_exp)

```{r, middle plots ne}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(no_exp_lit$rep))){
#   myine<-whale_gen(no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[1])
```

### Pheno End (no_exp)

```{r, end plots ne}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(no_exp_lit$rep))){
#   myine<-whale_gen(no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[1])
```

### Dif Beginning (no_exp)
```{r, early plots 1a ne}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(no_exp_lit$rep))){
#   myine<-two_hist(no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[1] )

```

### Dif Middle (no_exp)
```{r, early plots 2a ne}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(no_exp_lit$rep))){
#   myine<-two_hist(no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[1] )

```

### Dif End (no_exp)
```{r, early plots 3a ne}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(no_exp_lit$rep))){
#   myine<-two_hist(no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(no_exp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_exp_lit$rep)[1] )

```

## {-}

## Summary (both_lower_w_no_exp) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary}

min_gen=100
max_gen=5000
GA_summary(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3}
min_gen=45000
max_gen=50000

# summary
GA_summary(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1}

min_gen=100
max_gen=5000

GA_summary(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2}
min_gen=25000
max_gen=30000

GA_summary(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3}
min_gen=45000
max_gen=50000
GA_summary(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1}
min_gen=100
max_gen=5000
#

GA_summary_by_species(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1}
min_gen=100
max_gen=5000
#

GA_summary_by_species(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Summary (lower_w) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary lw}

min_gen=100
max_gen=5000
GA_summary(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2 lw}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3 lw}
min_gen=45000
max_gen=50000

# summary
GA_summary(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1 lw}

min_gen=100
max_gen=5000

GA_summary(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2 lw}
min_gen=25000
max_gen=30000

GA_summary(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3 lw}
min_gen=45000
max_gen=50000
GA_summary(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1 lw}
min_gen=100
max_gen=5000
#

GA_summary_by_species(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2 lw}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3 lw}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1 lw}
min_gen=100
max_gen=5000
#

GA_summary_by_species(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2 lw}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3 lw}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(lower_w_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Summary (no_exp) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary ne}

min_gen=100
max_gen=5000
GA_summary(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2 ne}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3 ne}
min_gen=45000
max_gen=50000

# summary
GA_summary(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1 ne}

min_gen=100
max_gen=5000

GA_summary(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2 ne}
min_gen=25000
max_gen=30000

GA_summary(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3 ne}
min_gen=45000
max_gen=50000
GA_summary(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1 ne}
min_gen=100
max_gen=5000
#

GA_summary_by_species(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2 ne}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3 ne}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1 ne}
min_gen=100
max_gen=5000
#

GA_summary_by_species(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2 ne}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3 ne}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(no_exp_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Heatmap (both_lower_w_no_exp) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)  
```{r, early plots Heatmap 2}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late) 
```{r, early plots Heatmap 3}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early) 
```{r, early plots Heatmap pheno 1}
min_gen=100
max_gen=5000
build_heatmap(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid) 
```{r, early plots Heatmap pheno 2}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late) 
```{r, early plots Heatmap pheno 3}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(both_lower_w_no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

## Heatmap (lower_w) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap lw}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(lower_w_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)  
```{r, early plots Heatmap 2 lw}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(lower_w_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late) 
```{r, early plots Heatmap 3 lw}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(lower_w_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early) 
```{r, early plots Heatmap pheno 1 lw}
min_gen=100
max_gen=5000
build_heatmap(lower_w_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid) 
```{r, early plots Heatmap pheno 2 lw}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(lower_w_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late) 
```{r, early plots Heatmap pheno 3 lw}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(lower_w_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

## Heatmap (no_exp) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap ne}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)  
```{r, early plots Heatmap 2 ne}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late) 
```{r, early plots Heatmap 3 ne}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early) 
```{r, early plots Heatmap pheno 1 ne}
min_gen=100
max_gen=5000
build_heatmap(no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid) 
```{r, early plots Heatmap pheno 2 ne}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late) 
```{r, early plots Heatmap pheno 3 ne}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(no_exp_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

```{r, red in grid files}
require(readr)
both_lower_w_no_exp_grid<- read.csv("~/Desktop/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep)
both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd)
both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)]
both_lower_w_no_exp_grid$grid_num = 5

```

```{r, red in grid files lw}
require(readr)
lower_w_grid<- read.csv("~/Desktop/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep)
lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd)
lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)]
lower_w_grid$grid_num = 5

```

```{r, red in grid files ne}
require(readr)
no_exp_grid<- read.csv("~/Desktop/no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
no_exp_grid$group_rep <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd, "_", no_exp_grid$rep)
no_exp_grid$group <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd)
no_exp_grid$sim=LETTERS[factor(no_exp_grid$group)]
no_exp_grid$grid_num = 5

```

## What is up with the correlations

## Early Simulation Correlation (both_lower_w_no_exp)  {.tabset}

### Mean 
```{r, cor grid high cor mean}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

```

## {-}

## Early Simulation Correlation (lower_w)  {.tabset}

### Mean 
```{r, cor grid high cor mean}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

```

## {-}

## Early Simulation Correlation (no_exp)  {.tabset}

### Mean 
```{r, cor grid high cor mean}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

```

## {-}

```{r, red in grid files 2}
require(readr)
both_lower_w_no_exp_grid<- read.csv("~/Desktop/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep)
both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd)
both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)]
both_lower_w_no_exp_grid$grid_num = 5

```

```{r, red in grid files 2 lw}
require(readr)
lower_w_grid<- read.csv("~/Desktop/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep)
lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd)
lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)]
lower_w_grid$grid_num = 5

```

```{r, red in grid files 2 ne}
require(readr)
no_exp_grid<- read.csv("~/Desktop/no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
no_exp_grid$group_rep <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd, "_", no_exp_grid$rep)
no_exp_grid$group <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd)
no_exp_grid$sim=LETTERS[factor(no_exp_grid$group)]
no_exp_grid$grid_num = 5

```

## Late Simulation Correlation (both_lower_w_no_exp) {.tabset}

### Mean 
```{r, cor grid high cor mean late}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max late}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min late}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

```

## {-}

## Late Simulation Correlation (lower_w) {.tabset}

### Mean 
```{r, cor grid high cor mean late}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max late}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min late}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

```

## {-}

## Late Simulation Correlation (no_exp) {.tabset}

### Mean 
```{r, cor grid high cor mean late}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max late}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min late}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

```

## {-}

### 2023-01-11 graphs_newt_snakes/move_together.Rmd
added some more r markdown for a few experiments

--- 2022-12-06 graphs_newt_snakes/dif_cost_grade.Rmd
@@
 ---
-title: "Cost Gradient"
+title: "Moving Together"
 output: html_document
-date: '2022-10-21'
+date: '2023-01-10'
 ---
-
 ```{r setup, include=FALSE}
@@
 
-What does it mean to be correlated?
+What does it mean to be correlated? Might this occur if I simulatate some controlled movement?
 
@@
 thepath=/Users/victoria/Desktop/
-foldername=cost_grade
+foldername=move_together
 thefolder=${thepath}${foldername}/*
@@
 
-cost_grade_lit<- read.csv("~/Desktop/cost_grade/all_lit.txt" , header = TRUE)
-
-cost_grade_lit$group_rep <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep)
-
-cost_grade_lit$group <- paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd)
-
-cost_grade_lit$sim=LETTERS[factor(cost_grade_lit$group)]
-cost_grade_lit$dif <- cost_grade_lit$Snake_mean_Pheno-cost_grade_lit$Newt_mean_Pheno
-
-cost_grade_cor<- read.csv("~/Desktop/cost_grade/all_cor.txt" , header = TRUE)
-cost_grade_cor$group_rep <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd, "_", cost_grade_cor$rep)
-cost_grade_cor$group <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd)
-cost_grade_cor$sim=LETTERS[factor(cost_grade_cor$group)]
+move_together_lit<- read.csv("~/Desktop/move_together/all_lit.txt" , header = TRUE)
+
+move_together_lit$group_rep <- paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd, "_", move_together_lit$rep)
+
+move_together_lit$group <- paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd)
+
+move_together_lit$sim=LETTERS[factor(move_together_lit$group)]
+move_together_lit$dif <- move_together_lit$Snake_mean_Pheno-move_together_lit$Newt_mean_Pheno
+
+move_together_cor<- read.csv("~/Desktop/move_together/all_cor.txt" , header = TRUE)
+move_together_cor$group_rep <- paste0(move_together_cor$snake_mu_rate, "_", move_together_cor$snake_mu_effect_sd,"_",move_together_cor$newt_mu_rate, "_", move_together_cor$newt_mu_effect_sd, "_", move_together_cor$rep)
+move_together_cor$group <- paste0(move_together_cor$snake_mu_rate, "_", move_together_cor$snake_mu_effect_sd,"_",move_together_cor$newt_mu_rate, "_", move_together_cor$newt_mu_effect_sd)
+move_together_cor$sim=LETTERS[factor(move_together_cor$group)]
 
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=cost_grade_lit
-#cfile=cost_grade_cor 
+#file=move_together_lit
+#cfile=move_together_cor 
  # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=cost_grade_lit
+  #file=move_together_lit
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 
@@
 ```{r, graphing by gen}
-trends_by_gen(cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 250, 50000, rep=1)
-
-#aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group_rep), FUN=mean)
+trends_by_gen(move_together_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+#aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$dif, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$group_rep), FUN=mean)
 
@@
 ```{r, average difference}
-aggregate(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$dif, list(cost_grade_lit[which(cost_grade_lit$generation>=100 & cost_grade_lit$generation<=50000),]$group), FUN=mean)
+aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$dif, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$group), FUN=mean)
 ```
@@
 
-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
-suppressMessages(print(two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
-
-#suppressMessages(print(two_hist_all_rep(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+suppressMessages(print(two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
 
@@
 
-boxplot_cors_by_gen(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-#four_types_boxplot_cors_by_gen(cost_grade_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(move_together_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(move_together_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
@@
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ```{r, GA1 cor and pheno}
-GA1_pattern <- unique(paste0(cost_grade_lit$snake_mu_rate, "_", cost_grade_lit$snake_mu_effect_sd,"_",cost_grade_lit$newt_mu_rate, "_", cost_grade_lit$newt_mu_effect_sd, "_", cost_grade_lit$rep))
+GA1_pattern <- unique(paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd, "_", move_together_lit$rep))
 
@@
 # for(i in myrandomlist){
-#   myine<-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   myine<-cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
 #   plot(myine)
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
 
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
 ```
@@
 
-cor_trends_by_gen(cost_grade_lit, cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
 ```
@@
 
-# for(i in 1:length(unique(cost_grade_lit$rep))){
-#   myine<-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i])
+# for(i in 1:length(unique(move_together_lit$rep))){
+#   myine<-whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i])
 #   plot(myine)
@@
 # }
-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1])
+whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1])
 ```
@@
 
-# for(i in 1:length(unique(cost_grade_lit$rep))){
-#   myine<-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[i] )
+# for(i in 1:length(unique(move_together_lit$rep))){
+#   myine<-two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i] )
 #   suppressMessages(plot(myine))
@@
 
-two_hist(cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(cost_grade_lit$rep)[1] )
+two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1] )
 
@@
 max_gen=5000
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
@@
 
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 ```
@@
 
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 max_gen=50000
-GA_summary(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 
-GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
 
@@
 
-GA_summary_by_species(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
 
@@
 #heatmap
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 ```
@@
 #heatmap
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
@@
 max_gen=5000
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 require(readr)
-cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
-cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
-cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
-cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
-cost_grade_grid$grid_num = 5
+move_together_grid<- read.csv("~/Desktop/move_together/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+move_together_grid$group_rep <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd, "_", move_together_grid$rep)
+move_together_grid$group <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd)
+move_together_grid$sim=LETTERS[factor(move_together_grid$group)]
+move_together_grid$grid_num = 5
 
@@
 
-file=cost_grade_grid
+file=move_together_grid
 file_name="1e-11_5_1e-10_0.5_0"
@@
 require(readr)
-cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
-cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
-cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
-cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
-cost_grade_grid$grid_num = 5
+move_together_grid<- read.csv("~/Desktop/move_together/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
+move_together_grid$group_rep <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd, "_", move_together_grid$rep)
+move_together_grid$group <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd)
+move_together_grid$sim=LETTERS[factor(move_together_grid$group)]
+move_together_grid$grid_num = 5
 

### 2023-01-11 Slim4/snake_newt_gv_slimv4.py
Worjed with Peter to make my code compatible with slim4 will be used for future projects

@@ -1,0 +1,128 @@
+import pyslim
+import tskit
+import msprime
+import numpy as np
+import os
+import sys
+from sys import argv
+# import util
+
+sequence_length = 10000000
+mytag="no_tag"
+
+datadir = "."
+snake_mu_rate = 6.25e-12
+newt_mu_rate = 2.5e-09 # does this need to be 50 times more than the snake?
+snake_mu_effect_sd = 0.2
+newt_mu_effect_sd = 0.2
+mytag="beta_exp"
+'''
+
+snake_mu_rate = float(sys.argv[1])
+newt_mu_rate = float(sys.argv[2])  # does this need to be 50 times more than the snake?
+snake_mu_effect_sd = float(sys.argv[3])
+newt_mu_effect_sd = float(sys.argv[4])
+datadir = sys.argv[5]
+mytag = sys.argv[6]
+'''
+newt_name_of_file = "newt_" + "nu_" + str(newt_mu_rate) + "_nue_" + str(newt_mu_effect_sd) + "_" + mytag + ".init.trees"
+snake_name_of_file = "snake_" + "su_" + str(snake_mu_rate) + "_sue_" + str(snake_mu_effect_sd) + "_" + mytag + ".init.trees"
+print(newt_name_of_file, snake_name_of_file)
+
+
+def add_mutations(ts, mut_type, mu_rate, effect_sd, next_id=0):
+    # s_fn draws the selection coefficient
+    # need to assign metadata to be able to put the mutations in
+    mut_model = msprime.SLiMMutationModel(type=mut_type, next_id=next_id)
+    mts = msprime.sim_mutations(
+        ts,
+        mu_rate,
+        model=mut_model,
+    )
+    print(f"The tree sequence now has {mts.num_mutations} mutations, at "
+          f"{mts.num_sites} distinct sites.")
+    tables = mts.tables
+    tables.mutations.clear()
+    mut_map = {}
+    for m in mts.mutations():
+        md_list = m.metadata["mutation_list"]
+        slim_ids = m.derived_state.split(",")
+        assert len(slim_ids) == len(md_list)
+        for sid, md in zip(slim_ids, md_list):
+            if sid not in mut_map:
+                mut_map[sid] = np.random.normal(loc=0.0, scale=effect_sd)
+            md["selection_coeff"] = mut_map[sid]
+        tables.mutations.add_row(
+            site=m.site,
+            node=m.node,
+            time=m.time,
+            derived_state=m.derived_state,
[…]

### 2023-01-18 graphs_newt_snakes/Same_V.Rmd
I have updated the results for the last set of experiments. Tomorrow I will need to spend some time reviewing them.

---
title: "Same V"
output: html_document
date: '2023-01-13'
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
library(stringr)
library(patchwork)
```

## Goal:

### Questions:

What does it mean to be correlated?

## Background

## Experiment

I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction with different genetic architectures (GAs) in a spatial setting. I hypothesized that we would see an interaction (co-evolutionary arms race) between newt and snake phenotype under some GA combinations when newts and snakes were evolving over geographical space. Each GA is paired with another GA creating 16 combinations.

Experiment values:

### The data

many of the experiments did not run to completion (i will run this part 3 times)

```{bash, data file gathering 1}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=same_v/v_a
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{bash, data file gathering 2}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=same_v/v_b
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{bash, data file gathering 33}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=same_v/v_c
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{bash, data file gathering 32}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=same_v/v_d
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{r, data gathering}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

v_a_lit<- read.csv("~/Desktop/same_v/v_a/all_lit.txt" , header = TRUE)

v_a_lit$group_rep <- paste0(v_a_lit$snake_mu_rate, "_", v_a_lit$snake_mu_effect_sd,"_",v_a_lit$newt_mu_rate, "_", v_a_lit$newt_mu_effect_sd, "_", v_a_lit$rep)

v_a_lit$group <- paste0(v_a_lit$snake_mu_rate, "_", v_a_lit$snake_mu_effect_sd,"_",v_a_lit$newt_mu_rate, "_", v_a_lit$newt_mu_effect_sd)

v_a_lit$sim=LETTERS[factor(v_a_lit$group)]
v_a_lit$dif <- v_a_lit$Snake_mean_Pheno-v_a_lit$Newt_mean_Pheno

v_a_cor<- read.csv("~/Desktop/same_v/v_a/all_cor.txt" , header = TRUE)
v_a_cor$group_rep <- paste0(v_a_cor$snake_mu_rate, "_", v_a_cor$snake_mu_effect_sd,"_",v_a_cor$newt_mu_rate, "_", v_a_cor$newt_mu_effect_sd, "_", v_a_cor$rep)
v_a_cor$group <- paste0(v_a_cor$snake_mu_rate, "_", v_a_cor$snake_mu_effect_sd,"_",v_a_cor$newt_mu_rate, "_", v_a_cor$newt_mu_effect_sd)
v_a_cor$sim=LETTERS[factor(v_a_cor$group)]

# Mu B
v_b_lit<- read.csv("~/Desktop/same_v/v_b/all_lit.txt" , header = TRUE)

v_b_lit$group_rep <- paste0(v_b_lit$snake_mu_rate, "_", v_b_lit$snake_mu_effect_sd,"_",v_b_lit$newt_mu_rate, "_", v_b_lit$newt_mu_effect_sd, "_", v_b_lit$rep)

v_b_lit$group <- paste0(v_b_lit$snake_mu_rate, "_", v_b_lit$snake_mu_effect_sd,"_",v_b_lit$newt_mu_rate, "_", v_b_lit$newt_mu_effect_sd)

v_b_lit$sim=LETTERS[factor(v_b_lit$group)]
v_b_lit$dif <- v_b_lit$Snake_mean_Pheno-v_b_lit$Newt_mean_Pheno

v_b_cor<- read.csv("~/Desktop/same_v/v_b/all_cor.txt" , header = TRUE)
v_b_cor$group_rep <- paste0(v_b_cor$snake_mu_rate, "_", v_b_cor$snake_mu_effect_sd,"_",v_b_cor$newt_mu_rate, "_", v_b_cor$newt_mu_effect_sd, "_", v_b_cor$rep)
v_b_cor$group <- paste0(v_b_cor$snake_mu_rate, "_", v_b_cor$snake_mu_effect_sd,"_",v_b_cor$newt_mu_rate, "_", v_b_cor$newt_mu_effect_sd)
v_b_cor$sim=LETTERS[factor(v_b_cor$group)]

# no exp

v_c_lit<- read.csv("~/Desktop/same_v/v_c/all_lit.txt" , header = TRUE)

v_c_lit$group_rep <- paste0(v_c_lit$snake_mu_rate, "_", v_c_lit$snake_mu_effect_sd,"_",v_c_lit$newt_mu_rate, "_", v_c_lit$newt_mu_effect_sd, "_", v_c_lit$rep)

v_c_lit$group <- paste0(v_c_lit$snake_mu_rate, "_", v_c_lit$snake_mu_effect_sd,"_",v_c_lit$newt_mu_rate, "_", v_c_lit$newt_mu_effect_sd)

v_c_lit$sim=LETTERS[factor(v_c_lit$group)]
v_c_lit$dif <- v_c_lit$Snake_mean_Pheno-v_c_lit$Newt_mean_Pheno

v_c_cor<- read.csv("~/Desktop/same_v/v_c/all_cor.txt" , header = TRUE)
v_c_cor$group_rep <- paste0(v_c_cor$snake_mu_rate, "_", v_c_cor$snake_mu_effect_sd,"_",v_c_cor$newt_mu_rate, "_", v_c_cor$newt_mu_effect_sd, "_", v_c_cor$rep)
v_c_cor$group <- paste0(v_c_cor$snake_mu_rate, "_", v_c_cor$snake_mu_effect_sd,"_",v_c_cor$newt_mu_rate, "_", v_c_cor$newt_mu_effect_sd)
v_c_cor$sim=LETTERS[factor(v_c_cor$group)]

# mu d

v_d_lit<- read.csv("~/Desktop/same_v/v_d/all_lit.txt" , header = TRUE)

v_d_lit$group_rep <- paste0(v_d_lit$snake_mu_rate, "_", v_d_lit$snake_mu_effect_sd,"_",v_d_lit$newt_mu_rate, "_", v_d_lit$newt_mu_effect_sd, "_", v_d_lit$rep)

v_d_lit$group <- paste0(v_d_lit$snake_mu_rate, "_", v_d_lit$snake_mu_effect_sd,"_",v_d_lit$newt_mu_rate, "_", v_d_lit$newt_mu_effect_sd)

v_d_lit$sim=LETTERS[factor(v_d_lit$group)]
v_d_lit$dif <- v_d_lit$Snake_mean_Pheno-v_d_lit$Newt_mean_Pheno

v_d_cor<- read.csv("~/Desktop/same_v/v_d/all_cor.txt" , header = TRUE)
v_d_cor$group_rep <- paste0(v_d_cor$snake_mu_rate, "_", v_d_cor$snake_mu_effect_sd,"_",v_d_cor$newt_mu_rate, "_", v_d_cor$newt_mu_effect_sd, "_", v_d_cor$rep)
v_d_cor$group <- paste0(v_d_cor$snake_mu_rate, "_", v_d_cor$snake_mu_effect_sd,"_",v_d_cor$newt_mu_rate, "_", v_d_cor$newt_mu_effect_sd)
v_d_cor$sim=LETTERS[factor(v_d_cor$group)]

```

```{r, cor box set up}

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

suppressMessages(print(plot))

  return(plot)
}

var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  real_snewt_var = var(snewt$dif)
  var_cor_table=data.frame()

  for(i in 1:length(unique(file$snake_newt_rep))){
    pattern<-unique(file$snake_newt_rep)[i]
    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]

    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  }

  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)

  plot <- ggplot(var_cor_table) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

  return(plot)
}

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=v_a_lit
#cfile=v_a_cor 
 # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]

  if(nrow(cfile)>nrow(file)){
    toDelete <- seq(0, nrow(cfile), 2)
    cfile_short <-  cfile[-toDelete, ]
  }else{
    cfile_short <-  cfile
  }

  if(nrow(cfile_short)>nrow(file)){
      toDelete <- seq(0, nrow(cfile_short), 2)
      cfile_short <-  cfile_short[-toDelete, ]
    }
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}

four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

```

```{r, general file and graph making}

#the functions to make the params file and the summary and heatmap figures

create_parm_file <- function(file, min_gen, max_gen){
params <- data_frame()

for(i in 1:length(unique(file$snake_newt_rep))){

  pattern=unique(file$snake_newt_rep)[i]
  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]

  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=sumitup$snake_mu_rate[1],
                           newt_mu_rate=sumitup$newt_mu_rate[1],
                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
                           rep=sumitup$rep[1])

  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$snake_newt <- paste0(params$snake, "_", params$newt)
return(params)
}

 create_parm_file_nc <- function(file, min_gen, max_gen){

   file$test_factor <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params <- data_frame()

for(i in 1:length(unique(file$test_factor))){

  pattern=unique(file$test_factor)[i]

  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$test_factor ==pattern),]

  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=unlist(strsplit(pattern, "_"))[2],
                           newt_mu_rate=unlist(strsplit(pattern, "_"))[4],
                           snake_mu_effect_sd=unlist(strsplit(pattern, "_"))[3],
                           newt_mu_effect_sd=unlist(strsplit(pattern, "_"))[5],
                           rep=unlist(strsplit(pattern, "_"))[6],
                           test_factor=pattern)

  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$snake_newt <- paste0(params$snake, "_", params$newt)
return(params)
}

GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label ){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)
params = na.omit(params)
my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}

GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)
params = na.omit(params)
my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}

build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
  params<-create_parm_file(file, min_gen, max_gen)
  params = na.omit(params)

 my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))

 if(red_blue==FALSE){
  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
  }
 if(red_blue==TRUE){
  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
 }

  return(my_plot)
}

trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){

  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
  return(plot)
}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
  xlim((-1*themax)-5, themax+5)+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)
}

pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  themin <- min(file$dif) 
  themax <- max(file$dif)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(dif), fill="aquamarine4")+
  xlim((-1*true_max)-1, true_max+1)+

  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]

  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])

dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file=v_a_lit
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]

  thepopmin <- min(file$newt_deaths)
  thepopmax <- max(file$newt_deaths)
  thedifmin <- min(file$snake_deaths) 
  thedifmax <- max(file$snake_deaths)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])

dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
  #scale_y_continuous(labels = scales::percent)+
  #xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  #geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

#two_hist_death_all_rep(v_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)

grid_plot<- function(file_name, spegen, file, type, row_num, col_num){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
GA1_type = paste0("generation|", type)

GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
GA1_type <- GA1_type[-1]

data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)

data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)

data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))

main_plot<-ggplot(data_long_type_comp)+

  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  #ylim(0, row_num)+
  #xlim(0, col_num)+
  theme_bw()+
  theme(legend.justification = "top")

if(type != "num_ind"){
main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
 scale_fill_viridis_c()
}
if(type == "num_ind"){
main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Newt/Snake PopSize")+
scale_fill_viridis_c(option = "plasma")
}

snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
newt$snake_value <- snake$measurement
print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))

newt$info <- "middle"

#need to look into, coloring problem
newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"

extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
return(final_plot)}

```

## Mean Phenotype Whole Simulation {.tabset}

### Phenotype differences (v_a)
```{r, graphing by gen}
trends_by_gen(v_a_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

#aggregate(v_a_lit[which(v_a_lit$generation>=100 & v_a_lit$generation<=50000),]$dif, list(v_a_lit[which(v_a_lit$generation>=100 & v_a_lit$generation<=50000),]$group_rep), FUN=mean)

```

### Table of average Differences (v_a)

```{r, average difference}
aggregate(v_a_lit[which(v_a_lit$generation>=100 & v_a_lit$generation<=50000),]$dif, list(v_a_lit[which(v_a_lit$generation>=100 & v_a_lit$generation<=50000),]$group), FUN=mean) 
```

### Phenotype differences (v_b)
```{r, graphing by gen lw}
trends_by_gen(v_b_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

```

### Table of average Differences (v_b)

```{r, average difference lw}
aggregate(v_b_lit[which(v_b_lit$generation>=100 & v_b_lit$generation<=50000),]$dif, list(v_b_lit[which(v_b_lit$generation>=100 & v_b_lit$generation<=50000),]$group), FUN=mean) 
```

### Phenotype differences (v_c)
```{r, graphing by gen ne}
trends_by_gen(v_c_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

```

### Table of average Differences (v_c)

```{r, average difference ne}
aggregate(v_c_lit[which(v_c_lit$generation>=100 & v_c_lit$generation<=50000),]$dif, list(v_c_lit[which(v_c_lit$generation>=100 & v_c_lit$generation<=50000),]$group), FUN=mean) 
```

### Phenotype differences (v_d)
```{r, graphing by gen vd}
trends_by_gen(v_d_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

```

### Table of average Differences (v_d)

```{r, average difference vd}
aggregate(v_d_lit[which(v_d_lit$generation>=100 & v_d_lit$generation<=50000),]$dif, list(v_d_lit[which(v_d_lit$generation>=100 & v_d_lit$generation<=50000),]$group), FUN=mean) 
```

## {-}

## Connection between higher phenotype and population{.tabset}

### Phenotype differences (v_a)
```{r, whale}
min_gen=5000
max_gen=10000
rep=1

whale_gen(v_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (v_a)
```{r, popsize and pheno}

suppressMessages(print(two_hist(v_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

### Phenotype differences (v_b)
```{r, whale lw}
min_gen=5000
max_gen=10000
rep=1

whale_gen(v_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (v_b)
```{r, popsize and pheno lw}

suppressMessages(print(two_hist(v_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

### Phenotype differences (v_c)
```{r, whale ne}
min_gen=5000
max_gen=10000
rep=1

whale_gen(v_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (v_c)
```{r, popsize and pheno ne}

suppressMessages(print(two_hist(v_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

### Phenotype differences (v_d)
```{r, whale vd}
min_gen=5000
max_gen=10000
rep=1

whale_gen(v_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (v_d)
```{r, popsize and pheno vd}

suppressMessages(print(two_hist(v_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

## {-}

## Correlation{.tabset}

### cor (v_a)
```{r, combo myplots}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(v_a_cor, "Simulation Correlation Comparied to Real Correlation Trials", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

### cor (v_b)
```{r, combo myplots vb}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(v_b_cor, "Simulation Correlation Comparied to Real Correlation Trials", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

### cor (v_c)
```{r, combo myplots ne}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(v_c_cor, "Simulation Correlation Comparied to Real Correlation Trials", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

### cor (v_d)
```{r, combo myplots vd}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(v_d_cor, "Simulation Correlation Comparied to Real Correlation Trials", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

## {-}

## Correlation Histograms Mu A{.tabset}

### Plot 1
```{r, GA1 cor by dif windows}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(v_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation Histograms Mu B {.tabset}

### Plot 1
```{r, GA1 cor by dif windows vb}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2 bvv}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3 vb}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4 vb}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5 vb}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6 bv}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7 vb}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8 vb}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9 vb}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10 vb}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(v_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation Histograms Mu C {.tabset}

### Plot 1
```{r, GA1 cor by dif windows ne}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2 ne}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3 ne}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4 ne}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5 ne}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6 ne}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7 ne}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8 ne}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9 ne}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10 ne}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(v_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation Histograms Mu D {.tabset}

### Plot 1
```{r, GA1 cor by dif windows vd}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2 vd}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3 vd}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4 vd}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5 vd}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6 vd}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7 vd}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8 vd}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9 vd}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10 vd}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(v_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation across time (v_a)  {.tabset}

### Random 1 (v_a)  
```{r, GA1 cor and pheno}
GA1_pattern <- unique(paste0(v_a_lit$snake_mu_rate, "_", v_a_lit$snake_mu_effect_sd,"_",v_a_lit$newt_mu_rate, "_", v_a_lit$newt_mu_effect_sd, "_", v_a_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(v_a_lit, v_a_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(v_a_lit, v_a_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (v_a)
```{r, random cor-pheno plot 2}

cor_trends_by_gen(v_a_lit, v_a_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (v_a)
```{r, random cor-pheno plot 3}

cor_trends_by_gen(v_a_lit, v_a_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## Correlation across time (v_b)  {.tabset}

### Random 1 (v_b)  
```{r, GA1 cor and pheno  lw}
GA1_pattern <- unique(paste0(v_b_lit$snake_mu_rate, "_", v_b_lit$snake_mu_effect_sd,"_",v_b_lit$newt_mu_rate, "_", v_b_lit$newt_mu_effect_sd, "_", v_b_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(v_b_lit, v_b_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(v_b_lit, v_b_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (v_b)
```{r, random cor-pheno plot 2  lw}

cor_trends_by_gen(v_b_lit, v_b_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (v_b)
```{r, random cor-pheno plot 3  lw}

cor_trends_by_gen(v_b_lit, v_b_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## Correlation across time (v_c)  {.tabset}

### Random 1 (v_c)  
```{r, GA1 cor and pheno ne}
GA1_pattern <- unique(paste0(v_c_lit$snake_mu_rate, "_", v_c_lit$snake_mu_effect_sd,"_",v_c_lit$newt_mu_rate, "_", v_c_lit$newt_mu_effect_sd, "_", v_c_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(v_c_lit, v_c_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(v_c_lit, v_c_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (v_c)
```{r, random cor-pheno plot 2 ne}

cor_trends_by_gen(v_c_lit, v_c_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (v_c)
```{r, random cor-pheno plot 3 ne}

cor_trends_by_gen(v_c_lit, v_c_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## Correlation across time (v_d)  {.tabset}

### Random 1 (v_d)  
```{r, GA1 cor and pheno  vd}
GA1_pattern <- unique(paste0(v_d_lit$snake_mu_rate, "_", v_d_lit$snake_mu_effect_sd,"_",v_d_lit$newt_mu_rate, "_", v_d_lit$newt_mu_effect_sd, "_", v_d_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(v_d_lit, v_d_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(v_d_lit, v_d_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (v_d)
```{r, random cor-pheno plot 2  vd}

cor_trends_by_gen(v_d_lit, v_d_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (v_d)
```{r, random cor-pheno plot 3  vd}

cor_trends_by_gen(v_d_lit, v_d_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (v_a) {.tabset}

### Pheno Beginning (v_a)

```{r, early plots}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(v_a_lit$rep))){
#   myine<-whale_gen(v_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[1])
```

### Pheno Middle (v_a)

```{r, middle plots}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(v_a_lit$rep))){
#   myine<-whale_gen(v_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[1])
```

### Pheno End (v_a)

```{r, end plots}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(v_a_lit$rep))){
#   myine<-whale_gen(v_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[1])
```

### Dif Beginning (v_a)
```{r, early plots 1a}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(v_a_lit$rep))){
#   myine<-two_hist(v_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[1] )

```

### Dif Middle (v_a)
```{r, early plots 2a}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(v_a_lit$rep))){
#   myine<-two_hist(v_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[1] )

```

### Dif End (v_a)
```{r, early plots 3a}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(v_a_lit$rep))){
#   myine<-two_hist(v_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_a_lit$rep)[1] )

```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (v_b) {.tabset}

### Pheno Beginning (v_b)

```{r, early plots lw}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(v_b_lit$rep))){
#   myine<-whale_gen(v_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[1])
```

### Pheno Middle (v_b)

```{r, middle plots lw}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(v_b_lit$rep))){
#   myine<-whale_gen(v_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[1])
```

### Pheno End (v_b)

```{r, end plots lw}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(v_b_lit$rep))){
#   myine<-whale_gen(v_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[1])
```

### Dif Beginning (v_b)
```{r, early plots 1a lw}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(v_b_lit$rep))){
#   myine<-two_hist(v_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[1] )

```

### Dif Middle (v_b)
```{r, early plots 2a lw}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(v_b_lit$rep))){
#   myine<-two_hist(v_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[1] )

```

### Dif End (v_b)
```{r, early plots 3a lw}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(v_b_lit$rep))){
#   myine<-two_hist(v_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_b_lit$rep)[1] )

```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (v_c) {.tabset}

### Pheno Beginning (v_c)

```{r, early plots ne}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(v_c_lit$rep))){
#   myine<-whale_gen(v_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[1])
```

### Pheno Middle (v_c)

```{r, middle plots ne}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(v_c_lit$rep))){
#   myine<-whale_gen(v_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[1])
```

### Pheno End (v_c)

```{r, end plots ne}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(v_c_lit$rep))){
#   myine<-whale_gen(v_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[1])
```

### Dif Beginning (v_c)
```{r, early plots 1a ne}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(v_c_lit$rep))){
#   myine<-two_hist(v_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[1] )

```

### Dif Middle (v_c)
```{r, early plots 2a ne}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(v_c_lit$rep))){
#   myine<-two_hist(v_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[1] )

```

### Dif End (v_c)
```{r, early plots 3a ne}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(v_c_lit$rep))){
#   myine<-two_hist(v_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_c_lit$rep)[1] )

```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (v_d) {.tabset}

### Pheno Beginning (v_d)

```{r, early plots vd}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(v_d_lit$rep))){
#   myine<-whale_gen(v_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[1])
```

### Pheno Middle (v_d)

```{r, middle plots vd}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(v_d_lit$rep))){
#   myine<-whale_gen(v_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[1])
```

### Pheno End (v_d)

```{r, end plots vd}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(v_d_lit$rep))){
#   myine<-whale_gen(v_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(v_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[1])
```

### Dif Beginning (v_d)
```{r, early plots 1a vd}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(v_d_lit$rep))){
#   myine<-two_hist(v_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[1] )

```

### Dif Middle (v_d)
```{r, early plots 2a vd}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(v_d_lit$rep))){
#   myine<-two_hist(v_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[1] )

```

### Dif End (v_d)
```{r, early plots 3a vd}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(v_d_lit$rep))){
#   myine<-two_hist(v_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(v_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(v_d_lit$rep)[1] )

```

## {-}

## Summary (v_a) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary}

min_gen=100
max_gen=5000
GA_summary(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3}
min_gen=45000
max_gen=50000

# summary
GA_summary(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1}

min_gen=100
max_gen=5000

GA_summary(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2}
min_gen=25000
max_gen=30000

GA_summary(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3}
min_gen=45000
max_gen=50000
GA_summary(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1}
min_gen=100
max_gen=5000
#

GA_summary_by_species(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1}
min_gen=100
max_gen=5000
#

GA_summary_by_species(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(v_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Summary (v_b) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary lw}

min_gen=100
max_gen=5000
GA_summary(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2 lw}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3 lw}
min_gen=45000
max_gen=50000

# summary
GA_summary(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1 lw}

min_gen=100
max_gen=5000

GA_summary(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2 lw}
min_gen=25000
max_gen=30000

GA_summary(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3 lw}
min_gen=45000
max_gen=50000
GA_summary(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1 lw}
min_gen=100
max_gen=5000
#

GA_summary_by_species(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2 lw}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3 lw}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1 lw}
min_gen=100
max_gen=5000
#

GA_summary_by_species(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2 lw}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3 lw}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(v_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Summary (v_c) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary ne}

min_gen=100
max_gen=5000
GA_summary(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2 ne}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3 ne}
min_gen=45000
max_gen=50000

# summary
GA_summary(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1 ne}

min_gen=100
max_gen=5000

GA_summary(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2 ne}
min_gen=25000
max_gen=30000

GA_summary(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3 ne}
min_gen=45000
max_gen=50000
GA_summary(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1 ne}
min_gen=100
max_gen=5000
#

GA_summary_by_species(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2 ne}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3 ne}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1 ne}
min_gen=100
max_gen=5000
#

GA_summary_by_species(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2 ne}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3 ne}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(v_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Summary (v_d) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary vd}

min_gen=100
max_gen=5000
GA_summary(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2 vd}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3 vd}
min_gen=45000
max_gen=50000

# summary
GA_summary(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1 vd}

min_gen=100
max_gen=5000

GA_summary(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2 vd}
min_gen=25000
max_gen=30000

GA_summary(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3 vd}
min_gen=45000
max_gen=50000
GA_summary(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1 vd}
min_gen=100
max_gen=5000
#

GA_summary_by_species(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2 vd}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3 vd}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1 vd}
min_gen=100
max_gen=5000
#

GA_summary_by_species(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2 vd}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3 vd}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(v_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Heatmap (v_a) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(v_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)
```{r, early plots Heatmap 2}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(v_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late)
```{r, early plots Heatmap 3}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(v_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early)
```{r, early plots Heatmap pheno 1}
min_gen=100
max_gen=5000
build_heatmap(v_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid)
```{r, early plots Heatmap pheno 2}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(v_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late)
```{r, early plots Heatmap pheno 3}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(v_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

## Heatmap (v_b) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap lw}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(v_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)
```{r, early plots Heatmap 2 lw}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(v_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late)
```{r, early plots Heatmap 3 lw}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(v_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early)
```{r, early plots Heatmap pheno 1 lw}
min_gen=100
max_gen=5000
build_heatmap(v_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid)
```{r, early plots Heatmap pheno 2 lw}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(v_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late)
```{r, early plots Heatmap pheno 3 lw}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(v_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

## Heatmap (v_c) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap ne}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(v_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)
```{r, early plots Heatmap 2 ne}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(v_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late)
```{r, early plots Heatmap 3 ne}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(v_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early)
```{r, early plots Heatmap pheno 1 ne}
min_gen=100
max_gen=5000
build_heatmap(v_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid)
```{r, early plots Heatmap pheno 2 ne}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(v_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late)
```{r, early plots Heatmap pheno 3 ne}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(v_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

## Heatmap (v_d) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap vd}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(v_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)
```{r, early plots Heatmap 2 vd}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(v_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late)
```{r, early plots Heatmap 3 vd}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(v_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early)
```{r, early plots Heatmap pheno 1 vd}
min_gen=100
max_gen=5000
build_heatmap(v_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid)
```{r, early plots Heatmap pheno 2 vd}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(v_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late)
```{r, early plots Heatmap pheno 3 vd}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(v_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

```{r, red in grid files}
require(readr)
v_a_grid<- read.csv("~/Desktop/same_v/v_a/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
v_a_grid$group_rep <- paste0(v_a_grid$snake_mu_rate, "_", v_a_grid$snake_mu_effect_sd,"_",v_a_grid$newt_mu_rate, "_", v_a_grid$newt_mu_effect_sd, "_", v_a_grid$rep)
v_a_grid$group <- paste0(v_a_grid$snake_mu_rate, "_", v_a_grid$snake_mu_effect_sd,"_",v_a_grid$newt_mu_rate, "_", v_a_grid$newt_mu_effect_sd)
v_a_grid$sim=LETTERS[factor(v_a_grid$group)]
v_a_grid$grid_num = 5

```

```{r, red in grid files lw}
require(readr)
v_b_grid<- read.csv("~/Desktop/same_v/v_b/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
v_b_grid$group_rep <- paste0(v_b_grid$snake_mu_rate, "_", v_b_grid$snake_mu_effect_sd,"_",v_b_grid$newt_mu_rate, "_", v_b_grid$newt_mu_effect_sd, "_", v_b_grid$rep)
v_b_grid$group <- paste0(v_b_grid$snake_mu_rate, "_", v_b_grid$snake_mu_effect_sd,"_",v_b_grid$newt_mu_rate, "_", v_b_grid$newt_mu_effect_sd)
v_b_grid$sim=LETTERS[factor(v_b_grid$group)]
v_b_grid$grid_num = 5

```

```{r, red in grid files ne}
require(readr)
v_c_grid<- read.csv("~/Desktop/same_v/v_c/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
v_c_grid$group_rep <- paste0(v_c_grid$snake_mu_rate, "_", v_c_grid$snake_mu_effect_sd,"_",v_c_grid$newt_mu_rate, "_", v_c_grid$newt_mu_effect_sd, "_", v_c_grid$rep)
v_c_grid$group <- paste0(v_c_grid$snake_mu_rate, "_", v_c_grid$snake_mu_effect_sd,"_",v_c_grid$newt_mu_rate, "_", v_c_grid$newt_mu_effect_sd)
v_c_grid$sim=LETTERS[factor(v_c_grid$group)]
v_c_grid$grid_num = 5

```

```{r, red in grid files mud}
require(readr)
v_d_grid<- read.csv("~/Desktop/same_v/v_d/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
v_d_grid$group_rep <- paste0(v_d_grid$snake_mu_rate, "_", v_d_grid$snake_mu_effect_sd,"_",v_d_grid$newt_mu_rate, "_", v_d_grid$newt_mu_effect_sd, "_", v_d_grid$rep)
v_d_grid$group <- paste0(v_d_grid$snake_mu_rate, "_", v_d_grid$snake_mu_effect_sd,"_",v_d_grid$newt_mu_rate, "_", v_d_grid$newt_mu_effect_sd)
v_d_grid$sim=LETTERS[factor(v_d_grid$group)]
v_d_grid$grid_num = 5

```

## What is up with the correlations

## Early Simulation Correlation (v_a)  {.tabset}

### Mean
```{r, cor grid high cor mean}

file=v_a_grid
file_name_a="1e-09_0.0158_1e-10_0.05_1"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max}

file=v_a_grid
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min}

file=v_a_grid
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize}

file=v_a_grid
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_a, spegen, file, type, row_num, col_num)

```

## {-}

## Early Simulation Correlation (v_b)  {.tabset}

### Mean
```{r, cor grid high cor mean lw}

file=v_b_grid
file_name_b="1e-09_0.05_1e-10_0.158_1"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max lw}

file=v_b_grid
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min lw}

file=v_b_grid
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize lw}

file=v_b_grid
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_b, spegen, file, type, row_num, col_num)

```

## {-}

## Early Simulation Correlation (v_c)  {.tabset}

### Mean
```{r, cor grid high cor mean ne}

file=v_c_grid
file_name_c="1e-09_0.158_1e-10_0.5_1"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max  ne}

file=v_c_grid
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min ne}

file=v_c_grid
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize ne}

file=v_c_grid
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_c, spegen, file, type, row_num, col_num)

```

## {-}

## Early Simulation Correlation (v_d)  {.tabset}

### Mean
```{r, cor grid high cor mean vd}

file=v_d_grid
file_name_d="1e-09_0.5_1e-10_1.58_1"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max vd}

file=v_d_grid
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min vd}

file=v_d_grid
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize lwvd}

file=v_d_grid
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_d, spegen, file, type, row_num, col_num)

```

## {-}

```{r, red in grid files 2}
require(readr)
v_a_grid<- read.csv("~/Desktop/same_v/v_a/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
v_a_grid$group_rep <- paste0(v_a_grid$snake_mu_rate, "_", v_a_grid$snake_mu_effect_sd,"_",v_a_grid$newt_mu_rate, "_", v_a_grid$newt_mu_effect_sd, "_", v_a_grid$rep)
v_a_grid$group <- paste0(v_a_grid$snake_mu_rate, "_", v_a_grid$snake_mu_effect_sd,"_",v_a_grid$newt_mu_rate, "_", v_a_grid$newt_mu_effect_sd)
v_a_grid$sim=LETTERS[factor(v_a_grid$group)]
v_a_grid$grid_num = 5

```

```{r, red in grid files 2 lwvb}
require(readr)
v_b_grid<- read.csv("~/Desktop/same_v/v_b/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
v_b_grid$group_rep <- paste0(v_b_grid$snake_mu_rate, "_", v_b_grid$snake_mu_effect_sd,"_",v_b_grid$newt_mu_rate, "_", v_b_grid$newt_mu_effect_sd, "_", v_b_grid$rep)
v_b_grid$group <- paste0(v_b_grid$snake_mu_rate, "_", v_b_grid$snake_mu_effect_sd,"_",v_b_grid$newt_mu_rate, "_", v_b_grid$newt_mu_effect_sd)
v_b_grid$sim=LETTERS[factor(v_b_grid$group)]
v_b_grid$grid_num = 5

```

```{r, red in grid files 2 ne}
require(readr)
v_c_grid<- read.csv("~/Desktop/same_v/v_c/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
v_c_grid$group_rep <- paste0(v_c_grid$snake_mu_rate, "_", v_c_grid$snake_mu_effect_sd,"_",v_c_grid$newt_mu_rate, "_", v_c_grid$newt_mu_effect_sd, "_", v_c_grid$rep)
v_c_grid$group <- paste0(v_c_grid$snake_mu_rate, "_", v_c_grid$snake_mu_effect_sd,"_",v_c_grid$newt_mu_rate, "_", v_c_grid$newt_mu_effect_sd)
v_c_grid$sim=LETTERS[factor(v_c_grid$group)]
v_c_grid$grid_num = 5

```

```{r, red in grid files 2 lwvd}
require(readr)
v_d_grid<- read.csv("~/Desktop/same_v/v_d/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
v_d_grid$group_rep <- paste0(v_d_grid$snake_mu_rate, "_", v_d_grid$snake_mu_effect_sd,"_",v_d_grid$newt_mu_rate, "_", v_d_grid$newt_mu_effect_sd, "_", v_d_grid$rep)
v_d_grid$group <- paste0(v_d_grid$snake_mu_rate, "_", v_d_grid$snake_mu_effect_sd,"_",v_d_grid$newt_mu_rate, "_", v_d_grid$newt_mu_effect_sd)
v_d_grid$sim=LETTERS[factor(v_d_grid$group)]
v_d_grid$grid_num = 5

```

## Late Simulation Correlation (v_a) {.tabset}

### Mean
```{r, cor grid high cor mean late}
#1e-11_5_1e-10_0.5_0
file=v_a_grid
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max late}

file=v_a_grid
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min late}

file=v_a_grid
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late}

file=v_a_grid
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_a, spegen, file, type, row_num, col_num)

```

## {-}

## Late Simulation Correlation (v_b) {.tabset}

### Mean
```{r, cor grid high cor mean late lw}

file=v_b_grid
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max late lw}

file=v_b_grid
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min late lw}

file=v_b_grid
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late lw}

file=v_b_grid
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_b, spegen, file, type, row_num, col_num)

```

## {-}

## Late Simulation Correlation (v_c) {.tabset}

### Mean
```{r, cor grid high cor mean late ne}

file=v_c_grid
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max late ne}

file=v_c_grid
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min late ne}

file=v_c_grid
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late ne}

file=v_c_grid
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_c, spegen, file, type, row_num, col_num)

```

## {-}

## Late Simulation Correlation (v_d) {.tabset}

### Mean
```{r, cor grid high cor mean late lwvd}

file=v_d_grid
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max late lwvd}

file=v_d_grid
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min late lwvd}

file=v_d_grid
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late lwvd}

file=v_d_grid
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_d, spegen, file, type, row_num, col_num)

```

## {-}

### 2023-01-18 graphs_newt_snakes/bob_notes.Rmd
I have updated the results for the last set of experiments. Tomorrow I will need to spend some time reviewing them.

@@
 
----
-title: "Moving Together"
-output: html_document
-date: '2023-01-10'
----
 ```{r setup, include=FALSE}
@@
 
-both_lower_w_no_exp_cor<- read.csv("~/Desktop/both_lower_w_no_exp/all_cor.txt" , header = TRUE)
+both_lower_w_no_exp_cor<- read.csv("~/Desktop/bob_suggestion/both_lower_w_no_exp/all_cor.txt" , header = TRUE)
 both_lower_w_no_exp_cor$group_rep <- paste0(both_lower_w_no_exp_cor$snake_mu_rate, "_", both_lower_w_no_exp_cor$snake_mu_effect_sd,"_",both_lower_w_no_exp_cor$newt_mu_rate, "_", both_lower_w_no_exp_cor$newt_mu_effect_sd, "_", both_lower_w_no_exp_cor$rep)
@@
 
-lower_w_cor<- read.csv("~/Desktop/lower_w/all_cor.txt" , header = TRUE)
+lower_w_cor<- read.csv("~/Desktop/bob_suggestion/lower_w/all_cor.txt" , header = TRUE)
 lower_w_cor$group_rep <- paste0(lower_w_cor$snake_mu_rate, "_", lower_w_cor$snake_mu_effect_sd,"_",lower_w_cor$newt_mu_rate, "_", lower_w_cor$newt_mu_effect_sd, "_", lower_w_cor$rep)
@@
 
-no_exp_cor<- read.csv("~/Desktop/no_exp/all_cor.txt" , header = TRUE)
+no_exp_cor<- read.csv("~/Desktop/bob_suggestion/no_exp/all_cor.txt" , header = TRUE)
 no_exp_cor$group_rep <- paste0(no_exp_cor$snake_mu_rate, "_", no_exp_cor$snake_mu_effect_sd,"_",no_exp_cor$newt_mu_rate, "_", no_exp_cor$newt_mu_effect_sd, "_", no_exp_cor$rep)
@@
 
-GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
+ create_parm_file_nc <- function(file, min_gen, max_gen){
+
+   file$test_factor <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+params <- data_frame()
+
+for(i in 1:length(unique(file$test_factor))){
+
+  pattern=unique(file$test_factor)[i]
+
+  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$test_factor ==pattern),]
+
+  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
+                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
+                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
+                           Newt_pop_size=mean(sumitup$Newt_pop_size),
+                           Snake_pop_size=mean(sumitup$Snake_pop_size),
+                           dif=mean(sumitup$dif),
+                           snake_mu_rate=unlist(strsplit(pattern, "_"))[2],
+                           newt_mu_rate=unlist(strsplit(pattern, "_"))[4],
+                           snake_mu_effect_sd=unlist(strsplit(pattern, "_"))[3],
+                           newt_mu_effect_sd=unlist(strsplit(pattern, "_"))[5],
+                           rep=unlist(strsplit(pattern, "_"))[6],
+                           test_factor=pattern)
+
+  params <- rbind(params, params_temp)
+}
+
+params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
+params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
+params$snake_newt <- paste0(params$snake, "_", params$newt)
+return(params)
+}
+
+GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label ){
 
@@
 params<-create_parm_file(file, min_gen, max_gen)
-
+params = na.omit(params)
 my_plot <- ggplot(params) +
@@
 }
+
 GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){
@@
   params<-create_parm_file(file, min_gen, max_gen)
+  params = na.omit(params)
 
@@
 
-### Phenotype differences (lower_wp)
+### Phenotype differences (lower_w)
 ```{r, whale lw}
@@
 
-whale_gen(lower_wp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
-```
-
-### Phenotype & Populationsize differences (lower_wp)
+whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+```
+
+### Phenotype & Populationsize differences (lower_w)
 ```{r, popsize and pheno lw}
 
-suppressMessages(print(two_hist(lower_wp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+suppressMessages(print(two_hist(lower_w_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
 
@@
 HEREREERERERER
+
 ### cor (both_lower_w_no_exp)
@@
 
-```{r, red in grid files}
-require(readr)
-both_lower_w_no_exp_grid<- read.csv("~/Desktop/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
-both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep)
-both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd)
-both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)]
-both_lower_w_no_exp_grid$grid_num = 5
-
-```
-
-```{r, red in grid files lw}
-require(readr)
-lower_w_grid<- read.csv("~/Desktop/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
-lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep)
-lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd)
-lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)]
-lower_w_grid$grid_num = 5
-
-```
-
-```{r, red in grid files ne}
-require(readr)
-no_exp_grid<- read.csv("~/Desktop/no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
-no_exp_grid$group_rep <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd, "_", no_exp_grid$rep)
-no_exp_grid$group <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd)
-no_exp_grid$sim=LETTERS[factor(no_exp_grid$group)]
-no_exp_grid$grid_num = 5
-
-```
-
-## What is up with the correlations
-
-## Early Simulation Correlation (both_lower_w_no_exp)  {.tabset}
-
-### Mean 
-```{r, cor grid high cor mean}
-
-file=both_lower_w_no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="mean"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Max 
-```{r, cor grid high cor max}
-
-file=both_lower_w_no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="max"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Min 
-```{r, cor grid high cor min}
-
-file=both_lower_w_no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="min"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### popsize
-```{r, cor grid high cor popsize}
-
-file=both_lower_w_no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="num_ind"
-row_num=20
-col_num=5
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-
-```
-
-## {-}
-
-## Early Simulation Correlation (lower_w)  {.tabset}
-
-### Mean 
-```{r, cor grid high cor mean}
-
-file=lower_w_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="mean"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Max 
-```{r, cor grid high cor max}
-
-file=lower_w_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="max"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Min 
-```{r, cor grid high cor min}
-
-file=lower_w_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="min"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### popsize
-```{r, cor grid high cor popsize}
-
-file=lower_w_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="num_ind"
-row_num=20
-col_num=5
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-
-```
-
-## {-}
-
-## Early Simulation Correlation (no_exp)  {.tabset}
-
-### Mean 
-```{r, cor grid high cor mean}
-
-file=no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="mean"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Max 
-```{r, cor grid high cor max}
-
-file=no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="max"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Min 
-```{r, cor grid high cor min}
-
-file=no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="min"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### popsize
-```{r, cor grid high cor popsize}
-
-file=no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=9501
-type="num_ind"
-row_num=20
-col_num=5
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-
-```
-
-## {-}
-
-```{r, red in grid files 2}
-require(readr)
-both_lower_w_no_exp_grid<- read.csv("~/Desktop/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
-both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep)
-both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd)
-both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)]
-both_lower_w_no_exp_grid$grid_num = 5
-
-```
-
-```{r, red in grid files 2 lw}
-require(readr)
-lower_w_grid<- read.csv("~/Desktop/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
-lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep)
-lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd)
-lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)]
-lower_w_grid$grid_num = 5
-
-```
-
-```{r, red in grid files 2 ne}
-require(readr)
-no_exp_grid<- read.csv("~/Desktop/no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
-no_exp_grid$group_rep <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd, "_", no_exp_grid$rep)
-no_exp_grid$group <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd)
-no_exp_grid$sim=LETTERS[factor(no_exp_grid$group)]
-no_exp_grid$grid_num = 5
-
-```
-
-## Late Simulation Correlation (both_lower_w_no_exp) {.tabset}
-
-### Mean 
-```{r, cor grid high cor mean late}
-
-file=both_lower_w_no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="mean"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Max 
-```{r, cor grid high cor max late}
-
-file=both_lower_w_no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="max"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Min 
-```{r, cor grid high cor min late}
-
-file=both_lower_w_no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="min"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Pop size
-```{r, cor grid high cor popsize late}
-
-file=both_lower_w_no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="num_ind"
-row_num=20
-col_num=5
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-
-```
-
-## {-}
-
-## Late Simulation Correlation (lower_w) {.tabset}
-
-### Mean 
-```{r, cor grid high cor mean late}
-
-file=lower_w_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="mean"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Max 
-```{r, cor grid high cor max late}
-
-file=lower_w_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="max"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Min 
-```{r, cor grid high cor min late}
-
-file=lower_w_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="min"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Pop size
-```{r, cor grid high cor popsize late}
-
-file=lower_w_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="num_ind"
-row_num=20
-col_num=5
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-
-```
-
-## {-}
-
-## Late Simulation Correlation (no_exp) {.tabset}
-
-### Mean 
-```{r, cor grid high cor mean late}
-
-file=no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="mean"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Max 
-```{r, cor grid high cor max late}
-
-file=no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="max"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Min 
-```{r, cor grid high cor min late}
-
-file=no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="min"
-row_num=20
-col_num=5
-
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-```
-
-### Pop size
-```{r, cor grid high cor popsize late}
-
-file=no_exp_grid
-file_name="1e-11_5_1e-10_0.5_0"
-spegen=44501
-type="num_ind"
-row_num=20
-col_num=5
-grid_plot(file_name, spegen, file, type, row_num, col_num)
-
-```
-
-## {-}
+<!-- ```{r, red in grid files} -->
+<!-- require(readr) -->
+<!-- both_lower_w_no_exp_grid<- read.csv("~/Desktop/bob_suggestion/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000)) -->
+<!-- both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep) -->
+<!-- both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd) -->
+<!-- both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)] -->
+<!-- both_lower_w_no_exp_grid$grid_num = 5 -->
+
+<!-- ``` -->
+
+<!-- ```{r, red in grid files lw} -->
+<!-- require(readr) -->
+<!-- lower_w_grid<- read.csv("~/Desktop/bob_suggestion/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000)) -->
+<!-- lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep) -->
+<!-- lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd) -->
+<!-- lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)] -->
+<!-- lower_w_grid$grid_num = 5 -->
+
+<!-- ``` -->
+
+<!-- ```{r, red in grid files ne} -->
+<!-- require(readr) -->
+<!-- no_exp_grid<- read.csv("~/Desktop/bob_suggestion/no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000)) -->
+<!-- no_exp_grid$group_rep <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd, "_", no_exp_grid$rep) -->
+<!-- no_exp_grid$group <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd) -->
+<!-- no_exp_grid$sim=LETTERS[factor(no_exp_grid$group)] -->
+<!-- no_exp_grid$grid_num = 5 -->
+
+<!-- ``` -->
+
+<!-- ## What is up with the correlations -->
+
+<!-- ## Early Simulation Correlation (both_lower_w_no_exp)  {.tabset} -->
+
+<!-- ### Mean  -->
+<!-- ```{r, cor grid high cor mean} -->
+
+<!-- file=both_lower_w_no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="mean" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Max  -->
+<!-- ```{r, cor grid high cor max} -->
+
+<!-- file=both_lower_w_no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="max" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Min  -->
+<!-- ```{r, cor grid high cor min} -->
+
+<!-- file=both_lower_w_no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="min" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### popsize -->
+<!-- ```{r, cor grid high cor popsize} -->
+
+<!-- file=both_lower_w_no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="num_ind" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+
+<!-- ``` -->
+
+<!-- ## {-} -->
+
+<!-- ## Early Simulation Correlation (lower_w)  {.tabset} -->
+
+<!-- ### Mean  -->
+<!-- ```{r, cor grid high cor mean lw} -->
+
+<!-- file=lower_w_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="mean" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Max  -->
+<!-- ```{r, cor grid high cor max lw} -->
+
+<!-- file=lower_w_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="max" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Min  -->
+<!-- ```{r, cor grid high cor min lw} -->
+
+<!-- file=lower_w_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="min" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### popsize -->
+<!-- ```{r, cor grid high cor popsize lw} -->
+
+<!-- file=lower_w_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="num_ind" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+
+<!-- ``` -->
+
+<!-- ## {-} -->
+
+<!-- ## Early Simulation Correlation (no_exp)  {.tabset} -->
+
+<!-- ### Mean  -->
+<!-- ```{r, cor grid high cor mean ne} -->
+
+<!-- file=no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="mean" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Max  -->
+<!-- ```{r, cor grid high cor max  ne} -->
+
+<!-- file=no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="max" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Min  -->
+<!-- ```{r, cor grid high cor min ne} -->
+
+<!-- file=no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="min" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### popsize -->
+<!-- ```{r, cor grid high cor popsize ne} -->
+
+<!-- file=no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=9501 -->
+<!-- type="num_ind" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+
+<!-- ``` -->
+
+<!-- ## {-} -->
+
+<!-- ```{r, red in grid files 2} -->
+<!-- require(readr) -->
+<!-- both_lower_w_no_exp_grid<- read.csv("~/Desktop/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000)) -->
+<!-- both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep) -->
+<!-- both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd) -->
+<!-- both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)] -->
+<!-- both_lower_w_no_exp_grid$grid_num = 5 -->
+
+<!-- ``` -->
+
+<!-- ```{r, red in grid files 2 lw} -->
+<!-- require(readr) -->
+<!-- lower_w_grid<- read.csv("~/Desktop/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000)) -->
+<!-- lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep) -->
+<!-- lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd) -->
+<!-- lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)] -->
+<!-- lower_w_grid$grid_num = 5 -->
+
+<!-- ``` -->
+
+<!-- ```{r, red in grid files 2 ne} -->
+<!-- require(readr) -->
+<!-- no_exp_grid<- read.csv("~/Desktop/no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000)) -->
+<!-- no_exp_grid$group_rep <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd, "_", no_exp_grid$rep) -->
+<!-- no_exp_grid$group <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd) -->
+<!-- no_exp_grid$sim=LETTERS[factor(no_exp_grid$group)] -->
+<!-- no_exp_grid$grid_num = 5 -->
+
+<!-- ``` -->
+
+<!-- ## Late Simulation Correlation (both_lower_w_no_exp) {.tabset} -->
+
+<!-- ### Mean  -->
+<!-- ```{r, cor grid high cor mean late} -->
+
+<!-- file=both_lower_w_no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="mean" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Max  -->
+<!-- ```{r, cor grid high cor max late} -->
+
+<!-- file=both_lower_w_no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="max" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Min  -->
+<!-- ```{r, cor grid high cor min late} -->
+
+<!-- file=both_lower_w_no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="min" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Pop size -->
+<!-- ```{r, cor grid high cor popsize late} -->
+
+<!-- file=both_lower_w_no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="num_ind" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+
+<!-- ``` -->
+
+<!-- ## {-} -->
+
+<!-- ## Late Simulation Correlation (lower_w) {.tabset} -->
+
+<!-- ### Mean  -->
+<!-- ```{r, cor grid high cor mean late lw} -->
+
+<!-- file=lower_w_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="mean" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Max  -->
+<!-- ```{r, cor grid high cor max late lw} -->
+
+<!-- file=lower_w_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="max" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Min  -->
+<!-- ```{r, cor grid high cor min late lw} -->
+
+<!-- file=lower_w_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="min" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Pop size -->
+<!-- ```{r, cor grid high cor popsize late lw} -->
+
+<!-- file=lower_w_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="num_ind" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+
+<!-- ``` -->
+
+<!-- ## {-} -->
+
+<!-- ## Late Simulation Correlation (no_exp) {.tabset} -->
+
+<!-- ### Mean  -->
+<!-- ```{r, cor grid high cor mean late ne} -->
+
+<!-- file=no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="mean" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Max  -->
+<!-- ```{r, cor grid high cor max late ne} -->
+
+<!-- file=no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="max" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Min  -->
+<!-- ```{r, cor grid high cor min late ne} -->
+
+<!-- file=no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="min" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+<!-- ``` -->
+
+<!-- ### Pop size -->
+<!-- ```{r, cor grid high cor popsize late ne} -->
+
+<!-- file=no_exp_grid -->
+<!-- file_name="1e-11_5_1e-10_0.5_0" -->
+<!-- spegen=44501 -->
+<!-- type="num_ind" -->
+<!-- row_num=20 -->
+<!-- col_num=5 -->
+<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
+
+<!-- ``` -->
+
+<!-- ## {-} -->

### 2023-01-18 graphs_newt_snakes/high_to_low_v.Rmd
I have updated the results for the last set of experiments. Tomorrow I will need to spend some time reviewing them.

---
title: "high to low v"
output: html_document
date: '2023-01-13'
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
library(stringr)
library(patchwork)
```

## Goal:

### Questions:

What does it mean to be correlated?

## Background

## Experiment

I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction with different genetic architectures (GAs) in a spatial setting. I hypothesized that we would see an interaction (co-evolutionary arms race) between newt and snake phenotype under some GA combinations when newts and snakes were evolving over geographical space. Each GA is paired with another GA creating 16 combinations.

Experiment values:

### The data

many of the experiments did not run to completion (i will run this part 3 times)

```{bash, data file gathering 1}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=low_to_high_v/mu_a
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{bash, data file gathering 2}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=low_to_high_v/mu_b
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{bash, data file gathering 3}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=low_to_high_v/mu_c
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{bash, data file gathering 4}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=low_to_high_v/mu_d
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{r, data gathering}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

mu_a_lit<- read.csv("~/Desktop/low_to_high_v/mu_a/all_lit.txt" , header = TRUE)

mu_a_lit$group_rep <- paste0(mu_a_lit$snake_mu_rate, "_", mu_a_lit$snake_mu_effect_sd,"_",mu_a_lit$newt_mu_rate, "_", mu_a_lit$newt_mu_effect_sd, "_", mu_a_lit$rep)

mu_a_lit$group <- paste0(mu_a_lit$snake_mu_rate, "_", mu_a_lit$snake_mu_effect_sd,"_",mu_a_lit$newt_mu_rate, "_", mu_a_lit$newt_mu_effect_sd)

mu_a_lit$sim=LETTERS[factor(mu_a_lit$group)]
mu_a_lit$dif <- mu_a_lit$Snake_mean_Pheno-mu_a_lit$Newt_mean_Pheno

mu_a_cor<- read.csv("~/Desktop/low_to_high_v/mu_a/all_cor.txt" , header = TRUE)
mu_a_cor$group_rep <- paste0(mu_a_cor$snake_mu_rate, "_", mu_a_cor$snake_mu_effect_sd,"_",mu_a_cor$newt_mu_rate, "_", mu_a_cor$newt_mu_effect_sd, "_", mu_a_cor$rep)
mu_a_cor$group <- paste0(mu_a_cor$snake_mu_rate, "_", mu_a_cor$snake_mu_effect_sd,"_",mu_a_cor$newt_mu_rate, "_", mu_a_cor$newt_mu_effect_sd)
mu_a_cor$sim=LETTERS[factor(mu_a_cor$group)]

# Mu B
mu_b_lit<- read.csv("~/Desktop/low_to_high_v/mu_b/all_lit.txt" , header = TRUE)

mu_b_lit$group_rep <- paste0(mu_b_lit$snake_mu_rate, "_", mu_b_lit$snake_mu_effect_sd,"_",mu_b_lit$newt_mu_rate, "_", mu_b_lit$newt_mu_effect_sd, "_", mu_b_lit$rep)

mu_b_lit$group <- paste0(mu_b_lit$snake_mu_rate, "_", mu_b_lit$snake_mu_effect_sd,"_",mu_b_lit$newt_mu_rate, "_", mu_b_lit$newt_mu_effect_sd)

mu_b_lit$sim=LETTERS[factor(mu_b_lit$group)]
mu_b_lit$dif <- mu_b_lit$Snake_mean_Pheno-mu_b_lit$Newt_mean_Pheno

mu_b_cor<- read.csv("~/Desktop/low_to_high_v/mu_b/all_cor.txt" , header = TRUE)
mu_b_cor$group_rep <- paste0(mu_b_cor$snake_mu_rate, "_", mu_b_cor$snake_mu_effect_sd,"_",mu_b_cor$newt_mu_rate, "_", mu_b_cor$newt_mu_effect_sd, "_", mu_b_cor$rep)
mu_b_cor$group <- paste0(mu_b_cor$snake_mu_rate, "_", mu_b_cor$snake_mu_effect_sd,"_",mu_b_cor$newt_mu_rate, "_", mu_b_cor$newt_mu_effect_sd)
mu_b_cor$sim=LETTERS[factor(mu_b_cor$group)]

# no exp

mu_c_lit<- read.csv("~/Desktop/low_to_high_v/mu_c/all_lit.txt" , header = TRUE)

mu_c_lit$group_rep <- paste0(mu_c_lit$snake_mu_rate, "_", mu_c_lit$snake_mu_effect_sd,"_",mu_c_lit$newt_mu_rate, "_", mu_c_lit$newt_mu_effect_sd, "_", mu_c_lit$rep)

mu_c_lit$group <- paste0(mu_c_lit$snake_mu_rate, "_", mu_c_lit$snake_mu_effect_sd,"_",mu_c_lit$newt_mu_rate, "_", mu_c_lit$newt_mu_effect_sd)

mu_c_lit$sim=LETTERS[factor(mu_c_lit$group)]
mu_c_lit$dif <- mu_c_lit$Snake_mean_Pheno-mu_c_lit$Newt_mean_Pheno

mu_c_cor<- read.csv("~/Desktop/low_to_high_v/mu_c/all_cor.txt" , header = TRUE)
mu_c_cor$group_rep <- paste0(mu_c_cor$snake_mu_rate, "_", mu_c_cor$snake_mu_effect_sd,"_",mu_c_cor$newt_mu_rate, "_", mu_c_cor$newt_mu_effect_sd, "_", mu_c_cor$rep)
mu_c_cor$group <- paste0(mu_c_cor$snake_mu_rate, "_", mu_c_cor$snake_mu_effect_sd,"_",mu_c_cor$newt_mu_rate, "_", mu_c_cor$newt_mu_effect_sd)
mu_c_cor$sim=LETTERS[factor(mu_c_cor$group)]

# mu d

mu_d_lit<- read.csv("~/Desktop/low_to_high_v/mu_d/all_lit.txt" , header = TRUE)

mu_d_lit$group_rep <- paste0(mu_d_lit$snake_mu_rate, "_", mu_d_lit$snake_mu_effect_sd,"_",mu_d_lit$newt_mu_rate, "_", mu_d_lit$newt_mu_effect_sd, "_", mu_d_lit$rep)

mu_d_lit$group <- paste0(mu_d_lit$snake_mu_rate, "_", mu_d_lit$snake_mu_effect_sd,"_",mu_d_lit$newt_mu_rate, "_", mu_d_lit$newt_mu_effect_sd)

mu_d_lit$sim=LETTERS[factor(mu_d_lit$group)]
mu_d_lit$dif <- mu_d_lit$Snake_mean_Pheno-mu_d_lit$Newt_mean_Pheno

mu_d_cor<- read.csv("~/Desktop/low_to_high_v/mu_d/all_cor.txt" , header = TRUE)
mu_d_cor$group_rep <- paste0(mu_d_cor$snake_mu_rate, "_", mu_d_cor$snake_mu_effect_sd,"_",mu_d_cor$newt_mu_rate, "_", mu_d_cor$newt_mu_effect_sd, "_", mu_d_cor$rep)
mu_d_cor$group <- paste0(mu_d_cor$snake_mu_rate, "_", mu_d_cor$snake_mu_effect_sd,"_",mu_d_cor$newt_mu_rate, "_", mu_d_cor$newt_mu_effect_sd)
mu_d_cor$sim=LETTERS[factor(mu_d_cor$group)]

```

```{r, cor box set up}

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

suppressMessages(print(plot))

  return(plot)
}

var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  real_snewt_var = var(snewt$dif)
  var_cor_table=data.frame()

  for(i in 1:length(unique(file$snake_newt_rep))){
    pattern<-unique(file$snake_newt_rep)[i]
    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]

    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  }

  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)

  plot <- ggplot(var_cor_table) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

  return(plot)
}

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=mu_a_lit
#cfile=mu_a_cor 
 # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]

  if(nrow(cfile)>nrow(file)){
    toDelete <- seq(0, nrow(cfile), 2)
    cfile_short <-  cfile[-toDelete, ]
  }else{
    cfile_short <-  cfile
  }

  if(nrow(cfile_short)>nrow(file)){
      toDelete <- seq(0, nrow(cfile_short), 2)
      cfile_short <-  cfile_short[-toDelete, ]
    }
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}

four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

```

```{r, general file and graph making}

#the functions to make the params file and the summary and heatmap figures

create_parm_file <- function(file, min_gen, max_gen){
params <- data_frame()

for(i in 1:length(unique(file$snake_newt_rep))){

  pattern=unique(file$snake_newt_rep)[i]
  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]

  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=sumitup$snake_mu_rate[1],
                           newt_mu_rate=sumitup$newt_mu_rate[1],
                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
                           rep=sumitup$rep[1])

  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$snake_newt <- paste0(params$snake, "_", params$newt)
return(params)
}

 create_parm_file_nc <- function(file, min_gen, max_gen){

   file$test_factor <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params <- data_frame()

for(i in 1:length(unique(file$test_factor))){

  pattern=unique(file$test_factor)[i]

  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$test_factor ==pattern),]

  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=unlist(strsplit(pattern, "_"))[2],
                           newt_mu_rate=unlist(strsplit(pattern, "_"))[4],
                           snake_mu_effect_sd=unlist(strsplit(pattern, "_"))[3],
                           newt_mu_effect_sd=unlist(strsplit(pattern, "_"))[5],
                           rep=unlist(strsplit(pattern, "_"))[6],
                           test_factor=pattern)

  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$snake_newt <- paste0(params$snake, "_", params$newt)
return(params)
}

GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label ){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)
params = na.omit(params)
my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}

GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)
params = na.omit(params)
my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}

build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
  params<-create_parm_file(file, min_gen, max_gen)
  params = na.omit(params)

 my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))

 if(red_blue==FALSE){
  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
  }
 if(red_blue==TRUE){
  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
 }

  return(my_plot)
}

trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){

  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
  return(plot)
}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
  xlim((-1*themax)-5, themax+5)+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)
}

pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  themin <- min(file$dif) 
  themax <- max(file$dif)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(dif), fill="aquamarine4")+
  xlim((-1*true_max)-1, true_max+1)+

  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]

  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]

  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])

dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file=mu_a_lit
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]

  thepopmin <- min(file$newt_deaths)
  thepopmax <- max(file$newt_deaths)
  thedifmin <- min(file$snake_deaths) 
  thedifmax <- max(file$snake_deaths)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])

dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
  #scale_y_continuous(labels = scales::percent)+
  #xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  #geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

#two_hist_death_all_rep(mu_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)

grid_plot<- function(file_name, spegen, file, type, row_num, col_num){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
GA1_type = paste0("generation|", type)

GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
GA1_type <- GA1_type[-1]

data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)

data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)

data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))

main_plot<-ggplot(data_long_type_comp)+

  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  #ylim(0, row_num)+
  #xlim(0, col_num)+
  theme_bw()+
  theme(legend.justification = "top")

if(type != "num_ind"){
main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
 scale_fill_viridis_c()
}
if(type == "num_ind"){
main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Newt/Snake PopSize")+
scale_fill_viridis_c(option = "plasma")
}

snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
newt$snake_value <- snake$measurement
print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))

newt$info <- "middle"

#need to look into, coloring problem
newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"

extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
return(final_plot)}

```

## Mean Phenotype Whole Simulation {.tabset}

### Phenotype differences (mu_a)
```{r, graphing by gen}
trends_by_gen(mu_a_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

#aggregate(mu_a_lit[which(mu_a_lit$generation>=100 & mu_a_lit$generation<=50000),]$dif, list(mu_a_lit[which(mu_a_lit$generation>=100 & mu_a_lit$generation<=50000),]$group_rep), FUN=mean)

```

### Table of average Differences (mu_a)

```{r, average difference}
aggregate(mu_a_lit[which(mu_a_lit$generation>=100 & mu_a_lit$generation<=50000),]$dif, list(mu_a_lit[which(mu_a_lit$generation>=100 & mu_a_lit$generation<=50000),]$group), FUN=mean) 
```

### Phenotype differences (mu_b)
```{r, graphing by gen lw}
trends_by_gen(mu_b_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

```

### Table of average Differences (mu_b)

```{r, average difference lw}
aggregate(mu_b_lit[which(mu_b_lit$generation>=100 & mu_b_lit$generation<=50000),]$dif, list(mu_b_lit[which(mu_b_lit$generation>=100 & mu_b_lit$generation<=50000),]$group), FUN=mean) 
```

### Phenotype differences (mu_c)
```{r, graphing by gen ne}
trends_by_gen(mu_c_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

```

### Table of average Differences (mu_c)

```{r, average difference ne}
aggregate(mu_c_lit[which(mu_c_lit$generation>=100 & mu_c_lit$generation<=50000),]$dif, list(mu_c_lit[which(mu_c_lit$generation>=100 & mu_c_lit$generation<=50000),]$group), FUN=mean) 
```

### Phenotype differences (mu_d)
```{r, graphing by gen mud}
trends_by_gen(mu_d_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

```

### Table of average Differences (mu_d)

```{r, average difference mud}
aggregate(mu_d_lit[which(mu_d_lit$generation>=100 & mu_d_lit$generation<=50000),]$dif, list(mu_d_lit[which(mu_d_lit$generation>=100 & mu_d_lit$generation<=50000),]$group), FUN=mean) 
```

## {-}

## Connection between higher phenotype and population{.tabset}

### Phenotype differences (mu_a)
```{r, whale}
min_gen=5000
max_gen=10000
rep=1

whale_gen(mu_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (mu_a)
```{r, popsize and pheno}

suppressMessages(print(two_hist(mu_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

### Phenotype differences (mu_b)
```{r, whale lw}
min_gen=5000
max_gen=10000
rep=1

whale_gen(mu_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (mu_b)
```{r, popsize and pheno lw}

suppressMessages(print(two_hist(mu_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

### Phenotype differences (mu_c)
```{r, whale ne}
min_gen=5000
max_gen=10000
rep=1

whale_gen(mu_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (mu_c)
```{r, popsize and pheno ne}

suppressMessages(print(two_hist(mu_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

### Phenotype differences (mu_d)
```{r, whale mud}
min_gen=5000
max_gen=10000
rep=1

whale_gen(mu_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (mu_d)
```{r, popsize and pheno mud}

suppressMessages(print(two_hist(mu_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

```

## {-}

## Correlation{.tabset}

### cor (mu_a)
```{r, combo myplots}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(mu_a_cor, "Simulation Correlation Comparied to Real Correlation Trials", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

### cor (mu_b)
```{r, combo myplots lw}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(mu_b_cor, "Simulation Correlation Comparied to Real Correlation Trials", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

### cor (mu_c)
```{r, combo myplots ne}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(mu_c_cor, "Simulation Correlation Comparied to Real Correlation Trials", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

### cor (mu_d)
```{r, combo myplots mud}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(mu_d_cor, "Simulation Correlation Comparied to Real Correlation Trials", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

```

## {-}

## Correlation Histograms Mu A{.tabset}

### Plot 1
```{r, GA1 cor by dif windows}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_a_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation Histograms Mu B {.tabset}

### Plot 1
```{r, GA1 cor by dif windows lw}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2 lw}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3 lw}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4 lw}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5 lw}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6 lw}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7 lw}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8 lw}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9 lw}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10 lw}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_b_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation Histograms Mu C {.tabset}

### Plot 1
```{r, GA1 cor by dif windows ne}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2 ne}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3 ne}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4 ne}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5 ne}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6 ne}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7 ne}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8 ne}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9 ne}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10 ne}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_c_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation Histograms Mu D {.tabset}

### Plot 1
```{r, GA1 cor by dif windows mud}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2 mud}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3 mud}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4 mud}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5 mud}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6 mud}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7 mud}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8 mud}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9 mud}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10 mud}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(mu_d_cor, "Simulation Correlation Comparied to Real Correlation", "mu = NUM", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

## Correlation across time (mu_a)  {.tabset}

### Random 1 (mu_a)  
```{r, GA1 cor and pheno}
GA1_pattern <- unique(paste0(mu_a_lit$snake_mu_rate, "_", mu_a_lit$snake_mu_effect_sd,"_",mu_a_lit$newt_mu_rate, "_", mu_a_lit$newt_mu_effect_sd, "_", mu_a_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(mu_a_lit, mu_a_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(mu_a_lit, mu_a_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (mu_a)
```{r, random cor-pheno plot 2}

cor_trends_by_gen(mu_a_lit, mu_a_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (mu_a)
```{r, random cor-pheno plot 3}

cor_trends_by_gen(mu_a_lit, mu_a_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## Correlation across time (mu_b)  {.tabset}

### Random 1 (mu_b)  
```{r, GA1 cor and pheno  lw}
GA1_pattern <- unique(paste0(mu_b_lit$snake_mu_rate, "_", mu_b_lit$snake_mu_effect_sd,"_",mu_b_lit$newt_mu_rate, "_", mu_b_lit$newt_mu_effect_sd, "_", mu_b_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(mu_b_lit, mu_b_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(mu_b_lit, mu_b_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (mu_b)
```{r, random cor-pheno plot 2  lw}

cor_trends_by_gen(mu_b_lit, mu_b_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (mu_b)
```{r, random cor-pheno plot 3  lw}

cor_trends_by_gen(mu_b_lit, mu_b_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## Correlation across time (mu_c)  {.tabset}

### Random 1 (mu_c)  
```{r, GA1 cor and pheno ne}
GA1_pattern <- unique(paste0(mu_c_lit$snake_mu_rate, "_", mu_c_lit$snake_mu_effect_sd,"_",mu_c_lit$newt_mu_rate, "_", mu_c_lit$newt_mu_effect_sd, "_", mu_c_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(mu_c_lit, mu_c_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(mu_c_lit, mu_c_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (mu_c)
```{r, random cor-pheno plot 2 ne}

cor_trends_by_gen(mu_c_lit, mu_c_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (mu_c)
```{r, random cor-pheno plot 3 ne}

cor_trends_by_gen(mu_c_lit, mu_c_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## Correlation across time (mu_d)  {.tabset}

### Random 1 (mu_d)  
```{r, GA1 cor and pheno  mud}
GA1_pattern <- unique(paste0(mu_d_lit$snake_mu_rate, "_", mu_d_lit$snake_mu_effect_sd,"_",mu_d_lit$newt_mu_rate, "_", mu_d_lit$newt_mu_effect_sd, "_", mu_d_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(mu_d_lit, mu_d_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(mu_d_lit, mu_d_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  (mu_d)
```{r, random cor-pheno plot 2  mud}

cor_trends_by_gen(mu_d_lit, mu_d_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  (mu_d)
```{r, random cor-pheno plot 3  mud}

cor_trends_by_gen(mu_d_lit, mu_d_cor, "test", "mu = NUM", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (mu_a) {.tabset}

### Pheno Beginning (mu_a)

```{r, early plots}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(mu_a_lit$rep))){
#   myine<-whale_gen(mu_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[1])
```

### Pheno Middle (mu_a)

```{r, middle plots}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(mu_a_lit$rep))){
#   myine<-whale_gen(mu_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[1])
```

### Pheno End (mu_a)

```{r, end plots}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(mu_a_lit$rep))){
#   myine<-whale_gen(mu_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_a_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[1])
```

### Dif Beginning (mu_a)
```{r, early plots 1a}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(mu_a_lit$rep))){
#   myine<-two_hist(mu_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[1] )

```

### Dif Middle (mu_a)
```{r, early plots 2a}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(mu_a_lit$rep))){
#   myine<-two_hist(mu_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[1] )

```

### Dif End (mu_a)
```{r, early plots 3a}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(mu_a_lit$rep))){
#   myine<-two_hist(mu_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_a_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_a_lit$rep)[1] )

```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (mu_b) {.tabset}

### Pheno Beginning (mu_b)

```{r, early plots lw}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(mu_b_lit$rep))){
#   myine<-whale_gen(mu_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[1])
```

### Pheno Middle (mu_b)

```{r, middle plots lw}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(mu_b_lit$rep))){
#   myine<-whale_gen(mu_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[1])
```

### Pheno End (mu_b)

```{r, end plots lw}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(mu_b_lit$rep))){
#   myine<-whale_gen(mu_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_b_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[1])
```

### Dif Beginning (mu_b)
```{r, early plots 1a lw}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(mu_b_lit$rep))){
#   myine<-two_hist(mu_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[1] )

```

### Dif Middle (mu_b)
```{r, early plots 2a lw}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(mu_b_lit$rep))){
#   myine<-two_hist(mu_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[1] )

```

### Dif End (mu_b)
```{r, early plots 3a lw}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(mu_b_lit$rep))){
#   myine<-two_hist(mu_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_b_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_b_lit$rep)[1] )

```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (mu_c) {.tabset}

### Pheno Beginning (mu_c)

```{r, early plots ne}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(mu_c_lit$rep))){
#   myine<-whale_gen(mu_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[1])
```

### Pheno Middle (mu_c)

```{r, middle plots ne}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(mu_c_lit$rep))){
#   myine<-whale_gen(mu_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[1])
```

### Pheno End (mu_c)

```{r, end plots ne}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(mu_c_lit$rep))){
#   myine<-whale_gen(mu_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_c_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[1])
```

### Dif Beginning (mu_c)
```{r, early plots 1a ne}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(mu_c_lit$rep))){
#   myine<-two_hist(mu_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[1] )

```

### Dif Middle (mu_c)
```{r, early plots 2a ne}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(mu_c_lit$rep))){
#   myine<-two_hist(mu_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[1] )

```

### Dif End (mu_c)
```{r, early plots 3a ne}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(mu_c_lit$rep))){
#   myine<-two_hist(mu_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_c_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_c_lit$rep)[1] )

```

## {-}

## What happens over time (looking at the beginning, middle, and late part of my simulations) (mu_d) {.tabset}

### Pheno Beginning (mu_d)

```{r, early plots mud}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(mu_d_lit$rep))){
#   myine<-whale_gen(mu_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[1])
```

### Pheno Middle (mu_d)

```{r, middle plots mud}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(mu_d_lit$rep))){
#   myine<-whale_gen(mu_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[1])
```

### Pheno End (mu_d)

```{r, end plots mud}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(mu_d_lit$rep))){
#   myine<-whale_gen(mu_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(mu_d_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[1])
```

### Dif Beginning (mu_d)
```{r, early plots 1a mud}

min_gen=100
max_gen=5000

# for(i in 1:length(unique(mu_d_lit$rep))){
#   myine<-two_hist(mu_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[1] )

```

### Dif Middle (mu_d)
```{r, early plots 2a mud}

min_gen=25000
max_gen=30000

# for(i in 1:length(unique(mu_d_lit$rep))){
#   myine<-two_hist(mu_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[1] )

```

### Dif End (mu_d)
```{r, early plots 3a mud}

min_gen=45000
max_gen=50000

# for(i in 1:length(unique(mu_d_lit$rep))){
#   myine<-two_hist(mu_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(mu_d_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(mu_d_lit$rep)[1] )

```

## {-}

## Summary (mu_a) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary}

min_gen=100
max_gen=5000
GA_summary(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3}
min_gen=45000
max_gen=50000

# summary
GA_summary(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1}

min_gen=100
max_gen=5000

GA_summary(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2}
min_gen=25000
max_gen=30000

GA_summary(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3}
min_gen=45000
max_gen=50000
GA_summary(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1}
min_gen=100
max_gen=5000
#

GA_summary_by_species(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1}
min_gen=100
max_gen=5000
#

GA_summary_by_species(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(mu_a_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Summary (mu_b) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary lw}

min_gen=100
max_gen=5000
GA_summary(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2 lw}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3 lw}
min_gen=45000
max_gen=50000

# summary
GA_summary(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1 lw}

min_gen=100
max_gen=5000

GA_summary(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2 lw}
min_gen=25000
max_gen=30000

GA_summary(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3 lw}
min_gen=45000
max_gen=50000
GA_summary(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1 lw}
min_gen=100
max_gen=5000
#

GA_summary_by_species(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2 lw}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3 lw}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1 lw}
min_gen=100
max_gen=5000
#

GA_summary_by_species(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2 lw}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3 lw}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(mu_b_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Summary (mu_c) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary ne}

min_gen=100
max_gen=5000
GA_summary(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2 ne}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3 ne}
min_gen=45000
max_gen=50000

# summary
GA_summary(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1 ne}

min_gen=100
max_gen=5000

GA_summary(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2 ne}
min_gen=25000
max_gen=30000

GA_summary(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3 ne}
min_gen=45000
max_gen=50000
GA_summary(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1 ne}
min_gen=100
max_gen=5000
#

GA_summary_by_species(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2 ne}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3 ne}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1 ne}
min_gen=100
max_gen=5000
#

GA_summary_by_species(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2 ne}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3 ne}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(mu_c_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Summary (mu_d) {.tabset}

### Early-Sim Population Size Summary

```{r, early plots summary mud}

min_gen=100
max_gen=5000
GA_summary(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2 mud}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3 mud}
min_gen=45000
max_gen=50000

# summary
GA_summary(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1 mud}

min_gen=100
max_gen=5000

GA_summary(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2 mud}
min_gen=25000
max_gen=30000

GA_summary(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3 mud}
min_gen=45000
max_gen=50000
GA_summary(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### By Snake GA (Early)
```{r, snakega plots summary 1 mud}
min_gen=100
max_gen=5000
#

GA_summary_by_species(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2 mud}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3 mud}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1 mud}
min_gen=100
max_gen=5000
#

GA_summary_by_species(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2 mud}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Late)
```{r, newtga plots summary 3 mud}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(mu_d_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Heatmap (mu_a) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(mu_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)
```{r, early plots Heatmap 2}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(mu_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late)
```{r, early plots Heatmap 3}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(mu_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early)
```{r, early plots Heatmap pheno 1}
min_gen=100
max_gen=5000
build_heatmap(mu_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid)
```{r, early plots Heatmap pheno 2}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(mu_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late)
```{r, early plots Heatmap pheno 3}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(mu_a_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

## Heatmap (mu_b) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap lw}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(mu_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)
```{r, early plots Heatmap 2 lw}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(mu_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late)
```{r, early plots Heatmap 3 lw}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(mu_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early)
```{r, early plots Heatmap pheno 1 lw}
min_gen=100
max_gen=5000
build_heatmap(mu_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid)
```{r, early plots Heatmap pheno 2 lw}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(mu_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late)
```{r, early plots Heatmap pheno 3 lw}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(mu_b_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

## Heatmap (mu_c) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap ne}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(mu_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)
```{r, early plots Heatmap 2 ne}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(mu_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late)
```{r, early plots Heatmap 3 ne}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(mu_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early)
```{r, early plots Heatmap pheno 1 ne}
min_gen=100
max_gen=5000
build_heatmap(mu_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid)
```{r, early plots Heatmap pheno 2 ne}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(mu_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late)
```{r, early plots Heatmap pheno 3 ne}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(mu_c_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

## Heatmap (mu_d) {.tabset}

### Population Size (Early)

```{r, early plots Heatmap mud}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(mu_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)
```{r, early plots Heatmap 2 mud}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(mu_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late)
```{r, early plots Heatmap 3 mud}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(mu_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early)
```{r, early plots Heatmap pheno 1 mud}
min_gen=100
max_gen=5000
build_heatmap(mu_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid)
```{r, early plots Heatmap pheno 2 mud}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(mu_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late)
```{r, early plots Heatmap pheno 3 mud}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(mu_d_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}

```{r, red in grid files}
require(readr)
mu_a_grid<- read.csv("~/Desktop/low_to_high_v/mu_a/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
mu_a_grid$group_rep <- paste0(mu_a_grid$snake_mu_rate, "_", mu_a_grid$snake_mu_effect_sd,"_",mu_a_grid$newt_mu_rate, "_", mu_a_grid$newt_mu_effect_sd, "_", mu_a_grid$rep)
mu_a_grid$group <- paste0(mu_a_grid$snake_mu_rate, "_", mu_a_grid$snake_mu_effect_sd,"_",mu_a_grid$newt_mu_rate, "_", mu_a_grid$newt_mu_effect_sd)
mu_a_grid$sim=LETTERS[factor(mu_a_grid$group)]
mu_a_grid$grid_num = 5

```

```{r, red in grid files lw}
require(readr)
mu_b_grid<- read.csv("~/Desktop/low_to_high_v/mu_b/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
mu_b_grid$group_rep <- paste0(mu_b_grid$snake_mu_rate, "_", mu_b_grid$snake_mu_effect_sd,"_",mu_b_grid$newt_mu_rate, "_", mu_b_grid$newt_mu_effect_sd, "_", mu_b_grid$rep)
mu_b_grid$group <- paste0(mu_b_grid$snake_mu_rate, "_", mu_b_grid$snake_mu_effect_sd,"_",mu_b_grid$newt_mu_rate, "_", mu_b_grid$newt_mu_effect_sd)
mu_b_grid$sim=LETTERS[factor(mu_b_grid$group)]
mu_b_grid$grid_num = 5

```

```{r, red in grid files ne}
require(readr)
mu_c_grid<- read.csv("~/Desktop/low_to_high_v/mu_c/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
mu_c_grid$group_rep <- paste0(mu_c_grid$snake_mu_rate, "_", mu_c_grid$snake_mu_effect_sd,"_",mu_c_grid$newt_mu_rate, "_", mu_c_grid$newt_mu_effect_sd, "_", mu_c_grid$rep)
mu_c_grid$group <- paste0(mu_c_grid$snake_mu_rate, "_", mu_c_grid$snake_mu_effect_sd,"_",mu_c_grid$newt_mu_rate, "_", mu_c_grid$newt_mu_effect_sd)
mu_c_grid$sim=LETTERS[factor(mu_c_grid$group)]
mu_c_grid$grid_num = 5

```

```{r, red in grid files mud}
require(readr)
mu_d_grid<- read.csv("~/Desktop/low_to_high_v/mu_d/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
mu_d_grid$group_rep <- paste0(mu_d_grid$snake_mu_rate, "_", mu_d_grid$snake_mu_effect_sd,"_",mu_d_grid$newt_mu_rate, "_", mu_d_grid$newt_mu_effect_sd, "_", mu_d_grid$rep)
mu_d_grid$group <- paste0(mu_d_grid$snake_mu_rate, "_", mu_d_grid$snake_mu_effect_sd,"_",mu_d_grid$newt_mu_rate, "_", mu_d_grid$newt_mu_effect_sd)
mu_d_grid$sim=LETTERS[factor(mu_d_grid$group)]
mu_d_grid$grid_num = 5

```

## What is up with the correlations

## Early Simulation Correlation (mu_a)  {.tabset}

### Mean
```{r, cor grid high cor mean}

file=mu_a_grid
file_name_a="1e-08_0.05_1e-08_0.0158_1"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max}

file=mu_a_grid
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min}

file=mu_a_grid
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize}

file=mu_a_grid
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_a, spegen, file, type, row_num, col_num)

```

## {-}

## Early Simulation Correlation (mu_b)  {.tabset}

### Mean
```{r, cor grid high cor mean lw}

file=mu_b_grid
file_name_b="1e-09_0.158_1e-09_0.5_1"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max lw}

file=mu_b_grid
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min lw}

file=mu_b_grid
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize lw}

file=mu_b_grid
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_b, spegen, file, type, row_num, col_num)

```

## {-}

## Early Simulation Correlation (mu_c)  {.tabset}

### Mean
```{r, cor grid high cor mean ne}

file=mu_c_grid
file_name_c="1e-10_0.5_1e-10_1.58_1"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max  ne}

file=mu_c_grid
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min ne}

file=mu_c_grid
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize ne}

file=mu_c_grid
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_c, spegen, file, type, row_num, col_num)

```

## {-}

## Early Simulation Correlation (mu_d)  {.tabset}

### Mean
```{r, cor grid high cor mean vd}

file=mu_d_grid
file_name_d="1e-11_1.58_1e-11_5_1"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max vd}

file=mu_d_grid
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min vd}

file=mu_d_grid
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize vd}

file=mu_d_grid
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_d, spegen, file, type, row_num, col_num)

```

## {-}

```{r, red in grid files 2}
require(readr)
mu_a_grid<- read.csv("~/Desktop/low_to_high_v/mu_a/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
mu_a_grid$group_rep <- paste0(mu_a_grid$snake_mu_rate, "_", mu_a_grid$snake_mu_effect_sd,"_",mu_a_grid$newt_mu_rate, "_", mu_a_grid$newt_mu_effect_sd, "_", mu_a_grid$rep)
mu_a_grid$group <- paste0(mu_a_grid$snake_mu_rate, "_", mu_a_grid$snake_mu_effect_sd,"_",mu_a_grid$newt_mu_rate, "_", mu_a_grid$newt_mu_effect_sd)
mu_a_grid$sim=LETTERS[factor(mu_a_grid$group)]
mu_a_grid$grid_num = 5

```

```{r, red in grid files 2 lw}
require(readr)
mu_b_grid<- read.csv("~/Desktop/low_to_high_v/mu_b/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
mu_b_grid$group_rep <- paste0(mu_b_grid$snake_mu_rate, "_", mu_b_grid$snake_mu_effect_sd,"_",mu_b_grid$newt_mu_rate, "_", mu_b_grid$newt_mu_effect_sd, "_", mu_b_grid$rep)
mu_b_grid$group <- paste0(mu_b_grid$snake_mu_rate, "_", mu_b_grid$snake_mu_effect_sd,"_",mu_b_grid$newt_mu_rate, "_", mu_b_grid$newt_mu_effect_sd)
mu_b_grid$sim=LETTERS[factor(mu_b_grid$group)]
mu_b_grid$grid_num = 5

```

```{r, red in grid files 2 ne}
require(readr)
mu_c_grid<- read.csv("~/Desktop/low_to_high_v/mu_c/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
mu_c_grid$group_rep <- paste0(mu_c_grid$snake_mu_rate, "_", mu_c_grid$snake_mu_effect_sd,"_",mu_c_grid$newt_mu_rate, "_", mu_c_grid$newt_mu_effect_sd, "_", mu_c_grid$rep)
mu_c_grid$group <- paste0(mu_c_grid$snake_mu_rate, "_", mu_c_grid$snake_mu_effect_sd,"_",mu_c_grid$newt_mu_rate, "_", mu_c_grid$newt_mu_effect_sd)
mu_c_grid$sim=LETTERS[factor(mu_c_grid$group)]
mu_c_grid$grid_num = 5

```

```{r, red in grid files 2 mud}
require(readr)
mu_d_grid<- read.csv("~/Desktop/low_to_high_v/mu_d/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
mu_d_grid$group_rep <- paste0(mu_d_grid$snake_mu_rate, "_", mu_d_grid$snake_mu_effect_sd,"_",mu_d_grid$newt_mu_rate, "_", mu_d_grid$newt_mu_effect_sd, "_", mu_d_grid$rep)
mu_d_grid$group <- paste0(mu_d_grid$snake_mu_rate, "_", mu_d_grid$snake_mu_effect_sd,"_",mu_d_grid$newt_mu_rate, "_", mu_d_grid$newt_mu_effect_sd)
mu_d_grid$sim=LETTERS[factor(mu_d_grid$group)]
mu_d_grid$grid_num = 5

```

## Late Simulation Correlation (mu_a) {.tabset}

### Mean
```{r, cor grid high cor mean late}
#1e-11_5_1e-10_0.5_0
file=mu_a_grid
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max late}

file=mu_a_grid
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min late}

file=mu_a_grid
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name_a, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late}

file=mu_a_grid
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_a, spegen, file, type, row_num, col_num)

```

## {-}

## Late Simulation Correlation (mu_b) {.tabset}

### Mean
```{r, cor grid high cor mean late lw}

file=mu_b_grid
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max late lw}

file=mu_b_grid
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min late lw}

file=mu_b_grid
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name_b, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late lw}

file=mu_b_grid
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_b, spegen, file, type, row_num, col_num)

```

## {-}

## Late Simulation Correlation (mu_c) {.tabset}

### Mean
```{r, cor grid high cor mean late ne}

file=mu_c_grid
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max late ne}

file=mu_c_grid
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min late ne}

file=mu_c_grid
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name_c, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late ne}

file=mu_c_grid
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_c, spegen, file, type, row_num, col_num)

```

## {-}

## Late Simulation Correlation (mu_d) {.tabset}

### Mean
```{r, cor grid high cor mean late mud}

file=mu_d_grid
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Max
```{r, cor grid high cor max late mud}

file=mu_d_grid
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Min
```{r, cor grid high cor min late mud}

file=mu_d_grid
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name_d, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late mud}

file=mu_d_grid
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name_d, spegen, file, type, row_num, col_num)

```

## {-}

### 2023-01-18 graphs_newt_snakes/move_together.Rmd
I have updated the results for the last set of experiments. Tomorrow I will need to spend some time reviewing them.

@@
 ## {-}
+
+```{r, finding the slope of coevolution}
+
+newt_first_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$Newt_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$group_rep), FUN=mean), c("group_rep", "Nstart" ))
+
+snake_first_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$Snake_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$group_rep), FUN=mean) , c("group_rep", "Sstart" ))
+
+newt_last_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$Newt_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$group_rep), FUN=mean), c("group_rep", "Nend" ))
+
+snake_last_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$Snake_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$group_rep), FUN=mean), c("group_rep", "Send" ))
+
+mean_phenotype_of_group = cbind(newt_first_mean_pheno, newt_last_mean_pheno[2], snake_first_mean_pheno[2], snake_last_mean_pheno[2])
+
+move_together_lit$Nstart = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"Nstart"]
+
+move_together_lit$Sstart = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"Sstart"]
+
+move_together_lit$Nend = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"Nend"]
+
+move_together_lit$Send = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"Send"]
+
+genstart_newt = setNames(aggregate(move_together_lit[which(move_together_lit$Newt_mean_Pheno<=(move_together_lit$Nstart)) ,]$generation, list(move_together_lit[which(move_together_lit$Newt_mean_Pheno<=(move_together_lit$Nstart)),]$group_rep), FUN=max), c("group_rep", "Nstr_gen"))
+
+genstart_snake = setNames(aggregate(move_together_lit[which(move_together_lit$Snake_mean_Pheno<=(move_together_lit$Sstart)) ,]$generation, list(move_together_lit[which(move_together_lit$Snake_mean_Pheno<=(move_together_lit$Sstart)),]$group_rep), FUN=max), c("group_rep", "Sstr_gen"))
+
+move_together_lit$Nstr_gen <- genstart_newt[match(move_together_lit$group_rep, genstart_newt$group_rep),'Nstr_gen']
+move_together_lit$Sstr_gen <- genstart_snake[match(move_together_lit$group_rep, genstart_snake$group_rep),'Sstr_gen']
+
+genend_newt = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(move_together_lit$Nend)) ,]$generation, list(move_together_lit[which( move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(move_together_lit$Nend)),]$group_rep), FUN=min)
+
+genend_snake = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(move_together_lit$Send)) ,]$generation, list(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(move_together_lit$Send)),]$group_rep), FUN=min)
+
+move_together_lit$genend_newt <- genend_newt[match(move_together_lit$group_rep, genend_newt$Group.1),'x']
+move_together_lit$genend_snake <- genend_snake[match(move_together_lit$group_rep, genend_snake$Group.1),'x']
+
+# get the difference in generation time and the difference in phenotype
+
+```
+
+```{r, making newts and snakes in grid form}
+
+duo_grid_plot<- function(file_name, spegen, file, type, row_num, col_num){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
+GA1_type = paste0("generation|", type)
+
+GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
+GA1_type <- GA1_type[-1]
+
+data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
+data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)
+
+data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)
+
+data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))
+
+main_plot<-ggplot(data_long_type_comp, aes(x = x_loc, y = y_loc))+
+  geom_tile(aes(fill = as.numeric(measurement)))+
+  facet_wrap(~species)+
+
+  theme_bw()+
+  theme(legend.justification = "top")
+
+if(type != "num_ind"){
+  main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
+                               subtitle = paste0(file_name, ", Generation: ", spegen),
+                               fill = "Toxicity/Resistance")+
+    scale_fill_viridis_c()
+}
+if(type == "num_ind"){
+  main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
+                               subtitle = paste0(file_name, ", Generation: ", spegen),
+                               fill = "Newt/Snake PopSize")+
+    scale_fill_viridis_c(option = "plasma")
+}
+
+snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
+newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
+newt$snake_value <- snake$measurement
+print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))
+
+newt$info <- "middle"
+
+#need to look into, coloring problem
+newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"
+
+extra_plot <- ggplot(newt)+
+  ggtitle("Mean Phenotype") +
+  xlab("Newt") + ylab("Snake")+
+  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
+  theme_bw()+
+  theme(text = element_text(size=10),title =element_text(size=8),
+        legend.text = element_text(size = 8),
+        legend.position ="bottom",
+        legend.key.size = unit(0.1, "lines"),
+        legend.title=element_blank())+
+  guides(shape = guide_legend(override.aes = list(size = 1)),
+         color = guide_legend(override.aes = list(size = 1)))
+
+final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
+
+return(final_plot)}
+
+```

### 2023-01-26 graphs_newt_snakes/Same_V.Rmd
small sim to community for slim 4 and some edits to other files

@@
 
+Run four sets of simulations each with 16 different genetic architectures (GA), to explore how changing mutation rate and the standard deviation of mutation effect size can impact how traits coevolve.
+Each GA within a simulation set will have the same mutational variance.
+
 ### Questions:
 
-What does it mean to be correlated?
+What does it mean to be correlated and can I get spatial phenotypic correlation when populations of newts and snakes are coevolving?
 
@@
 Experiment values:
+
+V = 2.5e^-13:
+
+- mu = 1e^-8 sig = 0.005
+- mu = 1e^-9 sig = 0.0158
+- mu = 1e^-10 sig = 0.05
+- mu = 1e^-11 sig = 0.158
+
+V = 2.5e^-12:
+
+- mu = 1e^-8 sig = 0.0158
+- mu = 1e^-9 sig = 0.05
+- mu = 1e^-10 sig = 0.158
+- mu = 1e^-11 sig = 0.5
+
+V = 2.5e^-11:
+
+- mu = 1e^-8 sig = 0.05
+- mu = 1e^-9 sig = 0.158
+- mu = 1e^-10 sig = 0.5
+- mu = 1e^-11 sig = 1.58
+
+V = 2.5e^-10:
+
+- mu = 1e^-8 sig = 0.158
+- mu = 1e^-9 sig = 0.5
+- mu = 1e^-10 sig = 1.58
+- mu = 1e^-11 sig = 5.0
 

### 2023-01-26 graphs_newt_snakes/high_to_low_v.Rmd
small sim to community for slim 4 and some edits to other files

@@
 
+I ran 4 simulation sets, where in each set the mutation rate stayed constant and I changed the mutation effect size to create varying levels of mutational variance.
+
 ### Questions:
 
-What does it mean to be correlated?
+What does it mean to be correlated? How much of an advantage is an increase in mutational variance for a species involved in an coevolutionary race?
 
@@
 Experiment values:
+
+mu = 1e^-8:
+
+ - sig = 0.005, MV = 2.5e^-13
+ - sig = 0.0158, MV = 2.5e^-12
+ - sig = 0.05, MV = 2.5e^-11
+ - sig = 0.158, MV = 2.5e^-10
+
+ mu = 1e^-9:
+
+ - sig = 0.0158, MV = 2.5e^-13
+ - sig = 0.05, MV = 2.5e^-12
+ - sig = 0.158, MV = 2.5e^-11
+ - sig = 0.5, MV = 2.5e^-10
+
+ mu = 1e^-10:
+
+ - sig = 0.05, MV = 2.5e^-13
+ - sig = 0.158, MV = 2.5e^-12
+ - sig = 0.5, MV = 2.5e^-11
+ - sig = 1.58, MV = 2.5e^-10
+
+ mu = 1e^-11:
+
+ - sig = 0.158, MV = 2.5e^-13
+ - sig = 0.5, MV = 2.5e^-12
+ - sig = 1.58, MV = 2.5e^-11
+ - sig = 5.0, MV = 2.5e^-10
 

### 2023-01-26 graphs_newt_snakes/move_together.Rmd
small sim to community for slim 4 and some edits to other files

@@
 
+Start populations in the lower third of the simulation and let them move as they co-evolve.
+It is possible that as newts and snakes move into new territory they might create more spatial phenotype correlation.
+
 ### Questions:
 
-What does it mean to be correlated? Might this occur if I simulatate some controlled movement?
+What does it mean to be correlated? Might this occur if I simulate some controlled movement?
 
 ## Background
+
+I am running a coevolution experiment where newts and snakes interaction with each other over long periods of time.
+When they interact the newt or snake with the highest level of toxicity or resistance will survive.
+As newts and snake interact across space, they develop exaggerated traits that can become spatial correlated.
+My experiments examine when traits became exaggerated or correlated.
 
@@
 
-genend_newt = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(move_together_lit$Nend)) ,]$generation, list(move_together_lit[which( move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(move_together_lit$Nend)),]$group_rep), FUN=min)
-
-genend_snake = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(move_together_lit$Send)) ,]$generation, list(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(move_together_lit$Send)),]$group_rep), FUN=min)
+genend_newt = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(.98*(move_together_lit$Nend))) ,]$generation, list(move_together_lit[which( move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(.98*move_together_lit$Nend)),]$group_rep), FUN=min)
+
+genend_snake = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(.98*move_together_lit$Send)) ,]$generation, list(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(.98*move_together_lit$Send)),]$group_rep), FUN=min)
 
@@
 
-```
-
-```{r, making newts and snakes in grid form}
+npt<-ggplot(move_together_lit) +
+geom_boxplot(aes(sim, genend_newt), color="darkred")
+spt<-ggplot(move_together_lit) +
+geom_boxplot(aes(sim, genend_snake), color="steelblue")
+#  geom_point(aes(group_rep, genend_newt), color="darkred")+
+ # geom_point(aes(group_rep, genend_snake), color="steelblue")
+grid.arrange(npt, spt, ncol=1)
+ggplot(move_together_lit) +
+  facet_wrap(~sim)+
+geom_point(aes(rep, genend_newt), color="darkred")+
+geom_point(aes(rep, genend_snake), color="steelblue")
+
+ggplot(move_together_lit) +
+geom_boxplot(aes(sim, genend_snake-genend_newt), color="black")
+
+```
+
+```{r, making newts and snakes in grid form look nice}
 
@@
   facet_wrap(~species)+
-
+  coord_fixed() +
   theme_bw()+
-  theme(legend.justification = "top")
-
+  #margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")+
+  theme( legend.justification = "top", 
+         plot.margin = margin(t = 0.3,  # Top margin
+                             r = 0,  # Right margin
+                             b = 0.3,  # Bottom margin
+                             l = 0,  # Left margin
+                             unit = "cm")  ) # legend.position ="bottom"
+#plot.margin = unit(c(1, 1, 3, 1), "cm"),
 if(type != "num_ind"){
@@
 
-final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
+bloan <- ggplot() + theme_void()
+final_plot <- grid.arrange(main_plot, arrangeGrob(bloan, extra_plot), ncol = 2)
+
+grid.arrange(main_plot, bloan, extra_plot, ncol = 2, 
+             layout_matrix=cbind(c(1,1),c(2,3)))
+
+#final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
 
@@
 
-```
+file=move_together_grid
+file_name="1e-11_5_1e-10_0.5_0"
+spegen=44501
+type="min"
+row_num=20
+col_num=5
+
+duo_grid_plot(file_name, spegen, file, type, row_num, col_num)
+```
+
+```{r, looking at the slop}
+
+file = move_together_lit
+title = "test"
+subt = "test"
+x_label ="xx"
+y_label = "yy"
+min_gen = 100
+max_gen = 50000
+
+  ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
+    facet_wrap(~sim)+
+    #geom_line(aes(generation, dif, group=rep, col="dif"))+
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
+    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
+    #geom_hline(yintercept=0, linetype="dashed", color="gray54")+
+    #coord_trans(y="log2")+
+    scale_y_continuous(trans = "log2")+
+    #ylim(-1.,2.5)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Type",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
+labels = c("Snake", "Newt", "Dif"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
+                      strip.background = element_blank(), strip.text.x = element_blank(),
+                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
+                      axis.title.y = element_blank())
+
+```

### 2023-02-07 graphs_newt_snakes/Paper_figs.Rmd
working on making some figures for the paper

---
title: "Paper Figs"
output: html_document
date: '2023-01-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(gridtext)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library(reshape2)
library(ggplot2)
library(ggpubr)
library(stringr)
library(patchwork)
```

```{r, data gathering}
move_together_lit<- read.csv("~/Desktop/move_together/all_lit.txt" , header = TRUE)

move_together_lit$group_rep <- paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd, "_", move_together_lit$rep)

move_together_lit$group <- paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd)

move_together_lit$sim=LETTERS[factor(move_together_lit$group)]
move_together_lit$dif <- move_together_lit$Snake_mean_Pheno-move_together_lit$Newt_mean_Pheno

```

```{r, red in grid files 2}
require(readr)
move_together_grid<- read.csv("~/Desktop/move_together/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
move_together_grid$group_rep <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd, "_", move_together_grid$rep)
move_together_grid$group <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd)
move_together_grid$sim=LETTERS[factor(move_together_grid$group)]
move_together_grid$grid_num = 5

cost_grade_grid<- read.csv("~/Desktop/cost_grade/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
cost_grade_grid$group_rep <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd, "_", cost_grade_grid$rep)
cost_grade_grid$group <- paste0(cost_grade_grid$snake_mu_rate, "_", cost_grade_grid$snake_mu_effect_sd,"_",cost_grade_grid$newt_mu_rate, "_", cost_grade_grid$newt_mu_effect_sd)
cost_grade_grid$sim=LETTERS[factor(cost_grade_grid$group)]
cost_grade_grid$grid_num = 5

```

```{r, finding the slope of coevolution}

newt_first_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$Newt_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$group_rep), FUN=mean), c("group_rep", "N_pheno_start" ))

snake_first_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$Snake_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$group_rep), FUN=mean) , c("group_rep", "S_pheno_start" ))

newt_last_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$Newt_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$group_rep), FUN=mean), c("group_rep", "N_pheno_end" ))

snake_last_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$Snake_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$group_rep), FUN=mean), c("group_rep", "S_pheno_end" ))

mean_phenotype_of_group = cbind(newt_first_mean_pheno, newt_last_mean_pheno[2], snake_first_mean_pheno[2], snake_last_mean_pheno[2])

move_together_lit$N_pheno_start = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"N_pheno_start"]

move_together_lit$S_pheno_start = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"S_pheno_start"]

move_together_lit$N_pheno_end = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"N_pheno_end"]

move_together_lit$S_pheno_end = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"S_pheno_end"]

N_str_gen = setNames(aggregate(move_together_lit[which(move_together_lit$Newt_mean_Pheno<=(move_together_lit$N_pheno_start)) ,]$generation, list(move_together_lit[which(move_together_lit$Newt_mean_Pheno<=(move_together_lit$N_pheno_start)),]$group_rep), FUN=max), c("group_rep", "N_str_gen"))

S_str_gen = setNames(aggregate(move_together_lit[which(move_together_lit$Snake_mean_Pheno<=(move_together_lit$S_pheno_start)) ,]$generation, list(move_together_lit[which(move_together_lit$Snake_mean_Pheno<=(move_together_lit$S_pheno_start)),]$group_rep), FUN=max), c("group_rep", "S_str_gen"))

move_together_lit$N_str_gen <- N_str_gen[match(move_together_lit$group_rep, N_str_gen$group_rep),'N_str_gen']
move_together_lit$S_str_gen <- S_str_gen[match(move_together_lit$group_rep, S_str_gen$group_rep),'S_str_gen']

N_end_gen = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$N_str_gen  & move_together_lit$Newt_mean_Pheno>=(.98*(move_together_lit$N_pheno_end))) ,]$generation, list(move_together_lit[which( move_together_lit$generation>=move_together_lit$N_str_gen  & move_together_lit$Newt_mean_Pheno>=(.98*move_together_lit$N_pheno_end)),]$group_rep), FUN=min)

S_end_gen = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$S_str_gen  & move_together_lit$Snake_mean_Pheno>=(.98*move_together_lit$S_pheno_end)) ,]$generation, list(move_together_lit[which(move_together_lit$generation>=move_together_lit$S_str_gen  & move_together_lit$Snake_mean_Pheno>=(.98*move_together_lit$S_pheno_end)),]$group_rep), FUN=min)

move_together_lit$N_end_gen <- N_end_gen[match(move_together_lit$group_rep, N_end_gen$Group.1),'x']
move_together_lit$S_end_gen <- S_end_gen[match(move_together_lit$group_rep, S_end_gen$Group.1),'x']

# get the difference in generation time and the difference in phenotype

npt<-ggplot(move_together_lit) +
geom_boxplot(aes(sim, N_end_gen), color="darkred")
spt<-ggplot(move_together_lit) +
  geom_boxplot(aes(sim, S_end_gen), color="steelblue")
#  geom_point(aes(group_rep, N_end_gen), color="darkred")+
 # geom_point(aes(group_rep, S_end_gen), color="steelblue")
grid.arrange(npt, spt, ncol=1)

ggplot(move_together_lit) +
  facet_wrap(~sim)+
geom_point(aes(rep, N_end_gen), color="darkred")+
geom_point(aes(rep, S_end_gen), color="steelblue")

npt2<-ggplot(move_together_lit) + # How long did coevolution last?
geom_boxplot(aes(sim, N_end_gen-N_str_gen), color="darkred")
spt2<-ggplot(move_together_lit) +
  geom_boxplot(aes(sim, S_end_gen-S_str_gen), color="steelblue")

grid.arrange(npt2, spt2, ncol=1)

npt3<-ggplot(move_together_lit) + #change in phenotype
geom_boxplot(aes(sim, N_pheno_end-N_pheno_start), color="darkred")
spt3<-ggplot(move_together_lit) +
  geom_boxplot(aes(sim, S_pheno_end-S_pheno_start), color="steelblue")

grid.arrange(npt3, spt3, ncol=1)

ggplot(move_together_lit) +
geom_boxplot(aes(sim, S_end_gen-N_end_gen), color="black")

```

```{r, summary of slopw}

create_parm_file <- function(file, newt_x_line_start, newt_x_line_end, snake_x_line_start, snake_x_line_end, newt_y_line_start, newt_y_line_end, snake_y_line_start, snake_y_line_end){
params <- data_frame()

for(i in 1:length(unique(file$snake_newt_rep))){

  pattern=unique(file$snake_newt_rep)[i]
  sumitup <- file[which(file$snake_newt_rep ==pattern),]

  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           snake_mu_rate=sumitup$snake_mu_rate[1],
                           newt_mu_rate=sumitup$newt_mu_rate[1],
                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
                           rep=sumitup$rep[1],
                           newt_x_line_start=sumitup[[newt_x_line_start]][1], 
                           newt_x_line_end=sumitup[[newt_x_line_end]][1], 
                           snake_x_line_start=sumitup[[snake_x_line_start]][1], 
                           snake_x_line_end=sumitup[[snake_x_line_end]][1], 
                           newt_y_line_start=sumitup[[newt_y_line_start]][1], 
                           newt_y_line_end=sumitup[[newt_y_line_end]][1],
                           snake_y_line_start=sumitup[[snake_y_line_start]][1], 
                           snake_y_line_end=sumitup[[snake_y_line_end]][1])

  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$snake_newt <- paste0(params$snake, "_", params$newt)
return(params)
}

GA_summary_first_species <- function(file, newt_x_line_start, newt_x_line_end, snake_x_line_start, snake_x_line_end, newt_y_line_start, newt_y_line_end, snake_y_line_start, snake_y_line_end, title, subt, y_label, x_label, time){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, newt_x_line_start, newt_x_line_end, snake_x_line_start, snake_x_line_end, newt_y_line_start, newt_y_line_end, snake_y_line_start, snake_y_line_end)

my_plot <- 
  ggplot(params) +

  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab("Newt") + ylab(" ")+
  geom_point(aes(x=(as.numeric((newt_x_line_end)) - as.numeric((newt_x_line_start))), y=(as.numeric((newt_y_line_end)) - as.numeric((newt_y_line_start))), color = factor(newt), shape=factor(snake)),size=3)+

  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(legend.position='none', axis.text.x = element_text( hjust=1, size = 8))

my_plot2 <- 
  ggplot(params) +

  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab("Snake") + ylab(" ")+
  #geom_point(aes(x=(as.numeric(newt_x_line_end) - as.numeric((newt_x_line_start))), y=(as.numeric((newt_y_line_end)) - as.numeric((newt_y_line_start))), color = factor(snake), shape=factor(newt)),size=3)+
geom_point(aes(x=(as.numeric((snake_x_line_end)) - as.numeric((snake_x_line_start))), y=(as.numeric((snake_y_line_end)) - as.numeric((snake_y_line_start))), color = factor(snake), shape=factor(newt)),size=3)+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  labs(color = "GA 1", shape = "GA 2")+
  theme_bw() +  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text( hjust=1, size = 8))

if(time=="ony"){
  my_plot <- my_plot+ylim(0, 50000)
  my_plot2 <-my_plot2+ ylim(0, 50000)
}

if(time=="onx"){
  my_plot <- my_plot+xlim(0, 50000)
  my_plot2 <- my_plot2+xlim(0, 50000)
}

final_plot = grid.arrange(my_plot, my_plot2, ncol=2, widths = c(1,1.2),
                           top = title, left = y_label, bottom = x_label)

return(final_plot)
}

GA_summary_second_species <- function(file, newt_x_line_start, newt_x_line_end, snake_x_line_start, snake_x_line_end, newt_y_line_start, newt_y_line_end, snake_y_line_start, snake_y_line_end, title, subt, y_label, x_label, time){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, newt_x_line_start, newt_x_line_end, snake_x_line_start, snake_x_line_end, newt_y_line_start, newt_y_line_end, snake_y_line_start, snake_y_line_end)

my_plot <- 
  ggplot(params) +

  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab("Newt") + ylab(" ")+
  geom_point(aes(x=(as.numeric((newt_x_line_end)) - as.numeric((newt_x_line_start))), y=(as.numeric((newt_y_line_end)) - as.numeric((newt_y_line_start))), color = factor(snake), shape=factor(newt)),size=3)+

  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(legend.position='none', axis.text.x = element_text( hjust=1, size = 8))

my_plot2 <- 
  ggplot(params) +

  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab("Snake") + ylab(" ")+
  #geom_point(aes(x=(as.numeric(newt_x_line_end) - as.numeric((newt_x_line_start))), y=(as.numeric((newt_y_line_end)) - as.numeric((newt_y_line_start))), color = factor(snake), shape=factor(newt)),size=3)+
geom_point(aes(x=(as.numeric((snake_x_line_end)) - as.numeric((snake_x_line_start))), y=(as.numeric((snake_y_line_end)) - as.numeric((snake_y_line_start))), color = factor(newt), shape=factor(snake)),size=3)+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  labs(color = "GA 2", shape = "GA 1")+
  theme_bw() +  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text( hjust=1, size = 8))

if(time=="ony"){
  my_plot <- my_plot+ylim(0, 50000)
  my_plot2 <-my_plot2+ ylim(0, 50000)
}

if(time=="onx"){
  my_plot <- my_plot+xlim(0, 50000)
  my_plot2 <- my_plot2+xlim(0, 50000)
}

final_plot = grid.arrange(my_plot, my_plot2, ncol=2, widths = c(1,1.2),
                           top = title, left = y_label, bottom = x_label)

return(final_plot)
}

file = move_together_lit
newt_x_line_start = "N_pheno_start"
newt_x_line_end = "N_pheno_end"
newt_y_line_start = "N_str_gen"
newt_y_line_end = "N_end_gen"
snake_x_line_start = "S_pheno_start"
snake_x_line_end = "S_pheno_end"
snake_y_line_start = "S_str_gen"
snake_y_line_end = "S_end_gen"
title = "GA slope summary Focus on GA of Center Species"
subt = "test"
y_label = "# Gen Coevolving"
x_label = "Change in phenotype"
time ="ony"

GA_summary_first_species(file, newt_x_line_start, newt_x_line_end, snake_x_line_start, snake_x_line_end, newt_y_line_start, newt_y_line_end, snake_y_line_start, snake_y_line_end, title, subt, y_label, x_label, time)

title = "GA slope summary Focus on GA of Second Species"
GA_summary_second_species(file, newt_x_line_start, newt_x_line_end, snake_x_line_start, snake_x_line_end, newt_y_line_start, newt_y_line_end, snake_y_line_start, snake_y_line_end, title, subt, y_label, x_label, time)

file = move_together_lit
newt_y_line_start = "N_pheno_start"
newt_y_line_end = "N_pheno_end"
newt_x_line_start = "N_str_gen"
newt_x_line_end = "N_end_gen"
snake_y_line_start = "S_pheno_start"
snake_y_line_end = "S_pheno_end"
snake_x_line_start = "S_str_gen"
snake_x_line_end = "S_end_gen"
title = "GA slope summary Focus on GA of Center Species"
subt = "test"
x_label = "# Gen Coevolving"
y_label = "Change in phenotype"
time ="onx"

GA_summary_second_species(file, newt_x_line_start, newt_x_line_end, snake_x_line_start, snake_x_line_end, newt_y_line_start, newt_y_line_end, snake_y_line_start, snake_y_line_end, title, subt, y_label, x_label, time)

title = "GA slope summary Focus on GA of Second Species"
GA_summary_second_species(file, newt_x_line_start, newt_x_line_end, snake_x_line_start, snake_x_line_end, newt_y_line_start, newt_y_line_end, snake_y_line_start, snake_y_line_end, title, subt, y_label, x_label, time)

```

```{r, making newts and snakes in grid form look nice}

duo_grid_plot<- function(file_name, spegen, file, type, row_num, col_num){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
GA1_type = paste0("generation|", type)

GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
GA1_type <- GA1_type[-1]

data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)

data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)

data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))

main_plot<-ggplot(data_long_type_comp, aes(x = x_loc, y = y_loc))+
  geom_tile(aes(fill = as.numeric(measurement)))+
  facet_wrap(~species)+
  coord_fixed() +
  theme_bw()+
  #margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")+
  theme( legend.justification = "top", 
         plot.margin = margin(t = 0.3,  # Top margin
                             r = 0,  # Right margin
                             b = 0.3,  # Bottom margin
                             l = 0,  # Left margin
                             unit = "cm")  ) # legend.position ="bottom"
#plot.margin = unit(c(1, 1, 3, 1), "cm"),
if(type != "num_ind"){
  main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
                               subtitle = paste0(file_name, ", Generation: ", spegen),
                               fill = "Toxicity/Resistance")+
    scale_fill_viridis_c()
}
if(type == "num_ind"){
  main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
                               subtitle = paste0(file_name, ", Generation: ", spegen),
                               fill = "Newt/Snake PopSize")+
    scale_fill_viridis_c(option = "plasma")
}

snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
newt$snake_value <- snake$measurement
print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))

newt$info <- "middle"

#need to look into, coloring problem
newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"

extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
  theme(text = element_text(size=10),title =element_text(size=8),
        legend.text = element_text(size = 8),
        legend.position ="bottom",
        legend.key.size = unit(0.1, "lines"),
        legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))

bloan <- ggplot() + theme_void()
final_plot <- grid.arrange(main_plot, arrangeGrob(bloan, extra_plot), ncol = 2)

grid.arrange(main_plot, bloan, extra_plot, ncol = 2, 
             layout_matrix=cbind(c(1,1),c(2,3)))

#final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)

return(final_plot)}

file=move_together_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="mean"
row_num=20
col_num=5

duo_grid_plot(file_name, spegen, file, type, row_num, col_num)

file=cost_grade_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="mean"
row_num=20
col_num=5

duo_grid_plot(file_name, spegen, file, type, row_num, col_num)

```

```{r, looking at the slop}

file = move_together_lit
title = "test"
subt = "test"
x_label ="xx"
y_label = "yy"
min_gen = 100
max_gen = 50000

  ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    #coord_trans(y="log2")+
    scale_y_continuous(trans = "log2")+
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

```

```{r, see the correlations}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

GA1_cor<- read.csv("~/Desktop/GA1_tall_redo/all_cor.txt" , header = TRUE)
GA1_cor$group_rep <- paste0(GA1_cor$snake_mu_rate, "_", GA1_cor$snake_mu_effect_sd,"_",GA1_cor$newt_mu_rate, "_", GA1_cor$newt_mu_effect_sd, "_", GA1_cor$rep)
GA1_cor$group <- paste0(GA1_cor$snake_mu_rate, "_", GA1_cor$snake_mu_effect_sd,"_",GA1_cor$newt_mu_rate, "_", GA1_cor$newt_mu_effect_sd)
GA1_cor$sim=LETTERS[factor(GA1_cor$group)]
GA1_cor$exp="Flat Map"

cost_grade_cor<- read.csv("~/Desktop/cost_grade/all_cor.txt" , header = TRUE)
cost_grade_cor$group_rep <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd, "_", cost_grade_cor$rep)
cost_grade_cor$group <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd)
cost_grade_cor$sim=LETTERS[factor(cost_grade_cor$group)]
cost_grade_cor$exp="Cost Gradent Map"

interrate_grade<- read.csv("~/Desktop/interrate_grade/all_cor.txt" , header = TRUE)
interrate_grade$group_rep <- paste0(interrate_grade$snake_mu_rate, "_", interrate_grade$snake_mu_effect_sd,"_",interrate_grade$newt_mu_rate, "_", interrate_grade$newt_mu_effect_sd, "_", interrate_grade$rep)
interrate_grade$group <- paste0(interrate_grade$snake_mu_rate, "_", interrate_grade$snake_mu_effect_sd,"_",interrate_grade$newt_mu_rate, "_", interrate_grade$newt_mu_effect_sd)
interrate_grade$sim=LETTERS[factor(interrate_grade$group)]
interrate_grade$exp="Interaction Gradent Map"

boxplot_cors_by_gen_col_rep <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
file <- rbind(file1, file2, file3)

file$cor_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")

file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map"))

  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c("A","B", "C", "D", "E", "I", "M", "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
    geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
  facet_wrap(~exp, ncol=1)+
  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('No Coevolution', 'Coevolution'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

  return(plot)
}

file1 = GA1_cor
file2 = cost_grade_cor
file3 = interrate_grade
title = "Spatial Phenotype Correlation Across Different Simulation Conditions"
subt = " "
exp_labeles=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map")
x_label = "Simulations"
y_label = "Spatila Correlation"
min_gen = 40000
max_gen = 50000

boxplot_cors_by_gen_col_rep(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen)

```

```{r, slope function}

find_coevo_slope <- function(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent){

  # coevo_begin_start_gen - number of generations to skip as coevo could begin 
newt_first_mean_pheno = setNames(aggregate(file[which(file$generation>=coevo_begin_start_gen & file$generation<=coevo_begin_end_gen),]$Newt_mean_Pheno, list(file[which(file$generation>=coevo_begin_start_gen & file$generation<=coevo_begin_end_gen),]$group_rep), FUN=mean), c("group_rep", "N_pheno_start" ))

snake_first_mean_pheno = setNames(aggregate(file[which(file$generation>=coevo_begin_start_gen & file$generation<=coevo_begin_end_gen),]$Snake_mean_Pheno, list(file[which(file$generation>=coevo_begin_start_gen & file$generation<=coevo_begin_end_gen),]$group_rep), FUN=mean) , c("group_rep", "S_pheno_start" ))

newt_last_mean_pheno = setNames(aggregate(file[which(file$generation>=(max(file$generation)-coevo_endlength_gen) & file$generation<=max(file$generation)),]$Newt_mean_Pheno, list(file[which(file$generation>=(max(file$generation)-coevo_endlength_gen) & file$generation<=max(file$generation)),]$group_rep), FUN=mean), c("group_rep", "N_pheno_end" ))

snake_last_mean_pheno = setNames(aggregate(file[which(file$generation>=(max(file$generation)-coevo_endlength_gen) & file$generation<=max(file$generation)),]$Snake_mean_Pheno, list(file[which(file$generation>=(max(file$generation)-coevo_endlength_gen) & file$generation<=max(file$generation)),]$group_rep), FUN=mean), c("group_rep", "S_pheno_end" ))

mean_phenotype_of_group = cbind(newt_first_mean_pheno, newt_last_mean_pheno[2], snake_first_mean_pheno[2], snake_last_mean_pheno[2])

file$N_pheno_start = mean_phenotype_of_group[match(file$group_rep, mean_phenotype_of_group$group_rep),"N_pheno_start"]

file$S_pheno_start = mean_phenotype_of_group[match(file$group_rep, mean_phenotype_of_group$group_rep),"S_pheno_start"]

file$N_pheno_end = mean_phenotype_of_group[match(file$group_rep, mean_phenotype_of_group$group_rep),"N_pheno_end"]

file$S_pheno_end = mean_phenotype_of_group[match(file$group_rep, mean_phenotype_of_group$group_rep),"S_pheno_end"]

N_str_gen = setNames(aggregate(file[which(file$Newt_mean_Pheno<=(file$N_pheno_start)) ,]$generation, list(file[which(file$Newt_mean_Pheno<=(file$N_pheno_start)),]$group_rep), FUN=max), c("group_rep", "N_str_gen"))

S_str_gen = setNames(aggregate(file[which(file$Snake_mean_Pheno<=(file$S_pheno_start)) ,]$generation, list(file[which(file$Snake_mean_Pheno<=(file$S_pheno_start)),]$group_rep), FUN=max), c("group_rep", "S_str_gen"))

file$N_str_gen <- N_str_gen[match(file$group_rep, N_str_gen$group_rep),'N_str_gen']
file$S_str_gen <- S_str_gen[match(file$group_rep, S_str_gen$group_rep),'S_str_gen']

N_end_gen = aggregate(file[which(file$generation>=file$N_str_gen  & file$Newt_mean_Pheno>=(close_percent*(file$N_pheno_end))) ,]$generation, list(file[which( file$generation>=file$N_str_gen  & file$Newt_mean_Pheno>=(close_percent*file$N_pheno_end)),]$group_rep), FUN=min)

S_end_gen = aggregate(file[which(file$generation>=file$S_str_gen  & file$Snake_mean_Pheno>=(close_percent*file$S_pheno_end)) ,]$generation, list(file[which(file$generation>=file$S_str_gen  & file$Snake_mean_Pheno>=(close_percent*file$S_pheno_end)),]$group_rep), FUN=min)

file$N_end_gen <- N_end_gen[match(file$group_rep, N_end_gen$Group.1),'x']
file$S_end_gen <- S_end_gen[match(file$group_rep, S_end_gen$Group.1),'x']

return(file)

}

boxplot_coevo_slope <- function(file1, file2, file3, title, subt, x_label, y_label){

   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
file <- rbind(file1, file2, file3)
file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)

file$coevo_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")

file$exp = factor(file$exp, levels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))

file_long <- tidyr::pivot_longer(file, c(newt_pheno_change, snake_pheno_change))

  plot <-  ggplot(file_long) +
  ggtitle(title, subtitle = paste0(subt))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c("A","B", "C", "D", "E", "I", "M", "F","G","H","J","K","L","N","O","P")), y=as.numeric(value), fill=factor(name)))+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  facet_wrap(~exp, ncol=1)+
  scale_fill_manual(values =c("darkred", "steelblue"), labels=c('Newt', 'Snake'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

  return(plot)
}

boxplot_coevo_slope_spec_avg <- function(file1, file2, file3, title, subt, x_label, y_label){

   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)

file <- rbind(file1, file2, file3)
file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)

file$coevo_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
file$cor_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
file$exp = factor(file$exp, levels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))

file$newt_snake_pheno_avg= (file$newt_pheno_change+file$snake_pheno_change)/2

  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c("A","B", "C", "D", "E", "I", "M", "F","G","H","J","K","L","N","O","P")), y=as.numeric(newt_snake_pheno_avg), fill=factor(cor_score)))+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  facet_wrap(~exp, ncol=1)+
  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('No Coevolution', 'Coevolution'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

  return(plot)
}

file=move_together_lit
coevo_begin_start_gen=100
coevo_begin_end_gen=1000
coevo_endlength_gen=1000 # this is to take the average of the last ___ of generations
close_percent = .98

move_together_lit = find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)

```

```{r, look at the change in phenotyp}

no_interaction_lit<- read.csv("~/Desktop/no_interaction/all_lit.txt" , header = TRUE)

no_interaction_lit$group_rep <- paste0(no_interaction_lit$snake_mu_rate, "_", no_interaction_lit$snake_mu_effect_sd,"_",no_interaction_lit$newt_mu_rate, "_", no_interaction_lit$newt_mu_effect_sd, "_", no_interaction_lit$rep)

no_interaction_lit$group <- paste0(no_interaction_lit$snake_mu_rate, "_", no_interaction_lit$snake_mu_effect_sd,"_",no_interaction_lit$newt_mu_rate, "_", no_interaction_lit$newt_mu_effect_sd)

no_interaction_lit$sim=LETTERS[factor(no_interaction_lit$group)]
no_interaction_lit$dif <- no_interaction_lit$Snake_mean_Pheno-no_interaction_lit$Newt_mean_Pheno
no_interaction_lit$exp="No Interaction"

no_hair_lit<- read.csv("~/Desktop/no_hair/all_lit.txt" , header = TRUE)

no_hair_lit$group_rep <- paste0(no_hair_lit$snake_mu_rate, "_", no_hair_lit$snake_mu_effect_sd,"_",no_hair_lit$newt_mu_rate, "_", no_hair_lit$newt_mu_effect_sd, "_", no_hair_lit$rep)

no_hair_lit$group <- paste0(no_hair_lit$snake_mu_rate, "_", no_hair_lit$snake_mu_effect_sd,"_",no_hair_lit$newt_mu_rate, "_", no_hair_lit$newt_mu_effect_sd)

no_hair_lit$sim=LETTERS[factor(no_hair_lit$group)]
no_hair_lit$dif <- no_hair_lit$Snake_mean_Pheno-no_hair_lit$Newt_mean_Pheno
no_hair_lit$exp= "No Heritability"

GA1_lit<- read.csv("~/Desktop/GA1_tall_redo/all_lit.txt" , header = TRUE)
GA1_lit$group_rep <- paste0(GA1_lit$snake_mu_rate, "_", GA1_lit$snake_mu_effect_sd,"_",GA1_lit$newt_mu_rate, "_", GA1_lit$newt_mu_effect_sd, "_", GA1_lit$rep)

GA1_lit$group <- paste0(GA1_lit$snake_mu_rate, "_", GA1_lit$snake_mu_effect_sd,"_",GA1_lit$newt_mu_rate, "_", GA1_lit$newt_mu_effect_sd)

GA1_lit$sim=LETTERS[factor(GA1_lit$group)]
GA1_lit$dif <- GA1_lit$Snake_mean_Pheno-GA1_lit$Newt_mean_Pheno
GA1_lit$exp="Coevolution Flat Map"

file=no_interaction_lit
file1=find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
file=no_hair_lit
file2=find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
file=GA1_lit
file3=find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)

title = "test"
subt = "test4"
x_label = "SIM"
y_label = "Change in Phenotype"

boxplot_coevo_slope(file1, file2, file3, title, subt, x_label, y_label)

boxplot_coevo_slope_spec_avg(file1, file2, file3, title, subt, x_label, y_label)
```

```{r, middle four}

# look at coevo slopes for F, G, L, K for same V and high to low V

coevo_begin_start_gen=100
coevo_begin_end_gen=1000
coevo_endlength_gen=1000 # this is to take the average of the last ___ of generations
close_percent = .98

mu_a_lit<- read.csv("~/Desktop/low_to_high_v/mu_a/all_lit.txt" , header = TRUE)

mu_a_lit$group_rep <- paste0(mu_a_lit$snake_mu_rate, "_", mu_a_lit$snake_mu_effect_sd,"_",mu_a_lit$newt_mu_rate, "_", mu_a_lit$newt_mu_effect_sd, "_", mu_a_lit$rep)

mu_a_lit$group <- paste0(mu_a_lit$snake_mu_rate, "_", mu_a_lit$snake_mu_effect_sd,"_",mu_a_lit$newt_mu_rate, "_", mu_a_lit$newt_mu_effect_sd)

mu_a_lit$sim=LETTERS[factor(mu_a_lit$group)]
mu_a_lit$dif <- mu_a_lit$Snake_mean_Pheno-mu_a_lit$Newt_mean_Pheno
mu_a_lit$exp = "Low to High MuV (2.5e-12 to 2.5e-11) Mu=1e-8"
mu_a_lit$change = "yes"
file=mu_a_lit
mu_a_lit = find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
sub_mu_a_lit = subset(mu_a_lit, mu_a_lit$sim == c("F", "G", "J", "K") )

# Mu B
mu_b_lit<- read.csv("~/Desktop/low_to_high_v/mu_b/all_lit.txt" , header = TRUE)

mu_b_lit$group_rep <- paste0(mu_b_lit$snake_mu_rate, "_", mu_b_lit$snake_mu_effect_sd,"_",mu_b_lit$newt_mu_rate, "_", mu_b_lit$newt_mu_effect_sd, "_", mu_b_lit$rep)

mu_b_lit$group <- paste0(mu_b_lit$snake_mu_rate, "_", mu_b_lit$snake_mu_effect_sd,"_",mu_b_lit$newt_mu_rate, "_", mu_b_lit$newt_mu_effect_sd)

mu_b_lit$sim=LETTERS[factor(mu_b_lit$group)]
mu_b_lit$dif <- mu_b_lit$Snake_mean_Pheno-mu_b_lit$Newt_mean_Pheno
mu_b_lit$exp = "Low to High MuV (2.5e-12 to 2.5e-11) Mu=1e-9"
mu_b_lit$change = "yes"
file=mu_b_lit
mu_b_lit = find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
sub_mu_b_lit = subset(mu_b_lit, mu_b_lit$sim == c("F", "G", "J", "K") )

# mu c

mu_c_lit<- read.csv("~/Desktop/low_to_high_v/mu_c/all_lit.txt" , header = TRUE)

mu_c_lit$group_rep <- paste0(mu_c_lit$snake_mu_rate, "_", mu_c_lit$snake_mu_effect_sd,"_",mu_c_lit$newt_mu_rate, "_", mu_c_lit$newt_mu_effect_sd, "_", mu_c_lit$rep)

mu_c_lit$group <- paste0(mu_c_lit$snake_mu_rate, "_", mu_c_lit$snake_mu_effect_sd,"_",mu_c_lit$newt_mu_rate, "_", mu_c_lit$newt_mu_effect_sd)

mu_c_lit$sim=LETTERS[factor(mu_c_lit$group)]
mu_c_lit$dif <- mu_c_lit$Snake_mean_Pheno-mu_c_lit$Newt_mean_Pheno
mu_c_lit$exp = "Low to High MuV (2.5e-12 to 2.5e-11) Mu=1e-10"
mu_c_lit$change = "yes"
file=mu_c_lit
mu_c_lit = find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
sub_mu_c_lit = subset(mu_c_lit, mu_c_lit$sim == c("F", "G", "J", "K") )

# mu d

mu_d_lit<- read.csv("~/Desktop/low_to_high_v/mu_d/all_lit.txt" , header = TRUE)

mu_d_lit$group_rep <- paste0(mu_d_lit$snake_mu_rate, "_", mu_d_lit$snake_mu_effect_sd,"_",mu_d_lit$newt_mu_rate, "_", mu_d_lit$newt_mu_effect_sd, "_", mu_d_lit$rep)

mu_d_lit$group <- paste0(mu_d_lit$snake_mu_rate, "_", mu_d_lit$snake_mu_effect_sd,"_",mu_d_lit$newt_mu_rate, "_", mu_d_lit$newt_mu_effect_sd)

mu_d_lit$sim=LETTERS[factor(mu_d_lit$group)]
mu_d_lit$dif <- mu_d_lit$Snake_mean_Pheno-mu_d_lit$Newt_mean_Pheno
mu_d_lit$exp = "Low to High MuV (2.5e-12 to 2.5e-11) Mu=1e-11"
mu_d_lit$change = "yes"
file=mu_d_lit
mu_d_lit = find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
sub_mu_d_lit = subset(mu_d_lit, mu_d_lit$sim == c("F", "G", "J", "K") )

v_a_lit<- read.csv("~/Desktop/same_v/v_a/all_lit.txt" , header = TRUE)

v_a_lit$group_rep <- paste0(v_a_lit$snake_mu_rate, "_", v_a_lit$snake_mu_effect_sd,"_",v_a_lit$newt_mu_rate, "_", v_a_lit$newt_mu_effect_sd, "_", v_a_lit$rep)

v_a_lit$group <- paste0(v_a_lit$snake_mu_rate, "_", v_a_lit$snake_mu_effect_sd,"_",v_a_lit$newt_mu_rate, "_", v_a_lit$newt_mu_effect_sd)

v_a_lit$sim=LETTERS[factor(v_a_lit$group)]
v_a_lit$dif <- v_a_lit$Snake_mean_Pheno-v_a_lit$Newt_mean_Pheno
v_a_lit$exp = "MuV = 2.5e-13 (low to high sigma: high to low mu)"
v_a_lit$change = "no"
file=v_a_lit
v_a_lit = find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
sub_v_a_lit = subset(v_a_lit, v_a_lit$sim == c("F", "G", "J", "K") )

# Mu B
v_b_lit<- read.csv("~/Desktop/same_v/v_b/all_lit.txt" , header = TRUE)

v_b_lit$group_rep <- paste0(v_b_lit$snake_mu_rate, "_", v_b_lit$snake_mu_effect_sd,"_",v_b_lit$newt_mu_rate, "_", v_b_lit$newt_mu_effect_sd, "_", v_b_lit$rep)

v_b_lit$group <- paste0(v_b_lit$snake_mu_rate, "_", v_b_lit$snake_mu_effect_sd,"_",v_b_lit$newt_mu_rate, "_", v_b_lit$newt_mu_effect_sd)

v_b_lit$sim=LETTERS[factor(v_b_lit$group)]
v_b_lit$dif <- v_b_lit$Snake_mean_Pheno-v_b_lit$Newt_mean_Pheno
v_b_lit$exp = "MuV = 2.5e-12 (low to high sigma: high to low mu)"
v_b_lit$change = "no"
file=v_b_lit
v_b_lit = find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
sub_v_b_lit = subset(v_b_lit, v_b_lit$sim == c("F", "G", "J", "K") )

# Mu C

v_c_lit<- read.csv("~/Desktop/same_v/v_c/all_lit.txt" , header = TRUE)

v_c_lit$group_rep <- paste0(v_c_lit$snake_mu_rate, "_", v_c_lit$snake_mu_effect_sd,"_",v_c_lit$newt_mu_rate, "_", v_c_lit$newt_mu_effect_sd, "_", v_c_lit$rep)

v_c_lit$group <- paste0(v_c_lit$snake_mu_rate, "_", v_c_lit$snake_mu_effect_sd,"_",v_c_lit$newt_mu_rate, "_", v_c_lit$newt_mu_effect_sd)

v_c_lit$sim=LETTERS[factor(v_c_lit$group)]
v_c_lit$dif <- v_c_lit$Snake_mean_Pheno-v_c_lit$Newt_mean_Pheno

v_c_lit$exp = "MuV = 2.5e-11 (low to high sigma: high to low mu)"
v_c_lit$change = "no"
file=v_c_lit
v_c_lit = find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
sub_v_c_lit = subset(v_c_lit, v_c_lit$sim == c("F", "G", "J", "K") )

# mu d

v_d_lit<- read.csv("~/Desktop/same_v/v_d/all_lit.txt" , header = TRUE)

v_d_lit$group_rep <- paste0(v_d_lit$snake_mu_rate, "_", v_d_lit$snake_mu_effect_sd,"_",v_d_lit$newt_mu_rate, "_", v_d_lit$newt_mu_effect_sd, "_", v_d_lit$rep)

v_d_lit$group <- paste0(v_d_lit$snake_mu_rate, "_", v_d_lit$snake_mu_effect_sd,"_",v_d_lit$newt_mu_rate, "_", v_d_lit$newt_mu_effect_sd)

v_d_lit$sim=LETTERS[factor(v_d_lit$group)]
v_d_lit$dif <- v_d_lit$Snake_mean_Pheno-v_d_lit$Newt_mean_Pheno

v_d_lit$exp = "MuV = 2.5e-10 (low to high sigma: high to low mu)"
v_d_lit$change = "no"
file=v_d_lit
v_d_lit = find_coevo_slope(file, coevo_begin_start_gen, coevo_begin_end_gen, coevo_endlength_gen, close_percent)
sub_v_d_lit = subset(v_d_lit, v_d_lit$sim == c("F", "G", "J", "K") )

GA_stage = rbind(sub_mu_b_lit, sub_mu_c_lit, sub_v_b_lit, sub_v_c_lit)

#rbind(sub_mu_a_lit, sub_mu_b_lit, sub_mu_c_lit, sub_mu_d_lit, sub_v_a_lit, sub_v_b_lit, sub_v_c_lit, sub_v_d_lit)

GA_stage$snake_newt <- paste0(GA_stage$snake_mu_rate, "_", GA_stage$snake_mu_effect_sd, "_", GA_stage$newt_mu_rate, "_", GA_stage$newt_mu_effect_sd)

GA_stage$newt_coevo_slope = (GA_stage$N_pheno_end - GA_stage$N_pheno_start)/ (GA_stage$N_end_gen - GA_stage$N_str_gen)
GA_stage$snake_coevo_slope = (GA_stage$S_pheno_end - GA_stage$S_pheno_start)/ (GA_stage$S_end_gen - GA_stage$S_str_gen)

GA_stage$newt_pheno_change = (GA_stage$N_pheno_end - GA_stage$N_pheno_start)
GA_stage$snake_pheno_change = (GA_stage$S_pheno_end - GA_stage$S_pheno_start)

GA_stage$newt_gen_change = (GA_stage$N_end_gen - GA_stage$N_str_gen)
GA_stage$snake_gen_change = (GA_stage$S_end_gen - GA_stage$S_str_gen)
```

```{r, plotting all of the changes}
title = "Coevolution Slope (Phenotype Change/ Time)"
subt = "Simulation F, G, F, H"
GA_stage_long <- tidyr::pivot_longer(GA_stage, c(newt_coevo_slope, snake_coevo_slope))
y_label="change in phenotype/change in generations"
x_label="Genetic Architectures (red=newt, blue=snake)"
ggplot(GA_stage_long) +
  ggtitle(title, subtitle = paste0(subt))+
  coord_trans(y = "log10")+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c("F","J","G","K")), y=(as.numeric(value)), fill=factor(name)), show.legend = FALSE)+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  facet_wrap(~exp, ncol=2, dir="v")+
  scale_fill_manual(values =c("darkred", "steelblue"), labels=c('Newt', 'Snake'))+ #
  #  labs(fill = " ")
  scale_x_discrete(labels=c('A/A', 'A/B', 'B/A','B/B'))+
  theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                 #     title =element_text(size=8, face='bold'))+
    theme(legend.position = "none")

title = "Coevolution Phenotype Change"
subt = "Simulation F, G, F, H"
GA_stage_long <- tidyr::pivot_longer(GA_stage, c(newt_pheno_change, snake_pheno_change))
y_label="change in phenotype"
x_label="Genetic Architectures (red=newt, blue=snake)"
ggplot(GA_stage_long) +
  ggtitle(title, subtitle = paste0(subt))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c("F","J","G","K")), y=(as.numeric(value)), fill=factor(name)), show.legend = FALSE)+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  facet_wrap(~exp, ncol=2, dir="v")+
  scale_fill_manual(values =c("darkred", "steelblue"), labels=c('Newt', 'Snake'))+ #
  #  labs(fill = " ")
  scale_x_discrete(labels=c('A/A', 'A/B', 'B/A','B/B'))+
  theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                 #     title =element_text(size=8, face='bold'))+
    theme(legend.position = "none")

title = "Coevolution Change in Time"
subt = "Simulation F, G, F, H"
GA_stage_long <- tidyr::pivot_longer(GA_stage, c(newt_gen_change, snake_gen_change))
y_label="change in geneerations"
x_label="Genetic Architectures (red=newt, blue=snake)"
ggplot(GA_stage_long) +
  ggtitle(title, subtitle = paste0(subt))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c("F","J","G","K")), y=(as.numeric(value)), fill=factor(name)), show.legend = FALSE)+ #
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  facet_wrap(~exp, ncol=2, dir="v")+
  scale_fill_manual(values =c("darkred", "steelblue"), labels=c('Newt', 'Snake'))+ #
  #  labs(fill = " ")
  scale_x_discrete(labels=c('A/A', 'A/B', 'B/A','B/B'))+
  theme_bw() #+  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                 #     title =element_text(size=8, face='bold'))+
    #theme(legend.position = "none")

```

### 2023-02-14 graphs_newt_snakes/Paper_figs.Rmd
I am working out some of the figurse that should be on the paper

@@
 
-file$coevo_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
 file$cor_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
@@
   scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('No Coevolution', 'Coevolution'))+
+    labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+
+  return(plot)
+}
+
+boxplot_coevo_slope_spec_avg_advantage <- function(file1, file2, file3, title, subt, x_label, y_label){
+
+   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
+   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
+   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
+
+file <- rbind(file1, file2, file3)
+file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
+file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
+#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
+#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)
+
+file$exp = factor(file$exp, levels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))
+
+newt_adv= c("D", "C", "B", "H", "G", "L")
+mid= c("A", "F", "K", "P")
+snake_adv = c("E", "I", "J", "M", "N", "O")
+
+file$coevo_score = 0
+
+file$coevo_score[file$sim %in% newt_adv] = "Newt Advantage"
+file$coevo_score[file$sim %in% mid] = "No Advantage"
+file$coevo_score[file$sim %in% snake_adv] = "Snake Advantage"
+file$newt_snake_pheno_avg= (file$newt_pheno_change+file$snake_pheno_change)/2
+
+  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "I", "J", "M", "N", "O")), y=as.numeric(newt_snake_pheno_avg), fill=factor(coevo_score)))+
+
+  theme(plot.title = element_text(size=5)) +
+  #xlim(-1.1, 1.1)+
+  facet_wrap(~exp, ncol=1)+
+  scale_fill_manual(values =c("red", "purple", "blue"), labels=c('Newt Advantage', 'No Advantage', 'Snake Advantage'))+
     labs(fill = " ")+
@@
 boxplot_coevo_slope_spec_avg(file1, file2, file3, title, subt, x_label, y_label)
+
+boxplot_coevo_slope_spec_avg_advantage(file1, file2, file3, title, subt, x_label, y_label)
 ```

### 2023-02-22 graphs_newt_snakes/Paper_figs.Rmd
making fig improvements

@@
 
-file$cor_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
+file$sim <- str_replace_all(file$sim, "[ABCDEIM]", 'Sims')
+#c("A"='Low Mu Var', "B"='Low Mu Var', "C"='Low Mu Var', "D"='Low Mu Var', "E"='Low Mu Var', "I"='Low Mu Var', "M"='Low Mu Var'))
+
+file$cor_score <- ifelse(file$sim == "Sims", "False","True")
+
+#file$cor_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
 
@@
   xlab(x_label) + ylab(y_label)+
-  geom_boxplot(aes(x=factor(sim, level=c("A","B", "C", "D", "E", "I", "M", "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
+  geom_boxplot(aes(x=factor(sim, level=c('Sims', "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
   theme(plot.title = element_text(size=5)) +
@@
   facet_wrap(~exp, ncol=1)+
-  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('No Coevolution', 'Coevolution'))+
+  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutatinal Variance', 'Coevolution'))+
     labs(fill = " ")+
@@
 
-file1 = GA1_cor
+file1 = GA1_cor[which(1:nrow(GA1_cor) %% 2 != 0) , ]
 file2 = cost_grade_cor
@@
 
-  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  plot <-  ggplot(file) +
+  ggtitle(title, subtitle = subt)+
   xlab(x_label) + ylab(y_label)+
@@
   facet_wrap(~exp, ncol=1)+
-  scale_fill_manual(values =c("red", "purple", "blue"), labels=c('Newt Advantage', 'No Advantage', 'Snake Advantage'))+
+  scale_fill_manual(values =c("darkred", "purple", "steelblue"), labels=c('Newt Advantage', 'No Advantage', 'Snake Advantage'))+
+    labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+
+  return(plot)
+}
+
+boxplot_coevo_slope_flat_map <- function(file, title, subt, x_label, y_label){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
+file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
+#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
+#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)
+
+newt_adv= c("D", "C", "B", "H", "G", "L")
+mid= c("A", "F", "K", "P")
+snake_adv = c("E", "I", "J", "M", "N", "O")
+
+file$coevo_score = 0
+
+file$coevo_score[file$sim %in% newt_adv] = "Newt Advantage"
+file$coevo_score[file$sim %in% mid] = "No Advantage"
+file$coevo_score[file$sim %in% snake_adv] = "Snake Advantage"
+file$newt_snake_pheno_avg= (file$newt_pheno_change+file$snake_pheno_change)/2
+
+file_long <- tidyr::pivot_longer(file, c(newt_pheno_change, snake_pheno_change))
+
+  plot <-  ggplot(file_long) +
+  ggtitle(title, subtitle = subt)+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)))+
+  theme(plot.title = element_text(size=5)) +
+  #xlim(-1.1, 1.1)+
+  scale_fill_manual(values =c("darkred", "steelblue"), labels=c('Newt', 'Snake'))+
+    labs(fill = " ")+
+    #scale_fill_manual(values =c("darkred", "purple", "steelblue"), labels=c('Newt Advantage', 'No Advantage', 'Snake Advantage'))+
+    labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+
+  return(plot)
+}
+
+boxplot_coevo_slope_small <- function(file1, file2, file3, title, subt, x_label, y_label){
+
+   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
+   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
+   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
+
+file <- rbind(file1, file2, file3)
+file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
+file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
+#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
+#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)
+
+file$exp = factor(file$exp, levels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))
+
+newt_adv= c("D", "C", "B", "H", "G", "L")
+mid= c("A", "F", "K", "P")
+snake_adv = c("E", "I", "J", "M", "N", "O")
+
+file$coevo_score = 0
+
+file$coevo_score[file$sim %in% newt_adv] = "Newt Advantage"
+file$coevo_score[file$sim %in% mid] = "No Advantage"
+file$coevo_score[file$sim %in% snake_adv] = "Snake Advantage"
+
+file<- subset(file, !sim %in% c("A", "B", "C", "D", "E", "I", "M"))
+
+file$newt_snake_pheno_avg= (file$newt_pheno_change+file$snake_pheno_change)/2
+
+  plot <-  ggplot(file) +
+  ggtitle(title, subtitle = subt)+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(newt_snake_pheno_avg), fill=factor(coevo_score)))+
+  theme(plot.title = element_text(size=5)) +
+  #xlim(-1.1, 1.1)+
+  facet_wrap(~exp, ncol=1)+
+  scale_fill_manual(values =c("darkred", "purple", "steelblue"), labels=c('Newt Advantage', 'No Advantage', 'Snake Advantage'))+
     labs(fill = " ")+
@@
 
-title = "test"
-subt = "test4"
+title = "Whole Simulation Phenotype Change"
+subt = "Three Experiments"
 x_label = "SIM"
@@
 boxplot_coevo_slope_spec_avg_advantage(file1, file2, file3, title, subt, x_label, y_label)
+
+boxplot_coevo_slope_small(file1, file2, file3, title, subt, x_label, y_label)
+
+title = "Phenotype Change Coevolution FLat Map"
+boxplot_coevo_slope_flat_map(file3, title, subt, x_label, y_label)
 ```
@@
 title = "Coevolution Slope (Phenotype Change/ Time)"
-subt = "Simulation F, G, F, H"
+subt = "Simulation F, J, G, K"
 GA_stage_long <- tidyr::pivot_longer(GA_stage, c(newt_coevo_slope, snake_coevo_slope))
-y_label="change in phenotype/change in generations"
+y_label="Coevolution Speed"
 x_label="Genetic Architectures (red=newt, blue=snake)"
@@
   #  labs(fill = " ")
-  scale_x_discrete(labels=c('A/A', 'A/B', 'B/A','B/B'))+
+  scale_x_discrete(labels=c('low/low', 'low/high', 'low/high','high/high'))+
   theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
@@
 title = "Coevolution Phenotype Change"
-subt = "Simulation F, G, F, H"
+subt = "Simulation F, J, G, K"
 GA_stage_long <- tidyr::pivot_longer(GA_stage, c(newt_pheno_change, snake_pheno_change))
@@
 title = "Coevolution Change in Time"
-subt = "Simulation F, G, F, H"
+subt = "Simulation F, J, G, K"
 GA_stage_long <- tidyr::pivot_longer(GA_stage, c(newt_gen_change, snake_gen_change))
@@
   #  labs(fill = " ")
-  scale_x_discrete(labels=c('A/A', 'A/B', 'B/A','B/B'))+
+  scale_x_discrete(labels=c('low/low', 'low/high', 'low/high','high/high'))+
   theme_bw() #+  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 

### 2023-02-24 graphs_newt_snakes/Paper_figs.Rmd
I made some minor legend edit

@@
   #  labs(fill = " ")
-  scale_x_discrete(labels=c('low/low', 'low/high', 'low/high','high/high'))+
+  scale_x_discrete(labels=c('low/low', 'low/high', 'high/low','high/high'))+
   theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
@@
   #  labs(fill = " ")
-  scale_x_discrete(labels=c('low/low', 'low/high', 'low/high','high/high'))+
+  scale_x_discrete(labels=c('low/low', 'low/high', 'high/low','high/high'))+
   theme_bw() #+  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 

### 2023-03-09 graphs_newt_snakes/Paper_figs.Rmd
I have been filling out my thoughts about these experiments. They are truly some cool results

@@
 move_together_grid$grid_num = 5
+
+GA1_final_csv<- read.csv("~/Desktop/GA1_final_csv/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
+GA1_final_csv$group_rep <- paste0(GA1_final_csv$snake_mu_rate, "_", GA1_final_csv$snake_mu_effect_sd,"_",GA1_final_csv$newt_mu_rate, "_", GA1_final_csv$newt_mu_effect_sd, "_", GA1_final_csv$rep)
+GA1_final_csv$group <- paste0(GA1_final_csv$snake_mu_rate, "_", GA1_final_csv$snake_mu_effect_sd,"_",GA1_final_csv$newt_mu_rate, "_", GA1_final_csv$newt_mu_effect_sd)
+GA1_final_csv$sim=LETTERS[factor(GA1_final_csv$group)]
+GA1_final_csv$grid_num = 5
 
@@
 
+file=GA1_final_csv
+file_name="1e-11_5_1e-10_0.5_0"
+spegen=44501
+type="mean"
+row_num=20
+col_num=5
+
+duo_grid_plot(file_name, spegen, file, type, row_num, col_num)
+
 file=cost_grade_grid
@@
 
-GA1_cor<- read.csv("~/Desktop/GA1_tall_redo/all_cor.txt" , header = TRUE)
+GA1_cor<- read.csv("~/Desktop/GA1_final_csv/all_cor.txt" , header = TRUE)
 GA1_cor$group_rep <- paste0(GA1_cor$snake_mu_rate, "_", GA1_cor$snake_mu_effect_sd,"_",GA1_cor$newt_mu_rate, "_", GA1_cor$newt_mu_effect_sd, "_", GA1_cor$rep)
@@
 
-GA1_lit<- read.csv("~/Desktop/GA1_tall_redo/all_lit.txt" , header = TRUE)
+GA1_lit<- read.csv("~/Desktop/GA1_final_csv/all_lit.txt" , header = TRUE)
 GA1_lit$group_rep <- paste0(GA1_lit$snake_mu_rate, "_", GA1_lit$snake_mu_effect_sd,"_",GA1_lit$newt_mu_rate, "_", GA1_lit$newt_mu_effect_sd, "_", GA1_lit$rep)

### 2023-03-09 graphs_newt_snakes/dif_cost_grade.Rmd
I have been filling out my thoughts about these experiments. They are truly some cool results

@@
 
+The goal of this experiment was to create a gradient picture and to assign different cost values to areas of the map
+
 ### Questions:
 
-What does it mean to be correlated?
+What does it mean to be correlated? How might an uneven environment (its easier to have a higher phenotype in some area of the map) impact co-evolution?
 
 ## Background
+
+Previously I have been looking at how newts and snakes can co-evolve under different genetic architectures (mutation rate and mutation effect size), and have found that while the mean phenotype increases there is no spatial phenotype correlation.
+This has puzzled me, how can there be a constant increase in phenotype but no spatial phenotype correlation?
+I think that there might be other factors that lead to spatial phenotype correlation.
 
@@
 
-Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.
-
-### The data
+Each GA combination and trial has its own msprime simulation.
+
+I created a gradient map where at the top there is a higher fitness cost for having a large phenotype (set to 50) and at the bottom there is a lower cost for having a higher phenotype (set to 250).
+Both newts and snakes are effected by this gradient.
+
+![Gradient Map](/Users/victoria/Desktop/Coevo/newt_snake/data/gradent.png)
 
@@
 
+In this first section I look at the entire populations mean phenotype for both snakes (blue) and newts (red).
+The difference between mean snake and mean newt phenotype is shown on the black line.
+For each GA combination there are 4 sets of lines (red, blue, black).
+Each line is a different trial with the same simulation parameters.
+I also present the average difference (of the trials) between snake and newt phenotype in the table of average differences.
+
 ### Phenotype differences 
@@
 
+These results look very similar to the results seen in my other simulations where there is no gradient map.
+The mean phenotypes of newts and snakes go up, until they reach an equilibrium.
+Here the aver values are higher than what I have seen before.
+
 ## Connection between higher phenotype and population{.tabset}
+
+Here I plot the interaction between newt/snake phenotype and population size.
+Typically, when a species had a higher phenotype they also had a larger population size.
+This relation between phenotype and population size had specific outcomes that depended on the GA of newts and snakes.
+
+The first figure compares the population size of newts and snakes to the difference between mean snake and mean newt phenotype for a time slice (5,000-10,000 generations).
+Color in this plot is the difference between snake and newt phenotype, with blue indicating snakes have a larger phenotype and red indicating newts have a larger phenotype.
+Cream color points indicate that the two phenotypes are nearly the same.
+The second figure present the histograms of the difference between snake and newt population size (green) and phenotype (purple) for a time slice (5,000-10,000 generations).
 
@@
 
-whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
+These results are similar to what I have seen before.
+There might be an increase in the differences between snake and newt phenotype, but the overall message higher phenotype = more individuals in unchanged.
+GA3 seems to create the larger difference in mean newt/snake phenotype.
+
 ## Correlation
 
-### cor
+The next section I am examining the spatial correlation between newt and snake phenotypes and I predicted that there would be a positive correlation between the phenotypes.
+I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
+The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
+
 ```{r, combo myplots}
@@
 
+In my previous results (no gradient map) I saw no positive spatial phenotype correlation between snakes and newts.
+Here, with a cost gradient map I see that there are quite a few simulations where newt and snake local mean phenotypes are correlated when compared across space.
+
 ## Correlation Histograms{.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
 
@@
 
+Spatial phenotype correlation increases for most of the simulation as I move through the time slices.
+Once a simulation reach a high spatial phenotype correlation, it did not go back down.
+The simulations where non surpassed the empirical newt and snake spatial phenotype correlation all contained a genetic architecture that had a small mutational varance.
+
 ## Correlation across time {.tabset}
+
+Next, I examine three randomly chosen plots.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
 
@@
 
+Most of these plots show that as time increases both the mean newt & snake phenotype as well as the   spatial phenotype correlation (pink line) increase (very few show no change).
+Spatial phenotype correlation increases the most when the newt and snake mean phenotypes are increasing the most.
+Some of these plots are very interesting to see.
+
 ## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+Then each msprime simulation is put into slim and data is generated.
+Plots show newt by snake population size, with the point color representing the difference between mean snake and newt phenotype (red=newts have a higher phenotype and blue=snakes have a higher phenotype).
+The other plots show histograms of difference between snakes and newts phenotype and population size (purple and green).
 
@@
 
+The results looked similar to results that I have seen in other experiments.
+In the beginning of the simulation both newt and snake population grows.
+The difference in phenotype quickly becomes polarized.
+The population size reaches a steady point and then newts and snakes co-evolve.
+In the middle part of my simulation, the difference between newt and snakes mean phenotype solidifies.
+Often, the difference in mean phenotype decreases (where compared to the beginning of the simulation).
+When the GA has a high mutation rate and low mutation effect size (GA 1), the difference in mean phenotype grows.
+This leads to the species with GA 1 losing the co-evolutionary arms race.
+More frequent smaller steps does not help a species win in an arms race (might also be due to lower mutational variance).
+The histograms reflect what is seen in the scatter plots.
+
 ## Summary {.tabset}
+
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
 
@@
 
+Firstly, these plots are very similar to the plots seen without a gradient map and have the same results.
+There are clusters of points that create lines of shapes and lines of colors.
+The best GA for newts and snakes was 1e-09_0.05 (can be seen as green near the top of all the lines of shapes and triangles near the bottom right look at all the lines of color).
+It is interesting to see how these points spread apart, but remain similar between trials.
+When putting these figures together it seems like the population size of snakes is lower when the newt phenotype is larger than the snake phenotype.
+
 ## Heatmap {.tabset}
+
+In the heatmap plots each GA combination and trails is presented by combining newt GA in the x-axis to snake GA and trial number in the y-axis.
+The result is the color in that section.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+I look at 3 time slices for both types of heatmaps.
 
@@
 ## {-}
+
+Heatmap results are very similar to the no cost gradient maps.
+They star off sort of neutral, but each trial of the GA combination creates very similar patterns.
+Which shows that under certain GA either newts or snakes have an co-evolutionary advantage (1e-9(0.05)^2 = 2.5e-12 or 1e-10(0.5)^2 = 2.5e-11).
+The cost gradient results look more dramatic than the results with out the map.
 
@@
 
+This section goes over the results from the local measurements (grid calculations).
+I divided my map up into smaller area (grids) and calculated mean phenotype, max phenotype, min phenotype, and population size.
+In each of these plots newts are represented by circles and snakes are represented by squares.
+Parameter values increase from a dark color to a lighter color (green-blue themed for phenotype, orange-pinked themed for population size) There is also a subplot that plots each parameter (mean, max, …) of newt by snake colored by map location (red=corner, green=edge, blue=middle).
+I look at the one simulation at one time in the begging and end.
+
 ## Early Simulation Correlation {.tabset}
@@
 ## {-}
+
+Newt and snake phenotypes are positively spatially correlated. Newt and snake population sizes are negativly correlated (look at the mini plots and not the values)

### 2023-03-09 graphs_newt_snakes/interrate_grade.Rmd
I have been filling out my thoughts about these experiments. They are truly some cool results

@@
 
+The goal of this experiment was to create a gradient picture and to assign different interaction values to areas of the map
+
 ### Questions:
@@
 ## Background
+
+Previously I have been looking at how newts and snakes can co-evolve under different genetic architectures (mutation rate and mutation effect size), and have found that while the mean phenotype increases there is no spatial phenotype correlation.
+After adding a cost gradient map and seeing high phenotype spatial correlations I wondered if there were other things that could vary and still create spatial phenotype correlation.
 
@@
 
-Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.
-
-### The data
+Each GA combination and trial has its own msprime simulation.
+I created a gradient map where at the top there is a lower rate of newt and snake interaction (0.01) and at the bottom there is a higher rate of newt/snake interaction (0.1 so high that there might be local species extinction).
+My simulation typically use 0.05 as an interaction rate (interaction rate was explores in the interaction rate simulations)
 
@@
 
+These results follow a similar pattern to what I have seen in other simulations.
+Both newt and snake mean phenotype go up, but they go up slowly and reach a low equilibrium.
+The traits do not seem exaggerated, but they do not head towards zero.
+In simulations with a low mutational variance GA one of the species mean phenotype flat line.
+I wonder if the results would change if the interaction rate was different.
+
 ## Connection between higher phenotype and population{.tabset}
+
+Here I plot the interaction between newt/snake phenotype and population size.
+Typically, when a species had a higher phenotype they also had a larger population size.
+This relation between phenotype and population size had specific outcomes that depended on the GA of newts and snakes.
+
+The first figure compares the population size of newts and snakes to the difference between mean snake and mean newt phenotype for a time slice (5,000-10,000 generations).
+Color in this plot is the difference between snake and newt phenotype, with blue indicating snakes have a larger phenotype and red indicating newts have a larger phenotype.
+Cream color points indicate that the two phenotypes are nearly the same.
+The second figure present the histograms of the difference between snake and newt population size (green) and phenotype (purple) for a time slice (5,000-10,000 generations).
 
@@
 
-whale_gen(interrate_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(interrate_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
+The overall meaning of these plots suggest that a higher phenotype leads to more individuals.
+The dot smear is longer than what I have seen in my other simulations.
+I wonder if the varying the interaction rate leads to more stocatic values.
+
 ## Correlation
 
-### cor
+The next section I am examining the spatial correlation between newt and snake phenotypes and I predicted that there would be a positive correlation between the phenotypes.
+I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
+The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
+
 ```{r, combo myplots}
@@
 
+The spatial phenotype correlations of this simulation set are positive (when excluding low mutational variance GA sims).
+Many of the spatial phenotype correlation values are near the real newt/snake phenotype correlation.
+
 ## Correlation Histograms{.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
 
@@
 
+These plots reveal that the spatial phenotype correlation between snakes and newts increase with time and end up being close to the empirical newt snake spatial phenotype correlation.
+These correlation values are higher than when there is no gradient map, but lower then the cost gradient map.
+There is no spatial phenotype correlation when the GA has low mutational variance.
+
 ## Correlation across time {.tabset}
+
+Next, I examine three randomly chosen plots.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
 
@@
 
+Most of these plots show that as time increases both the mean newt & snake phenotype (read and blue lines) as well as the spatial phenotype correlation (pink line) increase (very few show no change).
+Spatial phenotype correlation increases the gradually as the newt and snake mean phenotypes gradually increases.
+There is a lot of variation of the spatial phenotype correlation between different time points (every 20 generations) (it seems to go up and down quiet a bit).
+
 ## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+his next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+Then each msprime simulation is put into slim and data is generated.
+Plots show newt by snake population size, with the point color representing the difference between mean snake and newt phenotype (red=newts have a higher phenotype and blue=snakes have a higher phenotype).
+The other plots show histograms of difference between snakes and newts phenotype and population size (purple and green).
 
@@
 
+In the beginning of the simulation both newt and snake population grows.
+The difference in phenotype quickly becomes polarized.
+The population size reaches a steady point as the newts and snakes co-evolve.
+In this experiment set the point clusters are more elongated, which suggests that the newt and snake population size flucates more than what I have seen in my other experiments.
+When the GA has a high mutation rate and low mutation effect size (GA 1), the difference in mean phenotype grows.
+This leads to the species with GA 1 losing the co-evolutionary arms race.
+The histograms reflect what is seen in the scatter plots.
+
 ## Summary {.tabset}
+
+n the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
 
@@
 
+These plots mimic the plots seen with and without a cost gradient map, where clusters of points create lines of shapes and lines of colors, but there are some differences.
+In the late newt popsize by snake popsize the points seem to be spread out more (like more extreme population sizes).
+In the late phenotype difference and snake population size there is more of a difference between snake population size and the difference between snake and newt mean phenotype (most other plots things are more linear).
+For GA 1e-11_5 (purple points for snakes and plus points for newts) seem to have lead to a lower phenotype (or larger phenotype difference, i.e.
+when snakes have this GA newts tend to have a higher mean phenotype).
+These results puzzles me.
+
 ## Heatmap {.tabset}
+
+In the heatmap plots each GA combination and trails is presented by combining newt GA in the x-axis to snake GA and trial number in the y-axis.
+The result is the color in that section.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+I look at 3 time slices for both types of heatmaps.
 
@@
 ## {-}
+
+In the heat maps there is more variance between in both snake population size and phenotype difference simulation trials.
+The results tell similar stories when the GA of a species is 1e-09_0.05 the population size and phenotype are higher.
+Something is going on that is changing the difference between snake and newt phenotype in simulations with a GA 1e-11_5.
+These phenotype results are similar to the results seen when a species has a GA 1e-09_0.05.
+Something about a gradient interaction rate is changing the phenotype results.
+I think it might be the way things are averaged across the entire population.
+For example, if mutation that have a high cost lead to the individual to not reproducing, we lose out on higher phenotypes (for GA=1e-11_5) which we would see in areas of higher interaction.
+If we average between areas with few interactions (low phenotype) at the top and more interactions at the bottom (higher phenotype), but there are less individuals with a higher phenotype due to cost, the over all population average would be smaller.
 
@@
 ## {-}
+
+In the beginning of this particular simulations results look very spatially correlated, but later in this simulation there are not enough newts at the bottom of the map to make a good spacial correlation calculation so results look uncorrelated.

### 2023-03-09 graphs_newt_snakes/newt_change.Rmd
I have been filling out my thoughts about these experiments. They are truly some cool results

@@
 
+To test what would happen with the spatial phenotype correlation between newts and snakes when the fitness cost for newts in on a scale (dependent on location) and the fitness cost for snakes is constant.
+
 ### Questions:
@@
 ## Background
+
+Previously I have been looking at how newts and snakes can co-evolve under different genetic architectures (mutation rate and mutation effect size), and have found that while the mean phenotype increases there is no spatial phenotype correlation.
+This has puzzled me, how can there be a constant increase in phenotype but no spatial phenotype correlation?
+I think that there might be other factors that lead to spatial phenotype correlation.
+When I used a cost gradient map, I found that newt and snakes mean phenotype were spatially correlated.
+This is similar to an environmental condition.
+But what if the condition was only applies to one speceices?
 
@@
 
-Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.
-
-### The data
+Each GA combination and trial has its own msprime simulation.
+I created a gradient map where at the top there is a higher fitness cost for having a large phenotype and at the bottom there is a lower cost for having a higher phenotype.
+Only newts are effected by this gradient.
+Snakes fitness cost remain at 100.
+To see the gradient figure see cost gradient file.
 
@@
 
+These results look very similar to the results seen in my other simulations (no gradient map and gradient map).
+The mean phenotypes of newts and snakes go up, until they reach an equilibrium.
+Here the average values are higher than what I have seen in the no gradent map, but are lower than what I see in the cost gradient map.
+
 ## Connection between higher phenotype and population{.tabset}
+
+Here I plot the interaction between newt/snake phenotype and population size.
+Typically, when a species had a higher phenotype they also had a larger population size.
+This relation between phenotype and population size had specific outcomes that depended on the GA of newts and snakes.
+
+The first figure compares the population size of newts and snakes to the difference between mean snake and mean newt phenotype for a time slice (5,000-10,000 generations).
+Color in this plot is the difference between snake and newt phenotype, with blue indicating snakes have a larger phenotype and red indicating newts have a larger phenotype.
+Cream color points indicate that the two phenotypes are nearly the same.
+The second figure present the histograms of the difference between snake and newt population size (green) and phenotype (purple) for a time slice (5,000-10,000 generations).
 
@@
 
-whale_gen(newt_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(newt_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
+These results are similar to what I have seen before.
+There might be an increase in the differences between snake and newt phenotype, but the overall message higher phenotype = more individuals in unchanged.
+
 ## Correlation
 
-### cor
+The next section I am examining the spatial correlation between newt and snake phenotypes and I predicted that there would be a positive correlation between the phenotypes.
+I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
+The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
+
 ```{r, combo myplots}
@@
 
+In my previous results (no gradient map) I saw no positive spatial phenotype correlation between snakes and newts.
+Here, with a cost gradient map for newts I see that there are quite a few simulations where newt and snake local mean phenotypes are correlated when compared across space.
+This correlation is not as high or as frequent as what I saw when both newt and snake fitness cost was dependent on location.
+
 ## Correlation Histograms{.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
 
@@
 
+Spatial phenotype correlation increases for most of the simulations as time increases.
+Once a simulation reach a high spatial phenotype correlation, it typically did not go back down.
+The simulations where the simulations correlation values did not come close to the empirical newt and snake spatial phenotype correlation all contained a genetic architecture that had a small mutational variance.
+The exception to this is in the simulation where both newts and snakes had a low mutational variance, the local phenotypes became correlated then it faded (I wonder why).
+The spatial phenotype correlation is a lot higher than when there was not gradient map, but lower than when both newt and snakes fitness cost was on a gradient.
+When compared to the correlation results of snakes on a cost gradient and newts constant, the results in this document are more spatially correlated.
+
 ## Correlation across time {.tabset}
+
+Next, I examine three randomly chosen plots.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
 
@@
 
+Most of these plots show that as time increases both the mean newt & snake phenotype as well as the spatial phenotype correlation (pink line) increase (very few show no change).
+Spatial phenotype correlation increases the most when the newt and snake mean phenotypes are increasing the most.
+Some of these plots are very interesting to see.
+
 ## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+Then each msprime simulation is put into slim and data is generated.
+Plots show newt by snake population size, with the point color representing the difference between mean snake and newt phenotype (red=newts have a higher phenotype and blue=snakes have a higher phenotype).
+The other plots show histograms of difference between snakes and newts phenotype and population size (purple and green).
 
@@
 
+The results looked similar to results that I have seen in other experiments.
+In the beginning of the simulation both newt and snake population grows.
+The difference in phenotype quickly becomes polarized.
+The population size reaches a steady point and then newts and snakes co-evolve.
+In the middle part of my simulation, the difference between newt and snakes mean phenotype solidifies.
+Often, the difference in mean phenotype decreases (where compared to the beginning of the simulation).
+When newts had a GA that with a high mutation rate and low mutation effect size (GA 1), the difference in mean phenotype grows, leading to the newts losing the co-evolutionary arms race.
+In all other GA combinations newts had a larger phenotype.
+When looking at the snakes on a cost fitness scale, the results are flipped.
+When snakes had a GA that with a high mutation rate and low mutation effect size (GA 1), leading to the snakes losing the co-evolutionary arms race.
+Could there be something with in the environments causing one species to out compete the other?
+The histograms reflect what is seen in the scatter plots.
+
 ## Summary {.tabset}
+
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
 
@@
 
+Firstly, these plots are very similar to the plots seen with and without a gradient map.
+There are clusters of points that create lines of shapes and lines of colors.
+Points began clustered then spread apart.
+These points are similar between trials.
+There is one striking differences in these results, it seems that the results are shifted toward the newts favor (in the snakes cost gradient results things are shifted towards the snakes side).
+The shift does not seem to effect the circles (newt GA1).
+Thes plots are fun to look at.
+
 ## Heatmap {.tabset}
+
+In the heatmap plots each GA combination and trails is presented by combining newt GA in the x-axis to snake GA and trial number in the y-axis.
+The result is the color in that section.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+I look at 3 time slices for both types of heatmaps.
 
@@
 ## {-}
+
+Heatmap results are different, the seem more muted (less differences between GA combinations).
+They start off sort of neutral, and then become set in the favor of the newt (snake has a smaller population size while newts have a larger phenotype).
+Each trial of the GA combination creates very similar patterns.
 
@@
 ## {-}
+
+Newt and snake phenotypes are positively spatially correlated.
+Newt and snake population sizes are negativly correlated (look at the mini plots and not the values).
+Phenotypes in this simulation did not get as high as seen in the cost gradient simulations.

### 2023-03-09 graphs_newt_snakes/no_inter_cost_grade.Rmd
I have been filling out my thoughts about these experiments. They are truly some cool results

@@
 
+The goal of this experiment was to create a gradient picture and to assign different cost values to areas of the map and turn the interaction off.
+This will see if the interaction is needed to create spatial phenotype correlations between newts and snakes.
+
 ### Questions:
@@
 ## Background
+
+Previously I have been looking at how newts and snakes can co-evolve under different genetic architectures (mutation rate and mutation effect size), and have found that while the mean phenotype increases there is no spatial phenotype correlation.
+This has puzzled me, so I added in an environment factor (cost gradient) and found that newt and snake mean phenotypes became spatially correlated.
 
@@
 
-Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.
-
-### The data
+I created a gradient map where at the top there is a higher fitness cost for having a large phenotype and at the bottom there is a lower cost for having a higher phenotype.
+Both newts and snakes are effected by this gradient.
+However, in this simulation I break the interaction between newts and snakes.
+Survival of the newt or snake depends on a coin flip and not their phenotype.
 
@@
 
+In this first section I look at the entire populations mean phenotype for both snakes (blue) and newts (red).
+The difference between mean snake and mean newt phenotype is shown on the black line.
+For each GA combination there are 4 sets of lines (red, blue, black).
+Each line is a different trial with the same simulation parameters.
+I also present the average difference (of the trials) between snake and newt phenotype in the table of average differences.
+
 ### Phenotype differences 
 ```{r, graphing by gen}
-trends_by_gen(no_interaction_cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+trends_by_gen(no_interaction_cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 1000, 50000, rep=1)
 
@@
 
+These results look very similar to the results seen in the simulation with no interaction and no gradient map. The mean phenotypes of newts and snakes go down, until they reach an equilibrium.
+
 ## Connection between higher phenotype and population{.tabset}
+
+Here I plot the interaction between newt/snake phenotype and population size.
+Typically, when a species had a higher phenotype they also had a larger population size.
+This relation between phenotype and population size had specific outcomes that depended on the GA of newts and snakes.
+
+The first figure compares the population size of newts and snakes to the difference between mean snake and mean newt phenotype for a time slice (5,000-10,000 generations).
+Color in this plot is the difference between snake and newt phenotype, with blue indicating snakes have a larger phenotype and red indicating newts have a larger phenotype.
+Cream color points indicate that the two phenotypes are nearly the same.
+The second figure present the histograms of the difference between snake and newt population size (green) and phenotype (purple) for a time slice (5,000-10,000 generations).
 
@@
 
+These results are similar to what I have seen in the initial no interaction simulation.
+Higher phenotype does not equal more individuals, a lower GA mutational variance ends up having a higher phenotype.
+
 ## Correlation
 
-### cor
+The next section I am examining the spatial correlation between newt and snake phenotypes and I predicted that there would be a positive correlation between the phenotypes.
+I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
+The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
+
 ```{r, combo myplots}
@@
 
+There is no positive or negative spatail correlation. The spatial phenotype correlation is close to zero.
+
 ## Correlation Histograms{.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
 
@@
 
+The spatial phenotype correlation does not increase over time, it stays around zero (similar to the no interaction/cost gradient map).
+
 ## Correlation across time {.tabset}
+
+Next, I examine three randomly chosen plots.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
 
@@
 
+The mean phenotypes of newt (red) and snake (blue) go down as the number of generations increase.
+The spatial correlation between newt and snake mean phenotype (pink) is randomly increasing and decreasing, but hanging out around zero.
+
 ## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+Then each msprime simulation is put into slim and data is generated.
+Plots show newt by snake population size, with the point color representing the difference between mean snake and newt phenotype (red=newts have a higher phenotype and blue=snakes have a higher phenotype).
+The other plots show histograms of difference between snakes and newts phenotype and population size (purple and green).
 
@@
 
+The results looked similar to results that I have seen in the other no interaction experiment.
+In the beginning of the simulation both newt and snake population grows.
+The difference in phenotype quickly becomes polarized (depending on GA).
+The population size reaches a steady point and then newts and snakes co-evolve.
+In the middle part of my simulation, the difference between newt and snakes mean phenotype solidifies.
+The histograms reflect what is seen in the scatter plots.
+
 ## Summary {.tabset}
+
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
 
@@
 
+After examining these plots I found that there is no relationship between GA and population size or population size and phenotype.
+A higher newt mutational variance led to a lower newt phenotype (possibly pushed down due to cost and no interaction).
+These results are very similar to the no interaction/ no coat gradient simulation.
+It seems like the gradient map has little effect when the interaction of newt and snake is not dependent on phenotype.
+What if there was an interaction, but the rate was smaller?
+
 ## Heatmap {.tabset}
+
+In the heatmap plots each GA combination and trails is presented by combining newt GA in the x-axis to snake GA and trial number in the y-axis.
+The result is the color in that section.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+I look at 3 time slices for both types of heatmaps.
 
@@
 ## {-}
+
+The results of this section how that there is no relationship between GA and population size (colors seem random).
+There is relationship between GA and phenotype.
+Again, the difference in phenotype is symmetrical across the diagonal (right diagonal this time).
+Species have a higher phenotype is they have a GA with lower mutational variance.
+This might be due to the mutational effect size distribution and phenotype cost.
 
@@
 ## {-}
+
+Prototypes remain low so there is no spatial correlation.

### 2023-03-09 graphs_newt_snakes/snake_change.Rmd
I have been filling out my thoughts about these experiments. They are truly some cool results

@@
 
+To test what would happen with the spatial phenotype correlation between newts and snakes when the fitness cost for snakes in on a scale (dependent on location) and the fitness cost for newts is constant.
+
 ### Questions:
@@
 ## Background
+
+Previously I have been looking at how newts and snakes can co-evolve under different genetic architectures (mutation rate and mutation effect size), and have found that while the mean phenotype increases there is no spatial phenotype correlation.
+This has puzzled me, how can there be a constant increase in phenotype but no spatial phenotype correlation?
+I think that there might be other factors that lead to spatial phenotype correlation.
+When I used a cost gradient map, I found that newt and snakes mean phenotype were spatially correlated.
+This is similar to an environmental condition.
+But what if the condition was only applies to one species?
 
@@
 
-Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.
-
-### The data
+Each GA combination and trial has its own msprime simulation.
+I created a gradient map where at the top there is a higher fitness cost for having a large phenotype and at the bottom there is a lower cost for having a higher phenotype.
+Only snakes are effected by this gradient.
+Newts fitness cost remain at 100.
+To see the gradient figure see cost gradient file.
 
@@
 
+These results look very similar to the results seen in my other simulations (no gradient map and gradient map).
+The mean phenotypes of newts and snakes go up, until they reach an equilibrium.
+Here the average values are higher than what I have seen in the no gradient map, but are lower than what I see in the cost gradient map.
+There are more simulations where snakes have a higher mean phenotype.
+
 ## Connection between higher phenotype and population{.tabset}
+
+Here I plot the interaction between newt/snake phenotype and population size.
+Typically, when a species had a higher phenotype they also had a larger population size.
+This relation between phenotype and population size had specific outcomes that depended on the GA of newts and snakes.
+
+The first figure compares the population size of newts and snakes to the difference between mean snake and mean newt phenotype for a time slice (5,000-10,000 generations).
+Color in this plot is the difference between snake and newt phenotype, with blue indicating snakes have a larger phenotype and red indicating newts have a larger phenotype.
+Cream color points indicate that the two phenotypes are nearly the same.
+The second figure present the histograms of the difference between snake and newt population size (green) and phenotype (purple) for a time slice (5,000-10,000 generations).
 
@@
 
-whale_gen(snake_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(snake_change_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
+These results are similar to what I have seen before.
+There might be an increase in the differences between snake and newt phenotype, but the overall message higher phenotype = more individuals in unchanged.
+
 ## Correlation
+
+The next section I am examining the spatial correlation between newt and snake phenotypes and I predicted that there would be a positive correlation between the phenotypes.
+I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
+The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
 
@@
 
+In my previous results (no gradient map) I saw no positive spatial phenotype correlation between snakes and newts.
+Here, with a cost gradient map for snakes I see that there are quite a few simulations where newt and snake local mean phenotypes are correlated when compared across space.
+This correlation is not as high or as frequent as what I saw when both newt and snake fitness cost was dependent on location.
+It is more similar to what I saw in the newts cost gradient results.
+
 ## Correlation Histograms{.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
 
@@
 
+Spatial phenotype correlation increases for most of the simulations as time increases.
+Once a simulation reach a high spatial phenotype correlation, it typically did not go back down.
+The simulations where the simulations correlation values did not come close to the empirical newt and snake spatial phenotype correlation all contained a genetic architecture that had a small mutational variance.
+The spatial phenotype correlation is a lot higher here, than when there was not gradient map, but lower than when both newt and snakes fitness cost was on a gradient.
+Results presented here are less spatially correlated, when compared to the correlation results of newts on a cost gradient and snakes constant.
+
 ## Correlation across time {.tabset}
+
+Next, I examine three randomly chosen plots.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
 
@@
 ## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+Then each msprime simulation is put into slim and data is generated.
+Plots show newt by snake population size, with the point color representing the difference between mean snake and newt phenotype (red=newts have a higher phenotype and blue=snakes have a higher phenotype).
+The other plots show histograms of difference between snakes and newts phenotype and population size (purple and green).
 
@@
 
+The results looked similar to results that I have seen in other experiments.
+In the beginning of the simulation both newt and snake population grows.
+The difference in phenotype quickly becomes polarized.
+The population size reaches a steady point and then newts and snakes co-evolve.
+In the middle part of my simulation, the difference between newt and snakes mean phenotype solidifies.
+Often, the difference in mean phenotype decreases (where compared to the beginning of the simulation).
+When snakes had a GA that with a high mutation rate and low mutation effect size (GA 1), the difference in mean phenotype grows, leading to the snakes losing the co-evolutionary arms race.
+In all other GA combinations snakes had a larger phenotype.
+When looking at the newts on a cost fitness scale, the results are flipped.
+When newts had a GA that with a high mutation rate and low mutation effect size (GA 1), leading to the newts losing the co-evolutionary arms race.
+Could there be something with in the environments causing one species to out compete the other?
+This was not a complete symmetric image, what could make things slightly different?
+The histograms reflect what is seen in the scatter plots.
+
 ## Summary {.tabset}
+
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
 
@@
 
+These plots are very similar to the plots seen with and without a gradient map.
+There are clusters of points that create lines of shapes and lines of colors.
+Points began clustered then spread apart as time increases.
+These points are similar between trials.
+There is one striking differences in these results, it seems that the results are shifted toward the snakes favor (in the newt cost gradient results things are shifted towards the newt side).
+The shift does not seem to effect the pink points (snake GA1).
+These plots are fun to look at and compare.
+
 ## Heatmap {.tabset}
+
+In the heatmap plots each GA combination and trails is presented by combining newt GA in the x-axis to snake GA and trial number in the y-axis.
+The result is the color in that section.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+I look at 3 time slices for both types of heatmaps.
 
@@
 ## {-}
+
+Heatmap results are different, the seem more muted (less differences between GA combinations).
+They start off sort of neutral, and then become set in the favor of the snake (newts have a smaller population size while snakes have a larger phenotype).
+Each trial of the GA combination creates very similar patterns.
+The differences between GA combinations are more pronounced than when newts had a fitness cost gradient, but less pronounced when compared to both newts and snakes being on a cost gradient.
 

### 2023-03-14 graphs_newt_snakes/move_together.Rmd
got some writting done for this markdown.

@@
 
-What does it mean to be correlated? Might this occur if I simulate some controlled movement?
+What does it mean to be correlated? Might this occur if I simulate some semi-controlled movement?
 
@@
 
-Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.
-
-### The data
+Each GA combination and trial has its own msprime simulation.
+I start both the newt and snake population in the bottom third section of my map.
+Over time they eventually disperse into the entire map.
+The background enverionment is homogeneous.
 
@@
 
+There are some interesting differences taking place here, when compared to simulation without movement and maps.
+It seems like it takes a bit longer to reach a steady state (but this could also be the stochasticity of the simulation).
+The mean newt and snake phenotype get to similar values as my original simulations.
+Still follows what I have seen before, the mean phenotypes of newts and snakes go up, until they reach an equilibrium.
+
 ## Connection between higher phenotype and population{.tabset}
+
+Here I plot the interaction between newt/snake phenotype and population size.
+Typically, when a species had a higher phenotype they also had a larger population size.
+This relation between phenotype and population size had specific outcomes that depended on the GA of newts and snakes.
+
+The first figure compares the population size of newts and snakes to the difference between mean snake and mean newt phenotype for a time slice (5,000-10,000 generations).
+Color in this plot is the difference between snake and newt phenotype, with blue indicating snakes have a larger phenotype and red indicating newts have a larger phenotype.
+Cream color points indicate that the two phenotypes are nearly the same.
+The second figure present the histograms of the difference between snake and newt population size (green) and phenotype (purple) for a time slice (5,000-10,000 generations).
 
@@
 
+These results are similar to what I have seen before.
+There might be an increase in the differences between snake and newt phenotype, but the overall message higher phenotype = more individuals in unchanged.
+However, the layout of the points seems to be flatter and stretched.
+
 ## Correlation
+
+The next section I am examining the spatial correlation between newt and snake phenotypes and I predicted that there would be a positive correlation between the phenotypes.
+I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
+The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
 
@@
 
+The spatial phenotype correlation seems very random.
+
 ## Correlation Histograms{.tabset}
+
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
 
@@
 
+It seems like there is an increase in phenotype spatial correlation near the beginning of the simulation (<25,000 generations), but as time goes on it is lost.
+The spatial phenotype correlation is also lower than the spatial correlation that result from simulations run with a gradient map.
+
 ## Correlation across time {.tabset}
+
+Next, I examine three randomly chosen plots.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
 
@@
 
+Most of these plots show that as time increases both the mean newt & snake phenotype.
+Some of these plots have an increase in the spatial phenotype correlation (pink line), but this increase in the correlation between local newt and snake phenotypes can also seem very random.
+Sometimes the spatial phenotype correlation increases and then decreases overtime.
+Under certain GA combinations (both 1e09_0.05) spatial phenotype correlation increases the most when the newt and snake mean phenotypes are increasing the most.
+
 ## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+Then each msprime simulation is put into slim and data is generated.
+Plots show newt by snake population size, with the point color representing the difference between mean snake and newt phenotype (red=newts have a higher phenotype and blue=snakes have a higher phenotype).
+The other plots show histograms of difference between snakes and newts phenotype and population size (purple and green).
 
@@
 
+The results looked similar to results that I have seen in other experiments, with an exception at the beginning.
+In the beginning of the simulation both newt and snake population grows, but this growth has a longer tail do to the populations expanding territory.
+The population size reaches a steady point and then newts and snakes co-evolve.
+In the middle part of my simulation, the difference between newt and snakes mean phenotype solidifies.
+Often, the difference in mean phenotype decreases (where compared to the beginning of the simulation).
+When the GA has a high mutation rate and low mutation effect size (GA 1), the difference in mean phenotype grows.
+This leads to the species with GA 1 losing the co-evolutionary arms race.
+More frequent smaller steps does not help a species win in an arms race (might also be due to lower mutational variance).
+The histograms reflect what is seen in the scatter plots.
+
 ## Summary {.tabset}
+
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
 
@@
 
+Overall, these plots are very similar to the plots seen with and without a gradient map.
+The largest difference is seen from plots at the beginning of the simulation.
+At the beginning of the simulation the points are more spread out (less in a line), eventually they form the line of shapes and colors seen in my previous simulations.
+There are clusters of points that create lines of shapes and lines of colors.
+The best GA for newts and snakes was 1e-09_0.05 (can be seen as green near the top of all the lines of shapes and triangles near the bottom right look at all the lines of color).
+It is interesting to see how these points spread apart, but remain similar between trials.
+When putting these figures together it seems like the population size of snakes is lower when the newt phenotype is larger than the snake phenotype.
+
 ## Heatmap {.tabset}
+
+In the heatmap plots each GA combination and trails is presented by combining newt GA in the x-axis to snake GA and trial number in the y-axis.
+The result is the color in that section.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+I look at 3 time slices for both types of heatmaps
 
@@
 ## {-}
+
+As with results seen in the summary plots, the heat map plots tell a similar story.
+At the beginning of the simulation the snake population size and the mean difference between snake and newt phenotype varies a lot between the simulation trials, more than any other simulation that I have currently run.
+But by the end of the simulation the results remain similar to all of the other simulations that I have run.
+Theses plots shows that under certain GA either newts or snakes have an co-evolutionary advantage (best GAs 1e-9(0.05)^2 = 2.5e-12 or 1e-10(0.5)^2 = 2.5e-11).
 
@@
 ## {-}
+
+These results are interesting, they show that movement might create an increase in spatial phenotype correlation, but that this correlation disappears over time. Very interesting results.

### 2023-03-15 graphs_newt_snakes/bob_notes.Rmd
I made edits to the file to write about my thoughts

@@
 
-What does it mean to be correlated? Bob made some sugestions for the caculation of phenotype and the slope of the interaction.
-prob_of_survive = 1.0/(1+exp(-((compair_pheno-c)/w))) In this equation c=0 and w=10. W may be too high, which could limit interaction/coevolution outcomes.
-The way phenotypes are defined might be creating a multiplicative effect: exp(ind.sumOfMutationsOfType(m2)/10))
+What does it mean to be correlated?
+Bob made some suggestions for the calculation of phenotype and the slope of the interaction.
+So in this markdown I explore there things: 1) I will change the way I calculate the newt and snake phenotype (making it more additive and less multiplicative), 2) I will also change the slope of the interaction by setting w lower, and 3) I will change both of these parameters.
+
+LInes within my code that will be changed:
+
+- prob_of_survive = 1.0/(1+exp(-((compair_pheno-c)/w))) In this equation c=0 and w=10. W may be too high, which could limit interaction/coevolution outcomes.
+- The way phenotypes are defined might be creating a multiplicative effect: exp(ind.sumOfMutationsOfType(m2)/10))
 
 ## Background
+
+Previously I have been looking at how newts and snakes can co-evolve under different genetic architectures (mutation rate and mutation effect size), and have found that while the mean phenotype increases there is no spatial phenotype correlation.
+This has puzzled me, how can there be a constant increase in phenotype but no spatial phenotype correlation?
+After adding a gradient map (for a fitness cost and interaction) and seeing high phenotype spatial correlations I wondered if there were other things that could vary and still create spatial phenotype correlation.
 
@@
 Each GA combination and trial has its own msprime simulation.
+
 I ran 3 experiments a) no exp in the phenotype, b) lower w and, c) both no exp and a lower w
@@
 
-many of the experiments did not run to completion (i will run this part 3 times)
+Note: Many of the experiments did not run to completion (I will ran this part 3 times, then ran a fourth time where I let a species die out)
 
@@
 
+In this first section I look at the entire populations mean phenotype for both snakes (blue) and newts (red) for each of the there experiments.
+The difference between mean snake and mean newt phenotype is shown on the black line.
+For each GA combination there are 4 sets of lines (red, blue, black).
+Each line is a different trial with the same simulation parameters.
+I also present the average difference (of the trials) between snake and newt phenotype in the table of average differences.
+
 ### Phenotype differences (both_lower_w_no_exp)
@@
 
+These results have similar and different qualities to the simulations that I have run before.
+The similar aspects are that both newt and snake mean phenotype go up as time in the simulation progress (newt and snake mean phenotype seem to follow each other).
+Some things that I noticed that are extremity different: When both w is lower and no exp in the phenotype calculation most of the simulations end up crashing.
+In the lower w most of the simulation run to completion and newt and snake mean phenotypes are closely matched.
+The mean phenotype in these simulations ended up higher, simulations that creased were simulations that one of the species had a GA with low mutational variance.
+In the no exp phenotype simulations most of the simulations end up with newts having a dramatically higher mean phenotype.
+In this simulation there are some negative phenotype values.
+
 ## Connection between higher phenotype and population{.tabset}
+
+Here I plot the interaction between newt/snake phenotype and population size.
+Typically, when a species had a higher phenotype they also had a larger population size.
+This relation between phenotype and population size had specific outcomes that depended on the GA of newts and snakes.
+
+The first figure compares the population size of newts and snakes to the difference between mean snake and mean newt phenotype for a time slice (5,000-10,000 generations).
+Color in this plot is the difference between snake and newt phenotype, with blue indicating snakes have a larger phenotype and red indicating newts have a larger phenotype.
+Cream color points indicate that the two phenotypes are nearly the same.
+The second figure present the histograms of the difference between snake and newt population size (green) and phenotype (purple) for a time slice (5,000-10,000 generations).
 
@@
 
-whale_gen(both_lower_w_no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(both_lower_w_no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
-whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
-whale_gen(no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(no_exp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
+In the time points that I view the interaction between newt and snake population sizes and phenotypes some of the simulations had already crashed, I will only be explaining the ones that made it.
+The overall meaning of these plots suggest that a higher phenotype leads to more individuals.
+However, most of these plots seem to indicate that newts have an advantage in all three experiments (only 5 cases where snakes have a higher population size/ phenotype).
+
 ## Correlation{.tabset}
-HEREREERERERER
+
+The next section I am examining the spatial correlation between newt and snake phenotypes and I predicted that there would be a positive correlation between the phenotypes.
+I first look at the correlation between mean newt phenotype and mean snake phenotype for each of the four trials in every GA combination from 10,000-15,000 generations.
+The solid line is a 0 with a dashed line at the level of correlation seen in natural newt-snake population(s).
 
@@
 
+The spatial phenotype correlations of these experiments are all near zero.
+There was one trial of one GA combination of one experiment that made it near the real newt and snake spatial phenotype correlation.
+These results are similar to the results I saw before working with a gradient map.
+
 ## Correlation Histograms Both{.tabset}
+
+These next three sections are what I was mostly interested in looking at!
+In order to understand how spatial correlations where changing with time I took 5,000 generation time slices to look at all four trials correlation values.
+Each color is a different trial per GA combination.
+The histogram values are stacked.
 
@@
 
+Sadly, there were no simulations that continuously had high spatial phenotype correlations.
+Some simulation did end up having one time slice of high spatial correlations, but they died out before the end of the next time slice.
+Some conditions under a lower w might lead to more spatial phenotype correlations, but I am not sure what other things might need to change.
+Under both a lower w and no exp in the phenotype there was one GA combination that had high spatial correlation values, however it did not last.
+
 ## Correlation across time (both_lower_w_no_exp)  {.tabset}
+
+Next, I examine three randomly chosen plots.
+Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis.
+Newt whole population mean phenotype is red, while snake mean phenotype is blue.
+The pink line is the phenotype spatial correlation.
 
@@
 
+There are various examples of what can occur in these plots.
+Mostly we see that newt and snake mean phenotype will increase (red and blue line) with the number of generations.
+Sometimes one or both of these lines stays flat.
+The phenotype spatial correlation line (pink) can become high, but tends to be randomly fluctuating.
+
 ## What happens over time (looking at the beginning, middle, and late part of my simulations) (both_lower_w_no_exp) {.tabset}
+
+This next section is just getting a glimpse at how newt & snake phenotype and population size differ over time.
+The populations start off with about 250 individuals each.
+Each individual has a different genetic background created from msprime.
+Then each msprime simulation is put into slim and data is generated.
+Plots show newt by snake population size, with the point color representing the difference between mean snake and newt phenotype (red=newts have a higher phenotype and blue=snakes have a higher phenotype).
+The other plots show histograms of difference between snakes and newts phenotype and population size (purple and green).
 
@@
 
+There are so many missing plots that it is difficult to under what is going on.
+I will try my best.
+In the both low w and no exp in the phenotype experiment snake population size dramatically increases then falls in nearly all GA combinations.
+Only a few simulations run to completion and those are when the snake or newt has the GA with the highest mutational variance.
+In the low w experiment more simulations finish and the results look similar to the experiments I ran without a gradient map, except that when one of the species had a GA with low mutational variance the simulation did not complete.
+In the no exp phenotype experiment all of the simulations end up with newts having a higher mean phenotype, but the population sizes of snakes increased as the GA mutational variance increased.
+The difference in the mean phenotype (snake - newt) grew as the newts GA increased.
+These results were really interesting to look at.
+
 ## Summary (both_lower_w_no_exp) {.tabset}
+
+In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results.
+In all of these plots snakes GA is represented by color and newt GA is represented by shape.
+There 16 color-shape combinations (with 4 repeats for trials).
+There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA.
+There are three figures in each set, taken at the begging, middle, and end time chunks.
 
@@
 
+Again, since a bunch of the simulations died out the results in this section might be a bit sparse.
+
+In the both low w and no exp experiment all GA 1e-8_0.005 disappear.
+In the population size plot as time progressed groups of color emerged.
+These indicate that the population size of newts and snakes depended on the GA of the snake.
+In the difference between snake and newt phenotype by snake population size there was no discernible relationship between phenotype deference and population size.
+In the low w experiment there was a slight relationship between newt and snake population size at the extremes of the GA combinations, but for the most part all other GA combinations lead to similar population sizes.
+similar things were seen in the phenotype difference by snake population size plots.
+There was a bit more separation by color and shape here beneficial to the snake is when newt had a GA of 1e-11_5 > 1e-10_0.5 > 1e-9_0.05 (separation by shape) beneficial to the newt when the snake had a GA of 1e-11_5 > 1e-10_0.5 > 1e-9_0.05 (separation by color).
+In the no exp simulation the was a separation of color.
+There was also color separation in the difference in phenotype and snake population size plots.
+The best GA for snake was 1e-11_5:1e-10_0.5 > 1e-9_0.05 > 1e-8_0.005.
+A best GA for the newt was difficult to decipher.
+
 ## Heatmap (both_lower_w_no_exp) {.tabset}
+
+In the heatmap plots each GA combination and trails is presented by combining newt GA in the x-axis to snake GA and trial number in the y-axis.
+The result is the color in that section.
+There are two types of heatmap plots shown below.
+One shows the average snake population size for a time chunk with darker colors indicating a smaller snake population and lighter colors indicating a larger snake population.
+The other heatmap shows the average difference between snake and newt mean phenotype (red=newts had a higher phenotype, blue=snakes had a higher phenotype).
+I look at 3 time slices for both types of heatmaps.
 
@@
 ## {-}
+
+In the both low w and no exp experiment about half the values are missing.
+There is some agreement between trials on snake population size there might be a relationship between snake GA and newt GA in that when there is more mutational arrange in the snake GA the snake population size and phenotype increases.
+This is not true for the newts.
+In the low w experiment there is only a relationship between snake GA and newt GA when viewing the extreme GA combinations.
+When the GA creates the highest and the low mutational variance the species with the higher MV will have a higher phenotype and population size.
+All other GA combinations had average snake population size with some variation in the mean phenotype difference.
+In the no exp experiment there is agreement amongst the GA trials.
+There is a difference between the snake GA and not the newt GA.
+As the snakes GA with mutational variance gets smaller so does the population size.
+As the snakes GA with mutational variance gets smaller the difference between snake and newt mean phenotype gets longer (newts have a higher mean phenotype).
 

### 2023-03-22 graphs_newt_snakes/Paper_figs.Rmd
I made some more figures that look really nice

@@
 
-grid.arrange(main_plot, bloan, extra_plot, ncol = 2, 
-             layout_matrix=cbind(c(1,1),c(2,3)))
+plot(main_plot)
+
+#grid.arrange(main_plot, bloan, extra_plot, ncol = 2, 
+#             layout_matrix=cbind(c(1,1),c(2,3)))
 
@@
 
+cost_grade_no_interact_cor<- read.csv("~/Desktop/no_interaction_cost_grade/all_cor.txt" , header = TRUE)
+cost_grade_no_interact_cor$group_rep <- paste0(cost_grade_no_interact_cor$snake_mu_rate, "_", cost_grade_no_interact_cor$snake_mu_effect_sd,"_",cost_grade_no_interact_cor$newt_mu_rate, "_", cost_grade_no_interact_cor$newt_mu_effect_sd, "_", cost_grade_no_interact_cor$rep)
+cost_grade_no_interact_cor$group <- paste0(cost_grade_no_interact_cor$snake_mu_rate, "_", cost_grade_no_interact_cor$snake_mu_effect_sd,"_",cost_grade_no_interact_cor$newt_mu_rate, "_", cost_grade_no_interact_cor$newt_mu_effect_sd)
+cost_grade_no_interact_cor$sim=LETTERS[factor(cost_grade_no_interact_cor$group)]
+cost_grade_no_interact_cor$exp="Cost Gradent Map No Interaction"
+
+snake_change_cor<- read.csv("~/Desktop/snake_change/all_cor.txt" , header = TRUE)
+snake_change_cor$group_rep <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd, "_", snake_change_cor$rep)
+snake_change_cor$group <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd)
+snake_change_cor$sim=LETTERS[factor(snake_change_cor$group)]
+snake_change_cor$exp="Snake Gradent Map"
+
+newt_change_cor<- read.csv("~/Desktop/newt_change/all_cor.txt" , header = TRUE)
+newt_change_cor$group_rep <- paste0(newt_change_cor$snake_mu_rate, "_", newt_change_cor$snake_mu_effect_sd,"_",newt_change_cor$newt_mu_rate, "_", newt_change_cor$newt_mu_effect_sd, "_", newt_change_cor$rep)
+newt_change_cor$group <- paste0(newt_change_cor$snake_mu_rate, "_", newt_change_cor$snake_mu_effect_sd,"_",newt_change_cor$newt_mu_rate, "_", newt_change_cor$newt_mu_effect_sd)
+newt_change_cor$sim=LETTERS[factor(newt_change_cor$group)]
+newt_change_cor$exp="Newt Gradent Map"
+
 boxplot_cors_by_gen_col_rep <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){
@@
 
-file1 = GA1_cor[which(1:nrow(GA1_cor) %% 2 != 0) , ]
+boxplot_cors_by_gen_col_rep_6_file <- function(file1, file2, file3, file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
+   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
+   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
+    file4$snake_newt <- paste0(file4$snake_mu_rate, "_", file4$snake_mu_effect_sd, "_", file4$newt_mu_rate, "_", file4$newt_mu_effect_sd)
+   file5$snake_newt <- paste0(file5$snake_mu_rate, "_", file5$snake_mu_effect_sd, "_", file5$newt_mu_rate, "_", file5$newt_mu_effect_sd)
+   file6$snake_newt <- paste0(file6$snake_mu_rate, "_", file6$snake_mu_effect_sd, "_", file6$newt_mu_rate, "_", file6$newt_mu_effect_sd)
+file <- rbind(file1, file2, file3, file4, file5, file6)
+
+file$sim <- str_replace_all(file$sim, "[ABCDEIM]", 'Sims')
+#c("A"='Low Mu Var', "B"='Low Mu Var', "C"='Low Mu Var', "D"='Low Mu Var', "E"='Low Mu Var', "I"='Low Mu Var', "M"='Low Mu Var'))
+
+file$cor_score <- ifelse(file$sim == "Sims", "False","True")
+
+#file$cor_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
+
+file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map No Interaction", "Cost Gradent Map", "Snake Gradent Map", "Interaction Gradent Map", "Newt Gradent Map"))
+
+  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim, level=c('Sims', "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
+  theme(plot.title = element_text(size=5)) +
+  #xlim(-1.1, 1.1)+
+    geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+  facet_wrap(~exp, ncol=2)+
+  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutatinal Variance', 'Coevolution'))+
+    labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+
+  return(plot)
+}
+
+file1 = GA1_cor
 file2 = cost_grade_cor
 file3 = interrate_grade
+file4 = cost_grade_no_interact_cor
+file5 = snake_change_cor
+file6 = newt_change_cor
 title = "Spatial Phenotype Correlation Across Different Simulation Conditions"
@@
 boxplot_cors_by_gen_col_rep(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen)
+boxplot_cors_by_gen_col_rep_6_file(file1, file2, file3, file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen)
 
@@
 file$newt_snake_pheno_avg= (file$newt_pheno_change+file$snake_pheno_change)/2
+file$rect_type = ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
+
+target=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
+
+file$xmin = match(file$sim, target) - 0.5
+
+file$xmax = match(file$sim, target) + 0.5
 
@@
 geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)))+
-  theme(plot.title = element_text(size=5)) +
-  #xlim(-1.1, 1.1)+
-  scale_fill_manual(values =c("darkred", "steelblue"), labels=c('Newt', 'Snake'))+
-    labs(fill = " ")+
-    #scale_fill_manual(values =c("darkred", "purple", "steelblue"), labels=c('Newt Advantage', 'No Advantage', 'Snake Advantage'))+
+  geom_rect(aes(xmin = as.numeric(xmin), xmax = as.numeric(xmax), ymin = -Inf, ymax = Inf, fill = rect_type)) +
+  scale_fill_manual( values =c("darkred", "steelblue", "white","aliceblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change', "True", "False"),  labels = c('Newt', 'Snake', "True", "False"))+ #labels=c("False",'Newt', 'Snake', "True")
+      geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)),show.legend = FALSE)+
+     theme(plot.title = element_text(size=5)) +
     labs(fill = " ")+
@@
 
+boxplot_coevo_slope_small_exp_color <- function(file1, file2, file3, title, subt, x_label, y_label){
+
+   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
+   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
+   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
+
+file <- rbind(file1, file2, file3)
+file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
+file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
+#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
+#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)
+
+file$exp = factor(file$exp, levels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))
+
+file<- subset(file, !sim %in% c("A", "B", "C", "D", "E", "I", "M"))
+
+file$newt_snake_pheno_avg= (file$newt_pheno_change+file$snake_pheno_change)/2
+
+  plot <-  ggplot(file) +
+  ggtitle(title, subtitle = subt)+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim), y=as.numeric(newt_snake_pheno_avg), fill=factor(exp)))+
+  theme(plot.title = element_text(size=5)) +
+  #xlim(-1.1, 1.1)+
+  scale_fill_manual(values =c("darkolivegreen1", "azure2", "darkorange3"), labels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))+
+    labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+
+  return(plot)
+}
+
 file=move_together_lit
@@
 boxplot_coevo_slope_small(file1, file2, file3, title, subt, x_label, y_label)
+
+boxplot_coevo_slope_small_exp_color(file1, file2, file3, title, subt, x_label, y_label)
 

### 2023-04-12 graphs_newt_snakes/Paper_figs.Rmd
I made some plot changes

@@
 
-target=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
-
-file$xmin = match(file$sim, target) - 0.5
-
-file$xmax = match(file$sim, target) + 0.5
+file$rect_type_a = ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", .9,1)
+
+#target=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
+
+#file$xmin = match(file$sim, target) - 0.5
+
+#file$xmax = match(file$sim, target) + 0.5
 
@@
   xlab(x_label) + ylab(y_label)+
-geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)))+
-  geom_rect(aes(xmin = as.numeric(xmin), xmax = as.numeric(xmax), ymin = -Inf, ymax = Inf, fill = rect_type)) +
-  scale_fill_manual( values =c("darkred", "steelblue", "white","aliceblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change', "True", "False"),  labels = c('Newt', 'Snake', "True", "False"))+ #labels=c("False",'Newt', 'Snake', "True")
-      geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)),show.legend = FALSE)+
-     theme(plot.title = element_text(size=5)) +
+geom_boxplot(aes(x=factor(sim), y=as.numeric(value), fill=factor(name), alpha = rect_type_a))+ #, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
+  #geom_rect(aes(xmin = as.numeric(xmin), xmax = as.numeric(xmax), ymin = -Inf, ymax = Inf, fill = rect_type)) +
+  #scale_fill_manual( values =c("darkred", "steelblue", "white","aliceblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change', "True", "False"),  labels = c('Newt', 'Snake', "True", "False"))+ #labels=c("False",'Newt', 'Snake', "True")
+  scale_fill_manual( values = c("darkred", "steelblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change'),  labels = c('Newt', 'Snake'))+
+      #geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)),show.legend = FALSE)+
+     theme(plot.title = element_text(size=5)) +
+  scale_alpha(guide = 'none')+
+    labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+
+  return(plot)
+}
+
+boxplot_coevo_popsize_flat_map <- function(file, title, subt, x_label, y_label){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+newt_adv= c("D", "C", "B", "H", "G", "L")
+mid= c("A", "F", "K", "P")
+snake_adv = c("E", "I", "J", "M", "N", "O")
+
+file$coevo_score = 0
+
+file$coevo_score[file$sim %in% newt_adv] = "Newt Advantage"
+file$coevo_score[file$sim %in% mid] = "No Advantage"
+file$coevo_score[file$sim %in% snake_adv] = "Snake Advantage"
+file$rect_type = ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
+
+file$rect_type_a = ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", .9,1)
+
+target=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
+
+file_long <- tidyr::pivot_longer(file, c(Newt_pop_size, Snake_pop_size))
+
+plot <-   ggplot(file_long[which(file_long$generation>=40000),]) +
+  ggtitle(title, subtitle = subt)+
+  xlab(x_label) + ylab(y_label)+
+geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name), alpha = rect_type_a))+
+  scale_fill_manual( values = c("darkred", "steelblue" ), breaks = c('Newt_pop_size', 'Snake_pop_size'),  labels = c('Newt Pop Size', 'Snake Pop Size'))+
+  theme(plot.title = element_text(size=5)) +
+  scale_alpha(guide = 'none')+
   labs(fill = " ")+
@@
 
+fast_slow_no_coevolution <- function(file, choices,min_gen, max_gen, title, subt, x_label, y_label){
+
+   file<- subset(file, sim %in% choices)
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+file$coevo_speed = 0
+
+file$coevo_speed[file$sim %in% choices[1]] = "Fast Coevolution"
+file$coevo_speed[file$sim %in% choices[2]] = "Slow Coevolution"
+file$coevo_speed[file$sim %in% choices[3]] = "No Coevolution"
+file$coevo_speed = factor(file$coevo_speed, levels=c("Fast Coevolution", "Slow Coevolution", "No Coevolution"))
+plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==0),]) +
+    facet_wrap(~coevo_speed, ncol=1)+
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+#group=rep
+    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"))+#group=rep
+    #ylim(-1.,2.5)+
+    xlab(x_label) + ylab(y_label)+
+    scale_color_manual(name = "Species",
+values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
+labels = c("Snake", "Newt"))+
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
+                      title =element_text(size=8, face='bold'))
+  return(plot)
+
+}
+
 file=move_together_lit
@@
 GA1_lit$exp="Coevolution Flat Map"
+
+```
+
+```{r, look at the change in phenotyp the plots}
 
@@
 boxplot_coevo_slope_flat_map(file3, title, subt, x_label, y_label)
+
+title = "Population Size Coevolution FLat Map"
+y_label= "Population Size"
+boxplot_coevo_popsize_flat_map(file3, title, subt, x_label, y_label)
+
+file= GA1_lit
+choices=c("K", "F", "E")
+min_gen=100
+max_gen=50000
+title="Different Speeds of Coevolution" 
+subt="" 
+x_label= "Generations"
+y_label= "Phenotype"
+fast_slow_no_coevolution(file, choices, min_gen, max_gen, title, subt, x_label, y_label)
 ```

### 2023-05-31 graphs_newt_snakes/Paper_figs.Rmd
I adding a new plot

@@
 library(patchwork)
+library(RColorBrewer)
 ```
@@
   xlab(x_label) + ylab(y_label)+
-geom_boxplot(aes(x=factor(sim), y=as.numeric(value), fill=factor(name), alpha = rect_type_a))+ #, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
+geom_boxplot(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(value), fill=factor(name), alpha = rect_type_a))+ #, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
   #geom_rect(aes(xmin = as.numeric(xmin), xmax = as.numeric(xmax), ymin = -Inf, ymax = Inf, fill = rect_type)) +
@@
     labs(fill = " ")+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      title =element_text(size=8, face='bold'))
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
+                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+
+  return(plot)
+}
+
+both_coevo_slope_flat_map <- function(file, title, subt, x_label, y_label){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+file$snake_GA <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+file$newt_GA <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
+file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
+#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
+#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)
+
+#file_long <- tidyr::pivot_longer(file, c(newt_pheno_change, snake_pheno_change))
+cols <- brewer.pal(11, "RdBu")
+fornewt <- cols[1:4]
+forsnake <- cols[8:11]
+
+plot1 <-   ggplot(file) +
+  labs(subtitle = "Snake")+
+  geom_boxplot(aes(x=factor(snake_GA), y=snake_pheno_change, fill=newt_GA))+
+  ylab(y_label) + 
+  xlab("Snake GA")+
+  ylim(0,6)+
+ scale_x_discrete(labels=c("1e-08_0.005" = "GA 1", "1e-09_0.05" = "GA 2", "1e-10_0.5" = "GA 3",
+                             "1e-11_5" = "GA 4"))+
+     theme(plot.title = element_text(size=5)) +
+  #scale_fill_discrete(fornewt, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+  scale_fill_manual(values = rev(fornewt), labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+   #scale_fill_brewer(fornewt , labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+  #scale_alpha(guide = 'none')+
+    #labs(fill = " ")+
+  guides(fill=guide_legend(title="Newt GA"))+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
+                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+
+plot2 <-   ggplot(file) +
+ labs(subtitle = "Newt")+
+  geom_boxplot(aes(x=factor(newt_GA), y=newt_pheno_change, fill=snake_GA))+
+  ylab(" ")+ 
+  xlab("Newt GA")+
+  ylim(0,6)+
+ scale_x_discrete(labels=c("1e-08_0.005" = "GA 1", "1e-09_0.05" = "GA 2", "1e-10_0.5" = "GA 3",
+                             "1e-11_5" = "GA 4"))+
+     theme(plot.title = element_text(size=5)) +
+  #scale_fill_discrete(labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+  #scale_fill_brewer(forsnake)+
+  scale_fill_manual(values = forsnake, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+  #scale_alpha(guide = 'none')+
+    #labs(fill = " ")+
+  guides(fill=guide_legend(title="Snake GA"))+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
+                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+
+leg <- get_legend(plot1)
+legp1 <- as_ggplot(leg)
+leg2 <- get_legend(plot2)
+legp2 <- as_ggplot(leg2)
+
+myplot = ggarrange(plot1+theme(legend.position = "none"), (plot2+theme(legend.position = "none")), arrangeGrob(legp1, legp2, nrow = 2), ncol = 3) + plot_annotation(title = title) & theme(title = element_text( size=18,face = 'bold')) #top=grid::textGrob("title"))
+
+  return(myplot)
+}
+
+newt_coevo_slope_flat_map <- function(file, title, subt, x_label, y_label){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+file$snake_GA <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+file$newt_GA <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
+#file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
+#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
+#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)
+
+#file_long <- tidyr::pivot_longer(file, c(newt_pheno_change, snake_pheno_change))
+
+plot <-   ggplot(file) +
+  ggtitle(title, subtitle = subt)+
+  geom_boxplot(aes(x=factor(newt_GA), y=newt_pheno_change, fill=snake_GA))+
+  xlab(x_label) + ylab(y_label)+
+
+     theme(plot.title = element_text(size=5)) +
+  #scale_alpha(guide = 'none')+
+    #labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
+                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
 
@@
 labels = c("Snake", "Newt"))+
-    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
-                      title =element_text(size=8, face='bold'))
+    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
+                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
   return(plot)
@@
 title = "Phenotype Change Coevolution FLat Map"
-boxplot_coevo_slope_flat_map(file3, title, subt, x_label, y_label)
+boxplot_coevo_slope_flat_map(file3, title, subt, x_label, y_label) #coevo_boxplot =
+#ggsave("coevo_boxplot.png", plot=coevo_boxplot, height=10, width=15, units=c("in"), dpi=600)
 
@@
 boxplot_coevo_popsize_flat_map(file3, title, subt, x_label, y_label)
+
+title = "Phenotype Change vs Snake GA, FLat Map"
+y_label= "Phenotype Change"
+x_label = "Snake GA"
+both_coevo_slope_flat_map(file3, title, subt, x_label, y_label)
 
@@
 y_label= "Phenotype"
-fast_slow_no_coevolution(file, choices, min_gen, max_gen, title, subt, x_label, y_label)
+#png("image.png", width = 1600, height = 1200)
+p1=fast_slow_no_coevolution(file, choices, min_gen, max_gen, title, subt, x_label, y_label)
+ggsave("three_speeds_of_coevolution.png", plot=p1, height=10, width=10, units=c("in"), dpi=600)
+
+#dev.off()
 ```

### 2023-06-01 graphs_newt_snakes/Paper_figs.Rmd
I have updated some figures

@@
 
+#smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
 file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map"))
@@
 
+point_coevo_start_stop_flat_map <- function(file, title, subt, x_label, y_label){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
+file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
+#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
+#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)
+
+newt_adv= c("D", "C", "B", "H", "G", "L")
+mid= c("A", "F", "K", "P")
+snake_adv = c("E", "I", "J", "M", "N", "O")
+
+file$coevo_score = 0
+
+file$coevo_score[file$sim %in% newt_adv] = "Newt Advantage"
+file$coevo_score[file$sim %in% mid] = "No Advantage"
+file$coevo_score[file$sim %in% snake_adv] = "Snake Advantage"
+file$newt_snake_pheno_avg= (file$newt_pheno_change+file$snake_pheno_change)/2
+
+plot1 <-   ggplot(file) +
+  labs(subtitle = "Start")+
+  xlab(x_label) + ylab(y_label)+
+  ylim(0,10)+
+  geom_point(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(N_pheno_start)), color="darkred")+
+
+    geom_point(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(S_pheno_start)), color="steelblue")+
+
+     theme(plot.title = element_text(size=5)) +
+    labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
+                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+
+plot2 <-   ggplot(file) +
+  labs(subtitle = "End")+
+  xlab(x_label) + ylab(y_label)+
+  ylim(0,10)+
+  geom_point(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(N_pheno_end)), color="darkred")+
+
+  geom_point(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(S_pheno_end)), color="steelblue")+
+
+     theme(plot.title = element_text(size=5)) +
+    labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
+                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+
+myplot = ggarrange(plot1, plot2, ncol = 2) + plot_annotation(title = title) & theme(title = element_text( size=18,face = 'bold')) #top=grid::textGrob("title"))
+
+  return(myplot)
+}
+
 both_coevo_slope_flat_map <- function(file, title, subt, x_label, y_label){
@@
 plot1 <-   ggplot(file) +
-  labs(subtitle = "Snake")+
+  labs(subtitle = "Snake Phenotype Change")+
   geom_boxplot(aes(x=factor(snake_GA), y=snake_pheno_change, fill=newt_GA))+
@@
   ylim(0,6)+
- scale_x_discrete(labels=c("1e-08_0.005" = "GA 1", "1e-09_0.05" = "GA 2", "1e-10_0.5" = "GA 3",
-                             "1e-11_5" = "GA 4"))+
+ scale_x_discrete(labels=c("1e-08_0.005" = "1", "1e-09_0.05" = "2", "1e-10_0.5" = "3",
+                             "1e-11_5" = "4"))+
      theme(plot.title = element_text(size=5)) +
   #scale_fill_discrete(fornewt, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
-  scale_fill_manual(values = rev(fornewt), labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+  scale_fill_manual(values = rev(fornewt), labels=c('1', '2', '3', '4'))+
    #scale_fill_brewer(fornewt , labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
@@
   guides(fill=guide_legend(title="Newt GA"))+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
-                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), 
+                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16))
 
 plot2 <-   ggplot(file) +
- labs(subtitle = "Newt")+
+ labs(subtitle = "Newt Phenotype Change")+
   geom_boxplot(aes(x=factor(newt_GA), y=newt_pheno_change, fill=snake_GA))+
@@
   ylim(0,6)+
- scale_x_discrete(labels=c("1e-08_0.005" = "GA 1", "1e-09_0.05" = "GA 2", "1e-10_0.5" = "GA 3",
-                             "1e-11_5" = "GA 4"))+
+ scale_x_discrete(labels=c("1e-08_0.005" = "1", "1e-09_0.05" = "2", "1e-10_0.5" = "3",
+                             "1e-11_5" = "4"))+
      theme(plot.title = element_text(size=5)) +
@@
   #scale_fill_brewer(forsnake)+
-  scale_fill_manual(values = forsnake, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+  scale_fill_manual(values = forsnake, labels=c('1', '2', '3', '4'))+
   #scale_alpha(guide = 'none')+
@@
   guides(fill=guide_legend(title="Snake GA"))+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
-                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), 
+                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16))
 
@@
 
-file$coevo_speed[file$sim %in% choices[1]] = "Fast Coevolution"
-file$coevo_speed[file$sim %in% choices[2]] = "Slow Coevolution"
-file$coevo_speed[file$sim %in% choices[3]] = "No Coevolution"
-file$coevo_speed = factor(file$coevo_speed, levels=c("Fast Coevolution", "Slow Coevolution", "No Coevolution"))
+file$coevo_speed[file$sim %in% choices[1]] = "Fast Evolution"
+file$coevo_speed[file$sim %in% choices[2]] = "Slow Evolution"
+file$coevo_speed[file$sim %in% choices[3]] = "No Evolution"
+file$coevo_speed = factor(file$coevo_speed, levels=c("Fast Evolution", "Slow Evolution", "No Evolution"))
 plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==0),]) +
@@
 #ggsave("coevo_boxplot.png", plot=coevo_boxplot, height=10, width=15, units=c("in"), dpi=600)
+
+title = "Phenotype Start and Stop Coevolution FLat Map"
+point_coevo_start_stop_flat_map(file3, title, subt, x_label, y_label)
 

### 2023-08-08 graphs_newt_snakes/Paper_figs.Rmd
improving the figures for the paper

@@
 
+main_grid_plot<- function(file_name, spegen, file, type, row_num, col_num){
+
+file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
+
+GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
+GA1_type = paste0("generation|", type)
+
+GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
+GA1_type <- GA1_type[-1]
+
+data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
+data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)
+
+data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)
+
+data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))
+
+main_plot<-ggplot(data_long_type_comp, aes(x = x_loc, y = y_loc))+
+  geom_tile(aes(fill = as.numeric(measurement)))+
+  facet_wrap(~species)+
+  coord_fixed() +
+  theme_bw()+
+  #margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")+
+  theme( legend.justification = "top", 
+         plot.margin = margin(t = 0.3,  # Top margin
+                             r = 0,  # Right margin
+                             b = 0.3,  # Bottom margin
+                             l = 0,  # Left margin
+                             unit = "cm")  ) # legend.position ="bottom"
+#plot.margin = unit(c(1, 1, 3, 1), "cm"),
+if(type != "num_ind"){
+  main_plot<- main_plot + labs(title = paste0(str_to_title(type),"Local Mean Phenotypes"),
+                               subtitle = paste0("Simulation: ", file_name, ", Generation: ", spegen),
+                               fill = "Toxicity/Resistance")+
+    scale_fill_viridis_c()
+}
+if(type == "num_ind"){
+  main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
+                               subtitle = paste0(file_name, ", Generation: ", spegen),
+                               fill = "Newt/Snake PopSize")+
+    scale_fill_viridis_c(option = "plasma")
+}
+
+snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
+newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
+newt$snake_value <- snake$measurement
+print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))
+
+newt$info <- "middle"
+
+#need to look into, coloring problem
+newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"
+
+newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"
+
+return(main_plot)}
+
 file=move_together_grid
@@
 duo_grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+grid_example = main_grid_plot(file_name, spegen, file, type, row_num, col_num)
+
+ggsave("grid_example.png", plot=grid_example, height=7, width=5, units=c("in"), dpi=600)
 
@@
   plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
-  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "th generation to ", max_gen, "th generation"))+
   xlab(x_label) + ylab(y_label)+
@@
     labs(fill = " ")+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      title =element_text(size=8, face='bold'))
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
+                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
 
@@
 
-boxplot_cors_by_gen_col_rep(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen)
+boxplot_cors_by_gen_col_rep = boxplot_cors_by_gen_col_rep(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen)
+
+ggsave("three_correlation.png", plot=boxplot_cors_by_gen_col_rep, height=7, width=11, units=c("in"), dpi=600)
+
 boxplot_cors_by_gen_col_rep_6_file(file1, file2, file3, file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen)
@@
   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), 
-                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16))
+                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16), aspect.ratio = 1)
 
@@
   return(myplot)
+}
+
+coevo_slope_flat_map_snake_change <- function(file, title, subt, x_label, y_label){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+file$snake_GA <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+file$newt_GA <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
+file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
+#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
+#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)
+
+#file_long <- tidyr::pivot_longer(file, c(newt_pheno_change, snake_pheno_change))
+cols <- brewer.pal(11, "RdBu")
+fornewt <- cols[1:4]
+forsnake <- cols[8:11]
+
+plot1 <-   ggplot(file) +
+  labs(subtitle = "Snake Phenotype Change")+
+  geom_boxplot(aes(x=factor(snake_GA), y=snake_pheno_change, fill=newt_GA))+
+  ylab(y_label) + 
+  xlab("Snake Genetic Architecture")+
+  ylim(0,6)+
+ scale_x_discrete(labels=c("1e-08_0.005" = "1", "1e-09_0.05" = "2", "1e-10_0.5" = "3",
+                             "1e-11_5" = "4"))+
+     theme(plot.title = element_text(size=5)) +
+  #scale_fill_discrete(fornewt, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+  scale_fill_manual(values = rev(fornewt), labels=c('1', '2', '3', '4'))+
+   #scale_fill_brewer(fornewt , labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+  #scale_alpha(guide = 'none')+
+    #labs(fill = " ")+
+  guides(fill=guide_legend(title="Newt GA"))+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), 
+                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16), aspect.ratio = 1)
+
+  return(plot1)
+}
+
+coevo_slope_flat_map_newt_change <- function(file, title, subt, x_label, y_label){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+
+file$snake_GA <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+file$newt_GA <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
+file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
+#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
+#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)
+
+#file_long <- tidyr::pivot_longer(file, c(newt_pheno_change, snake_pheno_change))
+cols <- brewer.pal(11, "RdBu")
+fornewt <- cols[1:4]
+forsnake <- cols[8:11]
+
+plot2 <-   ggplot(file) +
+ labs(subtitle = "Newt Phenotype Change")+
+  geom_boxplot(aes(x=factor(newt_GA), y=newt_pheno_change, fill=snake_GA))+
+  ylab(" ")+ 
+  xlab("Newt Genetic Architecture")+
+  ylim(0,6)+
+ scale_x_discrete(labels=c("1e-08_0.005" = "1", "1e-09_0.05" = "2", "1e-10_0.5" = "3",
+                             "1e-11_5" = "4"))+
+     theme(plot.title = element_text(size=5)) +
+  #scale_fill_discrete(labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
+  #scale_fill_brewer(forsnake)+
+  scale_fill_manual(values = forsnake, labels=c('1', '2', '3', '4'))+
+  #scale_alpha(guide = 'none')+
+    #labs(fill = " ")+
+  guides(fill=guide_legend(title="Snake GA"))+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), 
+                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16), aspect.ratio = 1)
+
+  return(plot2)
 }
@@
 
-boxplot_coevo_slope_small_exp_color <- function(file1, file2, file3, title, subt, x_label, y_label){
+boxplot_coevo_slope_small_exp_color <- function(file1, file2, file3, title, x_label, y_label){
 
@@
   plot <-  ggplot(file) +
-  ggtitle(title, subtitle = subt)+
+  ggtitle(title)+
   xlab(x_label) + ylab(y_label)+
@@
     labs(fill = " ")+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
-                      title =element_text(size=8, face='bold'))
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
+                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+
+    #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),title =element_text(size=8, face='bold'))
 
@@
     facet_wrap(~coevo_speed, ncol=1)+
-    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "th generation to ", max_gen, "th generation")) +
     geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+#group=rep
@@
 
-title = "Whole Simulation Phenotype Change"
+title = "Total Phenotype Change"
 subt = "Three Experiments"
-x_label = "SIM"
+x_label = "Simulation"
 y_label = "Change in Phenotype"
@@
 
-boxplot_coevo_slope_small_exp_color(file1, file2, file3, title, subt, x_label, y_label)
+three_experiments = boxplot_coevo_slope_small_exp_color(file1, file2, file3, title, x_label, y_label)
+ggsave("three_experiments.png", plot=three_experiments, height=7, width=10, units=c("in"), dpi=600)
 
@@
 
-title = "Phenotype Change vs Snake GA, FLat Map"
+title = "Phenotype Change, FLat Map"
 y_label= "Phenotype Change"
 x_label = "Snake GA"
-both_coevo_slope_flat_map(file3, title, subt, x_label, y_label)
+coevo_boxplot=both_coevo_slope_flat_map(file3, title, subt, x_label, y_label)
+ggsave("coevo_pheno_change_boxplot.png", plot=coevo_boxplot, height=10, width=15, units=c("in"), dpi=600)
+
+title = "Phenotype Change, FLat Map"
+y_label= "Phenotype Change"
+x_label = "Newt GA"
+coevo_boxplo_newt=coevo_slope_flat_map_newt_change(file3, title, subt, x_label, y_label)
+ggsave("coevo_boxplo_newt.png", plot=coevo_boxplo_newt, height=4, width=6, units=c("in"), dpi=600)
+
+title = "Phenotype Change, FLat Map"
+y_label= "Phenotype Change"
+x_label = "Snake GA"
+coevo_boxplo_snake=coevo_slope_flat_map_snake_change(file3, title, subt, x_label, y_label)
+ggsave("coevo_boxplo_snake.png", plot=coevo_boxplo_snake, height=4, width=6, units=c("in"), dpi=600)
 
@@
 x_label="Genetic Architectures (red=newt, blue=snake)"
-ggplot(GA_stage_long) +
+coevo_speed = ggplot(GA_stage_long) +
   ggtitle(title, subtitle = paste0(subt))+
@@
 
+ggsave("coevo_speed.png", plot=coevo_speed, height=7, width=10, units=c("in"), dpi=600)
+
 title = "Coevolution Phenotype Change"

### 2023-08-08 graphs_newt_snakes/same_start.Rmd
improving the figures for the paper

--- 2023-03-14 graphs_newt_snakes/move_together.Rmd
@@
 ---
-title: "Moving Together"
+title: "Same Start"
 output: html_document
-date: '2023-01-10'
+date: '2023-06-02'
 ---
@@
 
-Start populations in the lower third of the simulation and let them move as they co-evolve.
-It is possible that as newts and snakes move into new territory they might create more spatial phenotype correlation.
+Start all simultions off with the same msprime paramiters to see if the final results change. My prediction is that they will not.
 
@@
 
-What does it mean to be correlated? Might this occur if I simulate some semi-controlled movement?
+What does it mean to be correlated?
 
@@
 thepath=/Users/victoria/Desktop/
-foldername=move_together
+foldername=same_start
 thefolder=${thepath}${foldername}/*
@@
 
-move_together_lit<- read.csv("~/Desktop/move_together/all_lit.txt" , header = TRUE)
-
-move_together_lit$group_rep <- paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd, "_", move_together_lit$rep)
-
-move_together_lit$group <- paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd)
-
-move_together_lit$sim=LETTERS[factor(move_together_lit$group)]
-move_together_lit$dif <- move_together_lit$Snake_mean_Pheno-move_together_lit$Newt_mean_Pheno
-
-move_together_cor<- read.csv("~/Desktop/move_together/all_cor.txt" , header = TRUE)
-move_together_cor$group_rep <- paste0(move_together_cor$snake_mu_rate, "_", move_together_cor$snake_mu_effect_sd,"_",move_together_cor$newt_mu_rate, "_", move_together_cor$newt_mu_effect_sd, "_", move_together_cor$rep)
-move_together_cor$group <- paste0(move_together_cor$snake_mu_rate, "_", move_together_cor$snake_mu_effect_sd,"_",move_together_cor$newt_mu_rate, "_", move_together_cor$newt_mu_effect_sd)
-move_together_cor$sim=LETTERS[factor(move_together_cor$group)]
+same_start_lit<- read.csv("~/Desktop/same_start/all_lit.txt" , header = TRUE)
+
+same_start_lit$group_rep <- paste0(same_start_lit$snake_mu_rate, "_", same_start_lit$snake_mu_effect_sd,"_",same_start_lit$newt_mu_rate, "_", same_start_lit$newt_mu_effect_sd, "_", same_start_lit$rep)
+
+same_start_lit$group <- paste0(same_start_lit$snake_mu_rate, "_", same_start_lit$snake_mu_effect_sd,"_",same_start_lit$newt_mu_rate, "_", same_start_lit$newt_mu_effect_sd)
+
+same_start_lit$sim=LETTERS[factor(same_start_lit$group)]
+same_start_lit$dif <- same_start_lit$Snake_mean_Pheno-same_start_lit$Newt_mean_Pheno
+
+same_start_cor<- read.csv("~/Desktop/same_start/all_cor.txt" , header = TRUE)
+same_start_cor$group_rep <- paste0(same_start_cor$snake_mu_rate, "_", same_start_cor$snake_mu_effect_sd,"_",same_start_cor$newt_mu_rate, "_", same_start_cor$newt_mu_effect_sd, "_", same_start_cor$rep)
+same_start_cor$group <- paste0(same_start_cor$snake_mu_rate, "_", same_start_cor$snake_mu_effect_sd,"_",same_start_cor$newt_mu_rate, "_", same_start_cor$newt_mu_effect_sd)
+same_start_cor$sim=LETTERS[factor(same_start_cor$group)]
 
@@
 cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
-#file=move_together_lit
-#cfile=move_together_cor 
+#file=same_start_lit
+#cfile=same_start_cor 
  # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
@@
 two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
-  #file=move_together_lit
+  #file=same_start_lit
   file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
@@
 
-#two_hist_death_all_rep(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
+#two_hist_death_all_rep(same_start_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)
 
@@
 ```{r, graphing by gen}
-trends_by_gen(move_together_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
-
-#aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$dif, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$group_rep), FUN=mean)
+trends_by_gen(same_start_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)
+
+#aggregate(same_start_lit[which(same_start_lit$generation>=100 & same_start_lit$generation<=50000),]$dif, list(same_start_lit[which(same_start_lit$generation>=100 & same_start_lit$generation<=50000),]$group_rep), FUN=mean)
 
@@
 ```{r, average difference}
-aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$dif, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$group), FUN=mean)
+aggregate(same_start_lit[which(same_start_lit$generation>=100 & same_start_lit$generation<=50000),]$dif, list(same_start_lit[which(same_start_lit$generation>=100 & same_start_lit$generation<=50000),]$group), FUN=mean)
 ```
@@
 
-whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
+whale_gen(same_start_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
 ```
@@
 
-suppressMessages(print(two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
-
-#suppressMessages(print(two_hist_all_rep(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
+suppressMessages(print(two_hist(same_start_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))
+
+#suppressMessages(print(two_hist_all_rep(same_start_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))
 
@@
 
-boxplot_cors_by_gen(move_together_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
-
-#four_types_boxplot_cors_by_gen(move_together_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+boxplot_cors_by_gen(same_start_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
+
+#four_types_boxplot_cors_by_gen(same_start_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
 
@@
 ginmax = 5000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 10000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 15000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 20000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 25000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 30000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 35000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 40000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 45000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ginmax = 50000
-suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
+suppressMessages(print(hist_cors_by_gen_col_rep(same_start_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
 ```
@@
 ```{r, GA1 cor and pheno}
-GA1_pattern <- unique(paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd, "_", move_together_lit$rep))
+GA1_pattern <- unique(paste0(same_start_lit$snake_mu_rate, "_", same_start_lit$snake_mu_effect_sd,"_",same_start_lit$newt_mu_rate, "_", same_start_lit$newt_mu_effect_sd, "_", same_start_lit$rep))
 
@@
 # for(i in myrandomlist){
-#   myine<-cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
+#   myine<-cor_trends_by_gen(same_start_lit, same_start_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
 #   plot(myine)
@@
 
-cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
+cor_trends_by_gen(same_start_lit, same_start_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])
 
@@
 
-cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
+cor_trends_by_gen(same_start_lit, same_start_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
 ```
@@
 
-cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
+cor_trends_by_gen(same_start_lit, same_start_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
 ```
@@
 
-# for(i in 1:length(unique(move_together_lit$rep))){
-#   myine<-whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i])
+# for(i in 1:length(unique(same_start_lit$rep))){
+#   myine<-whale_gen(same_start_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(same_start_lit$rep)[i])
 #   plot(myine)
@@
 # }
-whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1])
+whale_gen(same_start_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(same_start_lit$rep)[1])
 ```
@@
 
-# for(i in 1:length(unique(move_together_lit$rep))){
-#   myine<-two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i] )
+# for(i in 1:length(unique(same_start_lit$rep))){
+#   myine<-two_hist(same_start_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(same_start_lit$rep)[i] )
 #   suppressMessages(plot(myine))
@@
 
-two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1] )
+two_hist(same_start_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(same_start_lit$rep)[1] )
 
@@
 max_gen=5000
-GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(same_start_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(same_start_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 ```
@@
 # summary
-GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
+GA_summary(same_start_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
 
@@
 
-GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(same_start_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 ```
@@
 
-GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(same_start_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 max_gen=50000
-GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
+GA_summary(same_start_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
 
@@
 
-GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
+GA_summary_by_species(same_start_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")
 
@@
 
-GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
+GA_summary_by_species(same_start_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")
 
@@
 #heatmap
-build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(same_start_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 ```
@@
 #heatmap
-build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
+build_heatmap(same_start_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
 
@@
 max_gen=5000
-build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(same_start_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(same_start_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 ```
@@
 
-build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
+build_heatmap(same_start_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
 
@@
 require(readr)
-move_together_grid<- read.csv("~/Desktop/move_together/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
-move_together_grid$group_rep <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd, "_", move_together_grid$rep)
-move_together_grid$group <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd)
-move_together_grid$sim=LETTERS[factor(move_together_grid$group)]
-move_together_grid$grid_num = 5
+same_start_grid<- read.csv("~/Desktop/same_start/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
+same_start_grid$group_rep <- paste0(same_start_grid$snake_mu_rate, "_", same_start_grid$snake_mu_effect_sd,"_",same_start_grid$newt_mu_rate, "_", same_start_grid$newt_mu_effect_sd, "_", same_start_grid$rep)
+same_start_grid$group <- paste0(same_start_grid$snake_mu_rate, "_", same_start_grid$snake_mu_effect_sd,"_",same_start_grid$newt_mu_rate, "_", same_start_grid$newt_mu_effect_sd)
+same_start_grid$sim=LETTERS[factor(same_start_grid$group)]
+same_start_grid$grid_num = 5
 
@@
 
-file=move_together_grid
+file=same_start_grid
 file_name="1e-11_5_1e-10_0.5_0"
@@
 require(readr)
-move_together_grid<- read.csv("~/Desktop/move_together/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
-move_together_grid$group_rep <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd, "_", move_together_grid$rep)
-move_together_grid$group <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd)
-move_together_grid$sim=LETTERS[factor(move_together_grid$group)]
-move_together_grid$grid_num = 5
+same_start_grid<- read.csv("~/Desktop/same_start/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
+same_start_grid$group_rep <- paste0(same_start_grid$snake_mu_rate, "_", same_start_grid$snake_mu_effect_sd,"_",same_start_grid$newt_mu_rate, "_", same_start_grid$newt_mu_effect_sd, "_", same_start_grid$rep)
+same_start_grid$group <- paste0(same_start_grid$snake_mu_rate, "_", same_start_grid$snake_mu_effect_sd,"_",same_start_grid$newt_mu_rate, "_", same_start_grid$newt_mu_effect_sd)
+same_start_grid$sim=LETTERS[factor(same_start_grid$group)]
+same_start_grid$grid_num = 5
 

### 2023-09-22 graphs_newt_snakes/Paper_figs.Rmd
I am making the figures better

@@
 library(RColorBrewer)
+library(scales)
 ```
@@
   facet_wrap(~species)+
+  xlab("Eastings") +
+  ylab("Northings") +
   coord_fixed() +
@@
 if(type != "num_ind"){
-  main_plot<- main_plot + labs(title = paste0(str_to_title(type),"Local Mean Phenotypes"),
-                               subtitle = paste0("Simulation: ", file_name, ", Generation: ", spegen),
+  main_plot<- main_plot + labs(title = "Local Mean Phenotypes",
+                               #subtitle = paste0("Simulation: ", file_name, ", Generation: ", spegen),
                                fill = "Toxicity/Resistance")+
@@
   facet_wrap(~exp, ncol=1)+
-  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutatinal Variance', 'Coevolution'))+
+  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutational Variance', 'Coevolution'))+
     labs(fill = " ")+
@@
   facet_wrap(~exp, ncol=2)+
-  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutatinal Variance', 'Coevolution'))+
+  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutational Variance', 'Coevolution'))+
     labs(fill = " ")+
@@
 file6 = newt_change_cor
-title = "Spatial Phenotype Correlation Across Different Simulation Conditions"
+title = "Spatial Phenotype Correlation"
 subt = " "
@@
 x_label = "Simulations"
-y_label = "Spatila Correlation"
+y_label = "Spatial Correlation"
 min_gen = 40000
@@
   ylim(0,6)+
- scale_x_discrete(labels=c("1e-08_0.005" = "1", "1e-09_0.05" = "2", "1e-10_0.5" = "3",
-                             "1e-11_5" = "4"))+
+ scale_x_discrete(labels=c("1e-08_0.005" = "1a", "1e-09_0.05" = "2a", "1e-10_0.5" = "3a",
+                             "1e-11_5" = "4a"))+
      theme(plot.title = element_text(size=5)) +
   #scale_fill_discrete(fornewt, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
-  scale_fill_manual(values = rev(fornewt), labels=c('1', '2', '3', '4'))+
+  scale_fill_manual(values = rev(fornewt), labels=c('1a', '2a', '3a', '4a'))+
    #scale_fill_brewer(fornewt , labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
@@
   guides(fill=guide_legend(title="Newt GA"))+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), 
-                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16), aspect.ratio = 1)
+  theme_bw() +  theme(title =element_text(size=18, face='bold'), legend.text=element_text(size=18), strip.text.x = element_text(size = 18), aspect.ratio = 1)#axis.text.x = element_text(angle = 45, hjust=1, size = 14),
 
@@
   geom_boxplot(aes(x=factor(newt_GA), y=newt_pheno_change, fill=snake_GA))+
-  ylab(" ")+ 
+  ylab("Phenotype Change")+ 
   xlab("Newt Genetic Architecture")+
   ylim(0,6)+
- scale_x_discrete(labels=c("1e-08_0.005" = "1", "1e-09_0.05" = "2", "1e-10_0.5" = "3",
-                             "1e-11_5" = "4"))+
+ scale_x_discrete(labels=c("1e-08_0.005" = "1a", "1e-09_0.05" = "2a", "1e-10_0.5" = "3a",
+                             "1e-11_5" = "4a"))+
      theme(plot.title = element_text(size=5)) +
@@
   #scale_fill_brewer(forsnake)+
-  scale_fill_manual(values = forsnake, labels=c('1', '2', '3', '4'))+
+  scale_fill_manual(values = forsnake, labels=c('1a', '2a', '3a', '4a'))+
   #scale_alpha(guide = 'none')+
@@
   guides(fill=guide_legend(title="Snake GA"))+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), 
-                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16), aspect.ratio = 1)
+  theme_bw() +  theme(title =element_text(size=18, face='bold'), legend.text=element_text(size=18), strip.text.x = element_text(size = 18), aspect.ratio = 1) #axis.text.x = element_text(angle = 45, hjust=1, size = 14),
 
@@
   #xlim(-1.1, 1.1)+
-  scale_fill_manual(values =c("darkolivegreen1", "azure2", "darkorange3"), labels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))+
+  scale_fill_manual(values =c("darkolivegreen1", "azure2", "darkorange3"), labels=c("No Interaction", "No Heritability", "Standard Simulation"))+
     labs(fill = " ")+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
-                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+  theme_bw() +  theme(title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20)) #axis.text.x = element_text(angle = 45, hjust=1, size = 18),
 
@@
 x_label="Genetic Architectures (red=newt, blue=snake)"
-coevo_speed = ggplot(GA_stage_long) +
+
+coevo_speed = 
+  ggplot(GA_stage_long) +
   ggtitle(title, subtitle = paste0(subt))+
-  coord_trans(y = "log10")+
+  #coord_trans(y = "log10")+
+  #scale_y_log10()+
+  #scale_y_continuous(trans = "log10")+
+  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
+              labels = trans_format("log10", math_format(10^.x))) +
   xlab(x_label) + ylab(y_label)+

### 2023-09-27 graphs_newt_snakes/Paper_figs.Rmd
made some fig improvements

@@
   theme(plot.title = element_text(size=5)) +
+    scale_x_discrete(breaks=c('Sims',"F","G","H", "J", "K", "L", "N", "O", "P"), labels=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")) + 
+  #  level=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")+
   #xlim(-1.1, 1.1)+
@@
 exp_labeles=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map")
-x_label = "Simulations"
+x_label = "Newt/Snake Genetic Architecture"
 y_label = "Spatial Correlation"
@@
   scale_fill_manual(values =c("darkolivegreen1", "azure2", "darkorange3"), labels=c("No Interaction", "No Heritability", "Standard Simulation"))+
+    scale_x_discrete(breaks=c("F","G","H", "J", "K", "L", "N", "O", "P"), labels=c("2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")) + # label newt/snake
     labs(fill = " ")+
@@
 subt = "Three Experiments"
-x_label = "Simulation"
+x_label = "Simulation Genetic Architecture"
 y_label = "Change in Phenotype"
@@
 ```{r, plotting all of the changes}
-title = "Coevolution Slope (Phenotype Change/ Time)"
+title = "Coevolution Slope"
 subt = "Simulation F, J, G, K"
 GA_stage_long <- tidyr::pivot_longer(GA_stage, c(newt_coevo_slope, snake_coevo_slope))
-y_label="Coevolution Speed"
+y_label="Coevolution Speed (Phenotype Change/ Time)"
 x_label="Genetic Architectures (red=newt, blue=snake)"

### 2023-10-31 graphs_newt_snakes/Paper_figs.Rmd
making more plots

@@
     labs(fill = " ")+
-  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
-                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+  #theme(axis.text.x = element_text(angle = 45, hjust=1))
+
+  return(plot)
+}
+
+boxplot_cors_by_gen_col_rep_other3 <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){
+ snewt$mean_res = snewt$mean_toxin+snewt$dif
+  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
+   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
+   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
+file <- rbind(file1, file2, file3)
+
+file$sim <- str_replace_all(file$sim, "[ABCDEIM]", 'Sims')
+#c("A"='Low Mu Var', "B"='Low Mu Var', "C"='Low Mu Var', "D"='Low Mu Var', "E"='Low Mu Var', "I"='Low Mu Var', "M"='Low Mu Var'))
+
+file$cor_score <- ifelse(file$sim == "Sims", "False","True")
+
+#file$cor_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
+
+#smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
+file$exp = factor(file$exp, levels=c("Cost Gradent Map No Interaction", "Snake Gradent Map", "Newt Gradent Map"))
+
+  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "th generation to ", max_gen, "th generation"))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=factor(sim, level=c('Sims', "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
+  theme(plot.title = element_text(size=5)) +
+    scale_x_discrete(breaks=c('Sims',"F","G","H", "J", "K", "L", "N", "O", "P"), labels=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")) + 
+  #  level=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")+
+  #xlim(-1.1, 1.1)+
+    geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
+  facet_wrap(~exp, ncol=1)+
+  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutational Variance', 'Coevolution'))+
+    labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
+  #theme(axis.text.x = element_text(angle = 45, hjust=1))
 
@@
 
+boxplot_cors_by_gen_col_rep_other3 = boxplot_cors_by_gen_col_rep_other3(file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen)
+
+ggsave("three_correlation_app.png", plot=boxplot_cors_by_gen_col_rep_other3, height=7, width=11, units=c("in"), dpi=600)
+
 boxplot_cors_by_gen_col_rep_6_file(file1, file2, file3, file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen)
@@
 ```
+
+```{r, looking at the realtionship between pop size and phenotype}
+
+whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, letter){
+  #file$rep==rep
+  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
+  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+  file$sim_snake_name = NA
+  file$sim_newt_name = NA
+  #file$sim == "A" | "B" | "C" | "D"
+  file[which(file$sim  == "A" | file$sim  == "B" | file$sim  == "C" | file$sim  == "D"), ]$sim_snake_name = paste0("1",letter)
+  file[which(file$sim  == "E" | file$sim  == "F" | file$sim  == "G" | file$sim  == "H"), ]$sim_snake_name = paste0("2",letter)
+  file[which(file$sim  == "I" | file$sim  == "J" | file$sim  == "K" | file$sim  == "L"), ]$sim_snake_name = paste0("3",letter)
+  file[which(file$sim  == "M" | file$sim  == "N" | file$sim  == "O" | file$sim  == "P"), ]$sim_snake_name =  paste0("4",letter)
+
+  file[which(file$sim  == "A" | file$sim  == "E" | file$sim  == "I" | file$sim  == "M"), ]$sim_newt_name =  paste0("1",letter)
+  file[which(file$sim  == "B" | file$sim  == "F" | file$sim  == "J" | file$sim  == "N"), ]$sim_newt_name =  paste0("2",letter)
+  file[which(file$sim  == "C" | file$sim  == "G" | file$sim  == "K" | file$sim  == "O"), ]$sim_newt_name = paste0("3",letter)
+  file[which(file$sim  == "D" | file$sim  == "H" | file$sim  == "L" | file$sim  == "P"), ]$sim_newt_name =  paste0("4",letter)
+  file$sim_name = paste0("S:", file$sim_snake_name,"/N:", file$sim_newt_name)
+
+dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
+  #xlim(0, 1000)+
+  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
+  xlab(x_label) + ylab(y_label)+
+  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif, shape=factor(rep)))+
+  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
+  theme(plot.title = element_text(size=5)) +
+  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred", name = "Phenotype Difference (S-N)")+
+  scale_shape_discrete(name="Simulation Rep")+
+  #labs(colour = color_label) +
+  facet_wrap(~fct_reorder(sim_name, sim))+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      # strip.background = element_blank(), 
+                      # strip.text.x = element_blank(), 
+                      # panel.grid.major = element_blank(), 
+                      # panel.grid.minor = element_blank(),
+                      # panel.background = element_blank(), 
+                      axis.line = element_line(colour = "black"))
+
+return(dif)
+
+}
+
+min_gen=5000
+max_gen=10000
+letter="a"
+wg1 = whale_gen(GA1_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt="Experiment 1", y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+ggsave("Early_Popsize_vs_pheno.png", plot=wg1, height=10, width=10, units=c("in"), dpi=600)
+wg1
+
+min_gen=45000
+max_gen=50000
+wg2 = whale_gen(GA1_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt="Experiment 1", y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+ggsave("Late_Popsize_vs_pheno.png", plot=wg2, height=10, width=10, units=c("in"), dpi=600)
+wg2
+
+min_gen=5000
+max_gen=10000
+letter="b"
+whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt="Experiment 2", y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+min_gen=45000
+max_gen=50000
+whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt="Experiment 2", y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+
+my_cur_file = mu_b_lit
+min_gen=5000
+max_gen=10000
+letter="c"
+experiment_on ="Experiment 2"
+whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+min_gen=45000
+max_gen=50000
+whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+
+my_cur_file = mu_c_lit
+min_gen=5000
+max_gen=10000
+letter="d"
+experiment_on ="Experiment 2"
+whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+min_gen=45000
+max_gen=50000
+whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+
+my_cur_file = mu_d_lit
+min_gen=5000
+max_gen=10000
+letter="e"
+experiment_on ="Experiment 2"
+whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+min_gen=45000
+max_gen=50000
+whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+
+my_cur_file = v_a_lit
+min_gen=5000
+max_gen=10000
+letter="f"
+experiment_on ="Experiment 3"
+whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+min_gen=45000
+max_gen=50000
+whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+
+my_cur_file = v_b_lit
+min_gen=5000
+max_gen=10000
+letter="g"
+experiment_on ="Experiment 3"
+whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+min_gen=45000
+max_gen=50000
+whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+
+my_cur_file = v_c_lit
+min_gen=5000
+max_gen=10000
+letter="h"
+experiment_on ="Experiment 3"
+whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+min_gen=45000
+max_gen=50000
+whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+
+my_cur_file = v_d_lit
+min_gen=5000
+max_gen=10000
+letter="i"
+experiment_on ="Experiment 3"
+whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+min_gen=45000
+max_gen=50000
+whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
+```
+
+```{r, testing the differences between phenotypes and pop sizes for E1, E2, E3}
+
+boxplot_dif_in_phenotype <- function(file, title, subt, x_label, y_label,gen_l, gen_h,lowest){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+file$dif = file$Snake_mean_Pheno- file$Newt_mean_Pheno
+file$mv_dif <- (log10((file$snake_mu_rate * (file$snake_mu_effect_sd)^2)) - log10((file$newt_mu_rate * (file$newt_mu_effect_sd)^2)))
+
+lowest_mv_gone = file[which(paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)  != lowest & paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)  != lowest),]
+
+data <- lowest_mv_gone[order(lowest_mv_gone$mv_dif), ]
+data = data[which(data$generation>=gen_l & data$generation<=gen_h),]
+rownames(data) <- 1 : length(rownames(data))
+
+data$order = paste0("(",data$mv_dif,")", data$snake_newt)
+
+data_long <- tidyr::pivot_longer(data, c(Newt_mean_Pheno, Snake_mean_Pheno,dif))
+
+plot <-   
+ggplot(data_long) +
+  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
+  xlab(x_label) + ylab(y_label)+
+  geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(value),fill=name), alpha=0.3)+
+  #geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(Snake_mean_Pheno),fill=name),  alpha=0.3)+
+  #geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(dif),fill=name), alpha=0.3)+ # group=paste0(mv_dif,snake_newt)
+    theme(plot.title = element_text(size=5)) +
+  scale_alpha(guide = 'none')+
+  #labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+
+#geom_boxplot(data=file[which(file$generation>=45000),],aes(x=(factor(paste0("(",mv_dif,")", snake_newt))), y=as.numeric(dif), group=paste0(mv_dif,snake_newt),  fill="pink"), alpha=0.3)+
+#geom_boxplot(data=file[which(file$generation>=100 & file$generation<=5000),],aes(x=(factor(paste0("(",mv_dif,")", snake_newt))), y=as.numeric(dif), group=paste0(mv_dif,snake_newt), fill="green"), alpha=0.3)+
+
+#geom_boxplot(data=file[which(file$generation>=25000 & file$generation<=30000),],aes(x=(factor(paste0("(",mv_dif,")", snake_newt))), y=as.numeric(dif), group=paste0(mv_dif,snake_newt), fill="purple"), alpha=0.3)+
+
+#scale_fill_manual(values = c("purple", "green", "pink" ), labels = c('begin', 'mid', 'end'))+ #values = c("pink", "green", "purple" ),
+
+  return(plot)
+}
+
+boxplot_dif_in_phopulationsize <- function(file, title, subt, x_label, y_label, gen_l, gen_h, lowest){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+file$dif = file$Snake_pop_size- file$Newt_pop_size
+file$mv_dif <- (log10((file$snake_mu_rate * (file$snake_mu_effect_sd)^2)) - log10((file$newt_mu_rate * (file$newt_mu_effect_sd)^2)))
+
+file = file[order(file$mv_dif, file$mv_dif),]
+lowest_mv_gone = file[which(paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)  != lowest & paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)  != lowest),]
+
+data <- lowest_mv_gone[order(lowest_mv_gone$mv_dif) , ]
+data = data[which(data$generation>=gen_l & data$generation<=gen_h),]
+rownames(data) <- 1 : length(rownames(data))
+
+data$order = paste0("(",data$mv_dif,")", data$snake_newt)
+
+data_long <- tidyr::pivot_longer(data, c(Newt_pop_size, Snake_pop_size,dif))
+
+plot <-    ggplot(data_long) +
+  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
+  xlab(x_label) + ylab(y_label)+
+geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value),  fill=name), alpha=0.3)+
+    theme(plot.title = element_text(size=5)) +
+  scale_alpha(guide = 'none')+
+  #labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+
+  return(plot)
+}
+
+boxplot_dif_in_phenotype_less_log <- function(file, title, subt, x_label, y_label,gen_l, gen_h){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+file$dif = file$Snake_mean_Pheno- file$Newt_mean_Pheno
+file$mv_dif <- (log10(file$snake_mu_rate) - log10(file$newt_mu_rate))
+
+data <- file[order(file$mv_dif) , ]
+data = data[which(data$generation>=gen_l & data$generation<=gen_h),]
+rownames(data) <- 1 : length(rownames(data))
+
+data$order = paste0("(",data$mv_dif,")", data$snake_newt)
+data_long <- tidyr::pivot_longer(data, c(Newt_mean_Pheno, Snake_mean_Pheno,dif))
+
+plot <-   
+  ggplot(data_long) +
+  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
+  xlab(x_label) + ylab(y_label)+
+geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value), fill=name), alpha=0.3)+
+    theme(plot.title = element_text(size=5)) +
+  scale_alpha(guide = 'none')+
+  #labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+  return(plot)
+}
+
+boxplot_dif_in_phopulationsize_less_log <- function(file, title, subt, x_label, y_label, gen_l, gen_h){
+
+   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
+file$dif = file$Snake_pop_size- file$Newt_pop_size
+file$mv_dif <- (log10(file$snake_mu_rate) - log10(file$newt_mu_rate))
+
+file = file[order(file$mv_dif, file$mv_dif),]
+
+data <- file[order(file$mv_dif) , ]
+data = data[which(data$generation>=gen_l & data$generation<=gen_h),]
+rownames(data) <- 1 : length(rownames(data))
+
+data$order = paste0("(",data$mv_dif,")", data$snake_newt)
+data_long <- tidyr::pivot_longer(data, c(Newt_pop_size, Snake_pop_size,dif))
+
+plot <-    ggplot(data_long) +
+  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
+  xlab(x_label) + ylab(y_label)+
+geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value), fill=name), alpha=0.3)+
+    theme(plot.title = element_text(size=5)) +
+  scale_alpha(guide = 'none')+
+  #labs(fill = " ")+
+  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
+                      title =element_text(size=8, face='bold'))
+  return(plot)
+}
+
+gen_l=45000
+gen_h=50000
+lowest="1e-08_0.005"
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment GA1_lit"
+x_label = "Sanke GA - Newt GA"
+y_label = "Difference in Phenotype (Snake - Newt)"
+boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size (Snake - Newt)"
+boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance" 
+subt="Experiment mu_a_lit"
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+lowest="1e-08_0.005"
+boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment mu_b_lit"
+x_label = "Simulations" 
+y_label = "Difference in Phenotype"
+lowest="1e-09_0.0158"
+boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment mu_c_lit" 
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+lowest="1e-10_0.05"
+boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment mu_d_lit" 
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+lowest="1e-11_0.158"
+boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance" 
+subt="Experiment v_a_lit" 
+x_label = "Simulations" 
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment v_b_lit"
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment v_c_lit"
+x_label = "Simulations" 
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment v_d_lit" 
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+```
+
+```{r, waht about different points in sim}
+gen_l=100
+gen_h=5000
+lowest="1e-08_0.005"
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment GA1_lit"
+x_label = "Sanke GA - Newt GA"
+y_label = "Difference in Phenotype (Snake - Newt)"
+boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size (Snake - Newt)"
+boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance" 
+subt="Experiment mu_a_lit"
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+lowest="1e-08_0.005"
+boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment mu_b_lit"
+x_label = "Simulations" 
+y_label = "Difference in Phenotype"
+lowest="1e-09_0.0158"
+boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment mu_c_lit" 
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+lowest="1e-10_0.05"
+boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment mu_d_lit" 
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+lowest="1e-11_0.158"
+boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance" 
+subt="Experiment v_a_lit" 
+x_label = "Simulations" 
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment v_b_lit"
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment v_c_lit"
+x_label = "Simulations" 
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment v_d_lit" 
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+gen_l=25000
+gen_h=30000
+
+lowest="1e-08_0.005"
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment GA1_lit"
+x_label = "Sanke GA - Newt GA"
+y_label = "Difference in Phenotype (Snake - Newt)"
+boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size (Snake - Newt)"
+boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance" 
+subt="Experiment mu_a_lit"
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+lowest="1e-08_0.005"
+boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment mu_b_lit"
+x_label = "Simulations" 
+y_label = "Difference in Phenotype"
+lowest="1e-09_0.0158"
+boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment mu_c_lit" 
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+lowest="1e-10_0.05"
+boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment mu_d_lit" 
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+lowest="1e-11_0.158"
+boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
+
+title="Phenotype Difference by Mutatinal Varance" 
+subt="Experiment v_a_lit" 
+x_label = "Simulations" 
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment v_b_lit"
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment v_c_lit"
+x_label = "Simulations" 
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+title="Phenotype Difference by Mutatinal Varance"
+subt="Experiment v_d_lit" 
+x_label = "Simulations"
+y_label = "Difference in Phenotype"
+boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
+title="Populationsize Difference by Mutatinal Varance"
+y_label = "Difference in Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
+
+```

### 2023-10-31 graphs_newt_snakes/correlation_part2.Rmd
making more plots

@@
 scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation>14000 & newt_info$generation<15000 ),]
-scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation==20981 ),]
-#scatter_pheno[scatter_pheno == 0] <- NA
-#scatter_pheno[scatter_pheno == 1] <- NA
+#scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation==20981 ),]
+scatter_pheno[scatter_pheno == 0] <- NA
+scatter_pheno[scatter_pheno == 1] <- NA
 ggplot(scatter_pheno)+

### 2023-11-17 graphs_newt_snakes/Paper_figs.Rmd
more figure edit

@@
 library(scales)
+library(cowplot)
 ```
@@
 
-snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)
+snewt <- 0.71 #correlation value from https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.0060060
 
@@
 cost_grade_cor$sim=LETTERS[factor(cost_grade_cor$group)]
-cost_grade_cor$exp="Cost Gradent Map"
+cost_grade_cor$exp="Heterogeneous Cost Map"
 
@@
 cost_grade_no_interact_cor$sim=LETTERS[factor(cost_grade_no_interact_cor$group)]
-cost_grade_no_interact_cor$exp="Cost Gradent Map No Interaction"
+cost_grade_no_interact_cor$exp="Heterogeneous Cost Map No Interaction"
 
@@
 snake_change_cor$sim=LETTERS[factor(snake_change_cor$group)]
-snake_change_cor$exp="Snake Gradent Map"
+snake_change_cor$exp="Snake Heterogeneous Cost Map"
 
@@
 boxplot_cors_by_gen_col_rep <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){
- snewt$mean_res = snewt$mean_toxin+snewt$dif
-  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+
+  real_snewt_cor = snewt
    file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
@@
 #smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
-file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map"))
+file$exp = factor(file$exp, levels=c("Flat Map", "Heterogeneous Cost Map", "Interaction Gradent Map"))
 
@@
 boxplot_cors_by_gen_col_rep_other3 <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){
- snewt$mean_res = snewt$mean_toxin+snewt$dif
-  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  real_snewt_cor = snewt
    file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
@@
 #smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
-file$exp = factor(file$exp, levels=c("Cost Gradent Map No Interaction", "Snake Gradent Map", "Newt Gradent Map"))
+file$exp = factor(file$exp, levels=c("Heterogeneous Cost Map No Interaction", "Snake Heterogeneous Cost Map", "Newt Heterogeneous Cost Map"))
 
@@
 boxplot_cors_by_gen_col_rep_6_file <- function(file1, file2, file3, file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen){
- snewt$mean_res = snewt$mean_toxin+snewt$dif
-  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
+  real_snewt_cor = snewt
    file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
@@
 
-file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map No Interaction", "Cost Gradent Map", "Snake Gradent Map", "Interaction Gradent Map", "Newt Gradent Map"))
+file$exp = factor(file$exp, levels=c("Flat Map", "Heterogeneous Cost Map No Interaction", "Heterogeneous Cost Map", "Snake Heterogeneous Cost Map", "Interaction Gradent Map", "Newt Heterogeneous Cost Map"))
 
@@
 subt = " "
-exp_labeles=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map")
+exp_labeles=c("Flat Map", "Heterogeneous Cost Map", "Interaction Gradent Map")
 x_label = "Newt/Snake Genetic Architecture"
@@
 
-boxplot_dif_in_phenotype <- function(file, title, subt, x_label, y_label,gen_l, gen_h,lowest){
+boxplot_dif_in_phenotype <- function(file, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter){
 
@@
 
+file$sim_snake_name = NA
+  file$sim_newt_name = NA
+  #file$sim == "A" | "B" | "C" | "D"
+  file[which(file$sim  == "A" | file$sim  == "B" | file$sim  == "C" | file$sim  == "D"), ]$sim_snake_name = paste0("1",letter)
+  file[which(file$sim  == "E" | file$sim  == "F" | file$sim  == "G" | file$sim  == "H"), ]$sim_snake_name = paste0("2",letter)
+  file[which(file$sim  == "I" | file$sim  == "J" | file$sim  == "K" | file$sim  == "L"), ]$sim_snake_name = paste0("3",letter)
+  file[which(file$sim  == "M" | file$sim  == "N" | file$sim  == "O" | file$sim  == "P"), ]$sim_snake_name =  paste0("4",letter)
+
+  file[which(file$sim  == "A" | file$sim  == "E" | file$sim  == "I" | file$sim  == "M"), ]$sim_newt_name =  paste0("1",letter)
+  file[which(file$sim  == "B" | file$sim  == "F" | file$sim  == "J" | file$sim  == "N"), ]$sim_newt_name =  paste0("2",letter)
+  file[which(file$sim  == "C" | file$sim  == "G" | file$sim  == "K" | file$sim  == "O"), ]$sim_newt_name = paste0("3",letter)
+  file[which(file$sim  == "D" | file$sim  == "H" | file$sim  == "L" | file$sim  == "P"), ]$sim_newt_name =  paste0("4",letter)
+  file$sim_name = paste0("S:", file$sim_snake_name,"/N:", file$sim_newt_name)
+
 lowest_mv_gone = file[which(paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)  != lowest & paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)  != lowest),]
@@
 
-data$order = paste0("(",data$mv_dif,")", data$snake_newt)
+data$order = paste0("(",round(data$mv_dif),")", data$sim_name)
 
@@
   #geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(dif),fill=name), alpha=0.3)+ # group=paste0(mv_dif,snake_newt)
+  scale_fill_manual(values=c(Newt_mean_Pheno="red",Snake_mean_Pheno="blue",dif="purple"),breaks=c('Newt_mean_Pheno','Snake_mean_Pheno','dif'), labels=c( "Newt Phenotype", "Snake Phenotype", "Phenotype Difference (S-N)"), name="Mean")+
     theme(plot.title = element_text(size=5)) +
@@
 
-boxplot_dif_in_phopulationsize <- function(file, title, subt, x_label, y_label, gen_l, gen_h, lowest){
+boxplot_dif_in_phopulationsize <- function(file, title, subt, x_label, y_label, gen_l, gen_h, lowest, letter){
 
@@
 
+file$sim_snake_name = NA
+  file$sim_newt_name = NA
+  #file$sim == "A" | "B" | "C" | "D"
+  file[which(file$sim  == "A" | file$sim  == "B" | file$sim  == "C" | file$sim  == "D"), ]$sim_snake_name = paste0("1",letter)
+  file[which(file$sim  == "E" | file$sim  == "F" | file$sim  == "G" | file$sim  == "H"), ]$sim_snake_name = paste0("2",letter)
+  file[which(file$sim  == "I" | file$sim  == "J" | file$sim  == "K" | file$sim  == "L"), ]$sim_snake_name = paste0("3",letter)
+  file[which(file$sim  == "M" | file$sim  == "N" | file$sim  == "O" | file$sim  == "P"), ]$sim_snake_name =  paste0("4",letter)
+
+  file[which(file$sim  == "A" | file$sim  == "E" | file$sim  == "I" | file$sim  == "M"), ]$sim_newt_name =  paste0("1",letter)
+  file[which(file$sim  == "B" | file$sim  == "F" | file$sim  == "J" | file$sim  == "N"), ]$sim_newt_name =  paste0("2",letter)
+  file[which(file$sim  == "C" | file$sim  == "G" | file$sim  == "K" | file$sim  == "O"), ]$sim_newt_name = paste0("3",letter)
+  file[which(file$sim  == "D" | file$sim  == "H" | file$sim  == "L" | file$sim  == "P"), ]$sim_newt_name =  paste0("4",letter)
+  file$sim_name = paste0("S:", file$sim_snake_name,"/N:", file$sim_newt_name)
+
 file = file[order(file$mv_dif, file$mv_dif),]
@@
   scale_alpha(guide = 'none')+
+  scale_fill_manual(values=c(Newt_pop_size="red",Snake_pop_size="blue",dif="green"),breaks=c('Newt_pop_size','Snake_pop_size','dif'), labels=c( "Newt Population Size", "Snake Population Size", "Population Size Difference (S-N)"), name="Population Size")+
   #labs(fill = " ")+
@@
 
-boxplot_dif_in_phenotype_less_log <- function(file, title, subt, x_label, y_label,gen_l, gen_h){
+boxplot_dif_in_phenotype_less_log <- function(file, title, subt, x_label, y_label,gen_l, gen_h, letter){
 
@@
 
+file$sim_snake_name = NA
+  file$sim_newt_name = NA
+  #file$sim == "A" | "B" | "C" | "D"
+  file[which(file$sim  == "A" | file$sim  == "B" | file$sim  == "C" | file$sim  == "D"), ]$sim_snake_name = paste0("1",letter)
+  file[which(file$sim  == "E" | file$sim  == "F" | file$sim  == "G" | file$sim  == "H"), ]$sim_snake_name = paste0("2",letter)
+  file[which(file$sim  == "I" | file$sim  == "J" | file$sim  == "K" | file$sim  == "L"), ]$sim_snake_name = paste0("3",letter)
+  file[which(file$sim  == "M" | file$sim  == "N" | file$sim  == "O" | file$sim  == "P"), ]$sim_snake_name =  paste0("4",letter)
+
+  file[which(file$sim  == "A" | file$sim  == "E" | file$sim  == "I" | file$sim  == "M"), ]$sim_newt_name =  paste0("1",letter)
+  file[which(file$sim  == "B" | file$sim  == "F" | file$sim  == "J" | file$sim  == "N"), ]$sim_newt_name =  paste0("2",letter)
+  file[which(file$sim  == "C" | file$sim  == "G" | file$sim  == "K" | file$sim  == "O"), ]$sim_newt_name = paste0("3",letter)
+  file[which(file$sim  == "D" | file$sim  == "H" | file$sim  == "L" | file$sim  == "P"), ]$sim_newt_name =  paste0("4",letter)
+  file$sim_name = paste0("S:", file$sim_snake_name,"/N:", file$sim_newt_name)
+
 data <- file[order(file$mv_dif) , ]
@@
 
-data$order = paste0("(",data$mv_dif,")", data$snake_newt)
+data$order = paste0("(",data$mv_dif,")", data$sim_name)
 data_long <- tidyr::pivot_longer(data, c(Newt_mean_Pheno, Snake_mean_Pheno,dif))
@@
   scale_alpha(guide = 'none')+
+  scale_fill_manual(values=c(Newt_mean_Pheno="red",Snake_mean_Pheno="blue",dif="purple"),breaks=c('Newt_mean_Pheno','Snake_mean_Pheno','dif'), labels=c( "Newt Phenotype", "Snake Phenotype", "Phenotype Difference (S-N)"), name="Mean")+
   #labs(fill = " ")+
@@
 
-boxplot_dif_in_phopulationsize_less_log <- function(file, title, subt, x_label, y_label, gen_l, gen_h){
+boxplot_dif_in_phopulationsize_less_log <- function(file, title, subt, x_label, y_label, gen_l, gen_h,  letter){
 
@@
 file$mv_dif <- (log10(file$snake_mu_rate) - log10(file$newt_mu_rate))
+file$sim_snake_name = NA
+  file$sim_newt_name = NA
+  #file$sim == "A" | "B" | "C" | "D"
+  file[which(file$sim  == "A" | file$sim  == "B" | file$sim  == "C" | file$sim  == "D"), ]$sim_snake_name = paste0("1",letter)
+  file[which(file$sim  == "E" | file$sim  == "F" | file$sim  == "G" | file$sim  == "H"), ]$sim_snake_name = paste0("2",letter)
+  file[which(file$sim  == "I" | file$sim  == "J" | file$sim  == "K" | file$sim  == "L"), ]$sim_snake_name = paste0("3",letter)
+  file[which(file$sim  == "M" | file$sim  == "N" | file$sim  == "O" | file$sim  == "P"), ]$sim_snake_name =  paste0("4",letter)
+
+  file[which(file$sim  == "A" | file$sim  == "E" | file$sim  == "I" | file$sim  == "M"), ]$sim_newt_name =  paste0("1",letter)
+  file[which(file$sim  == "B" | file$sim  == "F" | file$sim  == "J" | file$sim  == "N"), ]$sim_newt_name =  paste0("2",letter)
+  file[which(file$sim  == "C" | file$sim  == "G" | file$sim  == "K" | file$sim  == "O"), ]$sim_newt_name = paste0("3",letter)
+  file[which(file$sim  == "D" | file$sim  == "H" | file$sim  == "L" | file$sim  == "P"), ]$sim_newt_name =  paste0("4",letter)
+  file$sim_name = paste0("S:", file$sim_snake_name,"/N:", file$sim_newt_name)
 
@@
 
-data$order = paste0("(",data$mv_dif,")", data$snake_newt)
+data$order = paste0("(",data$mv_dif,")", data$sim_name)
 data_long <- tidyr::pivot_longer(data, c(Newt_pop_size, Snake_pop_size,dif))
@@
 lowest="1e-08_0.005"
-title="Phenotype Difference by Mutatinal Varance"
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment GA1_lit"
-x_label = "Sanke GA - Newt GA"
-y_label = "Difference in Phenotype (Snake - Newt)"
-boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size (Snake - Newt)"
-boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance" 
+letter="a"
+x_label = "Snake GA - Newt GA"
+y_label = "Phenotype"
+ga1pp = boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+ga1ps = boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+pg1 = plot_grid(ga1pp, ga1ps, labels = c('A', 'B'), label_size = 12, nrow =2)
+ggsave("PD_PSD.png", plot=pg1, height=7, width=7, units=c("in"), dpi=600)
+
+title="Phenotype Difference by Mutational Variance" 
 subt="Experiment mu_a_lit"
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
+letter="b"
+x_label = "Simulations"
+y_label = "Phenotype"
 lowest="1e-08_0.005"
-boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance"
+mu_a = boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+mu_a
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment mu_b_lit"
-x_label = "Simulations" 
-y_label = "Difference in Phenotype"
+letter="c"
+x_label = "Simulations" 
+y_label = "Phenotype"
 lowest="1e-09_0.0158"
-boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance"
+mu_b = boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+mu_b
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment mu_c_lit" 
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
+letter="d"
+x_label = "Simulations"
+y_label = "Phenotype"
 lowest="1e-10_0.05"
-boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance"
+mu_c = boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+mu_c
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment mu_d_lit" 
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
+letter="e"
+x_label = "Simulations"
+y_label = "Phenotype"
 lowest="1e-11_0.158"
-boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance" 
+mu_d = boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+pg1 = plot_grid(mu_a, mu_b, mu_c, mu_d, labels = c('A', 'B', "C", "D"), label_size = 12)
+ggsave("mus_app.png", plot=pg1, height=7, width=10, units=c("in"), dpi=600)
+
+title="Phenotype Difference by Mutational Variance" 
 subt="Experiment v_a_lit" 
-x_label = "Simulations" 
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
-
-title="Phenotype Difference by Mutatinal Varance"
+letter="f"
+x_label = "Simulations" 
+y_label = "Phenotype"
+v_a = boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+v_a
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment v_b_lit"
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
-
-title="Phenotype Difference by Mutatinal Varance"
+letter="g"
+x_label = "Simulations"
+y_label = "Phenotype"
+v_b = boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+v_b
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment v_c_lit"
-x_label = "Simulations" 
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
-
-title="Phenotype Difference by Mutatinal Varance"
+letter="h"
+x_label = "Simulations" 
+y_label = "Phenotype"
+v_c = boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+v_c
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment v_d_lit" 
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
+letter="i"
+x_label = "Simulations"
+y_label = "Phenotype"
+v_d = boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+pg2 = plot_grid(v_a, v_b, v_c, v_d, labels = c('A', 'B', "C", "D"), label_size = 12)
+ggsave("vms_app.png", plot=pg2, height=7, width=10, units=c("in"), dpi=600)
 
@@
 lowest="1e-08_0.005"
-title="Phenotype Difference by Mutatinal Varance"
+letter="a"
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment GA1_lit"
-x_label = "Sanke GA - Newt GA"
-y_label = "Difference in Phenotype (Snake - Newt)"
-boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size (Snake - Newt)"
-boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance" 
+x_label = "Snake GA - Newt GA"
+y_label = "Phenotype"
+boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance" 
 subt="Experiment mu_a_lit"
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
+letter="b"
+x_label = "Simulations"
+y_label = "Phenotype"
 lowest="1e-08_0.005"
-boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance"
+boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment mu_b_lit"
-x_label = "Simulations" 
-y_label = "Difference in Phenotype"
+letter="c"
+x_label = "Simulations" 
+y_label = "Phenotype"
 lowest="1e-09_0.0158"
-boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance"
+boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment mu_c_lit" 
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
+letter="d"
+x_label = "Simulations"
+y_label = "Phenotype"
 lowest="1e-10_0.05"
-boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance"
+boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment mu_d_lit" 
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
+letter="e"
+x_label = "Simulations"
+y_label = "Phenotype"
 lowest="1e-11_0.158"
-boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance" 
+boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance" 
 subt="Experiment v_a_lit"
-x_label = "Simulations" 
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
-
-title="Phenotype Difference by Mutatinal Varance"
+letter="f"
+x_label = "Simulations" 
+y_label = "Phenotype"
+boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment v_b_lit"
 x_label = "Simulations"
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
-
-title="Phenotype Difference by Mutatinal Varance"
+letter="g"
+y_label = "Phenotype"
+boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment v_c_lit"
-x_label = "Simulations" 
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
-
-title="Phenotype Difference by Mutatinal Varance"
+letter="h"
+x_label = "Simulations" 
+y_label = "Phenotype"
+boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment v_d_lit" 
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
+letter="i"
+x_label = "Simulations"
+y_label = "Phenotype"
+boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
 
@@
 lowest="1e-08_0.005"
-title="Phenotype Difference by Mutatinal Varance"
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment GA1_lit"
-x_label = "Sanke GA - Newt GA"
-y_label = "Difference in Phenotype (Snake - Newt)"
-boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size (Snake - Newt)"
-boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance" 
+letter="a"
+x_label = "Snake GA - Newt GA"
+y_label = "Phenotype"
+boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance" 
 subt="Experiment mu_a_lit"
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
+letter="b"
+x_label = "Simulations"
+y_label = "Phenotype"
 lowest="1e-08_0.005"
-boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance"
+boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment mu_b_lit"
-x_label = "Simulations" 
-y_label = "Difference in Phenotype"
+letter="c"
+x_label = "Simulations" 
+y_label = "Phenotype"
 lowest="1e-09_0.0158"
-boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance"
+boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment mu_c_lit"
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
+letter="d"
+x_label = "Simulations"
+y_label = "Phenotype"
 lowest="1e-10_0.05"
-boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance"
+boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment mu_d_lit"
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
+letter="e"
+x_label = "Simulations"
+y_label = "Phenotype"
 lowest="1e-11_0.158"
-boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
-
-title="Phenotype Difference by Mutatinal Varance" 
+boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
+
+title="Phenotype Difference by Mutational Variance" 
 subt="Experiment v_a_lit" 
-x_label = "Simulations" 
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
-
-title="Phenotype Difference by Mutatinal Varance"
+letter="f"
+x_label = "Simulations" 
+y_label = "Phenotype"
+boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment v_b_lit"
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
-
-title="Phenotype Difference by Mutatinal Varance"
+letter="g"
+x_label = "Simulations"
+y_label = "Phenotype"
+boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment v_c_lit"
-x_label = "Simulations" 
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
-
-title="Phenotype Difference by Mutatinal Varance"
+letter="h"
+x_label = "Simulations" 
+y_label = "Phenotype"
+boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+
+title="Phenotype Difference by Mutational Variance"
 subt="Experiment v_d_lit" 
-x_label = "Simulations"
-y_label = "Difference in Phenotype"
-boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
-title="Populationsize Difference by Mutatinal Varance"
-y_label = "Difference in Population Size"
-boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
+letter="i"
+x_label = "Simulations"
+y_label = "Phenotype"
+boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
+title="Population size Difference by Mutational Variance"
+y_label = "Population Size"
+boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
 

### 2023-12-04 graphs_newt_snakes/Paper_figs.Rmd
updated files

@@
 library(kableExtra)
-library(reshape2)
-library(ggplot2)
 library(ggpubr)
@@
 newt_change_cor$sim=LETTERS[factor(newt_change_cor$group)]
-newt_change_cor$exp="Newt Gradent Map"
+newt_change_cor$exp="Newt Heterogeneous Cost Map"
 
